### 2020-08-01 papers/execution-model/model.tex
first version

\documentclass[a4paper]{llncs}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\newtheorem{mydef}{Definition}
\newtheorem{mylemma}{Lemma}
\newtheorem{mytheorem}{Theorem}
\newtheorem{mypro}{Proposition}

\title{Blockchain System}

\author{}
\institute{}

\date{\today}

\begin{document}
\maketitle

\section{Definitions}
\begin{definition}[Set]
Let $\mathbf{Elt}$ be the set of (concrete) elements. Let $\emptyset$ be an empty set and $\mathbf{e}$ $\in$  $\mathbf{Elt}$. A set of elements is expressed as the following syntax:
\\
$\mathbf{s}$ :: = $\emptyset$ $\mid$ $\mathbf{e}$ $\mid$ $\mathbf{s :: s}$
\end{definition}

\begin{definition}[Account]
An account is expressed as a tuple $<$ $\mathbf{als}$, $\mathbf{pak}$, $\mathbf{puk}$, $\mathbf{pkh}$ $>$, where $\mathbf{als}$ is the alias of the account, $\mathbf{pak}$ is its private key, $\mathbf{puk}$ is its public key and $\mathbf{pkh}$ is its public key hash . 
\end{definition}

\begin{definition}[Contract]
An contract is expressed as a tuple $<$ $\mathbf{als}$, $\mathbf{puh}$, $\mathbf{code}$ $>$, where $\mathbf{als}$ is the alias of the contract, $\mathbf{puh}$ is its public hash and $\mathbf{code}$ is the code of the contract.
\end{definition}

\begin{definition}[Manager]
An manager manages accounts on the blockchain. It is expressed as a tuple $<$ $\mathbf{puk}$, $\mathbf{pkh}$, $\mathbf{bal}$,  $\mathbf{cou}$ $>$, where  $\mathbf{puk}$ is the public key of an account, $\mathbf{pkh}$ is its public key hash, $\mathbf{bal}$ is its balance and $\mathbf{cou}$ is its counter whose form is a pair ($\mathbf{n}$, $\mathbf{b}$), where $\mathbf{n}$ is a nature number and $\mathbf{b}$ is a boolean value. 
\end{definition}

\begin{definition}[Contractor]
A contractor manages smart contracts on the blockchain. It is expressed as a tuple $<$ $\mathbf{puh}$, $\mathbf{bal}$,  $\mathbf{code}$,  $\mathbf{storage}$ $>$, where $\mathbf{puh}$ is the public hash of the contract, $\mathbf{bal}$ is its balance, $\mathbf{code}$ is its code and  $\mathbf{storage}$ is its storage. 
\end{definition}

\begin{definition}[Operation]
An operation is expressed as the following syntax:
\\
$\mathbf{op}$ ::= transfer  $\mathbf{n}$ from $\mathbf{pkh}$ to $\mathbf{pkh'}$ fee $\mathbf{m}$
%\\$\mid$ register key $\mathbf{pkh}$ as delegate fee $\mathbf{m}$ 
%\\$\mid$ set delegate for $\mathbf{pkh}$ to $\mathbf{pkh'}$  fee $\mathbf{m}$ 
%\\$\mid$ withdraw delegate from $\mathbf{pkh}$ fee $\mathbf{m}$ 
\\$\mid$ originate contract $\mathbf{id}$ transferring  $\mathbf{n}$ from $\mathbf{pkh}$ running $\mathbf{code}$ init $\mathbf{s}$ fee $\mathbf{m}$
\\$\mid$ transfer $\mathbf{n}$ from $\mathbf{pkh}$ to  $\mathbf{puh}$ arg $\mathbf{s}$ fee $\mathbf{m}$
\end{definition}

\begin{definition}[Query]
An query is expressed as the following syntax:
\\
$\mathbf{qry}$ ::= get balance for $\mathbf{pkh}$
%$\mid$ get delegate for $\mathbf{pkh}$
\\$\mid$ get status for $\mathbf{oph}$ 
\\$\mid$ get contract storage $\mathbf{pkh}$ 
\\$\mid$ get code for $\mathbf{pkh}$ 
%\\$\mid$ waiting for $\mathbf{oph}$ to be included in $\mathbf{m}$ blocks
%\\$\mid$ get timestamp
%\\$\mid$ get contracts
%\\$\mid$ show contracts for $\mathbf{pkh}$
\\$\mid$ get public key for $\mathbf{pkh}$
%\\$\mid$ get balance for $\mathbf{pkh}$
\\$\mid$ get counter for $\mathbf{pkh}$

\end{definition}
Let $\mathbf{C}$ be the set of accounts,   $\mathbf{O}$ be a set of operations, and $\mathbf{S}$ be the set of contracts. 
 \begin{definition}[State of a node]
The state of a node is expressed as a tuple $[$$\mathbf{C}$, $\mathbf{O}$, $\mathbf{S}$$]$ .
\end{definition}

When an operation is injected in a node, it enters in a pending pool (and called a pending operation). 
 \begin{definition}[Pending operation]
A pending operation is expressed as a pair  $<$ $\mathbf{op}$, $\mathbf{oph}$, $\mathbf{t}$ $>$, where $\mathbf{op}$ is an operation, $\mathbf{oph}$ is the operation hash and $\mathbf{t}$ is the time when it is injected. 
\end{definition}
After sometime, a pending operation could be included in the blockchain as a accepted operation.
%Let \textit{P} is the set of pending operations.
 \begin{definition}[Accepted operation]
An accepted operation  is expressed as a tuple $<$ $\mathbf{op}$, $\mathbf{oph}$, $\mathbf{t}$ $>$, where $\mathbf{op}$ is an operation, $\mathbf{oph}$ is the operation hash and $\mathbf{t}$ is the time when it is included in the blockchain. 
\end{definition}
Let $\mathbf{P}$ be a set of pending operations,  $\mathbf{A}$ be a set of accepted operations, $\mathbf{K}$ be a set of managers, $\mathbf{T}$ be a set of contractors % $\mathbf{h}$ be the hash of the current block head 
and $\mathbf{t}$ is the current time of the blockchain.

\begin{definition}[Blockchain]
The state of a blockchain is expressed as a tuple $[$$\mathbf{P}$, $\mathbf{A}$, $\mathbf{K}$, $\mathbf{T}$, $\mathbf{t}$$]$.  
\end{definition}

\begin{definition}[Blockchain system]
A blockchain system 
$\mathbf{S}$ $\triangleq\langle$ $\mathbf{M}$, $\mathbf{B}$ $\rangle$ consists of
\begin{enumerate}
\item $\mathbf{M}$ $\equiv$ [C, O, S] is the state of a node, and
\item $\mathbf{B}$ $\equiv$ [P, A, K, T, t] is the state of a blockchain 
such as $\forall$ c $\in$ C $\implies$ $\exists$ k $\in$ K, k.pkh = c.pkh and $\forall$ s $\in$ S $\implies$ $\exists$ p $\in$ T, s.puh = p.puh.
\end{enumerate}
\end{definition}

\section{Rules}
\subsection{Transfers}

Rule 1 [proposal]:

\begin{equation}{}
\frac{\text{checkAcc($pkh$, C)}}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$)} \\\text{ :: O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
\\
\\
Rule 2 [injected]:

\begin{equation}{}
\frac{\text{checkBan(K, $pkh$, $n$, $m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ checkPub(K, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$}\\
\text{$\langle$[C, O, S],[($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
\text{$pkh'$, $n$, $m$, t), t $>$) :: P, A, updateCou(K, $pkh$, True), T, t]$\rangle$}}} 
\end{equation}
\\
\\
Rule 3 [rejected of counter]:

\begin{equation}{}
\frac{\text{$\neg$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ }\\
\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
\\
\\
Rule 4 [rejected of balance]:

\begin{equation}{}
\frac{\text{$\neg$ checkBan(K, $pkh$, $m$, $n$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ }\\
\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
\\
\\
Rule 5 [rejected of public key]:

\begin{equation}{}
\frac{\text{$\neg$ checkPub(K, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ }\\
\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
\\
\\
Rule 6 [included]:
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$ } \\
 \text{[P,$<$ transfer $n$ from  $puk$ to $puk'$ fee $m$, oph, t' $>$ :: A, updateSucc(K, } \\
\text{$puk$, $puk'$, $n$, $m$), T, t' + 1]}}} 
\end{equation}
\\
Rule 7 [timeout]:
\begin{equation}{}
\frac{\text{t' - t $>=$ 60}}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$} \\
 \hspace*{0cm} \text{[P, A, updateCou(K, $puk$, False), T, t']}}} 
\end{equation}

\subsection{Smart Contracts}

\subsubsection*{A. Originate}

Rule 1 [proposal]:

\begin{equation}{}
\frac{\text{checkAcc($pkh$, C) $\wedge$ checkId($id$, S) $\wedge$ \text{checkPrg($code$, $s$)}}}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, (originate contract ${puh}$ transferring} \\
  \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 2 [injected]:}

\begin{equation}{}
\frac{\text{checkBan(K, $pkh$, $n$, $m$) $\wedge$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: O, S], [P, A, K, T, t] $\rangle$ $\rightarrow$ $\langle$ [C, O, S],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: P, A, updateCou(K, $pkh$, True), T, t] $\rangle$}}} 
\end{equation}

\subsubsection*{Rule 3 [rejected of code]:}

\begin{equation}{}
\frac{\text{$\neg$ checkPrg($code$, $s$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, O, S],} \text{[P, A, K, T, t]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 4 [rejected of counter]:}

\begin{equation}{}
\frac{\text{$\neg$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$))} \text{:: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$ [C, O, S],} \text{[P, A, K, T, t]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 5 [rejected of balance]:}

\begin{equation}{}
\frac{\text{$\neg$ checkBan(K, $pkh$, $n$, $m$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, O, S],} \text{[P, A, K, T, t]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 6 [included]:}
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{$\langle$[C, O, S], [$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running } \\
\text{${code}$ init ${s}$), t $>$ :: P, A, K, T, t' ]$\rangle$ $\rightarrow$ $\langle$[C, O, addContr(S, $id$, } \\
\text{generateHash($id$, $code$, $s$, t'), $code$)], [P,$<$ (originate contract ${id}$ } \\
\text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), t' $>$ :: A, updateSucc(K, } \\
\text{$puk$, $n$, $m$), addOrig(T, $<$ generateHash($id$, $code$, $s$, t'), $0$, $code$, } \\
 \text{getStorage($code$, $s$) $>$), t' + 1]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 7 [timeout]:}
\begin{equation}{}
\frac{\text{t' - t $>=$ 60}}{\parbox{4.2in}{\text{[$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$) $>$ } \\
\text{:: P, A, K, T, t' ] $\rightarrow$[P, A, updateCou(K, $puk$, False), T, t']}}} 
\end{equation}

\subsubsection*{B. Transfer}

\subsubsection*{Rule 1 [proposal]:}

\begin{equation}{}
\frac{\text{checkAcc($pkh$, C)  }}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ }  \\
\text{fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 2 [injected]:}

\begin{equation}{}
\frac{\text{checkBan(K, $pkh$, $n$, $m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ checkContr(T, $puh$, s) }}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}\\
\text{$\rightarrow$  $\langle$[C, O, S], [($<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), }\\
 \text{generateOph($pkh$, $puh$, $s$, $n$, $m$, t $>$) :: P, A, updateCou(K, $pkh$, True), }\\
\text{T, t] $\rangle$}}} 
\end{equation}

\subsubsection*{Rule 3 [rejected of counter]:}

\begin{equation}{}
\frac{\text{$\neg$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$  }\\
\text{$\rightarrow$ $\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 4 [rejected of balance]:}

\begin{equation}{}
\frac{\text{$\neg$ checkBan(K, $pkh$, $n$, $m$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$ }\\
\text{$\rightarrow$ $\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 5 [rejected of public key]:}

\begin{equation}{}
\frac{\text{$\neg$ checkContr(T, $puh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$ }\\
\text{$\rightarrow$ $\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 6 [rejected of argument]:}

\begin{equation}{}
\frac{\text{$\neg$ checkArg(T, $puh$, $s$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}\\
\text{$\rightarrow$ $\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 7 [included]:}
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puh$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$ } \\
\text{[P, $<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), oph, t' $>$ :: A, } \\
\text{updateSucc(K, puk, '', $n$, $m$), updateConstr(T, $puh$, $s$), t' + 1]}}} 
\end{equation}

\subsubsection*{Rule 8 [timeout]:}
\begin{equation}{}
\frac{\text{t' - t $>=$ 60}}{\parbox{4.2in}{\text{[transfer $n$ from $puk$ to  $puh$ fee $m$, t $>$ :: P, A, K, T, t' ] $\rightarrow$} \\
\text{[P, A, updatecou(K, $puk$, False), T, t']}}} 
\end{equation}

\section{Functions}
\begin{enumerate}
    \item Function \verb!checkAcc(pkh, C)! checks whether an account $pkh$ exists in C
    \item Function \verb!checkPub(K, pkh)! checks whether the public key of the public key hash $pkh$ is reveled to the blockchain.
    \item Function \verb!checkBan(K, pkh, n, m)! checks whether the balance of the account $pkh$ is greater or equal to $m$ + $n$
    \item Function \verb!checkCou(K, pkh)! checks whether the current counter of an account $phk$ is used
    \item Function \verb!updateSuc(K, pkh, pkh', n, m)! updates the balance and the counter of the account $phk$ and the balance of the account $phk'$, where
    \begin{itemize}
        \item  \verb!< puk, pkh, bal, (n, True) >!  \verb!=>! \\ \verb!< puk, pkh, bal - n - m, (n + 1, False) >!
        \item  \verb!< puk', pkh', bal', cou' >! \verb!=>! \verb!< puk', pkh', bal' + n, cou' >!
    \end{itemize}

    \item Function \verb!updateCou(K, puk, b')! updates the counter of the account $phk$, where
    \begin{itemize}
        \item  \verb!< puk, pkh, bal, (n, b) >!  \verb!=>! \verb!< puk, pkh, bal, (n, b') >!
    \end{itemize}

    \item Function \verb!checkId(id, S)! checks whether a contract $id$ exists in S

    \item Function \verb!checkPrg(code, s)! checks whether the code $code$ are well type and $s$ is well type input

    \item Function \verb!addContr(S, id, puh, code)! adds a new  contract $<$ $id$, $puh$, $code$ $>$  into S

    \item Function \verb! generateOph(pkh,pkh', n, m, t)! generates a operation hash

    \item Function \verb!generateHash(S, id, puh, code, t)! generates the public hash of a contract

    \item Function \verb!addOrig(T,< hash, 0, code, storage >)! add the a new originator $<$ $puh$, 0, $code$, $storage$ $>$ 
    \item Function \verb!getStorage(code, s)! gets the storage for the code $code$ and the input $s$
\end{enumerate}

\section{Some implementations}
Function \verb!checkAcc(puh, C)! checks whether an account exists and and \verb!checkPuk(puh, K)! checks the revelation of its public key to the blockchain.
\begin{verbatim}
let rec checkAcc puh C =
  match C with
  | 0 -> false
  | < als, pak, puk, pkh' > :: C' ->
    if (puh = puh')  then true 
    else checkAcc (puh, C')
\end{verbatim}

\begin{verbatim}
let rec checkPuk puh K =
  match C with
  | 0 -> false
  | < als, pak, puk, pkh' > :: K' ->
    if (puh = puh') and (puk =/= nil) then true 
    else 5checkPuk (puh, K')
\end{verbatim}

The following functions interact with $\mathbf{K}$.

\begin{verbatim}
let rec checkBal K puk n m =
  match K with
  | 0 -> true
  | < puk', bal, cou > :: K' ->
    if (puk = puk') and (n + m) <= bal then true 
    else checkBal (K', puk, n, m)
\end{verbatim}

\begin{verbatim}
let rec checkPub K puk =
  match K with
  | 0 -> false
  | < puk', bal, cou > :: K' ->
    if (puk = puk') then true 
    else checkExi (K', puk)
\end{verbatim}

\begin{verbatim}
let rec checkCou K puk =
  match K with
  | 0 -> false
  | < puk', bal, cou > :: K' ->
    if (puk = puk') and (cou = T) then true 
    else checkCou (K', puk)
\end{verbatim}

\begin{verbatim}
let rec updateCou K puk =
  match K with
  | 0 -> 0
  | < puk', bal, cou > :: K' ->
    if (puk = puk') then < puk', bal, F > :: K'
    else < puk', bal, cou > :: updateCou (K', puk)
\end{verbatim}

\begin{verbatim}
let rec updateSuc K puk puk' m n =
  match K with
  | 0 -> 0
  | < puk'', bal, cou > :: K' ->
    if (puk = puk'') then < puk'', bal - (n + m), T > 
       :: updateSuc (K', puk, puk', n, m)
    else if (puk' = puk'') then < puk'', bal + n, cou > :: K'
         else  < puk'', bal, cou > 
               ::updateSuc (K', puk, puk', n, m)
\end{verbatim}

\end{document}

### 2020-08-01 reports/2020-07-31/COOC-report.tex
as submitted

\documentclass[a4paper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{hyperref}

\title{Contract Orchestration for OCaml \\
  Progress Report 
}
\date{31 July 2020}
\author{Prof.\ Dr.\ Peter Thiemann, University of Freiburg, Germany}
\begin{document}
\maketitle{}

\section{Introduction}
\label{sec:introduction}

The project Contract Orchestration for OCaml (COOC) is funded by the Tezos foundation. Its overarching  objective is to provide a framework to guarantee correct orchestration of contract invocation from an  application program in the OCaml language.

\section{Timeline of Events}
\label{sec:timeline-events}

January 2020
\begin{itemize}
\item starting employment of postdoc Dr Ha Thi Thu Doan. Her tasks are as follows.
\begin{itemize}
\item Supporting the students workers 
\item Supporting the blockchain lecture
\item Providing documentation
\item Working on a formal model
\end{itemize}
\item supporting the travel of scientific collaborator Prof. Vasco Vasconcelos of University of Lisbon, Portugal, to conference POPL (New Orleans, LA, USA).
\end{itemize}

March 2020
\begin{itemize}
\item acquisition of dedicated server for supporting project work and
  to run Tezos full node on Carthagenet
\item hiring of student worker (Max Hertenstein, a Master's student) to reverse engineer functions of the tezos-client; first job: getting up to speed with OCaml; second job: implement transfer as a standalone OCaml program using the Tezos node's RPC API; current job: implement contract invocation in the same way. 
\end{itemize}

May 2020
\begin{itemize}
\item hiring second student worker (Tamara Bernhardt, a Master's student) for administration of the server. In that facility she improved accessibility of the server (which must be installed behind a firewall due to university's security regulations), experimented with running several node instances on the same host, experimented with installing and using the sandbox
\item At the same time, Tamara is doing a Master's project in my group where she develops a first cut of an OCaml API to invoke Tezos contracts. Her background was Haskell programming, so she also had to get up to speed with OCaml, first. She is building on the results of Max as well as on the recently published Tezos client library. The current status is that she can do transfers using the library, but we find the verbose output inappropriate for a library. Our next step is to have a meeting with Tamara, Ha, and myself (on August 6) to  investigate the structure of the library and to determine whether there are appropriate layers to connect to or whether we will have to rely on the RPC API of the node. 
\end{itemize}
For the OCaml API, we envision an asynchronous design based on futures. The first version will only cover transfers. The next version will only the type safe invocation of contracts. We expect that Tamara does her Master's thesis with us on the design and implementation of the OCaml API (starting from about October 2020).

May 2020-July 2020
\begin{itemize}
\item Ha and I are running the course ``Blockchain and Cryptocurrencies''. This course builds on the book ``Bitcoin and Cryptocurrency Technologies'' by Narayanan and others.  It covers seven weeks worth of material from the book; two weeks on Ethereum, Solidity, and its security issues; and two weeks on Tezos, with the bulk of material on Michelson. 
\item Ha developed slides and exercises, she conducted the weekly exercise session, and she will help with designing and grading the final exam (ongoing in August and September 2020).
\item We felt that it was easier to do supportive exercises for the book (where students could program in Python) as well as for Ethereum (where there are web interfaces that allow you to check out Solidity). For Tezos, we didn't have a good way to connect the students to our server and we felt it overwhelming for the students to install their own Tezos node just for one week worth of exercises. Hence, our Michelson exercises deal with type checking and dry-running the code.
\end{itemize}

May 2020-August 2020
\begin{itemize}
\item Ha (with Max) is documenting the way the Tezos client accesses the node for various operations, initially for transfers (see attached file model\_transaction.pdf). 
\item Ha and I are developing an operational semantics suitable for modeling the interaction of an OCaml program with the Tezos blockchain. The challenge is to find the right level of abstraction. The goal is not to model the execution on the blockchain (others have done that in general \cite{DBLP:conf/ccs/LuuCOSH16}, for Bitcoin \cite{DBLP:conf/ccs/BartolettiZ18}, or for the Cardano blockchain  \cite{DBLP:conf/fc/ChakravartyCMMPW20}), but to have just enough detail to describe the interaction between contract invocations on the blockchain and a program (or potentially multiple programs).

  The current version may be found in the attachment model.pdf.
\end{itemize}

\section{Relation to the Contract}
\label{sec:relation-contract}

We have made progress on several bullet points in the contract.
\begin{itemize}
\item ``Enrich the type system\dots'' Not started because of missing preliminaries.
\item ``Collaborate with JG\dots'' We haven't reached that point, yet. However, it would be interesting to have a meeting next year (if conditions allow) to find out how work on the type inferencer is proceeding.
\item ``Provide a framework\dots'' We started with the groundwork for the second subitem. We are now able to write the code by hand that should be generated by the compiler and we work on wrapping that code framework into a library.
\item ``Apply the newly developed framework\dots'' This framework has just been accepted for publication at ICFP 2020. We are currently working on the first subitem ``A type-safe integration of RPC-invocations of the Tezos API.''
\item ``Mini-OCaml'' The model that Ha and I work on constitutes the first step.
\item ``Publish work \dots'' This year, we published work at POPL and ICFP \cite{DBLP:journals/pacmpl/ThiemannV20,DBLP:journals/pacmpl/RadanneST20}. In the past semester, we taught the course ``blockchain and cryptocurrencies'' as well as a course ``essentials of programming languages'', which teaches verified semantics with Agda.
\end{itemize}

\section{Next Steps}
\label{sec:next-steps}

We are currently recruiting another student (from the blockchain course) to do his Master's thesis with us. He is interested in coordinating on-chain and off-chain computation, but he has a C++ background. It is unclear whether he could usefully contribute to OCaml development, so we expect that his contribution would be more on a conceptual level with a proof of concept in a different implementation.

We hope to attract further students from the course after the examination period.

Tamara will continue working on design and implementation of the OCaml API. We expect her Master's thesis topic to be the type-safe API for contract invocation and contract creation.

Ha and I will work out the execution model into the operational semantics of the full system that is called Mini-OCaml in the  contract.

\bibliography{report}
\bibliographystyle{plainurl}
\end{document}

### 2020-08-13 meeting-notes/20200812-expose.tex
expose created

\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{mathpartir}
\usepackage{listings}

\input{solidity-highlighting}

\title{Expos\'{e} Master Thesis\\
  Checking Assertions for Smart Contracts}
\author{Peter Thiemann}
\begin{document}
\maketitle{}

\section{Introduction}
\label{sec:introduction}

Every computation performed by a Smart Contract on the blockchain generates costs. Each
unit of computation and each unit of storage used by an algorithm must be paid for. To
avoid this cost, users might perform some computation offchain and submit the result as a
parameter to a contract. Typically, such a computation asserts certain properties of the
submitted parameter.

However, this approach raises the issue that on the one hand the contract should take
advantage of the offchain computation and just assume that the submitted parameter has
these properties, but on the other hand, the offchain computation might be wrong and
submit illegal parameters. So, we need a mechanism that checks the validity of the
assumptions before the contract starts executing.

As an example, consider a contract that takes a prime number as a parameter.
\begin{lstlisting}[numbers=none]
contract Example {
  function (int p) public {
    // assume p is prime
    ...
  }
}
\end{lstlisting}
We express the assumption with an explicit assertion.
\begin{displaymath}
  (\forall n) (2 \le n \le \sqrt p) \Rightarrow (p \mathbin{\%} n) \ne 0
\end{displaymath}
We could test this assumption with a loop in the contract, but the test would take
$O(\sqrt p)$ time (assuming constant time for computing the modulus) and thus produce cost
depending on $p$ accordingly. 
However, we could do better by recruiting the validators of the contract for a distributed
effort to find a counterexample. To this end, we consider the negation of the assertion.
\begin{displaymath}
  (\exists n) (2 \le n \le \sqrt p) \wedge (p \mathbin{\%} n) = 0
\end{displaymath}
This assertion can be checked pointwise by having each validator independently choose a
random $n$ fulfilling $2 \le n \le 
\sqrt p$ and checking whether $(p \mathbin{\%} n) = 0$. If the remainder is $0$, the
validator found a counterexample, posts its veto to the P2P net, and stops further
exection. Otherwise, it accepts $p$ knowing that other points will be checked by other
validators.

In this scenario, each validator only needs to be paid to generate a random number and
perform a division, which is a constant cost independant from $p$.

Of course, this validation is only probabilistic, so its effectiveness depends on the
number of validators. One could say that the community of validators implements a Bloom
filter for the set of primes: if a value $p$ is rejected it is certainly not a prime (because
there exists a counterexample); if a value $p$ is not rejected it is prime with a
probability that depends on $p$ and the number of validators.

As another example, consider a contract that takes a sorted array of integers.
\begin{lstlisting}[numbers=none]
contract Sorted {
  function find (int[50] a, int v) public {
    // assume a is sorted
  }
}
\end{lstlisting}
The explicit assertion would be
\begin{displaymath}
  (\forall k) (0\le k <49) \Rightarrow a[k] \le a[k+1]
\end{displaymath}
While we can check this contract in $O(1)$ time, the constant factor is large! So we
consider its negation.
\begin{displaymath}
  (\exists k) (0\le k <49) \wedge a[k] > a[k+1]
\end{displaymath}
Again, we can have the validators generate a random number $k$ and check the
condition. If it is true, then the validator found a counterexample for the sortedness
of the array. Otherwise, the validator relies on the others.

Let's assume the array is unsorted only at position $0$, the size of the array is $n$,
and the number of validators is $m$. Each validator independently has a probability of
$1/n$ to detect the problem. The probability that no validator checks at
position $0$ converges to $0$ as the number of validators approaches infinity.
\begin{displaymath}
  \lim_{m\to\infty}\frac{(n-1)^m}{n^m}
  = \lim_{m\to\infty} \left(\frac{n-1}{n}\right)^m
  = 0
\end{displaymath}

\section{Further Thoughts}
\label{sec:further-thoughts}

There may be an alternative way of implementing this scheme without modifying the
protocol, but instead adding instructions to the virtual machine. One instruction would
generate a random number (EVM uses 512 bit unsigned integer IIRC), the other would
raise an overriding failure. Ideally, once a counterexample has been found, this
counterexample is broadcast to the network where it can be verified by further nodes.

This approach poses the danger of a DOS attack. Someone could post a false
counterexample, which does not really lead to a failure. If everyone switches to check
this proposed counterexample instead of generating a random number, then the real
problem may remain hidden. So, there has to be a component in the protocol that
penalizes someone who broadcasts a false counterexample. Moreover, not all validators
should switch to recheck a proposed counterexample; or they could check it in addition
to their own random check.

The interesting assertion formulas are those with prenex universal
quantification. Negation turns them into prenex existential quantification. But it
would be ineffective to generate a random integer and then check that it falls in the
interesting range (e.g., $2\le n \le \sqrt p$ and $0\le k< n-1$). Rather, the formula
needs to be analzed and the random generator should be restricted to only generate
interesting values.

It would not be significantly more expensive to have every validator perform a
predetermined finite number of checks for each assertion.

What is the minimum number $m$ of validators such that the probability of spotting an
error is less than a given threshold $q$?

Instead of using random numbers, is there a way to coordinate a systematic exploration
of the iteration space? (Is this at all necessary?)

One could also check properties of the values stored by the contract.

\end{document}

### 2020-08-17 meeting-notes/20200812-expose.tex
update
more examples

@@
 \usepackage{listings}
+\usepackage{url}
 
@@
 The explicit assertion would be
-\begin{displaymath}
+\begin{gather}\label{eq:1}
   (\forall k) (0\le k <49) \Rightarrow a[k] \le a[k+1]
-\end{displaymath}
+\end{gather}
 While we can check this contract in $O(1)$ time, the constant factor is large! So we
@@
 
+Connections to random testing?
+
+In Dafny (citation) \url{https://rise4fun.com/Dafny/tutorialcontent/guide#h29} you can
+write
+\begin{lstlisting}
+forall j, k :: 0 <= j < k < a.Length ==> a[j] <= a[k]
+\end{lstlisting}
+to express that an array is sorted. This predicate is equivalent to the one given in
+\eqref{eq:1}, but it might be more challenging to test. Its negation is
+\begin{gather}
+  \label{eq:2}
+  (\exists j, k ) (0\le j< k < |a|) \wedge a[j] > a[k]
+\end{gather}
+So we'd have to generate two random numbers $j$ and $k$ such that the condition $0 \le
+j < k < |a|$ is fulfilled.
+
+Another condition that might be tested on an array is the heap condition
+\begin{gather}
+  \label{eq:3}
+  (\forall i) (0 \le i < \lfloor|a|/2\rfloor) \Rightarrow a[i] \le a[2i+1] \wedge (2i+2
+  < |a| \Rightarrow a[i] \le a[2i+2])
+\end{gather}
+
 \end{document}

### 2020-08-18 meeting-notes/20200812-expose.tex
integrated remarks by Ha

@@
 \usepackage{url}
+
+\usepackage{xcolor}
+\usepackage{tcolorbox}
+\tcbuselibrary{breakable}
+
+\newenvironment{changethis}{%
+  \begin{tcolorbox}[breakable,notitle,boxrule=0pt,colback=blue!20,colframe=blue!20]}{%
+  \end{tcolorbox}}
 
@@
 counterexample is broadcast to the network where it can be verified by further nodes.
+But this broadcast and the reaction to this broadcast requires an update of the
+protocol: all receivers of the broadcast will check the counterexample and revert the
+transaction. This probably means that a transaction using this feature has to wait for
+a couple of cycles in the transaction pool until the node feels safe to include the
+transaction in a block.
 
+\begin{changethis}
+  Tezos specific remarks, here the number of validators is really small compared to
+  Bitcoin or Ethereum
+  \begin{itemize}
+  \item maybe we need to propose and validate the same block multiple times before it
+    gets accepted. E.g, a transaction containing this feature is only accepted if it is
+    revalidated $n$ times.
+  \item Extra validators only for this kind of transaction.
+  \end{itemize}
+\end{changethis}
 This approach poses the danger of a DOS attack. Someone could post a false

### 2020-08-18 papers/execution-model/model.tex
Add files via upload

@@
 \\
-$\mathbf{qry}$ ::= get balance for $\mathbf{pkh}$
+$\mathbf{qry}$ ::= get balance for $\mathbf{pkh}$ $/$ $\mathbf{puh}$
 %$\mid$ get delegate for $\mathbf{pkh}$
 \\$\mid$ get status for $\mathbf{oph}$ 
-\\$\mid$ get contract storage $\mathbf{pkh}$ 
-\\$\mid$ get code for $\mathbf{pkh}$ 
+\\$\mid$ get contract storage $\mathbf{puh}$ 
+\\$\mid$ get code for $\mathbf{puh}$ 
 %\\$\mid$ waiting for $\mathbf{oph}$ to be included in $\mathbf{m}$ blocks
@@
 \subsection{Transfers}
-
+\\
+\\
 Rule 1 [proposal]:
@@
 \frac{\text{checkBan(K, $pkh$, $n$, $m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ checkPub(K, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$}\\
-\text{$\langle$[C, O, S],[($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
+\text{$\langle$[C, O, S], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
 \text{$pkh'$, $n$, $m$, t), t $>$) :: P, A, updateCou(K, $pkh$, True), T, t]$\rangle$}}} 
@@
 \frac{}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$ } \\
- \text{[P,$<$ transfer $n$ from  $puk$ to $puk'$ fee $m$, oph, t' $>$ :: A, updateSucc(K, } \\
+ \text{[P, $<$ transfer $n$ from  $puk$ to $puk'$ fee $m$, oph, t' $>$ :: A, updateSucc(K, } \\
 \text{$puk$, $puk'$, $n$, $m$), T, t' + 1]}}} 
@@
 \subsection{Smart Contracts}
-
-\subsubsection*{A. Originate}
-
+\\
+A. Originate
+\\
+\\
 Rule 1 [proposal]:
@@
 \begin{equation}{}
-\frac{\text{checkAcc($pkh$, C) $\wedge$ checkId($id$, S) $\wedge$ \text{checkPrg($code$, $s$)}}}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, (originate contract ${puh}$ transferring} \\
+\frac{\text{checkAcc($pkh$, C) $\wedge$ checkId($id$, S)}}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, (originate contract ${id}$ transferring} \\
   \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: O, S], [P, A, K, T, t]$\rangle$}}} 
 \end{equation}
-
-\subsubsection*{Rule 2 [injected]:}
+\\
+\\
+Rule 2 [injected]:
 
 \begin{equation}{}
-\frac{\text{checkBan(K, $pkh$, $n$, $m$) $\wedge$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: O, S], [P, A, K, T, t] $\rangle$ $\rightarrow$ $\langle$ [C, O, S],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: P, A, updateCou(K, $pkh$, True), T, t] $\rangle$}}}
+\frac{\text{checkBan(K, $pkh$, $n$, $m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ \text{checkPrg($code$, $s$)}}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: O, S], [P, A, K, T, t] $\rangle$ $\rightarrow$ $\langle$ [C, O, S],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: P, A, updateCou(K, $pkh$, True), T, t] $\rangle$}}}
 \end{equation}
-
-\subsubsection*{Rule 3 [rejected of code]:}
+\\
+\\
+Rule 3 [rejected of code]:
 
@@
 \end{equation}
-
-\subsubsection*{Rule 4 [rejected of counter]:}
+\\
+\\
+Rule 4 [rejected of counter]:
 
@@
 \end{equation}
-
-\subsubsection*{Rule 5 [rejected of balance]:}
+\\
+\\
+Rule 5 [rejected of balance]:
 
@@
 \end{equation}
-
-\subsubsection*{Rule 6 [included]:}
+\\
+\\
+Rule 6 [included]:
 \begin{equation}{}
 \frac{}{\parbox{4.2in}{\text{$\langle$[C, O, S], [$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running } \\
-\text{${code}$ init ${s}$), t $>$ :: P, A, K, T, t' ]$\rangle$ $\rightarrow$ $\langle$[C, O, addContr(S, $id$, } \\
-\text{generateHash($id$, $code$, $s$, t'), $code$)], [P,$<$ (originate contract ${id}$ } \\
+\text{${code}$ init ${s}$), t $>$ :: P, A, K, T, t' ]$\rangle$ $\rightarrow$ $\langle$[C, O,($<$ $id$, } \\
+\text{generateHash($id$, $code$, $s$, t'), $code$ $>$ :: S)], [P, $<$ (originate contract ${id}$ } \\
 \text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), t' $>$ :: A, updateSucc(K, } \\
-\text{$puk$, $n$, $m$), addOrig(T, $<$ generateHash($id$, $code$, $s$, t'), $0$, $code$, } \\
- \text{getStorage($code$, $s$) $>$), t' + 1]$\rangle$}}} 
+\text{$puk$, $n$, $m$), ($<$ generateHash($id$, $code$, $s$, t'), $n$, $code$, } \\
+ \text{getStorage($code$, $s$) $>$) :: T), t' + 1]$\rangle$}}} 
 \end{equation}
-
-\subsubsection*{Rule 7 [timeout]:}
+\\
+Rule 7 [timeout]:
 \begin{equation}{}
@@
 \end{equation}
-
-\subsubsection*{B. Transfer}
-
-\subsubsection*{Rule 1 [proposal]:}
+\\
+\\
+B. \mathbf{Transfer}
+\\
+\\
+Rule 1 [proposal]:
 
@@
 \end{equation}
-
-\subsubsection*{Rule 2 [injected]:}
+\\
+\\
+Rule 2 [injected]:
 
 \begin{equation}{}
-\frac{\text{checkBan(K, $pkh$, $n$, $m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ checkContr(T, $puh$, s) }}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}\\
+\frac{\text{checkBan(K, $pkh$, $n$, $m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ checkPuh(T, $puh$)}
+\\
+\text{ $\wedge$ checkArg(T, $puh$, $s$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}\\
 \text{$\rightarrow$  $\langle$[C, O, S], [($<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), }\\
- \text{generateOph($pkh$, $puh$, $s$, $n$, $m$, t $>$) :: P, A, updateCou(K, $pkh$, True), }\\
+ \text{generateOph($pkh$, $puh$, $s$, $n$, $m$, t), t $>$) :: P, A, updateCou(K, $pkh$, True), }\\
 \text{T, t] $\rangle$}}} 
 \end{equation}
-
-\subsubsection*{Rule 3 [rejected of counter]:}
+\\
+\\
+Rule 3 [rejected of counter]:
 
@@
 \end{equation}
-
-\subsubsection*{Rule 4 [rejected of balance]:}
+\\
+\\
+Rule 4 [rejected of balance]:
 
@@
 \end{equation}
-
-\subsubsection*{Rule 5 [rejected of public key]:}
+\\
+\\
+Rule 5 [rejected of public hash]:
 
 \begin{equation}{}
-\frac{\text{$\neg$ checkContr(T, $puh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$ }\\
+\frac{\text{$\neg$ checkPuh(T, $puh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$ }\\
 \text{$\rightarrow$ $\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
 \end{equation}
-
-\subsubsection*{Rule 6 [rejected of argument]:}
+\\
+\\
+Rule 6 [rejected of argument]:
 
@@
 \end{equation}
-
-\subsubsection*{Rule 7 [included]:}
+\\
+\\
+Rule 7 [included]:
 \begin{equation}{}
@@
 \text{[P, $<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), oph, t' $>$ :: A, } \\
-\text{updateSucc(K, puk, '', $n$, $m$), updateConstr(T, $puh$, $s$), t' + 1]}}} 
+\text{updateSucc(K, puk, \'\', $n$, $m$), updateConstr(T, $puh$, $n$, $s$), t' + 1]}}} 
 \end{equation}
-
-\subsubsection*{Rule 8 [timeout]:}
+\\
+Rule 8 [timeout]:
 \begin{equation}{}
@@
 
-    \item Function \verb!checkId(id, S)! checks whether a contract $id$ exists in S
+    \item Function \verb!checkId(id, S)! checks whether a contract $id$ does not already exist in S
 
@@
 
-    \item Function \verb!addContr(S, id, puh, code)! adds a new  contract $<$ $id$, $puh$, $code$ $>$  into S
+    %\item Function \verb!addContr(S, id, puh, code)! adds a new  contract $<$ $id$, $puh$, $code$ $>$  into S
 
-    \item Function \verb! generateOph(pkh,pkh', n, m, t)! generates a operation hash
+    \item Function \verb! generateOph(pkh,pkh′, n, m, t)! generates a operation hash
 
@@
 
-    \item Function \verb!addOrig(T,< hash, 0, code, storage >)! add the a new originator $<$ $puh$, 0, $code$, $storage$ $>$ 
+   % \item Function \verb!addOrig(T,< hash, 0, code, storage >)! add the a new originator $<$ $puh$, 0, $code$, $storage$ $>$ 
     \item Function \verb!getStorage(code, s)! gets the storage for the code $code$ and the input $s$

### 2020-08-24 papers/execution-model/model.tex
cleanup

@@
 \newtheorem{mypro}{Proposition}
+
+\input{macros}
 
@@
 \\
-$\mathbf{s}$ :: = $\emptyset$ $\mid$ $\mathbf{e}$ $\mid$ $\mathbf{s :: s}$
+$\mathbf{s} :: = \emptyset \mid \mathbf{e} \mid \mathbf{s :: s}$
 \end{definition}
@@
 \begin{definition}[Account]
-An account is expressed as a tuple $<$ $\mathbf{als}$, $\mathbf{pak}$, $\mathbf{puk}$, $\mathbf{pkh}$ $>$, where $\mathbf{als}$ is the alias of the account, $\mathbf{pak}$ is its private key, $\mathbf{puk}$ is its public key and $\mathbf{pkh}$ is its public key hash .
+An account is a tuple $\langle \ALS, \PAK, \PUK, \PKH \rangle $, where $\ALS$ is the alias of the account, $\PAK$ is its private key, $\PUK$ is its public key and $\PKH$ is its public key hash . 
 \end{definition}
@@
 \begin{definition}[Contract]
-An contract is expressed as a tuple $<$ $\mathbf{als}$, $\mathbf{puh}$, $\mathbf{code}$ $>$, where $\mathbf{als}$ is the alias of the contract, $\mathbf{puh}$ is its public hash and $\mathbf{code}$ is the code of the contract.
+An contract is a tuple $\langle  \ALS, \PUH, \CODE \rangle $, where
+$\ALS$ is the alias of the contract, $\PUH$ is its public hash, and
+$\CODE$ is the code of the contract. 
 \end{definition}
@@
 \begin{definition}[Manager]
-An manager manages accounts on the blockchain.
-It is expressed as a tuple $<$ $\mathbf{puk}$, $\mathbf{pkh}$, $\mathbf{bal}$,  $\mathbf{cou}$ $>$, where  $\mathbf{puk}$ is the public key of an account, $\mathbf{pkh}$ is its public key hash, $\mathbf{bal}$ is its balance and $\mathbf{cou}$ is its counter whose form is a pair ($\mathbf{n}$, $\mathbf{b}$), where $\mathbf{n}$ is a nature number and $\mathbf{b}$ is a boolean value.
+An manager manages accounts on the blockchain. It is represented by a
+tuple $\langle  \PUK, \PKH, \BAL, \COU \rangle $, where  $\PUK$ is the
+public key of an account, $\PKH$ is its public key hash, $\BAL$ is its
+balance and $\COU$ is its counter whose form is a pair ($\mathbf{n},
+\mathbf{b}$), where $\mathbf{n}$ is a nature number and $\mathbf{b}$
+is a boolean value.  
 \end{definition}
@@
 \begin{definition}[Contractor]
-A contractor manages smart contracts on the blockchain.
-It is expressed as a tuple $<$ $\mathbf{puh}$, $\mathbf{bal}$,  $\mathbf{code}$,  $\mathbf{storage}$ $>$, where $\mathbf{puh}$ is the public hash of the contract, $\mathbf{bal}$ is its balance, $\mathbf{code}$ is its code and  $\mathbf{storage}$ is its storage.
+  A contractor manages smart contracts on the blockchain. It is
+  represented by a tuple
+  $\langle \PUH, \BAL, \CODE, \STORAGE \rangle $, where $\PUH$ is the
+  public hash of the contract, $\BAL$ is its balance, $\CODE$ is its
+  code and $\STORAGE$ is its storage.
 \end{definition}
@@
 \\
-$\mathbf{op}$ ::= transfer  $\mathbf{n}$ from $\mathbf{pkh}$ to $\mathbf{pkh'}$ fee $\mathbf{m}$
-%\\$\mid$ register key $\mathbf{pkh}$ as delegate fee $\mathbf{m}$ 
-%\\$\mid$ set delegate for $\mathbf{pkh}$ to $\mathbf{pkh'}$  fee $\mathbf{m}$ 
-%\\$\mid$ withdraw delegate from $\mathbf{pkh}$ fee $\mathbf{m}$ 
-\\$\mid$ originate contract $\mathbf{id}$ transferring  $\mathbf{n}$ from $\mathbf{pkh}$ running $\mathbf{code}$ init $\mathbf{s}$ fee $\mathbf{m}$
-\\$\mid$ transfer $\mathbf{n}$ from $\mathbf{pkh}$ to  $\mathbf{puh}$ arg $\mathbf{s}$ fee $\mathbf{m}$
+$\OP$ ::= transfer  $\mathbf{n}$ from $\PKH$ to $\PKH'$ fee $\mathbf{m}$
+%\\$\mid$ register key $\PKH$ as delegate fee $\mathbf{m}$ 
+%\\$\mid$ set delegate for $\PKH$ to $\PKH'$  fee $\mathbf{m}$ 
+%\\$\mid$ withdraw delegate from $\PKH$ fee $\mathbf{m}$ 
+\\$\mid$ originate contract $\mathbf{id}$ transferring  $\mathbf{n}$ from $\PKH$ running $\CODE$ init $\mathbf{s}$ fee $\mathbf{m}$
+\\$\mid$ transfer $\mathbf{n}$ from $\PKH$ to  $\PUH$ arg $\mathbf{s}$ fee $\mathbf{m}$
 \end{definition}
@@
 \\
-$\mathbf{qry}$ ::= get balance for $\mathbf{pkh}$ $/$ $\mathbf{puh}$
-%$\mid$ get delegate for $\mathbf{pkh}$
-\\$\mid$ get status for $\mathbf{oph}$ 
-\\$\mid$ get contract storage $\mathbf{puh}$ 
-\\$\mid$ get code for $\mathbf{puh}$ 
-%\\$\mid$ waiting for $\mathbf{oph}$ to be included in $\mathbf{m}$ blocks
+$\mathbf{qry}$ ::= get balance for $\PKH / \PUH$
+%$\mid$ get delegate for $\PKH$
+\\$\mid$ get status for $\OPH$ 
+\\$\mid$ get contract storage $\PUH$ 
+\\$\mid$ get code for $\PUH$ 
+%\\$\mid$ waiting for $\OPH$ to be included in $\mathbf{m}$ blocks
 %\\$\mid$ get timestamp
 %\\$\mid$ get contracts
-%\\$\mid$ show contracts for $\mathbf{pkh}$
-\\$\mid$ get public key for $\mathbf{pkh}$
-%\\$\mid$ get balance for $\mathbf{pkh}$
-\\$\mid$ get counter for $\mathbf{pkh}$
+%\\$\mid$ show contracts for $\PKH$
+\\$\mid$ get public key for $\PKH$
+%\\$\mid$ get balance for $\PKH$
+\\$\mid$ get counter for $\PKH$
 
 \end{definition}
-Let $\mathbf{C}$ be the set of accounts,   $\mathbf{O}$ be a set of operations, and $\mathbf{S}$ be the set of contracts. 
  \begin{definition}[State of a node]
-The state of a node is expressed as a tuple $[$$\mathbf{C}$, $\mathbf{O}$, $\mathbf{S}$$]$ .
+   The state of a node is a tuple
+   $[\mathbf{C}, \mathbf{O}, \mathbf{S}]$ where $\mathbf{C}$ is a set of accounts,
+   $\mathbf{O}$ a set of operations, and $\mathbf{S}$  a set of contracts. 
 \end{definition}
 
-When an operation is injected in a node, it enters in a pending pool (and called a pending operation). 
+When an operation is injected in a node, it enters in a pending pool
+(and is called a pending operation). 
  \begin{definition}[Pending operation]
-A pending operation is expressed as a pair  $<$ $\mathbf{op}$, $\mathbf{oph}$, $\mathbf{t}$ $>$, where $\mathbf{op}$ is an operation, $\mathbf{oph}$ is the operation hash and $\mathbf{t}$ is the time when it is injected.
+A pending operation is a tuple  $\langle  \OP, \OPH, \TIME
+\rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash
+and $\TIME$ is the time when the operation was injected. 
 \end{definition}
-After sometime, a pending operation could be included in the blockchain as a accepted operation.
+After some time, a pending operation may be included in the blockchain as an accepted operation.
 %Let \textit{P} is the set of pending operations.
  \begin{definition}[Accepted operation]
-An accepted operation  is expressed as a tuple $<$ $\mathbf{op}$, $\mathbf{oph}$, $\mathbf{t}$ $>$, where $\mathbf{op}$ is an operation, $\mathbf{oph}$ is the operation hash and $\mathbf{t}$ is the time when it is included in the blockchain.
+An accepted operation  is expressed as a tuple $\langle  \OP, \OPH, \TIME \rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash and $\TIME$ is the time when it is included in the blockchain.
 \end{definition}
-Let $\mathbf{P}$ be a set of pending operations,  $\mathbf{A}$ be a set of accepted operations, $\mathbf{K}$ be a set of managers, $\mathbf{T}$ be a set of contractors % $\mathbf{h}$ be the hash of the current block head
-and $\mathbf{t}$ is the current time of the blockchain.
 
 \begin{definition}[Blockchain]
-The state of a blockchain is expressed as a tuple $[$$\mathbf{P}$, $\mathbf{A}$, $\mathbf{K}$, $\mathbf{T}$, $\mathbf{t}$$]$.  
+  The state of a blockchain is a tuple
+  $[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ where
+  $\PENDING$ is a set of pending operations,  $\ACCEPTED$ is a set
+  of accepted operations, $\MANAGERS$ is a set of managers,
+  $\CONTRACTORS$ is a set of contractors, and $\TIME$ is the current time of the blockchain. 
 \end{definition}
@@
 \begin{definition}[Blockchain system]
-A blockchain system 
-$\mathbf{S}$ $\triangleq\langle$ $\mathbf{M}$, $\mathbf{B}$ $\rangle$ consists of
+A blockchain system is a pair
+$\mathbf{S} \triangleq\langle \mathbf{M}, \mathbf{B} \rangle$ where
 \begin{enumerate}
-\item $\mathbf{M}$ $\equiv$ [C, O, S] is the state of a node, and
-\item $\mathbf{B}$ $\equiv$ [P, A, K, T, t] is the state of a blockchain 
-such as $\forall$ c $\in$ C $\implies$ $\exists$ k $\in$ K, k.pkh = c.pkh and $\forall$ s $\in$ S $\implies$ $\exists$ p $\in$ T, s.puh = p.puh.
+\item $\mathbf{M} = [C, O, S]$ is the state of a node, and
+\item $\mathbf{B} = [P, A, K, T, t]$ is the state of a blockchain 
+  such that $\forall c \in C \implies \exists k\in K, k.pkh = c.pkh$
+  and $\forall s \in S \implies \exists p \in T, s.puh = p.puh$.
 \end{enumerate}
@@
 \subsection{Transfers}
-\\
-\\
+~\\
 Rule 1 [proposal]:
@@
 \begin{equation}{}
-\frac{\text{checkAcc($pkh$, C)}}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$)} \\\text{ :: O, S], [P, A, K, T, t]$\rangle$}}}
+\frac{\text{checkAcc($pkh$, C)}}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle \rightarrow \langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$)} ~\\\text{ :: O, S], [P, A, K, T, t]$\rangle$}}}
 \end{equation}
-\\
-\\
+~\\
+~\\
 Rule 2 [injected]:
@@
 \begin{equation}{}
-\frac{\text{checkBan(K, $pkh$, $n$, $m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ checkPub(K, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$}\\
+\frac{\text{checkBan(K, $pkh, n, m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ checkPub(K, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle \rightarrow$}\\
 \text{$\langle$[C, O, S], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
-\text{$pkh'$, $n$, $m$, t), t $>$) :: P, A, updateCou(K, $pkh$, True), T, t]$\rangle$}}} 
+\text{$pkh', n, m$, t), t $>$) :: P, A, updateCou(K, $pkh$, True), T, t]$\rangle$}}} 
 \end{equation}
-\\
-\\
+~\\
+~\\
 Rule 3 [rejected of counter]:
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ }\\
+\frac{\text{$\neg$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle \rightarrow$ }\\
 \text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
 \end{equation}
-\\
-\\
+~\\
+~\\
 Rule 4 [rejected of balance]:
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkBan(K, $pkh$, $m$, $n$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ }\\
+\frac{\text{$\neg$ checkBan(K, $pkh, m, n$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle \rightarrow$ }\\
 \text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
 \end{equation}
-\\
-\\
+~\\
+~\\
 Rule 5 [rejected of public key]:
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkPub(K, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ }\\
+\frac{\text{$\neg$ checkPub(K, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle \rightarrow$ }\\
 \text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
 \end{equation}
-\\
-\\
+~\\
+~\\
 Rule 6 [included]:
@@
  \text{[P, $<$ transfer $n$ from  $puk$ to $puk'$ fee $m$, oph, t' $>$ :: A, updateSucc(K, } \\
-\text{$puk$, $puk'$, $n$, $m$), T, t' + 1]}}} 
+\text{$puk, puk', n, m$), T, t' + 1]}}} 
 \end{equation}
-\\
+~\\
 Rule 7 [timeout]:
 \begin{equation}{}
-\frac{\text{t' - t $>=$ 60}}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$} \\
+\frac{\text{t' - t $\ge$ 60}}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$} \\
  \hspace*{0cm} \text{[P, A, updateCou(K, $puk$, False), T, t']}}} 
@@
 \subsection{Smart Contracts}
-\\
+~\\
 A. Originate
-\\
-\\
+~\\
+~\\
 Rule 1 [proposal]:
@@
 \begin{equation}{}
-\frac{\text{checkAcc($pkh$, C) $\wedge$ checkId($id$, S)}}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, (originate contract ${id}$ transferring} \\
+\frac{\text{checkAcc($pkh$, C) $\wedge$ checkId($id$, S)}}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle \rightarrow \langle$[C, (originate contract ${id}$ transferring} \\
   \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: O, S], [P, A, K, T, t]$\rangle$}}} 
 \end{equation}
-\\
-\\
+~\\
+~\\
 Rule 2 [injected]:
@@
 \begin{equation}{}
-\frac{\text{checkBan(K, $pkh$, $n$, $m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ \text{checkPrg($code$, $s$)}}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: O, S], [P, A, K, T, t] $\rangle$ $\rightarrow$ $\langle$ [C, O, S],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: P, A, updateCou(K, $pkh$, True), T, t] $\rangle$}}}
+\frac{\text{checkBan(K, $pkh, n, m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: O, S], [P, A, K, T, t] $\rangle \rightarrow \langle$ [C, O, S],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: P, A, updateCou(K, $pkh$, True), T, t] $\rangle$}}}
 \end{equation}
-\\
-\\
+~\\
+~\\
 Rule 3 [rejected of code]:
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkPrg($code$, $s$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, O, S],} \text{[P, A, K, T, t]$\rangle$}}}
+\frac{\text{$\neg$ checkPrg($code, s$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: O, S], [P, A, K, T, t]$\rangle \rightarrow \langle$[C, O, S],} \text{[P, A, K, T, t]$\rangle$}}}
 \end{equation}
-\\
-\\
+~\\
+~\\
 Rule 4 [rejected of counter]:
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$))} \text{:: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$ [C, O, S],} \text{[P, A, K, T, t]$\rangle$}}}
+\frac{\text{$\neg$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$))} \text{:: O, S], [P, A, K, T, t]$\rangle \rightarrow \langle$ [C, O, S],} \text{[P, A, K, T, t]$\rangle$}}}
 \end{equation}
-\\
-\\
+~\\
+~\\
 Rule 5 [rejected of balance]:
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkBan(K, $pkh$, $n$, $m$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, O, S],} \text{[P, A, K, T, t]$\rangle$}}}
+\frac{\text{$\neg$ checkBan(K, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: O, S], [P, A, K, T, t]$\rangle \rightarrow \langle$[C, O, S],} \text{[P, A, K, T, t]$\rangle$}}}
 \end{equation}
-\\
-\\
+~\\
+~\\
 Rule 6 [included]:
@@
 \frac{}{\parbox{4.2in}{\text{$\langle$[C, O, S], [$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running } \\
-\text{${code}$ init ${s}$), t $>$ :: P, A, K, T, t' ]$\rangle$ $\rightarrow$ $\langle$[C, O,($<$ $id$, } \\
-\text{generateHash($id$, $code$, $s$, t'), $code$ $>$ :: S)], [P, $<$ (originate contract ${id}$ } \\
+\text{${code}$ init ${s}$), t $>$ :: P, A, K, T, t' ]$\rangle \rightarrow \langle$[C, O,($< id$, } \\
+\text{generateHash($id, code, s$, t'), $code >$ :: S)], [P, $<$ (originate contract ${id}$ } \\
 \text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), t' $>$ :: A, updateSucc(K, } \\
-\text{$puk$, $n$, $m$), ($<$ generateHash($id$, $code$, $s$, t'), $n$, $code$, } \\
- \text{getStorage($code$, $s$) $>$) :: T), t' + 1]$\rangle$}}} 
+\text{$puk, n, m$), ($<$ generateHash($id, code, s$, t'), $n, code$, } \\
+ \text{getStorage($code, s$) $>$) :: T), t' + 1]$\rangle$}}} 
 \end{equation}
-\\
+~\\
 Rule 7 [timeout]:
 \begin{equation}{}
-\frac{\text{t' - t $>=$ 60}}{\parbox{4.2in}{\text{[$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$) $>$ } \\
+\frac{\text{t' - t $\ge$ 60}}{\parbox{4.2in}{\text{[$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$) $>$ } \\
 \text{:: P, A, K, T, t' ] $\rightarrow$[P, A, updateCou(K, $puk$, False), T, t']}}} 
 \end{equation}
+~\\
+~\\
+B. \textbf{Transfer}
 \\
-\\
-B. \mathbf{Transfer}
-\\
-\\
+~\\
 Rule 1 [proposal]:
@@
 \begin{equation}{}
-\frac{\text{checkAcc($pkh$, C)  }}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ }  \\
+\frac{\text{checkAcc($pkh$, C)  }}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle \rightarrow \langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ }  \\
 \text{fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}}} 
 \end{equation}
-\\
-\\
+~\\
+~\\
 Rule 2 [injected]:
@@
 \begin{equation}{}
-\frac{\text{checkBan(K, $pkh$, $n$, $m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ checkPuh(T, $puh$)}
+\frac{\text{checkBan(K, $pkh, n, m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ checkPuh(T, $puh$)}
 \\
-\text{ $\wedge$ checkArg(T, $puh$, $s$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}\\
+\text{ $\wedge$ checkArg(T, $puh, s$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}\\
 \text{$\rightarrow$  $\langle$[C, O, S], [($<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), }\\
- \text{generateOph($pkh$, $puh$, $s$, $n$, $m$, t), t $>$) :: P, A, updateCou(K, $pkh$, True), }\\
+ \text{generateOph($pkh, puh, s, n, m$, t), t $>$) :: P, A, updateCou(K, $pkh$, True), }\\
 \text{T, t] $\rangle$}}} 
 \end{equation}
-\\
-\\
+~\\
+~\\
 Rule 3 [rejected of counter]:
@@
 \frac{\text{$\neg$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$  }\\
-\text{$\rightarrow$ $\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
+\text{$\rightarrow \langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
 \end{equation}
-\\
-\\
+~\\
+~\\
 Rule 4 [rejected of balance]:
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkBan(K, $pkh$, $n$, $m$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$ }\\
-\text{$\rightarrow$ $\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
+\frac{\text{$\neg$ checkBan(K, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$ }\\
+\text{$\rightarrow \langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
 \end{equation}
-\\
-\\
+~\\
+~\\
 Rule 5 [rejected of public hash]:
@@
 \frac{\text{$\neg$ checkPuh(T, $puh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$ }\\
-\text{$\rightarrow$ $\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
+\text{$\rightarrow \langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
 \end{equation}
-\\
-\\
+~\\
+~\\
 Rule 6 [rejected of argument]:
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkArg(T, $puh$, $s$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}\\
-\text{$\rightarrow$ $\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
+\frac{\text{$\neg$ checkArg(T, $puh, s$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}\\
+\text{$\rightarrow \langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
 \end{equation}
-\\
-\\
+~\\
+~\\
 Rule 7 [included]:
-\begin{equation}{}
-\frac{}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puh$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$ } \\
+
+\begin{equation}
+\frac{}{
+  \begin{array}{l}
+\text{[$<$ transfer $n$ from $puk$ to  $puh$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$ } \\
 \text{[P, $<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), oph, t' $>$ :: A, } \\
-\text{updateSucc(K, puk, \'\', $n$, $m$), updateConstr(T, $puh$, $n$, $s$), t' + 1]}}} 
+\text{updateSucc(K, puk, '', $n, m$), updateConstr(T, $puh, n$,
+  $s$), $t' + 1$]}
+  \end{array}
+}\label{eq:1}
 \end{equation}
-\\
+~\\
 Rule 8 [timeout]:
 \begin{equation}{}
-\frac{\text{t' - t $>=$ 60}}{\parbox{4.2in}{\text{[transfer $n$ from $puk$ to  $puh$ fee $m$, t $>$ :: P, A, K, T, t' ] $\rightarrow$} \\
+\frac{\text{t' - t $\ge$ 60}}{\parbox{4.2in}{\text{[transfer $n$ from $puk$ to  $puh$ fee $m$, t $>$ :: P, A, K, T, t' ] $\rightarrow$} \\
 \text{[P, A, updatecou(K, $puk$, False), T, t']}}} 
@@
 
-    %\item Function \verb!addContr(S, id, puh, code)! adds a new  contract $<$ $id$, $puh$, $code$ $>$  into S
+    %\item Function \verb!addContr(S, id, puh, code)! adds a new  contract $< id, puh, code >$  into S
 
-    \item Function \verb! generateOph(pkh,pkh′, n, m, t)! generates a operation hash
+    \item Function \verb! generateOph(pkh,pkh', n, m, t)! generates a operation hash
 
@@
 
-   % \item Function \verb!addOrig(T,< hash, 0, code, storage >)! add the a new originator $<$ $puh$, 0, $code$, $storage$ $>$ 
+   % \item Function \verb!addOrig(T,< hash, 0, code, storage >)! add the a new originator $\langle  puh$, 0, $code, storage \rangle $ 
     \item Function \verb!getStorage(code, s)! gets the storage for the code $code$ and the input $s$
@@
 
-The following functions interact with $\mathbf{K}$.
+The following functions interact with $\MANAGERS$.
 

### 2020-08-25 papers/execution-model/model.tex
cleanup halfway

@@
 \begin{definition}[Manager]
-An manager manages accounts on the blockchain. It is represented by a
+A manager manages a single account. It is represented by a
 tuple $\langle  \PUK, \PKH, \BAL, \COU \rangle $, where  $\PUK$ is the
 public key of an account, $\PKH$ is its public key hash, $\BAL$ is its
-balance and $\COU$ is its counter whose form is a pair ($\mathbf{n},
-\mathbf{b}$), where $\mathbf{n}$ is a nature number and $\mathbf{b}$
+balance and $\COU$ is its counter whose form is a pair $(n, b)$, where $n$ is a natural number and ${b}$
 is a boolean value.  
@@
 \begin{definition}[Contractor]
-  A contractor manages smart contracts on the blockchain. It is
+  A contractor manages a smart contract. It is
   represented by a tuple
   $\langle \PUH, \BAL, \CODE, \STORAGE \rangle $, where $\PUH$ is the
-  public hash of the contract, $\BAL$ is its balance, $\CODE$ is its
-  code and $\STORAGE$ is its storage.
+  public key hash of the contract, $\BAL$ is its current balance, $\CODE$ is its
+  code, and $\STORAGE$ is its current storage.
 \end{definition}
@@
 \begin{definition}[Operation]
-An operation is expressed as the following syntax:
-\\
-$\OP$ ::= transfer  $\mathbf{n}$ from $\PKH$ to $\PKH'$ fee $\mathbf{m}$
+  Operations are defined by the following grammar:
+  \begin{align*}
+    \OP &::= \TRANSFER[\STRING]\NTEZ\PKH{\PKH'}\MTEZ
+    \\&\mid \ORIGINATE\ID\NTEZ\PKH\CODE\STRING\MTEZ
+    % \\&\mid transfer $\mathbf{n}$ from $\PKH$ to  $\PUH$ arg $\mathbf{s}$ fee $\mathbf{m}$
+  \end{align*}
 %\\$\mid$ register key $\PKH$ as delegate fee $\mathbf{m}$ 
@@
 %\\$\mid$ withdraw delegate from $\PKH$ fee $\mathbf{m}$ 
-\\$\mid$ originate contract $\mathbf{id}$ transferring  $\mathbf{n}$ from $\PKH$ running $\CODE$ init $\mathbf{s}$ fee $\mathbf{m}$
-\\$\mid$ transfer $\mathbf{n}$ from $\PKH$ to  $\PUH$ arg $\mathbf{s}$ fee $\mathbf{m}$
 \end{definition}
@@
 \begin{definition}[Query]
-An query is expressed as the following syntax:
-\\
-$\mathbf{qry}$ ::= get balance for $\PKH / \PUH$
+Queries are defined by the following grammar:
+\begin{align*}
+  \QRY & ::= \GETBALANCE {\PKH / \PUH}
+  \\&\mid \GETSTATUS\OPH
+  \\&\mid \GETSTORAGE\PUH
+  \\&\mid \GETCODE\PUH 
+  \\&\mid \GETPUBLICKEY\PKH
+  \\&\mid \GETCOUNTER\PKH
+\end{align*}
+
 %$\mid$ get delegate for $\PKH$
-\\$\mid$ get status for $\OPH$ 
-\\$\mid$ get contract storage $\PUH$ 
-\\$\mid$ get code for $\PUH$ 
 %\\$\mid$ waiting for $\OPH$ to be included in $\mathbf{m}$ blocks
@@
 %\\$\mid$ show contracts for $\PKH$
-\\$\mid$ get public key for $\PKH$
 %\\$\mid$ get balance for $\PKH$
-\\$\mid$ get counter for $\PKH$
 
@@
    The state of a node is a tuple
-   $[\mathbf{C}, \mathbf{O}, \mathbf{S}]$ where $\mathbf{C}$ is a set of accounts,
-   $\mathbf{O}$ a set of operations, and $\mathbf{S}$  a set of contracts. 
+   $[\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ where $\ACCOUNTS$ is a set of accounts,
+   $\OPERATIONS$ a set of operations, and $\CONTRACTS$  a set of contracts. 
 \end{definition}
 
-When an operation is injected in a node, it enters in a pending pool
+When an operation is injected in a node, it enters a \emph{pending pool}
 (and is called a pending operation). 
@@
  \begin{definition}[Accepted operation]
-An accepted operation  is expressed as a tuple $\langle  \OP, \OPH, \TIME \rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash and $\TIME$ is the time when it is included in the blockchain.
+An accepted operation  is a tuple $\langle  \OP, \OPH, \TIME \rangle
+$, where $\OP$ is an operation, $\OPH$ is the operation hash and
+$\TIME$ is the time when it was included in the blockchain. 
 \end{definition}
@@
 A blockchain system is a pair
-$\mathbf{S} \triangleq\langle \mathbf{M}, \mathbf{B} \rangle$ where
+$\langle \mathbf{M}, \mathbf{B} \rangle$ where
 \begin{enumerate}
-\item $\mathbf{M} = [C, O, S]$ is the state of a node, and
-\item $\mathbf{B} = [P, A, K, T, t]$ is the state of a blockchain 
-  such that $\forall c \in C \implies \exists k\in K, k.pkh = c.pkh$
-  and $\forall s \in S \implies \exists p \in T, s.puh = p.puh$.
+\item $\mathbf{M} = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ is the state of a node, and
+\item $\mathbf{B} = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ is the state of a blockchain 
+  such that $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.pkh = c.pkh$
+  and $\forall s \in \CONTRACTS \implies \exists p \in \CONTRACTORS, s.puh = p.puh$.
 \end{enumerate}
@@
 \begin{equation}{}
-\frac{\text{checkAcc($pkh$, C)}}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle \rightarrow \langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$)} ~\\\text{ :: O, S], [P, A, K, T, t]$\rangle$}}}
+\frac{\text{checkAcc($pkh$, \ACCOUNTS)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$)} ~\\\text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}}
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{checkBan(K, $pkh, n, m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ checkPub(K, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle \rightarrow$}\\
-\text{$\langle$[C, O, S], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
-\text{$pkh', n, m$, t), t $>$) :: P, A, updateCou(K, $pkh$, True), T, t]$\rangle$}}} 
+\frac{\text{checkBan(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$}\\
+\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
+\text{$pkh', n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME]$\rangle$}}} 
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle \rightarrow$ }\\
-\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
+\frac{\text{$\neg$ checkCou(\MANAGERS, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
+\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkBan(K, $pkh, m, n$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle \rightarrow$ }\\
-\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
+\frac{\text{$\neg$ checkBan(\MANAGERS, $pkh, m, n$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
+\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkPub(K, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle \rightarrow$ }\\
-\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
+\frac{\text{$\neg$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
+\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
 \end{equation}
@@
 \begin{equation}{}
-\frac{}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$ } \\
- \text{[P, $<$ transfer $n$ from  $puk$ to $puk'$ fee $m$, oph, t' $>$ :: A, updateSucc(K, } \\
-\text{$puk, puk', n, m$), T, t' + 1]}}} 
+\frac{}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$ } \\
+ \text{[\PENDING, $<$ transfer $n$ from  $puk$ to $puk'$ fee $m$, oph, \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
+\text{$puk, puk', n, m$), \CONTRACTORS, \TIME' + 1]}}} 
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{t' - t $\ge$ 60}}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$} \\
- \hspace*{0cm} \text{[P, A, updateCou(K, $puk$, False), T, t']}}} 
+\frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$} \\
+ \hspace*{0cm} \text{[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{checkAcc($pkh$, C) $\wedge$ checkId($id$, S)}}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle \rightarrow \langle$[C, (originate contract ${id}$ transferring} \\
-  \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: O, S], [P, A, K, T, t]$\rangle$}}} 
+\frac{\text{checkAcc($pkh$, \ACCOUNTS) $\wedge$ checkId($id$, \CONTRACTS)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, (originate contract ${id}$ transferring} \\
+  \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{checkBan(K, $pkh, n, m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: O, S], [P, A, K, T, t] $\rangle \rightarrow \langle$ [C, O, S],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: P, A, updateCou(K, $pkh$, True), T, t] $\rangle$}}}
+\frac{\text{checkBan(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] $\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME] $\rangle$}}}
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkPrg($code, s$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: O, S], [P, A, K, T, t]$\rangle \rightarrow \langle$[C, O, S],} \text{[P, A, K, T, t]$\rangle$}}}
+\frac{\text{$\neg$ checkPrg($code, s$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}}
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$))} \text{:: O, S], [P, A, K, T, t]$\rangle \rightarrow \langle$ [C, O, S],} \text{[P, A, K, T, t]$\rangle$}}}
+\frac{\text{$\neg$ checkCou(\MANAGERS, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$))} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}}
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkBan(K, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: O, S], [P, A, K, T, t]$\rangle \rightarrow \langle$[C, O, S],} \text{[P, A, K, T, t]$\rangle$}}}
+\frac{\text{$\neg$ checkBan(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}}
 \end{equation}
@@
 \begin{equation}{}
-\frac{}{\parbox{4.2in}{\text{$\langle$[C, O, S], [$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running } \\
-\text{${code}$ init ${s}$), t $>$ :: P, A, K, T, t' ]$\rangle \rightarrow \langle$[C, O,($< id$, } \\
-\text{generateHash($id, code, s$, t'), $code >$ :: S)], [P, $<$ (originate contract ${id}$ } \\
-\text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), t' $>$ :: A, updateSucc(K, } \\
-\text{$puk, n, m$), ($<$ generateHash($id, code, s$, t'), $n, code$, } \\
- \text{getStorage($code, s$) $>$) :: T), t' + 1]$\rangle$}}} 
+\frac{}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running } \\
+\text{${code}$ init ${s}$), \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS,($< id$, } \\
+\text{generateHash($id, code, s$, \TIME'), $code >$ :: \CONTRACTS)], [\PENDING, $<$ (originate contract ${id}$ } \\
+\text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
+\text{$puk, n, m$), ($<$ generateHash($id, code, s$, \TIME'), $n, code$, } \\
+ \text{getStorage($code, s$) $>$) :: \CONTRACTORS), \TIME' + 1]$\rangle$}}} 
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{t' - t $\ge$ 60}}{\parbox{4.2in}{\text{[$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$) $>$ } \\
-\text{:: P, A, K, T, t' ] $\rightarrow$[P, A, updateCou(K, $puk$, False), T, t']}}} 
+\frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$) $>$ } \\
+\text{:: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{checkAcc($pkh$, C)  }}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle \rightarrow \langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ }  \\
-\text{fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}}} 
+\frac{\text{checkAcc($pkh$, \ACCOUNTS)  }}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ }  \\
+\text{fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{checkBan(K, $pkh, n, m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ checkPuh(T, $puh$)}
+\frac{\text{checkBan(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPuh(\CONTRACTORS, $puh$)}
 \\
-\text{ $\wedge$ checkArg(T, $puh, s$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}\\
-\text{$\rightarrow$  $\langle$[C, O, S], [($<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), }\\
- \text{generateOph($pkh, puh, s, n, m$, t), t $>$) :: P, A, updateCou(K, $pkh$, True), }\\
-\text{T, t] $\rangle$}}} 
+\text{ $\wedge$ checkArg(\CONTRACTORS, $puh, s$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}\\
+\text{$\rightarrow$  $\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), }\\
+ \text{generateOph($pkh, puh, s, n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), }\\
+\text{\CONTRACTORS, \TIME] $\rangle$}}} 
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$  }\\
-\text{$\rightarrow \langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
+\frac{\text{$\neg$ checkCou(\MANAGERS, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$  }\\
+\text{$\rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkBan(K, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$ }\\
-\text{$\rightarrow \langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
+\frac{\text{$\neg$ checkBan(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$ }\\
+\text{$\rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkPuh(T, $puh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$ }\\
-\text{$\rightarrow \langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
+\frac{\text{$\neg$ checkPuh(\CONTRACTORS, $puh$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$ }\\
+\text{$\rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkArg(T, $puh, s$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}\\
-\text{$\rightarrow \langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
+\frac{\text{$\neg$ checkArg(\CONTRACTORS, $puh, s$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}\\
+\text{$\rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
 \end{equation}
@@
   \begin{array}{l}
-\text{[$<$ transfer $n$ from $puk$ to  $puh$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$ } \\
-\text{[P, $<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), oph, t' $>$ :: A, } \\
-\text{updateSucc(K, puk, '', $n, m$), updateConstr(T, $puh, n$,
-  $s$), $t' + 1$]}
+\text{[$<$ transfer $n$ from $puk$ to  $puh$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$ } \\
+\text{[\PENDING, $<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), oph, \TIME' $>$ :: \ACCEPTED, } \\
+\text{updateSucc(\MANAGERS, puk, '', $n, m$), updateConstr(\CONTRACTORS, $puh, n$,
+  $s$), $\TIME' + 1$]}
   \end{array}
@@
 \begin{equation}{}
-\frac{\text{t' - t $\ge$ 60}}{\parbox{4.2in}{\text{[transfer $n$ from $puk$ to  $puh$ fee $m$, t $>$ :: P, A, K, T, t' ] $\rightarrow$} \\
-\text{[P, A, updatecou(K, $puk$, False), T, t']}}} 
+\frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[transfer $n$ from $puk$ to  $puh$ fee $m$, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$} \\
+\text{[\PENDING, \ACCEPTED, updatecou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
 \end{equation}
@@
 \begin{enumerate}
-    \item Function \verb!checkAcc(pkh, C)! checks whether an account $pkh$ exists in C
+    \item Function \verb!checkAcc(pkh, C)! checks whether an account $pkh$ exists in \ACCOUNTS
     \item Function \verb!checkPub(K, pkh)! checks whether the public key of the public key hash $pkh$ is reveled to the blockchain.
@@
 
-    \item Function \verb!checkId(id, S)! checks whether a contract $id$ does not already exist in S
+    \item Function \verb!checkId(id, S)! checks whether a contract $id$ does not already exist in \CONTRACTS
 
@@
 
-    %\item Function \verb!addContr(S, id, puh, code)! adds a new  contract $< id, puh, code >$  into S
+    %\item Function \verb!addContr(S, id, puh, code)! adds a new  contract $< id, puh, code >$  into \CONTRACTS
 

### 2020-08-25 papers/execution-model/model.tex
rule1

@@
 \subsection{Transfers}
-~\\
+
 Rule 1 [proposal]:
@@
 \begin{equation}{}
-\frac{\text{checkAcc($pkh$, \ACCOUNTS)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$)} ~\\\text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}}
+  \frac{
+    \text{checkAcc($pkh$, \ACCOUNTS)}
+  }{
+    \parbox{4.5in}{\text{$\langle[\ACCOUNTS, \OPERATIONS,
+        \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS,
+        \TIME]\rangle \rightarrow$} \\
+      \text{$\langle [\ACCOUNTS, (\TRANSFER\NTEZ\PKH{\PKH'}\MTEZ)$ ::
+        \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS,
+        \CONTRACTORS, \TIME]$\rangle$}}}  
 \end{equation}

### 2020-08-25 papers/execution-model/model.tex
update

@@
 \maketitle
+\pagestyle{plain}
 
@@
 \begin{equation}{}
-\frac{\text{checkBan(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$}\\
+\frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$}\\
 \text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkBan(\MANAGERS, $pkh, m, n$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
+\frac{\text{$\neg$ checkBal(\MANAGERS, $pkh, m, n$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
 \text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
@@
 \begin{equation}{}
-\frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$} \\
+\frac{\TIME' - \TIME \ge 60}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$} \\
  \hspace*{0cm} \text{[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
@@
 \begin{equation}{}
-\frac{\text{checkBan(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] $\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME] $\rangle$}}}
+\frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] $\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME] $\rangle$}}}
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkBan(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}}
+\frac{\text{$\neg$ checkBal(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}}
 \end{equation}
@@
 \begin{equation}{}
-\frac{\text{checkBan(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPuh(\CONTRACTORS, $puh$)}
+\frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPuh(\CONTRACTORS, $puh$)}
 \\
@@
 \begin{equation}{}
-\frac{\text{$\neg$ checkBan(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$ }\\
+\frac{\text{$\neg$ checkBal(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$ }\\
 \text{$\rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
@@
   \begin{array}{l}
-\text{[$<$ transfer $n$ from $puk$ to  $puh$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$ } \\
-\text{[\PENDING, $<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), oph, \TIME' $>$ :: \ACCEPTED, } \\
-\text{updateSucc(\MANAGERS, puk, '', $n, m$), updateConstr(\CONTRACTORS, $puh, n$,
-  $s$), $\TIME' + 1$]}
+    {[\langle \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \OPH, \TIME
+    \rangle :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']}
+    \rightarrow \\
+    {}[\PENDING, \langle \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \OPH, \TIME' \rangle :: \ACCEPTED,  \\
+    \text{updateSucc(\MANAGERS, \PUK, '', \NTEZ, \MTEZ), updateConstr$(\CONTRACTORS, \PUH, \NTEZ,
+  s)$, $\TIME' + 1$]}
   \end{array}
@@
 \begin{equation}{}
-\frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[transfer $n$ from $puk$ to  $puh$ fee $m$, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$} \\
+\frac{\TIME' - \TIME \ge 60}{\parbox{4.2in}{\text{[transfer $n$ from $puk$ to  $puh$ fee $m$, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$} \\
 \text{[\PENDING, \ACCEPTED, updatecou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
@@
     \item Function \verb!checkPub(K, pkh)! checks whether the public key of the public key hash $pkh$ is reveled to the blockchain.
-    \item Function \verb!checkBan(K, pkh, n, m)! checks whether the balance of the account $pkh$ is greater or equal to $m$ + $n$
-    \item Function \verb!checkCou(K, pkh)! checks whether the current counter of an account $phk$ is used
-    \item Function \verb!updateSuc(K, pkh, pkh', n, m)! updates the balance and the counter of the account $phk$ and the balance of the account $phk'$, where
+    \item Function \verb!checkBal(K, pkh, n, m)! checks whether the balance of the account $pkh$ is greater or equal to $m$ + $n$
+    \item Function \verb!checkCou(K, pkh)! checks whether the current
+      counter of an account $phk$ is unlocked (i.e., its flag is False)
+    \item Function \verb!updateSucc(K, pkh, pkh', n, m)! updates the balance and the counter of the account $phk$ and the balance of the account $phk'$, where
     \begin{itemize}
@@
 
-    \item Function \verb!updateCou(K, puk, b')! updates the counter of the account $phk$, where
+    \item Function \verb!updateCou(K, puk, b')! updates the counter
+      lock of the account $phk$ (True $=$ lockeed, False $=$ unlocked), where
     \begin{itemize}
@@
 \begin{verbatim}
-let rec updateSuc K puk puk' m n =
+let rec updateSucc K puk puk' m n =
   match K with
@@
     if (puk = puk'') then < puk'', bal - (n + m), T > 
-       :: updateSuc (K', puk, puk', n, m)
+       :: updateSucc (K', puk, puk', n, m)
     else if (puk' = puk'') then < puk'', bal + n, cou > :: K'
          else  < puk'', bal, cou > 
-               ::updateSuc (K', puk, puk', n, m)
+               ::updateSucc (K', puk, puk', n, m)
 \end{verbatim}

### 2020-08-25 papers/execution-model/model.tex
partial update

@@
 \usepackage[colorinlistoftodos]{todonotes}
-\newtheorem{mydef}{Definition}
-\newtheorem{mylemma}{Lemma}
-\newtheorem{mytheorem}{Theorem}
-\newtheorem{mypro}{Proposition}
+\usepackage{mathpartir}
 
@@
    The state of a node is a tuple
-   $[\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ where $\ACCOUNTS$ is a set of accounts,
+   $\NODE = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ where $\ACCOUNTS$ is a set of accounts,
    $\OPERATIONS$ a set of operations, and $\CONTRACTS$  a set of contracts. 
@@
 A blockchain system is a pair
-$\langle \mathbf{M}, \mathbf{B} \rangle$ where
+$ \NODE \| \BLOCKCHAIN$ where
 \begin{enumerate}
-\item $\mathbf{M} = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ is the state of a node, and
-\item $\mathbf{B} = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ is the state of a blockchain 
+\item $\NODE = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ is the state of a node, and
+\item $\BLOCKCHAIN = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ is the state of a blockchain 
   such that $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.pkh = c.pkh$
@@
 \section{Rules}
+
+\subsection{Transitions on Nodes}
+\label{sec:transitions-nodes}
+
+Each node has (nondeterministic) rules to propose an operation.
+
+\begin{mathpar}
+  \inferrule[Node-Transfer]
+  {\CHECKACC (\PUK, \ACCOUNTS)
+  }{
+    [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
+    \NodeTrans
+    [\ACCOUNTS, (\TRANSFER\NTEZ\PUK{\PUK'}\MTEZ) :: \OPERATIONS, \CONTRACTS]
+  }
+
+  \inferrule[Node-Originate]
+  {\CHECKACC (\PUK, \ACCOUNTS) \\
+    \CHECKID (\ID, \CONTRACTS)
+  }{
+    [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
+    \NodeTrans \\
+    [\ACCOUNTS, (\ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ) :: \OPERATIONS, \CONTRACTS]
+  }
+
+  \inferrule[Node-System]
+  {\NODE \NodeTrans \NODE'}
+  { {\NODE \| \BLOCKCHAIN} \SystemTrans {\NODE'\| \BLOCKCHAIN}}
+\end{mathpar}
+
 \subsection{Transfers}
@@
 
-\begin{equation}{}
-\frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$}\\
-\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
-\text{$pkh', n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
+\begin{mathpar}
+  \inferrule{
+    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
+    \CHECKCOU (\MANAGERS, \PUK) \\
+    \CHECKPUB (\MANAGERS, \PUK') \\\\
+    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ)
+  }{
+   { [\ACCOUNTS, \OP :: \OPERATIONS, \CONTRACTS] \| [\PENDING,
+     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
+   { [\ACCOUNTS, \OPERATIONS, \CONTRACTS] \|
+     [ \Angle{\OP,\OPH, \TIME}
+     ::\PENDING,
+     \ACCEPTED,
+     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
+     \CONTRACTORS,
+     \TIME]
+   }
+  }
+\end{mathpar}
+% \begin{equation}{}
+% \frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$}\\
+% \text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
+% \text{$pkh', n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME]$\rangle$}}} 
+% \end{equation}
 ~\\
@@
 \begin{equation}{}
-\frac{\text{checkAcc($pkh$, \ACCOUNTS) $\wedge$ checkId($id$, \CONTRACTS)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, (originate contract ${id}$ transferring} \\
+  \frac{\text{checkAcc($pkh$, \ACCOUNTS) $\wedge$ checkId($id$, \CONTRACTS)}}
+  {\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
+        [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle
+        \rightarrow \langle$[\ACCOUNTS, 
+        (originate contract ${id}$ transferring} \\
   \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
@@
 \begin{equation}{}
-\frac{\TIME' - \TIME \ge 60}{\parbox{4.2in}{\text{[transfer $n$ from $puk$ to  $puh$ fee $m$, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$} \\
-\text{[\PENDING, \ACCEPTED, updatecou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
+  \frac{\TIME' - \TIME \ge 60}{
+    \begin{array}{l}
+      {}[\langle\TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \TIME\rangle ::
+      \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ]
+      \rightarrow \\
+      {}[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE), \CONTRACTORS, \TIME']
+    \end{array}
+    }
 \end{equation}

### 2020-09-02 meeting-notes/20200812-expose.tex
specified some tasks

@@
 unit of computation and each unit of storage used by an algorithm must be paid for. To
-avoid this cost, users might perform some computation offchain and submit the result as a
-parameter to a contract. Typically, such a computation asserts certain properties of the
+avoid this cost, an application might perform some computation away from the blockchain
+(i.e., off-chain) and submit the result as a parameter to a contract on the
+blockchain. Typically, such a computation asserts certain properties of the 
 submitted parameter.
@@
 However, this approach raises the issue that on the one hand the contract should take
-advantage of the offchain computation and just assume that the submitted parameter has
-these properties, but on the other hand, the offchain computation might be wrong and
+advantage of the offchain computation and assume that the submitted parameter has
+these properties, but on the other hand, the off-chain computation might be wrong and
 submit illegal parameters. So, we need a mechanism that checks the validity of the
@@
 \end{lstlisting}
-We express the assumption with an explicit assertion.
+This assumption can be expressed with an explicit assertion in predicate logic.
 \begin{displaymath}
@@
 \end{displaymath}
-We could test this assumption with a loop in the contract, but the test would take
-$O(\sqrt p)$ time (assuming constant time for computing the modulus) and thus produce cost
-depending on $p$ accordingly. 
+To test the validity of this assumption requires a loop in the contract, but the test would take
+$O(\sqrt p)$ time (assuming constant time for computing the remainder) and thus produce extra cost
+linear in $\sqrt p$ accordingly. 
 However, we could do better by recruiting the validators of the contract for a distributed
 effort to find a counterexample. To this end, we consider the negation of the assertion.
-\begin{displaymath}
+\begin{gather}\label{eq:4}
   (\exists n) (2 \le n \le \sqrt p) \wedge (p \mathbin{\%} n) = 0
-\end{displaymath}
+\end{gather}
 This assertion can be checked pointwise by having each validator independently choose a
@@
 In this scenario, each validator only needs to be paid to generate a random number and
-perform a division, which is a constant cost independant from $p$.
+perform a division, which is a constant cost independent from $p$.
 
@@
 \end{gather}
-While we can check this contract in $O(1)$ time, the constant factor is large! So we
+While we can check this contract in $O(1)$ time, the constant factor is big! So we
 consider its negation.
@@
 \end{displaymath}
-Again, we can have the validators generate a random number $k$ and check the
-condition. If it is true, then the validator found a counterexample for the sortedness
-of the array. Otherwise, the validator relies on the others.
+Again, we can have every validator generate a random number $k$. If the
+condition is true for such $k$, then the validator found a counterexample for the sortedness
+of the array. Otherwise, the validator relies on the other validators to check
+different numbers.
 
-Let's assume the array is unsorted only at position $0$, the size of the array is $n$,
+To obtain an estimate of the number of validators needed to find a counterexample with
+high probibility, 
+let's assume the array is unsorted only at position $0$, the size of the array is $n$,
 and the number of validators is $m$. Each validator independently has a probability of
-$1/n$ to detect the problem. The probability that no validator checks at
+$1/n$ to detect the problem and thus probability $\frac{n-1} n$ not to detect the
+problem. Hence, if we assume that each $k$ is chosen independenty from a uniform distribution,
+the probability that no validator checks at
 position $0$ converges to $0$ as the number of validators approaches infinity.
@@
 \begin{changethis}
-  Tezos specific remarks, here the number of validators is really small compared to
+  Tezos specific remarks: here the number of validators is really small compared to
   Bitcoin or Ethereum
@@
 
+\section{Tasks}
+\label{sec:tasks}
+
+\subsection{Offline Design}
+\label{sec:offline-design}
+
+\begin{itemize}
+\item Identify a set of logical formulas that are amenable to the kind of checking
+  described above.
+\item Formalize the cost incurred by checking a formula.
+\item Extend the contract language with assertions stating these logical formulas.
+\item Implement the transformation: negation of the formula followed by transformation
+  of existentials to picking a random value.
+
+  The random choice should be performed in a ``clever'' way that does not waste too
+  much effort. For a wasteful example, consider~\eqref{eq:2}:
+  \begin{gather*}
+    (\exists j, k ) (0\le j< k < |a|) \wedge a[j] > a[k]
+  \end{gather*}
+  In the worst case, we would generate two arbitrary non-negative integers $j$ and $k$
+  and then check the predicate. However, the predicate $(0\le j< k < |a|)$ will fail
+  almost always, so we do not get to test the interesting part of the predicate
+  $a[j]>a[k]$.
+
+  In the best case, the generated testing code would be equivalent to the following code fragment
+  in Python
+\begin{lstlisting}[language=Python]
+def exists_counterexample (a : list) -> bool:
+  if len(a) < 2: return False
+  j = random.randint (0, len(a) - 2)
+  k = random.randint (j+1, len(a) - 1)
+  return a[j] > a[k]
+\end{lstlisting}
+
+  As another, simpler example consider~\eqref{eq:4} (checking for prime numbers)
+\begin{lstlisting}[language=Python]
+def exists_counterexample (p : int) -> bool:
+  r = math.isqrt (p)
+  if r < 2: return False
+  n = random.randint (2, r)
+  return (p % n) == 0
+\end{lstlisting}
+
+  Observe that in each case there is a test to eliminate trivial cases, which avoids
+  illegal invocations of \lstinline/randint/.
+\item Each test function should come with a formula that gives an estimate of
+  its effectiveness, i.e., how many times do we have to run the test to find a
+  counterexample with a given probability $p$. Ideally, the formula returns a lower
+  bound on the number of tests for any $p$.
+\end{itemize}
+
+\subsection{Protocol Design}
+\label{sec:protocol-design}
+
 \end{document}

### 2020-09-08 meeting-notes/20200812-expose.tex
update

@@
   \begin{tcolorbox}[breakable,notitle,boxrule=0pt,colback=blue!20,colframe=blue!20]}{%
+  \end{tcolorbox}}
+
+\newenvironment{ethereum}{%
+  \begin{tcolorbox}[breakable,notitle,boxrule=0pt,colback=red!20,colframe=red!20]}{%
   \end{tcolorbox}}
@@
 
-\section{Further Thoughts}
-\label{sec:further-thoughts}
-
-There may be an alternative way of implementing this scheme without modifying the
-protocol, but instead adding instructions to the virtual machine. One instruction would
-generate a random number (EVM uses 512 bit unsigned integer IIRC), the other would
-raise an overriding failure. Ideally, once a counterexample has been found, this
-counterexample is broadcast to the network where it can be verified by further nodes.
-But this broadcast and the reaction to this broadcast requires an update of the
-protocol: all receivers of the broadcast will check the counterexample and revert the
-transaction. This probably means that a transaction using this feature has to wait for
-a couple of cycles in the transaction pool until the node feels safe to include the
-transaction in a block.
-
-\begin{changethis}
-  Tezos specific remarks: here the number of validators is really small compared to
-  Bitcoin or Ethereum
-  \begin{itemize}
-  \item maybe we need to propose and validate the same block multiple times before it
-    gets accepted. E.g, a transaction containing this feature is only accepted if it is
-    revalidated $n$ times.
-  \item Extra validators only for this kind of transaction.
-  \end{itemize}
-\end{changethis}
-This approach poses the danger of a DOS attack. Someone could post a false
-counterexample, which does not really lead to a failure. If everyone switches to check
-this proposed counterexample instead of generating a random number, then the real
-problem may remain hidden. So, there has to be a component in the protocol that
-penalizes someone who broadcasts a false counterexample. Moreover, not all validators
-should switch to recheck a proposed counterexample; or they could check it in addition
-to their own random check.
-
-The interesting assertion formulas are those with prenex universal
-quantification. Negation turns them into prenex existential quantification. But it
-would be ineffective to generate a random integer and then check that it falls in the
-interesting range (e.g., $2\le n \le \sqrt p$ and $0\le k< n-1$). Rather, the formula
-needs to be analzed and the random generator should be restricted to only generate
-interesting values.
-
-It would not be significantly more expensive to have every validator perform a
-predetermined finite number of checks for each assertion.
-
-What is the minimum number $m$ of validators such that the probability of spotting an
-error is less than a given threshold $q$?
-
-Instead of using random numbers, is there a way to coordinate a systematic exploration
-of the iteration space? (Is this at all necessary?)
-
-One could also check properties of the values stored by the contract.
-
-Connections to random testing?
-
 In Dafny (citation) \url{https://rise4fun.com/Dafny/tutorialcontent/guide#h29} you can
@@
 \begin{itemize}
-\item Identify a set of logical formulas that are amenable to the kind of checking
-  described above.
+\item Formally define a set of logical formulas that are amenable to the kind of checking
+  described above. In a first approximation, the interesting assertion formulas seem to
+  be those with prenex universal quantification. 
+\item Collect examples for interesting formulas.
 \item Formalize the cost incurred by checking a formula.
@@
 \item Implement the transformation: negation of the formula followed by transformation
-  of existentials to picking a random value.
+  of existentials to picking a random value. For initial experiments, the target of the
+  translation can be any language; later on, the target has to be a language hosted on
+  the blockchain.
+
+  Negation turns prenex universial quantification into prenex existential quantification. But it
+  would be ineffective to generate a random integer and then check that it falls in the
+  interesting range (e.g., $2\le n \le \sqrt p$ and $0\le k< n-1$). Rather, the formula
+  needs to be analzed and the random generator should be restricted to only generate
+  interesting values.
 
@@
   bound on the number of tests for any $p$.
+\item What is the minimum number $m$ of validators such that the probability of
+  spotting an error is less than a given threshold $q$?
+\item Instead of using random numbers, is there a way to coordinate a systematic
+  exploration of the iteration space? (Is this at all necessary?)
+\item What are the connections to random testing? 
+\item I think this scheme implements a Bloom filter, globally? We are testing whether a value is a
+  member of an implicitly given set. We may accept a value even if it does not belong
+  to the set, but if we reject a value, it definitely does not belong to the set.
 \end{itemize}
 
+\subsection{Blockchain-Specific Tasks}
+\label{sec:blockch-spec-tasks}
+
+\begin{ethereum}
+  Ethereum-specific remarks:
+  Implementing this scheme requires adding instructions to the virtual machine. One
+  instruction would generate a random number (EVM uses 512 bit unsigned integer IIRC),
+  the other would raise an overriding failure. This failure will have to indicate that
+  validation of the contract fails.
+\end{ethereum}
+
+\begin{itemize}
+\item The VM interpreter needs to be extended with these instructions.
+\item The translation (of formulas) needs to retargetted to VM code. This may have to
+  be hacked into the compiler.
+\item The translation has to be amended so that counterexamples can also be checked.
+\item (extension) Every validator could perform a predetermined finite number of checks for each
+  assertion. This would not be significantly more expensive. Moreover, the number of
+  checks could be set individually depending on the contract and on the size of the
+  input.
+\item (extension) One could also check properties of the values stored with the contract.
+\end{itemize}
 \subsection{Protocol Design}
@@
 
+\begin{changethis}
+  Tezos specific remarks: here the number of validators is really small compared to
+  Bitcoin or Ethereum
+  \begin{itemize}
+  \item Maybe we need to propose and validate the same block multiple times before it
+    gets accepted. E.g, a transaction containing this feature is only accepted if it is
+    revalidated $n$ times.
+  \item Extra validators only for this kind of transaction.
+  \item Maybe each validator needs to conduct multiple test runs.
+  \item Maybe test runs need to be coordinated
+  \end{itemize}
+\end{changethis}
+
+\begin{itemize}
+\item   Once a counterexample has been found,
+  this counterexample is broadcast to the network where it can be verified by further
+  nodes.  I think this broadcast and the reaction to this broadcast requires an update of
+  the protocol: all receivers of the broadcast will check the counterexample and revert
+  the transaction. 
+\item A transaction using counterexamples has to
+  wait for a couple of cycles in the transaction pool until the node feels safe to
+  include the transaction in a block.
+  The number of cycles to wait depends on the contract and on the size of the input.
+  So that number should be variable.
+\item (low priority) This approach poses the danger of a DOS attack. Someone could post a false
+  counterexample, which does not really lead to a failure. If everyone switches to
+  check this proposed counterexample instead of generating a random number, then the
+  real problem may remain hidden. So, there has to be a component in the protocol that
+  penalizes someone who broadcasts a false counterexample. Moreover, not all validators
+  should switch to recheck a proposed counterexample; or they could check it in
+  addition to their own random check.
+
+  More precisely:
+  \begin{itemize}
+  \item Every validator must run at least one (round of) random tests.  
+  \item If it receives a proposed counterexample, it must check the counterexample,
+    too.
+  \item It remains to investigate a countermeasure for nodes generating a flood of
+    false counterexamples, which would keep every validator busy. Perhaps checking of
+    the counterexample should also be done probabilistically.
+  \end{itemize}
+\end{itemize}
+
+\section{Rejected Ideas}
+\label{sec:rejected-ideas}
+
+This section contains some ideas that we discussed but rejected. Feel free to resurrect
+any of this if you find new arguments.
+
+\begin{itemize}
+\item Q: How about instead of generating and checking random number, it could
+  store a Bloom filter for already checked number, so a validator can
+  generate a random number and check it if it is rejected by Bloom filter,
+  but this also happen that there will be some number never get checked
+  because it is rejected by Bloom filter, but actually never been checked.
+
+  A: This is not a good idea for several reasons.
+  \begin{enumerate}
+  \item It's not clear where we should store the Bloom filter. It has to be available
+    everywhere, so it has to be stored on the blockchain.
+  \item If it's on the blockchain, then it serializes the tests for counterexamples:
+    the point of the scheme is to test many random values concurrently without
+    interference.
+  \item The Bloom filter errs in the wrong direction. It may accept elements that have
+    not been added before, which means that elements that should be tested are not. We
+    would need a co-Bloom filter that errs in the other direction: it should reject all
+    elements that have not been added, and it may also reject elements that have been added.
+  \end{enumerate}
+
+\end{itemize}
+
 \end{document}

### 2020-10-04 meeting-notes/20200928-expose.tex

--- 2020-09-08 meeting-notes/20200812-expose.tex
@@
 \item Formalize the cost incurred by checking a formula.
-\item Extend the contract language with assertions stating these logical formulas.
-\item Implement the transformation: negation of the formula followed by transformation
-  of existentials to picking a random value. For initial experiments, the target of the
-  translation can be any language; later on, the target has to be a language hosted on
-  the blockchain.
-
+\item Extend the contract language with assertions stating these logical
+  formulas. There are several approaches to perform this extension.
+  \begin{enumerate}
+  \item (Solidity) Extend the syntax of the assert statement. Requires an extension of
+    the compiler.
+  \item (Tezos/Solidity) The assertion is stated in its own syntax in a file separate from the
+    contract implementation. Requires a dedicated compiler of assertions to
+    Michelson. The generated code is either combined with the contract implementation
+    or stored separately on the blockchain. Several entry points may lead to difficulties.
+  \end{enumerate}
+\item Implement the transformation in two steps:
+  \begin{enumerate}
+  \item negation of the formula
+  \item followed by the translation of an existentially quantified formula to code that picks a
+    random value subject to predicate. For initial experiments, the target of the
+    translation can be any programming 
+    language; later on, the target has to be a language hosted on the blockchain
+    (e.g. Michelson or Solidity). These languages have to be extended with a random
+    generator. There has to be a special execution mode for ``challenge contracts''
+    that search for a counterexample of an assertion.
+  \end{enumerate}
   Negation turns prenex universial quantification into prenex existential quantification. But it
@@
 \begin{itemize}
+\item (Tezos) Proposal for an architecture. The assertion for contract C gets compiled
+  to a separate contract A(C). A(C) takes C's argument x and attempts to challenge 
+  the assertion by finding a counterexample. Given x, we determine a number n of
+  ``probation cycles'' during which the net attempts to find a counterexample. The
+  injecting node broadcasts A(C)(x) for n cycles. If A(C)(x) finishes successfully,
+  this execution vanishes (as no counterexample has been found). If A(C)(x) finds a
+  counterexample, it records the counterexample along with the data to check it on the
+  blockchain as in A(C,x,y) where it can be validated by the net as usual.
+  After n cycles the injecting node broadcasts C(x), which is processed as
+  usual. However, a valid blockchain either contains C(x) or A(C,x,y), but not both. It
+  is an error to attempt to enter C(x) after A(C,x,y) is on the chain, and vice versa.
+
+  It needs to be investigated which aspects of the protocol need to be
+  adapted. Moreover, A(C,x) must execute in a different mode that enables the random
+  instruction. This instruction is not available in the default execution mode.
 \item   Once a counterexample has been found,
@@
   the transaction. 
-\item A transaction using counterexamples has to
+\item (see above for a revised approach) A transaction using counterexamples has to
   wait for a couple of cycles in the transaction pool until the node feels safe to

### 2020-10-12 papers/execution-model/model.tex
revising rules

@@
 \usepackage{mathpartir}
+\usepackage{fixme}
 
@@
 When an operation is injected in a node, it enters a \emph{pending pool}
-(and is called a pending operation). 
+(and is called a \emph{pending operation}). 
  \begin{definition}[Pending operation]
 A pending operation is a tuple  $\langle  \OP, \OPH, \TIME
-\rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash
+\rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash,
 and $\TIME$ is the time when the operation was injected. 
@@
 An accepted operation  is a tuple $\langle  \OP, \OPH, \TIME \rangle
-$, where $\OP$ is an operation, $\OPH$ is the operation hash and
+$, where $\OP$ is an operation, $\OPH$ is the operation hash, and
 $\TIME$ is the time when it was included in the blockchain. 
@@
   of accepted operations, $\MANAGERS$ is a set of managers,
-  $\CONTRACTORS$ is a set of contractors, and $\TIME$ is the current time of the blockchain. 
+  $\CONTRACTORS$ is a set of contractors, and $\TIME$ is the current time. 
 \end{definition}
@@
 $ \NODE \| \BLOCKCHAIN$ where
+\fxnote[inline]{Should the model contain multiple nodes?}
 \begin{enumerate}
@@
 \item $\BLOCKCHAIN = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ is the state of a blockchain 
-  such that $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.pkh = c.pkh$
-  and $\forall s \in \CONTRACTS \implies \exists p \in \CONTRACTORS, s.puh = p.puh$.
+  such that $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.\PKH = c.\PKH$
+  and $\forall s \in \CONTRACTS \implies \exists p \in \CONTRACTORS, s.\PUH = p.\PUH$.
 \end{enumerate}
@@
 
-Rule 1 [proposal]:
+% Rule 1 [proposal]:
+%
+% \begin{mathpar}
+%   \inferrule[Xfer-Propose]{
+%     \CHECKACC (\PKH, \ACCOUNTS)
+%   }{
+% \langle[\ACCOUNTS, \OPERATIONS,
+%         \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS,
+%         \TIME]\rangle \rightarrow \\
+%         \langle [\ACCOUNTS, (\TRANSFER\NTEZ\PKH{\PKH'}\MTEZ) ::
+%         \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS,
+%         \CONTRACTORS, \TIME]\rangle      }
+% \end{mathpar}
 
-\begin{equation}{}
-  \frac{
-    \text{checkAcc($pkh$, \ACCOUNTS)}
-  }{
-    \parbox{4.5in}{\text{$\langle[\ACCOUNTS, \OPERATIONS,
-        \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS,
-        \TIME]\rangle \rightarrow$} \\
-      \text{$\langle [\ACCOUNTS, (\TRANSFER\NTEZ\PKH{\PKH'}\MTEZ)$ ::
-        \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS,
-        \CONTRACTORS, \TIME]$\rangle$}}}  
-\end{equation}
-~\\
-~\\
 Rule 2 [injected]:
@@
 Rule 6 [included]:
-\begin{equation}{}
-\frac{}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$ } \\
- \text{[\PENDING, $<$ transfer $n$ from  $puk$ to $puk'$ fee $m$, oph, \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
-\text{$puk, puk', n, m$), \CONTRACTORS, \TIME' + 1]}}} 
-\end{equation}
-~\\
+\begin{mathpar}
+  \inferrule[Block-Accept]{
+    % \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+    \TIME'-\TIME < 60
+  }{
+    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
+      \CONTRACTORS, \TIME']} \rightarrow 
+    {[\PENDING, \Angle{\OP,\OPH,\TIME'} :: \ACCEPTED, \MANAGERS,
+      \CONTRACTORS, \TIME'+1]}
+  }
+\end{mathpar}
 Rule 7 [timeout]:
-\begin{equation}{}
-\frac{\TIME' - \TIME \ge 60}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$} \\
- \hspace*{0cm} \text{[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
-\end{equation}
+\begin{mathpar}
+  \inferrule[Block-Timeout]{
+    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+    \TIME'-\TIME \ge 60
+  }{
+    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
+      \CONTRACTORS, \TIME']} \rightarrow 
+    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
+      \CONTRACTORS, \TIME']}
+  }
+\end{mathpar}
 
@@
 ~\\
-Rule 1 [proposal]:
+% Rule 1 [proposal]:
 
-\begin{equation}{}
-  \frac{\text{checkAcc($pkh$, \ACCOUNTS) $\wedge$ checkId($id$, \CONTRACTS)}}
-  {\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
-        [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle
-        \rightarrow \langle$[\ACCOUNTS, 
-        (originate contract ${id}$ transferring} \\
-  \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
-~\\
-~\\
+% \begin{equation}{}
+%   \frac{\text{checkAcc($pkh$, \ACCOUNTS) $\wedge$ checkId($id$, \CONTRACTS)}}
+%   {\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
+%         [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle
+%         \rightarrow \langle$[\ACCOUNTS, 
+%         (originate contract ${id}$ transferring} \\
+%   \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
+% \end{equation}
+% ~\\
+% ~\\
 Rule 2 [injected]:
 
-\begin{equation}{}
-\frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] $\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME] $\rangle$}}}
-\end{equation}
+\begin{mathpar}
+  \inferrule[Block-Originate]{
+    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
+    \CHECKCOU (\MANAGERS, \PUK) \\
+    \CHECKPRG (\CODE, \STRING) \\\\
+    \ORIG = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ 
+  }{
+    \Angle{[
+      \ACCOUNTS, \ORIG :: \OPERATIONS, \CONTRACTS
+      ], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]} \to \\
+    \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
+      [\ORIG :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]}
+  }
+\end{mathpar}
+% \begin{equation}{}
+% \frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] $\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME] $\rangle$}}}
+% \end{equation}
 ~\\

### 2020-10-20 meeting-notes/20200928-expose.tex
examples for syntax

@@
 \usepackage{url}
+
+\usepackage{hyperref}
 
@@
 This assumption can be expressed with an explicit assertion in predicate logic.
-\begin{displaymath}
+\begin{gather}\label{eq:5}
   (\forall n) (2 \le n \le \sqrt p) \Rightarrow (p \mathbin{\%} n) \ne 0
-\end{displaymath}
+\end{gather}
 To test the validity of this assumption requires a loop in the contract, but the test would take
@@
   be those with prenex universal quantification.
+
+  In a first iteration, we want to restrict ourselves to formulas of
+  predicate logic with prenex universal quantification only.
+  \begin{align*}
+    t &::= \text{primitive types like int, bool, string, \dots} \\
+    \Theta &::= \Phi \mid \forall (x:t) \Theta \\
+    \Phi,\Psi &::= \neg\Phi \mid \Phi\wedge\Psi \mid \Phi\vee\Psi \mid
+                M \rho N \\
+    \rho &::= < \mid > \mid \le \mid \ge \mid = \mid \ne \mid \dots \\
+    M, N &::= x \mid c \mid M \oplus N  \mid f (\overline M) \\
+    \oplus &::= +\mid -\mid * \mid / \mid \% \mid \dots \\
+    c &::= \text{constants: numbers, strings, etc} \\
+    f &::= \text{operations (existing in the blockchain VM)}
+  \end{align*}
+  Later, we might consider existential quantification and user-defined
+  functions (for example, sqrt, length of a list, access list element
+  are not predefined by the VM and have to be implemented. The list
+  operations would be really good to have, though). See
+  Section~\ref{sec:suggestions-tezos} for suggestions for a concrete syntax.
 \item Collect examples for interesting formulas.
@@
 
+\section{Suggestions (Tezos)}
+\label{sec:suggestions-tezos}
+
+The syntax for assertions should be chosen to be similar to OCaml.
+A proposal for the assertion in \eqref{eq:5} could be
+\begin{lstlisting}[language=caml]
+parameter (_, (_, p)) =
+  forall (n : int)
+    if (2 <= n && n <= p / 2)
+      p % n <> 0
+\end{lstlisting}
+Such a parameter phrase may occur multiple times. Its single argument
+is a pattern that matches the contract's argument. The type of the
+pattern variables (here just \lstinline/p/) is determined from the code of the
+contract.
+
+Multiple parameter phrases can be used to state assertion for
+contracts with multiple entry points. In Tezos/Michelson, entry points are
+modeled by having a sum type as parameter type. For example, a
+contract with two entry points can be equipped with assertions as
+follows.
+\begin{lstlisting}[language=caml]
+parameter (Left x) =
+  0 < x && x < 100
+
+parameter (Right (a, b)) =
+  exists (c : int)
+    if (0 < c && c <= a + b)
+      a*a + b*b = c*c
+\end{lstlisting}
+BTW, this is an example for a useful contract with an existential!
+
+The idea would be to have two files with the same basename, but
+different extensions. One file contains the Michelson code, the other
+the assertion.
+
 \section{Rejected Ideas}

### 2020-10-20 papers/execution-model/model.tex
further consolidation

@@
 \section{Definitions}
-\begin{definition}[Set]
+\begin{definition}%[Set]
 Let $\mathbf{Elt}$ be the set of (concrete) elements. Let $\emptyset$ be an empty set and $\mathbf{e}$ $\in$  $\mathbf{Elt}$. A set of elements is expressed as the following syntax:
@@
 
-\begin{definition}[Account]
-An account is a tuple $\langle \ALS, \PAK, \PUK, \PKH \rangle $, where $\ALS$ is the alias of the account, $\PAK$ is its private key, $\PUK$ is its public key and $\PKH$ is its public key hash . 
+\begin{definition}%[Account]
+An \emph{account} is a tuple $\langle \ALS, \PAK, \PUK, \PKH \rangle $, where $\ALS$ is the alias of the account, $\PAK$ is its private key, $\PUK$ is its public key and $\PKH$ is its public key hash .
 \end{definition}
 
-\begin{definition}[Contract]
-An contract is a tuple $\langle  \ALS, \PUH, \CODE \rangle $, where
+\begin{definition}%[Contract]
+An \emph{contract} is a tuple $\langle  \ALS, \PUH, \CODE \rangle $, where
 $\ALS$ is the alias of the contract, $\PUH$ is its public hash, and
@@
 
-\begin{definition}[Manager]
-A manager manages a single account. It is represented by a
+\begin{definition}%[Manager]
+A \emph{manager} manages a single account. It is represented by a
 tuple $\langle  \PUK, \PKH, \BAL, \COU \rangle $, where  $\PUK$ is the
@@
 
-\begin{definition}[Contractor]
-  A contractor manages a smart contract. It is
+\begin{definition}%[Contractor]
+  A \emph{contractor} manages a smart contract. It is
   represented by a tuple
@@
 
-\begin{definition}[Operation]
-  Operations are defined by the following grammar:
+\begin{definition}%[Operation]
+  \emph{Operations} are defined by the following grammar:
   \begin{align*}
@@
 
-\begin{definition}[Query]
-Queries are defined by the following grammar:
+\begin{definition}%[Query]
+A \emph{query} is defined by the following grammar:
 \begin{align*}
@@
 \end{definition}
- \begin{definition}[State of a node]
-   The state of a node is a tuple
+ \begin{definition}%[State of a node]
+   The \emph{state of a node} is a tuple
    $\NODE = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ where $\ACCOUNTS$ is a set of accounts,
@@
 (and is called a \emph{pending operation}). 
- \begin{definition}[Pending operation]
-A pending operation is a tuple  $\langle  \OP, \OPH, \TIME
+ \begin{definition}%[Pending operation]
+A \emph{pending operation} is a tuple  $\langle  \OP, \OPH, \TIME
 \rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash,
@@
 %Let \textit{P} is the set of pending operations.
- \begin{definition}[Accepted operation]
-An accepted operation  is a tuple $\langle  \OP, \OPH, \TIME \rangle
+ \begin{definition}%[Accepted operation]
+An \emph{accepted operation}  is a tuple $\langle  \OP, \OPH, \TIME \rangle
 $, where $\OP$ is an operation, $\OPH$ is the operation hash, and
@@
 
-\begin{definition}[Blockchain]
-  The state of a blockchain is a tuple
+\begin{definition}%[Blockchain]
+  The \emph{state of a blockchain} is a tuple
   $[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ where
@@
 
-\begin{definition}[Blockchain system]
-A blockchain system is a pair
+\begin{definition}%[Blockchain system]
+A \emph{blockchain configuration} is a pair
 $ \NODE \| \BLOCKCHAIN$ where
@@
 
+\clearpage{}
 \section{Rules}
@@
   \inferrule[Node-Transfer]
-  {\CHECKACC (\PUK, \ACCOUNTS)
+  {\CHECKACC (\PUK, \ACCOUNTS) \\
+    \OP = \TRANSFER[\STRING]\NTEZ\PUK{\PUK'}\MTEZ
   }{
@@
     \NodeTrans
-    [\ACCOUNTS, (\TRANSFER\NTEZ\PUK{\PUK'}\MTEZ) :: \OPERATIONS, \CONTRACTS]
+    [\ACCOUNTS, \OP:: \OPERATIONS, \CONTRACTS]
   }
@@
   {\CHECKACC (\PUK, \ACCOUNTS) \\
-    \CHECKID (\ID, \CONTRACTS)
+    \CHECKID (\ID, \CONTRACTS) \\
+    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ
   }{
     [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
-    \NodeTrans \\
-    [\ACCOUNTS, (\ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ) :: \OPERATIONS, \CONTRACTS]
+    \NodeTrans 
+    [\ACCOUNTS, \OP :: \OPERATIONS, \CONTRACTS]
   }
@@
   { {\NODE \| \BLOCKCHAIN} \SystemTrans {\NODE'\| \BLOCKCHAIN}}
+
+  \inferrule[Block-System]
+  {\BLOCKCHAIN \BlockTrans \BLOCKCHAIN'}
+  { {\NODE \| \BLOCKCHAIN} \SystemTrans {\NODE\| \BLOCKCHAIN'}}
 \end{mathpar}
@@
     {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
-      \CONTRACTORS, \TIME']} \rightarrow 
+      \CONTRACTORS, \TIME']}
+    \BlockTrans 
     {[\PENDING, \Angle{\OP,\OPH,\TIME'} :: \ACCEPTED, \MANAGERS,
@@
     {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
-      \CONTRACTORS, \TIME']} \rightarrow 
+      \CONTRACTORS, \TIME']}
+    \BlockTrans
     {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
@@
     \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
-      [\ORIG :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]}
+      [\Angle{\ORIG,\TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]}
   }
@@
 Rule 6 [included]:
-\begin{equation}{}
-\frac{}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running } \\
-\text{${code}$ init ${s}$), \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS,($< id$, } \\
-\text{generateHash($id, code, s$, \TIME'), $code >$ :: \CONTRACTS)], [\PENDING, $<$ (originate contract ${id}$ } \\
-\text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
-\text{$puk, n, m$), ($<$ generateHash($id, code, s$, \TIME'), $n, code$, } \\
- \text{getStorage($code, s$) $>$) :: \CONTRACTORS), \TIME' + 1]$\rangle$}}} 
-\end{equation}
+\begin{mathpar}
+  \inferrule[Block-Accept]{
+    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ \\
+    \OPH = \GENERATEHASH (\ID,\CODE,\STRING,\TIME') \\
+    \TIME'-\TIME < 60
+  }{
+    \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
+      [\Angle{\OP,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']}
+    \SystemTrans \\
+    \langle
+      [\ACCOUNTS, \OPERATIONS, \Angle{\ID, \OPH, \CODE} ::\CONTRACTS],
+      \\
+      [\PENDING, \Angle{\OP, \TIME'} :: \ACCEPTED, \UPDATESUCC
+      (\MANAGERS, \PUK, \NTEZ, \MTEZ), \Angle{\OPH, \GETSTORAGE
+      (\CODE,\STRING)} :: \CONTRACTORS, \TIME'+1]
+    \rangle
+  }
+\end{mathpar}
+
+% \begin{equation}{}
+% \frac{}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS,
+% \CONTRACTS], [$<$ (originate contract ${id}$ transferring  ${n}$
+% from ${pkh}$ running } \\ 
+% \text{${code}$ init ${s}$), \TIME $>$ :: \PENDING, \ACCEPTED,
+% \MANAGERS, \CONTRACTORS, \TIME' ]$\rangle \rightarrow
+% \langle$[\ACCOUNTS, \OPERATIONS,($< id$, } \\ 
+% \text{generateHash($id, code, s$, \TIME'), $code >$ :: \CONTRACTS)],
+%  [\PENDING, $<$ (originate contract ${id}$ } \\
+% \text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
+% \text{$puk, n, m$), ($<$ generateHash($id, code, s$, \TIME'), $n, code$, } \\
+%  \text{getStorage($code, s$) $>$) :: \CONTRACTORS), \TIME' + 1]$\rangle$}}} 
+% \end{equation}
 ~\\
 Rule 7 [timeout]:
-\begin{equation}{}
-\frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$) $>$ } \\
-\text{:: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
-\end{equation}
+\begin{mathpar}
+  \inferrule[Block-Timeout]{
+    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ \\
+    \TIME'-\TIME \ge 60
+}{
+    %\Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
+      [\Angle{\OP,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
+      \CONTRACTORS, \TIME']
+    %}
+    \BlockTrans
+    % \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
+      [\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\FALSE), \CONTRACTORS, \TIME']
+    % }
+}
+\end{mathpar}
+% \begin{equation}{}
+% \frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[$<$
+% (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running
+% ${code}$ init ${s}$) $>$ } \\ 
+% \text{:: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ]
+% $\rightarrow$[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$,
+% False), \CONTRACTORS, \TIME']}}}  
+% \end{equation}
 ~\\

### 2020-10-20 papers/contract-modules/modules.tex
new paper

--- 2020-08-25 papers/execution-model/model.tex
@@
 \usepackage{mathpartir}
+\usepackage{fixme}
 
-\input{macros}
-
-\title{Blockchain System}
-
+\title{Contract Modules}
 \author{}
@@
 
-\section{Definitions}
-\begin{definition}[Set]
-Let $\mathbf{Elt}$ be the set of (concrete) elements. Let $\emptyset$ be an empty set and $\mathbf{e}$ $\in$  $\mathbf{Elt}$. A set of elements is expressed as the following syntax:
-\\
-$\mathbf{s} :: = \emptyset \mid \mathbf{e} \mid \mathbf{s :: s}$
-\end{definition}
-
-\begin{definition}[Account]
-An account is a tuple $\langle \ALS, \PAK, \PUK, \PKH \rangle $, where $\ALS$ is the alias of the account, $\PAK$ is its private key, $\PUK$ is its public key and $\PKH$ is its public key hash . 
-\end{definition}
-
-\begin{definition}[Contract]
-An contract is a tuple $\langle  \ALS, \PUH, \CODE \rangle $, where
-$\ALS$ is the alias of the contract, $\PUH$ is its public hash, and
-$\CODE$ is the code of the contract. 
-\end{definition}
-
-\begin{definition}[Manager]
-A manager manages a single account. It is represented by a
-tuple $\langle  \PUK, \PKH, \BAL, \COU \rangle $, where  $\PUK$ is the
-public key of an account, $\PKH$ is its public key hash, $\BAL$ is its
-balance and $\COU$ is its counter whose form is a pair $(n, b)$, where $n$ is a natural number and ${b}$
-is a boolean value.  
-\end{definition}
-
-\begin{definition}[Contractor]
-  A contractor manages a smart contract. It is
-  represented by a tuple
-  $\langle \PUH, \BAL, \CODE, \STORAGE \rangle $, where $\PUH$ is the
-  public key hash of the contract, $\BAL$ is its current balance, $\CODE$ is its
-  code, and $\STORAGE$ is its current storage.
-\end{definition}
-
-\begin{definition}[Operation]
-  Operations are defined by the following grammar:
-  \begin{align*}
-    \OP &::= \TRANSFER[\STRING]\NTEZ\PKH{\PKH'}\MTEZ
-    \\&\mid \ORIGINATE\ID\NTEZ\PKH\CODE\STRING\MTEZ
-    % \\&\mid transfer $\mathbf{n}$ from $\PKH$ to  $\PUH$ arg $\mathbf{s}$ fee $\mathbf{m}$
-  \end{align*}
-%\\$\mid$ register key $\PKH$ as delegate fee $\mathbf{m}$ 
-%\\$\mid$ set delegate for $\PKH$ to $\PKH'$  fee $\mathbf{m}$ 
-%\\$\mid$ withdraw delegate from $\PKH$ fee $\mathbf{m}$ 
-\end{definition}
-
-\begin{definition}[Query]
-Queries are defined by the following grammar:
-\begin{align*}
-  \QRY & ::= \GETBALANCE {\PKH / \PUH}
-  \\&\mid \GETSTATUS\OPH
-  \\&\mid \GETSTORAGE\PUH
-  \\&\mid \GETCODE\PUH 
-  \\&\mid \GETPUBLICKEY\PKH
-  \\&\mid \GETCOUNTER\PKH
-\end{align*}
-
-%$\mid$ get delegate for $\PKH$
-%\\$\mid$ waiting for $\OPH$ to be included in $\mathbf{m}$ blocks
-%\\$\mid$ get timestamp
-%\\$\mid$ get contracts
-%\\$\mid$ show contracts for $\PKH$
-%\\$\mid$ get balance for $\PKH$
-
-\end{definition}
- \begin{definition}[State of a node]
-   The state of a node is a tuple
-   $\NODE = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ where $\ACCOUNTS$ is a set of accounts,
-   $\OPERATIONS$ a set of operations, and $\CONTRACTS$  a set of contracts. 
-\end{definition}
-
-When an operation is injected in a node, it enters a \emph{pending pool}
-(and is called a pending operation). 
- \begin{definition}[Pending operation]
-A pending operation is a tuple  $\langle  \OP, \OPH, \TIME
-\rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash
-and $\TIME$ is the time when the operation was injected. 
-\end{definition}
-After some time, a pending operation may be included in the blockchain as an accepted operation.
-%Let \textit{P} is the set of pending operations.
- \begin{definition}[Accepted operation]
-An accepted operation  is a tuple $\langle  \OP, \OPH, \TIME \rangle
-$, where $\OP$ is an operation, $\OPH$ is the operation hash and
-$\TIME$ is the time when it was included in the blockchain. 
-\end{definition}
-
-\begin{definition}[Blockchain]
-  The state of a blockchain is a tuple
-  $[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ where
-  $\PENDING$ is a set of pending operations,  $\ACCEPTED$ is a set
-  of accepted operations, $\MANAGERS$ is a set of managers,
-  $\CONTRACTORS$ is a set of contractors, and $\TIME$ is the current time of the blockchain. 
-\end{definition}
-
-\begin{definition}[Blockchain system]
-A blockchain system is a pair
-$ \NODE \| \BLOCKCHAIN$ where
-\begin{enumerate}
-\item $\NODE = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ is the state of a node, and
-\item $\BLOCKCHAIN = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ is the state of a blockchain 
-  such that $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.pkh = c.pkh$
-  and $\forall s \in \CONTRACTS \implies \exists p \in \CONTRACTORS, s.puh = p.puh$.
-\end{enumerate}
-\end{definition}
-
-\section{Rules}
-
-\subsection{Transitions on Nodes}
-\label{sec:transitions-nodes}
-
-Each node has (nondeterministic) rules to propose an operation.
-
-\begin{mathpar}
-  \inferrule[Node-Transfer]
-  {\CHECKACC (\PUK, \ACCOUNTS)
-  }{
-    [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
-    \NodeTrans
-    [\ACCOUNTS, (\TRANSFER\NTEZ\PUK{\PUK'}\MTEZ) :: \OPERATIONS, \CONTRACTS]
-  }
-
-  \inferrule[Node-Originate]
-  {\CHECKACC (\PUK, \ACCOUNTS) \\
-    \CHECKID (\ID, \CONTRACTS)
-  }{
-    [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
-    \NodeTrans \\
-    [\ACCOUNTS, (\ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ) :: \OPERATIONS, \CONTRACTS]
-  }
-
-  \inferrule[Node-System]
-  {\NODE \NodeTrans \NODE'}
-  { {\NODE \| \BLOCKCHAIN} \SystemTrans {\NODE'\| \BLOCKCHAIN}}
-\end{mathpar}
-
-\subsection{Transfers}
-
-Rule 1 [proposal]:
-
-\begin{equation}{}
-  \frac{
-    \text{checkAcc($pkh$, \ACCOUNTS)}
-  }{
-    \parbox{4.5in}{\text{$\langle[\ACCOUNTS, \OPERATIONS,
-        \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS,
-        \TIME]\rangle \rightarrow$} \\
-      \text{$\langle [\ACCOUNTS, (\TRANSFER\NTEZ\PKH{\PKH'}\MTEZ)$ ::
-        \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS,
-        \CONTRACTORS, \TIME]$\rangle$}}}  
-\end{equation}
-~\\
-~\\
-Rule 2 [injected]:
-
-\begin{mathpar}
-  \inferrule{
-    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
-    \CHECKCOU (\MANAGERS, \PUK) \\
-    \CHECKPUB (\MANAGERS, \PUK') \\\\
-    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
-    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ)
-  }{
-   { [\ACCOUNTS, \OP :: \OPERATIONS, \CONTRACTS] \| [\PENDING,
-     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
-   { [\ACCOUNTS, \OPERATIONS, \CONTRACTS] \|
-     [ \Angle{\OP,\OPH, \TIME}
-     ::\PENDING,
-     \ACCEPTED,
-     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
-     \CONTRACTORS,
-     \TIME]
-   }
-  }
-\end{mathpar}
-% \begin{equation}{}
-% \frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$}\\
-% \text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
-% \text{$pkh', n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME]$\rangle$}}} 
-% \end{equation}
-~\\
-~\\
-Rule 3 [rejected of counter]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkCou(\MANAGERS, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
-\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
-~\\
-~\\
-Rule 4 [rejected of balance]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkBal(\MANAGERS, $pkh, m, n$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
-\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
-~\\
-~\\
-Rule 5 [rejected of public key]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
-\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
-~\\
-~\\
-Rule 6 [included]:
-\begin{equation}{}
-\frac{}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$ } \\
- \text{[\PENDING, $<$ transfer $n$ from  $puk$ to $puk'$ fee $m$, oph, \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
-\text{$puk, puk', n, m$), \CONTRACTORS, \TIME' + 1]}}} 
-\end{equation}
-~\\
-Rule 7 [timeout]:
-\begin{equation}{}
-\frac{\TIME' - \TIME \ge 60}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$} \\
- \hspace*{0cm} \text{[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
-\end{equation}
-
-\subsection{Smart Contracts}
-~\\
-A. Originate
-~\\
-~\\
-Rule 1 [proposal]:
-
-\begin{equation}{}
-  \frac{\text{checkAcc($pkh$, \ACCOUNTS) $\wedge$ checkId($id$, \CONTRACTS)}}
-  {\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
-        [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle
-        \rightarrow \langle$[\ACCOUNTS, 
-        (originate contract ${id}$ transferring} \\
-  \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
-~\\
-~\\
-Rule 2 [injected]:
-
-\begin{equation}{}
-\frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] $\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME] $\rangle$}}}
-\end{equation}
-~\\
-~\\
-Rule 3 [rejected of code]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkPrg($code, s$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}}
-\end{equation}
-~\\
-~\\
-Rule 4 [rejected of counter]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkCou(\MANAGERS, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$))} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}}
-\end{equation}
-~\\
-~\\
-Rule 5 [rejected of balance]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkBal(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}}
-\end{equation}
-~\\
-~\\
-Rule 6 [included]:
-\begin{equation}{}
-\frac{}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running } \\
-\text{${code}$ init ${s}$), \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS,($< id$, } \\
-\text{generateHash($id, code, s$, \TIME'), $code >$ :: \CONTRACTS)], [\PENDING, $<$ (originate contract ${id}$ } \\
-\text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
-\text{$puk, n, m$), ($<$ generateHash($id, code, s$, \TIME'), $n, code$, } \\
- \text{getStorage($code, s$) $>$) :: \CONTRACTORS), \TIME' + 1]$\rangle$}}} 
-\end{equation}
-~\\
-Rule 7 [timeout]:
-\begin{equation}{}
-\frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$) $>$ } \\
-\text{:: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
-\end{equation}
-~\\
-~\\
-B. \textbf{Transfer}
-\\
-~\\
-Rule 1 [proposal]:
-
-\begin{equation}{}
-\frac{\text{checkAcc($pkh$, \ACCOUNTS)  }}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ }  \\
-\text{fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
-~\\
-~\\
-Rule 2 [injected]:
-
-\begin{equation}{}
-\frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPuh(\CONTRACTORS, $puh$)}
-\\
-\text{ $\wedge$ checkArg(\CONTRACTORS, $puh, s$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}\\
-\text{$\rightarrow$  $\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), }\\
- \text{generateOph($pkh, puh, s, n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), }\\
-\text{\CONTRACTORS, \TIME] $\rangle$}}} 
-\end{equation}
-~\\
-~\\
-Rule 3 [rejected of counter]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkCou(\MANAGERS, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$  }\\
-\text{$\rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
-~\\
-~\\
-Rule 4 [rejected of balance]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkBal(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$ }\\
-\text{$\rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
-~\\
-~\\
-Rule 5 [rejected of public hash]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkPuh(\CONTRACTORS, $puh$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$ }\\
-\text{$\rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
-~\\
-~\\
-Rule 6 [rejected of argument]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkArg(\CONTRACTORS, $puh, s$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}\\
-\text{$\rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
-~\\
-~\\
-Rule 7 [included]:
-
-\begin{equation}
-\frac{}{
-  \begin{array}{l}
-    {[\langle \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \OPH, \TIME
-    \rangle :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']}
-    \rightarrow \\
-    {}[\PENDING, \langle \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \OPH, \TIME' \rangle :: \ACCEPTED,  \\
-    \text{updateSucc(\MANAGERS, \PUK, '', \NTEZ, \MTEZ), updateConstr$(\CONTRACTORS, \PUH, \NTEZ,
-  s)$, $\TIME' + 1$]}
-  \end{array}
-}\label{eq:1}
-\end{equation}
-~\\
-Rule 8 [timeout]:
-\begin{equation}{}
-  \frac{\TIME' - \TIME \ge 60}{
-    \begin{array}{l}
-      {}[\langle\TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \TIME\rangle ::
-      \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ]
-      \rightarrow \\
-      {}[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE), \CONTRACTORS, \TIME']
-    \end{array}
-    }
-\end{equation}
-
-\section{Functions}
-\begin{enumerate}
-    \item Function \verb!checkAcc(pkh, C)! checks whether an account $pkh$ exists in \ACCOUNTS
-    \item Function \verb!checkPub(K, pkh)! checks whether the public key of the public key hash $pkh$ is reveled to the blockchain.
-    \item Function \verb!checkBal(K, pkh, n, m)! checks whether the balance of the account $pkh$ is greater or equal to $m$ + $n$
-    \item Function \verb!checkCou(K, pkh)! checks whether the current
-      counter of an account $phk$ is unlocked (i.e., its flag is False)
-    \item Function \verb!updateSucc(K, pkh, pkh', n, m)! updates the balance and the counter of the account $phk$ and the balance of the account $phk'$, where
-    \begin{itemize}
-        \item  \verb!< puk, pkh, bal, (n, True) >!  \verb!=>! \\ \verb!< puk, pkh, bal - n - m, (n + 1, False) >!
-        \item  \verb!< puk', pkh', bal', cou' >! \verb!=>! \verb!< puk', pkh', bal' + n, cou' >!
-    \end{itemize}
-
-    \item Function \verb!updateCou(K, puk, b')! updates the counter
-      lock of the account $phk$ (True $=$ lockeed, False $=$ unlocked), where
-    \begin{itemize}
-        \item  \verb!< puk, pkh, bal, (n, b) >!  \verb!=>! \verb!< puk, pkh, bal, (n, b') >!
-    \end{itemize}
-
-    \item Function \verb!checkId(id, S)! checks whether a contract $id$ does not already exist in \CONTRACTS
-
-    \item Function \verb!checkPrg(code, s)! checks whether the code $code$ are well type and $s$ is well type input
-
-    %\item Function \verb!addContr(S, id, puh, code)! adds a new  contract $< id, puh, code >$  into \CONTRACTS
-
-    \item Function \verb! generateOph(pkh,pkh', n, m, t)! generates a operation hash
-
-    \item Function \verb!generateHash(S, id, puh, code, t)! generates the public hash of a contract
-
-   % \item Function \verb!addOrig(T,< hash, 0, code, storage >)! add the a new originator $\langle  puh$, 0, $code, storage \rangle $ 
-    \item Function \verb!getStorage(code, s)! gets the storage for the code $code$ and the input $s$
-\end{enumerate}
-
-\section{Some implementations}
-Function \verb!checkAcc(puh, C)! checks whether an account exists and and \verb!checkPuk(puh, K)! checks the revelation of its public key to the blockchain.
-\begin{verbatim}
-let rec checkAcc puh C =
-  match C with
-  | 0 -> false
-  | < als, pak, puk, pkh' > :: C' ->
-    if (puh = puh')  then true 
-    else checkAcc (puh, C')
-\end{verbatim}
-
-\begin{verbatim}
-let rec checkPuk puh K =
-  match C with
-  | 0 -> false
-  | < als, pak, puk, pkh' > :: K' ->
-    if (puh = puh') and (puk =/= nil) then true 
-    else 5checkPuk (puh, K')
-\end{verbatim}
-
-The following functions interact with $\MANAGERS$.
-
-\begin{verbatim}
-let rec checkBal K puk n m =
-  match K with
-  | 0 -> true
-  | < puk', bal, cou > :: K' ->
-    if (puk = puk') and (n + m) <= bal then true 
-    else checkBal (K', puk, n, m)
-\end{verbatim}
-
-\begin{verbatim}
-let rec checkPub K puk =
-  match K with
-  | 0 -> false
-  | < puk', bal, cou > :: K' ->
-    if (puk = puk') then true 
-    else checkExi (K', puk)
-\end{verbatim}
-
-\begin{verbatim}
-let rec checkCou K puk =
-  match K with
-  | 0 -> false
-  | < puk', bal, cou > :: K' ->
-    if (puk = puk') and (cou = T) then true 
-    else checkCou (K', puk)
-\end{verbatim}
-
-\begin{verbatim}
-let rec updateCou K puk =
-  match K with
-  | 0 -> 0
-  | < puk', bal, cou > :: K' ->
-    if (puk = puk') then < puk', bal, F > :: K'
-    else < puk', bal, cou > :: updateCou (K', puk)
-\end{verbatim}
-
-\begin{verbatim}
-let rec updateSucc K puk puk' m n =
-  match K with
-  | 0 -> 0
-  | < puk'', bal, cou > :: K' ->
-    if (puk = puk'') then < puk'', bal - (n + m), T > 
-       :: updateSucc (K', puk, puk', n, m)
-    else if (puk' = puk'') then < puk'', bal + n, cou > :: K'
-         else  < puk'', bal, cou > 
-               ::updateSucc (K', puk, puk', n, m)
-\end{verbatim}
-
 \end{document}

### 2020-10-21 papers/execution-model/model.tex
update after discussion

@@
 
+\subsection{Local Node}
+\label{sec:local-node}
+
 \begin{definition}%[Account]
-An \emph{account} is a tuple $\langle \ALS, \PAK, \PUK, \PKH \rangle $, where $\ALS$ is the alias of the account, $\PAK$ is its private key, $\PUK$ is its public key and $\PKH$ is its public key hash .
+  An \emph{account} is a tuple $\langle
+  %\ALS,
+  \PAK, \PUK
+  %, \PKH
+  \rangle $, where
+  % $\ALS$ is the alias of the account,
+  $\PAK$ is its private key and $\PUK$ is its public key.
+  % and $\PKH$ is its public key hash . 
 \end{definition}
 
-\begin{definition}%[Contract]
-An \emph{contract} is a tuple $\langle  \ALS, \PUH, \CODE \rangle $, where
-$\ALS$ is the alias of the contract, $\PUH$ is its public hash, and
-$\CODE$ is the code of the contract. 
+% \begin{definition}%[Contract]
+%   An \emph{contract} is a tuple $\langle
+%   % \ALS,
+%   \PUH, \CODE \rangle $, where
+%   % $\ALS$ is the alias of the contract, 
+%   $\PUH$ is its public hash, and
+%   $\CODE$ is the code of the contract. 
+% \end{definition}
+
+\begin{definition}%[Operation]
+  \emph{Operations} are defined by the following grammar:
+  \begin{align*}
+    \OP &::= \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ
+    \\&\mid \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ
+    % \\&\mid transfer $\mathbf{n}$ from $\PKH$ to  $\PUH$ arg $\mathbf{s}$ fee $\mathbf{m}$
+  \end{align*}
+%\\$\mid$ register key $\PKH$ as delegate fee $\mathbf{m}$ 
+%\\$\mid$ set delegate for $\PKH$ to $\PKH'$  fee $\mathbf{m}$ 
+%\\$\mid$ withdraw delegate from $\PKH$ fee $\mathbf{m}$ 
 \end{definition}
+
+\begin{definition}%[State of a node]
+  The \emph{state of a node} is a tuple
+  $\NODE = [\ACCOUNTS, \OPERATIONS]$ where $\ACCOUNTS$ is a set of
+  accounts and
+  $\OPERATIONS$ a set of operations.
+\end{definition}
+
+\subsection{Global}
+\label{sec:global}
 
@@
   $\langle \PUH, \BAL, \CODE, \STORAGE \rangle $, where $\PUH$ is the
-  public key hash of the contract, $\BAL$ is its current balance, $\CODE$ is its
+  public hash of the contract, $\BAL$ is its current balance, $\CODE$ is its
   code, and $\STORAGE$ is its current storage.
-\end{definition}
-
-\begin{definition}%[Operation]
-  \emph{Operations} are defined by the following grammar:
-  \begin{align*}
-    \OP &::= \TRANSFER[\STRING]\NTEZ\PKH{\PKH'}\MTEZ
-    \\&\mid \ORIGINATE\ID\NTEZ\PKH\CODE\STRING\MTEZ
-    % \\&\mid transfer $\mathbf{n}$ from $\PKH$ to  $\PUH$ arg $\mathbf{s}$ fee $\mathbf{m}$
-  \end{align*}
-%\\$\mid$ register key $\PKH$ as delegate fee $\mathbf{m}$ 
-%\\$\mid$ set delegate for $\PKH$ to $\PKH'$  fee $\mathbf{m}$ 
-%\\$\mid$ withdraw delegate from $\PKH$ fee $\mathbf{m}$ 
 \end{definition}
@@
 
-\end{definition}
- \begin{definition}%[State of a node]
-   The \emph{state of a node} is a tuple
-   $\NODE = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ where $\ACCOUNTS$ is a set of accounts,
-   $\OPERATIONS$ a set of operations, and $\CONTRACTS$  a set of contracts. 
 \end{definition}
@@
 Each node has (nondeterministic) rules to propose an operation.
+When an operation $\OP$ appears, we check that the account is local by
+looking up its public key $\OP.\PUK$ in the local accounts $\ACCOUNTS$ and
+consider it signed with the corresponding private key $\PAK$.
 
 \begin{mathpar}
-  \inferrule[Node-Transfer]
-  {\CHECKACC (\PUK, \ACCOUNTS) \\
-    \OP = \TRANSFER[\STRING]\NTEZ\PUK{\PUK'}\MTEZ
+  \inferrule[Node-Op]
+  { % \CHECKACC (\OP.\PUK, \ACCOUNTS)
+    \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS
+    % \\
+    % \OP = \TRANSFER[\STRING]\NTEZ\PUK{\PUK'}\MTEZ
   }{
-    [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
+    [\ACCOUNTS, \OPERATIONS]
     \NodeTrans
-    [\ACCOUNTS, \OP:: \OPERATIONS, \CONTRACTS]
+    [\ACCOUNTS, \OP:: \OPERATIONS]
   }
 
-  \inferrule[Node-Originate]
-  {\CHECKACC (\PUK, \ACCOUNTS) \\
-    \CHECKID (\ID, \CONTRACTS) \\
-    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ
-  }{
-    [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
-    \NodeTrans 
-    [\ACCOUNTS, \OP :: \OPERATIONS, \CONTRACTS]
-  }
-
+  % \inferrule[Node-Originate]
+  % {\CHECKACC (\PUK, \ACCOUNTS) \\
+  %   % \CHECKID (\ID, \CONTRACTS) \\
+  %   \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ
+  % }{
+  %   [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
+  %   \NodeTrans 
+  %   [\ACCOUNTS, \OP :: \OPERATIONS, \CONTRACTS]
+  % }
+  %
   \inferrule[Node-System]
   {\NODE \NodeTrans \NODE'}
-  { {\NODE \| \BLOCKCHAIN} \SystemTrans {\NODE'\| \BLOCKCHAIN}}
+  { {\NODE :: \overline\NODE \| \BLOCKCHAIN}
+    \SystemTrans
+    {\NODE' :: \overline\NODE \| \BLOCKCHAIN}}
 
@@
   {\BLOCKCHAIN \BlockTrans \BLOCKCHAIN'}
-  { {\NODE \| \BLOCKCHAIN} \SystemTrans {\NODE\| \BLOCKCHAIN'}}
+  { {\overline\NODE \| \BLOCKCHAIN}
+    \SystemTrans
+    {\overline\NODE\| \BLOCKCHAIN'}}
 \end{mathpar}
@@
     \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
-    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ)
+    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ, \TIME)
   }{
-   { [\ACCOUNTS, \OP :: \OPERATIONS, \CONTRACTS] \| [\PENDING,
+   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
      \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
-   { [\ACCOUNTS, \OPERATIONS, \CONTRACTS] \|
+   { [\ACCOUNTS, \OPERATIONS] \|
      [ \Angle{\OP,\OPH, \TIME}
@@
   \inferrule[Block-Accept]{
-    % \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
     \TIME'-\TIME < 60
@@
       \CONTRACTORS, \TIME']}
-    \BlockTrans 
-    {[\PENDING, \Angle{\OP,\OPH,\TIME'} :: \ACCEPTED, \MANAGERS,
+    \BlockTrans  \\
+    {[\PENDING, \Angle{\OP,\OPH, \TIME,\TIME'} :: \ACCEPTED,
+      \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ),
       \CONTRACTORS, \TIME'+1]}
@@
 \end{mathpar}
-Rule 7 [timeout]:
+Rule 7 [timeout]: (applies to both, implicit transfers and contract invocations)
 \begin{mathpar}
   \inferrule[Block-Timeout]{
-    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+    \OP = \TRANSFER[\STRING]\NTEZ\PUK{\PUK'/\PUH}\MTEZ \\
     \TIME'-\TIME \ge 60
@@
     \CHECKPRG (\CODE, \STRING) \\\\
-    \ORIG = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ 
+    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ \\
+    \OPH = \GENERATEHASH (\ID,\CODE,\STRING,\TIME) 
   }{
     \Angle{[
-      \ACCOUNTS, \ORIG :: \OPERATIONS, \CONTRACTS
+      \ACCOUNTS, \OP :: \OPERATIONS, \CONTRACTS
       ], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]} \to \\
     \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
-      [\Angle{\ORIG,\TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]}
+      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]}
   }
@@
     \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ \\
-    \OPH = \GENERATEHASH (\ID,\CODE,\STRING,\TIME') \\
     \TIME'-\TIME < 60
@@
     \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
-      [\Angle{\OP,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']}
+      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']}
     \SystemTrans \\
@@
       \\
-      [\PENDING, \Angle{\OP, \TIME'} :: \ACCEPTED, \UPDATESUCC
+      [\PENDING, \Angle{\OP, \OPH,\TIME,\TIME'} :: \ACCEPTED, \UPDATESUCC
       (\MANAGERS, \PUK, \NTEZ, \MTEZ), \Angle{\OPH, \GETSTORAGE
@@
     %\Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
-      [\Angle{\OP,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
+      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
       \CONTRACTORS, \TIME']
@@
 \\
-~\\
-Rule 1 [proposal]:
+% ~\\
+% Rule 1 [proposal]:
 
-\begin{equation}{}
-\frac{\text{checkAcc($pkh$, \ACCOUNTS)  }}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ }  \\
-\text{fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
-~\\
+% \begin{equation}{}
+% \frac{\text{checkAcc($pkh$, \ACCOUNTS)  }}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ }  \\
+% \text{fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
+% \end{equation}
+% ~\\
 ~\\
 Rule 2 [injected]:
-
-\begin{equation}{}
-\frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPuh(\CONTRACTORS, $puh$)}
-\\
-\text{ $\wedge$ checkArg(\CONTRACTORS, $puh, s$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}\\
-\text{$\rightarrow$  $\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), }\\
- \text{generateOph($pkh, puh, s, n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), }\\
-\text{\CONTRACTORS, \TIME] $\rangle$}}} 
-\end{equation}
+\begin{mathpar}
+  \inferrule[Block-Call]{
+    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
+    \CHECKCOU (\MANAGERS, \PUK) \\
+    \CHECKPUH (\CONTRACTORS, \PUH) \\
+    \CHECKARG (\CONTRACTORS, \PUH, \STRING) \\
+    \OP =  \TRANSFER[\STRING]\NTEZ\PUK{\PUH}\MTEZ \\
+    \OPH = \GENERATEOPH (\PUK,\PUH, \STRING,\NTEZ, \MTEZ, \TIME)
+  }{
+    \Angle{[\ACCOUNTS, \OP :: \OPERATIONS], 
+      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
+    }
+    \SystemTrans \\
+    \Angle{[\ACCOUNTS, \OPERATIONS],
+      [\Angle{\OP, \OPH, \TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(
+      \MANAGERS, \PUK, \TRUE), \CONTRACTORS, \TIME]
+    }
+  }
+\end{mathpar}
+% \begin{equation}{}
+% \frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPuh(\CONTRACTORS, $puh$)}
+% \\
+% \text{ $\wedge$ checkArg(\CONTRACTORS, $puh,
+%   s$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from
+%     ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS,
+%     \CONTRACTS], 
+%     [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
+%     $\rangle$}\\
+% \text{$\rightarrow$  $\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), }\\
+%  \text{generateOph($pkh, puh, s, n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), }\\
+% \text{\CONTRACTORS, \TIME] $\rangle$}}} 
+% \end{equation}
 ~\\
@@
 Rule 7 [included]:
-
-\begin{equation}
-\frac{}{
-  \begin{array}{l}
-    {[\langle \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \OPH, \TIME
-    \rangle :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']}
-    \rightarrow \\
-    {}[\PENDING, \langle \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \OPH, \TIME' \rangle :: \ACCEPTED,  \\
-    \text{updateSucc(\MANAGERS, \PUK, '', \NTEZ, \MTEZ), updateConstr$(\CONTRACTORS, \PUH, \NTEZ,
-  s)$, $\TIME' + 1$]}
-  \end{array}
-}\label{eq:1}
-\end{equation}
+\begin{mathpar}
+  \inferrule{
+    \OP = \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ \\
+    \TIME'-\TIME < 60
+  }{
+    [\Angle{\OP, \OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
+    \CONTRACTORS, \TIME']
+    \BlockTrans \\
+    [\PENDING,
+    \Angle{\OP,\OPH, \TIME, \TIME'} :: \ACCEPTED,
+    \UPDATESUCC (\MANAGERS, \PUK, '', \NTEZ, \MTEZ),
+    \UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \STRING),
+    \TIME'+1]
+  }
+\end{mathpar}
+% \begin{equation}
+% \frac{}{
+%   \begin{array}{l}
+%     {[\langle \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \OPH, \TIME
+%     \rangle :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']}
+%     \rightarrow \\
+%     {}[\PENDING, \langle \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \OPH, \TIME' \rangle :: \ACCEPTED,  \\
+%     \text{updateSucc(\MANAGERS, \PUK, '', \NTEZ, \MTEZ), updateConstr$(\CONTRACTORS, \PUH, \NTEZ,
+%   s)$, $\TIME' + 1$]}
+%   \end{array}
+% }\label{eq:1}
+% \end{equation}
 ~\\

### 2020-10-21 papers/contract-modules/modules.tex
update after meeting

@@
 \usepackage{fixme}
+\usepackage{listings}
+
+\lstset{language=caml}
 
@@
 
+\section{Motivation}
+\label{sec:motivation}
+
+\begin{lstlisting}[language=caml]
+contract module MyContract = "kt1..."
+  entry point bid_for_auction Left (_ : int) 
+  raises "closed" as closed       (* auction closed*)
+         "bid too low" as too_low (* bid received is too low *)
+         42 as the_answer         (* failwith received argument 42 *)
+         (_ : int) as failedwith  (* failwith received an integer arg *)
+
+  entry point close_auction Right (_ : unit)
+  raises "not owner"         (* caller cannot close the auction *)
+\end{lstlisting}
+
+The contract module is compiled into an OCaml module which provides a typed API to the
+contract. Internally, the typed API builds on the untyped API developed by us.
+
+\begin{lstlisting}[language=caml]
+signature MyContract =
+sig 
+  type bid_for_auction_errors = 
+     | closed 
+     | too_low 
+     | the_answer
+     | failedwith of int
+
+  val bid_for_auction : int -> x Tezos
+
+  type close_auction_errors = 
+     | not_owner
+
+  val close_auction : unit -> x Tezos
+end
+\end{lstlisting}
+
+If the contract source is available, then an extended type checker verifies that the entry points
+exist and that all failures that may arise during contract execution from a particular entry point
+are covered by the listed cases.
+
+Q: how should we deal with built-in errors? Like Java's (unchecked?) exceptions?
+
+If only the public hash of the contract is known, then obtain the source code through the tezos
+client and proceed as above.
+
+\clearpage
+\section{Tools}
+\label{sec:tools}
+
+An extended type checker that collects information about explicit failures along execution paths
+starting from each possible entry point. We may also wish to provide an entry point so that the
+checker only gathers information for that entry point. This alternative may be interesting if there
+is an entry point taking a parameter of sum type, rather than using all injections to distinguish
+between entry points.
+
+It seems like the type checking is doable using symbolic execution. In this framework, it would also
+be possible to assume further invariants about the inputs and place them into the contract
+module. Essentially, every formula that an SMT solver can deal with should be fine.
+
 \end{document}

### 2020-11-08 meeting-notes/20201108-expose-input-language.tex
first step at typed interaction

\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{mathpartir}
\usepackage{listings}
\usepackage{url}

\usepackage{hyperref}

\usepackage{xcolor}
\usepackage{tcolorbox}
\tcbuselibrary{breakable}

\newenvironment{changethis}{%
  \begin{tcolorbox}[breakable,notitle,boxrule=0pt,colback=blue!20,colframe=blue!20]}{%
  \end{tcolorbox}}

\newenvironment{ethereum}{%
  \begin{tcolorbox}[breakable,notitle,boxrule=0pt,colback=red!20,colframe=red!20]}{%
  \end{tcolorbox}}

\input{solidity-highlighting}

\title{Expos\'{e}\\
  Input Language for Smart Contract API}
\author{Peter Thiemann}
\begin{document}
\maketitle{}

\section{Introduction}
\label{sec:introduction}

The current Tezos API facing to OCaml (as well as the one provided by
the Tezos client) is untyped. Here we propose a DSL to make it typed.
First we recall some information from the Michelson white paper
\url{https://tezos.gitlab.io/whitedoc/michelson.html#core-data-types-and-notations}.

\subsection{Core data types and notations}

\begin{itemize}
\item \texttt{string}, \texttt{nat}, \texttt{int} and \texttt{bytes}: The core primitive constant types.
\item 
  \texttt{bool}: The type for booleans whose values are \texttt{True} and \texttt{False}.
\item 
  \texttt{unit}: The type whose only value is \texttt{Unit}, to use as a placeholder
  when some result or parameter is not necessary. For instance, when
  the only goal of a contract is to update its storage.
\item 
  \texttt{list (t)}: A single, immutable, homogeneous linked list, whose
  elements are of type (t), and that we write \texttt{\{\}} for the empty list or
  \texttt{\{ first ; ... \}}. 
\item 
  \texttt{pair (l) (r)}: A pair of values a and b of types (l) and (r), that we
  write \texttt{(Pair a b)}.
\item 
  \texttt{option (t)}: Optional value of type (t) that we write \texttt{None} or \texttt{(Some
  v)}.
\item 
  \texttt{or (l) (r)}: A union of two types: a value holding either a value a
  of type (l) or a value b of type (r), that we write \texttt{(Left a)} or
  \texttt{(Right b)}.
\item 
  \texttt{set (t)}: Immutable sets of values of type (t) that we write as lists
  \texttt{\{ item ; ... \}}, of course with their elements unique, and sorted.
\item 
  \texttt{map (k) (t)}: Immutable maps from keys of type (k) of values of type
  (t) that we write \texttt{\{ Elt key value ; ... \}}, with keys sorted.
\item 
  \texttt{big\_map (k) (t)}: Lazily deserialized maps from keys of type (k) of
  values of type (t) that we write \texttt{\{ Elt key value ; ... \}}, with keys
  sorted. These maps should be used if one intends to store large
  amounts of data in a map. They have higher gas costs than standard
  maps as data is lazily deserialized. A \texttt{big\_map} cannot appear inside
  another \texttt{big\_map}.
\end{itemize}

\subsection{Relation to OCaml datatypes}
\label{sec:relat-ocaml-datatyp}

\begin{center}
  \begin{tabular}{|l|l|}
    Michelson & OCaml \\\hline
    \texttt{string}& \texttt{string}  \\
    \texttt{nat} & ? (\texttt{int}) \\
    \texttt{int} & \texttt{int} \\ 
    \texttt{bytes}& ? \\
    \texttt{bool}&\texttt{bool} \\
    \texttt{unit}&\texttt{unit} \\
    \texttt{list t}&\texttt{t list} \\
    \texttt{pair l r}&\texttt{l * r} \\
    \texttt{option t}     &\texttt{t option} \\
    \texttt{or l r}&\texttt{[`Left of l | `Right of r]} \\
    \texttt{set t}&? \texttt{Set.Make (T).t} \\
    \texttt{map k t}&? \texttt{`t Map.Make(K).t} \\
    \texttt{big\_map k t}&? \texttt{`t Map.Make(K).t} \\
    \hline
  \end{tabular}
\end{center}

\section{Tasks}
\label{sec:tasks}

We can represent Michelson parameter values with the following OCaml type using GADTs.
\begin{lstlisting}[language=Caml]
type _ Mvalue =
  | Mstring : string -> string Mvalue
  | Mint  : int -> int Mvalue
  | Mbool : bool -> bool Mvalue
  | Munit : unit -> unit Mvalue
  | Mnil  : 't list Mvalue
  | Mcons : 't Mvalue * 't list Mvalue -> 't list Mvalue
  | Mpair : 'l Mvalue * 'r Mvalue -> ('l * 'r) Mvalue
  | Mnone : 't option Mvalue
  | Msome : 't Mvalue -> 't option Mvalue
  | Mleft : 'l Mvalue -> [`Left of 'l | `Right 'r] Mvalue
  | Mright : 'r Mvalue -> [`Left of 'l | `Right 'r] Mvalue
\end{lstlisting}

\begin{lstlisting}[language=Caml]
type _ Mtype = 
  | Tstring : string Mtype
  | Tint    : int Mtype
  | Tbool   : bool Mtype
  | Tunit   : unit Mtype
  | Tlist   : 't Mtype -> 't list Mtype
  | Tpair   : 'l Mtype * 'r Mtype -> ('l * 'r) Mtype
  | Toption : 't Mtype -> 't option Mtype
  | Tor     : 'l Mtype * 'r Mtype -> [`Left of 'l | `Right of 'r] Mtype
\end{lstlisting}
Instead of using polymorphic variants, one could also define a binary
sum type like Haskell's Either type.
\begin{lstlisting}[language=Caml]
type ('a, 'b) either = Left of 'a | Right of 'b
\end{lstlisting}

To read input values, we'd need a function like the following.
\begin{lstlisting}[language=Caml]
mread : 't Mtype -> 't -> 't Mvalue
\end{lstlisting}

Or given a contract for index type \lstinline/t/, we'd have an
invocation function
\begin{lstlisting}[language=Caml]
invoke : 't Mtype Tezos.contract -> 't -> result Tezos.apimonad
\end{lstlisting}
with an internal serialization function
\begin{lstlisting}[language=Caml]
serialize : 't Mtype -> 't -> string
\end{lstlisting}
Not sure if deserialization is also needed, but it might be necessary
to decode the current state of a contract. Deserialization may fail
and thus raise an exception.
\begin{lstlisting}[language=Caml]
deserialize : 't Mtype -> string -> 't
\end{lstlisting}
\end{document}

### 2020-11-08 meeting-notes/20201108-expose-input-language.tex
fine tuning

@@
 \input{solidity-highlighting}
+
+\lstset{numbers=none}
 
@@
   | Toption : 't Mtype -> 't option Mtype
-  | Tor     : 'l Mtype * 'r Mtype -> [`Left of 'l | `Right of 'r] Mtype
+  | Tor     : 'l Mtype * 'r Mtype 
+            -> [`Left of 'l | `Right of 'r] Mtype
 \end{lstlisting}
@@
 \end{lstlisting}
+
+One can get rid of the \lstinline/Mtype/ datatype by directly
+composing serializers in tagless style. I think. But having the type
+representation might be more flexible.
+\begin{lstlisting}[language=Caml]
+s_string : string -> string
+s_int : int -> string
+s_bool : bool -> string
+s_unit : unit -> string
+s_list : ('t -> string) -> ('t list -> string)
+s_pair : ('l -> string) -> ('r -> string) -> ('l * 'r -> string)
+s_option : ('t -> string) -> ('t option -> string)
+s_or : ('l -> string) -> ('r -> string) 
+     -> ([`Left of 'l | `Right of 'r] -> string)
+\end{lstlisting}
+
+Example
+\begin{lstlisting}[language=Caml]
+mytype = Tor (Tbool, Toption (Tstring))
+myserializer = serialize mytype : 
+               [`Left of bool | `Right of string option] -> string
+
+tlserializer = s_or s_bool (s_option s_string) :
+               [`Left of bool | `Right of string option] -> string
+\end{lstlisting}
 \end{document}

### 2020-11-16 meeting-notes/20200928-expose.tex
revised entrypoints, transforming assertions

@@
 
-\section{Suggestions (Tezos)}
+\section{Suggestions}
+
+\subsection{General}
+\label{sec:suggestions-general}
+
+In the example, we checked if all elements satisfy a certain condition:
+\begin{lstlisting}[language=Caml]
+forall (n : Int)
+   if ( 2 <= n && n <= sqrt(p))
+       assert(p%n != 0)
+\end{lstlisting}
+However, if we consider  parameter p to be a sorted list and we want
+to assert that it is indeed sorted, we would need to check two values: 
+\begin{lstlisting}[language=Caml]
+forall (n : Int, m: Int)
+   if ( n > m)
+       assert(p.(n) > p.(m))
+\end{lstlisting}
+
+You can have foralls with more than one variable, but you could also nest the foralls as in
+
+\begin{lstlisting}[language=Caml]
+forall( n : int)
+ forall(m : int) ...
+\end{lstlisting}
+Externally, I think your proposed syntax is nicer, but internally it will be simpler to just have 
+\lstinline/Forall( ident, type, expr)/
+in the type for the AST.
+
+Somehow the smart random generator will have to know in which range to
+generate the values.  Considering the second example, the generator should generate 
+\begin{lstlisting}[language=Caml]
+m = random(0, length(list))
+n = random(m, length(list))
+\end{lstlisting}
+For this transformation, the assertion should be completely explicit.
+That is, in the example, there should be an additional condition
+
+\begin{lstlisting}[language=Caml]
+... if (n < length(p) && m < length(p)) ...
+\end{lstlisting}
+which means we should have the length of a list available as a primitive.
+
+Can we realize this transformation from the above syntax, or do we
+need additional syntax that expresses this transformation separately? 
+Do I even have to consider these things when creating the grammar?
+
+The process could be something like this:
+\begin{enumerate}
+\item  calculate the negation of the formula. This amounts to
+  swapping forall and exists, skipping the conditions, and negating
+  the body of the assertion. This last step should also be done by
+  applying de Morgan exhaustively down to the literals. In your
+  example you'd end up with
+
+\begin{lstlisting}[language=Caml]
+exists(n : int)
+ exists(m : int)
+    if (n< length(p) && m < length(p))
+      if (n>m)
+         check( p.(n) <= p.(m) )
+\end{lstlisting}
+\item look at the atomic constraints that bound the exists and move them upfront. Example: 
+  \begin{itemize}
+  \item  the first constraint is \lstinline/n<length(p)/ $\to$ you need to break up
+    the conjunction
+  \item independent of \lstinline/exists(m)/, hence move backward
+  \end{itemize}
+\begin{lstlisting}[language=Caml]
+exists(n : int)
+ if (n < length(p))
+   exists(m : int)
+     if (m < length(p))
+       ...
+\end{lstlisting}
+\item  if the constraint meets its generator (exists), then merge it:
+
+\begin{lstlisting}[language=Caml]
+exists(n : int, n < length(p))
+\end{lstlisting}
+\item  same for m
+
+\begin{lstlisting}[language=Caml]
+ exists(m : int, m < length(p))
+\end{lstlisting}
+( at this point, each generator / exists could come with a number of upper and lower bounds )
+\item now we need to consider this
+
+\begin{lstlisting}[language=Caml]
+exists(n : int, n < length(p))
+ exists(m : int, m < length(p))
+   if (n>m)
+     ...
+\end{lstlisting}
+this condition gives us an upper bound on m (this requires some manipulation of the formula, in general)
+so we just add it as another bound to m:
+
+\begin{lstlisting}[language=Caml]
+exists(n : int, n < length(p))
+ exists(m : int, m < length(p) && m < n)
+    ...
+\end{lstlisting}
+\item  you can find out (but this is more involved and thus optional)
+  that \lstinline/0 < n/ is required for the \lstinline/exists(m ...)/ to be nonempty and that
+  \lstinline/m < n/ implies \lstinline/m < length(p)/:
+
+\begin{lstlisting}[language=Caml]
+exists(n : int, 0 < n,  n < length(p))
+ exists(m : int, 0 <=m, m < n)
+   check( p.(n) <= p.(m) )
+\end{lstlisting}
+At this point, you can read off the invocation for the random generator.
+If any constraints remain, they'd have to be checked at run time.
+In the best case, things work out like in the example. Otherwise, each if-constaint that turns out to be false results in a useless test run.
+\end{enumerate}
+
+For background, there is a nice paper about the underlying testing methodology:
+How to specify it! by John Hughes:
+\url{https://www.tfp2019.org/resources/tfp2019-how-to-specify-it.pdf}
+
+\subsection{Tezos}
 \label{sec:suggestions-tezos}
+
+Michelson and the Tezos infrastructure directly support entry points
+with a specific notation. Hence, the syntax should reflect and reuse
+that notation.
 
@@
 \begin{lstlisting}[language=caml]
+entrypoint %default
   parameter (_, (_, p)) =
@@
 \end{lstlisting}
-Such a parameter phrase may occur multiple times. Its single argument
-is a pattern that matches the contract's argument. The type of the
+A parameter phrase may occur multiple times. Its single argument
+is a pattern that matches the contract's entrypoint's argument. The type of the
 pattern variables (here just \lstinline/p/) is determined from the code of the
@@
 
-Multiple parameter phrases can be used to state assertion for
-contracts with multiple entry points. In Tezos/Michelson, entry points are
+The entrypoint phrase may also occur multiple times. However, it is
+illegal to have patterns that overlap, i.e., which match the same
+contract invocation. Overlapping may occur due to a repeated pattern
+in clauses for the same entrypoint, but also due to a pattern for the
+\lstinline/%default/ overlapping with a pattern for another entrypoint.
+
+In Tezos/Michelson, entry points are
 modeled by having a sum type as parameter type. For example, a
@@
 BTW, this is an example for a useful contract with an existential!
+
+These phrases would refer to the \lstinline/%default/ entrypoint, as
+none is explicitly specified. Suppose the parameter type for the
+contract in question was specified in Michelson as follows.
+\begin{lstlisting}
+parameter (or (int %set_scale) (pair int int %set_triangle))
+\end{lstlisting}
+An equivalent way to stating the previous assertions would be to use
+entrypoints.
+\begin{lstlisting}[language=caml]
+entrypoint %set_scale
+  parameter (x) =
+    0 < x && x < 100
+
+entrypoint %set_triangle
+  parameter (a, b) =
+    exists (c : int)
+      if (0 < c && c <= a + b)
+        a*a + b*b = c*c
+\end{lstlisting}
 

### 2020-11-18 papers/execution-model/model.tex
Add files via upload

@@
 \begin{definition}%[Account]
-  An \emph{account} is a tuple $\langle
+  An implicit \emph{account} is a tuple $\langle
   %\ALS,
@@
   \rangle $, where
-  % $\ALS$ is the alias of the account,
   $\PAK$ is its private key and $\PUK$ is its public key.
-  % and $\PKH$ is its public key hash . 
 \end{definition}
-
-% \begin{definition}%[Contract]
-%   An \emph{contract} is a tuple $\langle
-%   % \ALS,
-%   \PUH, \CODE \rangle $, where
-%   % $\ALS$ is the alias of the contract, 
-%   $\PUH$ is its public hash, and
-%   $\CODE$ is the code of the contract. 
-% \end{definition}
 
@@
   \begin{align*}
-    \OP &::= \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ
-    \\&\mid \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ
-    % \\&\mid transfer $\mathbf{n}$ from $\PKH$ to  $\PUH$ arg $\mathbf{s}$ fee $\mathbf{m}$
+    \OP &::= \TRANSFER[\PARAMETER]\NTEZ\PUK\ADDR\MTEZ
+    \\&\mid \ORIGINATE\NTEZ\PUK\CODE\INIT\MTEZ
   \end{align*}
-%\\$\mid$ register key $\PKH$ as delegate fee $\mathbf{m}$ 
-%\\$\mid$ set delegate for $\PKH$ to $\PKH'$  fee $\mathbf{m}$ 
-%\\$\mid$ withdraw delegate from $\PKH$ fee $\mathbf{m}$ 
+  where \NTEZ\ and \MTEZ\ are amount of Tez, \ADDR\ is either a public key for an implicit account  or a public hash for a smart contract,  \PARAMETER\ is an argument passed to the smart contract's script, which is emtry if it is a transfer to an implicit account, \CODE\ is a script of the smart contract, \INIT\ is an initial value of the contract's storage.
 \end{definition}
@@
   The \emph{state of a node} is a tuple
-  $\NODE = [\ACCOUNTS, \OPERATIONS]$ where $\ACCOUNTS$ is a set of
+  $\NODE = [\ACCOUNTS, \OPERATIONS]$, where $\ACCOUNTS$ is a set of
   accounts and
-  $\OPERATIONS$ a set of operations.
+  $\OPERATIONS$ is a set of operations.
 \end{definition}
@@
 \begin{definition}%[Manager]
-A \emph{manager} manages a single account. It is represented by a
-tuple $\langle  \PUK, \PKH, \BAL, \COU \rangle $, where  $\PUK$ is the
-public key of an account, $\PKH$ is its public key hash, $\BAL$ is its
-balance and $\COU$ is its counter whose form is a pair $(n, b)$, where $n$ is a natural number and ${b}$
-is a boolean value.  
+A \emph{manager} manages a single implicit account. It is represented by a
+tuple $\langle  \PUK, \BAL, \COU \rangle $, where  $\PUK$ is the
+public key of an account, $\BAL$ is its
+balance and $\COU$ is its counter whose form is a value-flag pair $(n, b)$, where $n$, which is called the value of the counter,  is a natural number and ${b}$, which is called the flag of the counter, is a boolean value.
 \end{definition}
@@
 \begin{align*}
-  \QRY & ::= \GETBALANCE {\PKH / \PUH}
+  \QRY & ::= \GETBALANCE\ADDR
   \\&\mid \GETSTATUS\OPH
@@
   \\&\mid \GETCODE\PUH 
-  \\&\mid \GETPUBLICKEY\PKH
-  \\&\mid \GETCOUNTER\PKH
+  \\&\mid \GETCOUNTER\PUK
 \end{align*}
-
-%$\mid$ get delegate for $\PKH$
-%\\$\mid$ waiting for $\OPH$ to be included in $\mathbf{m}$ blocks
-%\\$\mid$ get timestamp
-%\\$\mid$ get contracts
-%\\$\mid$ show contracts for $\PKH$
-%\\$\mid$ get balance for $\PKH$
 
@@
  \begin{definition}%[Accepted operation]
-An \emph{accepted operation}  is a tuple $\langle  \OP, \OPH, \TIME \rangle
-$, where $\OP$ is an operation, $\OPH$ is the operation hash, and
-$\TIME$ is the time when it was included in the blockchain. 
+An \emph{accepted operation}  is a tuple $\langle  \OP, \OPH, \TIME, \TIME' \rangle
+$, where $\OP$ is an operation, $\OPH$ is the operation hash, $\TIME$ is the time when the operation was injected, and
+$\TIME'$ is the time when it was included in the blockchain. 
 \end{definition}
@@
 \begin{enumerate}
-\item $\NODE = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ is the state of a node, and
+\item $\NODE = [\ACCOUNTS, \OPERATIONS]$ is the state of a node, and
 \item $\BLOCKCHAIN = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ is the state of a blockchain 
-  such that $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.\PKH = c.\PKH$
-  and $\forall s \in \CONTRACTS \implies \exists p \in \CONTRACTORS, s.\PUH = p.\PUH$.
+  such that $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.\PUK = c.\PUK$.
 \end{enumerate}
@@
 
-  % \inferrule[Node-Originate]
-  % {\CHECKACC (\PUK, \ACCOUNTS) \\
-  %   % \CHECKID (\ID, \CONTRACTS) \\
-  %   \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ
-  % }{
-  %   [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
-  %   \NodeTrans 
-  %   [\ACCOUNTS, \OP :: \OPERATIONS, \CONTRACTS]
-  % }
-  %
   \inferrule[Node-System]
@@
 
-% Rule 1 [proposal]:
-%
-% \begin{mathpar}
-%   \inferrule[Xfer-Propose]{
-%     \CHECKACC (\PKH, \ACCOUNTS)
-%   }{
-% \langle[\ACCOUNTS, \OPERATIONS,
-%         \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS,
-%         \TIME]\rangle \rightarrow \\
-%         \langle [\ACCOUNTS, (\TRANSFER\NTEZ\PKH{\PKH'}\MTEZ) ::
-%         \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS,
-%         \CONTRACTORS, \TIME]\rangle      }
-% \end{mathpar}
-
-Rule 2 [injected]:
+Rule 1 [injected]:
 
@@
     \CHECKCOU (\MANAGERS, \PUK) \\
-    \CHECKPUB (\MANAGERS, \PUK') \\\\
+    \CHECKPUB (\MANAGERS, \PUK') \\
+    \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
     \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
@@
 \end{mathpar}
-% \begin{equation}{}
-% \frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$}\\
-% \text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
-% \text{$pkh', n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME]$\rangle$}}} 
-% \end{equation}
 ~\\
 ~\\
-Rule 3 [rejected of counter]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkCou(\MANAGERS, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
-\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
+Rule 2 [rejected of counter]:
+\begin{mathpar}
+  \inferrule{
+    %\NEG\ \CHECKCOU (\MANAGERS, \PUK)\\
+    %\OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+    \NEG\ \CHECKCOU (\MANAGERS, \PUK) \\
+    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+  }{
+   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
+     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
+   { [\ACCOUNTS, \OPERATIONS] \|
+     [ \PENDING,
+     \ACCEPTED,
+     \MANAGERS,
+     \CONTRACTORS,
+     \TIME]
+   }
+  }
+\end{mathpar}
 ~\\
 ~\\
-Rule 4 [rejected of balance]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkBal(\MANAGERS, $pkh, m, n$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
-\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
+Rule 3 [rejected of balance]:
+\begin{mathpar}
+  \inferrule{
+    \NEG\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
+    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+  }{
+   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
+     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
+   { [\ACCOUNTS, \OPERATIONS] \|
+     [ \PENDING,
+     \ACCEPTED,
+     \MANAGERS,
+     \CONTRACTORS,
+     \TIME]
+   }
+  }
+\end{mathpar}
 ~\\
 ~\\
-Rule 5 [rejected of public key]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
-\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
+Rule 4 [rejected of public key]:
+\begin{mathpar}
+  \inferrule{
+    \NEG\ \CHECKPUB (\MANAGERS, \PUK') \\
+    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+  }{
+   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
+     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
+   { [\ACCOUNTS, \OPERATIONS] \|
+     [ \PENDING,
+     \ACCEPTED,
+     \MANAGERS,
+     \CONTRACTORS,
+     \TIME]
+   }
+  }
+\end{mathpar}
+~\\
+~\\
+Rule 5 [rejected of fee]:
+\begin{mathpar}
+  \inferrule{
+    \NEG\ \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
+    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+  }{
+   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
+     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
+   { [\ACCOUNTS, \OPERATIONS] \|
+     [ \PENDING,
+     \ACCEPTED,
+     \MANAGERS,
+     \CONTRACTORS,
+     \TIME]
+   }
+  }
+\end{mathpar}
 ~\\
@@
   \inferrule[Block-Timeout]{
-    \OP = \TRANSFER[\STRING]\NTEZ\PUK{\PUK'/\PUH}\MTEZ \\
+    \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
     \TIME'-\TIME \ge 60
@@
 \subsection{Smart Contracts}
-~\\
 A. Originate
@@
 ~\\
-% Rule 1 [proposal]:
-
-% \begin{equation}{}
-%   \frac{\text{checkAcc($pkh$, \ACCOUNTS) $\wedge$ checkId($id$, \CONTRACTS)}}
-%   {\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
-%         [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle
-%         \rightarrow \langle$[\ACCOUNTS, 
-%         (originate contract ${id}$ transferring} \\
-%   \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-% \end{equation}
-% ~\\
-% ~\\
-Rule 2 [injected]:
+Rule 1 [injected]:
 
@@
     \CHECKCOU (\MANAGERS, \PUK) \\
+    \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ)  \\
     \CHECKPRG (\CODE, \STRING) \\\\
-    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ \\
-    \OPH = \GENERATEHASH (\ID,\CODE,\STRING,\TIME) 
+    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
+    \OPH = \GENERATEOPH(\PUK, \CODE, \NTEZ, \MTEZ, \STRING,\TIME) 
   }{
-    \Angle{[
-      \ACCOUNTS, \OP :: \OPERATIONS, \CONTRACTS
-      ], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]} \to \\
-    \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
-      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]}
+    [
+      \ACCOUNTS, \OP :: \OPERATIONS
+      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to \\
+    [\ACCOUNTS, \OPERATIONS] \|
+      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]
   }
 \end{mathpar}
-% \begin{equation}{}
-% \frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] $\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME] $\rangle$}}}
-% \end{equation}
 ~\\
 ~\\
-Rule 3 [rejected of code]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkPrg($code, s$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}}
-\end{equation}
+Rule 2 [rejected of code]:
+\begin{mathpar}
+  \inferrule{
+    \NEG\ \CHECKPRG (\CODE, \STRING) \\
+    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
+  }{
+    [
+      \ACCOUNTS, \OP :: \OPERATIONS
+      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
+    [\ACCOUNTS, \OPERATIONS] \|
+      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
+  }
+\end{mathpar}
 ~\\
 ~\\
-Rule 4 [rejected of counter]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkCou(\MANAGERS, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$))} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}}
-\end{equation}
+Rule 3 [rejected of counter]:
+\begin{mathpar}
+  \inferrule{
+    \NEG\ \CHECKCOU (\MANAGERS, \PUK) \\
+    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
+  }{
+    [
+      \ACCOUNTS, \OP :: \OPERATIONS
+      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to
+    [\ACCOUNTS, \OPERATIONS] \|
+      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
+  }
+\end{mathpar}
 ~\\
 ~\\
-Rule 5 [rejected of balance]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkBal(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}}
-\end{equation}
+Rule 4 [rejected of balance]:
+\begin{mathpar}
+  \inferrule{
+    \NEG\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
+    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
+  }{
+    [
+      \ACCOUNTS, \OP :: \OPERATIONS
+      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
+    [\ACCOUNTS, \OPERATIONS] \|
+      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
+  }
+\end{mathpar}
+~\\
+~\\
+Rule 5 [rejected of fee]:
+\begin{mathpar}
+  \inferrule{
+    \NEG\ \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ) \\
+    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
+  }{
+    [
+      \ACCOUNTS, \OP :: \OPERATIONS
+      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
+    [\ACCOUNTS, \OPERATIONS] \|
+      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
+  }
+\end{mathpar}
 ~\\
@@
   \inferrule[Block-Accept]{
-    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ \\
+    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
     \TIME'-\TIME < 60
   }{
-    \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
-      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']}
-    \SystemTrans \\
-    \langle
-      [\ACCOUNTS, \OPERATIONS, \Angle{\ID, \OPH, \CODE} ::\CONTRACTS],
-      \\
+      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']
+    \SystemTrans
       [\PENDING, \Angle{\OP, \OPH,\TIME,\TIME'} ::  \ACCEPTED, \UPDATESUCC
-      (\MANAGERS, \PUK, \NTEZ, \MTEZ), \Angle{\OPH, \GETSTORAGE
-      (\CODE,\STRING)} :: \CONTRACTORS, \TIME'+1]
-    \rangle
+      (\MANAGERS, \PUK, \NTEZ, \MTEZ), \\ \Angle{\GENERATEHASH(\CODE, \INIT, \TIME, \TIME'), \NTEZ, \CODE, \UPDATESTORAGE(\STRING, '', '')} :: \CONTRACTORS, \TIME'+1]
   }
 \end{mathpar}
-
-% \begin{equation}{}
-% \frac{}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS,
-% \CONTRACTS], [$<$ (originate contract ${id}$ transferring  ${n}$
-% from ${pkh}$ running } \\ 
-% \text{${code}$ init ${s}$), \TIME $>$ :: \PENDING, \ACCEPTED,
-% \MANAGERS, \CONTRACTORS, \TIME' ]$\rangle \rightarrow
-% \langle$[\ACCOUNTS, \OPERATIONS,($< id$, } \\ 
-% \text{generateHash($id, code, s$, \TIME'), $code >$ :: \CONTRACTS)],
-%  [\PENDING, $<$ (originate contract ${id}$ } \\
-% \text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
-% \text{$puk, n, m$), ($<$ generateHash($id, code, s$, \TIME'), $n, code$, } \\
-%  \text{getStorage($code, s$) $>$) :: \CONTRACTORS), \TIME' + 1]$\rangle$}}} 
-% \end{equation}
+~\\
 ~\\
@@
   \inferrule[Block-Timeout]{
-    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ \\
+    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
     \TIME'-\TIME \ge 60
@@
 \end{mathpar}
-% \begin{equation}{}
-% \frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[$<$
-% (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running
-% ${code}$ init ${s}$) $>$ } \\ 
-% \text{:: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ]
-% $\rightarrow$[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$,
-% False), \CONTRACTORS, \TIME']}}}  
-% \end{equation}
 ~\\
@@
 B. \textbf{Transfer}
-\\
-% ~\\
-% Rule 1 [proposal]:
-
-% \begin{equation}{}
-% \frac{\text{checkAcc($pkh$, \ACCOUNTS)  }}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ }  \\
-% \text{fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-% \end{equation}
-% ~\\
 ~\\
-Rule 2 [injected]:
+~\\
+Rule 1 [injected]:
 \begin{mathpar}
@@
     \CHECKPUH (\CONTRACTORS, \PUH) \\
-    \CHECKARG (\CONTRACTORS, \PUH, \STRING) \\
-    \OP =  \TRANSFER[\STRING]\NTEZ\PUK{\PUH}\MTEZ \\
-    \OPH = \GENERATEOPH (\PUK,\PUH, \STRING,\NTEZ, \MTEZ, \TIME)
-  }{
-    \Angle{[\ACCOUNTS, \OP :: \OPERATIONS], 
+    \CHECKARG (\CONTRACTORS, \PUH, \PARAMETER) \\
+    \CHECKGAS (\CONTRACTORS, \PUH, \PARAMETER, \MTEZ) \\
+    \OP =  \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
+    \OPH = \GENERATEOPH (\PUK,\PUH, \PARAMETER,\NTEZ, \MTEZ, \TIME)
+  }{[\ACCOUNTS, \OP :: \OPERATIONS] \|
       [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
-    }
     \SystemTrans \\
-    \Angle{[\ACCOUNTS, \OPERATIONS],
-      [\Angle{\OP, \OPH, \TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(
-      \MANAGERS, \PUK, \TRUE), \CONTRACTORS, \TIME]
-    }
-  }
+    [\ACCOUNTS, \OPERATIONS] \|
+      [\Angle{\OP, \OPH, \TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \TRUE), \CONTRACTORS, \TIME]}
 \end{mathpar}
-% \begin{equation}{}
-% \frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPuh(\CONTRACTORS, $puh$)}
-% \\
-% \text{ $\wedge$ checkArg(\CONTRACTORS, $puh,
-%   s$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from
-%     ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS,
-%     \CONTRACTS], 
-%     [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
-%     $\rangle$}\\
-% \text{$\rightarrow$  $\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), }\\
-%  \text{generateOph($pkh, puh, s, n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), }\\
-% \text{\CONTRACTORS, \TIME] $\rangle$}}} 
-% \end{equation}
 ~\\
 ~\\
-Rule 3 [rejected of counter]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkCou(\MANAGERS, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$  }\\
-\text{$\rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
+Rule 2 [rejected of counter]:
+\begin{mathpar}
+  \inferrule{
+    \NEG\ \CHECKCOU (\MANAGERS, \PUK) \\
+    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
+  }{[\ACCOUNTS, \OP :: \OPERATIONS] \|
+      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
+    \SystemTrans
+    [\ACCOUNTS, \OPERATIONS] \|
+      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}
+\end{mathpar}
 ~\\
 ~\\
-Rule 4 [rejected of balance]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkBal(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$ }\\
-\text{$\rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
+Rule 3 [rejected of balance]:
+\begin{mathpar}
+  \inferrule{
+    \NEG\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
+    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
+  }{[\ACCOUNTS, \OP :: \OPERATIONS] \|
+      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
+    \SystemTrans
+    [\ACCOUNTS, \OPERATIONS] \|
+      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}
+\end{mathpar}
 ~\\
 ~\\
-Rule 5 [rejected of public hash]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkPuh(\CONTRACTORS, $puh$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$ }\\
-\text{$\rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
+Rule 4 [rejected of public hash]:
+\begin{mathpar}
+  \inferrule{
+    \NEG\ \CHECKPUH (\CONTRACTORS, \PUH)\\
+    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
+  }{[\ACCOUNTS, \OP :: \OPERATIONS] \|
+      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
+    \SystemTrans
+    [\ACCOUNTS, \OPERATIONS] \|
+      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}
+\end{mathpar}
 ~\\
 ~\\
-Rule 6 [rejected of argument]:
-
-\begin{equation}{}
-\frac{\text{$\neg$ checkArg(\CONTRACTORS, $puh, s$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}\\
-\text{$\rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
-\end{equation}
+Rule 5 [rejected of argument]:
+\begin{mathpar}
+  \inferrule{
+    \NEG\ \CHECKARG (\CONTRACTORS, \PUH, \PARAMETER)\\
+    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
+  }{[\ACCOUNTS, \OP :: \OPERATIONS] \|
+      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
+    \SystemTrans
+    [\ACCOUNTS, \OPERATIONS] \|
+      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}
+\end{mathpar}
+~\\
+~\\
+Rule 6 [rejected of fee]:
+\begin{mathpar}
+  \inferrule{
+    \NEG\ \CHECKGAS (\CONTRACTORS, \PUH, \PARAMETER, \MTEZ)\\
+    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
+  }{[\ACCOUNTS, \OP :: \OPERATIONS] \|
+      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
+    \SystemTrans
+    [\ACCOUNTS, \OPERATIONS] \|
+      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}
+\end{mathpar}
 ~\\
@@
   \inferrule{
-    \OP = \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ \\
+    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK\PUH\MTEZ \\
     \TIME'-\TIME < 60
@@
     \UPDATESUCC (\MANAGERS, \PUK, '', \NTEZ, \MTEZ),
-    \UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \STRING),
+    \UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \PARAMETER),
     \TIME'+1]
@@
 \end{mathpar}
-% \begin{equation}
-% \frac{}{
-%   \begin{array}{l}
-%     {[\langle \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \OPH, \TIME
-%     \rangle :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']}
-%     \rightarrow \\
-%     {}[\PENDING, \langle \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \OPH, \TIME' \rangle :: \ACCEPTED,  \\
-%     \text{updateSucc(\MANAGERS, \PUK, '', \NTEZ, \MTEZ), updateConstr$(\CONTRACTORS, \PUH, \NTEZ,
-%   s)$, $\TIME' + 1$]}
-%   \end{array}
-% }\label{eq:1}
-% \end{equation}
+\section{Queries}
+Query 1 [balance of an account]:
+\begin{mathpar}
+  \inferrule{
+    \QRY = \GETBALANCE\PUK \\
+    \BLOCKSYSTEM = 
+      [\PENDING, \ACCEPTED,  \Angle{\PUK, \BAL, \COU} :: \MANAGERS, \CONTRACTORS, \TIME]
+  }{\BAL}
+\end{mathpar}
 ~\\
-Rule 8 [timeout]:
-\begin{equation}{}
-  \frac{\TIME' - \TIME \ge 60}{
-    \begin{array}{l}
-      {}[\langle\TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \TIME\rangle ::
-      \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ]
-      \rightarrow \\
-      {}[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE), \CONTRACTORS, \TIME']
-    \end{array}
-    }
-\end{equation}
+~\\
+Query 2 [balance of smart contract]:
+\begin{mathpar}
+  \inferrule{
+    \QRY = \GETBALANCE\PUH \\
+    \BLOCKSYSTEM = 
+      [\PENDING, \ACCEPTED,  \MANAGERS, \Angle{\PUH, \BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
+  }{\BAL}
+\end{mathpar}
+~\\
+~\\
+Query 3 [storage]:
+\begin{mathpar}
+  \inferrule{
+    \QRY = \GETSTORAGE\PUH \\
+    \BLOCKSYSTEM = 
+      [\PENDING, \ACCEPTED,  \MANAGERS, \Angle{\PUH, \BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
+  }{\STORAGE}
+\end{mathpar}
+~\\
+~\\
+Query 4 [code]:
+\begin{mathpar}
+  \inferrule{
+    \QRY = \GETSTORAGE\PUH \\
+    \BLOCKSYSTEM = 
+      [\PENDING, \ACCEPTED,  \MANAGERS, \Angle{\PUH, \BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
+  }{\CODE}
+\end{mathpar}
+~\\
+~\\
+Query 5 [counter]:
+\begin{mathpar}
+  \inferrule{
+    \QRY = \GETCOUNTER\PUK \\
+    \BLOCKSYSTEM = 
+      [\PENDING, \ACCEPTED,  \Angle{\PUK, \BAL, \COU} :: \MANAGERS, \CONTRACTORS, \TIME]
+  }{\COU}
+\end{mathpar}
+~\\
+~\\
+Query 6 [status-pending]:
+\begin{mathpar}
+  \inferrule{
+    \QRY = \GETSTATUS\OPH \\
+    \BLOCKSYSTEM = 
+      [\Angle{\OP, \OPH, \TIME} :: \PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
+  }{\STATUSPENDING}
+\end{mathpar}
+~\\
+~\\
+Query 7 [status-including]:
+\begin{mathpar}
+  \inferrule{
+    \QRY = \GETSTATUS\OPH \\
+    \BLOCKSYSTEM = 
+      [\PENDING, \Angle{\OP, \OPH, \TIME, \TIME'} :: \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
+  }{\STATUSINCLUDING}
+\end{mathpar}
+~\\
+~\\
 
@@
 \begin{enumerate}
-    \item Function \verb!checkAcc(pkh, C)! checks whether an account $pkh$ exists in \ACCOUNTS
-    \item Function \verb!checkPub(K, pkh)! checks whether the public key of the public key hash $pkh$ is reveled to the blockchain.
-    \item Function \verb!checkBal(K, pkh, n, m)! checks whether the balance of the account $pkh$ is greater or equal to $m$ + $n$
-    \item Function \verb!checkCou(K, pkh)! checks whether the current
-      counter of an account $phk$ is unlocked (i.e., its flag is False)
-    \item Function \verb!updateSucc(K, pkh, pkh', n, m)! updates the balance and the counter of the account $phk$ and the balance of the account $phk'$, where
+    \item Function \CHECKPUB (\PUK, \MANAGERS)\ checks whether a public key \PUK\ exists in \MANAGERS.
+    \item Function \CHECKPUH (\PUH, \CONTRACTORS)\ checks whether a public hash \PUH\ exists in \CONTRACTORS.
+    \item Function \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) checks whether the balance of the account that associates with the public key \PUK\ is greater or equal to \NTEZ\ plus \MTEZ.
+    \item Function \CHECKCOU (\MANAGERS, \PUK)\ checks whether the current counter of an account that associates with the public key \PUK\ is unlocked (its flag is False).
+
+    \item Function \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ) updates the balance and the counter of the account that associates with the public key \PUK\ and the balance of the account that associates with the public key \PUK', where
     \begin{itemize}
-        \item  \verb!< puk, pkh, bal, (n, True) >!  \verb!=>! \\ \verb!< puk, pkh, bal - n - m, (n + 1, False) >!
-        \item  \verb!< puk', pkh', bal', cou' >! \verb!=>! \verb!< puk', pkh', bal' + n, cou' >!
+        \item[]  $\langle  \PUK, \BAL, (\NTEZ, \TRUE) \rangle $ $\Rightarrow$ $\langle  \PUK, \BAL - \NTEZ - \MTEZ, (\NTEZ + 1, \FALSE) \rangle $      
+        \item[] $\langle  \PUK', \BAL', \COU' \rangle$ $\Rightarrow$ $\langle  \PUK', \BAL' + \NTEZ, \COU' \rangle $         
     \end{itemize}
 
-    \item Function \verb!updateCou(K, puk, b')! updates the counter
-      lock of the account $phk$ (True $=$ lockeed, False $=$ unlocked), where
+    \item Function \UPDATECOU(\MANAGERS, \PUK, \BOOLEAN) updates the counter flag (True $=$ locked, False $=$ unlocked) of the account that associates with the public key \PUK, where
     \begin{itemize}
-        \item  \verb!< puk, pkh, bal, (n, b) >!  \verb!=>! \verb!< puk, pkh, bal, (n, b') >!
+        \item[]  $\langle  \PUK, \BAL, (\NTEZ, \BOOLEAN') \rangle $ $\Rightarrow$ $\langle  \PUK, \BAL, (\NTEZ, \BOOLEAN) \rangle $ 
     \end{itemize}
 
-    \item Function \verb!checkId(id, S)! checks whether a contract $id$ does not already exist in \CONTRACTS
+    \item Function  \UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \STRING) updates the contractor that associates with the public hash \PUH\, where
+    \begin{itemize}
+        \item[] $\langle  \PUH, \BAL, \CODE, \STORAGE, \rangle $ $\Rightarrow$ $\langle  \PUH, \BAL + \NTEZ, \CODE, \\ \UPDATESTORAGE(\STORAGE,\CODE,\STRING) \rangle $
+    \end{itemize}
 
-    \item Function \verb!checkPrg(code, s)! checks whether the code $code$ are well type and $s$ is well type input
+    \item Function \CHECKPRG (\CODE, {\INIT /\PARAMETER}) checks whether the code \CODE\ and the initil stogare's valude (or the input parameter \PARAMETER) are well type.
+   % \item Function \CHECKGAS(\CODE, \INIT, \MTEZ) checks whether the gas that is consumed to run the code \CODE\ for the initial value \INIT\ is less or equal to \MTEZ.
+    \item Function \CHECKGAS (...) checks whether the fee that is consumed to emit the opertion is less or equal to the fee \MTEZ. 
+    %run the code \CODE\ that associates with the public hash \PUH\ for the paremeter \PARAMETER\ is less or equal to \MTEZ.
+    \item Function \GENERATEOPH (\PUK, {\ADDR /\CODE}, \NTEZ, \MTEZ, {\INIT /\PARAMETER}, \TIME) generates an operation hash.
 
-    %\item Function \verb!addContr(S, id, puh, code)! adds a new  contract $< id, puh, code >$  into \CONTRACTS
+    \item Function \GENERATEHASH (\CODE, \INIT, \TIME, \TIME')  generates the public hash of a smart contract.
 
-    \item Function \verb! generateOph(pkh,pkh', n, m, t)! generates a operation hash
-
-    \item Function \verb!generateHash(S, id, puh, code, t)! generates the public hash of a contract
-
-   % \item Function \verb!addOrig(T,< hash, 0, code, storage >)! add the a new originator $\langle  puh$, 0, $code, storage \rangle $ 
-    \item Function \verb!getStorage(code, s)! gets the storage for the code $code$ and the input $s$
+    \item Function \UPDATESTORAGE(\STORAGE, \CODE,  \PARAMETER) returns the new storage by running the code \CODE\ on the  storage  \STORAGE\ with  the input parameter \PARAMETER.
 \end{enumerate}
-
-\section{Some implementations}
-Function \verb!checkAcc(puh, C)! checks whether an account exists and and \verb!checkPuk(puh, K)! checks the revelation of its public key to the blockchain.
-\begin{verbatim}
-let rec checkAcc puh C =
-  match C with
-  | 0 -> false
-  | < als, pak, puk, pkh' > :: C' ->
-    if (puh = puh')  then true 
-    else checkAcc (puh, C')
-\end{verbatim}
-
-\begin{verbatim}
-let rec checkPuk puh K =
-  match C with
-  | 0 -> false
-  | < als, pak, puk, pkh' > :: K' ->
-    if (puh = puh') and (puk =/= nil) then true 
-    else 5checkPuk (puh, K')
-\end{verbatim}
-
-The following functions interact with $\MANAGERS$.
-
-\begin{verbatim}
-let rec checkBal K puk n m =
-  match K with
-  | 0 -> true
-  | < puk', bal, cou > :: K' ->
-    if (puk = puk') and (n + m) <= bal then true 
-    else checkBal (K', puk, n, m)
-\end{verbatim}
-
-\begin{verbatim}
-let rec checkPub K puk =
-  match K with
-  | 0 -> false
-  | < puk', bal, cou > :: K' ->
-    if (puk = puk') then true 
-    else checkExi (K', puk)
-\end{verbatim}
-
-\begin{verbatim}
-let rec checkCou K puk =
-  match K with
-  | 0 -> false
-  | < puk', bal, cou > :: K' ->
-    if (puk = puk') and (cou = T) then true 
-    else checkCou (K', puk)
-\end{verbatim}
-
-\begin{verbatim}
-let rec updateCou K puk =
-  match K with
-  | 0 -> 0
-  | < puk', bal, cou > :: K' ->
-    if (puk = puk') then < puk', bal, F > :: K'
-    else < puk', bal, cou > :: updateCou (K', puk)
-\end{verbatim}
-
-\begin{verbatim}
-let rec updateSucc K puk puk' m n =
-  match K with
-  | 0 -> 0
-  | < puk'', bal, cou > :: K' ->
-    if (puk = puk'') then < puk'', bal - (n + m), T > 
-       :: updateSucc (K', puk, puk', n, m)
-    else if (puk' = puk'') then < puk'', bal + n, cou > :: K'
-         else  < puk'', bal, cou > 
-               ::updateSucc (K', puk, puk', n, m)
-\end{verbatim}
-
 \end{document}

### 2020-11-25 papers/contract-modules/modules.tex
update
syntax

@@
 
+Suppose the parameter type of a smart contract is defined by this Michelson code:
+\begin{verbatim}
+parameter union (int %bid_for_auction) (unit %close_auction)
+...
+\end{verbatim}
+
 \begin{lstlisting}[language=caml]
-contract module MyContract = "kt1..."
-  entry point bid_for_auction Left (_ : int) 
+contract type MyContract = sig
+  entrypoint %bid_for_auction (_ : int) 
   raises "closed" as closed       (* auction closed*)
-         "bid too low" as too_low (* bid received is too low *)
-         42 as the_answer         (* failwith received argument 42 *)
-         (_ : int) as failedwith  (* failwith received an integer arg *)
+       | "bid too low" as too_low (* bid received is too low *)
+       | 42 as the_answer         (* failwith received argument 42 *)
+       | (_ : int) as failedwith  (* failwith received an integer arg *)
 
-  entry point close_auction Right (_ : unit)
+  entrypoint %close_auction (_ : unit)
   raises "not owner"         (* caller cannot close the auction *)
+end
 \end{lstlisting}
@@
 \begin{lstlisting}[language=caml]
-signature MyContract =
+module type MyContract =
 sig 
@@
 
+A starting point for the implementation could be the module \lstinline/Tezos_micheline/, which has a
+Michelson parser.
+
 \end{document}

### 2020-11-25 papers/execution-model/model.tex

@@
 
+\begin{definition}%[Query]
+\emph{Queries} are defined by the following grammar:
+\begin{align*}
+  \QRY & ::= \GETBALANCE\ADDR
+  \\&\mid \GETSTATUS\OPH
+  \\&\mid \GETSTORAGE\PUH
+  \\&\mid \GETCODE\PUH 
+  \\&\mid \GETCOUNTER\PUK
+\end{align*}
+\end{definition}
+
+\begin{definition}%[Program]
+\emph{Programs} are defined by the following grammar:
+\begin{align*}
+	\PROGRAM & :: =  \VARIABLE\ \mid \VALUE \mid \lambda \VARIABLE \PROGRAM\ 
+	\\&\mid \PROGRAM\PROGRAM\ \mid (\PROGRAM,\PROGRAM) 	%\mid \NI \EI
+	\\&\mid \PROGRAM\ \PLUS\ \PROGRAM\ \mid \PROGRAM\ \MINUS\ \PROGRAM\ \mid \PROGRAM\ \EQUAL\ \PROGRAM\ \mid \PROGRAM\ \LESS\ \PROGRAM
+	\\&\mid \PROGRAM\ \AND\ \PROGRAM\ \mid \PROGRAM\ \OR\ \PROGRAM\ \mid \NOT\ \PROGRAM
+	\\&\mid \NIL\ \mid \CONS\ \PROGRAM \PROGRAM
+	\\&\mid \lambda \VARIABLE\QRY
+\end{align*}
+\end{definition}
+
 \begin{definition}%[State of a node]
   The \emph{state of a node} is a tuple
-  $\NODE = [\ACCOUNTS, \OPERATIONS]$, where $\ACCOUNTS$ is a set of
-  accounts and
+  $\NODE = [ \PROGRAMS, \ACCOUNTS, \OPERATIONS]$, where $\PROGRAMS$ is the set of the programs, $\ACCOUNTS$ is a set of
+  accounts, and
   $\OPERATIONS$ is a set of operations.
@@
 
-\begin{definition}%[Query]
-A \emph{query} is defined by the following grammar:
-\begin{align*}
-  \QRY & ::= \GETBALANCE\ADDR
-  \\&\mid \GETSTATUS\OPH
-  \\&\mid \GETSTORAGE\PUH
-  \\&\mid \GETCODE\PUH 
-  \\&\mid \GETCOUNTER\PUK
-\end{align*}
-
-\end{definition}
-
 When an operation is injected in a node, it enters a \emph{pending pool}
 (and is called a \emph{pending operation}).
+
  \begin{definition}%[Pending operation]
@@
 \end{definition}
+
 After some time, a pending operation may be included in the blockchain as an accepted operation.
-%Let \textit{P} is the set of pending operations.
+
  \begin{definition}%[Accepted operation]
@@
   \inferrule[Node-Op]
-  { % \CHECKACC (\OP.\PUK, \ACCOUNTS)
+  {
     \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS
-    % \\
-    % \OP = \TRANSFER[\STRING]\NTEZ\PUK{\PUK'}\MTEZ
   }{
-    [\ACCOUNTS, \OPERATIONS]
+    [\PROGRAMS, \ACCOUNTS, \OPERATIONS]
     \NodeTrans
-    [\ACCOUNTS, \OP:: \OPERATIONS]
+    [\PROGRAMS, \ACCOUNTS, \OP:: \OPERATIONS]
+  }
+
+  \inferrule[Node-Oph]
+  {
+   \\
+  }{
+    [\epsilon[\OP] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]
+    \NodeTrans
+    [\epsilon[\OPH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]
   }
@@
       [\PENDING, \Angle{\OP, \OPH,\TIME,\TIME'} ::  \ACCEPTED, \UPDATESUCC
-      (\MANAGERS, \PUK, \NTEZ, \MTEZ), \\ \Angle{\GENERATEHASH(\CODE, \INIT, \TIME, \TIME'), \NTEZ, \CODE, \UPDATESTORAGE(\STRING, '', '')} :: \CONTRACTORS, \TIME'+1]
+      (\MANAGERS, \PUK, \NTEZ, \MTEZ), \\ \Angle{\GENERATEHASH(\CODE, \INIT, \TIME, \TIME'), \NTEZ, \CODE, \STRING} :: \CONTRACTORS, \TIME'+1]
   }
@@
   \inferrule{
-    \QRY = \GETBALANCE\PUK \\
-    \BLOCKSYSTEM = 
+    \BLOCKCHAIN = 
       [\PENDING, \ACCEPTED,  \Angle{\PUK, \BAL, \COU} :: \MANAGERS, \CONTRACTORS, \TIME]
-  }{\BAL}
+  }{[\epsilon[\GETBALANCE\PUK] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
+    \NodeTrans [\epsilon[\BAL] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   \inferrule{
-    \QRY = \GETBALANCE\PUH \\
     \BLOCKSYSTEM = 
       [\PENDING, \ACCEPTED,  \MANAGERS, \Angle{\PUH, \BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
-  }{\BAL}
+  }{[\epsilon[\GETBALANCE\PUH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
+    \NodeTrans [\epsilon[\BAL] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   \inferrule{
-    \QRY = \GETSTORAGE\PUH \\
     \BLOCKSYSTEM = 
       [\PENDING, \ACCEPTED,  \MANAGERS, \Angle{\PUH, \BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
-  }{\STORAGE}
+  }{[\epsilon[\GETSTORAGE\PUH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
+    \NodeTrans [\epsilon[\STORAGE] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   \inferrule{
-    \QRY = \GETSTORAGE\PUH \\
     \BLOCKSYSTEM = 
       [\PENDING, \ACCEPTED,  \MANAGERS, \Angle{\PUH, \BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
-  }{\CODE}
+  }{[\epsilon[\GETCODE\PUH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
+    \NodeTrans [\epsilon[\CODE] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   \inferrule{
-    \QRY = \GETCOUNTER\PUK \\
     \BLOCKSYSTEM = 
       [\PENDING, \ACCEPTED,  \Angle{\PUK, \BAL, \COU} :: \MANAGERS, \CONTRACTORS, \TIME]
-  }{\COU}
+  }{[\epsilon[\GETCOUNTER\PUK] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
+    \NodeTrans [\epsilon[\COU] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   \inferrule{
-    \QRY = \GETSTATUS\OPH \\
     \BLOCKSYSTEM = 
       [\Angle{\OP, \OPH, \TIME} :: \PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
-  }{\STATUSPENDING}
+  }{[\epsilon[\GETSTATUS\OPH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
+    \NodeTrans [\epsilon[\STATUSPENDING] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   \inferrule{
-    \QRY = \GETSTATUS\OPH \\
     \BLOCKSYSTEM = 
       [\PENDING, \Angle{\OP, \OPH, \TIME, \TIME'} :: \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
-  }{\STATUSINCLUDING}
+  }{[\epsilon[\GETSTATUS\OPH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
+    \NodeTrans [\epsilon[\STATUSINCLUDING] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
 
-    \item Function  \UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \STRING) updates the contractor that associates with the public hash \PUH\, where
+    \item Function  \UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \PARAMETER) updates the contractor that associates with the public hash \PUH\, where
     \begin{itemize}
-        \item[] $\langle  \PUH, \BAL, \CODE, \STORAGE, \rangle $ $\Rightarrow$ $\langle  \PUH, \BAL + \NTEZ, \CODE, \\ \UPDATESTORAGE(\STORAGE,\CODE,\STRING) \rangle $
+        \item[] $\langle  \PUH, \BAL, \CODE, \STORAGE, \rangle $ $\Rightarrow$ $\langle  \PUH, \BAL + \NTEZ, \CODE, \\ \UPDATESTORAGE(\STORAGE,\CODE,\PARAMETER) \rangle $
     \end{itemize}

### 2020-11-25 papers/execution-model/model.tex
after-meeting

@@
 \begin{definition}%[Program]
-\emph{Programs} are defined by the following grammar:
+\emph{Expressions} are defined by the following grammar:
 \begin{align*}
-	\PROGRAM & :: =  \VARIABLE\ \mid \VALUE \mid \lambda \VARIABLE \PROGRAM\ 
-	\\&\mid \PROGRAM\PROGRAM\ \mid (\PROGRAM,\PROGRAM) 	%\mid \NI \EI
-	\\&\mid \PROGRAM\ \PLUS\ \PROGRAM\ \mid \PROGRAM\ \MINUS\ \PROGRAM\ \mid \PROGRAM\ \EQUAL\ \PROGRAM\ \mid \PROGRAM\ \LESS\ \PROGRAM
-	\\&\mid \PROGRAM\ \AND\ \PROGRAM\ \mid \PROGRAM\ \OR\ \PROGRAM\ \mid \NOT\ \PROGRAM
-	\\&\mid \NIL\ \mid \CONS\ \PROGRAM \PROGRAM
-	\\&\mid \lambda \VARIABLE\QRY
+  \CONSTANT & ::= \ADDR \mid \OPH \mid \PUH \mid\PUK \mid \CODE \mid
+              \NTEZ \mid \SUNIT \mid \FALSE \mid \TRUE \\
+	\EXPR & :: =  \CONSTANT \mid \VARIABLE \mid \lambda \VARIABLE. \EXPR\ 
+	\mid \EXPR\EXPR \mid (\EXPR,\EXPR) \mid \FST\ \EXPR \mid \SND\ \EXPR 	%\mid \NI \EI
+	\\&\mid \EXPR\ \PLUS\ \EXPR\ \mid \EXPR\ \MINUS\ \EXPR\ \mid \EXPR\ \EQUAL\ \EXPR\ \mid \EXPR\ \LESS\ \EXPR
+	\\&\mid \EXPR\ \AND\ \EXPR\ \mid \EXPR\ \OR\ \EXPR\ \mid \NOT\ \EXPR
+  \\&\mid \NIL\ \mid \CONS\ \EXPR\ \EXPR \mid \LEFT\ \EXPR \mid\RIGHT\
+  \EXPR \mid \SOME\ \EXPR \mid \NONE
+  \\& \mid \RAISE\ \EXPR \mid \TRY\ \EXPR\ \EXCEPT\ \EXPR
+  \\& \mid \MATCH\ \EXPR\ \WITH\ \PATTERN\to\EXPR \dots
+  \\& \mid \TRANSFER[\EXPR]\EXPR\EXPR\EXPR\EXPR
+  \\& \mid \ORIGINATE\EXPR\EXPR\EXPR\EXPR\EXPR
+  \\&\mid \QOP\  \EXPR\\
+  \QOP & ::= balance \mid status \mid storage \mid code \mid counter
 \end{align*}
@@
   The \emph{state of a node} is a tuple
-  $\NODE = [ \PROGRAMS, \ACCOUNTS, \OPERATIONS]$, where $\PROGRAMS$ is the set of the programs, $\ACCOUNTS$ is a set of
+  $\NODE = [ \EXPRS, \ACCOUNTS, \OPERATIONS]$, where $\EXPRS$ is the set of the programs, $\ACCOUNTS$ is a set of
   accounts, and
@@
 
+\begin{mathpar}
+  \inferrule[Node-Opp]
+    {
+    \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS
+  }{
+    [\EC\OP :: \EXPRS, \ACCOUNTS, \OPERATIONS] \NodeTrans
+    [\EXPRS, \ACCOUNTS, (\EC{},\OP):: \OPERATIONS]
+  }
+\end{mathpar}
+
+\begin{mathpar}
+  \inferrule{
+    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
+    \CHECKCOU (\MANAGERS, \PUK) \\
+    \CHECKPUB (\MANAGERS, \PUK') \\
+    \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
+    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ, \TIME)
+  }{
+   { [\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \| [\PENDING,
+     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
+   { [\EC{?\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
+     [ \Angle{\OP,\OPH, \TIME}
+     ::\PENDING,
+     \ACCEPTED,
+     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
+     \CONTRACTORS,
+     \TIME]
+   }
+  }
+\end{mathpar}
+
 \subsection{Transitions on Nodes}
@@
   }{
-    [\PROGRAMS, \ACCOUNTS, \OPERATIONS]
+    [\EXPRS, \ACCOUNTS, \OPERATIONS]
     \NodeTrans
-    [\PROGRAMS, \ACCOUNTS, \OP:: \OPERATIONS]
+    [\EXPRS, \ACCOUNTS, \OP:: \OPERATIONS]
   }
@@
   }{
-    [\epsilon[\OP] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]
+    [\EC\OP :: \EXPRS, \ACCOUNTS, \OPERATIONS]
     \NodeTrans
-    [\epsilon[\OPH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]
+    [\EC\OPH :: \EXPRS, \ACCOUNTS, \OPERATIONS]
   }
@@
       [\PENDING, \ACCEPTED,  \Angle{\PUK, \BAL, \COU} :: \MANAGERS, \CONTRACTORS, \TIME]
-  }{[\epsilon[\GETBALANCE\PUK] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans [\epsilon[\BAL] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+  }{[\epsilon[\GETBALANCE\PUK] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
+    \NodeTrans [\epsilon[\BAL] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
       [\PENDING, \ACCEPTED,  \MANAGERS, \Angle{\PUH, \BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
-  }{[\epsilon[\GETBALANCE\PUH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans [\epsilon[\BAL] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+  }{[\epsilon[\GETBALANCE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
+    \NodeTrans [\epsilon[\BAL] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
       [\PENDING, \ACCEPTED,  \MANAGERS, \Angle{\PUH, \BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
-  }{[\epsilon[\GETSTORAGE\PUH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans [\epsilon[\STORAGE] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+  }{[\epsilon[\GETSTORAGE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
+    \NodeTrans [\epsilon[\STORAGE] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
       [\PENDING, \ACCEPTED,  \MANAGERS, \Angle{\PUH, \BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
-  }{[\epsilon[\GETCODE\PUH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans [\epsilon[\CODE] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+  }{[\epsilon[\GETCODE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
+    \NodeTrans [\epsilon[\CODE] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
       [\PENDING, \ACCEPTED,  \Angle{\PUK, \BAL, \COU} :: \MANAGERS, \CONTRACTORS, \TIME]
-  }{[\epsilon[\GETCOUNTER\PUK] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans [\epsilon[\COU] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+  }{[\epsilon[\GETCOUNTER\PUK] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
+    \NodeTrans [\epsilon[\COU] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
       [\Angle{\OP, \OPH, \TIME} :: \PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
-  }{[\epsilon[\GETSTATUS\OPH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans [\epsilon[\STATUSPENDING] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+  }{[\epsilon[\GETSTATUS\OPH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
+    \NodeTrans [\epsilon[\STATUSPENDING] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
       [\PENDING, \Angle{\OP, \OPH, \TIME, \TIME'} :: \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
-  }{[\epsilon[\GETSTATUS\OPH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans [\epsilon[\STATUSINCLUDING] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+  }{[\epsilon[\GETSTATUS\OPH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
+    \NodeTrans [\epsilon[\STATUSINCLUDING] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}

### 2020-11-26 papers/contract-modules/modules.tex
more specific

--- 2020-10-20 papers/contract-modules/modules.tex
@@
 \usepackage{fixme}
+\usepackage{listings}
+
+\lstset{
+  language=caml,
+  morekeywords={contract,sig,entrypoint,module,raises,val},
+  % predefined types
+  classoffset=1,
+  morekeywords={nat,int,unit,string},
+  keywordstyle=\color{blue},
+  classoffset=2,
+  morekeywords={Left,Right},
+  keywordstyle=\color{magenta},
+  backgroundcolor=\color{brown!20}
+}
+
+\lstdefinelanguage{michelson}{
+  % basicstyle=\ttfamily{},
+  classoffset=0,
+  morekeywords={parameter,storage,code},
+  keywordstyle=\bfseries, 
+  % predefined types
+  classoffset=1,
+  morekeywords={nat,int,unit,string,union,pair,option,address},
+  keywordstyle=\color{blue},
+  classoffset=2,
+  morekeywords={CAR,CDR,CONS,DUP,EQ,FAILWITH,IF,IF_LEFT,LE,LEFT,NIL,POP,PUSH,RIGHT,SENDER,SUB},
+  keywordstyle=\color{magenta},
+  backgroundcolor=\color{pink!20}
+}
 
 \title{Contract Modules}
-\author{}
+\author{Peter Thiemann}
 \institute{}
@@
 
+\section{Motivation}
+\label{sec:motivation}
+
+Consider this Michelson code fragment:
+\begin{lstlisting}[language=michelson,caption={Michelson code example},label={lst:code-example}]
+parameter (union (int %bid_for_auction)
+                 (unit %close_auction));
+storage address;
+code { DUP; CAR; 
+       IF_LEFT {
+       # %bid_for_auction
+        DUP; PUSH int 10000; SUB; LE;
+        IF { FAILWITH; } {} # fails with argument value
+        # ...
+        { PUSH string "closed"; FAILWITH; }
+        # ...
+        { PUSH string "bid too low"; FAILWITH; }
+        # ...
+        { PUSH int 42; FAILWITH; }
+        # ...
+       }
+       {
+       # %close_auction
+         POP; CDR; SENDER; EQ;
+         IF {} { PUSH string "not owner"; FAILWITH; }
+         # ...
+       }
+     }
+\end{lstlisting}
+
+Here is a contract type that describes / specifies the above Michelson code.
+\begin{lstlisting}[caption={Contract module example},label={lst:contract-module-example}]
+contract type MyContract = sig
+  entrypoint %bid_for_auction (_ : int) 
+  raises "closed" as closed       (** auction closed*)
+       | "bid too low" as too_low (** bid received is too low *)
+       | 42 as the_answer         (** failwith received argument 42 *)
+       | (_ : int) as failedwith  (** failwith received an integer arg *)
+
+  entrypoint %close_auction (_ : unit)
+  raises "not owner"         (** caller cannot close the auction *)
+end
+\end{lstlisting}
+
+Alternatively and equivalently, the contracts can be specified using
+patterns on the default entrypoint.
+
+\begin{lstlisting}
+...
+  entrypoint bid_for_auction (Left (_ : int))
+...
+  entrypoint close_auction (Right (_ : unit))
+\end{lstlisting}
+
+The contract module is compiled to an OCaml module which provides a typed API to the
+contract. It includes the documentation comments from the contract
+module. Internally, the typed API builds on the untyped API developed
+by us.
+
+\begin{lstlisting}
+module type MyContract =
+sig
+  type bid_for_auction_errors = 
+     | closed       (** auction closed*)
+     | too_low      (** bid received is too low *)
+     | the_answer   (** failwith received argument 42 *)
+     | failedwith of int (** failwith received an integer arg *)
+
+  val bid_for_auction
+    : int -> (status, bid_for_auction_errors) Tezos.monad
+
+  type close_auction_errors = 
+     | not_owner    (** caller cannot close the auction *)
+
+  val close_auction
+    : unit -> (status, close_auction_errors) Tezos.monad
+end
+\end{lstlisting}
+
+\begin{itemize}
+\item The type \lstinline/Tezos.monad/ is defined by the underlying
+  API. The untyped API uses a type \lstinline/Answer.t/. The exact
+  relationship is TBD.
+\item Error reporting assumes that the monad returns a sum type. But
+  things could be handled differently (for the
+  \lstinline/close_auction/entrypoint): by an error continuation of
+  type \lstinline/close_auction_errors -> Answer.t/ or by
+  raising an exception that encapsulates the error type:
+\begin{lstlisting}
+exception Close_Auction_Exn of close_auction_errors
+\end{lstlisting}
+\end{itemize}
+
+If the contract source is available, then an extended type checker verifies that the entry points
+exist and that all failures that may arise during contract execution from a particular entry point
+are covered by the listed cases.
+
+If the contract source is unavailable, then we can obtain it from the
+contract's public hash using an API call. In that case, we would
+specify the hash in the contract header as follows
+\begin{lstlisting}
+contract type MyContract "KT1ThEdxfUcWUwqsdergy..." = sig
+...
+\end{lstlisting}
+
+We propose to deal with the remaining errors (i.e., built-in errors
+and failures that are not specifed) like Java's unchecked
+exceptions. That is, the API function throws an exception.
+
+\clearpage
+\section{Tools}
+\label{sec:tools}
+
+An extended type checker collects information about explicit failures along execution paths
+starting from each possible entry point. This checker will be able to
+verify the contract module specification in
+\ref{lst:contract-module-example} against the Michelson code in
+\ref{lst:code-example}. We may also wish to provide an entry point so
+that the checker only gathers information for that entry point. This alternative may be interesting if there
+is an entry point taking a parameter of sum type, rather than using all injections to distinguish
+between entry points.
+
+The recommended technology for the type checker is symbolic
+execution. In this framework, it would also 
+be possible to specify further invariants about the inputs and place them into the contract
+module. Essentially, every formula that an SMT solver can deal with
+should be fine, although a first version of the symbolic executor
+could work without using SMT.
+
+A starting point for the implementation could be the module \lstinline/Tezos_micheline/, which has a
+Michelson parser.
+
 \end{document}

### 2020-11-26 papers/contract-modules/modules.tex
even more specific - fragments of an implementation

@@
   language=caml,
-  morekeywords={contract,sig,entrypoint,module,raises,val},
+  morekeywords={contract,entrypoint,module,hash,paid,raises,sig,val},
   % predefined types
   classoffset=1,
-  morekeywords={nat,int,unit,string},
+  morekeywords={nat,int,unit,string,pukh,status,tz},
   keywordstyle=\color{blue},
@@
   keywordstyle=\color{magenta},
-  backgroundcolor=\color{brown!20}
+  backgroundcolor=\color{brown!20},
+  captionpos=b,
+  literate={->}{{$\to$}}1
 }
@@
 
-\title{Contract Modules}
+\title{Whitepaper: Contract Modules}
 \author{Peter Thiemann}
@@
 contract type MyContract = sig
-  entrypoint %bid_for_auction (_ : int) 
-  raises "closed" as closed       (** auction closed*)
+  paid entrypoint %bid_for_auction (value : int) 
+  raises "closed"                 (** auction closed*)
        | "bid too low" as too_low (** bid received is too low *)
@@
 
+The body of the \lstinline/sig ... end/ can be stored in a
+\texttt{.tzm} file where the basename matches the one of the
+\texttt{.tz} file. The output is a \texttt{.mli} file which contains a
+valid OCaml signature. In the next step, we are also generating the
+corresponding \texttt{.ml} file implementing the signature.
+
+Each \lstinline/entrypoint/ is mapped to a function. The final pattern
+variable may be a wildcard \lstinline/_/ or an OCaml identifier, which
+is used in generating the implementation. For \lstinline/_/ a standard
+name will be generated.
+
+A \lstinline/paid/ entrypoint requires the caller to specify an amount of tokens to
+accompany the contract invocation. Accordingly, the generated function has an extra
+argument. Otherwise, the entrypoint is unpaid.
+
+The \lstinline/raises/ clauses specify values that the contract might
+pass to the \texttt{FAILWITH} instruction. The \lstinline/as/ clause
+maps the matched value to an OCaml identifier, which is used to
+generate the corresponding case in the error type. There is a standard
+translation (to be specified) that maps a value without an
+\lstinline/as/ clause to an identifier.
+
 Alternatively and equivalently, the contracts can be specified using
@@
 
-\begin{lstlisting}
-...
-  entrypoint bid_for_auction (Left (_ : int))
+\begin{lstlisting}[caption={Alternative syntax for entrypoints},label={lst:alternative-syntax}]
+  paid entrypoint bid_for_auction (Left (_ : int))
 ...
@@
 
-\begin{lstlisting}
+\begin{lstlisting}[caption={Generated signature},label={lst:generated-signature}]
 module type MyContract =
@@
   val bid_for_auction
-    : int -> (status, bid_for_auction_errors) Tezos.monad
+    : Tezos.pukh -> ?fee:Tezos.tz -> Tezos.tz
+    -> int -> (Tezos.status, bid_for_auction_errors) Tezos.monad
 
@@
   val close_auction
-    : unit -> (status, close_auction_errors) Tezos.monad
+    : Tezos.pukh -> ?fee:Tezos.tz -> ?amount:Tezos.tz
+    -> unit -> (Tezos.status, close_auction_errors) Tezos.monad
 end
@@
 \begin{itemize}
+\item The first argument is the public key hash of the caller. 
+\item The \lstinline/paid/ entrypoint requires an \lstinline/amount/
+  argument, which is optional (with default 0) for an unpaid
+  entrypoint.
+\item The \lstinline/fee/ parameter is optional in both
+  cases. It is precomputed and supplied as the default value in the
+  implementation.
+
+  Q (extension): Would it make sense to specify something about fees in the
+  contract module? For example, we might specify a fee schedule which
+  raises the fee until the call is accepted.
 \item The type \lstinline/Tezos.monad/ is defined by the underlying
@@
 contract's public hash using an API call. In that case, we would
-specify the hash in the contract header as follows
+specify the hash in the contract.
 \begin{lstlisting}
-contract type MyContract "KT1ThEdxfUcWUwqsdergy..." = sig
+sig
+  hash "KT1ThEdxfUcWUwqsdergy..."
 ...
@@
 
-We propose to deal with the remaining errors (i.e., built-in errors
+We propose to treat the remaining errors (i.e., built-in errors
 and failures that are not specifed) like Java's unchecked
 exceptions. That is, the API function throws an exception.
+
+\begin{lstlisting}[caption={Generated implementation},label={lst:generated-implementation}]
+(* constant template *)
+open Tezos_api
+open Tezos_serialization (* Tint, Tunit, serialize, ... *)
+
+let failwith_regex = 
+  "A FAILWITH instruction was reached.*"
+let int_regex = 
+  "[+-]?[0-9]+"
+
+(* variable part *)
+let contract_addr = 
+  get_contract "KT1ThEdxfUcWUwqsdergy..." >>=? fun contract -> ???
+
+type bid_for_auction_errors = 
+   | closed       (** auction closed*)
+   | too_low      (** bid received is too low *)
+   | the_answer   (** failwith received argument 42 *)
+   | failedwith of int (** failwith received an integer arg *)
+
+let big_for_auction_errors_map =
+  let open Base in
+  Base.Map.of_alist_exn (module String)
+    [
+      (failwith_regex ^ "closed", closed);
+      (failwith_regex ^ "bid too low", too_low);
+      (failwith_regex ^ "42", the_answer);
+      (failwith_regex ^ int_regex, failedwith (0)); (* badness 10000 *)
+    ]
+  (* inadequate in several ways;
+   * should just generate code instead of using a map*)
+
+let bid_for_auction destination ?(fee=100.0) amount value =
+  ...
+  begin
+    SyncAPIV0.call_contract
+      amount
+      destination
+      contract_addr
+      ~(serialize Tint value)
+      fee
+    >>=? fun oph ->
+    wait_for_inclusion oph (* busy waiting *)
+    >>=? fun _ ->
+    return 0
+  end
+  >>= function
+  | Ok _ -> ...
+  | Error (Rejection Michelson_runtime_error s) -> ...
+
+type close_auction_errors = 
+   | not_owner    (** caller cannot close the auction *)
+
+let close_auction destination ?(fee=50.0) ?(amount=0.0) _ =
+  ...
+  SyncAPIV0.call_contract
+    amount
+    destination
+    contract_addr
+    ~(serialize Tunit)
+    fee
+\end{lstlisting}
 
@@
 
+The checker should warn about unhandled failures (both checked and unchecked).
+
 The recommended technology for the type checker is symbolic
@@
 
+The checker should also make sure that unpaid entrypoints do not
+depend on a non-zero amount being passed to the contract
+invocation. For example, the \texttt{AMOUNT} instruction of Michelson
+should not be used in the code.
+
+The checker should precalculate the fee. It essentially obtains
+this value from the Tezos library.
+
+Failures might arise in contracts that are transitively invoked. In
+this case, the checker would obtain the callees' code and process
+it. The first step, not too difficult, in this direction would be to
+approximate the contents of the list of operations that is produced by
+the contract.
+
 A starting point for the implementation could be the module \lstinline/Tezos_micheline/, which has a

### 2020-12-03 meeting-notes/20201108-expose-input-language.tex

@@
 
-The current Tezos API facing to OCaml (as well as the one provided by
-the Tezos client) is untyped. Here we propose a DSL to make it typed.
+The current Tezos API for invoking contracts with parameters is
+untyped. This manifests in the input of the Tezos client where
+parameters have to be supplied as strings and are then parsed before
+they are passed to the contract execution. For example:
+\begin{lstlisting}[language=sh]
+tezos-client transfer 10000 from contractOwner to v1-public-pool 
+--arg '(Left Unit)' --burn-cap 0.004
+\end{lstlisting}
+This is also true for the first cut of the OCaml API.
+
+ Here we propose a DSL to make it typed.
 First we recall some information from the Michelson white paper
@@
 \end{lstlisting}
+
+Query the Tezos blockchain for the type of a contract and its
+entrypoints.
+\begin{lstlisting}[language=Caml]
+make_typed_contract : contract_hash -> 't Mtype -> 't Contract
+\end{lstlisting}
+The function call \lstinline/make_typed_contract hash mty/ would query
+the node (via client lib or rpc) for the type of the contract
+\lstinline/hash/ and check it against \lstinline/mty/.
+This call fails if the type \lstinline/mty/ does not match the
+stored type of the contract.
+The returned value contains the serializer from \lstinline/'t -> string/.
+\begin{lstlisting}[language=Caml]
+invoke_typed : 't Contract -> 't -> result Tezos.apimonad
+\end{lstlisting}
 \end{document}

### 2020-12-03 papers/contract-modules/modules.tex

@@
   classoffset=1,
-  morekeywords={nat,int,unit,string,union,pair,option,address},
+  morekeywords={nat,int,unit,string,or,pair,option,address},
   keywordstyle=\color{blue},
   classoffset=2,
-  morekeywords={CAR,CDR,CONS,DUP,EQ,FAILWITH,IF,IF_LEFT,LE,LEFT,NIL,POP,PUSH,RIGHT,SENDER,SUB},
+  morekeywords={CAR,CDR,CONS,DUP,EQ,FAILWITH,IF,IF_LEFT,LE,LEFT,NIL,DROP,PUSH,RIGHT,SENDER,SUB},
   keywordstyle=\color{magenta},
@@
 \begin{lstlisting}[language=michelson,caption={Michelson code example},label={lst:code-example}]
-parameter (union (int %bid_for_auction)
+parameter (or (int %bid_for_auction)
               (unit %close_auction));
@@
        # %close_auction
-         POP; CDR; SENDER; EQ;
+         DROP; CDR; SENDER; EQ;
          IF {} { PUSH string "not owner"; FAILWITH; }

### 2020-12-04 papers/contract-modules/modules.tex
update

@@
 
-Here is a contract type that describes / specifies the above Michelson code.
+Here is a \textbf{contract module} that describes / specifies the above Michelson code.
 \begin{lstlisting}[caption={Contract module example},label={lst:contract-module-example}]
@@
 
-The body of the \lstinline/sig ... end/ can be stored in a
+To specify the contract module, we store
+the body of the \lstinline/sig ... end/ in a
 \texttt{.tzm} file where the basename matches the one of the
-\texttt{.tz} file. The output is a \texttt{.mli} file which contains a
-valid OCaml signature. In the next step, we are also generating the
-corresponding \texttt{.ml} file implementing the signature.
+\texttt{.tz} file which implements the contract.
 
-Each \lstinline/entrypoint/ is mapped to a function. The final pattern
-variable may be a wildcard \lstinline/_/ or an OCaml identifier, which
+A contract module gets compiled to an \texttt{.mli} file which contains a
+valid OCaml signature and the corresponding \texttt{.ml} file
+implementing the signature.
+
+Each \lstinline/entrypoint/ is mapped to a function. The variables
+used in the pattern may be a wildcard \lstinline/_/ or an OCaml identifier, which
 is used in generating the implementation. For \lstinline/_/ a standard
@@
   val bid_for_auction
-    : Tezos.pukh -> ?fee:Tezos.tz -> Tezos.tz
+    : Tezos.pukh -> ?fee:Tezos.tz -> amount:Tezos.tz
     -> int -> (Tezos.status, bid_for_auction_errors) Tezos.monad
@@
 let contract_addr = 
-  get_contract "KT1ThEdxfUcWUwqsdergy..." >>=? fun contract -> ???
+  get_contract "KT1ThEdxfUcWUwqsdergy..." >>=? 
+  fun ca -> ???
 
@@
       (failwith_regex ^ "42", the_answer);
-      (failwith_regex ^ int_regex, failedwith (0)); (* badness 10000 *)
+      (failwith_regex ^ int_regex, failedwith (0)); 
+      (* badness 10000: actual implementation must obtain the int value *)
     ]
@@
 
-let bid_for_auction destination ?(fee=100.0) amount value =
+let bid_for_auction destination ?(fee=100.0) amount v =
   ...
@@
       contract_addr
-      ~(serialize Tint value)
+      ~(serialize Tint v)
       fee
@@
   | Ok _ -> ...
-  | Error (Rejection Michelson_runtime_error s) -> ...
+  | Error (Rejection Michelson_runtime_error s) -> 
+    (*match s against expected errors from ...errors_map *)
+    (*throw exception if no match *)
+    ...
 
@@
 \end{lstlisting}
+This code example is incomplete and likely incorrect. It contains
+fragments from an example implemented on top of the synchronous API.
+The call to \lstinline/serialize/ refers to a proposal to improve on
+the typing properties of the synchronous API.
 
@@
 
-An extended type checker collects information about explicit failures along execution paths
-starting from each possible entry point. This checker will be able to
-verify the contract module specification in
-\ref{lst:contract-module-example} against the Michelson code in
-\ref{lst:code-example}. We may also wish to provide an entry point so
-that the checker only gathers information for that entry point. This alternative may be interesting if there
-is an entry point taking a parameter of sum type, rather than using all injections to distinguish
-between entry points.
+An extended type checker collects information about explicit failures
+along execution paths starting from each possible entry point. This
+checker will be able to verify the contract module specification in
+Listing~\ref{lst:contract-module-example} against the Michelson code
+in Listing~\ref{lst:code-example}. We may also wish to provide an
+entry point so that the checker only gathers information for that
+entry point. This alternative may be interesting if there is an entry
+point taking a parameter of sum type, rather than using all injections
+to distinguish between entry points.
 
@@
 
+\subsection{The Checker}
+\label{sec:checker}
+
+\subsubsection{Input}
+\begin{itemize}
+\item A contract in the form of a \texttt{.tz} file containing a
+  Michelson program.
+\item An entrypoint in the program
+\end{itemize}
+
+The checker performs symbolic execution of the Michelson stack
+machine.
+
+A symbolic value is either a concrete value
+constructor (like a number, a pair, left, right, nil, cons, etc) where
+the components are symbolic values, or it is a Michelson type which
+may be associated with a constraint, e.g., for an integer $x$ there 
+may be the constraint that $0<x<10$. Subcomponents of the type are
+again types with constraints. In a first iteration, constraints may be
+restricted to a disjunction of equations, e.g., $x=1 \vee x=2$.
+
+\subsubsection{Type checking}
+\label{sec:type-checking}
+
+ The stack is initialized with a symbolic value corresponding to a pair
+of the storage type and the parameter type. The latter is concretized
+according to the path to the specified entrypoint. That is, to
+investigate the entrypoint \lstinline/bid_for_auction/ in
+Listing~\ref{lst:code-example}, symbolic execution would start with a
+one-element stack that contains
+\begin{lstlisting}[language=michelson]
+(PAIR (LEFT x1:int) x2:address)
+\end{lstlisting}
+without any constraints on \texttt{x1} or \texttt{x2}.
+
+The checker executes instructions as far as possible using the
+concrete part and updates the stack according to the typing rules and
+semantics of the instruction. It tries to keep the
+stack contents as concrete as possible by exploiting all known information
+(e.g., constraints). If control flow cannot be decided, the checker
+explores all alternatives, potentially adding constraints that reify the
+checked condition, and joins the results. Execution paths with
+unsatisfiable constraints are pruned.
+
+\subsubsection{Exception tracking}
+\label{sec:exception-tracking}
+
+If the checker encounters an instruction that can make the contract
+fail, it saves this potential failure along with the (control flow) constraints
+leading to it. For a \texttt{FAILWITH} instruction, it saves
+this failure along with the constraints and with the symbolic value on
+top of the stack.
+
+\subsubsection{Token tracking}
+\label{sec:token-tracking}
+
+Instructions that generate tokens (e.g., \texttt{AMOUNT},
+\texttt{BALANCE}) create symbolic values marked with 
+the instruction. Further processing of these symbolic values leads to
+constraints on tokens and to their usage. These are also saved to
+infer if an amount argument is needed.
+
 \end{document}

### 2020-12-07 papers/execution-model/model.tex
update
clarified synchronicity, added proposal for type language

@@
               \NTEZ \mid \SUNIT \mid \FALSE \mid \TRUE \\
-	\EXPR & :: =  \CONSTANT \mid \VARIABLE \mid \lambda \VARIABLE. \EXPR\ 
+  \STATUS & ::= \STATUSPENDING \mid \STATUSINCLUDING (\dots) \mid \STATUSTIMEOUT \\
+	\EXPR & :: =  \CONSTANT \mid \STATUS \mid \VARIABLE \mid \lambda \VARIABLE. \EXPR\ 
 	\mid \EXPR\EXPR \mid (\EXPR,\EXPR) \mid \FST\ \EXPR \mid \SND\ \EXPR 	%\mid \NI \EI
@@
 \end{definition}
+
+Example code
+\begin{align*}
+  \OPH &=  \TRANSFER[\EXPR]\EXPR\EXPR\EXPR\EXPR \\
+       & \MATCH\ {status\ \OPH}\ \WITH \\
+       & \mid \STATUSPENDING \to \textrm{not yet included, continue waiting} \\
+       & \mid \STATUSINCLUDING (n) \to \textrm{included with $n$
+         blocks confirmation}\\
+       & \mid \STATUSTIMEOUT \to \textrm{lost, try again}
+\end{align*}
+Grammar of types
+\begin{align*}
+  \TYPE & ::= \ADDR \mid \OPH \mid \PUH \mid \PUK \mid \CODE\ \TYPE \mid
+          \TINT \mid \TUNIT \mid \TBOOL \mid \TSTRING \mid \TSTATUS \\
+  & \mid \TYPE\to\TYPE \mid \TPAIR\ \TYPE\ \TYPE \mid \TLIST\ \TYPE
+    \mid \TSUM\ \TYPE\ \TYPE \mid \TOPTION\ \TYPE \mid \TEXCEPTION
+\end{align*}
 
@@
 \begin{mathpar}
-  \inferrule[Node-Opp]
+  \inferrule[Node-Eval]
+  {
+    \EXPR \ExprTrans \EXPR'
+  }{
+    [\EC\EXPR :: \EXPRS, \ACCOUNTS, \OPERATIONS] \NodeTrans{}
+    [\EC{\EXPR'} :: \EXPRS, \ACCOUNTS, \OPERATIONS]
+  }
+\end{mathpar}
+
+\begin{mathpar}
+  \inferrule[Node-Op']
     {
@@
   }{
-    [\EC\OP :: \EXPRS, \ACCOUNTS, \OPERATIONS] \NodeTrans
+    [\EC\OP :: \EXPRS, \ACCOUNTS, \OPERATIONS] \NodeTrans{}
     [\EXPRS, \ACCOUNTS, (\EC{},\OP):: \OPERATIONS]
@@
 \begin{mathpar}
-  \inferrule{
+  \inferrule[Node-Inject']{
     \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
@@
      \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
-   { [\EC{?\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
+   { [\EC{\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [ \Angle{\OP,\OPH, \TIME}
@@
 \end{mathpar}
+
+\begin{mathpar}
+  \inferrule[Block-Accept'']{
+    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+    \TIME'-\TIME < 60
+  }{
+    { % [\EC{?\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
+      [\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
+      \CONTRACTORS, \TIME']}
+    \BlockTrans  \\
+    { % [\EC{\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
+      [\PENDING, \Angle{\OP,\OPH, \TIME,\TIME'} :: \ACCEPTED,
+      \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ),
+      \CONTRACTORS, \TIME'+1]}
+  }
+\end{mathpar}
+
+\begin{mathpar}
+  \inferrule[Block-Timeout'']{
+    \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
+    \TIME'-\TIME \ge 60
+  }{ % [\EC{?\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
+    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
+      \CONTRACTORS, \TIME']}
+    \BlockTrans 
+    { % [\EC{\RAISE timeout}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
+      [\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
+      \CONTRACTORS, \TIME']}
+  }
+\end{mathpar}
+
+\begin{itemize}
+\item library call \texttt{call\_contract} with \texttt{confirmations:None} corresponds to
+  \begin{enumerate}
+  \item{} first \TirName{Node-Op'}, \TirName{Node-Inject'}
+  \item{} first \TirName{Node-Op'}, \TirName{Node-Inject'}
+  \item{} first \TirName{Node-Op'}, \TirName{Node-Reject(balance,count,pubkey,fee)}
+  \end{enumerate}
+\item afterwards must check the status to find whether the
+  transfer is still pending or \TirName{Block-Accept''} or
+  \TirName{Block-Timeout''} has happened.
+\item no further transfer is possible before the status is resolved to
+  accept or timeout.
+\end{itemize}
 
@@
     [\EXPRS, \ACCOUNTS, \OPERATIONS]
-    \NodeTrans
+    \NodeTrans{}
     [\EXPRS, \ACCOUNTS, \OP:: \OPERATIONS]
@@
     [\EC\OP :: \EXPRS, \ACCOUNTS, \OPERATIONS]
-    \NodeTrans
+    \NodeTrans{}
     [\EC\OPH :: \EXPRS, \ACCOUNTS, \OPERATIONS]

### 2020-12-09 papers/execution-model/model.tex
Add files via upload

@@
 \begin{mathpar}
-  \inferrule[Node-Op']
+  \inferrule[Node-Op]
     {
@@
 \begin{mathpar}
-  \inferrule[Node-Inject']{
+  \inferrule[Node-Inject]{
     \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
@@
 \begin{mathpar}
-  \inferrule[Block-Accept'']{
+  \inferrule[Block-Accept]{
     \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
@@
 \begin{mathpar}
-  \inferrule[Block-Timeout'']{
+  \inferrule[Block-Timeout]{
     \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
@@
 
+\iffalse 
 \begin{mathpar}
+
  \inferrule[Node-Op]
@@
   }
+\end{mathpar}
+\fi
 
+\begin{mathpar}
   \inferrule[Node-System]
@@
 \subsection{Transfers}
-
+\iffalse 
 Rule 1 [injected]:
@@
      \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
-   { [\ACCOUNTS, \OPERATIONS] \|
+   { [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [ \Angle{\OP,\OPH, \TIME}
@@
 ~\\
-Rule 2 [rejected of counter]:
+\fi
+Rule 1 [rejected of counter]:
 \begin{mathpar}
@@
   }{
-   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
+   { [\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \| [\PENDING,
      \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
-   { [\ACCOUNTS, \OPERATIONS] \|
+   { [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [ \PENDING,
@@
 ~\\
-Rule 3 [rejected of balance]:
+Rule 2 [rejected of balance]:
 \begin{mathpar}
@@
 ~\\
-Rule 4 [rejected of public key]:
+Rule 3 [rejected of public key]:
 \begin{mathpar}
@@
 ~\\
-Rule 5 [rejected of fee]:
+Rule 4 [rejected of fee]:
 \begin{mathpar}
@@
 \end{mathpar}
-~\\
-~\\
+\iffalse 
 Rule 6 [included]:
@@
 \end{mathpar}
-
+\fi
 \subsection{Smart Contracts}
@@
   }{
-    [
-      \ACCOUNTS, \OP :: \OPERATIONS
+    [\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
       ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to \\
-    [\ACCOUNTS, \OPERATIONS] \|
+    [\EC{\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
       [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]
@@
     [
-      \ACCOUNTS, \OP :: \OPERATIONS
+     \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
       ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
-    [\ACCOUNTS, \OPERATIONS] \|
+    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
       [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
@@
     [
-      \ACCOUNTS, \OP :: \OPERATIONS
+      \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
       ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to
-    [\ACCOUNTS, \OPERATIONS] \|
+    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
       [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
@@
     [
-      \ACCOUNTS, \OP :: \OPERATIONS
+      \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
       ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
-    [\ACCOUNTS, \OPERATIONS] \|
+    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
       [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
@@
 \end{mathpar}
+
 ~\\
@@
 }{
-    %\Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
       [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
       \CONTRACTORS, \TIME']  
-    %}
-    \BlockTrans
-    % \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
-      [\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\FALSE), \CONTRACTORS, \TIME']
-    % }
+      \BlockTrans \    
+      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
+      \CONTRACTORS, \TIME'] 
   }
+
 \end{mathpar}
@@
     \OPH = \GENERATEOPH (\PUK,\PUH, \PARAMETER,\NTEZ, \MTEZ, \TIME)
-  }{[\ACCOUNTS, \OP :: \OPERATIONS] \|
+  }{[\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \|
       [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
     \SystemTrans \\
-    [\ACCOUNTS, \OPERATIONS] \|
+    [\EC{\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
       [\Angle{\OP, \OPH, \TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \TRUE), \CONTRACTORS, \TIME]}
@@
     \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
-  }{[\ACCOUNTS, \OP :: \OPERATIONS] \|
+  }{[\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \|
       [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
     \SystemTrans
-    [\ACCOUNTS, \OPERATIONS] \|
+    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
       [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}
@@
   }{[\epsilon[\GETBALANCE\PUK] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans [\epsilon[\BAL] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+    \NodeTrans\ [\epsilon[\BAL] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   }{[\epsilon[\GETBALANCE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans [\epsilon[\BAL] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+    \NodeTrans\ [\epsilon[\BAL] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   }{[\epsilon[\GETSTORAGE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans [\epsilon[\STORAGE] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+    \NodeTrans\ [\epsilon[\STORAGE] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   }{[\epsilon[\GETCODE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans [\epsilon[\CODE] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+    \NodeTrans\ [\epsilon[\CODE] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   }{[\epsilon[\GETCOUNTER\PUK] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans [\epsilon[\COU] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+    \NodeTrans\ [\epsilon[\COU] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
 ~\\
-Query 6 [status-pending]:
+Query 6 [fail of a query for an account]:
+\begin{mathpar}
+  \inferrule{
+    \NEG\ \CHECKPUB (\MANAGERS, \PUK) \
+  }{[\epsilon[\GETBALANCE\PUK/\GETCOUNTER\PUK] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
+    \NodeTrans\\ [\epsilon[\FAIL] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]}
+\end{mathpar}
+~\\
+~\\
+Query 7 [fail of a query for an account]:
+\begin{mathpar}
+  \inferrule{
+    \NEG\ \CHECKPUB (\CONTRACTORS, \PUH) 
+  }{[\epsilon[\GETBALANCE\PUH/\GETSTORAGE\PUH/\GETCODE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
+    \NodeTrans\\ [\epsilon[\FAIL] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]}
+\end{mathpar}
+~\\
+~\\
+Query 8 [status-pending]:
 \begin{mathpar}
@@
     \BLOCKSYSTEM = 
-      [\Angle{\OP, \OPH, \TIME} :: \PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
+      [\Angle{\OP, \OPH, \TIME'} :: \PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
   }{[\epsilon[\GETSTATUS\OPH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans [\epsilon[\STATUSPENDING] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+    \NodeTrans\ [\epsilon[\STATUSPENDING] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
 ~\\
-Query 7 [status-including]:
+Query 9 [status-including]:
 \begin{mathpar}
@@
     \BLOCKSYSTEM = 
-      [\PENDING, \Angle{\OP, \OPH, \TIME, \TIME'} :: \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
+      [\PENDING, \Angle{\OP, \OPH, \TIME', \TIME''} :: \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME] \\
+    $n$ = \TIME\ - \TIME''
   }{[\epsilon[\GETSTATUS\OPH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans [\epsilon[\STATUSINCLUDING] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+    \NodeTrans\ [\epsilon[\STATUSINCLUDING($n$)] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
 ~\\
-
+Query 10 [status-timeout]:
+\begin{mathpar}
+  \inferrule{ 
+    \NEG\ \CHECKEXIST (\ADDR, \PENDING, \ACCEPTED)
+  }{[\epsilon[\GETSTATUS\OPH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
+    \NodeTrans\ [\epsilon[\STATUSTIMEOUT] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}
+\end{mathpar}
 \section{Functions}
@@
     \item Function \CHECKCOU (\MANAGERS, \PUK)\ checks whether the current counter of an account that associates with the public key \PUK\ is unlocked (its flag is False).
-
+    \item Function \CHECKEXIST (\ADDR, \PENDING, \ACCEPTED)\ checks whether an address  \ADDR\ exists in either \PENDING\ or \ACCEPTED.
     \item Function \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ) updates the balance and the counter of the account that associates with the public key \PUK\ and the balance of the account that associates with the public key \PUK', where

### 2020-12-14 papers/execution-model/model.tex
final-touchup

@@
               \NTEZ \mid \SUNIT \mid \FALSE \mid \TRUE \\
-  \STATUS & ::= \STATUSPENDING \mid \STATUSINCLUDING (\dots) \mid \STATUSTIMEOUT \\
-	\EXPR & :: =  \CONSTANT \mid \STATUS \mid \VARIABLE \mid \lambda \VARIABLE. \EXPR\ 
+  \STATUS & ::= \STATUSPENDING \mid \STATUSINCLUDING (\dots) \mid
+            \STATUSTIMEOUT \\
+  \ERROR &::= \ERRPRG \mid \ERRBAL \mid \ERRCOUNT \mid \ERRFEE \mid
+           \ERRPUK \mid \ERRPUH \mid \ERRARG\\
+	\EXPR & :: =  \CONSTANT \mid \STATUS \mid \ERROR \mid \VARIABLE \mid \lambda \VARIABLE. \EXPR\ 
 	\mid \EXPR\EXPR \mid (\EXPR,\EXPR) \mid \FST\ \EXPR \mid \SND\ \EXPR 	%\mid \NI \EI
@@
 
+A \emph{pending operation} is a tuple
+$\langle  \OP, \OPH, \TIME, \STATUSPENDING\rangle $,
+where $\OP$ is an operation, $\OPH$ is the operation hash,
+and $\TIME$ is the time when the operation was injected.
+Once it is accepted, it changes to an \emph{accepted operation}:
+$\langle  \OP, \OPH, \TIME, \STATUSINCLUDED\ \TIME'\rangle $, where
+$\TIME'$ is the  when it was included in the blockchain.
+
 \begin{definition}%[Blockchain system]
@@
 \item $\NODE = [\ACCOUNTS, \OPERATIONS]$ is the state of a node, and
-\item $\BLOCKCHAIN = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ is the state of a blockchain 
-  such that $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.\PUK = c.\PUK$.
+\item $\BLOCKCHAIN = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS,
+  \TIME]$ is the state of a blockchain  
+  such that
+  \begin{itemize}
+  \item
+    $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.\PUK =
+    c.\PUK$;
+  \item 
+  \end{itemize}
 \end{enumerate}
@@
   \begin{enumerate}
-  \item{} first \TirName{Node-Op'}, \TirName{Node-Inject'}
   \item{} first \TirName{Node-Op'}, \TirName{Node-Inject'}
@@
   }{[\epsilon[\GETBALANCE\PUK/\GETCOUNTER\PUK] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
-    \NodeTrans\\ [\epsilon[\FAIL] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]}
+    \NodeTrans\\ [\epsilon[\RAISE\ \ERRPUK] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]}
 \end{mathpar}
@@
   }{[\epsilon[\GETBALANCE\PUH/\GETSTORAGE\PUH/\GETCODE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
-    \NodeTrans\\ [\epsilon[\FAIL] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]}
+    \NodeTrans\\ [\epsilon[\RAISE\ \ERRPUH] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]}
 \end{mathpar}
@@
   \inferrule{ 
-    \NEG\ \CHECKEXIST (\ADDR, \PENDING, \ACCEPTED)
+    \NEG\ \CHECKEXIST (\OPH, \PENDING, \ACCEPTED)
   }{[\epsilon[\GETSTATUS\OPH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]

### 2020-12-18 papers/execution-model/model.tex
after discussion: transformed most components into partial maps

@@
 $\langle  \OP, \OPH, \TIME, \STATUSINCLUDED\ \TIME'\rangle $, where
-$\TIME'$ is the  when it was included in the blockchain.
+$\TIME'> \TIME$ is the  when the operation was included in the blockchain.
+
+Properties of blockchain state transitions
+
+\begin{align*}
+  P &= \OPH \partialto \OP\times \TIME \times (\STATUSPENDING +
+      \STATUSINCLUDED\ \TIME + \STATUSTIMEOUT)
+\end{align*}
+If $[\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \BlockTrans{}
+[\PENDING', \MANAGERS', \CONTRACTORS', \TIME']$, then
+\begin{itemize}
+\item $\TIME \le \TIME'$
+\item $\DOM (\PENDING) \subseteq \DOM(\PENDING')$
+\item for all $\OPH \in \DOM(P)$, if  $\PENDING (\OPH) = \Angle{\OP, \TIME, \STATUS}$, then 
+  \begin{itemize}
+  \item if $\STATUS = \STATUSTIMEOUT$, then $\PENDING'
+    (\OPH) = \PENDING (\OPH)$
+  \item if $\STATUS = \STATUSINCLUDED\ \TIME'$,
+    then $\PENDING'(\OPH) = \PENDING (\OPH)$
+  \item if $\STATUS  = \STATUSPENDING$, then either
+    \begin{itemize}
+    \item % $\BLOCKCHAIN'.\TIME - \TIME \le 60 $ and
+      $\PENDING' (\OPH) = \PENDING (\OPH)$
+    \item $\PENDING' (\OPH) =       \Angle{\OP, \TIME, \STATUSINCLUDED\ \BLOCKCHAIN.\TIME}$, 
+    \item $\BLOCKCHAIN'.\TIME - \TIME > 60$ and $\PENDING' (\OPH) =
+      \Angle{\OP, \TIME, \STATUSTIMEOUT}$, 
+    \end{itemize}
+  \item $ \DOM (\MANAGERS) \subseteq \DOM (\MANAGERS')$
+    (Q: can accounts disappear? Do we want to model that?)
+  \item for all $\PUK \in \DOM (\MANAGERS)$ if $\MANAGERS (\PUK) =
+    \Angle{\BAL, \COU}$ where $\COU = (n, b)$
+    \begin{itemize}
+    \item if $b= \FALSE$, then $n' = n$
+    \item if $b= \TRUE$ and $b'=\TRUE$, then $n' =n$
+    \item if $b=\TRUE$ and $b'=\FALSE$, then $n' \in \{ n,  n+1\}$
+    \end{itemize}
+
+  \item $ \DOM (\CONTRACTORS) \subseteq \DOM (\CONTRACTORS')$
+
+  \end{itemize}
+
+\end{itemize}
 
@@
     c.\PUK$;
-  \item 
+  \item if $\PENDING (\OPH) = \Angle{\OP,\TIME, \STATUSINCLUDED\ \TIME'}$,
+    then $\TIME' > \TIME$
   \end{itemize}

### 2020-12-21 papers/execution-model/model.tex
intermediate; ongoing discussion

--- 2020-12-14 papers/execution-model/model.tex
@@
 \begin{definition}%[Account]
-  An implicit \emph{account} is a tuple $\langle
+  An implicit \emph{account} is represented by a key pair $\langle
   %\ALS,
@@
 \end{align*}
+We let $\EXPRS$ range over sets of expressions.
+
+We let $\ECS$ range over evaluation contexts. They are defined as
+follows.
+\begin{align*}
+  \EC{} & :: = \SC[\overline\VAL\ \EC{}\ \overline\EXPR] \mid \RAISE\ \EC{} \mid \TRY\ \EC{}\ \EXCEPT\ \EXPR
+  \mid \MATCH\ \EC{}\ \WITH\ \PATTERN\to\EXPR \dots
+\end{align*}
+Here $\SC$ ranges over the remaining syntactic constructors, which are
+treated uniformly: evaluation proceeds from left to right.
+\begin{align*}
+  \VAL & ::= \CONSTANT \mid \STATUS \mid \ERROR \mid \lambda x.\EXPR \mid(\VAL, \VAL) \mid
+         \NIL \mid \CONS\ \VAL\ \VAL \mid \LEFT\ \VAL \mid \RIGHT\
+         \VAL \mid \SOME\ \VAL\mid \NONE
+\end{align*}
 \end{definition}
 
-Example code
+Example pseudo code
 \begin{align*}
@@
 \begin{align*}
-  \TYPE & ::= \ADDR \mid \OPH \mid \PUH \mid \PUK \mid \CODE\ \TYPE \mid
+  \TYPE & ::= \TADDR \mid \TOPH \mid \TPUH \mid \TPUK \mid \TCODE\ \TYPE \mid
           \TINT \mid \TUNIT \mid \TBOOL \mid \TSTRING \mid \TSTATUS \\
@@
   The \emph{state of a node} is a tuple
-  $\NODE = [ \EXPRS, \ACCOUNTS, \OPERATIONS]$, where $\EXPRS$ is the set of the programs, $\ACCOUNTS$ is a set of
-  accounts, and
-  $\OPERATIONS$ is a set of operations.
+  $\NODE = [ \EXPRS, \ACCOUNTS, \OPERATIONS]$, where $\EXPRS$ is a
+  set of programs, $\ACCOUNTS \subseteq \TPAK \times \TPUK$  is a set of
+  implicit accounts, and
+  $\OPERATIONS \subseteq \ECS \times \TOP $ is a set of pairs of
+  expression contexts and operations.
 \end{definition}
@@
 \begin{definition}%[Manager]
-A \emph{manager} manages a single implicit account. It is represented by a
-tuple $\langle  \PUK, \BAL, \COU \rangle $, where  $\PUK$ is the
+A \emph{manager} manages a single implicit account. Managers are
+represented by a partial mapping $\MANAGERS : \TPUK \partialto \TBAL
+\times \TCOU$. If $\MANAGERS (\PUK) = \Angle{\BAL, \COU}$ is defined, then  $\PUK$ is the
 public key of an account, $\BAL$ is its
-balance and $\COU$ is its counter whose form is a value-flag pair $(n, b)$, where $n$, which is called the value of the counter,  is a natural number and ${b}$, which is called the flag of the counter, is a boolean value.
+balance and $\COU$ is its counter whose form is a value-flag pair
+$(n,b) \in \Nat\times\TBOOL$, where $n$ is the value of the counter
+and ${b}$ is its flag.   
 \end{definition}
@@
 \begin{definition}%[Contractor]
-  A \emph{contractor} manages a smart contract. It is
-  represented by a tuple
-  $\langle \PUH, \BAL, \CODE, \STORAGE \rangle $, where $\PUH$ is the
-  public hash of the contract, $\BAL$ is its current balance, $\CODE$ is its
+  A \emph{contractor} manages a smart contract. Contractors are
+  represented by a partial mapping $\CONTRACTORS : \TPUH \partialto
+  \TBAL \times \TCODE \times \TSTORAGE$. If $\CONTRACTORS (\PUH) = \langle
+  \BAL, \CODE, \STORAGE \rangle $ is defined, then $\PUH$ is the
+  public hash of a contract, $\BAL$ is its current balance, $\CODE$ is its
   code, and $\STORAGE$ is its current storage.
@@
 
-When an operation is injected in a node, it enters a \emph{pending pool}
-(and is called a \emph{pending operation}).
+When an operation is injected in a node, it enters a \emph{pending
+  pool}. Later on, such a pending operation is either dismissed or
+promoted to an accepted operation.
 
  \begin{definition}%[Pending operation]
-A \emph{pending operation} is a tuple  $\langle  \OP, \OPH, \TIME
-\rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash,
-and $\TIME$ is the time when the operation was injected. 
+An \emph{operation} is represented by a tuple  $\langle  \OP, \TIME, \STATUS
+\rangle $, where $\OP$ is an operation, $\TIME$ is the time when the
+operation was injected, and $\STATUS$ is either $\STATUSPENDING$,
+$\STATUSINCLUDING\ \TIME'$, or $\STATUSTIMEOUT$.  
+\end{definition}
+\begin{definition}
+  The pool of operations is defined as a partial mapping from
+  operation hashes $\OPH$:
+  \begin{align*}
+    \PENDING &= \TOPH \partialto \TOP\times \TTIME \times \TSTATUS \\
+    \TSTATUS&= (\STATUSPENDING + \STATUSINCLUDED\ \TTIME + \STATUSTIMEOUT)
+  \end{align*}
 \end{definition}
 
-After some time, a pending operation may be included in the blockchain as an accepted operation.
+A \emph{pending operation} is represented by
+$\langle  \OP, \TIME, \STATUSPENDING\rangle $,
+where $\OP$ is an operation, $\OPH$ is the operation hash,
+and $\TIME$ is the time when the operation was injected.
+Once it is accepted, it changes to an \emph{accepted operation}:
+$\langle  \OP, \TIME, \STATUSINCLUDED\ \TIME'\rangle $, where
+$\TIME'> \TIME$ is the  when the operation was included in the
+blockchain.  The operation can also be dropped at any time, which is
+represented by
+$\langle  \OP, \TIME, \STATUSTIMEOUT\rangle $. There are several
+causes for dropping, primarily timeout or overflow of the pending
+pool which is limited in size in the implementation.
 
- \begin{definition}%[Accepted operation]
-An \emph{accepted operation}  is a tuple $\langle  \OP, \OPH, \TIME, \TIME' \rangle
-$, where $\OP$ is an operation, $\OPH$ is the operation hash, $\TIME$ is the time when the operation was injected, and
-$\TIME'$ is the time when it was included in the blockchain. 
-\end{definition}
+% After some time, a pending operation may be included in the blockchain as an accepted operation.
+
+ % \begin{definition}%[Accepted operation]
+% An \emph{accepted operation}  is a tuple $\langle  \OP, \OPH, \TIME, \TIME' \rangle
+% $, where $\OP$ is an operation, $\OPH$ is the operation hash, $\TIME$ is the time when the operation was injected, and
+% $\TIME'$ is the time when it was included in the blockchain. 
+% \end{definition}
 
@@
   The \emph{state of a blockchain} is a tuple
-  $[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ where
-  $\PENDING$ is a set of pending operations,  $\ACCEPTED$ is a set
-  of accepted operations, $\MANAGERS$ is a set of managers,
-  $\CONTRACTORS$ is a set of contractors, and $\TIME$ is the current time. 
+  $\BLOCKCHAIN = [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]$ where
+  $\PENDING$ is a pool of operations, $\MANAGERS$ is a map of managers,
+  $\CONTRACTORS$ is a map of contractors, and $\TIME$ is the current time. 
 \end{definition}
 
-A \emph{pending operation} is a tuple
-$\langle  \OP, \OPH, \TIME, \STATUSPENDING\rangle $,
-where $\OP$ is an operation, $\OPH$ is the operation hash,
-and $\TIME$ is the time when the operation was injected.
-Once it is accepted, it changes to an \emph{accepted operation}:
-$\langle  \OP, \OPH, \TIME, \STATUSINCLUDED\ \TIME'\rangle $, where
-$\TIME'$ is the  when it was included in the blockchain.
+Properties of blockchain state transitions
+
+If $[\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \BlockTrans{}
+[\PENDING', \MANAGERS', \CONTRACTORS', \TIME']$, then
+\begin{itemize}
+\item $\TIME \le \TIME'$
+\item $\DOM (\PENDING) \subseteq \DOM(\PENDING')$
+\item for all $\OPH \in \DOM(P)$, if  $\PENDING (\OPH) = \Angle{\OP,
+    \TIME, \STATUS}$, then either
+  \begin{itemize}
+  \item     $\PENDING'    (\OPH) = \PENDING (\OPH)$; or
+  \item $\STATUS  = \STATUSPENDING$ and $\PENDING' (\OPH) =
+    \Angle{\OP, \TIME, \STATUSTIMEOUT}$; or
+  \item  $\STATUS  = \STATUSPENDING$, $\BLOCKCHAIN'.\TIME - \TIME
+    \le 60 $, and
+    $\PENDING' (\OPH) =       \Angle{\OP, \TIME, \STATUSINCLUDED\
+      \BLOCKCHAIN.\TIME}$.
+  \end{itemize}
+
+ \item $ \DOM (\MANAGERS) \subseteq \DOM (\MANAGERS')$
+ \item for all $\PUK \in \DOM (\MANAGERS)$ if $\MANAGERS (\PUK) =
+   \Angle{\BAL, \COU}$ where $\COU = (n, b)$
+   \begin{itemize}
+   \item if $b= \FALSE$, then $n' = n$
+   \item if $b= \TRUE$ and $b'=\TRUE$, then $n' =n$
+   \item if $b=\TRUE$ and $b'=\FALSE$, then $n' \in \{ n,  n+1\}$
+   \end{itemize}
+
+ \item $ \DOM (\CONTRACTORS) \subseteq \DOM (\CONTRACTORS')$
+
+\end{itemize}
 
@@
 \begin{enumerate}
-\item $\NODE = [\ACCOUNTS, \OPERATIONS]$ is the state of a node, and
-\item $\BLOCKCHAIN = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS,
+\item $\NODE = [\EXPRS, \ACCOUNTS, \OPERATIONS]$ is the state of a node, and
+\item $\BLOCKCHAIN = [\PENDING, \MANAGERS, \CONTRACTORS,
   \TIME]$ is the state of a blockchain  

### 2020-12-22 papers/execution-model/model.tex
further simplification to local node

@@
   \end{align*}
-  where \NTEZ\ and \MTEZ\ are amount of Tez, \ADDR\ is either a public key for an implicit account  or a public hash for a smart contract,  \PARAMETER\ is an argument passed to the smart contract's script, which is emtry if it is a transfer to an implicit account, \CODE\ is a script of the smart contract, \INIT\ is an initial value of the contract's storage.
+  where \NTEZ\ and \MTEZ\ are tokens, \ADDR\ is either a public
+  key for an implicit account  or a public hash for a smart contract,
+  \PARAMETER\ is an argument passed to the smart contract's script,
+  which is empty if it is a transfer to an implicit account, \CODE\ is
+  a script of the smart contract, \INIT\ is an initial value of the
+  contract's storage. 
 \end{definition}
@@
   \end{align*}
+
+  A pool $\PENDING$ is \emph{well-formed} if, for all $\OPH$, if $\PENDING (\OPH) =
+  \Angle{\OP,\TIME, \STATUSINCLUDED\ \TIME'}$, 
+  then $\TIME' > \TIME$.
 \end{definition}
@@
   $\PENDING$ is a pool of operations, $\MANAGERS$ is a map of managers,
-  $\CONTRACTORS$ is a map of contractors, and $\TIME$ is the current time. 
+  $\CONTRACTORS$ is a map of contractors, and $\TIME$ is the current
+  time. 
 \end{definition}
@@
     c.\PUK$;
-  \item if $\PENDING (\OPH) = \Angle{\OP,\TIME, \STATUSINCLUDED\ \TIME'}$,
-    then $\TIME' > \TIME$
   \end{itemize}
@@
 
-\clearpage{}
-\section{Rules}
+\section{Transitions}
+\label{sec:transitions}
 
+We distinguish several kinds of transitions depending on their scope:
+\begin{enumerate}
+\item $\ExprTrans$ single-step evaluation of expressions in the node state,
+\item $\NodeTrans$ internal transitions of a node,
+\item $\BlockTrans$ transitions of the blockchain state,
+\item $\SystemTrans$ blockchain system transitions.
+\end{enumerate}
+
+Evaluation of expressions is standard call-by-value lambda calculus defined
+using evaluation contexts $\EC{}$.
+\begin{mathpar}
+  \inferrule{}{
+    \EC{(\lambda x.\EXPR)\VAL} \ExprTrans \EC{\EXPR[\VAL/x]}
+  }
+
+  \inferrule{}{
+    \EC{\FST (\VAL_1, \VAL_2)} \ExprTrans \EC{\VAL_1}
+  }
+
+  \inferrule{}{
+    \EC{\SND (\VAL_1, \VAL_2)} \ExprTrans \EC{\VAL_2}
+  }
+
+  \inferrule{
+    \TRY \notin \EC[F]{}
+  }{
+    \EC{\TRY\ {\EC[F]{\RAISE\ \VAL}}\ \EXCEPT\ \EXPR} \ExprTrans
+    \EC{\EXPR\ \VAL}
+  }
+
+  \inferrule{}{
+    \EC{\MATCH\ \NIL\ \WITH\ \NIL\to\EXPR \mid \dots}
+    \ExprTrans
+    \EC{\EXPR}
+  }
+
+  \inferrule{}{
+    \EC{\MATCH\ (\CONS\ \VAL_1\ \VAL_2)\ \WITH\ (\CONS\ x_1\ x_2)\to\EXPR \mid \dots}
+    \ExprTrans
+    \EC{\EXPR[\VAL_1,\VAL_2/x_1, x_2]}
+  }
+
+  \inferrule{}{
+    \EC{\MATCH\ \NONE\ \WITH\ \NONE\to\EXPR \mid \dots}
+    \ExprTrans
+    \EC{\EXPR}
+  }
+
+  \inferrule{}{
+    \EC{\MATCH\ (\SOME\ \VAL)\ \WITH\ (\SOME\ x)\to\EXPR \mid \dots}
+    \ExprTrans
+    \EC{\EXPR[\VAL/x]}
+  }
+
+  \inferrule{}{
+    \EC{\MATCH\ (\LEFT\ \VAL)\ \WITH\ (\LEFT\ x)\to\EXPR \mid \dots}
+    \ExprTrans
+    \EC{\EXPR[\VAL/x]}
+  }
+
+  \inferrule{}{
+    \EC{\MATCH\ (\RIGHT\ \VAL)\ \WITH\ (\RIGHT\ x)\to\EXPR \mid \dots}
+    \ExprTrans
+    \EC{\EXPR[\VAL/x]}
+  }
+\end{mathpar}
+
+The internal transitions of a node are just evaluation of expressions.
 \begin{mathpar}
@@
 \end{mathpar}
+% \begin{mathpar}
+%   \inferrule[Node-Op]
+%     {
+%     \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS
+%   }{
+%     [\EC\OP :: \EXPRS, \ACCOUNTS, \OPERATIONS] \NodeTrans{}
+%     [\EXPRS, \ACCOUNTS, (\EC{},\OP):: \OPERATIONS]
+%   }
+% \end{mathpar}
 
 \begin{mathpar}
-  \inferrule[Node-Op]
-    {
-    \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS
+  \inferrule[Node-Inject-NEW]{
+    \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS \\
+    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
+    \CHECKCOU (\MANAGERS, \PUK) \\
+    \CHECKPUB (\MANAGERS, \PUK') \\
+    \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
+    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ, \TIME)
   }{
-    [\EC\OP :: \EXPRS, \ACCOUNTS, \OPERATIONS] \NodeTrans{}
-    [\EXPRS, \ACCOUNTS, (\EC{},\OP):: \OPERATIONS]
+    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
+      [\PENDING, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
+   { [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \|
+     [ \OPH \mapsto \Angle{\OP, \TIME, \STATUSPENDING}
+     ::\PENDING,
+     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
+     \CONTRACTORS,
+     \TIME]
+   }
   }
@@
   \inferrule{
-    %\NEG\ \CHECKCOU (\MANAGERS, \PUK)\\
-    %\OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
-    \NEG\ \CHECKCOU (\MANAGERS, \PUK) \\
-    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+    \NEG\ \CHECKCOU (\BLOCKCHAIN.\MANAGERS, \OP.\PUK) \\
+    % \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
   }{
-   { [\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \| [\PENDING,
-     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
-   { [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
-     [ \PENDING,
-     \ACCEPTED,
-     \MANAGERS,
-     \CONTRACTORS,
-     \TIME]
+    { [\EC\OP  :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+      % [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
+    }
+    \SystemTrans
+    { [\EC{\RAISE\ \ERRCOUNT} :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+      % [ \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    }
@@
   \inferrule{
-    \NEG\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
-    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+    \NEG\ \CHECKBAL (\BLOCKCHAIN.\MANAGERS, \OP.\PUK, \OP.\NTEZ, \OP.\MTEZ) \\
+    % \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
   }{
-   { [\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \| [\PENDING,
-     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
-   { [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
-     [ \PENDING,
-     \ACCEPTED,
-     \MANAGERS,
-     \CONTRACTORS,
-     \TIME]
+    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+      % [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
+    } \SystemTrans
+    { [\EC{\RAISE\ \ERRBAL} :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+      % [ \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    }
@@
   \inferrule{
-    \NEG\ \CHECKPUB (\MANAGERS, \PUK') \\
-    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+    \NEG\ \CHECKPUB (\BLOCKCHAIN.\MANAGERS, \OP.\ADDR) \\
+    % \OP = \TRANSFER\NTEZ\PUK{\ADDR}\MTEZ \\
   }{
-   { [\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \| [\PENDING,
-     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
-   { [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
-     [ \PENDING,
-     \ACCEPTED,
-     \MANAGERS,
-     \CONTRACTORS,
-     \TIME]
+    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+      % [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
+    } \SystemTrans
+   { [\EC{\RAISE\ \ERRPUK} :: \EXPRS, \ACCOUNTS] \|
+     \BLOCKCHAIN
+     % [ \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    }
@@
 ~\\
-Rule 4 [rejected of fee]:
+Rule 4 [rejected of fee]:\todo{Q: is this a local test? move to node transitions?}
 \begin{mathpar}
   \inferrule{
-    \NEG\ \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
-    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+    \NEG\ \CHECKGAS (\PUK, \ADDR, \NTEZ, \MTEZ) \\
+    \OP = \TRANSFER\NTEZ\PUK{\ADDR}\MTEZ \\
   }{
-   { [\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \| [\PENDING,
-     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
-   { [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
-     [ \PENDING,
-     \ACCEPTED,
-     \MANAGERS,
-     \CONTRACTORS,
-     \TIME]
+    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+      % [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
+    } \SystemTrans
+    { [\EC{\RAISE\ \ERRFEE} :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+      % [ \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    }

### 2021-01-04 papers/execution-model/model.tex

@@
 $\langle  \OP, \TIME, \STATUSINCLUDED\ \TIME'\rangle $, where
-$\TIME'> \TIME$ is the  when the operation was included in the
+$\TIME'> \TIME$ is  when the operation was included in the
 blockchain.  The operation can also be dropped at any time, which is
@@
   \inferrule{
-    \NEG\ \CHECKPUB (\BLOCKCHAIN.\MANAGERS, \OP.\ADDR) \\
+    \NEG\ \CHECKPUB (\BLOCKCHAIN.\MANAGERS, \OP.\PUK) \\
     % \OP = \TRANSFER\NTEZ\PUK{\ADDR}\MTEZ \\
@@
   \inferrule{
-    \NEG\ \CHECKGAS (\PUK, \ADDR, \NTEZ, \MTEZ) \\
-    \OP = \TRANSFER\NTEZ\PUK{\ADDR}\MTEZ \\
+    \NEG\ \CHECKGAS (\OP.\PUK, \OP.\PUK', \NTEZ, \MTEZ) \\
+    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
   }{
@@
   \inferrule[Block-Originate]{
-    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
+   \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS \\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
     \CHECKCOU (\MANAGERS, \PUK) \\
@@
   }{
-    [\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
+    [\EC\OP  :: \EXPRS, \ACCOUNTS,
       ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to \\
@@
   \inferrule{
-    \NEG\ \CHECKPUB (\MANAGERS, \PUK) \
-  }{[\epsilon[\GETBALANCE\PUK/\GETCOUNTER\PUK] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
-    \NodeTrans\\ [\epsilon[\RAISE\ \ERRPUK] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]}
+    \NEG\ \CHECKPUB (\BLOCKCHAIN.\MANAGERS, \PUK) \
+  }{[\epsilon[\GETBALANCE\PUK/\GETCOUNTER\PUK] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
+    \NodeTrans\\ [\epsilon[\RAISE\ \ERRPUK] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   \inferrule{
-    \NEG\ \CHECKPUB (\CONTRACTORS, \PUH) 
-  }{[\epsilon[\GETBALANCE\PUH/\GETSTORAGE\PUH/\GETCODE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
-    \NodeTrans\\ [\epsilon[\RAISE\ \ERRPUH] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]}
+    \NEG\ \CHECKPUB (\BLOCKCHAIN.\CONTRACTORS, \PUH) 
+  }{[\epsilon[\GETBALANCE\PUH/\GETSTORAGE\PUH/\GETCODE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
+    \NodeTrans\\ [\epsilon[\RAISE\ \ERRPUH] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
       [\PENDING, \Angle{\OP, \OPH, \TIME', \TIME''} :: \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME] \\
-    $n$ = \TIME\ - \TIME''
+    $n$ \ = \TIME\ - \TIME''
   }{[\epsilon[\GETSTATUS\OPH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
@@
   \inferrule{ 
-    \NEG\ \CHECKEXIST (\OPH, \PENDING, \ACCEPTED)
-  }{[\epsilon[\GETSTATUS\OPH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
-    \NodeTrans\ [\epsilon[\STATUSTIMEOUT] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}
+    \NEG\ \CHECKEXIST (\OPH, \BLOCKCHAIN.\PENDING, \BLOCKCHAIN.\ACCEPTED)
+  }{[\epsilon[\GETSTATUS\OPH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
+    \NodeTrans\ [\epsilon[\STATUSTIMEOUT] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
     \item Function \CHECKCOU (\MANAGERS, \PUK)\ checks whether the current counter of an account that associates with the public key \PUK\ is unlocked (its flag is False).
-    \item Function \CHECKEXIST (\ADDR, \PENDING, \ACCEPTED)\ checks whether an address  \ADDR\ exists in either \PENDING\ or \ACCEPTED.
+    \item Function \CHECKEXIST (\OPH, \PENDING, \ACCEPTED)\ checks whether an operation  \OPH\ exists in either \PENDING\ or \ACCEPTED.
     \item Function \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ) updates the balance and the counter of the account that associates with the public key \PUK\ and the balance of the account that associates with the public key \PUK', where

### 2021-01-04 papers/execution-model/model.tex
after monday meeting

@@
 operation was injected, and $\STATUS$ is either $\STATUSPENDING$,
-$\STATUSINCLUDING\ \TIME'$, or $\STATUSTIMEOUT$.  
+$\STATUSINCLUDED\ \TIME'$, or $\STATUSTIMEOUT$.  
 \end{definition}
@@
   \Angle{\OP,\TIME, \STATUSINCLUDED\ \TIME'}$, 
-  then $\TIME' > \TIME$.
+  then $\TIME' \ge \TIME$.
 \end{definition}
@@
 $\langle  \OP, \TIME, \STATUSINCLUDED\ \TIME'\rangle $, where
-$\TIME'> \TIME$ is  when the operation was included in the
+$\TIME' \ge \TIME$ is  when the operation was included in the
 blockchain.  The operation can also be dropped at any time, which is
@@
 \end{definition}
-
-Properties of blockchain state transitions
+\clearpage{}
+\subsection{Properties of blockchain state transitions}
 
@@
 \item $\DOM (\PENDING) \subseteq \DOM(\PENDING')$
-\item for all $\OPH \in \DOM(P)$, if  $\PENDING (\OPH) = \Angle{\OP,
-    \TIME, \STATUS}$, then either
+\item for all $\OPH \in \DOM(P)$, if 
+  $\PENDING (\OPH) = \Angle{\OP,  \hat\TIME, \STATUS}$, then either
   \begin{itemize}
@@
   \item $\STATUS  = \STATUSPENDING$ and $\PENDING' (\OPH) =
-    \Angle{\OP, \TIME, \STATUSTIMEOUT}$; or
-  \item  $\STATUS  = \STATUSPENDING$, $\BLOCKCHAIN'.\TIME - \TIME
+    \Angle{\OP, \hat\TIME, \STATUSTIMEOUT}$; or
+  \item  $\STATUS  = \STATUSPENDING$, $\TIME - \hat\TIME
     \le 60 $, and
-    $\PENDING' (\OPH) =       \Angle{\OP, \TIME, \STATUSINCLUDED\
-      \BLOCKCHAIN.\TIME}$.
+    $\PENDING' (\OPH) =       \Angle{\OP, \hat\TIME, \STATUSINCLUDED\
+      \TIME}$.
   \end{itemize}
@@
  \item $ \DOM (\MANAGERS) \subseteq \DOM (\MANAGERS')$
- \item for all $\PUK \in \DOM (\MANAGERS)$ if $\MANAGERS (\PUK) =
-   \Angle{\BAL, \COU}$ where $\COU = (n, b)$
+ \item for all $\PUK \in \DOM (\MANAGERS)$\\
+   if $\MANAGERS (\PUK) =
+   \Angle{\BAL, \COU}$, 
+   then $\MANAGERS' (\PUK) =
+   \Angle{\BAL', \COU'}$ and
    \begin{itemize}
-   \item if $b= \FALSE$, then $n' = n$
-   \item if $b= \TRUE$ and $b'=\TRUE$, then $n' =n$
-   \item if $b=\TRUE$ and $b'=\FALSE$, then $n' \in \{ n,  n+1\}$
+   \item if $\COU.b=\TRUE$ and $\COU'.b=\FALSE$, then $\COU.n' \in \{
+     \COU.n,  \COU.n+1\}$,
+   \item otherwise $\COU.n = \COU'.n$
+   \item If $\COU.n = \COU'.n$, then $\BAL = \BAL'$.
+   % \item if $\COU.b= \FALSE$, then $n' = n$
+   % \item if $\COU.b= \TRUE$ and $b'=\TRUE$, then $n' =n$
    \end{itemize}
@@
  \item $ \DOM (\CONTRACTORS) \subseteq \DOM (\CONTRACTORS')$
-
+   \todo{say something about contract state}
 \end{itemize}

### 2021-01-04 papers/execution-model/model.tex
cleanup

@@
   The \emph{state of a node} is a tuple
-  $\NODE = [ \EXPRS, \ACCOUNTS, \OPERATIONS]$, where $\EXPRS$ is a
-  set of programs, $\ACCOUNTS \subseteq \TPAK \times \TPUK$  is a set of
-  implicit accounts, and
-  $\OPERATIONS \subseteq \ECS \times \TOP $ is a set of pairs of
-  expression contexts and operations.
+  $\NODE = [ \EXPRS, \ACCOUNTS
+  % , \OPERATIONS
+  ]$, where $\EXPRS$ is a
+  set of programs and $\ACCOUNTS \subseteq \TPAK \times \TPUK$  is a set of
+  implicit accounts.
+  % , and
+  % $\OPERATIONS \subseteq \ECS \times \TOP $ is a set of pairs of
+  % expression contexts and operations.
 \end{definition}
@@
 \begin{definition}
-  The pool of operations is defined as a partial mapping from
+  The pool of operations, $\PENDING$, is defined as a partial mapping from
   operation hashes $\OPH$:
@@
     \PENDING &= \TOPH \partialto \TOP\times \TTIME \times \TSTATUS \\
-    \TSTATUS&= (\STATUSPENDING + \STATUSINCLUDED\ \TTIME + \STATUSTIMEOUT)
+    \TSTATUS&= \STATUSPENDING + \STATUSINCLUDED\ \TTIME + \STATUSTIMEOUT
   \end{align*}
 
-  A pool $\PENDING$ is \emph{well-formed} if, for all $\OPH$, if $\PENDING (\OPH) =
-  \Angle{\OP,\TIME, \STATUSINCLUDED\ \TIME'}$, 
-  then $\TIME' \ge \TIME$.
+  A pool $\PENDING$ is \emph{well-formed} if, for all $\OPH$, $\PENDING (\OPH) =
+  \Angle{\OP,\TIME, \STATUSINCLUDED\ \TIME'}$ implies $\TIME' \ge \TIME$.
 \end{definition}

### 2021-01-05 papers/execution-model/model.tex
more properties of blockchainstate

@@
 \end{definition}
+\begin{definition}%[Blockchain system]
+A \emph{blockchain configuration} is a pair
+$ \NODE \| \BLOCKCHAIN$ where
+\fxnote[inline]{Should the model contain multiple nodes?}
+\begin{enumerate}
+\item $\NODE = [\EXPRS, \ACCOUNTS]$ is the state of a node, and
+\item $\BLOCKCHAIN = [\PENDING, \MANAGERS, \CONTRACTORS,
+  \TIME]$ is the state of a blockchain  
+  such that
+  \begin{itemize}
+  \item
+    $\forall a \in \ACCOUNTS \implies a.\PUK \in \DOM( \MANAGERS)$;
+  \end{itemize}
+\end{enumerate}
+\end{definition}
+
 \clearpage{}
@@
    \todo{say something about contract state}
+   \begin{itemize}
+   \item for all $\PUH \in \DOM (\CONTRACTORS)$,
+     $\CONTRACTORS (\PUH).\CODE = \CONTRACTORS' (\PUH).\CODE$
+   \end{itemize}
 \end{itemize}
 
-\begin{definition}%[Blockchain system]
-A \emph{blockchain configuration} is a pair
-$ \NODE \| \BLOCKCHAIN$ where
-\fxnote[inline]{Should the model contain multiple nodes?}
-\begin{enumerate}
-\item $\NODE = [\EXPRS, \ACCOUNTS, \OPERATIONS]$ is the state of a node, and
-\item $\BLOCKCHAIN = [\PENDING, \MANAGERS, \CONTRACTORS,
-  \TIME]$ is the state of a blockchain  
-  such that
+\subsection{Typing related properties}
+
+To describe contracts we associate each public hash to a pair of
+types, the parameter type and the storage type.
+\begin{align*}
+  \Delta & ::= \EmptyEnv \mid \PUH: \TPAIR\ \TYPE\ \TYPE, \Delta
+\end{align*}
+
+Define $ \Delta \vdash \CONTRACTORS$ by
 \begin{itemize}
-  \item
-    $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.\PUK =
-    c.\PUK$;
+\item $\DOM (\Delta) = \DOM (\CONTRACTORS)$
+\item $\CONTRACTORS (\PUH).\CODE : \Delta (\PUH) \to FIXEDOUTPUTTYPE$
+\item $\CONTRACTORS (\PUH).\STORAGE : \TYPE_s$ where $\Delta (\PUH) =
+  \TPAIR\ \TYPE_p\ \TYPE_s$. 
 \end{itemize}
-\end{enumerate}
-\end{definition}
+
+Preservation
+
+If $[\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \BlockTrans{}
+[\PENDING', \MANAGERS', \CONTRACTORS', \TIME']$
+and $\Delta \vdash \CONTRACTORS$, \\
+then
+there is some $\Delta' \supseteq \Delta$ such that $\Delta' \vdash
+\CONTRACTORS'$.
+
+Consider a blockchain state  $[\PENDING, \MANAGERS, \CONTRACTORS,
+\TIME]$ where $\Delta \vdash \CONTRACTORS$.
+
+For all $\OPH\in\DOM (\PENDING)$,
+if  $\PENDING (\OPH) =  \Angle{\OP, \hat\TIME, \STATUS}$
+\begin{itemize}
+\item if $\OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ$, then
+  $\PUK, \PUK' \in \DOM (\MANAGERS)$
+  \todo{anything else to say here?}
+\item if $\OP = \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ$, then
+  \begin{itemize}
+  \item $\PUH\in\DOM (\CONTRACTORS)$
+  \item $\STRING : \TYPE_p$
+  \item $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$. 
+  \end{itemize}
+\item if $\OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ$ and $\STATUS =
+  \STATUSINCLUDED\ \TIME'$, then
+  \todo{what is the right thing to say here? Where do we obtain the
+    $\PUH$? How is it related to the $\OPH$?}
+
+\end{itemize}
 

### 2021-01-18 papers/execution-model/model.tex
changed puh calculation and storing of contract

@@
 \begin{align*}
-  \QRY & ::= \GETBALANCE\ADDR
+  \QRY & ::=
+  \GETCOUNTER\PUK  
+  \\&\mid \GETBALANCE\ADDR
   \\&\mid \GETSTATUS\OPH
@@
   \\&\mid \GETCODE\PUH 
-  \\&\mid \GETCOUNTER\PUK
+  \\&\mid \GETTYPE\PUH
 \end{align*}
@@
 \begin{align*}
-  \CONSTANT & ::= \ADDR \mid \OPH \mid \PUH \mid\PUK \mid \CODE \mid
+  \CONSTANT & ::= \INT %\mid \ADDR
+              \mid \OPH \mid \PUH \mid\PUK \mid \CODE \mid
               \NTEZ \mid \SUNIT \mid \FALSE \mid \TRUE \\
-  \STATUS & ::= \STATUSPENDING \mid \STATUSINCLUDING (\dots) \mid
+  \STATUS & ::= \STATUSPENDING \mid \STATUSINCLUDING (\INT) \mid
             \STATUSTIMEOUT \\
   \ERROR &::= \ERRPRG \mid \ERRBAL \mid \ERRCOUNT \mid \ERRFEE \mid
-           \ERRPUK \mid \ERRPUH \mid \ERRARG\\
+           \ERRPUK \mid \ERRPUH \mid \ERRARG \mid \ERRINIT\\
 	\EXPR & :: =  \CONSTANT \mid \STATUS \mid \ERROR \mid \VARIABLE \mid \lambda \VARIABLE. \EXPR\ 
@@
   \\&\mid \QOP\  \EXPR\\
-  \QOP & ::= balance \mid status \mid storage \mid code \mid counter
+  \QOP & ::= balance \mid status \mid storage \mid code \mid counter \mid type
 \end{align*}
@@
   represented by a partial mapping $\CONTRACTORS : \TPUH \partialto
-  \TBAL \times \TCODE \times \TSTORAGE$. If $\CONTRACTORS (\PUH) = \langle
-  \BAL, \CODE, \STORAGE \rangle $ is defined, then $\PUH$ is the
-  public hash of a contract, $\BAL$ is its current balance, $\CODE$ is its
-  code, and $\STORAGE$ is its current storage.
+  \TCODE \times \TIME  \times \TBAL \times  \TSTORAGE$. If $\CONTRACTORS (\PUH) = \langle
+  \CODE, \TIME, \BAL, \STORAGE \rangle $ is defined, then $\PUH$ is the
+  public hash of a contract,
+  $\CODE$ is its  code,
+  $\TIME$ is the time when it was accepted,
+  $\BAL$ is its current balance,
+  and $\STORAGE$ is its current storage.
 \end{definition}
@@
 
- \begin{definition}%[Pending operation]
-An \emph{operation} is represented by a tuple  $\langle  \OP, \TIME, \STATUS
-\rangle $, where $\OP$ is an operation, $\TIME$ is the time when the
-operation was injected, and $\STATUS$ is either $\STATUSPENDING$,
-$\STATUSINCLUDED\ \TIME'$, or $\STATUSTIMEOUT$.  
-\end{definition}
+ %\begin{definition}%[Pending operation]
+%An \emph{operation} is represented by a tuple  $\langle  \OP, \TIME, \STATUS \rangle $, where $\OP$ is an operation, $\TIME$ is the time when the operation was injected, and $\STATUS$ is either $\STATUSPENDING$,$\STATUSINCLUDED\ \TIME'$, or $\STATUSTIMEOUT$.
+%\end{definition}
 \begin{definition}
@@
 
+  if $\PENDING(\OPH) = \langle  \OP, \TIME, \STATUS
+\rangle $ is defined, then $\OPH$ is the public hash of the operation, $\OP$ is the operation, $\TIME$ is the time when the
+operation was injected, and $\STATUS$ is either $\STATUSPENDING$,
+$\STATUSINCLUDED\ \TIME'$, or $\STATUSTIMEOUT$.
 A pool $\PENDING$ is \emph{well-formed} if, for all $\OPH$, $\PENDING (\OPH) =
-  \Angle{\OP,\TIME, \STATUSINCLUDED\ \TIME'}$ implies $\TIME' \ge \TIME$.
+  \Angle{\OP,\TIME, \STATUSINCLUDED\ \TIME'}$ implies $\TIME' \ge
+  \TIME$ and $\OPH = \GENERATEOPH (\OP, \TIME)$.
 \end{definition}
@@
 A \emph{pending operation} is represented by
-$\langle  \OP, \TIME, \STATUSPENDING\rangle $,
+$\OPH \mapsto \langle  \OP, \TIME, \STATUSPENDING\rangle $,
 where $\OP$ is an operation, $\OPH$ is the operation hash,
@@
 Once it is accepted, it changes to an \emph{accepted operation}:
-$\langle  \OP, \TIME, \STATUSINCLUDED\ \TIME'\rangle $, where
+$\OPH \mapsto \langle  \OP, \TIME, \STATUSINCLUDED\ \TIME'\rangle $, where
 $\TIME' \ge \TIME$ is  when the operation was included in the
@@
 represented by
-$\langle  \OP, \TIME, \STATUSTIMEOUT\rangle $. There are several
+$\OPH \mapsto \langle  \OP, \TIME, \STATUSTIMEOUT\rangle $. There are several
 causes for dropping, primarily timeout or overflow of the pending
@@
 \end{definition}
+\begin{definition}
+  Preserved by a step on a well-formed configuration $ [\EXPRS, \ACCOUNTS] \|
+  [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]$:
+  \todo[inline]{Is this preserved?}
+  \begin{itemize}
+  \item for all $\OPH$ in $\EXPRS$, $\OPH \in \DOM (\PENDING)$,
+  \item for all $\PUK$ in $\EXPRS$, $\PUK \in \DOM (\MANAGERS)$,
+  \item for all $\PUH$ in $\EXPRS$, $\PUH \in \DOM (\CONTRACTORS)$.
+  \end{itemize}
+\end{definition}
 
@@
   \end{itemize}
-
+ \item for all $\OPH \in \DOM(P)$ and $\PENDING (\OPH) = \Angle{\OP,  \hat\TIME, \STATUSPENDING}$, 
+    \begin{itemize}
+    	\item  if $\MANAGERS(\OP.\PUK) =  \Angle{\BAL, \COU}$ then  
+  $\COU.b = \TRUE$.
+    \end{itemize}
  \item $ \DOM (\MANAGERS) \subseteq \DOM (\MANAGERS')$
@@
  \item $ \DOM (\CONTRACTORS) \subseteq \DOM (\CONTRACTORS')$
-   \todo{say something about contract state}
    \begin{itemize}
@@
 \item if $\OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ$, then
+\begin{itemize}
+  \item
   $\PUK, \PUK' \in \DOM (\MANAGERS)$
-  \todo{anything else to say here?}
-\item if $\OP = \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ$, then
+\end{itemize}
+\item if $\OP = \TRANSFER[\PARAMETER]\NTEZ\PUK\PUH\MTEZ$, then
   \begin{itemize}
-  \item $\PUH\in\DOM (\CONTRACTORS)$
-  \item $\STRING : \TYPE_p$
-  \item $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$. 
+  \item $\PUK \in \DOM (\MANAGERS)$ and $\PUH\in\DOM (\CONTRACTORS)$
+  \item $\PARAMETER : \TYPE_p$ where $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$. 
   \end{itemize}
+
 \item if $\OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ$ and $\STATUS =
   \STATUSINCLUDED\ \TIME'$, then
-  \todo{what is the right thing to say here? Where do we obtain the
-    $\PUH$? How is it related to the $\OPH$?}
+   \begin{itemize}
+   \item $\PUK \in \DOM (\MANAGERS)$
+  \item $\CODE : \TPAIR\ \TYPE_p\ \TYPE_s$
+  \item $\STRING : \TYPE_s$
+  \item if $\STATUS =
+  \STATUSINCLUDED\ \TIME'$, then $\PUH =\GENERATEHASH (\CODE, \hat\TIME) \in \DOM (\CONTRACTORS)$ and $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$ (or $\CONTRACTORS(\PUH).\CODE = \CODE$).
 
+  \end{itemize}
+
+ \item if $st = \STATUSPENDING$ and $\MANAGERS(\PUK) = \Angle{\BAL,
+     \COU}$, then $\BAL \ge \NTEZ +  \MTEZ$ 
 \end{itemize}
@@
   }{
-    [\EC\EXPR :: \EXPRS, \ACCOUNTS, \OPERATIONS] \NodeTrans{}
-    [\EC{\EXPR'} :: \EXPRS, \ACCOUNTS, \OPERATIONS]
+    [\EC\EXPR :: \EXPRS, \ACCOUNTS] \NodeTrans{}
+    [\EC{\EXPR'} :: \EXPRS, \ACCOUNTS]
   }
 \end{mathpar}
-% \begin{mathpar}
-%   \inferrule[Node-Op]
-%     {
-%     \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS
-%   }{
-%     [\EC\OP :: \EXPRS, \ACCOUNTS, \OPERATIONS] \NodeTrans{}
-%     [\EXPRS, \ACCOUNTS, (\EC{},\OP):: \OPERATIONS]
-%   }
-% \end{mathpar}
 
 \begin{mathpar}
-  \inferrule[Node-Inject-NEW]{
-    \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS \\
+  \inferrule[Node-Inject]{
+    \Angle{\PAK,\PUK} \in \ACCOUNTS \\
     \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
@@
     \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
-    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
-    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ, \TIME)
+    %\OPH = \GENERATEOPH (\PUK, \PUK','', \NTEZ, \MTEZ, \TIME) \\
+    \OPH = \GENERATEOPH (\OP, \TIME) \\
+    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ    
   }{
@@
 \begin{mathpar}
-  \inferrule[Node-Inject]{
-    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
-    \CHECKCOU (\MANAGERS, \PUK) \\
-    \CHECKPUB (\MANAGERS, \PUK') \\
-    \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
+  \inferrule[Block-Accept]{
     \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
-    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ, \TIME)
+    \TIME - \hat\TIME \le 60
   }{
-   { [\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \| [\PENDING,
-     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
-   { [\EC{\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
-     [ \Angle{\OP,\OPH, \TIME}
-     ::\PENDING,
-     \ACCEPTED,
-     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
-     \CONTRACTORS,
-     \TIME]
-   }
+    { 
+      [\OPH \mapsto \Angle{\OP, \hat \TIME, \STATUSPENDING}
+     ::\PENDING, \MANAGERS,
+      \CONTRACTORS, \TIME]}
+    \BlockTrans  \\
+    { 
+      [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING, 
+      \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ),
+      \CONTRACTORS, \TIME +1]}
   }
@@
 
+The timeout transition applies to all operations.
 \begin{mathpar}
-  \inferrule[Block-Accept]{
-    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
-    \TIME'-\TIME < 60
+  \inferrule[Block-Timeout]{
+    % \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
+    \TIME-\hat\TIME > 60
   }{ 
-    { % [\EC{?\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
-      [\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
-      \CONTRACTORS, \TIME']}
+    {[\OPH \mapsto \Angle{\OP, \hat \TIME, \STATUSPENDING}
+     ::\PENDING, \MANAGERS,
+      \CONTRACTORS, \TIME]}
     \BlockTrans \\
-    { % [\EC{\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
-      [\PENDING, \Angle{\OP,\OPH, \TIME,\TIME'} :: \ACCEPTED,
-      \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ),
-      \CONTRACTORS, \TIME'+1]}
+    { 
+      [\OPH \mapsto \Angle{\OP, \hat \TIME, \STATUSTIMEOUT}
+     :: \PENDING, \UPDATECOU(\MANAGERS, \OP.\PUK, \FALSE),
+      \CONTRACTORS, \TIME]}
   }
@@
 
-\begin{mathpar}
-  \inferrule[Block-Timeout]{
-    \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
-    \TIME'-\TIME \ge 60
-  }{ % [\EC{?\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
-    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
-      \CONTRACTORS, \TIME']}
-    \BlockTrans 
-    { % [\EC{\RAISE timeout}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
-      [\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
-      \CONTRACTORS, \TIME']}
-  }
-\end{mathpar}
-
-\begin{itemize}
-\item library call \texttt{call\_contract} with \texttt{confirmations:None} corresponds to
-  \begin{enumerate}
-  \item{} first \TirName{Node-Op'}, \TirName{Node-Inject'}
-  \item{} first \TirName{Node-Op'}, \TirName{Node-Reject(balance,count,pubkey,fee)}
-  \end{enumerate}
-\item afterwards must check the status to find whether the
-  transfer is still pending or \TirName{Block-Accept''} or
-  \TirName{Block-Timeout''} has happened.
-\item no further transfer is possible before the status is resolved to
-  accept or timeout.
-\end{itemize}
+% \begin{itemize}
+% \item library call \texttt{call\_contract} with \texttt{confirmations:None} corresponds to
+%   \begin{enumerate}
+%   \item{} first \TirName{Node-Op'}, \TirName{Node-Inject'}
+%   \item{} first \TirName{Node-Op'}, \TirName{Node-Reject(balance,count,pubkey,fee)}
+%   \end{enumerate}
+% \item afterwards must check the status to find whether the
+%   transfer is still pending or \TirName{Block-Accept''} or
+%   \TirName{Block-Timeout''} has happened.
+% \item no further transfer is possible before the status is resolved to
+%   accept or timeout.
+% \end{itemize}
 
@@
 consider it signed with the corresponding private key $\PAK$.
-
-\iffalse 
-\begin{mathpar}
-
- \inferrule[Node-Op]
-  {
-    \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS
-  }{
-    [\EXPRS, \ACCOUNTS, \OPERATIONS]
-    \NodeTrans{}
-    [\EXPRS, \ACCOUNTS, \OP:: \OPERATIONS]
-  }
-
-  \inferrule[Node-Oph]
-  {
-   \\
-  }{
-    [\EC\OP :: \EXPRS, \ACCOUNTS, \OPERATIONS]
-    \NodeTrans{}
-    [\EC\OPH :: \EXPRS, \ACCOUNTS, \OPERATIONS]
-  }
-\end{mathpar}
-\fi
 
@@
 
-\subsection{Transfers}
-\iffalse 
-Rule 1 [injected]:
-
 \begin{mathpar}
-  \inferrule{
-    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
-    \CHECKCOU (\MANAGERS, \PUK) \\
-    \CHECKPUB (\MANAGERS, \PUK') \\
-    \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
-    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
-    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ, \TIME)
-  }{
-   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
-     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
-   { [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
-     [ \Angle{\OP,\OPH, \TIME}
-     ::\PENDING,
-     \ACCEPTED,
-     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
-     \CONTRACTORS,
-     \TIME]
-   }
-  }
-\end{mathpar}
-~\\
-~\\
-\fi
-Rule 1 [rejected of counter]:
-\begin{mathpar}
-  \inferrule{
+  \inferrule[rejected of counter]{
     \NEG\ \CHECKCOU (\BLOCKCHAIN.\MANAGERS, \OP.\PUK) \\
-    % \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
     }{
@@
       \BLOCKCHAIN
-      % [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
     }
@@
       \BLOCKCHAIN
-      % [ \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    }
@@
 \end{mathpar}
-~\\
-~\\
-Rule 2 [rejected of balance]:
+
 \begin{mathpar}
-  \inferrule{
+  \inferrule[rejected of balance]{
     \NEG\ \CHECKBAL (\BLOCKCHAIN.\MANAGERS, \OP.\PUK, \OP.\NTEZ, \OP.\MTEZ) \\
-    % \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
     }{
@@
       \BLOCKCHAIN
-      % [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
       } \SystemTrans
@@
       \BLOCKCHAIN
-      % [ \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
     }
@@
 \end{mathpar}
-~\\
-~\\
-Rule 3 [rejected of public key]:
+
+\subsection{An Implicit Account Transfer}
+\iffalse 
+\fi
+
 \begin{mathpar}
-  \inferrule{
-    \NEG\ \CHECKPUB (\BLOCKCHAIN.\MANAGERS, \OP.\PUK) \\
-    % \OP = \TRANSFER\NTEZ\PUK{\ADDR}\MTEZ \\
-  }{
-    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
-      \BLOCKCHAIN
-      % [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
-    } \SystemTrans
-   { [\EC{\RAISE\ \ERRPUK} :: \EXPRS, \ACCOUNTS] \|
-     \BLOCKCHAIN
-     % [ \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
-   }
-  }
-\end{mathpar}
-~\\
-~\\
-Rule 4 [rejected of fee]:\todo{Q: is this a local test? move to node transitions?}
-\begin{mathpar}
-  \inferrule{
-    \NEG\ \CHECKGAS (\OP.\PUK, \OP.\PUK', \NTEZ, \MTEZ) \\
+  \inferrule[rejected of public key]{
+    \NEG\ \CHECKPUB (\BLOCKCHAIN.\MANAGERS, \PUK') \\
     \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
@@
       \BLOCKCHAIN
-      % [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
+    } \SystemTrans
+   { [\EC{\RAISE\ \ERRPUK} :: \EXPRS, \ACCOUNTS] \|
+     \BLOCKCHAIN
+    }
+  }
+\end{mathpar}
+
+\begin{mathpar}
+  \inferrule[rejected of fee]{
+    \NEG\ \CHECKGAS (\BLOCKCHAIN.\MANAGERS, \PUK,\PUK',\NTEZ, \MTEZ) \\
+    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+  }{
+    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
      } \SystemTrans
@@
 \end{mathpar}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \iffalse 
@@
     \BlockTrans
-    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
+    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \OP.\PUK, \FALSE),
       \CONTRACTORS, \TIME']}
@@
 \fi
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Smart Contracts}
 A. Originate
-~\\
-~\\
-Rule 1 [injected]:
 
@@
   \inferrule[Block-Originate]{
-   \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS \\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
+   \Angle{\PAK,\PUK} \in \ACCOUNTS \\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
     \CHECKCOU (\MANAGERS, \PUK) \\
+    \CHECKPRG (\CODE) \\
     \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ)  \\
-    \CHECKPRG (\CODE, \STRING) \\\\
-    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
-    \OPH = \GENERATEOPH(\PUK, \CODE, \NTEZ, \MTEZ, \STRING,\TIME) 
+    \CHECKINIT (\CODE, \STRING) \\
+    %\OPH = \GENERATEOPH(\PUK, \CODE, \STRING, \NTEZ, \MTEZ, \TIME) \\
+    \OPH = \GENERATEOPH(\OP, \TIME) \\
+    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ    
   }{
     [\EC\OP  :: \EXPRS, \ACCOUNTS,
-      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to \\
-    [\EC{\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
-      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]
+      ] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \to \\
+    [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \|
+      [\OPH \mapsto \Angle{\OP, \TIME, \STATUSPENDING}
+     ::\PENDING, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]
   }
 \end{mathpar}
-~\\
-~\\
-Rule 2 [rejected of code]:
+
 \begin{mathpar}
-  \inferrule{
-    \NEG\ \CHECKPRG (\CODE, \STRING) \\
+  \inferrule[rejected of code]{
+    \NEG\ \CHECKPRG (\CODE) \\
     \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
   }{
-    [
-     \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
-      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
-    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
-      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
+    [\EC\OP :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN \to 
+    [\EXPRS[\RAISE\ \ERRPRG] :: \EXPRS, \ACCOUNTS] \|
+     \BLOCKCHAIN
   }
 \end{mathpar}
-~\\
-~\\
+
+\iffalse 
 Rule 3 [rejected of counter]:
@@
   \inferrule{
-    \NEG\ \CHECKCOU (\MANAGERS, \PUK) \\
+    \NEG\ \CHECKCOU (\BLOCKCHAIN.\MANAGERS, \PUK) \\
     \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
   }{
-    [
-      \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
-      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to
-    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
-      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
+    [\EC\OP :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN \to 
+    [\EXPRS[\RAISE\ \ERRCOUNT] :: \EXPRS, \ACCOUNTS] \|
+     \BLOCKCHAIN
   }
 \end{mathpar}
-~\\
-~\\
-Rule 4 [rejected of balance]:
+
 \begin{mathpar}
-  \inferrule{
-    \NEG\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
+  \inferrule[rejected of balance]{
+    \NEG\ \CHECKBAL (\BLOCKCHAIN.\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
     \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
   }{
-    [
-      \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
-      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
-    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
-      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
+    [\EC\OP :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN \to 
+    [\EXPRS[\RAISE\ \ERRBAL] :: \EXPRS, \ACCOUNTS] \|
+     \BLOCKCHAIN
   }
 \end{mathpar}
-~\\
-~\\
-Rule 5 [rejected of fee]:
+\fi
+
 \begin{mathpar}
-  \inferrule{
+  \inferrule[rejected of fee]{
     \NEG\ \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ) \\
@@
   }{
-    [
-      \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
-      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
-    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
-      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
+    [\EC\OP :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN \to 
+    [\EXPRS[\RAISE\ \ERRFEE] :: \EXPRS, \ACCOUNTS] \|
+     \BLOCKCHAIN
   }
@@
 
-~\\
-~\\
-Rule 6 [included]:
+\begin{mathpar}
+  \inferrule[rejected of initial storage]{
+    \NEG\ \CHECKINIT (\CODE, \INIT) \\
+    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
+  }{
+    [\EC\OP :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN \to 
+    [\EXPRS[\RAISE\ \ERRINIT] :: \EXPRS, \ACCOUNTS] \|
+     \BLOCKCHAIN
+  }
+\end{mathpar}
+
 \begin{mathpar}
@@
     \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
-    \TIME'-\TIME < 60
+    \PUH = \GENERATEHASH(\CODE, \TIME) \\
+    \TIME-\hat\TIME  \le 60
   }{
-      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']
-    \SystemTrans
-      [\PENDING, \Angle{\OP, \OPH,\TIME,\TIME'} ::  \ACCEPTED, \UPDATESUCC
-      (\MANAGERS, \PUK, \NTEZ, \MTEZ), \\ \Angle{\GENERATEHASH(\CODE, \INIT, \TIME, \TIME'), \NTEZ, \CODE, \STRING} :: \CONTRACTORS, \TIME'+1]
+      [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \| [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING} :: \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
+    \SystemTrans \\
+     [\EC{ \PUH}  :: \EXPRS, \ACCOUNTS] \|  [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING, \UPDATESUCC
+      (\MANAGERS, \PUK, \NTEZ, \MTEZ),\\ \PUH \mapsto  \Angle{\CODE, \TIME, \NTEZ, \STRING} :: \CONTRACTORS, \TIME+1]
   }
 \end{mathpar}
-~\\
-~\\
-Rule 7 [timeout]:
-\begin{mathpar}
-  \inferrule[Block-Timeout]{
-    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
-    \TIME'-\TIME \ge 60
-}{
-      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
-      \CONTRACTORS, \TIME']  
-      \BlockTrans \    
-      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
-      \CONTRACTORS, \TIME'] 
-  }
 
-\end{mathpar}
+% \begin{mathpar}
+%   \inferrule[Block-Timeout]{
+%     %\OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
+%     \TIME-\hat\TIME > 60
+% }{
+%       [ \OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING}
+%      ::\PENDING, \MANAGERS,
+%       \CONTRACTORS, \TIME]  
+%       \BlockTrans \\    
+%       [ \OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSTIMEOUT}
+%      :: \PENDING, \UPDATECOU(\MANAGERS, \OP.\PUK, \FALSE),
+%       \CONTRACTORS, \TIME] 
+%   }
+
+% \end{mathpar}
 ~\\
@@
 B. \textbf{Transfer}
-~\\
-~\\
-Rule 1 [injected]:
+
 \begin{mathpar}
@@
     \CHECKGAS (\CONTRACTORS, \PUH, \PARAMETER, \MTEZ) \\
+%    \OPH = \GENERATEOPH (\PUK,\PUH, \PARAMETER,\NTEZ, \MTEZ, \TIME) \\
+    \OPH = \GENERATEOPH (\OP, \TIME) \\
     \OP =  \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\    
-    \OPH = \GENERATEOPH (\PUK,\PUH, \PARAMETER,\NTEZ, \MTEZ, \TIME)
-  }{[\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \|
-      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
+  }{ [\EC\OP  :: \EXPRS, \ACCOUNTS,
+      ] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]     
     \SystemTrans \\
-    [\EC{\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
-      [\Angle{\OP, \OPH, \TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \TRUE), \CONTRACTORS, \TIME]}
+    [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \|
+      [\OPH \mapsto \Angle{\OP, \TIME, \STATUSPENDING}
+     :: \PENDING, \UPDATECOU(\MANAGERS, \PUK, \TRUE), \CONTRACTORS, \TIME]}
 \end{mathpar}
-~\\
-~\\
+
+\iffalse 
 Rule 2 [rejected of counter]:
@@
   \inferrule{
-    \NEG\ \CHECKCOU (\MANAGERS, \PUK) \\
+    \NEG\ \CHECKCOU (\BLOCKCHAIN.\MANAGERS, \PUK) \\
     \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
-  }{[\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \|
-      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
+  }{[\EC\OP :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN      
     \SystemTrans
-    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
-      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}
+   [\EC[\RAISE\ \ERRCOUNT] :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN }
 \end{mathpar}
@@
 \end{mathpar}
-~\\
-~\\
-Rule 4 [rejected of public hash]:
+\fi
+
 \begin{mathpar}
-  \inferrule{
-    \NEG\ \CHECKPUH (\CONTRACTORS, \PUH)\\
-    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
-  }{[\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \|
-      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
+  \inferrule[rejected of public hash]{
+    \NEG\ \CHECKPUH (\BLOCKCHAIN.\CONTRACTORS, \PUH) \\
+    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ
+  }{[\EC\OP  :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN    
     \SystemTrans
-    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
-      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}
+    [\EXPRS[\RAISE\ \ERRPUH], \ACCOUNTS] \| \BLOCKCHAIN}
 \end{mathpar}
-~\\
-~\\
-Rule 5 [rejected of argument]:
+
 \begin{mathpar}
-  \inferrule{
-    \NEG\ \CHECKARG (\CONTRACTORS, \PUH, \PARAMETER)\\
-    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
-  }{[\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \|
-      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
+  \inferrule[rejected of argument]{
+    \NEG\ \CHECKARG (\BLOCKCHAIN.\CONTRACTORS, \PUH, \PARAMETER)\\
+    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ
+  }{[\EC\OP  :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN    
     \SystemTrans
-    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
-      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}
+    [\EXPRS[\RAISE\ \ERRARG], \ACCOUNTS] \| \BLOCKCHAIN}
 \end{mathpar}
-~\\
-~\\
-Rule 6 [rejected of fee]:
+
 \begin{mathpar}
-  \inferrule{
-    \NEG\ \CHECKGAS (\CONTRACTORS, \PUH, \PARAMETER, \MTEZ)\\
-    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
-  }{[\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \|
-      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
+  \inferrule[rejected of fee]{
+    \NEG\ \CHECKGAS (\BLOCKCHAIN.\CONTRACTORS, \PUH, \PARAMETER, \MTEZ) \\ \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ 
+  }{[\EC\OP  :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN    
     \SystemTrans
-    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
-      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}
+    [\EXPRS[\RAISE\ \ERRFEE], \ACCOUNTS] \| \BLOCKCHAIN}
 \end{mathpar}
-~\\
-~\\
-Rule 7 [included]:
+
 \begin{mathpar}
-  \inferrule{
+  \inferrule[block Accept]{
     \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK\PUH\MTEZ \\
-    \TIME'-\TIME < 60
+    \TIME-\hat\TIME \le 60
   }{
-    [\Angle{\OP, \OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
-    \CONTRACTORS, \TIME']
+    [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING} :: \PENDING, \MANAGERS,
+    \CONTRACTORS, \TIME]
     \BlockTrans \\
-    [\PENDING,
-    \Angle{\OP,\OPH, \TIME, \TIME'} :: \ACCEPTED,
-    \UPDATESUCC (\MANAGERS, \PUK, '', \NTEZ, \MTEZ),
+    [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING, 
+    \UPDATESUCC (\MANAGERS, \PUK, '', \NTEZ, \MTEZ), \\
     \UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \PARAMETER),
-    \TIME'+1]
+    \TIME+1]
   }
@@
 \section{Queries}
-Query 1 [balance of an account]:
 \begin{mathpar}
-  \inferrule{
+  \inferrule[counter]{
+    \BLOCKSYSTEM = 
+      [\PENDING, \PUK \mapsto \Angle{\BAL, \COU} :: \MANAGERS, \CONTRACTORS, \TIME]
+  }{[\EC{\GETCOUNTER\PUK} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
+    \NodeTrans\ [\EC{\COU} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
+\end{mathpar}
+
+\begin{mathpar}
+  \inferrule[balance of an implicit account]{
     \BLOCKCHAIN = 
-      [\PENDING, \ACCEPTED,  \Angle{\PUK, \BAL, \COU} :: \MANAGERS, \CONTRACTORS, \TIME]
-  }{[\epsilon[\GETBALANCE\PUK] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans\ [\epsilon[\BAL] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+      [\PENDING, \PUK \mapsto \Angle{\BAL, \COU} :: \MANAGERS, \CONTRACTORS, \TIME]
+  }{[\EC{\GETBALANCE\PUK} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
+    \NodeTrans\ [\EC{\BAL} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
 \end{mathpar}
-~\\
-~\\
-Query 2 [balance of smart contract]:
+
 \begin{mathpar}
-  \inferrule{
+\inferrule[balance of smart contract]{
     \BLOCKSYSTEM = 
-      [\PENDING, \ACCEPTED,  \MANAGERS, \Angle{\PUH, \BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
-  }{[\epsilon[\GETBALANCE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans\ [\epsilon[\BAL] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
+  }{[\EC{\GETBALANCE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
+    \NodeTrans\ [\EC{\BAL} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
 \end{mathpar}
-~\\
-~\\
-Query 3 [storage]:
+
 \begin{mathpar}
-  \inferrule{
+  \inferrule[storage]{
     \BLOCKSYSTEM = 
-      [\PENDING, \ACCEPTED,  \MANAGERS, \Angle{\PUH, \BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
-  }{[\epsilon[\GETSTORAGE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans\ [\epsilon[\STORAGE] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+      [\PENDING, \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
+  }{[\EC{\GETSTORAGE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
+    \NodeTrans\ [\EC{\STORAGE} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
 \end{mathpar}
-~\\
-~\\
-Query 4 [code]:
+
 \begin{mathpar}
-  \inferrule{
+  \inferrule[code]{
     \BLOCKSYSTEM = 
-      [\PENDING, \ACCEPTED,  \MANAGERS, \Angle{\PUH, \BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
-  }{[\epsilon[\GETCODE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans\ [\epsilon[\CODE] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
+  }{[\EC{\GETCODE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
+    \NodeTrans\ [\EC{\CODE} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
 \end{mathpar}
-~\\
-~\\
-Query 5 [counter]:
+
 \begin{mathpar}
-  \inferrule{
+  \inferrule[type]{
     \BLOCKSYSTEM = 
-      [\PENDING, \ACCEPTED,  \Angle{\PUK, \BAL, \COU} :: \MANAGERS, \CONTRACTORS, \TIME]
-  }{[\epsilon[\GETCOUNTER\PUK] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans\ [\epsilon[\COU] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
+  }{[\EC{\GETTYPE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
+    \NodeTrans\ [\EC{\Delta (\PUH)} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
 \end{mathpar}
-~\\
-~\\
-Query 6 [fail of a query for an account]:
+
 \begin{mathpar}
-  \inferrule{
+  \inferrule[fail of a query for an implicit account]{
     \NEG\ \CHECKPUB (\BLOCKCHAIN.\MANAGERS, \PUK) \
-  }{[\epsilon[\GETBALANCE\PUK/\GETCOUNTER\PUK] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans\\ [\epsilon[\RAISE\ \ERRPUK] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+  }{[\EC{\GETBALANCE\PUK/\GETCOUNTER\PUK} :: \EXPRS, \ACCOUNTS]  \| 
+  \BLOCKCHAIN 
+    \NodeTrans {[\EC{\RAISE\ \ERRPUK} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}}
 \end{mathpar}
-~\\
-~\\
-Query 7 [fail of a query for an account]:
+
 \begin{mathpar}
-  \inferrule{
-    \NEG\ \CHECKPUB (\BLOCKCHAIN.\CONTRACTORS, \PUH) 
-  }{[\epsilon[\GETBALANCE\PUH/\GETSTORAGE\PUH/\GETCODE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans\\ [\epsilon[\RAISE\ \ERRPUH] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+  \inferrule[fail of a query for a smart contract]{
+    \NEG\ \CHECKPUH (\BLOCKCHAIN.\CONTRACTORS, \PUH) 
+  }{[\EC{\GETBALANCE\PUH/\GETSTORAGE\PUH/\GETCODE\PUH/\GETTYPE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
+    \NodeTrans\\ [\EC{\RAISE\ \ERRPUH} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
 \end{mathpar}
-~\\
-~\\
-Query 8 [status-pending]:
+
 \begin{mathpar}
-  \inferrule{
+  \inferrule[status-pending]{
     \BLOCKSYSTEM = 
-      [\Angle{\OP, \OPH, \TIME'} :: \PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
-  }{[\epsilon[\GETSTATUS\OPH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans\ [\epsilon[\STATUSPENDING] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+      [\OPH \mapsto \Angle{\OP, \TIME, \STATUSPENDING} :: \PENDING,  \CONTRACTORS, \TIME]
+  }{[\EC{\GETSTATUS\OPH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
+    \NodeTrans\ [\EC{\STATUSPENDING} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
 \end{mathpar}
-~\\
-~\\
-Query 9 [status-including]:
+
 \begin{mathpar}
-  \inferrule{
+  \inferrule[status-including]{
     \BLOCKSYSTEM = 
-      [\PENDING, \Angle{\OP, \OPH, \TIME', \TIME''} :: \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME] \\
-    $n$ \ = \TIME\ - \TIME''
-  }{[\epsilon[\GETSTATUS\OPH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans\ [\epsilon[\STATUSINCLUDING($n$)] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+      [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME'} :: \PENDING,  \CONTRACTORS, \TIME] \\
+    $n$ \ = \TIME\ - \TIME'
+  }{[\EC{\GETSTATUS\OPH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
+    \NodeTrans\ [\EC{\STATUSINCLUDING($n$)} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
 \end{mathpar}
-~\\
-~\\
-Query 10 [status-timeout]:
+
 \begin{mathpar}
-  \inferrule{ 
-    \NEG\ \CHECKEXIST (\OPH, \BLOCKCHAIN.\PENDING, \BLOCKCHAIN.\ACCEPTED)
-  }{[\epsilon[\GETSTATUS\OPH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
-    \NodeTrans\ [\epsilon[\STATUSTIMEOUT] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
+  \inferrule[status-timeout]{ 
+   \BLOCKSYSTEM = 
+      [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSTIMEOUT} :: \PENDING, \CONTRACTORS, \TIME]
+  }{[\EC{\GETSTATUS\OPH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
+    \NodeTrans\ [\EC{\STATUSTIMEOUT} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
 \begin{enumerate}
-    \item Function \CHECKPUB (\PUK, \MANAGERS)\ checks whether a public key \PUK\ exists in \MANAGERS.
-    \item Function \CHECKPUH (\PUH, \CONTRACTORS)\ checks whether a public hash \PUH\ exists in \CONTRACTORS.
-    \item Function \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) checks whether the balance of the account that associates with the public key \PUK\ is greater or equal to \NTEZ\ plus \MTEZ.
-    \item Function \CHECKCOU (\MANAGERS, \PUK)\ checks whether the current counter of an account that associates with the public key \PUK\ is unlocked (its flag is False).
-    \item Function \CHECKEXIST (\OPH, \PENDING, \ACCEPTED)\ checks whether an operation  \OPH\ exists in either \PENDING\ or \ACCEPTED.
-    \item Function \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ) updates the balance and the counter of the account that associates with the public key \PUK\ and the balance of the account that associates with the public key \PUK', where
+    \item Function $\CHECKPUB(\MANAGERS, \PUK)$ checks whether a public key $\PUK$ exists in $\MANAGERS$.
     \begin{itemize}
-        \item[]  $\langle  \PUK, \BAL, (\NTEZ, \TRUE) \rangle $ $\Rightarrow$ $\langle  \PUK, \BAL - \NTEZ - \MTEZ, (\NTEZ + 1, \FALSE) \rangle $      
-        \item[] $\langle  \PUK', \BAL', \COU' \rangle$ $\Rightarrow$ $\langle  \PUK', \BAL' + \NTEZ, \COU' \rangle $         
+    \item[] $\CHECKPUB(\MANAGERS, \PUK)$ = $\TRUE$ iff $\PUK \in \DOM(\MANAGERS)$
+    \end{itemize}
+    \item Function $\CHECKPUH(\CONTRACTORS, \PUH)$ checks whether a public hash $\PUH$ exists in $\CONTRACTORS$.
+     \begin{itemize}
+    \item[] $\CHECKPUH(\CONTRACTORS, \PUH)$ = $\TRUE$ iff $\PUH \in \DOM(\CONTRACTORS)$
+    \end{itemize}
+    \item Function $\CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ)$ checks whether the balance of the account that associates with the public key $\PUK$ is greater or equal to $\NTEZ$ plus $\MTEZ$.
+    \begin{itemize}
+    \item[] $\MANAGERS(\PUK)$ = $\Angle{\BAL, \COU}$ and $\BAL \ge \NTEZ + \MTEZ$
+    \end{itemize}
+    \item Function $\CHECKCOU (\MANAGERS, \PUK)$ checks whether the current counter of an account that associates with the public key $\PUK$ is unlocked (its flag is False).
+    \begin{itemize}
+    \item[] $\MANAGERS(\PUK)$ = $\Angle{\BAL, \COU}$ and $\COU.b = \FALSE$
+    \end{itemize}
+   % \item Function \CHECKEXIST (\OPH, \PENDING, \ACCEPTED)\ checks whether an operation  \OPH\ exists in either \PENDING\ or \ACCEPTED.
+    \item Function $\UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ)$ updates the balance and the counter of the account that associates with the public key $\PUK$ and the balance of the account that associates with the public key $\PUK'$, where
+    \begin{itemize}
+        \item[]  $\PUK \mapsto \Angle{\BAL, (\hat\NTEZ, \TRUE)}$ $\Rightarrow$ $ \PUK \mapsto \Angle{\BAL - \NTEZ - \MTEZ, (\hat\NTEZ + 1, \FALSE)}$     
+        \item[] $\PUK' \mapsto \langle  \BAL', \COU' \rangle$ $\Rightarrow$ $\PUK' \mapsto \langle \BAL' + \NTEZ, \COU' \rangle $         
     \end{itemize}
 
-    \item Function \UPDATECOU(\MANAGERS, \PUK, \BOOLEAN) updates the counter flag (True $=$ locked, False $=$ unlocked) of the account that associates with the public key \PUK, where
+    \item Function $\UPDATECOU(\MANAGERS, \PUK, \BOOLEAN)$ updates the counter flag (True $=$ locked, False $=$ unlocked) of the account that associates with the public key $\PUK$, where
     \begin{itemize}
-        \item[]  $\langle  \PUK, \BAL, (\NTEZ, \BOOLEAN') \rangle $ $\Rightarrow$ $\langle  \PUK, \BAL, (\NTEZ, \BOOLEAN) \rangle $ 
+        \item[]  $ \PUK \mapsto \langle \BAL, (\NTEZ, \hat\BOOLEAN) \rangle $ $\Rightarrow$ $\PUK \mapsto \langle \BAL, (\NTEZ, \BOOLEAN) \rangle $ 
     \end{itemize}
 
-    \item Function  \UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \PARAMETER) updates the contractor that associates with the public hash \PUH\, where
+    \item Function  $\UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \PARAMETER)$ updates the contractor that associates with the public hash $\PUH$, where
     \begin{itemize}
-        \item[] $\langle  \PUH, \BAL, \CODE, \STORAGE, \rangle $ $\Rightarrow$ $\langle  \PUH, \BAL + \NTEZ, \CODE, \\ \UPDATESTORAGE(\STORAGE,\CODE,\PARAMETER) \rangle $
+        \item[] $\PUH  \mapsto \langle   \CODE, \TIME, \BAL, \STORAGE, \rangle $ $\Rightarrow$ $\PUH  \mapsto \langle  \BAL + \NTEZ, \CODE, \\ \UPDATESTORAGE(\STORAGE,\CODE,\PARAMETER) \rangle $
     \end{itemize}
 
-    \item Function \CHECKPRG (\CODE, {\INIT /\PARAMETER}) checks whether the code \CODE\ and the initil stogare's valude (or the input parameter \PARAMETER) are well type.
+     \item Function $\UPDATESTORAGE(\STORAGE, \CODE,  \PARAMETER)$ returns the new storage by running the code $\CODE$ on the  current storage  $\STORAGE$ with  the input parameter $\PARAMETER$.
+
+    \item Function $\CHECKPRG (\CODE)$ checks whether the code $\CODE$ is well type.
+
+    \begin{itemize}
+        \item[] $\CHECKPRG (\CODE) = \TRUE$ iff $\CODE : \TPAIR\ \TYPE_p\ \TYPE_s$
+    \end{itemize}
+    \item Function $\CHECKINIT (\CODE, \INIT)$ checks whether the initil stogare valude is well type with corresponding to the code $\CODE$.
+    \begin{itemize}
+        \item[] $\CHECKINIT (\CODE, \INIT) = \TRUE$ iff $\CODE : \TPAIR\ \TYPE_p\ \TYPE_s$ and $\STRING : \TYPE_s$
+    \end{itemize}
+
+    \item Function $\CHECKARG (\CONTRACTORS, \PUH, \PARAMETER)$ checks whether the input parameter  $\PARAMETER$ to the smart contract $\PUH$ in $\CONTRACTORS$ is well type with corresponding to its code.
+    \begin{itemize}
+        \item[] $\CHECKARG (\CONTRACTORS, \PUH, \PARAMETER) = \TRUE$ iff $\Delta (\PUH) =
+  \TPAIR\ \TYPE_p\ \TYPE_s$ and $\PARAMETER : \TYPE_p$
+    \end{itemize}
+
    % \item Function \CHECKGAS(\CODE, \INIT, \MTEZ) checks whether the gas that is consumed to run the code \CODE\ for the initial value \INIT\ is less or equal to \MTEZ.
-    \item Function \CHECKGAS (...) checks whether the fee that is consumed to emit the opertion is less or equal to the fee \MTEZ. 
+    \item Function  $\CHECKGAS (\MANAGERS, \PUK,\NTEZ, \MTEZ)$/ $\CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ)$ / $\CHECKGAS (\CONTRACTORS, \PUH, \PARAMETER, \MTEZ)$ check whether the fee that is consumed to emit the opertion is less or equal to the fee \MTEZ.
     %run the code \CODE\ that associates with the public hash \PUH\ for the paremeter \PARAMETER\ is less or equal to \MTEZ.
-    \item Function \GENERATEOPH (\PUK, {\ADDR /\CODE}, \NTEZ, \MTEZ, {\INIT /\PARAMETER}, \TIME) generates an operation hash.
+    \item Function \GENERATEOPH (\PUK, {\ADDR /\CODE},{\INIT /\PARAMETER}, \NTEZ, \MTEZ,  \TIME) generates an operation hash.
 
-    \item Function \GENERATEHASH (\CODE, \INIT, \TIME, \TIME')  generates the public hash of a smart contract.
+    \item Function \GENERATEHASH (\CODE, \TIME)  generates the public hash of a smart contract.
 
-    \item Function \UPDATESTORAGE(\STORAGE, \CODE,  \PARAMETER) returns the new storage by running the code \CODE\ on the  storage  \STORAGE\ with  the input parameter \PARAMETER.
 \end{enumerate}

### 2021-01-18 assertions/examples/main.tex
Adds the assertion examples latex document

\documentclass{article}
\usepackage[utf8]{inputenc}

% Packages
\usepackage{xcolor}
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref} % for url command
\usepackage{amsmath}
\usepackage{xfrac}
\usepackage{listings}

% Command defines
\newcommand{\narrow}{\setlength\itemsep{0pt}}
\newcounter{todos}
\setcounter{todos}{0}
\newcommand{\todo}[1]{\textbf{\textcolor{red}{(TODO: #1)}}\refstepcounter{todos}\label{todo \thetodos}}

\input{solidity-highlighting}

\title{Examples for Interesting Formulas}
\author{Tamara Bernhardt, Julian Veigel}
\date{December 2020}

\begin{document}

\maketitle

%----------------------------------------------------------------------------------------
%	COLLECTION
%----------------------------------------------------------------------------------------
\section{Collection}\label{sec:collection}
The following list includes our whole collection of interesting formulas for distributed assertion checking. We went into more detail for some examples (marked in color) in the following chapter. The discussion, whether or not it's possible to implement assertion contracts for these examples for the Tezos and Ethereum blockchains is left out for the moment.

\begin{itemize}\narrow
    \item \textbf{Logic}
    \begin{itemize}
        \item \textcolor{olive}{CNF SAT Problem}
        \item \textcolor{olive}{DNF SAT Problem}
    \end{itemize}
    \item \textbf{Numerical}
    \begin{itemize}
        \item Number is a prime number
        \item One number is the greatest common divisor ($gcd$) of two other numbers
        \begin{itemize}
            \item \textcolor{olive}{Special case: Two numbers are coprime, i.e., $gcd(a,b) = 1$}
        \end{itemize}
        \item One number is the least common multiple of two other numbers
    \end{itemize}
\item \textbf{Arrays}
    \begin{itemize}
        \item Array is sorted
        \item Fulfills (balanced) binary search tree property, i.e., the left elements of subtree are smaller, right elements of subtree are greater than parent
        \begin{itemize}
            \item Problem: handling trees which are not full, e.g. by defining empty elements?!
        \end{itemize}
        \item \textcolor{olive}{Fulfills heap property, i.e.}
        \begin{itemize}
            \item Max-Heap: any child is smaller or equal than its parent
            \item \textcolor{olive}{Min-Heap: any child is greater or equal than its parent}
            \item Problem: handling trees which are not full, e.g. by defining empty elements?!
        \end{itemize}
        \item All Elements in one are bigger / smaller than in another
        \item One array is the reverse of another (similar to sorted array)
    \end{itemize}
    \item \textbf{Strings}
    \begin{itemize}
        \item All characters are upper case, lower case, \textcolor{olive}{alphanumerical}, ...
        \item One string is (not) a substring of another string (using slices)
    \end{itemize}
    \item \textbf{Sets}
    \begin{itemize}
        \item Set property is fulfilled: no element occurs twice (if set is represented as an array)
        \item \textcolor{olive}{Two sets are disjoint}
    \end{itemize}
\end{itemize}

\section{Examples}\label{sec:examples}

%----------------------------------------------------------------------------------------
%	CNF SAT Assignment
%----------------------------------------------------------------------------------------
\subsection{CNF SAT Problem}\label{subsec:cnfsat}
Instances of the SAT-problem consist of a propositional logic formula $F$, for which it needs to be determined if there exists a variable assignment $\mathcal{A}$ to the values $True$ or $False$, s.t. the formula is satisfied ($\mathcal{A}(F) = 1$). Most SAT-solvers expect $F$ to be in conjunctive normal form (CNF), i.e., a conjunction of a set of clauses, where clauses are disjunctions of variables or their negations (called literals).

Verifying whether a given assignment satisfies the formula takes $\mathcal{O}(n*m)$, where $n$ is the number of clauses and $m$ the number of variables (in the worst case, every variable is present as a literal in each clause).

\subsubsection{Encoding of variables, literals and clauses}
Consider a contract that takes a SAT problem formulated in CNF as a list of clauses $c$ and a variable assignment $a$, s.t. the formula is satisfied. To avoid having to handle the variables and their literals as strings and thus optimize runtime and memory consumption, we use an encoding scheme taken from this blogpost \cite{sabablog}: \\
Variables are encoded by a unique number starting from $0$ to $n-1$, where $n$ is the number of variables. The positive and negative literals of a variable encoded by $x$ is encoded by the function
\begin{align*}
encode(x) =
\begin{cases}
  $2x$  & \text{if x is a positive literal}\\
  $2x+1$ & \text{if x is a negated literal}\\
\end{cases}   
\end{align*}

Let's consider the following example:
\begin{align*}
F = (A \vee B) \wedge (B \vee \neg C) \text{, } \mathcal{A} = \{A \rightarrow False, B \rightarrow True, C \rightarrow False\}
\end{align*}
The list of variables $v=[A,B,C]$ occurring in $F$ is encoded as $v_{enc} = [0,1,2]$. We've already considered $F$ to be a list of clauses, but we can also look at clauses as a list of literals. After encoding the literals, $F$ is represented as $F_{enc} = [[0,2],[2,5]]$. Since the encoding of variables corresponds to their index in the list of variables, we can simply pass $\mathcal{A}$ as a list of booleans: $\mathcal{A}_{enc} = [False, True, False]$. Alternatively, $\mathcal{A}$ can be represented as a bitarray to reduce the memory consumption further. \\
Checking whether a literal is positive or negative is a simple bit-wise $AND$ operation:
\begin{align*}
\texttt{isPositive(x) = x \& 1 == 0}
\end{align*}
Looking up the variable of a literal is done by dividing the encoded literal by two, which corresponds to a bit-wise shift to the right:
\begin{align*}
\texttt{decode(x) = x >> 1}
\end{align*}

\subsubsection{Formulation in predicate logic}
Given that $F$ and $\mathcal{A}$ are encoded like this, the assumption that $\mathcal{A}$ satisfies $F$ can be expressed in predicate logic as follows:
\begin{gather*}\label{eq:cnf_sat_formal}
\begin{aligned}
(\forall i, \exists j) (0 \leq i < |F|) \wedge (0 \leq j < |F[i]|) &\Rightarrow ((isPos(F[i][j]) \wedge \mathcal{A}[decode(F[i][j])]) \\
&\vee (\neg isPos(F[i][j]) \wedge \neg \mathcal{A}[decode(F[i][j])])))
\end{aligned}
\end{gather*}

The transformed formula to check for any counterexamples is then:
\begin{gather*}\label{eq:cnf_sat_formal}
\begin{aligned}
(\exists i, \forall j) (0 \leq i < |F|) \wedge (0 \leq j < |F[i]|) &\wedge ((isPos(F[i][j]) \wedge \neg \mathcal{A}[decode(F[i][j])]) \\
&\vee (\neg isPos(F[i][j]) \wedge \mathcal{A}[decode(F[i][j])])))
\end{aligned}
\end{gather*}

\subsubsection{Assertion contract}
The corresponding assertion contract for this example is shown in listings \ref{lst:sattz} and \ref{lst:sattza}:
\lstinputlisting[caption=Michelson contract signature, label={lst:sattz}]{listings/sat.tz}
\lstinputlisting[caption=Assertion contract,label={lst:sattza}]{listings/sat.tza}

%----------------------------------------------------------------------------------------
%	DNF SAT Assignment
%----------------------------------------------------------------------------------------
\subsection{DNF SAT Problem and Proofs of Correctness}
SAT problems can also be formulated using the disjunctive normal form (DNF), a disjunction of clauses, which consist of conjunctions of literals. At first glance, one might think handling this case is just a matter of swapping the two quantifiers, i.e.
\begin{gather*}\label{eq:dnf_sat_formal}
\begin{aligned}
(\exists i, \forall j) (0 \leq i < |F|) \wedge (0 \leq j < |F[i]|) &\Rightarrow ((isPos(F[i][j]) \wedge \mathcal{A}[decode(F[i][j])]) \\
&\vee (\neg isPos(F[i][j]) \wedge \neg \mathcal{A}[decode(F[i][j])])))
\end{aligned}
\end{gather*}

However, this formula raises an interesting problem for distributed assertion checking. Let's look at the transformation of the formula:
\begin{gather*}\label{eq:cnf_sat_formal}
\begin{aligned}
(\forall i, \exists j) (0 \leq i < |F|) \wedge (0 \leq j < |F[i]|) &\wedge ((isPos(F[i][j]) \wedge \neg \mathcal{A}[decode(F[i][j])]) \\
&\vee (\neg isPos(F[i][j]) \wedge \mathcal{A}[decode(F[i][j])])))
\end{aligned}
\end{gather*}

Due to the disjunction, finding two random numbers $i,j$ for which the transformed formula evaluates to false will produce a false counterexample - more so, it will actually produce a proof of correctness! In that case, the caller of the contract would need to wait until it receives a proof from one of the validators. \\
This raises an important question: how can the caller differentiate between the two cases, i.e., waiting for a counterexample vs. waiting for a proof?
In the cases of single quantifiers, the answer is trivial. Existential quantifiers will require a proof, whereas universal quantifiers require a counterexample. However, it's less obvious for nested quantifiers, especially since nothing is stopping the programmer of an assertion contract from swapping the order of quantifiers. Currently, the following two cases are not handled differently in our transformation:
\begin{lstlisting}
(forall(i: int)
  (exists(j: int)
    ... ))

(exists(j: int)
  (forall(i: int)
    ... ))
\end{lstlisting}

Things we need to clarify/consider:
\begin{itemize}
    \item Is there a way to differentiate between requiring a proof/counterexample in case of nested quantifiers?
    \item If not:
        \begin{itemize}
            \item Does a defined order of quantifiers fix this?
                \begin{itemize}
                    \item Responsibility of programmer?
                    \item Can we even enforce a "correct" order of quantifiers?
                \end{itemize}
            \item Add explicit directives 'proof' and 'counterexample'?
            \begin{itemize}
                \item Could this replace "forall" and "exists" (see listing \ref{lst:proof})? Does it make writing the assertion less intuitive?
            \end{itemize}
        \end{itemize}
\end{itemize}

\begin{lstlisting}[label=lst:proof, caption=Alternative syntax using proof or counterexample expressions]
proof(n: int, m: int) ...

(proof
  (generate (n: int)
    (generate (m: int)
      ... )))
\end{lstlisting}

%----------------------------------------------------------------------------------------
%	COPRIME
%----------------------------------------------------------------------------------------
\subsection{Two numbers are coprime}\label{subsec:coprime}
The greatest common divisor ($gcd$) of two non zero integers is the largest integer that divides both evenly \cite{knuthtaocp02}. A more specific $gcd$-problem is to find two numbers which are coprime, also called relative prime. Coprime expresses the relation between two integers a and b, where the greatest common divisor between those two is one \cite{coprimewiki}, i.e., $gcd(a, b) = 1$. To check if two numbers are coprime it has to be ensured that there is no greater $gcd$ than one, which can be stated in a propositional formula.
\begin{equation}\label{eq:coprime-universial}
    (a < b): (\forall n) (2 \le n \le a) \Rightarrow \neg((a \mathbin{\%} n) = 0 \land (b \mathbin{\%} n) = 0)
\end{equation}
To check this it would take $\mathcal{O}(a)$, means linear time complexity. To find a contradiction to this condition we can formulate:
\begin{equation}\label{eq:coprime-existential}
    (a < b): (\exists n) (2 \le n \le a) \land ((a \mathbin{\%} n) = 0 \land (b \mathbin{\%} n) = 0)
\end{equation}
When it is ensured that the greater number is not evenly divided by the smaller one ($b\mathbin{\%}a=0$), the search space can reduced by half to $(2 \le n \le \lfloor \frac{a}{2} \rfloor)$, because in the upper half of the lower number no integer can evenly divide this number.

In order to take advantage of this, the assertion syntax would need to be able to create different generators for different conditions. Currently, we only allow \texttt{if-else} instructions inside an \texttt{assertion} expression; this use-case could be an argument to lift that restriction and allow contracts like this:
\lstinputlisting[caption=Assertion contract with conditional generators, label={lst:coprime}]{listings/coprime.tza}

However, this will make the transformation more involved, as the bounds cannot simply be merged with the generator anymore.

\subsubsection{Least common multiple}
A similar problem would be to check the least common multiple ($lcm$) of two numbers. There the space between the greater number and the stated $lcm$ has to be checked for a smaller one. This search space can be significantly reduced by only selecting numbers, which are multiples of the greater number and check if the smaller number can divide this number without remainder.
\begin{equation}\label{eq:lcm-existential}
    (a < b): (\exists n) (2 \le n < \frac{lcm}{b}) \land ((b*n) \mathbin{\%} a = 0)
\end{equation}

%----------------------------------------------------------------------------------------
%	HEAP
%----------------------------------------------------------------------------------------
\subsection{Array fulfills heap property}\label{subsec:heap}
There are two categories of heaps: min and max heaps. Both can be represented as binary trees. In a max heap, any given node has a lower or equal value than the value of its parent. In a min heap, the value is greater or equal \cite{heapwiki}. Binary heaps are often implemented as an array. Given an array representation of the tree according to Eytzinger's layout \cite{tree_array}, the parents and children of a node can be accessed as follows: \cite{heapgeeks}

\begin{lstlisting}[language=Solidity, style=Solidity, numbers=none, caption=Access a heap in array representation]
heap_array[(k-1)/2] // Get parent of actual node k
heap_array[(k*2)+1] // Get left child of actual node k
heap_array[(k*2)+2] // Get right child of actual node k
\end{lstlisting}
So to check if an array $a$ fulfills the min heap property, we can formulate it in the following predicate logic:
\begin{equation}\label{eq:heap-unversial}
  (\forall k) (1 \le k < |a|) \Rightarrow a[\lfloor(k-1)/2)\rfloor] \le a[k]
\end{equation}
This equation checks the direction from the child to the parent node. (Following the Exposé) The direction could also be turned around and every parent node could be checked against its child nodes, which does not change the number of comparisons.
\begin{equation}\label{eq:heap-unversial}
  (\forall k) (0 \le k \le \lfloor |a|/2 \rfloor) \Rightarrow a[k] \le a[2k+1] \land (2k+2 < |a| \Rightarrow a[k] \le a[2k+2])
\end{equation}
This test would need $\mathcal{O}(|a|)$, i.e., linear time complexity. To find a contradiction this can be formulated to
\begin{equation}\label{eq:heap-unversial}
  (\exists k) (1 \le k \le |a|) \land a[\lfloor(k-1)/2)\rfloor] > a[k]
\end{equation}
This example is similar to the example for checking if an array is sorted. Further such examples could be:
\begin{itemize}
    \item One array is the reverse of another
    \item Array fulfills binary search tree property (If not balanced, empty fields must be identified correctly)
\end{itemize}

%----------------------------------------------------------------------------------------
%	ALPHANUMERIC
%----------------------------------------------------------------------------------------
\subsection{String is alphanumeric}\label{subsec:alnum}
The characters used in an input string $s$ might need to fulfill different properties. For instance, all characters of a string must be alphanumeric, or expressed in regex each character must match \texttt{[a-zA-Z0-9] $\equiv$ [[:alnum:]]}. Similarly to checking every element of an array, this can be checked with a linear $\mathcal{O}(|s|)$ time complexity. To formulate this property we can state the logic
\begin{equation}\label{eq:alnum-unversial}
  (\forall n) (0 \le n < |s|) \Rightarrow alnum(s[n])
\end{equation}
The negation of this formula for finding a counterexample can also easily be stated as
\begin{equation}\label{eq:alnum-existential}
  (\exists n) (0 \le n < |s|) \land \neg alnum(s[n])
\end{equation}
Where
\begin{equation*}
    alnum(x) =
    \begin{cases}
    \bot & \quad \text{if } x \text{ is not alphanumeric}\\
    \top & \quad \text{if } x \text{ is alphanumeric}
  \end{cases}
\end{equation*}
Note that more complicated regular expressions involving operators like repetition or option are not feasible, since they require state, which is not compatible with our random testing approach.

%----------------------------------------------------------------------------------------
%	INTERSECTION
%----------------------------------------------------------------------------------------
\subsection{No intersection between two sets}\label{subsec:nointersection}
To check if two sets $u$ and $v$ have no common subset, every element of one set must be compared to all other elements of the other set. This comparison leads to a complexity of $\mathcal{O}(|u|*|v|)$. We furthermore can define the size of both sets together as n, i.e., $n = |u|+|v|$. The worst case for the run time would be that both sets have the same size, i.e., $|u| = |v| = n/2$. So we can see that this leads to a quadratic complexity $\mathcal{O}(n/2 * n/2) = \mathcal{O}(n^2/4) = \mathcal{O}(n^2)$. The formula to state this property is
\begin{equation}\label{eq:intersection-unversial}
  (\forall i, \forall j) (0 \le i < |u|) \land (0 \le j < |v|) \Rightarrow u[i] \neq v[j]
\end{equation}
To check this property the formula can be translated to existential quantification:
\begin{equation}\label{eq:intersection-existential}
  (\exists i, \exists j) (0 \le i < |u|) \land (0 \le j < |v|) \land u[i] = v[j]
\end{equation}
Further such examples could be:
\begin{itemize}
    \item All elements in one array are bigger than in another
\end{itemize}

%----------------------------------------------------------------------------------------
%	Estimate of effectiveness
%----------------------------------------------------------------------------------------
\section{Estimate of effectiveness}
What remains to be analyzed is how many test runs are needed for a formula in order to reach a specified certainty threshold. This is especially important for Tezos, where the number of active validators per cycle is rather small. To compensate for this, each validator might need to execute several test runs.

\subsection{Approach 1: Coupon Collector Problem}
A simple, yet naive first approach on finding a formula that gives the number of test runs, is to set it to the size of the search space $|\mathcal{S}|$.
However, the probability of finding a counterexample is low, since the generated random numbers will most likely contain duplicates and thus not cover the entire search space. Given $|\mathcal{S}| = n$, the probability that no duplicates are generated is given by
\begin{equation*}
    p = \prod_{i=1}^{n} \frac{i}{n}
\end{equation*}
For $n = 10$ the probability already drops to $0.036\%$.

This is called the "Coupon collector's problem"\cite{coupons} in probability theory. Let $T$ be the number of test runs that are executed until every element in the search space has been generated. The goal is to identify its expectation $E(T)$. For this, we apply the geometric probability distribution:

Since our random generator generates elements with an equal distribution, each number is generated with a probability of $1/n$. The probability to generate the $i$th new number is given by 
\begin{equation}
    p_i = \frac{n-i+1}{n}
\end{equation}
The expected value of a random variable $X$ is given by $E(X) = \frac{1}{p}$\cite{coupon_wiki}, thus the expected number of test runs for $n$ is 
\begin{equation}
E(T) = n \sum_{i=1}^{n} \frac{1}{i}
\end{equation}
The following table \ref{tab:prob_outcomes} shows the expected number of test runs $E(T)$ for different sizes of $\mathcal{S}$.\\
The variance of this value is given by
\begin{equation}
    \sigma^2 = \sum_{i=1}^{n-1} \frac{i}{n-1}
\end{equation}
from which the standard derivation $\sigma$ can easily be obtained by taking the square root. Some values for $\sigma$ are shown in table \ref{tab:prob_outcomes}. Having determined the expected value and the standard derivation, the \textit{central limit theorem} can be used to calculate a lower and an upper bound for the number of needed test runs. A 95\% confidence interval is found by adding $1.96 * \sigma$ on both sides of $E(T)$\cite{coupons}, as shown in table \ref{tab:prob_outcomes}.
\begin{table}[h]
    \centering
    \begin{tabular}{lllll}\label{tab:prob_outcomes}
        \thead{$n$} & \thead{$E(T)$} & \thead{$\sigma$} & lower bound & upper bound\\ \hline
        2 & 3.0 & 1.0 & 1.04 & 4.96\\
        5 & 11.4 & 2.53 & 6 & 16\\
        10 & 29.3 & 19.29 & 21 & 38\\
        20 & 71.95 & 7.21 & 58 & 86\\
        50 & 224.96 & 13.23 & 199 & 251 
    \end{tabular}
    \caption{$E(T)$ for search spaces of different sizes $n$}
    \label{tab:my_label}
\end{table}

This method targets a 100\% coverage of the search space, e.g. it obtains the number of test runs to find a counterexample with probability $p\approx1$. Section \ref{subsec:numberoftestruns} describes an approach to calculate the number of test runs necessary to reach a specified probability threshold.

\subsection{Approach 2: Achieving probability thresholds}\label{subsec:numberoftestruns}
As in the previous chapter defining the search space $\mathcal{S}$ as the set of all test runs, therefore any potentially existing counterexample is in this set. The size of this set is defined as $n = |\mathcal{S}|$, which is the number of test runs to test all possibilities.
For this calculation it is assumed that there exist exactly one counterexample in the complete search space.
Goal is to find a number $t$ of test runs (which should ideally be smaller than the size of the search space $n$), s.t. the probability $P_{c,t}$ of not finding the counterexample drops below a certain threshold $c$.

The probability of finding the counterexample with one test run is $n^{-1}$, and of not finding the counterexample $(1-\frac{1}{n})$. The probability of $t$ test runs not finding the counterexample is $(1-\frac{1}{n})^t$.

Making small changes to the Bernoulli's inequality approximation can be used for further calculation \cite{bernoulliwiki}:
\begin{equation}
    (1-\frac{1}{n})^t = ((1-\frac{1}{n})^n)^{\frac{t}{n}} \le e^{-\frac{t}{n}}
\end{equation}
because
\begin{equation*}
m>1: (1-\frac{1}{m})^m \le e^{-1}
\end{equation*}
So we can define the probability $P_{c,t}$ of not finding the counterexample with $t$ test runs \cite{peertopeerlecture}:
\begin{equation}
    P_{c,t} \le e^{-\sfrac{t}{n}}
\end{equation}
Now we can check how many test runs are necessary that this probability drops below a certain threshold $c$:
\begin{align}
    e^{-\sfrac{t}{n}} &\leq c && \text{with $c\le1$} \nonumber\\
    t &\geq -n\:\ln(c) \label{eq:testthreshold}
\end{align}
For $c = e^{-1}$ ($\approx 0.36788 = 36.788\:\%$) $t$ is exactly $n$. So for every threshold below this value there are more test runs needed than there are possibilities in the search space itself.

\subsection{Tezos Bakers}
In the current cycle (311) there are 418 registered bakers \cite{tezos_cycle}. However, not every baker that has been granted rights for baking are also actively making use of that right. According to \cite{bakendorse}, only 398 of the 418 bakers have participated in the current cycle. \\
Theoretically, every assertion formula with $E(T), t \le \text{\#active bakers}$ can be verified with a single test run per validator (baker), assuming that \textbf{all} validators execute the test run after receiving a request. If this assumption cannot be made, it might be necessary to request more test runs per validator, if $E(T)/t$  is too close to the number of active bakers. However, this conversely means accepting a potentially high overshoot of test runs (this is also the case for values of $E(T)/t$ slightly above the number of bakers).

\subsection{Results for the given examples}
For the first example, we provide full calculations with a given input size using both approaches for comparison. Since the calculations for the other examples will not differ, we only state the sizes of their search spaces.
\subsubsection{CNF SAT Problem}
In the case of the CNF SAT problem, at least one variable in every clause needs to be checked to verify the correctness of the assignment. Thus, the size of the search space is the number of clauses, i.e., $n = \#clauses$.

Let's assume a CNF with 20 clauses, i.e., $n = 20$. Using approach 1, we calculate the expected number of test runs:
\begin{equation*}
    E(T) = 20 \sum_{i=1}^{20} \frac{1}{i} = 71.95
\end{equation*}
As explained above, this will give us $p\approx 1$ that a counterexample is found if one exists. Using equation \ref{eq:testthreshold} to calculate the same, we set $c=0.01$ (as $c = 0$ will result in infinity) to achieve $p=0.99$:
\begin{equation*}
    t \geq -20\:\ln(0.01) = 92.1
\end{equation*}
A certainty of e.g. 90\% of finding a counterexample if one exists is achieved by
\begin{equation*}
    t \geq -20\:\ln(0.1) = 46.1
\end{equation*}

\subsubsection{DNF SAT Problem}
Similarly to CNF, the search space is also given by the number of clauses, i.e., $n = \#clauses$.

\subsubsection{Coprime numbers}
The size of the search space is defined by the smaller of the two numbers (named $a$ in the formula given above), namely
\begin{equation*}
    n =
    \begin{cases}
    a - 1 & \quad \text{if } b\mathbin{\%}a = 0\\
    \lfloor \frac{a}{2} \rfloor -1 & \quad \text{if } b\mathbin{\%}a \neq 0
  \end{cases}
\end{equation*}

\subsubsection{Array heap property}
The size of the search space equals the size of the array without the root node, i.e., $n = |a| - 1$.

\subsubsection{String is alphanumeric}
The size of the search space equals the size of the string, i.e., $n = |s|$.

\subsubsection{Disjoint sets}
In this case, the number of test runs can't simply be derived from a single search space, but both set sizes must be considered. In practice, the sets most likely won't be of the same size; therefore we must chose the size of the bigger set to make sure no element of the smaller set is included:
\begin{equation*}
    n =
    \begin{cases}
    |u| & \quad \text{if } |u| \ge |v| \\
    |v| & \quad \text{if } |u| < |v|
  \end{cases}
\end{equation*}

%----------------------------------------------------------------------------------------
%	EMBEDDED BIBLIOGRAPHY
%----------------------------------------------------------------------------------------
\begin{thebibliography}{9}
    \bibitem{tree_array}
    \url{https://algorithmica.org/en/eytzinger},\\
    accessed: December 26\textsuperscript{th}, 2020 16:14

    \bibitem{sabablog}
    \url{https://sahandsaba.com/understanding-sat-by-implementing-a-simple-sat-solver-in-python.html},\\
    accessed: December 18\textsuperscript{th}, 2020 16:54

    \bibitem{knuthtaocp02}
    Donald E. Knuth,
    \textit{The Art of Computer Programming, Vol. 2: Seminumerical Algorithms},
    Addison Wesley,
    3rd edition,
    1998.

    \bibitem{coprimewiki}
    \url{https://en.wikipedia.org/wiki/Coprime_integers},\\
    accessed: December 18\textsuperscript{th}, 2020 12:20

    \bibitem{heapwiki}
    \url{https://en.wikipedia.org/wiki/Heap_(data_structure)},\\
    accessed: December 18\textsuperscript{th}, 2020 15:31

    \bibitem{heapgeeks}
    \url{https://www.geeksforgeeks.org/array-representation-of-binary-heap/},\\
    accessed: December 18\textsuperscript{th}, 2020 15:40

    \bibitem{coupons} John Croucher, 2006, Collecting Coupon-A Mathematical Approach, Australian Senior Mathematics Journal
    \url{https://files.eric.ed.gov/fulltext/EJ744035.pdf},\\
    accessed: December 27\textsuperscript{th}, 2020 14:07

    \bibitem{coupon_wiki}
    \url{https://en.wikipedia.org/wiki/Coupon_collector},\\
    accessed: December 27\textsuperscript{th}, 2020 14:15

    \bibitem{tezos_cycle}
    \url{https://tzkt.io/cycles} \\
    accessed: December 28\textsuperscript{th}, 2020 11:54

    \bibitem{bakendorse}
    \url{https://bakendorse.com/#/cycles/311/projected_stats},\\
    accessed: December 28\textsuperscript{th}, 2020 12:17

    \bibitem{bernoulliwiki}
    \url{https://en.wikipedia.org/wiki/Bernoulli\%27s_inequality#Related_inequalities},\\
    accessed: January 5\textsuperscript{th}, 2021 19:29

    \bibitem{peertopeerlecture}
    Schindelhauer, Christian. \textit{"Chapter 3: First Structures, Part 2: CAN - The Next Level"}, Peer-to-Peer Networks, 2 April 2019, University of Freiburg. Lecture.
\end{thebibliography}

\end{document}

### 2021-01-18 assertions/examples/solidity-highlighting.tex
Adds the assertion examples latex document

% Copyright 2017 Sergei Tikhomirov, MIT License
% https://github.com/s-tikhomirov/solidity-latex-highlighting/

\usepackage{listings, xcolor}

\definecolor{verylightgray}{rgb}{.97,.97,.97}

\lstdefinelanguage{Solidity}{
	keywords=[1]{anonymous, assembly, assert, balance, break, call, callcode, case, catch, class, constant, continue, constructor, contract, debugger, default, delegatecall, delete, do, else, emit, event, experimental, export, external, false, finally, for, function, gas, if, implements, import, in, indexed, instanceof, interface, internal, is, length, library, log0, log1, log2, log3, log4, memory, modifier, new, payable, pragma, private, protected, public, pure, push, require, return, returns, revert, selfdestruct, send, solidity, storage, struct, suicide, super, switch, then, this, throw, transfer, true, try, typeof, using, value, view, while, with, addmod, ecrecover, keccak256, mulmod, ripemd160, sha256, sha3}, % generic keywords including crypto operations
	keywordstyle=[1]\color{blue}\bfseries,
	keywords=[2]{address, bool, byte, bytes, bytes1, bytes2, bytes3, bytes4, bytes5, bytes6, bytes7, bytes8, bytes9, bytes10, bytes11, bytes12, bytes13, bytes14, bytes15, bytes16, bytes17, bytes18, bytes19, bytes20, bytes21, bytes22, bytes23, bytes24, bytes25, bytes26, bytes27, bytes28, bytes29, bytes30, bytes31, bytes32, enum, int, int8, int16, int24, int32, int40, int48, int56, int64, int72, int80, int88, int96, int104, int112, int120, int128, int136, int144, int152, int160, int168, int176, int184, int192, int200, int208, int216, int224, int232, int240, int248, int256, mapping, string, uint, uint8, uint16, uint24, uint32, uint40, uint48, uint56, uint64, uint72, uint80, uint88, uint96, uint104, uint112, uint120, uint128, uint136, uint144, uint152, uint160, uint168, uint176, uint184, uint192, uint200, uint208, uint216, uint224, uint232, uint240, uint248, uint256, var, void, ether, finney, szabo, wei, days, hours, minutes, seconds, weeks, years},	% types; money and time units
	keywordstyle=[2]\color{teal}\bfseries,
	keywords=[3]{block, blockhash, coinbase, difficulty, gaslimit, number, timestamp, msg, data, gas, sender, sig, value, now, tx, gasprice, origin},	% environment variables
	keywordstyle=[3]\color{violet}\bfseries,
	identifierstyle=\color{black},
	sensitive=false,
	comment=[l]{//},
	morecomment=[s]{/*}{*/},
	commentstyle=\color{gray}\ttfamily,
	stringstyle=\color{red}\ttfamily,
	morestring=[b]',
	morestring=[b]"
}

\lstdefinestyle{Solidity}{
	backgroundcolor=\color{verylightgray},
	extendedchars=true,
	basicstyle=\footnotesize\ttfamily,
	showstringspaces=false,
	showspaces=false,
	numbers=left,
	numberstyle=\footnotesize,
	numbersep=9pt,
	tabsize=2,
	breaklines=true,
	showtabs=false,
	captionpos=b
}

### 2021-01-19 meeting-notes/20201108-expose-input-language.tex
Merge Master

@@
 \begin{center}
-  \begin{tabular}{|l|l|}
-    Michelson & OCaml \\\hline
+  \begin{tabular}{|l|l|l}
+    Michelson type & OCaml type & Comment \\\hline
     \texttt{string}& \texttt{string}  \\
-    \texttt{nat} & ? (\texttt{int}) \\
-    \texttt{int} & \texttt{int} \\ 
-    \texttt{bytes}& ? \\
+    \texttt{nat} & ? (\texttt{Z.t}) & \texttt{Zarith} \\
+    \texttt{int} & \texttt{Z.t} & \texttt{Zarith}\\ 
+    \texttt{bytes}& \texttt{bytes} \\
     \texttt{bool}&\texttt{bool} \\
@@
     \texttt{set t}&? \texttt{Set.Make (T).t} \\
-    \texttt{map k t}&? \texttt{`t Map.Make(K).t} \\
-    \texttt{big\_map k t}&? \texttt{`t Map.Make(K).t} \\
+    \texttt{map k t}&? \texttt{T Map.Make(K).t} \\
+    \texttt{big\_map k t}&? \texttt{T Map.Make(K).t} \\
+    \texttt{mutez} & \texttt{int64} \\
     \hline
@@
 
-We can represent Michelson parameter values with the following OCaml type using GADTs.
+We can represent Michelson parameter values with the following OCaml GADT.
 \begin{lstlisting}[language=Caml]
@@
 \end{lstlisting}
-Instead of using polymorphic variants, one could also define a binary
+Instead of using polymorphic variants for expressing alternatives, one could also define a binary
 sum type like Haskell's Either type.
@@
 \end{lstlisting}
-Not sure if deserialization is also needed, but it might be necessary
-to decode the current state of a contract. Deserialization may fail
+Deserialization is also needed to inspect values in the store of a
+contract. Deserialization may fail 
 and thus raise an exception.
@@
 stored type of the contract.
-The returned value contains the serializer from \lstinline/'t -> string/.
+The returned value contains the serializer from \lstinline/'t -> string/. The most
+straightforward implementation would be to invoke the untyped sync API
+with the serialized parameter.
 \begin{lstlisting}[language=Caml]

### 2021-01-19 papers/contract-modules/modules.tex
typo...
Merge Master

@@
 contract type MyContract = sig
-  paid entrypoint %bid_for_auction (value : int) 
+  paid entrypoint %bid_for_auction (v : int) 
   raises "closed"                 (** auction closed*)
@@
     : Tezos.pukh -> ?fee:Tezos.tz -> amount:Tezos.tz
-    -> int -> (Tezos.status, bid_for_auction_errors) Tezos.monad
+    -> int
+    -> (Tezos.status, bid_for_auction_errors) Tezos.monad
 
@@
     : Tezos.pukh -> ?fee:Tezos.tz -> ?amount:Tezos.tz
-    -> unit -> (Tezos.status, close_auction_errors) Tezos.monad
+    -> unit
+    -> (Tezos.status, close_auction_errors) Tezos.monad
 end
@@
 
-let close_auction destination ?(fee=50.0) ?(amount=0.0) _ =
+let close_auction destination ?(fee=50.0) ?(amount=0.0) v =
   ...
@@
     contract_addr
-    ~(serialize Tunit)
+    ~(serialize Tunit v)
     fee

### 2021-01-19 papers/execution-model/model.tex
Merge Master

@@
 \begin{align*}
-  \CONSTANT & ::= \INT %\mid \ADDR
-              \mid \OPH \mid \PUH \mid\PUK \mid \CODE \mid
+  \CONSTANT & ::= \ADDR \mid \OPH \mid \PUH \mid\PUK \mid \CODE \mid
               \NTEZ \mid \SUNIT \mid \FALSE \mid \TRUE \\
-  \STATUS & ::= \STATUSPENDING \mid \STATUSINCLUDING (\INT) \mid
+  \STATUS & ::= \STATUSPENDING \mid \STATUSINCLUDING (\dots) \mid
             \STATUSTIMEOUT \\
@@
   represented by a partial mapping $\CONTRACTORS : \TPUH \partialto
-  \TCODE \times \TIME  \times \TBAL \times  \TSTORAGE$. If $\CONTRACTORS (\PUH) = \langle
-  \CODE, \TIME, \BAL, \STORAGE \rangle $ is defined, then $\PUH$ is the
-  public hash of a contract,
-  $\CODE$ is its  code,
-  $\TIME$ is the time when it was accepted,
-  $\BAL$ is its current balance,
-  and $\STORAGE$ is its current storage.
+  \TBAL \times \TCODE \times \TSTORAGE$. If $\CONTRACTORS (\PUH) = \langle
+  \BAL, \CODE, \STORAGE \rangle $ is defined, then $\PUH$ is the
+  public hash of a contract, $\BAL$ is its current balance, $\CODE$ is its
+  code, and $\STORAGE$ is its current storage.
 \end{definition}
@@
 operation was injected, and $\STATUS$ is either $\STATUSPENDING$,
-$\STATUSINCLUDED\ \TIME'$, or $\STATUSTIMEOUT$.
-A pool $\PENDING$ is \emph{well-formed} if, for all $\OPH$, $\PENDING (\OPH) =
-  \Angle{\OP,\TIME, \STATUSINCLUDED\ \TIME'}$ implies $\TIME' \ge
-  \TIME$ and $\OPH = \GENERATEOPH (\OP, \TIME)$.
+$\STATUSINCLUDED\ \TIME'$, or $\STATUSTIMEOUT$. A pool $\PENDING$ is \emph{well-formed} if, for all $\OPH$, $\PENDING (\OPH) =
+  \Angle{\OP,\TIME, \STATUSINCLUDED\ \TIME'}$ implies $\TIME' \ge \TIME$.
 \end{definition}
@@
 \end{enumerate}
-\end{definition}
-\begin{definition}
-  Preserved by a step on a well-formed configuration $ [\EXPRS, \ACCOUNTS] \|
-  [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]$:
-  \todo[inline]{Is this preserved?}
-  \begin{itemize}
-  \item for all $\OPH$ in $\EXPRS$, $\OPH \in \DOM (\PENDING)$,
-  \item for all $\PUK$ in $\EXPRS$, $\PUK \in \DOM (\MANAGERS)$,
-  \item for all $\PUH$ in $\EXPRS$, $\PUH \in \DOM (\CONTRACTORS)$.
-  \end{itemize}
 \end{definition}
@@
   \item if $\STATUS =
-  \STATUSINCLUDED\ \TIME'$, then $\PUH =\GENERATEHASH (\CODE, \hat\TIME) \in \DOM (\CONTRACTORS)$ and $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$ (or $\CONTRACTORS(\PUH).\CODE = \CODE$).
+  \STATUSINCLUDED\ \TIME'$, then $\PUH =\GENERATEHASH (\CODE, \INIT, \hat\TIME) \in \DOM (\CONTRACTORS)$ and $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$ (or $\CONTRACTORS(\PUH).\CODE = \CODE$).
 
@@
 
- \item if $st = \STATUSPENDING$ and $\MANAGERS(\PUK) = \Angle{\BAL,
-     \COU}$, then $\BAL \ge \NTEZ +  \MTEZ$ 
+ \item if $st = \STATUSPENDING$ and $\MANAGERS(\PUK) = \Angle{\BAL, \COU}$, then $\BAL >= \NTEZ +  \MTEZ$
 \end{itemize}
@@
     \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
-    %\OPH = \GENERATEOPH (\PUK, \PUK','', \NTEZ, \MTEZ, \TIME) \\
-    \OPH = \GENERATEOPH (\OP, \TIME) \\
+    \OPH = \GENERATEOPH (\PUK, \PUK','', \NTEZ, \MTEZ, \TIME) \\
     \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ    
@@
 
-The timeout transition applies to all operations.
 \begin{mathpar}
   \inferrule[Block-Timeout]{
-    % \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
+    \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
     \TIME-\hat\TIME > 60
@@
       [\OPH \mapsto \Angle{\OP, \hat \TIME, \STATUSTIMEOUT}
-     :: \PENDING, \UPDATECOU(\MANAGERS, \OP.\PUK, \FALSE),
+     :: \PENDING, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
       \CONTRACTORS, \TIME]}
@@
 
-% \begin{itemize}
-% \item library call \texttt{call\_contract} with \texttt{confirmations:None} corresponds to
-%   \begin{enumerate}
-%   \item{} first \TirName{Node-Op'}, \TirName{Node-Inject'}
-%   \item{} first \TirName{Node-Op'}, \TirName{Node-Reject(balance,count,pubkey,fee)}
-%   \end{enumerate}
-% \item afterwards must check the status to find whether the
-%   transfer is still pending or \TirName{Block-Accept''} or
-%   \TirName{Block-Timeout''} has happened.
-% \item no further transfer is possible before the status is resolved to
-%   accept or timeout.
-% \end{itemize}
+\begin{itemize}
+\item library call \texttt{call\_contract} with \texttt{confirmations:None} corresponds to
+  \begin{enumerate}
+  \item{} first \TirName{Node-Op'}, \TirName{Node-Inject'}
+  \item{} first \TirName{Node-Op'}, \TirName{Node-Reject(balance,count,pubkey,fee)}
+  \end{enumerate}
+\item afterwards must check the status to find whether the
+  transfer is still pending or \TirName{Block-Accept''} or
+  \TirName{Block-Timeout''} has happened.
+\item no further transfer is possible before the status is resolved to
+  accept or timeout.
+\end{itemize}
 
@@
 \end{mathpar}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \iffalse 
@@
     \BlockTrans
-    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \OP.\PUK, \FALSE),
+    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
       \CONTRACTORS, \TIME']}
@@
 \fi
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Smart Contracts}
@@
     \CHECKINIT (\CODE, \STRING) \\
-    %\OPH = \GENERATEOPH(\PUK, \CODE, \STRING, \NTEZ, \MTEZ, \TIME) \\
-    \OPH = \GENERATEOPH(\OP, \TIME) \\
+    \OPH = \GENERATEOPH(\PUK, \CODE, \STRING, \NTEZ, \MTEZ, \TIME) \\
     \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ    
@@
     \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
-    \PUH = \GENERATEHASH(\CODE, \TIME) \\
+    \PUH = \GENERATEHASH(\CODE, \INIT, \TIME) \\
     \TIME-\hat\TIME  \le 60
@@
      [\EC{ \PUH}  :: \EXPRS, \ACCOUNTS] \|  [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING, \UPDATESUCC
-      (\MANAGERS, \PUK, \NTEZ, \MTEZ),\\ \PUH \mapsto  \Angle{\CODE, \TIME, \NTEZ, \STRING} :: \CONTRACTORS, \TIME+1]
+      (\MANAGERS, \PUK, \NTEZ, \MTEZ),\\ \PUH \mapsto  \Angle{\NTEZ, \CODE, \STRING} :: \CONTRACTORS, \TIME+1]
   }
@@
 
-% \begin{mathpar}
-%   \inferrule[Block-Timeout]{
-%     %\OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
-%     \TIME-\hat\TIME > 60
-% }{
-%       [ \OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING}
-%      ::\PENDING, \MANAGERS,
-%       \CONTRACTORS, \TIME]  
-%       \BlockTrans \\    
-%       [ \OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSTIMEOUT}
-%      :: \PENDING, \UPDATECOU(\MANAGERS, \OP.\PUK, \FALSE),
-%       \CONTRACTORS, \TIME] 
-%   }
+\begin{mathpar}
+  \inferrule[Block-Timeout]{
+    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
+    \TIME-\hat\TIME > 60
+}{
+      [ \OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING}
+     ::\PENDING, \MANAGERS,
+      \CONTRACTORS, \TIME]  
+      \BlockTrans \\    
+      [ \OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSTIMEOUT}
+     :: \PENDING, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
+      \CONTRACTORS, \TIME] 
+  }
 
-% \end{mathpar}
+\end{mathpar}
 ~\\
@@
     \CHECKGAS (\CONTRACTORS, \PUH, \PARAMETER, \MTEZ) \\
-%    \OPH = \GENERATEOPH (\PUK,\PUH, \PARAMETER,\NTEZ, \MTEZ, \TIME) \\
-    \OPH = \GENERATEOPH (\OP, \TIME) \\
+    \OPH = \GENERATEOPH (\PUK,\PUH, \PARAMETER,\NTEZ, \MTEZ, \TIME) \\
     \OP =  \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\    
@@
     \BLOCKSYSTEM = 
-      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
+      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
   }{[\EC{\GETBALANCE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
@@
     \BLOCKSYSTEM = 
-      [\PENDING, \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
+      [\PENDING, \MANAGERS, \PUH \mapsto \Angle{\BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
   }{[\EC{\GETSTORAGE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
@@
     \BLOCKSYSTEM = 
-      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
+      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
   }{[\EC{\GETCODE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
@@
     \BLOCKSYSTEM = 
-      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
+      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
   }{[\EC{\GETTYPE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
@@
     \begin{itemize}
-        \item[] $\PUH  \mapsto \langle   \CODE, \TIME, \BAL, \STORAGE, \rangle $ $\Rightarrow$ $\PUH  \mapsto \langle  \BAL + \NTEZ, \CODE, \\ \UPDATESTORAGE(\STORAGE,\CODE,\PARAMETER) \rangle $
+        \item[] $\PUH  \mapsto \langle   \BAL, \CODE, \STORAGE, \rangle $ $\Rightarrow$ $\PUH  \mapsto \langle  \BAL + \NTEZ, \CODE, \\ \UPDATESTORAGE(\STORAGE,\CODE,\PARAMETER) \rangle $
     \end{itemize}
@@
 
-    \item Function \GENERATEHASH (\CODE, \TIME)  generates the public hash of a smart contract.
+    \item Function \GENERATEHASH (\CODE, \INIT, \TIME)  generates the public hash of a smart contract.
 

### 2021-01-27 papers/execution-model/model.tex
another invariant
some typing rules
some changes to typing

--- 2021-01-18 papers/execution-model/model.tex
@@
 \begin{align*}
-  \TYPE & ::= \TADDR \mid \TOPH \mid \TPUH \mid \TPUK \mid \TCODE\ \TYPE \mid
+  \TYPE & ::= \TADDR \mid \TOPH \mid \TPUH\ \TYPE\ \TYPE \mid \TPUK \mid \TCODE\
+          \TYPE\ \TYPE \mid \TTEZ \mid
           \TINT \mid \TUNIT \mid \TBOOL \mid \TSTRING \mid \TSTATUS \\
@@
 \end{align*}
+
+Typing rules, relying on an external typing judgment
+$\JTypeCode\CODE\TYPE$ for the contract language and
+$\JTypeValue\STRING\TYPE$ for serialized values as stored on the blockchain.
+\begin{mathpar}
+  \inferrule{}{\JTypeExpr\TEnv\INT\TINT}
+
+  \inferrule{}{\JTypeExpr\TEnv\OPH\TOPH}
+
+  \inferrule{}{\JTypeExpr\TEnv\PUH{\TPUH\ ?\ ?}}
+
+  \inferrule{}{\JTypeExpr\TEnv\PUK\TPUK}
+
+  \inferrule{\JTypeCode \CODE{ \TPAIR\ \TYPE_p\ \TYPE_s}}{\JTypeExpr\TEnv\CODE{\TCODE\ \TYPE_p\ \TYPE_s}}
+
+  \inferrule{}{\JTypeExpr\TEnv\NTEZ\TTEZ}
+
+  \inferrule{}{\JTypeExpr\TEnv\SUNIT\TUNIT}
+
+  \inferrule{}{\JTypeExpr\TEnv\FALSE\TBOOL}
+
+  \inferrule{}{\JTypeExpr\TEnv\TRUE\TBOOL}
+
+  \inferrule{}{\JTypeExpr\TEnv\STATUSPENDING\TSTATUS}
+
+  \inferrule{}{\JTypeExpr\TEnv\STATUSTIMEOUT\TSTATUS}
+
+  \inferrule{}{\JTypeExpr\TEnv{\STATUSINCLUDING (\INT)}\TSTATUS}
+
+  \inferrule{}{\JTypeExpr\TEnv\ERROR\TEXCEPTION}
+
+  \inferrule{}{\JTypeExpr\TEnv\VARIABLE{\TEnv (\VARIABLE)}}
+
+  \inferrule{
+    \JTypeExpr{\TEnv, \VARIABLE:\TYPE'}\EXPR{\TYPE}
+  }{
+    \JTypeExpr\TEnv{\lambda\VARIABLE.\EXPR}{\TYPE'\to\TYPE}}
+
+  \inferrule{
+    \JTypeExpr\TEnv\EXPR{\TYPE'\to\TYPE} \\
+    \JTypeExpr\TEnv{\EXPR'}{\TYPE'}
+  }{
+    \JTypeExpr\TEnv{\EXPR\ \EXPR'}\TYPE
+  }
+
+  \inferrule{
+    \JTypeExpr\TEnv\EXPR\TYPE \\
+    \JTypeExpr\TEnv{\EXPR'}{\TYPE'}
+  }{
+    \JTypeExpr\TEnv{(\EXPR, \EXPR')}{\TPAIR\ \TYPE\ \TYPE'}
+  }
+
+  \inferrule{
+    \JTypeExpr\TEnv{\EXPR}{\TPAIR\ \TYPE\ \TYPE'}
+  }{
+    \JTypeExpr\TEnv{\FST\ \EXPR}\TYPE
+  }
+
+  \inferrule{
+    \JTypeExpr\TEnv{\EXPR}{\TPAIR\ \TYPE\ \TYPE'}
+  }{
+    \JTypeExpr\TEnv{\SND\ \EXPR}{\TYPE'}
+  }
+  \\\\
+  \inferrule{
+    \JTypeExpr\TEnv\EXPR\TEXCEPTION
+  }{
+    \JTypeExpr\TEnv{\RAISE\ \EXPR}\TYPE
+  }
+
+  \inferrule{
+    \JTypeExpr\TEnv\EXPR\TYPE \\
+    \JTypeExpr\TEnv{\EXPR'}{\TEXCEPTION\to\TYPE}
+  }{
+    \JTypeExpr\TEnv{\TRY\ \EXPR\ \EXCEPT\ \EXPR'}\TYPE
+  }
+  \\\\
+  % too generic
+  % \inferrule{
+  %   \JTypeExpr\TEnv{\EXPR_1}\TTEZ \\
+  %   \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
+  %   \JTypeExpr\TEnv{\EXPR_3}\TADDR \\
+  %   \JTypeExpr\TEnv{\EXPR_4}\TSTRING \\
+  %   \JTypeExpr\TEnv{\EXPR_5}\TTEZ
+  % }{
+  %   \JTypeExpr\TEnv{\TRANSFER[\EXPR_4]{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_5}}\TOPH
+  % }
+  %   
+  \inferrule{
+    \JTypeExpr\TEnv{\EXPR_1}\TTEZ \\
+    \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
+    \JTypeExpr\TEnv{\EXPR_3}\TPUK \\
+    % \JTypeExpr\TEnv{\EXPR_4}\TSTRING \\
+    \JTypeExpr\TEnv{\EXPR_5}\TTEZ
+  }{
+    \JTypeExpr\TEnv{\TRANSFER{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_5}}\TOPH
+  }
+
+  \inferrule{
+    \JTypeExpr\TEnv{\EXPR_1}\TTEZ \\
+    \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
+    \JTypeExpr\TEnv{\EXPR_3}\TPUH\ \TYPE_p\ \TYPE_s \\
+    \JTypeExpr\TEnv{\EXPR_4}{\TYPE_p} \\
+    \JTypeExpr\TEnv{\EXPR_5}\TTEZ
+  }{
+    \JTypeExpr\TEnv{\TRANSFER[\EXPR_4]{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_5}}\TOPH
+  }
+
+  \inferrule{
+    \JTypeExpr\TEnv{\EXPR_1}\TTEZ \\
+    \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
+    \JTypeExpr\TEnv{\EXPR_3}{\TCODE\ (\TPAIR\ \TYPE_p\ \TYPE_s)} \\
+    \JTypeExpr\TEnv{\EXPR_4}\TYPE_s \\ % really \TSTRING \\
+    \JTypeExpr\TEnv{\EXPR_5}\TTEZ
+  }{
+    \JTypeExpr\TEnv{\ORIGINATE{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_4}{\EXPR_5}}{
+      \TPUH\ \TYPE_p\ \TYPE_s} 
+  }
+\end{mathpar}
 
@@
    \end{itemize}
+ \item invariant for contractors:
+   for all $\PUH \in \DOM (\CONTRACTORS)$,
+   $\CONTRACTORS (\PUH) = \Angle{ \CODE, \TIME, \BAL, \STORAGE}$
+   implies that $\PUH = \GENERATEHASH (\CODE, \TIME)$.
 \end{itemize}
@@
 \item $\DOM (\Delta) = \DOM (\CONTRACTORS)$
-\item $\CONTRACTORS (\PUH).\CODE : \Delta (\PUH) \to FIXEDOUTPUTTYPE$
-\item $\CONTRACTORS (\PUH).\STORAGE : \TYPE_s$ where $\Delta (\PUH) =
-  \TPAIR\ \TYPE_p\ \TYPE_s$. 
+\item $\JTypeCode{\CONTRACTORS (\PUH).\CODE} {\Delta (\PUH)}$
+\item $\JTypeValue{\CONTRACTORS (\PUH).\STORAGE}{ \TYPE_s}$ where
+  $\Delta (\PUH) = \TPAIR\ \TYPE_p\ \TYPE_s$. 
 \end{itemize}

### 2021-01-28 papers/execution-model/model.tex
first cut on motivation

@@
 
-\title{Blockchain System}
+\title{A Typed Programmatic Interface to Contracts on the Blockchain}
 
@@
 \pagestyle{plain}
+\begin{abstract}
+  Integrating blockchain contracts in software systems requires a
+  programmatic interface. We propose a typed interface for this
+  purpose and establish some properties of the combined system. A
+  prototype of the interface is implemented in OCaml for the Tezos
+  blockchain. 
+\end{abstract}
+
+\section{Motivation}
+\label{sec:motivation}
+
+An auctioneer wants to run an auction on the blockchain using a smart
+contract. Once to the contract is deployed on the blockchain, the
+auction is open for bidding, but it should be closed after 48 hours,
+say. Bidding on the auction and closing the auction are two different
+entrypoints / methods of the auction contract.
+
+While it is acceptable for the auctioneer to deploy the contract manually, it
+is desirable to have a mechanism that reliably closes the auction
+after 48 hours have passed. So the auctioneer wants to write a program
+to do so.
+
+On the other side, a bidder may want to implement a certain bidding
+strategy that starts at a certain amount and increases the bid until a
+certain limit is reached. Of course, the bidder only increases if
+someone else placed a higher bid. So the bidder also wants to write a
+program to implement this strategy.
+
+Both tasks cannot be implemented as smart contracts because they react
+to external triggers. Closing requires
+to schedule the activation of a contract at a certain time and bidding
+requires to watch the state of the contract (current highest bid) and
+react if another bidder places a higher bid.
+
+On another level, running a contract requires to propose a fee to the
+blockchain, which may or may not be accepted. In any case, starting a
+contract may timeout for a range of different reasons. So just
+starting a contract with a fixed fee does not guarantee the contract's execution.
+This scenario can also be addressed by a program that tries to run the
+contract with successively increasing fees until the blockchain
+accepts the contract invocation. The program can also calculate the
+required fee by observing the current state of the blockchain.
+
+(From this scenario we see the required functionality for a
+programmatic interface to a blockchain:)
+
+\begin{itemize}
+\item query certain components like the state of a contract (to obtain
+  the current highest bid, to check the fees of the last block)
+\item invoke contracts and initiate transfers
+\end{itemize}
 
@@
 \begin{align*}
-  \TYPE & ::= \TADDR \mid \TOPH \mid \TPUH\ \TYPE\ \TYPE \mid \TPUK \mid \TCODE\
-          \TYPE\ \TYPE \mid \TTEZ \mid
+  \TYPE, \TYPEU & ::= \TADDR \mid \TOPH \mid \TPUH\ \TYPE\ \TYPEU \mid
+                  \TPUK \mid
+                  \TCODE\ \TYPE\ \TYPEU \mid \TTEZ \mid
           \TINT \mid \TUNIT \mid \TBOOL \mid \TSTRING \mid \TSTATUS \\
-  & \mid \TYPE\to\TYPE \mid \TPAIR\ \TYPE\ \TYPE \mid \TLIST\ \TYPE
-    \mid \TSUM\ \TYPE\ \TYPE \mid \TOPTION\ \TYPE \mid \TEXCEPTION
+  & \mid \TYPE\to\TYPEU \mid \TPAIR\ \TYPE\ \TYPEU \mid \TLIST\ \TYPE
+    \mid \TSUM\ \TYPE\ \TYPEU \mid \TOPTION\ \TYPE \mid \TEXCEPTION
 \end{align*}

### 2021-01-29 papers/execution-model/model.tex
Add files via upload
Add some more to Motivation (blue line)

@@
 \usepackage{fixme}
+\usepackage{listings}
+\usepackage{xcolor}
 
@@
 
+{\color{blue} Let us consider how this auction contract could be written in Michelson, the language of smart contracts in Tezos.
+The state of a smart contract is presented by the data in its storage on the blockchain.
+The input data provided with a contract invocation is specified as a parameter.
+
+\begin{lstlisting}[numbers=none]
+parameter (or (unit %close)
+              (mutez %bid)); # participant's bid
+storage (pair
+              (pair bool address)  # is bidding allowed,
+               contract owner's address
+              (pair mutez address) # current highest bid
+               and bidder's address
+        );
+\end{lstlisting}
+
+where \texttt{unit} is the type whose only value is \texttt{Unit}, \texttt{mutez} is a specific type for manipulating tokens in Tezos, and \texttt{pair} is a pair of values a and b of types (l) and (r) written as (\texttt{Pair a b}).
+
+There are two purposes for calling an auction contract: (1) a bid by a bidder, or (2) a contract closing by the contract owner.
+Michelson supports multiple entrypoints, distinguished by \texttt{or}.
+The contract's storage on the blockchain contains two pairs, the first pair containing the flag indicating whether bidding is allowed or the contract is closed and the address of the contract owner, and the second pair containing the current highest bid and the address of the bidder.
+Michelson is stack-based.
+It takes a pair of the parameter and the current storage as inputs and returns the updated storage and a list of internal operations.
+When a bidder invokes the contract to bid, its bid and address are updated in the storage if its bid is higher than the current highest bid, otherwise they are discharged.
+The closing of the contract is called by the contract owner when it reaches 48 hours }
+
 Both tasks cannot be implemented as smart contracts because they react
@@
 react if another bidder places a higher bid.
+
+{\color{blue} In contrast, these tasks are able to implement as programs that interact with the blockchain.
+We call the function that deploy a contract \texttt{originate-contract}, and the function that invokes a contract \texttt{call-contract}.
+The \texttt{get-state} function queries data on the blockchain and returns the storage of a contract.
+The \texttt{originate-contract} function results the contract's address on the blockchain.
+The program for a contract owner could be implemented by first deploying the contract, waiting 48 hours, and then calling the contract with the entrypoint \texttt{Unit} to close the contract.
+
+\begin{lstlisting}[numbers=none]
+address = orinigate-contract(script);
+Time.sleep(to-second(48));
+call-contract(address, Unit);
+\end{lstlisting}
+
+The bidding strategy could be implemented by first calling a contract with a minimum amount, watching the state of the contract, say every 5 minutes.
+If the bidder is not the current highest bidder and bidding is allowed, the bid has not reached the limit.
+He emits a contract call with a higher bid.
+
+\begin{lstlisting}[numbers=none]
+while get-state(address).flag = true and bid < limit do
+    bid = bid + a;
+    call_contract(address, bid);
+    Time.speep(5);
+done;
+\end{lstlisting}
+
+}
 

### 2021-01-29 papers/execution-model/model.tex
Add files via upload
Some on the abstract (blue lines)

@@
 \pagestyle{plain}
-\begin{abstract}
+\begin{abstract} {\color{blue} Smart contract applications can reach their full potential if software programs can sufficiently interact with smart contracts on the blockchain.}
   Integrating blockchain contracts in software systems requires a
-  programmatic interface. We propose a typed interface for this
-  purpose and establish some properties of the combined system. A
-  prototype of the interface is implemented in OCaml for the Tezos
-  blockchain. 
+  programmatic interface.
+We propose a typed interface for this purpose and establish some properties of the combined system.
+{\color{blue} In detail, we provide an execution model that allows type-safe interaction between programs and the blockchain.
+Some designed properties are proven by the model.} A
+  prototype of the interface is implemented in OCaml for the Tezos blockchain.
+{\color{blue} The OCaml API allows user-programs to interact with an auction smart contract on the blockchain in a type-safe manner.}
 \end{abstract}
@@
 \begin{lstlisting}[numbers=none]
-while get-state(address).flag = true and bid < limit do
+while get-state(address).flag = true and 
+get-state(address).highestBid > bid and bid < limit do
     bid = bid + a;

### 2021-01-29 papers/execution-model/model.tex
abstract

--- 2021-01-29 papers/execution-model/model.tex
@@
 
-\author{}
-\institute{}
+\author{Doan Thi Thu Ha \and
+Peter Thiemann\orcidID{0000-0002-9000-1239}}
+\institute{University of Freiburg, Germany\\
+\email{\{doanha,thiemann\}@informatik.uni-freiburg.de}
+}
 
@@
 \begin{abstract}
-  Integrating blockchain contracts in software systems requires a
-  programmatic interface. We propose a typed interface for this
-  purpose and establish some properties of the combined system. A
-  prototype of the interface is implemented in OCaml for the Tezos
-  blockchain. 
+  Smart contract applications on the blocking can only reach their full potential if
+  they can be integrated with traditional software systems. Invoking
+  contracts and observing the state of the blockchain requires a
+  programmatic interface. We propose a typed API for this
+  purpose and establish some properties of the combined
+  system. Specifically, we provide an execution model that
+  enables us to prove type-safe interaction between programs and the 
+  blockchain. We establish further properties of the model that
+  translate into requirements on the API. A prototype of the interface
+  is implemented in OCaml for the Tezos blockchain.
 \end{abstract}

### 2021-02-01 papers/execution-model/model.tex
Add files via upload

@@
 
-{\color{blue} Let us consider how this auction contract could be written in Michelson, the language of smart contracts in Tezos.
-The state of a smart contract is presented by the data in its storage on the blockchain.
+Both tasks cannot be implemented as smart contracts because they react
+to external triggers. Closing requires
+to schedule the activation of a contract at a certain time and bidding
+requires to watch the state of the contract (current highest bid) and
+react if another bidder places a higher bid.
+
+Let us consider how this auction contract could be written in Michelson, the language of smart contracts in Tezos.
+The state of a smart contract is presented in its storage on the blockchain.
 The input data provided with a contract invocation is specified as a parameter.
@@
 \end{lstlisting}
-
-where \texttt{unit} is the type whose only value is \texttt{Unit}, \texttt{mutez} is a specific type for manipulating tokens in Tezos, and \texttt{pair} is a pair of values a and b of types (l) and (r) written as (\texttt{Pair a b}).
+where \texttt{unit} is the type whose only value is \texttt{Unit}, \texttt{mutez} is a specific type for tokens in Tezos, and \texttt{pair} is a pair of values a and b of types (l) and (r) written as (\texttt{Pair a b}).
 
@@
 Michelson supports multiple entrypoints, distinguished by \texttt{or}.
-The contract's storage on the blockchain contains two pairs, the first pair containing the flag indicating whether bidding is allowed or the contract is closed and the address of the contract owner, and the second pair containing the current highest bid and the address of the bidder.
+The contract's storage contains two pairs, the first pair containing the flag indicating whether bidding is allowed or the contract is closed and the address of the contract owner, and the second pair containing the current highest bid and the address of the bidder.
 Michelson is stack-based.
 It takes a pair of the parameter and the current storage as inputs and returns the updated storage and a list of internal operations.
-When a bidder invokes the contract to bid, its bid and address are updated in the storage if its bid is higher than the current highest bid, otherwise they are discharged.
-The closing of the contract is called by the contract owner when it reaches 48 hours }
-
-Both tasks cannot be implemented as smart contracts because they react
-to external triggers. Closing requires
-to schedule the activation of a contract at a certain time and bidding
-requires to watch the state of the contract (current highest bid) and
-react if another bidder places a higher bid.
-
-{\color{blue} In contrast, these tasks are able to implement as programs that interact with the blockchain.
-We call the function that deploy a contract \texttt{originate-contract}, and the function that invokes a contract \texttt{call-contract}.
+When a bidder invokes the contract to bid, its bid and address are updated in the storage if the bid is higher than the current highest bid, otherwise they are discharged.
+The closing of the contract is called by the contract owner when it reaches 48 hours.
+
+Although closing contract and bidding strategy tasks are not able to be implemented in a smart contract, they could be in programs that interact with the blockchain.
+We call the function that deploy a contract \texttt{originate-contract}, and  it results the contract's address on the blockchain.
+The function that invokes a contract is \texttt{call-contract}.
 The \texttt{get-state} function queries data on the blockchain and returns the storage of a contract.
-The \texttt{originate-contract} function results the contract's address on the blockchain.
-The program for a contract owner could be implemented by first deploying the contract, waiting 48 hours, and then calling the contract with the entrypoint \texttt{Unit} to close the contract.
+The owner could first deploy the contract, waitg 48 hours, and then call the contract with the entrypoint \texttt{Unit} to close the contract.
 
@@
 \end{lstlisting}
-
-}
 

### 2021-02-01 papers/execution-model/model.tex
Add files via upload

@@
 
-\author{Doan Thi Thu Ha \and
+\author{Thi Thu Ha Doan\and
 Peter Thiemann\orcidID{0000-0002-9000-1239}}
@@
 
-Although closing contract and bidding strategy tasks are not able to be implemented in a smart contract, they could be in programs that interact with the blockchain.
-We call the function that deploy a contract \texttt{originate-contract}, and  it results the contract's address on the blockchain.
+Although contract closing  and bidding strategy tasks are not able to be implemented in a smart contract, they could be in programs that interact with smart contracts on the blockchain.
+We call the function that deploys a contract \texttt{originate-contract}, and  it returns the contract's address on the blockchain.
 The function that invokes a contract is \texttt{call-contract}.
-The \texttt{get-state} function queries data on the blockchain and returns the storage of a contract.
-The owner could first deploy the contract, waitg 48 hours, and then call the contract with the entrypoint \texttt{Unit} to close the contract.
+\texttt{get-state} function queries data on the blockchain and returns the storage of a contract.
+The owner could first deploy the contract, wait 48 hours, and then call the contract with the entrypoint \texttt{Unit} to close the contract.
 
@@
 \end{lstlisting}
+where \texttt{script} is the contract's script and \texttt{to-second} function converts hour to second.
 

### 2021-02-15 papers/execution-model/model.tex
semantics and typing of originate fixed
sync
abstract, intro, and start of motivation

@@
 \usepackage{fixme}
+\usepackage{xcolor}
 \usepackage{listings}
-\usepackage{xcolor}
-
+\lstdefinelanguage{michelson}{
+%  basicstyle=\ttfamily,
+  morekeywords={parameter,storage,or,unit,mutez,pair,bool,address}, sensitive=false,
+  morecomment=[l]{\#},
+  morecomment=[s]{/*}{*/},
+  morestring=[b]",
+}
+\lstset{language=michelson}
 \input{macros}
@@
 \begin{abstract}
-  Smart contract applications on the blocking can only reach their full potential if
+  Smart contract applications on the block chain can only reach their full potential if
   they can be integrated with traditional software systems. Invoking
@@
   blockchain. We establish further properties of the model that
-  translate into requirements on the API. A prototype of the interface
+  give rise to requirements on the API. A prototype of the interface
   is implemented in OCaml for the Tezos blockchain.
@@
 
+\section{Introduction}
+\label{sec:introduction}
+
+Smart contracts rarely live in isolation. To reach their full
+potential, it should be possible to integrate them with traditional
+software systems and to enable input from outside the blockchain. Such
+input requires trusted intermediaries that run so-called oracles \cite{oracles}. A
+smart contract registers a request and a callback with an oracle. The
+oracle invokes the callback as soon as an answer is available.
+
+We present two examples where integration of smart contracts is needed
+and propose a typed API for making such integration type safe.
+
 \section{Motivation}
@@
 
-An auctioneer wants to run an auction on the blockchain using a smart
-contract. Once to the contract is deployed on the blockchain, the
+Suppose you want to run an auction on the blockchain using a smart
+contract. Once to the contract is deployed, the
 auction is open for bidding, but it should be closed after 48 hours,
-say. Bidding on the auction and closing the auction are two different
-entrypoints / methods of the auction contract.
-
-While it is acceptable for the auctioneer to deploy the contract manually, it
-is desirable to have a mechanism that reliably closes the auction
-after 48 hours have passed. So the auctioneer wants to write a program
-to do so.
-
-On the other side, a bidder may want to implement a certain bidding
+say. Such a timeout is a typical task for an oracle. Rather than
+trusting a generic oracle, you prefer to roll your own mechanism that reliably closes the auction
+after 48 hours have passed. So you want to write a program to do so.
+
+As a bidder, you may want to implement a bidding
 strategy that starts at a certain amount and increases the bid until a
-certain limit is reached. Of course, the bidder only increases if
-someone else placed a higher bid. So the bidder also wants to write a
+limit is reached. Of course, you only want to increase if
+someone else placed a higher bid. So you also want to write a
 program to implement this strategy.
 
-Both tasks cannot be implemented as smart contracts because they react
-to external triggers. Closing requires
-to schedule the activation of a contract at a certain time and bidding
-requires to watch the state of the contract (current highest bid) and
+Neither task can be implemented as a smart contract alone because they react
+to external triggers. Closing requires to schedule the activation of a
+contract at a certain time and bidding 
+requires to watch the current highest bid of the contract and
 react if another bidder places a higher bid.
 
-Let us consider how this auction contract could be written in Michelson, the language of smart contracts in Tezos.
-The state of a smart contract is presented in its storage on the blockchain.
-The input data provided with a contract invocation is specified as a parameter.
-
-\begin{lstlisting}[numbers=none]
+For concreteness, Listing~\ref{lst:auction-contract-header} shows the
+header of an auction contract in Michelson \cite{michelson}. The
+\lstinline/parameter/ clause specifies the contract's parameter
+type. It is a sum type (indicated by \lstinline/or/) and each
+alternative constitutes an entrypoint, named \lstinline/%close/ and
+\lstinline/%bid/. Entrypoint \lstinline/%close/ takes a \texttt{unit}
+parameter and \lstinline/%bid/ takes an amount of tokens \texttt{mutez}.
+The \lstinline/storage/ clause declares the state of the contract,
+which is a nested pair type indicating whether bidding is allowed, the address of the
+contract owner (to prohibit unauthorized calls to \lstinline/%close/),
+the highest bid, and the bidder's address.
+\begin{lstlisting}[numbers=none,float,caption={Header of the auction contract},label={lst:auction-contract-header},captionpos=b,emph={close,bid},emphstyle=\underbar]
 parameter (or (unit %close)
@@
 storage (pair
-              (pair bool address)  # is bidding allowed,
-               contract owner's address
-              (pair mutez address) # current highest bid
-               and bidder's address
+          (pair bool address)  # bidding allowed, contract owner
+          (pair mutez address) # highest bid, bidder's address
         );
 \end{lstlisting}
-where \texttt{unit} is the type whose only value is \texttt{Unit}, \texttt{mutez} is a specific type for tokens in Tezos, and \texttt{pair} is a pair of values a and b of types (l) and (r) written as (\texttt{Pair a b}).
 
@@
 \begin{lstlisting}[numbers=none]
-address = orinigate-contract(script);
+address = originate-contract(script);
 Time.sleep(to-second(48));
@@
   \\&\mid \GETSTORAGE\PUH
-  \\&\mid \GETCODE\PUH 
-  \\&\mid \GETTYPE\PUH
+  % \\&\mid \GETCODE\PUH 
+  % \\&\mid \GETTYPE\PUH
+  \\&\mid \GETCONTRACT\OPH
 \end{align*}
@@
   \\& \mid \ORIGINATE\EXPR\EXPR\EXPR\EXPR\EXPR
-  \\&\mid \QOP\  \EXPR\\
+  \\&\mid \QOP\  \EXPR \mid \CONTRACT\ \TYPE\ \EXPR \mid \TOSTRING\
+  \EXPR \mid \FROMSTRING\ \TYPE\ \EXPR\\
   \QOP & ::= balance \mid status \mid storage \mid code \mid counter \mid type
@@
 \begin{align*}
-  \TYPE, \TYPEU & ::= \TADDR \mid \TOPH \mid \TPUH\ \TYPE\ \TYPEU \mid
+  \TYPE, \TYPEU & ::= \TADDR \mid \TOPH \mid
+                  \TCONTRACT\ \TYPE \mid
+                  % \TPUH\ \TYPE \mid
                   \TPUK \mid
@@
 
-  \inferrule{}{\JTypeExpr\TEnv\PUH{\TPUH\ ?\ ?}}
+  \inferrule{}{\JTypeExpr\TEnv\PUH{\TADDR}}
 
@@
 
-  \inferrule{\JTypeCode \CODE{ \TPAIR\ \TYPE_p\ \TYPE_s}}{\JTypeExpr\TEnv\CODE{\TCODE\ \TYPE_p\ \TYPE_s}}
+  \inferrule{\JTypeCode \CODE{ \TPAIR\ \TYPE_p\
+      \TYPE_s}}{\JTypeExpr\TEnv\CODE{\TCODE\ \TYPE_p\ \TYPE_s}}
+
+  \inferrule{\JTypeExpr\TEnv\EXPR\TADDR}{\JTypeExpr\TEnv{\CONTRACT\ \TYPE\ \EXPR}{\TOPTION
+      (\TCONTRACT\ \TYPE)}}
 
@@
     \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
-    \JTypeExpr\TEnv{\EXPR_3}\TPUK \\
+    % \JTypeExpr\TEnv{\EXPR_3}\TPUK \\
+    \JTypeExpr\TEnv{\EXPR_3}{\TCONTRACT\ \TUNIT} \\
     % \JTypeExpr\TEnv{\EXPR_4}\TSTRING \\
@@
     \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
-    \JTypeExpr\TEnv{\EXPR_3}\TPUH\ \TYPE_p\ \TYPE_s \\
-    \JTypeExpr\TEnv{\EXPR_4}{\TYPE_p} \\
+    \JTypeExpr\TEnv{\EXPR_3}\TCONTRACT\ \TYPE \\
+    \JTypeExpr\TEnv{\EXPR_4}{\TYPE} \\
     \JTypeExpr\TEnv{\EXPR_5}\TTEZ
@@
     \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
-    \JTypeExpr\TEnv{\EXPR_3}{\TCODE\ (\TPAIR\ \TYPE_p\ \TYPE_s)} \\
+    \JTypeExpr\TEnv{\EXPR_3}{\TCODE\ \TYPE_p\ \TYPE_s} \\
     \JTypeExpr\TEnv{\EXPR_4}\TYPE_s \\ % really \TSTRING \\
@@
   }{
-    \JTypeExpr\TEnv{\ORIGINATE{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_4}{\EXPR_5}}{
-      \TPUH\ \TYPE_p\ \TYPE_s} 
+    \JTypeExpr\TEnv{\ORIGINATE{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_4}{\EXPR_5}}\TOPH 
+  }
+\end{mathpar}
+
+Types for queries
+\begin{mathpar}
+  \inferrule{
+    \JTypeExpr\TEnv\EXPR\TPUK
+  }{
+    \JTypeExpr\TEnv {\QRY\ \GETCOUNTER\EXPR}\TINT
+  }
+
+  \inferrule{
+    \JTypeExpr\TEnv\EXPR\TADDR
+  }{
+    \JTypeExpr\TEnv {\QRY\ \GETBALANCE\EXPR}\TTEZ
+  }
+
+  \inferrule{
+    \JTypeExpr\TEnv\EXPR\TOPH
+  }{
+    \JTypeExpr\TEnv {\QRY\ \GETSTATUS\EXPR}\TSTATUS
+  }
+
+  \inferrule{
+    \JTypeExpr\TEnv\EXPR{\CONTRACT\ \TYPE}
+  }{
+    \JTypeExpr\TEnv {\QRY\ \GETSTORAGE\EXPR}\TSTRING
+  }
+
+  % \inferrule{
+  %   \JTypeExpr\TEnv\EXPR{\CONTRACT\ \TYPE}
+  % }{
+  %   \JTypeExpr\TEnv {\QRY\ \GETCODE\EXPR}?
+  % }
+  %   
+  % \inferrule{
+  %   \JTypeExpr\TEnv\EXPR{\CONTRACT\ \TYPE}
+  % }{
+  %   \JTypeExpr\TEnv {\QRY\ \GETTYPE\EXPR}?
+  % }
+  %   
+  \inferrule{
+    \JTypeExpr\TEnv\EXPR{\TOPH}
+  }{
+    \JTypeExpr\TEnv {\QRY\ \GETCONTRACT\EXPR}\TPUH
+  }
+\end{mathpar}
+
+Conversion to and from serialized storage; deserialization may fail
+with an exception
+\begin{mathpar}
+  \inferrule{
+    \JTypeExpr\TEnv\EXPR\TYPE \\
+    \SERIALIZABLE (\TYPE)
+  }{
+    \JTypeExpr\TEnv{\TOSTRING\ \EXPR}\TSTRING
+  }
+
+  \inferrule{
+    \JTypeExpr\TEnv{\EXPR}\TSTRING
+  }{
+    \JTypeExpr\TEnv{\FROMSTRING\ \TYPE\ \EXPR}\TYPE
   }
@@
 
+\subsection{Special reductions}
+\label{sec:special-reductions}
+
+\begin{mathpar}
+  \inferrule[Contract?]{
+    \JTypeCode\CODE{\TPAIR\ \TYPE\ \TYPEU} \\
+    \BLOCKCHAIN.\CONTRACTORS (\PUH) =  \Angle{\CODE, \tilde\TIME, \NTEZ', \STRING'}
+    %
+    }{
+    { [\EC{\CONTRACT\ \TYPE\ \PUH}  :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+    }
+    \SystemTrans
+    { [\EC{\SOME\ \PUH} :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+   }
+  }
+
+  \inferrule[Contract-Implicit?]{
+    \PUK \in \DOM(\BLOCKCHAIN.\MANAGERS)
+    %
+    }{
+    { [\EC{\CONTRACT\ \TUNIT\ \PUK}  :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+    }
+    \SystemTrans
+    { [\EC{\SOME\ \PUK} :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+   }
+  }
+
+  \inferrule[Contract-No?]{
+    \ADDR \in \DOM (\BLOCKCHAIN.\MANAGERS) \Rightarrow \TYPE\ne\TUNIT \\
+    \BLOCKCHAIN.\CONTRACTORS (\ADDR) = \Angle{\CODE, \tilde\TIME,
+      \NTEZ', \STRING'} \Rightarrow {}
+        \JTypeCode\CODE{\TPAIR\ \TYPE'\ \TYPEU} \wedge \TYPE \ne \TYPE' \\
+    }{
+    { [\EC{\CONTRACT\ \TYPE\ \ADDR}  :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+    }
+    \SystemTrans
+    { [\EC{\NONE} :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+   }
+  }
+\end{mathpar}
+
 \subsection{Transitions on Nodes}
@@
   }{
-      [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \| [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING} :: \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
-    \SystemTrans \\
-     [\EC{ \PUH}  :: \EXPRS, \ACCOUNTS] \|  [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING, \UPDATESUCC
+    [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING} :: \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
+    \BlockTrans \\
+     [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING, \UPDATESUCC
       (\MANAGERS, \PUK, \NTEZ, \MTEZ),\\ \PUH \mapsto  \Angle{\CODE, \TIME, \NTEZ, \STRING} :: \CONTRACTORS, \TIME+1]
+  }
+\end{mathpar}
+\begin{mathpar}
+  \inferrule[Block-Accept-Query]{
+    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
+    \PENDING (\OPH) =  \Angle{\OP,
+       \hat\TIME, \STATUSINCLUDING\ \tilde\TIME} \\
+    \CONTRACTORS (\PUH) =  \Angle{\CODE, \tilde\TIME, \NTEZ', \STRING'}
+  }{
+      [\EC{\QRY\ \GETCONTRACT\ \OPH}  :: \EXPRS, \ACCOUNTS] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
+    \SystemTrans 
+     [\EC{ \PUH}  :: \EXPRS, \ACCOUNTS] \|  [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
   }

### 2021-02-15 papers/execution-model/model.tex
more motivation

@@
 }
-\lstset{language=michelson}
+\lstset{language=Caml}
 \input{macros}
@@
 alternative constitutes an entrypoint, named \lstinline/%close/ and
-\lstinline/%bid/. Entrypoint \lstinline/%close/ takes a \texttt{unit}
-parameter and \lstinline/%bid/ takes an amount of tokens \texttt{mutez}.
+\lstinline/%bid/. Entrypoint \lstinline/%close/ takes a \lstinline{unit}
+parameter and \lstinline/%bid/ takes an amount of tokens of type \lstinline{mutez}.
 The \lstinline/storage/ clause declares the state of the contract,
-which is a nested pair type indicating whether bidding is allowed, the address of the
+which is a nested pair type indicating whether bidding is allowed (\lstinline{bool}), the address of the
 contract owner (to prohibit unauthorized calls to \lstinline/%close/),
-the highest bid, and the bidder's address.
-\begin{lstlisting}[numbers=none,float,caption={Header of the auction contract},label={lst:auction-contract-header},captionpos=b,emph={close,bid},emphstyle=\underbar]
+the highest bid (of type \lstinline{mutez}), and the bidder's address.
+\begin{lstlisting}[language=michelson,numbers=none,float,caption={Header of the auction contract},label={lst:auction-contract-header},captionpos=b,emph={close,bid},emphstyle=\underbar]
 parameter (or (unit %close)
@@
 
-There are two purposes for calling an auction contract: (1) a bid by a bidder, or (2) a contract closing by the contract owner.
-Michelson supports multiple entrypoints, distinguished by \texttt{or}.
-The contract's storage contains two pairs, the first pair containing the flag indicating whether bidding is allowed or the contract is closed and the address of the contract owner, and the second pair containing the current highest bid and the address of the bidder.
-Michelson is stack-based.
-It takes a pair of the parameter and the current storage as inputs and returns the updated storage and a list of internal operations.
-When a bidder invokes the contract to bid, its bid and address are updated in the storage if the bid is higher than the current highest bid, otherwise they are discharged.
-The closing of the contract is called by the contract owner when it reaches 48 hours.
-
-Although contract closing  and bidding strategy tasks are not able to be implemented in a smart contract, they could be in programs that interact with smart contracts on the blockchain.
-We call the function that deploys a contract \texttt{originate-contract}, and  it returns the contract's address on the blockchain.
-The function that invokes a contract is \texttt{call-contract}.
-\texttt{get-state} function queries data on the blockchain and returns the storage of a contract.
-The owner could first deploy the contract, wait 48 hours, and then call the contract with the entrypoint \texttt{Unit} to close the contract.
-
+Here is an outline of the implementation of the entrypoints. The
+\lstinline/%close/ entrypoint first checks its sender's address
+against the owner's address in the store. Then it transfers the funds
+to the owner, closes the contract, and trusts the owner to deliver the
+goods.\footnote{For simplicity we elide safeguarding by a third-party oracle.}
+The \lstinline/%bid/ entrypoint rejects and reimburses each bid that is not higher
+than the existing highest bid. Otherwise, it keeps the funds
+transferred, returns the previous highest bid to its owner, and stores
+the current bid as the new highest bid.
+
+Timed contract closing and strategic bidding cannot be implemented in
+a smart contract, but could be implemented in separate programs that
+interact with the blockchain. We present some idealized code for these tasks.
+
+First the code that creates an auction contract and closes it after 48 hours. 
+\begin{lstlisting}[language=Caml,numbers=none]
+let initial_store = ((true, my_address), (1, my_address))
+let contract = Cl.originate(auction_script, 1, initial_store)
+Time.sleep(48 * 3600); (* 48h in seconds *)
+Cl.call_contract(contract, left ());
+\end{lstlisting}
+We assume that \lstinline/Cl/ is the contract library,  \lstinline/originate/ deploys its argument contract along with
+the provided funds and the \lstinline/initial_store/, 
+\lstinline{auction_script} is the contract from Listing~\ref{lst:auction-contract-header}, and 
+\lstinline{call_contract} invokes a contract with a parameter.
+
+To implement the bidding strategy, we first check the state of the
+contract to find the current highest bid. As long as bidding is
+allowed and the current bid is below our \lstinline/limit/, we update
+our bid by a given amount \lstinline/step/, and then keep watching the state of the contract by
+polling it every five minutes. 
 \begin{lstlisting}[numbers=none]
-address = originate-contract(script);
-Time.sleep(to-second(48));
-call-contract(address, Unit);
+let rec poll (limit, step, ((bidding, _), (high_bid, _))) =
+  if bidding and high_bid < limit then
+    Cl.call_contract (contract, 
+      right (min (high_bid + step, limit)));
+    Time.sleep(5);
+    let state = Cl.get_state (contract);
+    poll (limit, step, state)
+in
+poll (limit, step, Cl.get_state (contract))
 \end{lstlisting}
-where \texttt{script} is the contract's script and \texttt{to-second} function converts hour to second.
-
-The bidding strategy could be implemented by first calling a contract with a minimum amount, watching the state of the contract, say every 5 minutes.
-If the bidder is not the current highest bidder and bidding is allowed, the bid has not reached the limit.
-He emits a contract call with a higher bid.
-
-\begin{lstlisting}[numbers=none]
-while get-state(address).flag = true and 
-get-state(address).highestBid > bid and bid < limit do
-    bid = bid + a;
-    call_contract(address, bid); 
-    Time.speep(5);
-done;
-\end{lstlisting}
+The \lstinline{get_state} function queries data on
+the blockchain and returns the storage of a contract.
 

### 2021-02-16 papers/execution-model/model.tex
more motivation

@@
 strategy that starts at a certain amount and increases the bid until a
-limit is reached. Of course, you only want to increase if
+limit is reached. Of course, you only want to increase your bid if
 someone else placed a higher bid. So you also want to write a
@@
 
-Neither task can be implemented as a smart contract alone because they react
-to external triggers. Closing requires to schedule the activation of a
-contract at a certain time and bidding 
+Neither task can be implemented as a smart contract alone because both react
+to external triggers. Closing requires to schedule the invocation of a
+contract at a certain time. Bidding 
 requires to watch the current highest bid of the contract and
@@
 alternative constitutes an entrypoint, named \lstinline/%close/ and
-\lstinline/%bid/. Entrypoint \lstinline/%close/ takes a \lstinline{unit}
+\lstinline/%bid/. The caller selects the entrypoint by injecting the argument into the
+\lstinline/left/ or \lstinline/right/ summand. Entrypoint \lstinline/%close/ takes a \lstinline{unit}
 parameter and \lstinline/%bid/ takes an amount of tokens of type \lstinline{mutez}.
@@
 
-Here is an outline of the implementation of the entrypoints. The
+To avoid too much detail, we just outline the implementation of the entrypoints. The
 \lstinline/%close/ entrypoint first checks its sender's address
 against the owner's address in the store. Then it transfers the funds
-to the owner, closes the contract, and trusts the owner to deliver the
+to the owner, closes the contract by clearing the bidding flag, and
+leaves it to the owner to deliver the
 goods.\footnote{For simplicity we elide safeguarding by a third-party oracle.}
-The \lstinline/%bid/ entrypoint rejects and reimburses each bid that is not higher
+The \lstinline/%bid/ entrypoint immediately returns each bid that is not higher
 than the existing highest bid. Otherwise, it keeps the funds
@@
 First the code that creates an auction contract and closes it after 48 hours. 
-\begin{lstlisting}[language=Caml,numbers=none]
+\begin{lstlisting}[language=Caml,numbers=none,basicstyle=\small]
 let initial_store = ((true, my_address), (1, my_address))
@@
 Time.sleep(48 * 3600);               (* 48h in seconds *)
-Cl.call_contract(contract, left ());
+Cl.call_contract(contract, left ()); (* entrypoint %close *)
 \end{lstlisting}
-We assume that \lstinline/Cl/ is the contract library,  \lstinline/originate/ deploys its argument contract along with
-the provided funds and the \lstinline/initial_store/, 
+We assume that \lstinline/Cl/ is the module containing the contract
+library,  \lstinline/originate/ deploys its argument contract along
+with the provided funds and the \lstinline/initial_store/, 
 \lstinline{auction_script} is the contract from Listing~\ref{lst:auction-contract-header}, and 
@@
 polling it every five minutes. 
-\begin{lstlisting}[numbers=none]
+\begin{lstlisting}[numbers=none,basicstyle=\small]
 let rec poll (limit, step, ((bidding, _), (high_bid, _))) =
@@
     Cl.call_contract (contract, 
-      right (min (high_bid + step, limit)));
-    Time.sleep(5);
+      right (min (high_bid + step, limit))); (* entrypoint %bid *)
+    Time.sleep(5 * 60);
     let state = Cl.get_state (contract);
@@
 
-On another level, running a contract requires to propose a fee to the
-blockchain, which may or may not be accepted. In any case, starting a
-contract may timeout for a range of different reasons. So just
-starting a contract with a fixed fee does not guarantee the contract's execution.
-This scenario can also be addressed by a program that tries to run the
-contract with successively increasing fees until the blockchain
-accepts the contract invocation. The program can also calculate the
-required fee by observing the current state of the blockchain.
-
+This code is idealized in several respects. Originating or running a contract
+requires to propose a fee to the blockchain, which may or may not be
+accepted.
+Starting a contract may also time out for a variety of reasons. So just
+invoking a contract with a fixed fee does not guarantee the contract's
+execution.  Even if the invocation is locally accepted, it still takes
+a couple of cycles before we can be sure the invocation is globally
+accepted and incorporated in the blockchain.
+Hence, after starting the invocation, we have to observe the fate of
+this invocation. If it does not get incorporated, then we need to
+analyse the reason and react accordingly. For example, if the
+invocation was rejected because of a insufficient fee, we might want
+to restart with an increased fee. Or we might decide to wait until the
+invocation goes through with the low fee, if it is not that important.
+
+Hence, we would implement a scheme similar to
+the bidding strategy: start with a low fee and increase until the
+contract is accepted or a fee cap is reached. On the other hand, an
+observer function like \lstinline/get_state/ always succeeds.
+
+The low-level interface that we propose in this paper requires 
 (From this scenario we see the required functionality for a

### 2021-02-16 papers/execution-model/model.tex
sec 2 and 3

@@
 and propose a typed API for making such integration type safe.
+
+\subsection{Contributions}
+\label{sec:contributions}
+
+\begin{itemize}
+\item An operational semantics for functional programs running
+  alongside smart contracts in a blockchain. 
+\item Proofs of various properties of the combined system.
+\item An implementation of a low-level OCaml-API to the Tezos
+  blockchain, which corresponds to the operational semantics.
+\end{itemize}
 
@@
 analyse the reason and react accordingly. For example, if the
-invocation was rejected because of a insufficient fee, we might want
+invocation was rejected because of an insufficient fee, we might want
 to restart with an increased fee. Or we might decide to wait until the
-invocation goes through with the low fee, if it is not that important.
+invocation goes through without increasing the fee.
 
 Hence, we would implement a scheme similar to
-the bidding strategy: start with a low fee and increase until the
+the bidding strategy: start with a low fee and increase (or wait) until the
 contract is accepted or a fee cap is reached. On the other hand, an
@@
 
-The low-level interface that we propose in this paper requires 
-(From this scenario we see the required functionality for a
-programmatic interface to a blockchain:)
-
-\begin{itemize}
-\item query certain components like the state of a contract (to obtain
-  the current highest bid, to check the fees of the last block)
-\item invoke contracts and initiate transfers
-\end{itemize}
-
-\section{Definitions}
-\begin{definition}%[Set]
-Let $\mathbf{Elt}$ be the set of (concrete) elements. Let $\emptyset$ be an empty set and $\mathbf{e}$ $\in$  $\mathbf{Elt}$. A set of elements is expressed as the following syntax:
-\\
-$\mathbf{s} :: = \emptyset \mid \mathbf{e} \mid \mathbf{s :: s}$
-\end{definition}
+The low-level interface that we propose in this paper requires the
+programmer to be explicit about fees, waiting, and polling the state
+of contract invocations.
+
+In summary, a useful smart-contract-API  has facilities to
+\begin{itemize}
+\item query the current state of the blockchain (e.g., fees in the
+  current block),
+\item query the state and the balance of a contract (e.g., to obtain
+  the current highest bid),
+\item originate contracts, invoke contracts, and initiate
+  transfers. To this end, the program using the API has to run on
+  behalf of some authority (i.e., expressed by holding the private key
+  for some account).
+\end{itemize}
+All these facilities are supported by the (untyped) RPC interface of the Tezos
+blockchain, which is the basis of our implementation.
+
+\section{Execution Model}
+\label{sec:execution-model}
+
+The execution model is an abstraction of the Tezos blockchain \cite{Tezos}
+augmented with functional (OCaml) programs that interact with the
+blockchain. As the blockchain is realized by a peer-to-peer network of
+independent nodes, interaction happens through
+\emph{local nodes} that receive requests to originate and invoke
+contracts from programs that run on a particular node. We model the blockchain
+itself as a separate, abstract global entity that represents the
+current consensual state of the system. Our model does not express
+low-level details, but relies on nondeterminism to describe
+the possible behaviors of the system.
+
+We write $\emptyset$ for the empty set and $\mathbf{e :: s}$ to
+decompose a set into an element $\mathbf{e}$ and a set  $\mathbf{s}$.
 

### 2021-02-16 papers/execution-model/model.tex
sec 3

@@
 low-level details, but relies on nondeterminism to describe
-the possible behaviors of the system.
+the possible behaviors of the system. In particular, we do
+\textbf{not} formalize the execution of the smart contracts
+themselves, we rather consider them as black boxes that execute in a
+safe-safe way. Tezos' smart contract language Michelson and its
+properties have been formalized elsewhere \cite{type-safe-michelson}.
 
@@
 
-\begin{definition}%[Account]
-  An implicit \emph{account} is represented by a key pair $\langle
-  %\ALS,
+A local node runs on behalf of authorities, which are called
+\emph{accounts} in Tezos. An account is represented by a key pair $\Angle{
   \PAK, \PUK
-  %, \PKH
-  \rangle $, where
-  $\PAK$ is its private key and $\PUK$ is its public key.
-\end{definition}
-
-\begin{definition}%[Operation]
-  \emph{Operations} are defined by the following grammar:
+} $, where $\PAK$ is a private key and $\PUK$ the corresponding public
+key in a public key encryption scheme.
+
+The local node offers operations to transfer tokens from one account
+to another, to invoke a contract, and to originate a contract on the blockchain.
 \begin{align*}
@@
 \end{align*}
-  where \NTEZ\ and \MTEZ\ are tokens, \ADDR\ is either a public
-  key for an implicit account  or a public hash for a smart contract,
-  \PARAMETER\ is an argument passed to the smart contract's script,
-  which is empty if it is a transfer to an implicit account, \CODE\ is
-  a script of the smart contract, \INIT\ is an initial value of the
-  contract's storage. 
-\end{definition}
-
-\begin{definition}%[Query]
+Here, \NTEZ\ and \MTEZ\ are tokens, \PUK\ is the public key of the
+sender, \ADDR\ is either a public 
+key for an implicit account (in case of a simple transfer)  or a
+public hash for a smart contract (for an invocation), \PARAMETER\ is
+the argument passed to the smart contract, 
+which is empty for a simple transfer. Furthermore,  \CODE\ is
+a script of a smart contract and \INIT\ is the initial value of the
+contract's storage. Each operation returns an \emph{operation hash}
+\OPH, on which we can query the status of the operation.
+
+The local node also offer several ways to query the current state of
+the blockchain.
 \emph{Queries} are defined by the following grammar:
@@
   \QRY & ::=
-  \GETCOUNTER\PUK  
-  \\&\mid \GETBALANCE\ADDR
-  \\&\mid \GETSTATUS\OPH
-  \\&\mid \GETSTORAGE\PUH
-  % \\&\mid \GETCODE\PUH 
-  % \\&\mid \GETTYPE\PUH
-  \\&\mid \GETCONTRACT\OPH
+  % \GETCOUNTER\PUK  
+  %        \mid
+         \GETBALANCE\ADDR
+  \mid \GETSTATUS\OPH
+  \mid \GETSTORAGE\PUH
+  % \mid \GETCODE\PUH 
+  % \mid \GETTYPE\PUH
+  \mid \GETCONTRACT\OPH
 \end{align*}
-\end{definition}
-
-\begin{definition}%[Program]
-\emph{Expressions} are defined by the following grammar:
+We obtain the balance associated with an implicit account or a
+contract by its public key or public hash, respectively; the status of
+a submitted operation by its operation hash; the stored value of a
+contract by its public hash; and the code of a contract by the
+operation hash of its originating transaction.
+
+\begin{figure}[tp]
 \begin{align*}
-  \CONSTANT & ::= \INT %\mid \ADDR
+  \CONSTANT & ::= \INT \mid \FIX
               \mid \OPH \mid \PUH \mid\PUK \mid \CODE \mid
@@
 	\EXPR & :: =  \CONSTANT \mid \STATUS \mid \ERROR \mid \VARIABLE \mid \lambda \VARIABLE. \EXPR\ 
-	\mid \EXPR\EXPR \mid (\EXPR,\EXPR) \mid \FST\ \EXPR \mid \SND\ \EXPR 	%\mid \NI \EI
-	\\&\mid \EXPR\ \PLUS\ \EXPR\ \mid \EXPR\ \MINUS\ \EXPR\ \mid \EXPR\ \EQUAL\ \EXPR\ \mid \EXPR\ \LESS\ \EXPR
-	\\&\mid \EXPR\ \AND\ \EXPR\ \mid \EXPR\ \OR\ \EXPR\ \mid \NOT\ \EXPR
-  \\&\mid \NIL\ \mid \CONS\ \EXPR\ \EXPR \mid \LEFT\ \EXPR \mid\RIGHT\
+	\mid \EXPR\EXPR  %\mid \FST\ \EXPR \mid \SND\ \EXPR 	%\mid \NI \EI
+  \mid \EXPR\ \PLUS\ \EXPR\ \mid
+  % \EXPR\ \MINUS\ \EXPR\ \mid
+  \EXPR\ \EQUAL\ \EXPR\
+  % \mid  \EXPR\ \LESS\ \EXPR
+  \mid \EXPR\ \AND\ \EXPR\ \mid \EXPR\ \OR\ \EXPR\ \mid \NOT\ \EXPR
+  \\& \mid (\EXPR,\EXPR)\mid \NIL\ \mid \CONS\ \EXPR\ \EXPR \mid \LEFT\ \EXPR \mid\RIGHT\
   \EXPR \mid \SOME\ \EXPR \mid \NONE
+  \mid \MATCH\ \EXPR\ \WITH\ \PATTERN\to\EXPR \dots 
   \\& \mid \RAISE\ \EXPR \mid \TRY\ \EXPR\ \EXCEPT\ \EXPR
-  \\& \mid \MATCH\ \EXPR\ \WITH\ \PATTERN\to\EXPR \dots
   \\& \mid \TRANSFER[\EXPR]\EXPR\EXPR\EXPR\EXPR
   \\& \mid \ORIGINATE\EXPR\EXPR\EXPR\EXPR\EXPR
-  \\&\mid \QOP\  \EXPR \mid \CONTRACT\ \TYPE\ \EXPR \mid \TOSTRING\
-  \EXPR \mid \FROMSTRING\ \TYPE\ \EXPR\\
-  \QOP & ::= balance \mid status \mid storage \mid code \mid counter \mid type
+  \\&\mid \QOP\  \EXPR \mid
+  \CONTRACT\ \TYPE\ \EXPR \mid \TOSTRING\
+  \EXPR \mid \FROMSTRING\ \TYPE\ \EXPR
+  \\
+  \PATTERN &::= \VARIABLE \mid (\PATTERN, \PATTERN) \mid \NIL \mid \CONS\ \PATTERN\ \PATTERN \mid \LEFT\ \PATTERN \mid\RIGHT\
+             \PATTERN \mid \SOME\ \PATTERN \mid \NONE \\
+  &\mid \FALSE \mid \TRUE \mid \STATUS \mid \ERROR\\
+  \QOP & ::= balance \mid status \mid storage \mid code \mid counter
+         \mid type
+  \\[2ex]
+  \TYPE, \TYPEU & ::=
+                  \TADDR \mid \TOPH \mid
+                  \TCONTRACT\ \TYPE \mid
+                  % \TPUH\ \TYPE \mid
+                  \TPUK \mid
+                  \TCODE\ \TYPE\ \TYPEU \mid \TTEZ \mid
+          \TSTATUS \mid \TEXCEPTION \\
+  & \mid \TINT \mid \TUNIT \mid \TBOOL \mid \TSTRING \mid \TYPE\to\TYPEU \mid \TPAIR\ \TYPE\ \TYPEU \mid \TLIST\ \TYPE
+    \mid \TSUM\ \TYPE\ \TYPEU \mid \TOPTION\ \TYPE 
 \end{align*}
-We let $\EXPRS$ range over sets of expressions.
-
-We let $\ECS$ range over evaluation contexts. They are defined as
-follows.
+  \caption{Syntax of expressions, \EXPR, and types, \TYPE}
+  \label{fig:syntax-expressions}
+\end{figure}
+All queries and operations are started by closed expressions that run on the
+local node. Figure~\ref{fig:syntax-expressions} defines the syntax of
+expressions, which describe the usual constructs of call-by-value PCF
+with sum, product, list, and option types and exceptions. Moreover, there are
+primitive types and constants \CONSTANT\ to support blockchain
+operations, as well as several exceptional values collected in \ERROR.
+Pattern matching is the only means to decompose values, cf.\ \PATTERN.
+There is syntax to initiate transfers and to originate contracts as
+well as for the queries. Finally, the three constructs 
+\CONTRACT\ \TYPE\ \EXPR, \TOSTRING\  \EXPR, and \FROMSTRING\ \TYPE\
+\EXPR\ are casts between untyped and typed representations of
+contracts and their parameters.
+
+\begin{figure}[tp]
 \begin{align*}
-  \EC{} & :: = \SC[\overline\VAL\ \EC{}\ \overline\EXPR] \mid \RAISE\ \EC{} \mid \TRY\ \EC{}\ \EXCEPT\ \EXPR
-  \mid \MATCH\ \EC{}\ \WITH\ \PATTERN\to\EXPR \dots
-\end{align*}
-Here $\SC$ ranges over the remaining syntactic constructors, which are
-treated uniformly: evaluation proceeds from left to right.
-\begin{align*}
+  \ECN{} & :: = \ECHOLE \mid \SC[\overline\VAL\ \ECN{}\ \overline\EXPR] \mid \RAISE\ \ECN{} \mid \TRY\ \ECN{}\ \EXCEPT\ \EXPR
+  \mid \MATCH\ \ECN{}\ \WITH\ \PATTERN\to\EXPR \dots
+  \\
   \VAL & ::= \CONSTANT \mid \STATUS \mid \ERROR \mid \lambda x.\EXPR \mid(\VAL, \VAL) \mid
@@
 \end{align*}
-\end{definition}
-
-Example pseudo code
+  \caption{Evaluation contexts and values}
+  \label{fig:evaluation-contexts-values}
+\end{figure}
+Figure~\ref{fig:evaluation-contexts-values} defines evaluation
+contexts $\ECS$ and values $\VAL$.
+Here $\SC$ ranges over the remaining syntactic constructors, which are
+treated uniformly: evaluation proceeds from left to right. Values are
+standard for call-by-value lambda calculus.
+
+\begin{figure}[tp]
   \begin{align*}
-  \OPH &=  \TRANSFER[\EXPR]\EXPR\EXPR\EXPR\EXPR \\
+    \OPH &=  \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ \\
+    \\
          & \MATCH\ {status\ \OPH}\ \WITH \\
@@
   \end{align*}
+  \caption{Pseudocode example}
+  \label{fig:pseudocode-example}
+\end{figure}
+Figure~\ref{fig:pseudocode-example} shows an expression that invokes a
+contract at \PUH\ with argument \STRING.
+
 Grammar of types
-\begin{align*}
-  \TYPE, \TYPEU & ::= \TADDR \mid \TOPH \mid
-                  \TCONTRACT\ \TYPE \mid
-                  % \TPUH\ \TYPE \mid
-                  \TPUK \mid
-                  \TCODE\ \TYPE\ \TYPEU \mid \TTEZ \mid
-          \TINT \mid \TUNIT \mid \TBOOL \mid \TSTRING \mid \TSTATUS \\
-  & \mid \TYPE\to\TYPEU \mid \TPAIR\ \TYPE\ \TYPEU \mid \TLIST\ \TYPE
-    \mid \TSUM\ \TYPE\ \TYPEU \mid \TOPTION\ \TYPE \mid \TEXCEPTION
-\end{align*}
 

### 2021-02-17 papers/execution-model/model.tex
snapshot (with subtyping)

@@
 \label{sec:introduction}
+
+{[Ultra-brief intro to blockchain]}
 
@@
 
-Grammar of types
-
-Typing rules, relying on an external typing judgment
-$\JTypeCode\CODE\TYPE$ for the contract language and
-$\JTypeValue\STRING\TYPE$ for serialized values as stored on the blockchain.
+Subtyping
+\begin{mathpar}
+  \inferrule{}{\TPUH \SubType \TADDR}
+
+  \inferrule{}{\TPUK \SubType \TADDR}
+
+  \inferrule{}{\TCONTRACT\ \TYPE \SubType \TPUH}
+
+  \inferrule{\TYPEU' \SubType \TYPE' \\ \TYPE \SubType \TYPEU}{
+    \TYPE' \to \TYPE \SubType \TYPEU' \to \TYPEU}
+\end{mathpar}
+
+Figure~\ref{fig:typing-expressions} presents selected typing rules for
+expressions. We rely on an external typing judgment
+$\JTypeCode\CODE\TYPE$ for the contract language, which we leave
+unspecified, and $\JTypeValue\STRING\TYPE$ for serialized values as
+stored on the blockchain. The latter judgment states $\STRING$ is
+a string parseable as a value of type $\TYPE$.
+\begin{figure}[tp]
   \begin{mathpar}
@@
 
-  \inferrule{}{\JTypeExpr\TEnv\PUH{\TADDR}}
+    \inferrule{}{\JTypeExpr\TEnv\PUH{\TPUH}}
 
@@
 
-  \inferrule{\JTypeExpr\TEnv\EXPR\TADDR}{\JTypeExpr\TEnv{\CONTRACT\ \TYPE\ \EXPR}{\TOPTION
-      (\TCONTRACT\ \TYPE)}}
+    \inferrule{\JTypeExpr\TEnv\EXPR\TADDR}{\JTypeExpr\TEnv{\CONTRACT\
+        \TYPE\ \EXPR}{\TOPTION (\TCONTRACT\ \TYPE)}}
 
@@
 
-  \inferrule{}{\JTypeExpr\TEnv{\STATUSINCLUDING (\INT)}\TSTATUS}
+    \inferrule{\JTypeExpr\TEnv\EXPR\TINT}{\JTypeExpr\TEnv{\STATUSINCLUDING
+        (\EXPR)}\TSTATUS}
 
@@
 
+    \inferrule{\JTypeExpr\TEnv\EXPR\TYPE \\ \TYPE \SubType
+      \TYPEU}{\JTypeExpr\TEnv\EXPR\TYPEU}
+
     \inferrule{}{\JTypeExpr\TEnv\VARIABLE{\TEnv (\VARIABLE)}}
 
-  \inferrule{
-    \JTypeExpr{\TEnv, \VARIABLE:\TYPE'}\EXPR{\TYPE}
-  }{
+    \inferrule{ \JTypeExpr{\TEnv, \VARIABLE:\TYPE'}\EXPR{\TYPE} }{
       \JTypeExpr\TEnv{\lambda\VARIABLE.\EXPR}{\TYPE'\to\TYPE}}
@@
       \JTypeExpr\TEnv\EXPR{\TYPE'\to\TYPE} \\
-    \JTypeExpr\TEnv{\EXPR'}{\TYPE'}
-  }{
-    \JTypeExpr\TEnv{\EXPR\ \EXPR'}\TYPE
-  }
+      \JTypeExpr\TEnv{\EXPR'}{\TYPE'} }{ \JTypeExpr\TEnv{\EXPR\
+        \EXPR'}\TYPE }
 
@@
       \JTypeExpr\TEnv\EXPR\TYPE \\
-    \JTypeExpr\TEnv{\EXPR'}{\TYPE'}
-  }{
-    \JTypeExpr\TEnv{(\EXPR, \EXPR')}{\TPAIR\ \TYPE\ \TYPE'}
-  }
-
-  \inferrule{
-    \JTypeExpr\TEnv{\EXPR}{\TPAIR\ \TYPE\ \TYPE'}
-  }{
-    \JTypeExpr\TEnv{\FST\ \EXPR}\TYPE
-  }
-
-  \inferrule{
-    \JTypeExpr\TEnv{\EXPR}{\TPAIR\ \TYPE\ \TYPE'}
-  }{
-    \JTypeExpr\TEnv{\SND\ \EXPR}{\TYPE'}
-  }
-  \\\\
-  \inferrule{
-    \JTypeExpr\TEnv\EXPR\TEXCEPTION
-  }{
-    \JTypeExpr\TEnv{\RAISE\ \EXPR}\TYPE
-  }
-
-  \inferrule{
-    \JTypeExpr\TEnv\EXPR\TYPE \\
-    \JTypeExpr\TEnv{\EXPR'}{\TEXCEPTION\to\TYPE}
-  }{
-    \JTypeExpr\TEnv{\TRY\ \EXPR\ \EXCEPT\ \EXPR'}\TYPE
-  }
-  \\\\
-  % too generic
+      \JTypeExpr\TEnv{\EXPR'}{\TYPE'} }{ \JTypeExpr\TEnv{(\EXPR,
+        \EXPR')}{\TPAIR\ \TYPE\ \TYPE'} }
+  % 
     % \inferrule{
-  %   \JTypeExpr\TEnv{\EXPR_1}\TTEZ \\
-  %   \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
-  %   \JTypeExpr\TEnv{\EXPR_3}\TADDR \\
-  %   \JTypeExpr\TEnv{\EXPR_4}\TSTRING \\
-  %   \JTypeExpr\TEnv{\EXPR_5}\TTEZ
+    % \JTypeExpr\TEnv{\EXPR}{\TPAIR\ \TYPE\ \TYPE'}
     % }{
-  %   \JTypeExpr\TEnv{\TRANSFER[\EXPR_4]{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_5}}\TOPH
+    %   \JTypeExpr\TEnv{\FST\ \EXPR}\TYPE
     % }
   %   
+    %   \inferrule{
+    %   \JTypeExpr\TEnv{\EXPR}{\TPAIR\ \TYPE\ \TYPE'}
+    % }{
+    %   \JTypeExpr\TEnv{\SND\ \EXPR}{\TYPE'}
+    % }
+
+    \inferrule{ \JTypeExpr\TEnv\EXPR\TEXCEPTION }{
+      \JTypeExpr\TEnv{\RAISE\ \EXPR}\TYPE }
+
+    \inferrule{
+      \JTypeExpr\TEnv\EXPR\TYPE \\
+      \JTypeExpr\TEnv{\EXPR'}{\TEXCEPTION\to\TYPE} }{
+      \JTypeExpr\TEnv{\TRY\ \EXPR\ \EXCEPT\ \EXPR'}\TYPE }
+  \end{mathpar}
+  \caption{Typing rules for expressions}
+  \label{fig:typing-expressions}
+\end{figure}
+\begin{figure}[tp]
+  \begin{mathpar}
     \inferrule{
@@
       \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
-    % \JTypeExpr\TEnv{\EXPR_3}\TPUK \\
-    \JTypeExpr\TEnv{\EXPR_3}{\TCONTRACT\ \TUNIT} \\
-    % \JTypeExpr\TEnv{\EXPR_4}\TSTRING \\
-    \JTypeExpr\TEnv{\EXPR_5}\TTEZ
-  }{
-    \JTypeExpr\TEnv{\TRANSFER{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_5}}\TOPH
+      \JTypeExpr\TEnv{\EXPR_3}\TPUK \\
+      % \JTypeExpr\TEnv{\EXPR_3}{\TCONTRACT\ \TUNIT} \\
+      \JTypeExpr\TEnv{\EXPR_4}\TUNIT \\
+      \JTypeExpr\TEnv{\EXPR_5}\TTEZ }{
+      \JTypeExpr\TEnv{\TRANSFER[\EXPR_4]{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_5}}\TOPH
     }
@@
       \JTypeExpr\TEnv{\EXPR_4}{\TYPE} \\
-    \JTypeExpr\TEnv{\EXPR_5}\TTEZ
-  }{
+      \JTypeExpr\TEnv{\EXPR_5}\TTEZ }{
       \JTypeExpr\TEnv{\TRANSFER[\EXPR_4]{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_5}}\TOPH
@@
       \JTypeExpr\TEnv{\EXPR_4}\TYPE_s \\ % really \TSTRING \\
-    \JTypeExpr\TEnv{\EXPR_5}\TTEZ
-  }{
+      \JTypeExpr\TEnv{\EXPR_5}\TTEZ }{
       \JTypeExpr\TEnv{\ORIGINATE{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_4}{\EXPR_5}}\TOPH
@@
   \end{mathpar}
-
-Types for queries
 \begin{mathpar}
@@
   \inferrule{
-    \JTypeExpr\TEnv\EXPR{\CONTRACT\ \TYPE}
+    \JTypeExpr\TEnv\EXPR{\TPUH}
   }{
@@
 \end{mathpar}
+  \caption{Typing rules for blockchain operations and queries}
+  \label{fig:typing-blockchain-operations}
+\end{figure}
+% Generic rule for transfers
+% \begin{mathpar}
+%  \inferrule{
+%    \JTypeExpr\TEnv{\EXPR_1}\TTEZ \\
+%    \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
+%    \JTypeExpr\TEnv{\EXPR_3}\TADDR \\
+%    \JTypeExpr\TEnv{\EXPR_4}\TSTRING \\
+%    \JTypeExpr\TEnv{\EXPR_5}\TTEZ
+%  }{
+%    \JTypeExpr\TEnv{\TRANSFER[\EXPR_4]{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_5}}\TOPH
+%  }
+% \end{mathpar}
 

### 2021-02-17 papers/execution-model/model.tex
explain typing

@@
   \TYPE, \TYPEU & ::=
-                  \TADDR \mid \TOPH \mid
+                  \TPUH \mid
+                  \TPUK \mid
+                  \TADDR \mid 
                   \TCONTRACT\ \TYPE \mid
-                  % \TPUH\ \TYPE \mid
-                  \TPUK \mid
                   \TCODE\ \TYPE\ \TYPEU \mid \TTEZ \mid
+                  \TOPH \mid
                   \TSTATUS \mid \TEXCEPTION \\
@@
 
+Types (also in Figure~\ref{fig:syntax-expressions}) comprise a
+collection of standard base types as well as 
+functions, pairs, lists, sums, and option types. In addition, there
+are domain specific types of public hashes $\TPUH$ and public keys $\TPUK$ subsumed by
+a type of addresses $\TADDR$. $\TCONTRACT\ \TYPE$ is the type of
+a contract with parameter type $\TYPE$. $\CODE\ \TYPE\ \TYPEU$
+indicates a Michelson program with parameter type $\TYPE$ and storage
+type $\TYPEU$. Tezos tokens have type $\TTEZ$. The type $\TOPH$ signifies operation hashes
+returned by blockchain operations. Querying the status of an operation
+returns a value of type $\TSTATUS$. Exceptions have type
+$\TEXCEPTION$.
+
 \begin{figure}[tp]
@@
   \begin{align*}
-    \OPH &=  \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ \\
-    \\
-         & \MATCH\ {status\ \OPH}\ \WITH \\
+    \LET\ \OPH &=  \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+         & \MATCH\ \QRY\ \GETSTATUS\OPH\ \WITH \\
          & \mid \STATUSPENDING \to \textrm{not yet included, continue waiting} \\
@@
            blocks confirmation}\\
-         & \mid \STATUSTIMEOUT \to \textrm{lost, try again}
+         & \mid \STATUSTIMEOUT \to \textrm{lost operation, try again}
   \end{align*}
-  \caption{Pseudocode example}
+  \caption{Pseudocode example for a token transfer}
   \label{fig:pseudocode-example}
@@
 
-Subtyping
+Subtyping in Figure~\ref{fig:subtyping} etablishes that public hashes
+and public keys can both stand for addresses. Moreover, a smart
+contract with parameter type $\TYPE$ is represented by its public hash
+at run time. Subtyping for function types has the usual co-/contravariant definition.
+\begin{figure}[tp]
   \begin{mathpar}
@@
   \end{mathpar}
-
+  \caption{Subtyping}
+  \label{fig:subtyping}
+\end{figure}
 Figure~\ref{fig:typing-expressions} presents selected typing rules for

### 2021-02-18 papers/execution-model/model.tex
sec 3

@@
 We write $\emptyset$ for the empty set and $\mathbf{e :: s}$ to
-decompose a set into an element $\mathbf{e}$ and a set  $\mathbf{s}$.
+decompose a set into an element $\mathbf{e}$ and a set
+$\mathbf{s}$. We generally use lowercase boldface for metavariables
+ranging over values of a certain syntactic category, e.g., \PUK\ for
+public keys, and the corresponding uppercase name for the
+corresponding type or the set of these values (as in \TPUK).
 
@@
 \end{align*}
-Here, \NTEZ\ and \MTEZ\ are tokens, \PUK\ is the public key of the
+In the transfer, \NTEZ\ is the amount of tokens transferred, \PUK\ is the public key of the
 sender, \ADDR\ is either a public 
@@
 the argument passed to the smart contract, 
-which is empty for a simple transfer. Furthermore,  \CODE\ is
-a script of a smart contract and \INIT\ is the initial value of the
+which is empty for a simple transfer, and \MTEZ\ is
+the amount of tokens for the transaction fee. In originate,  \CODE\ is
+the script of a smart contract and \INIT\ is the initial value of the
 contract's storage. Each operation returns an \emph{operation hash}
@@
 
-The local node also offer several ways to query the current state of
+The local node offers several ways to query the current state of
 the blockchain.
@@
 operation hash of its originating transaction.
+
+\begin{definition}%[State of a node]
+  The \emph{state of a node} is a pair
+  $\NODE = [ \EXPRS, \ACCOUNTS
+  % , \OPERATIONS
+  ]$, where $\EXPRS$ is a
+  set of programs and $\ACCOUNTS \subseteq \TPAK \times \TPUK$  is a set of
+  implicit accounts.
+  % , and
+  % $\OPERATIONS \subseteq \ECS \times \TOP $ is a set of pairs of
+  % expression contexts and operations.
+\end{definition}
 
@@
   \mid \MATCH\ \EXPR\ \WITH\ \PATTERN\to\EXPR \dots 
-  \\& \mid \RAISE\ \EXPR \mid \TRY\ \EXPR\ \EXCEPT\ \EXPR
-  \\& \mid \TRANSFER[\EXPR]\EXPR\EXPR\EXPR\EXPR
+  \\& \mid \RAISE\ \EXPR \mid \TRY\ \EXPR\ \EXCEPT\ \EXPR \mid \CAST\EXPR\TYPE\TYPEU
+  \\& \mid \QOP\  \EXPR \mid \TRANSFER[\EXPR]\EXPR\EXPR\EXPR\EXPR
   \\& \mid \ORIGINATE\EXPR\EXPR\EXPR\EXPR\EXPR
-  \\&\mid \QOP\  \EXPR \mid
-  \CONTRACT\ \TYPE\ \EXPR \mid \TOSTRING\
-  \EXPR \mid \FROMSTRING\ \TYPE\ \EXPR
+  % \\&\mid \CONTRACT\ \TYPE\ \EXPR
+  \\& \mid \TOSTRING\ \EXPR \mid \FROMSTRING\ \TYPE\ \EXPR
   \\
@@
   &\mid \FALSE \mid \TRUE \mid \STATUS \mid \ERROR\\
-  \QOP & ::= balance \mid status \mid storage \mid code \mid counter
-         \mid type
+  \QOP & ::= \GETBALANCE{} \mid \GETSTATUS{} \mid \GETSTORAGE{} \mid \GETCODE{} \mid \GETCOUNTER{}
+         \mid \GETTYPE{}
   \\[2ex]
@@
 \end{figure}
-All queries and operations are started by closed expressions that run on the
+All queries and operations are started by programs, i.e., closed expressions that run on the
 local node. Figure~\ref{fig:syntax-expressions} defines the syntax of
 expressions, which describe the usual constructs of call-by-value PCF
-with sum, product, list, and option types and exceptions. Moreover, there are
+with sum, product, list, and option types, exceptions and fixpoint. Moreover, there are
 primitive types and constants \CONSTANT\ to support blockchain
@@
 There is syntax to initiate transfers and to originate contracts as
-well as for the queries. Finally, the three constructs 
-\CONTRACT\ \TYPE\ \EXPR, \TOSTRING\  \EXPR, and \FROMSTRING\ \TYPE\
-\EXPR\ are casts between untyped and typed representations of
-contracts and their parameters.
+well as for the queries. Finally, there is a type cast
+$\CAST\EXPR\TYPE\TYPEU$, which is only applicable to pairs of
+types related in the reflexive, transitive, and symmetric closure of
+the subtyping relation in Figure~\ref{fig:subtyping}. Upcasts will
+just go through, but downcasts may raise an exception, as usual.
 
@@
   \begin{align*}
-    \LET\ \OPH &=  \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
-         & \MATCH\ \QRY\ \GETSTATUS\OPH\ \WITH \\
-         & \mid \STATUSPENDING \to \textrm{not yet included, continue waiting} \\
-         & \mid \STATUSINCLUDING (n) \to \textrm{included with $n$
-           blocks confirmation}\\
-         & \mid \STATUSTIMEOUT \to \textrm{lost operation, try again}
+    \LET\ \mathit{oph} &=  \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+         & \FIX \lambda f.\lambda x. \MATCH\ \GETSTATUS{\mathit{oph}}\ \WITH \\
+         & \mid \STATUSPENDING \to \text{Time.sleep(1)}; f () \textrm{\qquad(* not yet included,
+           continue waiting *)} \\
+         & \mid \STATUSINCLUDING (n) \to \text{if } n < 50\text{ then
+           Time.sleep(1)};f ()\textrm{\quad(* included with $n$
+           blocks confirmation *)}\\
+         & \mid \STATUSTIMEOUT \to \textrm{(* lost operation, try
+           again *)}
   \end{align*}
@@
 \end{figure}
-Figure~\ref{fig:pseudocode-example} shows an expression that invokes a
-contract at \PUH\ with argument \STRING.
-
-Subtyping in Figure~\ref{fig:subtyping} etablishes that public hashes
-and public keys can both stand for addresses. Moreover, a smart
+Figure~\ref{fig:pseudocode-example} shows an incomplete example
+expression that transfers tokens from $\PUK$ to $\PUK'$ and then
+checks the status of the operation. The outer loop to raise the fee
+and retry is omitted.
+
+Our type system does not include subtyping. The relation in
+Figure~\ref{fig:subtyping} just etablishes pairs of types that can be
+subjected to casting. A cast from $\TYPE$ to $\TYPEU$ is only allowed
+if $\TYPE \SubType^* \TYPEU$ (upcast) or $\TYPEU \SubType^* \TYPE$
+(downcast). Upcasts always succeed, but downcasts may fail at run time.
+In particular,  public hashes and public keys can both stand for addresses. Moreover, a smart
 contract with parameter type $\TYPE$ is represented by its public hash
-at run time. Subtyping for function types has the usual co-/contravariant definition.
+at run time. The corresponding downcast must check whether the public
+hash is valid and has the expected parameter type.
 \begin{figure}[tp]
@@
     \inferrule{}{\TCONTRACT\ \TYPE \SubType \TPUH}
-
-    \inferrule{\TYPEU' \SubType \TYPE' \\ \TYPE \SubType \TYPEU}{
-      \TYPE' \to \TYPE \SubType \TYPEU' \to \TYPEU}
   \end{mathpar}
@@
 
-    \inferrule{\JTypeExpr\TEnv\EXPR\TADDR}{\JTypeExpr\TEnv{\CONTRACT\
-        \TYPE\ \EXPR}{\TOPTION (\TCONTRACT\ \TYPE)}}
-
+    % \inferrule{\JTypeExpr\TEnv\EXPR\TADDR}{\JTypeExpr\TEnv{\CONTRACT\
+    %     \TYPE\ \EXPR}{\TOPTION (\TCONTRACT\ \TYPE)}}
+    %     
     \inferrule{}{\JTypeExpr\TEnv\NTEZ\TTEZ}
@@
       \JTypeExpr\TEnv{\TRY\ \EXPR\ \EXCEPT\ \EXPR'}\TYPE }
+
+    \inferrule{
+      \JTypeExpr\TEnv\EXPR\TYPE \\
+      \TYPE \SubType \TYPEU \vee \TYPEU \SubType \TYPE
+    }{
+      \JTypeExpr\TEnv{\CAST\EXPR\TYPE\TYPEU}\TYPEU
+    }
   \end{mathpar}
@@
 \end{mathpar}
-
-\begin{definition}%[State of a node]
-  The \emph{state of a node} is a tuple
-  $\NODE = [ \EXPRS, \ACCOUNTS
-  % , \OPERATIONS
-  ]$, where $\EXPRS$ is a
-  set of programs and $\ACCOUNTS \subseteq \TPAK \times \TPUK$  is a set of
-  implicit accounts.
-  % , and
-  % $\OPERATIONS \subseteq \ECS \times \TOP $ is a set of pairs of
-  % expression contexts and operations.
-\end{definition}
 

### 2021-02-18 papers/execution-model/model.tex
slight revisions in section 2

@@
 \lstinline/%bid/. The caller selects the entrypoint by injecting the argument into the
-\lstinline/left/ or \lstinline/right/ summand. Entrypoint \lstinline/%close/ takes a \lstinline{unit}
-parameter and \lstinline/%bid/ takes an amount of tokens of type \lstinline{mutez}.
+\lstinline/left/ or \lstinline/right/ summand. Both entrypoints take a \lstinline{unit}
+parameter. The \lstinline/%bid/ entrypoint considers the transferred
+tokens as the bid.
 The \lstinline/storage/ clause declares the state of the contract,
-which is a nested pair type indicating whether bidding is allowed (\lstinline{bool}), the address of the
-contract owner (to prohibit unauthorized calls to \lstinline/%close/),
-the highest bid (of type \lstinline{mutez}), and the bidder's address.
+which is a nested pair type indicating whether bidding is allowed
+(\lstinline{bool}), the address of the contract owner (to prohibit
+unauthorized calls to \lstinline/%close/), and the bidder's
+address. The highest bid corresponds to the token balance of the contract.
 \begin{lstlisting}[language=michelson,numbers=none,float,caption={Header of the auction contract},label={lst:auction-contract-header},captionpos=b,emph={close,bid},emphstyle=\underbar]
 parameter (or (unit %close)
-              (mutez %bid)); # participant's bid
-storage (pair
-          (pair bool address)  # bidding allowed, contract owner
-          (pair mutez address) # highest bid, bidder's address
-        );
+              (unit %bid)); # bid in transfer
+storage (pair bool          # bidding allowed
+         (pair address      #  contract owner
+          address           # highest bidder's address
+        ));
 \end{lstlisting}
@@
 transferred, returns the previous highest bid to its owner, and stores
-the current bid as the new highest bid.
+the current bidder as the new highest bidder.
 
@@
 \begin{lstlisting}[language=Caml,numbers=none,basicstyle=\small]
-let initial_store = ((true, my_address), (1, my_address))
+let _ = Cl.set_authority (my_address)
+let initial_store = (true, (my_address, my_address))
 let contract = Cl.originate(auction_script, 1, initial_store)
@@
 We assume that \lstinline/Cl/ is the module containing the contract
-library,  \lstinline/originate/ deploys its argument contract along
-with the provided funds and the \lstinline/initial_store/, 
+library, \lstinline{set_authority} sets the sender address for
+upcoming operations,  \lstinline/originate/ deploys its argument contract along
+with the provided funds of one token and the \lstinline/initial_store/, 
 \lstinline{auction_script} is the contract from Listing~\ref{lst:auction-contract-header}, and 
-\lstinline{call_contract} invokes a contract with a parameter.
+\lstinline{call_contract} invokes a contract with a parameter. The
+\lstinline{initial_store} sets the bidding flag, and both owner and
+highest bidder to the sender account.
 

### 2021-02-18 papers/execution-model/model.tex
section-3

@@
 ranging over values of a certain syntactic category, e.g., \PUK\ for
-public keys, and the corresponding uppercase name for the
-corresponding type or the set of these values (as in \TPUK).
+public keys, and the capitalized name for the
+corresponding type as well as the set of these values (as in \TPUK).
 
@@
 operation hash of its originating transaction.
+
+The domain-specific types come with different guarantees. Values of
+type \TPUH\ and \TPUK\ as well as \TADDR\ are not necessarily valid,
+as there might be no contract associated with a hash / no account
+associated with a public key. In contrast, a value of type
+$\TCONTRACT\ \TYPE$ is a public hash that is verified to be associated
+with a contract with parameter type $\TYPE$. Operation hashes \OPH\
+are only returned from blockchain operations. As the surface language
+neither contains literals of type \TOPH\ nor are there casts into
+that type, all values of \TOPH\ are valid.
 
@@
 All queries and operations are started by programs, i.e., closed expressions that run on the
-local node. Figure~\ref{fig:syntax-expressions} defines the syntax of
+local node. Each program can send transactions on behalf of any
+account on the local node.  Figure~\ref{fig:syntax-expressions} defines the syntax of
 expressions, which describe the usual constructs of call-by-value PCF
 with sum, product, list, and option types, exceptions and fixpoint. Moreover, there are
-primitive types and constants \CONSTANT\ to support blockchain
+domain-specific primitive types and constants \CONSTANT\ to support blockchain
 operations, as well as several exceptional values collected in \ERROR.
@@
 subjected to casting. A cast from $\TYPE$ to $\TYPEU$ is only allowed
-if $\TYPE \SubType^* \TYPEU$ (upcast) or $\TYPEU \SubType^* \TYPE$
+if $\TYPE \SubType \TYPEU$ (upcast) or $\TYPEU \SubType \TYPE$
 (downcast). Upcasts always succeed, but downcasts may fail at run time.
@@
 
-\subsection{Global}
+\subsection{Global Structures}
 \label{sec:global}
 
-\begin{definition}%[Manager]
-A \emph{manager} manages a single implicit account. Managers are
-represented by a partial mapping $\MANAGERS : \TPUK \partialto \TBAL
+Our execution model abstracts from the particulars of the blockchain
+implementation, like the peer-to-peer structure or the distributed
+consensus protocol. Hence, we represent the blockchain by a few global
+entities: managers, contractors, and a pool of operations.
+
+%\begin{definition}%[Manager]
+A \emph{manager} keeps track of a single implicit account. Managers are
+represented by a partial map $\MANAGERS : \TPUK \partialto \TBAL
 \times \TCOU$. If $\MANAGERS (\PUK) = \Angle{\BAL, \COU}$ is defined, then  $\PUK$ is the
@@
 $(n,b) \in \Nat\times\TBOOL$, where $n$ is the value of the counter
-and ${b}$ is its flag.   
-\end{definition}
-
-\begin{definition}%[Contractor]
+and ${b}$ is its flag.   The counter is used internally to serialize transactions.
+%\end{definition}
+
+%\begin{definition}%[Contractor]
 A \emph{contractor} manages a smart contract. Contractors are
-  represented by a partial mapping $\CONTRACTORS : \TPUH \partialto
+represented by a partial map $\CONTRACTORS : \TPUH \partialto
 \TCODE \times \TIME  \times \TBAL \times  \TSTORAGE$. If $\CONTRACTORS (\PUH) = \langle
@@
 $\BAL$ is its current balance,
-  and $\STORAGE$ is its current storage.
-\end{definition}
-
-When an operation is injected in a node, it enters a \emph{pending
-  pool}. Later on, such a pending operation is either dismissed or
-promoted to an accepted operation.
+and $\STORAGE$ is its current storage. The hash $\PUH$ is
+self-verifying as it is calculated from the fixed components $\CODE$
+and $\TIME$. All time stamps will be different in our model.
+% \end{definition}
+
+When an operation is started on a node, it enters a \emph{pool} as a
+pending operation. A pending operation is either dismissed after some time or
+promoted to an included operation, which has become a permanent part
+of the blockchain.
 
@@
 %\end{definition}
-\begin{definition}
-  The pool of operations, $\PENDING$, is defined as a partial mapping from
-  operation hashes $\OPH$: 
+%\begin{definition}
+The pool is a partial map $  \PENDING= \TOPH \partialto
+\TOP\times \TTIME \times \TSTATUS$ where
 \begin{align*}
-    \PENDING &= \TOPH \partialto \TOP\times \TTIME \times \TSTATUS \\
   \TSTATUS&= \STATUSPENDING + \STATUSINCLUDED\ \TTIME + \STATUSTIMEOUT
 \end{align*}
-
+such that
 if $\PENDING(\OPH) = \langle  \OP, \TIME, \STATUS
@@
 \TIME$ and $\OPH = \GENERATEOPH (\OP, \TIME)$.
-\end{definition}
+%\end{definition}
 
 A \emph{pending operation} is represented by
-$\OPH \mapsto \langle  \OP, \TIME, \STATUSPENDING\rangle $,
-where $\OP$ is an operation, $\OPH$ is the operation hash,
-and $\TIME$ is the time when the operation was injected.
-Once it is accepted, it changes to an \emph{accepted operation}:
+$\OPH \mapsto \langle  \OP, \TIME, \STATUSPENDING\rangle $.
+Once the operation is accepted, it changes its status to included:
 $\OPH \mapsto \langle  \OP, \TIME, \STATUSINCLUDED\ \TIME'\rangle $, where
 $\TIME' \ge \TIME$ is  when the operation was included in the
-blockchain.  The operation can also be dropped at any time, which is
+blockchain.  The operation may also be dropped at any time, which is
 represented by
@@
 
-\begin{definition}%[Blockchain]
-  The \emph{state of a blockchain} is a tuple
+%\begin{definition}%[Blockchain]
+In summary, the \emph{state of a blockchain} is a tuple
 $\BLOCKCHAIN = [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]$ where
@@
 time. 
-\end{definition}
-\begin{definition}%[Blockchain system]
-A \emph{blockchain configuration} is a pair
-$ \NODE \| \BLOCKCHAIN$ where
-\fxnote[inline]{Should the model contain multiple nodes?}
+% \end{definition}
+
+We often use the dot notation to project a component from a tuple. For
+instance, we write $\BLOCKCHAIN.\MANAGERS$ to access the managers
+component.
+
+%\begin{definition}%[Blockchain system]
+A \emph{blockchain configuration} has the form
+$\BLOCKCHAIN[ \NODE_1, \dots, \NODE_n]$, for some $n>0$, where $\BLOCKCHAIN$ is a
+blockchain and the $\NODE_i$ are local nodes, for $1\le i\le n$.
+Moreover, the accounts on the local nodes are all different and each
+local account has a manager in $\BLOCKCHAIN$:
 \begin{enumerate}
-\item $\NODE = [\EXPRS, \ACCOUNTS]$ is the state of a node, and
-\item $\BLOCKCHAIN = [\PENDING, \MANAGERS, \CONTRACTORS,
-  \TIME]$ is the state of a blockchain  
-  such that
-  \begin{itemize}
-  \item
-    $\forall a \in \ACCOUNTS \implies a.\PUK \in \DOM( \MANAGERS)$;
-  \end{itemize}
+\item for all $1\le i< j\le n$, $\NODE_i.\ACCOUNTS \cap
+  \NODE_j.\ACCOUNTS = \emptyset$;
+\item for all $1\le i \le n$, 
+    $\forall a \in \NODE_i.\ACCOUNTS \implies a.\PUK \in \DOM( \BLOCKCHAIN.\MANAGERS)$.
 \end{enumerate}
-\end{definition}
+%\end{definition}
 \begin{definition}
@@
 Evaluation of expressions is standard call-by-value lambda calculus defined
-using evaluation contexts $\EC{}$.
-\begin{mathpar}
-  \inferrule{}{
-    \EC{(\lambda x.\EXPR)\VAL} \ExprTrans \EC{\EXPR[\VAL/x]}
-  }
-
-  \inferrule{}{
-    \EC{\FST (\VAL_1, \VAL_2)} \ExprTrans \EC{\VAL_1}
-  }
-
-  \inferrule{}{
-    \EC{\SND (\VAL_1, \VAL_2)} \ExprTrans \EC{\VAL_2}
-  }
-
-  \inferrule{
-    \TRY \notin \EC[F]{}
-  }{
-    \EC{\TRY\ {\EC[F]{\RAISE\ \VAL}}\ \EXCEPT\ \EXPR} \ExprTrans
-    \EC{\EXPR\ \VAL}
-  }
-
-  \inferrule{}{
-    \EC{\MATCH\ \NIL\ \WITH\ \NIL\to\EXPR \mid \dots}
-    \ExprTrans
-    \EC{\EXPR}
-  }
-
-  \inferrule{}{
-    \EC{\MATCH\ (\CONS\ \VAL_1\ \VAL_2)\ \WITH\ (\CONS\ x_1\ x_2)\to\EXPR \mid \dots}
-    \ExprTrans
-    \EC{\EXPR[\VAL_1,\VAL_2/x_1, x_2]}
-  }
-
-  \inferrule{}{
-    \EC{\MATCH\ \NONE\ \WITH\ \NONE\to\EXPR \mid \dots}
-    \ExprTrans
-    \EC{\EXPR}
-  }
-
-  \inferrule{}{
-    \EC{\MATCH\ (\SOME\ \VAL)\ \WITH\ (\SOME\ x)\to\EXPR \mid \dots}
-    \ExprTrans
-    \EC{\EXPR[\VAL/x]}
-  }
-
-  \inferrule{}{
-    \EC{\MATCH\ (\LEFT\ \VAL)\ \WITH\ (\LEFT\ x)\to\EXPR \mid \dots}
-    \ExprTrans
-    \EC{\EXPR[\VAL/x]}
-  }
-
-  \inferrule{}{
-    \EC{\MATCH\ (\RIGHT\ \VAL)\ \WITH\ (\RIGHT\ x)\to\EXPR \mid \dots}
-    \ExprTrans
-    \EC{\EXPR[\VAL/x]}
-  }
-\end{mathpar}
-
+using evaluation contexts
+$\EC{}$. Figure~\ref{fig:expression-reduction} shows some of the
+reduction rules. 
+\begin{figure}[tp]
+  \begin{mathpar}
+    \inferrule{}{ \EC{(\lambda x.\EXPR)\VAL} \ExprTrans
+      \EC{\EXPR[\VAL/x]} }
+
+    % \inferrule{}{
+    % \EC{\FST (\VAL_1, \VAL_2)} \ExprTrans \EC{\VAL_1}
+    % }
+  %   
+    %   \inferrule{}{
+    %   \EC{\SND (\VAL_1, \VAL_2)} \ExprTrans \EC{\VAL_2}
+    % }
+  %   
+    \inferrule{ \TRY \notin \EC[F]{} }{ \EC{\TRY\ {\EC[F]{\RAISE\
+            \VAL}}\ \EXCEPT\ \EXPR} \ExprTrans \EC{\EXPR\ \VAL} }
+
+    \inferrule{}{ \EC{\MATCH\ (\VAL_1, \VAL_2) \WITH\ (x_1,
+        x_2)\to\EXPR \mid \dots} \ExprTrans \EC{\EXPR[\VAL_1,
+        \VAL_2/x_1, x_2]} }
+
+    \inferrule{}{ \EC{\MATCH\ \NIL\ \WITH\ \NIL\to\EXPR \mid \dots}
+      \ExprTrans \EC{\EXPR} }
+
+    \inferrule{}{ \EC{\MATCH\ (\CONS\ \VAL_1\ \VAL_2)\ \WITH\ (\CONS\
+        x_1\ x_2)\to\EXPR \mid \dots} \ExprTrans
+      \EC{\EXPR[\VAL_1,\VAL_2/x_1, x_2]} }
+
+    \inferrule{}{ \EC{\MATCH\ \NONE\ \WITH\ \NONE\to\EXPR \mid \dots}
+      \ExprTrans \EC{\EXPR} }
+
+    \inferrule{}{ \EC{\MATCH\ (\SOME\ \VAL)\ \WITH\ (\SOME\ x)\to\EXPR
+        \mid \dots} \ExprTrans \EC{\EXPR[\VAL/x]} }
+
+    \inferrule{}{ \EC{\MATCH\ (\LEFT\ \VAL)\ \WITH\ (\LEFT\ x)\to\EXPR
+        \mid \dots} \ExprTrans \EC{\EXPR[\VAL/x]} }
+
+    \inferrule{}{ \EC{\MATCH\ (\RIGHT\ \VAL)\ \WITH\ (\RIGHT\
+        x)\to\EXPR \mid \dots} \ExprTrans \EC{\EXPR[\VAL/x]} }
+
+    \inferrule{\TYPE \SubType \TYPEU}{ \EC{\CAST\VAL\TYPE\TYPEU} \ExprTrans \EC{\VAL}}
+  \end{mathpar}
+  \caption{Select expression reduction rules}
+  \label{fig:expression-reduction}
+\end{figure}
 The internal transitions of a node are just evaluation of expressions.

### 2021-02-18 papers/execution-model/model.tex
Add files via upload
section 3

@@
 \label{sec:execution-model}
+The context of our work is the Tezos blockchain \cite{tezos-whitepaper}\cite{tezos-intropaper}. Tezos is a self-amending blockchain that improves on several aspects compared to more established 
+blockchains.
+Tezos introduces an original consensus algorithm called Liquid Proof of Stake that allows consensus not only on the state of its ledger, like Bitcoin \cite{bitcoin-whitepaper} or Ethereum \cite{eth-whitepaper}, but also on how the economic protocol and the nodes should adapt and upgrade, and serves as a decentralized smart contract platform that facilitates formal verification and focuses on formal methods to improve security.
+
+In Tezos, there are two types of accounts: implicit accounts and smart contracts, and they are stateful.
+An implicit account is a non-programmable account, whose tokens are spendable and associated with a pair of private/public keys.
+A smart contract is a programmable account that is created with an origination operation and has no corresponding secret key.
+The address of a smart contract is a unique public hash that depends on the creation operation.
+All existing accounts are stored in a context component on the blockchain.
+An implicit account is managed with its public key, balance, and counter, whose job is to prevent replay attacks.
+A smart contract account is stored with its script, storage, and balance.
+Tezos provides the Michelson language for writing a smart contract.
+Michelson is a stack-based language with strict static type checking.
+A contract is a function that maps a pair of parameters and a storage that have fixed and monomorphic types to a pair of a list of internal operations and an updated storage.
+The script of a smart contract must be type-checked before it is introduced into the system.
+
+An implicit account can perform three kinds of transactions: (1) transfer tokens to another implicit account, (2) transfer (invoke) a smart contract, or (3) originate a smart contract to create a new smart contract on the blockchain.
+An origination transaction specifies the script of the contract and the initial content of the storage of the contract.
+A smart contract invocation provides input data.
+Each transaction usually includes a fee that is for either by paying to a baker or by destroying (burning).
+A transaction can only be sent if it has been signed with the sender contract's private key and it is injected into the blockchain network via a node that runs Gossip network and updates the context.
+The node first validates the transaction before submitting it to the network.
+In general, a transaction can fail for a number of reasons,  including an incorrect recipient address, insufficient balance, an incorrect counter, and an incorrect type of input parameter(or script).
+A transaction is valid only if the counter of the sender contract is equal to the counter that is used in the transaction.
+A smart contract invocation may fail for reasons determined by the contract's script.
+An invalid transaction is rejected by the node.
+
+Once the transaction is valid, it is injected into the mempool, which contains all pending transactions before they can be included in a block.
+These transactions are then broadcasted to the network.
+On the other hand, a pending transaction may get lost in the mempool.
+Namely, it may be dropped.
+There are several
+causes for dropping, primarily timeout or overflow of the mempool, which is limited in size in the implementation.
+A transaction times out when 60 blocks have passed and it no longer be included anymore in a block.
+When a transaction is included in a blockchain, the amount of tokens transferred is added to the balance of destination contract and when a smart contract call is made, the script of the destination contract is executed.
+%This script uses the parameters passed to it, reads the contract's storage and then executes its intructions.
+Once a transaction is applied, the counter increments by one, preventing the transaction from being reused.
 
@@
 \end{enumerate}
+
+\bibliographystyle{splncs04}
+\bibliography{bio}
 \end{document}

### 2021-02-18 papers/execution-model/model.tex
Add files via upload
section-3

--- 2021-02-18 papers/execution-model/model.tex
@@
 \label{sec:execution-model}
+The context of our work is the Tezos blockchain \cite{tezos-whitepaper, tezos-intropaper}. Tezos is a self-amending blockchain that improves several aspects compared to established 
+blockchains.
+Tezos introduces an original consensus algorithm called Liquid Proof of Stake that allows consensus not only on the state of its ledger, like Bitcoin \cite{bitcoin-whitepaper} or Ethereum \cite{eth-whitepaper}, but also on how the economic protocol and the nodes should  upgrade, and serves as a decentralized smart contract platform that focuses on formal methods to improve security.
+
+In Tezos, there are two types of accounts: implicit accounts and smart contracts, and they are stateful.
+An implicit account is a non-programmable account and is associated with a pair of private/public keys.
+A smart contract is a programmable account created by an origination operation and has no corresponding secret key.
+The address of a smart contract is a unique public hash that depends on the creation operation.
+All existing accounts are stored in a context component on the blockchain.
+An implicit account is managed with its public key, balance, and counter, whose job is to prevent replay attacks.
+A smart contract account is stored with its script, storage, and balance.
+Tezos provides the Michelson language for writing a smart contract.
+Michelson is a stack-based language with strict static type checking.
+A contract is a function that maps a pair of a parameter and a storage, which have fixed and monomorphic types to a pair of a list of internal operations and an updated storage.
+The script of a smart contract must be type-checked before it is introduced into the system.
+
+An implicit account can perform three kinds of transactions: (1) transfer tokens to another implicit account, (2) transfer (invoke) a smart contract, or (3) originate a new smart contract.E ach transaction includes the address of the sender contract, the address of the destination contract, the amount of tokens transferred, and a fee to be paid either by payment to a baker or by destruction (burning).
+In addition, a smart contract invocation must provide input data and and an origination transaction specifies the script of the contract and the initial content of the contract storage.
+A transaction can only be sent if it has been signed with the sender contract's private key.
+It is then injected into the blockchain network via a node that runs the gossip network and updates the context.
+The node first validates the transaction before submitting it to the network.
+In general, a transaction can fail for a number of reasons, including incorrect destination address, insufficient balances, incorrect counters, and incorrect type of input parameters (or scripts).
+A transaction is valid only if the counter of the sender contract is the same as the counter  used in the transaction.
+The invocation of a smart contract may fail for reasons determined by the contract's script.
+An invalid transaction is rejected by the node.
+
+Once the transaction is valid, it is injected into the mempool, which contains all pending transactions before they can be included in a block.
+On the other hand, a pending transaction may get lost in the mempool.
+That is, it may be dropped.
+There are several
+causes for dropping, primarily timeout or overflow of the mempool, which is limited in size in the implementation.
+A transaction is timed out when 60 blocks have passed and it can no longer be included in a block.
+When a transaction is included in a blockchain, the amount of tokens transferred is added to the balance of destination contract and when a smart contract call is made, the script of the destination contract is executed.
+Once a transaction is applied, the counter increments by one, preventing the transaction from being reused.
 

### 2021-02-19 papers/execution-model/model.tex
major reorganization

--- 2021-02-18 papers/execution-model/model.tex
@@
 blockchain and the $\NODE_i$ are local nodes, for $1\le i\le n$.
-Moreover, the accounts on the local nodes are all different and each
+In a \emph{well-formed configuration}, the accounts on the local nodes are all different and each
 local account has a manager in $\BLOCKCHAIN$:
@@
 %\end{definition}
-\begin{definition}
-  Preserved by a step on a well-formed configuration $ [\EXPRS, \ACCOUNTS] \|
-  [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]$:
-  \todo[inline]{Is this preserved?}
-  \begin{itemize}
-  \item for all $\OPH$ in $\EXPRS$, $\OPH \in \DOM (\PENDING)$,
-  \item for all $\PUK$ in $\EXPRS$, $\PUK \in \DOM (\MANAGERS)$,
-  \item for all $\PUH$ in $\EXPRS$, $\PUH \in \DOM (\CONTRACTORS)$.
-  \end{itemize}
-\end{definition}
-
-\clearpage{}
-\subsection{Properties of blockchain state transitions}
-
-If $[\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \BlockTrans{}
-[\PENDING', \MANAGERS', \CONTRACTORS', \TIME']$, then
-\begin{itemize}
-\item $\TIME \le \TIME'$
-\item $\DOM (\PENDING) \subseteq \DOM(\PENDING')$
-\item for all $\OPH \in \DOM(P)$, if 
-  $\PENDING (\OPH) = \Angle{\OP,  \hat\TIME, \STATUS}$, then either
-  \begin{itemize}
-  \item     $\PENDING'    (\OPH) = \PENDING (\OPH)$; or
-  \item $\STATUS  = \STATUSPENDING$ and $\PENDING' (\OPH) =
-    \Angle{\OP, \hat\TIME, \STATUSTIMEOUT}$; or
-  \item  $\STATUS  = \STATUSPENDING$, $\TIME - \hat\TIME
-    \le 60 $, and
-    $\PENDING' (\OPH) =       \Angle{\OP, \hat\TIME, \STATUSINCLUDED\
-      \TIME}$.
-  \end{itemize}
- \item for all $\OPH \in \DOM(P)$ and $\PENDING (\OPH) = \Angle{\OP,  \hat\TIME, \STATUSPENDING}$, 
-    \begin{itemize}
-    	\item  if $\MANAGERS(\OP.\PUK) =  \Angle{\BAL, \COU}$ then  
-  $\COU.b = \TRUE$.
-    \end{itemize}
- \item $ \DOM (\MANAGERS) \subseteq \DOM (\MANAGERS')$
- \item for all $\PUK \in \DOM (\MANAGERS)$\\
-   if $\MANAGERS (\PUK) =
-   \Angle{\BAL, \COU}$, 
-   then $\MANAGERS' (\PUK) =
-   \Angle{\BAL', \COU'}$ and
-   \begin{itemize}
-   \item if $\COU.b=\TRUE$ and $\COU'.b=\FALSE$, then $\COU.n' \in \{
-     \COU.n,  \COU.n+1\}$,
-   \item otherwise $\COU.n = \COU'.n$
-   \item If $\COU.n = \COU'.n$, then $\BAL = \BAL'$.
-   % \item if $\COU.b= \FALSE$, then $n' = n$
-   % \item if $\COU.b= \TRUE$ and $b'=\TRUE$, then $n' =n$
-   \end{itemize}
-
- \item $ \DOM (\CONTRACTORS) \subseteq \DOM (\CONTRACTORS')$
-   \begin{itemize}
-   \item for all $\PUH \in \DOM (\CONTRACTORS)$,
-     $\CONTRACTORS (\PUH).\CODE = \CONTRACTORS' (\PUH).\CODE$
-   \end{itemize}
- \item invariant for contractors:
-   for all $\PUH \in \DOM (\CONTRACTORS)$,
-   $\CONTRACTORS (\PUH) = \Angle{ \CODE, \TIME, \BAL, \STORAGE}$
-   implies that $\PUH = \GENERATEHASH (\CODE, \TIME)$.
-\end{itemize}
-
-\subsection{Typing related properties}
-
-To describe contracts we associate each public hash to a pair of
-types, the parameter type and the storage type.
-\begin{align*}
-  \Delta & ::= \EmptyEnv \mid \PUH: \TPAIR\ \TYPE\ \TYPE, \Delta
-\end{align*}
-
-Define $ \Delta \vdash \CONTRACTORS$ by
-\begin{itemize}
-\item $\DOM (\Delta) = \DOM (\CONTRACTORS)$
-\item $\JTypeCode{\CONTRACTORS (\PUH).\CODE} {\Delta (\PUH)}$
-\item $\JTypeValue{\CONTRACTORS (\PUH).\STORAGE}{ \TYPE_s}$ where
-  $\Delta (\PUH) = \TPAIR\ \TYPE_p\ \TYPE_s$. 
-\end{itemize}
-
-Preservation
-
-If $[\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \BlockTrans{}
-[\PENDING', \MANAGERS', \CONTRACTORS', \TIME']$
-and $\Delta \vdash \CONTRACTORS$, \\
-then
-there is some $\Delta' \supseteq \Delta$ such that $\Delta' \vdash
-\CONTRACTORS'$.
-
-Consider a blockchain state  $[\PENDING, \MANAGERS, \CONTRACTORS,
-\TIME]$ where $\Delta \vdash \CONTRACTORS$.
-
-For all $\OPH\in\DOM (\PENDING)$,
-if  $\PENDING (\OPH) =  \Angle{\OP, \hat\TIME, \STATUS}$
-\begin{itemize}
-\item if $\OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ$, then
-\begin{itemize}
-  \item
-  $\PUK, \PUK' \in \DOM (\MANAGERS)$
-\end{itemize}
-\item if $\OP = \TRANSFER[\PARAMETER]\NTEZ\PUK\PUH\MTEZ$, then
-  \begin{itemize}
-  \item $\PUK \in \DOM (\MANAGERS)$ and $\PUH\in\DOM (\CONTRACTORS)$
-  \item $\PARAMETER : \TYPE_p$ where $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$. 
-  \end{itemize}
-
-\item if $\OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ$ and $\STATUS =
-  \STATUSINCLUDED\ \TIME'$, then
-   \begin{itemize}
-   \item $\PUK \in \DOM (\MANAGERS)$
-  \item $\CODE : \TPAIR\ \TYPE_p\ \TYPE_s$
-  \item $\STRING : \TYPE_s$
-  \item if $\STATUS =
-  \STATUSINCLUDED\ \TIME'$, then $\PUH =\GENERATEHASH (\CODE, \hat\TIME) \in \DOM (\CONTRACTORS)$ and $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$ (or $\CONTRACTORS(\PUH).\CODE = \CODE$).
-
-  \end{itemize}
-
- \item if $st = \STATUSPENDING$ and $\MANAGERS(\PUK) = \Angle{\BAL,
-     \COU}$, then $\BAL \ge \NTEZ +  \MTEZ$ 
-\end{itemize}
-
-\section{Transitions}
+
+\section{Operational Semantics}
 \label{sec:transitions}
 
-We distinguish several kinds of transitions depending on their scope:
+The operational semantics is defined by several kinds of transitions depending on their scope:
 \begin{enumerate}
-\item $\ExprTrans$ single-step evaluation of expressions in the node state,
+\item $\ExprTrans$ single-step evaluation of an expression in a local node,
 \item $\NodeTrans$ internal transitions of a node,
@@
 
-Evaluation of expressions is standard call-by-value lambda calculus defined
+Evaluation of expressions is standard for call-by-value lambda calculus defined
 using evaluation contexts
@@
 
-    \inferrule{}{ \EC{\MATCH\ (\VAL_1, \VAL_2) \WITH\ (x_1,
-        x_2)\to\EXPR \mid \dots} \ExprTrans \EC{\EXPR[\VAL_1,
-        \VAL_2/x_1, x_2]} }
-
-    \inferrule{}{ \EC{\MATCH\ \NIL\ \WITH\ \NIL\to\EXPR \mid \dots}
-      \ExprTrans \EC{\EXPR} }
-
-    \inferrule{}{ \EC{\MATCH\ (\CONS\ \VAL_1\ \VAL_2)\ \WITH\ (\CONS\
-        x_1\ x_2)\to\EXPR \mid \dots} \ExprTrans
-      \EC{\EXPR[\VAL_1,\VAL_2/x_1, x_2]} }
-
-    \inferrule{}{ \EC{\MATCH\ \NONE\ \WITH\ \NONE\to\EXPR \mid \dots}
-      \ExprTrans \EC{\EXPR} }
-
-    \inferrule{}{ \EC{\MATCH\ (\SOME\ \VAL)\ \WITH\ (\SOME\ x)\to\EXPR
-        \mid \dots} \ExprTrans \EC{\EXPR[\VAL/x]} }
-
-    \inferrule{}{ \EC{\MATCH\ (\LEFT\ \VAL)\ \WITH\ (\LEFT\ x)\to\EXPR
-        \mid \dots} \ExprTrans \EC{\EXPR[\VAL/x]} }
-
-    \inferrule{}{ \EC{\MATCH\ (\RIGHT\ \VAL)\ \WITH\ (\RIGHT\
-        x)\to\EXPR \mid \dots} \ExprTrans \EC{\EXPR[\VAL/x]} }
-
     \inferrule{\TYPE \SubType \TYPEU}{ \EC{\CAST\VAL\TYPE\TYPEU} \ExprTrans \EC{\VAL}}
-  \end{mathpar}
-  \caption{Select expression reduction rules}
+    %
+    % \inferrule{}{ \EC{\MATCH\ (\VAL_1, \VAL_2) \WITH\ (x_1,
+    %     x_2)\to\EXPR \mid \dots} \ExprTrans \EC{\EXPR[\VAL_1,
+    %     \VAL_2/x_1, x_2]} }
+    % \inferrule{}{ \EC{\MATCH\ \NIL\ \WITH\ \NIL\to\EXPR \mid \dots}
+    %   \ExprTrans \EC{\EXPR} }
+    % \inferrule{}{ \EC{\MATCH\ (\CONS\ \VAL_1\ \VAL_2)\ \WITH\ (\CONS\
+    %     x_1\ x_2)\to\EXPR \mid \dots} \ExprTrans
+    %   \EC{\EXPR[\VAL_1,\VAL_2/x_1, x_2]} }
+    % \inferrule{}{ \EC{\MATCH\ \NONE\ \WITH\ \NONE\to\EXPR \mid \dots}
+    %   \ExprTrans \EC{\EXPR} }
+    % \inferrule{}{ \EC{\MATCH\ (\SOME\ \VAL)\ \WITH\ (\SOME\ x)\to\EXPR
+    %     \mid \dots} \ExprTrans \EC{\EXPR[\VAL/x]} }
+    % \inferrule{}{ \EC{\MATCH\ (\LEFT\ \VAL)\ \WITH\ (\LEFT\ x)\to\EXPR
+    %     \mid \dots} \ExprTrans \EC{\EXPR[\VAL/x]} }
+    % \inferrule{}{ \EC{\MATCH\ (\RIGHT\ \VAL)\ \WITH\ (\RIGHT\
+    %     x)\to\EXPR \mid \dots} \ExprTrans \EC{\EXPR[\VAL/x]} }
+  \end{mathpar}
+  \caption{Select expression reduction rules (pattern matching omitted)}
   \label{fig:expression-reduction}
@@
 \end{mathpar}
-
+The remaining transitions affect a local node in the context of the
+blockchain. To this end, any local node may be selected.
+\begin{mathpar}
+  \inferrule[Config-System]{
+    \NODE\|\BLOCKCHAIN \SystemTrans \NODE'\|\BLOCKCHAIN'
+}{
+    \BLOCKCHAIN[\NODE :: \overline{\NODE}] \SystemTrans
+    \BLOCKCHAIN'[\NODE' :: \overline{\NODE}]
+  }
+
+  \inferrule[Config-Node]
+  {\NODE \NodeTrans \NODE'}
+  { {\BLOCKCHAIN[\NODE :: \overline\NODE]}
+    \SystemTrans
+    {\BLOCKCHAIN[\NODE' :: \overline\NODE]}}
+
+  \inferrule[Config-Block]
+  {\BLOCKCHAIN \BlockTrans \BLOCKCHAIN'}
+  { \BLOCKCHAIN[{\overline\NODE}]
+    \SystemTrans
+    \BLOCKCHAIN'[{\overline\NODE}]}
+\end{mathpar}
+
+\begin{figure}[tp]
 \begin{mathpar}
@@
  }
-\end{mathpar}
-
-\begin{mathpar}
+
+  \inferrule[Node-Reject]{
+    \NEG\ \CHECKBAL (\BLOCKCHAIN.\MANAGERS, \OP.\PUK, \OP.\NTEZ, \OP.\MTEZ) \\
+    }{
+    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+      } \SystemTrans
+    { [\EC{\RAISE\ \ERRBAL} :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+    }
+  }
+
   \inferrule[Block-Accept]{
@@
   }
-\end{mathpar}
-
-The timeout transition applies to all operations.
-\begin{mathpar}
+
     \inferrule[Block-Timeout]{
@@
 \end{mathpar}
+
+  \caption{Lifecycle transitions of a transaction}
+  \label{fig:lifecycle-transaction}
+\end{figure}
+Figure~\ref{fig:lifecycle-transaction} shows the transitions to start
+and finalize a transfer transaction.
+\TirName{Node-Inject} affects a local node and the blockchain. It
+nondeterminstically selects a program that wants to do a transfer
+operation. It
+checks whether the sender of the transfer is a valid local account, whether
+the balance is sufficient to pay the fee and the transferred amount,
+whether there is an active transition for this sender (chkCount),
+whether the receiver's address is valid, and whether the fee is
+sufficient. If these conditions are fulfilled, the transition forges
+an operation hash and returns it to the local node. 
+The pending operation enters the pool and the sender's counter is set
+to indicate an ongoing transition.
+
+We give just one example \TirName{Node-Reject} of the numerous
+transitions that cover the cases where one of the 
+premises of \TirName{Node-Inject} is not fulfilled. Each of them
+raises an exception that describes which condition was violated.
+
+Acceptance or rejection of a pending operation happens on the
+blockchain independent of any local node. In our model, these
+transitions are nondeterministic so that acceptance can happen any
+time in the next 60 cycles \TirName{Block-Accept}. Afterwards, a
+pending operation can only time out \TirName{Block-Timeout}.
+If the transaction is accepted, then the sender's counter is reset,
+the balances of sender and receiver are adjusted (updSucc), and the
+time stamp increases.
+
+Whereas \TirName{Node-Inject} and \TirName{Block-Accept} are
+particular to the transfer operation, the timeout transition applies
+to all operations. It just changes the state of the operation and
+resets the sender's counter, thus rolling back the transaction.
 
@@
 
-\subsection{Special reductions}
+\subsection{Cast Reductions}
 \label{sec:special-reductions}
 
-\begin{mathpar}
-  \inferrule[Contract?]{
+\begin{figure}[tp]
+\begin{mathpar}
+  \inferrule[Contract-Yes]{
     \JTypeCode\CODE{\TPAIR\ \TYPE\ \TYPEU} \\
@@
     }{
-    { [\EC{\CONTRACT\ \TYPE\ \PUH}  :: \EXPRS, \ACCOUNTS] \|
+    { [\EC{\CAST\PUH\TPUH{\TCONTRACT\ \TYPE}}  :: \EXPRS, \ACCOUNTS] \|
       \BLOCKCHAIN
@@
     \SystemTrans
-    { [\EC{\SOME\ \PUH} :: \EXPRS, \ACCOUNTS] \|
-      \BLOCKCHAIN
-   }
-  }
-
-  \inferrule[Contract-Implicit?]{
-    \PUK \in \DOM(\BLOCKCHAIN.\MANAGERS)
+    { [\EC{\PUH} :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+   }
+  }
+
+  % \inferrule[Contract-Implicit?]{
+  %   \PUK \in \DOM(\BLOCKCHAIN.\MANAGERS)
+  %   %
+  %   }{
+  %   { [\EC{\CONTRACT\ \TUNIT\ \PUK}  :: \EXPRS, \ACCOUNTS] \|
+  %     \BLOCKCHAIN
+  %   }
+  %   \SystemTrans
+  %   { [\EC{\SOME\ \PUK} :: \EXPRS, \ACCOUNTS] \|
+  %     \BLOCKCHAIN
+  %  }
+  % }
   %
-    }{
-    { [\EC{\CONTRACT\ \TUNIT\ \PUK}  :: \EXPRS, \ACCOUNTS] \|
-      \BLOCKCHAIN
-    }
-    \SystemTrans
-    { [\EC{\SOME\ \PUK} :: \EXPRS, \ACCOUNTS] \|
-      \BLOCKCHAIN
-   }
-  }
-
-  \inferrule[Contract-No?]{
-    \ADDR \in \DOM (\BLOCKCHAIN.\MANAGERS) \Rightarrow \TYPE\ne\TUNIT \\
-    \BLOCKCHAIN.\CONTRACTORS (\ADDR) = \Angle{\CODE, \tilde\TIME,
+  \inferrule[Contract-No]{
+    % \ADDR \in \DOM (\BLOCKCHAIN.\MANAGERS) \Rightarrow \TYPE\ne\TUNIT \\
+    \BLOCKCHAIN.\CONTRACTORS (\PUH) = \Angle{\CODE, \tilde\TIME,
       \NTEZ', \STRING'} \Rightarrow {}
@@
     }{
-    { [\EC{\CONTRACT\ \TYPE\ \ADDR}  :: \EXPRS, \ACCOUNTS] \|
+    { [\EC{\CAST\PUH\TPUH{\TCONTRACT\ \TYPE}}  :: \EXPRS, \ACCOUNTS] \|
       \BLOCKCHAIN
@@
     \SystemTrans
-    { [\EC{\NONE} :: \EXPRS, \ACCOUNTS] \|
-      \BLOCKCHAIN
-   }
-  }
-\end{mathpar}
-
-\subsection{Transitions on Nodes}
-\label{sec:transitions-nodes}
-
-Each node has (nondeterministic) rules to propose an operation.
-When an operation $\OP$ appears, we check that the account is local by
-looking up its public key $\OP.\PUK$ in the local accounts $\ACCOUNTS$ and
-consider it signed with the corresponding private key $\PAK$.
-
-\begin{mathpar}
-  \inferrule[Node-System]
-  {\NODE \NodeTrans \NODE'}
-  { {\NODE :: \overline\NODE \| \BLOCKCHAIN}
+    { [\EC{\RAISE\ \ERRPRG} :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+   }
+  }
+\end{mathpar}
+  \caption{Cast reductions (excerpt)}
+  \label{fig:cast-reductions}
+\end{figure}
+\begin{figure}[tp]
+  \begin{mathpar}
+    \inferrule[Block-Originate]{
+      \Angle{\PAK,\PUK} \in \ACCOUNTS \\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
+      \CHECKCOU (\MANAGERS, \PUK) \\
+      \CHECKPRG (\CODE) \\
+      \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ)  \\
+      \CHECKINIT (\CODE, \STRING) \\
+      % \OPH = \GENERATEOPH(\PUK, \CODE, \STRING, \NTEZ, \MTEZ, \TIME)
+      % \\
+      \OPH = \GENERATEOPH(\OP, \TIME) \\
+      \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ }{ [\EC\OP :: \EXPRS,
+      \ACCOUNTS
+      ] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \to \\
+      [\EC{\OPH} :: \EXPRS, \ACCOUNTS] \| [\OPH \mapsto \Angle{\OP,
+        \TIME, \STATUSPENDING} ::\PENDING,
+      \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME] }
+
+  \inferrule[Block-Accept]{
+    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
+    \PUH = \GENERATEHASH(\CODE, \TIME) \\
+    \TIME-\hat\TIME  \le 60
+  }{
+    [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING} :: \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
+    \BlockTrans \\
+     [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING, \UPDATESUCC
+      (\MANAGERS, \PUK, \NTEZ, \MTEZ),\\ \PUH \mapsto  \Angle{\CODE, \TIME, \NTEZ, \STRING} :: \CONTRACTORS, \TIME+1]
+  }
+
+    \inferrule[Block-Accept-Query]{
+    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
+    \PENDING (\OPH) =  \Angle{\OP,
+      \hat\TIME, \STATUSINCLUDING\ \tilde\TIME} \\
+    \PUH = \GENERATEHASH (\CODE, \tilde\TIME)
+    % \CONTRACTORS (\PUH) =  \Angle{\CODE, \tilde\TIME, \NTEZ', \STRING'}
+  }{
+      [\EC{\GETCONTRACT\ \OPH}  :: \EXPRS, \ACCOUNTS] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
     \SystemTrans 
-    {\NODE' :: \overline\NODE \| \BLOCKCHAIN}}
-
-  \inferrule[Block-System]
-  {\BLOCKCHAIN \BlockTrans \BLOCKCHAIN'}
-  { {\overline\NODE \| \BLOCKCHAIN}
-    \SystemTrans
-    {\overline\NODE\| \BLOCKCHAIN'}}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[rejected of counter]{
-    \NEG\ \CHECKCOU (\BLOCKCHAIN.\MANAGERS, \OP.\PUK) \\
-    }{
-    { [\EC\OP  :: \EXPRS, \ACCOUNTS] \|
-      \BLOCKCHAIN
-    }
-    \SystemTrans
-    { [\EC{\RAISE\ \ERRCOUNT} :: \EXPRS, \ACCOUNTS] \|
-      \BLOCKCHAIN
-   }
-  }
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[rejected of balance]{
-    \NEG\ \CHECKBAL (\BLOCKCHAIN.\MANAGERS, \OP.\PUK, \OP.\NTEZ, \OP.\MTEZ) \\
-    }{
-    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
-      \BLOCKCHAIN
-      } \SystemTrans
-    { [\EC{\RAISE\ \ERRBAL} :: \EXPRS, \ACCOUNTS] \|
-      \BLOCKCHAIN
-    }
-  }
-\end{mathpar}
+     [\EC{ \PUH}  :: \EXPRS, \ACCOUNTS] \|  [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
+  }
+\end{mathpar}
+  \caption{Smart contract origination}
+  \label{fig:contract-origination}
+\end{figure}
+\begin{figure}[tp]
+  \begin{mathpar}
+    \inferrule[Query-Balance-Implicit]{
+      % \BLOCKCHAIN =
+      % [\PENDING, \PUK \mapsto \Angle{\BAL, \COU} :: \MANAGERS,
+      % \CONTRACTORS, \TIME]
+      \BLOCKCHAIN.\MANAGERS (\PUK) = \Angle{\BAL,\COU}
+    }{[\EC{\GETBALANCE\PUK} :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN
+      \SystemTrans\ [\EC{\BAL} ::\EXPRS, \ACCOUNTS] \| \BLOCKCHAIN}
+
+    \inferrule[Query-Balance-Fail]{ \PUK \notin \DOM
+      (\BLOCKCHAIN.\MANAGERS) \ }{[\EC{\GETBALANCE\PUK} :: \EXPRS,
+      \ACCOUNTS] \| \BLOCKCHAIN \SystemTrans {[\EC{\RAISE\ \ERRPUK}
+        ::\EXPRS, \ACCOUNTS] \| \BLOCKCHAIN}}
+  \end{mathpar}
+  \caption{Example queries}
+  \label{fig:example-queries}
+\end{figure}
+
+Figure~\ref{fig:cast-reductions} contains the most interesting
+example of cast reductions, from a public hash to a typed
+contract. These reductions force the local node to obtain information
+from the blockchain. The cast succeeds \TirName{Contract-Yes} on \PUH, if there is a
+contractor for \PUH\ such that the stored code has the parameter type
+expected by the cast. The cast fails \TirName{Contract-No}, if \PUH\
+is invalid or if the types do not match.
+
+\subsection{Smart Contracts}
+\label{sec:smart-contracts}
+
+The invocation of smart contracts is similar to a transfer, so we
+elide the details. Figure~\ref{fig:contract-origination} contains the
+transition \TirName{Block-Originate} to originate a smart contract. The basic scheme is similar
+to the transfer. The preconditions for the operation are checked, but
+there are extra preconditions for origination:  the program must be
+well-formed and typed, the initial storage value must match its
+type. The operation ends up in the pool in pending status.
+
+Acceptance of origination is slightly different as for transfers as
+shown in \TirName{Block-Accept}. We calculate the public hash \PUH\ of the
+contract from the code and the current time stamp and create a new
+contractor at that address.
+
+We obtain the handle of the contract through a query, once the
+contract is accepted on the blockchain in
+\TirName{Block-Accept-Query}. The query's argument is the operation
+hash, which is used to obtain the code and the time stamp of its
+acceptance. From this information, we can re-calculate the public
+hash.
+
+\subsection{Queries}
+\label{sec:queries}
+
+We conclude with two example transitions for a simple query in
+Figure~\ref{fig:example-queries}. To obtain the balance of an implicit
+account \PUK, we obtain the account info from the manager and extract
+the balance (\TirName{Query-Balance-Implicit}). If the account is
+unknown, then we raise an exception
+(\TirName{Query-Balance-Fail}). Other queries are implemented analogously.
+
+\section{Properties}
+\label{sec:properties}
+
+\subsection{Properties of blockchain state transitions}
+
+Running a program that starts with valid references to accounts,
+operations, and contracts does not get corrupted by a transition.
+\begin{proposition}
+  The following property is preserved by a step on a well-formed
+  configuration $ [\EXPRS, \ACCOUNTS] \| \BLOCKCHAIN$:
+  \begin{itemize}
+  \item for all $\OPH$ in $\EXPRS$, $\OPH \in \DOM (\BLOCKCHAIN.\PENDING)$,
+  \item for all $\PUK$ in $\EXPRS$, $\PUK \in \DOM (\BLOCKCHAIN.\MANAGERS)$,
+  \item for all $\PUH$ in $\EXPRS$, $\PUH \in \DOM (\BLOCKCHAIN.\CONTRACTORS)$.
+  \end{itemize}
+\end{proposition}
+
+\begin{proposition}
+If $[\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \BlockTrans{}
+[\PENDING', \MANAGERS', \CONTRACTORS', \TIME']$, then
+\begin{enumerate}
+\item $\TIME \le \TIME'$
+\item\label{item:1} $\DOM (\PENDING) \subseteq \DOM(\PENDING')$
+\item invariant for the pool: if  $\PENDING (\OPH) = \Angle{\OP,
+    \hat\TIME, \STATUS}$, then $\OPH = \GENERATEOPH (\OP,
+  \hat\TIME)$. 
+\item for all $\OPH \in \DOM(P)$, if 
+  $\PENDING (\OPH) = \Angle{\OP,  \hat\TIME, \STATUS}$, then either
+  \begin{itemize}
+  \item     $\PENDING'    (\OPH) = \PENDING (\OPH)$; or
+  \item $\STATUS  = \STATUSPENDING$ and $\PENDING' (\OPH) =
+    \Angle{\OP, \hat\TIME, \STATUSTIMEOUT}$; or
+  \item  $\STATUS  = \STATUSPENDING$, $\TIME - \hat\TIME
+    \le 60 $, and
+    $\PENDING' (\OPH) =       \Angle{\OP, \hat\TIME, \STATUSINCLUDED\
+      \TIME}$.
+  \end{itemize}
+ \item\label{item:2} for all $\OPH \in \DOM(P)$ and $\PENDING (\OPH) = \Angle{\OP,  \hat\TIME, \STATUSPENDING}$, 
+    \begin{itemize}
+    	\item  if $\MANAGERS(\OP.\PUK) =  \Angle{\BAL, \COU}$ then  
+  $\COU.b = \TRUE$.
+    \end{itemize}
+ \item\label{item:3} $ \DOM (\MANAGERS) \subseteq \DOM (\MANAGERS')$
+ \item\label{item:4} for all $\PUK \in \DOM (\MANAGERS)$\\
+   if $\MANAGERS (\PUK) =
+   \Angle{\BAL, \COU}$, 
+   then $\MANAGERS' (\PUK) =
+   \Angle{\BAL', \COU'}$ and
+   \begin{itemize}
+   \item if $\COU.b=\TRUE$ and $\COU'.b=\FALSE$, then $\COU.n' \in \{
+     \COU.n,  \COU.n+1\}$,
+   \item otherwise $\COU.n = \COU'.n$
+   \item If $\COU.n = \COU'.n$, then $\BAL = \BAL'$.
+   % \item if $\COU.b= \FALSE$, then $n' = n$
+   % \item if $\COU.b= \TRUE$ and $b'=\TRUE$, then $n' =n$
+   \end{itemize}
+
+ \item\label{item:5} $ \DOM (\CONTRACTORS) \subseteq \DOM (\CONTRACTORS')$
+   \begin{itemize}
+   \item for all $\PUH \in \DOM (\CONTRACTORS)$,
+     $\CONTRACTORS (\PUH).\CODE = \CONTRACTORS' (\PUH).\CODE$
+   \end{itemize}
+ \item\label{item:6} invariant for contractors:
+   for all $\PUH \in \DOM (\CONTRACTORS)$,
+   $\CONTRACTORS (\PUH) = \Angle{ \CODE, \tilde\TIME, \BAL, \STORAGE}$
+   implies that $\PUH = \GENERATEHASH (\CODE, \tilde\TIME)$.
+\end{enumerate}
+\end{proposition}
+Establishing these properties relies on the preimage resistance of the
+various hash functions used to calculate operation hashes and public
+hashes. Items~\ref{item:1}--\ref{item:2} describe an invariant and the lifecycle of
+operations. Items~\ref{item:3} and \ref{item:4} describe the lifecycle
+of a transfer and items~\ref{item:5} and~\ref{item:6} describe
+invariants for contractors. The invariants establish the
+self-verifying property common of blockchain entities.
+
+\subsection{Typing related properties}
+
+To describe contracts we associate each public hash with a pair of
+types, the parameter type and the storage type.
+\begin{align*}
+  \Delta & ::= \EmptyEnv \mid \PUH: \TPAIR\ \TYPE\ \TYPEU, \Delta
+\end{align*}
+
+Define $ \Delta \vdash \CONTRACTORS$ by
+\begin{itemize}
+\item $\DOM (\Delta) = \DOM (\CONTRACTORS)$
+\item $\JTypeCode{\CONTRACTORS (\PUH).\CODE} {\Delta (\PUH)}$
+\item $\JTypeValue{\CONTRACTORS (\PUH).\STORAGE}{ \TYPE_s}$ where
+  $\Delta (\PUH) = \TPAIR\ \TYPE_p\ \TYPE_s$. 
+\end{itemize}
+
+Preservation
+
+If $[\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \BlockTrans{}
+[\PENDING', \MANAGERS', \CONTRACTORS', \TIME']$
+and $\Delta \vdash \CONTRACTORS$, \\
+then
+there is some $\Delta' \supseteq \Delta$ such that $\Delta' \vdash
+\CONTRACTORS'$.
+
+Consider a blockchain state  $[\PENDING, \MANAGERS, \CONTRACTORS,
+\TIME]$ where $\Delta \vdash \CONTRACTORS$.
+
+For all $\OPH\in\DOM (\PENDING)$,
+if  $\PENDING (\OPH) =  \Angle{\OP, \hat\TIME, \STATUS}$
+\begin{itemize}
+\item if $\OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ$, then
+\begin{itemize}
+  \item
+  $\PUK, \PUK' \in \DOM (\MANAGERS)$
+\end{itemize}
+\item if $\OP = \TRANSFER[\PARAMETER]\NTEZ\PUK\PUH\MTEZ$, then
+  \begin{itemize}
+  \item $\PUK \in \DOM (\MANAGERS)$ and $\PUH\in\DOM (\CONTRACTORS)$
+  \item $\PARAMETER : \TYPE_p$ where $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$. 
+  \end{itemize}
+
+\item if $\OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ$ and $\STATUS =
+  \STATUSINCLUDED\ \TIME'$, then
+   \begin{itemize}
+   \item $\PUK \in \DOM (\MANAGERS)$
+  \item $\CODE : \TPAIR\ \TYPE_p\ \TYPE_s$
+  \item $\STRING : \TYPE_s$
+  \item if $\STATUS =
+  \STATUSINCLUDED\ \TIME'$, then $\PUH =\GENERATEHASH (\CODE, \hat\TIME) \in \DOM (\CONTRACTORS)$ and $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$ (or $\CONTRACTORS(\PUH).\CODE = \CODE$).
+
+  \end{itemize}
+
+ \item if $st = \STATUSPENDING$ and $\MANAGERS(\PUK) = \Angle{\BAL,
+     \COU}$, then $\BAL \ge \NTEZ +  \MTEZ$ 
+\end{itemize}
+
+\newpage{}
+\appendix
+
+\section{Unused}
+\label{sec:unused}
 
 \subsection{An Implicit Account Transfer}
-\iffalse 
-\fi
 
@@
 \end{mathpar}
+\begin{mathpar}
+  \inferrule[rejected of counter]{
+    \NEG\ \CHECKCOU (\BLOCKCHAIN.\MANAGERS, \OP.\PUK) \\
+    }{
+    { [\EC\OP  :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+    }
+    \SystemTrans
+    { [\EC{\RAISE\ \ERRCOUNT} :: \EXPRS, \ACCOUNTS] \|
+      \BLOCKCHAIN
+   }
+  }
+\end{mathpar}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Smart Contracts}
-A. Originate
-
-\begin{mathpar}
-  \inferrule[Block-Originate]{
-   \Angle{\PAK,\PUK} \in \ACCOUNTS \\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
-    \CHECKCOU (\MANAGERS, \PUK) \\
-    \CHECKPRG (\CODE) \\
-    \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ)  \\
-    \CHECKINIT (\CODE, \STRING) \\
-    %\OPH = \GENERATEOPH(\PUK, \CODE, \STRING, \NTEZ, \MTEZ, \TIME) \\
-    \OPH = \GENERATEOPH(\OP, \TIME) \\
-    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ    
-  }{
-    [\EC\OP  :: \EXPRS, \ACCOUNTS,
-      ] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \to \\
-    [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \|
-      [\OPH \mapsto \Angle{\OP, \TIME, \STATUSPENDING}
-     ::\PENDING, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]
-  }
-\end{mathpar}
+
+\subsection{Contracts}
+\label{sec:contracts}
 
@@
      \BLOCKCHAIN
-  }
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[Block-Accept]{
-    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
-    \PUH = \GENERATEHASH(\CODE, \TIME) \\
-    \TIME-\hat\TIME  \le 60
-  }{
-    [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING} :: \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
-    \BlockTrans \\
-     [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING, \UPDATESUCC
-      (\MANAGERS, \PUK, \NTEZ, \MTEZ),\\ \PUH \mapsto  \Angle{\CODE, \TIME, \NTEZ, \STRING} :: \CONTRACTORS, \TIME+1]
-  }
-\end{mathpar}
-\begin{mathpar}
-  \inferrule[Block-Accept-Query]{
-    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
-    \PENDING (\OPH) =  \Angle{\OP,
-       \hat\TIME, \STATUSINCLUDING\ \tilde\TIME} \\
-    \CONTRACTORS (\PUH) =  \Angle{\CODE, \tilde\TIME, \NTEZ', \STRING'}
-  }{
-      [\EC{\QRY\ \GETCONTRACT\ \OPH}  :: \EXPRS, \ACCOUNTS] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
-    \SystemTrans 
-     [\EC{ \PUH}  :: \EXPRS, \ACCOUNTS] \|  [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
   }
@@
 \end{mathpar}
-\section{Queries}
+
+\subsection{Queries}
+\label{sec:queries-1}
+
 \begin{mathpar}
@@
   }{[\EC{\GETCOUNTER\PUK} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \NodeTrans\ [\EC{\COU} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[balance of an implicit account]{
-    \BLOCKCHAIN = 
-      [\PENDING, \PUK \mapsto \Angle{\BAL, \COU} :: \MANAGERS, \CONTRACTORS, \TIME]
-  }{[\EC{\GETBALANCE\PUK} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \NodeTrans\ [\EC{\BAL} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
+    \SystemTrans\ [\EC{\COU} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   }{[\EC{\GETBALANCE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \NodeTrans\ [\EC{\BAL} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
+    \SystemTrans\ [\EC{\BAL} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   }{[\EC{\GETSTORAGE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \NodeTrans\ [\EC{\STORAGE} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
+    \SystemTrans\ [\EC{\STORAGE} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   }{[\EC{\GETCODE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \NodeTrans\ [\EC{\CODE} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
+    \SystemTrans\ [\EC{\CODE} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   }{[\EC{\GETTYPE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \NodeTrans\ [\EC{\Delta (\PUH)} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
+    \SystemTrans\ [\EC{\Delta (\PUH)} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   \BLOCKCHAIN 
-    \NodeTrans {[\EC{\RAISE\ \ERRPUK} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}}
+    \SystemTrans {[\EC{\RAISE\ \ERRPUK} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}}
 \end{mathpar}
@@
   }{[\EC{\GETBALANCE\PUH/\GETSTORAGE\PUH/\GETCODE\PUH/\GETTYPE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \NodeTrans\\ [\EC{\RAISE\ \ERRPUH} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
+    \SystemTrans\\ [\EC{\RAISE\ \ERRPUH} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   }{[\EC{\GETSTATUS\OPH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \NodeTrans\ [\EC{\STATUSPENDING} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
+    \SystemTrans\ [\EC{\STATUSPENDING} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   }{[\EC{\GETSTATUS\OPH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \NodeTrans\ [\EC{\STATUSINCLUDING($n$)} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
+    \SystemTrans\ [\EC{\STATUSINCLUDING($n$)} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
 \end{mathpar}
@@
   }{[\EC{\GETSTATUS\OPH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \NodeTrans\ [\EC{\STATUSTIMEOUT} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
-\end{mathpar}
-\section{Functions}
+    \SystemTrans\ [\EC{\STATUSTIMEOUT} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
+\end{mathpar}
+
+\subsection{Functions}
+\label{sec:functions}
+
 \begin{enumerate}
@@
     \end{enumerate}
+
 \end{document}

### 2021-02-19 papers/execution-model/model.tex

@@
     \item Function \GENERATEHASH (\CODE, \TIME)  generates the public hash of a smart contract.
-
     \end{enumerate}
 
+\bibliographystyle{splncs04}
+\bibliography{bio}
+
 \end{document}

### 2021-02-19 papers/execution-model/model.tex
section-7

--- 2021-02-18 papers/execution-model/model.tex
@@
 
+\section{Related Work}
+\label{sec:related work}
+Smart contracts can only access information within their blockchain network.
+The inability to interact directly with external data sources limits the potential of smart contracts.
+Oracles \cite{oracle-patterns}\cite{call-action-oracle}\cite{oracles-study} can help overcome this limitation by providing a bridge between the outside world and the blockchain network.
+Oracles, a third-party service, can be used to provide external data to smart contracts.
+Several research works have been done to provide oracle solutions for blockchain.
+The work in \cite{blockchain-oracles} attempts to explore the relationship between oracles and blockchain and classifies different types of oracles.
+This framework aims to provide developers with a guide for incorporating oracles into blockchain-based applications.
+Chainlink \cite{chainlink-whitepaper} promises to provide reliable, tamper-proof input and output for smart contracts on any blockchain.
+For a specific application, a system called Town Crier \cite{town-crier} provides an authenticated data feed sourced from HTTPS-enabled data websites to smart contracts on Ethereum.
+The authors in \cite{oracle-real-value} construct a general-purpose decentralized oracle that can estimate the value of a real-world quantity, such as $R$.
+For application to prediction markets, the Truthcoin \cite{truthcoin-whitepaper} system proposes a proof-of-work sidechain that collects information about the creation and state of Prediction Markets.
+The paper \cite{astraea} briefly discusses some oracle solutions and provides a trustless decentralized oracle and prediction market platform.
+
+The main issues in using an oracle are trust and security \cite{trustworthy}.
+There are few studies that consider the issues of trust and reliability in blockchain oracles.
+The researchers in \cite{reliable-oracle} address the verification of blockchain oracles.
+They propose a decentralized oracle to verify the interactions between blockchain smart contracts and oracles.
+Similarly, in the paper in \cite{reliablity-oracles}, the researchers focus on the notion of trust and offer a framework to perform reliability analysis of different blockchain oracle platforms.
+In our research, we care about guaranteeing security over the interface system by utilizing type-system.
+Closely to our work, in \cite{interact-coq}, the authors present a model-executable specification of smart-contract execution in Coq.
+Their formalizations target to Ethereum and Tezos.
+
 \bibliographystyle{splncs04}

### 2021-02-19 papers/execution-model/model.tex
some cutting

--- 2021-02-19 papers/execution-model/model.tex
@@
 
-\subsection{Contributions}
+\subsubsection{Contributions}
 \label{sec:contributions}
@@
   alongside smart contracts in a blockchain. 
-\item Proofs of various properties of the combined system.
+\item Established various properties of the combined system withs
+  proofs in upcoming techreport.
 \item An implementation of a low-level OCaml-API to the Tezos
@@
 \end{lstlisting}
-The \lstinline{get_state} function queries data on
-the blockchain and returns the storage of a contract.
+The \lstinline{get_state} function obtains the storage of a contract from
+the blockchain.
 
@@
   current block),
-\item query the state and the balance of a contract (e.g., to obtain
+\item query storage and balance of a contract (to obtain
   the current highest bid),
 \item originate contracts, invoke contracts, and initiate
-  transfers. To this end, the program using the API has to run on
-  behalf of some authority (i.e., expressed by holding the private key
-  for some account).
+  transfers. Hence, the API has to run on
+  behalf of some account (by holding its private key).
 \end{itemize}
@@
 \label{sec:execution-model}
-The context of our work is the Tezos blockchain \cite{tezos-whitepaper, tezos-intropaper}. Tezos is a self-amending blockchain that improves several aspects compared to established 
+The context of our work is the Tezos blockchain \cite{tezos-whitepaper,tezos-intropaper}. Tezos is a self-amending blockchain that improves several aspects compared to established 
 blockchains.
@@
 
-\begin{figure}[tp]
-  \begin{align*}
-    \LET\ \mathit{oph} &=  \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
-         & \FIX \lambda f.\lambda x. \MATCH\ \GETSTATUS{\mathit{oph}}\ \WITH \\
-         & \mid \STATUSPENDING \to \text{Time.sleep(1)}; f () \textrm{\qquad(* not yet included,
-           continue waiting *)} \\
-         & \mid \STATUSINCLUDING (n) \to \text{if } n < 50\text{ then
-           Time.sleep(1)};f ()\textrm{\quad(* included with $n$
-           blocks confirmation *)}\\
-         & \mid \STATUSTIMEOUT \to \textrm{(* lost operation, try
-           again *)}
-  \end{align*}
-  \caption{Pseudocode example for a token transfer}
-  \label{fig:pseudocode-example}
-\end{figure}
-Figure~\ref{fig:pseudocode-example} shows an incomplete example
-expression that transfers tokens from $\PUK$ to $\PUK'$ and then
-checks the status of the operation. The outer loop to raise the fee
-and retry is omitted.
-
-Our type system does not include subtyping. The relation in
-Figure~\ref{fig:subtyping} just etablishes pairs of types that can be
-subjected to casting. A cast from $\TYPE$ to $\TYPEU$ is only allowed
+% \begin{figure}[tp]
+%   \begin{align*}
+%     \LET\ \mathit{oph} &=  \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+%          & \FIX \lambda f.\lambda x. \MATCH\ \GETSTATUS{\mathit{oph}}\ \WITH \\
+%          & \mid \STATUSPENDING \to \text{Time.sleep(1)}; f () \textrm{\qquad(* not yet included,
+%            continue waiting *)} \\
+%          & \mid \STATUSINCLUDING (n) \to \text{if } n < 50\text{ then
+%            Time.sleep(1)};f ()\textrm{\quad(* included with $n$
+%            blocks confirmation *)}\\
+%          & \mid \STATUSTIMEOUT \to \textrm{(* lost operation, try
+%            again *)}
+%   \end{align*}
+%   \caption{Pseudocode example for a token transfer}
+%   \label{fig:pseudocode-example}
+% \end{figure}
+% Figure~\ref{fig:pseudocode-example} shows an incomplete example
+% expression that transfers tokens from $\PUK$ to $\PUK'$ and then
+% checks the status of the operation. The outer loop to raise the fee
+% and retry is omitted.
+
+We define a relation $\SubType$ that establishes pairs of types that can be
+subjected to casting. It is given by the axioms
+$\inferrule{}{\TPUH \SubType \TADDR}$, $\inferrule{}{\TPUK \SubType
+  \TADDR}$, and $\inferrule{}{\TCONTRACT\ \TYPE \SubType \TPUH}$.
+A cast from $\TYPE$ to $\TYPEU$ is only allowed
 if $\TYPE \SubType \TYPEU$ (upcast) or $\TYPEU \SubType \TYPE$
@@
 hash is valid and has the expected parameter type.
-\begin{figure}[tp]
-  \begin{mathpar}
-    \inferrule{}{\TPUH \SubType \TADDR}
-
-    \inferrule{}{\TPUK \SubType \TADDR}
-
-    \inferrule{}{\TCONTRACT\ \TYPE \SubType \TPUH}
-  \end{mathpar}
-  \caption{Subtyping}
-  \label{fig:subtyping}
-\end{figure}
+
 Figure~\ref{fig:typing-expressions} presents selected typing rules for
@@
   \begin{mathpar}
-    \inferrule{}{ \EC{(\lambda x.\EXPR)\VAL} \ExprTrans
+    \inferrule{}{ \EC{(\lambda x.\EXPR)\VAL} 
+      \ExprTrans 
       \EC{\EXPR[\VAL/x]} }
+
+    \inferrule{}{ \EC{\TRY\ \VAL\ \EXCEPT\ \EXPR} \ExprTrans \EC{\VAL} }
 
@@
   %   
+    \inferrule{\TYPE \SubType \TYPEU}{ \EC{\CAST\VAL\TYPE\TYPEU} \ExprTrans \EC{\VAL}}
+
     \inferrule{ \TRY \notin \EC[F]{} }{ \EC{\TRY\ {\EC[F]{\RAISE\
             \VAL}}\ \EXCEPT\ \EXPR} \ExprTrans \EC{\EXPR\ \VAL} }
-
-    \inferrule{\TYPE \SubType \TYPEU}{ \EC{\CAST\VAL\TYPE\TYPEU} \ExprTrans \EC{\VAL}}
     %
@@
 \newpage{}
+
+\bibliographystyle{splncs04}
+\bibliography{bio}
+
+\newpage{}
 \appendix
@@
 
-\bibliographystyle{splncs04}
-\bibliography{bio}
-
 \end{document}

### 2021-02-19 papers/execution-model/model.tex

@@
 
+\section{Related Work}
+\label{sec:related work}
+Smart contracts can only access information within their blockchain network.
+The inability to interact directly with external data sources limits the potential of smart contracts.
+Oracles \cite{oracle-patterns}\cite{call-action-oracle}\cite{oracles-study} can help overcome this limitation by providing a bridge between the outside world and the blockchain network.
+Oracles, a third-party service, can be used to provide external data to smart contracts.
+Several research works have been done to provide oracle solutions for blockchain.
+The work in \cite{blockchain-oracles} attempts to explore the relationship between oracles and blockchain and classifies different types of oracles.
+This framework aims to provide developers with a guide for incorporating oracles into blockchain-based applications.
+Chainlink \cite{chainlink-whitepaper} promises to provide reliable, tamper-proof input and output for smart contracts on any blockchain.
+For a specific application, a system called Town Crier \cite{town-crier} provides an authenticated data feed sourced from HTTPS-enabled data websites to smart contracts on Ethereum.
+The authors in \cite{oracle-real-value} construct a general-purpose decentralized oracle that can estimate the value of a real-world quantity, such as $R$.
+For application to prediction markets, the Truthcoin \cite{truthcoin-whitepaper} system proposes a proof-of-work sidechain that collects information about the creation and state of Prediction Markets.
+The paper \cite{astraea} briefly discusses some oracle solutions and provides a trustless decentralized oracle and prediction market platform.
+
+The main issues in using an oracle are trust and security \cite{trustworthy}.
+There are few studies that consider the issues of trust and reliability in blockchain oracles.
+The researchers in \cite{reliable-oracle} address the verification of blockchain oracles.
+They propose a decentralized oracle to verify the interactions between blockchain smart contracts and oracles.
+Similarly, in the paper in \cite{reliablity-oracles}, the researchers focus on the notion of trust and offer a framework to perform reliability analysis of different blockchain oracle platforms.
+In our research, we care about guaranteeing security over the interface system by utilizing type-system.
+Closely to our work, in \cite{interact-coq}, the authors present a model-executable specification of smart-contract execution in Coq.
+Their formalizations target to Ethereum and Tezos.
+
 \newpage{}

### 2021-02-19 papers/execution-model/model.tex
Add files via upload
revised Sec-3 and Sec-6

--- 2021-02-19 papers/execution-model/model.tex
@@
 \label{sec:execution-model}
-The context of our work is the Tezos blockchain \cite{tezos-whitepaper,tezos-intropaper}. Tezos is a self-amending blockchain that improves several aspects compared to established 
-blockchains.
-Tezos introduces an original consensus algorithm called Liquid Proof of Stake that allows consensus not only on the state of its ledger, like Bitcoin \cite{bitcoin-whitepaper} or Ethereum \cite{eth-whitepaper}, but also on how the economic protocol and the nodes should  upgrade, and serves as a decentralized smart contract platform that focuses on formal methods to improve security.
-
-In Tezos, there are two types of accounts: implicit accounts and smart contracts, and they are stateful.
-An implicit account is a non-programmable account and is associated with a pair of private/public keys.
-A smart contract is a programmable account created by an origination operation and has no corresponding secret key.
+The context of our work is the Tezos blockchain \cite{tezos-whitepaper,tezos-intropaper}.
+Tezos is a self-amending blockchain that improves several aspects compared to established blockchains.
+Tezos proposes an original consensus algorithm called Liquid Proof of Stake that allows consensus not only on the state of its ledger, like Bitcoin \cite{bitcoin-whitepaper} or Ethereum \cite{eth-whitepaper}, but also on how the economic protocol and nodes should upgrade, and serves as a decentralized smart contract platform that focuses on formal methods to improve security.
+
+In Tezos, there are two types of accounts: implicit accounts, which are associated with a pair of private/public keys, and smart contracts, which are a programmable account created by an origination operation and have no corresponding secret key.
 The address of a smart contract is a unique public hash that depends on the creation operation.
-All existing accounts are stored in a context component on the blockchain.
-An implicit account is managed with its public key, balance, and counter, whose job is to prevent replay attacks.
+An implicit account is maintained on the blockchain with its public key, balance, and counter, whose job is to prevent replay attacks.
 A smart contract account is stored with its script, storage, and balance.
-Tezos provides the Michelson language for writing a smart contract.
-Michelson is a stack-based language with strict static type checking.
-A contract is a function that maps a pair of a parameter and a storage, which have fixed and monomorphic types to a pair of a list of internal operations and an updated storage.
-The script of a smart contract must be type-checked before it is introduced into the system.
-
-An implicit account can perform three kinds of transactions: (1) transfer tokens to another implicit account, (2) transfer (invoke) a smart contract, or (3) originate a new smart contract.E ach transaction includes the address of the sender contract, the address of the destination contract, the amount of tokens transferred, and a fee to be paid either by payment to a baker or by destruction (burning).
-In addition, a smart contract invocation must provide input data and and an origination transaction specifies the script of the contract and the initial content of the contract storage.
-A transaction can only be sent if it has been signed with the sender contract's private key.
-It is then injected into the blockchain network via a node that runs the gossip network and updates the context.
-The node first validates the transaction before submitting it to the network.
-In general, a transaction can fail for a number of reasons, including incorrect destination address, insufficient balances, incorrect counters, and incorrect type of input parameters (or scripts).
-A transaction is valid only if the counter of the sender contract is the same as the counter  used in the transaction.
-The invocation of a smart contract may fail for reasons determined by the contract's script.
-An invalid transaction is rejected by the node.
-
+A contract script maps a pair of a parameter and a storage, which have fixed and monomorphic types to a pair of a list of internal operations and an updated storage.
+An implicit account performs three kinds of transactions: (1) transfer tokens to another implicit account, (2) invoke a smart contract, or (3) originate a new smart contract.
+A contract origination specifies the script of the contract and the initial contents of the contract storage, while a contract invocation must provide input data.
+Each transaction contains a fee to be paid either by payment to a baker or by destruction (burning).
+A transaction is injected into the blockchain network via a node, which then validates the transaction before submitting it to the network.
+Generally, a transaction can be rejected by the node for a number of reasons.
 Once the transaction is valid, it is injected into the mempool, which contains all pending transactions before they can be included in a block.
-On the other hand, a pending transaction may get lost in the mempool.
-That is, it may be dropped.
-There are several
-causes for dropping, primarily timeout or overflow of the mempool, which is limited in size in the implementation.
+On the other hand, a pending transaction can be lost in the mempool.
 A transaction is timed out when 60 blocks have passed and it can no longer be included in a block.
-When a transaction is included in a blockchain, the amount of tokens transferred is added to the balance of destination contract and when a smart contract call is made, the script of the destination contract is executed.
-Once a transaction is applied, the counter increments by one, preventing the transaction from being reused.
+When a transaction is included in a blockchain, the related accounts are updated according to the transaction result.
 
@@
 
+\section{Related Work}
+\label{sec:related work}
+The inability to access external data sources limits the potential of smart contracts.
+Oracles \cite{oracle-patterns}\cite{call-action-oracle}\cite{oracles-study} can help overcome this limitation by providing a bridge between the outside sources and the blockchain network.
+A blockchain oracle is used to provide external data to smart contracts.
+Several researches have been done to provide oracle solutions for blockchain.
+The work in \cite{blockchain-oracles} proposes a framework to explain blockchain oracles and various key aspects of oracles.
+This framework aims to provide developers with a guide for incorporating oracles into blockchain-based applications.
+Practically, the decentralized oracle network Chainlink \cite{chainlink-whitepaper} is being developed to provide reliable, tamper-proof input for smart contracts on any blockchain.
+For a specific application, a system called Town Crier \cite{town-crier} provides an authenticated data feed, sourced from HTTPS-enabled data websites, for smart contracts on Ethereum.
+The authors in \cite{oracle-real-value} construct an oracle that can estimate the value of a real quantity, such as $R$.
+For application to prediction markets, there are Truthcoin system \cite{truthcoin-whitepaper} and Astraea, a trustless decentralized oracle \cite{astraea}.
+
+The main issues in using a blockchain oracle are trust and security \cite{trustworthy}.
+The researchers in \cite{reliable-oracle} have proposed a decentralized oracle to verify the interactions and solve the disputes between blockchain smart contracts and oracles.
+Similarly, researchers in \cite{reliablity-oracles} focus on the notion of trust and provide a framework to perform reliability analysis of various blockchain oracle platforms.
+Closely following our work, in \cite{interact-coq} the authors present a model-executable specification of smart-contract execution in Coq.
+Their formalizations target Ethereum and Tezos.
+
 \newpage{}

### 2021-02-19 papers/execution-model/model.tex
Add files via upload
revised sec-3 and sec-6

@@
 
-The main issues in using a blockchain oracle are trust and security \cite{trustworthy}.
-The researchers in \cite{reliable-oracle} have proposed a decentralized oracle to verify the interactions and solve the disputes between blockchain smart contracts and oracles.
-Similarly, researchers in \cite{reliablity-oracles} focus on the notion of trust and provide a framework to perform reliability analysis of various blockchain oracle platforms.
-Closely following our work, in \cite{interact-coq} the authors present a model-executable specification of smart-contract execution in Coq.
+The main problems with using a blockchain oracle are the untrusted data provided maliciously or inaccurately \cite{trustworthy}.
+The researchers in \cite{reliable-oracle} propose an oracle equipped with verification and disputation mechanisms.
+Similarly, researchers in \cite{reliablity-oracles} provide a framework for performing reliability analysis of various blockchain oracle platforms.
+Closely following our work, the authors in \cite{interact-coq} present a model-executable specification of smart-contract execution in Coq.
 Their formalizations target Ethereum and Tezos.

### 2021-02-20 papers/execution-model/model.tex
Add files via upload
updated bio.bib

@@
 software systems and to enable input from outside the blockchain. Such
-input requires trusted intermediaries that run so-called oracles \cite{oracles}. A
+input requires trusted intermediaries that run so-called oracles \cite{oracle-patterns, call-action-oracle}. A
 smart contract registers a request and a callback with an oracle. The
@@
 
-The execution model is an abstraction of the Tezos blockchain \cite{Tezos}
+The execution model is an abstraction of the Tezos blockchain \cite{tezos-whitepaper}
 augmented with functional (OCaml) programs that interact with the
@@
 The inability to access external data sources limits the potential of smart contracts.
-Oracles \cite{oracle-patterns}\cite{call-action-oracle}\cite{oracles-study} can help overcome this limitation by providing a bridge between the outside sources and the blockchain network.
+Oracles \cite{oracle-patterns, call-action-oracle, oracles-study} can help overcome this limitation by providing a bridge between the outside sources and the blockchain network.
 A blockchain oracle is used to provide external data to smart contracts.

### 2021-02-20 papers/execution-model/model.tex
fixed citations  Please enter the commit message for your changes. Lines starting

@@
 software systems and to enable input from outside the blockchain. Such
-input requires trusted intermediaries that run so-called oracles \cite{oracle-patterns, call-action-oracle}. A
+input requires trusted intermediaries that run so-called oracles \cite{oracle-patterns,call-action-oracle}. A
 smart contract registers a request and a callback with an oracle. The
@@
 We write $\emptyset$ for the empty set and $\mathbf{e :: s}$ to
-decompose a set into an element $\mathbf{e}$ and a set
+decompose a set nondeterministically into an element $\mathbf{e}$ and a set
 $\mathbf{s}$. We generally use lowercase boldface for metavariables
@@
 public keys, and the capitalized name for the
-corresponding type as well as the set of these values (as in \TPUK).
+corresponding type as well as for the set of these values (as in \TPUK).
 
@@
 \end{align*}
-In the transfer, \NTEZ\ is the amount of tokens transferred, \PUK\ is the public key of the
+In the transfer, which also serves as invocation, \NTEZ\ is the amount of tokens transferred, \PUK\ is the public key of the
 sender, \ADDR\ is either a public 
@@
 \end{figure}
-All queries and operations are started by programs, i.e., closed expressions that run on the
+All queries and operations are started by programs, i.e., closed
+expressions of type unit that run on the
 local node. Each program can send transactions on behalf of any
@@
 
-    \inferrule{\JTypeExpr\TEnv\EXPR\TYPE \\ \TYPE \SubType
-      \TYPEU}{\JTypeExpr\TEnv\EXPR\TYPEU}
-
     \inferrule{}{\JTypeExpr\TEnv\VARIABLE{\TEnv (\VARIABLE)}}
@@
   \end{mathpar}
-  \caption{Typing rules for expressions}
+  \caption{Typing rules for expressions (excerpt)}
   \label{fig:typing-expressions}
@@
 \begin{mathpar}
-  \inferrule{
-    \JTypeExpr\TEnv\EXPR\TPUK
-  }{
-    \JTypeExpr\TEnv {\QRY\ \GETCOUNTER\EXPR}\TINT
-  }
-
+  % \inferrule{
+  %   \JTypeExpr\TEnv\EXPR\TPUK
+  % }{
+  %   \JTypeExpr\TEnv {\GETCOUNTER\EXPR}\TINT
+  % }
+  %   
   \inferrule{
@@
   }{
-    \JTypeExpr\TEnv {\QRY\ \GETBALANCE\EXPR}\TTEZ
+    \JTypeExpr\TEnv {\GETBALANCE\EXPR}\TTEZ
   }
@@
   }{
-    \JTypeExpr\TEnv {\QRY\ \GETSTATUS\EXPR}\TSTATUS
+    \JTypeExpr\TEnv {\GETSTATUS\EXPR}\TSTATUS
   }
@@
   }{
-    \JTypeExpr\TEnv {\QRY\ \GETSTORAGE\EXPR}\TSTRING
+    \JTypeExpr\TEnv {\GETSTORAGE\EXPR}\TSTRING
   }
@@
   % }{
-  %   \JTypeExpr\TEnv {\QRY\ \GETCODE\EXPR}?
+  %   \JTypeExpr\TEnv {\GETCODE\EXPR}?
   % }
@@
   % }{
-  %   \JTypeExpr\TEnv {\QRY\ \GETTYPE\EXPR}?
+  %   \JTypeExpr\TEnv {\GETTYPE\EXPR}?
   % }
@@
   }{
-    \JTypeExpr\TEnv {\QRY\ \GETCONTRACT\EXPR}\TPUH
+    \JTypeExpr\TEnv {\GETCONTRACT\EXPR}\TPUH
   }
@@
 \begin{proposition}
-  The following property is preserved by a step on a well-formed
+  The following properties are preserved by a step on a well-formed
   configuration $ [\EXPRS, \ACCOUNTS] \| \BLOCKCHAIN$:
@@
   \hat\TIME)$. 
-\item for all $\OPH \in \DOM(P)$, if 
+\item\label{item:7} for all $\OPH \in \DOM(P)$, if 
   $\PENDING (\OPH) = \Angle{\OP,  \hat\TIME, \STATUS}$, then either
@@
   \item  $\STATUS  = \STATUSPENDING$, $\TIME - \hat\TIME
-    \le 60 $, and
+    \le 60 $, 
     $\PENDING' (\OPH) =       \Angle{\OP, \hat\TIME, \STATUSINCLUDED\
-      \TIME}$.
-  \end{itemize}
- \item\label{item:2} for all $\OPH \in \DOM(P)$ and $\PENDING (\OPH) = \Angle{\OP,  \hat\TIME, \STATUSPENDING}$, 
-    \begin{itemize}
-    	\item  if $\MANAGERS(\OP.\PUK) =  \Angle{\BAL, \COU}$ then  
-  $\COU.b = \TRUE$.
+      \TIME}$, and $\TIME'=\TIME+1$.
+  \end{itemize}
+ \item\label{item:2} for all $\OPH \in \DOM(P)$ and $\PENDING (\OPH) = \Angle{\OP,  \hat\TIME, \STATUS}$, 
+    \begin{itemize}
+    	\item  if $\STATUS=\STATUSPENDING$ and $\MANAGERS(\OP.\PUK) =  \Angle{\BAL, \COU}$ then  
+  $\COU.b = \TRUE$ and $\BAL \ge \OP.\NTEZ + \OP.\MTEZ$;
+\item if $\STATUS=\STATUSINCLUDED\ \hat\TIME$, then $\hat\TIME<\TIME'$.
     \end{itemize}
@@
 \end{proposition}
-Establishing these properties relies on the preimage resistance of the
+Establishing items~\ref{item:7} and~\ref{item:4} relies on the preimage resistance of the
 various hash functions used to calculate operation hashes and public
-hashes. Items~\ref{item:1}--\ref{item:2} describe an invariant and the lifecycle of
+hashes: we always feed a fresh timestamp into the hash
+functions for operations and code. Items~\ref{item:1}--\ref{item:2} describe an invariant and
+the lifecycle of 
 operations. Items~\ref{item:3} and \ref{item:4} describe the lifecycle
@@
 \subsection{Typing related properties}
-
-To describe contracts we associate each public hash with a pair of
-types, the parameter type and the storage type.
-\begin{align*}
-  \Delta & ::= \EmptyEnv \mid \PUH: \TPAIR\ \TYPE\ \TYPEU, \Delta
-\end{align*}
-
-Define $ \Delta \vdash \CONTRACTORS$ by
-\begin{itemize}
-\item $\DOM (\Delta) = \DOM (\CONTRACTORS)$
-\item $\JTypeCode{\CONTRACTORS (\PUH).\CODE} {\Delta (\PUH)}$
-\item $\JTypeValue{\CONTRACTORS (\PUH).\STORAGE}{ \TYPE_s}$ where
-  $\Delta (\PUH) = \TPAIR\ \TYPE_p\ \TYPE_s$. 
-\end{itemize}
-
-Preservation
-
-If $[\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \BlockTrans{}
-[\PENDING', \MANAGERS', \CONTRACTORS', \TIME']$
-and $\Delta \vdash \CONTRACTORS$, \\
-then
-there is some $\Delta' \supseteq \Delta$ such that $\Delta' \vdash
-\CONTRACTORS'$.
-
-Consider a blockchain state  $[\PENDING, \MANAGERS, \CONTRACTORS,
-\TIME]$ where $\Delta \vdash \CONTRACTORS$.
+% , the parameter type and the storage type.
+To describe the typing of contracts we maintain an environment
+$\Delta ::= \EmptyEnv \mid \PUH: \TYPE, \Delta$ that associates a
+public hash with a type.
+We define typing for blockchains, local nodes, and configurations.
+\begin{mathpar}
+  \inferrule{
+    \DOM (\Delta) = \DOM (\BLOCKCHAIN.\CONTRACTORS) \\
+    (\forall\PUH\in\DOM (\Delta)) \\
+    \Delta (\PUH) = \TPAIR\ \TYPE_p\ \TYPE_s \\
+    \JTypeCode{\BLOCKCHAIN.\CONTRACTORS (\PUH).\CODE} {\TPAIR\ \TYPE_p\ \TYPE_s}
+    \\
+    \JTypeValue{\BLOCKCHAIN.\CONTRACTORS (\PUH).\STORAGE}{ \TYPE_s}
+  }{\JTypeBlockchain\Delta\BLOCKCHAIN}
+\end{mathpar}
+The type for a hash is a pair type, which coincides with the type of
+the code stored at that hash. The storage at that hash has the type
+expected by the code.
+\begin{mathpar}
+  \inferrule{
+    \JTypeExpr\cdot{ \EXPR_i}\TUNIT  }{
+    \JTypeNode{[\overline{\EXPR}, \ACCOUNTS]}
+  }
+
+  \inferrule{\JTypeBlockchain\Delta\BLOCKCHAIN \\
+    \JTypeNode{\NODE_i}
+  }{\JTypeConfig\Delta{\BLOCKCHAIN[\overline\NODE]}}
+\end{mathpar}
+
+\begin{lemma}[Preservation]
+  If $\BLOCKCHAIN[\overline\NODE] \SystemTrans{} \BLOCKCHAIN'[\overline\NODE']$ and
+  $\JTypeBlockchain\Delta \BLOCKCHAIN$, then there is some
+  $\Delta' \supseteq \Delta$ such that
+  $\JTypeBlockchain{\Delta'}{ \BLOCKCHAIN'}$.
+\end{lemma}
+This lemma includes the standard preservation for the lambda calculus part.
+\begin{lemma}[Progress]
+  If $\JTypeConfig\Delta{\BLOCKCHAIN[\overline\NODE]}$, then either
+  all expressions in all nodes are unit values or there is a
+  configuration $\BLOCKCHAIN'[\overline\NODE']$ such that
+  $\BLOCKCHAIN[\overline\NODE] \SystemTrans \BLOCKCHAIN'[\overline\NODE']$.
+\end{lemma}
+The consistency lemma says that all committed transactions respect the
+typing.
+\begin{lemma}[Consistency]
+Consider a blockchain state with $\JTypeBlockchain\Delta {[\PENDING, \MANAGERS, \CONTRACTORS,
+\TIME]}$.
 
@@
 \item if $\OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ$, then
-\begin{itemize}
-  \item
-  $\PUK, \PUK' \in \DOM (\MANAGERS)$
-\end{itemize}
+  $\PUK, \PUK' \in \DOM (\MANAGERS)$;
 \item if $\OP = \TRANSFER[\PARAMETER]\NTEZ\PUK\PUH\MTEZ$, then
   \begin{itemize}
-  \item $\PUK \in \DOM (\MANAGERS)$ and $\PUH\in\DOM (\CONTRACTORS)$
-  \item $\PARAMETER : \TYPE_p$ where $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$. 
-  \end{itemize}
-
+  \item $\PUK \in \DOM (\MANAGERS)$ and $\PUH\in\DOM (\CONTRACTORS)$,
+  \item $\JTypeValue\PARAMETER{ \TYPE_p}$ where $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$;
+  \end{itemize}
 \item if $\OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ$ and $\STATUS =
@@
   \begin{itemize}
-   \item $\PUK \in \DOM (\MANAGERS)$
-  \item $\CODE : \TPAIR\ \TYPE_p\ \TYPE_s$
-  \item $\STRING : \TYPE_s$
-  \item if $\STATUS =
-  \STATUSINCLUDED\ \TIME'$, then $\PUH =\GENERATEHASH (\CODE, \hat\TIME) \in \DOM (\CONTRACTORS)$ and $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$ (or $\CONTRACTORS(\PUH).\CODE = \CODE$).
-
-  \end{itemize}
-
- \item if $st = \STATUSPENDING$ and $\MANAGERS(\PUK) = \Angle{\BAL,
-     \COU}$, then $\BAL \ge \NTEZ +  \MTEZ$ 
-\end{itemize}
+  \item $\PUK \in \DOM (\MANAGERS)$ and  $\PUH =\GENERATEHASH (\CODE, \hat\TIME) \in \DOM (\CONTRACTORS)$,
+  \item $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$,  $\JTypeCode\CODE{
+      \TPAIR\ \TYPE_p\ \TYPE_s}$ and $\JTypeValue\STRING{ \TYPE_s}$.
+  \end{itemize}
+\end{itemize}
+\end{lemma}
 
@@
 The inability to access external data sources limits the potential of smart contracts.
-Oracles \cite{oracle-patterns, call-action-oracle, oracles-study} can help overcome this limitation by providing a bridge between the outside sources and the blockchain network.
+Oracles \cite{oracle-patterns,call-action-oracle,oracles-study} can help overcome this limitation by providing a bridge between the outside sources and the blockchain network.
 A blockchain oracle is used to provide external data to smart contracts.

### 2021-02-20 papers/execution-model/model.tex
parenthetical bibrefs

@@
 \label{sec:related work}
-The inability to access external data sources limits the potential of smart contracts.
-Oracles \cite{oracle-patterns,call-action-oracle,oracles-study} can help overcome this limitation by providing a bridge between the outside sources and the blockchain network.
-A blockchain oracle is used to provide external data to smart contracts.
-Several researches have been done to provide oracle solutions for blockchain.
-The work in \cite{blockchain-oracles} proposes a framework to explain blockchain oracles and various key aspects of oracles.
-This framework aims to provide developers with a guide for incorporating oracles into blockchain-based applications.
-Practically, the decentralized oracle network Chainlink \cite{chainlink-whitepaper} is being developed to provide reliable, tamper-proof input for smart contracts on any blockchain.
-For a specific application, a system called Town Crier \cite{town-crier} provides an authenticated data feed, sourced from HTTPS-enabled data websites, for smart contracts on Ethereum.
-The authors in \cite{oracle-real-value} construct an oracle that can estimate the value of a real quantity, such as $R$.
-For application to prediction markets, there are Truthcoin system \cite{truthcoin-whitepaper} and Astraea, a trustless decentralized oracle \cite{astraea}.
-
-The main problems with using a blockchain oracle are the untrusted data provided maliciously or inaccurately \cite{trustworthy}.
-The researchers in \cite{reliable-oracle} propose an oracle equipped with verification and disputation mechanisms.
-Similarly, researchers in \cite{reliablity-oracles} provide a framework for performing reliability analysis of various blockchain oracle platforms.
-Closely following our work, the authors in \cite{interact-coq} present a model-executable specification of smart-contract execution in Coq.
-Their formalizations target Ethereum and Tezos.
+The inability to access external data sources limits the potential of
+smart contracts. Oracles
+\cite{oracle-patterns,call-action-oracle,oracles-study} can help
+overcome this limitation by providing a bridge between the outside
+sources and the blockchain network. A blockchain oracle is used to
+provide external data to smart contracts. Several researches have been
+done to provide oracle solutions for blockchain. Adler et al
+\cite{blockchain-oracles} propose a framework to explain blockchain
+oracles and various key aspects of oracles. This framework aims to
+provide developers with a guide for incorporating oracles into
+blockchain-based applications. Practically, the decentralized oracle
+network Chainlink \cite{chainlink-whitepaper} is being developed to
+provide reliable, tamper-proof input for smart contracts on any
+blockchain. For a specific application, a system called Town Crier
+\cite{town-crier} provides an authenticated data feed, sourced from
+HTTPS-enabled data websites, for smart contracts on Ethereum. George
+and Lesaege \cite{oracle-real-value} construct an oracle that can
+estimate the value of a real quantity, such as $R$.  
+For application to prediction markets, there are Truthcoin system
+\cite{truthcoin-whitepaper} and Astraea, a trustless decentralized
+oracle \cite{astraea}.
+
+The main problems with using a blockchain oracle are the untrusted
+data provided maliciously or inaccurately \cite{trustworthy}. Ma at el
+\cite{reliable-oracle} propose an oracle equipped with 
+verification and disputation mechanisms. Similarly, Lo et al
+\cite{reliablity-oracles} provide a framework for performing
+reliability analysis of various blockchain oracle platforms. Closely
+following our work, Nielsen and Spitters \cite{interact-coq} present a
+model-executable specification of smart-contract execution in
+Coq. Their formalizations target Ethereum and Tezos.
 

### 2021-02-21 papers/execution-model/model.tex
intro & conclusion

@@
 
-{[Ultra-brief intro to blockchain]}
-
-Smart contracts rarely live in isolation. To reach their full
-potential, it should be possible to integrate them with traditional
-software systems and to enable input from outside the blockchain. Such
-input requires trusted intermediaries that run so-called oracles \cite{oracle-patterns,call-action-oracle}. A
+First generation blockchains were primarily geared towards supporting
+cryptocurrencies. The most prominent system of this kind is Bitcoin
+\cite{bitcoin-whitepaper}. Though Bitcoin already features a
+rudimentary programming language called Script, second generation
+blockchains like the Ethereum blockchain \cite{eth-whitepaper} feature
+Turing-complete programming facilities, called 
+Smart Contracts. They provide robust trustworthy distributed computing
+facilities even though the programs run on a peer-to-peer network with
+untrusted participants. Each peer in the network runs the same program
+and uses cryptographic methods to check the results among the other
+peers and to create a persistent ledger of all transactions, the
+blockchain, thus ensuring the integrity of the results. Third
+generation blockchains, like Tezos \cite{tezos-whitepaper}, are even adaptable to
+new requirements without breaking participating peers (no ``hard
+forks'' required).
+
+The strength of programs on the blockchain is also their
+weakness. They are fully deterministic in that they can only depend on
+data that is stored on the chain and on contract invocations, which are
+also stored on the chain. Moreover, the entire data as well as all
+transactions are public. These properties make it hard to react to
+external stimuli like time triggers or events like an exchange rate or
+a share price hitting a limit.
+
+As smart contracts rarely live in isolation, it should be possible to
+integrate them with traditional software systems and to enable
+triggering contracts from outside the blockchain. Such triggers
+require trusted intermediaries that provide so-called oracles \cite{oracle-patterns,call-action-oracle}. A
 smart contract registers a request and a callback with an oracle. The
@@
 
-We present two examples where integration of smart contracts is needed
-and propose a typed API for making such integration type safe.
+We present a typed API for invoking contracts from OCaml
+programs. Such an API with a reliable computing facility and network
+connection is sufficient to self provision an oracle and to avoid
+having to trust an oracle provider. Moreover, our approach provides a
+type-safe facility rather than oracles which are intrisically untyped
+because they aim to provide a generic service.
 
@@
 
+\section{Conclusion}
+\label{sec:conclusion}
+
+We present a first step towards a typed API for smart contracts on the
+Tezos blockchain. Our formalization enables us to establish basic
+properties of the interaction between ordinary programs and smart
+contracts. We see ample scope for future work to provide a
+higher-level interface that exploits the similarities between
+blockchain programming and concurrent programs.
+
 \newpage{}

### 2021-02-22 papers/execution-model/model.tex
final touches

@@
 \item An implementation of a low-level OCaml-API to the Tezos
-  blockchain, which corresponds to the operational semantics.
+  blockchain, which corresponds to the operational semantics.\footnote{%
+    Available at \url{https://github.com/tezos-project/Tezos-Ocaml-API}.}
 \end{itemize}
@@
 safe-safe way. Tezos' smart contract language Michelson and its
-properties have been formalized elsewhere \cite{type-safe-michelson}.
+properties have been formalized elsewhere \cite{DBLP:conf/fm/BernardoCHPT19}.
 
@@
 the blockchain.
-\emph{Queries} are defined by the following grammar:
+\emph{Query operators} are defined by the following grammar:
 \begin{align*}
-  \QRY & ::=
+  \QOP & ::=
   % \GETCOUNTER\PUK  
   %        \mid
-         \GETBALANCE\ADDR
-  \mid \GETSTATUS\OPH
-  \mid \GETSTORAGE\PUH
+         \GETBALANCE{}%\ADDR
+  \mid \GETSTATUS{}%\OPH
+  \mid \GETSTORAGE{}%\PUH
   % \mid \GETCODE\PUH 
   % \mid \GETTYPE\PUH
-  \mid \GETCONTRACT\OPH
+  \mid \GETCONTRACT{}%\OPH
 \end{align*}
@@
 a submitted operation by its operation hash; the stored value of a
-contract by its public hash; and the code of a contract by the
+contract by its public hash; and the public hash of a contract by the
 operation hash of its originating transaction.
@@
              \PATTERN \mid \SOME\ \PATTERN \mid \NONE \\
-  &\mid \FALSE \mid \TRUE \mid \STATUS \mid \ERROR\\
-  \QOP & ::= \GETBALANCE{} \mid \GETSTATUS{} \mid \GETSTORAGE{} \mid \GETCODE{} \mid \GETCOUNTER{}
-         \mid \GETTYPE{}
+            &\mid \FALSE \mid \TRUE \mid \STATUS \mid \ERROR
+  % \\
+  % \QOP & ::= \GETBALANCE{} \mid \GETSTATUS{} \mid \GETSTORAGE{} \mid \GETCODE{} \mid \GETCOUNTER{}
+  %        \mid \GETTYPE{}
   \\[2ex]
@@
 well as for the queries. Finally, there is a type cast
-$\CAST\EXPR\TYPE\TYPEU$, which is only applicable to pairs of
-types related in the reflexive, transitive, and symmetric closure of
-the subtyping relation in Figure~\ref{fig:subtyping}. Upcasts will
-just go through, but downcasts may raise an exception, as usual.
+$\CAST\EXPR\TYPE\TYPEU$, which we describe after discussing types.
 
@@
 
-We define a relation $\SubType$ that establishes pairs of types that can be
-subjected to casting. It is given by the axioms
+Type casts are only applicable to certain pairs of
+types governed by a relation $\SubType$, which could also serve as a
+subtyping relation. It is given by the axioms
 $\inferrule{}{\TPUH \SubType \TADDR}$, $\inferrule{}{\TPUK \SubType

### 2021-03-10 assertions/doc/thesis-bernhardt/assertion_highlighting.tex
Introduction first draft

\usepackage{listings, xcolor}

\definecolor{verylightgray}{rgb}{.97,.97,.97}

\lstdefinelanguage{Assertion}{
	keywords=[1]{entrypoint, assert, if, else, true, false, forall, exists},
	keywordstyle=[1]\color{blue}\bfseries,
	keywords=[2]{address, unit, never, bool, int, nat, string, chain_id, bytes, mutez, key_hash, key, signature, timestamp,
	option, or, pair, list, set, operation, lambda, map, big_map},	% types; money and time units
	keywordstyle=[2]\color{teal}\bfseries,
	keywords=[3]{left, right, some, none, cons, nil, _},
	keywordstyle=[3]\color{violet}\bfseries,
	identifierstyle=\color{black},
	sensitive=false,
	comment=[l]{//},
	morecomment=[s]{(*}{*)},
	commentstyle=\color{gray}\ttfamily,
	stringstyle=\color{red}\ttfamily,
	morestring=[b]',
	morestring=[b]"
}

### 2021-03-10 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
Introduction first draft

\chapter{Introduction}\label{chap:introduction}
Each execution of a blockchain-based Smart Contract in a gas-instrumented virtual machine generates costs proportional to the amount and complexity of computations and the  memory consumption \cite{goodman_tezos_2014}\cite{wood_ethereum_2021}. These fees, often calculated in gas, have to be paid for by the sender of the transaction and thus provides a powerful incentive to keep  smart contracts simple. However, in reality meaningful applications might need to perform some resource intensive computations at some point, which would be too expensive to execute inside the blockchain's virtual machine. Moreover, some blockchains impose a hard cap of how much gas can be consumed in one transaction, limiting the amount of operations that can be executed \cite{goodman_tezos_2014}.\\
In order to avoid these costs and restrictions, an application could perform some computations outside of the blockchain context (i.e., off-chain) and only submit the results to a smart contract as input parameter for further processing or to store it on the chain. This approach raises another problem though - trusting that the submitted results are correct poses a safety as well as a security risk. Invalid results can be submitted unintentionally, if the computation is faulty, or a third party may pass them intentionally to cause harm or take advantage. Consequently, submitted parameters need to be checked for specified properties before the smart contract is executed. Although in many cases, verification is less expensive than computing the result itself, the generated costs for checking the validity increase with the size of the problem or input, ultimately becoming too expensive. \\
Consider, for instance, the following contract from \cite{thiemann_2020} that expects a prime number :\todo{State programming language?!}
\begin{lstlisting}[caption=Smart contract expecting a prime number, numbers=none, language=Solidity]
contract Example {
	function ( int p ) public {
	// assume p is prime
	...
	}
}
\end{lstlisting}

The assumption that the given integer $p$ is a prime can be expressed as an explicit assertion in predicate logic: 
\begin{equation}\label{eq:prime}
    (\forall n) (2 \le n \le \sqrt{p}) \Rightarrow (p \% n) \neq 0
\end{equation}

Checking if this property holds requires the contract to execute a loop in $\mathcal{O}(\sqrt{p})$ time and therefore generate costs linear in $\sqrt{p}$ on top of the actual contract execution, assuming computing the body of the loop takes constant time.\\
Thus it appears that we need a mechanism that allows the smart contract to make use of the computed result from an off-chain source without having to validate its validity locally with scaling costs.

\section{A distributed approach for assertion checking}
A more efficient way to solve the issue at hand is to engage the validators of the blockchain into a distributed effort to find a counterexample that disproves an assumption. If no counterexample could be found by any validator, the assumption is considered to be valid and the execution of the contract may resume. On the other hand, an identified counterexample is made public on the peer-to-peer network and thus cancels the contract execution (i.e., the transaction fails). \\
In order to find counterexamples of an assertion, the formula in \ref{eq:prime} has to be transformed to its negation:
\begin{equation}\label{eq:prime_neg}
	(\exists n) (2 \le n \le \sqrt{p}) \wedge (p \% n) = 0
\end{equation}

Each validator then checks the inverse property $(p \% n) = 0$ point-wise for some random $n$ within the given boundaries $2 \le n \le \sqrt{p}$. If a validator finds a counterexample, i.e., a value for $n$ where the reminder is $0$, it posts an objection to the network. For each involved validator the constant cost of generating one random number and calculating one division have to be paid, which is independent from $p$. \\
However, distributed assertion checking is not only applicable for parameters or properties of dynamic size. Another example given in \cite{thiemann_2020} shows a contract that expects an array of integers sorted in ascending order:

\begin{lstlisting}[caption=Smart Contract expecting a sorted array, numbers=none, language=Solidity]
contract Sorted {
  function find ( int [50] a , int v ) public {
    // assume a is sorted
  }
}
\end{lstlisting}

The assumption that the list is sorted, expressed in predicate logic, is
\begin{equation}\label{eq:sorted}
	(\forall n) (0 \leq n \le |a| - 1) \Rightarrow a[n] \leq a[n+1]
\end{equation}

Even though the assertion can be checked in a loop in $\mathcal{O}(1)$, the constant factor is not negligible and can generate unreasonable costs. Hence, we consider the negation again and ask the validators to search for counterexamples by checking a random value for $n$:

\begin{equation}\label{eq:sorted_neg}
	(\exists n) (0 \leq n \le |a| - 1) \wedge a[n] > a[n+1]
\end{equation}

Since the validators do random sampling, none of them finding a counterexample doesn't prove that the assumption is correct - the validation is only probabilistic and the reliability depends on the number of validators in the network. This corresponds to the principle of Bloom filters, where a queried element is either certainly not or possibly in a defined set \cite{blustein_bloom_2002}. In the case of assertion checking, it's the assumption that is either definitely not or maybe valid. The probability of false positives in Bloom filters is an approximate function of the filter size and the number of inserted elements, supposing an optimal number of hash functions have been implemented. Tuning these parameters is a trade-off between making the filter more reliable, that is lowering its error rate, and space efficiency \cite{blustein_bloom_2002}. The same applies, with some reservations, to distributed assertion checking: less samples keep the costs to a minimum, whereas more samples increase the probability that, if it exists, a counterexample is found. In the last example, the probability of false positives depends on the size of $a$ and the number of validators.\\
How important the former parameter is, becomes clear if we look at the worst case scenario of the same example. Assume the array is unsorted at exactly one position - the probability that the each of the $m$ validators independently check this position is given by $\frac{1}{|a|}$, and any other position by $\frac{|a|-1}{|a|}$. If the random generator chooses each value for $n$ independently from a uniform distribution, the probability that the counterexample is not detected by any validator converges to 0 if the number of validators approach infinity \cite{thiemann_2020}
\begin{equation}\label{eq:limes_validators}
	\lim_{m\to\infty} \left(\frac{|a|-1}{|a|}\right)^m = 0
\end{equation}

\todo{Ueberleitung}

\section{Structure overview}
This thesis assesses uses cases for this kind of testing, defines a language/syntax to express properties/assumptions like in the examples and explores how the mechanism can be implemented, using the Tezos blockchain and its smart contract language as platform/example. 
How the mechanism could/would be implemented in the Tezos blockchain ...
which extensions to the Michelson language and the Tezos protocol are necessary

The effectiveness of this approach is analyzed in detail (how many samples are necessary to reach a certain confidence level? which levels are appropriate?)

Analyze the costs that are incurred by checking a formula with this approach; compare it with non-distributed approach.
Both effectiveness \& cost model are used to evaluate this approach. Some alternatives are discussed. (here or in final chapter?)

Finally, it gives an outlook what still needs to be done, what can be improved. It summarizes the results so far and evaluates.

### 2021-03-10 assertions/doc/thesis-bernhardt/chapters/2-offline_design.tex
Introduction first draft

\chapter{Background}\label{chap:background}
Explain the general context of your work.
Explain mathematical background required and introduce notation.
\input{figures/background/algBackpropagation}
\input{figures/background/figTikz}

effectiveness:
smaller search spaces = less needed test runs
example sorted list -> generate 1 random number and check neighbor = many test runs to cover all of them
partition search space \& generate 2 random numbers better? -> 2 smaller search spaces. would this improve anything?

\begin{lstlisting}[numbers=none, language=Assertion]
(entrypoint (left (right (pair ( a : address) _)))
  (forall (i : int)
     (if (gt i 10)
       (assert true))))
\end{lstlisting}

### 2021-03-10 assertions/doc/thesis-bernhardt/chapters/advice.tex
Introduction first draft

\section{Advice}\label{sec:advice}

This section gives some advice how to write a thesis ranging from writing style to formatting. To be sure, ask your advisor about his/her preferences.\\
For a more complete list we recommend to read Donald Knuth's paper on mathematical writing. (At least the first paragraph). \url{http://jmlr.csail.mit.edu/reviewing-papers/knuth_mathematical_writing.pdf}

    \begin{itemize}

        \item If you use formulae pay close attention to be consistent throughout the thesis!

        \item In a thesis you never write `In [24] the data is..'. You have more space than in a paper, so write `AuthorXY et al. prepare the data... [24]'. The rule is that the text should remain grammatically correct even if the reference is erased.
          For that reason, the template uses \texttt{natbib} with style \texttt{plainnat}, which makes it much easier to stick to the rule. Most of the time the citation should be at the end of the sentence before the full stop with a no-break space. \verb|... last word~\cite{XY}.| With \texttt{natbib} you can use the \texttt{citet} command to refer to the authors' name and cite at the same time. See \url{https://www.sharelatex.com/learn/Bibliography_management_with_natbib} for more information.

        \item Get your bibtex entries from \url{https://dblp.org/}.

        \item Pay attention to comma usage, there is a big difference between English and German. `...the fact that bla...' etc.

        \item Do not write contractions like `don't ', `can't', and so on. Instead write `do not', `cannot', and so on.

        \item If an equation is at the end of a sentence, add a full stop. If it is not the end, add a comma: {$a= b + c$~~~~(1),}

        \item Avoid footnotes if possible.

        \item Use \verb|``''| for citing, not \verb|""|.
        \item Captions of tables and figures do not end with a period, unless the caption is a full sentence.
        \item Titles and headings ought to be capitalized properly. Here is a tool to help: \url{https://capitalizemytitle.com/}

        \item Check the spelling of your thesis before submitting. There are tools like \texttt{aspell} that help you find such mistakes. 
        As a spell checker cannot find grammatical errors, it does not relieve you from properly reading your thesis again and from getting comments from somebody else.
        You can find an introduction under \url{https://git.fachschaft.tf/fachschaft/aspell}.

      \item If the thesis contains graphs or other drawings consider
        using \texttt{tikz}. Do not waste you time studying its manual
        except for the introduction and some examples, instead go for
        some of the examples available on the net and adapt. For
        function graphs or diagrams consider using \texttt{pgfplots}
        or \texttt{gnuplot}.  Using latex-related tools has the
        advantage that the style is more consistent (same font,
        formatting options etc.) than with some external program.

      \item Discuss with your advisor whether to use passive voice or
        not. In most computer science papers passive voice is
        avoided. It is harder to read, more likely to produce errors,
        and most of the times less precise. Of course, there are
        situations where passive voice fits but in scientific papers
        they are rare. Compare the sentence: `We created the wheel to
        solve this.' to `The wheel was created to solve this'.  You
        don't know who did it, making it harder to understand what is
        your contribution and what is not.

        The thesis should not be written in first person singular. First person plural is generally accepted, but it is good practice to avoid the pronouns `we', `our' etc as much as possible.

    \end{itemize}

### 2021-03-10 assertions/doc/thesis-bernhardt/michelson_highlighting.tex
Introduction first draft

\usepackage{listings, xcolor}

\definecolor{verylightgray}{rgb}{.97,.97,.97}

\lstdefinelanguage{Michelson}{
	keywords=[1]{parameter, storage, code},
	keywordstyle=[1]\color{blue}\bfseries,
	keywords=[2]{address, unit, never, bool, int, nat, string, chain_id, bytes, mutez, key_hash, key, signature, timestamp,
	option, or, pair, list, set, operation, ticket, lambda, map, big_map, sapling_transaction, sapling_state, bls12_381_g1,
	bls12_381_g2, bls12_381_fr},	% types; money and time units
	keywordstyle=[2]\color{teal}\bfseries,
	identifierstyle=\color{black},
	sensitive=false,
	comment=[l]{//},
	morecomment=[s]{(*}{*)},
	commentstyle=\color{gray}\ttfamily,
	stringstyle=\color{red}\ttfamily,
	morestring=[b]',
	morestring=[b]"
}

\lstset{
	language=Michelson,
	backgroundcolor=\color{verylightgray},
	extendedchars=true,
	basicstyle=\footnotesize\ttfamily,
	showstringspaces=false,
	showspaces=false,
	numbers=left,
	numberstyle=\footnotesize,
	numbersep=9pt,
	tabsize=2,
	breaklines=true,
	showtabs=false,
	captionpos=b
}

### 2021-03-12 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
Introduction & Tezos basics

@@
 Consider, for instance, the following contract from \cite{thiemann_2020} that expects a prime number :\todo{State programming language?!}
-\begin{lstlisting}[caption=Smart contract expecting a prime number, numbers=none, language=Solidity]
+\begin{lstlisting}[caption=Smart contract expecting a prime number, numbers=none, language=Solidity, label=lst:prime]
 contract Example {
@@
 In the last example, the probability of false positives depends on the size of $a$ and the number of validators.\\
-How important the former parameter is, becomes clear if we look at the worst case scenario of the same example.
+The importance of the former parameter becomes obvious when looking at the worst case scenario of the same example.
 Assume the array is unsorted at exactly one position - the probability that the each of the $m$ validators independently check this position is given by $\frac{1}{|a|}$, and any other position by $\frac{|a|-1}{|a|}$.
@@
 
+\move{maybe to detailed? move to efficiency section}
+
 \todo{Ueberleitung}
@@
 \section{Structure overview}
+which formulas are amendable?
+costs of testing them?
+
 This thesis assesses uses cases for this kind of testing, defines a language/syntax to express properties/assumptions like in the examples and explores how the mechanism can be implemented, using the Tezos blockchain and its smart contract language as platform/example.
@@
 which extensions to the Michelson language and the Tezos protocol are necessary
+-> roadmap welche schritte es gibt
+	- language (assertion syntax)
+	- pipeline -> compile to Michelson
+	- extend Michelson language/interpreter etc.
+	- how does protocol have to be adapted
 

### 2021-03-12 assertions/doc/thesis-bernhardt/chapters/2-tezos.tex
Introduction & Tezos basics

\chapter{Tezos}
The Tezos blockchain is presented in its Whitepaper as a \enquote{generic and self-amending crypto-ledger} \cite{goodman_tezos_2014}. It uses a proof-of-stake consensus mechanism that is not only used to agree on the current state of its ledger, but also allows its stakeholders to come to a consensus about changes in the economic protocol by a voting process. These changes included in a protocol upgrade, i.e. amendment, can influence which transactions are valid on the blockchain, the payment system or even the voting process itself without risking a fork of the blockchain. Everyone owning the cryptocurrency of Tezos, called Tez, is considered a stakeholder. The Whitepaper compares the self-amending protocol to Peter Suber's game Nomic \cite{nomic}, and a similar concept was also implemented in the virtual sports league Blaseball \cite{blaseball}, which became popular during the COVID-19 pandemic. In addition to user accounts associated with a public key, Tezos supports smart contracts, which are written in the built-in language Michelson. Tezos' transaction fee system is similar to Ethereum's - it is gas-instrumented and besides a base fee, every operation and byte of storage has to be paid for. However, Tezos imposes a hard cap on the amount of gas that can be consumed per transaction, whereas Ethereum limits the gas quota only in respect to blocks \cite{wood_ethereum_2021}.\\
Compiling the Tezos source code yields five essential binaries: the node, baker, endorser, accuser and client. The node is the entity that connects to the peer-to-peer network and keeps a copy of the chain. Bakers are responsible for producing new blocks, the endorsers for signing blocks and the accusers to call out bakers or endorsers which double-sign or -endorse. The client provides a command line interface to interact with the local node through remote procedure calls (RPC).

\section{Michelson}
Michelson is a lower-level, stack-based language with a strict type-checking and supports primitive data types, like integers or strings, as well as high-level data structures such as list, maps and sum types \cite{tezos_docs_michelson}. The type system reduces the occurrence of runtime errors and ensures that only well-typed contracts are originated on the blockchain. In OCaml the typing rules are implemented using generalized algebraic data types (GADTs) \cite{tezos_docs_michelson} and thus enforced by OCaml's typechecker. \\
The concrete syntax of Michelson is called Micheline. A program is represented in Micheline nodes, which can be a constant of type integer, string or byte sequence, or an application of a primitive, given as a string keyword, to a list of nodes. For documentation, readability and additional type constraints, Michelson and Micheline also offer three types of annotations - type, variable and field or constructor annotations, which are labelled with a unique special character in Micheline. The toplevel structure of a smart contract consists of a sequence of the three primitive applications \texttt{parameter, storage} and \texttt{code}, declaring the type of the input parameter, the storage type and the actual program code. Unlike in the contracts given in the introduction, described with the syntax of Solidity, Michelson doesn't have a concept of named functions with individual input parameter types.

\todo{Citations}

\subsection{Entrypoints}
Instead of named functions, Michelson programs can have separate entry points by taking a disjunctive type as input parameter and tagging the type constructors with a "function" name. The disjunctive type is built by nesting the \texttt{or} type, which has the constructors \texttt{left} and \texttt{right}. Assume we want to implement the contract from \lstref{lst:prime} in Michelson and add another function to it, which expects a string parameter. Omitting the actual program, the contract type declaration looks as follows:
\begin{lstlisting}[language=Michelson, numbers=none]
parameter (or (int %isPrime) (string %isUpper));
storage unit;
code { ... }
\end{lstlisting}
The input type declared in the primitive application \texttt{parameter} accepts input of either type \texttt{left int}, or \texttt{right string}. By adding the field annotations \texttt{isPrime} and \texttt{isUpper} the entry points are given tags and can be called explicitly by an external transaction. In that case, parameters of type \texttt{int} or \texttt{string} are accepted and the value is automatically wrapped into the wrapped into the respective constructors. It's possible to declare a \texttt{default} entrypoint, which is called when no explicit tag is specified and is by default assigned to the root of the parameter type.

\todo{Citations}

\section{OCaml}
The Tezos blockchain itself is implemented in the functional programming language OCaml, which emphasizes expressiveness and safety \cite{ocaml_doc}. It is statically type-checked and features parametric polymorphism and type inference. Developers can define algebraic data types and selectively apply functions to them using pattern-matching. The memory management is automatically handled by a garbage collector. Another notable feature of OCaml is its well-designed module system that allows organizing code in a module hierarchy and defining functors to create parametrized modules.\\
In \cite{canou_tezos_nodate}, the developers of the Tezos blockchain emphasize the importance of safety and security and speed for implementing Tezos, which OCaml is able to ensure through its static type-system and efficient compiler. The module system allowed to encapsulate and abstract the economic protocol to make it replaceable. Furthermore, OCamls ecosystem includes many tools for formal verification, in order to prove the correctness of both the protocol and Michelson smart contracts.

\todo{Citations}

\section{Developer tools in the Tezos ecosystem}
This section describes some relevant tools and projects for developers that are part of Tezos' ecosystem.

\subsection{Tezos Libraries}
Tezos' executables and libraries are available on \texttt{opam}, which is OCamls package manager \cite{tezos_opam}. The protocol libraries of every version are released separately, thus projects can be built on the protocol of choice. Important libraries that were used in this thesis are Tezos' Micheline library providing the internal abstract syntax tree (AST) and parser of the Michelson language, as well as the protocol specific libraries containing the typechecker.

\subsection{Testing tools}
Before a new protocol is proposed to the Tezos network, it has to be thoroughly tested with system, integration and regression tests. Of course this requires a sandboxed network to simulate the real peer-to-peer network, such that also interactions between the actors of the blockchain can be tested. Tezos provides two testing frameworks for this:

\begin{itemize}
\item[Flexible Network Sandboxes (Flextesa)] With Flextesa one can configure and run a small, fully functional sandboxed test network including nodes, bakers, endorsers and accusers. Accounts can be instantiated and used to send or receive funds. Configurable are, for instance, the size of the network, the time between blocks or enabling generation of random network traffic. Networks may either be fully autonomous, baking blocks automatically, or require manual baking of blocks. It also supports interactive sessions, where the tester can interact with the blockchain using the Tezos client. Flextesa's typical use-cases are interactive testing scenarios like double-baking, the voting process or protocol amendments. The Tezos repository already provides ready-to-use scenarios for accusations. Besides testing shell or protocol code, Flextesa can also be used to test smart contracts.\cite{tezos docs}
\item[Tezt] The Tezt framework is newer than Flextesa and planned as its replacement. It can also launch the Tezos binaries as external processes and build a sandboxed test network of configurable size. Its main advantages over Flextesa are simplicity, usability and the use of events instead of polling the node.\cite{tezos_docs_tezt}
\end{itemize}

\subsection{High-level languages}
Michelson is a compilation target for various high-level languages that provide more user-friendly and intuitive way of writing smart contracts. Additionally, some of them come with development environments, testing or verification tools. The following list comprises of the three most prominent languages that compile to Michelson:

\begin{itemize}
\item[\textbf{Liquidity}] is a language with an Ocaml-like syntax, which allows using local variables instead of stack manipulations. Its module system can be used to write reusable contract code or libraries. Besides an optimizing compiler, the project also includes a decompiler to compile Michelson programs to Liquidity. \cite{liquidity}
\item[\textbf{SmartPy}] is a language available through a Python library and lets developers write contracts and tests in Python. Its developer suite includes i.a. a compiler, a simulation engine and an online editor. \cite{smartpy}
\item [\textbf{fi}] 's syntax similar to JavaScript or Ethereum's contract language Solidity. It also provides an online editor and a simulator to test against the compiled contracts. However, it seems extensions to Michelson introduced by newer protocol versions are not supported yet. \cite{https://fi-code.com/}
\end{itemize}

### 2021-03-13 assertions/doc/thesis-bernhardt/chapters/2-offline_design.tex
Offline Chapter beginnign

@@
-\chapter{Background}\label{chap:background}
-Explain the general context of your work.
-Explain mathematical background required and introduce notation.
-\input{figures/background/algBackpropagation}
-\input{figures/background/figTikz}
+\chapter{Offline Design}\label{chap:offline}
+Implementing distributed assertion checking on Tezos requires some off-chain considerations and infrastructure.
+First of all, a formal set of logical formulae, that is suitable for distributed assertion checking as described in the introduction, has to be defined.
+Given this set, section \secref{sec:examples} gives some more in-depth examples for such and analyses them regarding costs and test efficiency.
+The subsequent section describes a concrete syntax used to write assertions checking these formulae, and demonstrates how some of the previous examples are expressed with it.
+With the specifications all set, the implementation section of this chapter assesses which of the necessary operations Tezos' smart contract language already provides, which extensions are needed and how the assertions can be made executable by Tezos' virtual machine.
+
+\section{Definition of a set of formulae}\label{sec:formulae} \todo{title}
+Assertion checking becomes expensive when a data structure (such as arrays), certain data types (such as byte sequences) or a range of values are iterated.
+Of interest are thus formulae with prenex universal or existential quantifiers their set is defined as follows\footnote{Extended version of the set given in \cite{thiemann_2020}.}
+  \begin{align*}
+    t &::= \text{primitive data types (existing in the blockchain VM)} \\
+    \sigma &::= \forall \mid \exists \\
+    \Theta &::= \Phi \mid \sigma (x:t) \Theta \\
+    \Phi,\Psi &::= \neg\Phi \mid \Phi \Rightarrow \Psi \mid \Phi\wedge\Psi \mid
+    				\Phi\vee\Psi \mid \Phi \oplus \Psi \mid M \rho N \\
+    \rho &::= < \mid > \mid \le \mid \ge \mid = \mid \ne \\
+    M, N &::= x \mid c \mid M \odot N  \mid f (\overline M) \\
+    \odot &::= +\mid -\mid * \mid / \mid \% \\
+    c &::= \text{constants: numbers, strings, } \top, \bot \\
+    f &::= \text{operations (existing in the blockchain VM)}
+  \end{align*}
+
+The sets of data types and operations depend on what is supported in the virtual machines of the blockchains.
+\refsec{?} goes into more detail about what is already supported in Michelson and how the language and VM have to be extended to facilitate the assertion examples given previously and in \refsec{sec:example_formulae}.
+
+\section{Transformation}\label{sec:transformation}
+
+\section{Existential quantifier and proofs of correctness}
+lksddlkdsfk
+- forall/exists -> benefit the most. are there use cases for others? or they implement just "normal" assertion
+	-> auf forall sowie exist case genauer eingehen. (counterexample vs. proof; take text from CBF/DNF examples)
+- formal set of formulae
+
+\subsection{Interesting formulae}\label{sec:example_formulae}
+- paper
+
+- First of all some offline stuff to think about - formalize which formulas are amenable for this checking. Formalize what to do for which formulas (exists/forall/mixed) etc.
+- Grammar/language to express these formulas (still general, not protocol specific)
+	-> which operations do we need?
+	-> use the form of expose?
+	-> uses ocaml/michelson like syntax; used by other BC as well though
+- effectiveness
+- formalize the costs for checking these formulas
+
+New Section/chapter? %\section{Implementation}
+- grammar ? concrete syntax; examples from examples :D
+- Tezos specific: what does VM support? needed extensions?
+	-> compilation target -> what is the result supposed to look like?
+- Description of pipeline
+-
 

### 2021-03-14 assertions/doc/thesis-bernhardt/chapters/2-offline_design.tex
Introduction Transformation

@@
 \section{Transformation}\label{sec:transformation}
+The validators will check the input parameter for the negation of the formula.
+Both quantifiers will ultimately be represented by code that generates a random value from a domain that is stated explicitly in the formula.
+% restrict the generator to the given domains; analyze the formula and "build" the ranges/domain for each generator, s.t.
+no uninteresting/unnecessary values are generated.
+
+In some cases, however, implicit boundaries are given by the data type itself.
+List indices, for instance, are always bound to the range $0..
+size(list) - 1$ and could thus be derived from the formula without an explicit specification.
+As this deduction makes the transformation more complex, as it requires a semantic analysis of the formula, a completely explicit formula in terms of the domain is required for now.
+Depending on the virtual machine, the lower bound for indexing operations can be handled by the random generator of an appropriate predicate type.
+As an example, Michelson supports the data type \texttt{nat} representing the natural numbers, which categorically excludes all values below zero.
+
+As a conclusion, the transformation of the formula consists of the two consecutive steps
+1. Negation of the logical formula
+2. Analysing the formula and definition of the generator domains.
+
+\subsection{Negation}
+- wann wird negiert (nur innerhalb v. quantifiern?) --> stimmt gar nicht :/ Code muss wieder geändert werden
+- skip conditions
+- forall -> exists etc.
+- relational/boolean expr. normal negiert
+
+\subsection{Defining the domain of random generators}
 

### 2021-03-14 assertions/doc/thesis-bernhardt/chapters/2-offline_design.tex
Negation

--- 2021-03-13 assertions/doc/thesis-bernhardt/chapters/2-offline_design.tex
@@
 \section{Transformation}\label{sec:transformation}
+Since the validators will check the input parameter for the negation of the formula, it has to be transformed before the compilation.
+Furthermore, the formula should explicitly state the domain for each quantifier, which will have to be translated into a set of bounds that belong to the random generator representing the respective quantifier.
+These restrictions are important to avoid wasting resources  through testing values out of the relevant (or legal) scope.
+Using the example from the exposé \cite{thiemann_2020},
+
+\subsection{Negation}
+The formula is negated using the negation rules of second-order logic and applying De Morgan's laws until the negation is applied to the literals.
+Universal quantifiers become existential ones and vice versa.
+The conditions, however, are not affected by the negation, since the domain stays the same.
+This is also reflected in the rules of predicate logic - if the bounds are given as a premise in the logical formula, its negation is equivalent.
+
+\subsection{Defining the domain of random generators}
+In some cases, however, implicit boundaries are given by the data type itself.
+List indices, for instance, are always bound to the range $0..
+size(list) - 1$ and could thus be derived from the formula without an explicit specification.
+As this deduction makes the transformation more complex, as it requires a semantic analysis of the formula, a completely explicit formula in terms of the domain is required for now.
+Depending on the virtual machine, the lower bound for indexing operations can be handled by the random generator of an appropriate predicate type.
+As an example, Michelson supports the data type \texttt{nat} representing the natural numbers, which categorically excludes all values below zero.
 
 \section{Existential quantifier and proofs of correctness}
-lksddlkdsfk
+Bisher, alle examples used univeral quantification and checks for counterexamples.
 - forall/exists -> benefit the most. are there use cases for others? or they implement just "normal" assertion

### 2021-03-15 meeting-notes/2021-03-15-expose-vaccination.tex
first version

\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{mathpartir}
\usepackage{listings}
\usepackage{url}
\usepackage{xcolor}
\usepackage{tcolorbox}

\title{Expos\'{e}\\
  Proof of Vaccination on the Blockchain}
\author{Peter Thiemann}

\begin{document}
\maketitle

\section{Introduction}
\label{sec:introduction}

The world is racing towards containing the Corona virus and fighting the pandemic.
One important step in this fight is to vaccinate as many people as possible.
At some point, it is expected that certain activities (e.g., air travel, cruises, sports) are only open to vaccinated  persons. To this end, there must be a central registry for all vaccinations so that everyone can proof their vaccination status.

The goal of the thesis is to investigate whether the blockchain is a suitable technical foundation for building such a registry. At first glance, this seems to be the case because the blockchain is a global decentralized database that can be maintained by mutually untrusting communities.

\section{Outline}
\label{sec:outline}

The thesis touches on several issues in computer science and economics.

\begin{enumerate}
\item Software engineering:
  \begin{itemize}
  \item identify the actors, design a data model, and specify the
    actions. Keep the data model simple, but realistic. Apply
    domain-driven engineering if possible.
  \item The data model maintains of persons to \emph{records} of vaccination.
  \item identify the non-functional requirements: size of the personal
    certificate, time needed to create the certificate (do you get it
    when you leave the doctor, or is it sufficient to get it the next day)
  \end{itemize}

\item Economics and scalability:
  \begin{itemize}
  \item what is the cost for registering a vaccination? Some cost is
    acceptable, but it should be kept down as much as possible.
  \item what is the cost for checking if someone if vaccinated? This
    check should be cheap and it should take no longer than a few
    seconds, even for millions of vaccination records
  \item consider the datastructures required. what is the best way of
    mapping the data to the blockchain?
  \end{itemize}
\item Programming:
  \begin{itemize}
  \item build a prototype implementation consisting of smart contracts
    and web-based user interfaces.
  \item some authorization infrastructure is necessary for
    registering; this is not the key focus, so some PK infrastructure
    for digital signatures should be sufficient.
  \item Records must be verifiably personalized.
  \item  Full records may not be needed, for example, it might be
    possible to collect many records in a Merkle tree and only store
    the hash on the blockchain. The certificate would contain a proof
    of containment of the record in the Merkle tree.
  \item optional: which blockchain platform is most suitable? Ethereum
    seems like the standard. Tezos? Permissioned blockchains? See here
    for an overview: \url{https://www.sciencedirect.com/science/article/pii/S2405959520301909}
  \end{itemize}
\end{enumerate}

\end{document}

### 2021-03-18 assertions/doc/thesis-bernhardt/chapters/2-offline_design.tex
Use Case chapter

@@
 Implementing distributed assertion checking on Tezos requires some off-chain considerations and infrastructure.
-First of all, a formal set of logical formulae, that is suitable for distributed assertion checking as described in the introduction, has to be defined.
-Given this set, section \secref{sec:examples} gives some more in-depth examples for such and analyses them regarding costs and test efficiency.
-The subsequent section describes a concrete syntax used to write assertions checking these formulae, and demonstrates how some of the previous examples are expressed with it.
-With the specifications all set, the implementation section of this chapter assesses which of the necessary operations Tezos' smart contract language already provides, which extensions are needed and how the assertions can be made executable by Tezos' virtual machine.
+The previous chapter defined a formal set of logical formulae amenable for this approach and gave some in-depth examples.
+\todo{Allgemeine Beschreibung was das Ziel des Chapters ist -> wir müssen aus einer Formula nun einen Contract erstellen, der einen assertion check ausführen kann.
+-> Define a syntax and a compilation pipeline that outputs a Michelson sc that can be originated.}
 
-\section{Definition of a set of formulae}\label{sec:formulae} \todo{title}
-Assertion checking becomes expensive when a data structure (such as arrays), certain data types (such as byte sequences) or a range of values are iterated.
-Of interest are thus formulae with prenex universal or existential quantifiers their set is defined as follows\footnote{Extended version of the set given in \cite{thiemann_2020}.}
-  \begin{align*}
-    t &::= \text{primitive data types (existing in the blockchain VM)} \\
-    \sigma &::= \forall \mid \exists \\
-    \Theta &::= \Phi \mid \sigma (x:t) \Theta \\
-    \Phi,\Psi &::= \neg\Phi \mid \Phi \Rightarrow \Psi \mid \Phi\wedge\Psi \mid
-    				\Phi\vee\Psi \mid \Phi \oplus \Psi \mid M \rho N \\
-    \rho &::= < \mid > \mid \le \mid \ge \mid = \mid \ne \\
-    M, N &::= x \mid c \mid M \odot N  \mid f (\overline M) \\
-    \odot &::= +\mid -\mid * \mid / \mid \% \\
-    c &::= \text{constants: numbers, strings, } \top, \bot \\
-    f &::= \text{operations (existing in the blockchain VM)}
-  \end{align*}
+A concrete syntax for writing assertions on these formulae is described in the subsequent section.
+It will also show how some of the previously given examples are expressed in that syntax.
+The transformation of the original assertions to assertions that check for counterexamples or proofs is formalized in \secref{sec:transformation}.
+\todo{rest}
 
-The sets of data types and operations depend on what is supported in the virtual machines of the blockchains.
-\refsec{?} goes into more detail about what is already supported in Michelson and how the language and VM have to be extended to facilitate the assertion examples given previously and in \refsec{sec:example_formulae}.
+\section{Assertion syntax}
+
+Argument against if/else conditions outside of assert():
+In order to take advantage of this, the assertion syntax would need to be able to create different generators for different conditions.
+Currently, we only allow \texttt{if-else} instructions inside an \texttt{assertion} expression; this use-case could be an argument to lift that restriction and allow contracts like this:
+%\lstinputlisting[caption=Assertion contract with conditional generators, label={lst:coprime}]{listings/coprime.tza}
+
+However, this will make the transformation more involved, as the bounds cannot simply be merged with the generator anymore.
 
@@
 Since the validators will check the input parameter for the negation of the formula, it has to be transformed before the compilation.
-Furthermore, the formula should explicitly state the domain for each quantifier, which will have to be translated into a set of bounds that belong to the random generator representing the respective quantifier.
-These restrictions are important to avoid wasting resources  through testing values out of the relevant (or legal) scope.
-Using the example from the exposé \cite{thiemann_2020},
+Furthermore, the formula should explicitly state the domain for each quantifier, which will have to be translated into a set of bounds that belong to the respective random generator.
+These restrictions are important in order to avoid wasting resources through testing values out of the relevant (or legal) scope.
 
@@
 The formula is negated using the negation rules of second-order logic and applying De Morgan's laws until the negation is applied to the literals.
-Universal quantifiers become existential ones and vice versa.
-The conditions, however, are not affected by the negation, since the domain stays the same.
-This is also reflected in the rules of predicate logic - if the bounds are given as a premise in the logical formula, its negation is equivalent.
+Negating universal quantification is equivalent to an existential quantification of its negated body (and vice versa): $\neg \forall x P(x) \equiv \exists x \neg P(x)$.
+The domain restrictions are not affected by the negation - the domain of the statement remains the same.
+This is also reflected in the rules of predicate logic, if the domain restrictions are given as a premise in the logical formula: $\neg (p \Rightarrow q) \equiv p \Rightarrow \neg q $.
+
+% Nested forall -> exists and reverse: no negation?
 
 \subsection{Defining the domain of random generators}
-In some cases, however, implicit boundaries are given by the data type itself.
+In order to assign each explicit bound to the respective quantifier, the formula has be skimmed for atomic constraints that contain bound variables.
+They're then moved and assigned to the quantifier that bounds the variable.
+If the constraint contains more than one, it is assigned to the quantifier with the highest depth in the order of quantifiers.
+\\
+Consider a variation of the example given in \eqref{eq:sorted}, a formula checking if a given list is sorted:
+\begin{equation}\label{eq:sorted_v2}
+	(\forall n : int)(\forall m : int) (0 \leq n \le m < |a|) \Rightarrow a[n] \leq a[m]
+\end{equation}
+The premise can be considered as a conjunction of the four constraints $0 \leq n$, $n < |a| $, $n \le m$ and $m < |a|$.
+Applying the rules given above after negating the formula, the constraints are assigned to the quantifiers as follows:
+\begin{equation}\label{eq:sorted_v2_bounds}
+	(\exists n : int, 0 \leq n \wedge n < |a|)(\exists m : int, m > n \wedge m < |a|) \text{ } a[n] > a[m]
+\end{equation}
+Ultimately, the quantifiers are then translated to the corresponding random generators shown in \lstref{lst:rand}.
+\begin{lstlisting}[label=lst:rand]
+n = random(0, size(list))
+m = random(n, size(list))
+\end{lstlisting}
+
+While conjunctions can be handled easily, other operators make it more difficult to derive efficient random generators. Consider the following constraints:
+\begin{align}
+(\forall n : int) (n < 10 \lor n > 20) ... \\
+(\forall n : int) (n \ne 10) ... \\
+(\forall n : int) (n = 10) ... 
+\end{align}
+
+Both constraints 1) and 2) complicate restricting the random generator in several ways.
+Firstly, they separate the domain into two disjoint sub-domains, which requires defining a random generator for each range and another one to decide which one is called.
+Secondly, the operands of a disjunction cannot be considered separately when more than one bound variable is involved.
+For the predicate whose random generator is executed first, the domain restriction is optional, while the generation of the following random values depend on the previous result.
+As the complexity of building efficient random generators in these cases is relatively high, restrictions formulated with these operators are kept, for now, as part of the assertion code rather than used as constraints for the generators.
+Consequently, some validators may generate irrelevant values when checking the assertion.
+Depending on the size of the gap between the sub-domains, this can significantly decrease the reliability of this kind of assertion checking.
+Constraint 3) effectively makes the quantifier, which binds $n$, obsolete.
+Adding this constraint to the respective generator will at least not affect the reliability, but a future improvement could be to optimize the assertion by replacing all occurrences of the bound variable with the assigned value and removing the quantification.\\
+
+In some cases, boundaries are given implicitly by data types.
 List indices, for instance, are always bound to the range $0..
@@
 As an example, Michelson supports the data type \texttt{nat} representing the natural numbers, which categorically excludes all values below zero.
-
-\section{Existential quantifier and proofs of correctness}
-Bisher, alle examples used univeral quantification and checks for counterexamples.
-- forall/exists -> benefit the most. are there use cases for others? or they implement just "normal" assertion
-	-> auf forall sowie exist case genauer eingehen. (counterexample vs. proof; take text from CBF/DNF examples)
-- formal set of formulae
+Developers aware of this can exploit this and, for instance, abbreviate \eqref{eq:sorted_v2} with the following formula:
+\begin{equation}\label{eq:sorted_v2_abbr}
+	(\forall n : nat)(\forall m : nat) (n \le m < |a|) \Rightarrow a[n] \leq a[m]
+\end{equation}
 

### 2021-03-18 assertions/doc/thesis-bernhardt/chapters/3-offline_design_tezos.tex
Use Case chapter

\chapter{Approach}\label{chap:approach}

With the specifications all set, the implementation section of this chapter assesses which of the necessary operations Tezos' smart contract language already provides, which extensions are needed and how the assertions can be made executable by Tezos' virtual machine.

### 2021-03-19 assertions/doc/thesis-bernhardt/chapters/2-offline_design.tex
Use case chapter almost finished

@@
 The previous chapter defined a formal set of logical formulae amenable for this approach and gave some in-depth examples.
-\todo{Allgemeine Beschreibung was das Ziel des Chapters ist -> wir müssen aus einer Formula nun einen Contract erstellen, der einen assertion check ausführen kann.
--> Define a syntax and a compilation pipeline that outputs a Michelson sc that can be originated.}
-
-A concrete syntax for writing assertions on these formulae is described in the subsequent section.
-It will also show how some of the previously given examples are expressed in that syntax.
+As was stated before, the proposed implementation in the following chapters is restricted to formulas of predicate logic using universal quantification.\\
+The goal of the offline infrastructure is to provide a syntax for stating an assertion that checks a logical formula.
+Furthermore, these assertions need to be transformed, s.t.
+they check for counterexamples, and compiled into Michelson code to extend the actual smart contract.
+This chapter describes a concrete syntax for writing these assertions, and shows how some of the previously given examples are expressed using it.
 The transformation of the original assertions to assertions that check for counterexamples or proofs is formalized in \secref{sec:transformation}.

### 2021-03-19 assertions/doc/thesis-bernhardt/chapters/2-use_cases.tex
Use case chapter almost finished

\chapter{Problem Definition and Use-cases}\label{chap:use_cases}
The introduction argued that validating properties on input parameters becomes expensive when a data structure (such as arrays), certain data types (such as byte sequences) or a range of values have to be iterated. It showed examples for such properties and identified logical formulas containing universal quantification as amenable for distributed assertion checking. As a matter of fact, the same is also valid for existential quantification, even though its negation has a different notion than that of its universal counterpart. The difference between the two is addressed later in this chapter. \\
The following section formally defines a set of applicable logical formulas for the first implementation of this approach. Given this set, section \secref{sec:examples} gives some more in-depth examples including cost analyses.

\section{Definition of a set of logical formulae}\label{sec:formulae}
\begin{align*}
    t &::= \text{primitive data types (existing in the blockchain VM)} \\
    \sigma &::= \forall \mid \exists \\
    \Theta &::= \Phi \mid \sigma (x:t) \Theta \\
    \Phi,\Psi &::= \neg\Phi \mid \Phi \Rightarrow \Psi \mid \Phi\wedge\Psi \mid
    				\Phi\vee\Psi \mid \Phi \oplus \Psi \mid M \rho N \\
    \rho &::= < \mid > \mid \le \mid \ge \mid = \mid \ne \\
    M, N &::= x \mid c \mid M \odot N  \mid f (\overline M) \\
    \odot &::= +\mid -\mid * \mid / \mid \% \\
    c &::= \text{constants: numbers, strings, } \top, \bot \\
    f &::= \text{operations (existing in the blockchain VM)}
\end{align*}
\begingroup\vspace*{-\baselineskip}
\captionof{figure}{Set of logical formulas amenable to distributed assertion checking (extension of set given in \cite{thiemann_2020})}
\vspace*{\baselineskip}\endgroup

The sets of supported data types $t$ and operations $f$ depend on what is supported in the virtual machines of the blockchains. \secref{lala} goes into more detail about what is already supported in Michelson and how the language and VM have to be extended to facilitate the assertion examples given previously and in \secref{sec:example_formulae}.

\section{Examples}\label{sec:examples}\todo{title}
The following examples are excerpts from \cite{bernhardt_veigel_2020}, which contains a more comprehensive collection of use-cases. A assessment of

\subsection{Two numbers are coprime}\label{subsec:coprime}
The greatest common divisor ($gcd$) of two non-zero integers $a$ and $b$ is the largest integer that divides both evenly \cite{hardy2008introduction}. A more specific $gcd$-problem is finding two numbers which are coprime, that is their greatest common divisor is one, i.e., $gcd(a, b) = 1$ \cite{hardy2008introduction}. To verify if two numbers are coprime, it has to be checked that there exists no $gcd > 1$ , which can be expressed in the following propositional formula:
\begin{equation}\label{eq:coprime-universial}
    (\forall n : int) (2 \le n \le \min(a,b)) \Rightarrow \neg((a \mathbin{\%} n) = 0 \land (b \mathbin{\%} n) = 0)
\end{equation}
Assuming constant time for calculating the two remainders, checking whether two numbers satisfy this property takes linear time, i.e. $\mathcal{O}(n)$, and depends on the size of the smaller number. Applying distributed assertion checking instead, we consider its negation to find a counterexample:
\begin{equation}\label{eq:coprime-existential}
    (\exists n : int) (2 \le n \le \min(a,b)) \land (a \mathbin{\%} n) = 0 \land (b \mathbin{\%} n) = 0
\end{equation}

\subsection{Heap property}
Heaps are data structures based on trees and can appear in two varieties: min and max heaps. Both can be represented as binary trees and have to satisfy the heap property \cite{dict_heap}. In a max heap, any given node has a lower or equal value than the value of its parent. In a min heap, the value is greater or equal than that of its parent \cite{dict_heap_property}. Binary heaps are often implemented as an array, with the root of the tree stored at index 0. The relatives of a node \texttt{k} can be accessed as follows \cite{dict_binary_heap}:
\begin{lstlisting}[language=Solidity, numbers=none, caption=Access a binary heap in array representation]
heap_array[(k-1)/2] // Get parent of node k
heap_array[(k*2)+1] // Get left child of node k
heap_array[(k*2)+2] // Get right child of node k
\end{lstlisting}

The min heap property, for instance, for a binary heap represented in an array $a$, can be expressed in predicate logic with the following formula:
\begin{equation}\label{eq:heap-unversial}
  (\forall k : int) (1 \le k < |a|) \Rightarrow a[\lfloor(k-1)/2)\rfloor] \le a[k]
\end{equation}

The time complexity of checking if $a$ satisfies the heap property is $\mathcal{O}(n)$ in the size of the array if it is dynamically sized, or $\mathcal{O}(1)$ when statically sized. Solidity, for instance, supports both types \cite{solidity_docs}. Similarly to the previous examples, the property of the array is validated by checking for counterexamples by considering its negation:
\begin{equation}\label{eq:heap-unversial-neg}
  (\exists k : int) (1 \le k \le |a|) \land a[\lfloor(k-1)/2)\rfloor] > a[k]
\end{equation}

\section{Existential quantifier and proofs of validity}
The examples given so far in this thesis used universal quantification and required a search for counterexamples in order to check if some assumption about an input parameter is true. However, the same cannot be applied to existential quantifiers. Consider a contract expecting a string $e$ and a list $l$ of strings that contains $e$ at least once. The assumption that \texttt{l} contains \texttt{e} can be expressed by
\begin{equation}\label{eq:contains}
	(\exists n : int) (0 \leq n < |l|) \Rightarrow l[n] = e
\end{equation}
and its negation is 
\begin{equation}\label{eq:contains_neg}
	(\forall n : int) (0 \leq n < |l|) \Rightarrow l[n] \ne e
\end{equation}

If the assertion fails for a random value of $n$, it does not produce a counterexample, but rather it produces a proof for the validity of the assumption. In that case, the validator finding such a proof should publish an approval instead of a veto to the network and the normal execution of the contract can proceed. Hence, there must be two different modi of assertion checking that implement different
types of assertions (proofs need assertions that don't abort the program).
\todo{Refer to a chapter where this is discussed further?}

\section{Nested quantification}
The previous example showed that universal and existential quantification have to be handled differently. However, other special cases caused by nested quantification have to be considered as well. Trivial cases of nested quantification are nesting of the same quantifiers, e.g. $(\forall i, j)$. They can be handled by generating a random value for each predicate and checking for a counterexample or proof respectively. It becomes less trivial though, if the nesting contains both universal and existential quantifiers. This section examines the the case of $\exists i, \forall j$ on the basis of a contract that expects a solution for a boolean satisfiability problem (SAT). Another instance of this use-case is also used to show that properties expressed with the nesting $\forall i, \exists j$ cannot be checked with the proposed approach for distributed assertion checking.

\subsection{Boolean satisfiability problem}\label{sec:sat}
Instances of SAT problems consist of a formula $F$ in propositional logic, and determine if there exists a variable assignment $\mathcal{A}$ to the values $true$ or $false$, s.t. the formula is satisfied ($\mathcal{A}(F) = 1$) \cite{Biere2009}. Modern SAT-solvers expect $F$ to be in conjunctive normal form (CNF), i.e., a conjunction of a set of clauses, where clauses are disjunctions of variables or their negations (called literals) \cite{cnf_math_encycl}. Verifying whether a given assignment satisfies the formula takes $\mathcal{O}(n*m)$, where $n$ is the number of clauses and $m$ the number of variables (in the worst case, every variable is present as a literal in each clause). In the case of k-SAT problems, where each clause contains at most k literals \cite{Biere2009}, the complexity is reduced to $\mathcal{O}(n)$.

\subsubsection{Encoding of variables, literals and clauses}
A SAT problem could be represented as a list of clauses $c$ and a variable assignment $a$. To avoid having to handle the variables and their literals as strings and thus optimize runtime and memory consumption, an encoding scheme taken from this blogpost\cite{sabablog} is used: \\
Variables are encoded by a unique number starting from $0$ to $n-1$, where $n$ is the total number of variables. The positive and negative literals of a variable with id $x$ are encoded by the function
\begin{align*}
encode(x) =
\begin{cases}
  $2x$  & \text{if x is present as a positive literal}\\
  $2x+1$ & \text{if x is present as a negated literal}\\
\end{cases}   
\end{align*}

Consequently, checking whether a literal $y$ is positive or negative is a simple bit-wise $AND$ operation:
\begin{align*}
\texttt{isPositive(y) = y \& 1 == 0}
\end{align*}

As already mentioned, $F$ can be represented as a list of clauses, and each clause in turn can be represented as a list of literals. Consider the following boolean formula and variable assignment:
\begin{align*}
F = (A \vee B) \wedge (B \vee \neg C) \text{, } \mathcal{A} = \{A \rightarrow false, B \rightarrow true, C \rightarrow false\}
\end{align*}

Following the encoding of variables given above, the list of variables $v=[A,B,C]$ occurring in $F$ is encoded as $v_{enc} = [0,1,2]$. $F$ is thus represented by the encoding $F_{enc} = [[0,2],[2,5]]$. Since the encoding of variables corresponds to their index in the list of variables, $\mathcal{A}$ can be passed as a list of booleans that maintains the same order of variables: $\mathcal{A}_{enc} = [False, True, False]$. If the blockchains VM supports a respective data type, $\mathcal{A}$ can alternatively be represented with a more efficient bitarray. Lastly, the variable encoding $x$ of a literal $y$ is obtained by dividing its encoding by two, which corresponds to a bit-wise shift to the right:
\begin{align*}
\texttt{decode(y) = y >> 1}
\end{align*}

\subsection{Satisfiability in predicate logic - DNF}\label{sec:dnf}
In opposition to the statement that modern SAT solvers expect $F$ to be in CNF, consider a contract that expects a SAT problem in disjunctive normal form (DNF) and a proposed assignment, both encoded as described above. A boolean formula in DNF is a disjunction of conjunctions \cite{dnf_math_encycl}. Assuming that $F$ is a k-SAT instance, the assumption that $\mathcal{A}$ satisfies $F$ can be expressed in predicate logic as follows:
\begin{gather*}\label{eq:dnf_sat}
\begin{aligned}
(\exists i : int, \forall j : int) (0 \leq i < |F|) \wedge (0 \leq j < k) &\Rightarrow ((isPositive(F[i][j]) \wedge \mathcal{A}[decode(F[i][j])]) \\
&\vee (\neg isPositive(F[i][j]) \wedge \neg \mathcal{A}[decode(F[i][j])])))
\end{aligned}
\end{gather*}
With single quantification, we so far considered the negation of the formula in order to identify counterexamples (or proofs). However, by checking some literal in some clause, the validator cannot make a statement about the validity of the property, as the clauses have to be examined as a whole in order to verify that the conjunction evaluates to true. Consequently, the distribution can only take place on the level of clauses, but not on the level of literals. Each validator thus checks all literals of one random clause and produces a proof of validity if all of them satisfy the property. This implies that the formula does not have to be negated. \\
Besides a distinct transformation, this case also has to be handled differently during the compilation process; instead of translating both quantifiers into a random generator, the universal quantifier has to be translated into a loop, cf. \lstref{lst:rand_loop}.
\begin{lstlisting}[label=lst:rand_loop]
i = random(0, size(F))
for (j : [0..k)):
	check(...)
\end{lstlisting}

Concerning the costs of checking such a formula, it's obvious that loops consume more gas than checking single elements. In the case of k-SAT problems with small values for $k$, the constant time factor for checking a clause might still be considered acceptable.

\subsection{Satisfiability in predicate logic - CNF}
Unfortunately, the same cannot be applied for the reverse quantification nesting. Consider the same contract, but instead of expecting $F$ in DNF, it expects it to be in CNF. The domain restrictions and open formula remain the same, but the quantifiers are in reverse order:
\begin{gather*}\label{eq:cnf_sat}
\begin{aligned}
(\forall i : int, \exists j : int) (0 \leq i < |F|) \wedge (0 \leq j < k) &\Rightarrow ((isPositive(F[i][j]) \wedge \mathcal{A}[decode(F[i][j])]) \\
&\vee (\neg isPositive(F[i][j]) \wedge \neg \mathcal{A}[decode(F[i][j])])))
\end{aligned}
\end{gather*}

Again, the validator has to check the whole clause in order to know whether it evaluates to true. Due to existential quantification, however, the literals in the clauses cannot be checked independent of each other. A single literal evaluating to false does not make the whole clause evaluating to false. Although technically possible, it requires a more sophisticated compiler that translates this nesting into the following code structure:
\begin{lstlisting}[label=lst:rand_loop_dependent]
i = random(0, size(F))
for (j : [0..k)):
	if check(...):
		assert(true)
assert(false)
\end{lstlisting}

\subsection{Further nesting}
Nesting is, of course, not limited to two quantifiers, but can contain many of them. Generally, formulas containing no quantification alterations benefit the most from distributed assertion checking, as each quantifier can be translated into a random generator. On the other hand, formulas with a quantifier alteration early in the order of quantifiers benefit the least. Starting from the first alteration, the quantifiers are translated to loops.\\
To substantiate this argument, consider a two variations of a contract that expect a list of boolean formulas in DNF, and an assignment $\mathcal{A}$. The first one checks, whether $\mathcal{A}$ satisfies at least one $F$, the other one checks if all $F$ are satisfied. This can be expressed by nesting quantifications as follows: 
\begin{itemize}
\item $\exists f \exists i \forall j$
\item $\forall f \exists i \forall j$
\end{itemize}
In the first case, each validator can pick a random clause in a random $F$ and check, if all literals evaluate to true. In the second case, the validators have to find a counterexample, namely a clause that is not satisfied by \mathcal{A}. Checking a random clause in isolation cannot disprove the satisfiability, hence the validator has to check all clauses.

\subsection{Restriction of use cases} %name?
The examples given in this chapter have shown that, depending on the type and order of quantification, not all properties can be checked in the same way and need different modi of assertion checking. This increases the complexity and requirements for a implementation of this approach; therefore, for a first iteration, this thesis focuses on providing the fundamentals and implementation for assertions using universal quantification.
\todo{Refer to section where proofs are picked up again?}

\section{Cost analysis} \todo{this}
%diagram cost increase?
%experiment: write Liquidity contract w. 1 loop and 1 single execution * loop size

### 2021-03-19 assertions/doc/thesis-bernhardt/chapters/3-offline_design_tezos.tex
Use case chapter almost finished

@@
 
+- Vorschlag von HA: geht so nur für counterexamples.
+- Case Proof-modus: some approval message has to be send actively if no assertion failed.
+	-> check if transaction fails? würde so ein mechanismus gehen? call case contracts n times. nach n times wird contract aber nicht aufgerufen
+	-> oder: case contracts callen parent wenn property check successful; nicht möglich, da dann manager contract nichts davon weiß
+
 With the specifications all set, the implementation section of this chapter assesses which of the necessary operations Tezos' smart contract language already provides, which extensions are needed and how the assertions can be made executable by Tezos' virtual machine.

### 2021-03-19 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
Offline Chapter beginnign
Started rework of Offline design

@@
 \\
-Consider, for instance, the following contract from \cite{thiemann_2020} that expects a prime number :\todo{State programming language?!}
+Consider, for instance, the following contract from \cite{thiemann_2020} that expects a prime number: \todo{State programming language?!}
 \begin{lstlisting}[caption=Smart contract expecting a prime number, numbers=none, language=Solidity, label=lst:prime]
@@
 
-\begin{lstlisting}[caption=Smart Contract expecting a sorted array, numbers=none, language=Solidity]
+\begin{lstlisting}[caption=Smart Contract expecting a sorted array, numbers=none, language=Solidity, label=lst:sorted]
 contract Sorted {
@@
 \begin{equation}\label{eq:sorted}
-	(\forall n) (0 \leq n \le |a| - 1) \Rightarrow a[n] \leq a[n+1]
+	(\forall n) (0 \leq n < |a| - 1) \Rightarrow a[n] \leq a[n+1]
 \end{equation}
@@
 \begin{equation}\label{eq:sorted_neg}
-	(\exists n) (0 \leq n \le |a| - 1) \wedge a[n] > a[n+1]
+	(\exists n) (0 \leq n < |a| - 1) \wedge a[n] > a[n+1]
 \end{equation}
@@
 
-\move{maybe to detailed? move to efficiency section}
+\move{maybe too detailed? move to efficiency section}
 

### 2021-03-19 assertions/doc/thesis-bernhardt/chapters/2-offline_design.tex
Started rework of Offline design

--- 2021-03-18 assertions/doc/thesis-bernhardt/chapters/2-offline_design.tex
@@
-\chapter{Offline Design}\label{chap:offline}
-Implementing distributed assertion checking on Tezos requires some off-chain considerations and infrastructure.
+\externaldocument{1-introduction}
+
+\chapter{Generic Offline Design}\label{chap:offline}
+The implementation of distributed assertion checking on any blockchain requires some off-chain considerations and infrastructure.
 The previous chapter defined a formal set of logical formulae amenable for this approach and gave some in-depth examples.
-\todo{Allgemeine Beschreibung was das Ziel des Chapters ist -> wir müssen aus einer Formula nun einen Contract erstellen, der einen assertion check ausführen kann.
--> Define a syntax and a compilation pipeline that outputs a Michelson sc that can be originated.}
-
-A concrete syntax for writing assertions on these formulae is described in the subsequent section.
-It will also show how some of the previously given examples are expressed in that syntax.
-The transformation of the original assertions to assertions that check for counterexamples or proofs is formalized in \secref{sec:transformation}.
-\todo{rest}
+As was stated before, the proposed implementation in the following chapters is, for the most part, restricted to formulas of predicate logic using universal quantification.\\
+The purpose of the offline infrastructure is to provide a syntax for stating assertions that check logical formulas, as well as a toolchain to compile these assertions into code that can be originated on the target blockchain.
+Depending on the individual solution for the respective blockchain, this can either be the original contract extended with the assertion code, or separate code that extends the contract in some other way.
+This chapter describes the generic part of the offline design, which corresponds to the front-end of the compilation pipeline shown in \figref{fig:pipeline_generic}.
+As a start, \secref{sec:syntax} describes the concrete syntax for writing assertions and shows how it expresses some of the previously given examples.
+The transformation of the original assertions to assertions that check for counterexamples is formalized in \secref{sec:transformation} \todo{how to handle proofs}.
+Lastly, \secref{sec:effectiveness} analyses the reliability of distributed assertion checking.
 
 \section{Assertion syntax}
+The assertion syntax is described in two versions by the EBNF grammars shown in appendix \ref{apx:grammar}.
+One version implements a prefix and the other one an infix notation.
+The pipeline currently supports the prefix notation with mandatory parentheses to avoid the need of handling operator precedences.
+To avoid context switches (at least for developers on Tezos), the assertion syntax references those of OCaml and Michelson.\\
+A file containing assertions (henceforth called `assertion contract') contains at least one assertion for some function or entrypoint of the original contract (henceforth called `parent contract').
+An assertion begins with a signature consisting of an optional tag followed by a parameter type declaration.
+The tag can be used for documentation, but may sometimes be needed to indicate to which function of the parent contract the assertion is assigned.
+The body is an (optional) nesting of quantifiers and conditions around exactly one assertion.
+Conditionals can be used to restrict the quantification domains or for some other constraints.
+For completeness, the existential quantifier is already included in the grammar, however the current version of the pipeline will reject any assertions containing it.\\
+Consider a variation of the formula in predicate logic that checks whether a given list is sorted in ascending order:
+\begin{equation}\label{eq:sorted_v2}
+	(\forall n : int)(\forall m : int) (0 \leq n < m < |a|) \Rightarrow a[n] \leq a[m]
+\end{equation}
+A respective assertion that checks this property for the parent contract from \lstref{lst:sorted} could be expressed as follows:
+\begin{lstlisting}[language=Assertion]
+(entrypoint %find (a : (list int))
+  (forall (n : int)
+    (forall (m : int)
+      (if (le 0 n)
+        (if (lt n m)
+          (if (lt n (size a))
+            (assert (le (nth a n) (nth a m)))))))))
+\end{lstlisting}
 
-Argument against if/else conditions outside of assert():
-In order to take advantage of this, the assertion syntax would need to be able to create different generators for different conditions.
+\subsection{Extensions}
+% possible extensions: variables, user defined functions
+
+%Argument against if/else conditions outside of assert():
+%In order to take advantage of this, the assertion syntax would need to be able to create different generators for different conditions.
 Currently, we only allow \texttt{if-else} instructions inside an \texttt{assertion} expression; this use-case could be an argument to lift that restriction and allow contracts like this:
 %\lstinputlisting[caption=Assertion contract with conditional generators, label={lst:coprime}]{listings/coprime.tza}
-
-However, this will make the transformation more involved, as the bounds cannot simply be merged with the generator anymore.
+%However, this will make the transformation more involved, as the bounds cannot simply be merged with the generator anymore.
 
@@
 \end{equation}
+\todo{variation given above. refer to that}
+
 The premise can be considered as a conjunction of the four constraints $0 \leq n$, $n < |a| $, $n \le m$ and $m < |a|$.
@@
 
-\subsection{Interesting formulae}\label{sec:example_formulae}
-- paper
-
-- First of all some offline stuff to think about - formalize which formulas are amenable for this checking. Formalize what to do for which formulas (exists/forall/mixed) etc.
-- Grammar/language to express these formulas (still general, not protocol specific)
-	-> which operations do we need?
-	-> use the form of expose?
-	-> uses ocaml/michelson like syntax; used by other BC as well though
-- effectiveness
-- formalize the costs for checking these formulas
-
 New Section/chapter? %\section{Implementation}

### 2021-03-19 assertions/doc/thesis-bernhardt/chapters/appendix.tex
Started rework of Offline design

\appendix
\chapter{Assertion Grammar in EBNF}\label{apx:grammar}
The following two versions of the grammar implement the prefix and infix notations for the assertion syntax. 
\todo{Rename mutez}

\section{Prefix notation}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=,
				 caption=Assertion grammar with prefix notation]{../grammar/assertion_grammar_prefix.txt}

\section{Infix notation}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=,
				 caption=Assertion grammar with infix notation]{../grammar/assertion_grammar_infix.txt}

### 2021-03-20 assertions/doc/thesis-bernhardt/chapters/2-offline_design.tex
Offline Design - Effectiveness

@@
 For completeness, the existential quantifier is already included in the grammar, however the current version of the pipeline will reject any assertions containing it.\\
+In order to make the front-end generic, the assertion grammar constitutes a union of operations and types for the target languages.
+This also allows the transformation to be oblivious of the target platform and be identical for all backends.
+The current version of the grammar recognizes all types present in the Tezos VM and a subset of operations that Michelson provides.
+Responsible for rejecting any assertions containing unsupported types or operations are the respective backends.
+
+\subsection{Assertion example}
 Consider a variation of the formula in predicate logic that checks whether a given list is sorted in ascending order:
@@
 A respective assertion that checks this property for the parent contract from \lstref{lst:sorted} could be expressed as follows:
-\begin{lstlisting}[language=Assertion]
-(entrypoint %find (a : (list int))
-  (forall (n : int)
-    (forall (m : int)
-      (if (le 0 n)
-        (if (lt n m)
-          (if (lt n (size a))
-            (assert (le (nth a n) (nth a m)))))))))
-\end{lstlisting}
+\lstinputlisting[caption=Assertion checking if a list is sorted, language=Assertion, label={lst:sorted_assertion}]{listings/sorted.tza}
 
 \subsection{Extensions}
-% possible extensions: variables, user defined functions
-
-%Argument against if/else conditions outside of assert():
-%In order to take advantage of this, the assertion syntax would need to be able to create different generators for different conditions.
-Currently, we only allow \texttt{if-else} instructions inside an \texttt{assertion} expression; this use-case could be an argument to lift that restriction and allow contracts like this:
-%\lstinputlisting[caption=Assertion contract with conditional generators, label={lst:coprime}]{listings/coprime.tza}
-%However, this will make the transformation more involved, as the bounds cannot simply be merged with the generator anymore.
+In future iterations, the assertion syntax could be extended with some more features to improve usability and readability:
+\begin{itemize}
+\item \textbf{Local variables} to store, reuse and denominate computed values
+\item \textbf{User-defined functions} to extract whole routines that can be reused in a single or even many assertion contracts, if defined as a module.
+\item \textbf{if-else conditions} to modify the domains of quantification if certain conditions hold.
+The assertion that checks whether two numbers are relatively prime (discussed in \secref{sec:coprime}) is a good use-case for this feature in several ways.
+Firstly, the minimum of the given number has to be determined, however the \texttt{min}-function might not be supported as a built-in function by the target language (Tezos, for instance, does not support it).
+A solution for that could be to implement two branches in the program to handle each case.
+Secondly, if the greater of the two numbers is not evenly divided by the smaller one, the formula can be optimized by reducing the quantification domain by half to $(2 \le n \le \lfloor \frac{min(a,b)}{2} \rfloor)$, as a number cannot be evenly divided by any number between itself and its half \cite{bernhardt_veigel_2020}.
+With a syntax supporting a \texttt{if-else} control structure, the respective assertion could look as follows:
+\lstinputlisting[caption=Assertion syntax with if-else structures \cite{bernhardt_veigel_2020}, language=Assertion, label={lst:coprime}]{listings/coprime_ifelse.tza}
+This feature is not included in the current version, because conditional domain restrictions make the translation from quantifiers to random generators or loops more complex.
+Aside from that, without the feature of variables and user-defined functions, the code is inflated significantly, thus causing increased origination cost.
+\end{itemize}
 
 \section{Transformation}\label{sec:transformation}
-Since the validators will check the input parameter for the negation of the formula, it has to be transformed before the compilation.
+Since the validators will check the input parameter for the negation of the formula, it has to be transformed before compilation.
 Furthermore, the formula should explicitly state the domain for each quantifier, which will have to be translated into a set of bounds that belong to the respective random generator.
@@
 The formula is negated using the negation rules of second-order logic and applying De Morgan's laws until the negation is applied to the literals.
-Negating universal quantification is equivalent to an existential quantification of its negated body (and vice versa): $\neg \forall x P(x) \equiv \exists x \neg P(x)$.
+Negating universal quantification is equivalent to an existential quantification of its negated body (and vice versa): $\neg \forall x P(x) \equiv \exists x \neg P(x)$ \cite{Sundstrom2020Quantifiers}.
 The domain restrictions are not affected by the negation - the domain of the statement remains the same.
 This is also reflected in the rules of predicate logic, if the domain restrictions are given as a premise in the logical formula: $\neg (p \Rightarrow q) \equiv p \Rightarrow \neg q $.
-
-% Nested forall -> exists and reverse: no negation?
 
@@
 
-New Section/chapter? %\section{Implementation}
-- grammar ? concrete syntax; examples from examples :D
-- Tezos specific: what does VM support? needed extensions?
-	-> compilation target -> what is the result supposed to look like?
-- Description of pipeline
--
+\section{Accuracy of the approach}
+Since the proposed approach implements a probabilistic test, its accuracy as well as the costs incurred by guaranteeing a specified certainty threshold, remains to be analysed.
+The goal is to identify a formula that, given the domain of a formula in predicate logic, returns an estimate of a lower bound of samples necessary to find an existing counterexample with a probability $p$.
+From this analysis, it can be derived how effective a formula can be checked on a blockchain with $m$ validators.
+For the remainder of this chapter, the assumptions hold that the random generator picks elements independently from a uniform distribution and that there exists exactly one counterexample for the passed parameter.
+\todo{further measures for blockchains with small number of validators}
+
+\subsection{Coupon Collector Problem Analysis}
+When checking properties with probabilistic testing, the result is either definitely not satisfied, or probably satisfied.
+Thus, errors only occur as false positives.
+In order to find an existing counterexample with $p = 1$, every element in the given domain $\mathcal{D}$ has to be checked by at least one validator.
+Deterministically, this is reachable with exactly $|\mathcal{D}|$ test runs.
+This is, however, invalid for the probabilistic approach, as some validators may generate duplicate random values and leave some elements of $\mathcal{D}$ unchecked.
+\\
+In probability theory, this is known as the Coupon Collector's Problem \cite{croucher_collecting_2006}. Given $n = |\mathcal{D}|$, the probability that no duplicate elements are generated is given by
+\begin{equation*}
+    p = \prod_{i=1}^{n} \frac{i}{n}
+\end{equation*}
+As an example, the probability that all validators generate a unique random value already drops to $0.036\%$ for $n = 10$.
+Let the random variable $T$ be number of test runs executed until every element in the domain has been checked.
+The goal is to identify its expectation $E(T)$.
+To this end, the geometric probability distribution is applied \cite{croucher_collecting_2006}:\\
+Each element is generated with a probability of $1/n$. Thus, the probability to generate the $i$th unique element is given by 
+\begin{equation}
+    p_i = \frac{n-i+1}{n}
+\end{equation}
+The expected value of a random variable $X$ is given by $E(X) = \frac{1}{p}$\cite{croucher_collecting_2006}, thus the expected number of test runs for $n$ is 
+\begin{equation}
+E(T) = n \sum_{i=1}^{n} \frac{1}{i}
+\end{equation}
+\tabref{tab:prob_outcomes} shows the expected number of test runs $E(T)$ and its standard deviation $\sigma$ for different $n$.
+In \cite{croucher_collecting_2006}, $E(T)$ and $\sigma$ and the application of the central limit theorem are used to calculate a 95\% confidence interval for $T$, which provides an upper and lower bound on the number of test runs.
+Rounded values for both bounds are also shown in \tabref{tab:prob_outcomes}.
+\begin{table}[h]
+    \centering
+    \begin{tabular}{lllll}\label{tab:prob_outcomes}
+        \thead{$n$} & \thead{$E(T)$} & \thead{$\sigma$} & \thead{lower bound} & \thead{upper bound}\\ \hline
+        5 & 11.4 & 2.53 & 6 & 16\\
+        10 & 29.3 & 4.32 & 21 & 38\\
+        20 & 72.0 & 7.21 & 58 & 86\\
+        30 & 119.8 & 9.48 & 101 & 138 \\
+        50 & 225.0 & 13.23 & 199 & 251 
+    \end{tabular}
+    \caption{Expectation, standard deviation and upper and lower bound of needed test runs for some $n$ \cite{croucher_collecting_2006}}
+    \label{tab:my_label}
+\end{table}
+
+The results show that checking random values is a very inefficient approach if false positives are not admissible.
+Even if the lower bound of $T$ is chosen as the number of test runs, it exceeds the size of the domain by far and increases the time complexity to $\mathcal{O}(n*log(n))$ for large $n$ \cite{xu_tang_2011}.
+Instead, the following section introduces a formula to calculate the number of test runs that detect counterexamples with a $p < 1$, for instances where false positives are tolerable.
+
+\subsection{Setting probability thresholds}
 

### 2021-03-23 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
Introduction revisited; offline design accuracy analysis

@@
 \chapter{Introduction}\label{chap:introduction}
-Each execution of a blockchain-based Smart Contract in a gas-instrumented virtual machine generates costs proportional to the amount and complexity of computations and the  memory consumption \cite{goodman_tezos_2014}\cite{wood_ethereum_2021}.
-These fees, often calculated in gas, have to be paid for by the sender of the transaction and thus provides a powerful incentive to keep  smart contracts simple.
-However, in reality meaningful applications might need to perform some resource intensive computations at some point, which would be too expensive to execute inside the blockchain's virtual machine.
-Moreover, some blockchains impose a hard cap of how much gas can be consumed in one transaction, limiting the amount of operations that can be executed \cite{goodman_tezos_2014}.\\
-In order to avoid these costs and restrictions, an application could perform some computations outside of the blockchain context (i.e., off-chain) and only submit the results to a smart contract as input parameter for further processing or to store it on the chain.
-This approach raises another problem though - trusting that the submitted results are correct poses a safety as well as a security risk.
-Invalid results can be submitted unintentionally, if the computation is faulty, or a third party may pass them intentionally to cause harm or take advantage.
-Consequently, submitted parameters need to be checked for specified properties before the smart contract is executed.
-Although in many cases, verification is less expensive than computing the result itself, the generated costs for checking the validity increase with the size of the problem or input, ultimately becoming too expensive.
+Headed by Bitcoin in 2009, ``cryptocurrencies have emerged as the first generation of blockchain technology'' \cite{alharby_blockchain_2017}.
+However, their transactions are mostly limited to simple monetary transactions or registration of assets or ownerships \cite{alharby_blockchain_2017}.
+More recent blockchains, considered as the second generation \cite{alharby_blockchain_2017}, aim to provide a platform for building more sophisticated and complex applications on top of the technology.
+These are built with smart contracts, programs written in Turing-complete languages.
+Running a smart contract, though, generates costs proportional to the amount and complexity of computations, as well as its storage usage \cite{chen_under-alharby_blockchain_2017}.
+These fees, often measured in a unit called ``gas'', have to be paid for by the user in order to compensate the miners for their efforts \cite{chen_under-optimized_2020}.
+This creates a powerful incentive to keep smart contracts simple and efficient, while in effect, meaningful applications still might need to perform some resource intensive computations.
+Not only can such applications generate unsustainable costs when executed on the blockchain, but they may also reach gas limits imposed by the blockchain's protocol.
 \\
-Consider, for instance, the following contract from \cite{thiemann_2020} that expects a prime number: \todo{State programming language?!}
-\begin{lstlisting}[caption=Smart contract expecting a prime number, numbers=none, language=Solidity, label=lst:prime]
+In order to avoid these costs and restrictions, such an application could perform some computations outside of the blockchain context (i.e., off-chain) and only submit the results to a smart contract as an input parameter for further processing or recording \cite{thiemann_2020}.
+By trusting that the submitted results are correct, this approach raises both safety and security issues.
+Invalid results can be submitted unintentionally as a result of a wrong computation, or a third party may pass them intentionally to cause harm or take advantage.
+Consequently, submitted parameters should be checked for assumed properties before the smart contract is executed.
+Although in many cases, verification is less expensive than computing the result itself\footnote{cf.
+sorting algorithms with average time complexities of $\mathcal{O}(n log n)$ - $\mathcal{O}(n^2)$ \cite{review_sorting} vs.
+linear time to check if it is sorted.}, the generated costs for checking the validity increase with the size of the input.
+\\
+Consider, for instance, the following contract:
+\begin{lstlisting}[caption=Smart contract expecting a prime number \cite{thiemann_2020}, numbers=none, language=Solidity, label=lst:prime]
 contract Example {
@@
 \end{lstlisting}
-
-The assumption that the given integer $p$ is a prime can be expressed as an explicit assertion in predicate logic: 
+The assumption, that the given integer $p$ is a prime, can be expressed as an explicit assertion in predicate logic \cite{thiemann_2020}: 
 \begin{equation}\label{eq:prime}
@@
 \end{equation}
-
-Checking if this property holds requires the contract to execute a loop in $\mathcal{O}(\sqrt{p})$ time and therefore generate costs linear in $\sqrt{p}$ on top of the actual contract execution, assuming computing the body of the loop takes constant time.\\
-Thus it appears that we need a mechanism that allows the smart contract to make use of the computed result from an off-chain source without having to validate its validity locally with scaling costs.
+To check whether this property holds for $p$, the contract has to execute a loop.
+Assuming computing the body of the loop takes constant time, this test has a time complexity of $\mathcal{O}(\sqrt{p})$ and therefore generates costs linear in $\sqrt{p}$ on top of the cost for executing the actual contract.
+Thus, a mechanism is required that allows the smart contract to make use of the result computed by an off-chain source, without having to check its validity locally with scaling costs.
 
 \section{A distributed approach for assertion checking}
+% analyse/propose/explore an approach that could solve this rather than "this is the solution"
 A more efficient way to solve the issue at hand is to engage the validators of the blockchain into a distributed effort to find a counterexample that disproves an assumption.

### 2021-03-23 assertions/doc/thesis-bernhardt/chapters/2-offline_design.tex
Introduction revisited; offline design accuracy analysis

@@
 From this analysis, it can be derived how effective a formula can be checked on a blockchain with $m$ validators.
-For the remainder of this chapter, the assumptions hold that the random generator picks elements independently from a uniform distribution and that there exists exactly one counterexample for the passed parameter.
+For the remainder of this chapter, the assumptions hold that the random generator picks elements independently from a uniform distribution and that there exists exactly one counterexample for the passed parameter.\\
+The following two sections depict the findings from \cite{bernhardt_veigel_2020}.
 \todo{further measures for blockchains with small number of validators}
+\todo{Refer to our example paper}
 
@@
 \subsection{Setting probability thresholds}
+The goal is to find a number $t$ of test runs, s.t.
+the probability $P_{c,t}$ of not finding the counterexample drops below a certain threshold $c$.
+A validator finds the counterexample in one test run with probability $\frac{1}{n}$, and misses it with probability $(1-\frac{1}{n})$.
+After $t$ tests runs, the probability that the counterexample has not been found is thus $(1-\frac{1}{n})^t$.
+Following the same approach as in \cite{mahl_schindel_2007} to retrieve a bound for $P_{c,t}$, we use
+\begin{equation}
+(1-\frac{1}{m})^m \leq \frac{1}{e}
+\end{equation}
+which holds for all $m > 0$. From this inequality, it follows that
+\begin{equation}
+(1-\frac{1}{n})^t = ((1-\frac{1}{n})^n)^{\frac{t}{n}} \le e^{-\frac{t}{n}}
+\end{equation}
+With this, the probability $P_{c,t}$ of not finding the counterexample with $t$ test runs can be defined as
+\begin{equation}
+P_{c,t} \le e^{-\frac{t}{n}}
+\end{equation}
+In order to retrieve the number of test runs $t$ necessary for $P_{c,t}$ to drop below a specified threshold $c$, the inequality is solved for $t$, which depends on the known parameter $n$ and an arbitrary value for $c$:
+\begin{align}
+    e^{-\frac{t}{n}} &\leq c && \text{with } c\le1 \nonumber\\
+    t &\geq -n\:\ln(c)
+\end{align}
+For $c = \frac{1}{e}$ ($\approx 36.79\:\%$) $t$ is bound by $n$, which means that for higher reliabilities the number of test runs needs to be greater than $n$.
+\figref{fig:graph_t_c} shows the lower bounds of $t$ as a function of the probability threshold and domain size.
+One can see that the increase in accuracy is approximately linear to the number of test runs below a threshold of $c=0.5$, but requires an exponential testing effort to reach higher thresholds.
+\begin{figure}[h]
+\includegraphics[width=0.95\linewidth]{figures/3-offline/graph_t_c}
+\label{fig:graph_t_c}
+\end{figure}
+For assertions with several quantifiers, which are translated to random generators, all domains have to be considered in the calculation.
+Revisiting the intersection of sets from \secref{sec:existential}, every element in set $u$ has to be compared to every element in set $v$.
+Thus, the lower bound of test runs needed to check they intersect with a certainty of 63.21\% is given by $t \leq t_1 * t_2$ with $t_1 \leq |u|$ and $t_2 \leq |v|$.
 
-effectiveness:
-smaller search spaces = less needed test runs 
-example sorted list -> generate 1 random number and check neighbor = many test runs to cover all of them
-partition search space \& generate 2 random numbers better? -> 2 smaller search spaces. would this improve anything?
+\subsection{Validators vs. test runs}
+The last section derived a formula to calculate a lower bound for a number of test runs $t$ in order to reach a certain level of confidence.
+However, $t$ is not a parameter that can be adjusted to an arbitrary value on the blockchain, as the assertion is checked by the validators.
+Assuming a blockchain has $m$ validators, the actual lower bound of test runs is $m$.
+For cases where there are not enough validators to reach a threshold $c$, a mechanism is required to have each validator to check the property for multiple random values.
+Hence, the actually executed number of checks is always a multiple of $m$.
 
-\begin{lstlisting}[numbers=none, language=Assertion]
-(entrypoint (left (right (pair ( a : address) _)))
-  (forall (i : int)
-     (if (gt i 10)
-       (assert true))))
-\end{lstlisting}
+\subsection{Alternatives to random testing}
+For applications where higher reliability is crucial, an alternative to checking elements randomly could be to coordinate a systematic iteration of the domain.
+The implementation of such a coordination is not trivial though; validators can't simply be passed an individual value as input.
+Instead, possible approaches could be to implement a central instance that allocates an element in the search space to each validator, or use some unique and intrinsic attribute, like an identification number, as input for a mapping.
+
+\subsubsection{Central instance assigning values}
+For this approach, the tool-chain would need to generate a separate contract that is called by the baker and validators as a proxy.
+This contract would then, for instance, generate a number using a modulo-n counter and pass this number as an additional parameter to the assertion code.
+The random generators would be omitted accordingly.
+However, this works only as expected if there are no simultaneous transactions calling the contract, otherwise it cannot be guaranteed that all elements have been assigned for each transaction.
+If and how this issue can be solved will not be discussed further in this thesis.
+
+\subsubsection{Using unique attributes of a validator}\label{sec:alt_attributes}
+This approach strongly depends on whether the validators have a unique id or other attribute that can be accessed from within a contract.
+If there is (or the language can be extended with such a feature), there needs to exist a non-injective surjective function that maps the respective attributes represented by type A to an element of the domain represented by type B.
+Furthermore, for cases where $t > m$, an offset needs to be added, s.t.
+a validator checks distinct elements for each test run.
+\\
+Implementing such an approach on Tezos does become even more challenging by the way endorsing rights are distributed in its proof-of-stake mechanism: for each block level, endorsing rights are assigned to the owner of a randomly selected roll, i.e., a set of tokens \cite{tezos_docs}.
+This means that the same endorser can be picked multiple times for endorsing one block and thus some elements in the domain may remain unchecked.
+\secref{lala} goes into more detail about this issue.
+\todo{Ref section}

### 2021-03-23 assertions/doc/thesis-bernhardt/chapters/2-tezos.tex
Offline Chapter beginnign
Use Case chapter
Introduction revisited; offline design accuracy analysis

@@
 \chapter{Tezos}
-The Tezos blockchain is presented in its Whitepaper as a \enquote{generic and self-amending crypto-ledger} \cite{goodman_tezos_2014}.
+The Tezos blockchain is presented in its whitepaper as a \enquote{generic and self-amending crypto-ledger} \cite{goodman_tezos_2014}.
 It uses a proof-of-stake consensus mechanism that is not only used to agree on the current state of its ledger, but also allows its stakeholders to come to a consensus about changes in the economic protocol by a voting process.
@@
 amendment, can influence which transactions are valid on the blockchain, the payment system or even the voting process itself without risking a fork of the blockchain.
-Everyone owning the cryptocurrency of Tezos, called Tez, is considered a stakeholder.
-The Whitepaper compares the self-amending protocol to Peter Suber's game Nomic \cite{nomic}, and a similar concept was also implemented in the virtual sports league Blaseball \cite{blaseball}, which became popular during the COVID-19 pandemic.
+Everyone owning the cryptocurrency of Tezos, called Tez , is considered a stakeholder.
+The whitepaper compares the self-amending protocol to Peter Suber's game Nomic \cite{nomic}, and a similar concept was also implemented in the virtual sports league Blaseball \cite{blaseball}, which became popular during the COVID-19 pandemic.
 In addition to user accounts associated with a public key, Tezos supports smart contracts, which are written in the built-in language Michelson.
@@
 
+\section{Proof-of-stake in Tezos}
+In Tezos, contracts that staked a minimum amount of tokens, called a roll, can participate in the consensus mechanism and can either have the role of a baker or endorser.
+Contracts who don't own enough tokens or infrastructure to participate directly can delegate their baking and endorsing rights to other contracts.
+The rights are determined and assigned at the beginning of each cycle, which consists of a specified number of blocks.
+For baking, a random roll is selected for each block level and the rights are assigned to its owner.
+The block produced by that baker is endorsed by a fixed number of endorsers (currently 32 in protocol 008 Edo), which have been assigned endorsing rights for this block level if their roll has been randomly selected.
+Since participants can stake more than one roll, an endorser may be assigned several endorsement slots at the same level.
+\\
+As an incentive for active participation in the consensus algorithm, delegates (and also delegators) receive rewards in form of tokens.
+However, if accusers detect double-baking or -endorsement, the delegate is penalized by burning (i.e., destroying) their security deposit.
+\cite{tezos_docs}
+
 \section{Michelson}
-Michelson is a lower-level, stack-based language with a strict type-checking and supports primitive data types, like integers or strings, as well as high-level data structures such as list, maps and sum types \cite{tezos_docs_michelson}.
+Michelson is a lower-level, stack-based language with a strict type-checking and supports primitive data types, like integers or strings, as well as high-level data structures such as list, maps and sum types \cite{tezos_docs}.
 The type system reduces the occurrence of runtime errors and ensures that only well-typed contracts are originated on the blockchain.
-In OCaml the typing rules are implemented using generalized algebraic data types (GADTs) \cite{tezos_docs_michelson} and thus enforced by OCaml's typechecker.
+In OCaml the typing rules are implemented using generalized algebraic data types (GADTs) \cite{tezos_docs} and thus enforced by OCaml's typechecker.
 \\
@@
 \todo{Citations}
+\todo{Put Michelsons grammar/list of operations in appendix?}
 
@@
 The Tezos repository already provides ready-to-use scenarios for accusations.
-Besides testing shell or protocol code, Flextesa can also be used to test smart contracts.\cite{tezos docs}
+Besides testing shell or protocol code, Flextesa can also be used to test smart contracts.\cite{tezos_docs}
 \item[Tezt] The Tezt framework is newer than Flextesa and planned as its replacement.
 It can also launch the Tezos binaries as external processes and build a sandboxed test network of configurable size.
-Its main advantages over Flextesa are simplicity, usability and the use of events instead of polling the node.\cite{tezos_docs_tezt}
+Its main advantages over Flextesa are simplicity, usability and the use of events instead of polling the node.\cite{tezos_docs}
 \end{itemize}
@@
 The following list comprises of the three most prominent languages that compile to Michelson:
-
 \begin{itemize}

### 2021-03-23 assertions/doc/thesis-bernhardt/chapters/2-use_cases.tex
Started rework of Offline design
Introduction revisited; offline design accuracy analysis

@@
 \begingroup\vspace*{-\baselineskip}
-\captionof{figure}{Set of logical formulas amenable to distributed assertion checking (extension of set given in \cite{thiemann_2020})}
+\captionof{figure}{Set of logical formulas amenable to distributed assertion checking (extension of set from \cite{thiemann_2020})}
 \vspace*{\baselineskip}\endgroup
@@
 
-\section{Existential quantifier and proofs of validity}
+\section{Existential quantifier and proofs of validity}\label{sec:existential}
 The examples given so far in this thesis used universal quantification and required a search for counterexamples in order to check if some assumption about an input parameter is true.
 However, the same cannot be applied to existential quantifiers.
-Consider a contract expecting a string $e$ and a list $l$ of strings that contains $e$ at least once.
-The assumption that \texttt{l} contains \texttt{e} can be expressed by
-\begin{equation}\label{eq:contains}
-	(\exists n : int) (0 \leq n < |l|) \Rightarrow l[n] = e
+Consider a contract expecting two intersecting sets of integers, represented as arrays.
+This property can be checked in $\mathcal{O}(|u|*|v|)$.
+With $n = |u|+|v|$, the worst case for the run time occurs when both sets have the same size, i.e., $|u| = |v| = n/2$.
+This leads to a quadratic complexity $\mathcal{O}(n/2 * n/2) = \mathcal{O}(n^2/4) = \mathcal{O}(n^2)$.\\
+The assumption, that the intersection of the sets is not empty, i.e., $u \cap v \neq \emptyset$, can be expressed by
+\begin{equation}\label{eq:intersect}
+  (\exists i, \exists j) (0 \le i < |u|) \land (0 \le j < |v|) \Rightarrow u[i] = v[j]
 \end{equation}
 and its negation is
-\begin{equation}\label{eq:contains_neg}
-	(\forall n : int) (0 \leq n < |l|) \Rightarrow l[n] \ne e
+\begin{equation}\label{eq:intersect_neg}
+  (\forall i, \forall j) (0 \le i < |u|) \land (0 \le j < |v|) \land u[i] \neq v[j]
 \end{equation}
-
-If the assertion fails for a random value of $n$, it does not produce a counterexample, but rather it produces a proof for the validity of the assumption.
+If the assertion `fails' for random values of $i,j$, it does not produce a counterexample, but it rather produces a proof for the validity of the assumption.
 In that case, the validator finding such a proof should publish an approval instead of a veto to the network and the normal execution of the contract can proceed.
-Hence, there must be two different modi of assertion checking that implement different
-types of assertions (proofs need assertions that don't abort the program).
+Hence, there must be two different modi of assertion checking that implement different types of assertions.
 \todo{Refer to a chapter where this is discussed further?}
@@
 In the first case, each validator can pick a random clause in a random $F$ and check, if all literals evaluate to true.
-In the second case, the validators have to find a counterexample, namely a clause that is not satisfied by \mathcal{A}.
+In the second case, the validators have to find a counterexample, namely a clause that is not satisfied by $\mathcal{A}$.
 Checking a random clause in isolation cannot disprove the satisfiability, hence the validator has to check all clauses.
@@
 \section{Cost analysis} \todo{this}
-%diagram cost increase?
-%experiment: write Liquidity contract w. 1 loop and 1 single execution * loop size
+% diagram cost increase?
+% experiment: write Liquidity contract w. 1 loop and 1 single execution * loop size

### 2021-03-24 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
Revision chap. 1-3

@@
 These are built with smart contracts, programs written in Turing-complete languages.
-Running a smart contract, though, generates costs proportional to the amount and complexity of computations, as well as its storage usage \cite{chen_under-alharby_blockchain_2017}.
+Running a smart contract, though, generates costs proportional to the amount and complexity of computations, as well as its storage usage \cite{alharby_blockchain_2017}.
 These fees, often measured in a unit called ``gas'', have to be paid for by the user in order to compensate the miners for their efforts \cite{chen_under-optimized_2020}.
@@
 Consequently, submitted parameters should be checked for assumed properties before the smart contract is executed.
-Although in many cases, verification is less expensive than computing the result itself\footnote{cf.
-sorting algorithms with average time complexities of $\mathcal{O}(n log n)$ - $\mathcal{O}(n^2)$ \cite{review_sorting} vs.
-linear time to check if it is sorted.}, the generated costs for checking the validity increase with the size of the input.
+Although in many cases, verifying a solution takes less time than computing the result itself\footnote{cf.
+NP-hard problems \cite{nph_problems}, sorting algorithms \cite{review_sorting}\cite{cpp_issorted}, etc.}, the generated costs for checking the validity increase with the size of the input.
 \\
@@
 \section{A distributed approach for assertion checking}
-% analyse/propose/explore an approach that could solve this rather than "this is the solution"
-A more efficient way to solve the issue at hand is to engage the validators of the blockchain into a distributed effort to find a counterexample that disproves an assumption.
+A more efficient way to solve the issue at hand could be to engage the validators of the blockchain into a distributed effort to find a counterexample.
 If no counterexample could be found by any validator, the assumption is considered to be valid and the execution of the contract may resume.
@@
 \\
-In order to find counterexamples of an assertion, the formula in \ref{eq:prime} has to be transformed to its negation:
+In order to find a counterexample to the assertion, the formula in \eqref{eq:prime} has to be transformed to its negation:
 \begin{equation}\label{eq:prime_neg}
@@
 If a validator finds a counterexample, i.e., a value for $n$ where the reminder is $0$, it posts an objection to the network.
-For each involved validator the constant cost of generating one random number and calculating one division have to be paid, which is independent from $p$.
-\\
+For each involved validator, the constant cost of generating one random number and calculating one division have to be paid, which is independent from $p$.
+\todo{Change if not true} \\
 However, distributed assertion checking is not only applicable for parameters or properties of dynamic size.
@@
 
-\begin{lstlisting}[caption=Smart Contract expecting a sorted array, numbers=none, language=Solidity, label=lst:sorted]
+\begin{lstlisting}[caption=Smart contract expecting a sorted array, numbers=none, language=Solidity, label=lst:sorted]
 contract Sorted {
@@
 
-Even though the assertion can be checked in a loop in $\mathcal{O}(1)$, the constant factor is not negligible and can generate unreasonable costs.
-Hence, we consider the negation again and ask the validators to search for counterexamples by checking a random value for $n$:
+Even though the assertion can be checked in a loop in $\mathcal{O}(1)$, the constant factor is not negligible.
+Hence, the same approach can be applied here by considering the negation and have the validators search for counterexamples, checking random values for $n$:
 
@@
 
-Since the validators do random sampling, none of them finding a counterexample doesn't prove that the assumption is correct - the validation is only probabilistic and the reliability depends on the number of validators in the network.
-This corresponds to the principle of Bloom filters, where a queried element is either certainly not or possibly in a defined set \cite{blustein_bloom_2002}.
-In the case of assertion checking, it's the assumption that is either definitely not or maybe valid.
+Since the validators sample the domain randomly, the absence of a counterexample doesn't prove that the assumption is correct; the validation is only probabilistic and the reliability depends on the number of validators in the network.
+This corresponds to the principle of Bloom filters, where a queried element is either ``certainly not'' or ``possibly'' a member of a defined set \cite{blustein_bloom_2002}.
+In the case of assertion checking, we consider the assumption to be either definitely not or possibly valid.
 The probability of false positives in Bloom filters is an approximate function of the filter size and the number of inserted elements, supposing an optimal number of hash functions have been implemented.
-Tuning these parameters is a trade-off between making the filter more reliable, that is lowering its error rate, and space efficiency \cite{blustein_bloom_2002}.
-The same applies, with some reservations, to distributed assertion checking: less samples keep the costs to a minimum, whereas more samples increase the probability that, if it exists, a counterexample is found.
-In the last example, the probability of false positives depends on the size of $a$ and the number of validators.\\
+Tuning these parameters is a trade-off between making the filter more reliable, i.e., lowering its error rate, and space efficiency \cite{blustein_bloom_2002}.
+The same applies, with some reservations, to distributed assertion checking: less samples keep the gas consumption to a minimum, whereas more samples increase the probability that an existing counterexample is found.
+Refering to the example of sorted lists,  the probability of false positives depends on the size of the list $a$ and the number of validators $m$.\\
 The importance of the former parameter becomes obvious when looking at the worst case scenario of the same example.
-Assume the array is unsorted at exactly one position - the probability that the each of the $m$ validators independently check this position is given by $\frac{1}{|a|}$, and any other position by $\frac{|a|-1}{|a|}$.
-If the random generator chooses each value for $n$ independently from a uniform distribution, the probability that the counterexample is not detected by any validator converges to 0 if the number of validators approach infinity \cite{thiemann_2020}
+Assume the array is unsorted at exactly one position - the probability that the each of the $m$ validators independently check this position is $\frac{1}{|a|}$, while all of them checking any other position $\frac{|a|-1}{|a|}$.
+If the random generator chooses each value for $n$ independently from a uniform distribution, the probability that the counterexample is not detected by any validator converges to 0 if the number of validators approaches infinity \cite{thiemann_2020}:
 \begin{equation}\label{eq:limes_validators}
@@
 
-\move{maybe too detailed? move to efficiency section}
-
-\todo{Ueberleitung}
+\section{Objective}
+This thesis conducts research into the feasibility and performance of the proposed approach and explores possible designs for the implementation of both the necessary off-chain infrastructure and the amendment of the blockchain protocol.
+To this end, a first approximation of a set of formulas amenable for distributed assertion checking is defined, special cases are identified and, if necessary, excluded.
+While parts of the offline design and infrastructure should be, in parts, applicable to any blockchain supporting smart contracts, the case example for the protocol-specific parts of the design target the Tezos blockchain and its built-in contract language Michelson.
+On the basis of the achieved results, the efficiency of the approach is ultimately assessed.
 
 \section{Structure overview}
-which formulas are amendable?
-costs of testing them?
-
-This thesis assesses uses cases for this kind of testing, defines a language/syntax to express properties/assumptions like in the examples and explores how the mechanism can be implemented, using the Tezos blockchain and its smart contract language as platform/example.
-How the mechanism could/would be implemented in the Tezos blockchain ...
-which extensions to the Michelson language and the Tezos protocol are necessary
--> roadmap welche schritte es gibt
-	- language (assertion syntax)
-	- pipeline -> compile to Michelson
-	- extend Michelson language/interpreter etc.
-	- how does protocol have to be adapted
-
-The effectiveness of this approach is analyzed in detail (how many samples are necessary to reach a certain confidence level? which levels are appropriate?)
-
-Analyze the costs that are incurred by checking a formula with this approach; compare it with non-distributed approach.
-Both effectiveness \& cost model are used to evaluate this approach. Some alternatives are discussed. (here or in final chapter?)
-
-Finally, it gives an outlook what still needs to be done, what can be improved. It summarizes the results so far and evaluates.
+\draft{Finish when structure \& chapters finalised.}
+\begin{itemize}
+\item Assessment of use cases for this kind of assertion checking (Chapter 2)
+	\begin{itemize}
+	\item defines a set of logical formula
+	\item gives some useful examples
+	\item cost analysis for checking them normally
+	\end{itemize}
+\item Generic Offline Design (Chapter 3)
+	\begin{itemize}
+	\item definition of language/syntax to express assertions over given set of logical formulas
+	\item formalizes the transformation
+	\item describes frontend of pipeline
+	\item analyses accuracy of this approach
+	\end{itemize}
+\item Tezos-specific Offline Design (Chapter 4)
+	\begin{itemize}
+	\item introduction/Overview to Tezos
+	\item necessary extensions to Michelson's instruction set \& evaluator
+	\item description of the pipeline backend
+	\item Cost analysis \& accuracy on Tezos
+	\end{itemize}
+\item Conclusion \& outlook
+	\begin{itemize}
+	\item Next steps/ToDos for development; open issues
+	\item Evaluation of costs -> is this approach promising?
+	\item Alternatives? E.g. Refer to TrueBit
+	\end{itemize}
+\end{itemize}

### 2021-03-24 assertions/doc/thesis-bernhardt/chapters/2-use_case_analysis.tex
Revision chap. 1-3

--- 2021-03-23 assertions/doc/thesis-bernhardt/chapters/2-use_cases.tex
@@
-\chapter{Problem Definition and Use-cases}\label{chap:use_cases}
+\chapter{Use-case analysis}\label{chap:use_cases}
 The introduction argued that validating properties on input parameters becomes expensive when a data structure (such as arrays), certain data types (such as byte sequences) or a range of values have to be iterated.
@@
 The following section formally defines a set of applicable logical formulas for the first implementation of this approach.
-Given this set, section \secref{sec:examples} gives some more in-depth examples including cost analyses.
+Given this set, section \secref{sec:examples} gives some more in-depth examples with their respective time complexity.
+\todo{General cost analysis?}
 
 \section{Definition of a set of logical formulae}\label{sec:formulae}
+As already mentioned, formulas containing universal and existential quantification are interesting use-cases.
+Predicate variables are, for now, limited to the primitive data types supported by the respective virtual machines (VM).
+Besides the basic logical, numerical and relational operators of predicate logic, the formula may contain any operation that is built into the VM.
 \begin{align*}
@@
 \begingroup\vspace*{-\baselineskip}
-\captionof{figure}{Set of logical formulas amenable to distributed assertion checking (extension of set from \cite{thiemann_2020})}
+\captionof{figure}{Set of logical formulas amenable to distributed assertion checking (based on \cite{thiemann_2020})}
 \vspace*{\baselineskip}\endgroup
 
-The sets of supported data types $t$ and operations $f$ depend on what is supported in the virtual machines of the blockchains.
-\secref{lala} goes into more detail about what is already supported in Michelson and how the language and VM have to be extended to facilitate the assertion examples given previously and in \secref{sec:example_formulae}.
+\secref{} goes into more detail about what this set comprises of concretely for assertions executed on Tezos, and which extensions to Michelson and the VM are necessary in order to facilitate the assertion examples given previously and in the following section.
+\todo{Secref}
 
-\section{Examples}\label{sec:examples}\todo{title}
-The following examples are excerpts from \cite{bernhardt_veigel_2020}, which contains a more comprehensive collection of use-cases. A assessment of
+\section{Interesting formulas and special cases}\label{sec:examples}
+The following use-cases are picked from \cite{bernhardt_veigel_2020}, which contains a more comprehensive collection of formulas and properties that can be checked using the proposed approach.
+The selection of examples demonstrates different meanings of their negations and special cases, which emerge from different compositions of quantification, and discusses possible implications thereof.
 
-\subsection{Two numbers are coprime}\label{subsec:coprime}
+\subsection{Two numbers are coprime}\label{sec:coprime}
 The greatest common divisor ($gcd$) of two non-zero integers $a$ and $b$ is the largest integer that divides both evenly \cite{hardy2008introduction}.
-A more specific $gcd$-problem is finding two numbers which are coprime, that is their greatest common divisor is one, i.e., $gcd(a, b) = 1$ \cite{hardy2008introduction}.
-To verify if two numbers are coprime, it has to be checked that there exists no $gcd > 1$ , which can be expressed in the following propositional formula:
+A more specific $gcd$-problem is finding two numbers which are coprime, meaning their greatest common divisor is one, i.e., $gcd(a, b) = 1$ \cite{hardy2008introduction}.
+In order to verify that two numbers are coprime, it has to be checked that there exists no $gcd > 1$, which can be expressed in the following formula in predicate logic:
 \begin{equation}\label{eq:coprime-universial}
@@
 $\mathcal{O}(n)$, and depends on the size of the smaller number.
-Applying distributed assertion checking instead, we consider its negation to find a counterexample:
+When checking the assumption through a distributed effort instead, the validators consider its negation:
 \begin{equation}\label{eq:coprime-existential}
@@
 \end{equation}
+If, within the given domain, this condition is true for a random value for $n$, the respective validator has found a counterexample.
 
@@
 Heaps are data structures based on trees and can appear in two varieties: min and max heaps.
-Both can be represented as binary trees and have to satisfy the heap property \cite{dict_heap}.
-In a max heap, any given node has a lower or equal value than the value of its parent.
-In a min heap, the value is greater or equal than that of its parent \cite{dict_heap_property}.
+Both can be represented as binary trees and have to satisfy the heap property \cite{dict_heap}: in a max heap, any given node holds a value lower or equal than that of its parent, whereas in a min heap, it is greater or equal \cite{dict_heap_property}.
 Binary heaps are often implemented as an array, with the root of the tree stored at index 0.
 The relatives of a node \texttt{k} can be accessed as follows \cite{dict_binary_heap}:
-\begin{lstlisting}[language=Solidity, numbers=none, caption=Access a binary heap in array representation]
+\begin{lstlisting}[language=Solidity, numbers=none, caption=Access a binary heap in array representation \cite{bernhardt_veigel_2020}]
 heap_array[(k-1)/2] // Get parent of node k
@@
 \end{lstlisting}
-
-The min heap property, for instance, for a binary heap represented in an array $a$, can be expressed in predicate logic with the following formula:
+The min heap property for a binary heap stored in an array $a$, for instance, can be expressed in predicate logic with the following formula:
 \begin{equation}\label{eq:heap-unversial}
@@
 \end{equation}
-
-The time complexity of checking if $a$ satisfies the heap property is $\mathcal{O}(n)$ in the size of the array if it is dynamically sized, or $\mathcal{O}(1)$ when statically sized.
-Solidity, for instance, supports both types \cite{solidity_docs}.
-Similarly to the previous examples, the property of the array is validated by checking for counterexamples by considering its negation:
+The time complexity of checking whether $a$ satisfies the heap property depends on how the array is allocated.
+If it is dynamically sized, it takes $\mathcal{O}(n)$ in the size of the array, otherwise it takes constant time, i.e.
+$\mathcal{O}(1)$.
+Similarly to the previous examples, counterexamples can be identified by considering the formula's negation:
 \begin{equation}\label{eq:heap-unversial-neg}
@@
 Consider a contract expecting two intersecting sets of integers, represented as arrays.
-This property can be checked in $\mathcal{O}(|u|*|v|)$.
-With $n = |u|+|v|$, the worst case for the run time occurs when both sets have the same size, i.e., $|u| = |v| = n/2$.
-This leads to a quadratic complexity $\mathcal{O}(n/2 * n/2) = \mathcal{O}(n^2/4) = \mathcal{O}(n^2)$.\\
-The assumption, that the intersection of the sets is not empty, i.e., $u \cap v \neq \emptyset$, can be expressed by
+The assumption, that the intersection of the sets is not empty, i.e., $U \cap V \neq \emptyset$, can be expressed by
 \begin{equation}\label{eq:intersect}
@@
 \end{equation}
-and its negation is
+Consider its negation:
 \begin{equation}\label{eq:intersect_neg}
@@
 \end{equation}
-If the assertion `fails' for random values of $i,j$, it does not produce a counterexample, but it rather produces a proof for the validity of the assumption.
+If the condition is true for random values of $i,j$, it does not produce a counterexample, but it rather produces a proof for the validity of the assumption.
 In that case, the validator finding such a proof should publish an approval instead of a veto to the network and the normal execution of the contract can proceed.
-Hence, there must be two different modi of assertion checking that implement different types of assertions.
-\todo{Refer to a chapter where this is discussed further?}
+Thus, the two quantifiers essentially represent two different modi of assertion checking that the executors need to be aware of.
+\todo{If I pick this up again in a later chapter, ref.}\\
+Concerning the complexity of this test, the property can be checked in $\mathcal{O}(|u|*|v|)$.
+By considering the cardinality of their union $n = |u|+|v|$, one can derive that the worst case occurs when both sets have the same size, i.e., $|u| = |v| = n/2$.
+This leads to a quadratic complexity $\mathcal{O}(n/2 * n/2) = \mathcal{O}(n^2/4) = \mathcal{O}(n^2)$.
 
@@
 The previous example showed that universal and existential quantification have to be handled differently.
-However, other special cases caused by nested quantification have to be considered as well.
-Trivial cases of nested quantification are nesting of the same quantifiers, e.g.
-$(\forall i, j)$.
-They can be handled by generating a random value for each predicate and checking for a counterexample or proof respectively.
+However, further special cases caused by nested quantification have to be considered as well.
+A nesting of the same type of quantifier, e.g.
+$\forall i \forall j$ can be considered as trivial.
+They can be handled by generating a random value for each predicate variable and checking for a counterexample or proof respectively.
 It becomes less trivial though, if the nesting contains both universal and existential quantifiers.
-This section examines the the case of $\exists i, \forall j$ on the basis of a contract that expects a solution for a boolean satisfiability problem (SAT).
-Another instance of this use-case is also used to show that properties expressed with the nesting $\forall i, \exists j$ cannot be checked with the proposed approach for distributed assertion checking.
+This section examines the case of $\exists i \forall j$ on the basis of a contract that expects a solution for a boolean satisfiability problem (SAT).
+Another instance of this use-case is also used to show that properties expressed with the nesting $\forall i \exists j$ cannot be checked with the proposed approach for distributed assertion checking offhand.
 
@@
 Modern SAT-solvers expect $F$ to be in conjunctive normal form (CNF), i.e., a conjunction of a set of clauses, where clauses are disjunctions of variables or their negations (called literals) \cite{cnf_math_encycl}.
-Verifying whether a given assignment satisfies the formula takes $\mathcal{O}(n*m)$, where $n$ is the number of clauses and $m$ the number of variables (in the worst case, every variable is present as a literal in each clause).
+While finding an assignment $\mathcal{A}$ that satisfies $F$ is a NP-complete problem \cite{Biere2009}, verifying whether a given assignment satisfies the formula takes $\mathcal{O}(n*m)$, where $n$ is the number of clauses and $m$ the number of variables (in the worst case, every variable is present as a literal in each clause).
 In the case of k-SAT problems, where each clause contains at most k literals \cite{Biere2009}, the complexity is reduced to $\mathcal{O}(n)$.
@@
 \subsubsection{Encoding of variables, literals and clauses}
-A SAT problem could be represented as a list of clauses $c$ and a variable assignment $a$.
+A SAT problem can be represented as a list of clauses $c$ and a variable assignment $\mathcal{A}$.
 To avoid having to handle the variables and their literals as strings and thus optimize runtime and memory consumption, an encoding scheme taken from this blogpost\cite{sabablog} is used: \\
@@
 \end{align*}
-
 Consequently, checking whether a literal $y$ is positive or negative is a simple bit-wise $AND$ operation:
@@
 \end{align*}
-
 As already mentioned, $F$ can be represented as a list of clauses, and each clause in turn can be represented as a list of literals. Consider the following boolean formula and variable assignment:
@@
 \end{align*}
-
 Following the encoding of variables given above, the list of variables $v=[A,B,C]$ occurring in $F$ is encoded as $v_{enc} = [0,1,2]$.
@@
 Consequently, the distribution can only take place on the level of clauses, but not on the level of literals.
-Each validator thus checks all literals of one random clause and produces a proof of validity if all of them satisfy the property.
+Each validator thus has to check all literals of one random clause and produce a proof of validity if all of them satisfy the property.
 This implies that the formula does not have to be negated.
 \\
-Besides a distinct transformation, this case also has to be handled differently during the compilation process; instead of translating both quantifiers into a random generator, the universal quantifier has to be translated into a loop, cf.
+Besides having a distinct transformation, this case also has to be handled differently during the compilation process; instead of translating both quantifiers into a random generator, the universal quantifier has to be translated into a loop, cf.
 \lstref{lst:rand_loop}.
-\begin{lstlisting}[label=lst:rand_loop]
+\begin{lstlisting}[label=lst:rand_loop, numbers=none]
 i = random(0, size(F))
@@
 \end{lstlisting}
-
-Concerning the costs of checking such a formula, it's obvious that loops consume more gas than checking single elements.
-In the case of k-SAT problems with small values for $k$, the constant time factor for checking a clause might still be considered acceptable.
+In the case of k-SAT instances, the validators still only have to be paid a constant amount of gas, albeit with a factor $k$.
+If the number of literals in a clause is not constant, the loop will introduce a linear cost factor for each validator.
 
@@
 \end{gather*}
-
 Again, the validator has to check the whole clause in order to know whether it evaluates to true.
@@
 Although technically possible, it requires a more sophisticated compiler that translates this nesting into the following code structure:
-\begin{lstlisting}[label=lst:rand_loop_dependent]
+\begin{lstlisting}[label=lst:rand_loop_dependent, numbers=none]
 i = random(0, size(F))
@@
 \subsection{Further nesting}
-Nesting is, of course, not limited to two quantifiers, but can contain many of them.
-Generally, formulas containing no quantification alterations benefit the most from distributed assertion checking, as each quantifier can be translated into a random generator.
-On the other hand, formulas with a quantifier alteration early in the order of quantifiers benefit the least.
-Starting from the first alteration, the quantifiers are translated to loops.\\
-To substantiate this argument, consider a two variations of a contract that expect a list of boolean formulas in DNF, and an assignment $\mathcal{A}$.
+Nesting is, of course, not limited to two quantifiers only.
+Generally, formulas containing no quantification alterations within the nesting benefit the most from distributed assertion checking, as each quantifier can be translated into a random generator.
+On the other hand, formulas with a quantifier alteration early in the order of quantifiers benefit the least, because starting from the first alteration, the following quantifiers are translated to loops.\\
+To substantiate this argument, consider two variations of a contract that expect a list of boolean formulas in DNF, and an assignment $\mathcal{A}$.
 The first one checks, whether $\mathcal{A}$ satisfies at least one $F$, the other one checks if all $F$ are satisfied.
@@
 \end{itemize}
-In the first case, each validator can pick a random clause in a random $F$ and check, if all literals evaluate to true.
-In the second case, the validators have to find a counterexample, namely a clause that is not satisfied by $\mathcal{A}$.
-Checking a random clause in isolation cannot disprove the satisfiability, hence the validator has to check all clauses.
+In the first case, each validator picks a random clause from a random $F$ and checks if all literals evaluate to true.
+In the second case, checking a random clause in isolation cannot disprove the satisfiability, hence the validator has to check all clauses in a loop.
+The same reasoning can be done for the reverse order, i.e.
+$\forall\forall\exists$ and $\exists\forall\exists$.
 
-\subsection{Restriction of use cases} %name?
+\subsection{Restriction of use-cases}\todo{Better title?}
 The examples given in this chapter have shown that, depending on the type and order of quantification, not all properties can be checked in the same way and need different modi of assertion checking.
-This increases the complexity and requirements for a implementation of this approach; therefore, for a first iteration, this thesis focuses on providing the fundamentals and implementation for assertions using universal quantification.
-\todo{Refer to section where proofs are picked up again?}
+This increases the complexity and requirements for a implementation of this approach; therefore, for a first iteration, this thesis focuses on providing the fundamentals and implementation for assertions using universal quantification only.
 
-\section{Cost analysis} \todo{this}
-% diagram cost increase?
-% experiment: write Liquidity contract w. 1 loop and 1 single execution * loop size
+\section{Cost analysis}
+\draft{Formalize the costs of checking a formula}
+\begin{itemize}
+\item Describe a general cost model for execution of a SC
+\item Calculate costs for checking a formula locally (in a loop)
+\item Calculate costs for checking a single element
+\item Compare results -> how high is the ``boilerplate'' cost?
+\item When do the costs of distributed checking drop below local checking?
+\end{itemize}

### 2021-03-24 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Revision chap. 1-3

--- 2021-03-23 assertions/doc/thesis-bernhardt/chapters/2-offline_design.tex
@@
 The previous chapter defined a formal set of logical formulae amenable for this approach and gave some in-depth examples.
-As was stated before, the proposed implementation in the following chapters is, for the most part, restricted to formulas of predicate logic using universal quantification.\\
+As stated before, the proposed implementation in the following chapters is, for the most part, restricted to formulas of predicate logic using universal quantification.\\
 The purpose of the offline infrastructure is to provide a syntax for stating assertions that check logical formulas, as well as a toolchain to compile these assertions into code that can be originated on the target blockchain.
-Depending on the individual solution for the respective blockchain, this can either be the original contract extended with the assertion code, or separate code that extends the contract in some other way.
-This chapter describes the generic part of the offline design, which corresponds to the front-end of the compilation pipeline shown in \figref{fig:pipeline_generic}.
+Depending on the individual solution for the respective blockchain protocol, this can either be the original contract extended directly with the assertion code, or as a separate contract that extends the original contract in some other way.
+This chapter describes the generic part of the offline design, which corresponds to the front-end of the compilation pipeline shown in \figref{fig:pipeline_frontend}.
 As a start, \secref{sec:syntax} describes the concrete syntax for writing assertions and shows how it expresses some of the previously given examples.
-The transformation of the original assertions to assertions that check for counterexamples is formalized in \secref{sec:transformation} \todo{how to handle proofs}.
-Lastly, \secref{sec:effectiveness} analyses the reliability of distributed assertion checking.
+The transformation of the original assertions to assertions that check for counterexamples is formalized in \secref{sec:transformation}.
+Lastly, \secref{sec:accuracy} analyses the reliability of distributed assertion checking as proposed and the cost incurred by increasing it.
 
-\section{Assertion syntax}
+\begin{figure}[h]
+\includegraphics[width=\linewidth]{figures/3-offline/pipeline_frontend}
+\caption{The stages of the generic frontend of the compilation pipeline}
+\label{fig:pipeline_frontend}
+\end{figure}
+
+\section{Assertion syntax}\label{sec:syntax}
 The assertion syntax is described in two versions by the EBNF grammars shown in appendix \ref{apx:grammar}.
@@
 The pipeline currently supports the prefix notation with mandatory parentheses to avoid the need of handling operator precedences.
-To avoid context switches (at least for developers on Tezos), the assertion syntax references those of OCaml and Michelson.\\
-A file containing assertions (henceforth called `assertion contract') contains at least one assertion for some function or entrypoint of the original contract (henceforth called `parent contract').
+To avoid context switches (at least for developers on Tezos), the assertion syntax references those of OCaml and thereby also Michelson.\\
+A file containing assertions (henceforth referred to as ``assertion contract'') contains at least one assertion for some function or entrypoint of the original contract (henceforth referred to as ``parent contract'').
 An assertion begins with a signature consisting of an optional tag followed by a parameter type declaration.
-The tag can be used for documentation, but may sometimes be needed to indicate to which function of the parent contract the assertion is assigned.
+The tag can be used for documentation, but may sometimes be needed to indicate to which function of the parent contract the assertion should be assigned.
 The body is an (optional) nesting of quantifiers and conditions around exactly one assertion.
 Conditionals can be used to restrict the quantification domains or for some other constraints.
-For completeness, the existential quantifier is already included in the grammar, however the current version of the pipeline will reject any assertions containing it.\\
+For completeness, the existential quantifier is already included in the grammar, however the current version of the pipeline will reject any assertions containing it.
+\\
 In order to make the front-end generic, the assertion grammar constitutes a union of operations and types for the target languages.
 This also allows the transformation to be oblivious of the target platform and be identical for all backends.
-The current version of the grammar recognizes all types present in the Tezos VM and a subset of operations that Michelson provides.
-Responsible for rejecting any assertions containing unsupported types or operations are the respective backends.
+The current version of the grammar recognizes all types present in the Tezos VM and a subset of operations that Michelson provides ( \secref{sec:tezos} contains an introduction to Tezos and Michelson and goes more into detail about this).
+Responsible for rejecting any assertions containing unsupported types or operations are the respective backends.\\
 
-\subsection{Assertion example}
-Consider a variation of the formula in predicate logic that checks whether a given list is sorted in ascending order:
+As an example, consider a variation of the formula given in \eqref{eq:sorted} that checks whether a given list is sorted in ascending order:
 \begin{equation}\label{eq:sorted_v2}
@@
 \end{equation}
-A respective assertion that checks this property for the parent contract from \lstref{lst:sorted} could be expressed as follows:
-\lstinputlisting[caption=Assertion checking if a list is sorted, language=Assertion, label={lst:sorted_assertion}]{listings/sorted.tza}
+The respective assertion that checks this property for the parent contract from \lstref{lst:sorted} could be expressed as follows:
+\lstinputlisting[caption=Assertion contract for checking if a list is sorted, language=Assertion, label={lst:sorted_assertion}]{listings/sorted.tza}
 
@@
 \item \textbf{User-defined functions} to extract whole routines that can be reused in a single or even many assertion contracts, if defined as a module.
-\item \textbf{if-else conditions} to modify the domains of quantification if certain conditions hold.
-The assertion that checks whether two numbers are relatively prime (discussed in \secref{sec:coprime}) is a good use-case for this feature in several ways.
-Firstly, the minimum of the given number has to be determined, however the \texttt{min}-function might not be supported as a built-in function by the target language (Tezos, for instance, does not support it).
+\item \textbf{if-else conditions} to adapt the domains of quantifications if certain conditions hold.
+The assertion that checks whether two numbers are relatively prime (discussed in \secref{sec:coprime}) is a good use-case for this feature: Firstly, the minimum of the given number has to be determined, however the \texttt{min}-function might not be supported as a built-in function by the target language (Tezos, for instance, does not support it).
 A solution for that could be to implement two branches in the program to handle each case.
 Secondly, if the greater of the two numbers is not evenly divided by the smaller one, the formula can be optimized by reducing the quantification domain by half to $(2 \le n \le \lfloor \frac{min(a,b)}{2} \rfloor)$, as a number cannot be evenly divided by any number between itself and its half \cite{bernhardt_veigel_2020}.
-With a syntax supporting a \texttt{if-else} control structure, the respective assertion could look as follows:
+With a syntax supporting an \texttt{if-else} control structure, the optimized assertion could look as follows:
 \lstinputlisting[caption=Assertion syntax with if-else structures \cite{bernhardt_veigel_2020}, language=Assertion, label={lst:coprime}]{listings/coprime_ifelse.tza}
@@
 Since the validators will check the input parameter for the negation of the formula, it has to be transformed before compilation.
-Furthermore, the formula should explicitly state the domain for each quantifier, which will have to be translated into a set of bounds that belong to the respective random generator.
-These restrictions are important in order to avoid wasting resources through testing values out of the relevant (or legal) scope.
+Furthermore, the formula should explicitly state the domain for each quantifier, which will have to be translated into a set of bounds that refer to the respective random generator.
+Restricting the ranges of the random generators is important in order to avoid wasting resources through testing values out of the relevant (or legal) scope.
 
 \subsection{Negation}
-The formula is negated using the negation rules of second-order logic and applying De Morgan's laws until the negation is applied to the literals.
+The formula is negated using the negation rules of second-order logic and applying De Morgan's laws \cite{de_morgan} until the negation is applied to the literals.
 Negating universal quantification is equivalent to an existential quantification of its negated body (and vice versa): $\neg \forall x P(x) \equiv \exists x \neg P(x)$ \cite{Sundstrom2020Quantifiers}.
-The domain restrictions are not affected by the negation - the domain of the statement remains the same.
-This is also reflected in the rules of predicate logic, if the domain restrictions are given as a premise in the logical formula: $\neg (p \Rightarrow q) \equiv p \Rightarrow \neg q $.
+The domain restrictions are not affected by the negation, which is also reflected in the rules of predicate logic if the domain is given as a premise in the logical formula: $\neg (p \Rightarrow q) \equiv p \Rightarrow \neg q $.
 
-\subsection{Defining the domain of random generators}
-In order to assign each explicit bound to the respective quantifier, the formula has be skimmed for atomic constraints that contain bound variables.
+\subsection{Building smart random generators}
+In order to assign each explicit bound to its appropriate quantifier, the formula has be skimmed for atomic constraints that contain predicate (bound) variables.
 They're then moved and assigned to the quantifier that bounds the variable.
-If the constraint contains more than one, it is assigned to the quantifier with the highest depth in the order of quantifiers.
+If the constraint contains more than one bound variable, it is assigned to the quantifier with the highest depth in the order of quantifiers, as they depend on the generated value(s) of the other variable(s).
 \\
-Consider a variation of the example given in \eqref{eq:sorted}, a formula checking if a given list is sorted:
-\begin{equation}\label{eq:sorted_v2}
-	(\forall n : int)(\forall m : int) (0 \leq n \le m < |a|) \Rightarrow a[n] \leq a[m]
-\end{equation}
-\todo{variation given above. refer to that}
-
-The premise can be considered as a conjunction of the four constraints $0 \leq n$, $n < |a| $, $n \le m$ and $m < |a|$.
+Revisiting the formula from \eqref{eq:sorted_v2}, its premise can be considered as a conjunction of the four constraints
+\begin{itemize}
+\itemsep-1em
+\item $0 \leq n$
+\item $n < |a| $
+\item $n \le m$ and
+\item $m < |a|$.
+\end{itemize}
 Applying the rules given above after negating the formula, the constraints are assigned to the quantifiers as follows:
 \begin{equation}\label{eq:sorted_v2_bounds}
-	(\exists n : int, 0 \leq n \wedge n < |a|)(\exists m : int, m > n \wedge m < |a|) \text{ } a[n] > a[m]
+	(\exists n : int, 0 \leq n \wedge n < |a|])(\exists m : int, m > n \wedge m < |a|) \text{ } a[n] > a[m]
 \end{equation}
-Ultimately, the quantifiers are then translated to the corresponding random generators shown in \lstref{lst:rand}.
+Ultimately, the quantifiers are then translated to the corresponding random generators as indicated in \lstref{lst:rand}.
 \begin{lstlisting}[label=lst:rand]
@@
 \end{lstlisting}
+While conjunctions can be handled easily, other operators make it more difficult to derive efficient random generators. Consider the following constraints:
+\begin{itemize}
+\itemsep-0.7em
+\item[1)] $(\forall n : int) (n < 10 \lor n > 20) ...$
+\item[2)] $(\forall n : int) (n \ne 10) ...$
+\item[3)] $(\forall n : int) (n = 10) ...$
+\end{itemize}
+Constraint 1) complicates restricting the random generator in several ways.
+Firstly, it separates the domain into two disjoint sub-domains, which requires defining a random generator for each range and another one to decide which one is called.
+Secondly, the operands of a disjunction cannot be considered separately when more than one bound variable is involved.
+For the predicate variable whose random generator is executed first, the domain restriction is optional, while the generation of the following random values depend on the previous result.
+Similarly to 1), constraint 2) splits the domain into sub-domains.
+To keep it simple for the time being, restrictions formulated with these operators are kept as part of the assertion code rather than used as constraints for the generators.
+Consequently, some validators may generate irrelevant values when checking the assertion and, depending on the size of the gap between the sub-domains, this can significantly decrease the reliability of this kind of assertion checking.
+Thus, further developed iterations should handle and translate them accordingly.\\
+Constraint 3) effectively makes the quantifier, which binds $n$, obsolete.
+Adding this constraint to the respective generator will at least not affect the reliability, but a future improvement could be to optimize the assertion by replacing all occurrences of the bound variable with the assigned value and removing the quantification.
 
-While conjunctions can be handled easily, other operators make it more difficult to derive efficient random generators. Consider the following constraints:
-\begin{align}
-(\forall n : int) (n < 10 \lor n > 20) ... \\
-(\forall n : int) (n \ne 10) ... \\
-(\forall n : int) (n = 10) ... 
-\end{align}
-
-Both constraints 1) and 2) complicate restricting the random generator in several ways.
-Firstly, they separate the domain into two disjoint sub-domains, which requires defining a random generator for each range and another one to decide which one is called.
-Secondly, the operands of a disjunction cannot be considered separately when more than one bound variable is involved.
-For the predicate whose random generator is executed first, the domain restriction is optional, while the generation of the following random values depend on the previous result.
-As the complexity of building efficient random generators in these cases is relatively high, restrictions formulated with these operators are kept, for now, as part of the assertion code rather than used as constraints for the generators.
-Consequently, some validators may generate irrelevant values when checking the assertion.
-Depending on the size of the gap between the sub-domains, this can significantly decrease the reliability of this kind of assertion checking.
-Constraint 3) effectively makes the quantifier, which binds $n$, obsolete.
-Adding this constraint to the respective generator will at least not affect the reliability, but a future improvement could be to optimize the assertion by replacing all occurrences of the bound variable with the assigned value and removing the quantification.\\
-
-In some cases, boundaries are given implicitly by data types.
+\subsection{Implicit constraints}
+In some cases, boundaries are imposed implicitly by data types.
 List indices, for instance, are always bound to the range $0..
 size(list) - 1$ and could thus be derived from the formula without an explicit specification.
-As this deduction makes the transformation more complex, as it requires a semantic analysis of the formula, a completely explicit formula in terms of the domain is required for now.
-Depending on the virtual machine, the lower bound for indexing operations can be handled by the random generator of an appropriate predicate type.
+As this deduction makes the transformation more complex, requiring a semantic analysis of the formula, a completely explicit formula in terms of the domain is required for now.
+Depending on the VM, the lower bound for indexing operations can be implicitly handled by the random generator of an appropriate predicate type.
 As an example, Michelson supports the data type \texttt{nat} representing the natural numbers, which categorically excludes all values below zero.
@@
 
-\section{Accuracy of the approach}
-Since the proposed approach implements a probabilistic test, its accuracy as well as the costs incurred by guaranteeing a specified certainty threshold, remains to be analysed.
+\section{Accuracy of the approach}\label{sec:accuracy}
+Since the proposed approach implements a probabilistic test, its accuracy as well as the costs incurred by guaranteeing a specified certainty threshold, need to be examined closely.
 The goal is to identify a formula that, given the domain of a formula in predicate logic, returns an estimate of a lower bound of samples necessary to find an existing counterexample with a probability $p$.
 From this analysis, it can be derived how effective a formula can be checked on a blockchain with $m$ validators.
-For the remainder of this chapter, the assumptions hold that the random generator picks elements independently from a uniform distribution and that there exists exactly one counterexample for the passed parameter.\\
+For the remainder of this chapter, the assumptions hold that the random generator picks elements independently from a uniform distribution and that there exists exactly one counterexample for the passed parameter.
+
 The following two sections depict the findings from \cite{bernhardt_veigel_2020}.
-\todo{further measures for blockchains with small number of validators}
-\todo{Refer to our example paper}
 

### 2021-03-24 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Revision - chapter 3

@@
 \section{Accuracy of the approach}\label{sec:accuracy}
-Since the proposed approach implements a probabilistic test, its accuracy as well as the costs incurred by guaranteeing a specified certainty threshold, need to be examined closely.
+Since the proposed approach implements a probabilistic test, the accuracy as well as the costs incurred by guaranteeing a specified certainty threshold, need to be examined closely.
 The goal is to identify a formula that, given the domain of a formula in predicate logic, returns an estimate of a lower bound of samples necessary to find an existing counterexample with a probability $p$.
 From this analysis, it can be derived how effective a formula can be checked on a blockchain with $m$ validators.
-For the remainder of this chapter, the assumptions hold that the random generator picks elements independently from a uniform distribution and that there exists exactly one counterexample for the passed parameter.
+Sections \ref{sec:coupon} and \ref{sec:prob_threshold} depict the findings from \cite{bernhardt_veigel_2020} and are based on the assumptions that the random generator picks elements independently from a uniform distribution and that there exists exactly one counterexample for the passed parameter.
 
-The following two sections depict the findings from \cite{bernhardt_veigel_2020}.
-
-\subsection{Coupon Collector Problem Analysis}
+\subsection{Coupon Collector's Problem Analysis}\label{sec:coupon}
 When checking properties with probabilistic testing, the result is either definitely not satisfied, or probably satisfied.
 Thus, errors only occur as false positives.
-In order to find an existing counterexample with $p = 1$, every element in the given domain $\mathcal{D}$ has to be checked by at least one validator.
+In order to find an existing counterexample with probability $p = 1$, every element in the given domain $\mathcal{D}$ has to be checked by at least one validator.
 Deterministically, this is reachable with exactly $|\mathcal{D}|$ test runs.
@@
 \\
-In probability theory, this is known as the Coupon Collector's Problem \cite{croucher_collecting_2006}. Given $n = |\mathcal{D}|$, the probability that no duplicate elements are generated is given by
+In probability theory, this is known as the Coupon Collector's Problem \cite{croucher_collecting_2006}.
+Given $n = |\mathcal{D}|$, the probability that no duplicate elements are generated with $n$ picks is given by
 \begin{equation*}
@@
 As an example, the probability that all validators generate a unique random value already drops to $0.036\%$ for $n = 10$.
-Let the random variable $T$ be number of test runs executed until every element in the domain has been checked.
-The goal is to identify its expectation $E(T)$.
+Let the random variable $T$ be the number of test runs executed until every element in the domain has been generated.
+In order to obtain an estimation of how many test runs are needed to find the counterexample for certain, the goal is to identify its expectation $E(T)$.
 To this end, the geometric probability distribution is applied \cite{croucher_collecting_2006}:\\
@@
 \end{equation}
-The expected value of a random variable $X$ is given by $E(X) = \frac{1}{p}$\cite{croucher_collecting_2006}, thus the expected number of test runs for $n$ is 
+\cite{croucher_collecting_2006}. The expected value of a random variable $X$ is given by $E(X) = \frac{1}{p}$\cite{croucher_collecting_2006}, thus the expected number of test runs for $n$ is 
 \begin{equation}
@@
 \tabref{tab:prob_outcomes} shows the expected number of test runs $E(T)$ and its standard deviation $\sigma$ for different $n$.
-In \cite{croucher_collecting_2006}, $E(T)$ and $\sigma$ and the application of the central limit theorem are used to calculate a 95\% confidence interval for $T$, which provides an upper and lower bound on the number of test runs.
+Furthermore, $E(T)$ and $\sigma$ are used to calculate a 95\% confidence interval for $T$ by applying the central limit theorem, which provides an upper and lower bound on the number of test runs \cite{croucher_collecting_2006}.
 Rounded values for both bounds are also shown in \tabref{tab:prob_outcomes}.
@@
     \centering
-    \begin{tabular}{lllll}\label{tab:prob_outcomes}
+    \begin{tabular}{lllll}
         \thead{$n$} & \thead{$E(T)$} & \thead{$\sigma$} & \thead{lower bound} & \thead{upper bound}\\ \hline
@@
     \caption{Expectation, standard deviation and upper and lower bound of needed test runs for some $n$ \cite{croucher_collecting_2006}}
-    \label{tab:my_label}
+    \label{tab:prob_outcomes}
 \end{table}
@@
 Even if the lower bound of $T$ is chosen as the number of test runs, it exceeds the size of the domain by far and increases the time complexity to $\mathcal{O}(n*log(n))$ for large $n$ \cite{xu_tang_2011}.
-Instead, the following section introduces a formula to calculate the number of test runs that detect counterexamples with a $p < 1$, for instances where false positives are tolerable.
+For instances where false positives are tolerable, the following section introduces a formula to calculate the number of test runs that detect counterexamples with a given probability threshold $p \leq 1$.
 
-\subsection{Setting probability thresholds}
+\subsection{Setting probability thresholds}\label{sec:prob_threshold}
 The goal is to find a number $t$ of test runs, s.t.
@@
 After $t$ tests runs, the probability that the counterexample has not been found is thus $(1-\frac{1}{n})^t$.
-Following the same approach as in \cite{mahl_schindel_2007} to retrieve a bound for $P_{c,t}$, we use
+Following the same approach as in \cite{mahl_schindel_2007} to retrieve an upper bound for $P_{c,t}$, we use the following inequality
 \begin{equation}
@@
 \end{equation}
-In order to retrieve the number of test runs $t$ necessary for $P_{c,t}$ to drop below a specified threshold $c$, the inequality is solved for $t$, which depends on the known parameter $n$ and an arbitrary value for $c$:
+In order to retrieve the number of test runs $t$ necessary for $P_{c,t}$ to drop below a specified threshold $c$, the inequality is solved for $t$, which is then dependent of the known parameter $n$ and an arbitrary value for $c$:
 \begin{align}
-    e^{-\frac{t}{n}} &\leq c && \text{with } c\le1 \nonumber\\
+    e^{-\frac{t}{n}} &\leq c && \text{with } 0 \leq c\le 1 \nonumber\\
     t &\geq -n\:\ln(c)
 \end{align}
-For $c = \frac{1}{e}$ ($\approx 36.79\:\%$) $t$ is bound by $n$, which means that for higher reliabilities the number of test runs needs to be greater than $n$.
+For $c = \frac{1}{e}$ ($\approx 36.79\:\%$) the lower bound of $t$ is exactly $n$, which means that for higher reliabilities the number of test runs needs to be greater than $n$.
 \figref{fig:graph_t_c} shows the lower bounds of $t$ as a function of the probability threshold and domain size.
@@
 \includegraphics[width=0.95\linewidth]{figures/3-offline/graph_t_c}
+\caption{The number of required test runs as a function of the probability of false positives $c$ and size of the domain $n$}
 \label{fig:graph_t_c}
@@
 For assertions with several quantifiers, which are translated to random generators, all domains have to be considered in the calculation.
-Revisiting the intersection of sets from \secref{sec:existential}, every element in set $u$ has to be compared to every element in set $v$.
-Thus, the lower bound of test runs needed to check they intersect with a certainty of 63.21\% is given by $t \leq t_1 * t_2$ with $t_1 \leq |u|$ and $t_2 \leq |v|$.
+Revisiting the intersection of sets from \secref{sec:existential}, every element in set $U$ has to be compared to every element in set $V$.
+Thus, the lower bound of test runs needed to check whether they intersect with a certainty of 63.21\% is given by $t \leq t_1 * t_2$ with $t_1 \geq |U|$ and $t_2 \geq |V|$.
 
@@
 Assuming a blockchain has $m$ validators, the actual lower bound of test runs is $m$.
-For cases where there are not enough validators to reach a threshold $c$, a mechanism is required to have each validator to check the property for multiple random values.
-Hence, the actually executed number of checks is always a multiple of $m$.
+For cases where there are not enough validators to reach a threshold $c$, a mechanism is required to have each validator check the property for multiple random values.
+Hence, the actual executed number of checks is always a multiple of $m$.
+\secref{} goes into a bit more detail about this based on the Tezos blockchain.
+\todo{Refer to section}
 
@@
 Instead, possible approaches could be to implement a central instance that allocates an element in the search space to each validator, or use some unique and intrinsic attribute, like an identification number, as input for a mapping.
+The discussion if this approach would provide any advantages over a local validation of the property is left open \todo{Depends on cost analysis?}.
 
 \subsubsection{Central instance assigning values}
-For this approach, the tool-chain would need to generate a separate contract that is called by the baker and validators as a proxy.
+For this approach, the tool-chain would need to generate a separate contract that is called by the miners and validators as a proxy.
 This contract would then, for instance, generate a number using a modulo-n counter and pass this number as an additional parameter to the assertion code.
 The random generators would be omitted accordingly.
-However, this works only as expected if there are no simultaneous transactions calling the contract, otherwise it cannot be guaranteed that all elements have been assigned for each transaction.
+However, this works only as expected if there are no simultaneous transactions calling the contract, otherwise it cannot be guaranteed that all elements have been checked for each of the transactions.
 If and how this issue can be solved will not be discussed further in this thesis.
@@
 This approach strongly depends on whether the validators have a unique id or other attribute that can be accessed from within a contract.
-If there is (or the language can be extended with such a feature), there needs to exist a non-injective surjective function that maps the respective attributes represented by type A to an element of the domain represented by type B.
+If there is (or the language can be extended with such a feature), there needs to exist a non-injective surjective function that maps the respective attributes represented by type A to an element of the domain represented by type B, i.e.
+$f: X \rightarrow Y$.
 Furthermore, for cases where $t > m$, an offset needs to be added, s.t.
@@
 \\
-Implementing such an approach on Tezos does become even more challenging by the way endorsing rights are distributed in its proof-of-stake mechanism: for each block level, endorsing rights are assigned to the owner of a randomly selected roll, i.e., a set of tokens \cite{tezos_docs}.
-This means that the same endorser can be picked multiple times for endorsing one block and thus some elements in the domain may remain unchecked.
-\secref{lala} goes into more detail about this issue.
+Implementing such an approach on Tezos becomes even more challenging due the way endorsing (i.e.
+validation) rights are distributed in its proof-of-stake mechanism: for each block level, endorsing rights are assigned to the owner of a randomly selected roll, i.e., a set of tokens \cite{tezos_docs}.
+This means that the same validator can be picked multiple times for endorsing one block and thus some elements in the domain may remain unchecked.
+\secref{} goes into more detail about this issue.
 \todo{Ref section}

### 2021-03-24 assertions/doc/thesis-bernhardt/chapters/4-offline_design_tezos.tex
Revision chap. 1-3
Revision - chapter 3

--- 2021-03-18 assertions/doc/thesis-bernhardt/chapters/3-offline_design_tezos.tex
@@
-\chapter{Approach}\label{chap:approach}
+\chapter{Tezos-specific Offline Design}\label{chap:offline_tezos}
 
-With the specifications all set, the implementation section of this chapter assesses which of the necessary operations Tezos' smart contract language already provides, which extensions are needed and how the assertions can be made executable by Tezos' virtual machine.
+%- Vorschlag von HA: geht so nur für counterexamples.
+%- Case Proof-modus: some approval message has to be send actively if no assertion failed.%
+%	-> check if transaction fails? würde so ein mechanismus gehen? call case contracts n times. nach n times wird contract aber nicht aufgerufen
+%	-> oder: case contracts callen parent wenn property check successful; nicht möglich, da dann manager contract nichts davon weiß
+
+%With the specifications all set, the implementation section of this chapter assesses which of the necessary operations Tezos' smart contract language already provides, which extensions are needed and how the assertions can be made executable by Tezos' virtual machine.

### 2021-03-25 meeting-notes/2021-03-15-expose-vaccination.tex
update

@@
 One important step in this fight is to vaccinate as many people as possible.
-At some point, it is expected that certain activities (e.g., air travel, cruises, sports) are only open to vaccinated  persons.
-To this end, there must be a central registry for all vaccinations so that everyone can proof their vaccination status.
+At some point, it is expected that certain activities (e.g., air travel, cruises, sports) are open
+exclusively to vaccinated  persons. To this end, there must be a central registry for all
+vaccinations so that everyone can prove their vaccination status.
 
-The goal of the thesis is to investigate whether the blockchain is a suitable technical foundation for building such a registry.
-At first glance, this seems to be the case because the blockchain is a global decentralized database that can be maintained by mutually untrusting communities.
+Trust is a major issue in this registry. Only certified authorities should be able to enter
+vaccination records. It should not be possible to enter fake records. Each record should be linked
+to an individual but without subverting data protection and privacy. Everyone
+should be able to verify a vaccination given the identity of an individual within seconds.
+A certified authority should be able to obtain the full record (which vaccine, when vaccinated)
+within a reasonable time.
+
+Entering records or obtaining a full record may incur a reasonable cost. Verifying a vaccination
+should be as cheap as possible.
+
+Authorities should be structured hierarchically. For example, there is a small number of worldwide
+authorities; they vouch for national authorities, which in turn vouch for regional authorities and
+then local authorities (e.g., doctors or vaccination centers). Such a structure is the standard for
+certificates for webpages, emails, etc.
+
+The goal of the thesis is to investigate whether the blockchain is a suitable technical foundation
+for building such a registry. At first glance, this seems to be the case because the blockchain is a
+global decentralized database that can be maintained by mutually untrusting communities.
+
+The main concern is the cost to store the (huge) information on the blockchain and the cost and time
+to verify.  So the most important task is to find out how to store and then verify the
+vaccinations records with reasonable cost and time.
 

### 2021-04-01 assertions/doc/thesis-bernhardt/chapters/2-use_case_analysis.tex
Extension of Michelson/Introduction chapter 4

@@
 \lstref{lst:rand_loop}.
-\begin{lstlisting}[label=lst:rand_loop, numbers=none]
+\begin{lstlisting}[label=lst:rand_loop, numbers=none, caption=Translation of an assertion for a DNF SAT problem in pseudo-code]
 i = random(0, size(F))
@@
 Although technically possible, it requires a more sophisticated compiler that translates this nesting into the following code structure:
-\begin{lstlisting}[label=lst:rand_loop_dependent, numbers=none]
+\begin{lstlisting}[label=lst:rand_loop_dependent, numbers=none, caption=Translation of an assertion for a CNF SAT problem in pseudo-code]
 i = random(0, size(F))

### 2021-04-01 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Extension of Michelson/Introduction chapter 4

@@
 As a start, \secref{sec:syntax} describes the concrete syntax for writing assertions and shows how it expresses some of the previously given examples.
-The transformation of the original assertions to assertions that check for counterexamples is formalized in \secref{sec:transformation}.
+The stages of the pipeline front-end, including parsing and transforming the original assertions to assertions that check for counterexamples, are described in \secref{sec:pipeline_front}.
 Lastly, \secref{sec:accuracy} analyses the reliability of distributed assertion checking as proposed and the cost incurred by increasing it.
-
-\begin{figure}[h]
-\includegraphics[width=\linewidth]{figures/3-offline/pipeline_frontend}
-\caption{The stages of the generic frontend of the compilation pipeline}
-\label{fig:pipeline_frontend}
-\end{figure}
 
@@
 
-\section{Transformation}\label{sec:transformation}
+\section{Front-end of the pipeline}\label{sec:pipeline_front}
+The front-end of the compilation pipeline comprises of a command-line interface (CLI), a parser and the transformation.
+These stages are generic and independent of the target platform and produce an abstract syntax tree (AST) of the assertion that is passed to the respective back-end through a public interface.
+\begin{figure}[h]
+\includegraphics[width=\linewidth]{figures/3-offline/pipeline_frontend}
+\caption{The stages of the generic frontend of the compilation pipeline}
+\label{fig:pipeline_frontend}
+\end{figure}
+OCaml was chosen as a programming language to implement the pipeline, given that it's also used to develop the Tezos blockchain refer to \secref{sec:tezos}).
+This avoids context switches within the Tezos eco-system and allows to build on top of the Tezos libraries.
+\chapref{chap:offline_tezos} goes into more details about this.
+
+\subsection{Parser}
+Assertions expressed in the syntax described above are passed as a simple text file to the pipeline.
+The file extension is irrelevant, but this thesis follows the convention of using the file extension \texttt{.tza} for assertion contracts (referring to the extension \texttt{.tz} for Michelson contracts).
+The file must contain at least one assertion, hence it is not admissible to create empty assertions for all functions (or entrypoints) of the parent contract.
+Furthermore, every syntax error will cause the pipeline to abort execution in order to ensure that no assertion is missing in the target code.
+Each of the contained assertions is, after parsing, represented as a separate abstract syntax tree (AST).
+The AST represents, like the syntax itself, a union of all target specific ASTs that contain the supported subsets of operations and types.
+\\
+Both lexer and parser have been generated using the OCaml tools \texttt{ocamllex} \cite{ocaml_docs} and \texttt{menhir} \cite{menhir_doc}.
+
+\subsection{Transformation}\label{sec:transformation}
 Since the validators will check the input parameter for the negation of the formula, it has to be transformed before compilation.
@@
 
-\subsection{Negation}
+\subsubsection{Negation}
 The formula is negated using the negation rules of second-order logic and applying De Morgan's laws \cite{de_morgan} until the negation is applied to the literals.
@@
 
-\subsection{Building smart random generators}
+\subsubsection{Building smart random generators}
 In order to assign each explicit bound to its appropriate quantifier, the formula has be skimmed for atomic constraints that contain predicate (bound) variables.
@@
 
-\subsection{Implicit constraints}
+\subsubsection{Implicit constraints}
 In some cases, boundaries are imposed implicitly by data types.

### 2021-04-01 assertions/doc/thesis-bernhardt/chapters/4-offline_design_tezos.tex
Extension of Michelson/Introduction chapter 4

@@
 \chapter{Tezos-specific Offline Design}\label{chap:offline_tezos}
+After parsing an assertion contract and transforming it, the resulting AST is passed to the target-specific backend.
+For this thesis, the platform target is Tezos, with Michelson as the compilation target.
+This chapter continues to describe the pipeline stages implemented in the Tezos back end, which are shown in \figref{fig:pipeline_backend}.
+Furthermore, it states the necessary extensions to Michelson and its evaluator to facilitate useful assertions using random generators and assesses several orchestration strategies between the parent and assertion contract code.
+As a preliminary, the following section gives a short introduction to the Tezos blockchain, the Michelson language and some relevant tools in Tezos' ecosystem.
+\begin{figure}[h]
+\includegraphics[width=\linewidth]{figures/4-offline_tezos/pipeline_backend}
+\caption{The stages of Tezos-specific back end of the compilation pipeline}
+\label{fig:pipeline_backend}
+\end{figure}
+
+\section{Introduction to Tezos}\label{sec:tezos}
+The Tezos blockchain is presented in its whitepaper as a \enquote{generic and self-amending crypto-ledger} \cite{goodman_tezos_2014}.
+It uses a proof-of-stake consensus mechanism that is not only used to agree on the current state of its ledger, but also allows its stakeholders to come to a consensus about changes in the economic protocol by participating in a voting process.
+The changes included in a protocol upgrade, called amendment, can influence i.a.
+which transactions are valid on the blockchain, the payment system or even the voting process itself without risking a fork of the blockchain.
+Everyone owning the cryptocurrency of Tezos, called Tez, is considered a stakeholder and can participate in the consensus mechanism.
+The whitepaper compares the self-amending protocol of Tezos to a game created by Philosopher Peter Suber called ``Nomic'', whose set of rules are subjected to a democratic voting system \cite{nomic}.
+Similar concepts can also be found in modern pop culture, such as the virtual sports league ``Blaseball'' \cite{blaseball} that became popular during the COVID-19 pandemic.
+
+In addition to user accounts associated with a public key, Tezos supports smart contracts, which are written in the built-in language Michelson.
+Tezos' transaction fee system is similar to that of Ethereum \cite{wood_ethereum_2021} - it is gas-instrumented and besides a base fee, every operation and byte of storage during contract execution has to be paid for.
+However, Tezos imposes a hard cap on the amount of gas that can be consumed per transaction \cite{goodman_tezos_2014}, whereas Ethereum limits the gas quota only in respect to blocks \cite{wood_ethereum_2021}.\\
+Tezos is written in the multi-paradigm programming language OCaml \cite{ocaml_doc}.
+Compiling the its source code yields five essential binaries: the node, baker, endorser, accuser and client.
+The node is the entity that connects to the peer-to-peer network and keeps a copy of the chain.
+Bakers are responsible for producing new blocks, the endorsers for validating new blocks and the accusers to call out bakers or endorsers which double-sign or -endorse.
+The client provides a command line interface to interact with the local node through remote procedure calls (RPC).
+
+\subsection{Proof-of-stake in Tezos}
+In Tezos, contracts that staked a minimum amount of tokens, called a roll, can participate in the consensus mechanism and can either have the role of a baker or endorser.
+Contracts who don't own enough tokens or infrastructure to participate directly can delegate their baking and endorsing rights to other contracts.
+The rights are determined and assigned at the beginning of each cycle, which consists of a specified number of blocks.
+For baking, a random roll is selected for each block level and the rights are assigned to its owner.
+The block produced by that baker is endorsed by a fixed number of endorsers (currently 32 in protocol 008 Edo), which also have been assigned endorsing rights for this block level by a random selection of rolls.
+Since participants can stake more than one roll, an endorser may be assigned several endorsement slots at the same block level.
+\\
+As an incentive for active participation in the consensus algorithm, delegates (and also delegators) receive rewards in form of tokens.
+However, if accusers detect double-baking or -endorsement, the delegate is penalized by burning (i.e., destroying) their security deposit.
+\cite{tezos_docs}
+
+\subsection{Michelson}
+Michelson is a lower-level, stack-based language with strict type-checking and supports primitive data types, like integers or strings, as well as high-level data structures such as list, maps and sum types \cite{tezos_docs}.
+The type system reduces the occurrence of runtime errors and ensures that only well-typed contracts are originated on the blockchain.
+\\
+The concrete syntax of Michelson is called Micheline. A program is represented in Micheline nodes, which can be one of the following constructs:
+\begin{itemize}
+\item A constant of type integer (in decimal notation)
+\item A constant of type string
+\item A byte sequence in hexadecimal notation
+\item An application of a language primitive to a sequence of nodes
+\item A sequence of nodes
+\end{itemize}
+For documentation, readability and additional type constraints, Michelson and Micheline also offer three types of annotations - type, variable and field or constructor annotations, which are labelled with a unique special character in Micheline.
+The toplevel structure of a smart contract consists of a sequence of the three primitives \texttt{parameter, storage} and \texttt{code}, declaring the type of the input parameter, the storage type and the actual program code.
+The full grammar of Micheline and Michelson can be found in the Tezos developer resources \cite{tezos_docs}.
+
+\subsubsection{Entrypoints}
+ Unlike the contracts shown so far, which were expressed with the syntax of Ethereum's contract language Solidity \cite{solidity_docs}, Michelson doesn't have a concept of named functions with individual input parameter types.
+Instead of named functions, Michelson programs can have separate entrypoints by taking a disjunctive type as input parameter and optionally tagging the type constructors with a "function" name.
+The disjunctive type is built by nesting the \texttt{or} type, which has the constructors \texttt{left} and \texttt{right}.
+Assume we want to implement the contract from \lstref{lst:prime} in Michelson and add another function to it, which expects a string parameter.
+Omitting the actual program, the contract type declaration looks as follows:
+\begin{lstlisting}[language=Michelson, numbers=none, caption=Michelson contract with two entrypoints]
+parameter (or (int %isPrime) (string %isUpper));
+storage unit;
+code {
+  ...
+  IF_LEFT { ... (* then *)}
+          { ... (* else *)}
+}
+\end{lstlisting}
+The input type declared in the primitive application \texttt{parameter} accepts input of either type \texttt{left int}, or \texttt{right string}.
+By adding the field annotations \texttt{isPrime} and \texttt{isUpper}, the entrypoints are given tags and can be called explicitly by an external transaction.
+In that case, parameters of type \texttt{int} or \texttt{string} are accepted and the value is automatically wrapped into the respective constructors.
+Furthermore, it's possible to declare a \texttt{default} entrypoint, which is called when no explicit tag is specified.
+By default, the default entrypoint is assigned to the root of the parameter type.
+\cite{tezos_docs}
+
+\subsection{Developer tools in the Tezos ecosystem}
+This section describes some relevant tools and projects for developers that are part of Tezos' ecosystem.
+
+\subsubsection{Tezos Libraries}
+Tezos' executables and libraries are developed in the programming language OCaml and are available on through OCaml's package manager \texttt{opam} \cite{tezos_opam}.
+The protocol libraries of every version are released separately, thus any projects can be built on the protocol of choice.
+Important libraries that were used in the development of the offline toolchain are the Micheline library providing the internal abstract syntax tree (AST) and parser of the Michelson language, as well as the protocol specific libraries containing i.a.
+the type checker.
+Additionally, the client libraries are used to retrieve any needed information from the node or blockchain via RPCs.
+
+\subsubsection{Testing tools}
+Before a new protocol is proposed to the Tezos network, it has to be thoroughly tested with system, integration and regression tests.
+This requires a sandboxed network to simulate the real peer-to-peer network, such that also interactions between the actors of the blockchain can be tested.
+Tezos' development environment provides two testing frameworks for this:
+\begin{itemize}
+\item[\textbf{Flextesa}] With Flextesa (Flexible network sandboxes)\cite{tezos_docs} one can configure and run a small, fully functional sandboxed test network including nodes, bakers, endorsers and accusers.
+Accounts can be instantiated and used to send or receive funds.
+Configurable are, for instance, the size of the network, the time between blocks or enabling generation of random network traffic.
+Networks may either be fully autonomous, baking blocks automatically, or require manual baking of blocks.
+It also supports interactive sessions, where the tester can interact with the blockchain using the Tezos client.
+Flextesa's typical use-cases are interactive testing scenarios like double-baking, the voting process or protocol amendments.
+The Tezos repository already provides ready-to-use scenarios for accusations.
+Besides testing shell or protocol code, Flextesa can also be used to test smart contracts.
+\item[\textbf{Tezt}] The Tezt framework \cite{tezos_docs} is newer than Flextesa and planned as its replacement.
+It launches the Tezos binaries as external processes to build a sandboxed test network of configurable size.
+Its main advantages over Flextesa are simplicity, better usability and extendibility and better performance due to the use of an event system instead of polling the node.
+\end{itemize}
+
+\subsubsection{High-level languages}
+Michelson is a compilation target for various high-level languages that provide a more user-friendly and intuitive way of writing smart contracts.
+Additionally, some of them come with development environments and testing or verification tools.
+The following list comprises of the three most prominent languages that compile to Michelson:
+\begin{itemize}
+\item[\textbf{Liquidity}] \cite{liquidity} is a language with an OCaml-like syntax, which allows using local variables instead of stack manipulations.
+Its module system can be used to write reusable contract code or libraries.
+Besides an optimizing compiler, the project also includes a decompiler to compile Michelson programs to Liquidity.
+\item[\textbf{SmartPy}] \cite{smartpy} is a language available through a Python library and lets developers write contracts and tests using Python syntax and structures (such as classes).
+Its developer suite includes i.a.
+a compiler, a simulation engine for testing contracts and an online editor.
+\item [\textbf{fi}] 's \cite{fi} syntax is similar to JavaScript or Ethereum's contract language Solidity.
+It also provides an online editor and a simulator to test against the compiled contracts.
+However, it seems extensions to Michelson introduced by newer protocol versions are not supported yet.
+\end{itemize}
+
+\section{Extensions to Michelson}
+The way Michelson is interpreted is purely functional; it takes the current stack and an operation and builds a return stack from the initial one, without causing any side effects \cite{tezos_docs}.
+The recursive Michelson interpreter is defined as as a list of rules comprising of all possible inputs, i.e.
+program and stack types, and the respective output stack type of the computation if the rules applies.
+Each rule is of the following form:
+\begin{lstlisting}[caption=Rules form in the Michelson interpreter \cite{tezos_docs}, language=, numbers=none, label=lst:rules]
+> (syntax pattern) / (initial stack pattern)  =>  (result stack pattern)
+    iff (conditions)
+    where (recursions)
+    and (more recursions)
+\end{lstlisting}
+For each valid program and initial stack exactly one rule matches (given that any extra conditions over values on the stack, stated after the \texttt{iff} keyword are true) \cite{tezos_docs}.
+If the result depends on the results of other program interpretations (given after the keywords \texttt{iff, where, and} in rule form), the rule only applies if these partial results also match the respective intermediate result stack patterns.\\
+In addition, there exists a typing rule for each syntax construct that restricts the valid input stacks.
+The typing rules use the meta variables \texttt{'a} for type and \texttt{'A} for stack type variables in order to express consistency within the program (not polymorphism).
+These rules are given in the following form:
+\begin{lstlisting}[caption=Form of typing rules \cite{tezos_docs}, language=, numbers=none, label=lst:type_rules]
+(syntax pattern)
+:: (type of stack before) -> (type of stack after) [rule-name]
+   iff (premises)
+\end{lstlisting}
+The type notations, as well as syntax and stack patterns are listed in \cite{tezos_docs}.
+
+From the given formulas and assertion examples so far, one can derive a set of necessary instructions that need be be present in the target language.
+The following subsections list the instructions which have to be added to Michelson's instruction set, specify their selection and typing rules and describes how they can be implemented in the interpreter.
+These do not necessarily include high level instructions, like \texttt{sqrt} from \eqref{eq:prime}, that can be reproduced by using lower level instructions.
+For these purposes, a later iteration of the syntax will provide the feature of user-defined functions.
+
+\subsection{Random}
+A vital instruction that cannot be expressed with Michelson's current instruction set (state of protocol 008 Edo \cite{tezos_docs}) is the generation of a random value of certain types.
+Since smart contracts need to be deterministic, s.t.
+the network can reach a consensus about the state of the ledger \cite{chatterjee_probabilistic_2019}, the prevalent workarounds for generating pseudo-random numbers cannot be used for assertion checking.
+Distributed assertion checking explicitly requires as many validators as possible to generate a unique value, whereas common schemes, like oracles or using block attributes as seeds \cite{chatterjee_probabilistic_2019}, will provide the same values for all validators.\\
+\lstref{lst:rand_type} specifies the selection and typing rule of the instruction \texttt{rand}, which consumes an offset and a positive range from the stack and pushes a randomly generated integer to the top.
+This instruction, of course, can also be provided for other data types, such as \texttt{nat}, \texttt{string} or \texttt{mutez}.
+\lstset{upquote=true}
+\begin{lstlisting}[caption=Selection and typing rules of the integer \texttt{rand} instruction, language=, numbers=none, label=lst:rand_type]
+:: int : nat: 'A   ->  int : 'A
+
+> RAND/ offset : range : S  => int : S
+\end{lstlisting}
+
+Within the Michelson interpreter, the selection of rules is implemented as a huge match case \cite{tezos_repo}.
+If the rule for \texttt{rand} applies, the respective computation in OCaml could look as drafted in \lstref{rand_impl}.
+\begin{lstlisting}[caption=Simplified evaluation of \texttt{rand} in the Michelson interpreter, language=, label=lst:rand_impl]
+match (instruction, stack) with
+...
+| (Rand (offset, (range, rest))) -> 
+   Random.self_init;
+   let rand_int = offset + Random.int(range) in
+   return (rand_int, rest)  (* Resulting stack *)
+\end{lstlisting}
+
+\subsection{Nth}
+An exception for not adding higher level instructions may be the more fundamental operation \texttt{nth} for accessing list elements, as it is used (sometimes more than once, ref.
+\eqref{eq:sorted_v2}) in many use cases.
+Adding an own predefined primitive for this reduces the origination costs of the assertion contract, given that its equivalent in the current instruction set requires the compiler to generate a workaround using iteration, for instance a loop or list iterator.
+As a first approximation, appendix \ref{apx:nth} shows a potential implementation of \texttt{nth} in Liquidity (\lstref{lst:nth_liq}) using a loop, and how the respective Michelson code looks like after compiling the contract with the Liquidity compiler (\lstref{lst:nth_tz}).
+\\
+In case the \texttt{nth} is added as a predefined primitive to Michelson for the type \texttt{'a list}, its selection and typing rules are specified as follows:
+\begin{lstlisting}[caption=Selection and type rule of the list \texttt{nth} instruction, language=, label=lst:nth_type]
+:: (list 'a) : nat : 'A   ->  	option 'a : 'A
+
+> NTH / l : index : S  =>  Some 'a: S
+     iff index is within bounds
+> NTH / l : index : S  =>  None 'a: S
+     iff index is out of  bounds
+\end{lstlisting}
+
+As Michelson lists are represented with OCamls list type within the VM \cite{tezos_repo}, the computation for \texttt{nth} is simply applying the \texttt{nth} function of OCaml's List module, as shown in \lstref{lst:nth_impl}.
+\begin{lstlisting}[caption=Simplified evaluation of \texttt{nth} in the Michelson interpreter, language=, label=lst:nth_impl]
+match (instruction, stack) with
+...
+| (Nth ({elements = []; _}, (_, rest))) ->
+  return ((None, rest)
+| (Nth ({elements = es; length}, (index, rest))) ->
+  let l_length = of_int length in
+  if index <= l_length
+    then return (Some (List.nth es index), rest)
+    else return (None, rest)
+\end{lstlisting}
+\lstset{upquote=false}
+
+\section{Type check}
+\draft{}
+\begin{itemize}
+\item How are entry points assertions mapped to entrypoints?
+\item Rules (e.g. overlapping entrypoint are not allowed, usage of tags)
+\item Get entrypoint list \& types from chain if parent contract is already originated
+\end{itemize}
+
+\section{Compiler}
+\draft{}
+\begin{itemize}
+\item Orchestration strategies
+	\begin{itemize}
+	\item monolithic vs. modular
+	\item advantages/disadvantages
+	\item \# validators in Tezos \& how to have them run n test runs
+	\item security mechanism? (prevent ``dodging'' assertions)
+	\end{itemize}
+\item Compilation strategies (direct vs. IR)
+\end{itemize}
+
+\section{Misc}
+\todo{Aspects/questions I don't know yet if or where to put it}
+\begin{itemize}
+\item Tezos specific costs analysis of chosen orchestration strategy
+\item How can bakers differentiate between transactions to ”normal” SC and SCs with assertions?
+\item Representation of counterexamples; how to verify them?
+\item Basic approach for proofs?
+\item Usage pipeline
+\end{itemize}
 

### 2021-04-01 assertions/doc/thesis-bernhardt/chapters/5-conclusion.tex
Extension of Michelson/Introduction chapter 4

\chapter{Conclusion and outlook}\label{chap:conclusion}
\draft{}
\begin{itemize}
\item Summarize what has been implemented so far
\item Next steps
	\begin{itemize}
	\item extending VM \& Michelson
	\item compiler
	\item list open questions
	\item Protocol-design
		\begin{itemize}
		\item Do endorsers validate or extra validators?
		\item How to differentiate between SC w/ and w/o assertions?
		\item How to implement the waiting?
		\item Which transactions/messages can be reused or need to be introduced
		\item Representing counterexamples and verifying them
		\item Penalty for incorrect counterexamples
		\end{itemize}
	\end{itemize}
\item Estimation of cost reduction (or increase?)
\item Alternatives (e.g. TrueBit)
\end{itemize}

### 2021-04-01 assertions/doc/thesis-bernhardt/chapters/appendix.tex
Extension of Michelson/Introduction chapter 4

@@
 				 caption=Assertion grammar with infix notation]{../grammar/assertion_grammar_infix.txt}
+
+\chapter{List accessing in Michelson}\label{apx:nth}
+
+\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
+				 backgroundcolor=\color{cverbbg},
+				 linewidth=14cm,
+				 xleftmargin=0.5cm,
+				 frame=lr,
+				 framesep=8pt,
+				 framerule=0pt,
+				 captionpos=b,
+				 numbers=none,
+				 language=,
+				 label=lst:nth_liq,
+				 caption=Possible implementation of \texttt{nth} in Liquidity]{listings/nth.liq}
+
+\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
+				 backgroundcolor=\color{cverbbg},
+				 linewidth=14cm,
+				 xleftmargin=0.5cm,
+				 frame=lr,
+				 framesep=8pt,
+				 framerule=0pt,
+				 captionpos=b,
+				 numbers=none,
+				 language=,
+				 label=lst:nth_tz,
+				 caption=\lstref{lst:nth_liq} compiled to Michelson]{listings/nth.tz}

### 2021-04-02 assertions/doc/thesis-bernhardt/chapters/4-offline_design_tezos.tex
Type checker

@@
 The recursive Michelson interpreter is defined as as a list of rules comprising of all possible inputs, i.e.
-program and stack types, and the respective output stack type of the computation if the rules applies.
+program and stack types, and the respective output stack type of the computation if a rule applies.
 Each rule is of the following form:
@@
 These rules are given in the following form:
-\begin{lstlisting}[caption=Form of typing rules \cite{tezos_docs}, language=, numbers=none, label=lst:type_rules]
+\begin{lstlisting}[caption=Form of typing rules in Michelson's specification \cite{tezos_docs}, language=, numbers=none, label=lst:type_rules]
 (syntax pattern)
@@
 \end{lstlisting}
-The type notations, as well as syntax and stack patterns are listed in \cite{tezos_docs}.
+The type notations, as well as syntax and stack patterns are listed in \cite{tezos_docs}.\\
 
 From the given formulas and assertion examples so far, one can derive a set of necessary instructions that need be be present in the target language.
-The following subsections list the instructions which have to be added to Michelson's instruction set, specify their selection and typing rules and describes how they can be implemented in the interpreter.
+The following subsections list the instructions which have to be added to Michelson's instruction set, specify their selection and typing rules and describe how they can be implemented in the interpreter.
 These do not necessarily include high level instructions, like \texttt{sqrt} from \eqref{eq:prime}, that can be reproduced by using lower level instructions.
@@
 the network can reach a consensus about the state of the ledger \cite{chatterjee_probabilistic_2019}, the prevalent workarounds for generating pseudo-random numbers cannot be used for assertion checking.
-Distributed assertion checking explicitly requires as many validators as possible to generate a unique value, whereas common schemes, like oracles or using block attributes as seeds \cite{chatterjee_probabilistic_2019}, will provide the same values for all validators.\\
-\lstref{lst:rand_type} specifies the selection and typing rule of the instruction \texttt{rand}, which consumes an offset and a positive range from the stack and pushes a randomly generated integer to the top.
+Distributed assertion checking explicitly requires as many validators as possible to generate a unique value, whereas common schemes for randomness, like oracles or using block attributes as seeds \cite{chatterjee_probabilistic_2019}, will provide the same values for all validators.\\
+\lstref{lst:rand_type} specifies the selection and typing rule of a new instruction \texttt{rand}, which consumes an offset and a positive range from the stack and pushes a randomly generated integer to the top.
 This instruction, of course, can also be provided for other data types, such as \texttt{nat}, \texttt{string} or \texttt{mutez}.
@@
 :: int : nat: 'A -> int : 'A
-
 > RAND/ offset : range : S  => int : S
@@
 Within the Michelson interpreter, the selection of rules is implemented as a huge match case \cite{tezos_repo}.
-If the rule for \texttt{rand} applies, the respective computation in OCaml could look as drafted in \lstref{rand_impl}.
+If the rule for \texttt{rand} applies, the respective computation in OCaml could look as drafted in \lstref{lst:rand_impl}.
 \begin{lstlisting}[caption=Simplified evaluation of \texttt{rand} in the Michelson interpreter, language=, label=lst:rand_impl]
@@
 :: (list 'a) : nat : 'A -> option 'a : 'A
-
 > NTH / l : index : S  =>  Some 'a: S
@@
 \end{lstlisting}
-
-As Michelson lists are represented with OCamls list type within the VM \cite{tezos_repo}, the computation for \texttt{nth} is simply applying the \texttt{nth} function of OCaml's List module, as shown in \lstref{lst:nth_impl}.
+As Michelson lists are represented with OCamls list type within the VM \cite{tezos_repo}, the computation for \texttt{nth} could look as shown in \lstref{lst:nth_impl}.
 \begin{lstlisting}[caption=Simplified evaluation of \texttt{nth} in the Michelson interpreter, language=, label=lst:nth_impl]
@@
 \section{Type check}
-\draft{}
-\begin{itemize}
-\item How are entry points assertions mapped to entrypoints?
-\item Rules (e.g. overlapping entrypoint are not allowed, usage of tags)
-\item Get entrypoint list \& types from chain if parent contract is already originated
-\end{itemize}
+The task of the type checker is to map the assertions from the given file to the respective entrypoints of the parent contract.
+To this end, the parameter types have to be compared and matched against each other in order to find a correct assignment.
+The type checker either reads the code of the parent contract from a given file or retrieves the code from a given address on the blockchain.
+It must be ensured that the created mapping is injective and unambiguous, i.e., each assertion matches exactly one entrypoint and no entrypoint is covered by more than one assertion.\\
+As explained in \secref{sec:tezos}, entrypoints can be selected by calling the default entrypoint and wrapping the parameter into the respective union constructors.
+Alternatively, they can be called explicitly using their tag and passing the parameter as raw value.
+The same applies for the assertions - by omitting the tag, the parameter type must be declared in respect to the default entrypoint type.
+If the assertion states an explicit tag, it may declare the raw parameter type.
+The tags do not necessarily have to be identical with the tags of the parent contract; in some cases, they may be chosen differently for documentation or for readability purposes.
+However, the tags can and should be used to resolve ambiguity in the mapping between assertions and entrypoints, that is if several entrypoints share the same input type.
+Ambiguity can also be caused by the fact that entrypoints can be sub-entrypoints of others, thus assertions overlap if a separate assertion is declared for both super- and sub-entrypoint.
+This is resolved by detecting overlapping assertions during the type check and rejecting assertion contracts where appropriate.
+\\
+As an exemplification, consider a Michelson contract with five entrypoints (including the default entrypoint):
+\begin{lstlisting}[numbers=none, language=Michelson]
+parameter (or (int %A) (or %BC (int %B) (int %C)))
+\end{lstlisting}
+The following assertion contract for the given PC contains some valid and some invalid assertions:
+\begin{lstlisting}[language=Assertion]
+(assertion %A (i : int) ...)			 		  (* valid *)
+(assertion %D (i : int) ...)			 		  (* invalid *)
+(assertion (right (left (i : int)) ...)	(* valid *)
+(assertion %BC (x : (or int int)) ...)	(* invalid *)
+\end{lstlisting}
+Due to its tag, the fist assertion can be assigned unambiguously to entrypoint A, whereas for the second it is not apparent whether it should be assigned to entrypoint B or C.
+Since the tag is omitted in the third assertion, the parameter type is given in respect to the default entrypoint and is assigned to B.
+The last assertion is invalid because it is overlapping with the previous assertion, which was already assigned to entrypoint B.
 

### 2021-04-04 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Monolithic orchestration

@@
 Depending on the individual solution for the respective blockchain protocol, this can either be the original contract extended directly with the assertion code, or as a separate contract that extends the original contract in some other way.
-This chapter describes the generic part of the offline design, which corresponds to the front-end of the compilation pipeline shown in \figref{fig:pipeline_frontend}.
+This chapter describes the generic part of the offline design, which corresponds to the frontend of the compilation pipeline shown in \figref{fig:pipeline_frontend}.
 As a start, \secref{sec:syntax} describes the concrete syntax for writing assertions and shows how it expresses some of the previously given examples.
-The stages of the pipeline front-end, including parsing and transforming the original assertions to assertions that check for counterexamples, are described in \secref{sec:pipeline_front}.
+The stages of the pipeline frontend, including parsing and transforming the original assertions to assertions that check for counterexamples, are described in \secref{sec:pipeline_front}.
 Lastly, \secref{sec:accuracy} analyses the reliability of distributed assertion checking as proposed and the cost incurred by increasing it.
@@
 \\
-In order to make the front-end generic, the assertion grammar constitutes a union of operations and types for the target languages.
+In order to make the frontend generic, the assertion grammar constitutes a union of operations and types for the target languages.
 This also allows the transformation to be oblivious of the target platform and be identical for all backends.
@@
 
-\section{Front-end of the pipeline}\label{sec:pipeline_front}
-The front-end of the compilation pipeline comprises of a command-line interface (CLI), a parser and the transformation.
+\section{Frontend of the pipeline}\label{sec:pipeline_front}
+The frontend of the compilation pipeline comprises of a command-line interface (CLI), a parser and the transformation.
 These stages are generic and independent of the target platform and produce an abstract syntax tree (AST) of the assertion that is passed to the respective back-end through a public interface.

### 2021-04-04 assertions/doc/thesis-bernhardt/chapters/4-offline_design_tezos.tex
Monolithic orchestration

@@
 For this thesis, the platform target is Tezos, with Michelson as the compilation target.
-This chapter continues to describe the pipeline stages implemented in the Tezos back end, which are shown in \figref{fig:pipeline_backend}.
+This chapter continues to describe the pipeline stages implemented in the Tezos backend, which are shown in \figref{fig:pipeline_backend}.
 Furthermore, it states the necessary extensions to Michelson and its evaluator to facilitate useful assertions using random generators and assesses several orchestration strategies between the parent and assertion contract code.
 As a preliminary, the following section gives a short introduction to the Tezos blockchain, the Michelson language and some relevant tools in Tezos' ecosystem.
-\begin{figure}[h]
-\includegraphics[width=\linewidth]{figures/4-offline_tezos/pipeline_backend}
-\caption{The stages of Tezos-specific back end of the compilation pipeline}
-\label{fig:pipeline_backend}
-\end{figure}
 
@@
 Tezos' transaction fee system is similar to that of Ethereum \cite{wood_ethereum_2021} - it is gas-instrumented and besides a base fee, every operation and byte of storage during contract execution has to be paid for.
-However, Tezos imposes a hard cap on the amount of gas that can be consumed per transaction \cite{goodman_tezos_2014}, whereas Ethereum limits the gas quota only in respect to blocks \cite{wood_ethereum_2021}.\\
+However, Tezos imposes a hard cap on the amount of gas that can be consumed per operation (including internal transactions) \cite{tezos_docs}\cite{morley_repo}, whereas Ethereum limits the gas quota only in respect to blocks \cite{wood_ethereum_2021}.\\
 Tezos is written in the multi-paradigm programming language OCaml \cite{ocaml_doc}.
@@
 
-\section{Type check}
+\section{Orchestration of contract and assertions}
+So far, the assertion and parent contract have been considered separately.
+However, on the blockchain they have to be orchestrated, s.t.
+the bakers and validators execute the assertion before the actual contract code.
+The orchestration does not only include the linking of assertion and contract code, but also a mechanism to execute an assertion $n$ times depending on the domain space that needs to be checked.
+There are basically two approaches - the assertion and contract code can be assembled into a single monolithic contract, or they can be originated separately as standalone contracts.
+As the strategy has an impact on the compilation process and output, it has to be determined in advance which of the two should be implemented and how.
+
+\subsection{Approach 1: Monolithic contract}
+In the monolithic approach, a new contract is built using both the assertion and parent code as input.
+As is outlined in \figref{fig:monolithic_orchestration_basic}, the assertions can either be appended to the original contract as separate entrypoints or by prepending them to the code of the respective entrypoint.
+This tightly couples and unites the code in one self-contained unit.
+\begin{figure}[!htb]
+\subfloat[Appending assertions as separate entrypoints]{\includegraphics[width=0.5\textwidth]{figures/4-offline_tezos/monolithic_ep.jpg}}
+\quad
+\subfloat[Inserting the assertion code into the original entrypoint]{\includegraphics[width=0.5\textwidth]{figures/4-offline_tezos/monolithic_insert.jpg}}
+\caption{Approaches for assembling a monolithic contract}
+\label{fig:monolithic_orchestration_basic}
+\end{figure}
+While the link between assertion and contract code is already given in a), the entrypoint and assertions in b) still need to be coupled, as it is not inherent which entrypoint represents a normal and which the respective assertion.
+For this reason, assertion entrypoints need to have fixed name pattern, s.t.
+it is derivable from the original entrypoint.
+As a proposal, the tag of the assertion is the tag of its parent entrypoint suffixed with a \texttt{\_a}, e.g.
+\texttt{A\_a} for entrypoint \texttt{A}.
+The baker can then execute the contract normally by calling the original entrypoint and prompt the validators to execute the assertion separately.
+\\
+Both approaches, however, do not yet provide any means to have validators execute the assertions $n$ times.
+Since only the contract itself knows how to calculate $n$ (as per the range(s) of the random generator(s)), it cannot be passed to the validators as a parameter to the validation request.
+Instead, the contract itself needs a test run manager which handles this.
+A test run manager can either be implemented as another entrypoint, say \texttt{A\_m}, which then calls \texttt{A\_a} (or \texttt{A} in case of a)) $n$ times as an internal transaction.
+Another possibility is to create a separate manager contract that acts as a proxy, contains the manager code and internally calls the monolithic contract.
+This solution is a hybrid of the monolithic and modular approach.
+The section covering the modular approach describes in more detail how it is implemented.\\
+It's important to realize that neither baker nor validators can differentiate between entrypoints that have an associated assertion and those that do not.
+In order to avoid transaction failures caused by calling assertions that do not exist, the compiler has to add dummy managers for empty assertions that call the actual contract code immediately.\\
+% Description figures
+% -> txa special transaction type
+% managers use internal transactions to call contract n times
+% depending on protocol, validators use normal tx or another special tx type
+% req message needs to contain the derived name of the assertion ep -> derivation needs to be part of the "assertion mode". is this possible?
+% veto message: the txa op hash it refers to, an instance of a counterexample (not yet clear how this looks like)
+
+\begin{figure}[h]
+\centering
+  \includegraphics[width=0.7\textwidth]{figures/4-offline_tezos/interaction_monolithic.jpg}
+	\caption{Interaction with a monolithic contract}
+	\label{fig:interaction_monolithic}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+  \includegraphics[width=0.8\textwidth]{figures/4-offline_tezos/interaction_monolithic_managertz.jpg}
+	\caption{Interaction with a manager and monolithic contract}
+	\label{fig:interaction_monolithic_managertz}
+\end{figure}
+
+\subsubsection{Evaluation}
+Generell:
+- parent code has to be modified
+	+ show code example
+	+ decompilation necessary
+	+ compilation is more complex
+- doesn't work if the parent code is already originated
+- inflexible -> tightly coupled code
+	+ if the assertion code changes, the whole contract has to be reoriginated
+
+ep assert + ep manager
++ baker can call basic ep; validators call manager
+	-> cost efficient; contract is only executed once
+- only works with explicit ep -> parameter types!
+- complex compilation (1-2 eps per ep more)
+- readability
+
+no ep assert + ep manager
+- contract code is also executed n times
+- only works with explicit ep -> parameter types!
++ bypassing assertion not possible!
++ less eps more readable? (aber nur bisschen)
+
+ep assert + contract manager
++ less complex compilation -> just copy assertion code before the actual code (less entrypoint handling)
++ if manager also has eps A and A\_m, the code and assertions can also be called separately
++ modularity -> readability, a bit more flexibility (if manager code changes)
+- \^ even more eps -> 2-3 eps more
+- more boilerplate, more origination costs
+
+no ep assert + contract manager
+- contract code is also executed n times
++ bypassing assertion not possible!
++ less complex compilation -> just copy assertion code before the actual code (less entrypoint handling)
++ modularity
+
+what happens to calls to default?
+
+\begin{itemize}
+\item Assertions are appended to the parent as separate entry points
+\item Parent contract has to be modified (parameter type \& addendum)
+\item Problems/Drawbacks:
+	\begin{itemize}
+	\item entrypoint names necessary - otherwise no unambiguous assignment
+	\item parameter types of original ep \& assertion ep are different
+	\item e.g. \%A and \%A\_a cannot be called with the same parameter (if not called explicitly; ref. \ref{lst:mono_unnamed} line 24, 25.)
+	\item Possible solution:
+		\begin{itemize}
+		\item all eps in the parent and assertion contract need to have a \%name \verb|->| calling both eps explicitly allows using the same parameter (ASAIK) ; ref. \ref{lst:mono} line 24, 25.
+		\item Assign dummy names if none are given - effort?
+		\item what to do with calls to \%default?
+			\begin{itemize}
+			\item Baker would need to
+			\item 1) look up entrypoints of contract 
+			\item 2) check which type matches \& find out the ep name
+			\item 3) derive assertion ep name from that
+			\end{itemize}
+		\item how to assign entry points given without names in .tza to their respective parent eps? \ref{lst:mono_unnamed} line 10, 11.
+		\end{itemize}
+	\end{itemize}
+\item EP names of the assertion code need to have a fixed pattern, s.t. the bakers know how to call them
+\item Similarly to strategy 1, there probably needs to be "empty" assertion code for normal eps
+\end{itemize}
+
+%\ref{fig:separate_contract_v2}:
+%\begin{figure}[h]
+%	\centering
+%  \includegraphics[width=\textwidth]{assembly_monolith}
+%	\caption{Interaction with a monolithic contract}
+%	\label{fig:monolithic_contract}
+%\end{figure}
+
+%\lstinputlisting[label=lst:mono, caption=Monolithic assembly w/ ep names, numbers=left]{monolithic.tz}
+%\lstinputlisting[label=lst:mono_unnamed, caption=Monolithic assembly w/o ep names, numbers=left]{monolithic_unnamed.tz}
+
+\subsection{Approach 2: }
+
+\section{Backend of the pipeline}
+The Tezos backend of the pipeline comprises of the three stages semantic check, type check and compilation.
+During the semantic check, the common AST is cast to a Tezos-specific AST type.
+If the assertion contains any data types or operations not supported in Michelson, the assertion contract is rejected.
+Since the subsequent stages are less straight forward, they are explained in more detail in the following.
+\begin{figure}[h]
+\includegraphics[width=\linewidth]{figures/4-offline_tezos/pipeline_backend}
+\caption{The stages of Tezos-specific backend of the compilation pipeline}
+\label{fig:pipeline_backend}
+\end{figure}
+
+\subsection{Type check}
 The task of the type checker is to map the assertions from the given file to the respective entrypoints of the parent contract.
@@
 
-\section{Compiler}
+\subsection{Compiler}
+The transformed and type checked assertion AST needs to be retargeted to Michelson code.
+
 \draft{}
@@
 \begin{itemize}
-\item Tezos specific costs analysis of chosen orchestration strategy
+\item Tezos specific costs analysis of chosen orchestration strategy -> PROBLEM: high n might reach operation gas limit?
 \item How can bakers differentiate between transactions to ”normal” SC and SCs with assertions?
@@
 %	-> oder: case contracts callen parent wenn property check successful; nicht möglich, da dann manager contract nichts davon weiß
-
-%With the specifications all set, the implementation section of this chapter assesses which of the necessary operations Tezos' smart contract language already provides, which extensions are needed and how the assertions can be made executable by Tezos' virtual machine.

### 2021-04-06 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
Extension of Michelson/Introduction chapter 4
Modular approach

@@
 \\
-In order to find a counterexample to the assertion, the formula in \eqref{eq:prime} has to be transformed to its negation:
+In order to find a counterexample, the formula in \eqref{eq:prime} has to be transformed to its negation:
 \begin{equation}\label{eq:prime_neg}
@@
 For each involved validator, the constant cost of generating one random number and calculating one division have to be paid, which is independent from $p$.
-\todo{Change if not true} \\
+\\
 However, distributed assertion checking is not only applicable for parameters or properties of dynamic size.
@@
 The same applies, with some reservations, to distributed assertion checking: less samples keep the gas consumption to a minimum, whereas more samples increase the probability that an existing counterexample is found.
-Refering to the example of sorted lists,  the probability of false positives depends on the size of the list $a$ and the number of validators $m$.\\
+Referring to the example of sorted lists,  the probability of false positives depends on the size of the list $a$ and the number of validators $m$.\\
 The importance of the former parameter becomes obvious when looking at the worst case scenario of the same example.

### 2021-04-06 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Modular approach

@@
 \end{equation}
-Ultimately, the quantifiers are then translated to the corresponding random generators as indicated in \lstref{lst:rand}.
-\begin{lstlisting}[label=lst:rand]
+Ultimately, the quantifiers are then translated to the corresponding random generators, drafted in pseudocode:
+\begin{lstlisting}[label=lst:rand, numbers=none]
 n = random(0, size(list))
@@
 If and how this issue can be solved will not be discussed further in this thesis.
+\todo{Serializes tests -> see expose rejected ideas}
 

### 2021-04-06 assertions/doc/thesis-bernhardt/chapters/4-offline_design_tezos.tex
Modular approach

@@
 \cite{tezos_docs}
+
+\todo{Add mempool? If Blockchain protocol is outlined}
 
@@
 \begin{figure}[!htb]
-\subfloat[Appending assertions as separate entrypoints]{\includegraphics[width=0.5\textwidth]{figures/4-offline_tezos/monolithic_ep.jpg}}
+\subfloat[Appending assertions as separate entrypoints]{\includegraphics[width=0.5\textwidth]{figures/4-offline_tezos/pipeline_output_mono_ep_basic.jpg}}
 \quad
-\subfloat[Inserting the assertion code into the original entrypoint]{\includegraphics[width=0.5\textwidth]{figures/4-offline_tezos/monolithic_insert.jpg}}
+\subfloat[Inserting the assertion code into the original entrypoint]{\includegraphics[width=0.5\textwidth]{figures/4-offline_tezos/pipeline_output_mono_basic.jpg}}
 \caption{Approaches for assembling a monolithic contract}
@@
 Instead, the contract itself needs a test run manager which handles this.
-A test run manager can either be implemented as another entrypoint, say \texttt{A\_m}, which then calls \texttt{A\_a} (or \texttt{A} in case of a)) $n$ times as an internal transaction.
+A test run manager can either be implemented as another entrypoint, say \texttt{A\_m}, which then calls \texttt{A\_a} (or \texttt{A} in case of a)) $n$ times as an internal operation.
+When extending the diagram for a) with the manager, the pipeline output thus look as shown in \figref{fig:monolithic_orchestration}.
+The output for b) is analogue.
+\begin{figure}[h]
+\centering
+  \includegraphics[width=0.5\textwidth]{figures/4-offline_tezos/pipeline_output_mono_ep.jpg}
+	\caption{Monolithic assembly with separate entrypoints for manager and assertion}
+	\label{fig:monolithic_orchestration}
+\end{figure}
 Another possibility is to create a separate manager contract that acts as a proxy, contains the manager code and internally calls the monolithic contract.
@@
 It's important to realize that neither baker nor validators can differentiate between entrypoints that have an associated assertion and those that do not.
-In order to avoid transaction failures caused by calling assertions that do not exist, the compiler has to add dummy managers for empty assertions that call the actual contract code immediately.\\
-% Description figures
-% -> txa special transaction type
-% managers use internal transactions to call contract n times
-% depending on protocol, validators use normal tx or another special tx type
-% req message needs to contain the derived name of the assertion ep -> derivation needs to be part of the "assertion mode". is this possible?
-% veto message: the txa op hash it refers to, an instance of a counterexample (not yet clear how this looks like)
+In order to avoid transaction failures caused by calling assertions that do not exist, the compiler has to add dummy managers for empty assertions that call the actual contract code immediately.
+\lstref{lst:manager} drafts the manager code for entrypoints with and without assertions in pseudocode.
+\begin{lstlisting}[label=lst:manager, caption=Implementation of the manager in pseudocode]
+%A (i : int) {
+	call(parent.A, i)
+}
 
+%A_m (i : int) {
+	n = compute_n(i)
+	Do j = 1 to n:
+		call(parent.A_a, i)
+}
+
+%B (i : int) {
+	call(parent.B, i)
+}
+
+%B_m (i : int) {
+	call(parent.B, i)
+}
+\end{lstlisting}
+
+\figref{fig:interaction_monolithic} and \ref{fig:interaction_monolithic_managertz} depict the interaction of the baker and validators with the resulting contracts on the blockchain for a variant using a single monolithic contract versus a hybrid solution.
+After calling a contract that includes an assertion, the baker has to keep the transaction in its mempool, a buffer where a node keeps prevalidated transactions not yet included in a block \todo{remove explanation if added to Tezos chapter}.
+Before it can be included, the transaction has to be kept there for a minimum amount of time, s.t.
+the validators have enough time to validate the assertion \todo{refer to blockchain protocol chapter if there is one}.
+The bakers therefore need to execute such transactions in a dedicated ``challenge'' mode, which could be signalled by using a special operation type to call such contracts.
+Operation types in Tezos are, i.a., transactions, originations or endorsements.
+By adding, for instance, a special transaction type (abbreviated by \texttt{txa} in the interaction diagrams), bakers can differentiate between normal transactions and those with assertions.
 \begin{figure}[h]
@@
 
-\subsubsection{Evaluation}
-Generell:
-- parent code has to be modified
-	+ show code example
-	+ decompilation necessary
-	+ compilation is more complex
-- doesn't work if the parent code is already originated
-- inflexible -> tightly coupled code
-	+ if the assertion code changes, the whole contract has to be reoriginated
+After prevalidating a transaction in the challenge mode, the baker then sends a request to the network to check the associated assertion.
+The request contains the address of the monolithic contract or manager, the operation hash (oph) of the prevalidated transaction, the derived entrypoint tag of the assertion and the parameter.
+The operation hash is used to relate a counterexample to the respective transaction.
+Upon receiving such a request, the validators call the assertion manager; what type of operation is used for is an open question for the protocol design.
+For efficiency, at most the test runs detecting a counterexample should be recorded on the blockchain, which would not be the case if validators use standard transactions.
+What has been left out so far in the offline design is the representation of a counterexample.
+\secref{} briefly discusses this as an open question and follow-up of this thesis \todo{secref}.
 
-ep assert + ep manager
-+ baker can call basic ep; validators call manager
-	-> cost efficient; contract is only executed once
-- only works with explicit ep -> parameter types!
-- complex compilation (1-2 eps per ep more)
-- readability
+\subsubsection{Evaluation of the monolithic approach}
+The presented implementations of the monolithic approach each have strengths and weaknesses.
+Generally, they all share a pivotal disadvantage - they require a modification of the parent contract.
+This not only complicates the compilation process by requiring a decompilation of the parent code and an interweaving of the assertion code, but it also restricts the integration of assertions to contracts that have not yet been originated on the blockchain.
+\lstref{lst:mono} shows the skeleton of a monolithic contract that results from the given parent and assertion contract; both the parameter type and the branching of the code body have to be adapted.
+Another problem are contract invocations using the default entrypoint: firstly, the derivation of the entrypoint for the assertion becomes considerably more complex, as no explicit tag is given.
+Secondly, the parameter cannot be passed unmodified to the assertion, because the parameter types in respect to the default entry point do not match.
+For instance, invoking the default entrypoint of \texttt{example\_monolithic.tz} (\lstref{lst:mono}) with parameter \texttt{Left 4} calls \texttt{A}, but the respective assertion \texttt{A\_a} expects the value as \texttt{Left (Left 4)}.
+\\
+Due to the tight coupling of parent and assertion code, this approach is also inflexible, since adaptions to either part require a recompilation and new origination of the whole code.
+\lstinputlisting[label=lst:mono, caption=Skeleton of a monolithic contract in Michelson, numbers=left]{listings/monolithic.tz}
 
-no ep assert + ep manager
-- contract code is also executed n times
-- only works with explicit ep -> parameter types!
-+ bypassing assertion not possible!
-+ less eps more readable? (aber nur bisschen)
+The distinct advantages and disadvantages of each combination of given implementation approaches are described briefly in the following matrix in \tabref{tab:mono_eval}.
+\begin{table}[h]
+	\centering
+	\newcommand{\tabitem}{~~\llap{\textbullet}~~}
+	\caption{Advantages and disadvantages of monolithic implementations}
+	\label{tab:mono_eval}
+	\subfloat[Monolithic w/ manager and assertion entrypoints] {
+		\centering
+		\begin{tabular}{ | p{0.5\linewidth} | p{0.5\linewidth} |}
+		\hline
+		\thead{Advantages} & \thead{Disadvantages} \\ \hline
+		\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+		\item Contract and assertion can be called separately $\rightarrow$ parent code is only executed once
+		\end{itemize} &
+		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+		\item More complex compilation; adds 1-2 entrypoints per native entrypoint
+		\item Less readability
+		\end{itemize} \\ \hline
+		\end{tabular}
+	}
 
-ep assert + contract manager
-+ less complex compilation -> just copy assertion code before the actual code (less entrypoint handling)
-+ if manager also has eps A and A\_m, the code and assertions can also be called separately
-+ modularity -> readability, a bit more flexibility (if manager code changes)
-- \^ even more eps -> 2-3 eps more
-- more boilerplate, more origination costs
+	\subfloat[Monolithic w/ manager entrypoints and prepended assertion] {
+		\centering
+		\begin{tabular}{ | p{0.5\linewidth} | p{0.5\linewidth} |}
+		\hline
+		\thead{Advantages} & \thead{Disadvantages} \\ \hline
+		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+		\item Bypassing the assertion is not possible
+		\end{itemize} &
+		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+		\item Cost inefficient - validators execute the assertion + code $n$ times
+		\item Also only works with explicit entrypoint tags
+		\end{itemize} \\ \hline
+		\end{tabular}
+	}
 
-no ep assert + contract manager
-- contract code is also executed n times
-+ bypassing assertion not possible!
-+ less complex compilation -> just copy assertion code before the actual code (less entrypoint handling)
-+ modularity
+	\subfloat[Hybrid w/ manager and assertion entrypoints] {
+		\centering
+		\begin{tabular}{ | p{0.5\linewidth} | p{0.5\linewidth} |}
+		\hline
+		\thead{Advantages} & \thead{Disadvantages} \\ \hline
+		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+		\item Contract and assertion can be called separately
+		\item Modularity $\rightarrow$ manager contract can be adapted independently
+		\item Readability
+		\end{itemize} &
+		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+		\item Higher initial origination costs due to more boilerplate code
+		\end{itemize} \\ \hline
+		\end{tabular}
+	}
 
-what happens to calls to default?
+	\subfloat[Hybrid w/ manager entrypoints and prepended assertion] {
+		\centering
+		\begin{tabular}{ | p{0.5\linewidth} | p{0.5\linewidth} |}
+		\hline
+		\thead{Advantages} & \thead{Disadvantages} \\ \hline
+		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+		\item Bypassing the assertion is not possible
+		\item Modularity
+		\item Readability
+		\end{itemize} &
+		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+		\item Cost inefficient - validators execute the assertion + code $n$ times
+		\item Higher initial origination costs due to more boilerplate code
+		\end{itemize} \\ \hline
+		\end{tabular}
+	}
+\end{table}
+
+\subsection{Approach 2: Modular contracts}
+With the modular approach, the assertion manager and each of the assertions are originated as separate contracts on the blockchain.
+The manager mirrors the interface of the parent contract, while each assertion each only has a single entrypoint which expects the raw parameter type.
+Due to the ``outsourcing'' of the assertion code, the parent contract remains pure and does not have to be modified.
+Similar to the hybrid solution from the last section, the manager calls the respective assertion contract $n$ times as an internal operation before calling the actual contract.
+In the case of empty assertions, it calls the parent contract immediately.
+Correspondingly, the pipeline outputs 1-$m$ contracts, where $m$ is the amount of entrypoints with an associated assertion, as depicted in \figref{fig:modular_assembly}.
+\begin{figure}[h]
+\centering
+  \includegraphics[width=0.9\textwidth]{figures/4-offline_tezos/pipeline_output_modular.jpg}
+	\caption{Modular assembly of assertion and manager code}
+	\label{fig:modular_assembly}
+\end{figure}
+
+In order to link the separate contracts to each other, the manager needs to know the addresses of the other contracts, which ultimately entails a fixed origination order.
+The independent assertion and parent contract(s) have been originated first, so that their addresses can be passed to the manager as initial storage values.
+If the storage is structured as a map from a unique identifier to an address, the entrypoints of the manager can then look up the address with its assigned identifier.
+The assignment of identifiers to entrypoints is hard-wired during the compilation.
+
+In the storage, the addresses could be stored in a mapping from a unique identifier
+
+\begin{figure}[h]
+\centering
+  \includegraphics[width=0.9\textwidth]{figures/4-offline_tezos/interaction_modular.jpg}
+	\caption{Interaction with a modular contract}
+	\label{fig:interaction_modular}
+\end{figure}
+
+\subsubsection{Evaluation of the modular approach}
+- fixes the problem of the monolithic approach, where calls to default cause problems -> mirrored interface can simply pass the parameter on as is to the parent and the extracted raw value to the assertion
+- parent code doesn't have to be touched -> works for originated contracts
+- flexibility -> case contracts independent of the rest; replace manager (with or without case contracts), parent with manager
+- assertions can be bypassed in any case -> big security issue
 
 \begin{itemize}
-\item Assertions are appended to the parent as separate entry points
-\item Parent contract has to be modified (parameter type \& addendum)
-\item Problems/Drawbacks:
+\item The address of the assertion contract needs to be provided in some way
 	\begin{itemize}
-	\item entrypoint names necessary - otherwise no unambiguous assignment
-	\item parameter types of original ep \& assertion ep are different
-	\item e.g. \%A and \%A\_a cannot be called with the same parameter (if not called explicitly; ref. \ref{lst:mono_unnamed} line 24, 25.)
-	\item Possible solution:
+	\item [a)] Parent storage contains the address of its assertion contract
 		\begin{itemize}
-		\item all eps in the parent and assertion contract need to have a \%name \verb|->| calling both eps explicitly allows using the same parameter (ASAIK) ; ref. \ref{lst:mono} line 24, 25.
-		\item Assign dummy names if none are given - effort?
-		\item what to do with calls to \%default?
+		\item Parent contract needs to be modified (storage declaration, every storage access \& return value)
+		\item Assertion contract must be originated first, so that address can be passed into initial storage of parent
+		\item Baker needs to retrieve address from contract storage (no obvious standard way to do this - storages can look differently)\\
+		 \verb|->| BigMap?
+		\end{itemize}
+	\item [b)] Address of the assertion contract is a parameter of the transaction
 		\begin{itemize}
-			\item Baker would need to
-			\item 1) look up entrypoints of contract 
-			\item 2) check which type matches \& find out the ep name
-			\item 3) derive assertion ep name from that
-			\end{itemize}
-		\item how to assign entry points given without names in .tza to their respective parent eps? \ref{lst:mono_unnamed} line 10, 11.
+		\item Address must be known to the caller
+		\item Decouples parent and assertion contract %\sout{(if calling assertion from parent is not necessary)}
+		\item Safety issue: can be passed a contract with correct type that never returns a counterexample
+		\item Parent contract doesn't need to be touched
 		\end{itemize}
 	\end{itemize}
-\item EP names of the assertion code need to have a fixed pattern, s.t. the bakers know how to call them
-\item Similarly to strategy 1, there probably needs to be "empty" assertion code for normal eps
 \end{itemize}
-
-%\ref{fig:separate_contract_v2}:
-%\begin{figure}[h]
-%	\centering
-%  \includegraphics[width=\textwidth]{assembly_monolith}
-%	\caption{Interaction with a monolithic contract}
-%	\label{fig:monolithic_contract}
-%\end{figure}
-
-%\lstinputlisting[label=lst:mono, caption=Monolithic assembly w/ ep names, numbers=left]{monolithic.tz}
-%\lstinputlisting[label=lst:mono_unnamed, caption=Monolithic assembly w/o ep names, numbers=left]{monolithic_unnamed.tz}
-
-\subsection{Approach 2: }
 

### 2021-04-07 assertions/doc/thesis-bernhardt/chapters/4-offline_design_tezos.tex
Compiler - direct approach

@@
 
+\subsection{failwith 2.0}
+\draft{}
+- failwith returns a failure string
+- assertion execution -> random number is generated
+- if counterexample is found, the random number somehow has to be extracted from the contract execution, s.t. other validators can verify the counterexample
+- some special failure operation may be needed that returns the that value
+- as representation of a counterexample is still an open question, there are not specifics yet as to how this instruction is supposed to look like (or if it is needed at all)
+
 \section{Orchestration of contract and assertions}
@@
 A test run manager can either be implemented as another entrypoint, say \texttt{A\_m}, which then calls \texttt{A\_a} (or \texttt{A} in case of a)) $n$ times as an internal operation.
+Because transactions on Tezos guarantee either total success or total failure \cite{tezos_docs}, the execution is stopped as soon as one of the internal operation fails, i.e.
+detects a counterexample.
 When extending the diagram for a) with the manager, the pipeline output thus look as shown in \figref{fig:monolithic_orchestration}.
@@
 In order to avoid transaction failures caused by calling assertions that do not exist, the compiler has to add dummy managers for empty assertions that call the actual contract code immediately.
-\lstref{lst:manager} drafts the manager code for entrypoints with and without assertions in pseudocode.
+\lstref{lst:manager} drafts the manager code for entrypoints with and without assertions in pseudocode (assuming a purely monolithic implementation).
 \begin{lstlisting}[label=lst:manager, caption=Implementation of the manager in pseudocode]
-%A (i : int) {
-	call(parent.A, i)
-}
+%A (i : int) { ... }
+
+%A_a (i : int) { .. assert (...) }
 
@@
 	n = compute_n(i)
-	Do j = 1 to n:
-		call(parent.A_a, i)
+	Do m = 1 to n
+		call(self, A_a, i)
 }
 
-%B (i : int) {
-	call(parent.B, i)
-}
+%B (j : int) { ... }
 
-%B_m (i : int) {
-	call(parent.B, i)
-}
+%B_m (j : int) { call(self, B, j) }
 \end{lstlisting}
@@
 \centering
-  \includegraphics[width=0.9\textwidth]{figures/4-offline_tezos/pipeline_output_modular.jpg}
+  \includegraphics[width=0.6\textwidth]{figures/4-offline_tezos/pipeline_output_modular.jpg}
 	\caption{Modular assembly of assertion and manager code}
@@
 If the storage is structured as a map from a unique identifier to an address, the entrypoints of the manager can then look up the address with its assigned identifier.
-The assignment of identifiers to entrypoints is hard-wired during the compilation.
+The assignment of identifiers to entrypoints is hard-wired during the compilation, as is shown in the pseudocode for the manager contract in \lstref{lst:manager_modular}.
+The corresponding initial storage for the given contract is the mapping \texttt{{0: <addr parent>; 1: <addr A\_a>; 2: <addr B\_a}}.
+\begin{lstlisting}[label=lst:manager_modular, caption=Implementation of the modular manager in pseudocode]
+storage (map int address);
 
-In the storage, the addresses could be stored in a mapping from a unique identifier
+%A (i : int) {
+	n = compute_n(i)
+	Do m = 1 to n:
+		call(storage.get(1), i)
+	call(storage.get(0), A, i)
+}
 
+%B (j : int) {
+	n = compute_n(j)
+	Do m = 1 to n:
+		call(storage.get(2), j)
+	call(storage.get(0), B, j)
+}
+\end{lstlisting}
+
+The interaction with the contracts in the modular approach is shown in \figref{fig:interaction_modular}.
+Even though the transactions shown in the diagram state an explicit entrypoint tag, contracts can, of course, also be called through \texttt{\%default}.
+In that case, the parameter passed with the internal operations to \texttt{A\_a.tz} is not equivalent, but the raw parameter value.
 \begin{figure}[h]
@@
 \subsubsection{Evaluation of the modular approach}
-- fixes the problem of the monolithic approach, where calls to default cause problems -> mirrored interface can simply pass the parameter on as is to the parent and the extracted raw value to the assertion
-- parent code doesn't have to be touched -> works for originated contracts
-- flexibility -> case contracts independent of the rest; replace manager (with or without case contracts), parent with manager
-- assertions can be bypassed in any case -> big security issue
-
-\begin{itemize}
-\item The address of the assertion contract needs to be provided in some way
-	\begin{itemize}
-	\item [a)] Parent storage contains the address of its assertion contract
-		\begin{itemize}
-		\item Parent contract needs to be modified (storage declaration, every storage access \& return value)
-		\item Assertion contract must be originated first, so that address can be passed into initial storage of parent
-		\item Baker needs to retrieve address from contract storage (no obvious standard way to do this - storages can look differently)\\
-		 \verb|->| BigMap?
-		\end{itemize}
-	\item [b)] Address of the assertion contract is a parameter of the transaction
-		\begin{itemize}
-		\item Address must be known to the caller
-		\item Decouples parent and assertion contract %\sout{(if calling assertion from parent is not necessary)}
-		\item Safety issue: can be passed a contract with correct type that never returns a counterexample
-		\item Parent contract doesn't need to be touched
-		\end{itemize}
-	\end{itemize}
-\end{itemize}
+This approach fixes the two central problems of the monolithic approach: by mirroring the interface of the parent contract, the parameters passed to the manager contract can be forwarded directly to the parent contract, regardless of whether the default or an explicit entrypoint was called.
+As sum type parameters are stripped to the raw values inside the code block (ref.
+\lstref{lst:mono}), they can be passed to the assertion contract without further ado.
+Furthermore, the parent contract does not need to be modified, which leads to a much simpler compilation process and allows to extend already originated contracts with assertions.
+Due to its modularity, adaptions to either contract do not entail the recompilation and origination of all components.
+The manager is the only component with tight coupling, thus adaptions regarding the manager do not affect any other component.
+Adaptions to single assertions or the parent affect themselves plus the manager.
+In order to optimize this and break the tight coupling, one could be inclined to add a setter entrypoint to the manager (as a sort of dependency injection).
+This, however, would break the mirroring of the parent contract and is thus not possible without annulling one of the key strengths of the design.\\
+The approach essentially has to weaknesses: on the one hand, the assertion and the parent cannot be called separately, as they are linked together by the manager.
+As a result, both the baker and validators execute the assertion, as well as the parent contract, which increases the cost of the contract execution.
+On the other hand, it exposes a security vulnerability, given that assertions can be bypassed by calling the parent contract directly with unevaluated parameters.
+This iteration of the design
+does not demand to close this vulnerability, hence possible solutions are not discussed in this thesis.
 
@@
 \\
-As an exemplification, consider a Michelson contract with five entrypoints (including the default entrypoint):
+As an exemplification, consider a Michelson contract with five entrypoints (including the \texttt{\%default}):
 \begin{lstlisting}[numbers=none, language=Michelson]
@@
 \subsection{Compiler}
-The transformed and type checked assertion AST needs to be retargeted to Michelson code.
+The transformed and type checked assertion AST needs to be retargeted to Michelson code according to the orchestration scheme.
+Since the modular approach is less complex to implement and avoids having to decompile the parent code, this section describes a compiler that assembles the assertion and contract code according to \figref{fig:modular_assembly}.
+The target language of the compiler of the pipeline can either be Michelson directly, or another high-level language which supports Michelson as a target.
+\secref{sec:tezos} lists some examples of such languages.
+The chosen language then serves as an intermediate representation (IR) of the assertion and manager code, which is ultimately compiled to Michelson by the compiler of the language.
+The outline of the implementation, advantages and disadvantages, as well as the entailed modifications to the pipeline are described and discussed in the following for both approaches.
 
-\draft{}
-\begin{itemize}
-\item Orchestration strategies
-	\begin{itemize}
-	\item monolithic vs. modular
-	\item advantages/disadvantages
-	\item \# validators in Tezos \& how to have them run n test runs
-	\item security mechanism? (prevent ``dodging'' assertions)
-	\end{itemize}
-\item Compilation strategies (direct vs. IR)
-\end{itemize}
+%- compilation strategies (direct vs. IR)
+%- output the initial storage configuration for the manager
+%- input: confidence threshold for computation of n
+%- formel for calc n
+
+\subsubsection{Direct compilation}
+With the direct approach, the compiler generates Michelson code, i.e., code for a stack machine.
+Based on the simplicity of stack machines and the assumption that the compiler does not need to generate optimal code, its implementation is expected to be simple \cite{cs5641}\cite{ferr_compiler}\cite{stach_machine}.
+In addition to that, the resulting contracts contain repeating patterns for each input, which can be exploited by using template code during compilation.
+
+\paragraph{Assertion contracts}
+Since the assertions are independent of each other and the manager code, each of them can be compiled in isolation to a separate Michelson program.
+The generated code of the assertion body and the parameter type can be plugged into a template that already contains the necessary boilerplate code for a contract.
+\lstref{lst:contract_templ} shows a possible template - the placeholder \texttt{<?>} marks the locations where the individual code is inserted.
+Lines 3-5 prepare the stack, s.t.
+the parameter and storage are the two top elements.
+The lines below the placeholder for the body clean up the stack and leaves it according to calling convention, i.e., the program returns an empty list of internal operations and the unit storage.
+\lstinputlisting[label=lst:contract_templ, language=Michelson, caption=Template of an assertion contract in Michelson, numbers=left]{listings/assertion_template.tz}
+
+\paragraph{Manager contract}
+Given that the manager contract mirrors the parent contract and assuming that the proposal for the storage type from \lstref{lst:manager_modular} is adopted, the \texttt{parameter} and \texttt{storage} primitives are already fixed.
+Algorithm \ref{alg:compile_manager} shows the outline of an algorithm that builds the \texttt{code} body recursively:
+\begin{algorithm}
+\caption{Recursive algorithm for building the manager contract during compilation}\label{alg:compile_manager}
+	\begin{algorithmic}[0]
+	\State global storage = \{0: parent\}
+	\State global i = 1
+	\Function{compile}{param\_ty}
+	\If{ty = Or(l,r)}
+	\State code\_left = "IF\_LEFT {" + compile(l) + "}"
+	\State code\_right = "{" + compile(r) + "}"
+	\State \Return code\_left + code\_right
+	\Else
+	\If{assertion exists for this entrypoint}
+	\State code = generate\_loop(ty, i)
+	\State storage.add(i++, entrypoint tag)
+	\Else
+	\State code = generate\_forward(ty)
+	\EndIf
+	\State \Return code
+	\EndIf
+	\EndFunction
+	\end{algorithmic}
+\end{algorithm}
+
+% add comments to algorithm
+% some boilerplate before and after the branching is missing in the algorithm
+% generate_loop template; i is hardwired
+% generate_forward for empty assertion; template
+% example/template loop for sorted list; for calculating n, a threshold of c = 1/e assumed (ergo t = |list|) generated with Liquidity; liq source given in section for the IR approach
+
+advantage: all-in-one pipeline from parsing to Michelson code; other than tezos libs no dependencies to external tools
+disadvantages:
+testing -> a bit more complex, from Michelson it's not so easy to see whether it does the correct thing
+use type checker of the Tezos libs for sanity check; type checker is protocol dependent and thus introduces the need for versioning
+
+\subsubsection{Compiling to an IR}
 

### 2021-04-07 assertions/doc/thesis-bernhardt/michelson_highlighting.tex
Compiler - direct approach

@@
 	keywordstyle=[2]\color{teal}\bfseries,
+	keywords=[3]{Do, call, assert},
+	keywordstyle=[3]\color{violet}\bfseries,
 	identifierstyle=\color{black},

### 2021-04-07 assertions/doc/thesis-bernhardt/chapters/4-offline_design_tezos.tex
Compilation general part

@@
 \cite{tezos_docs}
+
+\subsubsection{Internal operations}
+Smart contracts are able to call other smart contracts by emitting internal operations.
+The return type of Michelson programs is a tuple of a list of internal operations and the updated storage.
+Thus, after the actual contract has been executed, the operations of the returned list are run in sequence.
+Since the internal operations may in turn also emit internal operations, they are put into a queue and are processed in order.
+As an example, \figref{fig:internal_ops} shows an execution order of two external transactions, i.e., transactions which have been initiated by a user account, and their internal operations.
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\linewidth]{figures/4-offline_tezos/internal_ops}
+\caption{Execution order of two external operations and their internal operations; Source: \cite{tezos_docs}}
+\label{fig:internal_ops}
+\end{figure}
+
+Both external and internal operations can fail if the source does not have enough balance to spend the specified amount, a gas limit was reached or if a program fails when reaching a \texttt{FAILWITH} instruction.
+If a failure occurs, the whole sequence fails and all changes up to the point of failure are reverted.
 
@@
 the bakers and validators execute the assertion before the actual contract code.
-The orchestration does not only include the linking of assertion and contract code, but also a mechanism to execute an assertion $n$ times depending on the domain space that needs to be checked.
+The orchestration does not only include the linking of assertion and contract code, but also a mechanism to execute an assertion $t$ times depending on the domain space that needs to be checked.
 There are basically two approaches - the assertion and contract code can be assembled into a single monolithic contract, or they can be originated separately as standalone contracts.
@@
 \\
-Both approaches, however, do not yet provide any means to have validators execute the assertions $n$ times.
-Since only the contract itself knows how to calculate $n$ (as per the range(s) of the random generator(s)), it cannot be passed to the validators as a parameter to the validation request.
+Both approaches, however, do not yet provide any means to have validators execute the assertions $t$ times.
+Since only the contract itself knows how to calculate $t$ (as per the range(s) of the random generator(s)), it cannot be passed to the validators as a parameter to the validation request.
 Instead, the contract itself needs a test run manager which handles this.
-A test run manager can either be implemented as another entrypoint, say \texttt{A\_m}, which then calls \texttt{A\_a} (or \texttt{A} in case of a)) $n$ times as an internal operation.
+A test run manager can either be implemented as another entrypoint, say \texttt{A\_m}, which then calls \texttt{A\_a} (or \texttt{A} in case of a)) $t$ times as an internal operation.
 Because transactions on Tezos guarantee either total success or total failure \cite{tezos_docs}, the execution is stopped as soon as one of the internal operation fails, i.e.
@@
 		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-		\item Cost inefficient - validators execute the assertion + code $n$ times
+		\item Cost inefficient - validators execute the assertion + code $t$ times
 		\item Also only works with explicit entrypoint tags
@@
 		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-		\item Cost inefficient - validators execute the assertion + code $n$ times
+		\item Cost inefficient - validators execute the assertion + code $t$ times
 		\item Higher initial origination costs due to more boilerplate code
@@
 
-\subsection{Approach 2: Modular contracts}
+\subsection{Approach 2: Modular contracts}\label{sec:modular}
 With the modular approach, the assertion manager and each of the assertions are originated as separate contracts on the blockchain.
@@
 Due to the ``outsourcing'' of the assertion code, the parent contract remains pure and does not have to be modified.
-Similar to the hybrid solution from the last section, the manager calls the respective assertion contract $n$ times as an internal operation before calling the actual contract.
+Similar to the hybrid solution from the last section, the manager calls the respective assertion contract $t$ times as an internal operation before calling the actual contract.
 In the case of empty assertions, it calls the parent contract immediately.
@@
 The chosen language then serves as an intermediate representation (IR) of the assertion and manager code, which is ultimately compiled to Michelson by the compiler of the language.
-The outline of the implementation, advantages and disadvantages, as well as the entailed modifications to the pipeline are described and discussed in the following for both approaches.
+After specifying the steps of the compilation in a general way, the compilation approaches are described and discussed in more detail in \secref{sec:direct} and \ref{sec:IR}.
 
-%- compilation strategies (direct vs. IR)
-%- output the initial storage configuration for the manager
-%- input: confidence threshold for computation of n
-%- formel for calc n
-
-\subsubsection{Direct compilation}
-With the direct approach, the compiler generates Michelson code, i.e., code for a stack machine.
-Based on the simplicity of stack machines and the assumption that the compiler does not need to generate optimal code, its implementation is expected to be simple \cite{cs5641}\cite{ferr_compiler}\cite{stach_machine}.
-In addition to that, the resulting contracts contain repeating patterns for each input, which can be exploited by using template code during compilation.
-
-\paragraph{Assertion contracts}
+\subsubsection{Compilation of the assertion contracts}
 Since the assertions are independent of each other and the manager code, each of them can be compiled in isolation to a separate Michelson program.
 The generated code of the assertion body and the parameter type can be plugged into a template that already contains the necessary boilerplate code for a contract.
-\lstref{lst:contract_templ} shows a possible template - the placeholder \texttt{<?>} marks the locations where the individual code is inserted.
-Lines 3-5 prepare the stack, s.t.
-the parameter and storage are the two top elements.
-The lines below the placeholder for the body clean up the stack and leaves it according to calling convention, i.e., the program returns an empty list of internal operations and the unit storage.
-\lstinputlisting[label=lst:contract_templ, language=Michelson, caption=Template of an assertion contract in Michelson, numbers=left]{listings/assertion_template.tz}
 
-\paragraph{Manager contract}
-Given that the manager contract mirrors the parent contract and assuming that the proposal for the storage type from \lstref{lst:manager_modular} is adopted, the \texttt{parameter} and \texttt{storage} primitives are already fixed.
-Algorithm \ref{alg:compile_manager} shows the outline of an algorithm that builds the \texttt{code} body recursively:
+\subsubsection{Compilation of the manager contract}
+Given that the manager contract mirrors the parent contract and assuming that the proposal for the storage type from \lstref{lst:manager_modular} is adopted, the type declarations can be translated directly to the target language.
+Algorithm \ref{alg:compile_manager} shows the outline of a simplified algorithm that builds the code body recursively.
+For simplicity, entrypoints that take a sum type as parameter (e.g.
+\texttt{(or \%AB int int)} are not considered in the algorithm.
+However, in the actual compiler implementation they need to be taken care of.
 \begin{algorithm}
-\caption{Recursive algorithm for building the manager contract during compilation}\label{alg:compile_manager}
+\caption{Simplified recursive algorithm for building the manager contract}\label{alg:compile_manager}
 	\begin{algorithmic}[0]
-	\State global storage = \{0: parent\}
-	\State global i = 1
-	\Function{compile}{param\_ty}
+	\State global storage = \{0: <parent>\} \Comment{Stores the mapping of ids to entrypoints}
+	\State global i = 1 \Comment{Counter generating unique ids}
+	\Function{compile}{parent parameter type}
 	\If{ty = Or(l,r)}
-	\State code\_left = "IF\_LEFT {" + compile(l) + "}"
-	\State code\_right = "{" + compile(r) + "}"
+	\State code\_left = compile(l)
+	\State code\_right = compile(r)
 	\State \Return code\_left + code\_right
@@
 
-% add comments to algorithm
-% some boilerplate before and after the branching is missing in the algorithm
-% generate_loop template; i is hardwired
+The function \texttt{generate\_loop} generates code that does the following:
+\begin{enumerate}
+\item Retrieve the assertion contract and parent contract addresses from storage
+\item Calculate $t$
+\item Build a list of $t$ internal operations that call the assertion contract
+\item Return the list of emitted operations and the unchanged storage
+\end{enumerate}
+By passing the next id $i$ to the function, the access to the storage can be hard-wired into the generated code.
+The address of the parent contract is assumed to always be stored with the id 0.
+\secref{sec:prob_threshold} stated a formula for calculating $t_total$ with the parameters $n$, the size of the search space, and the probability threshold $c$.
+While $n$ can be calculated from the ranges of the random generator(s), $c$ must be given as parameter to the compiler through the CLI.
+After $t_total$ has been computed, a divison by 32, i.e., the number of validators, returns the upper bound of the loop.
+\\
+\texttt{generate\_forward} can be generated from a simple template with the id as the only variant and only consists of  an access to the storage and the emission of an internal operation.
+
+\subsubsection{Output}
+Besides the target code for the manager and assertion contracts, the compiler should return a piece of template code for the correct storage initialization of the manager.
+Since this code is passed to the origination operation, it must be in Michelson regardless of the compilation target language.
+The placeholders or accompanying info should be descriptive enough, s.t.
+the user can plug in the corresponding addresses after the origination of the parent and assertion contracts.
+For the example manager contract given in \secref{sec:modular}, the corresponding text output could be\\
+\texttt{(Elt 0 <addr parent>; Elt 1 <addr A\_a>; Elt 2 <addr B\_a>)}.
+
+\subsubsection{Direct compilation}\label{sec:direct}
+With the direct approach, the compiler generates Michelson code, i.e., code for a stack machine.
+Based on the simplicity of stack machines and the assumption that the compiler does not need to generate optimal code, its implementation is expected to be simple \cite{cs5641}\cite{ferr_compiler}\cite{wiki:stack_machine}.
+In addition to that, the resulting contracts contain repeating patterns for each input, which can be exploited by using template code during compilation.
+
+\paragraph{Assertion contracts}
+\lstref{lst:contract_templ} shows a possible template for an assertion contract - the placeholder \texttt{<?>} marks the locations where the individual code is inserted.
+Lines 3-5 prepare the stack, s.t.
+the parameter and storage are the two top elements.
+The lines below the placeholder for the body clean up the stack and leaves it according to calling convention, i.e., the program returns an empty list of internal operations and the unit storage.
+\lstinputlisting[label=lst:contract_templ, language=Michelson, caption=Template of an assertion contract in Michelson, numbers=left]{listings/assertion_template.tz}
+
+\paragraph{Manager contract}
+Given that the manager contract mirrors the parent contract and assuming that the proposal for the storage type from \lstref{lst:manager_modular} is adopted, the \texttt{parameter} and \texttt{storage} primitives are already fixed.
+\algref{alg:compile_manager_direct} shows the outline of an algorithm that builds the \texttt{code} body recursively:
+\begin{algorithm}
+\caption{Modification of algorithm \ref{alg:compile_manager} for direct compilation}\label{alg:compile_manager_direct}
+	\begin{algorithmic}[0]
+	\State ...
+	\Function{compile}{parent parameter type}
+	\If{ty = Or(l,r)} \Comment{Compile sum types to a branching}
+	\State code\_left = "IF\_LEFT {" + compile(l) + "}"
+	\State code\_right = "{" + compile(r) + "}"
+	\State \Return code\_left + code\_right
+	\EndIf
+	\State ...
+	\EndFunction
+	\end{algorithmic}
+\end{algorithm}
+
+As the algorithm generates the core code for each entrypoint only, another code sequence that prepares the stack similar to \lstref{lst:contract_templ} must be prepended.
+
+% generate_loop template; i is hardwired;  (works for contract w 1 entrypoint), last op first
 % generate_forward for empty assertion; template
@@
 
-\subsubsection{Compiling to an IR}
+\subsubsection{Compiling to an IR}\label{sec:IR}
 

### 2021-04-08 assertions/doc/thesis-bernhardt/chapters/4-offline_design_tezos.tex
Compiler - finished direct, started IR

@@
 Omitting the actual program, the contract type declaration looks as follows:
-\begin{lstlisting}[language=Michelson, numbers=none, caption=Michelson contract with two entrypoints]
+\begin{lstlisting}[language=Michelson, numbers=none, caption=Michelson contract with two entrypoints, label=lst:entrypoints]
 parameter (or (int %isPrime) (string %isUpper));
@@
 \end{lstlisting}
-The type notations, as well as syntax and stack patterns are listed in \cite{tezos_docs}.\\
+The type notations, as well as syntax and stack patterns are listed in \cite{tezos_docs}.
+
+Since Michelson is implemented in the protocol-specific part of the blockchain code, adding new instructions require a protocol update.
+The instruction must be added i.a.
+to the list of tokens, its computation to the interpreter and its typing rules to the type checker.
+As the computation of the new instruction must be paid for like any other instruction, the protocol must also specify a gas cost.
+Previous extensions to the Michelson language, such as \cite{tezos_michelson_ext}, can be used as a guideline for the implementation and the gas cost specification in \cite{tezos_repo_gas} as an orientation to how high the gas costs should be scheduled for comparable instructions.
 
@@
 \subsubsection{Direct compilation}\label{sec:direct}
-With the direct approach, the compiler generates Michelson code, i.e., code for a stack machine.
-Based on the simplicity of stack machines and the assumption that the compiler does not need to generate optimal code, its implementation is expected to be simple \cite{cs5641}\cite{ferr_compiler}\cite{wiki:stack_machine}.
-In addition to that, the resulting contracts contain repeating patterns for each input, which can be exploited by using template code during compilation.
+With the direct approach, the compiler generates Michelson code and hence code for a stack machine.
+Based on the simplicity of stack machines and the assumption that it does not need to generate optimal code, the compiler is expected to be simple \cite{cs5641}\cite{ferr_compiler}\cite{wiki:stack_machine}.
+As already indicate in the general part, the resulting contracts contain repeating structures and patterns for each input, which can be exploited by using template code during compilation.
+After compilation, the Michelson programs can be sanity-checked by type checking them using the provided Tezos libraries.
 
@@
 the parameter and storage are the two top elements.
-The lines below the placeholder for the body clean up the stack and leaves it according to calling convention, i.e., the program returns an empty list of internal operations and the unit storage.
-\lstinputlisting[label=lst:contract_templ, language=Michelson, caption=Template of an assertion contract in Michelson, numbers=left]{listings/assertion_template.tz}
+The lines below the placeholder for the body clean up the stack and leave it according to calling convention, i.e., the program returns an empty list of internal operations and the unit storage.
+\lstinputlisting[label=lst:contract_templ, language=Michelson, caption=Template code for assertion contracts in Michelson, numbers=left]{listings/assertion_template.tz}
 
 \paragraph{Manager contract}
-Given that the manager contract mirrors the parent contract and assuming that the proposal for the storage type from \lstref{lst:manager_modular} is adopted, the \texttt{parameter} and \texttt{storage} primitives are already fixed.
-\algref{alg:compile_manager_direct} shows the outline of an algorithm that builds the \texttt{code} body recursively:
+The generation of the \texttt{parameter} and \texttt{storage} primitives is trivial --- the parameter type can be carried over directly from the parent contract, whereas the storage type is a constant (\texttt{(map int address)}).
+Based on the algorithm given previously, the code body is generated by nesting \texttt{IF\_LEFT} instructions recursively (cf.
+\lstref{lst:entrypoints}).
+The adapted algorithm is given in Algorithm \ref{alg:compile_manager_direct}.
 \begin{algorithm}
@@
 
-As the algorithm generates the core code for each entrypoint only, another code sequence that prepares the stack similar to \lstref{lst:contract_templ} must be prepended.
+Owing to Michelson being a low-level language, the templates for the functions \texttt{generate\_loop} and \texttt{generate\_forward} go beyond the scope of this subsection.
+In order to provide an idea of how the generated code could look like, appendix \ref{apx:manager_michelson} contains two example contracts, one of which contains manager code for a non-empty and the other one for an empty assertion.
+The code was generated by the Liquidity compiler from two contracts written in Liquidity, as this provides a more compact and readable representation of the program logic.
+The corresponding source code can be found in \secref{sec:IR}.
 
-% generate_loop template; i is hardwired;  (works for contract w 1 entrypoint), last op first
-% generate_forward for empty assertion; template
-% example/template loop for sorted list; for calculating n, a threshold of c = 1/e assumed (ergo t = |list|) generated with Liquidity; liq source given in section for the IR approach
-
-advantage: all-in-one pipeline from parsing to Michelson code; other than tezos libs no dependencies to external tools
-disadvantages:
-testing -> a bit more complex, from Michelson it's not so easy to see whether it does the correct thing
-use type checker of the Tezos libs for sanity check; type checker is protocol dependent and thus introduces the need for versioning
+\paragraph{Evaluation}
+Compiling to Michelson directly is beneficial due of several reasons - the pipeline stays streamlined and outputs the final contracts ready for origination.
+It does not introduce dependencies to external tools and their support for new protocol versions of Tezos.
+Besides, the new instructions only have to be added to Tezos' protocol code, whereas using external tools and languages would need to be patched as well in order to support them.
+\\
+When it comes to verifying the compiler and integration testing of the pipeline, however, the low-level output causes more complexity than a high-level output.
+Due to the extend and restricted readability of non-trivial Michelson programs, their correctness is not always apparent in an instant.
+Tests can, on the one hand, compare the output with verified target contracts for a range of inputs, which requires a lot of Michelson code written by hand for each input.
+They, in turn, can also be prone to errors.
+On the other hand, the generated contracts can be tested as a black box using the test frameworks provided by Tezos, which use sandboxed networks to interact with contracts-under-test.
 
 \subsubsection{Compiling to an IR}\label{sec:IR}
+Instead of generating Michelson code directly, the compiler could also generate code in one of the high-level languages that provide a compiler with Michelson as a target.
+The output of the pipeline is then passed to this compiler in order to retrieve the final contracts.
+If the toolchain of the intermediate language doesn't provide a programmatic interface, the pipeline thus has to be extended with a separate step of procedure, as shown in \figref{fig:pipeline_liq}.
+This section demonstrates the implementation of this approach on the basis of Liquidity, hence the corresponding file extension \texttt{.liq}.
+\begin{figure}[h]
+\centering
+\includegraphics[width=\linewidth]{figures/4-offline_tezos/pipeline_liq}
+\caption{Pipeline with IR compilation and an external toolchain}
+\label{fig:pipeline_liq}
+\end{figure}
+
+\paragraph{Assertion contracts}
+\lstinputlisting[label=lst:contract_templ_liq, language=Michelson, caption=Template code for assertion contracts in Liquidity, numbers=left]{listings/assertion_template.liq}
+
+\paragraph{Manager contract}
+\lstinputlisting[label=lst:manager_templ_liq, language=Michelson, caption=Manager code in Liquidity for an entrypoint with a non-empty assertion, numbers=left]{listings/manager_loop.liq}
+
+\lstinputlisting[label=lst:manager_templ_liq, language=Michelson, caption=Manager code in Liquidity for an entrypoint with an empty assertion, numbers=left]{listings/manager_forward.liq}
+
+\paragraph{Evaluation}
++ optimization (Liq compiler)
++ testing: easier to verify correctness, as it reads like an ocaml program
+	+ compiler of hl language already tested -> only check if IR is correct
++ variable support -> variables in assertion easier to implement?
 
@@
 \item Tezos specific costs analysis of chosen orchestration strategy -> PROBLEM: high n might reach operation gas limit?
-\item How can bakers differentiate between transactions to ”normal” SC and SCs with assertions?
 \item Representation of counterexamples; how to verify them?
 \item Basic approach for proofs?
-\item Usage pipeline
 \end{itemize}
-
-%- Vorschlag von HA: geht so nur für counterexamples.
-%- Case Proof-modus: some approval message has to be send actively if no assertion failed.%
-%	-> check if transaction fails? würde so ein mechanismus gehen? call case contracts n times. nach n times wird contract aber nicht aufgerufen
-%	-> oder: case contracts callen parent wenn property check successful; nicht möglich, da dann manager contract nichts davon weiß

### 2021-04-08 assertions/doc/thesis-bernhardt/chapters/appendix.tex
Compiler - finished direct, started IR

@@
 				 caption=\lstref{lst:nth_liq} compiled to Michelson]{listings/nth.tz}
+
+\chapter{Manager contract code in Michelson}\label{apx:manager_michelson}
+\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
+				 backgroundcolor=\color{cverbbg},
+				 linewidth=14cm,
+				 xleftmargin=0.5cm,
+				 frame=lr,
+				 framesep=8pt,
+				 framerule=0pt,
+				 captionpos=b,
+				 numbers=none,
+				 language=Michelson,
+				 label=lst:manager_michelson_loop,
+				 caption=Manager code in Michelson for an entrypoint with a non-empty assertion (wrapped in contract boilerplate code)]{listings/manager_loop.tz}
+
+\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
+				 backgroundcolor=\color{cverbbg},
+				 linewidth=14cm,
+				 xleftmargin=0.5cm,
+				 frame=lr,
+				 framesep=8pt,
+				 framerule=0pt,
+				 captionpos=b,
+				 numbers=none,
+				 language=Michelson,
+				 label=lst:manager_michelson_forward,
+				 caption=Manager code in Michelson for an entrypoint with an empty assertion (wrapped in contract boilerplate code)]{listings/manager_forward.tz}

### 2021-04-08 assertions/doc/thesis-bernhardt/michelson_highlighting.tex
Compiler - finished direct, started IR

--- 2021-03-10 assertions/doc/thesis-bernhardt/michelson_highlighting.tex
@@
 	keywordstyle=[2]\color{teal}\bfseries,
+	keywords=[3]{Do, call, assert, failwith},
+	keywordstyle=[3]\color{violet}\bfseries,
 	identifierstyle=\color{black},

### 2021-04-09 assertions/doc/thesis-bernhardt/chapters/2-use_case_analysis.tex
IR done; add cost model; cost analysis

@@
 \section{Cost analysis}
+In order to be able to evaluate whether distributed assertion checking can indeed lower the cost in comparison to a local verification, the cost of checking a formula on the blockchain needs to be formalized.
+Since this thesis describes an implementation of the approach on the Tezos blockchain, the following costs refer to that specific gas model, s.t.
+the results of the cost analyses are comparable.
+The gas model of Tezos is described briefly in \secref{sec:tezos}.
+\\
+According to the gas model, the total gas consumption of a transaction $T(src,\, dst=C,\, arg, \, ...)$ to an originated contract $C(storage, \, parameter\, type, \, code)$ is calculated by \eqref{eq:gas_transaction}:
+\begin{align}\label{eq:gas_transaction}
+\begin{split}
+GasConsumed_{transaction} = \quad &read(code) \\
++& \, gasRead(storage) \\
++& \, gasDeserialize(storage, \, arg) \\
++& \, gasParseType(parameter \, type, \, storage) \\
++& \, gasParseData(storage, \, arg) \\
++& \, gasParseCode(code) \\
++& \, gasInterpret(code, \, arg, \, storage) \\
++& \, gasUnparse(storage) \\
++& \, gasSerialize(storage) \\
++& \, gasWrite(storage)
+\end{split}
+\end{align}
+Assuming that the storage is never increased, the amount of gas returned by the cost functions independent of the argument, i.e., the parameter value, remain constant for each $T$.
+The cost functions for the deserialization, parsing and interpretation, however, are functions of $arg$ that grow strictly monotonic with increasing sizes of $arg$.
+\\
+Consider the following simple contract --- it does not do anything useful, but it can be used to approximate the amplification of the cost functions with regard to $arg$.
+Appendix \ref{apx:cost_analysis_contract} contains the respective Michelson contract.
+\begin{lstlisting}
+contract Foo {
+	function bar (int a) public {
+		for (uint i = 0; i < a; i++) {
+			assert(a == a)
+		}
+		// ...
+	}
+}
+\end{lstlisting}
+
 \draft{Formalize the costs of checking a formula}

### 2021-04-09 assertions/doc/thesis-bernhardt/chapters/4-offline_design_tezos.tex
IR done; add cost model; cost analysis

@@
 \cite{tezos_docs}
-
-\todo{Add mempool? If Blockchain protocol is outlined}
 
@@
 
+\subsection{Gas model}
+In Tezos data is stored and transmitted as byte sequences --- in order to obtain a typed representation of their value for interpretation, a byte sequence is first deserialised into Micheline and subsequently parsed \cite{tezos_repo}.
+Conversely, before transmitting or storing something on the blockchain, the typed representation is first unparsed and then serialised.
+The gas consumption of an operation, e.g.
+a transaction or an origination, is thus composed of the following positions on top of a base cost \cite{morley_gasmodel}\cite{tezos_repo}:
+\begin{enumerate}
+\item \textbf{Reading costs} --- apply for reading contract code, storage or Big Maps from the internal database and, on top of the base cost, depend on the amount of bytes read
+\item \textbf{Deserialization costs} --- depend on the Micheline expression and their size
+\item \textbf{Parsing costs} --- are composed of three types of parsing costs:
+	\begin{itemize}
+	\item type parsing --- apply when a Micheline node is converted into a valid type and are computed by a recursive formula; parametrized types therefore generate more cost than plain types
+	\item data parsing --- apply when a node is converted into the value of a known type and depend on the byte length for non-parametrized types, on the number of contained elements for container types and on the parameters for parametrized types
+	\item code parsing --- computes the return type of the code by sequentially applying instructions and type checking if the result matches the expectation.The cost thus increases in the number of instructions, while some instructions incur additional costs besides their base cost, such as \texttt{IF} (both branched need to be checked and compared) or \texttt{CREATE\_CONTRACT} (called contracts needs to be type checked)
+	\end{itemize}
+\item \textbf{Type comparison costs} --- occur during parsing when types are checked for equality (e.g. when verifying that the branches of \texttt{IF} have the same type) or contract execution
+\item \textbf{Interpreter costs} --- apply for each executed instruction and are specified for each.
+Expensive instruction are, for instance, \texttt{CONTRACT} with a high base cost and additional cost for reading, deserializing and type checking of the target contract code.
+\item \textbf{Unparsing costs} --- depend on the type of the data; parametrized types incur cost for unparsing its inner types as well
+\item \textbf{Serialization costs} --- depend, similar to deserialization, on the Micheline expression and their size
+\item \textbf{Writing costs} --- apply when writing to the internal database.
+Depend on the amount of bytes written, but with a higher base cost than reading.
+Additional cost is inflicted if the storage of the contract increased in size
+\end{enumerate}
+If a transaction emits internal operations, their gas consumption is computed in the same way and are added to the total gas consumption of the external operation.
+
 \subsection{Developer tools in the Tezos ecosystem}
@@
 a compiler, a simulation engine for testing contracts and an online editor.
-\item [\textbf{fi}] 's \cite{fi} syntax is similar to JavaScript or Ethereum's contract language Solidity.
-It also provides an online editor and a simulator to test against the compiled contracts.
-However, it seems extensions to Michelson introduced by newer protocol versions are not supported yet.
+\item [\textbf{Ligo}] \cite{ligo} offers multiple syntax flavours that are close to Pascal, OCaml or Reason.
+Besides compilation, the toolchain allows to invoke or evaluate the generated code locally.
+The Ligo OCaml packages can be integrated into other OCaml projects, s.t.
+the compiler can be invoked from within third-party applications.
 \end{itemize}
@@
 
-\subsection{Random}
+\subsection{random}
 A vital instruction that cannot be expressed with Michelson's current instruction set (state of protocol 008 Edo \cite{tezos_docs}) is the generation of a random value of certain types.
@@
 
-\subsection{Nth}
+\subsection{nth}
 An exception for not adding higher level instructions may be the more fundamental operation \texttt{nth} for accessing list elements, as it is used (sometimes more than once, ref.
@@
 \lstset{upquote=false}
-
-\subsection{failwith 2.0}
-\draft{}
-- failwith returns a failure string
-- assertion execution -> random number is generated
-- if counterexample is found, the random number somehow has to be extracted from the contract execution, s.t. other validators can verify the counterexample
-- some special failure operation may be needed that returns the that value
-- as representation of a counterexample is still an open question, there are not specifics yet as to how this instruction is supposed to look like (or if it is needed at all)
 
@@
 \paragraph{Assertion contracts}
-\lstref{lst:contract_templ} shows a possible template for an assertion contract - the placeholder \texttt{<?>} marks the locations where the individual code is inserted.
+\lstref{lst:contract_templ} shows a possible template for an assertion contract --- the placeholder \texttt{<?>} marks the locations where the individual code is inserted.
 Lines 3-5 prepare the stack, s.t.
@@
 \paragraph{Evaluation}
-Compiling to Michelson directly is beneficial due of several reasons - the pipeline stays streamlined and outputs the final contracts ready for origination.
+Compiling to Michelson directly is beneficial due of several reasons --- the pipeline stays streamlined and outputs the final contracts ready for origination.
 It does not introduce dependencies to external tools and their support for new protocol versions of Tezos.
@@
 \paragraph{Assertion contracts}
+\lstref{lst:contract_templ_liq} shows the equivalent of the assertion contract template given in \lstref{lst:contract_templ}.
+Since the Liquidity compiler takes care of the handling of the stack, it basically consists only of a storage type declaration, a function signature and the ``empty'' return type.
 \lstinputlisting[label=lst:contract_templ_liq, language=Michelson, caption=Template code for assertion contracts in Liquidity, numbers=left]{listings/assertion_template.liq}
@@
 \paragraph{Manager contract}
-\lstinputlisting[label=lst:manager_templ_liq, language=Michelson, caption=Manager code in Liquidity for an entrypoint with a non-empty assertion, numbers=left]{listings/manager_loop.liq}
-
+Liquidity contracts are a list of OCaml-like functions that take a parameter and a storage.
+Instead of declaring the contract parameter type globally and nesting the code for each entrypoint, each entrypoint thus is declared as a separate function with a local parameter type.
+During compilation, the contract parameter type will then be composed according to the order of functions.
+Due to Algorithm \ref{alg:compile_manager} being left recursive, the output will automatically retain the correct order of entrypoints.
+In fact, the only adaptions necessary are the output of the two functions \texttt{generate\_loop} and \texttt{generate\_forward}, which should not only generate the code body, but return a coherent function.
+The function \texttt{entrypointA} in \lstref{lst:manager_templ_liq} is an example of such a function for an empty assertion.
+The non-empty version of the manager code can be found in appendix \ref{apx:apx:manager_liq}.
+As already noted, extracting a pure template for the code exceeds the scope of this section.
 \lstinputlisting[label=lst:manager_templ_liq, language=Michelson, caption=Manager code in Liquidity for an entrypoint with an empty assertion, numbers=left]{listings/manager_forward.liq}
@@
 \paragraph{Evaluation}
-+ optimization (Liq compiler)
-+ testing: easier to verify correctness, as it reads like an ocaml program
-	+ compiler of hl language already tested -> only check if IR is correct
-+ variable support -> variables in assertion easier to implement?
+This approach takes advantage of the usually more sophisticated high-level language compiler; they may provide options for optimizing generated code and are already thoroughly tested \cite{liq_repo}\cite{ligo_repo}.
+In contract to low-level code, the output of the pipeline compiler is easier to be verified, as it can be read like, for instance, an OCaml program.
+Providing target contracts for integration tests can be done much more efficiently and more reliable.
+\\
+Besides the amenities of these compilers, this approach has a crucial disadvantage of introducing an external dependency.
+The compiler of the respective language has to be extended with the additional Michelson instructions as well, requiring a fork of the project.
+Furthermore one has to rely on continuous support of new protocol versions in the root project and integrate the updates into the own codebase.
+All things considered, the effort for extending both Michelson and the compiler of the IR, followed by a continuous effort of version management, may outweigh the benefits of this approach.
 
-\section{Misc}
-\todo{Aspects/questions I don't know yet if or where to put it}
-\begin{itemize}
-\item Tezos specific costs analysis of chosen orchestration strategy -> PROBLEM: high n might reach operation gas limit?
-\item Representation of counterexamples; how to verify them?
-\item Basic approach for proofs?
-\end{itemize}
+When returning to the orchestration approach of generating a monolithic contract, using Liquidity as an IR would allow to decompile the parent contract using the decompiler of its toolchain.
+Since the Liquidity compiler handles the composition of the contract parameter type and the code nesting, the assertion function simply have to be appended to the parent code, which significantly decreases the compilation complexity.
+
+\section{Cost analysis}
+Tezos specific costs analysis of chosen orchestration strategy -> PROBLEM: high n might reach operation gas limit?
+
+\section{Open questions}
+
+\subsection{Representing counterexamples}
+\draft{}
+- the random number somehow has to be extracted from the contract execution, s.t. other validators can verify the counterexample
+- failwith exposes top element of the stack in error message -> can be used to "return" the random values? Question for protocol design how to process it further
+- if this is not possible, Michelson may have to be extended with a special failure message that can be handled differently
+- assertion execution -> random number is generated
+- if counterexample is found, the random number somehow has to be extracted from the contract execution, s.t. other validators can verify the counterexample
+- open question how the validators can check the counterexample -> send piece of code with random values as parameter?
+- incentives \& penalties part of the block chain protocol

### 2021-04-09 assertions/doc/thesis-bernhardt/chapters/appendix.tex
IR done; add cost model; cost analysis

@@
 \appendix
+\chapter{Michelson contract used for cost analysis}
+\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
+				 backgroundcolor=\color{cverbbg},
+				 linewidth=14cm,
+				 xleftmargin=0.5cm,
+				 frame=lr,
+				 framesep=8pt,
+				 framerule=0pt,
+				 captionpos=b,
+				 numbers=none,
+				 language=Michelson,
+				 caption=Foobar.tz]{listings/foobar.tz} \todo{Caption}
+
 \chapter{Assertion Grammar in EBNF}\label{apx:grammar}
@@
 
+\chapter{Manager contract code in Liquidity}\label{apx:manager_liq}
+\lstinputlisting[label=lst:manager_templ_liq, language=Michelson, caption=Manager code in Liquidity for an entrypoint with a non-empty assertion, numbers=left]{listings/manager_loop.liq}
+
 \chapter{Manager contract code in Michelson}\label{apx:manager_michelson}

### 2021-04-09 assertions/doc/thesis-bernhardt/chapters/2-use_case_analysis.tex
Cost analysis

@@
 Appendix \ref{apx:cost_analysis_contract} contains the respective Michelson contract.
-\begin{lstlisting}
+\begin{lstlisting}[numbers=none, language=Solidity]
 contract Foo {
@@
 
+\begin{lstlisting}[numbers=none, language=Solidity]
+contract Spam {
+	function ham (int [] b) public {
+		for (uint i = 0; i < b.length; i++) {
+			assert(b[i] < 10)
+		}
+		// ...
+	}
+}
+\end{lstlisting}
+
+second contract with more increasing deserialization and parsing costs -> list with the same elements * n; comparable operations
+both grow linear and the contract with the list way more due to the increasing deserialization and parsing costs
+check protocol version of node + which test network
+can we do better with distributed assertion checking?
+
 \draft{Formalize the costs of checking a formula}

### 2021-04-09 assertions/doc/thesis-bernhardt/chapters/appendix.tex
Cost analysis

--- 2021-04-08 assertions/doc/thesis-bernhardt/chapters/appendix.tex
@@
 \appendix
+\chapter{Michelson contracts used for cost analysis}\label{apx:cost_analysis_contract}
+
+\section{Foo}
+\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
+				 backgroundcolor=\color{cverbbg},
+				 linewidth=14cm,
+				 xleftmargin=0.5cm,
+				 frame=lr,
+				 framesep=8pt,
+				 framerule=0pt,
+				 captionpos=b,
+				 numbers=none,
+				 language=Michelson,
+				 caption=Foo.tz]{listings/foobar.tz} \todo{Caption}
+
+\section{Spam}
+\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
+				 backgroundcolor=\color{cverbbg},
+				 linewidth=14cm,
+				 xleftmargin=0.5cm,
+				 frame=lr,
+				 framesep=8pt,
+				 framerule=0pt,
+				 captionpos=b,
+				 numbers=none,
+				 language=Michelson,
+				 caption=Spam.tz]{listings/spamham.tz} \todo{Caption}
+
 \chapter{Assertion Grammar in EBNF}\label{apx:grammar}

### 2021-04-10 assertions/doc/thesis-bernhardt/chapters/2-use_case_analysis.tex
Cost analysis + counterexamples

--- 2021-04-01 assertions/doc/thesis-bernhardt/chapters/2-use_case_analysis.tex
@@
 
-\section{Cost analysis}
-\draft{Formalize the costs of checking a formula}
-\begin{itemize}
-\item Describe a general cost model for execution of a SC
-\item Calculate costs for checking a formula locally (in a loop)
-\item Calculate costs for checking a single element
-\item Compare results -> how high is the ``boilerplate'' cost?
-\item When do the costs of distributed checking drop below local checking?
-\end{itemize}
+\section{Cost analysis}\label{sec:usecase_cost}
+In order to be able to evaluate whether distributed assertion checking can indeed lower the cost in comparison to a local verification, the cost of checking a formula on the blockchain needs to be formalized.
+Since this thesis describes an implementation of the approach on the Tezos blockchain, the following costs refer to that specific gas model, s.t.
+the results of the cost analyses are comparable (Tezos and its gas model are described in more detail in \secref{sec:tezos}).
+\\
+According to the gas model, the total gas consumption of a transaction $T(src,\, dst=C,\, arg, \, ...)$ to an originated contract $C(storage, \, parameter\, type, \, code)$ is calculated by \eqref{eq:gas_transaction}, where $I$ is the set of internal operations:
+\begin{align}\label{eq:gas_transaction}
+\begin{split}
+GasConsumed(T) = \quad &base \, amount \\
++& \, gasRead(code) \\
++& \, gasRead(storage) \\
++& \, gasDeserialize(storage, \, arg) \\
++& \, gasParseType(parameter \, type, \, storage) \\
++& \, gasParseData(storage, \, arg) \\
++& \, gasParseCode(code) \\
++& \, gasInterpret(code, \, arg, \, storage) \\
++& \, gasUnparse(storage) \\
++& \, gasSerialize(storage) \\
++& \, gasWrite(storage) \\
++& \, \sum_{i \in I} GasConsumed(i)
+\end{split}
+\end{align}
+Assuming that the storage is never increased, the amount of gas returned by the cost functions independent of the argument, i.e., the parameter value, remain constant for each $T$.
+The cost functions for the deserialization, parsing and interpretation, however, are functions of $arg$ that grow strictly monotonic with increasing sizes of $arg$.
+\\
+Consider the following simple contracts --- they do not do anything useful, but can be used to approximate the amplification of costs with regard to $arg$.
+Contract \texttt{Foo} takes an integer, whose byte sequence does not increase significantly with higher values, thus the increase in overall cost is mainly accounted for by interpretation cost.
+Contract \texttt{Bar}, on the other hand, executes similar operations but expects a list of integers, which causes noticeably higher deserialization and parsing costs with increasing input size.
+\begin{lstlisting}[numbers=none, language=Solidity, caption=Simple dummy contract executing a loop]
+contract Foo {
+  function foo (int a) public {
+    for (uint i = 0; i < a; i++) {
+      assert(a == a)
+	}
+	// ...
+  }
+}
+\end{lstlisting}
+\begin{lstlisting}[numbers=none, language=Solidity, caption=Simple dummy contract iterating over a list]
+contract Bar {
+  function bar (int [] b) public {
+    for (uint i = 0; i < b.length; i++) {
+      assert(b[i] = b[i])
+	}
+	// ...
+  }
+}
+\end{lstlisting}
+
+\figref{fig:use_case_cost} shows the reported gas consumption of transactions calling the dummy contracts on the Delphinet test network running the protocol 007 Delphi \cite{tezos_docs}.
+As to be expected, the gradient of the cost function in the case of \texttt{Bar} is higher due to additional serialization and parsing costs, namely $\frac{dx}{dy} = 16$ compared to $\frac{dx}{dy} = 6$ for \texttt{Foo}.
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.9\linewidth]{figures/2-use_cases/cost_analysis}
+\caption{Gas consumption of transactions calling \texttt{Foo} and \texttt{Bar} for increasing input sizes}
+\label{fig:use_case_cost}
+\end{figure}
+
+A repeated cost analysis is carried out in \secref{sec:cost_analysis_distributed} in order to assess whether, or how, distributed assertion checking, as described in the following chapters, can achieve a reduction of these costs.

### 2021-04-10 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Cost analysis + counterexamples

@@
 
-\subsection{Alternatives to random testing}
+\subsection{Alternatives to random testing}\label{sec:alt_random}
 For applications where higher reliability is crucial, an alternative to checking elements randomly could be to coordinate a systematic iteration of the domain.

### 2021-04-10 assertions/doc/thesis-bernhardt/chapters/4-offline_design_tezos.tex
Cost analysis + counterexamples

@@
 The address of the parent contract is assumed to always be stored with the id 0.
-\secref{sec:prob_threshold} stated a formula for calculating $t_total$ with the parameters $n$, the size of the search space, and the probability threshold $c$.
+\secref{sec:prob_threshold} stated a formula for calculating $t_{total}$ with the parameters $n$, the size of the search space, and the probability threshold $c$.
 While $n$ can be calculated from the ranges of the random generator(s), $c$ must be given as parameter to the compiler through the CLI.
-After $t_total$ has been computed, a divison by 32, i.e., the number of validators, returns the upper bound of the loop.
-\\
+After $t_{total}$ has been computed, the upper bound of the loop is calculated according to \eqref{eq:t_validator}.
+\begin{equation}\label{eq:t_validator}
+t = \lceil t_{total} / \#validators \rceil
+\end{equation}
+
 \texttt{generate\_forward} can be generated from a simple template with the id as the only variant and only consists of  an access to the storage and the emission of an internal operation.
@@
 
-\section{Cost analysis}
-Tezos specific costs analysis of chosen orchestration strategy -> PROBLEM: high n might reach operation gas limit?
+\section{Cost analysis}\label{sec:cost_analysis_distributed}
+What remains to be evaluated is the cost of checking a formula with the proposed approach, and how they relate to the costs for a local validation which were analysed in \secref{sec:usecase_cost}.
+The previous analysis defined \eqref{eq:gas_transaction} to calculate the gas consumption of a transaction, including the emitted operations.
+For each validator, the transaction calling the manager contract emits $t+1$ internal operations, whose gas consumptions are also dependent of the input parameter.
+Based on the $t+1$ additional base, as well as deserialization and parsing costs of the parameter alone, it can be concluded that the total gas consumption of $n$ total distributed test runs is higher than the cost of checking $n$ values locally.
+\\
+The differential can be measured by implementing the orchestration scheme for the two dummy contracts given in \secref{sec:usecase_cost}.
+Appendix \ref{apx} contains the code of all three components for each of them.
+In order to measure the gas consumption for a comparable amount of executions as during the initial cost analysis, the probability threshold $c$ is set to $\frac{1}{e}$, s.t.
+that the necessary number of total test runs is $n$.
+However, it needs to be pointed out, that the actual number of test runs executed can only be a multiple of the number of validators (cf.
+\eqref{eq:t_validator}).
+\figref{fig:cost_distributed} shows the reported gas consumption per validator, i.e., a $32^{th}$ of the total cost for checking an assertion for the given threshold.
+Due to \eqref{eq:t_validator}, the cost function approximates a step function.
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.9\linewidth]{figures/4-offline_tezos/cost_analysis}
+\caption{Gas consumption per validator of transactions calling \texttt{Foo} and \texttt{Bar} for increasing input sizes}
+\label{fig:cost_distributed}
+\end{figure}
+The results show that the cost incurred by a single validator checking $t$ values is already considerably higher than by checking the property locally.
+Moreover, the cost-performance ratio is even worse, as the confidence that the property is indeed satisfied is only around 63\% with the given parameters.
+In conclusion to these results, it may be worth looking into some alternative approaches.
+\secref{sec:alt_random} already mentions the possibility to coordinate the validators for a systematic iteration of the search space.
+Alternatively, the proposed orchestration could be modified, s.t.
+the manager and assertion code are not implemented as separate contracts, but with one single contract.
+Instead of $(t+1)$ internal operations, one only has to pay for one internal operation that calls the parent contract, hence avoiding the base, deserialization and parsing costs for each test run.
+Similar to the monolithic orchestration approach, this increases the complexity of the compilation process.\\ Another idea worth exploring is the adaption of the blockchain protocol to avoid user costs for assertion checking, similar to the regular validation of blocks \cite{tezos_docs}.
+Instead of being paid by the user in gas, validators could be given a reward for checking an assertion, or a particularly high one for finding a counterexample.
 
-\section{Open questions}
-
-\subsection{Representing counterexamples}
-\draft{}
-- the random number somehow has to be extracted from the contract execution, s.t. other validators can verify the counterexample
-- failwith exposes top element of the stack in error message -> can be used to "return" the random values? Question for protocol design how to process it further
-- if this is not possible, Michelson may have to be extended with a special failure message that can be handled differently
-- assertion execution -> random number is generated
-- if counterexample is found, the random number somehow has to be extracted from the contract execution, s.t. other validators can verify the counterexample
-- open question how the validators can check the counterexample -> send piece of code with random values as parameter?
-- incentives \& penalties part of the block chain protocol
+\section{Representing counterexamples}
+There still remains an open question concerning the proposed implementation that could be answered in detail within the scope of this thesis - the representation and validation of a counterexamples.
+The interaction scheme in \figref{fig:interaction_modular} suggests, that validators publish an instance of a counterexample to the network if they found one.
+However, it has yet to be specified how the counterexample is represented and double-checked by the other validators.
+With the \texttt{failwith} instruction, the top element of the stack can be exposed \cite{tezos_docs}, providing a way to return an interpretable expression from the interpretation context \cite{tezos_repo}.
+Thus, as a first approximation, the counterexample could be represented as a tuple of assertion code and a list of randomly generated values.
+For instance, the counterexample for the assumption ``p is a prime'' (cf.
+\eqref{eq:prime}) is represented by \\
+\texttt{(n >= 2 \&\& n <= sqrt(p) \&\& p\%n = 0, <random value for n>)}. \\
+For validation of the counterexample, this tuple, together with the respective operation hash of the initial transaction this counterexample refers to, is published to the network.
+The other validators then interpret the given code with the respective value(s) and either confirm or object the counterexample.
+As Tezos transmits data as byte sequences, the counterexample needs to be unparsed and serialized, or deserialized and parsed respectively.
+If the cost for checking assertions is paid for be the user (in form of gas), then these costs have to be added to the total costs as well.\\
+In order to prevent denial-of-service attacks by spamming the network with false counterexamples, the protocol should implement penalties for such cases.
+Details about this and possible rewards for valid counterexamples should be considered in the protocol design.

### 2021-04-10 assertions/doc/thesis-bernhardt/chapters/appendix.tex
Cost analysis + counterexamples

--- 2021-04-08 assertions/doc/thesis-bernhardt/chapters/appendix.tex
@@
 \appendix
+\chapter{Michelson implementations of \texttt{Foo} and \texttt{Bar}}\label{apx:cost_analysis_contract}
+The following contracts are the Michelson equivalent of the dummy contracts given in \secref{sec:usecase_cost}.
+\section{Foo}
+\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
+				 backgroundcolor=\color{cverbbg},
+				 linewidth=14cm,
+				 xleftmargin=0.5cm,
+				 frame=lr,
+				 framesep=8pt,
+				 framerule=0pt,
+				 captionpos=b,
+				 numbers=none,
+				 language=Michelson,
+				 caption=Dummy Michelson contract executing a dynamic loop]{listings/foo.tz}
+
+\section{Bar}
+\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
+				 backgroundcolor=\color{cverbbg},
+				 linewidth=14cm,
+				 xleftmargin=0.5cm,
+				 frame=lr,
+				 framesep=8pt,
+				 framerule=0pt,
+				 captionpos=b,
+				 numbers=none,
+				 language=Michelson,
+				 caption=Dummy Michelson contract iterating over a dynamic list]{listings/bar.tz}
+
 \chapter{Assertion Grammar in EBNF}\label{apx:grammar}
@@
 				 caption=Manager code in Michelson for an entrypoint with an empty assertion (wrapped in contract boilerplate code)]{listings/manager_forward.tz}
+
+\chapter{Distributed Michelson implementation of \texttt{Foo} and \texttt{Bar}}\label{apx:foobar_distributed}
+The following contracts are a restructuring of the contracts given in Appendix \ref{apx:cost_analysis_contract}, s.t. they implement the proposed orchestration strategy.
+
+\section{\texttt{Foo}}
+\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
+				 backgroundcolor=\color{cverbbg},
+				 linewidth=14cm,
+				 xleftmargin=0.5cm,
+				 frame=lr,
+				 framesep=8pt,
+				 framerule=0pt,
+				 captionpos=b,
+				 numbers=none,
+				 language=Michelson,
+				 label=lst:foo_manager,
+				 caption=Manager contract of \texttt{Foo}]{listings/foo_manager.tz}
+\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
+				 backgroundcolor=\color{cverbbg},
+				 linewidth=14cm,
+				 xleftmargin=0.5cm,
+				 frame=lr,
+				 framesep=8pt,
+				 framerule=0pt,
+				 captionpos=b,
+				 numbers=none,
+				 language=Michelson,
+				 label=lst:foo_manager,
+				 caption=Assertion contract of \texttt{Foo}]{listings/foo_assertion.tz}
+\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
+				 backgroundcolor=\color{cverbbg},
+				 linewidth=14cm,
+				 xleftmargin=0.5cm,
+				 frame=lr,
+				 framesep=8pt,
+				 framerule=0pt,
+				 captionpos=b,
+				 numbers=none,
+				 language=Michelson,
+				 label=lst:foo_manager,
+				 caption=Parent contract of \texttt{Foo}]{listings/foo_parent.tz}
+
+\section{\texttt{Bar}}
+\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
+				 backgroundcolor=\color{cverbbg},
+				 linewidth=14cm,
+				 xleftmargin=0.5cm,
+				 frame=lr,
+				 framesep=8pt,
+				 framerule=0pt,
+				 captionpos=b,
+				 numbers=none,
+				 language=Michelson,
+				 label=lst:bar_manager,
+				 caption=Manager contract of \texttt{Bar}]{listings/bar_manager.tz}
+\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
+				 backgroundcolor=\color{cverbbg},
+				 linewidth=14cm,
+				 xleftmargin=0.5cm,
+				 frame=lr,
+				 framesep=8pt,
+				 framerule=0pt,
+				 captionpos=b,
+				 numbers=none,
+				 language=Michelson,
+				 label=lst:bar_manager,
+				 caption=Assertion contract of \texttt{Bar}]{listings/bar_assertion.tz}
+\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
+				 backgroundcolor=\color{cverbbg},
+				 linewidth=14cm,
+				 xleftmargin=0.5cm,
+				 frame=lr,
+				 framesep=8pt,
+				 framerule=0pt,
+				 captionpos=b,
+				 numbers=none,
+				 language=Michelson,
+				 label=lst:bar_manager,
+				 caption=Parent contract of \texttt{Bar}]{listings/bar_parent.tz}

### 2021-04-11 assertions/doc/thesis-bernhardt/chapters/5-conclusion.tex
started conclusion

@@
 \chapter{Conclusion and outlook}\label{chap:conclusion}
+In order to make use of off-chain computations in smart contracts, this thesis proposed an approach that engages the validators of the blockchain network in a distributed effort to check assertions over input parameters.
+It identified a set of properties, that can be checked in such a scheme, in form of logical formulas and demonstrated some use-cases and semantic differences among them.
+Based on this, a simple syntax was introduced to express assertions stating these formulas for a one or more entrypoints of a contract, followed by a formalization of their transformation that negates the formula and builds smart random generators.
+After analysing the accuracy of the approach and stating a formula to compute the minimum amount of random checks to reach a certain confidence level, the thesis explored several orchestration strategies of contract and assertion code, and, for a chosen strategy, discusses the necessary implementations within the off-chain infrastructure.
+In conclusion, it analysed the cost incurred by checking assertions as proposed and compared the results to a non-distributed approach.
+Based on these results, thesis discusses alternatives or possible modifications to solve some of the issues at hand.
+\\
+
+- high costs due to several reasons: random checking values require more test runs than size of iteration space.
+going below n checks does not provide a high certainty over validity.
+This approach is thus not suitable for safety or security critical applications.
+- more effort in compilation returns a better cost-performance ratio if the manager contract and assertions are merged. Still, more base costs
+- depends on the protocol design, whether this approach is worth pursuing -> if the cost for validation can be eliminated by using rewards, it might be realisable.
+- quantifiers: other semantics for certain combinations/existentials --> proofs; here not considered, but would be interesting for future work on this topic
+
+\subsection{Outlook}
+
 \draft{}

### 2021-04-12 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
Rework objective; add structure overview; some conclusion stuff

@@
 These fees, often measured in a unit called ``gas'', have to be paid for by the user in order to compensate the miners for their efforts \cite{chen_under-optimized_2020}.
-This creates a powerful incentive to keep smart contracts simple and efficient, while in effect, meaningful applications still might need to perform some resource intensive computations.
-Not only can such applications generate unsustainable costs when executed on the blockchain, but they may also reach gas limits imposed by the blockchain's protocol.
+This creates a powerful incentive to keep smart contracts simple and efficient, while in reality, meaningful applications still might need to perform some resource intensive computations.
+Not only can such applications generate unsustainable costs when executed on the blockchain, but may also reach gas limits imposed by the blockchain's protocol.
 \\
@@
 Consequently, submitted parameters should be checked for assumed properties before the smart contract is executed.
-Although in many cases, verifying a solution takes less time than computing the result itself\footnote{cf.
-NP-hard problems \cite{nph_problems}, sorting algorithms \cite{review_sorting}\cite{cpp_issorted}, etc.}, the generated costs for checking the validity increase with the size of the input.
+Although in many cases, verifying a solution takes less time than computing the result itself (cf.
+NP-hard problems \cite{nph_problems} or sorting algorithms \cite{review_sorting}\cite{cpp_issorted}), the generated costs for checking the validity increase with the size of the input.
 \\
-Consider, for instance, the following contract:
+Consider, for instance, the following smart contract:
 \begin{lstlisting}[caption=Smart contract expecting a prime number \cite{thiemann_2020}, numbers=none, language=Solidity, label=lst:prime]
@@
 \\
-However, distributed assertion checking is not only applicable for parameters or properties of dynamic size.
-Another example given in \cite{thiemann_2020} shows a contract that expects an array of integers sorted in ascending order:
+However, distributed assertion checking is not only applicable for parameters or properties of dynamic size. Another example is a contract that expects an array of integers sorted in ascending order:
 
-\begin{lstlisting}[caption=Smart contract expecting a sorted array, numbers=none, language=Solidity, label=lst:sorted]
+\begin{lstlisting}[caption=Smart contract expecting a sorted array \cite{thiemann_2020}, numbers=none, language=Solidity, label=lst:sorted]
 contract Sorted {
@@
 The same applies, with some reservations, to distributed assertion checking: less samples keep the gas consumption to a minimum, whereas more samples increase the probability that an existing counterexample is found.
-Referring to the example of sorted lists,  the probability of false positives depends on the size of the list $a$ and the number of validators $m$.\\
-The importance of the former parameter becomes obvious when looking at the worst case scenario of the same example.
-Assume the array is unsorted at exactly one position - the probability that the each of the $m$ validators independently check this position is $\frac{1}{|a|}$, while all of them checking any other position $\frac{|a|-1}{|a|}$.
+Referring to the example of sorted lists,  the probability of false positives depends on the size of the list $a$ and the number of validators $m$.
+
+The importance of the former parameter becomes apparent when considering the worst case scenario of the same example.
+Assuming the array is unsorted at exactly one position - the probability that the each of the $m$ validators independently check this position is $\frac{1}{|a|}$, whereas the probability of all of them checking any other position $\frac{|a|-1}{|a|}$.
 If the random generator chooses each value for $n$ independently from a uniform distribution, the probability that the counterexample is not detected by any validator converges to 0 if the number of validators approaches infinity \cite{thiemann_2020}:
@@
 \section{Objective}
-This thesis conducts research into the feasibility and performance of the proposed approach and explores possible designs for the implementation of both the necessary off-chain infrastructure and the amendment of the blockchain protocol.
+This thesis proposes the portrayed approach of a distributed assertion checking scheme in order to make more efficent use of off-chain resources.
+The realisation of such assertions consists of two components - the off-chain design and implementation of supporting infrastructure, as well as the extension of the smart contract language and amendment of the blockchain protocol, s.t.
+these assertions are triggered and handled correctly by the network.
+The focus of this thesis is put primarily on the off-chain component and the development of a toolchain that transforms and translates assertions to executable code for the target platform, but elaborates on the protocol design where necessary.
 To this end, a first approximation of a set of formulas amenable for distributed assertion checking is defined, special cases are identified and, if necessary, excluded.
-While parts of the offline design and infrastructure should be, in parts, applicable to any blockchain supporting smart contracts, the case example for the protocol-specific parts of the design target the Tezos blockchain and its built-in contract language Michelson.
-On the basis of the achieved results, the efficiency of the approach is ultimately assessed.
+While the off-chain design and toolchain should be partially applicable to any blockchain supporting smart contracts, the case example for the protocol-specific parts of the design targets the Tezos blockchain and its built-in contract language Michelson.
+On the basis of the chosen design, the thesis evaluates the efficiency of the approach in terms of costs incurred by checking a formula on Tezos, and discusses if, and under which conditions, these costs are competitive versus a local approach.
 
 \section{Structure overview}
-\draft{Finish when structure \& chapters finalised.}
-\begin{itemize}
-\item Assessment of use cases for this kind of assertion checking (Chapter 2)
-	\begin{itemize}
-	\item defines a set of logical formula
-	\item gives some useful examples
-	\item cost analysis for checking them normally
-	\end{itemize}
-\item Generic Offline Design (Chapter 3)
-	\begin{itemize}
-	\item definition of language/syntax to express assertions over given set of logical formulas
-	\item formalizes the transformation
-	\item describes frontend of pipeline
-	\item analyses accuracy of this approach
-	\end{itemize}
-\item Tezos-specific Offline Design (Chapter 4)
-	\begin{itemize}
-	\item introduction/Overview to Tezos
-	\item necessary extensions to Michelson's instruction set \& evaluator
-	\item description of the pipeline backend
-	\item Cost analysis \& accuracy on Tezos
-	\end{itemize}
-\item Conclusion \& outlook
-	\begin{itemize}
-	\item Next steps/ToDos for development; open issues
-	\item Evaluation of costs -> is this approach promising?
-	\item Alternatives? E.g. Refer to TrueBit
-	\end{itemize}
-\end{itemize}
+The structure of this thesis is as follows: in the first instance, \chapref{chap:use_cases} defines a set of logical formulas that describe parameter properties and are suitable for distributed assertion checking.
+Given this set, it demonstrates various practical use-cases for such properties and formalizes the costs of checking them locally, s.t.
+they can later be referenced to assess the efficiency of the distributed approach.
+\chapref{chap:offline} describes the generic aspects of the off-chain design and infrastructure, i.a.
+the definition of a syntax to express assertions on top of the logical formulas and how they are transformed to code that checks for counterexamples.
+Additionally, it analyses the effectiveness of the statistical validation for a given input and provides a formula to compute the lower bound of validators necessary to obtain a reliable result.
+Subsequently, \chapref{chap:offline_tezos} gives a brief introduction to Tezos, before it covers target specific aspects of the off-chain design.
+Besides identifying necessary extensions to Michelson's instruction set and virtual machine, it explores various orchestration strategies between assertion and contract code.
+The chapter closes with a cost analysis of distributed assertion checking on Tezos with the chosen orchestration strategy.
+In conclusion, the last chapter recaps the achieved results,
+addresses any open questions or issues and provides an outlook on upcoming work on this topic.

### 2021-04-12 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Rework objective; add structure overview; some conclusion stuff

@@
 
-\chapter{Generic Offline Design}\label{chap:offline}
+\chapter{Generic Off-Chain Design}\label{chap:offline}
 The implementation of distributed assertion checking on any blockchain requires some off-chain considerations and infrastructure.
@@
 As stated before, the proposed implementation in the following chapters is, for the most part, restricted to formulas of predicate logic using universal quantification.\\
-The purpose of the offline infrastructure is to provide a syntax for stating assertions that check logical formulas, as well as a toolchain to compile these assertions into code that can be originated on the target blockchain.
+The purpose of the off-chain infrastructure is to provide a syntax for stating assertions that check logical formulas, as well as a toolchain to compile these assertions into code that can be originated on the target blockchain.
 Depending on the individual solution for the respective blockchain protocol, this can either be the original contract extended directly with the assertion code, or as a separate contract that extends the original contract in some other way.
-This chapter describes the generic part of the offline design, which corresponds to the frontend of the compilation pipeline shown in \figref{fig:pipeline_frontend}.
+This chapter describes the generic part of the off-chain design, which corresponds to the frontend of the compilation pipeline shown in \figref{fig:pipeline_frontend}.
 As a start, \secref{sec:syntax} describes the concrete syntax for writing assertions and shows how it expresses some of the previously given examples.

### 2021-04-12 assertions/doc/thesis-bernhardt/chapters/4-offline_design_tezos.tex
Rework objective; add structure overview; some conclusion stuff

@@
 Since the internal operations may in turn also emit internal operations, they are put into a queue and are processed in order.
-As an example, \figref{fig:internal_ops} shows an execution order of two external transactions, i.e., transactions which have been initiated by a user account, and their internal operations.
+As an example, \figref{fig:internal_ops} shows an execution order of two external transactions in sequence, i.e., transactions which have been initiated by a user account, and their internal operations.
 \begin{figure}[h]
@@
 \includegraphics[width=0.5\linewidth]{figures/4-offline_tezos/internal_ops}
-\caption{Execution order of two external operations and their internal operations; Source: \cite{tezos_docs}}
+\captionsource{Execution order of two external operations and their internal operations}{\cite{tezos_docs}}
 \label{fig:internal_ops}

### 2021-04-12 assertions/doc/thesis-bernhardt/chapters/5-conclusion.tex
Rework objective; add structure overview; some conclusion stuff

--- 2021-04-01 assertions/doc/thesis-bernhardt/chapters/5-conclusion.tex
@@
 \chapter{Conclusion and outlook}\label{chap:conclusion}
+In order to make use of off-chain computations in smart contracts, this thesis proposed an approach that engages the validators of the blockchain network in a distributed effort to check assertions over input parameters.
+It covered the partially generic off-chain component of the design and implementation of this approach, while also providing some projections and considerations for the Tezos specific protocol design.
+
+As a first step, it identified properties that can be checked with the proposed scheme, represented by a set of formulas in propositional logic using quantification.
+By means of some practical use-cases, the semantic differences between universal and existential quantification in relation to assertion checking were highlighted, namely that existential quantification requires the validators to find proofs instead of counterexamples.
+Even though the thesis focused on distributed refutation, distributed verification is a meaningful extension of future work on this topic.
+
+Based on the set of formulas, the generic off-chain design introduced a simple syntax to express assertions for one or more entrypoints of a contract, followed by a formalization of their transformation which comprises the negation of the formula and translation of quantifiers to efficient random generators.
+After exploring several orchestration strategies of contract and assertion code, the Tezos specific off-chain design proposed to originate the assertion and manager code modularly and discussed the necessary implementations within the off-chain infrastructure and, partially, the protocol design.
+This off-chain infrastructure was implemented in OCaml in form of a toolchain, which translates a file of assertions to executable smart contracts for the target platform.\\
+
+% paragraph evaluation
+
+%In conclusion, it analysed the cost incurred by checking assertions as proposed and compared the results to a non-distributed approach.
+Based on these results, thesis discusses alternatives or possible modifications to solve some of the issues at hand.
+\\
+
+%contains a compilation pipeline written in OCaml that
+
+%An analysis of the general accuracy of the proposed scheme showed that 
+% and stating a formula to compute the minimum amount of random checks to reach a certain confidence level,
+%- high costs due to several reasons: random checking values require more test runs than size of iteration space.
+going below n checks does not provide a high certainty over validity.
+This approach is thus not suitable for safety or security critical applications.
+%- more effort in compilation returns a better cost-performance ratio if the manager contract and assertions are merged. Still, more base costs
+%- depends on the protocol design, whether this approach is worth pursuing -> if the cost for validation can be eliminated by using rewards, it might be realisable.
+%- quantifiers: other semantics for certain combinations/existentials --> proofs; here not considered, but would be interesting for future work on this topic
+
+\subsection{Outlook}
+
 \draft{}

### 2021-04-12 assertions/doc/thesis-bernhardt/chapters/appendix.tex
Rework objective; add structure overview; some conclusion stuff

@@
 				 language=Michelson,
-				 label=lst:foo_manager,
+				 label=lst:foo_assertion,
 				 caption=Assertion contract of \texttt{Foo}]{listings/foo_assertion.tz}
@@
 				 language=Michelson,
-				 label=lst:foo_manager,
+				 label=lst:foo_parent,
 				 caption=Parent contract of \texttt{Foo}]{listings/foo_parent.tz}
@@
 				 language=Michelson,
-				 label=lst:bar_manager,
+				 label=lst:bar_assertion,
 				 caption=Assertion contract of \texttt{Bar}]{listings/bar_assertion.tz}
@@
 				 language=Michelson,
-				 label=lst:bar_manager,
+				 label=lst:bar_parent,
 				 caption=Parent contract of \texttt{Bar}]{listings/bar_parent.tz}

### 2021-04-13 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
Revision Chapter 2

@@
 \section{Structure overview}
-The structure of this thesis is as follows: in the first instance, \chapref{chap:use_cases} defines a set of logical formulas that describe parameter properties and are suitable for distributed assertion checking.
+The structure of this thesis is as follows: in the first instance, \chapref{chap:use_cases} defines a set of logical formulas suitable for distributed assertion checking.
 Given this set, it demonstrates various practical use-cases for such properties and formalizes the costs of checking them locally, s.t.
@@
 In conclusion, the last chapter recaps the achieved results,
-addresses any open questions or issues and provides an outlook on upcoming work on this topic.
+addresses open questions or issues and provides an outlook on upcoming work on this topic.

### 2021-04-13 assertions/doc/thesis-bernhardt/chapters/2-use_case_analysis.tex
Rework objective; add structure overview; some conclusion stuff
Revision Chapter 2

@@
 \\
-The following section formally defines a set of applicable logical formulas for the first implementation of this approach.
-Given this set, section \secref{sec:examples} gives some more in-depth examples with their respective time complexity.
-\todo{General cost analysis?}
+The following section formally defines a set of applicable logical formulas for the basic implementation of this approach.
+Given this set, section \secref{sec:examples} gives some more in-depth examples.
+The last section formalizes the cost incurred by checking formulas on Tezos locally.
 
-\section{Definition of a set of logical formulae}\label{sec:formulae}
-As already mentioned, formulas containing universal and existential quantification are interesting use-cases.
+\section{Definition of a set of logical formulas}\label{sec:formulae}
+Formulas with universal and existential quantification are suitable for distributed assertion checking, because they span an iteration space with their domain of discourse.
+Within this space validators can check independently and point-wise, whether the property holds.
+Each validator is thus capable of making a statement about the validity by looking at a single element only.
 Predicate variables are, for now, limited to the primitive data types supported by the respective virtual machines (VM).
@@
 
-\secref{} goes into more detail about what this set comprises of concretely for assertions executed on Tezos, and which extensions to Michelson and the VM are necessary in order to facilitate the assertion examples given previously and in the following section.
-\todo{Secref}
+\secref{sec:syntax} and \secref{sec:ext} go into more detail about what this set comprises of concretely for assertions executed on Tezos, and which extensions to Michelson and the VM are necessary in order to facilitate the assertion examples given previously and in the following.
 
 \section{Interesting formulas and special cases}\label{sec:examples}
-The following use-cases are picked from \cite{bernhardt_veigel_2020}, which contains a more comprehensive collection of formulas and properties that can be checked using the proposed approach.
-The selection of examples demonstrates different meanings of their negations and special cases, which emerge from different compositions of quantification, and discusses possible implications thereof.
+This section contains a subset of use-cases that were collected in collaboration with Julian Veigl for an intermediate report \cite{bernhardt_veigel_2020}.
+The selection of examples covers different types and compositions of quantifiers, demonstrates different meanings of their negations, identifies special cases and discusses their implications for the implementation of distributed assertion checking.
 
@@
 A more specific $gcd$-problem is finding two numbers which are coprime, meaning their greatest common divisor is one, i.e., $gcd(a, b) = 1$ \cite{hardy2008introduction}.
-In order to verify that two numbers are coprime, it has to be checked that there exists no $gcd > 1$, which can be expressed in the following formula in predicate logic:
+In order to verify that two numbers are coprime, it has to be checked that there is no $gcd > 1$, hence the property of coprimeness can be expressed with the following formula in predicate logic:
 \begin{equation}\label{eq:coprime-universial}
@@
 \end{equation}
-Assuming constant time for calculating the two remainders, checking whether two numbers satisfy this property takes linear time, i.e.
-$\mathcal{O}(n)$, and depends on the size of the smaller number.
+Assuming constant time for calculating the two remainders, checking whether two numbers satisfy this property takes linear time, i.e. $\mathcal{O}(n)$, and depends on the size of the smaller number.
+
 When checking the assumption through a distributed effort instead, the validators consider its negation:
@@
 \subsection{Heap property}
-Heaps are data structures based on trees and can appear in two varieties: min and max heaps.
-Both can be represented as binary trees and have to satisfy the heap property \cite{dict_heap}: in a max heap, any given node holds a value lower or equal than that of its parent, whereas in a min heap, it is greater or equal \cite{dict_heap_property}.
+Heaps \cite{dict_heap} are data structures based on trees and can appear in two varieties: min and max heaps.
+Both can be represented as binary trees and have to satisfy the heap property: in a max heap, any given node holds a value lower or equal than that of its parent, whereas in a min heap, it is greater or equal \cite{dict_heap_property}.
 Binary heaps are often implemented as an array, with the root of the tree stored at index 0.
-The relatives of a node \texttt{k} can be accessed as follows \cite{dict_binary_heap}:
-\begin{lstlisting}[language=Solidity, numbers=none, caption=Access a binary heap in array representation \cite{bernhardt_veigel_2020}]
+The relatives of a node \texttt{k} can be accessed as follows:
+\begin{lstlisting}[language=Solidity, numbers=none, caption=Access a binary heap in array representation]
 heap_array[(k-1)/2] // Get parent of node k
@@
 \section{Existential quantifier and proofs of validity}\label{sec:existential}
-The examples given so far in this thesis used universal quantification and required a search for counterexamples in order to check if some assumption about an input parameter is true.
+The examples given so far in this thesis used universal quantification, and required a search for counterexamples in order to check if some assumption about an input parameter is true.
 However, the same cannot be applied to existential quantifiers.
@@
 \end{equation}
-If the condition is true for random values of $i,j$, it does not produce a counterexample, but it rather produces a proof for the validity of the assumption.
-In that case, the validator finding such a proof should publish an approval instead of a veto to the network and the normal execution of the contract can proceed.
-Thus, the two quantifiers essentially represent two different modi of assertion checking that the executors need to be aware of.
-\todo{If I pick this up again in a later chapter, ref.}\\
-Concerning the complexity of this test, the property can be checked in $\mathcal{O}(|u|*|v|)$.
+If the condition is true for random values of $i,j$, it does not produce a counterexample --- it produces a proof for the validity of the assumption.
+In that case, the validator finding such a proof should publish an approval instead of a veto to the network, and the normal execution of the contract can proceed.
+Thus, the universal and existential quantification essentially represent two different modi of assertion checking that the protocol needs to handle explicitly.\\
+Concerning the complexity of this assertion, the property can be checked in $\mathcal{O}(|u|*|v|)$.
 By considering the cardinality of their union $n = |u|+|v|$, one can derive that the worst case occurs when both sets have the same size, i.e., $|u| = |v| = n/2$.
@@
 It becomes less trivial though, if the nesting contains both universal and existential quantifiers.
-This section examines the case of $\exists i \forall j$ on the basis of a contract that expects a solution for a boolean satisfiability problem (SAT).
-Another instance of this use-case is also used to show that properties expressed with the nesting $\forall i \exists j$ cannot be checked with the proposed approach for distributed assertion checking offhand.
+This section examines the cases of $\forall i \exists j$ and $\exists i \forall j$ on the basis of a contract that expects a solution for a boolean satisfiability problem (SAT).
 
@@
 A SAT problem can be represented as a list of clauses $c$ and a variable assignment $\mathcal{A}$.
-To avoid having to handle the variables and their literals as strings and thus optimize runtime and memory consumption, an encoding scheme taken from this blogpost\cite{sabablog} is used: \\
+To avoid having to handle the variables and their literals as strings and thus optimize runtime and memory consumption, an encoding scheme taken from this blogpost \cite{sabablog} is used: \\
 Variables are encoded by a unique number starting from $0$ to $n-1$, where $n$ is the total number of variables.
@@
 \end{align*}
-As already mentioned, $F$ can be represented as a list of clauses, and each clause in turn can be represented as a list of literals. Consider the following boolean formula and variable assignment:
+Consider the following boolean formula and variable assignment:
 \begin{align*}
@@
 Following the encoding of variables given above, the list of variables $v=[A,B,C]$ occurring in $F$ is encoded as $v_{enc} = [0,1,2]$.
-$F$ is thus represented by the encoding $F_{enc} = [[0,2],[2,5]]$.
+If clauses are given as lists of literals, $F$ can be represented by the encoding $F_{enc} = [[0,2],[2,5]]$.
 Since the encoding of variables corresponds to their index in the list of variables, $\mathcal{A}$ can be passed as a list of booleans that maintains the same order of variables: $\mathcal{A}_{enc} = [False, True, False]$.
@@
 
-\subsection{Satisfiability in predicate logic - DNF}\label{sec:dnf}
-In opposition to the statement that modern SAT solvers expect $F$ to be in CNF, consider a contract that expects a SAT problem in disjunctive normal form (DNF) and a proposed assignment, both encoded as described above.
-A boolean formula in DNF is a disjunction of conjunctions \cite{dnf_math_encycl}.
+\subsection{Satisfiability in predicate logic - CNF}
+Consider a contract that expects a SAT problem in CNF and a proposed assignment, both encoded as described above.
 Assuming that $F$ is a k-SAT instance, the assumption that $\mathcal{A}$ satisfies $F$ can be expressed in predicate logic as follows:
-\begin{gather*}\label{eq:dnf_sat}
+\begin{equation}\label{eq:cnf_sat}
 \begin{aligned}
-(\exists i : int, \forall j : int) (0 \leq i < |F|) \wedge (0 \leq j < k) &\Rightarrow ((isPositive(F[i][j]) \wedge \mathcal{A}[decode(F[i][j])]) \\
+(\forall i : int, \exists j : int) &(0 \leq i < |F|) \wedge (0 \leq j < k) \\
+&\Rightarrow ((isPositive(F[i][j]) \wedge \mathcal{A}[decode(F[i][j])]) \\
 &\vee (\neg isPositive(F[i][j]) \wedge \neg \mathcal{A}[decode(F[i][j])])))
 \end{aligned}
-\end{gather*}
-With single quantification, we so far considered the negation of the formula in order to identify counterexamples (or proofs).
-However, by checking some literal in some clause, the validator cannot make a statement about the validity of the property, as the clauses have to be examined as a whole in order to verify that the conjunction evaluates to true.
+\end{equation}
+
+In the previous examples, where formulas contained only a single quantifier, the predicate variables of the negated formula are replaced by a randomly generated number during assertion checking.
+Quantifiers thus are translated to random generators during the generation of target code.
+However, by checking a random literal in a random clause, the validator cannot make a definite statement whether $\mathcal{A}$ satisfies $F$, since each clause has to be examined as a whole in order to verify that the conjunction evaluates to true.
 Consequently, the distribution can only take place on the level of clauses, but not on the level of literals.
-Each validator thus has to check all literals of one random clause and produce a proof of validity if all of them satisfy the property.
-This implies that the formula does not have to be negated.
-\\
-Besides having a distinct transformation, this case also has to be handled differently during the compilation process; instead of translating both quantifiers into a random generator, the universal quantifier has to be translated into a loop, cf.
-\lstref{lst:rand_loop}.
-\begin{lstlisting}[label=lst:rand_loop, numbers=none, caption=Translation of an assertion for a DNF SAT problem in pseudo-code]
+Each validator thus has to check all literals of one random clause, which translates into a random generator for the outer quantifier, and a loop for the inner quantifier.
+Whether the assertion requires a proof or a counterexample can be derived from the outer quantifier, hence validators produce a counterexample in this case.
+Due to the fact that the whole loop has to be run in order to identify a counterexample and the consequential code structure this translates to, the negation of the formula is not required but optional.
+\lstref{lst:cnf_test_code} shows the generated testing code of the CNF SAT problem with and without negating the formula first, where \texttt{check} evaluates the negated or non-negated condition respectively.
+While formulas with a single quantifier simply translate to generating a random value and checking the condition, this code is more extensive and requires a more sophisticated compiler that can differentiate between different quantification compositions.
+
+\vspace{\baselineskip}
+\noindent
+\begin{minipage}{.45\textwidth}
+\begin{lstlisting}[label=lst:cnf_code_neg, numbers=none]
 i = random(0, size(F))
 for (j : [0..k)):
-	check(...)
+  if not check( ... ):
+    // property holds
+    return true
+// counterexample found
+return false
 \end{lstlisting}
-In the case of k-SAT instances, the validators still only have to be paid a constant amount of gas, albeit with a factor $k$.
-If the number of literals in a clause is not constant, the loop will introduce a linear cost factor for each validator.
+\end{minipage}\hfill
+\begin{minipage}{.45\textwidth}
+\begin{lstlisting}[label=lst:cnf_code, numbers=none]
+i = random(0, size(F))
+for (j : [0..k)):
+  if check( ... ):
+    // property holds
+    return true
+// counterexample found
+return false
+\end{lstlisting}
+\end{minipage}
+\captionof{lstlisting}{Test code structure for single nested quantifiers with negation (left) and without negation (right)\label{lst:cnf_test_code}}
+\vspace{\baselineskip}
 
-\subsection{Satisfiability in predicate logic - CNF}
-Unfortunately, the same cannot be applied for the reverse quantification nesting.
-Consider the same contract, but instead of expecting $F$ in DNF, it expects it to be in CNF.
-The domain restrictions and open formula remain the same, but the quantifiers are in reverse order:
-\begin{gather*}\label{eq:cnf_sat}
+Due to the loop, the cost incurred by one validator checking the assertion becomes, in the worst case, linear in the number of literals in the clause.
+An exception is the case of k-SAT instances, where the cost per validators remains constant, albeit with a factor $k$.
+
+\subsection{Satisfiability in predicate logic - DNF}\label{sec:dnf}
+The same propositional formula with the reversed quantification nesting $\exists i \forall j$ describes the assertion for the assumption $\mathcal{A}(F) = 1$, where $F$ is given in disjunctive normal form (DNF), i.e., a disjunction of conjunctions \cite{dnf_math_encycl}:
+\begin{equation}\label{eq:dnf_sat}
 \begin{aligned}
-(\forall i : int, \exists j : int) (0 \leq i < |F|) \wedge (0 \leq j < k) &\Rightarrow ((isPositive(F[i][j]) \wedge \mathcal{A}[decode(F[i][j])]) \\
+(\exists i : int, \forall j : int) \: &(0 \leq i < |F|) \wedge (0 \leq j < k) \\
+&\Rightarrow ((isPositive(F[i][j]) \wedge \mathcal{A}[decode(F[i][j])]) \\
 &\vee (\neg isPositive(F[i][j]) \wedge \neg \mathcal{A}[decode(F[i][j])])))
 \end{aligned}
-\end{gather*}
-Again, the validator has to check the whole clause in order to know whether it evaluates to true.
-Due to existential quantification, however, the literals in the clauses cannot be checked independent of each other.
-A single literal evaluating to false does not make the whole clause evaluating to false.
-Although technically possible, it requires a more sophisticated compiler that translates this nesting into the following code structure:
-\begin{lstlisting}[label=lst:rand_loop_dependent, numbers=none, caption=Translation of an assertion for a CNF SAT problem in pseudo-code]
-i = random(0, size(F))
-for (j : [0..k)):
-	if check(...):
-		assert(true)
-assert(false)
-\end{lstlisting}
+\end{equation}
+The translation to code can be approached in the same way than its CNF counterpart. Instead of a counterexample, this use-case demands for a proof.
 
@@
 Nesting is, of course, not limited to two quantifiers only.
-Generally, formulas containing no quantification alterations within the nesting benefit the most from distributed assertion checking, as each quantifier can be translated into a random generator.
-On the other hand, formulas with a quantifier alteration early in the order of quantifiers benefit the least, because starting from the first alteration, the following quantifiers are translated to loops.\\
-To substantiate this argument, consider two variations of a contract that expect a list of boolean formulas in DNF, and an assignment $\mathcal{A}$.
-The first one checks, whether $\mathcal{A}$ satisfies at least one $F$, the other one checks if all $F$ are satisfied.
-This can be expressed by nesting quantifications as follows:
+Generally, formulas containing universal or existential quantification exclusively within the nesting benefit the most from distributed assertion checking, as each quantifier can be translated into a random generator.
+On the other hand, formulas with both types and a transition from one to the other early in the order benefit the least, because starting from the first transition, the subsequent quantifiers are translated to loops.\\
+To substantiate this argument, consider two variations of a contract that expect a list of boolean formulas in CNF, and an assignment $\mathcal{A}$.
+Variation one checks whether $\mathcal{A}$ satisfies at least one $F$, the other one checks if all $F$ are satisfied.
+This can be expressed by nesting quantifiers as follows:
 \begin{itemize}
-\item $\exists f \exists i \forall j$
-\item $\forall f \exists i \forall j$
+\item $\forall f \forall i \exists j$
+\item $\exists f \forall i \exists j$
 \end{itemize}
-In the first case, each validator picks a random clause from a random $F$ and checks if all literals evaluate to true.
-In the second case, checking a random clause in isolation cannot disprove the satisfiability, hence the validator has to check all clauses in a loop.
+In the first case, each validator picks a random clause from a random $F$ and checks if at least one literal evaluates to true.
+This translates to two random generators and a loop for the existential quantifier.
+In the second case, checking a random clause in isolation cannot prove the satisfiability, hence the validator has to check all clauses in a loop.
+This translates to one random generator and two loops.
 The same reasoning can be done for the reverse order, i.e.
-$\forall\forall\exists$ and $\exists\forall\exists$.
+$\exists\exists\forall$ and $\forall\exists\forall$.
 
-\subsection{Restriction of use-cases}\todo{Better title?}
-The examples given in this chapter have shown that, depending on the type and order of quantification, not all properties can be checked in the same way and need different modi of assertion checking.
-This increases the complexity and requirements for a implementation of this approach; therefore, for a first iteration, this thesis focuses on providing the fundamentals and implementation for assertions using universal quantification only.
+\section{Restriction of use-cases}\todo{Better title?}
+The examples given in this chapter have shown that, depending on the type and order of quantification, not all properties can be checked in the same way and need different modi of assertion checking, as well as a distinct translation to target code.
+This increases the complexity and requirements for an implementation of the off-chain infrastructure and protocol amendment; therefore, as a first iteration, this thesis focuses on providing a design and toolchain for assertions using universal quantification only.
 
 \section{Cost analysis}\label{sec:usecase_cost}
-In order to be able to evaluate whether distributed assertion checking can indeed lower the cost in comparison to a local verification, the cost of checking a formula on the blockchain needs to be formalized.
-Since this thesis describes an implementation of the approach on the Tezos blockchain, the following costs refer to that specific gas model, s.t.
-the results of the cost analyses are comparable (Tezos and its gas model are described in more detail in \secref{sec:tezos}).
-\\
-According to the gas model, the total gas consumption of a transaction $T(src,\, dst=C,\, arg, \, ...)$ to an originated contract $C(storage, \, parameter\, type, \, code)$ is calculated by \eqref{eq:gas_transaction}, where $I$ is the set of internal operations:
+For the purpose of having a benchmark for the evaluation of the distributed approach, this section analyses the cost of executing a contract on the blockchain that centrally checks a formula.
+Given that the target blockchain is Tezos, the computational and storage-related costs of a transaction are represented in units of gas.
+The following is thus based on the gas model of Tezos \cite{morley_gasmodel}\cite{tezos_repo}, which is described in more detail in \secref{sec:tezos}.
+According to this model, the total gas consumption of a transaction $T(source,\, destination=C,\, arg, \, ...)$ calling a smart contract $C(storage, \, parameter\, type, \, code)$ is calculated by \eqref{eq:gas_transaction}, where $I$ is the set of internal operations:
 \begin{align}\label{eq:gas_transaction}
@@
 \end{align}
-Assuming that the storage is never increased, the amount of gas returned by the cost functions independent of the argument, i.e., the parameter value, remain constant for each $T$.
-The cost functions for the deserialization, parsing and interpretation, however, are functions of $arg$ that grow strictly monotonic with increasing sizes of $arg$.
+Assuming that the storage of the contract is never increased, the amount of gas returned by the cost functions independent of the argument, i.e., the parameter value, remains constant for each $T$.
+The cost functions for the deserialization, parsing and interpretation, however, are functions of $arg$ that grow monotonically with increasing sizes of $arg$ \cite{morley_gasmodel}\cite{tezos_repo}.
 \\
 Consider the following simple contracts --- they do not do anything useful, but can be used to approximate the amplification of costs with regard to $arg$.
-Contract \texttt{Foo} takes an integer, whose byte sequence does not increase significantly with higher values, thus the increase in overall cost is mainly accounted for by interpretation cost.
-Contract \texttt{Bar}, on the other hand, executes similar operations but expects a list of integers, which causes noticeably higher deserialization and parsing costs with increasing input size.
+Contract \texttt{Foo} takes an integer, whose byte sequence representation does not increase significantly with higher values.
+Thus, the increase in overall costs is mainly accounted for by the interpretation.
+Contract \texttt{Bar}, on the other hand, executes similar operations but expects a list of integers, which causes noticeably higher deserialization and parsing costs with increasing input sizes.
 \begin{lstlisting}[numbers=none, language=Solidity, caption=Simple dummy contract executing a loop]
@@
     }
-	// ...
   }
@@
 As to be expected, the gradient of the cost function in the case of \texttt{Bar} is higher due to additional serialization and parsing costs, namely $\frac{dx}{dy} = 16$ compared to $\frac{dx}{dy} = 6$ for \texttt{Foo}.
-\begin{figure}[t]
+
+\begin{figure}[p]
 \centering
@@
 \label{fig:use_case_cost}
+\vspace{128in}
 \end{figure}

### 2021-04-13 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Revision Chapter 2

@@
 
-\subsection{Extensions}
+\subsection{Extensions}\label{sec:ext}
 In future iterations, the assertion syntax could be extended with some more features to improve usability and readability:

### 2021-04-15 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
Revise Introduction

@@
 \chapter{Introduction}\label{chap:introduction}
-Headed by Bitcoin in 2009, ``cryptocurrencies have emerged as the first generation of blockchain technology'' \cite{alharby_blockchain_2017}.
+Headed by Bitcoin in 2009 \cite{bitcoin-whitepaper}, the first generation of blockchain technology emerged in form of cryptocurrencies.
 However, their transactions are mostly limited to simple monetary transactions or registration of assets or ownerships \cite{alharby_blockchain_2017}.
-More recent blockchains, considered as the second generation \cite{alharby_blockchain_2017}, aim to provide a platform for building more sophisticated and complex applications on top of the technology.
-These are built with smart contracts, programs written in Turing-complete languages.
+More recent blockchains, considered as the second generation, aim to provide a platform for building more sophisticated and complex applications on top of the technology.
+Some prominent examples for such blockchains are Ethereum \cite{eth-whitepaper}, Tezos \cite{goodman_tezos_2014} or Cardano \cite{cardano_essay}, which plans to introduce smart contracts in an update this year \cite{cardano_alonzo}.
+Blockchain-based applications are built with smart contracts, programs written in Turing-complete languages.
 Running a smart contract, though, generates costs proportional to the amount and complexity of computations, as well as its storage usage \cite{alharby_blockchain_2017}.
-These fees, often measured in a unit called ``gas'', have to be paid for by the user in order to compensate the miners for their efforts \cite{chen_under-optimized_2020}.
+These fees, often measured in a unit called ``gas'', have to be paid for by the user in order to compensate the miners for their efforts \cite{narayanan_bitcoin}.
 This creates a powerful incentive to keep smart contracts simple and efficient, while in reality, meaningful applications still might need to perform some resource intensive computations.
@@
 \\
-In order to avoid these costs and restrictions, such an application could perform some computations outside of the blockchain context (i.e., off-chain) and only submit the results to a smart contract as an input parameter for further processing or recording \cite{thiemann_2020}.
+In order to avoid these costs and restrictions, such an application could perform some computations outside of the blockchain context (i.e., off-chain) and only submit the results to a smart contract as an input parameter for further processing or recording.
 By trusting that the submitted results are correct, this approach raises both safety and security issues.
@@
 \\
-Consider, for instance, the following smart contract:
-\begin{lstlisting}[caption=Smart contract expecting a prime number \cite{thiemann_2020}, numbers=none, language=Solidity, label=lst:prime]
+Consider the smart contract \texttt{Example}, which is shown in \lstref{lst:prime} and features a function \texttt{f}.
+The function takes an input value \texttt{p} of type integer and should make use of the assumption that \texttt{p} is a prime number.
+\begin{lstlisting}[caption=Smart contract with a function that expects a prime number \cite{thiemann_2020}, numbers=none, language=Solidity, label=lst:prime]
 contract Example {
-	function ( int p ) public {
+	function f ( int p ) public {
 	// assume p is prime
@@
 \end{lstlisting}
-The assumption, that the given integer $p$ is a prime, can be expressed as an explicit assertion in predicate logic \cite{thiemann_2020}: 
+This assumption ``$p$ is a prime number'' can be expressed with the following explicit assertion in predicate logic: 
 \begin{equation}\label{eq:prime}
@@
 \end{equation}
-To check whether this property holds for $p$, the contract has to execute a loop.
-Assuming computing the body of the loop takes constant time, this test has a time complexity of $\mathcal{O}(\sqrt{p})$ and therefore generates costs linear in $\sqrt{p}$ on top of the cost for executing the actual contract.
+To check whether this property holds for $p$, the contract has to execute a loop over the range $[2, \sqrt{p}]$.
+Assuming that computing the body of the loop takes constant time, this test has a time complexity of $\mathcal{O}(\sqrt{p})$ and therefore generates costs linear in $\sqrt{p}$ on top of the cost for executing the actual contract.
 Thus, a mechanism is required that allows the smart contract to make use of the result computed by an off-chain source, without having to check its validity locally with scaling costs.
@@
 \\
-However, distributed assertion checking is not only applicable for parameters or properties of dynamic size. Another example is a contract that expects an array of integers sorted in ascending order:
+However, distributed assertion checking is not only applicable for parameters or properties of dynamic size.
+Function \texttt{find} of contract \texttt{Sorted}, shown in \lstref{lst:sorted}, expects a statically sized array of integers and a single integer value.
+In order to find the value \texttt{v} in \texttt{a} more efficiently, the array is assumed to be sorted.
 
@@
     // assume a is sorted
+    ...
   }
@@
 
-The assumption that the list is sorted, expressed in predicate logic, is
+The explicit assertion of this assumption (in the variant of an ascending sorting) can be expressed as follows in predicate logic:
 \begin{equation}\label{eq:sorted}
@@
 \section{Objective}
-This thesis proposes the portrayed approach of a distributed assertion checking scheme in order to make more efficent use of off-chain resources.
-The realisation of such assertions consists of two components - the off-chain design and implementation of supporting infrastructure, as well as the extension of the smart contract language and amendment of the blockchain protocol, s.t.
-these assertions are triggered and handled correctly by the network.
-The focus of this thesis is put primarily on the off-chain component and the development of a toolchain that transforms and translates assertions to executable code for the target platform, but elaborates on the protocol design where necessary.
-To this end, a first approximation of a set of formulas amenable for distributed assertion checking is defined, special cases are identified and, if necessary, excluded.
-While the off-chain design and toolchain should be partially applicable to any blockchain supporting smart contracts, the case example for the protocol-specific parts of the design targets the Tezos blockchain and its built-in contract language Michelson.
-On the basis of the chosen design, the thesis evaluates the efficiency of the approach in terms of costs incurred by checking a formula on Tezos, and discusses if, and under which conditions, these costs are competitive versus a local approach.
+This thesis proposes a model for the portrayed approach of a distributed assertion checking scheme, to make more efficient use of off-chain computations.
+In this model, results of such computations are validated on-chain by the validators of the network.
+In order to do so, they invoke assertion smart contracts which point-wise check whether the result satisfies certain properties.
+When claiming an assertion failure, a validator publishes a counterexample to be scrutinized by the other validators.
+If they come to a consensus about the invalidity, the result is rejected.
+Provided that the assertion is cheaper than the computation itself, the purpose of this proposal is not only to reduce financial costs for the users, but also to overcome limitations in scalability.
+
+The realisation of such assertions consists of an off-chain and an on-chain component.
+The off-chain component is a toolchain to specify, integrate and generate assertion contracts that can be deployed to the blockchain.
+It defines of a domain-specific language which allows developers to specify assertions for each entrypoint of a Smart Contract.
+The toolchain implements a pipeline which transforms the assertion, links it with the Smart Contract and translates it to the Smart Contract language.
+\\
+The on-chain component consists of an amendment of the blockchain protocol to include transactions that can trigger the distributed execution of assertions and implement a consensus mechanism for counterexamples.
+
+The focus of this thesis is put primarily on the off-chain component, but it elaborates on the protocol design where necessary.
+Even though efforts were made to keep the design as generic and re-usable as possible, the implementation targets the Tezos blockchain and its built-in contract language Michelson.
+On the basis of the design and implementation for Tezos, the thesis evaluates the efficiency and incurred costs of this approach and discusses whether, and under which conditions, they can be competitive versus a centralized assertion approach.
+
+\section{Related work}
 

### 2021-04-15 assertions/doc/thesis-bernhardt/chapters/2-use_case_analysis.tex
Revise Introduction

@@
 Given that the target blockchain is Tezos, the computational and storage-related costs of a transaction are represented in units of gas.
-The following is thus based on the gas model of Tezos \cite{morley_gasmodel}\cite{tezos_repo}, which is described in more detail in \secref{sec:tezos}.
+Although they are not paid directly in terms of fees, the actual fees paid to the miner (called bakers in Tezos) are based on the gas consumption \cite{tezos_docs}.
+The gas model of Tezos is described in more detail in \secref{sec:tezos}.
 According to this model, the total gas consumption of a transaction $T(source,\, destination=C,\, arg, \, ...)$ calling a smart contract $C(storage, \, parameter\, type, \, code)$ is calculated by \eqref{eq:gas_transaction}, where $I$ is the set of internal operations:
@@
 \begin{split}
-GasConsumed(T) = \quad &base \, amount \\
+GasConsumed(T) = \quad &base \, gas \, cost \\
 +& \, gasRead(code) \\
@@
 Thus, the increase in overall costs is mainly accounted for by the interpretation.
-Contract \texttt{Bar}, on the other hand, executes similar operations but expects a list of integers, which causes noticeably higher deserialization and parsing costs with increasing input sizes.
+Contract \texttt{Bar}, on the other hand, executes similar operations but expects a list of integers, which additionally causes higher deserialization and parsing costs with increasing input sizes.
 \begin{lstlisting}[numbers=none, language=Solidity, caption=Simple dummy contract executing a loop]
@@
 
-\figref{fig:use_case_cost} shows the reported gas consumption of transactions calling the dummy contracts on the Delphinet test network running the protocol 007 Delphi \cite{tezos_docs}.
+\figref{fig:use_case_cost} shows the reported gas consumption of transactions calling corresponding dummy contracts in Michelson (cf.
+Appendix \ref{apx:cost_analysis_contract}) on the Delphinet test network, running the protocol 007 Delphi \cite{tezos_docs}.
 As to be expected, the gradient of the cost function in the case of \texttt{Bar} is higher due to additional serialization and parsing costs, namely $\frac{dx}{dy} = 16$ compared to $\frac{dx}{dy} = 6$ for \texttt{Foo}.
-
 \begin{figure}[p]
@@
 \end{figure}
-
-A repeated cost analysis is carried out in \secref{sec:cost_analysis_distributed} in order to assess whether, or how, distributed assertion checking, as described in the following chapters, can achieve a reduction of these costs.

### 2021-04-15 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Revise Introduction

@@
 The implementation of distributed assertion checking on any blockchain requires some off-chain considerations and infrastructure.
-The previous chapter defined a formal set of logical formulae amenable for this approach and gave some in-depth examples.
+The previous chapter defined a formal set of logical formulas amenable for this approach and gave some in-depth examples.
 As stated before, the proposed implementation in the following chapters is, for the most part, restricted to formulas of predicate logic using universal quantification.\\
@@
 The stages of the pipeline frontend, including parsing and transforming the original assertions to assertions that check for counterexamples, are described in \secref{sec:pipeline_front}.
-Lastly, \secref{sec:accuracy} analyses the reliability of distributed assertion checking as proposed and the cost incurred by increasing it.
+Lastly, \secref{sec:accuracy} analyses the reliability of distributed assertion checking as proposed and to what extent it affects the costs.
+
+% provide a high level language specifying complex computations that way  is  hard  and  inconvenient
+% 1) propose a model/approach to make use of off-chain computations that can be verified with explicit assertions
+% 2) contribute a toolchain that consists of a domain-specific language and a compilation pipeline that generates assertion smart contracts for the target blockchain Tezos.
+efforts were made to keep this as generic as possible, s.t.
+it can be extended for other target platforms as well
+% extend smart contracts and the VM with opcodes
 
 \section{Assertion syntax}\label{sec:syntax}
-The assertion syntax is described in two versions by the EBNF grammars shown in appendix \ref{apx:grammar}.
+The assertion syntax is described in two versions by the grammars in extended Backus-Naur form (EBNF) shown in appendix \ref{apx:grammar}.
 One version implements a prefix and the other one an infix notation.
@@
 To avoid context switches (at least for developers on Tezos), the assertion syntax references those of OCaml and thereby also Michelson.\\
+\lstinputlisting[caption=Assertion contract for checking if a list is sorted, language=Assertion, label={lst:sorted_assertion}]{listings/sorted.tza}
 A file containing assertions (henceforth referred to as ``assertion contract'') contains at least one assertion for some function or entrypoint of the original contract (henceforth referred to as ``parent contract'').
-An assertion begins with a signature consisting of an optional tag followed by a parameter type declaration.
-The tag can be used for documentation, but may sometimes be needed to indicate to which function of the parent contract the assertion should be assigned.
+An assertion begins with a signature consisting of an optional tag denoted by \%, followed by a parameter pattern.
+The tag can be used for documentation purposes, but may sometimes be needed to indicate which function of the parent contract the assertion should be assigned to by mirroring the entrypoint name.
+Parameter patterns are similar to patterns in OCaml --- they are templates that match shapes of data structures and binds identifiers to the components of them.
+The pattern given in the signature must match the parameter type of the entrypoint it refers to.
 The body is an (optional) nesting of quantifiers and conditions around exactly one assertion.
@@
 This also allows the transformation to be oblivious of the target platform and be identical for all backends.
-The current version of the grammar recognizes all types present in the Tezos VM and a subset of operations that Michelson provides ( \secref{sec:tezos} contains an introduction to Tezos and Michelson and goes more into detail about this).
+The current version of the grammar recognizes all types present in the Tezos VM and a subset of operations that Michelson provides (\secref{sec:tezos} contains an introduction to Tezos and Michelson and goes more into detail about this).
 Responsible for rejecting any assertions containing unsupported types or operations are the respective backends.\\
@@
 \end{equation}
-The respective assertion that checks this property for the parent contract from \lstref{lst:sorted} could be expressed as follows:
-\lstinputlisting[caption=Assertion contract for checking if a list is sorted, language=Assertion, label={lst:sorted_assertion}]{listings/sorted.tza}
+The respective assertion that checks this property for the parent contract, given in \lstref{lst:sorted}, is expressed in \lstref{lst:sorted_assertion}.
 
@@
 The frontend of the compilation pipeline comprises of a command-line interface (CLI), a parser and the transformation.
-These stages are generic and independent of the target platform and produce an abstract syntax tree (AST) of the assertion that is passed to the respective back-end through a public interface.
+These stages are generic and independent of the target platform, and produce an abstract syntax tree (AST) of the assertion.
+This AST	is then passed to the respective back-end through a public interface.
 \begin{figure}[h]
@@
 \end{figure}
-OCaml was chosen as a programming language to implement the pipeline, given that it's also used to develop the Tezos blockchain refer to \secref{sec:tezos}).
-This avoids context switches within the Tezos eco-system and allows to build on top of the Tezos libraries.
-\chapref{chap:offline_tezos} goes into more details about this.
+OCaml was chosen as a programming language to implement the pipeline, given that it's also used to develop the Tezos blockchain.
+This avoids context switches within the Tezos eco-system and allows to build on top of the Tezos libraries (cf.
+\secref{sec:tezos}).
 

### 2021-04-15 assertions/doc/thesis-bernhardt/chapters/4-offline_design_tezos.tex
Revision Chapter 2
Revise Introduction

@@
 
+\todo{Cheaper for the network if not all validators have to execute the whole local check!
+however, placing these costs on the users will cause them to use the local approach -> users need incentives to use it too!
+-> blockchain protocol could/should solve this!
+(e.g.
+use rewards instead of costs)}
+\todo{Every transaction is processed at every node in the network,which limits throughput}
+
 \section{Representing counterexamples}

### 2021-04-16 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
Revision use-cases + related work

@@
 \section{Objective}
-This thesis proposes a model for the portrayed approach of a distributed assertion checking scheme, to make more efficient use of off-chain computations.
+This thesis proposes a model for the portrayed approach of a distributed assertion checking scheme, in order to make more efficient use of off-chain computations.
 In this model, results of such computations are validated on-chain by the validators of the network.
@@
 If they come to a consensus about the invalidity, the result is rejected.
-Provided that the assertion is cheaper than the computation itself, the purpose of this proposal is not only to reduce financial costs for the users, but also to overcome limitations in scalability.
+Provided that the assertion is cheaper than the computation itself, the purpose of this proposal is not only to reduce financial costs for the users, but also to overcome limitations in scalability imposed by gas limits.
 
@@
 The off-chain component is a toolchain to specify, integrate and generate assertion contracts that can be deployed to the blockchain.
-It defines of a domain-specific language which allows developers to specify assertions for each entrypoint of a Smart Contract.
-The toolchain implements a pipeline which transforms the assertion, links it with the Smart Contract and translates it to the Smart Contract language.
-\\
-The on-chain component consists of an amendment of the blockchain protocol to include transactions that can trigger the distributed execution of assertions and implement a consensus mechanism for counterexamples.
+This includes the definition of a domain-specific language which allows developers to specify assertions for each entrypoint of a Smart Contract.
+The on-chain component, on the other hand, consists of an amendment of the blockchain protocol.
+This amendment includes an extension of the Smart Contract language with opcodes to generate random values in a non-deterministic way, a transaction type that can trigger the distributed execution of assertions, and the implementation of a consensus mechanism for counterexamples.
 
 The focus of this thesis is put primarily on the off-chain component, but it elaborates on the protocol design where necessary.
-Even though efforts were made to keep the design as generic and re-usable as possible, the implementation targets the Tezos blockchain and its built-in contract language Michelson.
-On the basis of the design and implementation for Tezos, the thesis evaluates the efficiency and incurred costs of this approach and discusses whether, and under which conditions, they can be competitive versus a centralized assertion approach.
+Even though efforts were made to keep the design as generic and re-usable as possible, the implementation targets the Tezos \cite{goodman_tezos_2014} blockchain and its built-in contract language Michelson \cite{michelson_ref}.
+On the basis of the design and implementation for Tezos, the thesis evaluates the efficiency and incurred costs of this approach compared to a centralized assertion approach.
 
 \section{Related work}
+Outsourcing computations or storage to off-chain resources in order to improve the scalability of blockchains has been the topic of several research papers and projects, which provide diverse solutions for different applications and use-cases.
+Eberhardt and Tai \cite{eberhardt_offonchain} give insights gained from a set of blockchain projects focusing on off-chaining.
+They provide five patterns to move either computations or storage off the chain without compromising the benefits of blockchains.
+The ``Delegated Computation Pattern'' outsources computations, which are too complex for on-chain execution, to an untrusted third party and only verifies the proof of correct execution on-chain.
+The proposed approach of a distributed assertion checking scheme can therefore be considered as an implementation of this pattern.
+
+ZoKrates \cite{eberhardt_zokrates_2018} proposes a processing model for the same pattern which employs non-interactive zero-knowledge proofs (zkSNARKs).
+When such proofs are supplied together with the results, the correctness can be validated fast and cheaply by the miners and nodes of the network.
+They additionally provide a toolbox and a domain-specific language to specify off-chain computations, generate respective proofs and export Smart Contracts verifying these proofs.
+
+The TrueBit \cite{teutsch_truebit} project provides another means for off-chaining computations on the Ethereum blockchain.
+It outsources computations to a pool of \textit{Solvers}, whose solutions are either verified or challenged by a pool of \textit{Verifiers}, or \textit{Challengers}.
+The protocol uses economic incentives to encourage active participation of all roles and only engages the miners as \textit{Judges} in case of a dispute between a Solver and a Challenger.
 

### 2021-04-16 assertions/doc/thesis-bernhardt/chapters/2-use_case_analysis.tex
Revision use-cases + related work

@@
 It showed examples for such properties and identified logical formulas containing universal quantification as amenable for distributed assertion checking.
+Through its domain of discourse, the quantification spans an iteration space whose elements can be checked independently by each validator.
 As a matter of fact, the same is also valid for existential quantification, even though its negation has a different notion than that of its universal counterpart.
@@
 The following section formally defines a set of applicable logical formulas for the basic implementation of this approach.
-Given this set, section \secref{sec:examples} gives some more in-depth examples.
-The last section formalizes the cost incurred by checking formulas on Tezos locally.
+Given this set, section \secref{sec:examples} gives some more in-depth examples of such formulas.
+As a benchmark for the distributed scheme, the last section formalizes the cost incurred by checking formulas on Tezos locally.
 
 \section{Definition of a set of logical formulas}\label{sec:formulae}
-Formulas with universal and existential quantification are suitable for distributed assertion checking, because they span an iteration space with their domain of discourse.
-Within this space validators can check independently and point-wise, whether the property holds.
-Each validator is thus capable of making a statement about the validity by looking at a single element only.
-Predicate variables are, for now, limited to the primitive data types supported by the respective virtual machines (VM).
-Besides the basic logical, numerical and relational operators of predicate logic, the formula may contain any operation that is built into the VM.
+The set of formulas that well-formed assertions can express is given in \figref{fig:formulas}.
+This corresponds, with some restrictions, to the language of second-order predicate logic.
+Besides universal and existential quantifiers with exactly one bound variable, the set definition contains logical connectives, relational symbols, constant values of a numerical, string or boolean type, variables and the basic functional symbols for basic arithmetic operations.
+This set of symbols is rather generic and should be valid for any target blockchain.
+Specific to the target blockchain are the sets of types $t$ and functional symbols $f$.
+These can only contain types and operations that can be translated to operation codes (opcodes) of the respective Smart Contract language and executed within the blockchain's virtual machine (VM).
+As an example, the primitive types in Michelson are \texttt{string}, \texttt{nat}, \texttt{int}, \texttt{bytes}, whereas Ethereum's Smart Contract language Solidity  \cite{solidity_docs} additionally supports an \texttt{enum} type and fixed-point numbers.
+
 \begin{align*}
@@
     \odot &::= +\mid -\mid * \mid / \mid \% \\
-    c &::= \text{constants: numbers, strings, } \top, \bot \\
+    c &::= \text{numerical value} \mid string \mid \top \mid \bot \\
     f &::= \text{operations (existing in the blockchain VM)}
@@
 \captionof{figure}{Set of logical formulas amenable to distributed assertion checking (based on \cite{thiemann_2020})}
+\label{fig:formulas}
 \vspace*{\baselineskip}\endgroup
-
-\secref{sec:syntax} and \secref{sec:ext} go into more detail about what this set comprises of concretely for assertions executed on Tezos, and which extensions to Michelson and the VM are necessary in order to facilitate the assertion examples given previously and in the following.
 
@@
 The greatest common divisor ($gcd$) of two non-zero integers $a$ and $b$ is the largest integer that divides both evenly \cite{hardy2008introduction}.
-A more specific $gcd$-problem is finding two numbers which are coprime, meaning their greatest common divisor is one, i.e., $gcd(a, b) = 1$ \cite{hardy2008introduction}.
+A more specific $gcd$-problem is finding two numbers which are coprime, meaning their greatest common divisor is one, i.e., $gcd(a, b) = 1$.
 In order to verify that two numbers are coprime, it has to be checked that there is no $gcd > 1$, hence the property of coprimeness can be expressed with the following formula in predicate logic:
@@
 
-\section{Existential quantifier and proofs of validity}\label{sec:existential}
-The examples given so far in this thesis used universal quantification, and required a search for counterexamples in order to check if some assumption about an input parameter is true.
-However, the same cannot be applied to existential quantifiers.
-Consider a contract expecting two intersecting sets of integers, represented as arrays.
-The assumption, that the intersection of the sets is not empty, i.e., $U \cap V \neq \emptyset$, can be expressed by
+\section{Existential quantification and proofs of validity}\label{sec:existential}
+So far, this thesis only considered formulas featuring universal quantification, for which the assertion scheme challenged the validators to find counterexamples.
+However, distributed assertion checking can not only be used to refute assumptions, but also to prove their validity.
+This is the case for formulas featuring existential quantification.
+As an example, consider the assumption that two sets $U$ and $V$ have a non-empty intersection, i.e., $U \cap V \neq \emptyset$.
+This assumption and its negation can be expressed in predicate logic by
 \begin{equation}\label{eq:intersect}
@@
 \end{equation}
-Consider its negation:
+and
 \begin{equation}\label{eq:intersect_neg}
@@
 \end{equation}
-If the condition is true for random values of $i,j$, it does not produce a counterexample --- it produces a proof for the validity of the assumption.
-In that case, the validator finding such a proof should publish an approval instead of a veto to the network, and the normal execution of the contract can proceed.
-Thus, the universal and existential quantification essentially represent two different modi of assertion checking that the protocol needs to handle explicitly.\\
+If the condition $u[i] \neq v[j]$ is false for random values of $i$ and $j$, it does not produce a counterexample --- it produces a proof for the validity of the assumption, because it identified an element that is present in both sets.
+In that case, the validator finding such a proof should publish an approval instead of a veto to the network.
+After an approval has been posted, and all validators have come to a consensus about the validity of the assumption, the transaction may be included in a block (assuming it doesn't fail due to other reasons).
+For the blockchain protocol, this implies that distributed refutation and validation have to be implemented as separate modi of assertion checking.
+\\
+
 Concerning the complexity of this assertion, the property can be checked in $\mathcal{O}(|u|*|v|)$.
@@
 
-\section{Cost analysis}\label{sec:usecase_cost}
-For the purpose of having a benchmark for the evaluation of the distributed approach, this section analyses the cost of executing a contract on the blockchain that centrally checks a formula.
+\section{Cost analysis of a local approach}\label{sec:usecase_cost}
+For the purpose of having a benchmark for the evaluation of the distributed approach, this section analyses the cost of invoking a contract on the blockchain that locally checks a formula.
 Given that the target blockchain is Tezos, the computational and storage-related costs of a transaction are represented in units of gas.
-Although they are not paid directly in terms of fees, the actual fees paid to the miner (called bakers in Tezos) are based on the gas consumption \cite{tezos_docs}.
+Although they are not paid directly in terms of fees, the actual fees paid to the miner (called bakers in Tezos) are based on the gas consumption.
 The gas model of Tezos is described in more detail in \secref{sec:tezos}.
@@
 Consider the following simple contracts --- they do not do anything useful, but can be used to approximate the amplification of costs with regard to $arg$.
-Contract \texttt{Foo} takes an integer, whose byte sequence representation does not increase significantly with higher values.
-Thus, the increase in overall costs is mainly accounted for by the interpretation.
-Contract \texttt{Bar}, on the other hand, executes similar operations but expects a list of integers, which additionally causes higher deserialization and parsing costs with increasing input sizes.
+Function \texttt{foo} of contract \texttt{Foo} takes an integer as input parameter, whose byte sequence representation does not increase significantly with higher values.
+Thus, the increase in overall costs is mainly accounted for by the interpretation cost.
+Contract \texttt{Bar}, on the other hand, executes similar operations in function \texttt{bar}, but expects a list of integers.
+The list data type additionally causes higher deserialization and parsing costs with increasing input sizes.
 \begin{lstlisting}[numbers=none, language=Solidity, caption=Simple dummy contract executing a loop]
@@
 \figref{fig:use_case_cost} shows the reported gas consumption of transactions calling corresponding dummy contracts in Michelson (cf.
-Appendix \ref{apx:cost_analysis_contract}) on the Delphinet test network, running the protocol 007 Delphi \cite{tezos_docs}.
-As to be expected, the gradient of the cost function in the case of \texttt{Bar} is higher due to additional serialization and parsing costs, namely $\frac{dx}{dy} = 16$ compared to $\frac{dx}{dy} = 6$ for \texttt{Foo}.
+Appendix \ref{apx:cost_analysis_contract}) on the Delphinet test network \footnote{\url{https://tezos.gitlab.io/introduction/test_networks.html\#delphinet}}.
+As to be expected, the gradient of the cost function in the case of \texttt{Bar.bar} is higher due to additional serialization and parsing costs, namely $\frac{dx}{dy} = 16$ compared to $\frac{dx}{dy} = 6$ for \texttt{Foo.foo}.
+
+Besides inflicting higher transaction costs on the user with increasing parameter sizes, a local approach also causes a higher ``footprint'' on the blockchain network.
+The transaction has to be processed at every full node of the network, which do not get any rewards in return (except for the nodes that were assigned baking or endorsement rights for the current block \footnote{Tezos' Proof of Stake consensus mechanism is described in \secref{sec:tezos}}).
+
 \begin{figure}[p]

### 2021-04-17 assertions/doc/thesis-bernhardt/chapters/2-use_case_analysis.tex
Revision chpt 3 assertion language

@@
 
-\section{Interesting formulas and special cases}\label{sec:examples}
+\section{Examples and special cases}\label{sec:examples}
 This section contains a subset of use-cases that were collected in collaboration with Julian Veigl for an intermediate report \cite{bernhardt_veigel_2020}.
@@
 
-\section{Existential quantification and proofs of validity}\label{sec:existential}
+\subsection{Existential quantification - intersection of sets}\label{sec:existential}
 So far, this thesis only considered formulas featuring universal quantification, for which the assertion scheme challenged the validators to find counterexamples.
@@
 
-\section{Nested quantification}
+\subsection{Nested quantification - SAT problems}
 The previous example showed that universal and existential quantification have to be handled differently.
@@
 This section examines the cases of $\forall i \exists j$ and $\exists i \forall j$ on the basis of a contract that expects a solution for a boolean satisfiability problem (SAT).
+\\
 
-\subsection{Boolean satisfiability problem}\label{sec:sat}
 Instances of SAT problems consist of a formula $F$ in propositional logic, and determine if there exists a variable assignment $\mathcal{A}$ to the values $true$ or $false$, s.t.
@@
 
-\subsection{Satisfiability in predicate logic - CNF}
+\subsubsection{Satisfiability in predicate logic - CNF}
 Consider a contract that expects a SAT problem in CNF and a proposed assignment, both encoded as described above.
@@
 
-\subsection{Satisfiability in predicate logic - DNF}\label{sec:dnf}
+\subsubsection{Satisfiability in predicate logic - DNF}\label{sec:dnf}
 The same propositional formula with the reversed quantification nesting $\exists i \forall j$ describes the assertion for the assumption $\mathcal{A}(F) = 1$, where $F$ is given in disjunctive normal form (DNF), i.e., a disjunction of conjunctions \cite{dnf_math_encycl}:
@@
 
-\section{Restriction of use-cases}\todo{Better title?}
-The examples given in this chapter have shown that, depending on the type and order of quantification, not all properties can be checked in the same way and need different modi of assertion checking, as well as a distinct translation to target code.
+\section{Restriction of use-cases}\label{sec:restrict}\todo{Better title? -> conclusion?}
+\todo{meh}
+The examples given in this chapter have shown that, depending on the type and order of quantification, not all properties can be checked in the same way and need different modi of assertion checking.
+Additionally,  as well as a distinct translation to target code.
 This increases the complexity and requirements for an implementation of the off-chain infrastructure and protocol amendment; therefore, as a first iteration, this thesis focuses on providing a design and toolchain for assertions using universal quantification only.

### 2021-04-17 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Revision chpt 3 assertion language

@@
 
-\chapter{Generic Off-Chain Design}\label{chap:offline}
-The implementation of distributed assertion checking on any blockchain requires some off-chain considerations and infrastructure.
-The previous chapter defined a formal set of logical formulas amenable for this approach and gave some in-depth examples.
-As stated before, the proposed implementation in the following chapters is, for the most part, restricted to formulas of predicate logic using universal quantification.\\
-The purpose of the off-chain infrastructure is to provide a syntax for stating assertions that check logical formulas, as well as a toolchain to compile these assertions into code that can be originated on the target blockchain.
-Depending on the individual solution for the respective blockchain protocol, this can either be the original contract extended directly with the assertion code, or as a separate contract that extends the original contract in some other way.
-This chapter describes the generic part of the off-chain design, which corresponds to the frontend of the compilation pipeline shown in \figref{fig:pipeline_frontend}.
-As a start, \secref{sec:syntax} describes the concrete syntax for writing assertions and shows how it expresses some of the previously given examples.
-The stages of the pipeline frontend, including parsing and transforming the original assertions to assertions that check for counterexamples, are described in \secref{sec:pipeline_front}.
-Lastly, \secref{sec:accuracy} analyses the reliability of distributed assertion checking as proposed and to what extent it affects the costs.
+\chapter{Toolchain Implementation - Frontend}\label{chap:offline}
+The purpose of the toolchain is to support the proposed model from specifying assertions for Smart Contracts, transforming them to their negation to generating assertion Smart Contracts that can be invoked by the validators.
+As determined in \secref{sec:restrict}, the current version of the toolchain only supports the processing of assertions featuring universal quantification.
+The code is available in a GitHub\footnote{\url{https://github.com/proglang/thesis-distributed-assertion-checking}\todo{commit}} repository of the Chair of Programming Languages.
+
+As an overview, \figref{fig:pipeline_frontend} depicts all stages of the processing pipeline implemented by the toolchain.
+The colourized stages highlight the frontend, which was designed to be as generic as possible, s.t.
+it can be used (or extended) to support any target blockchain.
+For the target-specific processing, the intermediate result of the frontend is passed to the respective backends via a public interface.
+
+First, developers can specify assertions in a domain-specific language, which is described in \secref{sec:syntax}.
+The toolchain then parses the assertions into abstract syntax trees (ASTs), which are passed to the transformation stage.
+In this stage, the ASTs are transformed into ASTs that represent their negation.
+This is described further in \secref{sec:transformation}.
+The resulting ASTs are then passed to the backend, which is introduced in the subsequent chapter for the Tezos blockchain.
+%Lastly, \secref{sec:accuracy} analyses the reliability of distributed assertion checking as proposed and to what extent it affects the costs.
 
@@
 \section{Assertion syntax}\label{sec:syntax}
-The assertion syntax is described in two versions by the grammars in extended Backus-Naur form (EBNF) shown in appendix \ref{apx:grammar}.
+Tezos' Smart Contract language Michelson is a low-level and stack-based language.
+Specifying assertions that way is complex and inconvenient, especially if the language is compiled to other targets as well.
+Therefore, this thesis defines a domain-specific high-level language to express assertions.
+
+The syntax of this language is described in two versions by the EBNF grammars given in appendix \ref{apx:grammar}.
 One version implements a prefix and the other one an infix notation.
-The pipeline currently supports the prefix notation with mandatory parentheses to avoid the need of handling operator precedences.
-To avoid context switches (at least for developers on Tezos), the assertion syntax references those of OCaml and thereby also Michelson.\\
+The parser currently supports the prefix notation and correct operator precedences must be handled explicitly with parentheses.
+To avoid context switches (for developers on Tezos), the syntax is inspired by OCaml \cite{ocaml_docs} and uses the same type notations as Michelson.
+
+\subsection{Code structure}
+Assertions are passed to the toolchain as simple text files.
+This thesis follows the convention of using the file extension \texttt{.tza} for such files (henceforth referred to as ``assertion contracts'') in reference to the file extension \texttt{.tz}used for Michelson source files.
+Assertion contracts contain at least one assertion for a specific entrypoint of the actual contract (henceforth referred to as ``parent contract'').
+For the remaining entrypoints the compiler automatically generates empty assertions\footnote{cf.
+\secref{sec:compiler}}.
+
+An assertion begins with the keyword \texttt{entrypoint} and a signature consisting of an optional tag denoted by \%, followed by a parameter pattern.
+Parameter patterns are similar to patterns in OCaml --- they are templates that match shapes of data structures and bind identifiers to the components of them.
+The given parameter pattern must match exactly the parameter type of the entrypoint it is associated with.
+The body of an assertion can contain a nesting of quantifiers and conditions around exactly one \texttt{assert} expression.
+Conditions can be used to restrict the quantification domains or for any other constraints.
+For completeness, the existential quantifier is already included in the grammar, however the current version of the pipeline will reject any assertions containing it.
+
+How the assertions are associated with the respective entrypoint of the parent contract depends on the Smart Contract language.
+In the case of Solidity, a tag that mirrors the function name is enough to link assertion and entrypoint.
+In Michelson contracts, on the other hand, entrypoints can be anonymous.
+Therefore, the assertions are linked to the entrypoints through the tags, the parameter type or both.
+\secref{sec:typecheck} describes in more detail how the linking is implemented in the Tezos backend.
+
+\subsection{Parameter patterns}
+\lstref{lst:patterns} gives an overview of the parameter patterns supported in the assertion language.
+\lstinputlisting[caption=Patterns in the assertion language, language=, numbers=none, label=lst:patterns]{listings/patterns.txt}
+
+By using patterns, developers can avoid the explicit handling of special cases, such as empty lists, in the assertion specification.
+Furthermore, they can be used to put emphasis on the relevant components of the input parameters by replacing the irrelevant ones with wildcards.
+As an example, the assertion given in \lstref{lst:patterns_usage} concerns the left element of a pair and only applies to non-empty lists.
+\begin{lstlisting}[label=lst:patterns_usage, language=Assertion, numbers=none]
+(entrypoint %g (pair (cons a as) _)  ...)
+\end{lstlisting}
+
+\subsection{Types and operations}
+In order to make the frontend generic, the sets of data types and operations supported by the grammar constitute unions of those present in the target languages.
+This not only the implementation of a single, common parser, but also allows the transformation to be oblivious of the target platform.
+As a consequence, the backends are responsible for performing a semantic check and  rejecting any assertions containing types or operations which are not supported by the target language.
+
+The current version of the language contains all data types present in Tezos' VM and a subset of operations that Michelson provides (as of protocol version 007 Delphi).
+Besides the primitive types \texttt{int}, \texttt{nat} (natural numbers), \texttt{string}, \texttt{bool}, \texttt{bytes} and \texttt{unit}, this includes composite types like \texttt{list}, \texttt{pair}, \texttt{map} or the union type \texttt{or}.
+Domain specific data types, like \texttt{timestamp} or \texttt{address}, are supported as well.
+The data type \texttt{fmu} represents a generic fractional monetary unit, which is translated to the corresponding token type of the target platform\footnote{Mutez in Tezos, or Wei in Ethereum}.
+
+\subsection{Example}
 \lstinputlisting[caption=Assertion contract for checking if a list is sorted, language=Assertion, label={lst:sorted_assertion}]{listings/sorted.tza}
-A file containing assertions (henceforth referred to as ``assertion contract'') contains at least one assertion for some function or entrypoint of the original contract (henceforth referred to as ``parent contract'').
-An assertion begins with a signature consisting of an optional tag denoted by \%, followed by a parameter pattern.
-The tag can be used for documentation purposes, but may sometimes be needed to indicate which function of the parent contract the assertion should be assigned to by mirroring the entrypoint name.
-Parameter patterns are similar to patterns in OCaml --- they are templates that match shapes of data structures and binds identifiers to the components of them.
-The pattern given in the signature must match the parameter type of the entrypoint it refers to.
-The body is an (optional) nesting of quantifiers and conditions around exactly one assertion.
-Conditionals can be used to restrict the quantification domains or for some other constraints.
-For completeness, the existential quantifier is already included in the grammar, however the current version of the pipeline will reject any assertions containing it.
-\\
-In order to make the frontend generic, the assertion grammar constitutes a union of operations and types for the target languages.
-This also allows the transformation to be oblivious of the target platform and be identical for all backends.
-The current version of the grammar recognizes all types present in the Tezos VM and a subset of operations that Michelson provides (\secref{sec:tezos} contains an introduction to Tezos and Michelson and goes more into detail about this).
-Responsible for rejecting any assertions containing unsupported types or operations are the respective backends.\\
 
@@
 \section{Accuracy of the approach}\label{sec:accuracy}
+\todo{Idea: own chapter "probabilistic model" oder so - OR: model description}
 Since the proposed approach implements a probabilistic test, the accuracy as well as the costs incurred by guaranteeing a specified certainty threshold, need to be examined closely.

### 2021-04-17 assertions/doc/thesis-bernhardt/chapters/4-offline_design_tezos.tex
Revision chpt 3 assertion language

@@
 
-\subsection{Type check}
+\subsection{Type check}\label{sec:typecheck}
 The task of the type checker is to map the assertions from the given file to the respective entrypoints of the parent contract.
@@
 \\
-As an exemplification, consider a Michelson contract with five entrypoints (including the \texttt{\%default}):
+As an example, consider a Michelson contract with five entrypoints (including the \texttt{\%default}):
 \begin{lstlisting}[numbers=none, language=Michelson]
@@
 
-\subsection{Compiler}
+\subsection{Compiler}\label{sec:compiler}
 The transformed and type checked assertion AST needs to be retargeted to Michelson code according to the orchestration scheme.
@@
 The generated code of the assertion body and the parameter type can be plugged into a template that already contains the necessary boilerplate code for a contract.
+% type inference from patterns
+% handling of patterns like cons
 

### 2021-04-18 assertions/doc/thesis-bernhardt/chapters/2-use_case_analysis.tex
Parser + Transformation

@@
 The cost functions for the deserialization, parsing and interpretation, however, are functions of $arg$ that grow monotonically with increasing sizes of $arg$ \cite{morley_gasmodel}\cite{tezos_repo}.
-\\
+
 Consider the following simple contracts --- they do not do anything useful, but can be used to approximate the amplification of costs with regard to $arg$.
@@
 As to be expected, the gradient of the cost function in the case of \texttt{Bar.bar} is higher due to additional serialization and parsing costs, namely $\frac{dx}{dy} = 16$ compared to $\frac{dx}{dy} = 6$ for \texttt{Foo.foo}.
-
-Besides inflicting higher transaction costs on the user with increasing parameter sizes, a local approach also causes a higher ``footprint'' on the blockchain network.
-The transaction has to be processed at every full node of the network, which do not get any rewards in return (except for the nodes that were assigned baking or endorsement rights for the current block \footnote{Tezos' Proof of Stake consensus mechanism is described in \secref{sec:tezos}}).
-
-\begin{figure}[p]
+\begin{figure}[h]
 \centering
@@
 \label{fig:use_case_cost}
-\vspace{128in}
+%\vspace{128in}
 \end{figure}
+
+Besides inflicting higher transaction costs on the user with increasing parameter sizes, a local approach also causes a higher ``footprint'' on the blockchain network.
+The transaction has to be processed at every full node of the network, which do not get any rewards in return (except for the nodes that were assigned baking or endorsement rights for the current block\footnote{Tezos' Proof of Stake consensus mechanism is described in \secref{sec:tezos}}).

### 2021-04-18 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Parser + Transformation

@@
 As determined in \secref{sec:restrict}, the current version of the toolchain only supports the processing of assertions featuring universal quantification.
-The code is available in a GitHub\footnote{\url{https://github.com/proglang/thesis-distributed-assertion-checking}\todo{commit}} repository of the Chair of Programming Languages.
+The toolchain was developed in the programming language OCaml \cite{ocaml_docs} --- the code is available in a GitHub\footnote{\url{https://github.com/proglang/thesis-distributed-assertion-checking}\todo{commit}} repository of the Chair of Programming Languages.
 
@@
 For the target-specific processing, the intermediate result of the frontend is passed to the respective backends via a public interface.
+
+\begin{figure}[h]
+\includegraphics[width=\linewidth]{figures/3-offline/pipeline_frontend}
+\caption{The stages of the generic frontend of the compilation pipeline}
+\label{fig:pipeline_frontend}
+\end{figure}
 
@@
 %Lastly, \secref{sec:accuracy} analyses the reliability of distributed assertion checking as proposed and to what extent it affects the costs.
-
-% provide a high level language specifying complex computations that way  is  hard  and  inconvenient
-% 1) propose a model/approach to make use of off-chain computations that can be verified with explicit assertions
-% 2) contribute a toolchain that consists of a domain-specific language and a compilation pipeline that generates assertion smart contracts for the target blockchain Tezos.
-efforts were made to keep this as generic as possible, s.t.
-it can be extended for other target platforms as well
-% extend smart contracts and the VM with opcodes
 
@@
 
+The grammar currently includes common arithmetic (e.g., \texttt{add}, \texttt{sub}, \texttt{abs}, \texttt{mod}), relational  (e.g., \texttt{eq}, \texttt{neq}, \texttt{lt}) and logic and bitwise operators (e.g., \texttt{and}, \texttt{or}, \texttt{lsr}, \texttt{lsl}).
+Some operations that operate on data structures (e.g., \texttt{nth} and \texttt{size}) are supported as well.
+Domain specific operations have not been included yet, but they may be added to the language if necessary.
+
 \subsection{Example}
+The example given in \lstref{lst:sorted_assertion} implements an assertion, which checks whether a list is sorted in ascending order based on a variation of the formula stated in \eqref{eq:sorted} in the introduction:
+\begin{equation}\label{eq:sorted_v2}
+	(\forall n,m : int) (0 \leq n < m < |a|) \Rightarrow a[n] \leq a[m]
+\end{equation}
+In contrast to the previous variation, which translates to an assertion that compares a random element of the list with its direct neighbour, this translates to a comparison of two random elements (under the constraint $n < m$).
+\lstref{lst:sorted_assertion} shows how this formula can be expressed in the assertion language.
 \lstinputlisting[caption=Assertion contract for checking if a list is sorted, language=Assertion, label={lst:sorted_assertion}]{listings/sorted.tza}
 
-As an example, consider a variation of the formula given in \eqref{eq:sorted} that checks whether a given list is sorted in ascending order:
-\begin{equation}\label{eq:sorted_v2}
-	(\forall n : int)(\forall m : int) (0 \leq n < m < |a|) \Rightarrow a[n] \leq a[m]
-\end{equation}
-The respective assertion that checks this property for the parent contract, given in \lstref{lst:sorted}, is expressed in \lstref{lst:sorted_assertion}.
+In line 1, the signature of the assertion is declared with tag \textit{find} and a parameter \texttt{a} of type integer list.
+The body is a nesting of two universal quantifiers which declare the predicate variables $n$ and $m$ of type integer (lines 2 and 3), followed by a nesting of conditions to define the domains of the quantifiers (lines 4-6), corresponding to the premise of the formula.
+The body of the last condition (line 7) ultimately contains the keyword \texttt{assert} followed by the specification of the property to be checked, i.e.,  $a[n] \leq a[m]$.
 
@@
 
-\section{Frontend of the pipeline}\label{sec:pipeline_front}
-The frontend of the compilation pipeline comprises of a command-line interface (CLI), a parser and the transformation.
-These stages are generic and independent of the target platform, and produce an abstract syntax tree (AST) of the assertion.
-This AST	is then passed to the respective back-end through a public interface.
-\begin{figure}[h]
-\includegraphics[width=\linewidth]{figures/3-offline/pipeline_frontend}
-\caption{The stages of the generic frontend of the compilation pipeline}
-\label{fig:pipeline_frontend}
-\end{figure}
-OCaml was chosen as a programming language to implement the pipeline, given that it's also used to develop the Tezos blockchain.
-This avoids context switches within the Tezos eco-system and allows to build on top of the Tezos libraries (cf.
-\secref{sec:tezos}).
+\section{Parser}
+Assertions expressed in the syntax described above are passed as a simple text file to the pipeline.
+It is not admissible to generate empty assertions for all entrypoints of the parent contract, hence empty files are rejected.
+Furthermore, the parser guarantees total success or total failure of parsing the assertion by aborting execution immediately after encountering a syntax error.
 
-\subsection{Parser}
-Assertions expressed in the syntax described above are passed as a simple text file to the pipeline.
-The file extension is irrelevant, but this thesis follows the convention of using the file extension \texttt{.tza} for assertion contracts (referring to the extension \texttt{.tz} for Michelson contracts).
-The file must contain at least one assertion, hence it is not admissible to create empty assertions for all functions (or entrypoints) of the parent contract.
-Furthermore, every syntax error will cause the pipeline to abort execution in order to ensure that no assertion is missing in the target code.
-Each of the contained assertions is, after parsing, represented as a separate abstract syntax tree (AST).
-The AST represents, like the syntax itself, a union of all target specific ASTs that contain the supported subsets of operations and types.
-\\
-Both lexer and parser have been generated using the OCaml tools \texttt{ocamllex} \cite{ocaml_docs} and \texttt{menhir} \cite{menhir_doc}.
+After successfully parsing all assertions, the parser returns a list of ASTs.
+On the toplevel, the AST type given in \lstref{lst:ast_type} is composed of an entrypoint specification and an assertion body.
+The parameter pattern and assertion body, in turn, are  subtrees representing their composition or the content of the assertion respectively.
+\begin{lstlisting}[label=lst:ast_type, language=, numbers=none, caption=Toplevel AST type definition in OCaml]
+type ast =
+  {entrypoint : string option * pattern; body : assertion}
+\end{lstlisting}
 
-\subsection{Transformation}\label{sec:transformation}
-Since the validators will check the input parameter for the negation of the formula, it has to be transformed before compilation.
-Furthermore, the formula should explicitly state the domain for each quantifier, which will have to be translated into a set of bounds that refer to the respective random generator.
-Restricting the ranges of the random generators is important in order to avoid wasting resources through testing values out of the relevant (or legal) scope.
+\begin{wrapfigure}{r}{0.45\textwidth}
+\vspace{-30pt}
+ \begin{center}
+  \includegraphics[width=0.4\textwidth]{figures/3-offline/ast_example_find}
+  \end{center}
+  \caption{Abstract syntax tree of the assertion given in \lstref{lst:sorted_assertion}}
+  \label{fig:ast_example}
+  \vspace{-30pt}
+\end{wrapfigure}
+
+\figref{fig:ast_example} shows the resulting AST after parsing the assertion given in \lstref{lst:sorted_assertion}.
+The subtype representing quantifiers contains a special field \textit{Bounds}, which is initially left empty by the parser.
+During the transformation, it is populated with a set of constraints concerning its predicate variable, cf.
+\secref{sec:transformation}.
+
+\section{Transformation}\label{sec:transformation}
+The assertion, as specified by a developer, is modified in two ways before the compiler translates it into target code: firstly, it has to be transformed into its negation.
+Secondly, quantifiers are converted to random generators, which generate values within a specified range (corresponding to the domains of discourse).
+In the assertion language, the ranges can be expressed using \texttt{if}-conditions.
+As a preliminary for the compilation, the transformation additionally analyses the condition nodes of the AST, identifies conditions that state a range constraint for a generator and assigns it to the respective quantification node (by adding it to the \textit{Bounds} field).
+Therefore, the transformation contains two consecutive steps:
+\begin{enumerate}
+\itemsep-0.5em
+\item Negation
+\item Domain constraint analysis and assignment
+\end{enumerate}
+Each step is described in more detail in the following subsections.
 
 \subsubsection{Negation}
-The formula is negated using the negation rules of second-order logic and applying De Morgan's laws \cite{de_morgan} until the negation is applied to the literals.
+The formula is negated according to the negation rules of second-order predicate logic and by applying De Morgan's laws \cite{de_morgan} until the negation is applied to the literals.
 Negating universal quantification is equivalent to an existential quantification of its negated body (and vice versa): $\neg \forall x P(x) \equiv \exists x \neg P(x)$ \cite{Sundstrom2020Quantifiers}.
@@
 
+Applied to an AST representation of the assertion, the negation recursively traverses the \texttt{assertion} subtree, replaces quantifier and expression nodes with the corresponding negations and skips condition nodes.
+The output is thus a modified AST.
+
+Pursuing the example of the assertion for sorted lists, the negated version of the AST given in \figref{fig:ast_example} is shown in \figref{fig:ast_example_neg}.
+% point out negated expressions
+\begin{figure}
+\subfloat[Negated AST\label{fig:ast_example_neg}]{%
+  \includegraphics[width=0.45\textwidth]{figures/3-offline/ast_example_neg}
+}
+\hfill
+\subfloat[Fully transformed AST\label{fig:ast_example_transf}]{%
+  \includegraphics[width=0.4\textwidth]{figures/3-offline/ast_example_transf}
+}
+\caption{Transformation (intermediate) results of the sorted list assertion AST}
+\end{figure}
+
 \subsubsection{Building smart random generators}
+% Restricting the ranges of the random generators is important in order to avoid wasting resources through testing values out of the relevant (or legal) scope.
+%At this point, you can read off the invocation for the random generator.
+If any constraints remain, they’d have to be checked at run time.
+In the best case, things work out like in the example.
+Otherwise, each if-constaint that turns out to be false results in a useless test run.
 In order to assign each explicit bound to its appropriate quantifier, the formula has be skimmed for atomic constraints that contain predicate (bound) variables.
@@
 Hence, the actual executed number of checks is always a multiple of $m$.
-\secref{} goes into a bit more detail about this based on the Tezos blockchain.
+\secref{} goes into more detail about this based on the Tezos blockchain.
 \todo{Refer to section}

### 2021-04-20 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Chapter 3 - transformation

@@
-\externaldocument{1-introduction}
-
 \chapter{Toolchain Implementation - Frontend}\label{chap:offline}
@@
 
-\begin{wrapfigure}{r}{0.45\textwidth}
-\vspace{-30pt}
- \begin{center}
-  \includegraphics[width=0.4\textwidth]{figures/3-offline/ast_example_find}
-  \end{center}
-  \caption{Abstract syntax tree of the assertion given in \lstref{lst:sorted_assertion}}
-  \label{fig:ast_example}
-  \vspace{-30pt}
-\end{wrapfigure}
-
 \figref{fig:ast_example} shows the resulting AST after parsing the assertion given in \lstref{lst:sorted_assertion}.
@@
 
-\subsubsection{Negation}
+\subsection{Negation}
 The formula is negated according to the negation rules of second-order predicate logic and by applying De Morgan's laws \cite{de_morgan} until the negation is applied to the literals.
@@
 The output is thus a modified AST.
+Further pursuing the example of the assertion for sorted lists, the negated version of the AST given in \figref{fig:ast_example} is shown in \figref{fig:ast_example_neg}.
+The universal quantifiers have been transformed to existential quantifiers, and the asserted condition from $a[n] <= a[m]$ to $a[n] > a[m]$.
 
-Pursuing the example of the assertion for sorted lists, the negated version of the AST given in \figref{fig:ast_example} is shown in \figref{fig:ast_example_neg}.
-% point out negated expressions
-\begin{figure}
+\begin{figure}[t]
+\hfill
+\subfloat[AST after parsing\label{fig:ast_example}]{%
+  \includegraphics[width=0.33\textwidth]{figures/3-offline/ast_example_find}
+}
 \subfloat[Negated AST\label{fig:ast_example_neg}]{%
-  \includegraphics[width=0.45\textwidth]{figures/3-offline/ast_example_neg}
+  \includegraphics[width=0.33\textwidth]{figures/3-offline/ast_example_neg}
 }
@@
 \subfloat[Fully transformed AST\label{fig:ast_example_transf}]{%
-  \includegraphics[width=0.4\textwidth]{figures/3-offline/ast_example_transf}
+  \includegraphics[width=0.3\textwidth]{figures/3-offline/ast_example_transf}
 }
-\caption{Transformation (intermediate) results of the sorted list assertion AST}
+\caption{Modifications to the sorted list assertion AST from parsing to completed transformation}
 \end{figure}
 
-\subsubsection{Building smart random generators}
-% Restricting the ranges of the random generators is important in order to avoid wasting resources through testing values out of the relevant (or legal) scope.
-%At this point, you can read off the invocation for the random generator.
-If any constraints remain, they’d have to be checked at run time.
-In the best case, things work out like in the example.
-Otherwise, each if-constaint that turns out to be false results in a useless test run.
-In order to assign each explicit bound to its appropriate quantifier, the formula has be skimmed for atomic constraints that contain predicate (bound) variables.
-They're then moved and assigned to the quantifier that bounds the variable.
-If the constraint contains more than one bound variable, it is assigned to the quantifier with the highest depth in the order of quantifiers, as they depend on the generated value(s) of the other variable(s).
+\subsection{Domain assignment}
+In order to obtain random generators which only generate values in the interesting range, i.e., within the domains of discourse, the second step of the transformation skims the condition nodes of the AST for atomic constraints that contain bound variables.
+These conditions are then moved to the \texttt{Bounds} field of the respective quantifier.
+If the constraint contains more than one bound variable, it is assigned to the quantifier with the highest depth in the quantifier nesting, as they depend on the generated values of the previous generators.
 \\
-Revisiting the formula from \eqref{eq:sorted_v2}, its premise can be considered as a conjunction of the four constraints
-\begin{itemize}
+Relating to the example of sorted lists, the premise in \eqref{eq:sorted_v2} can be considered as a conjunction of the four constraints
+\begin{enumerate}
 \itemsep-1em
@@
 \item $m < |a|$.
-\end{itemize}
-Applying the rules given above after negating the formula, the constraints are assigned to the quantifiers as follows:
-\begin{equation}\label{eq:sorted_v2_bounds}
-	(\exists n : int, 0 \leq n \wedge n < |a|])(\exists m : int, m > n \wedge m < |a|) \text{ } a[n] > a[m]
-\end{equation}
-Ultimately, the quantifiers are then translated to the corresponding random generators, drafted in pseudocode:
-\begin{lstlisting}[label=lst:rand, numbers=none]
-n = random(0, size(list))
-m = random(n, size(list))
+\end{enumerate}
+Constraint 1,2 and 4 only contain one bound variable ($n$ or $m$), thus they are assigned to the respective quantifier binding it.
+Constraint 3, on the other hand, features two bound variables -- this constraint is assigned to the quantifier last in the nesting, thus the quantifier binding $m$.
+The corresponding AST expressing this assignment is shown in \figref{fig:ast_example_transf}.
+
+During compilation, the quantifiers, and their list of bounds, are then translated to target code that corresponds to the following pseudocode (\lstref{lst:rand}):
+\begin{lstlisting}[label=lst:rand, caption=Random generators for sorted list assertion, numbers=none]
+n = random(0, size(a))
+m = random(n + 1, size(a))
 \end{lstlisting}
-While conjunctions can be handled easily, other operators make it more difficult to derive efficient random generators. Consider the following constraints:
-\begin{itemize}
+
+However, if constraints contain certain operators, deriving efficient random generators is less straight-forward. Consider the following constraints:
+\begin{enumerate}
 \itemsep-0.7em
-\item[1)] $(\forall n : int) (n < 10 \lor n > 20) ...$
-\item[2)] $(\forall n : int) (n \ne 10) ...$
-\item[3)] $(\forall n : int) (n = 10) ...$
-\end{itemize}
-Constraint 1) complicates restricting the random generator in several ways.
-Firstly, it separates the domain into two disjoint sub-domains, which requires defining a random generator for each range and another one to decide which one is called.
-Secondly, the operands of a disjunction cannot be considered separately when more than one bound variable is involved.
+\item $(\forall n : int) (n < 10 \lor n > 20) ...$
+\item $(\forall n : int) (n \ne 10) ...$
+\item $(\forall n : int) (n = 10) ...$
+\end{enumerate}
+Constraint 1 can complicate restricting the range of the random generator in two ways.
+Firstly, it separates the range into two disjoint sub-ranges, which translates to a random generator as shown in \lstref{lst:rand_disjoint}.
+\begin{lstlisting}[label=lst:rand_disjoint, caption=Random generator with two disjoint ranges, numbers=none]
+n = if random(0,2) == 0 then random(-MAX_INT, 10)
+                        else random(21, MAX_INT)
+\end{lstlisting}
+Secondly, the operands of a disjunction cannot be considered separately if they involve several bound variables.
 For the predicate variable whose random generator is executed first, the domain restriction is optional, while the generation of the following random values depend on the previous result.
-Similarly to 1), constraint 2) splits the domain into sub-domains.
-To keep it simple for the time being, restrictions formulated with these operators are kept as part of the assertion code rather than used as constraints for the generators.
-Consequently, some validators may generate irrelevant values when checking the assertion and, depending on the size of the gap between the sub-domains, this can significantly decrease the reliability of this kind of assertion checking.
-Thus, further developed iterations should handle and translate them accordingly.\\
-Constraint 3) effectively makes the quantifier, which binds $n$, obsolete.
-Adding this constraint to the respective generator will at least not affect the reliability, but a future improvement could be to optimize the assertion by replacing all occurrences of the bound variable with the assigned value and removing the quantification.
+\lstref{lst:rand_disjoint_nm} shows the corresponding random generators for a variation of constraint 1 featuring two bound variables, i.e., $(\forall n,m) (n < 10 \lor m > 20)...$.
+\begin{lstlisting}[label=lst:rand_disjoint_nm, caption=Random generators with two disjoint ranges and two bound variables, numbers=none]
+n = if random(0,2) == 0 then random(-MAX_INT, 10)
+                        else random(-MAX_INT, MAX_INT)
+m = if n < 10 then random(-MAX_INT, MAX_INT)
+              else random(20, MAX_INT)
+\end{lstlisting}
+Similarly to 1, constraint 2 splits the domain into sub-domains. Constraint 3 effectively makes the quantifier binding $n$ obsolete and thus can be translated to a variable with a constant value.
+
+In the current implementation of the transformation, constraints featuring the logical or, exclusive or or inequality operator are kept as part of the assertion body.
+They are considered to be exceptional cases, but will increase the overall complexity of the compilation beyond the scope of a first iteration.
+In the case that constraints remain part of the assertion body, they are checked during runtime.
+As a consequence, an invocation of the assertion contract can result in a futile assertion check if such a condition is not met.
 
 \subsubsection{Implicit constraints}
-In some cases, boundaries are imposed implicitly by data types.
+In some cases, boundaries are imposed to the random generators implicitly through the used data types.
 List indices, for instance, are always bound to the range $0..
 size(list) - 1$ and could thus be derived from the formula without an explicit specification.
-As this deduction makes the transformation more complex, requiring a semantic analysis of the formula, a completely explicit formula in terms of the domain is required for now.
-Depending on the VM, the lower bound for indexing operations can be implicitly handled by the random generator of an appropriate predicate type.
+As this requires a semantic analysis of the AST and thus a more complex transformation, the current implementation requires a completely explicit formula in terms of the domains.
+
+Depending on the blockchain VM, the lower bound for generated values used in indexing operations can be implicitly handled by the random generator of an appropriate predicate variable type.
 As an example, Michelson supports the data type \texttt{nat} representing the natural numbers, which categorically excludes all values below zero.
-Developers aware of this can exploit this and, for instance, abbreviate \eqref{eq:sorted_v2} with the following formula:
+\eqref{eq:sorted_v2} can thus be abbreviated with the formula given in \eqref{eq:sorted_v2_abbr}.
 \begin{equation}\label{eq:sorted_v2_abbr}

### 2021-04-21 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
Own chapt probabilistic model

@@
 Blockchain-based applications are built with smart contracts, programs written in Turing-complete languages.
-Running a smart contract, though, generates costs proportional to the amount and complexity of computations, as well as its storage usage \cite{alharby_blockchain_2017}.
+Running a smart contract generates costs proportional to the amount and complexity of computations, as well as its storage usage \cite{alharby_blockchain_2017}.
 These fees, often measured in a unit called ``gas'', have to be paid for by the user in order to compensate the miners for their efforts \cite{narayanan_bitcoin}.
-This creates a powerful incentive to keep smart contracts simple and efficient, while in reality, meaningful applications still might need to perform some resource intensive computations.
-Not only can such applications generate unsustainable costs when executed on the blockchain, but may also reach gas limits imposed by the blockchain's protocol.
+This creates a powerful incentive to keep smart contracts simple and efficient.
+In reality, however, meaningful applications still might need to perform resource intensive computations or store larger amounts of data.
+Not only can such applications generate unsustainable costs when executed on the blockchain, but they may also reach gas limits imposed by the blockchain's protocol.
 \\
@@
 By trusting that the submitted results are correct, this approach raises both safety and security issues.
-Invalid results can be submitted unintentionally as a result of a wrong computation, or a third party may pass them intentionally to cause harm or take advantage.
-Consequently, submitted parameters should be checked for assumed properties before the smart contract is executed.
+Invalid results can be submitted unintentionally as a result of a wrong computation, or a third party may pass them intentionally to cause harm or capitalize on it.
+Consequently, submitted parameters should be validated before the smart contract is executed.
 Although in many cases, verifying a solution takes less time than computing the result itself (cf.
@@
 The function takes an input value \texttt{p} of type integer and should make use of the assumption that \texttt{p} is a prime number.
-\begin{lstlisting}[caption=Smart contract with a function that expects a prime number \cite{thiemann_2020}, numbers=none, language=Solidity, label=lst:prime]
+\begin{lstlisting}[caption=Smart contract with a function expecting a prime number \cite{thiemann_2020}, numbers=none, language=Solidity, label=lst:prime]
 contract Example {
@@
 \end{lstlisting}
-This assumption ``$p$ is a prime number'' can be expressed with the following explicit assertion in predicate logic: 
+The assumption ``$p$ is a prime number'' can be expressed with the following explicit assertion in predicate logic: 
 \begin{equation}\label{eq:prime}
@@
 Each validator then checks the inverse property $(p \% n) = 0$ point-wise for some random $n$ within the given boundaries $2 \le n \le \sqrt{p}$.
-If a validator finds a counterexample, i.e., a value for $n$ where the reminder is $0$, it posts an objection to the network.
+If a validator finds a counterexample, i.e., a value for $n$ where the reminder is $0$, it posts a veto to the network.
 For each involved validator, the constant cost of generating one random number and calculating one division have to be paid, which is independent from $p$.
@@
 Even though the assertion can be checked in a loop in $\mathcal{O}(1)$, the constant factor is not negligible.
-Hence, the same approach can be applied here by considering the negation and have the validators search for counterexamples, checking random values for $n$:
+Again, by considering the negation, the validators can be engaged to search for counterexamples by checking random values for $n$:
 
@@
 Tuning these parameters is a trade-off between making the filter more reliable, i.e., lowering its error rate, and space efficiency \cite{blustein_bloom_2002}.
-The same applies, with some reservations, to distributed assertion checking: less samples keep the gas consumption to a minimum, whereas more samples increase the probability that an existing counterexample is found.
+The same applies, with some reservations, to distributed assertion checking: fewer samples keep the gas consumption (and thus cost) to a minimum, whereas more samples reduce the probability of accepting an invalid result.
 Referring to the example of sorted lists, the probability of false positives depends on the size of the list $a$ and the number of validators $m$.
@@
 In this model, results of such computations are validated on-chain by the validators of the network.
-In order to do so, they invoke assertion smart contracts which point-wise check whether the result satisfies certain properties.
+In order to do so, they invoke assertion smart contracts, which point-wise check the validity of certain properties.
 When claiming an assertion failure, a validator publishes a counterexample to be scrutinized by the other validators.
@@
 The off-chain component is a toolchain to specify, integrate and generate assertion contracts that can be deployed to the blockchain.
-This includes the definition of a domain-specific language which allows developers to specify assertions for each entrypoint of a Smart Contract.
+This includes the definition of a domain-specific language, which allows developers to specify assertions for each entrypoint of a Smart Contract.
 The on-chain component, on the other hand, consists of an amendment of the blockchain protocol.
-This amendment includes an extension of the Smart Contract language with opcodes to generate random values in a non-deterministic way, a transaction type that can trigger the distributed execution of assertions, and the implementation of a consensus mechanism for counterexamples.
+This amendment includes an extension of the Smart Contract language with instructions generating random values in a non-deterministic way, a transaction type that can trigger the distributed execution of assertions, and the implementation of a consensus mechanism for counterexamples.
 
@@
 \section{Related work}
-Outsourcing computations or storage to off-chain resources in order to improve the scalability of blockchains has been the topic of several research papers and projects, which provide diverse solutions for different applications and use-cases.
+Outsourcing computations or storage to off-chain resources, in order to improve the scalability of blockchains, has been the topic of several research papers and projects.
+They provide diverse solutions for different applications and use-cases.
 Eberhardt and Tai \cite{eberhardt_offonchain} give insights gained from a set of blockchain projects focusing on off-chaining.
@@
 The ``Delegated Computation Pattern'' outsources computations, which are too complex for on-chain execution, to an untrusted third party and only verifies the proof of correct execution on-chain.
-The proposed approach of a distributed assertion checking scheme can therefore be considered as an implementation of this pattern.
+The proposed approach of a distributed assertion checking scheme can therefore be considered as a possible implementation of this pattern.
 
-ZoKrates \cite{eberhardt_zokrates_2018} proposes a processing model for the same pattern which employs non-interactive zero-knowledge proofs (zkSNARKs).
+ZoKrates \cite{eberhardt_zokrates_2018} proposes a processing model for the same pattern, which employs non-interactive zero-knowledge proofs (zkSNARKs) to verify the results on-chain.
 When such proofs are supplied together with the results, the correctness can be validated fast and cheaply by the miners and nodes of the network.
@@
 \section{Structure overview}
-The structure of this thesis is as follows: in the first instance, \chapref{chap:use_cases} defines a set of logical formulas suitable for distributed assertion checking.
-Given this set, it demonstrates various practical use-cases for such properties and formalizes the costs of checking them locally, s.t.
-they can later be referenced to assess the efficiency of the distributed approach.
-\chapref{chap:offline} describes the generic aspects of the off-chain design and infrastructure, i.a.
-the definition of a syntax to express assertions on top of the logical formulas and how they are transformed to code that checks for counterexamples.
-Additionally, it analyses the effectiveness of the statistical validation for a given input and provides a formula to compute the lower bound of validators necessary to obtain a reliable result.
-Subsequently, \chapref{chap:offline_tezos} gives a brief introduction to Tezos, before it covers target specific aspects of the off-chain design.
-Besides identifying necessary extensions to Michelson's instruction set and virtual machine, it explores various orchestration strategies between assertion and contract code.
-The chapter closes with a cost analysis of distributed assertion checking on Tezos with the chosen orchestration strategy.
-In conclusion, the last chapter recaps the achieved results,
-addresses open questions or issues and provides an outlook on upcoming work on this topic.
+The structure of this thesis is as follows: in the first instance, \chapref{chap:use_cases} defines a set of logical formulas suitable for the proposed scheme of distributed assertion checking.
+Given this set, it demonstrates various practical use-cases  and formalizes the costs of checking them locally, s.t.
+they can later be used as a benchmark to assess the efficiency of the distributed approach.
+\chapref{chap:offline} describes the frontend of the toolchain and generic aspects of the off-chain design.
+As a premise for the toolchain backend, \chapref{chap:prob_model} defines the probabilistic model of the scheme and analyses the effectiveness of the probabilistic validation.
+After providing a brief introduction to the Tezos blockchain and its Smart Contract language Michelson, \chapref{chap:offline_tezos} covers target specific aspects of the off-chain design and the implementation of the toolchain backend.
+The chapter closes with an evaluation of the proposed scheme based with regard to Tezos as the target platform.
+In conclusion, the last chapter recaps the achieved results, addresses open questions or issues and provides an outlook on upcoming work on this topic.

### 2021-04-21 assertions/doc/thesis-bernhardt/chapters/2-use_case_analysis.tex
Own chapt probabilistic model

@@
 \chapter{Use-case analysis}\label{chap:use_cases}
-The introduction argued that validating properties on input parameters becomes expensive when a data structure (such as arrays), certain data types (such as byte sequences) or a range of values have to be iterated.
+The introduction argued, that validating properties on input parameters can become costly when data structures (such as arrays), certain data types (such as byte sequences) or a range of values have to be iterated.
 It showed examples for such properties and identified logical formulas containing universal quantification as amenable for distributed assertion checking.
-Through its domain of discourse, the quantification spans an iteration space whose elements can be checked independently by each validator.
+Through its domain of discourse, the quantification spans an iteration space whose elements can be checked independently by the validators.
 As a matter of fact, the same is also valid for existential quantification, even though its negation has a different notion than that of its universal counterpart.
 The difference between the two is addressed later in this chapter.
-\\
-The following section formally defines a set of applicable logical formulas for the basic implementation of this approach.
+
+The following section formally defines a set of applicable logical formulas for the basic implementation of the distributed assertion checking scheme.
 Given this set, section \secref{sec:examples} gives some more in-depth examples of such formulas.
@@
 \section{Definition of a set of logical formulas}\label{sec:formulae}
-The set of formulas that well-formed assertions can express is given in \figref{fig:formulas}.
+The set of formulas, which can be expressed in well-formed assertions, is given in \figref{fig:formulas}.
 This corresponds, with some restrictions, to the language of second-order predicate logic.
-Besides universal and existential quantifiers with exactly one bound variable, the set definition contains logical connectives, relational symbols, constant values of a numerical, string or boolean type, variables and the basic functional symbols for basic arithmetic operations.
+Besides universal and existential quantifiers (with exactly one bound variable), the definition contains logical connectives, relational symbols, constant values of a numerical, string or boolean type, variables and the functional symbols for basic arithmetic operations.
 This set of symbols is rather generic and should be valid for any target blockchain.
 Specific to the target blockchain are the sets of types $t$ and functional symbols $f$.
-These can only contain types and operations that can be translated to operation codes (opcodes) of the respective Smart Contract language and executed within the blockchain's virtual machine (VM).
+These can only contain types and operations, which can be translated to instructions of the respective Smart Contract language and interpreted by the blockchain's virtual machine (VM).
 As an example, the primitive types in Michelson are \texttt{string}, \texttt{nat}, \texttt{int}, \texttt{bytes}, whereas Ethereum's Smart Contract language Solidity  \cite{solidity_docs} additionally supports an \texttt{enum} type and fixed-point numbers.
-
 \begin{align*}
@@
 A more specific $gcd$-problem is finding two numbers which are coprime, meaning their greatest common divisor is one, i.e., $gcd(a, b) = 1$.
-In order to verify that two numbers are coprime, it has to be checked that there is no $gcd > 1$, hence the property of coprimeness can be expressed with the following formula in predicate logic:
+In order to verify that two numbers are coprime, it has to be verified that there is no $gcd > 1$, hence the property of coprimeness can be expressed with the following formula in predicate logic:
 \begin{equation}\label{eq:coprime-universial}
@@
 \end{equation}
-Assuming constant time for calculating the two remainders, checking whether two numbers satisfy this property takes linear time, i.e. $\mathcal{O}(n)$, and depends on the size of the smaller number.
+Assuming it takes constant time to calculate the two remainders, checking whether two numbers satisfy this property takes linear time, i.e.
+$\mathcal{O}(n)$, and depends on the size of the smaller number.
 
@@
 \subsection{Existential quantification - intersection of sets}\label{sec:existential}
-So far, this thesis only considered formulas featuring universal quantification, for which the assertion scheme challenged the validators to find counterexamples.
+So far, this thesis only considered formulas featuring universal quantification, for which the assertion scheme engaged the validators to find counterexamples.
 However, distributed assertion checking can not only be used to refute assumptions, but also to prove their validity.
@@
 In that case, the validator finding such a proof should publish an approval instead of a veto to the network.
-After an approval has been posted, and all validators have come to a consensus about the validity of the assumption, the transaction may be included in a block (assuming it doesn't fail due to other reasons).
+After an approval has been posted, and all validators have come to a consensus about the validity of the proof, the result is accepted.
 For the blockchain protocol, this implies that distributed refutation and validation have to be implemented as separate modi of assertion checking.
-\\
 
@@
 \subsection{Nested quantification - SAT problems}
-The previous example showed that universal and existential quantification have to be handled differently.
-However, further special cases caused by nested quantification have to be considered as well.
+The previous example demonstrated that universal and existential quantification have to be handled differently.
+However, further special cases, caused by nested quantification, have to be considered as well.
 A nesting of the same type of quantifier, e.g.
-$\forall i \forall j$ can be considered as trivial.
-They can be handled by generating a random value for each predicate variable and checking for a counterexample or proof respectively.
-It becomes less trivial though, if the nesting contains both universal and existential quantifiers.
+$\forall i \forall j$, can be considered as trivial.
+They are translated to code, which generates a random value for each predicate variable and checks for a counterexample or proof respectively.
+It becomes less trivial, if the nesting contains both universal and existential quantifiers.
 This section examines the cases of $\forall i \exists j$ and $\exists i \forall j$ on the basis of a contract that expects a solution for a boolean satisfiability problem (SAT).
-\\
 
@@
 A SAT problem can be represented as a list of clauses $c$ and a variable assignment $\mathcal{A}$.
-To avoid having to handle the variables and their literals as strings and thus optimize runtime and memory consumption, an encoding scheme taken from this blogpost \cite{sabablog} is used: \\
+To avoid having to handle the variables and their literals as strings, and thus optimize runtime and memory consumption, an encoding scheme \cite{sabablog} is used in the following.
+
 Variables are encoded by a unique number starting from $0$ to $n-1$, where $n$ is the total number of variables.
@@
 Since the encoding of variables corresponds to their index in the list of variables, $\mathcal{A}$ can be passed as a list of booleans that maintains the same order of variables: $\mathcal{A}_{enc} = [False, True, False]$.
-If the blockchains VM supports a respective data type, $\mathcal{A}$ can alternatively be represented with a more efficient bitarray.
+If the blockchain's VM supports a respective data type, $\mathcal{A}$ can alternatively be represented with a more efficient bitarray.
 Lastly, the variable encoding $x$ of a literal $y$ is obtained by dividing its encoding by two, which corresponds to a bit-wise shift to the right:
@@
 Quantifiers thus are translated to random generators during the generation of target code.
-However, by checking a random literal in a random clause, the validator cannot make a definite statement whether $\mathcal{A}$ satisfies $F$, since each clause has to be examined as a whole in order to verify that the conjunction evaluates to true.
+However, by checking a random literal in a random clause, the validator cannot make a definite statement about whether $\mathcal{A}$ satisfies $F$.
+Each clause has to be examined as a whole in order to verify, that the conjunction evaluates to true.
 Consequently, the distribution can only take place on the level of clauses, but not on the level of literals.
@@
 Whether the assertion requires a proof or a counterexample can be derived from the outer quantifier, hence validators produce a counterexample in this case.
-Due to the fact that the whole loop has to be run in order to identify a counterexample and the consequential code structure this translates to, the negation of the formula is not required but optional.
-\lstref{lst:cnf_test_code} shows the generated testing code of the CNF SAT problem with and without negating the formula first, where \texttt{check} evaluates the negated or non-negated condition respectively.
-While formulas with a single quantifier simply translate to generating a random value and checking the condition, this code is more extensive and requires a more sophisticated compiler that can differentiate between different quantification compositions.
+\lstref{lst:cnf_test_code} shows the generated testing code of the CNF SAT problem, where \texttt{check} evaluates the negated condition.
+While formulas with a single quantifier simply translate to generating a random value and checking the condition, this code is more extensive.
+It requires a more sophisticated compiler, which can differentiate between different quantification compositions.
 
-\vspace{\baselineskip}
-\noindent
-\begin{minipage}{.45\textwidth}
-\begin{lstlisting}[label=lst:cnf_code_neg, numbers=none]
+\begin{lstlisting}[label=lst:cnf_test_code, caption=Test code structure for single nested quantifiers, numbers=none]
 i = random(0, size(F))
@@
 \end{lstlisting}
-\end{minipage}\hfill
-\begin{minipage}{.45\textwidth}
-\begin{lstlisting}[label=lst:cnf_code, numbers=none]
-i = random(0, size(F))
-for (j : [0..k)):
-  if check( ... ):
-    // property holds
-    return true
-// counterexample found
-return false
-\end{lstlisting}
-\end{minipage}
-\captionof{lstlisting}{Test code structure for single nested quantifiers with negation (left) and without negation (right)\label{lst:cnf_test_code}}
-\vspace{\baselineskip}
 
@@
 \subsubsection{Satisfiability in predicate logic - DNF}\label{sec:dnf}
-The same propositional formula with the reversed quantification nesting $\exists i \forall j$ describes the assertion for the assumption $\mathcal{A}(F) = 1$, where $F$ is given in disjunctive normal form (DNF), i.e., a disjunction of conjunctions \cite{dnf_math_encycl}:
+The same propositional formula, with the reversed quantification nesting $\exists i \forall j$, describes the assertion for the assumption $\mathcal{A}(F) = 1$, where $F$ is given in disjunctive normal form (DNF), i.e., a disjunction of conjunctions \cite{dnf_math_encycl}:
 \begin{equation}\label{eq:dnf_sat}
@@
 \subsection{Further nesting}
-Nesting is, of course, not limited to two quantifiers only.
+Nesting is, of course, not limited to two quantifiers.
 Generally, formulas containing universal or existential quantification exclusively within the nesting benefit the most from distributed assertion checking, as each quantifier can be translated into a random generator.
-On the other hand, formulas with both types and a transition from one to the other early in the order benefit the least, because starting from the first transition, the subsequent quantifiers are translated to loops.\\
+On the other hand, formulas with both types and a transition from one to the other early in the order benefit the least; starting from the first transition, the subsequent quantifiers are translated to loops.
+
 To substantiate this argument, consider two variations of a contract that expect a list of boolean formulas in CNF, and an assignment $\mathcal{A}$.
-Variation one checks whether $\mathcal{A}$ satisfies at least one $F$, the other one checks if all $F$ are satisfied.
+Variation 1 checks, whether $\mathcal{A}$ satisfies at least one $F$.
+Variation 2 checks, if all $F$ are satisfied.
 This can be expressed by nesting quantifiers as follows:
-\begin{itemize}
+\begin{enumerate}
 \item $\forall f \forall i \exists j$
 \item $\exists f \forall i \exists j$
-\end{itemize}
-In the first case, each validator picks a random clause from a random $F$ and checks if at least one literal evaluates to true.
+\end{enumerate}
+In the first case, each validator picks a random clause from a random $F$, and checks if at least one literal evaluates to true.
 This translates to two random generators and a loop for the existential quantifier.
@@
 \section{Restriction of use-cases}\label{sec:restrict}\todo{Better title? -> conclusion?}
-\todo{meh}
 The examples given in this chapter have shown that, depending on the type and order of quantification, not all properties can be checked in the same way and need different modi of assertion checking.
-Additionally,  as well as a distinct translation to target code.
-This increases the complexity and requirements for an implementation of the off-chain infrastructure and protocol amendment; therefore, as a first iteration, this thesis focuses on providing a design and toolchain for assertions using universal quantification only.
+Additionally, they require a distinct translation to target code.
+This increases the complexity and requirements for an implementation of the toolchain and protocol amendment; therefore, as a first iteration, this thesis focuses on providing a design and toolchain for assertions using universal quantification only.
 
 \section{Cost analysis of a local approach}\label{sec:usecase_cost}
-For the purpose of having a benchmark for the evaluation of the distributed approach, this section analyses the cost of invoking a contract on the blockchain that locally checks a formula.
+For the purpose of having a benchmark for the evaluation of the distributed approach, this section analyses the cost of invoking a contract on the blockchain, which checks a formula locally.
 Given that the target blockchain is Tezos, the computational and storage-related costs of a transaction are represented in units of gas.
@@
 The gas model of Tezos is described in more detail in \secref{sec:tezos}.
-According to this model, the total gas consumption of a transaction $T(source,\, destination=C,\, arg, \, ...)$ calling a smart contract $C(storage, \, parameter\, type, \, code)$ is calculated by \eqref{eq:gas_transaction}, where $I$ is the set of internal operations:
+According to this model, the total gas consumption of a transaction $T(source,\, destination=C,\, arg, \, ...)$ invoking a smart contract $C(storage, \, parameter\, type, \, code)$ is calculated by \eqref{eq:gas_transaction}, where $I$ is the set of internal operations:
 \begin{align}\label{eq:gas_transaction}
@@
 \end{align}
-Assuming that the storage of the contract is never increased, the amount of gas returned by the cost functions independent of the argument, i.e., the parameter value, remains constant for each $T$.
-The cost functions for the deserialization, parsing and interpretation, however, are functions of $arg$ that grow monotonically with increasing sizes of $arg$ \cite{morley_gasmodel}\cite{tezos_repo}.
+Assuming the storage of the contract is never increased, the amount of gas returned by the cost functions independent of the argument, i.e., the parameter value, remains constant for each $T$.
+The cost functions for the deserialization, parsing and interpretation, however, are functions of $arg$ and grow monotonically with increasing sizes of $arg$ \cite{morley_gasmodel}\cite{tezos_repo}.
 

### 2021-04-21 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Own chapt probabilistic model

@@
 The resulting ASTs are then passed to the backend, which is introduced in the subsequent chapter for the Tezos blockchain.
-%Lastly, \secref{sec:accuracy} analyses the reliability of distributed assertion checking as proposed and to what extent it affects the costs.
 
@@
 \end{equation}
-
-\section{Accuracy of the approach}\label{sec:accuracy}
-\todo{Idea: own chapter "probabilistic model" oder so - OR: model description}
-Since the proposed approach implements a probabilistic test, the accuracy as well as the costs incurred by guaranteeing a specified certainty threshold, need to be examined closely.
-The goal is to identify a formula that, given the domain of a formula in predicate logic, returns an estimate of a lower bound of samples necessary to find an existing counterexample with a probability $p$.
-From this analysis, it can be derived how effective a formula can be checked on a blockchain with $m$ validators.
-Sections \ref{sec:coupon} and \ref{sec:prob_threshold} depict the findings from \cite{bernhardt_veigel_2020} and are based on the assumptions that the random generator picks elements independently from a uniform distribution and that there exists exactly one counterexample for the passed parameter.
-
-\subsection{Coupon Collector's Problem Analysis}\label{sec:coupon}
-When checking properties with probabilistic testing, the result is either definitely not satisfied, or probably satisfied.
-Thus, errors only occur as false positives.
-In order to find an existing counterexample with probability $p = 1$, every element in the given domain $\mathcal{D}$ has to be checked by at least one validator.
-Deterministically, this is reachable with exactly $|\mathcal{D}|$ test runs.
-This is, however, invalid for the probabilistic approach, as some validators may generate duplicate random values and leave some elements of $\mathcal{D}$ unchecked.
-\\
-In probability theory, this is known as the Coupon Collector's Problem \cite{croucher_collecting_2006}.
-Given $n = |\mathcal{D}|$, the probability that no duplicate elements are generated with $n$ picks is given by
-\begin{equation*}
-    p = \prod_{i=1}^{n} \frac{i}{n}
-\end{equation*}
-As an example, the probability that all validators generate a unique random value already drops to $0.036\%$ for $n = 10$.
-Let the random variable $T$ be the number of test runs executed until every element in the domain has been generated.
-In order to obtain an estimation of how many test runs are needed to find the counterexample for certain, the goal is to identify its expectation $E(T)$.
-To this end, the geometric probability distribution is applied \cite{croucher_collecting_2006}:\\
-Each element is generated with a probability of $1/n$. Thus, the probability to generate the $i$th unique element is given by 
-\begin{equation}
-    p_i = \frac{n-i+1}{n}
-\end{equation}
-\cite{croucher_collecting_2006}. The expected value of a random variable $X$ is given by $E(X) = \frac{1}{p}$\cite{croucher_collecting_2006}, thus the expected number of test runs for $n$ is 
-\begin{equation}
-E(T) = n \sum_{i=1}^{n} \frac{1}{i}
-\end{equation}
-\tabref{tab:prob_outcomes} shows the expected number of test runs $E(T)$ and its standard deviation $\sigma$ for different $n$.
-Furthermore, $E(T)$ and $\sigma$ are used to calculate a 95\% confidence interval for $T$ by applying the central limit theorem, which provides an upper and lower bound on the number of test runs \cite{croucher_collecting_2006}.
-Rounded values for both bounds are also shown in \tabref{tab:prob_outcomes}.
-\begin{table}[h]
-    \centering
-    \begin{tabular}{lllll}
-        \thead{$n$} & \thead{$E(T)$} & \thead{$\sigma$} & \thead{lower bound} & \thead{upper bound}\\ \hline
-        5 & 11.4 & 2.53 & 6 & 16\\
-        10 & 29.3 & 4.32 & 21 & 38\\
-        20 & 72.0 & 7.21 & 58 & 86\\
-        30 & 119.8 & 9.48 & 101 & 138 \\
-        50 & 225.0 & 13.23 & 199 & 251 
-    \end{tabular}
-    \caption{Expectation, standard deviation and upper and lower bound of needed test runs for some $n$ \cite{croucher_collecting_2006}}
-    \label{tab:prob_outcomes}
-\end{table}
-
-The results show that checking random values is a very inefficient approach if false positives are not admissible.
-Even if the lower bound of $T$ is chosen as the number of test runs, it exceeds the size of the domain by far and increases the time complexity to $\mathcal{O}(n*log(n))$ for large $n$ \cite{xu_tang_2011}.
-For instances where false positives are tolerable, the following section introduces a formula to calculate the number of test runs that detect counterexamples with a given probability threshold $p \leq 1$.
-
-\subsection{Setting probability thresholds}\label{sec:prob_threshold}
-The goal is to find a number $t$ of test runs, s.t.
-the probability $P_{c,t}$ of not finding the counterexample drops below a certain threshold $c$.
-A validator finds the counterexample in one test run with probability $\frac{1}{n}$, and misses it with probability $(1-\frac{1}{n})$.
-After $t$ tests runs, the probability that the counterexample has not been found is thus $(1-\frac{1}{n})^t$.
-Following the same approach as in \cite{mahl_schindel_2007} to retrieve an upper bound for $P_{c,t}$, we use the following inequality
-\begin{equation}
-(1-\frac{1}{m})^m \leq \frac{1}{e}
-\end{equation}
-which holds for all $m > 0$. From this inequality, it follows that
-\begin{equation}
-(1-\frac{1}{n})^t = ((1-\frac{1}{n})^n)^{\frac{t}{n}} \le e^{-\frac{t}{n}}
-\end{equation}
-With this, the probability $P_{c,t}$ of not finding the counterexample with $t$ test runs can be defined as
-\begin{equation}
-P_{c,t} \le e^{-\frac{t}{n}}
-\end{equation}
-In order to retrieve the number of test runs $t$ necessary for $P_{c,t}$ to drop below a specified threshold $c$, the inequality is solved for $t$, which is then dependent of the known parameter $n$ and an arbitrary value for $c$:
-\begin{align}
-    e^{-\frac{t}{n}} &\leq c && \text{with } 0 \leq c\le 1 \nonumber\\
-    t &\geq -n\:\ln(c)
-\end{align}
-For $c = \frac{1}{e}$ ($\approx 36.79\:\%$) the lower bound of $t$ is exactly $n$, which means that for higher reliabilities the number of test runs needs to be greater than $n$.
-\figref{fig:graph_t_c} shows the lower bounds of $t$ as a function of the probability threshold and domain size.
-One can see that the increase in accuracy is approximately linear to the number of test runs below a threshold of $c=0.5$, but requires an exponential testing effort to reach higher thresholds.
-\begin{figure}[h]
-\includegraphics[width=0.95\linewidth]{figures/3-offline/graph_t_c}
-\caption{The number of required test runs as a function of the probability of false positives $c$ and size of the domain $n$}
-\label{fig:graph_t_c}
-\end{figure}
-For assertions with several quantifiers, which are translated to random generators, all domains have to be considered in the calculation.
-Revisiting the intersection of sets from \secref{sec:existential}, every element in set $U$ has to be compared to every element in set $V$.
-Thus, the lower bound of test runs needed to check whether they intersect with a certainty of 63.21\% is given by $t \leq t_1 * t_2$ with $t_1 \geq |U|$ and $t_2 \geq |V|$.
-
-\subsection{Validators vs. test runs}
-The last section derived a formula to calculate a lower bound for a number of test runs $t$ in order to reach a certain level of confidence.
-However, $t$ is not a parameter that can be adjusted to an arbitrary value on the blockchain, as the assertion is checked by the validators.
-Assuming a blockchain has $m$ validators, the actual lower bound of test runs is $m$.
-For cases where there are not enough validators to reach a threshold $c$, a mechanism is required to have each validator check the property for multiple random values.
-Hence, the actual executed number of checks is always a multiple of $m$.
-\secref{} goes into more detail about this based on the Tezos blockchain.
-\todo{Refer to section}
-
-\subsection{Alternatives to random testing}\label{sec:alt_random}
-For applications where higher reliability is crucial, an alternative to checking elements randomly could be to coordinate a systematic iteration of the domain.
-The implementation of such a coordination is not trivial though; validators can't simply be passed an individual value as input.
-Instead, possible approaches could be to implement a central instance that allocates an element in the search space to each validator, or use some unique and intrinsic attribute, like an identification number, as input for a mapping.
-The discussion if this approach would provide any advantages over a local validation of the property is left open \todo{Depends on cost analysis?}.
-
-\subsubsection{Central instance assigning values}
-For this approach, the tool-chain would need to generate a separate contract that is called by the miners and validators as a proxy.
-This contract would then, for instance, generate a number using a modulo-n counter and pass this number as an additional parameter to the assertion code.
-The random generators would be omitted accordingly.
-However, this works only as expected if there are no simultaneous transactions calling the contract, otherwise it cannot be guaranteed that all elements have been checked for each of the transactions.
-If and how this issue can be solved will not be discussed further in this thesis.
-\todo{Serializes tests -> see expose rejected ideas}
-
-\subsubsection{Using unique attributes of a validator}\label{sec:alt_attributes}
-This approach strongly depends on whether the validators have a unique id or other attribute that can be accessed from within a contract.
-If there is (or the language can be extended with such a feature), there needs to exist a non-injective surjective function that maps the respective attributes represented by type A to an element of the domain represented by type B, i.e.
-$f: X \rightarrow Y$.
-Furthermore, for cases where $t > m$, an offset needs to be added, s.t.
-a validator checks distinct elements for each test run.
-\\
-Implementing such an approach on Tezos becomes even more challenging due the way endorsing (i.e.
-validation) rights are distributed in its proof-of-stake mechanism: for each block level, endorsing rights are assigned to the owner of a randomly selected roll, i.e., a set of tokens \cite{tezos_docs}.
-This means that the same validator can be picked multiple times for endorsing one block and thus some elements in the domain may remain unchecked.
-\secref{} goes into more detail about this issue.
-\todo{Ref section}

### 2021-04-21 assertions/doc/thesis-bernhardt/chapters/4-probabilistic_model.tex
Own chapt probabilistic model

\chapter{Probabilistic model}\label{chap:prob_model}
Since the proposed approach implements a probabilistic validation, the reliability of the result depends on the number of validators in the network in relation to the size of the iteration space. Given that the number of validators is finite, the probability of finding existing counterexamples may drop below an acceptable threshold for higher domain sizes. Thus, the distributed assertion checking scheme should provide a mechanism to have each validator invoke the assertion contract a specified number of times. To this end, it is necessary to identify a formula which, given the domain size and a probability threshold, returns a lower bound for the required number of test runs per validator.

Sections \ref{sec:coupon} and \ref{sec:prob_threshold} describe the findings from a collaborative work with Julian Veigl \cite{bernhardt_veigel_2020}. They are based on the assumption that random generators pick elements independently from a uniform distribution. Furthermore, all calculations are based on the worst case scenario, in which there exists exactly one counterexample for the given input.

\section{Sample spaces}
The sample space of an assertion in form of a logical formula is given by the domains of discourse of the quantifiers. \secref described, that the premises defining the domains are translated into a list range constraints of the random generators. Based on these constraints, the compiler can derive a formula to determine the size of the sample space at runtime. In simple cases, the sample space is given by a single domain. Such a space is given, for instance, in the introductory example checking whether a number is a prime, i.e., $\mathcal{S} = \lbrace n \in\mathbb{Z} : 2 \le n \le \sqrt{p} \rbrace$. Based on the constraints $2 \le n$ and $n \le \sqrt{p}$, the size of the search space can be determined at runtime with $|\mathcal{S}| = \sqrt{p} - 2$. If the assertion has to sample from more than one domain, the search space is given by the Cartesian product of these domains, or sub-search spaces. In the example of intersecting sets from \secref{sec:existential}, the sample space is $\mathcal{S} = \mathcal{S}_U \times \mathcal{S}_V$, where $\mathcal{S}_U = \lbrace n \in\mathbb{Z} : 0 \leq n \le |U| \rbrace$ (analogue for $\mathcal{S}_V$). At runtime, the size of the search space can be determined with $|\mathcal{S}| = (|U| - 0) + (|V| - 0)$.

\section{Coupon Collector's Problem Analysis}\label{sec:coupon}
When checking properties with probabilistic testing, the result is either definitely not satisfied, or probably satisfied. Thus, errors only occur as false positives. In order to find a counterexample with probability $p = 1$, every element in the given search space $\mathcal{S}$ has to be checked by at least one validator. Deterministically, this is reachable with exactly $|\mathcal{S}|$ test runs. This is, however, invalid for the probabilistic approach, as some validators may generate duplicate random values and leave some elements of $\mathcal{S}$ unchecked. \\
In probability theory, this is known as the Coupon Collector's Problem \cite{croucher_collecting_2006}. Given $n = |\mathcal{S}|$, the probability that no duplicate elements are generated with $n$ picks is given by
\begin{equation*}
    p = \prod_{i=1}^{n} \frac{i}{n}
\end{equation*}
As an example, the probability that all validators generate a unique random value already drops to $0.036\%$ for $n = 10$. Let the random variable $T$ be the number of test runs executed until every element in the search space has been generated. In order to obtain an estimation of how many test runs are needed to find the counterexample for certain, the goal is to identify its expectation $E(T)$. To this end, the geometric probability distribution is applied \cite{croucher_collecting_2006}:\\
Each element is generated with a probability of $1/n$. Thus, the probability to generate the $i$th unique element is given by 
\begin{equation}
    p_i = \frac{n-i+1}{n}
\end{equation}
\cite{croucher_collecting_2006}. The expected value of a random variable $X$ is given by $E(X) = \frac{1}{p}$\cite{croucher_collecting_2006}, thus the expected number of test runs for $n$ is 
\begin{equation}
E(T) = n \sum_{i=1}^{n} \frac{1}{i}
\end{equation}
\tabref{tab:prob_outcomes} shows the expected number of test runs $E(T)$ and its standard deviation $\sigma$ for different $n$. Furthermore, $E(T)$ and $\sigma$ are used to calculate a 95\% confidence interval for $T$ by applying the central limit theorem, which provides an upper and lower bound on the number of test runs \cite{croucher_collecting_2006}. Rounded values for both bounds are also shown in \tabref{tab:prob_outcomes}.
\begin{table}[h]
    \centering
    \begin{tabular}{lllll}
        \thead{$n$} & \thead{$E(T)$} & \thead{$\sigma$} & \thead{lower bound} & \thead{upper bound}\\ \hline
        5 & 11.4 & 2.53 & 6 & 16\\
        10 & 29.3 & 4.32 & 21 & 38\\
        20 & 72.0 & 7.21 & 58 & 86\\
        30 & 119.8 & 9.48 & 101 & 138 \\
        50 & 225.0 & 13.23 & 199 & 251 
    \end{tabular}
    \caption{Expectation, standard deviation and upper and lower bound of needed test runs for some $n$ \cite{croucher_collecting_2006}}
    \label{tab:prob_outcomes}
\end{table}

The results show that checking random values is a very inefficient approach if false positives are not admissible. Even if the lower bound of $T$ is chosen as the number of test runs, it exceeds the size of the search space by far and increases the time complexity to $\mathcal{O}(n*log(n))$ for large $n$ \cite{xu_tang_2011}. For instances where false positives are tolerable, the following section introduces a formula to calculate the number of test runs that detect counterexamples with a given probability threshold $p \leq 1$.

\section{Setting probability thresholds}\label{sec:prob_threshold}
The goal is to find a number $t$ of test runs, s.t. the probability $P_{c,t}$ of not finding the counterexample drops below a certain threshold $c$. A validator finds the counterexample in one test run with probability $\frac{1}{n}$, and misses it with probability $(1-\frac{1}{n})$. After $t$ tests runs, the probability that the counterexample has not been found is thus $(1-\frac{1}{n})^t$. Following the same approach as in \cite{mahl_schindel_2007} to retrieve an upper bound for $P_{c,t}$, we use the following inequality
\begin{equation}
(1-\frac{1}{m})^m \leq \frac{1}{e}
\end{equation}
which holds for all $m > 0$. From this inequality, it follows that
\begin{equation}
(1-\frac{1}{n})^t = ((1-\frac{1}{n})^n)^{\frac{t}{n}} \le e^{-\frac{t}{n}}
\end{equation}
With this, the probability $P_{c,t}$ of not finding the counterexample with $t$ test runs can be defined as
\begin{equation}
P_{c,t} \le e^{-\frac{t}{n}}
\end{equation}
In order to retrieve the number of test runs $t$ necessary for $P_{c,t}$ to drop below a specified threshold $c$, the inequality is solved for $t$, which is then dependent of the known parameter $n$ and an arbitrary value for $c$:
\begin{align}
    e^{-\frac{t}{n}} &\leq c && \text{with } 0 \leq c\le 1 \nonumber\\
    t &\geq -n\:\ln(c)
\end{align}
For $c = \frac{1}{e}$ ($\approx 36.79\:\%$) the lower bound of $t$ is exactly $n$, which means that for higher reliabilities the number of test runs needs to be greater than $n$. \figref{fig:graph_t_c} shows the lower bounds of $t$ as a function of the probability threshold and search space size. One can see that the increase in accuracy is approximately linear to the number of test runs below a threshold of $c=0.5$, but requires an exponential testing effort to reach higher thresholds.
\begin{figure}[h]
\includegraphics[width=0.95\linewidth]{figures/3-offline/graph_t_c}
\caption{The number of required test runs as a function of the probability of false positives $c$ and size of the search space $n$}
\label{fig:graph_t_c}
\end{figure}

\section{Validators vs. test runs}
The last section derived a formula to calculate a lower bound for a number of test runs $t$ in order to reach a certain level of confidence. However, $t$ is not a parameter that can be adjusted to an arbitrary value on the blockchain, as the assertion is checked by the validators. Assuming a blockchain has $m$ validators, the actual lower bound of test runs is $m$. For cases where there are not enough validators to reach a threshold $c$, a mechanism is required to have each validator check the property for multiple random values. Hence, the actual executed number of checks is always a multiple of $m$.

\section{Alternatives to random testing}\label{sec:alt_random}
For applications where higher reliability is crucial, an alternative to checking elements randomly could be to coordinate a systematic iteration of the domain. The implementation of such a coordination is not trivial though; validators can't simply be passed an individual value as input. Instead, possible approaches could be to implement a central instance that allocates an element in the search space to each validator, or use some unique and intrinsic attribute, like an identification number, as input for a mapping.

\subsection{Central instance assigning values}
For this approach, the tool-chain would need to generate a separate contract that is called by the miners and validators as a proxy. This contract would then, for instance, generate a number using a modulo-n counter and pass this number as an additional parameter to the assertion code. The random generators would be omitted accordingly. However, this works only as expected if there are no simultaneous transactions calling the contract, otherwise it cannot be guaranteed that all elements have been checked for each of the transactions. If and how this issue can be solved will not be discussed further in this thesis. Another drawback of this approach is that it leads to a serialization of the tests, as the contract has to update its internal storage.

\subsection{Using unique attributes of a validator}\label{sec:alt_attributes}
This approach strongly depends on whether the validators have a unique id or other attribute that can be accessed from within a contract.  If there is (or the language can be extended with such a feature), there needs to exist a non-injective surjective function that maps the respective attributes represented by type A to an element in the search space, represented by type B, i.e. $f: X \rightarrow Y$. Furthermore, for cases where $t > m$, an offset needs to be added, s.t. a validator checks distinct elements for each test run. \\
Implementing such an approach on Tezos becomes even more challenging due the way endorsing (i.e. validation) rights are distributed in its proof-of-stake mechanism: for each block level, endorsing rights are assigned to the owner of a randomly selected roll, i.e., a set of tokens \cite{tezos_docs}. This means that the same validator can be picked multiple times for endorsing one block and thus some elements in the search space may remain unchecked. \secref{} goes into more detail about this issue. \todo{Ref section}

### 2021-04-21 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Revision Chpt. 3

@@
 \chapter{Toolchain Implementation - Frontend}\label{chap:offline}
-The purpose of the toolchain is to support the proposed model from specifying assertions for Smart Contracts, transforming them to their negation to generating assertion Smart Contracts that can be invoked by the validators.
+The purpose of the toolchain is to support the process from specifying assertions to generating assertion Smart Contracts that can be invoked on-chain by the validators.
 As determined in \secref{sec:restrict}, the current version of the toolchain only supports the processing of assertions featuring universal quantification.
@@
 This is described further in \secref{sec:transformation}.
-The resulting ASTs are then passed to the backend, which is introduced in the subsequent chapter for the Tezos blockchain.
+The resulting ASTs are then passed to the backend, which is introduced in the \chapref{chap:offline_tezos} for the Tezos blockchain.
 
@@
 Tezos' Smart Contract language Michelson is a low-level and stack-based language.
-Specifying assertions that way is complex and inconvenient, especially if the language is compiled to other targets as well.
+Specifying assertions in such a target-specific language is complex and inconvenient, especially if the language should be compiled to other targets as well.
 Therefore, this thesis defines a domain-specific high-level language to express assertions.
 
-The syntax of this language is described in two versions by the EBNF grammars given in appendix \ref{apx:grammar}.
-One version implements a prefix and the other one an infix notation.
+The syntax of this language is described in two versions by the grammars given in appendix \ref{apx:grammar}.
+One version implements a prefix and the other an infix notation.
 The parser currently supports the prefix notation and correct operator precedences must be handled explicitly with parentheses.
-To avoid context switches (for developers on Tezos), the syntax is inspired by OCaml \cite{ocaml_docs} and uses the same type notations as Michelson.
+To avoid context switches (for developers on Tezos), the syntax is inspired by OCaml and uses the same type notations as Michelson.
 
@@
 Assertions are passed to the toolchain as simple text files.
-This thesis follows the convention of using the file extension \texttt{.tza} for such files (henceforth referred to as ``assertion contracts'') in reference to the file extension \texttt{.tz}used for Michelson source files.
-Assertion contracts contain at least one assertion for a specific entrypoint of the actual contract (henceforth referred to as ``parent contract'').
-For the remaining entrypoints the compiler automatically generates empty assertions\footnote{cf.
-\secref{sec:compiler}}.
+This thesis follows the convention of using the file extension \texttt{.tza} for such files (henceforth referred to as ``assertion contracts'') in reference to the file extension \texttt{.tz} used for Michelson source files.
+An assertion contract is always associated with a Smart Contract (henceforth referred to as ``parent contract'') and contains at least one assertion for a specific entrypoint thereof.
+For the remaining entrypoints, the compiler automatically generates empty assertions (cf.
+\secref{sec:compiler}).
 
-An assertion begins with the keyword \texttt{entrypoint} and a signature consisting of an optional tag denoted by \%, followed by a parameter pattern.
+An assertion begins with the keyword \texttt{entrypoint} and a signature consisting of an optional tag, denoted by \%, followed by a parameter pattern.
 Parameter patterns are similar to patterns in OCaml --- they are templates that match shapes of data structures and bind identifiers to the components of them.
 The given parameter pattern must match exactly the parameter type of the entrypoint it is associated with.
-The body of an assertion can contain a nesting of quantifiers and conditions around exactly one \texttt{assert} expression.
-Conditions can be used to restrict the quantification domains or for any other constraints.
+The body of an assertion can contain a nesting of quantifiers and conditions around exactly one \texttt{assert} expression, which tests a property.
+Conditions can be used to restrict the quantification domains or to impose any other constraints.
 For completeness, the existential quantifier is already included in the grammar, however the current version of the pipeline will reject any assertions containing it.
 
-How the assertions are associated with the respective entrypoint of the parent contract depends on the Smart Contract language.
+How the assertions are associated with the respective entrypoint of the parent contract, depends on the Smart Contract language.
 In the case of Solidity, a tag that mirrors the function name is enough to link assertion and entrypoint.
@@
 \lstinputlisting[caption=Patterns in the assertion language, language=, numbers=none, label=lst:patterns]{listings/patterns.txt}
-
 By using patterns, developers can avoid the explicit handling of special cases, such as empty lists, in the assertion specification.
@@
 In order to make the frontend generic, the sets of data types and operations supported by the grammar constitute unions of those present in the target languages.
-This not only the implementation of a single, common parser, but also allows the transformation to be oblivious of the target platform.
+This allows not only the implementation of a single, common parser, but also the transformation to be oblivious of the target platform.
 As a consequence, the backends are responsible for performing a semantic check and  rejecting any assertions containing types or operations which are not supported by the target language.
@@
 Domain specific data types, like \texttt{timestamp} or \texttt{address}, are supported as well.
-The data type \texttt{fmu} represents a generic fractional monetary unit, which is translated to the corresponding token type of the target platform\footnote{Mutez in Tezos, or Wei in Ethereum}.
+The data type \texttt{fmu} represents a generic fractional monetary unit, which is translated to the corresponding token type of the target platform\footnote{For example Mutez in Tezos, or Wei in Ethereum}.
 
@@
 \subsection{Example}
-The example given in \lstref{lst:sorted_assertion} implements an assertion, which checks whether a list is sorted in ascending order based on a variation of the formula stated in \eqref{eq:sorted} in the introduction:
+As an example, consider a variation of the explicit assertion for sorted lists, stated in \eqref{eq:sorted_v2}.
+In contrast to the variation given in the introduction (\eqref{eq:sorted}), which translates to comparing a random element of the list with its direct neighbour, this translates to a comparison of two random elements (under the constraint $n < m$).
+\lstref{lst:sorted_assertion} shows how this formula can be expressed in the assertion language.
 \begin{equation}\label{eq:sorted_v2}
@@
 \end{equation}
-In contrast to the previous variation, which translates to an assertion that compares a random element of the list with its direct neighbour, this translates to a comparison of two random elements (under the constraint $n < m$).
-\lstref{lst:sorted_assertion} shows how this formula can be expressed in the assertion language.
-\lstinputlisting[caption=Assertion contract for checking if a list is sorted, language=Assertion, label={lst:sorted_assertion}]{listings/sorted.tza}
+\lstinputlisting[caption=Assertion specification for sorted lists, language=Assertion, label={lst:sorted_assertion}]{listings/sorted.tza}
 
-In line 1, the signature of the assertion is declared with tag \textit{find} and a parameter \texttt{a} of type integer list.
-The body is a nesting of two universal quantifiers which declare the predicate variables $n$ and $m$ of type integer (lines 2 and 3), followed by a nesting of conditions to define the domains of the quantifiers (lines 4-6), corresponding to the premise of the formula.
-The body of the last condition (line 7) ultimately contains the keyword \texttt{assert} followed by the specification of the property to be checked, i.e.,  $a[n] \leq a[m]$.
+Line 1 declares the signature of the assertion.
+It specifies the explicit tag \textit{find} and the input parameter \texttt{a} of type integer list.
+The body is a nesting of two universal quantifiers, which declare the predicate variables $n$ and $m$ of type integer (lines 2 and 3), followed by a nesting of conditions.
+The conditions define the domains of the quantifiers (lines 4-6), corresponding to the premise of the formula.
+The body of the last condition (line 7) ultimately contains the keyword \texttt{assert} followed by a condition checking the property of ascending order, i.e.,  $a[n] \leq a[m]$.
 
@@
 \item \textbf{Local variables} to store, reuse and denominate computed values
-\item \textbf{User-defined functions} to extract whole routines that can be reused in a single or even many assertion contracts, if defined as a module.
+\item \textbf{User-defined functions} to extract whole routines, s.t. they can be reused in several assertions or other assertion contracts
 \item \textbf{if-else conditions} to adapt the domains of quantifications if certain conditions hold.
-The assertion that checks whether two numbers are relatively prime (discussed in \secref{sec:coprime}) is a good use-case for this feature: Firstly, the minimum of the given number has to be determined, however the \texttt{min}-function might not be supported as a built-in function by the target language (Tezos, for instance, does not support it).
-A solution for that could be to implement two branches in the program to handle each case.
-Secondly, if the greater of the two numbers is not evenly divided by the smaller one, the formula can be optimized by reducing the quantification domain by half to $(2 \le n \le \lfloor \frac{min(a,b)}{2} \rfloor)$, as a number cannot be evenly divided by any number between itself and its half \cite{bernhardt_veigel_2020}.
-With a syntax supporting an \texttt{if-else} control structure, the optimized assertion could look as follows:
-\lstinputlisting[caption=Assertion syntax with if-else structures \cite{bernhardt_veigel_2020}, language=Assertion, label={lst:coprime}]{listings/coprime_ifelse.tza}
-This feature is not included in the current version, because conditional domain restrictions make the translation from quantifiers to random generators or loops more complex.
-Aside from that, without the feature of variables and user-defined functions, the code is inflated significantly, thus causing increased origination cost.
+The assertion checking whether two numbers are relatively prime (discussed in \secref{sec:coprime}) is a good use-case for this feature: Firstly, the formula requires to determine the minimum of the given numbers --- however, the \texttt{min}-function might not be supported as a built-in function by the target language (as is the case on Tezos).
+A solution for that is to implement two branches in the program to handle each case.
+Secondly, if the greater of the two numbers is not evenly divided by the smaller one, the formula can be optimized by reducing the quantification domain by half to $2 \le n \le \lfloor \frac{min(a,b)}{2} \rfloor$.
+\lstref{lst:coprime} shows a hypothetical specification of an assertion validating the property of coprimeness using \texttt{if-else} control structures:
+\lstinputlisting[caption=Assertion for coprimeness using if-else structures, language=Assertion, label={lst:coprime}]{listings/coprime_ifelse.tza}
 \end{itemize}
@@
 
-After successfully parsing all assertions, the parser returns a list of ASTs.
-On the toplevel, the AST type given in \lstref{lst:ast_type} is composed of an entrypoint specification and an assertion body.
-The parameter pattern and assertion body, in turn, are  subtrees representing their composition or the content of the assertion respectively.
+After successfully parsing all assertions, the parser returns a list of their corresponding ASTs.
+\lstref{lst:ast_type} shows the toplevel definition of the AST type.
+It is composed of an entrypoint specification, consisting of an optional tag and the parameter pattern, and an assertion body.
+The parameter pattern and assertion body are subtrees representing their composition, or the nested assertion code respectively.
 \begin{lstlisting}[label=lst:ast_type, language=, numbers=none, caption=Toplevel AST type definition in OCaml]
@@
 Negating universal quantification is equivalent to an existential quantification of its negated body (and vice versa): $\neg \forall x P(x) \equiv \exists x \neg P(x)$ \cite{Sundstrom2020Quantifiers}.
-The domain restrictions are not affected by the negation, which is also reflected in the rules of predicate logic if the domain is given as a premise in the logical formula: $\neg (p \Rightarrow q) \equiv p \Rightarrow \neg q $.
+The domain restrictions are not affected by the negation.
+This is also reflected in the negation rules of predicate logic, if the domain is given as an implication premise in the logical formula: $\neg (p \Rightarrow q) \equiv p \Rightarrow \neg q $.
 
 Applied to an AST representation of the assertion, the negation recursively traverses the \texttt{assertion} subtree, replaces quantifier and expression nodes with the corresponding negations and skips condition nodes.
-The output is thus a modified AST.
 Further pursuing the example of the assertion for sorted lists, the negated version of the AST given in \figref{fig:ast_example} is shown in \figref{fig:ast_example_neg}.
-The universal quantifiers have been transformed to existential quantifiers, and the asserted condition from $a[n] <= a[m]$ to $a[n] > a[m]$.
+The universal quantifiers have been transformed to existential quantifiers, and the subtree of \texttt{assert}, representing the property check $a[n] <= a[m]$, to the negated expression $a[n] > a[m]$.
 
@@
 \subsection{Domain assignment}
-In order to obtain random generators which only generate values in the interesting range, i.e., within the domains of discourse, the second step of the transformation skims the condition nodes of the AST for atomic constraints that contain bound variables.
-These conditions are then moved to the \texttt{Bounds} field of the respective quantifier.
-If the constraint contains more than one bound variable, it is assigned to the quantifier with the highest depth in the quantifier nesting, as they depend on the generated values of the previous generators.
-\\
+In order to obtain random generators which only generate values in the interesting range, i.e., within the domains of discourse, the second step of the transformation skims the condition nodes of the AST for atomic constraints containing bound variables.
+These conditions are then moved to the \texttt{Bounds} field of the respective quantifier binding that variable.
+If the constraint contains more than one bound variable, it is assigned to the quantifier with the highest depth in the quantifier nesting.
+When translating the quantifiers to random generators, their ranges can then be constructed based on the associated list of constraints.
+After merging a constraint with a quantifier node, it is removed from the assertion body, as checking these constraints during runtime becomes redundant.
+Constraints not involving bound variables have to be checked during runtime.
+
 Relating to the example of sorted lists, the premise in \eqref{eq:sorted_v2} can be considered as a conjunction of the four constraints
@@
 Constraint 1,2 and 4 only contain one bound variable ($n$ or $m$), thus they are assigned to the respective quantifier binding it.
-Constraint 3, on the other hand, features two bound variables -- this constraint is assigned to the quantifier last in the nesting, thus the quantifier binding $m$.
+Constraint 3, on the other hand, features two bound variables -- this constraint is assigned to the quantifier furthest in the nesting, i.e., the quantifier binding $m$.
 The corresponding AST expressing this assignment is shown in \figref{fig:ast_example_transf}.
-
-During compilation, the quantifiers, and their list of bounds, are then translated to target code that corresponds to the following pseudocode (\lstref{lst:rand}):
+Based on the assigned constraints, the quantifiers can then be translated to target code corresponding to the following pseudocode (\lstref{lst:rand}):
 \begin{lstlisting}[label=lst:rand, caption=Random generators for sorted list assertion, numbers=none]
@@
 Secondly, the operands of a disjunction cannot be considered separately if they involve several bound variables.
-For the predicate variable whose random generator is executed first, the domain restriction is optional, while the generation of the following random values depend on the previous result.
+For the predicate variable whose random generator is executed first, the domain restriction is optional, while the generation of the following random values depends on the previous result.
 \lstref{lst:rand_disjoint_nm} shows the corresponding random generators for a variation of constraint 1 featuring two bound variables, i.e., $(\forall n,m) (n < 10 \lor m > 20)...$.
-\begin{lstlisting}[label=lst:rand_disjoint_nm, caption=Random generators with two disjoint ranges and two bound variables, numbers=none]
+\begin{lstlisting}[label=lst:rand_disjoint_nm, caption=Random generators of a disjunction of constraints on two bound variables, numbers=none]
 n = if random(0,2) == 0 then random(-MAX_INT, 10)
@@
 \end{lstlisting}
-Similarly to 1, constraint 2 splits the domain into sub-domains. Constraint 3 effectively makes the quantifier binding $n$ obsolete and thus can be translated to a variable with a constant value.
+Similarly to 1, constraint 2 splits the domain into sub-domains. Constraint 3 effectively makes the quantifier binding $n$ obsolete and can therefore be translated to a variable with a constant value.
 
@@
 In some cases, boundaries are imposed to the random generators implicitly through the used data types.
-List indices, for instance, are always bound to the range $0..
-size(list) - 1$ and could thus be derived from the formula without an explicit specification.
+List indices, for instance, are always bound to the range $[0..
+size(list))$ and could thus be derived from the formula without an explicit specification.
 As this requires a semantic analysis of the AST and thus a more complex transformation, the current implementation requires a completely explicit formula in terms of the domains.

### 2021-04-21 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Revision chpt 4

@@
 
-\subsection{Domain assignment}
+\subsection{Domain assignment}\label{sec:transf_domains}
 In order to obtain random generators which only generate values in the interesting range, i.e., within the domains of discourse, the second step of the transformation skims the condition nodes of the AST for atomic constraints containing bound variables.

### 2021-04-21 assertions/doc/thesis-bernhardt/chapters/4-probabilistic_model.tex
Revision chpt 4

@@
 \chapter{Probabilistic model}\label{chap:prob_model}
-Since the proposed approach implements a probabilistic validation, the reliability of the result depends on the number of validators in the network in relation to the size of the iteration space.
-Given that the number of validators is finite, the probability of finding existing counterexamples may drop below an acceptable threshold for higher domain sizes.
+Since the proposed approach implements a probabilistic validation, the reliability of the validation depends on the number of validators in the network in relation to the size of input.
+Given that the number of validators is finite, the probability of accepting an invalid result may exceed an acceptable threshold for big inputs.
 Thus, the distributed assertion checking scheme should provide a mechanism to have each validator invoke the assertion contract a specified number of times.
-To this end, it is necessary to identify a formula which, given the domain size and a probability threshold, returns a lower bound for the required number of test runs per validator.
+To this end, it is necessary to identify a formula which, given the input size and a probability threshold, returns a lower bound for the required number of test runs per validator.
 
@@
 They are based on the assumption that random generators pick elements independently from a uniform distribution.
-Furthermore, all calculations are based on the worst case scenario, in which there exists exactly one counterexample for the given input.
+Furthermore, all calculations are based on the worst case scenario, in which there exists exactly one counterexample for the validity of the given input.
 
 \section{Sample spaces}
-The sample space of an assertion in form of a logical formula is given by the domains of discourse of the quantifiers.
-\secref described, that the premises defining the domains are translated into a list range constraints of the random generators.
+The sample space of an assertion is given by the domains of discourse of the quantifiers.
+\secref{sec:transf_domains} described, that the premises defining the domains are translated into a list of range constraints for the random generators.
 Based on these constraints, the compiler can derive a formula to determine the size of the sample space at runtime.
@@
 Based on the constraints $2 \le n$ and $n \le \sqrt{p}$, the size of the search space can be determined at runtime with $|\mathcal{S}| = \sqrt{p} - 2$.
-If the assertion has to sample from more than one domain, the search space is given by the Cartesian product of these domains, or sub-search spaces.
-In the example of intersecting sets from \secref{sec:existential}, the sample space is $\mathcal{S} = \mathcal{S}_U \times \mathcal{S}_V$, where $\mathcal{S}_U = \lbrace n \in\mathbb{Z} : 0 \leq n \le |U| \rbrace$ (analogue for $\mathcal{S}_V$).
+If the assertion has to sample from more than one domain, the search space is given by the Cartesian product of these domains.
+In the example of intersecting sets from \secref{sec:existential}, the sample space is $\mathcal{S} = \mathcal{S}_U \times \mathcal{S}_V$, where $\mathcal{S}_U = \lbrace n \in\mathbb{Z} : 0 \leq n \le |U| \rbrace$ and $\mathcal{S}_V = \lbrace m \in\mathbb{Z} : 0 \leq m \le |V| \rbrace$).
 At runtime, the size of the search space can be determined with $|\mathcal{S}| = (|U| - 0) + (|V| - 0)$.
@@
 Deterministically, this is reachable with exactly $|\mathcal{S}|$ test runs.
-This is, however, invalid for the probabilistic approach, as some validators may generate duplicate random values and leave some elements of $\mathcal{S}$ unchecked.
+This is, however, invalid for the probabilistic approach, as some validators may generate the same random values and thus leave some elements of $\mathcal{S}$ unchecked.
 \\
 In probability theory, this is known as the Coupon Collector's Problem \cite{croucher_collecting_2006}.
-Given $n = |\mathcal{S}|$, the probability that no duplicate elements are generated with $n$ picks is given by
+Given $n = |\mathcal{S}|$, the probability that $n$ validators generate a unique element from $\mathcal{S}$ is given by
 \begin{equation*}
@@
 \end{equation*}
-As an example, the probability that all validators generate a unique random value already drops to $0.036\%$ for $n = 10$.
-Let the random variable $T$ be the number of test runs executed until every element in the search space has been generated.
-In order to obtain an estimation of how many test runs are needed to find the counterexample for certain, the goal is to identify its expectation $E(T)$.
-To this end, the geometric probability distribution is applied \cite{croucher_collecting_2006}:\\
+As an example, the probability already drops to $0.036\%$ for $n = 10$.
+
+Let the random variable $T$ be the number of completed test runs until every element in the search space has been generated at least once.
+By identifying its expectation $E(T)$, one can obtain an estimation of how many test runs are needed to find the counterexample with certainty.
+Since a generated value can either be unique (``success'') or a duplicate (``failure''), a test run can be seen as a Bernoulli trial \cite{papoulis02}.
+Therefore, the geometric probability distribution is applied \cite{croucher_collecting_2006}.
+
 Each element is generated with a probability of $1/n$. Thus, the probability to generate the $i$th unique element is given by 
@@
 \end{equation}
-\cite{croucher_collecting_2006}. The expected value of a random variable $X$ is given by $E(X) = \frac{1}{p}$\cite{croucher_collecting_2006}, thus the expected number of test runs for $n$ is 
+The expected value of a random variable $X$ is given by $E(X) = \frac{1}{p}$, thus the expected number of test runs for $n$ is 
 \begin{equation}
@@
 \tabref{tab:prob_outcomes} shows the expected number of test runs $E(T)$ and its standard deviation $\sigma$ for different $n$.
-Furthermore, $E(T)$ and $\sigma$ are used to calculate a 95\% confidence interval for $T$ by applying the central limit theorem, which provides an upper and lower bound on the number of test runs \cite{croucher_collecting_2006}.
+Furthermore, $E(T)$ and $\sigma$ are used to calculate a 95\% confidence interval for $T$ by applying the central limit theorem, which provides an upper and lower bound on the number of test runs.
 Rounded values for both bounds are also shown in \tabref{tab:prob_outcomes}.
@@
 
-The results show that checking random values is a very inefficient approach if false positives are not admissible.
+The results show that checking random values is a very inefficient approach if false positives are not admissible and an error rate of close to zero is targeted.
 Even if the lower bound of $T$ is chosen as the number of test runs, it exceeds the size of the search space by far and increases the time complexity to $\mathcal{O}(n*log(n))$ for large $n$ \cite{xu_tang_2011}.
-For instances where false positives are tolerable, the following section introduces a formula to calculate the number of test runs that detect counterexamples with a given probability threshold $p \leq 1$.
+For instances where false positives are tolerable, the following section introduces a formula to determine the number of needed test runs to detect counterexamples with a configurable probability.
 
-\section{Setting probability thresholds}\label{sec:prob_threshold}
+\section{Configuration of the error rate}\label{sec:prob_threshold}
 The goal is to find a number $t$ of test runs, s.t.
-the probability $P_{c,t}$ of not finding the counterexample drops below a certain threshold $c$.
+the probability $P_{c,t}$ of accepting an invalid result falls below a certain threshold $c$.
 A validator finds the counterexample in one test run with probability $\frac{1}{n}$, and misses it with probability $(1-\frac{1}{n})$.
 After $t$ tests runs, the probability that the counterexample has not been found is thus $(1-\frac{1}{n})^t$.
-Following the same approach as in \cite{mahl_schindel_2007} to retrieve an upper bound for $P_{c,t}$, we use the following inequality
+Following the same approach as Mahlmann and Schindelhauer \cite{mahl_schindel_2007} to retrieve an upper bound for $P_{c,t}$, the following inequality is used:
 \begin{equation}
@@
 \end{equation}
-With this, the probability $P_{c,t}$ of not finding the counterexample with $t$ test runs can be defined as
+With this, the probability $P_{c,t}$ of missing the counterexample with $t$ test runs can be defined as
 \begin{equation}
@@
 \end{equation}
-In order to retrieve the number of test runs $t$ necessary for $P_{c,t}$ to drop below a specified threshold $c$, the inequality is solved for $t$, which is then dependent of the known parameter $n$ and an arbitrary value for $c$:
+In order to determine a value for $t$, s.t.
+$P_{c,t}$ falls below a specified threshold $c$, the inequality is solved for $t$.
+The resulting inequality then depends on the known parameter $n$ and an arbitrary value for $c$:
 \begin{align}
@@
 \end{align}
-For $c = \frac{1}{e}$ ($\approx 36.79\:\%$) the lower bound of $t$ is exactly $n$, which means that for higher reliabilities the number of test runs needs to be greater than $n$.
-\figref{fig:graph_t_c} shows the lower bounds of $t$ as a function of the probability threshold and search space size.
-One can see that the increase in accuracy is approximately linear to the number of test runs below a threshold of $c=0.5$, but requires an exponential testing effort to reach higher thresholds.
+For $c = \frac{1}{e}$ ($\approx 36.79\:\%$) the lower bound of $t$ is exactly $n$.
+For lower error rates, the number of test runs needs to be greater than $n$.
+\figref{fig:graph_t_c} shows the lower bounds of $t$ as a function of the probability threshold and the size of the search space.
+One can see that the increase of test runs is approximately linear for higher thresholds, but transitions to an exponential testing effort to reach lower thresholds.
 \begin{figure}[h]
-\includegraphics[width=0.95\linewidth]{figures/3-offline/graph_t_c}
-\caption{The number of required test runs as a function of the probability of false positives $c$ and size of the search space $n$}
+\includegraphics[width=0.95\linewidth]{figures/4-probabilistic_model/graph_t_c}
+\caption{Number of required test runs as a function of the probability of false positives $c$ and size of the search space $n$}
 \label{fig:graph_t_c}
@@
 \section{Validators vs. test runs}
-The last section derived a formula to calculate a lower bound for a number of test runs $t$ in order to reach a certain level of confidence.
-However, $t$ is not a parameter that can be adjusted to an arbitrary value on the blockchain, as the assertion is checked by the validators.
-Assuming a blockchain has $m$ validators, the actual lower bound of test runs is $m$.
-For cases where there are not enough validators to reach a threshold $c$, a mechanism is required to have each validator check the property for multiple random values.
-Hence, the actual executed number of checks is always a multiple of $m$.
+The last section derived a formula which determines the lower bound of test runs to obtain a specified error rate.
+However, $t$ is not a parameter that can be adjusted to an arbitrary value on the blockchain.
+Assuming a blockchain has $m$ validators, the lowest possible bound of test runs is $m$, as every validator invokes the assertion at least once.
+In cases where $m$ test runs are not sufficient to fall below the threshold $c$, each validator has to invoke the assertion multiple times.
+More specifically, the number of test runs per validator is given by \eqref{eq:t_validator} and is always a multiple of $m$.
+\begin{equation}\label{eq:t_validator}
+t_{validator} = \lceil t / m \rceil
+\end{equation}
 
 \section{Alternatives to random testing}\label{sec:alt_random}
-For applications where higher reliability is crucial, an alternative to checking elements randomly could be to coordinate a systematic iteration of the domain.
-The implementation of such a coordination is not trivial though; validators can't simply be passed an individual value as input.
-Instead, possible approaches could be to implement a central instance that allocates an element in the search space to each validator, or use some unique and intrinsic attribute, like an identification number, as input for a mapping.
+For applications where low error rates are crucial and random sampling generates too much cost, an alternative could be to coordinate a systematic iteration of the domain.
+However, the implementation of such a coordination is not trivial, as the validators are engaged via a broadcast and cannot be passed an individual value as input.
+Instead, possible approaches could be to implement a central instance that allocates an element in the search space to each validator, or to use some unique and intrinsic attribute of validators as a seed or input of a mapping to elements in the search space.
 
-\subsection{Central instance assigning values}
-For this approach, the tool-chain would need to generate a separate contract that is called by the miners and validators as a proxy.
-This contract would then, for instance, generate a number using a modulo-n counter and pass this number as an additional parameter to the assertion code.
-The random generators would be omitted accordingly.
-However, this works only as expected if there are no simultaneous transactions calling the contract, otherwise it cannot be guaranteed that all elements have been checked for each of the transactions.
-If and how this issue can be solved will not be discussed further in this thesis.
-Another drawback of this approach is that it leads to a serialization of the tests, as the contract has to update its internal storage.
+\subsection{Central allocation of elements}
+For this approach, the toolchain would need to generate a separate contract that is called by the miners and validators as a proxy.
+When invoked, this proxy contract allocates the next element of the search space (for instance using a modulo-n counter) and passes this number as an additional parameter to the assertion contract.
+Furthermore, the proxy contract needs to avoid race conditions in case the assertion mechanism is triggered by several external transactions simultaneously.
+Another drawback of the proxy contract having to update its internal storage is the consequential serialization of the tests runs.
 
 \subsection{Using unique attributes of a validator}\label{sec:alt_attributes}
-This approach strongly depends on whether the validators have a unique id or other attribute that can be accessed from within a contract.
-If there is (or the language can be extended with such a feature), there needs to exist a non-injective surjective function that maps the respective attributes represented by type A to an element in the search space, represented by type B, i.e.
-$f: X \rightarrow Y$.
-Furthermore, for cases where $t > m$, an offset needs to be added, s.t.
-a validator checks distinct elements for each test run.
-\\
-Implementing such an approach on Tezos becomes even more challenging due the way endorsing (i.e.
-validation) rights are distributed in its proof-of-stake mechanism: for each block level, endorsing rights are assigned to the owner of a randomly selected roll, i.e., a set of tokens \cite{tezos_docs}.
-This means that the same validator can be picked multiple times for endorsing one block and thus some elements in the search space may remain unchecked.
-\secref{} goes into more detail about this issue.
-\todo{Ref section}
+This approach strongly depends on whether the validators have a unique id or another attribute, which can be accessed from within a contract.
+If there is (or the language can be extended with such a feature), the assertion contract needs to implement a non-injective surjective function $f: X_{:A} \rightarrow Y_{:B}$ mapping the respective attribute, represented by a type A, to an element in the search space, represented by type B.
+Furthermore, in cases where $t > m$, the function should add an offset for each test run, s.t.
+each iteration checks a distinct element.
+
+Due to the way how endorsing (i.e., validation) rights are assigned in Tezos' proof-of-stake mechanism, implementing such an approach on Tezos becomes even more challenging.
+For each block level, endorsing rights are assigned to the owner of a randomly selected roll, i.e., a set of tokens.
+Consequently, the same validator can be selected multiple times for endorsing one block, which would leave some elements in the search space unchecked.

### 2021-04-21 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
Own chapt probabilistic model
Revision chpt 4

--- 2021-04-17 assertions/doc/thesis-bernhardt/chapters/4-offline_design_tezos.tex
@@
+\todo{Make clear that we only engage validators on Tezos (not all nodes)}
+\todo{What happens if a validator has multiple endorsing rights?}
 \chapter{Tezos-specific Offline Design}\label{chap:offline_tezos}
@@
 \centering
-\includegraphics[width=0.5\linewidth]{figures/4-offline_tezos/internal_ops}
+\includegraphics[width=0.5\linewidth]{figures/5-offline_tezos/internal_ops}
 \captionsource{Execution order of two external operations and their internal operations}{\cite{tezos_docs}}
@@
 \begin{figure}[!htb]
-\subfloat[Appending assertions as separate entrypoints]{\includegraphics[width=0.5\textwidth]{figures/4-offline_tezos/pipeline_output_mono_ep_basic.jpg}}
+\subfloat[Appending assertions as separate entrypoints]{\includegraphics[width=0.5\textwidth]{figures/5-offline_tezos/pipeline_output_mono_ep_basic.jpg}}
 \quad
-\subfloat[Inserting the assertion code into the original entrypoint]{\includegraphics[width=0.5\textwidth]{figures/4-offline_tezos/pipeline_output_mono_basic.jpg}}
+\subfloat[Inserting the assertion code into the original entrypoint]{\includegraphics[width=0.5\textwidth]{figures/5-offline_tezos/pipeline_output_mono_basic.jpg}}
 \caption{Approaches for assembling a monolithic contract}
@@
 \centering
-  \includegraphics[width=0.5\textwidth]{figures/4-offline_tezos/pipeline_output_mono_ep.jpg}
+  \includegraphics[width=0.5\textwidth]{figures/5-offline_tezos/pipeline_output_mono_ep.jpg}
 	\caption{Monolithic assembly with separate entrypoints for manager and assertion}
@@
 \centering
-  \includegraphics[width=0.7\textwidth]{figures/4-offline_tezos/interaction_monolithic.jpg}
+  \includegraphics[width=0.7\textwidth]{figures/5-offline_tezos/interaction_monolithic.jpg}
 	\caption{Interaction with a monolithic contract}
@@
 \centering
-  \includegraphics[width=0.8\textwidth]{figures/4-offline_tezos/interaction_monolithic_managertz.jpg}
+  \includegraphics[width=0.8\textwidth]{figures/5-offline_tezos/interaction_monolithic_managertz.jpg}
 	\caption{Interaction with a manager and monolithic contract}
@@
 \centering
-  \includegraphics[width=0.6\textwidth]{figures/4-offline_tezos/pipeline_output_modular.jpg}
+  \includegraphics[width=0.6\textwidth]{figures/5-offline_tezos/pipeline_output_modular.jpg}
 	\caption{Modular assembly of assertion and manager code}
@@
 \centering
-  \includegraphics[width=0.9\textwidth]{figures/4-offline_tezos/interaction_modular.jpg}
+  \includegraphics[width=0.9\textwidth]{figures/5-offline_tezos/interaction_modular.jpg}
 	\caption{Interaction with a modular contract}
@@
 \begin{figure}[h]
-\includegraphics[width=\linewidth]{figures/4-offline_tezos/pipeline_backend}
+\includegraphics[width=\linewidth]{figures/5-offline_tezos/pipeline_backend}
 \caption{The stages of Tezos-specific backend of the compilation pipeline}
@@
 \end{enumerate}
+% calculate size of search space? -> need to derive a formula from range constraints
 By passing the next id $i$ to the function, the access to the storage can be hard-wired into the generated code.
@@
 After $t_{total}$ has been computed, the upper bound of the loop is calculated according to \eqref{eq:t_validator}.
-\begin{equation}\label{eq:t_validator}
+% remove -> refer to equation in previous chapter
+\begin{equation}
 t = \lceil t_{total} / \#validators \rceil
@@
 \centering
-\includegraphics[width=\linewidth]{figures/4-offline_tezos/pipeline_liq}
+\includegraphics[width=\linewidth]{figures/5-offline_tezos/pipeline_liq}
 \caption{Pipeline with IR compilation and an external toolchain}
@@
 \centering
-\includegraphics[width=0.9\linewidth]{figures/4-offline_tezos/cost_analysis}
+\includegraphics[width=0.9\linewidth]{figures/5-offline_tezos/cost_analysis}
 \caption{Gas consumption per validator of transactions calling \texttt{Foo} and \texttt{Bar} for increasing input sizes}

### 2021-04-22 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Begin revision chpt 5

@@
-\chapter{Toolchain Implementation - Frontend}\label{chap:offline}
+\chapter{Toolchain Frontend}\label{chap:offline}
 The purpose of the toolchain is to support the process from specifying assertions to generating assertion Smart Contracts that can be invoked on-chain by the validators.

### 2021-04-22 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
Begin revision chpt 5

@@
-\todo{Make clear that we only engage validators on Tezos (not all nodes)}
-\todo{What happens if a validator has multiple endorsing rights?}
-\chapter{Tezos-specific Offline Design}\label{chap:offline_tezos}
-After parsing an assertion contract and transforming it, the resulting AST is passed to the target-specific backend.
+\chapter{Toolchain Backend}\label{chap:offline_tezos}
+After parsing and transforming a list of assertions, the resulting ASTs are passed to the target-specific backend.
 For this thesis, the platform target is Tezos, with Michelson as the compilation target.
-This chapter continues to describe the pipeline stages implemented in the Tezos backend, which are shown in \figref{fig:pipeline_backend}.
+The pipeline stages of the backend comprise the ones colourized in \figref{fig:pipeline_backend}.
+First, the generic ASTs are subjected to a semantic check, which rejects any assertions containing unsupported types, operations or other invalid expressions.
+Valid ASTs are then cast to a target specific AST type and passed to the type checker.
+In this stage, the assertions are linked to the respective parent entrypoints based on the parameter patterns and tags.
+Given the list of target specific ASTs and a linking, the compiler finally generates target code.
+Each stage is described in more detail in \secref{sec:backend_impl}.
+
+As a preliminary for the compiler implementation, 
+% the chapter identifies/describes necessary amendments to Michelson and the VM -> part of protocol design, but also concerns the toolchain -> secref
+% furthermore, a scheme for the orchestration of assertion and parent code is required.
+the code somehow needs to collude -> explores some options; discusses advantages and disadvantages.
+picks a winner for the proof-of-concept impl.
+% for background/ as a basis for this chapter, section 1 gives an introduction to Tezos and Michelson
+
  Furthermore, it states the necessary extensions to Michelson and its evaluator to facilitate useful assertions using random generators and assesses several orchestration strategies between the parent and assertion contract code.
@@
 
-\section{Backend of the pipeline}
+\section{Backend implementation}\label{sec:backend_impl}
+\todo{Shorten a bit - overview already given in chpt intro}
 The Tezos backend of the pipeline comprises of the three stages semantic check, type check and compilation.
@@
 Details about this and possible rewards for valid counterexamples should be considered in the protocol design.
+
+\todo{Make clear that we only engage validators on Tezos (not all nodes)}
+\todo{What happens if a validator has multiple endorsing rights?}

### 2021-04-23 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
Revision chpt 5

@@
 
-As a preliminary for the compiler implementation, 
-% the chapter identifies/describes necessary amendments to Michelson and the VM -> part of protocol design, but also concerns the toolchain -> secref
-% furthermore, a scheme for the orchestration of assertion and parent code is required.
-the code somehow needs to collude -> explores some options; discusses advantages and disadvantages.
-picks a winner for the proof-of-concept impl.
-% for background/ as a basis for this chapter, section 1 gives an introduction to Tezos and Michelson
+As a preliminary for the compiler implementation, \secref{sec:ext_michelson} identifies necessary extensions to Michelson and Tezos' VM in order to facilitate the distributed assertion scheme.
+Although the extensions are formalized in this thesis, implementing the extension is part of the protocol amendment.
+Furthermore, the compiler needs to generate the target code according to an on-chain orchestration scheme between the assertion and parent contract.
+\secref{sec:orchestration} explores possible strategies for such a scheme, and discusses their strengths and weaknesses.
+Based on a resulting proposal for the orchestration, \secref{sec:cost_analysis_distributed} performs a cost analysis of the approach of distributed assertion checking and evaluates if, and under which conditions, it can solve the issue of scalability in blockchain applications.
 
- Furthermore, it states the necessary extensions to Michelson and its evaluator to facilitate useful assertions using random generators and assesses several orchestration strategies between the parent and assertion contract code.
-As a preliminary, the following section gives a short introduction to the Tezos blockchain, the Michelson language and some relevant tools in Tezos' ecosystem.
+As a foundation for the other sections, \secref{sec:tezos} provides important background on the Tezos blockchain, its built-in Smart Contract language Michelson and some relevant tools and projects within its ecosystem.
 
-\section{Introduction to Tezos}\label{sec:tezos}
+\section{Tezos}\label{sec:tezos}
 The Tezos blockchain is presented in its whitepaper as a \enquote{generic and self-amending crypto-ledger} \cite{goodman_tezos_2014}.
-It uses a proof-of-stake consensus mechanism that is not only used to agree on the current state of its ledger, but also allows its stakeholders to come to a consensus about changes in the economic protocol by participating in a voting process.
+It uses a proof-of-stake consensus mechanism, which is not only used to agree on the current state of its ledger, but also allows its stakeholders to come to a consensus about changes in the economic protocol by participating in a voting process.
 The changes included in a protocol upgrade, called amendment, can influence i.a.
-which transactions are valid on the blockchain, the payment system or even the voting process itself without risking a fork of the blockchain.
+which transactions are valid on the blockchain, the payment system or even the voting process itself.
+It does so without risking a fork of the blockchain.
 Everyone owning the cryptocurrency of Tezos, called Tez, is considered a stakeholder and can participate in the consensus mechanism.
 The whitepaper compares the self-amending protocol of Tezos to a game created by Philosopher Peter Suber called ``Nomic'', whose set of rules are subjected to a democratic voting system \cite{nomic}.
-Similar concepts can also be found in modern pop culture, such as the virtual sports league ``Blaseball'' \cite{blaseball} that became popular during the COVID-19 pandemic.
+Similar concepts can also be found in modern pop culture, such as the virtual sports league ``Blaseball'' \cite{blaseball}, which became popular during the COVID-19 pandemic.
 
 In addition to user accounts associated with a public key, Tezos supports smart contracts, which are written in the built-in language Michelson.
-Tezos' transaction fee system is similar to that of Ethereum \cite{wood_ethereum_2021} - it is gas-instrumented and besides a base fee, every operation and byte of storage during contract execution has to be paid for.
+Tezos' transaction fee system is similar to that of Ethereum \cite{wood_ethereum_2021} - it is gas-instrumented and besides a base fee, every operation and byte of storage during contract execution has to be paid for by the user.
 However, Tezos imposes a hard cap on the amount of gas that can be consumed per operation (including internal transactions) \cite{tezos_docs}\cite{morley_repo}, whereas Ethereum limits the gas quota only in respect to blocks \cite{wood_ethereum_2021}.\\
-Tezos is written in the multi-paradigm programming language OCaml \cite{ocaml_doc}.
-Compiling the its source code yields five essential binaries: the node, baker, endorser, accuser and client.
-The node is the entity that connects to the peer-to-peer network and keeps a copy of the chain.
-Bakers are responsible for producing new blocks, the endorsers for validating new blocks and the accusers to call out bakers or endorsers which double-sign or -endorse.
-The client provides a command line interface to interact with the local node through remote procedure calls (RPC).
+Tezos is written in the multi-paradigm programming language OCaml.
+Compiling its source code yields five essential binaries: the  node, baker, endorser, accuser and client.
+The node is the entity connecting to the peer-to-peer network and keeping a copy of the chain.
+Bakers are responsible for producing new blocks, the endorsers for validating and signing new blocks and the accusers to call out bakers or endorsers which double-sign or -endorse.
+The client provides a command line interface to interact with nodes through remote procedure calls (RPC).
 
 \subsection{Proof-of-stake in Tezos}
-In Tezos, contracts that staked a minimum amount of tokens, called a roll, can participate in the consensus mechanism and can either have the role of a baker or endorser.
-Contracts who don't own enough tokens or infrastructure to participate directly can delegate their baking and endorsing rights to other contracts.
-The rights are determined and assigned at the beginning of each cycle, which consists of a specified number of blocks.
+In Tezos, contracts which have staked a minimum amount of tokens, called a roll, can participate in the consensus mechanism.
+When participating, a contract has a chance to obtain the role of either a baker or an endorser.
+Contracts who don't own enough tokens, or infrastructure, to participate directly, can delegate their baking and endorsing rights to other contracts.
+The rights to bake or endorse are determined and assigned at the beginning of each cycle, which consists of a specified number of blocks.
 For baking, a random roll is selected for each block level and the rights are assigned to its owner.
-The block produced by that baker is endorsed by a fixed number of endorsers (currently 32 in protocol 008 Edo), which also have been assigned endorsing rights for this block level by a random selection of rolls.
-Since participants can stake more than one roll, an endorser may be assigned several endorsement slots at the same block level.
-\\
+The block produced by that baker is signed by a fixed number of endorsers (32 as of protocol 007 Delphi), which also have been assigned endorsing rights for this block level by a random selection of rolls.
+Since participants can stake more than one roll, they may be assigned several endorsement slots at the same block level.
+
 As an incentive for active participation in the consensus algorithm, delegates (and also delegators) receive rewards in form of tokens.
 However, if accusers detect double-baking or -endorsement, the delegate is penalized by burning (i.e., destroying) their security deposit.
-\cite{tezos_docs}
 
 \subsection{Michelson}
-Michelson is a lower-level, stack-based language with strict type-checking and supports primitive data types, like integers or strings, as well as high-level data structures such as list, maps and sum types \cite{tezos_docs}.
+Michelson is a lower-level, stack-based language with strict type-checking.
+It supports primitive data types, like integers or strings, as well as high-level data structures, such as list, maps and sum types.
 The type system reduces the occurrence of runtime errors and ensures that only well-typed contracts are originated on the blockchain.
-\\
-The concrete syntax of Michelson is called Micheline. A program is represented in Micheline nodes, which can be one of the following constructs:
+
+The concrete syntax of Michelson is called Micheline. A program is represented as Micheline nodes, which can be one of the following constructs:
 \begin{itemize}
@@
 For documentation, readability and additional type constraints, Michelson and Micheline also offer three types of annotations - type, variable and field or constructor annotations, which are labelled with a unique special character in Micheline.
-The toplevel structure of a smart contract consists of a sequence of the three primitives \texttt{parameter, storage} and \texttt{code}, declaring the type of the input parameter, the storage type and the actual program code.
+The toplevel structure of a Smart Contract consists of a sequence of the three primitives \texttt{parameter, storage} and \texttt{code}.
+They declare the type of the input parameter, the storage type and the script, which is interpreted when the contract is invoked.
 The full grammar of Micheline and Michelson can be found in the Tezos developer resources \cite{tezos_docs}.
@@
 \subsubsection{Entrypoints}
-Unlike the contracts shown so far, which were expressed with the syntax of Ethereum's contract language Solidity \cite{solidity_docs}, Michelson doesn't have a concept of named functions with individual input parameter types.
-Instead of named functions, Michelson programs can have separate entrypoints by taking a disjunctive type as input parameter and optionally tagging the type constructors with a "function" name.
-The disjunctive type is built by nesting the \texttt{or} type, which has the constructors \texttt{left} and \texttt{right}.
-Assume we want to implement the contract from \lstref{lst:prime} in Michelson and add another function to it, which expects a string parameter.
-Omitting the actual program, the contract type declaration looks as follows:
+Unlike Ethereum's contract language Solidity, Michelson doesn't have a concept of named functions with a dedicated parameter type.
+Instead of named functions, Michelson contracts models separate entrypoints by taking a sum type as an input parameter.
+The type constructors can optionally be tagged a field annotation, which can be considered an entrypoint name.
+The sum type is built by nesting the \texttt{or} type, which has the constructors \texttt{left} and \texttt{right}.
+
+As an example, the contract in \lstref{lst:entrypoints} has two entrypoints --- entrypoint \texttt{A}, which expects an integer wrapped in the \texttt{left} constructor, e.g.
+\texttt{left 1}, and entrypoint \texttt{B}, which expects a string wrapped in the \texttt{right} constructor, e.g.
+\texttt{right "hello world"}.
 \begin{lstlisting}[language=Michelson, numbers=none, caption=Michelson contract with two entrypoints, label=lst:entrypoints]
-parameter (or (int %isPrime) (string %isUpper));
+parameter (or (int %A) (string %B));
 storage unit;
@@
   ...
-  IF_LEFT { ... (* then *)}
-          { ... (* else *)}
+  IF_LEFT { ... (* entrypoint A *)}
+          { ... (* entrypoint B *)}
 }
 \end{lstlisting}
-The input type declared in the primitive application \texttt{parameter} accepts input of either type \texttt{left int}, or \texttt{right string}.
-By adding the field annotations \texttt{isPrime} and \texttt{isUpper}, the entrypoints are given tags and can be called explicitly by an external transaction.
-In that case, parameters of type \texttt{int} or \texttt{string} are accepted and the value is automatically wrapped into the respective constructors.
-Furthermore, it's possible to declare a \texttt{default} entrypoint, which is called when no explicit tag is specified.
+By adding the constructor annotations \texttt{A} and \texttt{B}, the entrypoints can be invoked explicitly.
+The passed parameter value is then wrapped automatically into the respective constructor.
+Furthermore, it's possible to declare a \texttt{default} entrypoint, which is invoked when no explicit tag is specified in the transaction.
 By default, the default entrypoint is assigned to the root of the parameter type.
-\cite{tezos_docs}
 
 \subsubsection{Internal operations}
-Smart contracts are able to call other smart contracts by emitting internal operations.
+Smart Contracts are able to invoke other Smart Contracts by emitting internal operations.
 The return type of Michelson programs is a tuple of a list of internal operations and the updated storage.
-Thus, after the actual contract has been executed, the operations of the returned list are run in sequence.
-Since the internal operations may in turn also emit internal operations, they are put into a queue and are processed in order.
-As an example, \figref{fig:internal_ops} shows an execution order of two external transactions in sequence, i.e., transactions which have been initiated by a user account, and their internal operations.
+After a contract completes, the operations in the returned list are run in sequence.
+Since internal operations may in turn also emit internal operations, the interpreter puts all emitted operations into a queue, which is processed in order.
+As an example, \figref{fig:internal_ops} shows an execution order of two external transactions and their internal operations in sequence.
 \begin{figure}[h]
@@
 
-Both external and internal operations can fail if the source does not have enough balance to spend the specified amount, a gas limit was reached or if a program fails when reaching a \texttt{FAILWITH} instruction.
+Both external and internal operations can fail, if the source contract does not have enough balance to spend the specified amount, a gas limit was reached, or if a program fails due to reaching a \texttt{FAILWITH} instruction.
 If a failure occurs, the whole sequence fails and all changes up to the point of failure are reverted.
@@
 \subsection{Gas model}
-In Tezos data is stored and transmitted as byte sequences --- in order to obtain a typed representation of their value for interpretation, a byte sequence is first deserialised into Micheline and subsequently parsed \cite{tezos_repo}.
-Conversely, before transmitting or storing something on the blockchain, the typed representation is first unparsed and then serialised.
-The gas consumption of an operation, e.g.
-a transaction or an origination, is thus composed of the following positions on top of a base cost \cite{morley_gasmodel}\cite{tezos_repo}:
+Tezos stores and transmits data as byte sequences --- in order to obtain a typed representation of their value for interpretation, a byte sequence is first deserialised into Micheline and subsequently parsed into a typed AST.
+Conversely, before transmitting or storing something on the blockchain, the typed representation is first unparsed into Micheline and then serialised.
+Since these working steps also entail computational effort, they consume gas and thus account for some of the transaction fees.
+The gas consumption of an operation (e.g., a transaction or a contract origination) is thus composed of the following positions \cite{morley_gasmodel}\cite{tezos_repo} on top of a base gas fee:
 \begin{enumerate}
-\item \textbf{Reading costs} --- apply for reading contract code, storage or Big Maps from the internal database and, on top of the base cost, depend on the amount of bytes read
-\item \textbf{Deserialization costs} --- depend on the Micheline expression and their size
-\item \textbf{Parsing costs} --- are composed of three types of parsing costs:
+\item \textbf{Reading costs} --- apply for reading the contract code and storage from the blockchain and, on top of a base cost, depend on the amount of bytes read
+\item \textbf{Deserialization costs} --- depend on the Micheline expression and the size of the byte sequence
+\item \textbf{Parsing costs} --- are composed of three types of costs:
 	\begin{itemize}
-	\item type parsing --- apply when a Micheline node is converted into a valid type and are computed by a recursive formula; parametrized types therefore generate more cost than plain types
-	\item data parsing --- apply when a node is converted into the value of a known type and depend on the byte length for non-parametrized types, on the number of contained elements for container types and on the parameters for parametrized types
-	\item code parsing --- computes the return type of the code by sequentially applying instructions and type checking if the result matches the expectation.The cost thus increases in the number of instructions, while some instructions incur additional costs besides their base cost, such as \texttt{IF} (both branched need to be checked and compared) or \texttt{CREATE\_CONTRACT} (called contracts needs to be type checked)
+	\item type parsing --- apply when a Micheline node is converted into a valid type
+	\item data parsing --- apply when a node is converted into the value of a known type and depends on the size of the value
+	\item code parsing --- apply when the instructions of a program are type checked and depends on the number and types of instructions.
+Some instructions are expensive, such as \texttt{IF} (both branches need to be checked and compared) or \texttt{CREATE\_CONTRACT} (requires type check of invoked contract)
 	\end{itemize}
-\item \textbf{Type comparison costs} --- occur during parsing when types are checked for equality (e.g. when verifying that the branches of \texttt{IF} have the same type) or contract execution
-\item \textbf{Interpreter costs} --- apply for each executed instruction and are specified for each.
-Expensive instruction are, for instance, \texttt{CONTRACT} with a high base cost and additional cost for reading, deserializing and type checking of the target contract code.
-\item \textbf{Unparsing costs} --- depend on the type of the data; parametrized types incur cost for unparsing its inner types as well
-\item \textbf{Serialization costs} --- depend, similar to deserialization, on the Micheline expression and their size
-\item \textbf{Writing costs} --- apply when writing to the internal database.
-Depend on the amount of bytes written, but with a higher base cost than reading.
-Additional cost is inflicted if the storage of the contract increased in size
+\item \textbf{Type comparison costs} --- apply when types are checked for equality (e.g. when type checking the branches of the \texttt{IF} instruction) or during contract interpretation
+\item \textbf{Interpretation costs} --- apply for each interpreted instruction and depend on their complexity.
+\item \textbf{Unparsing costs} --- apply when converting typed data to untyped Micheline nodes and depend on the data type and size
+\item \textbf{Serialization costs} --- apply when serializing Micheline nodes to byte sequences and depend on the expression and its size
+\item \textbf{Writing costs} --- apply when writing to the internal database and depend on the amount of bytes. A base fee applies for each additional byte of storage.
 \end{enumerate}
@@
 \subsection{Developer tools in the Tezos ecosystem}
-This section describes some relevant tools and projects for developers that are part of Tezos' ecosystem.
+This section describes some tools and projects within Tezos' ecosystem, which are relevant to the development of the toolchain or the protocol amendment.
 
 \subsubsection{Tezos Libraries}
-Tezos' executables and libraries are developed in the programming language OCaml and are available on through OCaml's package manager \texttt{opam} \cite{tezos_opam}.
+Tezos' executables and libraries are available on OCaml's package manager \texttt{opam} \cite{tezos_opam}.
 The protocol libraries of every version are released separately, thus any projects can be built on the protocol of choice.
-Important libraries that were used in the development of the offline toolchain are the Micheline library providing the internal abstract syntax tree (AST) and parser of the Michelson language, as well as the protocol specific libraries containing i.a.
-the type checker.
-Additionally, the client libraries are used to retrieve any needed information from the node or blockchain via RPCs.
+Relevant libraries included in the backend of the toolchain are, i.a, the Micheline library containing the internal abstract syntax tree (AST) and parser of the Michelson language, the protocol libraries providing functions to type check code or data, and client libraries to retrieve any needed information from the node or blockchain via wrapped RPCs.
 
@@
 Before a new protocol is proposed to the Tezos network, it has to be thoroughly tested with system, integration and regression tests.
-This requires a sandboxed network to simulate the real peer-to-peer network, such that also interactions between the actors of the blockchain can be tested.
-Tezos' development environment provides two testing frameworks for this:
-\begin{itemize}
-\item[\textbf{Flextesa}] With Flextesa (Flexible network sandboxes)\cite{tezos_docs} one can configure and run a small, fully functional sandboxed test network including nodes, bakers, endorsers and accusers.
-Accounts can be instantiated and used to send or receive funds.
-Configurable are, for instance, the size of the network, the time between blocks or enabling generation of random network traffic.
-Networks may either be fully autonomous, baking blocks automatically, or require manual baking of blocks.
-It also supports interactive sessions, where the tester can interact with the blockchain using the Tezos client.
-Flextesa's typical use-cases are interactive testing scenarios like double-baking, the voting process or protocol amendments.
-The Tezos repository already provides ready-to-use scenarios for accusations.
-Besides testing shell or protocol code, Flextesa can also be used to test smart contracts.
-\item[\textbf{Tezt}] The Tezt framework \cite{tezos_docs} is newer than Flextesa and planned as its replacement.
-It launches the Tezos binaries as external processes to build a sandboxed test network of configurable size.
-Its main advantages over Flextesa are simplicity, better usability and extendibility and better performance due to the use of an event system instead of polling the node.
-\end{itemize}
+This requires a sandboxed network to simulate the real peer-to-peer network.
+Tezos' development environment provides the two testing frameworks Flextesa (Flexible network sandboxes)\cite{tezos_docs} and its successor Tezt \cite{tezos_docs}.
+They allow to configure and run a small, fully functional sandboxed test network including nodes, bakers, endorsers and accusers.
+Besides testing new protocols, they can also be used to interactively test Smart Contracts.
 
 \subsubsection{High-level languages}
-Michelson is a compilation target for various high-level languages that provide a more user-friendly and intuitive way of writing smart contracts.
-Additionally, some of them come with development environments and testing or verification tools.
-The following list comprises of the three most prominent languages that compile to Michelson:
-\begin{itemize}
+Michelson is a compilation target for various high-level languages that provide a more user-friendly and intuitive way of writing Smart Contracts.
+Additionally, some of them come with development environments, testing or verification tools.
+The following list introduces three prominent languages compiling to Michelson:
+\begin{description}
 \item[\textbf{Liquidity}] \cite{liquidity} is a language with an OCaml-like syntax, which allows using local variables instead of stack manipulations.
 Its module system can be used to write reusable contract code or libraries.
-Besides an optimizing compiler, the project also includes a decompiler to compile Michelson programs to Liquidity.
+Besides an optimizing compiler, the project also includes a decompiler to compile Michelson programs to Liquidity source code.
 \item[\textbf{SmartPy}] \cite{smartpy} is a language available through a Python library and lets developers write contracts and tests using Python syntax and structures (such as classes).
-Its developer suite includes i.a.
-a compiler, a simulation engine for testing contracts and an online editor.
-\item [\textbf{Ligo}] \cite{ligo} offers multiple syntax flavours that are close to Pascal, OCaml or Reason.
+Its developer suite includes, i.a., a compiler, a simulation engine for testing contracts and an online editor.
+\item [\textbf{Ligo}] \cite{ligo} offers multiple syntax flavours close to Pascal, OCaml or Reason.
 Besides compilation, the toolchain allows to invoke or evaluate the generated code locally.
-The Ligo OCaml packages can be integrated into other OCaml projects, s.t.
-the compiler can be invoked from within third-party applications.
-\end{itemize}
+The project provides Ligo as OCaml packages, which can be integrated into other projects.
+\end{description}
 
-\section{Extensions to Michelson}
-The way Michelson is interpreted is purely functional; it takes the current stack and an operation and builds a return stack from the initial one, without causing any side effects \cite{tezos_docs}.
-The recursive Michelson interpreter is defined as as a list of rules comprising of all possible inputs, i.e.
-program and stack types, and the respective output stack type of the computation if a rule applies.
+\section{Extensions to Michelson}\label{sec:ext_michelson}
+For the assertion code to be executable by the VM of Tezos, Michelson and the VM have to be extended with new instructions.
+This includes an instruction to generate a random value of some primitive data type non-deterministically.
+The formalization and possible implementation of such an instruction is described in \secref{sec:random}.
+Aside from this, many useful use-cases involve checking random elements of lists, and possibly strings or bytes.
+For convenience, it is worth considering adding indexing operations for some data types to the VM.
+This is discussed in more detail in \secref{sec:nth}.
+
+As a foundation for the formalization of these new instructions, \secref{sec:michelson_semantics} gives a brief introduction to the Michelson interpreter and type system first.
+
+\subsection{Language semantics and type system}\label{sec:michelson_semantics}
+The way Michelson is interpreted is purely functional; the interpreter takes the current stack and an operation and builds a return stack from the initial one, without causing any side effects.
+The definition of the recursive interpreter is given in the form of a list of rules, comprising of all possible inputs (i.e., program and stack types) and the respective output stack type of the computation.
 Each rule is of the following form:
-\begin{lstlisting}[caption=Rules form in the Michelson interpreter \cite{tezos_docs}, language=, numbers=none, label=lst:rules]
+\begin{lstlisting}[caption=Selection rules in the Michelson interpreter \cite{tezos_docs}, language=, numbers=none, label=lst:rules]
 > (syntax pattern) / (initial stack pattern)  =>  (result stack pattern)
@@
 \end{lstlisting}
-For each valid program and initial stack exactly one rule matches (given that any extra conditions over values on the stack, stated after the \texttt{iff} keyword are true) \cite{tezos_docs}.
-If the result depends on the results of other program interpretations (given after the keywords \texttt{iff, where, and} in rule form), the rule only applies if these partial results also match the respective intermediate result stack patterns.\\
-In addition, there exists a typing rule for each syntax construct that restricts the valid input stacks.
-The typing rules use the meta variables \texttt{'a} for type and \texttt{'A} for stack type variables in order to express consistency within the program (not polymorphism).
-These rules are given in the following form:
+For each valid program and initial stack, exactly one rule matches.
+Following the keyword \texttt{iff}, the rule can add extra conditions over values on the stack.
+If the result depends on the results of other program interpretations, such as conditionals or function calls, the rule can contain \texttt{where} or \texttt{and} clauses.
+These clauses represent a recursive interpretation of an intermediate program.
+The rule thus only applies, if the interpretation of the intermediate result matches the expected pattern.
+
+The type system of Michelson consists of typing rules for each syntax construct, restricting the valid input stacks.
+The typing rules use the meta variables \texttt{'a} for type, and \texttt{'A} for stack type variables.
+Using these meta variables, the rules express consistency within the program.
+The typing rules are given in the form shown in \lstref{lst:type_rules}, where premises are additional typing requirements over values on the stack:
 \begin{lstlisting}[caption=Form of typing rules in Michelson's specification \cite{tezos_docs}, language=, numbers=none, label=lst:type_rules]
@@
 \end{lstlisting}
-The type notations, as well as syntax and stack patterns are listed in \cite{tezos_docs}.
+The Tezos developer resources \cite{tezos_docs} provide a comprehensive list of type notations, syntax and stack patterns.
 
-Since Michelson is implemented in the protocol-specific part of the blockchain code, adding new instructions require a protocol update.
-The instruction must be added i.a.
-to the list of tokens, its computation to the interpreter and its typing rules to the type checker.
-As the computation of the new instruction must be paid for like any other instruction, the protocol must also specify a gas cost.
-Previous extensions to the Michelson language, such as \cite{tezos_michelson_ext}, can be used as a guideline for the implementation and the gas cost specification in \cite{tezos_repo_gas} as an orientation to how high the gas costs should be scheduled for comparable instructions.
+Since the Michelson language and interpreter are implemented in the protocol-specific libraries of Tezos, adding new instructions require a protocol update.
+This entails adding the new instruction to the list of tokens, adding one or several selection rules to the interpreter and typing rules to the type checker \cite{tezos_repo}.
+Furthermore, the protocol must specify the gas cost of its computation.
+Previous extensions to the Michelson language, such as the addition of the instruction ``\texttt{DIG n}'' in protocol 005 Babylon \cite{tezos_michelson_ext}, can be used as a guideline for the extension.
+The gas cost specification of existing instructions \cite{tezos_repo_gas} should be used as an orientation in specifying the costs of new instructions.
 
-From the given formulas and assertion examples so far, one can derive a set of necessary instructions that need be be present in the target language.
-The following subsections list the instructions which have to be added to Michelson's instruction set, specify their selection and typing rules and describe how they can be implemented in the interpreter.
-These do not necessarily include high level instructions, like \texttt{sqrt} from \eqref{eq:prime}, that can be reproduced by using lower level instructions.
-For these purposes, a later iteration of the syntax will provide the feature of user-defined functions.
+\subsection{random}\label{sec:random}
+Since Smart Contracts generally need to be deterministic, s.t.
+the network can reach a consensus about the state of the ledger \cite{chatterjee_probabilistic_2019}, the prevalent workarounds for generating pseudo-random numbers cannot be used to implement the random generators in assertion contracts.
+The scheme explicitly requires as many validators as possible to check distinct elements in the search space.
+Common schemes for obtaining random values, like oracles or using block attributes as seeds \cite{chatterjee_probabilistic_2019}, would provide the same values for all validators.
+Thus, the VM should provide an instruction to generate a ``real'' random value for assertion checking only.
+The instruction should not be available in the normal execution mode, in order to preserve the deterministic behaviour of normal Smart Contracts.
 
-\subsection{random}
-A vital instruction that cannot be expressed with Michelson's current instruction set (state of protocol 008 Edo \cite{tezos_docs}) is the generation of a random value of certain types.
-Since smart contracts need to be deterministic, s.t.
-the network can reach a consensus about the state of the ledger \cite{chatterjee_probabilistic_2019}, the prevalent workarounds for generating pseudo-random numbers cannot be used for assertion checking.
-Distributed assertion checking explicitly requires as many validators as possible to generate a unique value, whereas common schemes for randomness, like oracles or using block attributes as seeds \cite{chatterjee_probabilistic_2019}, will provide the same values for all validators.\\
-\lstref{lst:rand_type} specifies the selection and typing rule of a new instruction \texttt{rand}, which consumes an offset and a positive range from the stack and pushes a randomly generated integer to the top.
-This instruction, of course, can also be provided for other data types, such as \texttt{nat}, \texttt{string} or \texttt{mutez}.
+\lstref{lst:rand_type} specifies the typing and selection rule of a new instruction \texttt{random} for integers (such an instruction can also be provided for other data types, such as \texttt{nat}, \texttt{string} or \texttt{mutez}).
+It consumes an offset and a positive range from the stack and pushes a randomly generated integer to the top.
+The typing rule (line 1) specifies, that the offset should be of type \texttt{integer}, and the range of type \texttt{nat}.
 \lstset{upquote=true}
-\begin{lstlisting}[caption=Selection and typing rules of the integer \texttt{rand} instruction, language=, numbers=none, label=lst:rand_type]
+\begin{lstlisting}[caption=Typing and selection rules of the integer \texttt{random} instruction, language=, showlines=true, label=lst:rand_type]
 :: int : nat: 'A -> int : 'A
-> RAND/ offset : range : S  => int : S
+> RANDOM / offset : range : S  => int : S
 \end{lstlisting}
@@
 Within the Michelson interpreter, the selection of rules is implemented as a huge match case \cite{tezos_repo}.
-If the rule for \texttt{rand} applies, the respective computation in OCaml could look as drafted in \lstref{lst:rand_impl}.
-\begin{lstlisting}[caption=Simplified evaluation of \texttt{rand} in the Michelson interpreter, language=, label=lst:rand_impl]
+If the rule for \texttt{random} applies, the instruction could be computed in OCaml as indicated in \lstref{lst:rand_impl}.
+\begin{lstlisting}[caption=Simplified evaluation of \texttt{random} in the Michelson interpreter, language=, label=lst:rand_impl]
 match (instruction, stack) with
 ...
-| (Rand (offset, (range, rest))) -> 
+| (Random (offset, (range, rest))) ->
    Random.self_init;
    let rand_int = offset + Random.int(range) in
-   return (rand_int, rest)  (* Resulting stack *)
+   return (rand_int, rest)  (* resulting stack *)
 \end{lstlisting}
 
-\subsection{nth}
-An exception for not adding higher level instructions may be the more fundamental operation \texttt{nth} for accessing list elements, as it is used (sometimes more than once, ref.
-\eqref{eq:sorted_v2}) in many use cases.
-Adding an own predefined primitive for this reduces the origination costs of the assertion contract, given that its equivalent in the current instruction set requires the compiler to generate a workaround using iteration, for instance a loop or list iterator.
-As a first approximation, appendix \ref{apx:nth} shows a potential implementation of \texttt{nth} in Liquidity (\lstref{lst:nth_liq}) using a loop, and how the respective Michelson code looks like after compiling the contract with the Liquidity compiler (\lstref{lst:nth_tz}).
-\\
-In case the \texttt{nth} is added as a predefined primitive to Michelson for the type \texttt{'a list}, its selection and typing rules are specified as follows:
+\subsection{nth}\label{sec:nth}
+Michelson currently does not provide any predefined indexed access operators for data types like lists, strings or bytes.
+Accessing a random element of a sequence can, of course, be implemented using low-level instructions.
+However, because such operations are used frequently in many of the given use-cases, adding it as a predefined primitive for some data types might be justifiable.
+This reduces the required code to express the indexing, and thus not only improves the readability of the contract code, but also lowers the costs of the contract origination and execution.
+
+\lstref{lst:nth_type} specifies the typing and selection rules of an instruction \texttt{nth} to access the $n^{th}$ element of a list.
+It consumes a list with elements of type \texttt{'a}, and an index of type \texttt{nat} from the top of the stack.
+After the computation, on top of the resulting stack is an optional value of the element type \texttt{'a}.
+A selection rule (line 2 and 3) is given for each of the two possible result stack patterns.
 \begin{lstlisting}[caption=Selection and type rule of the list \texttt{nth} instruction, language=, label=lst:nth_type]
@@
 \end{lstlisting}
-As Michelson lists are represented with OCamls list type within the VM \cite{tezos_repo}, the computation for \texttt{nth} could look as shown in \lstref{lst:nth_impl}.
+
+Within the VM, Michelson lists are represented with OCaml's list type --- the computation of \texttt{nth} thus simply calls the \texttt{nth} function of the List module, as indicated in \lstref{lst:nth_impl}.
 \begin{lstlisting}[caption=Simplified evaluation of \texttt{nth} in the Michelson interpreter, language=, label=lst:nth_impl]
@@
 
-\section{Orchestration of contract and assertions}
+As stated above, the indexing operation can also be translated to a sequence of already existing instructions.
+Michelson features instructions to execute a loop or iterate over a list, which can be used for such an implementation.
+An exemplary implementation of the operation \texttt{nth} for lists in the high-level language Liquidity is given by \lstref{lst:nth_liq} in appendix \ref{apx:nth}.
+The appendix also contains the corresponding Michelson code after compiling the source with the Liquidity compiler (\lstref{lst:nth_tz}).
+
+\section{Orchestration of contract and assertions}\label{sec:orchestration}
 So far, the assertion and parent contract have been considered separately.
@@
 They, in turn, can also be prone to errors.
-On the other hand, the generated contracts can be tested as a black box using the test frameworks provided by Tezos, which use sandboxed networks to interact with contracts-under-test.
+\todo{remove?}On the other hand, the generated contracts can be tested as a black box using the test frameworks provided by Tezos, which use sandboxed networks to interact with contracts-under-test.
 
@@
 This section demonstrates the implementation of this approach on the basis of Liquidity, hence the corresponding file extension \texttt{.liq}.
+\todo{provide Ligo as alternative -> could be included as package}
 \begin{figure}[h]
@@
 
-\paragraph{Evaluation}
+\paragraph{Evaluation}\todo{rename?}
 This approach takes advantage of the usually more sophisticated high-level language compiler; they may provide options for optimizing generated code and are already thoroughly tested \cite{liq_repo}\cite{ligo_repo}.
@@
 
-\section{Cost analysis}\label{sec:cost_analysis_distributed}
+\section{Cost analysis}\label{sec:cost_analysis_distributed}\todo{rename to evaluation and add some more stuff}
 What remains to be evaluated is the cost of checking a formula with the proposed approach, and how they relate to the costs for a local validation which were analysed in \secref{sec:usecase_cost}.
@@
 
-\section{Representing counterexamples}
+\section{Representing counterexamples}\todo{Move or rename?}
 There still remains an open question concerning the proposed implementation that could be answered in detail within the scope of this thesis - the representation and validation of a counterexamples.

### 2021-04-23 assertions/doc/thesis-bernhardt/chapters/appendix.tex
Own chapt probabilistic model
Revision chpt 5

@@
 The following two versions of the grammar implement the prefix and infix notations for the assertion syntax.
-\todo{Rename mutez}
 
@@
 				 label=lst:nth_liq,
-				 caption=Possible implementation of \texttt{nth} in Liquidity]{listings/nth.liq}
+				 caption=Possible implementation of \texttt{nth} for lists in Liquidity]{listings/nth.liq}
 
@@
 				 label=lst:nth_tz,
-				 caption=\lstref{lst:nth_liq} compiled to Michelson]{listings/nth.tz}
+				 caption=Implementation of \texttt{nth} for lists in Michelson]{listings/nth.tz}
 

### 2021-04-23 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
Revision chpt 5 - monolithic

@@
 So far, the assertion and parent contract have been considered separately.
-However, on the blockchain they have to be orchestrated, s.t.
-the bakers and validators execute the assertion before the actual contract code.
-The orchestration does not only include the linking of assertion and contract code, but also a mechanism to execute an assertion $t$ times depending on the domain space that needs to be checked.
-There are basically two approaches - the assertion and contract code can be assembled into a single monolithic contract, or they can be originated separately as standalone contracts.
-As the strategy has an impact on the compilation process and output, it has to be determined in advance which of the two should be implemented and how.
+However, they have to be orchestrated on-chain, such that the assertion code is either invoked automatically before the parent code is executed, or the assertion code can be invoked directly by the validators.
+Furthermore, the orchestration should include a mechanism to determine and trigger the required number of test runs per validator.
+Depending on the orchestration strategy, the compiler then assembles the assertion and parent code into one or several Smart Contracts.
 
-\subsection{Approach 1: Monolithic contract}
-In the monolithic approach, a new contract is built using both the assertion and parent code as input.
-As is outlined in \figref{fig:monolithic_orchestration_basic}, the assertions can either be appended to the original contract as separate entrypoints or by prepending them to the code of the respective entrypoint.
+This section describes two possible approaches for an orchestration --- a monolithic and a modular approach.
+It also discusses, which of the given architecture is chosen for the implementation of distributed assertion checking, and why.
+
+\subsection{Monolithic orchestration}
+In the monolithic approach, the assertion an parent code are merged into a single Smart Contract.
 This tightly couples and unites the code in one self-contained unit.
+The assertion code can be merged into the parent contract in two different ways.
+As shown in \figref{fig:mono_eps}, the assertions can be appended to the original contract as separate entrypoints.
+Alternatively, the assertion code can by prepended to the code of the respective entrypoint and thus become an integral part of the program (as shown in \figref{fig:mono_insert}).
 \begin{figure}[!htb]
-\subfloat[Appending assertions as separate entrypoints]{\includegraphics[width=0.5\textwidth]{figures/5-offline_tezos/pipeline_output_mono_ep_basic.jpg}}
+\subfloat[Appending assertions as separate entrypoints\label{fig:mono_eps}]{\includegraphics[width=0.5\textwidth]{figures/5-offline_tezos/pipeline_output_mono_ep_basic.jpg}}
 \quad
-\subfloat[Inserting the assertion code into the original entrypoint]{\includegraphics[width=0.5\textwidth]{figures/5-offline_tezos/pipeline_output_mono_basic.jpg}}
-\caption{Approaches for assembling a monolithic contract}
+\subfloat[Inserting the assertion code into the original entrypoint\label{fig:mono_insert}]{\includegraphics[width=0.5\textwidth]{figures/5-offline_tezos/pipeline_output_mono_basic.jpg}}
+\caption{Approaches for the assembly of a monolithic contract}
 \label{fig:monolithic_orchestration_basic}
 \end{figure}
-While the link between assertion and contract code is already given in a), the entrypoint and assertions in b) still need to be coupled, as it is not inherent which entrypoint represents a normal and which the respective assertion.
-For this reason, assertion entrypoints need to have fixed name pattern, s.t.
-it is derivable from the original entrypoint.
-As a proposal, the tag of the assertion is the tag of its parent entrypoint suffixed with a \texttt{\_a}, e.g.
-\texttt{A\_a} for entrypoint \texttt{A}.
-The baker can then execute the contract normally by calling the original entrypoint and prompt the validators to execute the assertion separately.
-\\
-Both approaches, however, do not yet provide any means to have validators execute the assertions $t$ times.
-Since only the contract itself knows how to calculate $t$ (as per the range(s) of the random generator(s)), it cannot be passed to the validators as a parameter to the validation request.
-Instead, the contract itself needs a test run manager which handles this.
-A test run manager can either be implemented as another entrypoint, say \texttt{A\_m}, which then calls \texttt{A\_a} (or \texttt{A} in case of a)) $t$ times as an internal operation.
-Because transactions on Tezos guarantee either total success or total failure \cite{tezos_docs}, the execution is stopped as soon as one of the internal operation fails, i.e.
-detects a counterexample.
-When extending the diagram for a) with the manager, the pipeline output thus look as shown in \figref{fig:monolithic_orchestration}.
-The output for b) is analogue.
+
+In variation (b), the link between the parent code and the respective assertion code is already established --- the assertion is executed automatically when invoking the entrypoint.
+Variation (a), on the other hand, still has to establish a link between the parent and the assertion entrypoint.
+It should be apparent, which of the entrypoints contains the original, and which one its respective assertion code.
+This can be solved by using fixed tag patterns for assertion entrypoints, which can be derived from the original entrypoint tag.
+\figref{fig:mono_eps} proposes the tag suffix ``\texttt{\_a}''.
+When an external transaction invokes such a monolithic contract, the bakers thus execute the contract normally.
+After completion, the baker then requests the validators to invoke the assertion separately.
+External transactions, of course, should only invoke the original entrypoints.
+
+Both variations, however, do not yet provide any means to trigger several test runs per validator.
+Since only the contract itself knows how to calculate the required number of test runs $t$ (as per the range(s) of the random generator(s)), it cannot be passed to the validators as a parameter to the validation request.
+Instead, the contract itself needs to contain a controller to handle this.
+Similar to the assertion code, such a controller can be integrated into the parent entrypoint, or implemented as another separate entrypoint, as shown in \figref{fig:monolithic_orchestration}.
+Instead of invoking the assertion entrypoint (\texttt{A\_a}), the validators would then invoke the manager entrypoint (\texttt{A\_c}).
+This entryoint then determines $t$ and invokes the assertion entrypoint (\texttt{A\_a}) $t$ times as an internal operation.
 \begin{figure}[h]
@@
 \end{figure}
-Another possibility is to create a separate manager contract that acts as a proxy, contains the manager code and internally calls the monolithic contract.
-This solution is a hybrid of the monolithic and modular approach.
-The section covering the modular approach describes in more detail how it is implemented.\\
-It's important to realize that neither baker nor validators can differentiate between entrypoints that have an associated assertion and those that do not.
-In order to avoid transaction failures caused by calling assertions that do not exist, the compiler has to add dummy managers for empty assertions that call the actual contract code immediately.
-\lstref{lst:manager} drafts the manager code for entrypoints with and without assertions in pseudocode (assuming a purely monolithic implementation).
-\begin{lstlisting}[label=lst:manager, caption=Implementation of the manager in pseudocode]
-%A (i : int) { ... }
 
-%A_a (i : int) { .. assert (...) }
+As a hybrid solution between a monolithic and a modular approach, the controller can be implemented as a separate Smart Contract, which operates as a proxy.
+This contract is invoked in pace of the monolithic contract, which in turn invokes the original or assertion entrypoints as internal operations.
+The implementation of the modular part can be adopted from \secref{sec:modular}.
 
-%A_m (i : int) {
-	n = compute_n(i)
-	Do m = 1 to n
-		call(self, A_a, i)
-}
+If a developer did not specify an assertion for all entrypoints of the parent contract, invoking their non-existing controller entrypoints would cause a transaction failure.
+To avoid this and thus increase the robustness, the compiler should generate dummy controllers for empty assertions.
+If the monolithic contract is assembled according to \figref{fig:mono_eps}, the dummy controller simply returns unit (i.e, an empty list of internal operations and the unchanged storage).
+For the variation given in \figref{fig:mono_insert}, the controller invokes the original entrypoint exactly once.
 
-%B (j : int) { ... }
+\lstref{lst:mono_liq} implements a monolithic contract in the high-level language Liquidity.
+The contract contains the two parent entrypoints \texttt{A} (line 3) and \texttt{B} (line 21), and provides an assertion entrypoint \texttt{A\_a} (line 5) for \texttt{A}.
+Entrypoint \texttt{B} does not have an associated assertion.
+The compiler generated a controller entrypoint for both parent entrypoints, i.e., \texttt{A\_c} (line 7) and \texttt{B\_c} (line 23).
+Controller \texttt{A\_c} determines the number of test runs in line 8 (the implementation of the formula is omitted here) and creates as many internal operations invoking the assertion entrypoint with the same parameter (lines 9-17).
+These are then run in sequence afterwards.
+Controller \texttt{B\_c}, on the other hand, does not emit any operations and immediately returns.
+This can never fail and thus accepts any input value for the parameter \texttt{i}.
+\lstinputlisting[label=lst:mono_liq, caption=Implementation of a monolithic contract in Liquidity, numbers=left]{listings/monolithic.liq}
 
-%B_m (j : int) { call(self, B, j) }
-\end{lstlisting}
+For the variation of using separate entrypoints for the controllers and assertions, \figref{fig:interaction_monolithic} depicts the interactions of the nodes, validators and Smart Contracts on the blockchain.
+The execution model for distributed assertion checking requires a dedicated execution modus.
+A possible mechanism to activate this modus is using a special transaction type, which is denoted by \texttt{txa(destination, entrypoint, parameter)} in the graphic.
+When an operation, such as a transaction or origination, is injected into a node, it is normally propagated to the network after it has been validated.
+After the injection of a \texttt{txa(1, \%A, parameter)} operation, however, the node broadcasts its derivation \texttt{txa(1, \%A_c, parameter)} to the network, which invokes the controller entrypoint instead.
+If this operation finishes successfully for all validators, hence no counterexample is published on the network after a certain amount of block cycles, the node can finally broadcast the initial operation as a normal transaction to the network.
+In case of an assertion failure, the respective validator broadcasts the counterexample with the generated value to the network to be included in an upcoming block.
+The counterexample is thus validated like a normal transaction.
+As a consequence of the broadcast the counterexample, the initial operation \texttt{txa(1, \%A, parameter)} should be rejected.
+How a counterexample is represented and included on the chain is an unresolved question --- \secref{sec:counterexample} picks this topic up and gives some ideas regarding possible implementations.
 
-\figref{fig:interaction_monolithic} and \ref{fig:interaction_monolithic_managertz} depict the interaction of the baker and validators with the resulting contracts on the blockchain for a variant using a single monolithic contract versus a hybrid solution.
-After calling a contract that includes an assertion, the baker has to keep the transaction in its mempool, a buffer where a node keeps prevalidated transactions not yet included in a block \todo{remove explanation if added to Tezos chapter}.
-Before it can be included, the transaction has to be kept there for a minimum amount of time, s.t.
-the validators have enough time to validate the assertion \todo{refer to blockchain protocol chapter if there is one}.
-The bakers therefore need to execute such transactions in a dedicated ``challenge'' mode, which could be signalled by using a special operation type to call such contracts.
-Operation types in Tezos are, i.a., transactions, originations or endorsements.
-By adding, for instance, a special transaction type (abbreviated by \texttt{txa} in the interaction diagrams), bakers can differentiate between normal transactions and those with assertions.
-\begin{figure}[h]
+% geht nur mit explicit eps. enforce by compiler and txa type
+% protocol design needs to address the execution mode, the handling of assertion failure and how to ensure that either counterexample or normal tx is recorded on the chain.
+
 \centering
-  \includegraphics[width=0.7\textwidth]{figures/5-offline_tezos/interaction_monolithic.jpg}
+  \includegraphics[width=0.7\textwidth]{figures/5-offline_tezos/interaction_monolithic_2}
 	\caption{Interaction with a monolithic contract}
 	\label{fig:interaction_monolithic}
-\end{figure}
-
-\begin{figure}[h]
-\centering
-  \includegraphics[width=0.8\textwidth]{figures/5-offline_tezos/interaction_monolithic_managertz.jpg}
-	\caption{Interaction with a manager and monolithic contract}
-	\label{fig:interaction_monolithic_managertz}
 \end{figure}
@@
 
-\subsection{Approach 2: Modular contracts}\label{sec:modular}
+\subsection{Modular orchestration}\label{sec:modular}
 With the modular approach, the assertion manager and each of the assertions are originated as separate contracts on the blockchain.
@@
 
-\section{Representing counterexamples}\todo{Move or rename?}
+\section{Representing counterexamples}\label{sec:counterexample}
+\todo{Adapt -> counterexample as separate contract?
+failwith returns address and data and validator broadcasts normal tx to this contract?
+is included in block and validated as any other normal tx.
+how to reject C(x) if A(C, x,y) is on the chain?}
+
 There still remains an open question concerning the proposed implementation that could be answered in detail within the scope of this thesis - the representation and validation of a counterexamples.

### 2021-04-24 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
Revision monolithic

@@
 When an operation, such as a transaction or origination, is injected into a node, it is normally propagated to the network after it has been validated.
-After the injection of a \texttt{txa(1, \%A, parameter)} operation, however, the node broadcasts its derivation \texttt{txa(1, \%A_c, parameter)} to the network, which invokes the controller entrypoint instead.
+After the injection of a \texttt{txa(1, \%A, parameter)} operation, however, the node broadcasts its derivation \texttt{txa(1, \%A\_c, parameter)} to the network, which invokes the controller entrypoint instead.
 If this operation finishes successfully for all validators, hence no counterexample is published on the network after a certain amount of block cycles, the node can finally broadcast the initial operation as a normal transaction to the network.
@@
 
-% geht nur mit explicit eps. enforce by compiler and txa type
-% protocol design needs to address the execution mode, the handling of assertion failure and how to ensure that either counterexample or normal tx is recorded on the chain.
-
+\begin{figure}
 \centering
@@
 
-After prevalidating a transaction in the challenge mode, the baker then sends a request to the network to check the associated assertion.
-The request contains the address of the monolithic contract or manager, the operation hash (oph) of the prevalidated transaction, the derived entrypoint tag of the assertion and the parameter.
-The operation hash is used to relate a counterexample to the respective transaction.
-Upon receiving such a request, the validators call the assertion manager; what type of operation is used for is an open question for the protocol design.
-For efficiency, at most the test runs detecting a counterexample should be recorded on the blockchain, which would not be the case if validators use standard transactions.
-What has been left out so far in the offline design is the representation of a counterexample.
-\secref{} briefly discusses this as an open question and follow-up of this thesis \todo{secref}.
+This orchestration scheme only works as described when using explicit entrypoint tags for the contract invocations.
+On the one hand, calling entrypoints implicitly by wrapping the parameter in the respective sum type constructors causes a type mismatch for the controller and assertion entrypoints.
+\lstref{lst:mono} shows the parameter type of the Michelson implementation corresponding to the contract given in \lstref{lst:mono_liq} --- entrypoint \texttt{A} can be invoked implicitly with parameter value \texttt{Left 4}.
+The respective assertion entrypoint \texttt{A\_a} expects the value as \texttt{Right (Right (Left 4))} and the controller \texttt{A\_c} as \texttt{Right (Right (Right (Left 4)))}.
+\\
+On the other hand, the explicit tags encode the link between production, controller and assertion code --- omitting them would dissolve all references between them.
+Explicit entrypoints in the parameter type declaration of the contract can be enforced by the compiler.
+A specification of an explicit entrypoint in the contract invocation can be enforced by the \texttt{txa} operation type.
+\lstinputlisting[label=lst:mono, language=Michelson, caption=Skeleton of a monolithic contract in Michelson, numbers=left]{listings/monolithic.tz}
 
-\subsubsection{Evaluation of the monolithic approach}
+This thesis does not go into more detail about how the described execution model for a monolithic orchestration is designed and implemented in the blockchain protocol.
+What needs to be considered in the protocol design is the separate execution mode, possibly a dedicated transaction type as proposed above, the derivation of a transaction which attempts to find a counterexample, the handling of assertion failures and the exclusive acceptance of either the parameter (and thus the transaction) or a counterexample.
+
+\subsubsection{Evaluation}
 The presented implementations of the monolithic approach each have strengths and weaknesses.
 Generally, they all share a pivotal disadvantage - they require a modification of the parent contract.
-This not only complicates the compilation process by requiring a decompilation of the parent code and an interweaving of the assertion code, but it also restricts the integration of assertions to contracts that have not yet been originated on the blockchain.
-\lstref{lst:mono} shows the skeleton of a monolithic contract that results from the given parent and assertion contract; both the parameter type and the branching of the code body have to be adapted.
-Another problem are contract invocations using the default entrypoint: firstly, the derivation of the entrypoint for the assertion becomes considerably more complex, as no explicit tag is given.
-Secondly, the parameter cannot be passed unmodified to the assertion, because the parameter types in respect to the default entry point do not match.
-For instance, invoking the default entrypoint of \texttt{example\_monolithic.tz} (\lstref{lst:mono}) with parameter \texttt{Left 4} calls \texttt{A}, but the respective assertion \texttt{A\_a} expects the value as \texttt{Left (Left 4)}.
-\\
-Due to the tight coupling of parent and assertion code, this approach is also inflexible, since adaptions to either part require a recompilation and new origination of the whole code.
-\lstinputlisting[label=lst:mono, caption=Skeleton of a monolithic contract in Michelson, numbers=left]{listings/monolithic.tz}
+This complicates the compilation process substantially and precludes the integration of assertions to contracts which have already been deployed to the blockchain.
+\lstref{lst:mono} shows how the parameter type and branching within the code body have to be adapted compared to the original parent contract in \lstref{lst:mono_parent}.
+Since the monolithic assembly result in deeper parameter and code nestings, the code becomes less readable overall.
+\lstinputlisting[label=lst:mono_parent, language=Michelson, caption=Skeleton of the parent contract in Michelson, numbers=left]{listings/monolithic_parent.tz}
 
-The distinct advantages and disadvantages of each combination of given implementation approaches are described briefly in the following matrix in \tabref{tab:mono_eval}.
-\begin{table}[h]
-	\centering
-	\newcommand{\tabitem}{~~\llap{\textbullet}~~}
-	\caption{Advantages and disadvantages of monolithic implementations}
-	\label{tab:mono_eval}
-	\subfloat[Monolithic w/ manager and assertion entrypoints] {
-		\centering
-		\begin{tabular}{ | p{0.5\linewidth} | p{0.5\linewidth} |}
-		\hline
-		\thead{Advantages} & \thead{Disadvantages} \\ \hline
-		\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-		\item Contract and assertion can be called separately $\rightarrow$ parent code is only executed once
-		\end{itemize} &
-		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-		\item More complex compilation; adds 1-2 entrypoints per native entrypoint
-		\item Less readability
-		\end{itemize} \\ \hline
-		\end{tabular}
-	}
+Another shortcoming, which applies to the implementation using separate entrypoints for controller and assertion, is the missing support of implicit entrypoint invocations.
+Even though the previously mentioned safety measures can prevent transactions failures, this still poses a restriction in the interaction with Smart Contracts.
 
-	\subfloat[Monolithic w/ manager entrypoints and prepended assertion] {
-		\centering
-		\begin{tabular}{ | p{0.5\linewidth} | p{0.5\linewidth} |}
-		\hline
-		\thead{Advantages} & \thead{Disadvantages} \\ \hline
-		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-		\item Bypassing the assertion is not possible
-		\end{itemize} &
-		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-		\item Cost inefficient - validators execute the assertion + code $t$ times
-		\item Also only works with explicit entrypoint tags
-		\end{itemize} \\ \hline
-		\end{tabular}
-	}
+Due to the tight coupling of parent and assertion code, this approach is also inflexible.
+Adaptions to either the assertion or the parent contract require a complete recompilation and origination of the monolithic contract.
+The hybrid solution breaks some of the tight coupling, as a new version of the controller contract can be originated independently of the monolithic contract.
 
-	\subfloat[Hybrid w/ manager and assertion entrypoints] {
-		\centering
-		\begin{tabular}{ | p{0.5\linewidth} | p{0.5\linewidth} |}
-		\hline
-		\thead{Advantages} & \thead{Disadvantages} \\ \hline
-		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-		\item Contract and assertion can be called separately
-		\item Modularity $\rightarrow$ manager contract can be adapted independently
-		\item Readability
-		\end{itemize} &
-		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-		\item Higher initial origination costs due to more boilerplate code
-		\end{itemize} \\ \hline
-		\end{tabular}
-	}
-
-	\subfloat[Hybrid w/ manager entrypoints and prepended assertion] {
-		\centering
-		\begin{tabular}{ | p{0.5\linewidth} | p{0.5\linewidth} |}
-		\hline
-		\thead{Advantages} & \thead{Disadvantages} \\ \hline
-		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-		\item Bypassing the assertion is not possible
-		\item Modularity
-		\item Readability
-		\end{itemize} &
-		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-		\item Cost inefficient - validators execute the assertion + code $t$ times
-		\item Higher initial origination costs due to more boilerplate code
-		\end{itemize} \\ \hline
-		\end{tabular}
-	}
-\end{table}
+Besides these disadvantages, the monolithic approach has some distinct advantages.
+If controllers and assertions are implemented as separate entrypoints, they can be invoked independently --- this means, that the validators do not have to run the production code while checking the assertion.
+Conversely, the assertion code is not rerun if the parameter is valid and the transaction is broadcast to the network.
+This reduces the transaction cost for the user, as well as the overall footprint of the transaction on the network.
+If the assertion (and possibly controller) code is integrated into the parent entrypoint, this separation is not possible; however, the inseparableness the code in return avoids any bypassing of the assertion.
 

### 2021-04-24 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
revision monolithic

@@
 This tightly couples and unites the code in one self-contained unit.
-The assertion code can be merged into the parent contract in two different ways.
-As shown in \figref{fig:mono_eps}, the assertions can be appended to the original contract as separate entrypoints.
-Alternatively, the assertion code can by prepended to the code of the respective entrypoint and thus become an integral part of the program (as shown in \figref{fig:mono_insert}).
-\begin{figure}[!htb]
-\subfloat[Appending assertions as separate entrypoints\label{fig:mono_eps}]{\includegraphics[width=0.5\textwidth]{figures/5-offline_tezos/pipeline_output_mono_ep_basic.jpg}}
-\quad
-\subfloat[Inserting the assertion code into the original entrypoint\label{fig:mono_insert}]{\includegraphics[width=0.5\textwidth]{figures/5-offline_tezos/pipeline_output_mono_basic.jpg}}
-\caption{Approaches for the assembly of a monolithic contract}
-\label{fig:monolithic_orchestration_basic}
+As shown in \figref{fig:mono_eps}, the assertions are appended to the original contract as separate entrypoints.
+Since the \texttt{random} instruction is only available in the execution mode for assertion checking, the assertion code cannot be directly prepended to the respective production code.
+Otherwise, transactions invoking such an entrypoint could not be included into blocks, as these are validated in the normal execution mode.
+\begin{figure}[h]
+\centering
+  \includegraphics[width=0.5\textwidth]{figures/5-offline_tezos/pipeline_output_mono_ep_basic.jpg}
+	\caption{Monolithic assembly - appending assertions as separate entrypoints}
+	\label{fig:mono_eps}
 \end{figure}
 
-In variation (b), the link between the parent code and the respective assertion code is already established --- the assertion is executed automatically when invoking the entrypoint.
-Variation (a), on the other hand, still has to establish a link between the parent and the assertion entrypoint.
-It should be apparent, which of the entrypoints contains the original, and which one its respective assertion code.
-This can be solved by using fixed tag patterns for assertion entrypoints, which can be derived from the original entrypoint tag.
+The interface of the contract should make apparent, which of the entrypoints contain production, and which contain their respective assertion code.
+This can be solved by using fixed tag patterns for assertion entrypoints, which can be derived from the production entrypoint tag.
 \figref{fig:mono_eps} proposes the tag suffix ``\texttt{\_a}''.
@@
 After completion, the baker then requests the validators to invoke the assertion separately.
-External transactions, of course, should only invoke the original entrypoints.
+External transactions, of course, should only invoke the production entrypoints.
 
-Both variations, however, do not yet provide any means to trigger several test runs per validator.
-Since only the contract itself knows how to calculate the required number of test runs $t$ (as per the range(s) of the random generator(s)), it cannot be passed to the validators as a parameter to the validation request.
-Instead, the contract itself needs to contain a controller to handle this.
-Similar to the assertion code, such a controller can be integrated into the parent entrypoint, or implemented as another separate entrypoint, as shown in \figref{fig:monolithic_orchestration}.
-Instead of invoking the assertion entrypoint (\texttt{A\_a}), the validators would then invoke the manager entrypoint (\texttt{A\_c}).
-This entryoint then determines $t$ and invokes the assertion entrypoint (\texttt{A\_a}) $t$ times as an internal operation.
+The current version of the monolithic contract, however, do not yet provide any means to trigger several test runs per validator.
+Since the required number of test runs $t$ can only be determined at runtime, it cannot be passed to the validators as a parameter to the validation request.
+Instead, the contract itself should contain a controller to handle this.
+Similar to the assertion code, such a controller can be appended as another separate entrypoint, as shown in \figref{fig:monolithic_orchestration}.
+Instead of invoking the assertion entrypoint (\texttt{A\_a}), the validators would then invoke the controller entrypoint (\texttt{A\_c}), which determines $t$ and invokes (\texttt{A\_a}) $t$ times as an internal operation.
 \begin{figure}[h]
 \centering
-  \includegraphics[width=0.5\textwidth]{figures/5-offline_tezos/pipeline_output_mono_ep.jpg}
-	\caption{Monolithic assembly with separate entrypoints for manager and assertion}
+  \includegraphics[width=0.5\textwidth]{figures/5-offline_tezos/pipeline_output_mono_ep}
+	\caption{Monolithic assembly with separate entrypoints for cotroller and assertion}
 	\label{fig:monolithic_orchestration}
@@
 If a developer did not specify an assertion for all entrypoints of the parent contract, invoking their non-existing controller entrypoints would cause a transaction failure.
-To avoid this and thus increase the robustness, the compiler should generate dummy controllers for empty assertions.
-If the monolithic contract is assembled according to \figref{fig:mono_eps}, the dummy controller simply returns unit (i.e, an empty list of internal operations and the unchanged storage).
-For the variation given in \figref{fig:mono_insert}, the controller invokes the original entrypoint exactly once.
+In order to avoid this and increase the robustness, the compiler should generate dummy controllers for empty assertions, which simply return unit (i.e, an empty list of internal operations and the unchanged storage).
 
@@
 
-For the variation of using separate entrypoints for the controllers and assertions, \figref{fig:interaction_monolithic} depicts the interactions of the nodes, validators and Smart Contracts on the blockchain.
+\figref{fig:interaction_monolithic} depicts the resulting interactions of the nodes, validators and monolithic Smart Contracts on the blockchain.
 The execution model for distributed assertion checking requires a dedicated execution modus.
@@
 The presented implementations of the monolithic approach each have strengths and weaknesses.
-Generally, they all share a pivotal disadvantage - they require a modification of the parent contract.
+Generally, they share a pivotal disadvantage - they require a modification of the parent contract.
 This complicates the compilation process substantially and precludes the integration of assertions to contracts which have already been deployed to the blockchain.
@@
 
-Another shortcoming, which applies to the implementation using separate entrypoints for controller and assertion, is the missing support of implicit entrypoint invocations.
-Even though the previously mentioned safety measures can prevent transactions failures, this still poses a restriction in the interaction with Smart Contracts.
+Another shortcoming is the missing support of implicit entrypoint invocations.
+Even though the previously mentioned measures can prevent transactions failures, this still poses a restriction in the interaction with Smart Contracts.
 
@@
 Besides these disadvantages, the monolithic approach has some distinct advantages.
-If controllers and assertions are implemented as separate entrypoints, they can be invoked independently --- this means, that the validators do not have to run the production code while checking the assertion.
+The production and controller entrypoints they can be invoked independently, which means that the validators do not have to run the production code while checking the assertion.
 Conversely, the assertion code is not rerun if the parameter is valid and the transaction is broadcast to the network.
-This reduces the transaction cost for the user, as well as the overall footprint of the transaction on the network.
-If the assertion (and possibly controller) code is integrated into the parent entrypoint, this separation is not possible; however, the inseparableness the code in return avoids any bypassing of the assertion.
+This reduces the transaction cost for the user, as well as the overall footprint of the transaction in the network.
 

### 2021-04-25 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
Revision type check + semantic analysis

@@
 If a failure occurs, the whole sequence fails and all changes up to the point of failure are reverted.
+Within a sequence, an operation can thus have one of the following result types:
+\begin{itemize}
+\item \textbf{Applied} --- the operation was successful
+\item \textbf{Failed} --- the operation failed
+\item \textbf{Skipped} --- the operation was in sequence after a failed operation
+\item \textbf{Backtracked} --- reverted operation due to a failed operation further along in the sequence
+\end{itemize}
 
@@
 \subsection{Monolithic orchestration}
-In the monolithic approach, the assertion an parent code are merged into a single Smart Contract.
+In the monolithic approach, the assertion and parent code are merged into a single Smart Contract.
 This tightly couples and unites the code in one self-contained unit.
@@
 The interface of the contract should make apparent, which of the entrypoints contain production, and which contain their respective assertion code.
-This can be solved by using fixed tag patterns for assertion entrypoints, which can be derived from the production entrypoint tag.
+This can be solved by using fixed tag patterns for assertion entrypoints, which can be derived from the parent entrypoint tag.
 \figref{fig:mono_eps} proposes the tag suffix ``\texttt{\_a}''.
-When an external transaction invokes such a monolithic contract, the bakers thus execute the contract normally.
-After completion, the baker then requests the validators to invoke the assertion separately.
-External transactions, of course, should only invoke the production entrypoints.
+External transactions should only invoke the production entrypoints.
 
-The current version of the monolithic contract, however, do not yet provide any means to trigger several test runs per validator.
+The monolithic contract in \figref{fig:mono_eps}, however, do not yet provide any means to trigger several test runs per validator.
 Since the required number of test runs $t$ can only be determined at runtime, it cannot be passed to the validators as a parameter to the validation request.
@@
   \includegraphics[width=0.5\textwidth]{figures/5-offline_tezos/pipeline_output_mono_ep}
-	\caption{Monolithic assembly with separate entrypoints for cotroller and assertion}
+	\caption{Monolithic assembly with separate entrypoints for controller and assertion}
 	\label{fig:monolithic_orchestration}
@@
 As a hybrid solution between a monolithic and a modular approach, the controller can be implemented as a separate Smart Contract, which operates as a proxy.
-This contract is invoked in pace of the monolithic contract, which in turn invokes the original or assertion entrypoints as internal operations.
+This contract is invoked in place of the monolithic contract, which in turn invokes the original or assertion entrypoints as internal operations.
 The implementation of the modular part can be adopted from \secref{sec:modular}.
@@
 The compiler generated a controller entrypoint for both parent entrypoints, i.e., \texttt{A\_c} (line 7) and \texttt{B\_c} (line 23).
-Controller \texttt{A\_c} determines the number of test runs in line 8 (the implementation of the formula is omitted here) and creates as many internal operations invoking the assertion entrypoint with the same parameter (lines 9-17).
+Controller \texttt{A\_c} determines the number of test runs in line 8 (the implementation of the formula is omitted here) and creates $t$ internal operations, which invoke the assertion entrypoint with the same parameter (lines 9-17).
 These are then run in sequence afterwards.
 Controller \texttt{B\_c}, on the other hand, does not emit any operations and immediately returns.
-This can never fail and thus accepts any input value for the parameter \texttt{i}.
+This code can never fail and thus accepts any input value for the parameter.
 \lstinputlisting[label=lst:mono_liq, caption=Implementation of a monolithic contract in Liquidity, numbers=left]{listings/monolithic.liq}
@@
 When an operation, such as a transaction or origination, is injected into a node, it is normally propagated to the network after it has been validated.
-After the injection of a \texttt{txa(1, \%A, parameter)} operation, however, the node broadcasts its derivation \texttt{txa(1, \%A\_c, parameter)} to the network, which invokes the controller entrypoint instead.
+After the injection of \texttt{txa(1, \%A, parameter)}, however, the node broadcasts its derivation \texttt{txa(1, \%A\_c, parameter)} to the network, which invokes the controller entrypoint instead.
 If this operation finishes successfully for all validators, hence no counterexample is published on the network after a certain amount of block cycles, the node can finally broadcast the initial operation as a normal transaction to the network.
@@
 The counterexample is thus validated like a normal transaction.
-As a consequence of the broadcast the counterexample, the initial operation \texttt{txa(1, \%A, parameter)} should be rejected.
+As a consequence of the broadcasted counterexample, the initial operation \texttt{txa(1, \%A, parameter)} should be rejected.
 How a counterexample is represented and included on the chain is an unresolved question --- \secref{sec:counterexample} picks this topic up and gives some ideas regarding possible implementations.
@@
 \lstref{lst:mono} shows the parameter type of the Michelson implementation corresponding to the contract given in \lstref{lst:mono_liq} --- entrypoint \texttt{A} can be invoked implicitly with parameter value \texttt{Left 4}.
-The respective assertion entrypoint \texttt{A\_a} expects the value as \texttt{Right (Right (Left 4))} and the controller \texttt{A\_c} as \texttt{Right (Right (Right (Left 4)))}.
-\\
+The respective assertion entrypoint \texttt{A\_a} expects the value as \texttt{Right (Right (Left 4))} and the controller \texttt{A\_c} as \texttt{Right (Right (Right (Left 4)))}.\\
 On the other hand, the explicit tags encode the link between production, controller and assertion code --- omitting them would dissolve all references between them.
+Hence, implicit entrypoint invocation cannot be supported in the execution mode of assertions.
 Explicit entrypoints in the parameter type declaration of the contract can be enforced by the compiler.
@@
 This thesis does not go into more detail about how the described execution model for a monolithic orchestration is designed and implemented in the blockchain protocol.
-What needs to be considered in the protocol design is the separate execution mode, possibly a dedicated transaction type as proposed above, the derivation of a transaction which attempts to find a counterexample, the handling of assertion failures and the exclusive acceptance of either the parameter (and thus the transaction) or a counterexample.
+What needs to be considered in future work concerning the protocol design is the separate execution mode, possibly a dedicated transaction type as proposed above, the derivation of a transaction which attempts to find a counterexample, the handling of assertion failures and the exclusive acceptance of either the parameter (and thus the transaction) or a counterexample.
 
@@
 \lstref{lst:mono} shows how the parameter type and branching within the code body have to be adapted compared to the original parent contract in \lstref{lst:mono_parent}.
-Since the monolithic assembly result in deeper parameter and code nestings, the code becomes less readable overall.
+Since the monolithic assembly results in deeper parameter and code nestings, the code becomes less readable overall.
 \lstinputlisting[label=lst:mono_parent, language=Michelson, caption=Skeleton of the parent contract in Michelson, numbers=left]{listings/monolithic_parent.tz}
@@
 Besides these disadvantages, the monolithic approach has some distinct advantages.
-The production and controller entrypoints they can be invoked independently, which means that the validators do not have to run the production code while checking the assertion.
+The production and controller entrypoints can be invoked independently, which means that the validators do not have to run the production code while checking the assertion.
 Conversely, the assertion code is not rerun if the parameter is valid and the transaction is broadcast to the network.
@@
 \subsection{Modular orchestration}\label{sec:modular}
-With the modular approach, the assertion manager and each of the assertions are originated as separate contracts on the blockchain.
-The manager mirrors the interface of the parent contract, while each assertion each only has a single entrypoint which expects the raw parameter type.
-Due to the ``outsourcing'' of the assertion code, the parent contract remains pure and does not have to be modified.
-Similar to the hybrid solution from the last section, the manager calls the respective assertion contract $t$ times as an internal operation before calling the actual contract.
-In the case of empty assertions, it calls the parent contract immediately.
-Correspondingly, the pipeline outputs 1-$m$ contracts, where $m$ is the amount of entrypoints with an associated assertion, as depicted in \figref{fig:modular_assembly}.
+In the modular approach, the controller and each of the assertions are originated as separate contracts on the blockchain.
+The controller mirrors the interface of the parent contract, while each assertion has only a single entrypoint expecting the raw parameter type.
+By keeping the assertion code separate, the parent contract remains pure and does not have to be modified.
+Similar to the hybrid solution mentioned in the monolithic approach, the controller calls the respective assertion contract $t$ times as an internal operation, before invoking the parent contract with operation $t+1$.
+In the case of empty assertions, the parent contract is invoked immediately.
+Correspondingly, the toolchain returns $m + 1$ contracts, where $m$ is the number of assertions in the input.
+The assembly and output of the toolchain is outlined in \figref{fig:modular_assembly}.
 \begin{figure}[h]
 \centering
-  \includegraphics[width=0.6\textwidth]{figures/5-offline_tezos/pipeline_output_modular.jpg}
+  \includegraphics[width=0.6\textwidth]{figures/5-offline_tezos/pipeline_output_modular.png}
 	\caption{Modular assembly of assertion and manager code}
@@
 
-In order to link the separate contracts to each other, the manager needs to know the addresses of the other contracts, which ultimately entails a fixed origination order.
-The independent assertion and parent contract(s) have been originated first, so that their addresses can be passed to the manager as initial storage values.
-If the storage is structured as a map from a unique identifier to an address, the entrypoints of the manager can then look up the address with its assigned identifier.
-The assignment of identifiers to entrypoints is hard-wired during the compilation, as is shown in the pseudocode for the manager contract in \lstref{lst:manager_modular}.
-The corresponding initial storage for the given contract is the mapping \texttt{{0: <addr parent>; 1: <addr A\_a>; 2: <addr B\_a}}.
-\begin{lstlisting}[label=lst:manager_modular, caption=Implementation of the modular manager in pseudocode]
-storage (map int address);
+In order to link the separate contracts to each other, the controller needs to know the addresses of the other contracts.
+As a result, the origination order is fixed ---- the assertion and parent contracts must be originated first, so that their addresses can be passed to the controller as initial storage values.
+A proposed structure of the storage is a map from a unique identifier to an address.
+The entrypoints of the controller can then look up the address with their assigned identifier.
+The assignment of identifiers to entrypoints is hard-wired during the compilation, as is demonstrated in the rudimentary and simplified Liquidity implementation of a controller contract in \lstref{lst:manager_modular}.
+The corresponding storage initiation is the map $\lbrace 0 \rightarrow \langle \text{addr parent} \rangle; 1 \rightarrow \langle \text{addr assertion} \rangle \rbrace$ .
+The hard-wired identifiers are used in lines 5 and 6 to retrieve the addresses from the storage.
+\lstinputlisting[label=lst:manager_modular, caption=Implementation of the modular controller in simplified Liquidity, language=Michelson, numbers=left]{listings/controller_basic.liq}
 
-%A (i : int) {
-	n = compute_n(i)
-	Do m = 1 to n:
-		call(storage.get(1), i)
-	call(storage.get(0), A, i)
-}
-
-%B (j : int) {
-	n = compute_n(j)
-	Do m = 1 to n:
-		call(storage.get(2), j)
-	call(storage.get(0), B, j)
-}
-\end{lstlisting}
-
-The interaction with the contracts in the modular approach is shown in \figref{fig:interaction_modular}.
-Even though the transactions shown in the diagram state an explicit entrypoint tag, contracts can, of course, also be called through \texttt{\%default}.
-In that case, the parameter passed with the internal operations to \texttt{A\_a.tz} is not equivalent, but the raw parameter value.
+The interaction with the modular contracts is shown in \figref{fig:interaction_modular}.
+Even though the transactions shown in the diagram state an explicit entrypoint tag, the scheme supports implicit entrypoint invocations.
+When invoking the assertion contract, the parameter is passed as the raw parameter value.
+The execution model is similar to the model for the monolithic approach.
+Because the controller mirrors the interface of the parent contract, the \texttt{txa} operation can be broadcast to the network directly --- a derivation to a distinct transaction to find the counterexamples is not necessary.
+If none of the validators publish a counterexample, the initial transaction is broadcasted to the network as a normal operation to be included in a block.
+Since this transaction will inevitably rerun the assertion code in the normal execution mode (as it invokes the controller), the VM needs to handle \texttt{random} instructions in normal transactions such that they do not cause the operation sequence to fail (e.g., by marking the internal operations as skipped, or by introducing a dedicated result type for this case).
 \begin{figure}[h]
 \centering
-  \includegraphics[width=0.9\textwidth]{figures/5-offline_tezos/interaction_modular.jpg}
-	\caption{Interaction with a modular contract}
+  \includegraphics[width=0.9\textwidth]{figures/5-offline_tezos/interaction_modular.png}
+	\caption{Interaction with modular contracts}
 	\label{fig:interaction_modular}
@@
 
-\subsubsection{Evaluation of the modular approach}
-This approach fixes the two central problems of the monolithic approach: by mirroring the interface of the parent contract, the parameters passed to the manager contract can be forwarded directly to the parent contract, regardless of whether the default or an explicit entrypoint was called.
-As sum type parameters are stripped to the raw values inside the code block (ref.
-\lstref{lst:mono}), they can be passed to the assertion contract without further ado.
+\subsubsection{Evaluation}
+This approach resolves the two crucial problems of the monolithic approach: by mirroring the interface of the parent contract, the parameters passed to the manager contract can be forwarded directly to the parent contract, regardless of whether the default or an explicit entrypoint was called.
 Furthermore, the parent contract does not need to be modified, which leads to a much simpler compilation process and allows to extend already originated contracts with assertions.
-Due to its modularity, adaptions to either contract do not entail the recompilation and origination of all components.
-The manager is the only component with tight coupling, thus adaptions regarding the manager do not affect any other component.
-Adaptions to single assertions or the parent affect themselves plus the manager.
-In order to optimize this and break the tight coupling, one could be inclined to add a setter entrypoint to the manager (as a sort of dependency injection).
-This, however, would break the mirroring of the parent contract and is thus not possible without annulling one of the key strengths of the design.\\
-The approach essentially has to weaknesses: on the one hand, the assertion and the parent cannot be called separately, as they are linked together by the manager.
-As a result, both the baker and validators execute the assertion, as well as the parent contract, which increases the cost of the contract execution.
-On the other hand, it exposes a security vulnerability, given that assertions can be bypassed by calling the parent contract directly with unevaluated parameters.
-This iteration of the design
-does not demand to close this vulnerability, hence possible solutions are not discussed in this thesis.
+Due to its modularity, adaptions to either contract do not necessarily require a recompilation and origination of all components, as the controller is the only component with tight coupling.
+In order to optimize this and break the tight coupling, one could be inclined to add a setter entrypoint to the controller (as a sort of dependency injection).
+This, however, would break the mirroring of the parent contract and is thus not possible without annulling one of the key strengths of the design.
+
+The approach essentially has two weaknesses: firstly, the assertion and the parent cannot be called separately.
+As a result, the production code is run by every validator while searching for counterexamples and when validating a block containing the accepted transaction.
+This increases the transaction cost for the user and requires a higher computational effort by the whole network.
+of the contract execution.
+Secondly, it exposes a security vulnerability, given that assertions can be bypassed by calling the parent contract directly.
+This iteration of the design does not demand to close this vulnerability, hence possible solutions are not discussed in this thesis.
 
 \section{Backend implementation}\label{sec:backend_impl}
-\todo{Shorten a bit - overview already given in chpt intro}
-The Tezos backend of the pipeline comprises of the three stages semantic check, type check and compilation.
-During the semantic check, the common AST is cast to a Tezos-specific AST type.
-If the assertion contains any data types or operations not supported in Michelson, the assertion contract is rejected.
-Since the subsequent stages are less straight forward, they are explained in more detail in the following.
+The following sections describe the tasks and implementations of the pipeline stages of the toolchain backend.
 \begin{figure}[h]
@@
 
+\subsection{Interaction with Tezos nodes}
+Some stages of the backend have to interact with a Tezos node, e.g.
+to retrieve information from the blockchain.
+For this, the backend uses the Tezos client libraries.
+The command line interface of the toolchain provides options for configuring the host address and port of the RPC interface to connect to a specific node.
+This can be either a local or public node.
+By default, the toolchain tries to connect to a local node on the default port.
+
+\subsection{Semantic analysis}
+After the transformation, the frontend passes a list of ASTs to the backend.
+Because the frontend was designed to be generic, they may contain type, operations or expressions which are not supported by the target language.
+Therefore, the semantic check should reject any assertions which can not be translated to Michelson (more precisely, the whole assertion contract is rejected).
+
+As an additional restriction, quantifiers should only bind variables of primitive data types.
+As the majority of use-cases seem to require quantification over numerical values, the current implementation of the semantic check only accepts predicate variables of type \texttt{int} and \texttt{nat}.
+Future iterations of the toolchain and protocol may add support for other primitive types, such as \texttt{string} or \texttt{bytes}.
+
+Semantic rules imposed by Michelson do not have to be checked explicitly by the toolchain --- the RPC interface of Tezos nodes provides a function to parse and type check Michelson programs, which can be used to verify the correctness of the compilation result.
+
+If the semantic check was successful, the module returns the assertions as a list of Tezos-specific ASTs. \lstref{lst:tezos_ast_type} shows the toplevel definition of this AST type.
+\begin{lstlisting}[label=lst:tezos_ast_type, language=, numbers=none, caption=Toplevel Tezos-specific AST type definition in OCaml]
+type tezos_ast =
+  {entrypoint : string * pattern; body : assertion}
+\end{lstlisting}
+As Tezos is currently the only target, the type differs only slightly from the generic type.
+If the assertion does not specify an explicit entrypoint tag, the optional value is replaced with Tezos' notation for the default entrypoint.
+The subtree types for the parameter pattern and the assertion remain equivalent to the generic types.
+
 \subsection{Type check}\label{sec:typecheck}
-The task of the type checker is to map the assertions from the given file to the respective entrypoints of the parent contract.
-To this end, the parameter types have to be compared and matched against each other in order to find a correct assignment.
-The type checker either reads the code of the parent contract from a given file or retrieves the code from a given address on the blockchain.
-It must be ensured that the created mapping is injective and unambiguous, i.e., each assertion matches exactly one entrypoint and no entrypoint is covered by more than one assertion.\\
-As explained in \secref{sec:tezos}, entrypoints can be selected by calling the default entrypoint and wrapping the parameter into the respective union constructors.
-Alternatively, they can be called explicitly using their tag and passing the parameter as raw value.
-The same applies for the assertions - by omitting the tag, the parameter type must be declared in respect to the default entrypoint type.
-If the assertion states an explicit tag, it may declare the raw parameter type.
-The tags do not necessarily have to be identical with the tags of the parent contract; in some cases, they may be chosen differently for documentation or for readability purposes.
-However, the tags can and should be used to resolve ambiguity in the mapping between assertions and entrypoints, that is if several entrypoints share the same input type.
-Ambiguity can also be caused by the fact that entrypoints can be sub-entrypoints of others, thus assertions overlap if a separate assertion is declared for both super- and sub-entrypoint.
-This is resolved by detecting overlapping assertions during the type check and rejecting assertion contracts where appropriate.
-\\
-As an example, consider a Michelson contract with five entrypoints (including the \texttt{\%default}):
-\begin{lstlisting}[numbers=none, language=Michelson]
-parameter (or (int %A) (or %BC (int %B) (int %C)))
+Given a list of Tezos-specific ASTs, the task of the type checker is to link each AST to the respective entrypoint of the parent contract.
+This stage can thus be alternatively referred to as the linker.
+The linking is needed by the compiler for type inference and to correctly assemble the controller contract.
+As a simple example, the linker should correctly assign the ASTs of the first assertion in \texttt{Example.tza} (\lstref{lst:linker_assertion}) to entrypoint A, and the second assertion to entrypoint B of \texttt{Example.tz} ( \lstref{lst:linker_parent}).
+
+\vspace{\baselineskip}
+\noindent
+\begin{minipage}{.45\textwidth}
+\begin{lstlisting}[label=lst:linker_parent, numbers=none, language=Michelson, caption=Example.tz]
+parameter (or (int %A)
+              (string %B));
+...
 \end{lstlisting}
-The following assertion contract for the given PC contains some valid and some invalid assertions:
-\begin{lstlisting}[language=Assertion]
-(assertion %A (i : int) ...)             (* valid *)
-(assertion %D (i : int) ...)             (* invalid *)
-(assertion (right (left (i : int)) ...)  (* valid *)
-(assertion %BC (x : (or int int)) ...)   (* invalid *)
+\end{minipage}\hfill
+\begin{minipage}{.5\textwidth}
+\begin{lstlisting}[label=lst:linker_assertion, numbers=none, language=Assertion, caption=Example.tza]
+(entrypoint %A (i : int) ...)
+(entrypoint %B (s : string) ...)
 \end{lstlisting}
-Due to its tag, the fist assertion can be assigned unambiguously to entrypoint A, whereas for the second it is not apparent whether it should be assigned to entrypoint B or C.
-Since the tag is omitted in the third assertion, the parameter type is given in respect to the default entrypoint and is assigned to B.
-The last assertion is invalid because it is overlapping with the previous assertion, which was already assigned to entrypoint B.
+\end{minipage}
+\vspace{\baselineskip}
+
+Because explicit entrypoint tags are optional in Michelson contracts, the linking is primarily done by type matching between the declared parameter types in the parent and the assertions.
+Tags, if specified, are only considered if type matching does not result in an unambiguous assignment.
+The linking fails, if an assertion cannot be matched to any parent entrypoint or several assertions match the same entrypoint, i.e., if no injective, non-surjective mapping was found.
+
+As a first step, the linker retrieves and parses the parameter type of the parent contract.
+The parent contract is provided by the user as a file, a blockchain address, or a raw string.
+In case the contract is given as an address, the code is retrieved (as a string) from the blockchain.
+Parsing and extracting the list of entrypoints with their parameter type from the typed Michelson AST is handled by the Tezos libraries.
+The parameter pattern of each assertion AST is then compared recursively to the entrypoint types, until a match has been found --- this entrypoint is then blocked for other assertions.
+
+As explained in \secref{sec:tezos}, entrypoints can be invoked implicitly by wrapping the parameter into the respective union type constructors.
+Alternatively, they can be called explicitly by stating an entrypoint tag and passing the raw parameter value.
+The same applies for the specification of assertions - when omitting the tag, the parameter pattern must be declared in respect to the default entrypoint.
+If the assertion states an explicit tag, it may declare a pattern of the raw parameter type.
+\lstref{lst:impl_expl} shows two valid assertion specifications for entrypoint A of \lstref{lst:linker_parent} --- the first uses an explicit and the second an implicit declaration of the parameter pattern.
+\begin{lstlisting}[language=Assertion, numbers=none, caption=Explicit and implicit assertion specification, label=lst:impl_expl]
+(entrypoint %A (i : int) ...)
+(entrypoint (left (i : int)) ...)
+\end{lstlisting}
+
+The tags given in the assertion specification do not necessarily have to be identical with the tags of the parent contract (if the parent states explicit tags); in some cases, they may be chosen differently for documentation or for readability purposes.
+However, the tags can and should be used to resolve ambiguity in the mapping between assertions and entrypoints.
+\lstref{lst:ambiguity_assertion} provides four examples of assertions, which cannot be assigned unambiguously to an entrypoint of the contract given in \lstref{lst:ambiguity_parent}.
+The assertions in lines 1, 2 and 3 specify anonymous or named wildcards as parameter pattern, which matches any parameter type.
+Since none of them specify the explicit tag \texttt{A} or \texttt{B}, the linker cannot know to which entrypoint the assertions belong to.
+The assertion in line 4 specifies the parameter type, but as both entrypoints have the same raw parameter type and none of the tags match, this assertion is also not linkable.
+In all four cases, providing the tag \texttt{A} or \texttt{B} resolves the ambiguity.
+
+\vspace{\baselineskip}
+\noindent
+\begin{minipage}{.4\textwidth}
+\begin{lstlisting}[label=lst:ambiguity_parent, numbers=none, language=Michelson, caption=Example2.tz]
+parameter (or (int %A)
+              (int %B));
+...
+\end{lstlisting}
+\end{minipage}\hfill
+\begin{minipage}{.5\textwidth}
+\begin{lstlisting}[label=lst:ambiguity_assertion, language=Assertion, caption=Ambiguous assertions for Example2.tz]
+(entrypoint _ ...)
+(entrypoint %C _ ...)
+(entrypoint %D i ...)
+(entrypoint %E (i : int)
+\end{lstlisting}
+\end{minipage}
+\vspace{\baselineskip}
+
+Another type of ambiguity can be caused by the fact that entrypoints can be sub-entrypoints of others.
+As an example, consider the parameter type \texttt{(or (int \%A) (or \%BC (int \%B) (int \%C)))}.
+Entrypoints \texttt{B} and \texttt{C} are sub-entrypoints of \texttt{BC} --- invoking \texttt{BC} will inevitably result in an invocation of either \texttt{B} or \texttt{C}, depending on the parameter value.
+Thus, assertions may ``overlap'', if a separate assertion is declared for a super- and a sub-entrypoint and result in two assertion specifications for the same entrypoint.
+Hence, the linker needs to detect overlapping assertions and reject assertion contracts where appropriate.
+
+In summary, the linker rejects any assertion contracts containing ambiguous, duplicate, overlapping and mismatching assertions.
+In case of failure, the problem is pointed out user.
+If each assertion could be linked to exactly one entrypoint, the mapping from entrypoint to assertion is returned.
+As entrypoints can be anonymous, the mapping represents the entrypoints by the constructor nesting of their parameters.
+The resulting mapping for \texttt{Example.tz} and \texttt{Example.tza}, for instance, is \\
+\texttt{\{ Left \textrightarrow <AST assertion A>; Right \textrightarrow <AST assertion B>\} }.
 
@@
 \subsubsection{Direct compilation}\label{sec:direct}
+\todo{verification by local node -> type check}
 With the direct approach, the compiler generates Michelson code and hence code for a stack machine.
@@
 \todo{Make clear that we only engage validators on Tezos (not all nodes)}
-\todo{What happens if a validator has multiple endorsing rights?}
+\todo{What happens if a validator has multiple endorsing rights? -> open issues section?}

### 2021-04-25 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
add missing orchestration decision
Revision compiler

@@
 
-\subsubsection{High-level languages}
+\subsubsection{High-level languages}\label{sec:languages}
 Michelson is a compilation target for various high-level languages that provide a more user-friendly and intuitive way of writing Smart Contracts.
@@
 
+Even though the monolithic approach is expected to be more efficient in terms of cost and network load, the following sections are based on the modular approach as the proposed architecture, due to its simplicity and flexibility.
+
 \section{Backend implementation}\label{sec:backend_impl}
@@
 \subsection{Compiler}\label{sec:compiler}
-The transformed and type checked assertion AST needs to be retargeted to Michelson code according to the orchestration scheme.
-Since the modular approach is less complex to implement and avoids having to decompile the parent code, this section describes a compiler that assembles the assertion and contract code according to \figref{fig:modular_assembly}.
-The target language of the compiler of the pipeline can either be Michelson directly, or another high-level language which supports Michelson as a target.
-\secref{sec:tezos} lists some examples of such languages.
-The chosen language then serves as an intermediate representation (IR) of the assertion and manager code, which is ultimately compiled to Michelson by the compiler of the language.
-After specifying the steps of the compilation in a general way, the compilation approaches are described and discussed in more detail in \secref{sec:direct} and \ref{sec:IR}.
+The compiler finally translates the transformed and type checked assertion ASTs to Michelson contracts according to the modular orchestration scheme.
+Assertion and parent contract are thus assembled as depicted in \figref{fig:modular_assembly}.
+The compilation stage was not implemented within the scope of this thesis, but the following subsections describe the compilation procedures for generating the assertion and controller contracts.
+Furthermore, this section discusses the possibility to compile to a high-level language as an intermediate representation.
+
+With Michelson as the target language, the compiler has to generate code for a stack machine.
+After compilation, the Michelson programs can be validated for correctness by the Tezos node.
+This will intercept any assertions containing type errors.
+After sanity-checking the programs, the compiler returns the target code for the controller and assertion contracts.
+As an additional output, it should return a piece of template code for the correct storage initialization of the controller, where the user can fill in the blockchain addresses of the other modules.
 
 \subsubsection{Compilation of the assertion contracts}
-Since the assertions are independent of each other and the manager code, each of them can be compiled in isolation to a separate Michelson program.
-The generated code of the assertion body and the parameter type can be plugged into a template that already contains the necessary boilerplate code for a contract.
-% type inference from patterns
-% handling of patterns like cons
+The assertion ASTs are independent and can thus be compiled in isolation to separate Michelson contracts.
+Because they only have a single entrypoint, the parameter type corresponds to the raw parameter type of the parent entrypoint.
+If the parameter pattern in the assertion does not contain any wildcards, the parameter type can be derived directly from the pattern.
+Otherwise, the compiler has to infer the type from the parent contract.
 
-\subsubsection{Compilation of the manager contract}
-Given that the manager contract mirrors the parent contract and assuming that the proposal for the storage type from \lstref{lst:manager_modular} is adopted, the type declarations can be translated directly to the target language.
-Algorithm \ref{alg:compile_manager} shows the outline of a simplified algorithm that builds the code body recursively.
-For simplicity, entrypoints that take a sum type as parameter (e.g.
-\texttt{(or \%AB int int)} are not considered in the algorithm.
-However, in the actual compiler implementation they need to be taken care of.
+If the pattern excludes any special values of the data type (e.g., \texttt{cons head tail} excludes empty lists), the generated code should reflect this.
+Excluded values should never cause the assertion to fail.
+In the example of \texttt{cons}, the generated code should thus contain the branching shown in \lstref{lst:cons}.
+The branch in line 1 is executed if the list contains at least one element, and should contain the assertion code.
+If the list is empty, the branch in line 2 should simply return successfully.
+\begin{lstlisting}[language=Michelson, label=lst:cons, caption=Exclusion of empty lists in the assertion]
+IF_CONS ( <assertion body> )
+        ( <return ([], ())>)
+\end{lstlisting}
+% Translation from quantifiers to random generators!
+
+The generated code of the assertion body and the parameter type can be plugged into a template, which contains the necessary boilerplate code for a contract.
+Such a template is shown in \lstref{lst:contract_templ} --- the placeholders \texttt{<?>} mark the locations where the individual code is inserted.
+Lines 3-5 prepare the stack, s.t.
+the parameter and storage are the two top elements.
+The lines below the placeholder for the body clean up the stack and leave it according to calling convention, i.e., the program returns an empty list of internal operations and the unit storage.
+\lstinputlisting[label=lst:contract_templ, language=Michelson, caption=Template code for assertion contracts in Michelson, numbers=left]{listings/assertion_template.tz}
+
+\subsubsection{Compilation of the controller contract}
+The generation of the \texttt{parameter} and \texttt{storage} primitives is trivial.
+Given that the controller acts as a proxy, the parameter type can be copied from the parent contract.
+Assuming that the proposal for the storage type from \lstref{lst:manager_modular} is adopted, the storage type is always the same, i.e., \texttt{(map int address)}.
+The code body is generated recursively based on the parameter type.
+It consists of two types of entrypoints, which either act as a direct gateway to the parent contract, or trigger an assertion check before invoking the parent.
+
+\paragraph{Gateway entrypoints}
+The code of gateway entrypoints only has to execute two steps; first, the address of the parent contract is read from the storage.
+It then creates an internal operation to this address, passing along the original parameter and funds.
+Assuming the parent address is always stored under the same key, e.g.
+with id 0, such gateways can be inserted as fixed boilerplate code.
+
+\paragraph{Assertion entrypoints}
+If the entrypoint should trigger an assertion, the compiler has to generated code executing the following steps:
+\begin{enumerate}
+\itemsep-0.5em
+\item Read the addresses from the assertion and parent contract from storage
+\item Calculate $t$
+\item Compile a list of $t$ internal operations invoking the assertion with the raw parameter
+\item Create an internal operation calling the parent contract, passing the original parameter and funds
+\item Return a list of all operations and the unchanged storage
+\end{enumerate}
+\secref{sec:prob_threshold} stated a formula to determine the total number $t_{total}$ of required test runs for a given probability threshold $c$ and the size of the search space $n$.
+From $t_{total}$, the number of test runs $t$ per validator can be calculated according to \eqref{eq:t_validator}.
+Since $n$ can only be obtained at runtime, the compiler needs to derive a formula to determine it from the ranges of the random generators.
+\secref{sec:sample_space} already gave some examples of this.
+The threshold $c$, on the other hand, must be given as parameter to the compiler. Therefore, the command line interface of the toolchain should provide an option to set the threshold.
+
+\paragraph{Algorithm}
+Algorithm \ref{alg:compile_manager} shows the outline of a simplified algorithm, which builds the code body of the controller.
+It recursively iterates over the parameter type and builds the body by nesting \texttt{IF\_LEFT} instructions (cf.
+\lstref{lst:entrypoints}).
+Within the entrypoint branches, the compiler either generates gateway or assertion triggering code, based on the mapping given by the linker.
+
 \begin{algorithm}
-\caption{Simplified recursive algorithm for building the manager contract}\label{alg:compile_manager}
-	\begin{algorithmic}[0]
-	\State global storage = \{0: <parent>\} \Comment{Stores the mapping of ids to entrypoints}
-	\State global i = 1 \Comment{Counter generating unique ids}
-	\Function{compile}{parent parameter type}
+\caption{Simplified recursive algorithm for building the controller}\label{alg:compile_manager}
+	\begin{algorithmic}[1]
+	\State global storage = \{0: <parent>\}
+	\State global i = 1
+	\Function{compile\_controller}{parameter type}
 	\If{ty = Or(l,r)}
-	\State code\_left = compile(l)
-	\State code\_right = compile(r)
+	\State code\_left = "IF\_LEFT {" + compile(l) + "}"
+	\State code\_right = "{" + compile(r) + "}"
 	\State \Return code\_left + code\_right
 	\Else
-	\If{assertion exists for this entrypoint}
-	\State code = generate\_loop(ty, i)
+	\If{entrypoint has assertion}
+	\State code = generate\_assertion\_trigger(parameter type, i, assertion)
 	\State storage.add(i++, entrypoint tag)
 	\Else
-	\State code = generate\_forward(ty)
+	\State code = generate\_gateway()
 	\EndIf
@@
 
-The function \texttt{generate\_loop} generates code that does the following:
-\begin{enumerate}
-\item Retrieve the assertion contract and parent contract addresses from storage
-\item Calculate $t$
-\item Build a list of $t$ internal operations that call the assertion contract
-\item Return the list of emitted operations and the unchanged storage
-\end{enumerate}
-% calculate size of search space? -> need to derive a formula from range constraints
-By passing the next id $i$ to the function, the access to the storage can be hard-wired into the generated code.
-The address of the parent contract is assumed to always be stored with the id 0.
-\secref{sec:prob_threshold} stated a formula for calculating $t_{total}$ with the parameters $n$, the size of the search space, and the probability threshold $c$.
-While $n$ can be calculated from the ranges of the random generator(s), $c$ must be given as parameter to the compiler through the CLI.
-After $t_{total}$ has been computed, the upper bound of the loop is calculated according to \eqref{eq:t_validator}.
-% remove -> refer to equation in previous chapter
-\begin{equation}
-t = \lceil t_{total} / \#validators \rceil
-\end{equation}
+During this recursion, the compiler also builds the address map for the storage, such that the entrypoints can look up the address of the assertion and parent contracts during runtime.
+To this end, it keeps the counter \texttt{i} to create unique IDs for each entrypoint with an assertion --- this ID is then hard-wired into the storage access within this entrypoint.
+The address of the parent contract is always stored under ID 0.
 
-\texttt{generate\_forward} can be generated from a simple template with the id as the only variant and only consists of  an access to the storage and the emission of an internal operation.
+After compilation, this map is translated to a template for a Michelson value and returned to the user together with the contract code.
+Because the addresses are not known at the time of compilation, the values should be descriptive place-holders, s.t.
+the user can replace them with the corresponding addresses.
+The completed Michelson value should then be passed to the origination as the initial storage.
+As an example, the compilation of the controller contract for \texttt{Example.tz} and \texttt{Example.tza} in Listings \ref{lst:linker_parent} and \ref{lst:linker_assertion} could return the following template:\\ \texttt{(Elt 0 <addr parent>; Elt 1 <addr A\_a>; Elt 2 <addr B\_a>)}.
 
-\subsubsection{Output}
-Besides the target code for the manager and assertion contracts, the compiler should return a piece of template code for the correct storage initialization of the manager.
-Since this code is passed to the origination operation, it must be in Michelson regardless of the compilation target language.
-The placeholders or accompanying info should be descriptive enough, s.t.
-the user can plug in the corresponding addresses after the origination of the parent and assertion contracts.
-For the example manager contract given in \secref{sec:modular}, the corresponding text output could be\\
-\texttt{(Elt 0 <addr parent>; Elt 1 <addr A\_a>; Elt 2 <addr B\_a>)}.
+In order to provide a detailed example, appendix \ref{apx:controller_michelson} contains the full Michelson code of a controller contract with one gateway and one assertion entrypoint.
+The code was generated by the Liquidity compiler from the source given in appendix \ref{apx:controller_liq}, which provides a more compact and readable representation of the program logic.
 
-\subsubsection{Direct compilation}\label{sec:direct}
-\todo{verification by local node -> type check}
-With the direct approach, the compiler generates Michelson code and hence code for a stack machine.
-Based on the simplicity of stack machines and the assumption that it does not need to generate optimal code, the compiler is expected to be simple \cite{cs5641}\cite{ferr_compiler}\cite{wiki:stack_machine}.
-As already indicate in the general part, the resulting contracts contain repeating structures and patterns for each input, which can be exploited by using template code during compilation.
-After compilation, the Michelson programs can be sanity-checked by type checking them using the provided Tezos libraries.
+\subsubsection{Compiling to an intermediate representation}\label{sec:IR}
+Instead of generating Michelson code directly, the compiler could also generate code in one of the high-level languages listed in \secref{sec:languages}.
+They all provide compilers targeting Michelson, and can thus serve as an intermediate representation (IR) of the contract code.
 
-\paragraph{Assertion contracts}
-\lstref{lst:contract_templ} shows a possible template for an assertion contract --- the placeholder \texttt{<?>} marks the locations where the individual code is inserted.
-Lines 3-5 prepare the stack, s.t.
-the parameter and storage are the two top elements.
-The lines below the placeholder for the body clean up the stack and leave it according to calling convention, i.e., the program returns an empty list of internal operations and the unit storage.
-\lstinputlisting[label=lst:contract_templ, language=Michelson, caption=Template code for assertion contracts in Michelson, numbers=left]{listings/assertion_template.tz}
+It depends on the language, how the compiler of the IR can be integrated into the toolchain.
+The Ligo project builds their compiler into a \texttt{dune}\footnote{dune \cite{dune} is a build system for OCaml} library, which can be imported directly into the code base of the toolchain.
+This keeps the pipeline coherent and would allow to output Michelson contracts without any intermediate steps.
+If the compiler cannot be embedded directly into the toolchain (as is the case with Liquidity), the output of the would have to be compiled manually to Michelson in a separate step, as depicted in \figref{fig:pipeline_liq}.
 
-\paragraph{Manager contract}
-The generation of the \texttt{parameter} and \texttt{storage} primitives is trivial --- the parameter type can be carried over directly from the parent contract, whereas the storage type is a constant (\texttt{(map int address)}).
-Based on the algorithm given previously, the code body is generated by nesting \texttt{IF\_LEFT} instructions recursively (cf.
-\lstref{lst:entrypoints}).
-The adapted algorithm is given in Algorithm \ref{alg:compile_manager_direct}.
-\begin{algorithm}
-\caption{Modification of algorithm \ref{alg:compile_manager} for direct compilation}\label{alg:compile_manager_direct}
-	\begin{algorithmic}[0]
-	\State ...
-	\Function{compile}{parent parameter type}
-	\If{ty = Or(l,r)} \Comment{Compile sum types to a branching}
-	\State code\_left = "IF\_LEFT {" + compile(l) + "}"
-	\State code\_right = "{" + compile(r) + "}"
-	\State \Return code\_left + code\_right
-	\EndIf
-	\State ...
-	\EndFunction
-	\end{algorithmic}
-\end{algorithm}
-
-Owing to Michelson being a low-level language, the templates for the functions \texttt{generate\_loop} and \texttt{generate\_forward} go beyond the scope of this subsection.
-In order to provide an idea of how the generated code could look like, appendix \ref{apx:manager_michelson} contains two example contracts, one of which contains manager code for a non-empty and the other one for an empty assertion.
-The code was generated by the Liquidity compiler from two contracts written in Liquidity, as this provides a more compact and readable representation of the program logic.
-The corresponding source code can be found in \secref{sec:IR}.
-
-\paragraph{Evaluation}
-Compiling to Michelson directly is beneficial due of several reasons --- the pipeline stays streamlined and outputs the final contracts ready for origination.
-It does not introduce dependencies to external tools and their support for new protocol versions of Tezos.
-Besides, the new instructions only have to be added to Tezos' protocol code, whereas using external tools and languages would need to be patched as well in order to support them.
-\\
-When it comes to verifying the compiler and integration testing of the pipeline, however, the low-level output causes more complexity than a high-level output.
-Due to the extend and restricted readability of non-trivial Michelson programs, their correctness is not always apparent in an instant.
-Tests can, on the one hand, compare the output with verified target contracts for a range of inputs, which requires a lot of Michelson code written by hand for each input.
-They, in turn, can also be prone to errors.
-\todo{remove?}On the other hand, the generated contracts can be tested as a black box using the test frameworks provided by Tezos, which use sandboxed networks to interact with contracts-under-test.
-
-\subsubsection{Compiling to an IR}\label{sec:IR}
-Instead of generating Michelson code directly, the compiler could also generate code in one of the high-level languages that provide a compiler with Michelson as a target.
-The output of the pipeline is then passed to this compiler in order to retrieve the final contracts.
-If the toolchain of the intermediate language doesn't provide a programmatic interface, the pipeline thus has to be extended with a separate step of procedure, as shown in \figref{fig:pipeline_liq}.
-This section demonstrates the implementation of this approach on the basis of Liquidity, hence the corresponding file extension \texttt{.liq}.
-\todo{provide Ligo as alternative -> could be included as package}
 \begin{figure}[h]
@@
 
-\paragraph{Assertion contracts}
-\lstref{lst:contract_templ_liq} shows the equivalent of the assertion contract template given in \lstref{lst:contract_templ}.
-Since the Liquidity compiler takes care of the handling of the stack, it basically consists only of a storage type declaration, a function signature and the ``empty'' return type.
-\lstinputlisting[label=lst:contract_templ_liq, language=Michelson, caption=Template code for assertion contracts in Liquidity, numbers=left]{listings/assertion_template.liq}
+\paragraph{Comparison to direct compilation}
+This approach takes advantage of the usually more sophisticated high-level language compiler; they may provide options for optimizing generated code and are already thoroughly tested.
+In contrast to large and obscure Michelson programs, the output is more comprehensible and thus easier to test and verify.
 
-\paragraph{Manager contract}
-Liquidity contracts are a list of OCaml-like functions that take a parameter and a storage.
-Instead of declaring the contract parameter type globally and nesting the code for each entrypoint, each entrypoint thus is declared as a separate function with a local parameter type.
-During compilation, the contract parameter type will then be composed according to the order of functions.
-Due to Algorithm \ref{alg:compile_manager} being left recursive, the output will automatically retain the correct order of entrypoints.
-In fact, the only adaptions necessary are the output of the two functions \texttt{generate\_loop} and \texttt{generate\_forward}, which should not only generate the code body, but return a coherent function.
-The function \texttt{entrypointA} in \lstref{lst:manager_templ_liq} is an example of such a function for an empty assertion.
-The non-empty version of the manager code can be found in appendix \ref{apx:apx:manager_liq}.
-As already noted, extracting a pure template for the code exceeds the scope of this section.
-\lstinputlisting[label=lst:manager_templ_liq, language=Michelson, caption=Manager code in Liquidity for an entrypoint with an empty assertion, numbers=left]{listings/manager_forward.liq}
+The crucial disadvantage of the IR approach is the introduction of an external dependency.
+The compiler of the respective language has to be extended with the \texttt{random} instruction as well, which requires forking the project.
+Furthermore, one has to rely on continuous support of new protocol versions in the root project and integrate the updates into the own code base regularly.
+To avoid such dependencies and increased effort in version management, this approach is not pursued in the development of the toolchain.
 
-\paragraph{Evaluation}\todo{rename?}
-This approach takes advantage of the usually more sophisticated high-level language compiler; they may provide options for optimizing generated code and are already thoroughly tested \cite{liq_repo}\cite{ligo_repo}.
-In contract to low-level code, the output of the pipeline compiler is easier to be verified, as it can be read like, for instance, an OCaml program.
-Providing target contracts for integration tests can be done much more efficiently and more reliable.
-\\
-Besides the amenities of these compilers, this approach has a crucial disadvantage of introducing an external dependency.
-The compiler of the respective language has to be extended with the additional Michelson instructions as well, requiring a fork of the project.
-Furthermore one has to rely on continuous support of new protocol versions in the root project and integrate the updates into the own codebase.
-All things considered, the effort for extending both Michelson and the compiler of the IR, followed by a continuous effort of version management, may outweigh the benefits of this approach.
-
-When returning to the orchestration approach of generating a monolithic contract, using Liquidity as an IR would allow to decompile the parent contract using the decompiler of its toolchain.
-Since the Liquidity compiler handles the composition of the contract parameter type and the code nesting, the assertion function simply have to be appended to the parent code, which significantly decreases the compilation complexity.
+However, a realistic use-case for using Liquidity as an IR is the implementation of the monolithic orchestration scheme.
+In Liquidity, each entrypoint is declared as a function expecting a parameter and the current storage.
+During compilation, the contract parameter type and code branching is composed according to the order of functions.
+For instance, the entrypoint declarations in \lstref{lst:liq_eps} are compiled to the contract parameter type \texttt{(or (int \%A) (int \%B))} and two branches in the code body.
+\begin{lstlisting}[numbers=none, label=lst:liq_eps, caption=Entrypoint declarations in Liquidity]
+let%entry A (a : int) storage = ...
+let%entry B (b : int) storage = ...
+\end{lstlisting}
+As the Liquidity project provides a decompiler to translate Michelson contracts into Liquidity programs, the compiled assertion functions can simply be appended to the decompiled parent contract.
+This outsources most of the compilation complexity to the Liquidity compiler.
 

### 2021-04-25 assertions/doc/thesis-bernhardt/chapters/appendix.tex
Revision compiler

@@
 
-\chapter{Manager contract code in Liquidity}\label{apx:manager_liq}
-\lstinputlisting[label=lst:manager_templ_liq, language=Michelson, caption=Manager code in Liquidity for an entrypoint with a non-empty assertion, numbers=left]{listings/manager_loop.liq}
+\chapter{Controller contract code in Liquidity}\label{apx:controller_liq}
+\lstinputlisting[label=lst:manager_templ_liq, language=Michelson, caption=Controller code in Liquidity]{listings/controller.liq}
 
-\chapter{Manager contract code in Michelson}\label{apx:manager_michelson}
+\chapter{Controller contract code in Michelson}\label{apx:controller_michelson}
 \lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
@@
 				 language=Michelson,
-				 label=lst:manager_michelson_loop,
-				 caption=Manager code in Michelson for an entrypoint with a non-empty assertion (wrapped in contract boilerplate code)]{listings/manager_loop.tz}
-
-\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
-				 backgroundcolor=\color{cverbbg},
-				 linewidth=14cm,
-				 xleftmargin=0.5cm,
-				 frame=lr,
-				 framesep=8pt,
-				 framerule=0pt,
-				 captionpos=b,
-				 numbers=none,
-				 language=Michelson,
-				 label=lst:manager_michelson_forward,
-				 caption=Manager code in Michelson for an entrypoint with an empty assertion (wrapped in contract boilerplate code)]{listings/manager_forward.tz}
+				 label=lst:controller_michelson,
+				 caption=Controller code in Michelson]{listings/controller.tz}
 

### 2021-04-26 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
Finish revision chpt 5

@@
 For baking, a random roll is selected for each block level and the rights are assigned to its owner.
-The block produced by that baker is signed by a fixed number of endorsers (32 as of protocol 007 Delphi), which also have been assigned endorsing rights for this block level by a random selection of rolls.
+The block produced by that baker is signed by a fixed number of endorsers\footnote{For consistency, endorsers are referred to as ``validators'' in this chapter} (32 as of protocol 007 Delphi), which also have been assigned endorsing rights for this block level by a random selection of rolls.
 Since participants can stake more than one roll, they may be assigned several endorsement slots at the same block level.
@@
 \item \textbf{Reading costs} --- apply for reading the contract code and storage from the blockchain and, on top of a base cost, depend on the amount of bytes read
-\item \textbf{Deserialization costs} --- depend on the Micheline expression and the size of the byte sequence
+\item \textbf{Deserialization costs} --- depend on the Micheline expression and the size of the byte sequence. Apply lazily, thus the deserialization of each value only has to be paid once
 \item \textbf{Parsing costs} --- are composed of three types of costs:
@@
 \item \textbf{Serialization costs} --- apply when serializing Micheline nodes to byte sequences and depend on the expression and its size
-\item \textbf{Writing costs} --- apply when writing to the internal database and depend on the amount of bytes. A base fee applies for each additional byte of storage.
+\item \textbf{Writing costs} --- apply when writing to the internal database and depend on the amount of bytes. A base gas fee is burned (destroyed) for each additional byte of storage.
 \end{enumerate}
@@
 
-\subsection{Monolithic orchestration}
+\subsection{Monolithic orchestration}\label{sec:monolithic}
 In the monolithic approach, the assertion and parent code are merged into a single Smart Contract.
@@
 \end{lstlisting}
-% Translation from quantifiers to random generators!
 
@@
 
-\section{Cost analysis}\label{sec:cost_analysis_distributed}\todo{rename to evaluation and add some more stuff}
-What remains to be evaluated is the cost of checking a formula with the proposed approach, and how they relate to the costs for a local validation which were analysed in \secref{sec:usecase_cost}.
-The previous analysis defined \eqref{eq:gas_transaction} to calculate the gas consumption of a transaction, including the emitted operations.
-For each validator, the transaction calling the manager contract emits $t+1$ internal operations, whose gas consumptions are also dependent of the input parameter.
-Based on the $t+1$ additional base, as well as deserialization and parsing costs of the parameter alone, it can be concluded that the total gas consumption of $n$ total distributed test runs is higher than the cost of checking $n$ values locally.
-\\
-The differential can be measured by implementing the orchestration scheme for the two dummy contracts given in \secref{sec:usecase_cost}.
-Appendix \ref{apx} contains the code of all three components for each of them.
-In order to measure the gas consumption for a comparable amount of executions as during the initial cost analysis, the probability threshold $c$ is set to $\frac{1}{e}$, s.t.
-that the necessary number of total test runs is $n$.
-However, it needs to be pointed out, that the actual number of test runs executed can only be a multiple of the number of validators (cf.
-\eqref{eq:t_validator}).
-\figref{fig:cost_distributed} shows the reported gas consumption per validator, i.e., a $32^{th}$ of the total cost for checking an assertion for the given threshold.
-Due to \eqref{eq:t_validator}, the cost function approximates a step function.
+\section{Cost analysis and evaluation}\label{sec:cost_analysis_distributed}
+In this section, the costs of checking a formula with the proposed approach and implementation for distributed assertion checking are evaluated.
+\secref{sec:usecase_cost} already determined the cost for a local validation as a benchmark.
+It stated \eqref{eq:gas_transaction} to calculate the gas consumption of a transaction, including internal operations.
+It identified the gas consumption of deserialization, data parsing and interpretation as growing factors, which depend on the size of the input parameter.
+
+According to the orchestration scheme, each validator executes $t+2$ operations with the same input parameter $p$.
+Since deserialization costs are applied lazily, they have to be paid only once for the parameter and the assertion contract code.
+In addition to the interpretation cost, the reading, parsing and base costs have to be paid for each internal operation.
+\begin{align}\label{eq:gas_validator}
+\begin{split}
+GasConsumed_{validator}(p) > \quad t * (&base\, gas \\
+&+ gasParsing(p) \\
+&+ gasRead(C_{assertion}) \\
+&+ gasParsing(C_{assertion}) \\
+&+ gasInterpretation(C_{assertion})) \\
+\end{split}
+\end{align}
+Based on the resulting inequality in \eqref{eq:gas_validator}, which specifies the costs incurred by each internal operation to the assertion contract as a basis of the total gas consumption per validator, it can be concluded that the overall gas consumption of the distributed validation is higher than in case of a local validation.
+
+The distributed approach was benchmarked by implementing the orchestration scheme for the two minimal dummy contracts \texttt{Foo} and \texttt{Bar} given in \secref{sec:usecase_cost}.
+Appendix \ref{apx:foobar_distributed} contains the Michelson code for the controller, assertion and parent contracts.
+In order to preserve comparability between the local and the distributed implementation, the controller contracts were configured with a probability threshold $c = \frac{1}{e}$, s.t.
+that the necessary number of test runs is equal to the sizes of the search spaces.
+\figref{fig:cost_distributed} shows the reported gas consumption per validator on the test network Delphinet.
+Since the effective number of test runs is always a multiple of 32, the cost function approximates a step function.
+
 \begin{figure}[t]
@@
 \includegraphics[width=0.9\linewidth]{figures/5-offline_tezos/cost_analysis}
-\caption{Gas consumption per validator of transactions calling \texttt{Foo} and \texttt{Bar} for increasing input sizes}
+\caption{Gas consumption per validator for different input sizes}
 \label{fig:cost_distributed}
 \end{figure}
-The results show that the cost incurred by a single validator checking $t$ values is already considerably higher than by checking the property locally.
-Moreover, the cost-performance ratio is even worse, as the confidence that the property is indeed satisfied is only around 63\% with the given parameters.
-In conclusion to these results, it may be worth looking into some alternative approaches.
-\secref{sec:alt_random} already mentions the possibility to coordinate the validators for a systematic iteration of the search space.
-Alternatively, the proposed orchestration could be modified, s.t.
-the manager and assertion code are not implemented as separate contracts, but with one single contract.
-Instead of $(t+1)$ internal operations, one only has to pay for one internal operation that calls the parent contract, hence avoiding the base, deserialization and parsing costs for each test run.
-Similar to the monolithic orchestration approach, this increases the complexity of the compilation process.\\ Another idea worth exploring is the adaption of the blockchain protocol to avoid user costs for assertion checking, similar to the regular validation of blocks \cite{tezos_docs}.
-Instead of being paid by the user in gas, validators could be given a reward for checking an assertion, or a particularly high one for finding a counterexample.
 
-\todo{Cheaper for the network if not all validators have to execute the whole local check!
-however, placing these costs on the users will cause them to use the local approach -> users need incentives to use it too!
--> blockchain protocol could/should solve this!
-(e.g.
-use rewards instead of costs)}
-\todo{Every transaction is processed at every node in the network,which limits throughput}
+The results show, that the cost incurred by a single validator, checking a subset of a search space with size $n$, is already considerably higher than a complete validation in a local approach (cf.
+\figref{sec:usecase_cost}).
+In the case of the list parameter (contract \texttt{Bar}), the gas consumption even increases exponentially due to the multiplied reading and parsing costs.
+Moreover, the probability of accepting an invalid parameter with the given configuration is 37\% in the worst case, which results in a bad cost-performance ratio.
 
-\section{Representing counterexamples}\label{sec:counterexample}
-\todo{Adapt -> counterexample as separate contract?
-failwith returns address and data and validator broadcasts normal tx to this contract?
-is included in block and validated as any other normal tx.
-how to reject C(x) if A(C, x,y) is on the chain?}
+In conclusion to these results, the proposed implementation of the distributed scheme has to be evaluated as inefficient and unable to achieve an improvement regarding the scalability of applications on Tezos.
+However, distributed assertion checking is nonetheless a promising approach to achieve an improvement, as it has the potential to not only lower the transaction costs for the user, but also to reduce the computational footprint of the transaction within the network.
+A prerequisite is lowering the gas consumption per validator.
+This thesis already mentioned some alternative approaches and implementations, which could achieve this; \secref{sec:alt_random} introduces the possibility to coordinate the validators in a systematic iteration of the search space.
+This chapter described several other orchestration schemes, some of which reduce the number of emitted internal operations.
+As the inter-contract communication accounts for most of the gas consumption in the modular approach, avoiding them is an effective way of reducing the costs.
+In this regard, a concrete improvement of the proposed architecture could be to merge the controller and assertion code into a single contract.
+This corresponds to the inverse hybrid architecture as described in \secref{sec:monolithic}.
+Instead of $(t+1)$ internal operations, this only requires a single internal operation calling the parent contract.
 
-There still remains an open question concerning the proposed implementation that could be answered in detail within the scope of this thesis - the representation and validation of a counterexamples.
-The interaction scheme in \figref{fig:interaction_modular} suggests, that validators publish an instance of a counterexample to the network if they found one.
-However, it has yet to be specified how the counterexample is represented and double-checked by the other validators.
-With the \texttt{failwith} instruction, the top element of the stack can be exposed \cite{tezos_docs}, providing a way to return an interpretable expression from the interpretation context \cite{tezos_repo}.
-Thus, as a first approximation, the counterexample could be represented as a tuple of assertion code and a list of randomly generated values.
-For instance, the counterexample for the assumption ``p is a prime'' (cf.
-\eqref{eq:prime}) is represented by \\
-\texttt{(n >= 2 \&\& n <= sqrt(p) \&\& p\%n = 0, <random value for n>)}. \\
-For validation of the counterexample, this tuple, together with the respective operation hash of the initial transaction this counterexample refers to, is published to the network.
-The other validators then interpret the given code with the respective value(s) and either confirm or object the counterexample.
-As Tezos transmits data as byte sequences, the counterexample needs to be unparsed and serialized, or deserialized and parsed respectively.
-If the cost for checking assertions is paid for be the user (in form of gas), then these costs have to be added to the total costs as well.\\
-In order to prevent denial-of-service attacks by spamming the network with false counterexamples, the protocol should implement penalties for such cases.
-Details about this and possible rewards for valid counterexamples should be considered in the protocol design.
+\section{Open questions}
+There remain two aspects of the off-chain design, which could not be addressed in detail by this thesis. These aspects are outlined briefly in the following sections.
 
-\todo{Make clear that we only engage validators on Tezos (not all nodes)}
-\todo{What happens if a validator has multiple endorsing rights? -> open issues section?}
+\subsection{Representing counterexamples}\label{sec:counterexample}
+It remains to be specified, how counterexamples are represented within the network.
+The interaction scheme in \figref{fig:interaction_modular} suggests, that validators publish a counterexample to the network in case of a failed assertion.
+For this, the validators have to obtain the randomly generated values from within the execution context of the VM.
+With the \texttt{failwith} instruction, the top element of the stack can be exposed, allowing to return an interpretable expression from the execution context.
+The generated values can thus be returned as a single value, a (nested) pair or a list.
+To allow other validators to check the assertion with a specific set of values, a modified version of the assertion code must be available on the blockchain.
+Instead of generating random values, this version should take these values as input parameters.
+Hence, the validator creates a normal transaction invoking this code with the values returned by the \texttt{failwith} instruction and publishes it to the network.
+The counterexample is then validated like any other transaction on the blockchain.
+
+To implement this scheme, the compiler has to generate one more contract per assertion.
+In addition, the assertion contract needs to know about the address of the counterexample contract and return the address together with the generated values.
+This requires a adjustment of the storage type of the assertion contract and changes the order of origination to:
+\begin{enumerate}
+\itemsep-0.5em
+\item \texttt{Origination(parent)}, \texttt{Origination(counterexample)}
+\item \texttt{Origination(assertion, address counterexample)}
+\item \texttt{Origination(controller, address [assertion], address parent)} 
+\end{enumerate}
+
+\subsection{Multi-slot validators}
+The proposed implementation for Tezos assumes that all 32 validators of the current block cycle execute a determined number of test runs.
+In fact, as mentioned in the section describing Tezos' proof-of-stake mechanism, a validator may have been assigned several endorsement slots per cycle.
+Since these validators only execute the assertion once, the test runs for the other endorsement slots are neglected.
+As a result, the error rate of the assertion check is unpredictable and may exceed the configured threshold.
+This issue should be addressed by the protocol design --- multi-slot validators should execute the assertion transaction for each of their endorsement slot.

### 2021-04-26 assertions/doc/thesis-bernhardt/chapters/appendix.tex
Finish revision chpt 5

@@
 
-\section{\texttt{Foo}}
+\section{Foo}
 \lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
@@
 				 label=lst:foo_manager,
-				 caption=Manager contract of \texttt{Foo}]{listings/foo_manager.tz}
+				 caption=Controller contract of \texttt{Foo}]{listings/foo_manager.tz}
 \lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
@@
 
-\section{\texttt{Bar}}
+\section{Bar}
 \lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
@@
 				 label=lst:bar_manager,
-				 caption=Manager contract of \texttt{Bar}]{listings/bar_manager.tz}
+				 caption=Controller contract of \texttt{Bar}]{listings/bar_manager.tz}
 \lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,

### 2021-04-27 assertions/doc/thesis-bernhardt/chapters/0_2-abstract.tex
Abstract

\chapter*{Abstract}
Modern blockchains provide a platform for building applications with Smart Contracts. Because transactions are processed at every node in the network, the quantity and complexity of computation, which can be performed by Smart Contracts, is limited. Furthermore, complex contracts can generate high transaction costs for the user. To overcome this limitation and increase cost efficiency, blockchain-based applications could move computations to an off-chain component and only process the result on the blockchain.
This thesis proposes a processing model, which engages the validators of the network in a distributed effort to verify a submitted off-chain computation. Based on a specification of properties, the validators are challenged to find a counterexample by asserting these properties for independent subsets of the result. This reduces the computational effort on the blockchain to the verification of the result, instead of the computation of the result itself. Due to the distributed scheme, the computations per node are decreased even further. As a further contribution, this thesis defines a domain-specific language to express explicit assertions for off-chain computations. It describes the model and a proof-of-concept implementation of a processing pipeline, which transforms and compiles these assertions into Smart Contracts for the target platform Tezos. These contracts conduct a point-wise search for a counterexample and are called during the verification process.

%Modern blockchains support building own applications with Smart Contracts.
%because transactions are processed by every node, the amount and complexity of computation which can be performed by such SC is limited. %Furthermore, complex SC can cause high transaction costs for the user.
%To overcome this limitation and increase efficiency, applications could move computations to an off-chain component and submit the results to the blockchain. 
%This thesis proposes a processing model which engages the validators of the network to a distributed validation of such a submitted result. It challenges them to find counterexamples by performing an assertion check for independent subsets of the submitted result.
% This reduces the computational efforts on the chain to the verification of the result instead of computing the result itself.
% due to the distributed approach, the computation per validator and node is reduced even further

% Furthermore, this thesis defines a domain-specific language to express explicit assertions over off-chain computations. It also provides a pipeline description for a toolchain, which transforms and compiles these assertions into SC searching for counterexamples. These contracts are then used in the distributed effort to validate the result.
% this toolchain was partially implemented and provided with this thesis.

% Tezos!

### 2021-04-27 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
Abstract

@@
 More recent blockchains, considered as the second generation, aim to provide a platform for building more sophisticated and complex applications on top of the technology.
-Some prominent examples for such blockchains are Ethereum \cite{eth-whitepaper}, Tezos \cite{goodman_tezos_2014} or Cardano \cite{cardano_essay}, which plans to introduce smart contracts in an update this year \cite{cardano_alonzo}.
-Blockchain-based applications are built with smart contracts, programs written in Turing-complete languages.
-Running a smart contract generates costs proportional to the amount and complexity of computations, as well as its storage usage \cite{alharby_blockchain_2017}.
+Some prominent examples for such blockchains are Ethereum \cite{eth-whitepaper}, Tezos \cite{goodman_tezos_2014} or Cardano \cite{cardano_essay}, which plans to introduce Smart Contracts in an update this year \cite{cardano_alonzo}.
+Blockchain-based applications are built with Smart Contracts, programs written in Turing-complete languages.
+Running a Smart Contract generates costs proportional to the amount and complexity of computations, as well as its storage usage \cite{alharby_blockchain_2017}.
 These fees, often measured in a unit called ``gas'', have to be paid for by the user in order to compensate the miners for their efforts \cite{narayanan_bitcoin}.
-This creates a powerful incentive to keep smart contracts simple and efficient.
+This creates a powerful incentive to keep Smart Contracts simple and efficient.
 In reality, however, meaningful applications still might need to perform resource intensive computations or store larger amounts of data.
@@
 \\
-In order to avoid these costs and restrictions, such an application could perform some computations outside of the blockchain context (i.e., off-chain) and only submit the results to a smart contract as an input parameter for further processing or recording.
+In order to avoid these costs and restrictions, such an application could perform some computations outside of the blockchain context (i.e., off-chain) and only submit the results to a Smart Contract as an input parameter for further processing or recording.
 By trusting that the submitted results are correct, this approach raises both safety and security issues.
 Invalid results can be submitted unintentionally as a result of a wrong computation, or a third party may pass them intentionally to cause harm or capitalize on it.
-Consequently, submitted parameters should be validated before the smart contract is executed.
+Consequently, submitted parameters should be validated before the Smart Contract is executed.
 Although in many cases, verifying a solution takes less time than computing the result itself (cf.
@@
 \\
-Consider the smart contract \texttt{Example}, which is shown in \lstref{lst:prime} and features a function \texttt{f}.
+Consider the Smart Contract \texttt{Example}, which is shown in \lstref{lst:prime} and features a function \texttt{f}.
 The function takes an input value \texttt{p} of type integer and should make use of the assumption that \texttt{p} is a prime number.
@@
 Assuming that computing the body of the loop takes constant time, this test has a time complexity of $\mathcal{O}(\sqrt{p})$ and therefore generates costs linear in $\sqrt{p}$ on top of the cost for executing the actual contract.
-Thus, a mechanism is required that allows the smart contract to make use of the result computed by an off-chain source, without having to check its validity locally with scaling costs.
+Thus, a mechanism is required that allows the Smart Contract to make use of the result computed by an off-chain source, without having to check its validity locally with scaling costs.
 
@@
 In this model, results of such computations are validated on-chain by the validators of the network.
-In order to do so, they invoke assertion smart contracts, which point-wise check the validity of certain properties.
+In order to do so, they invoke assertion Smart Contracts, which point-wise check the validity of certain properties.
 When claiming an assertion failure, a validator publishes a counterexample to be scrutinized by the other validators.

### 2021-04-28 assertions/doc/thesis-bernhardt/chapters/6-conclusion.tex
Own chapt probabilistic model
Revision chpt 5
Revision monolithic
Finish revision chpt 5
Conclusion

--- 2021-04-01 assertions/doc/thesis-bernhardt/chapters/5-conclusion.tex
@@
 \chapter{Conclusion and outlook}\label{chap:conclusion}
-\draft{}
-\begin{itemize}
-\item Summarize what has been implemented so far
-\item Next steps
-	\begin{itemize}
-	\item extending VM \& Michelson
-	\item compiler
-	\item list open questions
-	\item Protocol-design
-		\begin{itemize}
-		\item Do endorsers validate or extra validators?
-		\item How to differentiate between SC w/ and w/o assertions?
-		\item How to implement the waiting?
-		\item Which transactions/messages can be reused or need to be introduced
-		\item Representing counterexamples and verifying them
-		\item Penalty for incorrect counterexamples
-		\end{itemize}
-	\end{itemize}
-\item Estimation of cost reduction (or increase?)
-\item Alternatives (e.g. TrueBit)
-\end{itemize}
+Complex blockchain-based applications suffer from high computation costs and limited scalability.
+A consequential measure to address this issue, is to move computations off the chain and only verify the correctness of submitted results on the blockchain.
+This thesis  proposed assertions for distributed refutation as a probabilistic implementation of this verification.
+In the processing model of this approach, the validators of the system are challenged to assert specified properties for a random subset of the off-chain computation.
+If an assertion fails, the respective validator generates a counterexample and publishes it to the network.
+When the system acknowledges the counterexample, the off-chain computation is rejected.
+Suitable use-cases for this approach are computations, whose properties can be specified with formulas in predicate logic featuring universal quantification.
+To support this model on the target platform Tezos, a toolchain was developed to allow developers to specify explicit assertions and generate corresponding Smart Contracts.
+These contracts check the property point-wise within the quantification domain and identify counterexamples when executed by the validators.
+For the specification of assertions, a simple domain-specific language was defined.
+
+For the proposed architecture, the conducted costs analysis shows high transaction fees for the submission of off-chain computations,  due to high verification costs.
+Although the verification might still be more efficient than the execution itself, it can be assumed that the cost reductions are narrowed, or even equalised in cases of moderate complexity of off-chain computations.
+Inter-contract communication was identified as a main driving factor.
+To lower these costs and approach usability on production systems, the thesis provided possible improvements and modifications of the architecture.
+
+If it is possible to make the verification more efficient, this approach provides a simple solution for increasing of scalability of blockchain-based applications.
+Assertions can be specified in an expressive and familiar way and the processing model only requires moderate adaptions to the blockchain protocol.
+
+Based on either the proposed or a modification of the architecture, subsequent tasks include the implementation of the compiler in order to conclude the toolchain.
+As addressed in the introduction, the implementation of distributed assertions on blockchains also requires a design and implementation of a protocol amendment.
+Many of the aspects that need to be considered by the protocol design have already been pointed out by this work.
+This includes, i.a., the extensions to Michelson and Tezos' VM to support random value generation, the implementation of a dedicated execution mode, the withholding of the transaction submitting an off-chain computation until it has been verified, and the rejection of this transaction as a consequence of a verified counterexample.
+
+Besides the completion of the proof-of-concept implementation, the assertion language can be extended with features, such as variables and user-defined functions, to improve (re-)usability.
+Furthermore, an interesting extension is the support for properties formulated with existential quantification, as this allows to verify off-chain computations through distributed validation instead of refutation.
+
+Current work at the chair of programming languages includes another thesis to develop a model and an implementation of distributed assertion checking targeting the blockchain Ethereum.
+The groundwork provided in this thesis, such as the use-case analysis, the domain-specific language and frontend of the toolchain, is by design compatible for both targets.

### 2021-04-28 assertions/doc/thesis-bernhardt/chapters/0_2-abstract.tex
Conclusion
Revision

@@
 \chapter*{Abstract}
-Modern blockchains provide a platform for building applications with Smart Contracts.
-Because transactions are processed at every node in the network, the quantity and complexity of computation, which can be performed by Smart Contracts, is limited.
+Modern blockchains provide a platform for building sophisticated applications with Smart Contracts.
+Because transactions are processed at every node in the network, the quantity and complexity of computations, which can be performed by Smart Contracts, are limited.
 Furthermore, complex contracts can generate high transaction costs for the user.
-To overcome this limitation and increase cost efficiency, blockchain-based applications could move computations to an off-chain component and only process the result on the blockchain.
+To overcome this limitation and improve cost efficiency, blockchain-based applications could move computations to an off-chain component and only process the result on the blockchain.
 This thesis proposes a processing model, which engages the validators of the network in a distributed effort to verify a submitted off-chain computation.
 Based on a specification of properties, the validators are challenged to find a counterexample by asserting these properties for independent subsets of the result.
-This reduces the computational effort on the blockchain to the verification of the result, instead of the computation of the result itself.
-Due to the distributed scheme, the computations per node are decreased even further.
-As a further contribution, this thesis defines a domain-specific language to express explicit assertions for off-chain computations.
-It describes the model and a proof-of-concept implementation of a processing pipeline, which transforms and compiles these assertions into Smart Contracts for the target platform Tezos.
+This reduces the computational effort on the blockchain to the verification of the result, rather than the computation of the result itself.
+Moreover, by implementing a distributed scheme, each node  only has to process a fraction of the verification.
+As a further contribution, this thesis defines a domain-specific language to express explicit assertions for off-chain computations and specifies a processing pipeline to transform and compile these assertions into Smart Contracts.
 These contracts conduct a point-wise search for a counterexample and are called during the verification process.
-
-%Modern blockchains support building own applications with Smart Contracts.
-%because transactions are processed by every node, the amount and complexity of computation which can be performed by such SC is limited.
-%Furthermore, complex SC can cause high transaction costs for the user.
-%To overcome this limitation and increase efficiency, applications could move computations to an off-chain component and submit the results to the blockchain. 
-%This thesis proposes a processing model which engages the validators of the network to a distributed validation of such a submitted result.
-It challenges them to find counterexamples by performing an assertion check for independent subsets of the submitted result.
-% This reduces the computational efforts on the chain to the verification of the result instead of computing the result itself.
-% due to the distributed approach, the computation per validator and node is reduced even further
-
-% Furthermore, this thesis defines a domain-specific language to express explicit assertions over off-chain computations.
-It also provides a pipeline description for a toolchain, which transforms and compiles these assertions into SC searching for counterexamples.
-These contracts are then used in the distributed effort to validate the result.
-% this toolchain was partially implemented and provided with this thesis.
-
-% Tezos!
+A proof-of-concept implementation of this pipeline is provided and described for the target platform Tezos.

### 2021-04-28 assertions/doc/thesis-bernhardt/chapters/2-use_case_analysis.tex
Revision

@@
 
-\section{Restriction of use-cases}\label{sec:restrict}\todo{Better title? -> conclusion?}
+\section{Restriction of use-cases}\label{sec:restrict}\todo{Better title?}
 The examples given in this chapter have shown that, depending on the type and order of quantification, not all properties can be checked in the same way and need different modi of assertion checking.
@@
 \includegraphics[width=0.9\linewidth]{figures/2-use_cases/cost_analysis}
-\caption{Gas consumption of transactions calling \texttt{Foo} and \texttt{Bar} for increasing input sizes}
+\caption{Gas consumption of contracts \texttt{Foo} and \texttt{Bar} for increasing inputs}
 \label{fig:use_case_cost}

### 2021-04-28 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
Revision

@@
 For this, the validators have to obtain the randomly generated values from within the execution context of the VM.
-With the \texttt{failwith} instruction, the top element of the stack can be exposed, allowing to return an interpretable expression from the execution context.
+With the \texttt{failwith} instruction, the top element of the stack is exposed, allowing to return an interpretable expression from the execution context.
 The generated values can thus be returned as a single value, a (nested) pair or a list.
@@
 Instead of generating random values, this version should take these values as input parameters.
-Hence, the validator creates a normal transaction invoking this code with the values returned by the \texttt{failwith} instruction and publishes it to the network.
+Hence, the validator could create a normal transaction invoking this code with the values returned by the \texttt{failwith} instruction and publish it to the network.
 The counterexample is then validated like any other transaction on the blockchain.
@@
 To implement this scheme, the compiler has to generate one more contract per assertion.
-In addition, the assertion contract needs to know about the address of the counterexample contract and return the address together with the generated values.
-This requires a adjustment of the storage type of the assertion contract and changes the order of origination to:
+In addition, the assertion contract needs to know about the address of the counterexample contract, and return the address together with the generated values in case of a failure.
+This requires an adjustment of the storage type of the assertion contract and changes the order of origination to:
 \begin{enumerate}
@@
 
+In order to reject a transaction submitting off-chain computations in case of a published counterexample, however, the network needs to be able to relate a counterexample to the respective transaction.
+
 \subsection{Multi-slot validators}
-The proposed implementation for Tezos assumes that all 32 validators of the current block cycle execute a determined number of test runs.
+The proposed implementation assumes that all 32 validators of the current block cycle execute a determined number of test runs.
 In fact, as mentioned in the section describing Tezos' proof-of-stake mechanism, a validator may have been assigned several endorsement slots per cycle.
 Since these validators only execute the assertion once, the test runs for the other endorsement slots are neglected.
-As a result, the error rate of the assertion check is unpredictable and may exceed the configured threshold.
-This issue should be addressed by the protocol design --- multi-slot validators should execute the assertion transaction for each of their endorsement slot.
+As a result, the error rate of the assertion check is not deterministic and may exceed the configured threshold.
+This issue should be addressed by the protocol design --- multi-slot validators should execute the assertion check for each of their endorsement slots.

### 2021-04-28 assertions/doc/thesis-bernhardt/chapters/6-conclusion.tex
Revision

@@
 For the proposed architecture, the conducted costs analysis shows high transaction fees for the submission of off-chain computations,  due to high verification costs.
-Although the verification might still be more efficient than the execution itself, it can be assumed that the cost reductions are narrowed, or even equalised in cases of moderate complexity of off-chain computations.
-Inter-contract communication was identified as a main driving factor.
+Although the verification might still be more efficient than the execution itself, it can be assumed that the cost reductions are equalised in cases of moderate complexity of off-chain computations.
+Inter-contract communication was identified as a main driving factor of the verification cost.
 To lower these costs and approach usability on production systems, the thesis provided possible improvements and modifications of the architecture.
 
-If it is possible to make the verification more efficient, this approach provides a simple solution for increasing of scalability of blockchain-based applications.
-Assertions can be specified in an expressive and familiar way and the processing model only requires moderate adaptions to the blockchain protocol.
+In case the verification cost can be lowered to a feasible threshold, this approach provides a simple solution for increasing the scalability of blockchain-based applications.
+Assertions can be specified in an expressive and familiar way, and the processing model only requires moderate adaptions to the blockchain protocol.
 
@@
 Besides the completion of the proof-of-concept implementation, the assertion language can be extended with features, such as variables and user-defined functions, to improve (re-)usability.
-Furthermore, an interesting extension is the support for properties formulated with existential quantification, as this allows to verify off-chain computations through distributed validation instead of refutation.
+Furthermore, an interesting extension is the support for properties formulated with existential quantification, as this allows to verify off-chain computations by distributed validation in addition to distributed refutation.
 

### 2021-04-28 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
Finish revision

@@
 Valid ASTs are then cast to a target specific AST type and passed to the type checker.
-In this stage, the assertions are linked to the respective parent entrypoints based on the parameter patterns and tags.
+In this stage, the assertions are linked to the respective parent entrypoints, based on the parameter patterns and tags.
 Given the list of target specific ASTs and a linking, the compiler finally generates target code.
@@
 
-As a preliminary for the compiler implementation, \secref{sec:ext_michelson} identifies necessary extensions to Michelson and Tezos' VM in order to facilitate the distributed assertion scheme.
+As a preliminary for the compiler implementation, \secref{sec:ext_michelson} identifies necessary extensions to Michelson and Tezos' VM, in order to facilitate the distributed assertion scheme.
 Although the extensions are formalized in this thesis, implementing the extension is part of the protocol amendment.
@@
 \secref{sec:orchestration} explores possible strategies for such a scheme, and discusses their strengths and weaknesses.
-Based on a resulting proposal for the orchestration, \secref{sec:cost_analysis_distributed} performs a cost analysis of the approach of distributed assertion checking and evaluates if, and under which conditions, it can solve the issue of scalability in blockchain applications.
+Based on a resulting proposal for the orchestration, \secref{sec:cost_analysis_distributed} performs a cost analysis of the approach of distributed assertion checking and evaluates if, and under which conditions, it can increase the scalability in blockchain applications.
 
@@
 It uses a proof-of-stake consensus mechanism, which is not only used to agree on the current state of its ledger, but also allows its stakeholders to come to a consensus about changes in the economic protocol by participating in a voting process.
-The changes included in a protocol upgrade, called amendment, can influence i.a.
-which transactions are valid on the blockchain, the payment system or even the voting process itself.
+The changes included in a protocol upgrade, called amendment, can influence, i.a., which transactions are valid on the blockchain, the payment system or even the voting process itself.
 It does so without risking a fork of the blockchain.
@@
 
-In addition to user accounts associated with a public key, Tezos supports smart contracts, which are written in the built-in language Michelson.
-Tezos' transaction fee system is similar to that of Ethereum \cite{wood_ethereum_2021} - it is gas-instrumented and besides a base fee, every operation and byte of storage during contract execution has to be paid for by the user.
+In addition to user accounts associated with a public key, Tezos supports Smart Contracts, which are written in the built-in language Michelson.
+Tezos' transaction fee system is similar to Ethereum's \cite{wood_ethereum_2021} - it is gas-instrumented and besides a base fee, every operation and byte of storage during contract execution has to be paid for by the user.
 However, Tezos imposes a hard cap on the amount of gas that can be consumed per operation (including internal transactions) \cite{tezos_docs}\cite{morley_repo}, whereas Ethereum limits the gas quota only in respect to blocks \cite{wood_ethereum_2021}.\\
@@
 \subsection{Proof-of-stake in Tezos}
-In Tezos, contracts which have staked a minimum amount of tokens, called a roll, can participate in the consensus mechanism.
+In Tezos, contracts which have staked a minimum amount of tokens (called a roll), can participate in the consensus mechanism.
 When participating, a contract has a chance to obtain the role of either a baker or an endorser.
-Contracts who don't own enough tokens, or infrastructure, to participate directly, can delegate their baking and endorsing rights to other contracts.
+Contracts not owning enough tokens or infrastructure, to participate directly, can delegate their baking and endorsing rights to other contracts.
 The rights to bake or endorse are determined and assigned at the beginning of each cycle, which consists of a specified number of blocks.
 For baking, a random roll is selected for each block level and the rights are assigned to its owner.
-The block produced by that baker is signed by a fixed number of endorsers\footnote{For consistency, endorsers are referred to as ``validators'' in this chapter} (32 as of protocol 007 Delphi), which also have been assigned endorsing rights for this block level by a random selection of rolls.
+The block produced by that baker is signed by a fixed number of endorsers\footnote{For consistency, endorsers are referred to as ``validators'' in the remainder of this chapter} (32 as of protocol 007 Delphi), which also have been assigned endorsing rights for this block level by a random selection of rolls.
 Since participants can stake more than one roll, they may be assigned several endorsement slots at the same block level.
@@
 Unlike Ethereum's contract language Solidity, Michelson doesn't have a concept of named functions with a dedicated parameter type.
-Instead of named functions, Michelson contracts models separate entrypoints by taking a sum type as an input parameter.
-The type constructors can optionally be tagged a field annotation, which can be considered an entrypoint name.
+Instead of named functions, Michelson contracts model separate entrypoints by taking a sum type as an input parameter.
+The type constructors can optionally be tagged with a field annotation, which can be considered  as an entrypoint name.
 The sum type is built by nesting the \texttt{or} type, which has the constructors \texttt{left} and \texttt{right}.
@@
 
-\subsubsection{Internal operations}
+\subsubsection{Internal operations}\label{sec:internal_ops}
 Smart Contracts are able to invoke other Smart Contracts by emitting internal operations.
@@
 \begin{enumerate}
-\item \textbf{Reading costs} --- apply for reading the contract code and storage from the blockchain and, on top of a base cost, depend on the amount of bytes read
-\item \textbf{Deserialization costs} --- depend on the Micheline expression and the size of the byte sequence. Apply lazily, thus the deserialization of each value only has to be paid once
+\item \textbf{Reading costs} --- apply for reading the contract code and storage from the blockchain and depend on the amount of bytes read
+\item \textbf{Deserialization costs} --- depend on the Micheline expression and the size of the byte sequence. Apply lazily, thus the deserialization of each value only has to be paid for once
 \item \textbf{Parsing costs} --- are composed of three types of costs:
@@
 	\item code parsing --- apply when the instructions of a program are type checked and depends on the number and types of instructions.
-Some instructions are expensive, such as \texttt{IF} (both branches need to be checked and compared) or \texttt{CREATE\_CONTRACT} (requires type check of invoked contract)
+Some instructions are expensive, such as \texttt{IF} (both branches need to be checked and compared) or \texttt{CREATE\_CONTRACT} (requires type check of the invoked contract)
 	\end{itemize}
@@
 \item \textbf{Serialization costs} --- apply when serializing Micheline nodes to byte sequences and depend on the expression and its size
-\item \textbf{Writing costs} --- apply when writing to the internal database and depend on the amount of bytes. A base gas fee is burned (destroyed) for each additional byte of storage.
+\item \textbf{Writing costs} --- apply when writing to the internal database and depend on the amount of bytes. A base gas fee is burned for each additional byte of storage.
 \end{enumerate}
-If a transaction emits internal operations, their gas consumption is computed in the same way and are added to the total gas consumption of the external operation.
+If a transaction emits internal operations, their gas consumption is computed in the same way and is added to the total gas consumption of the external operation.
 
@@
 Michelson is a compilation target for various high-level languages that provide a more user-friendly and intuitive way of writing Smart Contracts.
-Additionally, some of them come with development environments, testing or verification tools.
-The following list introduces three prominent languages compiling to Michelson:
+Additionally, some of them provide development environments, testing or verification tools.
+The following list introduces three prominent languages, which compile to Michelson:
 \begin{description}
-\item[\textbf{Liquidity}] \cite{liquidity} is a language with an OCaml-like syntax, which allows using local variables instead of stack manipulations.
+\item[\textbf{Liquidity}] \cite{liquidity} is a language with an OCaml-like syntax, which allows to express contracts in a functional way.
+It supports using local variables instead of stack manipulations.
 Its module system can be used to write reusable contract code or libraries.
@@
 \subsection{Language semantics and type system}\label{sec:michelson_semantics}
-The way Michelson is interpreted is purely functional; the interpreter takes the current stack and an operation and builds a return stack from the initial one, without causing any side effects.
+Michelson is interpreted purely functional; the interpreter takes the current stack and an operation and builds a return stack from the initial one, without causing any side effects.
 The definition of the recursive interpreter is given in the form of a list of rules, comprising of all possible inputs (i.e., program and stack types) and the respective output stack type of the computation.
@@
 \end{lstlisting}
-For each valid program and initial stack, exactly one rule matches.
+For each valid program and initial stack, exactly one rule applies.
 Following the keyword \texttt{iff}, the rule can add extra conditions over values on the stack.
-If the result depends on the results of other program interpretations, such as conditionals or function calls, the rule can contain \texttt{where} or \texttt{and} clauses.
+If the result depends on the results of other program interpretations, such as conditionals or function calls, the rule can contain recursive rules in the \texttt{where} or \texttt{and} clauses.
 These clauses represent a recursive interpretation of an intermediate program.
@@
 the network can reach a consensus about the state of the ledger \cite{chatterjee_probabilistic_2019}, the prevalent workarounds for generating pseudo-random numbers cannot be used to implement the random generators in assertion contracts.
-The scheme explicitly requires as many validators as possible to check distinct elements in the search space.
-Common schemes for obtaining random values, like oracles or using block attributes as seeds \cite{chatterjee_probabilistic_2019}, would provide the same values for all validators.
-Thus, the VM should provide an instruction to generate a ``real'' random value for assertion checking only.
+The scheme explicitly requires the validators to check distinct elements in the search space.
+Common schemes for obtaining random values, like oracles or using block attributes as seeds \cite{chatterjee_probabilistic_2019}, would generate the same values for all validators.
+Thus, the VM needs to provide an instruction to generate a ``real'' random value exclusively for assertion checking.
 The instruction should not be available in the normal execution mode, in order to preserve the deterministic behaviour of normal Smart Contracts.
@@
 It consumes an offset and a positive range from the stack and pushes a randomly generated integer to the top.
-The typing rule (line 1) specifies, that the offset should be of type \texttt{integer}, and the range of type \texttt{nat}.
+The typing rule (line 1) specifies, that the offset should be of type \texttt{integer}, and the range of type \texttt{nat} (i.e., a natural number).
 \lstset{upquote=true}
@@
 However, because such operations are used frequently in many of the given use-cases, adding it as a predefined primitive for some data types might be justifiable.
-This reduces the required code to express the indexing, and thus not only improves the readability of the contract code, but also lowers the costs of the contract origination and execution.
+It reduces the required code to express the indexing, and thus not only improves the readability of the contract code, but also lowers the costs of the contract origination and execution.
 
@@
 After the computation, on top of the resulting stack is an optional value of the element type \texttt{'a}.
-A selection rule (line 2 and 3) is given for each of the two possible result stack patterns.
+A selection rule (line 2 and 3) is given for each of the two possible result stack patterns, i.e., a value of type \texttt{'a} or an undefined value if the given index is out of bounds.
 \begin{lstlisting}[caption=Selection and type rule of the list \texttt{nth} instruction, language=, label=lst:nth_type]
@@
 
-Within the VM, Michelson lists are represented with OCaml's list type --- the computation of \texttt{nth} thus simply calls the \texttt{nth} function of the List module, as indicated in \lstref{lst:nth_impl}.
+Within the VM, Michelson lists are represented with OCaml's list type --- the computation of \texttt{nth} thus simply calls the \texttt{nth} function of OCaml's List module, as indicated in \lstref{lst:nth_impl}.
+\\
 \begin{lstlisting}[caption=Simplified evaluation of \texttt{nth} in the Michelson interpreter, language=, label=lst:nth_impl]
@@
 Michelson features instructions to execute a loop or iterate over a list, which can be used for such an implementation.
-An exemplary implementation of the operation \texttt{nth} for lists in the high-level language Liquidity is given by \lstref{lst:nth_liq} in appendix \ref{apx:nth}.
+An exemplary and readable implementation of the operation \texttt{nth} for lists in the high-level language Liquidity is given by \lstref{lst:nth_liq} in appendix \ref{apx:nth}\footnote{Since Michelson is a low-level language, code examples in this chapter are mostly provided in Liquidity to provide a short and readable representation of the contract structure or logic.
+In most cases, the corresponding Michelson code generated by the Liquidity compiler is included in the appendix.}.
 The appendix also contains the corresponding Michelson code after compiling the source with the Liquidity compiler (\lstref{lst:nth_tz}).
@@
 So far, the assertion and parent contract have been considered separately.
-However, they have to be orchestrated on-chain, such that the assertion code is either invoked automatically before the parent code is executed, or the assertion code can be invoked directly by the validators.
+However, they have to be orchestrated on the blockchain, such that the assertion code is either invoked automatically before the parent code is executed, or the assertion code can be selectively invoked by the validators.
 Furthermore, the orchestration should include a mechanism to determine and trigger the required number of test runs per validator.
@@
 This section describes two possible approaches for an orchestration --- a monolithic and a modular approach.
-It also discusses, which of the given architecture is chosen for the implementation of distributed assertion checking, and why.
+It also discusses, which of the given architecture is chosen for the proof-of-concept implementation, and why.
 
@@
 This can be solved by using fixed tag patterns for assertion entrypoints, which can be derived from the parent entrypoint tag.
-\figref{fig:mono_eps} proposes the tag suffix ``\texttt{\_a}''.
+\figref{fig:mono_eps} proposes the tag suffix ``\texttt{\_a}'' for assertion entrypoints.
 External transactions should only invoke the production entrypoints.
 
-The monolithic contract in \figref{fig:mono_eps}, however, do not yet provide any means to trigger several test runs per validator.
+The assembly in \figref{fig:mono_eps}, however, does not yet provide any means to trigger several test runs per validator.
 Since the required number of test runs $t$ can only be determined at runtime, it cannot be passed to the validators as a parameter to the validation request.
-Instead, the contract itself should contain a controller to handle this.
+Instead, the contract itself should contain a controller to handle the calculation of $t$ and the initiation of as many test runs.
 Similar to the assertion code, such a controller can be appended as another separate entrypoint, as shown in \figref{fig:monolithic_orchestration}.
@@
 
-If a developer did not specify an assertion for all entrypoints of the parent contract, invoking their non-existing controller entrypoints would cause a transaction failure.
+If a developer does not specify an assertion for all entrypoints of the parent contract, invoking their non-existing controller entrypoints would cause a transaction failure.
 In order to avoid this and increase the robustness, the compiler should generate dummy controllers for empty assertions, which simply return unit (i.e, an empty list of internal operations and the unchanged storage).
 
-\lstref{lst:mono_liq} implements a monolithic contract in the high-level language Liquidity.
+\lstref{lst:mono_liq} implements a monolithic contract in Liquidity.
 The contract contains the two parent entrypoints \texttt{A} (line 3) and \texttt{B} (line 21), and provides an assertion entrypoint \texttt{A\_a} (line 5) for \texttt{A}.
 Entrypoint \texttt{B} does not have an associated assertion.
-The compiler generated a controller entrypoint for both parent entrypoints, i.e., \texttt{A\_c} (line 7) and \texttt{B\_c} (line 23).
+For both parent entrypoints, it provides the controller entrypoints \texttt{A\_c} (line 7) and \texttt{B\_c} (line 23).
 Controller \texttt{A\_c} determines the number of test runs in line 8 (the implementation of the formula is omitted here) and creates $t$ internal operations, which invoke the assertion entrypoint with the same parameter (lines 9-17).
@@
 \figref{fig:interaction_monolithic} depicts the resulting interactions of the nodes, validators and monolithic Smart Contracts on the blockchain.
-The execution model for distributed assertion checking requires a dedicated execution modus.
+The execution model requires a dedicated modus for distributed assertion checking.
 A possible mechanism to activate this modus is using a special transaction type, which is denoted by \texttt{txa(destination, entrypoint, parameter)} in the graphic.
-When an operation, such as a transaction or origination, is injected into a node, it is normally propagated to the network after it has been validated.
+When an operation, such as a transaction or origination, is injected into a node, it is normally propagated to the network after it has been pre-validated by the node.
 After the injection of \texttt{txa(1, \%A, parameter)}, however, the node broadcasts its derivation \texttt{txa(1, \%A\_c, parameter)} to the network, which invokes the controller entrypoint instead.
 If this operation finishes successfully for all validators, hence no counterexample is published on the network after a certain amount of block cycles, the node can finally broadcast the initial operation as a normal transaction to the network.
-In case of an assertion failure, the respective validator broadcasts the counterexample with the generated value to the network to be included in an upcoming block.
-The counterexample is thus validated like a normal transaction.
-As a consequence of the broadcasted counterexample, the initial operation \texttt{txa(1, \%A, parameter)} should be rejected.
+In case of an assertion failure, the respective validator broadcasts the counterexample with the generated value to the network.
+As a consequence of the broadcasted counterexample, the initial operation \texttt{txa(1, \%A, parameter)} should be reverted and rejected by the injecting node.
 How a counterexample is represented and included on the chain is an unresolved question --- \secref{sec:counterexample} picks this topic up and gives some ideas regarding possible implementations.
@@
 This orchestration scheme only works as described when using explicit entrypoint tags for the contract invocations.
-On the one hand, calling entrypoints implicitly by wrapping the parameter in the respective sum type constructors causes a type mismatch for the controller and assertion entrypoints.
+On the one hand, calling entrypoints implicitly (by wrapping the parameter in the respective sum type constructors) causes a type mismatch for the controller and assertion entrypoints.
 \lstref{lst:mono} shows the parameter type of the Michelson implementation corresponding to the contract given in \lstref{lst:mono_liq} --- entrypoint \texttt{A} can be invoked implicitly with parameter value \texttt{Left 4}.
-The respective assertion entrypoint \texttt{A\_a} expects the value as \texttt{Right (Right (Left 4))} and the controller \texttt{A\_c} as \texttt{Right (Right (Right (Left 4)))}.\\
+The respective assertion entrypoint \texttt{A\_a} expects the value as \texttt{Right (Right (Left 4))} and the controller \texttt{A\_c} as \texttt{Right (Right (Right (Left 4)))}.
+Calling these entrypoints with the same parameter is thus not possible.
+\\
 On the other hand, the explicit tags encode the link between production, controller and assertion code --- omitting them would dissolve all references between them.
 Hence, implicit entrypoint invocation cannot be supported in the execution mode of assertions.
-Explicit entrypoints in the parameter type declaration of the contract can be enforced by the compiler.
-A specification of an explicit entrypoint in the contract invocation can be enforced by the \texttt{txa} operation type.
-\lstinputlisting[label=lst:mono, language=Michelson, caption=Skeleton of a monolithic contract in Michelson, numbers=left]{listings/monolithic.tz}
+The compiler should enforce the use of explicit entrypoints in the parameter type declarations and the \texttt{txa} operation type must take a mandatory entrypoint specification as an argument.
 
 This thesis does not go into more detail about how the described execution model for a monolithic orchestration is designed and implemented in the blockchain protocol.
-What needs to be considered in future work concerning the protocol design is the separate execution mode, possibly a dedicated transaction type as proposed above, the derivation of a transaction which attempts to find a counterexample, the handling of assertion failures and the exclusive acceptance of either the parameter (and thus the transaction) or a counterexample.
+What needs to be considered in future work concerning the protocol design, is the separate execution mode, possibly a dedicated transaction type as proposed above, the derivation of a transaction which attempts to find a counterexample, the handling of assertion failures and the exclusive acceptance of either the parameter (and thus the transaction) or a counterexample.
 
-\subsubsection{Evaluation}
+\lstinputlisting[label=lst:mono, language=Michelson, caption=Skeleton of a monolithic contract in Michelson, numbers=left, float]{listings/monolithic.tz}
+
+\subsubsection{Evaluation of the monolithic approach}
 The presented implementations of the monolithic approach each have strengths and weaknesses.
@@
 \lstref{lst:mono} shows how the parameter type and branching within the code body have to be adapted compared to the original parent contract in \lstref{lst:mono_parent}.
-Since the monolithic assembly results in deeper parameter and code nestings, the code becomes less readable overall.
-\lstinputlisting[label=lst:mono_parent, language=Michelson, caption=Skeleton of the parent contract in Michelson, numbers=left]{listings/monolithic_parent.tz}
+Since the monolithic assembly results in deeper parameter and code nestings, the overall complexity of the contract increases and may obscure the production code.
+\lstinputlisting[label=lst:mono_parent, language=Michelson, caption=Skeleton of the pure parent contract in Michelson, numbers=left]{listings/monolithic_parent.tz}
 
@@
 Adaptions to either the assertion or the parent contract require a complete recompilation and origination of the monolithic contract.
-The hybrid solution breaks some of the tight coupling, as a new version of the controller contract can be originated independently of the monolithic contract.
+The hybrid solution resolves some of the tight coupling, as a new version of the controller contract can be originated independently of the monolithic contract.
 
 Besides these disadvantages, the monolithic approach has some distinct advantages.
-The production and controller entrypoints can be invoked independently, which means that the validators do not have to run the production code while checking the assertion.
+The production and controller entrypoints can be invoked independently, implicating that the validators do not have to run the production code while checking the assertion.
 Conversely, the assertion code is not rerun if the parameter is valid and the transaction is broadcast to the network.
-This reduces the transaction cost for the user, as well as the overall footprint of the transaction in the network.
+This reduces the transaction cost for the user, as well as the overall computational footprint of the transaction in the network.
 
@@
 In the modular approach, the controller and each of the assertions are originated as separate contracts on the blockchain.
-The controller mirrors the interface of the parent contract, while each assertion has only a single entrypoint expecting the raw parameter type.
-By keeping the assertion code separate, the parent contract remains pure and does not have to be modified.
-Similar to the hybrid solution mentioned in the monolithic approach, the controller calls the respective assertion contract $t$ times as an internal operation, before invoking the parent contract with operation $t+1$.
-In the case of empty assertions, the parent contract is invoked immediately.
-Correspondingly, the toolchain returns $m + 1$ contracts, where $m$ is the number of assertions in the input.
-The assembly and output of the toolchain is outlined in \figref{fig:modular_assembly}.
+The controller mirrors the interface of the parent contract, while each assertion contract only features a single entrypoint which corresponds to the raw type of the associated parent entrypoint.
+By keeping the assertion code separated, the parent contract remains pure and does not have to be modified.
+Similar to the hybrid solution mentioned in the monolithic approach, the controller calls the respective assertion contract $t$ times as an internal operation, before invoking the parent contract as operation $t+1$.
+In the case of empty assertions, the parent contract is invoked immediately --- the controller thus acts as a direct gateway.
+Corresponding to this architecture, the toolchain returns $m + 1$ contracts for a assertion specification, where $m$ is the number of specified assertions in the input.
+The code assembly and output of the toolchain is outlined in \figref{fig:modular_assembly}.
 \begin{figure}[h]
@@
 
-In order to link the separate contracts to each other, the controller needs to know the addresses of the other contracts.
-As a result, the origination order is fixed ---- the assertion and parent contracts must be originated first, so that their addresses can be passed to the controller as initial storage values.
+In order to link the separate contracts to each other, the controller needs to have a reference to the other contract modules.
+This results in a fixed origination order --- the assertion and parent contracts must be originated first, and their addresses are passed to the controller as initial storage values.
 A proposed structure of the storage is a map from a unique identifier to an address.
@@
 The interaction with the modular contracts is shown in \figref{fig:interaction_modular}.
-Even though the transactions shown in the diagram state an explicit entrypoint tag, the scheme supports implicit entrypoint invocations.
-When invoking the assertion contract, the parameter is passed as the raw parameter value.
-The execution model is similar to the model for the monolithic approach.
-Because the controller mirrors the interface of the parent contract, the \texttt{txa} operation can be broadcast to the network directly --- a derivation to a distinct transaction to find the counterexamples is not necessary.
+Even though the transactions shown in the diagram state an explicit entrypoint tag, the scheme also supports implicit entrypoint invocations.
+Invocations of the assertion contract pass the parameter as a raw value, i.e., unpacked from the sum type constructors.
+The general execution model is similar to the model for the monolithic approach, but requires a few modifications; because the controller mirrors the interface of the parent contract, the \texttt{txa} operation can be broadcast to the network directly --- a derivation to a distinct transaction, which calls the assertion selectively, is not necessary.
 If none of the validators publish a counterexample, the initial transaction is broadcasted to the network as a normal operation to be included in a block.
-Since this transaction will inevitably rerun the assertion code in the normal execution mode (as it invokes the controller), the VM needs to handle \texttt{random} instructions in normal transactions such that they do not cause the operation sequence to fail (e.g., by marking the internal operations as skipped, or by introducing a dedicated result type for this case).
+This transaction will inevitably rerun the assertion code in the normal execution mode (as it invokes the controller).
+Hence, the \texttt{random} instruction should not cause an internal operation to fail in the normal execution mode of the VM.
+This could be solved by marking these internal operations with the operation result ``Skipped'' (cf.
+\secref{sec:internal_ops}), or by introducing a dedicated result type for this case.
 \begin{figure}[h]
@@
 
-\subsubsection{Evaluation}
-This approach resolves the two crucial problems of the monolithic approach: by mirroring the interface of the parent contract, the parameters passed to the manager contract can be forwarded directly to the parent contract, regardless of whether the default or an explicit entrypoint was called.
+\subsubsection{Evaluation of the modular approach}
+This approach resolves the two crucial problems of the monolithic orchestration: by mirroring the interface of the parent contract, the parameters passed to the manager contract can be forwarded directly to the parent contract, regardless of whether the default or an explicit entrypoint was called.
 Furthermore, the parent contract does not need to be modified, which leads to a much simpler compilation process and allows to extend already originated contracts with assertions.
 Due to its modularity, adaptions to either contract do not necessarily require a recompilation and origination of all components, as the controller is the only component with tight coupling.
-In order to optimize this and break the tight coupling, one could be inclined to add a setter entrypoint to the controller (as a sort of dependency injection).
+In order to reduce this coupling, one could be inclined to add a setter entrypoint to the controller (as a sort of dependency injection).
 This, however, would break the mirroring of the parent contract and is thus not possible without annulling one of the key strengths of the design.
@@
 The approach essentially has two weaknesses: firstly, the assertion and the parent cannot be called separately.
-As a result, the production code is run by every validator while searching for counterexamples and when validating a block containing the accepted transaction.
+As a result, the production code is run by every validator while searching for counterexamples, and when validating a block containing the accepted transaction.
 This increases the transaction cost for the user and requires a higher computational effort by the whole network.
-of the contract execution.
 Secondly, it exposes a security vulnerability, given that assertions can be bypassed by calling the parent contract directly.
@@
 
-Even though the monolithic approach is expected to be more efficient in terms of cost and network load, the following sections are based on the modular approach as the proposed architecture, due to its simplicity and flexibility.
+Even though the monolithic approach is expected to be more efficient, the toolchain implementation described in the following sections is based on the modular architecture.
+It is simple to implement, requires less modifications to the blockchain protocol and provides more flexibility.
 
@@
 to retrieve information from the blockchain.
-For this, the backend uses the Tezos client libraries.
-The command line interface of the toolchain provides options for configuring the host address and port of the RPC interface to connect to a specific node.
-This can be either a local or public node.
+For this, the backend uses the Tezos client libraries, which provide high-level functions wrapping RPCs to a configured node.
+The command line interface of the toolchain provides options for configuring the host address and port of the RPC interface to connect to a specific local or public node.
 By default, the toolchain tries to connect to a local node on the default port.
@@
 Because the frontend was designed to be generic, they may contain type, operations or expressions which are not supported by the target language.
-Therefore, the semantic check should reject any assertions which can not be translated to Michelson (more precisely, the whole assertion contract is rejected).
+Therefore, the semantic check should reject any input which cannot be translated to Michelson.
 
 As an additional restriction, quantifiers should only bind variables of primitive data types.
-As the majority of use-cases seem to require quantification over numerical values, the current implementation of the semantic check only accepts predicate variables of type \texttt{int} and \texttt{nat}.
+As the majority of use-cases seem to require quantification over numerical values, the current implementation of the semantic check restricts predicate variables to the types \texttt{int} and \texttt{nat}.
 Future iterations of the toolchain and protocol may add support for other primitive types, such as \texttt{string} or \texttt{bytes}.
 
-Semantic rules imposed by Michelson do not have to be checked explicitly by the toolchain --- the RPC interface of Tezos nodes provides a function to parse and type check Michelson programs, which can be used to verify the correctness of the compilation result.
+Semantic rules imposed by Michelson do not have to be checked explicitly by the toolchain --- the RPC interface of Tezos nodes provides a function to parse and type check Michelson programs, which can be used to verify the correctness of the compilation result and reject any assertions with containing typing or other semantic errors.
 
@@
 \end{lstlisting}
-As Tezos is currently the only target, the type differs only slightly from the generic type.
+As Tezos is currently the only supported target platform, the type differs only slightly from the generic type.
 If the assertion does not specify an explicit entrypoint tag, the optional value is replaced with Tezos' notation for the default entrypoint.
-The subtree types for the parameter pattern and the assertion remain equivalent to the generic types.
+The subtree types for the parameter pattern and the assertion remain equivalent.
 
@@
 Given a list of Tezos-specific ASTs, the task of the type checker is to link each AST to the respective entrypoint of the parent contract.
-This stage can thus be alternatively referred to as the linker.
-The linking is needed by the compiler for type inference and to correctly assemble the controller contract.
-As a simple example, the linker should correctly assign the ASTs of the first assertion in \texttt{Example.tza} (\lstref{lst:linker_assertion}) to entrypoint A, and the second assertion to entrypoint B of \texttt{Example.tz} ( \lstref{lst:linker_parent}).
+This stage module can be alternatively referred to as the linker.
+The linking is needed by the compiler to correctly assemble and type the controller and assertion contracts.
+As a simple example, the linker should correctly assign the AST of the first assertion in \texttt{Example.tza} (\lstref{lst:linker_assertion}) to entrypoint A of the parent contract \texttt{Example.tz} ( \lstref{lst:linker_parent}), and the second assertion to entrypoint B.
 
@@
 Tags, if specified, are only considered if type matching does not result in an unambiguous assignment.
-The linking fails, if an assertion cannot be matched to any parent entrypoint or several assertions match the same entrypoint, i.e., if no injective, non-surjective mapping was found.
+The linking fails, if an assertion cannot be matched to any parent entrypoint, or several assertions match the same entrypoint, i.e., if no injective, non-surjective mapping was found.
 
@@
 The parent contract is provided by the user as a file, a blockchain address, or a raw string.
-In case the contract is given as an address, the code is retrieved (as a string) from the blockchain.
-Parsing and extracting the list of entrypoints with their parameter type from the typed Michelson AST is handled by the Tezos libraries.
-The parameter pattern of each assertion AST is then compared recursively to the entrypoint types, until a match has been found --- this entrypoint is then blocked for other assertions.
+In case the contract is given as an address, the code is retrieved from the blockchain.
+The parameter pattern of each assertion AST is then compared recursively to the types of each entrypoint, until a match has been found --- this entrypoint is then blocked for other assertions.
 
@@
 
-The tags given in the assertion specification do not necessarily have to be identical with the tags of the parent contract (if the parent states explicit tags); in some cases, they may be chosen differently for documentation or for readability purposes.
+The tags given in the assertion specification do not necessarily have to be identical with the tags of the parent contract; in some cases, they may be chosen differently for documentation purposes.
 However, the tags can and should be used to resolve ambiguity in the mapping between assertions and entrypoints.
 \lstref{lst:ambiguity_assertion} provides four examples of assertions, which cannot be assigned unambiguously to an entrypoint of the contract given in \lstref{lst:ambiguity_parent}.
-The assertions in lines 1, 2 and 3 specify anonymous or named wildcards as parameter pattern, which matches any parameter type.
-Since none of them specify the explicit tag \texttt{A} or \texttt{B}, the linker cannot know to which entrypoint the assertions belong to.
-The assertion in line 4 specifies the parameter type, but as both entrypoints have the same raw parameter type and none of the tags match, this assertion is also not linkable.
+Since the entrypoints of \texttt{Example2.tz} have the same raw parameter type, and none of the given assertions tags refer to one of them explicitly, the linker cannot infer which entrypoint they refer to.
 In all four cases, providing the tag \texttt{A} or \texttt{B} resolves the ambiguity.
+If the parent entrypoint does not specify a tag, the ambiguity can be resolved by specifying the parameter type in respect to the default entrypoint, which is unambiguous by design.
 
@@
 Entrypoints \texttt{B} and \texttt{C} are sub-entrypoints of \texttt{BC} --- invoking \texttt{BC} will inevitably result in an invocation of either \texttt{B} or \texttt{C}, depending on the parameter value.
-Thus, assertions may ``overlap'', if a separate assertion is declared for a super- and a sub-entrypoint and result in two assertion specifications for the same entrypoint.
+Thus, assertions may ``overlap'' if a separate assertion is declared for a super- and a sub-entrypoint and result in two assertion specifications for the same entrypoint.
 Hence, the linker needs to detect overlapping assertions and reject assertion contracts where appropriate.
 
-In summary, the linker rejects any assertion contracts containing ambiguous, duplicate, overlapping and mismatching assertions.
-In case of failure, the problem is pointed out user.
+In summary, the linker rejects any input containing ambiguous, duplicate, overlapping or mismatching assertions, i.e., assertions whose types do not match any entrypoint.
 If each assertion could be linked to exactly one entrypoint, the mapping from entrypoint to assertion is returned.
-As entrypoints can be anonymous, the mapping represents the entrypoints by the constructor nesting of their parameters.
-The resulting mapping for \texttt{Example.tz} and \texttt{Example.tza}, for instance, is \\
+Because entrypoints can be anonymous, the mapping represents the entrypoints by the constructor nesting of their parameters.
+The resulting mapping for \texttt{Example.tz} and \texttt{Example.tza}, for instance, would be \\
 \texttt{\{ Left \textrightarrow <AST assertion A>; Right \textrightarrow <AST assertion B>\} }.
@@
 The compilation stage was not implemented within the scope of this thesis, but the following subsections describe the compilation procedures for generating the assertion and controller contracts.
-Furthermore, this section discusses the possibility to compile to a high-level language as an intermediate representation.
+Furthermore, this section discusses the alternative of compiling to a high-level language as an intermediate representation, instead of compiling to Michelson directly.
 
-With Michelson as the target language, the compiler has to generate code for a stack machine.
-After compilation, the Michelson programs can be validated for correctness by the Tezos node.
-This will intercept any assertions containing type errors.
-After sanity-checking the programs, the compiler returns the target code for the controller and assertion contracts.
-As an additional output, it should return a piece of template code for the correct storage initialization of the controller, where the user can fill in the blockchain addresses of the other modules.
+With Michelson as the compilation target language, the compiler has to generate code for a stack machine.
+After compilation, the Michelson programs can be validated for correctness by the Tezos node, which will intercept any assertions containing type errors.
+After sanity-checking the programs, the output of the compiler is the target code for the controller and assertion contracts.
+As an additional output, it should return a piece of template code for the correct storage initialization of the controller.
+Before originating the controller contract, the user fills in the blockchain addresses of the other modules.
 
@@
 \paragraph{Assertion entrypoints}
-If the entrypoint should trigger an assertion, the compiler has to generated code executing the following steps:
+If the entrypoint should trigger an assertion, the compiler has to generate code executing the following steps:
 \begin{enumerate}
@@
 \end{enumerate}
-\secref{sec:prob_threshold} stated a formula to determine the total number $t_{total}$ of required test runs for a given probability threshold $c$ and the size of the search space $n$.
+\secref{sec:prob_threshold} stated a formula to determine the total number $t_{total}$ of required test runs for a given probability threshold $c$, and the size of the search space $n$.
 From $t_{total}$, the number of test runs $t$ per validator can be calculated according to \eqref{eq:t_validator}.
-Since $n$ can only be obtained at runtime, the compiler needs to derive a formula to determine it from the ranges of the random generators.
+Since $n$ can only be obtained at runtime, the compiler needs to derive a formula to determine this value from the ranges of the random generators.
 \secref{sec:sample_space} already gave some examples of this.
-The threshold $c$, on the other hand, must be given as parameter to the compiler. Therefore, the command line interface of the toolchain should provide an option to set the threshold.
+The threshold $c$, on the other hand, must be given as a parameter to the compiler. Therefore, the command line interface of the toolchain should provide an option to set this threshold.
 
@@
 
-After compilation, this map is translated to a template for a Michelson value and returned to the user together with the contract code.
-Because the addresses are not known at the time of compilation, the values should be descriptive place-holders, s.t.
+After compilation, this map is translated to a template for a Michelson value and returned to the user.
+Because the addresses are not known at compilation time, the map values should be descriptive place-holders, s.t.
 the user can replace them with the corresponding addresses.
-The completed Michelson value should then be passed to the origination as the initial storage.
+After the user replaced the placeholders with the actual addresses, this Michelson value should then be passed to the origination as the initial storage.
 As an example, the compilation of the controller contract for \texttt{Example.tz} and \texttt{Example.tza} in Listings \ref{lst:linker_parent} and \ref{lst:linker_assertion} could return the following template:\\ \texttt{(Elt 0 <addr parent>; Elt 1 <addr A\_a>; Elt 2 <addr B\_a>)}.
@@
 This keeps the pipeline coherent and would allow to output Michelson contracts without any intermediate steps.
-If the compiler cannot be embedded directly into the toolchain (as is the case with Liquidity), the output of the would have to be compiled manually to Michelson in a separate step, as depicted in \figref{fig:pipeline_liq}.
+If the compiler cannot be embedded directly into the toolchain (as is the case with Liquidity), the output of the toolchain would have to be compiled manually to Michelson in a separate step, as depicted in \figref{fig:pipeline_liq}.
 
@@
 \paragraph{Comparison to direct compilation}
-This approach takes advantage of the usually more sophisticated high-level language compiler; they may provide options for optimizing generated code and are already thoroughly tested.
+This approach takes advantage of the usually more sophisticated high-level language compilers; they may provide options for optimizing generated code and are already thoroughly tested.
 In contrast to large and obscure Michelson programs, the output is more comprehensible and thus easier to test and verify.
@@
 The compiler of the respective language has to be extended with the \texttt{random} instruction as well, which requires forking the project.
-Furthermore, one has to rely on continuous support of new protocol versions in the root project and integrate the updates into the own code base regularly.
-To avoid such dependencies and increased effort in version management, this approach is not pursued in the development of the toolchain.
+Furthermore, one has to rely on continuous support of new protocol versions in the root project, and integrate the updates into the own code base regularly.
 
-However, a realistic use-case for using Liquidity as an IR is the implementation of the monolithic orchestration scheme.
+However, a realistic use-case for using Liquidity as an IR ,is the implementation of the monolithic orchestration scheme.
 In Liquidity, each entrypoint is declared as a function expecting a parameter and the current storage.
-During compilation, the contract parameter type and code branching is composed according to the order of functions.
+During compilation, the contract parameter type and code branching is composed according to the order of functions given in the source file.
 For instance, the entrypoint declarations in \lstref{lst:liq_eps} are compiled to the contract parameter type \texttt{(or (int \%A) (int \%B))} and two branches in the code body.
@@
 It stated \eqref{eq:gas_transaction} to calculate the gas consumption of a transaction, including internal operations.
-It identified the gas consumption of deserialization, data parsing and interpretation as growing factors, which depend on the size of the input parameter.
+It identified the gas consumption of deserialization, data parsing and interpretation as growing factors, as they depend on the size of the input parameter.
 
 According to the orchestration scheme, each validator executes $t+2$ operations with the same input parameter $p$.
-Since deserialization costs are applied lazily, they have to be paid only once for the parameter and the assertion contract code.
+Since they apply lazily, the deserialization cost for the parameter and assertion code only have to be paid once.
 In addition to the interpretation cost, the reading, parsing and base costs have to be paid for each internal operation.
@@
 \end{align}
-Based on the resulting inequality in \eqref{eq:gas_validator}, which specifies the costs incurred by each internal operation to the assertion contract as a basis of the total gas consumption per validator, it can be concluded that the overall gas consumption of the distributed validation is higher than in case of a local validation.
+Based on the resulting inequality in \eqref{eq:gas_validator}, which specifies the costs incurred by each internal operation to the assertion contract as a basis of the total gas consumption per validator, it can be concluded that the overall gas consumption of the distributed validation is higher than in the case of a local validation.
 
@@
 Appendix \ref{apx:foobar_distributed} contains the Michelson code for the controller, assertion and parent contracts.
-In order to preserve comparability between the local and the distributed implementation, the controller contracts were configured with a probability threshold $c = \frac{1}{e}$, s.t.
+In order to preserve comparability between benchmark of the local and the distributed implementation, the controller contracts were configured with a probability threshold $c = \frac{1}{e}$, s.t.
 that the necessary number of test runs is equal to the sizes of the search spaces.
-\figref{fig:cost_distributed} shows the reported gas consumption per validator on the test network Delphinet.
+\figref{fig:cost_distributed} shows the reported gas consumption per validator on the test network Delphinet for different input sizes.
 Since the effective number of test runs is always a multiple of 32, the cost function approximates a step function.
@@
 \centering
-\includegraphics[width=0.9\linewidth]{figures/5-offline_tezos/cost_analysis}
-\caption{Gas consumption per validator for different input sizes}
+\includegraphics[width=\linewidth]{figures/5-offline_tezos/cost_analysis}
+\caption{Gas consumption per validator for different input sizes n}
 \label{fig:cost_distributed}
@@
 In the case of the list parameter (contract \texttt{Bar}), the gas consumption even increases exponentially due to the multiplied reading and parsing costs.
-Moreover, the probability of accepting an invalid parameter with the given configuration is 37\% in the worst case, which results in a bad cost-performance ratio.
+Moreover, the probability of accepting an invalid parameter with the given configuration is, in the worst case, 37\%, which results in a bad cost-performance ratio.
 
 In conclusion to these results, the proposed implementation of the distributed scheme has to be evaluated as inefficient and unable to achieve an improvement regarding the scalability of applications on Tezos.
-However, distributed assertion checking is nonetheless a promising approach to achieve an improvement, as it has the potential to not only lower the transaction costs for the user, but also to reduce the computational footprint of the transaction within the network.
-A prerequisite is lowering the gas consumption per validator.
-This thesis already mentioned some alternative approaches and implementations, which could achieve this; \secref{sec:alt_random} introduces the possibility to coordinate the validators in a systematic iteration of the search space.
+However, the approach is nonetheless promising, as it reduces the required computation per node to a fraction of the verification, and thus also reduces the computational footprint of the transaction within the network.
+As a prerequisite, it is crucial to lower the costs of the verification.
+This thesis already mentioned some alternative approaches and implementations, which might achieve this; \secref{sec:alt_random} introduces the possibility to coordinate the validators in a systematic iteration of the search space.
+Although this does not reduce the cost per test run, this reduces the quantify of necessary test runs to achieve a reliable result.
 This chapter described several other orchestration schemes, some of which reduce the number of emitted internal operations.

### 2021-05-11 assertions/examples/main.tex
Updates assertion examples document

@@
 \usepackage{amsmath}
+\usepackage{amsfonts}
 \usepackage{xfrac}
@@
 \newcommand{\todo}[1]{\textbf{\textcolor{red}{(TODO: #1)}}\refstepcounter{todos}\label{todo \thetodos}}
+\renewcommand{\vec}[1]{\mathbf{#1}}
+\newcommand{\mat}[1]{\mathbf{#1}}
+\usepackage{makecell}
 
@@
     \end{itemize}
+    \item \textbf{Matrices}
+    \begin{itemize}
+        \item Identity matrix $\mathbb{I}$: square matrix with only diagonal ones, else zeros
+        \item Logical matrix (only one or zero entries), matrix of ones (only one entries), zero matrix, ...
+        \item Symmetric matrix: $\mat{A} = \mat{A}^T$
+        \item Orthogonal matrix: $\mat{A}\mat{A}^T = \mathbb{I}$
+        \item Correct calculation result, e.g.
+matrix multiplication, multiplication with a constant, addition, ...
+(which might be more involved and mostly need all terms for verification, which is memory consuming)
+    \end{itemize}
 \end{itemize}
@@
 Given that $F$ and $\mathcal{A}$ are encoded like this, the assumption that $\mathcal{A}$ satisfies $F$ can be expressed in predicate logic as follows:
-\begin{gather*}\label{eq:cnf_sat_formal}
+\begin{gather*}\label{eq:cnf_sat_formal_1}
 \begin{aligned}
@@
 The transformed formula to check for any counterexamples is then:
-\begin{gather*}\label{eq:cnf_sat_formal}
+\begin{gather*}\label{eq:cnf_sat_formal_2}
 \begin{aligned}
@@
 \begin{equation}\label{eq:coprime-universial}
-    (a < b): (\forall n) (2 \le n \le a) \Rightarrow \neg((a \mathbin{\%} n) = 0 \land (b \mathbin{\%} n) = 0)
+    (\forall n) (2 \le n \le \min(a,b)) \Rightarrow \neg((a \mathbin{\%} n) = 0 \land (b \mathbin{\%} n) = 0)
 \end{equation}
@@
 \begin{equation}\label{eq:coprime-existential}
-    (a < b): (\exists n) (2 \le n \le a) \land ((a \mathbin{\%} n) = 0 \land (b \mathbin{\%} n) = 0)
+    (\exists n) (2 \le n \le \min(a,b)) \land (a \mathbin{\%} n) = 0 \land (b \mathbin{\%} n) = 0
 \end{equation}
-When it is ensured that the greater number is not evenly divided by the smaller one ($b\mathbin{\%}a=0$), the search space can reduced by half to $(2 \le n \le \lfloor \frac{a}{2} \rfloor)$, because in the upper half of the lower number no integer can evenly divide this number.
+When it is ensured that the greater number is not evenly divided by the smaller one ($\max(a,b)\mathbin{\%}\min(a,b)=0$), which automatically would then be a counterexample, the search space can reduced by half to $(2 \le n \le \lfloor \frac{a}{2} \rfloor)$, because in the upper half of the lower number no integer can evenly divide this number.
 
@@
 \begin{equation}\label{eq:lcm-existential}
-    (a < b): (\exists n) (2 \le n < \frac{lcm}{b}) \land ((b*n) \mathbin{\%} a = 0)
+    (\exists n) (2 \le n < \frac{lcm}{\max(a,b)}) \land ((\max(a,b)*n) \mathbin{\%} \min(a,b) = 0)
 \end{equation}
@@
 So to check if an array $a$ fulfills the min heap property, we can formulate it in the following predicate logic:
-\begin{equation}\label{eq:heap-unversial}
+\begin{equation}\label{eq:heap-unversial_1}
   (\forall k) (1 \le k < |a|) \Rightarrow a[\lfloor(k-1)/2)\rfloor] \le a[k]
@@
 (Following the Exposé) The direction could also be turned around and every parent node could be checked against its child nodes, which does not change the number of comparisons.
-\begin{equation}\label{eq:heap-unversial}
+\begin{equation}\label{eq:heap-unversial_2}
   (\forall k) (0 \le k \le \lfloor |a|/2 \rfloor) \Rightarrow a[k] \le a[2k+1] \land (2k+2 < |a| \Rightarrow a[k] \le a[2k+2])
@@
 This test would need $\mathcal{O}(|a|)$, i.e., linear time complexity. To find a contradiction this can be formulated to
-\begin{equation}\label{eq:heap-unversial}
+\begin{equation}\label{eq:heap-unversial_3}
   (\exists k) (1 \le k \le |a|) \land a[\lfloor(k-1)/2)\rfloor] > a[k]

### 2021-05-13 assertions/doc/thesis-bernhardt/chapters/0_2-abstract.tex
Final revision part 1

@@
 \chapter*{Abstract}
-Modern blockchains provide a platform for building sophisticated applications with Smart Contracts.
-Because transactions are processed at every node in the network, the quantity and complexity of computations, which can be performed by Smart Contracts, are limited.
+Modern blockchains provide a platform for building sophisticated applications with smart contracts.
+Because transactions are processed at every node in the network, the quantity and complexity of computations, which can be performed by smart contracts, are limited.
 Furthermore, complex contracts can generate high transaction costs for the user.
 To overcome this limitation and improve cost efficiency, blockchain-based applications could move computations to an off-chain component and only process the result on the blockchain.
-This thesis proposes a processing model, which engages the validators of the network in a distributed effort to verify a submitted off-chain computation.
+This thesis proposes a processing model for the Tezos blockchain, which engages the validators of the network in a distributed effort to verify a submitted off-chain computation.
 Based on a specification of properties, the validators are challenged to find a counterexample by asserting these properties for independent subsets of the result.
 This reduces the computational effort on the blockchain to the verification of the result, rather than the computation of the result itself.
-Moreover, by implementing a distributed scheme, each node  only has to process a fraction of the verification.
-As a further contribution, this thesis defines a domain-specific language to express explicit assertions for off-chain computations and specifies a processing pipeline to transform and compile these assertions into Smart Contracts.
-These contracts conduct a point-wise search for a counterexample and are called during the verification process.
-A proof-of-concept implementation of this pipeline is provided and described for the target platform Tezos.
+Moreover, by implementing a distributed scheme, each node only processes a fraction of the verification.
+For this processing model, this thesis contributes a domain-specific language to express explicit assertions for off-chain computations and specifies a processing pipeline to transform and compile these assertions into smart contracts.
+These contracts conduct a point-wise search for a counterexample and are called during the verification mechanism.
+The provided proof-of-concept implementation of this pipeline targets Tezos, but is by design extendible for other blockchains supporting smart contracts.

### 2021-05-13 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
Revision
Final revision part 1

--- 2021-04-21 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
@@
 Some prominent examples for such blockchains are Ethereum \cite{eth-whitepaper}, Tezos \cite{goodman_tezos_2014} or Cardano \cite{cardano_essay}, which plans to introduce smart contracts in an update this year \cite{cardano_alonzo}.
-Blockchain-based applications are built with smart contracts, programs written in Turing-complete languages.
+Blockchain-based applications are built with smart contracts, i.e., programs written in Turing-complete languages.
 Running a smart contract generates costs proportional to the amount and complexity of computations, as well as its storage usage \cite{alharby_blockchain_2017}.
@@
 In reality, however, meaningful applications still might need to perform resource intensive computations or store larger amounts of data.
-Not only can such applications generate unsustainable costs when executed on the blockchain, but they may also reach gas limits imposed by the blockchain's protocol.
+Not only can such applications generate unsustainable costs when run on the blockchain, but they may also reach gas limits imposed by the blockchain's protocol.
 \\
-In order to avoid these costs and restrictions, such an application could perform some computations outside of the blockchain context (i.e., off-chain) and only submit the results to a smart contract as an input parameter for further processing or recording.
+In order to avoid these costs and overcome gas restrictions, an application could perform some computations outside of the blockchain context (i.e., off-chain) and only submit the results to a smart contract as an input parameter for further processing or recording.
 By trusting that the submitted results are correct, this approach raises both safety and security issues.
@@
 Although in many cases, verifying a solution takes less time than computing the result itself (cf.
-NP-hard problems \cite{nph_problems} or sorting algorithms \cite{review_sorting}\cite{cpp_issorted}), the generated costs for checking the validity increase with the size of the input.
+NP-hard problems \cite{nph_problems} or sorting algorithms \cite{review_sorting}\cite{cpp_issorted}), the generated costs for checking the validity increase with the size or dimension of the input parameter.
 \\
@@
 
-\section{A distributed approach for assertion checking}
-A more efficient way to solve the issue at hand could be to engage the validators of the blockchain into a distributed effort to find a counterexample.
-If no counterexample could be found by any validator, the assumption is considered to be valid and the execution of the contract may resume.
+\section{Distributed Assertion Checking}
+A more efficient way to solve the issue at hand could be to engage the validators of the blockchain into a distributed effort of finding a counterexample.
+If none of the validators was able to find a counterexample, the assumption is considered to be valid and the execution of the contract may resume.
 On the other hand, an identified counterexample is made public on the peer-to-peer network and thus cancels the contract execution (i.e., the transaction fails).
 \\
-In order to find a counterexample, the formula in \eqref{eq:prime} has to be transformed to its negation:
+In order to find a counterexample for the assumption ``$p$ is a prime number'', the assertion in \eqref{eq:prime} has to be transformed to its negation:
 \begin{equation}\label{eq:prime_neg}
@@
 
-Each validator then checks the inverse property $(p \% n) = 0$ point-wise for some random $n$ within the given boundaries $2 \le n \le \sqrt{p}$.
-If a validator finds a counterexample, i.e., a value for $n$ where the reminder is $0$, it posts a veto to the network.
-For each involved validator, the constant cost of generating one random number and calculating one division have to be paid, which is independent from $p$.
+Each validator then checks the inverse property $(p \% n) = 0$ point-wise for some random number $n$ within the given boundaries $2 \le n \le \sqrt{p}$.
+If a validator finds a counterexample, i.e., a value for $n$ where the remainder is $0$, it posts a veto to the network.
+For each involved validator, the constant cost of generating one random number and calculating one division have to be paid, which is independent of the magnitude of $p$.
 \\
 However, distributed assertion checking is not only applicable for parameters or properties of dynamic size.
-Function \texttt{find} of contract \texttt{Sorted}, shown in \lstref{lst:sorted}, expects a statically sized array of integers and a single integer value.
+The function \texttt{find} of contract \texttt{Sorted}, shown in \lstref{lst:sorted}, expects a statically sized array of integers and a single integer value.
 In order to find the value \texttt{v} in \texttt{a} more efficiently, the array is assumed to be sorted.
 
-\begin{lstlisting}[caption=Smart contract expecting a sorted array \cite{thiemann_2020}, numbers=none, language=Solidity, label=lst:sorted]
+\begin{lstlisting}[caption=Smart contract expecting a sorted array and an integer \cite{thiemann_2020}, numbers=none, language=Solidity, label=lst:sorted]
 contract Sorted {
@@
     ...
-  }
-}
+ }}
 \end{lstlisting}
@@
 
-Since the validators sample the domain randomly, the absence of a counterexample doesn't prove that the assumption is correct; the validation is only probabilistic and the reliability depends on the number of validators in the network.
+Since the validators sample the domain randomly, the absence of a published counterexample doesn't prove that the assumption is correct; the validation is probabilistic and its reliability depends on the ratio between the number of validators in the network and the input size.
 This corresponds to the principle of Bloom filters, where a queried element is either ``certainly not'' or ``possibly'' a member of a defined set \cite{blustein_bloom_2002}.
-In the case of assertion checking, we consider the assumption to be either definitely not or possibly valid.
+In the case of assertion checking, we consider the assumption to be either definitely invalid or possibly valid.
 The probability of false positives in Bloom filters is an approximate function of the filter size and the number of inserted elements, supposing an optimal number of hash functions have been implemented.
 Tuning these parameters is a trade-off between making the filter more reliable, i.e., lowering its error rate, and space efficiency \cite{blustein_bloom_2002}.
-The same applies, with some reservations, to distributed assertion checking: fewer samples keep the gas consumption (and thus cost) to a minimum, whereas more samples reduce the probability of accepting an invalid result.
+The same applies, with some reservations, to distributed assertion checking: fewer samples keep the gas consumption (and thus cost) low, whereas more samples reduce the probability of accepting an invalid input parameter.
 Referring to the example of sorted lists, the probability of false positives depends on the size of the list $a$ and the number of validators $m$.
@@
 The importance of the former parameter becomes apparent when considering the worst case scenario of the same example.
-Assuming the array is unsorted at exactly one position - the probability that the each of the $m$ validators independently check this position is $\frac{1}{|a|}$, whereas the probability of all of them checking any other position $\frac{|a|-1}{|a|}$.
-If the random generator chooses each value for $n$ independently from a uniform distribution, the probability that the counterexample is not detected by any validator converges to 0 if the number of validators approaches infinity \cite{thiemann_2020}:
+Assuming the array is unsorted at exactly one position and the random generator chooses each value for $n$ independently from a uniform distribution, the probability that a validator checks this position is $\frac{1}{|a|}$, whereas the probability of checking any other position is $\frac{|a|-1}{|a|}$.
+Hence, the probability that the counterexample is not detected by any of the $m$ validators converges to 0 if $m$ approaches infinity \cite{thiemann_2020}:
 \begin{equation}\label{eq:limes_validators}
@@
 When claiming an assertion failure, a validator publishes a counterexample to be scrutinized by the other validators.
-If they come to a consensus about the invalidity, the result is rejected.
-Provided that the assertion is cheaper than the computation itself, the purpose of this proposal is not only to reduce financial costs for the users, but also to overcome limitations in scalability imposed by gas limits.
+If they come to a consensus about the invalidity, the transaction submitting the computation result is rejected.
+Provided that the verification using these assertions is cheaper than the computation itself, the purpose of this proposal is not only to reduce financial costs for the users, but also to overcome limitations in scalability imposed by gas limits.
 
@@
 The off-chain component is a toolchain to specify, integrate and generate assertion contracts that can be deployed to the blockchain.
-This includes the definition of a domain-specific language, which allows developers to specify assertions for each entrypoint of a Smart Contract.
+This includes the definition of a domain-specific language, which allows developers to specify assertions for each entrypoint of a smart contract.
 The on-chain component, on the other hand, consists of an amendment of the blockchain protocol.
-This amendment includes an extension of the Smart Contract language with instructions generating random values in a non-deterministic way, a transaction type that can trigger the distributed execution of assertions, and the implementation of a consensus mechanism for counterexamples.
+This amendment includes an extension of the smart contract language with instructions generating random values in a non-deterministic way, a transaction type that can trigger the distributed execution of assertions, and the implementation of a consensus mechanism for counterexamples.
 
@@
 
-\section{Related work}
+\section{Related Work}
 Outsourcing computations or storage to off-chain resources, in order to improve the scalability of blockchains, has been the topic of several research papers and projects.
@@
 When such proofs are supplied together with the results, the correctness can be validated fast and cheaply by the miners and nodes of the network.
-They additionally provide a toolbox and a domain-specific language to specify off-chain computations, generate respective proofs and export Smart Contracts verifying these proofs.
+They additionally provide a toolbox and a domain-specific language to specify off-chain computations, generate respective proofs and export smart contracts verifying these proofs.
 
@@
 
-\section{Structure overview}
+\section{Structure Overview}
 The structure of this thesis is as follows: in the first instance, \chapref{chap:use_cases} defines a set of logical formulas suitable for the proposed scheme of distributed assertion checking.
@@
 they can later be used as a benchmark to assess the efficiency of the distributed approach.
-\chapref{chap:offline} describes the frontend of the toolchain and generic aspects of the off-chain design.
+\chapref{chap:offline} describes the assertion language, the frontend of the toolchain and generic aspects of the off-chain design.
 As a premise for the toolchain backend, \chapref{chap:prob_model} defines the probabilistic model of the scheme and analyses the effectiveness of the probabilistic validation.
-After providing a brief introduction to the Tezos blockchain and its Smart Contract language Michelson, \chapref{chap:offline_tezos} covers target specific aspects of the off-chain design and the implementation of the toolchain backend.
-The chapter closes with an evaluation of the proposed scheme based with regard to Tezos as the target platform.
+After providing a brief introduction to the Tezos blockchain and its smart contract language Michelson, \chapref{chap:offline_tezos} covers target specific aspects of the off-chain design and the implementation of the toolchain backend.
+The chapter closes with an evaluation of the proposed scheme with regard to Tezos as the target platform.
 In conclusion, the last chapter recaps the achieved results, addresses open questions or issues and provides an outlook on upcoming work on this topic.

### 2021-05-13 assertions/doc/thesis-bernhardt/chapters/2-use_case_analysis.tex
Final revision part 1

@@
-\chapter{Use-case analysis}\label{chap:use_cases}
-The introduction argued, that validating properties on input parameters can become costly when data structures (such as arrays), certain data types (such as byte sequences) or a range of values have to be iterated.
+\chapter{Use-case Analysis}\label{chap:use_cases}
+The introduction argued that validating properties on input parameters can become costly when data structures (such as arrays), certain data types (such as byte sequences) or a range of values have to be iterated.
 It showed examples for such properties and identified logical formulas containing universal quantification as amenable for distributed assertion checking.
@@
 The following section formally defines a set of applicable logical formulas for the basic implementation of the distributed assertion checking scheme.
-Given this set, section \secref{sec:examples} gives some more in-depth examples of such formulas.
-As a benchmark for the distributed scheme, the last section formalizes the cost incurred by checking formulas on Tezos locally.
+\secref{sec:examples} gives some examples of such formulas.
+As a benchmark for the distributed scheme, the last section formalizes the cost incurred by checking formulas on Tezos in a non-distributed approach.
 
-\section{Definition of a set of logical formulas}\label{sec:formulae}
-The set of formulas, which can be expressed in well-formed assertions, is given in \figref{fig:formulas}.
+\section{A Set of Logical Formulas}\label{sec:formulae}
+The set of formulas that can be expressed in well-formed assertions, is given in \figref{fig:formulas}.
 This corresponds, with some restrictions, to the language of second-order predicate logic.
@@
 Specific to the target blockchain are the sets of types $t$ and functional symbols $f$.
-These can only contain types and operations, which can be translated to instructions of the respective Smart Contract language and interpreted by the blockchain's virtual machine (VM).
-As an example, the primitive types in Michelson are \texttt{string}, \texttt{nat}, \texttt{int}, \texttt{bytes}, whereas Ethereum's Smart Contract language Solidity  \cite{solidity_docs} additionally supports an \texttt{enum} type and fixed-point numbers.
+These can only contain types and operations, which can be translated to instructions of the respective smart contract language and interpreted by the blockchain's virtual machine (VM).
+As an example, the primitive types in Michelson are \texttt{string}, \texttt{nat}, \texttt{int} and \texttt{bytes}, whereas Ethereum's smart contract language Solidity \cite{solidity_docs} additionally supports an \texttt{enum} type and fixed-point numbers.
 \begin{align*}
@@
 \begingroup\vspace*{-\baselineskip}
-\captionof{figure}{Set of logical formulas amenable to distributed assertion checking (based on \cite{thiemann_2020})}
+\captionof{figure}{Set of logical formulas amenable to distributed assertion checking}
 \label{fig:formulas}
@@
 
-\section{Examples and special cases}\label{sec:examples}
+\section{Examples and Special Cases}\label{sec:examples}
 This section contains a subset of use-cases that were collected in collaboration with Julian Veigl for an intermediate report \cite{bernhardt_veigel_2020}.
@@
 
-\subsection{Two numbers are coprime}\label{sec:coprime}
+\subsection{Two Numbers are Coprime}\label{sec:coprime}
 The greatest common divisor ($gcd$) of two non-zero integers $a$ and $b$ is the largest integer that divides both evenly \cite{hardy2008introduction}.
@@
 \end{equation}
-If, within the given domain, this condition is true for a random value for $n$, the respective validator has found a counterexample.
+If, within the given domain, this condition is true for a random value of $n$, the respective validator has found a counterexample.
 
-\subsection{Heap property}
+\subsection{Heap Property}
 Heaps \cite{dict_heap} are data structures based on trees and can appear in two varieties: min and max heaps.
@@
 \end{lstlisting}
-The min heap property for a binary heap stored in an array $a$, for instance, can be expressed in predicate logic with the following formula:
+The min heap property for a binary heap stored in an array $a$ can be expressed in predicate logic with the following formula:
 \begin{equation}\label{eq:heap-unversial}
@@
 The time complexity of checking whether $a$ satisfies the heap property depends on how the array is allocated.
-If it is dynamically sized, it takes $\mathcal{O}(n)$ in the size of the array, otherwise it takes constant time, i.e.
-$\mathcal{O}(1)$.
+If it is dynamically sized, it takes $\mathcal{O}(n)$ in the size of the array, otherwise it takes constant time, i.e., $\mathcal{O}(1)$.
 Similarly to the previous examples, counterexamples can be identified by considering the formula's negation:
@@
 
-\subsection{Existential quantification - intersection of sets}\label{sec:existential}
-So far, this thesis only considered formulas featuring universal quantification, for which the assertion scheme engaged the validators to find counterexamples.
+\subsection{Existential Quantification - Intersection of Sets}\label{sec:existential}
+So far, this thesis only considered formulas featuring universal quantification, for which the assertion scheme engages the validators to find counterexamples.
 However, distributed assertion checking can not only be used to refute assumptions, but also to prove their validity.
 This is the case for formulas featuring existential quantification.
-As an example, consider the assumption that two sets $U$ and $V$ have a non-empty intersection, i.e., $U \cap V \neq \emptyset$.
-This assumption and its negation can be expressed in predicate logic by
+As an example, consider the assumption that the two sets $U$ and $V$ have a non-empty intersection, i.e., $U \cap V \neq \emptyset$.
+If these sets are represented as arrays or lists, this property and its negation can be expressed in predicate logic by
 \begin{equation}\label{eq:intersect}
@@
 \end{equation}
-If the condition $u[i] \neq v[j]$ is false for random values of $i$ and $j$, it does not produce a counterexample --- it produces a proof for the validity of the assumption, because it identified an element that is present in both sets.
+Due to the universal quantifiers in the negation, finding random values for $i$ and $j$ for which the condition $u[i] \neq v[j]$ is valid does not produce a counterexample.
+If the condition is false, however, it produces a proof for the validity of the assumption, as it identified an element that is present in both sets.
 In that case, the validator finding such a proof should publish an approval instead of a veto to the network.
@@
 
-\subsection{Nested quantification - SAT problems}
+\subsection{Nested Quantification - SAT Problems}
 The previous example demonstrated that universal and existential quantification have to be handled differently.
@@
 $\forall i \forall j$, can be considered as trivial.
-They are translated to code, which generates a random value for each predicate variable and checks for a counterexample or proof respectively.
+They can be translated to code generating a random value for each predicate variable and checking for a counterexample or proof respectively.
 It becomes less trivial, if the nesting contains both universal and existential quantifiers.
@@
 Modern SAT-solvers expect $F$ to be in conjunctive normal form (CNF), i.e., a conjunction of a set of clauses, where clauses are disjunctions of variables or their negations (called literals) \cite{cnf_math_encycl}.
-While finding an assignment $\mathcal{A}$ that satisfies $F$ is a NP-complete problem \cite{Biere2009}, verifying whether a given assignment satisfies the formula takes $\mathcal{O}(n*m)$, where $n$ is the number of clauses and $m$ the number of variables (in the worst case, every variable is present as a literal in each clause).
-In the case of k-SAT problems, where each clause contains at most k literals \cite{Biere2009}, the complexity is reduced to $\mathcal{O}(n)$.
+While finding an assignment $\mathcal{A}$ that satisfies $F$ is a NP-complete problem, verifying whether a given assignment satisfies the formula takes $\mathcal{O}(n*m)$, where $n$ is the number of clauses and $m$ the number of variables (in the worst case, every variable is present as a literal in each clause).
+In the case of k-SAT problems, where each clause contains at most k literals, the complexity is reduced to $\mathcal{O}(n)$.
 
-\subsubsection{Encoding of variables, literals and clauses}
+\subsubsection{Encoding of Variables, Literals and Clauses}
 A SAT problem can be represented as a list of clauses $c$ and a variable assignment $\mathcal{A}$.
-To avoid having to handle the variables and their literals as strings, and thus optimize runtime and memory consumption, an encoding scheme \cite{sabablog} is used in the following.
+To avoid having to handle the variables and their literals as strings, and thus optimize runtime and memory consumption, the following uses an encoding scheme \cite{sabablog}.
 
@@
 
-\subsubsection{Satisfiability in predicate logic - CNF}
+\subsubsection{Satisfiability in Predicate Logic - CNF}
 Consider a contract that expects a SAT problem in CNF and a proposed assignment, both encoded as described above.
@@
 However, by checking a random literal in a random clause, the validator cannot make a definite statement about whether $\mathcal{A}$ satisfies $F$.
-Each clause has to be examined as a whole in order to verify, that the conjunction evaluates to true.
+Each clause has to be examined as a whole in order to verify that the conjunction evaluates to true.
 Consequently, the distribution can only take place on the level of clauses, but not on the level of literals.
-Each validator thus has to check all literals of one random clause, which translates into a random generator for the outer quantifier, and a loop for the inner quantifier.
+Each validator thus has to check all literals of one random clause, which translates into a random generator for the universal quantifier, and a loop for the existential quantifier.
 Whether the assertion requires a proof or a counterexample can be derived from the outer quantifier, hence validators produce a counterexample in this case.
@@
 
-\subsubsection{Satisfiability in predicate logic - DNF}\label{sec:dnf}
-The same propositional formula, with the reversed quantification nesting $\exists i \forall j$, describes the assertion for the assumption $\mathcal{A}(F) = 1$, where $F$ is given in disjunctive normal form (DNF), i.e., a disjunction of conjunctions \cite{dnf_math_encycl}:
+\subsubsection{Satisfiability in Predicate logic - DNF}\label{sec:dnf}
+The same propositional formula with the reversed quantification nesting $\exists i \forall j$, describes the assertion for the assumption $\mathcal{A}(F) = 1$, where $F$ is given in disjunctive normal form (DNF), i.e., a disjunction of conjunctions \cite{dnf_math_encycl}:
 \begin{equation}\label{eq:dnf_sat}
@@
 
-\subsection{Further nesting}
+\subsection{Further Nesting}
 Nesting is, of course, not limited to two quantifiers.
@@
 
-\section{Restriction of use-cases}\label{sec:restrict}\todo{Better title?}
+\section{Restriction of Use-cases}\label{sec:restrict}
 The examples given in this chapter have shown that, depending on the type and order of quantification, not all properties can be checked in the same way and need different modi of assertion checking.
@@
 
-\section{Cost analysis of a local approach}\label{sec:usecase_cost}
-For the purpose of having a benchmark for the evaluation of the distributed approach, this section analyses the cost of invoking a contract on the blockchain, which checks a formula locally.
+\section{Cost Analysis of a Local Approach}\label{sec:usecase_cost}
+For the purpose of having a benchmark for the evaluation of the distributed approach, this section analyses the cost of invoking a contract on the blockchain which checks a formula locally.
 Given that the target blockchain is Tezos, the computational and storage-related costs of a transaction are represented in units of gas.
@@
 Thus, the increase in overall costs is mainly accounted for by the interpretation cost.
-Contract \texttt{Bar}, on the other hand, executes similar operations in function \texttt{bar}, but expects a list of integers.
-The list data type additionally causes higher deserialization and parsing costs with increasing input sizes.
-\begin{lstlisting}[numbers=none, language=Solidity, caption=Simple dummy contract executing a loop]
+Contract \texttt{Bar}, on the other hand, executes similar operations as function \texttt{foo} in function \texttt{bar}, but expects a list of integers instead.
+The list data type uses notably more memory with increasing input sized and thus causes higher deserialization and parsing costs on top of the interpretation cost.
+\begin{lstlisting}[numbers=none, language=Solidity, caption=Simple dummy contract expecting an integer and executing a loop]
 contract Foo {
@@
 \end{lstlisting}
-\begin{lstlisting}[numbers=none, language=Solidity, caption=Simple dummy contract iterating over a list]
+\begin{lstlisting}[numbers=none, language=Solidity, caption=Simple dummy contract expecting iterating over a list]
 contract Bar {
@@
 
-\figref{fig:use_case_cost} shows the reported gas consumption of transactions calling corresponding dummy contracts in Michelson (cf.
+\figref{fig:use_case_cost} shows the reported gas consumption of transactions calling the corresponding dummy contracts implemented in Michelson (cf.
 Appendix \ref{apx:cost_analysis_contract}) on the Delphinet test network \footnote{\url{https://tezos.gitlab.io/introduction/test_networks.html\#delphinet}}.
@@
 \includegraphics[width=0.9\linewidth]{figures/2-use_cases/cost_analysis}
-\caption{Gas consumption of contracts \texttt{Foo} and \texttt{Bar} for increasing inputs}
+\caption{Gas consumption of contracts \texttt{Foo} and \texttt{Bar} for increasing input sizes}
 \label{fig:use_case_cost}

### 2021-05-13 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Final revision part 1

--- 2021-04-21 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
@@
-\chapter{Toolchain Implementation - Frontend}\label{chap:offline}
-The purpose of the toolchain is to support the process from specifying assertions to generating assertion Smart Contracts that can be invoked on-chain by the validators.
+\chapter{Toolchain Frontend}\label{chap:offline}
+The purpose of the toolchain is to support the process from specifying assertions to generating assertion smart contracts that can be invoked on-chain by the validators.
 As determined in \secref{sec:restrict}, the current version of the toolchain only supports the processing of assertions featuring universal quantification.
-The toolchain was developed in the programming language OCaml \cite{ocaml_docs} --- the code is available in a GitHub\footnote{\url{https://github.com/proglang/thesis-distributed-assertion-checking}\todo{commit}} repository of the Chair of Programming Languages.
+The toolchain was developed in the programming language OCaml \cite{ocaml_docs} --- the code is available in a GitHub\footnote{\url{https://github.com/proglang/thesis-distributed-assertion-checking/commit/7c22038cebe44f779621d241a8ab156e105ead0c}} repository of the Chair of Programming Languages.
 
@@
 
-\section{Assertion syntax}\label{sec:syntax}
-Tezos' Smart Contract language Michelson is a low-level and stack-based language.
+\section{Assertion Syntax}\label{sec:syntax}
+Tezos' smart contract language Michelson is a low-level and stack-based language.
 Specifying assertions in such a target-specific language is complex and inconvenient, especially if the language should be compiled to other targets as well.
@@
 
-\subsection{Code structure}
+\subsection{Code Structure}
 Assertions are passed to the toolchain as simple text files.
-This thesis follows the convention of using the file extension \texttt{.tza} for such files (henceforth referred to as ``assertion contracts'') in reference to the file extension \texttt{.tz} used for Michelson source files.
-An assertion contract is always associated with a Smart Contract (henceforth referred to as ``parent contract'') and contains at least one assertion for a specific entrypoint thereof.
-For the remaining entrypoints, the compiler automatically generates empty assertions (cf.
+This thesis follows the convention of using the file extension \texttt{.tza} for such files (henceforth referred to as ``assertion contracts''), in reference to the file extension \texttt{.tz} used for Michelson source files.
+An assertion contract is always associated with a smart contract (henceforth referred to as ``parent contract'') and contains at least one assertion for a specific entrypoint thereof.
+For the remaining entrypoints, the compiler should automatically generate empty assertions (cf.
 \secref{sec:compiler}).
@@
 
-How the assertions are associated with the respective entrypoint of the parent contract, depends on the Smart Contract language.
+How the assertions are associated with the respective entrypoint of the parent contract, may depend on the smart contract language.
 In the case of Solidity, a tag that mirrors the function name is enough to link assertion and entrypoint.
@@
 
-\subsection{Parameter patterns}
+\subsection{Parameter Patterns}
 \lstref{lst:patterns} gives an overview of the parameter patterns supported in the assertion language.
@@
 
-\subsection{Types and operations}
+\subsection{Types and Operations}
 In order to make the frontend generic, the sets of data types and operations supported by the grammar constitute unions of those present in the target languages.
@@
 Domain specific operations have not been included yet, but they may be added to the language if necessary.
+\\
 
-\subsection{Example}
-As an example, consider a variation of the explicit assertion for sorted lists, stated in \eqref{eq:sorted_v2}.
+Let us consider a variation of the explicit assertion for sorted lists, stated in \eqref{eq:sorted_v2}.
 In contrast to the variation given in the introduction (\eqref{eq:sorted}), which translates to comparing a random element of the list with its direct neighbour, this translates to a comparison of two random elements (under the constraint $n < m$).
@@
 The body is a nesting of two universal quantifiers, which declare the predicate variables $n$ and $m$ of type integer (lines 2 and 3), followed by a nesting of conditions.
-The conditions define the domains of the quantifiers (lines 4-6), corresponding to the premise of the formula.
+The conditions define the domains of the quantifiers (lines 4-7), corresponding to the premise of the formula.
 The body of the last condition (line 7) ultimately contains the keyword \texttt{assert} followed by a condition checking the property of ascending order, i.e.,  $a[n] \leq a[m]$.
@@
 \item \textbf{if-else conditions} to adapt the domains of quantifications if certain conditions hold.
-The assertion checking whether two numbers are relatively prime (discussed in \secref{sec:coprime}) is a good use-case for this feature: Firstly, the formula requires to determine the minimum of the given numbers --- however, the \texttt{min}-function might not be supported as a built-in function by the target language (as is the case on Tezos).
+The assertion checking whether two numbers are relatively prime (introduced in \secref{sec:coprime}) is a good use-case for this feature: firstly, the formula requires to determine the minimum of the given numbers --- however, the \texttt{min}-function might not be supported as a built-in function by the target language (as is the case in Michelson).
 A solution for that is to implement two branches in the program to handle each case.
@@
 The subtype representing quantifiers contains a special field \textit{Bounds}, which is initially left empty by the parser.
-During the transformation, it is populated with a set of constraints concerning its predicate variable, cf.
-\secref{sec:transformation}.
+During the transformation, it is populated with a set of constraints concerning its predicate variable.
+This is described in the following section.
 
@@
 In the assertion language, the ranges can be expressed using \texttt{if}-conditions.
-As a preliminary for the compilation, the transformation additionally analyses the condition nodes of the AST, identifies conditions that state a range constraint for a generator and assigns it to the respective quantification node (by adding it to the \textit{Bounds} field).
+As a preliminary for the compilation, the transformation thus analyses the condition nodes of the AST, identifies conditions that state a range constraint for a generator and assigns it to the respective quantification node (by adding it to the \textit{Bounds} field).
 Therefore, the transformation contains two consecutive steps:
@@
 
-\subsection{Domain assignment}
+\subsection{Domain Assignment}\label{sec:transf_domains}
 In order to obtain random generators which only generate values in the interesting range, i.e., within the domains of discourse, the second step of the transformation skims the condition nodes of the AST for atomic constraints containing bound variables.
@@
 
-Relating to the example of sorted lists, the premise in \eqref{eq:sorted_v2} can be considered as a conjunction of the four constraints
+The assertion for sorted lists contains the four constraints
 \begin{enumerate}
@@
 \end{enumerate}
-Constraint 1,2 and 4 only contain one bound variable ($n$ or $m$), thus they are assigned to the respective quantifier binding it.
-Constraint 3, on the other hand, features two bound variables -- this constraint is assigned to the quantifier furthest in the nesting, i.e., the quantifier binding $m$.
+Constraint 1,2 and 4 only contain one bound variable ($n$ or $m$), hence they are assigned to the respective quantifier binding it.
+Constraint 3 features two bound variables -- this constraint is assigned to the quantifier furthest in the nesting, i.e., the quantifier binding $m$.
 The corresponding AST expressing this assignment is shown in \figref{fig:ast_example_transf}.
-Based on the assigned constraints, the quantifiers can then be translated to target code corresponding to the following pseudocode (\lstref{lst:rand}):
-\begin{lstlisting}[label=lst:rand, caption=Random generators for sorted list assertion, numbers=none]
+Based on the assigned constraints, the compiler can then translate the quantifiers to the random generators as indicated in \lstref{lst:rand}.
+\begin{lstlisting}[label=lst:rand, caption=Random generators for the sorted list assertion, numbers=none]
 n = random(0, size(a))
@@
 
-However, if constraints contain certain operators, deriving efficient random generators is less straight-forward. Consider the following constraints:
+For constraints containing certain operators, deriving efficient random generators is less straight-forward. Consider the following constraints:
 \begin{enumerate}
@@
 \item $(\forall n : int) (n < 10 \lor n > 20) ...$
+\item $(\forall n,m : int) (n < 10 \lor m > 20)$
 \item $(\forall n : int) (n \ne 10) ...$
@@
 \end{enumerate}
-Constraint 1 can complicate restricting the range of the random generator in two ways.
-Firstly, it separates the range into two disjoint sub-ranges, which translates to a random generator as shown in \lstref{lst:rand_disjoint}.
+Constraint 1 separates the range into two disjoint sub-ranges, which translates to a random generator as shown in \lstref{lst:rand_disjoint}.
 \begin{lstlisting}[label=lst:rand_disjoint, caption=Random generator with two disjoint ranges, numbers=none]
@@
 \end{lstlisting}
-Secondly, the operands of a disjunction cannot be considered separately if they involve several bound variables.
-For the predicate variable whose random generator is executed first, the domain restriction is optional, while the generation of the following random values depends on the previous result.
-\lstref{lst:rand_disjoint_nm} shows the corresponding random generators for a variation of constraint 1 featuring two bound variables, i.e., $(\forall n,m) (n < 10 \lor m > 20)...$.
-\begin{lstlisting}[label=lst:rand_disjoint_nm, caption=Random generators of a disjunction of constraints on two bound variables, numbers=none]
+If a disjunction involves several bound variables, as in constraint 2, the operands of this disjunction cannot be considered separately, as would be the case with a conjunction.
+For the predicate variable whose random generator is executed first, the domain restriction is optional, while the generation of the following random value depends on the previous result.
+\lstref{lst:rand_disjoint_nm} shows the corresponding random generators for this case.
+\begin{lstlisting}[label=lst:rand_disjoint_nm, caption=Random generators of a disjunction of constraints with two bound variables, numbers=none]
 n = if random(0,2) == 0 then random(-MAX_INT, 10)
@@
 \end{lstlisting}
-Similarly to 1, constraint 2 splits the domain into sub-domains. Constraint 3 effectively makes the quantifier binding $n$ obsolete and can therefore be translated to a variable with a constant value.
+Similarly to 1, constraint 3 splits the domain into sub-domains. Constraint 4 effectively makes the quantifier binding $n$ obsolete and can therefore be translated to a constant value.
 
-In the current implementation of the transformation, constraints featuring the logical or, exclusive or or inequality operator are kept as part of the assertion body.
+In the current implementation of the transformation, constraints featuring the logical or, exclusive or inequality operator are kept as part of the assertion body.
 They are considered to be exceptional cases, but will increase the overall complexity of the compilation beyond the scope of a first iteration.
-In the case that constraints remain part of the assertion body, they are checked during runtime.
+Constraints remaining within the assertion body will be checked during runtime.
 As a consequence, an invocation of the assertion contract can result in a futile assertion check if such a condition is not met.
 
-\subsubsection{Implicit constraints}
-In some cases, boundaries are imposed to the random generators implicitly through the used data types.
+\subsubsection{Implicit Constraints}
+In some cases, boundaries are imposed to the random generators implicitly by the used data types.
 List indices, for instance, are always bound to the range $[0..

### 2021-05-13 assertions/doc/thesis-bernhardt/chapters/4-probabilistic_model.tex
Revision compiler
Final revision part 1

@@
-\chapter{Probabilistic model}\label{chap:prob_model}
+\chapter{Probabilistic Model}\label{chap:prob_model}
 Since the proposed approach implements a probabilistic validation, the reliability of the validation depends on the number of validators in the network in relation to the size of input.
@@
 
-\section{Sample spaces}
+\section{Sample Spaces}\label{sec:sample_space}
 The sample space of an assertion is given by the domains of discourse of the quantifiers.
@@
 Such a space is given, for instance, in the introductory example checking whether a number is a prime, i.e., $\mathcal{S} = \lbrace n \in\mathbb{Z} : 2 \le n \le \sqrt{p} \rbrace$.
-Based on the constraints $2 \le n$ and $n \le \sqrt{p}$, the size of the search space can be determined at runtime with $|\mathcal{S}| = \sqrt{p} - 2$.
-If the assertion has to sample from more than one domain, the search space is given by the Cartesian product of these domains.
+Based on the constraints $2 \le n$ and $n \le \sqrt{p}$, the size of the search space can be determined at runtime with $|\mathcal{S}| = \sqrt{p} - 1$.
+If the assertion has to sample from more than one domain (for distinct predicate variables), the search space is given by the Cartesian product of these domains.
 In the example of intersecting sets from \secref{sec:existential}, the sample space is $\mathcal{S} = \mathcal{S}_U \times \mathcal{S}_V$, where $\mathcal{S}_U = \lbrace n \in\mathbb{Z} : 0 \leq n \le |U| \rbrace$ and $\mathcal{S}_V = \lbrace m \in\mathbb{Z} : 0 \leq m \le |V| \rbrace$).
-At runtime, the size of the search space can be determined with $|\mathcal{S}| = (|U| - 0) + (|V| - 0)$.
+At runtime, the size of the search space can be determined with $|\mathcal{S}| = (|U| - 0) * (|V| - 0)$.
 
@@
 
-\section{Configuration of the error rate}\label{sec:prob_threshold}
-The goal is to find a number $t$ of test runs, s.t.
-the probability $P_{c,t}$ of accepting an invalid result falls below a certain threshold $c$.
+\section{Configuration of the Error Rate}\label{sec:prob_threshold}
+The goal is to find a number of test runs $t$, s.t.
+the probability $P_{c,t}$ of accepting an invalid result is below a certain threshold $c$.
 A validator finds the counterexample in one test run with probability $\frac{1}{n}$, and misses it with probability $(1-\frac{1}{n})$.
@@
 The resulting inequality then depends on the known parameter $n$ and an arbitrary value for $c$:
-\begin{align}
+\begin{align}\label{eq:test_runs}
     e^{-\frac{t}{n}} &\leq c && \text{with } 0 \leq c\le 1 \nonumber\\
@@
 
-\section{Validators vs. test runs}
+\section{Validators vs. Test Runs}
 The last section derived a formula which determines the lower bound of test runs to obtain a specified error rate.
@@
 
-\section{Alternatives to random testing}\label{sec:alt_random}
+\section{Alternatives to Random Testing}\label{sec:alt_random}
 For applications where low error rates are crucial and random sampling generates too much cost, an alternative could be to coordinate a systematic iteration of the domain.
 However, the implementation of such a coordination is not trivial, as the validators are engaged via a broadcast and cannot be passed an individual value as input.
-Instead, possible approaches could be to implement a central instance that allocates an element in the search space to each validator, or to use some unique and intrinsic attribute of validators as a seed or input of a mapping to elements in the search space.
+Instead, possible approaches involve the implementation of a central instance that allocates an element in the search space to each validator, or to use some unique and intrinsic attribute of validators as a seed or input of a mapping to elements in the search space.
 
-\subsection{Central allocation of elements}
-For this approach, the toolchain would need to generate a separate contract that is called by the miners and validators as a proxy.
+\subsection{Central Allocation of Elements}
+When using a central instance for the allocation of elements, the toolchain would need to generate a separate contract that is called by the bakers and validators as a proxy.
 When invoked, this proxy contract allocates the next element of the search space (for instance using a modulo-n counter) and passes this number as an additional parameter to the assertion contract.
@@
 
-\subsection{Using unique attributes of a validator}\label{sec:alt_attributes}
-This approach strongly depends on whether the validators have a unique id or another attribute, which can be accessed from within a contract.
-If there is (or the language can be extended with such a feature), the assertion contract needs to implement a non-injective surjective function $f: X_{:A} \rightarrow Y_{:B}$ mapping the respective attribute, represented by a type A, to an element in the search space, represented by type B.
+\subsection{Using Unique Seeds}\label{sec:alt_attributes}
+Instead of installing a central instance, validators could use an intrinsic unique ID or attributed as a seed for a random generation or as an input for a mapping.
+This approach strongly depends on whether the validators have such an ID or attribute, which is accessible from within the VM.
+In the case of a mapping, the assertion contract needs to implement a non-injective surjective function $f: X_{:A} \rightarrow Y_{:B}$ mapping the respective attribute, represented by a type A, to an element in the search space, represented by type B.
 Furthermore, in cases where $t > m$, the function should add an offset for each test run, s.t.

### 2021-05-13 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
Final revision part 1

@@
 
-As a preliminary for the compiler implementation, \secref{sec:ext_michelson} identifies necessary extensions to Michelson and Tezos' VM, in order to facilitate the distributed assertion scheme.
+As a preliminary and preparation for the compiler implementation, \secref{sec:ext_michelson} identifies necessary extensions to Michelson and Tezos' VM, in order to facilitate the distributed assertion scheme.
 Although the extensions are formalized in this thesis, implementing the extension is part of the protocol amendment.
 Furthermore, the compiler needs to generate the target code according to an on-chain orchestration scheme between the assertion and parent contract.
+This orchestration includes the mechanism to trigger several assertion checks per validator based on \eqref{eq:test_runs}, which was derived in the previous chapter.
 \secref{sec:orchestration} explores possible strategies for such a scheme, and discusses their strengths and weaknesses.
-Based on a resulting proposal for the orchestration, \secref{sec:cost_analysis_distributed} performs a cost analysis of the approach of distributed assertion checking and evaluates if, and under which conditions, it can increase the scalability in blockchain applications.
+Based on a resulting proposal for the orchestration, \secref{sec:cost_analysis_distributed} performs a cost analysis of distributed assertion checking and evaluates if, and under which conditions, it can increase the scalability in blockchain applications.
 
-As a foundation for the other sections, \secref{sec:tezos} provides important background on the Tezos blockchain, its built-in Smart Contract language Michelson and some relevant tools and projects within its ecosystem.
+As a foundation for the other sections, \secref{sec:tezos} provides important background on the Tezos blockchain, its built-in smart contract language Michelson and some relevant tools and projects within its ecosystem.
 
@@
 
-In addition to user accounts associated with a public key, Tezos supports Smart Contracts, which are written in the built-in language Michelson.
+In addition to user accounts associated with a public key, Tezos supports smart contracts, which are written in the built-in language Michelson.
 Tezos' transaction fee system is similar to Ethereum's \cite{wood_ethereum_2021} - it is gas-instrumented and besides a base fee, every operation and byte of storage during contract execution has to be paid for by the user.
@@
 The node is the entity connecting to the peer-to-peer network and keeping a copy of the chain.
-Bakers are responsible for producing new blocks, the endorsers for validating and signing new blocks and the accusers to call out bakers or endorsers which double-sign or -endorse.
+Bakers are responsible for producing new blocks, the endorsers for validating new blocks and the accusers to call out bakers or endorsers which double-sign or -endorse.
 The client provides a command line interface to interact with nodes through remote procedure calls (RPC).
@@
 When participating, a contract has a chance to obtain the role of either a baker or an endorser.
-Contracts not owning enough tokens or infrastructure, to participate directly, can delegate their baking and endorsing rights to other contracts.
+Contracts not owning enough tokens or infrastructure to participate directly, can delegate their baking and endorsing rights to other contracts.
 The rights to bake or endorse are determined and assigned at the beginning of each cycle, which consists of a specified number of blocks.
@@
 For documentation, readability and additional type constraints, Michelson and Micheline also offer three types of annotations - type, variable and field or constructor annotations, which are labelled with a unique special character in Micheline.
-The toplevel structure of a Smart Contract consists of a sequence of the three primitives \texttt{parameter, storage} and \texttt{code}.
+The toplevel structure of a smart contract consists of a sequence of the three primitives \texttt{parameter, storage} and \texttt{code}.
 They declare the type of the input parameter, the storage type and the script, which is interpreted when the contract is invoked.
@@
 The type constructors can optionally be tagged with a field annotation, which can be considered  as an entrypoint name.
-The sum type is built by nesting the \texttt{or} type, which has the constructors \texttt{left} and \texttt{right}.
-
+The sum type is built by nesting the \texttt{or} data type, which has the constructors \texttt{left} and \texttt{right}.
 As an example, the contract in \lstref{lst:entrypoints} has two entrypoints --- entrypoint \texttt{A}, which expects an integer wrapped in the \texttt{left} constructor, e.g.
@@
 The passed parameter value is then wrapped automatically into the respective constructor.
-Furthermore, it's possible to declare a \texttt{default} entrypoint, which is invoked when no explicit tag is specified in the transaction.
+Furthermore, it is possible to declare a \texttt{default} entrypoint, which is invoked when no explicit tag is specified in the transaction.
 By default, the default entrypoint is assigned to the root of the parameter type.
 
-\subsubsection{Internal operations}\label{sec:internal_ops}
-Smart Contracts are able to invoke other Smart Contracts by emitting internal operations.
-The return type of Michelson programs is a tuple of a list of internal operations and the updated storage.
+\subsubsection{Internal Operations}\label{sec:internal_ops}
+Smart contracts are able to invoke other contracts by emitting internal operations.
+The return type of Michelson programs (more specifically, the type of the top element on the stack after the completed execution) is a tuple of a list of internal operations and the updated storage.
 After a contract completes, the operations in the returned list are run in sequence.
@@
 
-\subsection{Gas model}
+\subsection{Gas Model}
 Tezos stores and transmits data as byte sequences --- in order to obtain a typed representation of their value for interpretation, a byte sequence is first deserialised into Micheline and subsequently parsed into a typed AST.
@@
 Since these working steps also entail computational effort, they consume gas and thus account for some of the transaction fees.
-The gas consumption of an operation (e.g., a transaction or a contract origination) is thus composed of the following positions \cite{morley_gasmodel}\cite{tezos_repo} on top of a base gas fee:
+The gas consumption of an operation (e.g., a transaction or a contract origination) is thus composed of the following positions on top of a base gas fee \cite{morley_gasmodel}\cite{tezos_repo}:
 \begin{enumerate}
 \item \textbf{Reading costs} --- apply for reading the contract code and storage from the blockchain and depend on the amount of bytes read
-\item \textbf{Deserialization costs} --- depend on the Micheline expression and the size of the byte sequence. Apply lazily, thus the deserialization of each value only has to be paid for once
+\item \textbf{Deserialization costs} --- depend on the components of the Micheline expression and the size of the byte sequence.
+Apply lazily, thus the deserialization of each value only has to be paid for once
 \item \textbf{Parsing costs} --- are composed of three types of costs:
@@
 \item \textbf{Type comparison costs} --- apply when types are checked for equality (e.g. when type checking the branches of the \texttt{IF} instruction) or during contract interpretation
-\item \textbf{Interpretation costs} --- apply for each interpreted instruction and depend on their complexity.
+\item \textbf{Interpretation costs} --- apply for each interpreted instruction and depend on their computational complexity.
 \item \textbf{Unparsing costs} --- apply when converting typed data to untyped Micheline nodes and depend on the data type and size
@@
 
-\subsection{Developer tools in the Tezos ecosystem}
+\subsection{Developer Tools in the Tezos Ecosystem}
 This section describes some tools and projects within Tezos' ecosystem, which are relevant to the development of the toolchain or the protocol amendment.
@@
 
-\subsubsection{Testing tools}
+\subsubsection{Testing Tools}
 Before a new protocol is proposed to the Tezos network, it has to be thoroughly tested with system, integration and regression tests.
@@
 They allow to configure and run a small, fully functional sandboxed test network including nodes, bakers, endorsers and accusers.
-Besides testing new protocols, they can also be used to interactively test Smart Contracts.
+Besides testing new protocols, they can also be used to interactively test smart contracts.
 
-\subsubsection{High-level languages}\label{sec:languages}
-Michelson is a compilation target for various high-level languages that provide a more user-friendly and intuitive way of writing Smart Contracts.
+\subsubsection{High-level Languages}\label{sec:languages}
+Michelson is a compilation target for various high-level languages that provide a more user-friendly and intuitive way of writing smart contracts.
 Additionally, some of them provide development environments, testing or verification tools.
@@
 
-\subsection{Language semantics and type system}\label{sec:michelson_semantics}
+\subsection{Language Semantics and Type System}\label{sec:michelson_semantics}
 Michelson is interpreted purely functional; the interpreter takes the current stack and an operation and builds a return stack from the initial one, without causing any side effects.
@@
 
-\subsection{random}\label{sec:random}
-Since Smart Contracts generally need to be deterministic, s.t.
+\subsection{Random Instruction}\label{sec:random}
+Since smart contracts generally need to be deterministic, s.t.
 the network can reach a consensus about the state of the ledger \cite{chatterjee_probabilistic_2019}, the prevalent workarounds for generating pseudo-random numbers cannot be used to implement the random generators in assertion contracts.
@@
 Thus, the VM needs to provide an instruction to generate a ``real'' random value exclusively for assertion checking.
-The instruction should not be available in the normal execution mode, in order to preserve the deterministic behaviour of normal Smart Contracts.
+In order to preserve the deterministic behaviour of normal smart contracts, the instruction should not be available in the normal execution mode.
 
-\lstref{lst:rand_type} specifies the typing and selection rule of a new instruction \texttt{random} for integers (such an instruction can also be provided for other data types, such as \texttt{nat}, \texttt{string} or \texttt{mutez}).
+\lstref{lst:rand_type} specifies the typing and selection rule of a new instruction \texttt{random} for integers, although such an instruction could also be provided for other data types, such as \texttt{nat}, \texttt{string} or \texttt{mutez}.
+The selection rule for this instruction applies for the instruction identifier \texttt{RANDOM} and an input stack containing at least two elements.
 It consumes an offset and a positive range from the stack and pushes a randomly generated integer to the top.
@@
 If the rule for \texttt{random} applies, the instruction could be computed in OCaml as indicated in \lstref{lst:rand_impl}.
-\begin{lstlisting}[caption=Simplified evaluation of \texttt{random} in the Michelson interpreter, language=, label=lst:rand_impl]
+\begin{lstlisting}[caption=Simplified evaluation of \texttt{random} in the Michelson interpreter, language=, label=lst:rand_impl, float]
 match (instruction, stack) with
@@
 
-\subsection{nth}\label{sec:nth}
+\subsection{List Indexing}\label{sec:nth}
 Michelson currently does not provide any predefined indexed access operators for data types like lists, strings or bytes.
@@
 
-\lstref{lst:nth_type} specifies the typing and selection rules of an instruction \texttt{nth} to access the $n^{th}$ element of a list.
+\lstref{lst:nth_type} specifies the typing and selection rules of an instruction \texttt{nth} to access the element of a list at a specified index.
 It consumes a list with elements of type \texttt{'a}, and an index of type \texttt{nat} from the top of the stack.
@@
 
-\section{Orchestration of contract and assertions}\label{sec:orchestration}
+\section{Orchestration of Contract and Assertions}\label{sec:orchestration}
 So far, the assertion and parent contract have been considered separately.
@@
 Furthermore, the orchestration should include a mechanism to determine and trigger the required number of test runs per validator.
-Depending on the orchestration strategy, the compiler then assembles the assertion and parent code into one or several Smart Contracts.
+Depending on the orchestration strategy, the compiler then assembles and translates the assertion and parent code into one or several smart contracts.
 
@@
 
-\subsection{Monolithic orchestration}\label{sec:monolithic}
-In the monolithic approach, the assertion and parent code are merged into a single Smart Contract.
+\subsection{Monolithic Orchestration}\label{sec:monolithic}
+In the monolithic approach, the assertion and parent code are merged into a single smart contract.
 This tightly couples and unites the code in one self-contained unit.
@@
 Since the required number of test runs $t$ can only be determined at runtime, it cannot be passed to the validators as a parameter to the validation request.
-Instead, the contract itself should contain a controller to handle the calculation of $t$ and the initiation of as many test runs.
+Instead, the contract itself should contain a controller to handle the calculation of $t$ and the initiation of $t$ test runs.
 Similar to the assertion code, such a controller can be appended as another separate entrypoint, as shown in \figref{fig:monolithic_orchestration}.
@@
 
-As a hybrid solution between a monolithic and a modular approach, the controller can be implemented as a separate Smart Contract, which operates as a proxy.
+As a hybrid solution between a monolithic and a modular approach, the controller can be implemented as a separate smart contract, which operates as a proxy.
 This contract is invoked in place of the monolithic contract, which in turn invokes the original or assertion entrypoints as internal operations.
@@
 
-\figref{fig:interaction_monolithic} depicts the resulting interactions of the nodes, validators and monolithic Smart Contracts on the blockchain.
+\figref{fig:interaction_monolithic} depicts the resulting interactions of the nodes, validators and monolithic smart contracts on the blockchain.
 The execution model requires a dedicated modus for distributed assertion checking.
@@
 
-\subsubsection{Evaluation of the monolithic approach}
+\subsubsection{Evaluation of the Monolithic Approach}
 The presented implementations of the monolithic approach each have strengths and weaknesses.
@@
 Another shortcoming is the missing support of implicit entrypoint invocations.
-Even though the previously mentioned measures can prevent transactions failures, this still poses a restriction in the interaction with Smart Contracts.
+Even though the previously mentioned measures can prevent transactions failures, this still poses a restriction in the interaction with smart contracts.
 
@@
 
-\subsection{Modular orchestration}\label{sec:modular}
+\subsection{Modular Orchestration}\label{sec:modular}
 In the modular approach, the controller and each of the assertions are originated as separate contracts on the blockchain.
@@
 
-\subsubsection{Evaluation of the modular approach}
+\subsubsection{Evaluation of the Modular Approach}
 This approach resolves the two crucial problems of the monolithic orchestration: by mirroring the interface of the parent contract, the parameters passed to the manager contract can be forwarded directly to the parent contract, regardless of whether the default or an explicit entrypoint was called.
@@
 
-\section{Backend implementation}\label{sec:backend_impl}
+\section{Backend Implementation}\label{sec:backend_impl}
 The following sections describe the tasks and implementations of the pipeline stages of the toolchain backend.
@@
 
-\subsection{Interaction with Tezos nodes}
+\subsection{Interaction with Tezos Nodes}
 Some stages of the backend have to interact with a Tezos node, e.g.
@@
 
-\subsection{Semantic analysis}
+\subsection{Semantic Analysis}
 After the transformation, the frontend passes a list of ASTs to the backend.
@@
 
-\subsection{Type check}\label{sec:typecheck}
+\subsection{Type Check}\label{sec:typecheck}
 Given a list of Tezos-specific ASTs, the task of the type checker is to link each AST to the respective entrypoint of the parent contract.
@@
 
-\subsubsection{Compilation of the assertion contracts}
+\subsubsection{Compilation of the Assertion Contracts}
 The assertion ASTs are independent and can thus be compiled in isolation to separate Michelson contracts.
@@
 
-\subsubsection{Compilation of the controller contract}
+\subsubsection{Compilation of the Controller Contract}
 The generation of the \texttt{parameter} and \texttt{storage} primitives is trivial.
@@
 
-\subsubsection{Compiling to an intermediate representation}\label{sec:IR}
+\subsubsection{Compiling to an Intermediate Representation}\label{sec:IR}
 Instead of generating Michelson code directly, the compiler could also generate code in one of the high-level languages listed in \secref{sec:languages}.
@@
 
-\section{Cost analysis and evaluation}\label{sec:cost_analysis_distributed}
+\section{Cost Analysis and Evaluation}\label{sec:cost_analysis_distributed}
 In this section, the costs of checking a formula with the proposed approach and implementation for distributed assertion checking are evaluated.
@@
 
-\section{Open questions}
+\section{Open Questions}
 There remain two aspects of the off-chain design, which could not be addressed in detail by this thesis. These aspects are outlined briefly in the following sections.
 
-\subsection{Representing counterexamples}\label{sec:counterexample}
+\subsection{Representing Counterexamples}\label{sec:counterexample}
 It remains to be specified, how counterexamples are represented within the network.
@@
 
-\subsection{Multi-slot validators}
+\subsection{Multi-slot Validators}
 The proposed implementation assumes that all 32 validators of the current block cycle execute a determined number of test runs.

### 2021-05-13 assertions/doc/thesis-bernhardt/chapters/6-conclusion.tex
Final revision part 1

@@
-\chapter{Conclusion and outlook}\label{chap:conclusion}
+\chapter{Conclusion and Outlook}\label{chap:conclusion}
 Complex blockchain-based applications suffer from high computation costs and limited scalability.
@@
 Suitable use-cases for this approach are computations, whose properties can be specified with formulas in predicate logic featuring universal quantification.
-To support this model on the target platform Tezos, a toolchain was developed to allow developers to specify explicit assertions and generate corresponding Smart Contracts.
+To support this model on the target platform Tezos, a toolchain was developed to allow developers to specify explicit assertions and generate corresponding smart contracts.
 These contracts check the property point-wise within the quantification domain and identify counterexamples when executed by the validators.

### 2021-05-13 assertions/doc/thesis-bernhardt/chapters/appendix.tex
Final revision part 1

@@
 \appendix
-\chapter{Michelson implementations of \texttt{Foo} and \texttt{Bar}}\label{apx:cost_analysis_contract}
+\chapter{Michelson Implementations of \texttt{Foo} and \texttt{Bar}}\label{apx:cost_analysis_contract}
 The following contracts are the Michelson equivalent of the dummy contracts given in \secref{sec:usecase_cost}.
@@
 
-\section{Prefix notation}
+\section{Prefix Notation}
 \lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
@@
 
-\section{Infix notation}
+\section{Infix Notation}
 \lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
@@
 
-\chapter{List accessing in Michelson}\label{apx:nth}
+\chapter{List Accessing in Michelson}\label{apx:nth}
 
@@
 
-\chapter{Controller contract code in Liquidity}\label{apx:controller_liq}
+\chapter{Controller Contract Code in Liquidity}\label{apx:controller_liq}
 \lstinputlisting[label=lst:manager_templ_liq, language=Michelson, caption=Controller code in Liquidity]{listings/controller.liq}
 
-\chapter{Controller contract code in Michelson}\label{apx:controller_michelson}
+\chapter{Controller Contract Code in Michelson}\label{apx:controller_michelson}
 \lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
@@
 
-\chapter{Distributed Michelson implementation of \texttt{Foo} and \texttt{Bar}}\label{apx:foobar_distributed}
+\chapter{Distributed Michelson Implementation of \texttt{Foo} and \texttt{Bar}}\label{apx:foobar_distributed}
 The following contracts are a restructuring of the contracts given in Appendix \ref{apx:cost_analysis_contract}, s.t. they implement the proposed orchestration strategy.

### 2021-05-14 papers/contract-modules/fmbc2021/fmbc-main.tex
abstract

\documentclass[a4paper,USenglish,american,cleveref, autoref, thm-restate]{oasics-v2021}
%This is a template for producing OASIcs articles. 
%See oasics-v2021-authors-guidelines.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling autoref support, use "autoref"
%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
%for enabling thm-restate support, use "thm-restate"
%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
%for producing a PDF according the PDF/A standard, add "pdfa"

\listfiles

%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

\bibliographystyle{plainurl}% the mandatory bibstyle

\title{Towards Contract Modules for the Tezos Blockchain} %TODO Please add

% \titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line

\author{Ha Doan}{University of Freiburg, Germany}{doanha@cs.uni-freiburg.de}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional

\author{Peter Thiemann}{University of Freiburg, Germany}{thiemann@acm.org}{[orcid]}{[funding]}

\authorrunning{Ha Doan and P. Thiemann} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

\Copyright{Ha Doan and Peter Thiemann} %TODO mandatory, please use full first names. OASIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\ccsdesc[100]{\textcolor{red}{Replace ccsdesc macro with valid one}} %TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm

\keywords{Dummy keyword} %TODO mandatory; please add comma-separated list of keywords

\category{} %optional, e.g. invited paper

\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
%\relatedversiondetails[linktext={opt. text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g. Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional

%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
%\supplementdetails[linktext={opt. text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g. Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional

%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.

\acknowledgements{I want to thank \dots}%optional

%\nolinenumbers %uncomment to disable line numbering

%\hideOASIcs %uncomment to remove references to OASIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Access}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

%TODO mandatory: add short abstract of the document
\begin{abstract}
  Programmatic interaction with a blockchain is often clumsy.
  Many interfaces handle only loosely structured data, often in JSON
  format, that is inconvenient to handle and offers few guarantees.

  Contract modules provide a statically checked interface to interact
  with contracts on the Tezos blockchain. A module specification
  provides all types as well as information about potential failure
  conditions of the contract. The specification is checked against the
  contract implementation using symbolic execution. An OCaml module is
  generated that contains a function for each entrypoint of the
  contract. The types of these functions fully describe the interface
  including the failure conditions and guarantee type-safe and
  sometimes fail-safe invocation of the contract on the blockchain.
\end{abstract}

\section{Introduction}
\label{sec:introduction}

%%
%% Bibliography
%%

%% Please use bibtex,

\bibliography{oasics-v2021-sample-article}

\end{document}

### 2021-05-14 papers/contract-modules/modules.tex
abstract

@@
   language=caml,
-  morekeywords={contract,entrypoint,module,hash,paid,raises,sig,val},
+  morekeywords={requires,sender,amount,balance,storage,contract,entrypoint,module,hash,paid,raises,sig,val},
   % predefined types
@@
   classoffset=2,
-  morekeywords={Left,Right},
+  morekeywords={Pair,Left,Right},
   keywordstyle=\color{magenta},
@@
 
-\section{Motivation}
+\section{A simple example}
 \label{sec:motivation}
 
-Consider this Michelson code fragment:
+Consider this Michelson code fragment for implementing an auction contract:
 \begin{lstlisting}[language=michelson,caption={Michelson code example},label={lst:code-example}]
-parameter (or (int %bid_for_auction)
-              (unit %close_auction));
-storage address;
+parameter (or (unit %close)
+              (unit %bid));
+storage (pair bool (pair address address));
 code { DUP; CAR; 
        IF_LEFT {
-       # %bid_for_auction
-        DUP; PUSH int 10000; SUB; LE;
+       # %close
+         DROP; CDR; CAR; SENDER; EQ;
+         IF {} { PUSH string "not owner"; FAILWITH; }
+         # ...
+       }
+       {
+       # %bid
+        DROP; AMOUNT; PUSH mutez 10000; COMPARE; LE;
         IF { FAILWITH; } {} # fails with argument value
@@
        }
-       {
-       # %close_auction
-         DROP; CDR; SENDER; EQ;
-         IF {} { PUSH string "not owner"; FAILWITH; }
-         # ...
-       }
      }
@@
 
-Here is a \textbf{contract module} that describes / specifies the above Michelson code.
+Here is a simple \textbf{contract module} that describes / specifies
+the above Michelson code. 
 \begin{lstlisting}[caption={Contract module example},label={lst:contract-module-example}]
 contract type MyContract = sig
-  paid entrypoint %bid_for_auction (v : int) 
+  paid entrypoint %bid () 
   raises "closed"                 (** auction closed*)
@@
 
-  entrypoint %close_auction (_ : unit)
+  entrypoint %close ()
   raises "not owner"         (** caller cannot close the auction *)
@@
 
-Each \lstinline/entrypoint/ is mapped to a function. The variables
-used in the pattern may be a wildcard \lstinline/_/ or an OCaml identifier, which
-is used in generating the implementation. For \lstinline/_/ a standard
-name will be generated.
+Each \lstinline/entrypoint/ is mapped to a function. The entrypoint's
+parameter is described by a pattern.  Variables (OCaml identifier) or
+wildcards \lstinline/_/ in the pattern will be used as formal
+parameters in generating the implementation. For \lstinline/_/ a
+standard name will be generated. Each variable or wildcard needs a
+type annotation. Constructors in the pattern will be
+omitted from the interface, but automatically inserted in the contract
+invocation.
 
 A \lstinline/paid/ entrypoint requires the caller to specify an amount of tokens to
-accompany the contract invocation. Accordingly, the generated function has an extra
-argument. Otherwise, the entrypoint is unpaid.
+accompany the contract invocation. Accordingly, the generated function
+has a mandatory argument to specify this amount. Otherwise, the entrypoint is unpaid.
 
-The \lstinline/raises/ clauses specify values that the contract might
-pass to the \texttt{FAILWITH} instruction. The \lstinline/as/ clause
+The \lstinline/raises/ clause specifies values that the contract might
+pass to the \texttt{FAILWITH} instruction. The translation generates
+an error type from the clause that describes all possible
+failures. The \lstinline/as/ clause 
 maps the matched value to an OCaml identifier, which is used to
@@
 
-Alternatively and equivalently, the contracts can be specified using
+The \lstinline/raises/ clause must be exhaustive. Any failure arising
+during execution of the contract must be captured by one of the
+specified cases. If in doubt, include a catchall default case.
+
+Alternatively and equivalently, contracts can be specified using
 patterns on the default entrypoint.
@@
 \begin{lstlisting}[caption={Alternative syntax for entrypoints},label={lst:alternative-syntax}]
-  paid entrypoint bid_for_auction (Left (_ : int))
+  paid entrypoint bid (Right ())
 ...
-  entrypoint close_auction (Right (_ : unit))
+  entrypoint close (Left ())
 \end{lstlisting}
+
+The specification does not have to be exhaustive. The contract may
+have further entrypoints that are not described by the module.
+
+\clearpage{}
+\section{A safer example}
+\label{sec:safe-example}
+
+Alternatively, one may specify preconditions that are checked before
+the contract is deployed to the blockchain.
+
+\begin{lstlisting}[caption={Safer contract module},label={lst:safer-contract-module}]
+contract type SaferContract = sig
+  storage (Pair (bidding : bool) 
+                (Pair (owner : address) 
+                      (highest_bidder : address)))
+
+  entrypoint %close ()
+  requires (sender = owner) raises "not owner"
+
+  paid entrypoint %bid () 
+  requires bidding raises "closed" (** auction closed*)
+  requires (amount > balance)
+  requires (amount > 10000)
+  raises "bid too low" as too_low (** bid received is too low *)
+       | 42 as the_answer         (** failwith received argument 42 *)
+end
+\end{lstlisting}
+The \lstinline/storage/ clause defines a typed pattern to match the
+current storage of the contract. Moreover, it generates a suitably
+typed getter function (also named \lstinline/storage/) 
+to access the current storage from OCaml.
+
+The \lstinline/%close/ entrypoint comes with a \lstinline/requires/
+clause that specifies a precondition for invoking the contract. This
+precondition is checked in the OCaml interface \emph{before} invoking
+the contract. The entrypoint does not have a \lstinline/raises/
+clause anymore, which means that this precondition implies that no
+failures can occur.
+
+\textbf{For this reasoning to be true, we need to know that the owner
+  component of the storage is constant through all contract executions.}
+
+For the \lstinline/%bid/ entrypoint, the \lstinline/bidding/ component
+must be true. However, we cannot guarantee that there is nobody
+closing the contract between accessing the storage and the
+actual contract invocvation. Hence, the corresponding
+\lstinline/raises/ clause must remain in place.
+
+\textbf{To safely reject when \lstinline/bidding/ is false, we need to know
+  that there is no contract execution that can make it true, again.}
+
+Analogous reasoning applies to the condition
+\lstinline/amount > balance/. Here, we also need to know that the
+balance cannot decrease, which is non-trivial. However, we can accurately check that
+\lstinline/amount > 10000/ before the contract invocation, which rules
+out the unspecific integer failure.
+
+The interface of the generated functions remains the same, but some of
+the errors are generated without involving the blockchain.
+
+\section{Generated code}
+\label{sec:generated-code}
 
@@
 sig
-  type bid_for_auction_errors = 
+  type bid_errors = 
      | closed       (** auction closed*)
@@
 
-  val bid_for_auction
+  val bid
     : Tezos.pukh -> ?fee:Tezos.tz -> amount:Tezos.tz
-    -> int
-    -> (Tezos.status, bid_for_auction_errors) Tezos.monad
+    -> (Tezos.status, bid_errors) Tezos.monad
 
-  type close_auction_errors = 
+  type close_errors = 
      | not_owner    (** caller cannot close the auction *)
 
-  val close_auction
+  val close
     : Tezos.pukh -> ?fee:Tezos.tz -> ?amount:Tezos.tz
-    -> unit
-    -> (Tezos.status, close_auction_errors) Tezos.monad
+    -> (Tezos.status, close_errors) Tezos.monad
 end
@@
   relationship is TBD.
+\item In this example, there are no parameters that are passed to the
+  entrypoints because their type is \lstinline/Unit/.
 \item Error reporting assumes that the monad returns a sum type. But
   things could be handled differently (for the
-  \lstinline/close_auction/entrypoint): by an error continuation of
-  type \lstinline/close_auction_errors -> Answer.t/ or by
+  \lstinline/close/ entrypoint): by an error continuation of
+  type \lstinline/close_errors -> Answer.t/ or by
   raising an exception that encapsulates the error type:
 \begin{lstlisting}
-exception Close_Auction_Exn of close_auction_errors
+exception Close_Exn of close_errors
 \end{lstlisting}
@@
 
-type bid_for_auction_errors = 
+type bid_errors = 
    | closed       (** auction closed*)
@@
 
-let big_for_auction_errors_map =
+let big_errors_map =
   let open Base in
@@
 
-let bid_for_auction destination ?(fee=100.0) amount v =
+let bid destination ?(fee=100.0) amount v =
   ...
@@
 
-type close_auction_errors = 
+type close_errors = 
    | not_owner    (** caller cannot close the auction *)
 
-let close_auction destination ?(fee=50.0) ?(amount=0.0) v =
+let close destination ?(fee=50.0) ?(amount=0.0) v =
   ...
@@
 execution. In this framework, it would also 
-be possible to specify further invariants about the inputs and place them into the contract
-module. Essentially, every formula that an SMT solver can deal with
-should be fine, although a first version of the symbolic executor
-could work without using SMT.
+be possible to specify further invariants (like the
+\lstinline/require/ clauses) about the inputs and place
+them into the contract module. Essentially, every formula that an SMT
+solver can deal with should be fine, although a first version of the
+symbolic executor could work without using SMT.
 
@@
 according to the path to the specified entrypoint. That is, to
-investigate the entrypoint \lstinline/bid_for_auction/ in
+investigate the entrypoint \lstinline/bid/ in
 Listing~\ref{lst:code-example}, symbolic execution would start with a

### 2021-05-14 papers/contract-modules/fmbc2021/fmbc-main.tex
Update fmbc-main.tex

@@
 
-\author{Ha Doan}{University of Freiburg, Germany}{doanha@cs.uni-freiburg.de}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
+\author{Thi Thu Ha Doan}{University of Freiburg, Germany}{doanha@cs.uni-freiburg.de}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
 Please provide at least the name of the affiliation and the country.
@@
 
-\authorrunning{Ha Doan and P. Thiemann} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'
+\authorrunning{T.T.H Doan and P. Thiemann} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'
 

### 2021-05-17 papers/contract-modules/modules.tex
tiny fix

--- 2021-01-19 papers/contract-modules/modules.tex
@@
   classoffset=1,
+
   morekeywords={nat,int,unit,string,or,pair,option,address},

### 2021-05-17 papers/contract-modules/fmbc2021/fmbc-main.tex
Update fmbc-main.tex
first few sections

@@
 
-\author{Thi Thu Ha Doan}{University of Freiburg, Germany}{doanha@cs.uni-freiburg.de}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
+\author{Thi Thu Ha Doan}{University of Freiburg,
+  Germany}{doanha@cs.uni-freiburg.de}{https://orcid.org/0000-0002-1825-0097}{supported
+by a grant from the Tezos foundation}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
 Please provide at least the name of the affiliation and the country.
@@
 
-\author{Peter Thiemann}{University of Freiburg, Germany}{thiemann@acm.org}{[orcid]}{[funding]}
+\author{Peter Thiemann}{University of Freiburg, Germany}{thiemann@acm.org}{https://orcid.org/0000-0002-9000-1239}{}
 
@@
 
-\Copyright{Ha Doan and Peter Thiemann} %TODO mandatory, please use full first names. OASIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+\Copyright{Thi Thu Ha Doan and Peter Thiemann} %TODO mandatory, please use full first names. OASIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
 
-\ccsdesc[100]{\textcolor{red}{Replace ccsdesc macro with valid one}} %TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
+%\ccsdesc[100]{\textcolor{red}{Replace ccsdesc macro with valid one}}
+%%TODO mandatory: Please choose ACM 2012 classifications from
+%%https://dl.acm.org/ccs/ccs_flat.cfm
+\ccsdesc[100]{}
 
-\keywords{Dummy keyword} %TODO mandatory; please add comma-separated list of keywords
+\keywords{contract API, modules, static checking} %TODO mandatory; please add comma-separated list of keywords
 
@@
 
-\acknowledgements{I want to thank \dots}%optional
+% \acknowledgements{I want to thank \dots}%optional
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\input{macros}
 
@@
 
+Contracts on the blockchain rarely run in isolation. To be useful
+beyond shuffling tokens between user accounts, they need to interact
+with the outside world. On the other hand, the outside world also
+needs to interact by initiating transactions and starting contracts
+that feed information into the blockchain. One direction is addressed
+by oracles that watch certain events on the blockchain, create a
+response by calculation or gathering data, and then invoke a callback
+contract to inject this response into the chain. Trust is an essential
+aspect for an oracle.
+
+The other direction is about automatizing certain processes in
+connection with the blockchain. For example, opening or closing an
+auction according to a schedule, programming a strategy for an
+auction, or creating an NFT. To this end, an interface is needed to
+invoke contracts safely. Existing interfaces are lacking because they
+are essentially untyped (string-based or JSON-based) and often low
+level because they require dealing directly with RPC interfaces. Trust
+is not needed because the process runs on behalf of a certain user.
+
+Contract modules provide a clean, language-integrated way to interact
+with a blockchain. They abstract over underlying string-based
+interfaces and details like fee handling. They provide a high-level
+typed interface which reduces a contract invocation to a function call
+in the language.
+
+Contract modules do not provide a fixed API, but
+rather generate a specialized interface for each contract. This
+interface is statically checked against the contract implementation to
+ensure type safety and exception safety (every failure condition
+arising is handled by proper error reporting).
+
+Our work is situated in the context of the Tezos blockchain, which
+supports Michelson as its low-level contract language, and the
+language OCaml, which supports a powerful module concept that we
+enhance with contract modules.
+
+\section{Context}
+\label{sec:context}
+
+Tezos is a third generation, account-based, self amendable
+blockchain \cite{tezos-whitepaper}. It employs a proof-of-stake consensus protocol, which
+includes ways to evolve the protocol itself. The consensus protocol is
+executed by so-called bakers and their proposed blocks are checked by
+validators. They receive some compensation in the form of
+tokens (Tezzies) for their work.
+
+Each Tezos contract owns an account as well as some storage. Contracts
+are pure functions of type parameter $\times$ storage $\to$ operation
+list $\times$ storage. When a contract is invoked with a parameter,
+the blockchain provides the current storage and updates it with the
+second, storage component of its return value. The first component is
+a list of blockchain operations (contract deployments, token
+transfers, contract invocations) that are executed transactionally
+after the first invocation terminates. Each invocation may be
+accompanied with an amount of tokens that are added to the current
+account balance of the contract.
+
+Contracts are implemented in the Michelson language, a fully typed
+stack-based language. Each contract has fixed types for its parameter
+and for its storage. The storage is initialized when the contract is
+deployed. Besides primitive types like unit, int, bool, address, and string,
+there are pairs, sums, functions, lists, and maps (and many more) that
+can serve as types for storage and parameters.
+
+\section{An auction contract}
+\label{sec:an-auction-contract}
+
+As a concrete example, we consider an auction contract. 
+\begin{lstlisting}[language=michelson,numbers=none,emph={close,bid},emphstyle=\underbar]
+parameter (or (unit %close) (unit %bid));
+storage (pair bool          # bidding allowed
+         (pair address      #  contract owner
+          address           # highest bidder's address
+        ));
+\end{lstlisting}
+This contract has two entrypoints, \lstinline/close/ and \lstinline/bid/,
+expressed by giving the single parameter a sum type. To call the
+entrypoint \lstinline/close/ we use the parameter \lstinline/Left ()/
+otherwise we use \lstinline/Right ()/, where \lstinline/()/ is the sole
+value of type \lstinline/unit/. Its storage is a nested pair which
+contains a boolean flag and two addresses.
+
 %%

### 2021-05-17 papers/contract-modules/fmbc2021/macros.tex
first few sections

\usepackage{graphics}
\usepackage{listings}

\lstdefinelanguage{michelson}{
%  basicstyle=\ttfamily,
  backgroundcolor=\color{pink!20}, 
  classoffset=0,
  morekeywords={parameter,storage,code},
  keywordstyle=\bfseries, 
  % predefined types
  classoffset=1,
  morekeywords={nat,int,unit,string,or,pair,option,address,mutez,bool},
  keywordstyle=\color{blue},
  classoffset=2,
  morekeywords={CAR,CDR,CONS,DUP,EQ,FAILWITH,IF,IF_LEFT,LE,LEFT,NIL,DROP,PUSH,RIGHT,SENDER,SUB},
  keywordstyle=\color{magenta},
  sensitive=false,
  morecomment=[l]{\#},
  morecomment=[s]{/*}{*/},
  morestring=[b]",
}

\definecolor{pypypy}{rgb}{0.4,0.85,0.7}

\lstset{
  language=Caml,
  basicstyle=\ttfamily,
  backgroundcolor=\color{pypypy},
  morekeywords={module,contract,sig,val,paid,entrypoint,raises},
  classoffset=1,
  morekeywords={nat,int,unit,string,or,pair,option,address,bool},
  morekeywords={Tezos,pukh,tz,status,monad},
  keywordstyle=\color{blue},
}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "fmbc-main"
%%% End:

### 2021-05-21 papers/contract-modules/fmbc2021/fmbc-main.tex
good bib file
pretty complete

@@
 supports Michelson as its low-level contract language, and the
-language OCaml, which supports a powerful module concept that we
+language OCaml, which comes with an expressive polymorphic type system
+as well as a powerful module system that we
 enhance with contract modules.
@@
 validators. They receive some compensation in the form of
-tokens (Tezzies) for their work.
+tokens (Tezzies) for their work. According to proof-of-stake,
+bakers and validators are just nodes elected by the Tezos network
+according to their token balance.
 
@@
 
-Contracts are implemented in the Michelson language, a fully typed
+Contracts are implemented in the language Michelson, a fully typed
 stack-based language. Each contract has fixed types for its parameter
@@
 \label{sec:an-auction-contract}
-
-As a concrete example, we consider an auction contract. 
-\begin{lstlisting}[language=michelson,numbers=none,emph={close,bid},emphstyle=\underbar]
+\begin{lstlisting}[float,caption={Simple auction contract (auction.tz)},captionpos=b,label={lst:auction-header},language=michelson,numbers=none,emph={close,bid},emphstyle=\underbar]
 parameter (or (unit %close) (unit %bid));
@@
 \end{lstlisting}
+
+As a concrete example, we consider a simple auction contract with the
+header shown in Listing~\ref{lst:auction-header}. 
 This contract has two entrypoints, \lstinline/close/ and \lstinline/bid/,
 expressed by giving the single parameter a sum type. To call the
-entrypoint \lstinline/close/ we use the parameter \lstinline/Left ()/
+entrypoint \lstinline/close/ we invoke the contract with parameter \lstinline/Left ()/
 otherwise we use \lstinline/Right ()/, where \lstinline/()/ is the sole
-value of type \lstinline/unit/. Its storage is a nested pair which
+value of type \lstinline/unit/. The contract's storage is a nested pair which
 contains a boolean flag and two addresses.
+
+The contract works as follows. It is deployed with storage
+\lstinline/(true,(owner,owner))/ which indicates that bidding is
+allowed and the contract owner is currently also the highest
+bidder. On deployment the owner also deposits an initial balance to indicate the
+minimum bid. Closing the contract transfers the balance to the
+owner. It is restricted to the owner. Bidding fails if the contract is
+closed. If bidding is open and the amount of tokens with the bid exceeds the
+current highest bid, the current bidder replaces the previous highest
+bidder and the previous highest bidder is reimbursed. Otherwise,
+bidding fails, too.
+
+To invoke this contract from an OCaml program, we'd like to generate an
+OCaml module, say \lstinline/Auction/, from a specification of the
+contract. This module contains two functions
+\lstinline/close/ and \lstinline/bid/ corresponding to the
+entrypoints. The type of these entrypoints reflects further properties
+of these entrypoints as well as the ways in which an entrypoint might
+fail.
+
+Besides the obvious, technology induced ways that a contract invocation might fail
+(insufficient gas price offered, insufficient gas to complete, timeout
+due to lack of connectivity, etc) a Michelson contract can fail due to
+a programmer induced condition. To this end, there is a Michelson
+instruction \lstinline/FAILWITH/ that terminates contract execution
+with an error message which is reported back to the caller. This error
+message includes a rendering of the top value on the stack.
+
+We consider the technological failures like Java's unchecked
+exceptions, but we wish to deal with the explicit failures like
+checked exceptions.
+Our generated code handles failures in a suitable
+error monad that makes the failures explicit in a custom
+datatype.\footnote{Alternatively, this could be done using OCaml
+  exceptions, but we chose to stay within the monadic framework that
+  is already used by existing Tezos APIs.}
+
+\begin{lstlisting}[float,captionpos=b,caption={Contract module example},label={lst:contract-module-example}]
+contract type Auction = sig
+  paid entrypoint bid () 
+  raises "closed"               (** auction closed *)
+       | "too low"              (** bid too low    *)
+
+  entrypoint close ()
+  raises "not owner"            (** caller cannot close *)
+end
+\end{lstlisting}
+Listing~\ref{lst:contract-module-example} shows a contract module for
+the auction contract.  It declares the entrypoint \lstinline/bid/ as
+\lstinline/paid/, which means that it needs to be invoked with a
+non-zero amount of tokens, it gives the pattern \lstinline/()/ for the
+input value of type \lstinline/unit/, and it specifies two possible
+failure messages that we wish to deal with programmatically.
+The \lstinline/close/ entrypoint is similar, but requires no tokens.
+
+\begin{lstlisting}[float,captionpos=b,caption={Generated signature},label={lst:generated-signature}]
+module type MyContract = sig
+  type bid_errors = 
+     | closed       (** auction closed*)
+     | too_low      (** bid received is too low *)
+
+  val bid
+    : Tezos.pukh -> ?fee:Tezos.tz -> amount:Tezos.tz
+    -> (Tezos.status, bid_errors) Tezos.monad
+
+  type close_errors = 
+     | not_owner    (** caller cannot close the auction *)
+
+  val close
+    : Tezos.pukh -> ?fee:Tezos.tz -> ?amount:Tezos.tz
+    -> (Tezos.status, close_errors) Tezos.monad
+end
+\end{lstlisting}
+Listing~\ref{lst:generated-signature} contains an OCaml module
+signature as it could be generated from the contract module. The
+module \lstinline/Tezos/ supposedly contains types and other low-level
+Tezos-specific definitions. Specifically, the type \lstinline/pukh/ for public
+key hashes identifies contracts, the type \lstinline/tz/ stands for
+Tezos tokens, the type \lstinline/status/ reflects the internal return
+status, and \lstinline/monad/ is an internal monad type. The signature
+declares a function and an error type for each entrypoint.
+
+The error types mirror the raises clauses. The first argument of each
+function is the address of the contract, then an optional argument for
+the transaction fee, an argument for passing an amount of tokens
+(optional for an unpaid entrypoint), the next argument would be for
+the parameter; it is omitted here because its type is
+\lstinline/unit/. The return type refers to the specific error type.
+
+\section{Simple Checking}
+\label{sec:check-contr-against}
+
+We plan to check the contract by symbolic execution against its
+specification in the contract module. Here are some examples of
+checkable properties.
+
+For each entrypoint, we collect the set of reachable instructions.
+For example, the  \lstinline/AMOUNT/ instruction obtains the amount of
+tokens sent with a contract invocation.
+It should not be possible to reach that instruction from an unpaid
+entrypoint  like \lstinline/close/.
+
+For the \lstinline/FAILWITH/ instructions, we also collect their
+arguments. The symbolic interpreter needs to retain concrete values as
+much as possible to obtain precise results at this point. Each
+argument to \lstinline/FAILWITH/ should be accounted for by one
+\lstinline/raises/ clause.
+
+\section{Advanced Checking}
+\label{sec:advanced-checking}
+\begin{lstlisting}[float,captionpos=b,caption={Safer contract module},label={lst:safer-contract-module}]
+contract type SaferAuction = sig
+  storage (Pair (bidding : bool) 
+                (Pair (owner : address) (hi_bidder : address)))
+
+  entrypoint close ()
+  requires (sender = owner) raises "not owner"
+
+  paid entrypoint bid () 
+  requires bidding raises "closed" (** auction closed*)
+  requires (amount > balance)
+  raises "too low" as too_low      (** bid too low *)
+end
+\end{lstlisting}
+
+As it is expensive to invoke a contract just to find out that it
+fails, we propose to extend entrypoint specifications with
+preconditions as shown in Listing~\ref{lst:safer-contract-module}. The
+idea is that the generated OCaml module tries to check the
+preconditions off-chain before invoking the contract. To this end, the
+code needs to obtain properties like balance, storage etc of the
+contract, but this information is available from the Tezos node without a fee!
+We discuss two of the preconditions to highlight the properties that 
+need to be analyzed.
+
+The precondition \lstinline/sender = owner/ of \lstinline/close/ can
+be checked off-chain because the owner's address is part of the
+storage. However, it is in general unsound to perform such a test
+off-chain because the owner's address could change if an entrypoint
+changes that component of the storage. To safely check this
+precondition, the analysis must determine that the owner component of
+the storage remains the same across all possible execution paths of
+the contract.
+
+Moreover, the gathering of instructions must build path predicates,
+such that each \lstinline/FAILWITH/ instruction comes with a predicate
+that must be true to reach the instruction. In contract
+implementation, the path predicate is \lstinline/sender != owner/. As
+the conjunction of path predicate and precondition is unsatisfiable
+and because the \lstinline/owner/ component is constant, an off-chain
+test for \lstinline/sender = owner/ precisely predicts whether the
+failure condition arises.
+
+The situation is slightly more complex at the \lstinline/bid/
+entrypoint. The failure \lstinline/"closed"/ is guarded by
+\lstinline/bidding/. As the \lstinline/bidding/ component of the state can change,
+precise prediction is not possible. A closer look reveals some
+subtlety. If \lstinline/bidding/ is true, then the flag may have
+changed by some interleaved call to \lstinline/close/. However, if
+\lstinline/bidding/ is false, then there is no point in invoking the
+contract because \lstinline/bidding/ will never be reset to true.
+
+Hence the analysis should also record value transitions in the
+storage for non-failing executions. For \lstinline/bidding/
+\lstinline/bid/ transitions from true to true and \lstinline/close/
+transitions from true to false. Thus, if the off-chain check finds
+\lstinline/bidding/ $=$ false, then we can precisely predict that
+\lstinline/bid/ would fail and trigger the corresponding error without
+invoking the contract proper.
+
+For the failure \lstinline/"to low"/, the analysis is very similar:
+we need to know that there is no successful execution of
+\lstinline/bid/ after an execution of \lstinline/close/. Moreover,
+each invocation of \lstinline/bid/ raises the balance of the contract
+monotonically. Thus, if the off-chain check
+\lstinline/amount > balance/ fails, we can be sure that the contract
+invocation will also fail; either because some closed the auction or
+because the balance is at least as high as in the off-chain sample.
 
@@
 
-\bibliography{oasics-v2021-sample-article}
+\bibliography{biblio}
 

### 2021-05-21 papers/contract-modules/fmbc2021/macros.tex
pretty complete

@@
   backgroundcolor=\color{pypypy},
-  morekeywords={module,contract,sig,val,paid,entrypoint,raises},
+  morekeywords={requires,sender,amount,balance,storage,hash,module,contract,sig,val,paid,entrypoint,raises},
   classoffset=1,

### 2021-05-23 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Final revision chpt 5 until compiler

@@
 Therefore, the assertions are linked to the entrypoints through the tags, the parameter type or both.
-\secref{sec:typecheck} describes in more detail how the linking is implemented in the Tezos backend.
+How the linking is implemented in the Tezos backend is described in more detail in \secref{sec:typecheck}.
 
@@
 After successfully parsing all assertions, the parser returns a list of their corresponding ASTs.
-\lstref{lst:ast_type} shows the toplevel definition of the AST type.
+\lstref{lst:ast_type} shows the toplevel definition of the AST type in OCaml.
 It is composed of an entrypoint specification, consisting of an optional tag and the parameter pattern, and an assertion body.

### 2021-05-23 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
Final revision chpt 5 until compiler

@@
 \figref{fig:interaction_monolithic} depicts the resulting interactions of the nodes, validators and monolithic smart contracts on the blockchain.
-The execution model requires a dedicated modus for distributed assertion checking.
-A possible mechanism to activate this modus is using a special transaction type, which is denoted by \texttt{txa(destination, entrypoint, parameter)} in the graphic.
+The execution model requires a dedicated mode for distributed assertion checking.
+A possible mechanism to activate this mode is using a special transaction type, which is denoted by \texttt{txa(destination, entrypoint, parameter)} in the graphic.
 When an operation, such as a transaction or origination, is injected into a node, it is normally propagated to the network after it has been pre-validated by the node.
 After the injection of \texttt{txa(1, \%A, parameter)}, however, the node broadcasts its derivation \texttt{txa(1, \%A\_c, parameter)} to the network, which invokes the controller entrypoint instead.
-If this operation finishes successfully for all validators, hence no counterexample is published on the network after a certain amount of block cycles, the node can finally broadcast the initial operation as a normal transaction to the network.
-In case of an assertion failure, the respective validator broadcasts the counterexample with the generated value to the network.
+If this operation finishes successfully for all validators, i.e., no counterexample is published on the network after a certain amount of block cycles, the node can finally broadcast the initial operation as a normal transaction.
+In case of an assertion failure, the respective validator broadcasts the counterexample including the generated random values.
 As a consequence of the broadcasted counterexample, the initial operation \texttt{txa(1, \%A, parameter)} should be reverted and rejected by the injecting node.
@@
 \centering
-  \includegraphics[width=0.7\textwidth]{figures/5-offline_tezos/interaction_monolithic_2}
+  \includegraphics[width=0.9\textwidth]{figures/5-offline_tezos/interaction_monolithic_2}
 	\caption{Interaction with a monolithic contract}
@@
 Calling these entrypoints with the same parameter is thus not possible.
-\\
 On the other hand, the explicit tags encode the link between production, controller and assertion code --- omitting them would dissolve all references between them.
 Hence, implicit entrypoint invocation cannot be supported in the execution mode of assertions.
-The compiler should enforce the use of explicit entrypoints in the parameter type declarations and the \texttt{txa} operation type must take a mandatory entrypoint specification as an argument.
+The assertion compiler thus needs to enforce the use of explicit entrypoints in the parameter type declarations and the \texttt{txa} operation type must expect a mandatory entrypoint specification as an argument.
+\lstinputlisting[label=lst:mono, language=Michelson, caption=Skeleton of a monolithic contract in Michelson, numbers=left, float]{listings/monolithic.tz}
 
 This thesis does not go into more detail about how the described execution model for a monolithic orchestration is designed and implemented in the blockchain protocol.
-What needs to be considered in future work concerning the protocol design, is the separate execution mode, possibly a dedicated transaction type as proposed above, the derivation of a transaction which attempts to find a counterexample, the handling of assertion failures and the exclusive acceptance of either the parameter (and thus the transaction) or a counterexample.
-
-\lstinputlisting[label=lst:mono, language=Michelson, caption=Skeleton of a monolithic contract in Michelson, numbers=left, float]{listings/monolithic.tz}
+What needs to be considered in future work concerning the protocol design is the separate execution mode, a dedicated operation type as proposed above, the derivation of a transaction which attempts to find a counterexample, the handling of assertion failures and the exclusive acceptance of the off-chain computation (and thus the transaction submitting it) or the counterexample.
 
 \subsubsection{Evaluation of the Monolithic Approach}
-The presented implementations of the monolithic approach each have strengths and weaknesses.
+The purely and hybrid monolithic implementation each have strengths and weaknesses.
 Generally, they share a pivotal disadvantage - they require a modification of the parent contract.
@@
 
-Besides these disadvantages, the monolithic approach has some distinct advantages.
-The production and controller entrypoints can be invoked independently, implicating that the validators do not have to run the production code while checking the assertion.
-Conversely, the assertion code is not rerun if the parameter is valid and the transaction is broadcast to the network.
-This reduces the transaction cost for the user, as well as the overall computational footprint of the transaction in the network.
+Besides these disadvantages, the monolithic approach provides a distinct advantage: the production and controller entrypoints can be invoked independently, implicating that the validators do not have to run the production code while checking the assertion.
+Conversely, the assertion code is not rerun if the parameter was validated and the actual transaction is broadcast to the network.
+This reduces the transaction cost for the user, as well as the overall computational footprint of the transaction and the validation in the network.
 
@@
 In the modular approach, the controller and each of the assertions are originated as separate contracts on the blockchain.
-The controller mirrors the interface of the parent contract, while each assertion contract only features a single entrypoint which corresponds to the raw type of the associated parent entrypoint.
+The controller mirrors the interface of the parent contract, while each assertion contract only features a single entrypoint, which corresponds to the raw type of the associated parent entrypoint.
 By keeping the assertion code separated, the parent contract remains pure and does not have to be modified.
 Similar to the hybrid solution mentioned in the monolithic approach, the controller calls the respective assertion contract $t$ times as an internal operation, before invoking the parent contract as operation $t+1$.
-In the case of empty assertions, the parent contract is invoked immediately --- the controller thus acts as a direct gateway.
-Corresponding to this architecture, the toolchain returns $m + 1$ contracts for a assertion specification, where $m$ is the number of specified assertions in the input.
+In the case of empty assertions, the controller acts as a direct gateway by invoking the parent contract immediately.
+Corresponding to this architecture, the toolchain returns $m + 1$ contracts, where $m$ is the number of specified assertions in the input.
 The code assembly and output of the toolchain is outlined in \figref{fig:modular_assembly}.
@@
 A proposed structure of the storage is a map from a unique identifier to an address.
-The entrypoints of the controller can then look up the address with their assigned identifier.
-The assignment of identifiers to entrypoints is hard-wired during the compilation, as is demonstrated in the rudimentary and simplified Liquidity implementation of a controller contract in \lstref{lst:manager_modular}.
-The corresponding storage initiation is the map $\lbrace 0 \rightarrow \langle \text{addr parent} \rangle; 1 \rightarrow \langle \text{addr assertion} \rangle \rbrace$ .
+The entrypoints of the controller can then look up the addresses of the parent and the respective assertion contract with an assigned identifier.
+The assignment of the identifiers is hard-wired during the compilation, as is demonstrated in the rudimentary and simplified Liquidity implementation of a controller contract in \lstref{lst:manager_modular}.
+The corresponding storage initiation for this contract is the map $\lbrace 0 \rightarrow \langle \text{address parent} \rangle; 1 \rightarrow \langle \text{address assertion} \rangle \rbrace$ .
 The hard-wired identifiers are used in lines 5 and 6 to retrieve the addresses from the storage.
@@
 Even though the transactions shown in the diagram state an explicit entrypoint tag, the scheme also supports implicit entrypoint invocations.
-Invocations of the assertion contract pass the parameter as a raw value, i.e., unpacked from the sum type constructors.
+Invocations of the assertion contract pass the parameter as a raw value.
 The general execution model is similar to the model for the monolithic approach, but requires a few modifications; because the controller mirrors the interface of the parent contract, the \texttt{txa} operation can be broadcast to the network directly --- a derivation to a distinct transaction, which calls the assertion selectively, is not necessary.
@@
 \centering
-  \includegraphics[width=0.9\textwidth]{figures/5-offline_tezos/interaction_modular.png}
+  \includegraphics[width=\textwidth]{figures/5-offline_tezos/interaction_modular.png}
 	\caption{Interaction with modular contracts}
@@
 
-The approach essentially has two weaknesses: firstly, the assertion and the parent cannot be called separately.
-As a result, the production code is run by every validator while searching for counterexamples, and when validating a block containing the accepted transaction.
+The approach essentially exhibits two weaknesses: firstly, the assertion and the parent cannot be called separately.
+As a result, the production code is run by every validator while searching for counterexamples.
+Moreover, the assertion code is also run when validating a block containing the accepted transaction.
 This increases the transaction cost for the user and requires a higher computational effort by the whole network.
@@
 \section{Backend Implementation}\label{sec:backend_impl}
-The following sections describe the tasks and implementations of the pipeline stages of the toolchain backend.
+The following sections describe the tasks and implementation of the pipeline stages in the toolchain backend.
 \begin{figure}[h]
@@
 For this, the backend uses the Tezos client libraries, which provide high-level functions wrapping RPCs to a configured node.
-The command line interface of the toolchain provides options for configuring the host address and port of the RPC interface to connect to a specific local or public node.
+The command-line interface of the toolchain provides options for configuring the host address and port of the RPC interface to connect to a specific local or public node.
 By default, the toolchain tries to connect to a local node on the default port.
@@
 
-Semantic rules imposed by Michelson do not have to be checked explicitly by the toolchain --- the RPC interface of Tezos nodes provides a function to parse and type check Michelson programs, which can be used to verify the correctness of the compilation result and reject any assertions with containing typing or other semantic errors.
+Semantic rules imposed by Michelson do not have to be checked explicitly by the toolchain --- the RPC interface of Tezos nodes provides a function to parse and type check Michelson programs, which can be used to verify the correctness of the compilation result and reject any assertions containing type or other semantic errors.
 
@@
 If the assertion does not specify an explicit entrypoint tag, the optional value is replaced with Tezos' notation for the default entrypoint.
-The subtree types for the parameter pattern and the assertion remain equivalent.
+The subtree types for the parameter pattern and the assertion remain equivalent to the generic subtree types.
 
@@
 Given a list of Tezos-specific ASTs, the task of the type checker is to link each AST to the respective entrypoint of the parent contract.
-This stage module can be alternatively referred to as the linker.
+This stage module can therefore also be referred to as the ''linker``.
 The linking is needed by the compiler to correctly assemble and type the controller and assertion contracts.
-As a simple example, the linker should correctly assign the AST of the first assertion in \texttt{Example.tza} (\lstref{lst:linker_assertion}) to entrypoint A of the parent contract \texttt{Example.tz} ( \lstref{lst:linker_parent}), and the second assertion to entrypoint B.
+As a simple example, the linker should correctly assign the AST of the first assertion in \texttt{Example.tza} (\lstref{lst:linker_assertion}) to entrypoint A and the second assertion to entrypoint B of the parent contract \texttt{Example.tz} (\lstref{lst:linker_parent}).
 
@@
 
-Because explicit entrypoint tags are optional in Michelson contracts, the linking is primarily done by type matching between the declared parameter types in the parent and the assertions.
-Tags, if specified, are only considered if type matching does not result in an unambiguous assignment.
-The linking fails, if an assertion cannot be matched to any parent entrypoint, or several assertions match the same entrypoint, i.e., if no injective, non-surjective mapping was found.
+Because explicit entrypoint tags are optional in Michelson contracts, the linking is primarily done by type matching between the declared parameter types in the parent and parameter patterns in the assertions.
+If the type matching does not result in an unambiguous assignment between an assertion and an entrypoint, i.e., the parameter pattern matches the type of several entrypoints, the linker considers the specified tags in an effort to resolve the ambiguity.
+The linking fails if no injective, non-surjective mapping from the set of assertions to the set of entrypoints was found regardless.
 
-As a first step, the linker retrieves and parses the parameter type of the parent contract.
-The parent contract is provided by the user as a file, a blockchain address, or a raw string.
-In case the contract is given as an address, the code is retrieved from the blockchain.
-The parameter pattern of each assertion AST is then compared recursively to the types of each entrypoint, until a match has been found --- this entrypoint is then blocked for other assertions.
-
-As explained in \secref{sec:tezos}, entrypoints can be invoked implicitly by wrapping the parameter into the respective union type constructors.
-Alternatively, they can be called explicitly by stating an entrypoint tag and passing the raw parameter value.
-The same applies for the specification of assertions - when omitting the tag, the parameter pattern must be declared in respect to the default entrypoint.
+\subsubsection{Parameter Patterns Revisited}
+As explained in \secref{sec:tezos}, transactions on Tezos can invoke entrypoints implicitly by invoking the default entrypoint and wrapping the parameter value into the respective union type constructors.
+Alternatively, they can be called explicitly by stating an entrypoint tag and passing the raw parameter value as an argument.
+The same principle applies for the specification of assertions - when omitting the tag in the assertion signature, the parameter pattern must be declared in respect to the default entrypoint.
 If the assertion states an explicit tag, it may declare a pattern of the raw parameter type.
-\lstref{lst:impl_expl} shows two valid assertion specifications for entrypoint A of \lstref{lst:linker_parent} --- the first uses an explicit and the second an implicit declaration of the parameter pattern.
-\begin{lstlisting}[language=Assertion, numbers=none, caption=Explicit and implicit assertion specification, label=lst:impl_expl]
+\lstref{lst:impl_expl} shows two valid assertion specifications for entrypoint A of the contract \texttt{Example.tz} (\lstref{lst:linker_parent}) --- the first specification uses an explicit tag paired with the pattern of the raw parameter type, while the second does not specify a tag and declares the parameter pattern with respect to the default entrypoint, i.e, wrapped into the sum type constructor \texttt{left}.
+\begin{lstlisting}[language=Assertion, numbers=none, caption=Explicit and implicit parameter specification in assertions, label=lst:impl_expl]
 (entrypoint %A (i : int) ...)
@@
 
-The tags given in the assertion specification do not necessarily have to be identical with the tags of the parent contract; in some cases, they may be chosen differently for documentation purposes.
-However, the tags can and should be used to resolve ambiguity in the mapping between assertions and entrypoints.
-\lstref{lst:ambiguity_assertion} provides four examples of assertions, which cannot be assigned unambiguously to an entrypoint of the contract given in \lstref{lst:ambiguity_parent}.
-Since the entrypoints of \texttt{Example2.tz} have the same raw parameter type, and none of the given assertions tags refer to one of them explicitly, the linker cannot infer which entrypoint they refer to.
-In all four cases, providing the tag \texttt{A} or \texttt{B} resolves the ambiguity.
-If the parent entrypoint does not specify a tag, the ambiguity can be resolved by specifying the parameter type in respect to the default entrypoint, which is unambiguous by design.
+The tags given in the assertion specification do not necessarily have to be identical with the tags of the parent contract; they may be chosen differently for documentation purposes, particularly if the parent contract does not state any tags.
+However, tags can and should be used to resolve ambiguity in the linking between assertions and entrypoints by mirroring the entrypoint tags of the parent contract.
+
+\subsubsection{Resolving ambiguity}
+\lstref{lst:ambiguity_assertion} provides four examples of assertions which cannot be linked unambiguously to an entrypoint of the contract given in \lstref{lst:ambiguity_parent}.
+Since the entrypoints of \texttt{Example2.tz} have the same raw parameter type \texttt{int}, and none of the given assertions tags refer to one of them explicitly, the linker cannot infer which entrypoint they refer to.
+In all four cases, providing an explicit tag (\texttt{A} or \texttt{B}) can resolve the ambiguity.
+If the parent entrypoint does not specify a tag, the ambiguity can be resolved by omitting the tag and specifying the parameter pattern in respect to the default entrypoint, e.g.
+\texttt{left \_} or \texttt{right (i : int)}.
 
@@
 
-Another type of ambiguity can be caused by the fact that entrypoints can be sub-entrypoints of others.
-As an example, consider the parameter type \texttt{(or (int \%A) (or \%BC (int \%B) (int \%C)))}.
+Another type of ambiguity is caused by the fact that entrypoints can be sub-entrypoints of others.
+As an example, consider the parameter type of contract \texttt{Example3} in \lstref{lst:overlap_parent}.
 Entrypoints \texttt{B} and \texttt{C} are sub-entrypoints of \texttt{BC} --- invoking \texttt{BC} will inevitably result in an invocation of either \texttt{B} or \texttt{C}, depending on the parameter value.
-Thus, assertions may ``overlap'' if a separate assertion is declared for a super- and a sub-entrypoint and result in two assertion specifications for the same entrypoint.
-Hence, the linker needs to detect overlapping assertions and reject assertion contracts where appropriate.
+Thus, assertions may ``overlap'' if a separate assertion is declared for a super- and a sub-entrypoint and result in two assertion specifications for the same entrypoint, as is demonstrated in \lstref{lst:overlap_assertion}.
+The linker detects such overlapping assertions and rejects assertion specifications containing such.
+Hence, a valid assertion contract can specify an assertion for entrypoint \texttt{AB} only, or for entrypoints \texttt{A} and \texttt{B}, but not for \texttt{AB}.
 
-In summary, the linker rejects any input containing ambiguous, duplicate, overlapping or mismatching assertions, i.e., assertions whose types do not match any entrypoint.
-If each assertion could be linked to exactly one entrypoint, the mapping from entrypoint to assertion is returned.
-Because entrypoints can be anonymous, the mapping represents the entrypoints by the constructor nesting of their parameters.
-The resulting mapping for \texttt{Example.tz} and \texttt{Example.tza}, for instance, would be \\
-\texttt{\{ Left \textrightarrow <AST assertion A>; Right \textrightarrow <AST assertion B>\} }.
+\vspace{\baselineskip}
+\noindent
+\begin{minipage}{.45\textwidth}
+\begin{lstlisting}[label=lst:overlap_parent, numbers=none, language=Michelson, caption=Example3.tz]
+parameter (or %AB (int %A)
+                  (int %B));
+...
+\end{lstlisting}
+\end{minipage}\hfill
+\begin{minipage}{.5\textwidth}
+\begin{lstlisting}[label=lst:overlap_assertion, numbers=none, language=Assertion, caption=Example3.tza with overlapping assertions]
+(entrypoint %AB (left  i) ...)
+(entrypoint %A j ...)
+\end{lstlisting}
+\end{minipage}
+\vspace{\baselineskip}
+
+\subsubsection{Linking Process}
+As a first step, the linker retrieves and parses the parameter type of the parent contract.
+The parent contract is provided by the user as a file, a blockchain address, or a raw string.
+In case the contract is given as an address, the code is retrieved from the blockchain.
+From the parsed parameter type, a list of all named and anonymous entrypoints with their raw input types is extracted.
+For these steps, the Tezos client and protocol libraries are utilized.
+
+Based on the extracted pool of entrypoints and the list of assertion ASTs, the linker then iteratively builds a mapping between entrypoints and assertions.
+The parameter pattern of each assertion AST is compared to the parameter type of all entrypoints in the pool.
+All matching entrypoints are collected in a list.
+If this list is empty, linking the assertion fails due to a type mismatch and the pipeline terminates.
+In case the list contains several entrypoints, the linker considers the tags in order to resolve the ambiguity.
+If the tags do not lead to a resolution, the pipeline terminates due to an ambiguous assertion specification.
+Lists containing exactly one match can be resolved to an assignment directly.
+After an AST could be linked to an entrypoint, the assignment is added to the mapping and the matching entrypoint is removed from the pool of unlinked entrypoints.
+Additionally, all sub- and super-entrypoints are removed from the pool.
+By removing these entrypoints, the linker is able to detect duplicate or overlapping assertions.
+
+After successfully finding a valid assignment for all assertions, the linker returns the mapping.
+Because entrypoints can be anonymous, the mapping represents the entrypoints with the constructor nesting of their parameters.
+\lstref{lst:unionpath} shows the definition of the type for such a representation.
+\begin{lstlisting}[label=lst:unionpath, language=, numbers=none, caption=Type representing entrypoints according to the union constructor nesting]
+type union_path = Left of union_path
+                | Right of union_path
+                | T
+\end{lstlisting}
+Using this type, entrypoints \texttt{A} and \texttt{B} of \texttt{Example.tz}, for instance, are represented by \texttt{Left T} and \texttt{Right T}, while the default entrypoint is represented by \texttt{T}.
+Given \texttt{Example.tza}, the linker thus returns the mapping \\
+\texttt{\{ Left T \textrightarrow \, <AST assertion A>; Right T \textrightarrow \, <AST assertion B>\} }.
 
@@
 After compilation, the Michelson programs can be validated for correctness by the Tezos node, which will intercept any assertions containing type errors.
-After sanity-checking the programs, the output of the compiler is the target code for the controller and assertion contracts.
-As an additional output, it should return a piece of template code for the correct storage initialization of the controller.
+After this sanity-check, the compiler outputs the target code for the controller and assertion contracts.
+As an additional output, it should return a piece of template code for the correct storage initialization of the controller contract.
 Before originating the controller contract, the user fills in the blockchain addresses of the other modules.
@@
 If the pattern excludes any special values of the data type (e.g., \texttt{cons head tail} excludes empty lists), the generated code should reflect this.
-Excluded values should never cause the assertion to fail.
-In the example of \texttt{cons}, the generated code should thus contain the branching shown in \lstref{lst:cons}.
+It has not been specified yet, if excluded values should never or always cause the assertion to fail.
+In the example of \texttt{cons} and assuming excluded values pass the assertion, the generated code could contain the branching shown in \lstref{lst:cons}.
 The branch in line 1 is executed if the list contains at least one element, and should contain the assertion code.
@@
 
-The generated code of the assertion body and the parameter type can be plugged into a template, which contains the necessary boilerplate code for a contract.
+To simplify the compilation, the generated code of the assertion body and the parameter type can be plugged into a template containing the necessary boilerplate code for a contract.
 Such a template is shown in \lstref{lst:contract_templ} --- the placeholders \texttt{<?>} mark the locations where the individual code is inserted.
+Since assertions do not use any storage as of now, the storage type is set to unit.
 Lines 3-5 prepare the stack, s.t.
 the parameter and storage are the two top elements.
-The lines below the placeholder for the body clean up the stack and leave it according to calling convention, i.e., the program returns an empty list of internal operations and the unit storage.
+The lines below the placeholder for the body leave the stack according to calling convention, i.e., the program returns an empty list of internal operations and the unit storage.
 \lstinputlisting[label=lst:contract_templ, language=Michelson, caption=Template code for assertion contracts in Michelson, numbers=left]{listings/assertion_template.tz}
@@
 \subsubsection{Compilation of the Controller Contract}
-The generation of the \texttt{parameter} and \texttt{storage} primitives is trivial.
+The generation of the \texttt{parameter} and \texttt{storage} primitives for the controller contract is trivial.
 Given that the controller acts as a proxy, the parameter type can be copied from the parent contract.
@@
 The code body is generated recursively based on the parameter type.
-It consists of two types of entrypoints, which either act as a direct gateway to the parent contract, or trigger an assertion check before invoking the parent.
+It consists of two types of entrypoints, which either act as a direct gateway to the parent contract in the case of empty assertions, or trigger an assertion check before invoking the parent.
 
@@
 Assuming the parent address is always stored under the same key, e.g.
-with id 0, such gateways can be inserted as fixed boilerplate code.
+with id 0, such gateways can be generated as fixed boilerplate code.
 
@@
 \item Read the addresses from the assertion and parent contract from storage
-\item Calculate $t$
+\item Calculate the number of test runs $t$
 \item Compile a list of $t$ internal operations invoking the assertion with the raw parameter
 \item Create an internal operation calling the parent contract, passing the original parameter and funds
-\item Return a list of all operations and the unchanged storage
+\item Return (i.e., push to the stack) a list of all internal operations and the unchanged storage
 \end{enumerate}
-\secref{sec:prob_threshold} stated a formula to determine the total number $t_{total}$ of required test runs for a given probability threshold $c$, and the size of the search space $n$.
-From $t_{total}$, the number of test runs $t$ per validator can be calculated according to \eqref{eq:t_validator}.
+\secref{sec:prob_threshold} stated a formula to determine the total number $t_{total}$ of required test runs, given a probability threshold $c$ and the size of the search space $n$.
+From $t_{total}$ the number of test runs $t$ per validator can be calculated according to \eqref{eq:t_validator}.
 Since $n$ can only be obtained at runtime, the compiler needs to derive a formula to determine this value from the ranges of the random generators.
@@
 \paragraph{Algorithm}
-Algorithm \ref{alg:compile_manager} shows the outline of a simplified algorithm, which builds the code body of the controller.
+Algorithm \ref{alg:compile_manager} shows the outline of a simplified algorithm which builds the code body of the controller.
 It recursively iterates over the parameter type and builds the body by nesting \texttt{IF\_LEFT} instructions (cf.
 \lstref{lst:entrypoints}).
-Within the entrypoint branches, the compiler either generates gateway or assertion triggering code, based on the mapping given by the linker.
+Within the entrypoint branches, the compiler either generates gateway or assertion triggering code (based on the mapping given by the linker).
 
@@
 	\State global i = 1
-	\Function{compile\_controller}{parameter type}
+	\Function{compileController}{parameter type}
 	\If{ty = Or(l,r)}
-	\State code\_left = "IF\_LEFT {" + compile(l) + "}"
-	\State code\_right = "{" + compile(r) + "}"
-	\State \Return code\_left + code\_right
+	\State codeLeft = "IF\_LEFT {" + compile(l) + "}"
+	\State codeRight = "{" + compile(r) + "}"
+	\State \Return codeLeft + codeRight
 	\Else
 	\If{entrypoint has assertion}
-	\State code = generate\_assertion\_trigger(parameter type, i, assertion)
+	\State code = generateAssertionTrigger(parameter type, i, assertion)
 	\State storage.add(i++, entrypoint tag)
 	\Else
-	\State code = generate\_gateway()
+	\State code = generateGateway()
 	\EndIf
@@
 
-During this recursion, the compiler also builds the address map for the storage, such that the entrypoints can look up the address of the assertion and parent contracts during runtime.
-To this end, it keeps the counter \texttt{i} to create unique IDs for each entrypoint with an assertion --- this ID is then hard-wired into the storage access within this entrypoint.
+During this recursion, the compiler also builds the address map for the storage, such that the entrypoints can look up the addresses of the assertion and parent contracts during runtime.
+To this end, it keeps the counter \texttt{i} to create unique IDs for each entrypoint with an assertion --- this ID is then hard-wired into the instruction accessing the storage within this entrypoint.
 The address of the parent contract is always stored under ID 0.
 
-After compilation, this map is translated to a template for a Michelson value and returned to the user.
+After compilation, this map is translated to a template for a Michelson value of type \texttt{map} and returned to the user.
 Because the addresses are not known at compilation time, the map values should be descriptive place-holders, s.t.
-the user can replace them with the corresponding addresses.
-After the user replaced the placeholders with the actual addresses, this Michelson value should then be passed to the origination as the initial storage.
+the user can replace them with the corresponding addresses after the respective contracts have been originated.
+After the user replaced the placeholders with the actual addresses, this Michelson value should then be passed to the origination as the initial storage value.
 As an example, the compilation of the controller contract for \texttt{Example.tz} and \texttt{Example.tza} in Listings \ref{lst:linker_parent} and \ref{lst:linker_assertion} could return the following template:\\ \texttt{(Elt 0 <addr parent>; Elt 1 <addr A\_a>; Elt 2 <addr B\_a>)}.
@@
 
-It depends on the language, how the compiler of the IR can be integrated into the toolchain.
+It depends on the language how the compiler of the IR can be integrated into the toolchain.
 The Ligo project builds their compiler into a \texttt{dune}\footnote{dune \cite{dune} is a build system for OCaml} library, which can be imported directly into the code base of the toolchain.
@@
 \includegraphics[width=\linewidth]{figures/5-offline_tezos/pipeline_liq}
-\caption{Pipeline with IR compilation and an external toolchain}
+\caption{Pipeline with IR compilation and an external compiler}
 \label{fig:pipeline_liq}
@@
 
-However, a realistic use-case for using Liquidity as an IR ,is the implementation of the monolithic orchestration scheme.
+However, a realistic use-case for using Liquidity as an IR is the implementation of the monolithic orchestration scheme.
 In Liquidity, each entrypoint is declared as a function expecting a parameter and the current storage.
@@
 As the Liquidity project provides a decompiler to translate Michelson contracts into Liquidity programs, the compiled assertion functions can simply be appended to the decompiled parent contract.
-This outsources most of the compilation complexity to the Liquidity compiler.
+This results in an assembly scheme as depicted in \figref{fig:liq_assembly} and outsources most of the compilation complexity to the Liquidity compiler.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=\linewidth]{figures/5-offline_tezos/liquidity_assembly}
+\caption{Monolithic assembly using Liquidity as IR}
+\label{fig:liq_assembly}
+\end{figure}
 

### 2021-05-24 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
Final revision - evaluation chpt 5

@@
 \section{Cost Analysis and Evaluation}\label{sec:cost_analysis_distributed}
-In this section, the costs of checking a formula with the proposed approach and implementation for distributed assertion checking are evaluated.
+In this section, the costs of checking a formula, with the proposed approach and implementation for distributed assertion checking, are evaluated.
 \secref{sec:usecase_cost} already determined the cost for a local validation as a benchmark.
-It stated \eqref{eq:gas_transaction} to calculate the gas consumption of a transaction, including internal operations.
+It stated \eqref{eq:gas_transaction} to calculate the gas consumption of a transaction including internal operations.
 It identified the gas consumption of deserialization, data parsing and interpretation as growing factors, as they depend on the size of the input parameter.
@@
 \end{align}
-Based on the resulting inequality in \eqref{eq:gas_validator}, which specifies the costs incurred by each internal operation to the assertion contract as a basis of the total gas consumption per validator, it can be concluded that the overall gas consumption of the distributed validation is higher than in the case of a local validation.
+Based on the resulting inequality in \eqref{eq:gas_validator}, which specifies the costs incurred by each internal operation invoking the assertion contract as a basis of the total gas consumption per validator, it must be concluded that the overall gas consumption of the distributed validation is higher than in the case of a local validation.
 
@@
 Appendix \ref{apx:foobar_distributed} contains the Michelson code for the controller, assertion and parent contracts.
-In order to preserve comparability between benchmark of the local and the distributed implementation, the controller contracts were configured with a probability threshold $c = \frac{1}{e}$, s.t.
+In order to preserve comparability between the benchmark of the local and the distributed implementation, the controller contracts were configured with a probability threshold $c = \frac{1}{e}$, s.t.
 that the necessary number of test runs is equal to the sizes of the search spaces.
-\figref{fig:cost_distributed} shows the reported gas consumption per validator on the test network Delphinet for different input sizes.
-Since the effective number of test runs is always a multiple of 32, the cost function approximates a step function.
+\figref{fig:cost_distributed} shows the reported gas consumption per validator for different input sizes on the test network Delphinet.
+Since the effective number of test runs is always a multiple of 32, the cost functions approximate a step function.
 
@@
 
-The results show, that the cost incurred by a single validator, checking a subset of a search space with size $n$, is already considerably higher than a complete validation in a local approach (cf.
+The results show, that the cost incurred by a single validator, checking a subset of a search space of size $n$, is already considerably higher than a complete validation in a local approach (cf.
 \figref{sec:usecase_cost}).
 In the case of the list parameter (contract \texttt{Bar}), the gas consumption even increases exponentially due to the multiplied reading and parsing costs.
-Moreover, the probability of accepting an invalid parameter with the given configuration is, in the worst case, 37\%, which results in a bad cost-performance ratio.
+Moreover, the cost-performance ratio is also worse, as the probability of accepting an invalid parameter with the given configuration is 37\% in the worst case.
 
 In conclusion to these results, the proposed implementation of the distributed scheme has to be evaluated as inefficient and unable to achieve an improvement regarding the scalability of applications on Tezos.
-However, the approach is nonetheless promising, as it reduces the required computation per node to a fraction of the verification, and thus also reduces the computational footprint of the transaction within the network.
+However, by reducing the required computation per node to a fraction of the verification, it has the potential to reduce the computational footprint of the transaction within the network.
 As a prerequisite, it is crucial to lower the costs of the verification.
 This thesis already mentioned some alternative approaches and implementations, which might achieve this; \secref{sec:alt_random} introduces the possibility to coordinate the validators in a systematic iteration of the search space.
-Although this does not reduce the cost per test run, this reduces the quantify of necessary test runs to achieve a reliable result.
-This chapter described several other orchestration schemes, some of which reduce the number of emitted internal operations.
+Although this does not reduce the cost per test run, it reduces the quantity of necessary test runs to achieve a reliable result.
+Furthermore, this chapter described several other orchestration schemes, some of which reduce the number of emitted internal operations.
 As the inter-contract communication accounts for most of the gas consumption in the modular approach, avoiding them is an effective way of reducing the costs.
 In this regard, a concrete improvement of the proposed architecture could be to merge the controller and assertion code into a single contract.
-This corresponds to the inverse hybrid architecture as described in \secref{sec:monolithic}.
-Instead of $(t+1)$ internal operations, this only requires a single internal operation calling the parent contract.
+This corresponds, to some extend, to the inverse hybrid architecture as described in \secref{sec:monolithic}.
+Instead of $t+1$ internal operations, this only requires a single internal operation calling the parent contract (provided that the controller an assertion code are merged into one entrypoint).
 

### 2021-05-24 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
Final revision - chpt 5 open questions

@@
 \section{Open Questions}
-There remain two aspects of the off-chain design, which could not be addressed in detail by this thesis. These aspects are outlined briefly in the following sections.
+Two remaining aspects of the off-chain design could not be addressed in detail by this thesis. These aspects are outlined briefly in the following sections.
 
@@
 The counterexample is then validated like any other transaction on the blockchain.
+Nodes publishing false counterexamples should be penalized in order to prevent denial of service attacks.
+After a counterexample has been validated, the respective transaction submitting the invalid off-chain computation should be rejected.
+Consequently, the transaction and counterexample need to be relatable, e.g.
+by using an operation hash as an ID.
 
@@
 \item \texttt{Origination(assertion, address counterexample)}
-\item \texttt{Origination(controller, address [assertion], address parent)} 
+\item \texttt{Origination(controller, [address assertion], address parent)} 
 \end{enumerate}
-
-In order to reject a transaction submitting off-chain computations in case of a published counterexample, however, the network needs to be able to relate a counterexample to the respective transaction.
 

### 2021-05-24 assertions/doc/thesis-bernhardt/chapters/6-conclusion.tex
Final revision - conclusion + appendix

@@
 Complex blockchain-based applications suffer from high computation costs and limited scalability.
-A consequential measure to address this issue, is to move computations off the chain and only verify the correctness of submitted results on the blockchain.
+A consequential measure to address this issue is to move computations off the chain and only verify the correctness of submitted results on the blockchain.
 This thesis  proposed assertions for distributed refutation as a probabilistic implementation of this verification.
@@
 To support this model on the target platform Tezos, a toolchain was developed to allow developers to specify explicit assertions and generate corresponding smart contracts.
-These contracts check the property point-wise within the quantification domain and identify counterexamples when executed by the validators.
+These contracts check the property point-wise within the quantification domain and can identify counterexamples with a configurable probability when executed by the validators.
 For the specification of assertions, a simple domain-specific language was defined.
 
-For the proposed architecture, the conducted costs analysis shows high transaction fees for the submission of off-chain computations,  due to high verification costs.
-Although the verification might still be more efficient than the execution itself, it can be assumed that the cost reductions are equalised in cases of moderate complexity of off-chain computations.
+Based on the proposed architecture, the conducted costs analysis shows high transaction fees for the submission of off-chain computations due to high verification costs.
+Although the verification might still be more efficient than the execution itself, it can be assumed that the cost reductions are not significant enough in cases of low or moderate complexity of off-chain computations.
 Inter-contract communication was identified as a main driving factor of the verification cost.
@@
 
-Based on either the proposed or a modification of the architecture, subsequent tasks include the implementation of the compiler in order to conclude the toolchain.
+Based on the preparations and work done in this thesis, subsequent tasks on this project include the implementation of the compiler to conclude the toolchain.
 As addressed in the introduction, the implementation of distributed assertions on blockchains also requires a design and implementation of a protocol amendment.
-Many of the aspects that need to be considered by the protocol design have already been pointed out by this work.
-This includes, i.a., the extensions to Michelson and Tezos' VM to support random value generation, the implementation of a dedicated execution mode, the withholding of the transaction submitting an off-chain computation until it has been verified, and the rejection of this transaction as a consequence of a verified counterexample.
+Many of the aspects that need to be considered by the protocol design have already been pointed out throughout this thesis.
+This includes, i.a., the extensions to Michelson and Tezos' VM to support random value generation, the implementation of a dedicated execution mode, the withholding of the transaction submitting an off-chain computation until the assertions have been executed, and the rejection of this transaction as a consequence of a verified counterexample.
 
-Besides the completion of the proof-of-concept implementation, the assertion language can be extended with features, such as variables and user-defined functions, to improve (re-)usability.
-Furthermore, an interesting extension is the support for properties formulated with existential quantification, as this allows to verify off-chain computations by distributed validation in addition to distributed refutation.
+Besides the completion of the proof-of-concept implementation, the assertion language can be extended with features to improve its (re-)usability, such as variables and user-defined functions.
+Furthermore, an interesting extension to the execution model is the support for properties formulated with existential quantification, as this allows to verify off-chain computations by distributed validation as opposed to to distributed refutation.
 

### 2021-05-24 assertions/doc/thesis-bernhardt/chapters/appendix.tex
Final revision - conclusion + appendix

@@
 \chapter{Michelson Implementations of \texttt{Foo} and \texttt{Bar}}\label{apx:cost_analysis_contract}
-The following contracts are the Michelson equivalent of the dummy contracts given in \secref{sec:usecase_cost}.
+The following contracts are the Michelson implementations of the dummy contracts given in \secref{sec:usecase_cost}.
 \section{Foo}
@@
 				 language=Michelson,
-				 caption=Dummy Michelson contract executing a dynamic loop]{listings/foo.tz}
+				 caption=Dummy Michelson contract executing a dynamic loop (\texttt{Foo.tz})]{listings/foo.tz}
 
@@
 				 language=Michelson,
-				 caption=Dummy Michelson contract iterating over a dynamic list]{listings/bar.tz}
+				 caption=Dummy Michelson contract iterating over a dynamic list (\texttt{Bar.tz})]{listings/bar.tz}
 
 \chapter{Assertion Grammar in EBNF}\label{apx:grammar}
-The following two versions of the grammar implement the prefix and infix notations for the assertion syntax.
+The following two versions of a grammar in extended Backus-Naur form (EBNF) implement the prefix and infix notations for the assertion syntax.
 
@@
 
+The following listings show the implementation of the list accessing operator \texttt{nth} using the pre-defined loop instruction.
+\lstref{lst:nth_liq} shows a readable implementation in Liquidity; it contains necessary boilerplate code to make it compilable.
+The compilation result (including the boilerplate code) is given in \lstref{lst:nth_liq}.
+
 \lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
@@
 
-\chapter{Controller Contract Code in Liquidity}\label{apx:controller_liq}
+\chapter{Controller Contract Code in \\ \mbox{Liquidity}}\label{apx:controller_liq}
 \lstinputlisting[label=lst:manager_templ_liq, language=Michelson, caption=Controller code in Liquidity]{listings/controller.liq}
@@
 				 label=lst:controller_michelson,
-				 caption=Controller code in Michelson]{listings/controller.tz}
+				 caption=Controller code in Michelson featuring one gateway and one assertion entrypoint]{listings/controller.tz}
 
 \chapter{Distributed Michelson Implementation of \texttt{Foo} and \texttt{Bar}}\label{apx:foobar_distributed}
-The following contracts are a restructuring of the contracts given in Appendix \ref{apx:cost_analysis_contract}, s.t. they implement the proposed orchestration strategy.
+The following contracts are a restructuring of the contracts given in Appendix \ref{apx:cost_analysis_contract}, s.t. they implement the modular orchestration scheme.
 
-\section{Foo}
+\section{Contract Foo}
 \lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
@@
 				 label=lst:foo_manager,
-				 caption=Controller contract of \texttt{Foo}]{listings/foo_manager.tz}
+				 caption=Controller contract for \texttt{Foo.tz}]{listings/foo_manager.tz}
 \lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
@@
 				 label=lst:foo_assertion,
-				 caption=Assertion contract of \texttt{Foo}]{listings/foo_assertion.tz}
+				 caption=Assertion contract for \texttt{Foo.tz}]{listings/foo_assertion.tz}
 \lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
@@
 				 label=lst:foo_parent,
-				 caption=Parent contract of \texttt{Foo}]{listings/foo_parent.tz}
+				 caption=Parent contract (\texttt{Foo.tz})]{listings/foo_parent.tz}
 
-\section{Bar}
+\section{Contract Bar}
 \lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
@@
 				 label=lst:bar_manager,
-				 caption=Controller contract of \texttt{Bar}]{listings/bar_manager.tz}
+				 caption=Controller contract for \texttt{Bar.tz}]{listings/bar_manager.tz}
 \lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
@@
 				 label=lst:bar_assertion,
-				 caption=Assertion contract of \texttt{Bar}]{listings/bar_assertion.tz}
+				 caption=Assertion contract for \texttt{Bar.tz}]{listings/bar_assertion.tz}
 \lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
@@
 				 label=lst:bar_parent,
-				 caption=Parent contract of \texttt{Bar}]{listings/bar_parent.tz}
+				 caption=Parent contract (\texttt{Bar.tz})]{listings/bar_parent.tz}

### 2021-05-24 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
Final revision - conclusion + appendix
Last fixes

@@
 
-\section{Tezos}\label{sec:tezos}
+\section{Introduction to Tezos}\label{sec:tezos}
 The Tezos blockchain is presented in its whitepaper as a \enquote{generic and self-amending crypto-ledger} \cite{goodman_tezos_2014}.
@@
 Tezos' transaction fee system is similar to Ethereum's \cite{wood_ethereum_2021} - it is gas-instrumented and besides a base fee, every operation and byte of storage during contract execution has to be paid for by the user.
-However, Tezos imposes a hard cap on the amount of gas that can be consumed per operation (including internal transactions) \cite{tezos_docs}\cite{morley_repo}, whereas Ethereum limits the gas quota only in respect to blocks \cite{wood_ethereum_2021}.\\
+However, Tezos imposes a hard cap on the amount of gas that can be consumed per operation (including internal transactions) \cite{tezos_docs}\cite{morley_gasmodel}, whereas Ethereum limits the gas quota only in respect to blocks \cite{wood_ethereum_2021}.\\
 Tezos is written in the multi-paradigm programming language OCaml.
@@
 Previous extensions to the Michelson language, such as the addition of the instruction ``\texttt{DIG n}'' in protocol 005 Babylon \cite{tezos_michelson_ext}, can be used as a guideline for the extension.
-The gas cost specification of existing instructions \cite{tezos_repo_gas} should be used as an orientation in specifying the costs of new instructions.
+The gas cost specification of existing instructions should be used as an orientation in specifying the costs of new instructions.
 
@@
 The lines below the placeholder for the body leave the stack according to calling convention, i.e., the program returns an empty list of internal operations and the unit storage.
-\lstinputlisting[label=lst:contract_templ, language=Michelson, caption=Template code for assertion contracts in Michelson, numbers=left]{listings/assertion_template.tz}
+\lstinputlisting[label=lst:contract_templ, language=Michelson, float, caption=Template code for assertion contracts in Michelson, numbers=left]{listings/assertion_template.tz}
 

### 2021-05-24 papers/contract-modules/fmbc2021/fmbc-main.tex
Add files via upload

@@
 because the balance is at least as high as in the off-chain sample. 
+\section{Related work}
+\label{sec:related-work}
+RPC APIs, often provided by current blockchains such as Ethereum \cite{eth-whitepaper} and Tezos \cite{tezos-whitepaper}, use loosely structured data, such as a JSON-based format, which is difficult for a programmatic program to handle.
+As a result, there is increasing work on providing better programmatic interfaces to the blockchains.
+Web3.js \cite{web3.js} provides an Ethereum JavaScript API and offers Java Script users a convenient interface to interact with the Etherum blockchain.
+Later, Web3.py \cite{web3.py}, derived from Web3.js, is developed to provide a Python library for interacting with Ethereum.
+Tezos prove a PRC API that utilizes JSON format for both input and output data, which is neither convenient nor programmatic.
+
+Smart contract-based applications often require interaction between a smart contract on the blockchain and the outside world.
+However, smart contracts cannot connect to external sources on their own.
+This is where Oracles \cite{oracle-patterns,call-action-oracle,oracles-study} come into play.
+Oracles act as a bridge between smart contracts and external sources.
+Namely, they collect and verify external information and make it available to smart contracts on the blockchain.
+Oracles may need to observe the state of the chain to determine what information to send.
+Several research works have been conducted to provide oracle solutions for the Blockchain.
+Adler et al.\cite{blockchain-oracles} proposed a framework to provide developers with a guide for incorporating oracles into Blockchain-based applications.
+Practically, Ellis et al.
+\cite{chainlink-whitepaper} proposed the decentralized oracle network Chainlink to provide reliable, tamper-proof input for smart contracts on any blockchain.
+ChainLink securely provides data to APIs on behalf of a smart contract.
+
+An oracle responds to an event by 
+transmitting information to a smart contract through a smart contract invocation.
+In addition.
+the original smart contract must inherit an additional smart contract from Oracle in order to interact with external data sources.
+Deployment costs are increased when using Ethereum smart contracts with Oracle as the data carrier.
+To deal with this problem, the paper \cite{LIU2019590} proposes a low-cost data carrier architecture for a blockchain-enabled IoT environment.
+
+\section{Conclusion}
+\label{sec:conclusion}
+Current blockchains often provide low-level interfaces to interact with smart contracts.
+These interfaces work with loosely structured data that is impractical for programs to handle.
+This paper presents outgoing research on programmatic interaction with a smart contract on the Tezos blockchain that could benefit developers of smart contract applications and Oracles.
+The approach does not provide a general API, but targets each typical smart contract by generating a specialized contract module that provides a typed high-level interface from a smart contract implementation.
+In doing so, errors in contract calls are explicitly specified in a user-defined data type.
+A contract call is treated as a function call that grants a typed safe of data in the Ocaml language.
+In addition, the module can check preconditions before the actual call to reduce the waste of a failed call.
+As future work, we combine the contract module with our typed API designed to provide a general type-safe programmatic API for the Tezos blockchain.
 

### 2021-05-25 papers/contract-modules/fmbc2021/fmbc-main.tex
contract syntax

@@
   val close
-    : Tezos.pukh -> ?fee:Tezos.tz -> ?amount:Tezos.tz
+    : Tezos.pukh -> ?fee:Tezos.tz
     -> (Tezos.status, close_errors) Tezos.monad
@@
 the transaction fee, an argument for passing an amount of tokens
-(optional for an unpaid entrypoint), the next argument would be for
+(only for a paid entrypoint), the next argument would be for
 the parameter; it is omitted here because its type is
@@
   requires (amount > balance)
-  raises "too low" as too_low      (** bid too low *)
+  raises "too low"                 (** bid too low *)
 end
@@
 \label{sec:conclusion}
+
 Current blockchains often provide low-level interfaces to interact with smart contracts.

### 2021-05-25 papers/contract-modules/fmbc2021/fmbc-main.tex
conclusion

@@
 
-Current blockchains often provide low-level interfaces to interact with smart contracts.
-These interfaces work with loosely structured data that is impractical for programs to handle.
-This paper presents outgoing research on programmatic interaction with a smart contract on the Tezos blockchain that could benefit developers of smart contract applications and Oracles.
-The approach does not provide a general API, but targets each typical smart contract by generating a specialized contract module that provides a typed high-level interface from a smart contract implementation.
-In doing so, errors in contract calls are explicitly specified in a user-defined data type.
-A contract call is treated as a function call that grants a typed safe of data in the Ocaml language.
-In addition, the module can check preconditions before the actual call to reduce the waste of a failed call.
-As future work, we combine the contract module with our typed API designed to provide a general type-safe programmatic API for the Tezos blockchain.
+Current blockchains often provide low-level interfaces to interact
+with smart contracts. These interfaces work with loosely structured
+without static guarantees. This paper presents ongoing research on the
+programmatic interaction with smart contracts on the Tezos blockchain
+that could benefit developers of mixed applications and
+oracles comprised of on-chain and off-chain parts. The approach does
+not provide a general API, but targets each 
+individual smart contract by generating a specialized contract module
+that provides a typed high-level interface from a contract
+specification. In doing so, errors from contract calls are explicitly
+specified in a user-defined data type. A contract call is wrapped in a
+fully typed and integrated OCaml function. In addition, the wrapper can check preconditions before the 
+actual call to reduce the waste of gas of a failed call.
+% As future work, we
+% combine the contract module with our typed API designed to provide a
+% general type-safe programmatic API for the Tezos blockchain.
 

### 2021-05-25 papers/contract-modules/fmbc2021/fmbc-main.tex

@@
 
+The basic idea of our advanced checking, namely precondition checking, is derived from Java Modeling Language (JML)\cite{Leavens2006DesignBC, 101007}, where the behavior of program components is described as an executable contract between Java programs and their clients.
+This executable contract specifies preconditions that must be satisfied by clients and postconditions that are guaranteed by the program.
+A precondition supplied with a client call must be satisfied before a function defined by the program is called, and the program guarantees that the postconditions are satisfied in return after the call.
+The original use of such preconditions and postconditions dates back to Hoare's paper on formal verification \cite{101145}.
+The executable contracts are written as program code in the programming language.
+In our approach, the safe contract module in Ocaml plays a role as an executable contract.
+Several applications are based on JML \cite{Tran2017, keY}.
+Ahrendt et al.
+\cite{keY} propose a framework called The KeY for deductive software verification.
+The module specifies preconditions and then verifies where a user call satisfies those preconditions.
+Symbolic execution plays an important role in precondition checking in our method.
+A contract is verified against its specification in the contract module by symbolic execution.
+Hentschel et al.
+\cite{Hentschel} proposed the symbolic execution debugger (SED) platform based on the KeY framework.
+The platform SED has a static symbolic execution engine for sequential programs.
+
 Smart contract-based applications often require interaction between a smart contract on the blockchain and the outside world.

### 2021-05-25 papers/contract-modules/fmbc2021/fmbc-main.tex
Add files via upload

--- 2021-05-25 papers/contract-modules/fmbc2021/fmbc-main.tex
@@
 \label{sec:related-work}
-RPC APIs, often provided by current blockchains such as Ethereum \cite{eth-whitepaper} and Tezos \cite{tezos-whitepaper}, use loosely structured data, such as a JSON-based format, which is difficult for a programmatic program to handle.
+%RPC APIs, often provided by current blockchains such as Ethereum \cite{eth-whitepaper} and Tezos \cite{tezos-whitepaper}, use loosely structured data, such as a JSON-based format, which is difficult for a programmatic program to handle.
 As a result, there is increasing work on providing better programmatic interfaces to the blockchains.
@@
 However, smart contracts cannot connect to external sources on their own.
-This is where Oracles \cite{oracle-patterns,call-action-oracle,oracles-study} come into play.
+This is where oracles \cite{oracle-patterns,call-action-oracle} come into play.
 Oracles act as a bridge between smart contracts and external sources.
 Namely, they collect and verify external information and make it available to smart contracts on the blockchain.
+Several research works have been conducted to provide oracle solutions for the Blockchain.
+Adler et al.\cite{blockchain-oracles} proposed a framework to provide developers with a guide for incorporating oracles into blockchain-based applications.
 Oracles may need to observe the state of the chain to determine what information to send.
-Several research works have been conducted to provide oracle solutions for the Blockchain.
-Adler et al.\cite{blockchain-oracles} proposed a framework to provide developers with a guide for incorporating oracles into Blockchain-based applications.
-Practically, Ellis et al.
+In addition, oracles transmit data from external sources to the blockchain.
+Therefore, they would need to have a programmatic interface to interact with the blockchain.
+%Practically, Ellis et al.
 \cite{chainlink-whitepaper} proposed the decentralized oracle network Chainlink to provide reliable, tamper-proof input for smart contracts on any blockchain.
@@
 
-An oracle responds to an event by 
-transmitting information to a smart contract through a smart contract invocation.
+%An oracle responds to an event by  transmitting information to a smart contract through a smart contract invocation.
 In addition.
@@
 To deal with this problem, the paper \cite{LIU2019590} proposes a low-cost data carrier architecture for a blockchain-enabled IoT environment.
+
+The basic idea of our advanced checking, namely precondition checking, is derived from the Java modeling language (JML)\cite{Leavens2006DesignBC, 101007}, in which the behavior of program components is described as an executable contract between Java program and its clients.
+This executable contract specifies preconditions that must be satisfied by clients and postconditions that are guaranteed by the program.
+A precondition supplied with a client call must be verified  before a function defined by the program is called, and the program guarantees that the postconditions are satisfied in return after the call.
+The original use of such preconditions and postconditions dades back to Hoare's paper on formal verification \cite{101145}.
+The executable contracts are written as program code in the programming language.
+In our approach, the safe contract module in the Ocaml language plays a role as an executable contract.
+Several applications are based on JML \cite{Tran2017, keY}.
+Ahrendt et al.
+\cite{keY} propose a framework called The KeY for deductive software verification.
+
+Our contract module specifies preconditions and then off-chain checks whether a user call satisfies those preconditions.
+Symbolic execution plays an important role in the preconditions checking in our method.
+A smart contract is verified against its specification in the contract module by symbolic execution.
+In a paper on symbolic execution \cite{Hentschel}, Hentschel et al.
+proposed the symbolic execution debugger (SED) platform, which is based on the KeY framework.
+The platform SED has a static symbolic execution engine for sequential programs.
 

### 2021-05-26 papers/contract-modules/fmbc2021/fmbc-main.tex
+bartoletti

@@
 
-The basic idea of our advanced checking, namely precondition checking, is derived from the Java modeling language (JML)\cite{Leavens2006DesignBC, 101007}, in which the behavior of program components is described as an executable contract between Java program and its clients.
-This executable contract specifies preconditions that must be satisfied by clients and postconditions that are guaranteed by the program.
-A precondition supplied with a client call must be verified  before a function defined by the program is called, and the program guarantees that the postconditions are satisfied in return after the call.
-The original use of such preconditions and postconditions dades back to Hoare's paper on formal verification \cite{101145}.
-The executable contracts are written as program code in the programming language.
-In our approach, the safe contract module in the Ocaml language plays a role as an executable contract.
-Several applications are based on JML \cite{Tran2017, keY}.
-Ahrendt et al.
-\cite{keY} propose a framework called The KeY for deductive software verification.
+The basic idea of our advanced checking, namely precondition checking,
+is inspired by JML, the Java modeling
+language~\cite{Leavens2006DesignBC, 101007}, in which the behavior of 
+program components is described as a contract between Java
+program and its clients. This contract specifies
+preconditions that must be satisfied by clients and postconditions
+that are guaranteed by the program. A precondition supplied with a
+client call must be verified before a function defined by the program
+is called, and the program guarantees that the postconditions are
+satisfied in return after the call. The original idea of using
+preconditions and postconditions dates back to Hoare's paper
+\cite{101145}. Software contracts have also been proposed for
+blockchain \cite{DBLP:journals/fbloc/Bartoletti20}.
+% The executable contracts are written as program code in
+% the programming language.
+In our approach, the safe contract module in the Ocaml language comes
+close to contracts in this sense. Several
+applications are based on JML \cite{Tran2017}. Ahrendt et
+al. \cite{keY} propose the KeY framework for deductive software
+verification.
 

### 2021-05-26 papers/contract-modules/fmbc2021/fmbc-main.tex
as submitted to fmbc

@@
 allowed and the contract owner is currently also the highest
-bidder. On deployment the owner also deposits an initial balance to indicate the
+bidder. On deployment the owner deposits an initial balance to indicate the
 minimum bid. Closing the contract transfers the balance to the
-owner. It is restricted to the owner. Bidding fails if the contract is
-closed. If bidding is open and the amount of tokens with the bid exceeds the
+owner. It is restricted to the owner. Closing as well as bidding fails
+if the auction is
+closed. If bidding is open and the amount of tokens accompanying the bid exceeds the
 current highest bid, the current bidder replaces the previous highest
@@
 due to lack of connectivity, etc) a Michelson contract can fail due to
-a programmer induced condition. To this end, there is a Michelson
-instruction \lstinline/FAILWITH/ that terminates contract execution
+a programmer induced condition caused by the
+instruction \lstinline/FAILWITH/. It terminates contract execution
 with an error message which is reported back to the caller. This error
-message includes a rendering of the top value on the stack.
+message includes the top value on the stack.
 
@@
 exceptions, but we wish to deal with the explicit failures like
-checked exceptions.
+checked exceptions~\cite{DBLP:conf/oopsla/AnconaLZ01}.
 Our generated code handles failures in a suitable
@@
 
-\begin{lstlisting}[float,captionpos=b,caption={Contract module example},label={lst:contract-module-example}]
+\begin{lstlisting}[float,captionpos=b,caption={Example contract module},label={lst:contract-module-example}]
 contract type Auction = sig
@@
   entrypoint close ()
-  raises "not owner"            (** caller cannot close *)
+  raises "closed"               (** auction closed *)
+       | "not owner"            (** caller cannot close *)
 end
@@
 the auction contract.  It declares the entrypoint \lstinline/bid/ as
-\lstinline/paid/, which means that it needs to be invoked with a
+\lstinline/paid/, i.e., it needs to be invoked with a
 non-zero amount of tokens, it gives the pattern \lstinline/()/ for the
@@
 
+% module type MyContract = sig 
 \begin{lstlisting}[float,captionpos=b,caption={Generated signature},label={lst:generated-signature}]
-module type MyContract = sig
   type bid_errors = 
-     | closed       (** auction closed*)
-     | too_low      (** bid received is too low *)
+     | bid_closed      (** auction closed*)
+     | bid_too_low     (** bid received is too low *)
 
   val bid
-    : Tezos.pukh -> ?fee:Tezos.tz -> amount:Tezos.tz
+    : Tezos.pukh -> ?fee:Tezos.mutez -> amount:Tezos.mutez
     -> (Tezos.status, bid_errors) Tezos.monad
@@
   type close_errors = 
-     | not_owner    (** caller cannot close the auction *)
+     | close_closed    (** auction closed *)
+     | close_not_owner (** caller cannot close the auction *)
 
   val close
-    : Tezos.pukh -> ?fee:Tezos.tz
+    : Tezos.pukh -> ?fee:Tezos.mutez
     -> (Tezos.status, close_errors) Tezos.monad
-end
 \end{lstlisting}
+% end 
 Listing~\ref{lst:generated-signature} contains an OCaml module
@@
 module \lstinline/Tezos/ supposedly contains types and other low-level
-Tezos-specific definitions. Specifically, the type \lstinline/pukh/ for public
-key hashes identifies contracts, the type \lstinline/tz/ stands for
+Tezos-specific definitions. The type \lstinline/pukh/ for public
+key hashes identifies contracts, the type \lstinline/mutez/ stands for
 Tezos tokens, the type \lstinline/status/ reflects the internal return
@@
 \label{sec:advanced-checking}
-\begin{lstlisting}[float,captionpos=b,caption={Safer contract module},label={lst:safer-contract-module}]
+\begin{lstlisting}[float,captionpos=b,caption={Enhanced contract module},label={lst:safer-contract-module}]
 contract type SaferAuction = sig
@@
   entrypoint close ()
+  requires bidding raises "closed" (** auction closed*)
+  ensures not bidding
   requires (sender = owner) raises "not owner"
@@
   requires bidding raises "closed" (** auction closed*)
-  requires (amount > balance)
+  ensures bidding
+  requires (amount > old.balance)
   raises "too low"                 (** bid too low *)
+  ensures (balance >= old.balance)
+  ensures (owner = old.owner)
 end
@@
 preconditions off-chain before invoking the contract. To this end, the
-code needs to obtain properties like balance, storage etc of the
+off-chain code needs to obtain properties like balance, storage etc of the
 contract, but this information is available from the Tezos node without a fee!
@@
 % the programming language.
-In our approach, the safe contract module in the Ocaml language comes
+In our approach, the safe contract module in the OCaml language comes
 close to contracts in this sense. Several
@@
 actual call to reduce the waste of gas of a failed call.
+
+Status: we are currently working on a prototype of the symbolic interpreter.
 % As future work, we

### 2021-05-26 papers/contract-modules/fmbc2021/macros.tex
as submitted to fmbc

--- 2021-05-17 papers/contract-modules/fmbc2021/macros.tex
@@
   backgroundcolor=\color{pypypy},
-  morekeywords={module,contract,sig,val,paid,entrypoint,raises},
+  morekeywords={requires,ensures,sender,amount,balance,storage,hash,module,contract,sig,val,paid,entrypoint,raises},
   classoffset=1,
   morekeywords={nat,int,unit,string,or,pair,option,address,bool},
-  morekeywords={Tezos,pukh,tz,status,monad},
+  morekeywords={Tezos,pukh,mutez,status,monad},
   keywordstyle=\color{blue},

### 2021-06-08 papers/execution-model/APLAS 2021/paper.tex
Add files via upload

--- 2021-02-22 papers/execution-model/model.tex
@@
-\documentclass[a4paper]{llncs}
+% This is samplepaper.tex, a sample chapter demonstrating the
+% LLNCS macro package for Springer Computer Science proceedings;
+% Version 2.20 of 2017/10/04
+%
+\documentclass[runningheads]{llncs}
 \usepackage[english]{babel}
@@
 \input{macros}
-
+%
+\usepackage{graphicx}
+% Used for displaying a sample figure. If possible, figure files should
+% be included in EPS format.
+%
+% If you use the hyperref package, please uncomment the following line
+% to display URLs in blue roman font according to Springer's eBook style:
+% \renewcommand\UrlFont{\color{blue}\rmfamily}
+
+\begin{document}
+%
 \title{A Typed Programmatic Interface to Contracts on the Blockchain}
-
-\author{Thi Thu Ha Doan\and
+%
+%\titlerunning{Abbreviated paper title}
+% If the paper title is too long for the running head, you can set
+% an abbreviated paper title here
+%
+\author{Thi Thu Ha Doan\orcidID{0000-0001-7524-4497}\and
 Peter Thiemann\orcidID{0000-0002-9000-1239}}
-\institute{University of Freiburg, Germany\\
+
+%
+\authorrunning{F. Author et al.}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+%
+\institute{University of Freiburg, Germany \\
 \email{\{doanha,thiemann\}@informatik.uni-freiburg.de}
 }
-
-\date{\today}
-
-\begin{document}
-\maketitle
-\pagestyle{plain}
+%
+\maketitle              % typeset the header of the contribution
+%
 \begin{abstract}
@@
   is implemented in OCaml for the Tezos blockchain.
+
+\keywords{smart contract  \and Second keyword \and Another keyword.}
 \end{abstract}
-
+%
+%
+%
 \section{Introduction}
 \label{sec:introduction}
-
 First generation blockchains were primarily geared towards supporting
@@
 contract. Once to the contract is deployed, the
-auction is open for bidding, but it should be closed after 48 hours,
-say. Such a timeout is a typical task for an oracle. Rather than
+auction is open for bidding, but it should be closed after 48 hours. Such a timeout is a typical task for an oracle. Rather than
 trusting a generic oracle, you prefer to roll your own mechanism that reliably closes the auction
@@
 Neither task can be implemented as a smart contract alone because both react
-to external triggers. Closing requires to schedule the invocation of a
+to external triggers. Closing require scheduling the invocation of a
 contract at a certain time. Bidding 
-requires to watch the current highest bid of the contract and
+requires watching the current highest bid of the contract and
 react if another bidder places a higher bid.
@@
 
-In Tezos, there are two types of accounts: implicit accounts, which are associated with a pair of private/public keys, and smart contracts, which are a programmable account created by an origination operation and have no corresponding secret key.
+In Tezos, there are two types of accounts: implicit accounts, which are associated with a pair of private/public keys, and smart contracts, which are programmable accounts created by an origination operation and have no corresponding secret key.
 The address of a smart contract is a unique public hash that depends on the creation operation.
@@
 themselves, we rather consider them as black boxes that execute in a
-safe-safe way. Tezos' smart contract language Michelson and its
+safe way. Tezos' smart contract language Michelson and its
 properties have been formalized elsewhere \cite{DBLP:conf/fm/BernardoCHPT19}.
@@
   \begin{itemize}
-  \item $\PUK \in \DOM (\MANAGERS)$ and  $\PUH =\GENERATEHASH (\CODE, \hat\TIME) \in \DOM (\CONTRACTORS)$,
+  \item $\PUK \in \DOM (\MANAGERS)$ and  $\PUH =\GENERATEHASH (\CODE, \TIME') \in \DOM (\CONTRACTORS)$,
   \item $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$,  $\JTypeCode\CODE{
@@
 
-\newpage{}
-
 \bibliographystyle{splncs04}
@@
 
-\newpage{}
-\appendix
-
-\section{Unused}
-\label{sec:unused}
-
-\subsection{An Implicit Account Transfer}
-
-\begin{mathpar}
-  \inferrule[rejected of public key]{
-    \NEG\ \CHECKPUB (\BLOCKCHAIN.\MANAGERS, \PUK') \\
-    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
-  }{
-    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
-      \BLOCKCHAIN
-    } \SystemTrans
-   { [\EC{\RAISE\ \ERRPUK} :: \EXPRS, \ACCOUNTS] \|
-     \BLOCKCHAIN
-    }
-  }
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[rejected of fee]{
-    \NEG\ \CHECKGAS (\BLOCKCHAIN.\MANAGERS, \PUK,\PUK',\NTEZ, \MTEZ) \\
-    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
-  }{
-    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
-      \BLOCKCHAIN
-     } \SystemTrans
-    { [\EC{\RAISE\ \ERRFEE} :: \EXPRS, \ACCOUNTS] \|
-      \BLOCKCHAIN
-    }
-  }
-\end{mathpar}
-\begin{mathpar}
-  \inferrule[rejected of counter]{
-    \NEG\ \CHECKCOU (\BLOCKCHAIN.\MANAGERS, \OP.\PUK) \\
-    }{
-    { [\EC\OP  :: \EXPRS, \ACCOUNTS] \|
-      \BLOCKCHAIN
-    }
-    \SystemTrans
-    { [\EC{\RAISE\ \ERRCOUNT} :: \EXPRS, \ACCOUNTS] \|
-      \BLOCKCHAIN
-   }
-  }
-\end{mathpar}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\iffalse 
-Rule 6 [included]:
-\begin{mathpar}
-  \inferrule[Block-Accept]{
-    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
-    \TIME'-\TIME < 60
-  }{
-    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
-      \CONTRACTORS, \TIME']}
-    \BlockTrans  \\
-    {[\PENDING, \Angle{\OP,\OPH, \TIME,\TIME'} :: \ACCEPTED,
-      \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ),
-      \CONTRACTORS, \TIME'+1]}
-  }
-\end{mathpar}
-Rule 7 [timeout]: (applies to both, implicit transfers and contract invocations)
-\begin{mathpar}
-  \inferrule[Block-Timeout]{
-    \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
-    \TIME'-\TIME \ge 60
-  }{
-    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
-      \CONTRACTORS, \TIME']}
-    \BlockTrans
-    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \OP.\PUK, \FALSE),
-      \CONTRACTORS, \TIME']}
-  }
-\end{mathpar}
-\fi
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Contracts}
-\label{sec:contracts}
-
-\begin{mathpar}
-  \inferrule[rejected of code]{
-    \NEG\ \CHECKPRG (\CODE) \\
-    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
-  }{
-    [\EC\OP :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN \to 
-    [\EXPRS[\RAISE\ \ERRPRG] :: \EXPRS, \ACCOUNTS] \|
-     \BLOCKCHAIN
-  }
-\end{mathpar}
-
-\iffalse 
-Rule 3 [rejected of counter]:
-\begin{mathpar}
-  \inferrule{
-    \NEG\ \CHECKCOU (\BLOCKCHAIN.\MANAGERS, \PUK) \\
-    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
-  }{
-    [\EC\OP :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN \to 
-    [\EXPRS[\RAISE\ \ERRCOUNT] :: \EXPRS, \ACCOUNTS] \|
-     \BLOCKCHAIN
-  }
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[rejected of balance]{
-    \NEG\ \CHECKBAL (\BLOCKCHAIN.\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
-    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
-  }{
-    [\EC\OP :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN \to 
-    [\EXPRS[\RAISE\ \ERRBAL] :: \EXPRS, \ACCOUNTS] \|
-     \BLOCKCHAIN
-  }
-\end{mathpar}
-\fi
-
-\begin{mathpar}
-  \inferrule[rejected of fee]{
-    \NEG\ \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ) \\
-    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
-  }{
-    [\EC\OP :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN \to 
-    [\EXPRS[\RAISE\ \ERRFEE] :: \EXPRS, \ACCOUNTS] \|
-     \BLOCKCHAIN
-  }
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[rejected of initial storage]{
-    \NEG\ \CHECKINIT (\CODE, \INIT) \\
-    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
-  }{
-    [\EC\OP :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN \to 
-    [\EXPRS[\RAISE\ \ERRINIT] :: \EXPRS, \ACCOUNTS] \|
-     \BLOCKCHAIN
-  }
-\end{mathpar}
-
-% \begin{mathpar}
-%   \inferrule[Block-Timeout]{
-%     %\OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
-%     \TIME-\hat\TIME > 60
-% }{
-%       [ \OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING}
-%      ::\PENDING, \MANAGERS,
-%       \CONTRACTORS, \TIME]  
-%       \BlockTrans \\    
-%       [ \OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSTIMEOUT}
-%      :: \PENDING, \UPDATECOU(\MANAGERS, \OP.\PUK, \FALSE),
-%       \CONTRACTORS, \TIME] 
-%   }
-
-% \end{mathpar}
-~\\
-~\\
-B. \textbf{Transfer}
-
-\begin{mathpar}
-  \inferrule[Block-Call]{
-    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\ 
-    \CHECKCOU (\MANAGERS, \PUK) \\
-    \CHECKPUH (\CONTRACTORS, \PUH) \\
-    \CHECKARG (\CONTRACTORS, \PUH, \PARAMETER) \\
-    \CHECKGAS (\CONTRACTORS, \PUH, \PARAMETER, \MTEZ) \\
-%    \OPH = \GENERATEOPH (\PUK,\PUH, \PARAMETER,\NTEZ, \MTEZ, \TIME) \\
-    \OPH = \GENERATEOPH (\OP, \TIME) \\
-    \OP =  \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\    
-  }{ [\EC\OP  :: \EXPRS, \ACCOUNTS,
-      ] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]     
-    \SystemTrans \\
-    [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \|
-      [\OPH \mapsto \Angle{\OP, \TIME, \STATUSPENDING}
-     :: \PENDING, \UPDATECOU(\MANAGERS, \PUK, \TRUE), \CONTRACTORS, \TIME]}
-\end{mathpar}
-
-\iffalse 
-Rule 2 [rejected of counter]:
-\begin{mathpar}
-  \inferrule{
-    \NEG\ \CHECKCOU (\BLOCKCHAIN.\MANAGERS, \PUK) \\
-    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
-  }{[\EC\OP :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN      
-    \SystemTrans
-   [\EC[\RAISE\ \ERRCOUNT] :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN }
-\end{mathpar}
-~\\
-~\\
-Rule 3 [rejected of balance]:
-\begin{mathpar}
-  \inferrule{
-    \NEG\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
-    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
-  }{[\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \|
-      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
-    \SystemTrans
-    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
-      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}
-\end{mathpar}
-\fi
-
-\begin{mathpar}
-  \inferrule[rejected of public hash]{
-    \NEG\ \CHECKPUH (\BLOCKCHAIN.\CONTRACTORS, \PUH) \\
-    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ
-  }{[\EC\OP  :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN    
-    \SystemTrans
-    [\EXPRS[\RAISE\ \ERRPUH], \ACCOUNTS] \| \BLOCKCHAIN}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[rejected of argument]{
-    \NEG\ \CHECKARG (\BLOCKCHAIN.\CONTRACTORS, \PUH, \PARAMETER)\\
-    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ
-  }{[\EC\OP  :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN    
-    \SystemTrans
-    [\EXPRS[\RAISE\ \ERRARG], \ACCOUNTS] \| \BLOCKCHAIN}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[rejected of fee]{
-    \NEG\ \CHECKGAS (\BLOCKCHAIN.\CONTRACTORS, \PUH, \PARAMETER, \MTEZ) \\ \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ 
-  }{[\EC\OP  :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN    
-    \SystemTrans
-    [\EXPRS[\RAISE\ \ERRFEE], \ACCOUNTS] \| \BLOCKCHAIN}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[block Accept]{
-    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK\PUH\MTEZ \\
-    \TIME-\hat\TIME \le 60
-  }{
-    [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING} :: \PENDING, \MANAGERS,
-    \CONTRACTORS, \TIME]
-    \BlockTrans \\
-    [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING, 
-    \UPDATESUCC (\MANAGERS, \PUK, '', \NTEZ, \MTEZ), \\
-    \UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \PARAMETER),
-    \TIME+1]
-  }
-\end{mathpar}
-
-\subsection{Queries}
-\label{sec:queries-1}
-
-\begin{mathpar}
-  \inferrule[counter]{
-    \BLOCKSYSTEM = 
-      [\PENDING, \PUK \mapsto \Angle{\BAL, \COU} :: \MANAGERS, \CONTRACTORS, \TIME]
-  }{[\EC{\GETCOUNTER\PUK} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \SystemTrans\ [\EC{\COU} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[balance of smart contract]{
-    \BLOCKSYSTEM = 
-      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
-  }{[\EC{\GETBALANCE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \SystemTrans\ [\EC{\BAL} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[storage]{
-    \BLOCKSYSTEM = 
-      [\PENDING, \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
-  }{[\EC{\GETSTORAGE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \SystemTrans\ [\EC{\STORAGE} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[code]{
-    \BLOCKSYSTEM = 
-      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
-  }{[\EC{\GETCODE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \SystemTrans\ [\EC{\CODE} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[type]{
-    \BLOCKSYSTEM = 
-      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
-  }{[\EC{\GETTYPE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \SystemTrans\ [\EC{\Delta (\PUH)} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[fail of a query for an implicit account]{
-    \NEG\ \CHECKPUB (\BLOCKCHAIN.\MANAGERS, \PUK) \
-  }{[\EC{\GETBALANCE\PUK/\GETCOUNTER\PUK} :: \EXPRS, \ACCOUNTS]  \| 
-  \BLOCKCHAIN 
-    \SystemTrans {[\EC{\RAISE\ \ERRPUK} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[fail of a query for a smart contract]{
-    \NEG\ \CHECKPUH (\BLOCKCHAIN.\CONTRACTORS, \PUH) 
-  }{[\EC{\GETBALANCE\PUH/\GETSTORAGE\PUH/\GETCODE\PUH/\GETTYPE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \SystemTrans\\ [\EC{\RAISE\ \ERRPUH} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[status-pending]{
-    \BLOCKSYSTEM = 
-      [\OPH \mapsto \Angle{\OP, \TIME, \STATUSPENDING} :: \PENDING,  \CONTRACTORS, \TIME]
-  }{[\EC{\GETSTATUS\OPH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \SystemTrans\ [\EC{\STATUSPENDING} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[status-including]{
-    \BLOCKSYSTEM = 
-      [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME'} :: \PENDING,  \CONTRACTORS, \TIME] \\
-    $n$ \ = \TIME\ - \TIME'
-  }{[\EC{\GETSTATUS\OPH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \SystemTrans\ [\EC{\STATUSINCLUDING($n$)} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[status-timeout]{ 
-   \BLOCKSYSTEM = 
-      [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSTIMEOUT} :: \PENDING, \CONTRACTORS, \TIME]
-  }{[\EC{\GETSTATUS\OPH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
-    \SystemTrans\ [\EC{\STATUSTIMEOUT} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
-\end{mathpar}
-
-\subsection{Functions}
-\label{sec:functions}
-
-\begin{enumerate}
-    \item Function $\CHECKPUB(\MANAGERS, \PUK)$ checks whether a public key $\PUK$ exists in $\MANAGERS$.
-    \begin{itemize}
-    \item[] $\CHECKPUB(\MANAGERS, \PUK)$ = $\TRUE$ iff $\PUK \in \DOM(\MANAGERS)$
-    \end{itemize}
-    \item Function $\CHECKPUH(\CONTRACTORS, \PUH)$ checks whether a public hash $\PUH$ exists in $\CONTRACTORS$.
-     \begin{itemize}
-    \item[] $\CHECKPUH(\CONTRACTORS, \PUH)$ = $\TRUE$ iff $\PUH \in \DOM(\CONTRACTORS)$
-    \end{itemize}
-    \item Function $\CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ)$ checks whether the balance of the account that associates with the public key $\PUK$ is greater or equal to $\NTEZ$ plus $\MTEZ$.
-    \begin{itemize}
-    \item[] $\MANAGERS(\PUK)$ = $\Angle{\BAL, \COU}$ and $\BAL \ge \NTEZ + \MTEZ$
-    \end{itemize}
-    \item Function $\CHECKCOU (\MANAGERS, \PUK)$ checks whether the current counter of an account that associates with the public key $\PUK$ is unlocked (its flag is False).
-    \begin{itemize}
-    \item[] $\MANAGERS(\PUK)$ = $\Angle{\BAL, \COU}$ and $\COU.b = \FALSE$
-    \end{itemize}
-   % \item Function \CHECKEXIST (\OPH, \PENDING, \ACCEPTED)\ checks whether an operation  \OPH\ exists in either \PENDING\ or \ACCEPTED.
-    \item Function $\UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ)$ updates the balance and the counter of the account that associates with the public key $\PUK$ and the balance of the account that associates with the public key $\PUK'$, where
-    \begin{itemize}
-        \item[]  $\PUK \mapsto \Angle{\BAL, (\hat\NTEZ, \TRUE)}$ $\Rightarrow$ $ \PUK \mapsto \Angle{\BAL - \NTEZ - \MTEZ, (\hat\NTEZ + 1, \FALSE)}$     
-        \item[] $\PUK' \mapsto \langle  \BAL', \COU' \rangle$ $\Rightarrow$ $\PUK' \mapsto \langle \BAL' + \NTEZ, \COU' \rangle $         
-    \end{itemize}
-
-    \item Function $\UPDATECOU(\MANAGERS, \PUK, \BOOLEAN)$ updates the counter flag (True $=$ locked, False $=$ unlocked) of the account that associates with the public key $\PUK$, where
-    \begin{itemize}
-        \item[]  $ \PUK \mapsto \langle \BAL, (\NTEZ, \hat\BOOLEAN) \rangle $ $\Rightarrow$ $\PUK \mapsto \langle \BAL, (\NTEZ, \BOOLEAN) \rangle $ 
-    \end{itemize}
-
-    \item Function  $\UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \PARAMETER)$ updates the contractor that associates with the public hash $\PUH$, where
-    \begin{itemize}
-        \item[] $\PUH  \mapsto \langle   \CODE, \TIME, \BAL, \STORAGE, \rangle $ $\Rightarrow$ $\PUH  \mapsto \langle  \BAL + \NTEZ, \CODE, \\ \UPDATESTORAGE(\STORAGE,\CODE,\PARAMETER) \rangle $
-    \end{itemize}
-
-     \item Function $\UPDATESTORAGE(\STORAGE, \CODE,  \PARAMETER)$ returns the new storage by running the code $\CODE$ on the  current storage  $\STORAGE$ with  the input parameter $\PARAMETER$.
-
-    \item Function $\CHECKPRG (\CODE)$ checks whether the code $\CODE$ is well type.
-
-    \begin{itemize}
-        \item[] $\CHECKPRG (\CODE) = \TRUE$ iff $\CODE : \TPAIR\ \TYPE_p\ \TYPE_s$
-    \end{itemize}
-    \item Function $\CHECKINIT (\CODE, \INIT)$ checks whether the initil stogare valude is well type with corresponding to the code $\CODE$.
-    \begin{itemize}
-        \item[] $\CHECKINIT (\CODE, \INIT) = \TRUE$ iff $\CODE : \TPAIR\ \TYPE_p\ \TYPE_s$ and $\STRING : \TYPE_s$
-    \end{itemize}
-
-    \item Function $\CHECKARG (\CONTRACTORS, \PUH, \PARAMETER)$ checks whether the input parameter  $\PARAMETER$ to the smart contract $\PUH$ in $\CONTRACTORS$ is well type with corresponding to its code.
-    \begin{itemize}
-        \item[] $\CHECKARG (\CONTRACTORS, \PUH, \PARAMETER) = \TRUE$ iff $\Delta (\PUH) =
-  \TPAIR\ \TYPE_p\ \TYPE_s$ and $\PARAMETER : \TYPE_p$
-    \end{itemize}
-
-   % \item Function \CHECKGAS(\CODE, \INIT, \MTEZ) checks whether the gas that is consumed to run the code \CODE\ for the initial value \INIT\ is less or equal to \MTEZ.
-    \item Function  $\CHECKGAS (\MANAGERS, \PUK,\NTEZ, \MTEZ)$/ $\CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ)$ / $\CHECKGAS (\CONTRACTORS, \PUH, \PARAMETER, \MTEZ)$ check whether the fee that is consumed to emit the opertion is less or equal to the fee \MTEZ.
-    %run the code \CODE\ that associates with the public hash \PUH\ for the paremeter \PARAMETER\ is less or equal to \MTEZ.
-    \item Function \GENERATEOPH (\PUK, {\ADDR /\CODE},{\INIT /\PARAMETER}, \NTEZ, \MTEZ,  \TIME) generates an operation hash.
-
-    \item Function \GENERATEHASH (\CODE, \TIME)  generates the public hash of a smart contract.
-    \end{enumerate}
-
 \end{document}
+
+\subsection{A Subsection Sample}
+Please note that the first paragraph of a section or subsection is
+not indented. The first paragraph that follows a table, figure,
+equation etc. does not need an indent, either.
+
+Subsequent paragraphs, however, are indented.
+
+\subsubsection{Sample Heading (Third Level)} Only two levels of
+headings should be numbered. Lower level headings remain unnumbered;
+they are formatted as run-in headings.
+
+\paragraph{Sample Heading (Fourth Level)}
+The contribution should contain no more than four levels of
+headings. Table~\ref{tab1} gives a summary of all heading levels.
+
+\begin{table}
+\caption{Table captions should be placed above the
+tables.}\label{tab1}
+\begin{tabular}{|l|l|l|}
+\hline
+Heading level &  Example & Font size and style\\
+\hline
+Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
+1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
+2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
+3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
+4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
+\hline
+\end{tabular}
+\end{table}
+
+\noindent Displayed equations are centered and set on a separate
+line.
+\begin{equation}
+x + y = z
+\end{equation}
+Please try to avoid rasterized images for line-art diagrams and
+schemas. Whenever possible, use vector graphics instead (see
+Fig.~\ref{fig1}).
+
+\begin{figure}
+\includegraphics[width=\textwidth]{fig1.eps}
+\caption{A figure caption is always placed below the illustration.
+Please note that short captions are centered, while long ones are
+justified by the macro package automatically.} \label{fig1}
+\end{figure}
+
+\begin{theorem}
+This is a sample theorem. The run-in heading is set in bold, while
+the following text appears in italics. Definitions, lemmas,
+propositions, and corollaries are styled the same way.
+\end{theorem}
+%
+% the environments 'definition', 'lemma', 'proposition', 'corollary',
+% 'remark', and 'example' are defined in the LLNCS documentclass as well.
+%
+\begin{proof}
+Proofs, examples, and remarks have the initial word in italics,
+while the following text appears in normal font.
+\end{proof}
+For citations of references, we prefer the use of square brackets
+and consecutive numbers. Citations using labels or the author/year
+convention are also acceptable. The following bibliography provides
+a sample reference list with entries for journal
+articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
+book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
+and a homepage~\cite{ref_url1}. Multiple citations are grouped
+\cite{ref_article1,ref_lncs1,ref_book1},
+\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
+%
+% ---- Bibliography ----
+%
+% BibTeX users should specify bibliography style 'splncs04'.
+% References will then be sorted and formatted in the correct style.
+%
+% \bibliographystyle{splncs04}
+% \bibliography{mybibliography}
+%
+\begin{thebibliography}{8}
+\bibitem{ref_article1}
+Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
+
+\bibitem{ref_lncs1}
+Author, F., Author, S.: Title of a proceedings paper. In: Editor,
+F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
+Springer, Heidelberg (2016). \doi{10.10007/1234567890}
+
+\bibitem{ref_book1}
+Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
+Location (1999)
+
+\bibitem{ref_proc1}
+Author, A.-B.: Contribution title. In: 9th International Proceedings
+on Proceedings, pp. 1--2. Publisher, Location (2010)
+
+\bibitem{ref_url1}
+LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
+Oct 2017
+\end{thebibliography}
+\end{document}

### 2021-06-08 papers/execution-model/APLAS 2021/paper.tex
Add files via upload

@@
 \begin{abstract}
-  Smart contract applications on the block chain can only reach their full potential if
+  Smart contract applications on the blockchain can only reach their full potential if
   they can be integrated with traditional software systems. Invoking
@@
   alongside smart contracts in a blockchain. 
-\item Established various properties of the combined system withs
+\item Established various properties of the combined system with
   proofs in upcoming techreport.
@@
 Suppose you want to run an auction on the blockchain using a smart
-contract. Once to the contract is deployed, the
+contract. Once the contract is deployed, the
 auction is open for bidding, but it should be closed after 48 hours. Such a timeout is a typical task for an oracle. Rather than

### 2021-06-09 papers/execution-model/APLAS 2021/paper.tex

@@
 \input{macros}
-%
-\usepackage{graphicx}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
 
@@
 \lstinline/%bid/. The caller selects the entrypoint by injecting the argument into the
-\lstinline/left/ or \lstinline/right/ summand. Both entrypoints take a \lstinline{unit}
+\lstinline/left/ or \lstinline/right/ summand. Both entrypoints take a \lstinline/unit/
 parameter. The \lstinline/%bid/ entrypoint considers the transferred
@@
 which is a nested pair type indicating whether bidding is allowed
-(\lstinline{bool}), the address of the contract owner (to prohibit
+(\lstinline/bool/), the address of the contract owner (to prohibit
 unauthorized calls to \lstinline/%close/), and the bidder's
@@
 First the code that creates an auction contract and closes it after 48 hours.
+
 \begin{lstlisting}[language=Caml,numbers=none,basicstyle=\small]
@@
 \end{lstlisting}
-We assume that \lstinline/Cl/ is the module containing the contract
-library, \lstinline{set_authority} sets the sender address for
+
+We assume that \lstinline!Cl! is the module containing the contract
+library, \lstinline/set_authority/ sets the sender address for
 upcoming operations,  \lstinline/originate/ deploys its argument contract along
-with the provided funds of one token and the \lstinline/initial_store/, 
-\lstinline{auction_script} is the contract from Listing~\ref{lst:auction-contract-header}, and 
-\lstinline{call_contract} invokes a contract with a parameter. The
-\lstinline{initial_store} sets the bidding flag, and both owner and
+with the provided funds of one token and the \lstinline/initial_store/
+\lstinline/auction_script/ is the contract from Listing~\ref{lst:auction-contract-header}, and 
+\lstinline/call_contract/ invokes a contract with a parameter. The
+\lstinline/initial_store/ sets the bidding flag, and both owner and
 highest bidder to the sender account.
@@
 polling it every five minutes.
+
 \begin{lstlisting}[numbers=none,basicstyle=\small]
@@
 \end{lstlisting}
-The \lstinline{get_state} function obtains the storage of a contract from
+
+The \lstinline/get_state/ function obtains the storage of a contract from
 the blockchain.
@@
 \end{document}
-
-\subsection{A Subsection Sample}
-Please note that the first paragraph of a section or subsection is
-not indented. The first paragraph that follows a table, figure,
-equation etc. does not need an indent, either.
-
-Subsequent paragraphs, however, are indented.
-
-\subsubsection{Sample Heading (Third Level)} Only two levels of
-headings should be numbered. Lower level headings remain unnumbered;
-they are formatted as run-in headings.
-
-\paragraph{Sample Heading (Fourth Level)}
-The contribution should contain no more than four levels of
-headings. Table~\ref{tab1} gives a summary of all heading levels.
-
-\begin{table}
-\caption{Table captions should be placed above the
-tables.}\label{tab1}
-\begin{tabular}{|l|l|l|}
-\hline
-Heading level &  Example & Font size and style\\
-\hline
-Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
-1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
-2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
-3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
-4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
-\hline
-\end{tabular}
-\end{table}
-
-\noindent Displayed equations are centered and set on a separate
-line.
-\begin{equation}
-x + y = z
-\end{equation}
-Please try to avoid rasterized images for line-art diagrams and
-schemas. Whenever possible, use vector graphics instead (see
-Fig.~\ref{fig1}).
-
-\begin{figure}
-\includegraphics[width=\textwidth]{fig1.eps}
-\caption{A figure caption is always placed below the illustration.
-Please note that short captions are centered, while long ones are
-justified by the macro package automatically.} \label{fig1}
-\end{figure}
-
-\begin{theorem}
-This is a sample theorem. The run-in heading is set in bold, while
-the following text appears in italics. Definitions, lemmas,
-propositions, and corollaries are styled the same way.
-\end{theorem}
-%
-% the environments 'definition', 'lemma', 'proposition', 'corollary',
-% 'remark', and 'example' are defined in the LLNCS documentclass as well.
-%
-\begin{proof}
-Proofs, examples, and remarks have the initial word in italics,
-while the following text appears in normal font.
-\end{proof}
-For citations of references, we prefer the use of square brackets
-and consecutive numbers. Citations using labels or the author/year
-convention are also acceptable. The following bibliography provides
-a sample reference list with entries for journal
-articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
-book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
-and a homepage~\cite{ref_url1}. Multiple citations are grouped
-\cite{ref_article1,ref_lncs1,ref_book1},
-\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-% \bibliographystyle{splncs04}
-% \bibliography{mybibliography}
-%
-\begin{thebibliography}{8}
-\bibitem{ref_article1}
-Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
-
-\bibitem{ref_lncs1}
-Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-Springer, Heidelberg (2016). \doi{10.10007/1234567890}
-
-\bibitem{ref_book1}
-Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
-Location (1999)
-
-\bibitem{ref_proc1}
-Author, A.-B.: Contribution title. In: 9th International Proceedings
-on Proceedings, pp. 1--2. Publisher, Location (2010)
-
-\bibitem{ref_url1}
-LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
-Oct 2017
-\end{thebibliography}
-\end{document}

### 2021-06-09 papers/execution-model/APLAS 2021/paper.tex
motivating example

@@
 %
-\authorrunning{F. Author et al.}
+\authorrunning{~}
 % First names are abbreviated in the running head.
@@
   is implemented in OCaml for the Tezos blockchain.
-
-\keywords{smart contract  \and Second keyword \and Another keyword.}
 \end{abstract}
+
+\keywords{smart contract  \and embedded domain specific language \and types.}
 %
@@
 
-Suppose you want to run an auction on the blockchain using a smart
-contract. Once the contract is deployed, the
-auction is open for bidding, but it should be closed after 48 hours. Such a timeout is a typical task for an oracle. Rather than
-trusting a generic oracle, you prefer to roll your own mechanism that reliably closes the auction
-after 48 hours have passed. So you want to write a program to do so.
-
-As a bidder, you may want to implement a bidding
-strategy that starts at a certain amount and increases the bid until a
+Suppose you want to implement a bidding strategy for an auction that
+is deployed on the blockchain as a smart contract.
+% Once the contract is deployed, the
+% auction is open for bidding, but it should be closed after 48 hours. Such a timeout is a typical task for an oracle. Rather than
+% trusting a generic oracle, you prefer to roll your own mechanism that reliably closes the auction
+% after 48 hours have passed. So you want to write a program to do so. 
+Your bidding strategy may start at a certain amount and increase the bid until a
 limit is reached. Of course, you only want to increase your bid if
-someone else placed a higher bid. So you also want to write a
+someone else placed a higher bid. So you want to write a
 program to implement this strategy.
 
-Neither task can be implemented as a smart contract alone because both react
-to external triggers. Closing require scheduling the invocation of a
-contract at a certain time. Bidding 
-requires watching the current highest bid of the contract and
+This task cannot be implemented as a smart contract without
+cooperation of the auction contract because it reacts
+on external triggers.
+% Closing require scheduling the invocation of a
+% contract at a certain time.
+Bidding requires watching the current highest bid of the contract and
 react if another bidder places a higher bid.
+The auction contract could anticipate the need for such observations
+by allowing bidders to register callbacks that are invoked when a
+higher bid arrives. However, we cannot assume such cooperation of the
+auction contract nor would we be willing to pay the the fee for running
+that callback.
 
@@
 
-To avoid too much detail, we just outline the implementation of the entrypoints. The
+To avoid too much detail, we only outline the implementation of the entrypoints. The
 \lstinline/%close/ entrypoint first checks its sender's address
@@
 
-Timed contract closing and strategic bidding cannot be implemented in
-a smart contract, but could be implemented in separate programs that
-interact with the blockchain. We present some idealized code for these tasks.
-
-First the code that creates an auction contract and closes it after 48 hours.
-
+We present some idealized code for % timed contract closing and
+strategic bidding as a separate program that interacts with the
+blockchain.  The bidding strategy cannot be implemented as a smart
+contract.
+% A variation of timed contract closing could be
+% implemented as Tezos contracts have access to the current time: A
+% contract can enforce that bids arriving after a deadline are
+% immediately rejected or that the auction cannot be closed before the
+% deadline, but it cannot reliably execute the action associated with
+% closing the contract at the deadline
+
+In preparation, we need to obtain a typed handle for the contract. We
+assume that \lstinline!Cl! is the module containing the contract
+library. The respective library function
+\lstinline!Cl.make_contract_from_hash!
+takes the hash of the contract along with representations of
+the types of the parameter and the storage (from module
+\lstinline!Ct!). It checks the validity of the hash and the types with
+the blockchain and returns a typed
+handle, which is indexed with OCaml types corresponding to parameter
+and storage type.
 \begin{lstlisting}[language=Caml,numbers=none,basicstyle=\small]
-let _ = Cl.set_authority (my_address)
-let initial_store = (true, (my_address, my_address))
-let contract = Cl.originate(auction_script, 1, initial_store)
-Time.sleep(48 * 3600);               (* 48h in seconds *)
-Cl.call_contract(contract, left ()); (* entrypoint %close *)
+# let auction = Cl.make_contract_hash auction_hash
+#     ~parameter:(Ct.Or (Ct.Unit, Ct.Unit))
+#     ~storage:(Ct.Pair (Ct.Bool, Ct.Pair (Ct.Addr, Ct.Addr))));;
+val auction :
+  ((unit, unit) Either.t,
+   bool * (Cl.Addr.t * Cl.Addr.t)) Cl.contract
 \end{lstlisting}
 
-We assume that \lstinline!Cl! is the module containing the contract
-library, \lstinline/set_authority/ sets the sender address for
-upcoming operations,  \lstinline/originate/ deploys its argument contract along
-with the provided funds of one token and the \lstinline/initial_store/
-\lstinline/auction_script/ is the contract from Listing~\ref{lst:auction-contract-header}, and 
-\lstinline/call_contract/ invokes a contract with a parameter. The
-\lstinline/initial_store/ sets the bidding flag, and both owner and
-highest bidder to the sender account.
+% First the code that creates an auction contract and closes it after 48 hours.
+
+% \begin{lstlisting}[language=Caml,numbers=none,basicstyle=\small]
+% let _ = Cl.set_authority (my_address)
+% let initial_store = (true, (my_address, my_address))
+% let contract = Cl.originate auction 1 initial_store
+% Time.sleep(48 * 3600);               (* 48h in seconds *)
+% Cl.call_contract contract (left ()); (* entrypoint %close *)
+% \end{lstlisting}
+
+% \lstinline/set_authority/ sets the sender address for
+% upcoming operations,  \lstinline/originate/ deploys its argument contract along
+% with the provided funds of one token and the \lstinline/initial_store/
+% \lstinline/auction_script/ is the contract from Listing~\ref{lst:auction-contract-header}, and 
+% \lstinline/call_contract/ invokes a contract with a parameter. The
+% \lstinline/initial_store/ sets the bidding flag, and both owner and
+% highest bidder to the sender account.
 
@@
 
-\begin{lstlisting}[numbers=none,basicstyle=\small]
-let rec poll (limit, step, ((bidding, _), (high_bid, _))) =
-  if bidding and high_bid < limit then
-    Cl.call_contract (contract, 
-      right (min (high_bid + step, limit))); (* entrypoint %bid *)
+\begin{lstlisting}[language=Caml,numbers=none,basicstyle=\small]
+let rec poll limit step =
+  let (bidding, (_, highest_bidder)) = Cl.get_storage auction;
+  let high_bid = Cl.get_balance auction;
+  if bidding && high_bid < limit then
+    (if highest_bidder <> my_address then  (* entrypoint %bid *)
+      try
+        Cl.call_contract auction
+          (right (min (high_bid + step, limit))) 
+      with
+      | Cl.FAILWITH message -> poll limit step;
     Time.sleep(5 * 60);
-    let state = Cl.get_state (contract);
-    poll (limit, step, state)
-in
-poll (limit, step, Cl.get_state (contract))
+    poll limit step)
 \end{lstlisting}
 
-The \lstinline/get_state/ function obtains the storage of a contract from
-the blockchain.
+The functions \lstinline/get_storage/ and \lstinline/get_balance/
+obtains the storage and current balance, respectively, of a contract from
+the blockchain. They never fail. Function \lstinline/call_contract/
+takes a typed handle and a parameter of suitable type. It indicates
+failure by raising an exception. If failure is caused by the
+\lstinline/FAILWITH/ instruction in the contract, then the
+corresponding \lstinline/Cl.FAILWITH/ exception is raised, which
+carries a string corresponding to the argument of the instruction. In
+our particular example, the auction may fail with signaling the message
+\lstinline/"closed"/ or \lstinline/"bid to low"/. Our
+code ignores this message for simplicity.
 
@@
 this invocation. If it does not get incorporated, then we need to
-analyse the reason and react accordingly. For example, if the
+analyze the reason and react accordingly. For example, if the
 invocation was rejected because of an insufficient fee, we might want
@@
 \end{itemize}
-All these facilities are supported by the (untyped) RPC interface of the Tezos
+These facilities are supported by the (untyped) RPC interface of the Tezos
 blockchain, which is the basis of our implementation.

### 2021-06-11 papers/execution-model/APLAS 2021/paper.tex
Add files via upload
Revised introduction, the transition and proofs

@@
 
-We present a typed API for invoking contracts from OCaml
-programs. Such an API with a reliable computing facility and network
-connection is sufficient to self provision an oracle and to avoid
-having to trust an oracle provider. Moreover, our approach provides a
-type-safe facility rather than oracles which are intrisically untyped
-because they aim to provide a generic service.
+Building such oracles requires programmatic interfaces to implement the interactions.
+However, current blockchains often provide non-programmatic interfaces, such as the Ethereum JSON-RPC API and the Tezos RPC API.
+We present a typed API for invoking contracts from OCaml programs.
+Our type API supports the implementation of programs that safely interact with smart contracts on the blockchain.
+Such an API with a reliable computing facility and network connectivity is sufficient to self-provision an oracle.
+Moreover, our approach provides a type-safe facility instead of oracles, which are intrinsically untyped as they aim to provide a generic service.
 
@@
     \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
+    \CHECKARG (\CONTRACTORS, \PUH, \PARAMETER) \\
     \CHECKCOU (\MANAGERS, \PUK) \\
-    \CHECKPUB (\MANAGERS, \PUK') \\
-    \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
-    %\OPH = \GENERATEOPH (\PUK, \PUK','', \NTEZ, \MTEZ, \TIME) \\
+    \CHECKPUH (\CONTRACTORS, \PUH) \\
+    \CHECKGAS (\CONTRACTORS, \PUH, \PARAMETER, \MTEZ) \\
     \OPH = \GENERATEOPH (\OP, \TIME) \\
-    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ    
+    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ    
   }{
@@
   \inferrule[Block-Accept]{
-    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
+    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
     \TIME - \hat\TIME \le 60
@@
       \CONTRACTORS, \TIME]}
-    \BlockTrans  \\
+    \BlockTrans 
     {
-      [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING, 
-      \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ),
-      \CONTRACTORS, \TIME +1]}
+      [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING}, \\
+      { \UPDATESUCC (\MANAGERS, \PUK, \NTEZ, \MTEZ), 
+       \UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \PARAMETER), \TIME +1]
+    }
   }
@@
     \inferrule[Block-Timeout]{
-    % \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
     \TIME-\hat\TIME > 60
@@
 Figure~\ref{fig:lifecycle-transaction} shows the transitions to start
-and finalize a transfer transaction.
+and finalize a transfer transaction, namely a smart contract invocation.
 \TirName{Node-Inject} affects a local node and the blockchain. It
@@
 whether there is an active transition for this sender (chkCount),
-whether the receiver's address is valid, and whether the fee is
+whether the public hash is associated with a smart contract, whether the type of the input parameter matchs with the smart contract's parameter type (chkArg), and whether the fee is
 sufficient. If these conditions are fulfilled, the transition forges
@@
 If the transaction is accepted, then the sender's counter is reset,
-the balances of sender and receiver are adjusted (updSucc), and the
-time stamp increases.
+the balances of sender and receiver are adjusted (updSucc), the smart contract storage and balance are updated (updConstr), and the time stamp increases.
 
@@
 
+The proofs of these properties refer to all transitions with the detailed specifications of the related functions, such as chkCount and updSucc.
+Due to page limitations, not all transitions and their associated functions are presented in this paper, so the full proofs will be provided in an upcoming technical report.
+In this paper, since we only provide the proofs for Proposition 2 at 4 and 7.
+
+\begin{proof}[4]
+ After feeding into a node, the status of the operation is \STATUSPENDING\ according to the transition \TirName{ Node-Inject }.
+This operation could either be accepted by the blockchain on the condition that the elapsed time is less than 60 ($\TIME - \hat\TIME \le 60$), and then its status is \STATUSINCLUDED\ \TIME \ (the transition \TirName{ Block-Accept }) or it is timeout with the status \STATUSTIMEOUT\ (\TirName{ Block-Timeout}).
+When an operation is accepted or times out, its status is never changed.
+Therefore, we have
+
+ \begin{itemize}
+ \item if the operation remains in \STATUSPENDING, then $\PENDING' (\OPH) = \PENDING (\OPH)$; 
+ \item if the operation is timeout, then $\PENDING' (\OPH) = \Angle{\OP, \hat\TIME, \STATUSTIMEOUT}$ according to the transition \TirName{ Block-Timeout}; 
+ \item if the operation is accepted, then $\PENDING' (\OPH) = \Angle{\OP, \hat\TIME, \STATUSINCLUDED\ \TIME }$, and $\TIME'=\TIME +1$ because the timestamp is incremented to one when an operation is accepted, according to the transition \TirName{ Block-Accept}.
+ \end{itemize}
+
+\end{proof}
+
+\begin{proof}[7]The function $\UPDATECOU(\MANAGERS, \PUK, \BOOLEAN)$ updates the flag of the counter of the account associated with the public key $\PUK$. The specification is as follows:
+ \begin{itemize}
+   \item[] \UPDATECOU($\PUK \mapsto \langle \BAL, (\NAT, \hat\BOOLEAN) \rangle$, \BOOLEAN) = $\PUK \mapsto \langle \BAL, (\NAT, \BOOLEAN) \rangle $
+ \end{itemize}
+
+    Function $\UPDATESUCC(\MANAGERS, \PUK, \NTEZ, \MTEZ)$ updates the balance and the counter of the account that associates with the public key $\PUK$. The specification is as follows:
+ \begin{itemize}
+   \item[]  \UPDATESUCC($\PUK \mapsto \Angle{\BAL, (\NAT, \TRUE)}$, \PUK, \NTEZ, \MTEZ) = $ \PUK \mapsto \Angle{\BAL - \NTEZ - \MTEZ, (\NAT + 1, \FALSE)}$    
+ \end{itemize}
+
+\noindent Then we have
+ \begin{itemize}
+   \item[-] $\COU.b=\TRUE$ means that the operation is injected and its status is \STATUSPENDING\ at \TIME according to the transition \TirName{Node-Inject}, and $\COU'.b=\FALSE$ means that the operation is accepted.
+According to the transition \TirName{Block-Accept} and the specification of the function \UPDATESUCC, the counter of the account is incremented by 1.
+This means $\COU.n' \in \{\COU.n,  \COU.n+1\}$.
+   \item[-] If the operation is still pending or it is time out, the country's number is changed in both cases. This means $\COU.n = \COU'.n$.
+   \item[-] If $\COU.n = \COU'.n$, the balance of the account is also changed since the balance  is only changed when the operation is accepted. This means $\BAL = \BAL'$.
+ \end{itemize}
+\end{proof}
+
 \subsection{Typing related properties}

### 2021-06-14 papers/execution-model/APLAS 2021/paper.tex
snapshot-section3-types

@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
+% APLAS 2021: Regular research papers should not exceed 18 pages in
+% the Springer LNCS format(LaTeX template), including bibliography and
+% figures.
+% Lightweight double-blind: Author names and institutions must be
+% omitted and References to the authors’ own related work should be in
+% the third person 
 %
@@
 %
-\author{Thi Thu Ha Doan\orcidID{0000-0001-7524-4497}\and
-Peter Thiemann\orcidID{0000-0002-9000-1239}}
+% ANONYMOUS
+% \author{Thi Thu Ha Doan\orcidID{0000-0001-7524-4497}\and
+% Peter Thiemann\orcidID{0000-0002-9000-1239}}
 
@@
 %
-\institute{University of Freiburg, Germany \\
-\email{\{doanha,thiemann\}@informatik.uni-freiburg.de}
-}
+% ANONYMOUS
+% \institute{University of Freiburg, Germany \\
+% \email{\{doanha,thiemann\}@informatik.uni-freiburg.de}
+% }
 %
@@
 
-In Tezos, there are two types of accounts: implicit accounts, which are associated with a pair of private/public keys, and smart contracts, which are programmable accounts created by an origination operation and have no corresponding secret key.
-The address of a smart contract is a unique public hash that depends on the creation operation.
-An implicit account is maintained on the blockchain with its public key, balance, and counter, whose job is to prevent replay attacks.
-A smart contract account is stored with its script, storage, and balance.
-A contract script maps a pair of a parameter and a storage, which have fixed and monomorphic types to a pair of a list of internal operations and an updated storage.
-An implicit account performs three kinds of transactions: (1) transfer tokens to another implicit account, (2) invoke a smart contract, or (3) originate a new smart contract.
-A contract origination specifies the script of the contract and the initial contents of the contract storage, while a contract invocation must provide input data.
-Each transaction contains a fee to be paid either by payment to a baker or by destruction (burning).
-A transaction is injected into the blockchain network via a node, which then validates the transaction before submitting it to the network.
-Generally, a transaction can be rejected by the node for a number of reasons.
-Once the transaction is valid, it is injected into the mempool, which contains all pending transactions before they can be included in a block.
-On the other hand, a pending transaction can be lost in the mempool.
-A transaction is timed out when 60 blocks have passed and it can no longer be included in a block.
-When a transaction is included in a blockchain, the related accounts are updated according to the transaction result.
-
-The execution model is an abstraction of the Tezos blockchain \cite{tezos-whitepaper}
-augmented with functional (OCaml) programs that interact with the
-blockchain. As the blockchain is realized by a peer-to-peer network of
+Tezos supports two types of accounts: implicit accounts, which
+are associated with a pair of private/public keys, and smart
+contracts, which are programmable accounts created by an origination
+operation. The address of a smart
+contract is a unique public hash that depends on the creation
+operation. No key pair is associated with a smart contract. An
+implicit account is maintained on the blockchain with 
+its public key and balance.
+% , and counter, whose job is to preventreplay attacks.
+A smart contract account is stored with its script, storage,
+and balance. A contract script maps a pair of a parameter and a
+storage, which have fixed and monomorphic types, to a pair of a list of
+internal operations and an updated storage. An account can
+perform three kinds of transactions: (1) transfer tokens to an
+implicit account, (2) invoke a smart contract, or (3) originate a new
+smart contract. A contract origination specifies the script of the
+contract and the initial contents of the contract storage, while a
+contract invocation must provide input data. Each transaction contains
+a fee to be paid either by payment to a baker or by destruction
+(burning). A transaction is injected into the blockchain network via a
+node, which then validates the transaction before submitting it to the
+network. A transaction may be rejected by the node for a
+number of reasons. After validation, the transaction is injected into
+a \emph{mempool}, which contains all pending transactions before they can
+be included in a block. A pending transaction may simply disappear
+from the mempool, for example, a transaction times out when 60 blocks
+have passed and it can no longer be included in a block. When a transaction
+is included in the blockchain, the affected accounts are updated
+according to the transaction result.
+
+The execution model consists of functional (OCaml) programs that
+interact with an abstraction of the Tezos blockchain
+\cite{tezos-whitepaper}. As the blockchain is realized by a
+peer-to-peer network of 
 independent nodes, interaction happens through
@@
 \textbf{not} formalize the execution of the smart contracts
-themselves, we rather consider them as black boxes that execute in a
-safe way. Tezos' smart contract language Michelson and its
+themselves, we rather consider them as black boxes and probe their
+observable behavior. Tezos' smart contract language Michelson and its
 properties have been formalized elsewhere \cite{DBLP:conf/fm/BernardoCHPT19}.
@@
 \end{align*}
-In the transfer, which also serves as invocation, \NTEZ\ is the amount of tokens transferred, \PUK\ is the public key of the
+In the transfer, which also serves as contract invocation, \NTEZ\ is the amount of tokens transferred, \PUK\ is the public key of the
 sender, \ADDR\ is either a public 
@@
 the blockchain.
-\emph{Query operators} are defined by the following grammar:
+Some \emph{query operators} are defined by the following grammar:
 \begin{align*}
@@
          \mid \GETCONTRACT{}%\OPH
+         \mid \dots
 \end{align*}
@@
   % \\&\mid \CONTRACT\ \TYPE\ \EXPR
-  \\& \mid \TOSTRING\ \EXPR \mid \FROMSTRING\ \TYPE\ \EXPR
+  % \\& \mid \TOSTRING\ \EXPR \mid \FROMSTRING\ \TYPE\ \EXPR
   \\
@@
                   \TADDR \mid 
-                  \TCONTRACT\ \TYPE \mid
-                  \TCODE\ \TYPE\ \TYPEU \mid \TTEZ \mid
-                  \TOPH \mid
-                  \TSTATUS \mid \TEXCEPTION \\
-  & \mid \TINT \mid \TUNIT \mid \TBOOL \mid \TSTRING \mid \TYPE\to\TYPEU \mid \TPAIR\ \TYPE\ \TYPEU \mid \TLIST\ \TYPE
+                  \TCONTRACT\ \TYPE\ \TYPEU \mid
+                  \TCODE\ \TYPE\ \TYPEU \mid
+                  \TOPH\ \TYPE\ \TYPEU \mid
+                  \TSTATUS \mid \TEXCEPTION \mid \TTEZ \\
+  & \mid \TNO \mid \TINT \mid \TUNIT \mid \TBOOL \mid \TSTRING \mid \TYPE\to\TYPEU \mid \TPAIR\ \TYPE\ \TYPEU \mid \TLIST\ \TYPE
     \mid \TSUM\ \TYPE\ \TYPEU \mid \TOPTION\ \TYPE 
@@
 expressions, which describe the usual constructs of call-by-value PCF
-with sum, product, list, and option types, exceptions and fixpoint. Moreover, there are
+with sum, product, list, and option types, exceptions and fixpoint.
+Pattern matching is the only means to decompose values, cf.\ \PATTERN.
+
+Moreover, there are
 domain-specific primitive types and constants \CONSTANT\ to support blockchain
 operations, as well as several exceptional values collected in \ERROR.
-Pattern matching is the only means to decompose values, cf.\ \PATTERN.
 There is syntax to initiate transfers and to originate contracts as
 well as for the queries. Finally, there is a type cast
-$\CAST\EXPR\TYPE\TYPEU$, which we describe after discussing types.
+$\CAST\EXPR\TYPE\TYPEU$, which we describe after discussing types. An
+implementation provides all of these types and operations via a library API.
 
@@
 collection of standard base types as well as 
-functions, pairs, lists, sums, and option types. In addition, there
+functions, pairs, lists, sums, and option types. These types are
+chosen to match with built-in types of Michelson. 
+In addition, there
 are domain specific types of public hashes $\TPUH$ and public keys $\TPUK$ subsumed by
-a type of addresses $\TADDR$. $\TCONTRACT\ \TYPE$ is the type of
-a contract with parameter type $\TYPE$. $\CODE\ \TYPE\ \TYPEU$
+a type of addresses $\TADDR$. $\TCONTRACT\ \TYPE\ \TYPEU$ is the type of
+a contract with parameter type $\TYPE$ and storage type $\TYPEU$. $\CODE\ \TYPE\ \TYPEU$
 indicates a Michelson program with parameter type $\TYPE$ and storage
-type $\TYPEU$. Tezos tokens have type $\TTEZ$. The type $\TOPH$ signifies operation hashes
-returned by blockchain operations. Querying the status of an operation
+type $\TYPEU$. Tezos tokens have type $\TTEZ$. The type $\TOPH\ \TYPE\
+\TYPEU$ signifies operation hashes
+returned by blockchain operations. The parameters of the hash carry
+the types when originating a contract. Otherwise, they are set to the
+irrelevant type $\TNO$. We take the liberty of omitting irrelevant
+type parameters, that is, we write $\TOPH$ for $\TOPH\ \TNO\ \TNO$.
+Querying the status of an operation
 returns a value of type $\TSTATUS$. Exceptions have type
@@
 $\inferrule{}{\TPUH \SubType \TADDR}$, $\inferrule{}{\TPUK \SubType
-  \TADDR}$, and $\inferrule{}{\TCONTRACT\ \TYPE \SubType \TPUH}$.
+  \TADDR}$, and $\inferrule{}{\TCONTRACT\ \TYPE\ \TYPEU \SubType \TPUH}$.
 A cast from $\TYPE$ to $\TYPEU$ is only allowed
@@
 at run time. The corresponding downcast must check whether the public
-hash is valid and has the expected parameter type.
+hash is valid and has the expected parameter and storage type.
 
@@
 
-    \inferrule{}{\JTypeExpr\TEnv\OPH\TOPH}
+    \inferrule{}{\JTypeExpr\TEnv\OPH{\TOPH\ \TYPE\ \TYPEU}}
 
@@
       \JTypeExpr\TEnv{\EXPR_5}\TTEZ }{
-      \JTypeExpr\TEnv{\TRANSFER[\EXPR_4]{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_5}}\TOPH
+      \JTypeExpr\TEnv{\TRANSFER[\EXPR_4]{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_5}}\TOPH\
+      \TNO\ \TNO
     }
@@
       \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
-      \JTypeExpr\TEnv{\EXPR_3}\TCONTRACT\ \TYPE \\
-      \JTypeExpr\TEnv{\EXPR_4}{\TYPE} \\
+      \JTypeExpr\TEnv{\EXPR_3}\TCONTRACT\ \TYPE_p\ \TYPE_s \\
+      \JTypeExpr\TEnv{\EXPR_4}{\TYPE_p} \\
       \JTypeExpr\TEnv{\EXPR_5}\TTEZ }{
-      \JTypeExpr\TEnv{\TRANSFER[\EXPR_4]{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_5}}\TOPH
+      \JTypeExpr\TEnv{\TRANSFER[\EXPR_4]{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_5}}{\TOPH\
+      \TNO\ \TNO}
     }
@@
       \JTypeExpr\TEnv{\EXPR_5}\TTEZ }{
-      \JTypeExpr\TEnv{\ORIGINATE{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_4}{\EXPR_5}}\TOPH
+      \JTypeExpr\TEnv{\ORIGINATE{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_4}{\EXPR_5}}{\TOPH\
+      \TYPE_p\ \TYPE_s}
     }
@@
   \inferrule{
-    \JTypeExpr\TEnv\EXPR\TOPH
+    \JTypeExpr\TEnv\EXPR{\TOPH\ \TYPE\ \TYPEU}
   }{
@@
   \inferrule{
-    \JTypeExpr\TEnv\EXPR{\TPUH}
+    \JTypeExpr\TEnv\EXPR{\TCONTRACT\ \TYPE_p\ \TYPE_s}
   }{
-    \JTypeExpr\TEnv {\GETSTORAGE\EXPR}\TSTRING
+    \JTypeExpr\TEnv {\GETSTORAGE\EXPR}\TYPE_s
   }
@@
   \inferrule{
-    \JTypeExpr\TEnv\EXPR{\TOPH}
+    \JTypeExpr\TEnv\EXPR{\TOPH\ \TYPE\ \TYPEU}
   }{
-    \JTypeExpr\TEnv {\GETCONTRACT\EXPR}\TPUH
+    \JTypeExpr\TEnv {\GETCONTRACT\EXPR}{\TCONTRACT\ \TYPE\ \TYPEU}
   }
@@
 
-Conversion to and from serialized storage; deserialization may fail
-with an exception
-\begin{mathpar}
-  \inferrule{
-    \JTypeExpr\TEnv\EXPR\TYPE \\
-    \SERIALIZABLE (\TYPE)
-  }{
-    \JTypeExpr\TEnv{\TOSTRING\ \EXPR}\TSTRING
-  }
-
-  \inferrule{
-    \JTypeExpr\TEnv{\EXPR}\TSTRING
-  }{
-    \JTypeExpr\TEnv{\FROMSTRING\ \TYPE\ \EXPR}\TYPE
-  }
-\end{mathpar}
+% Conversion to and from serialized storage; deserialization may fail
+% with an exception
+% \begin{mathpar}
+%   \inferrule{
+%     \JTypeExpr\TEnv\EXPR\TYPE \\
+%     \SERIALIZABLE (\TYPE)
+%   }{
+%     \JTypeExpr\TEnv{\TOSTRING\ \EXPR}\TSTRING
+%   }
+
+%   \inferrule{
+%     \JTypeExpr\TEnv{\EXPR}\TSTRING
+%   }{
+%     \JTypeExpr\TEnv{\FROMSTRING\ \TYPE\ \EXPR}\TYPE
+%   }
+% \end{mathpar}
 

### 2021-06-14 papers/execution-model/APLAS 2021/paper.tex
types streamlined - all implementable in OCaml

@@
 \begin{lstlisting}[language=Caml,numbers=none,basicstyle=\small]
-# let auction = Cl.make_contract_hash auction_hash
+# let auction = Cl.make_contract_from_hash auction_hash
 #     ~parameter:(Ct.Or (Ct.Unit, Ct.Unit))
@@
 associated with a public key. In contrast, a value of type
-$\TCONTRACT\ \TYPE$ is a public hash that is verified to be associated
-with a contract with parameter type $\TYPE$. Operation hashes \OPH\
+$\TCONTRACT\ \TYPE\ \TYPEU$ is a public hash that is verified to be associated
+with a contract with parameter type $\TYPE$ and storage $\TYPEU$. Operation hashes \OPH\
 are only returned from blockchain operations. As the surface language
@@
 \begin{definition}%[State of a node]
-  The \emph{state of a node} is a pair
+  The \emph{state of a local node} is a pair
   $\NODE = [ \EXPRS, \ACCOUNTS
@@
 $\CAST\EXPR\TYPE\TYPEU$, which we describe after discussing types. An
-implementation provides all of these types and operations via a library API.
+implementation provides all of these types and operations via a library module.
 
@@
 returned by blockchain operations. The parameters of the hash carry
-the types when originating a contract. Otherwise, they are set to the
-irrelevant type $\TNO$. We take the liberty of omitting irrelevant
+the parameter and storage types when originating a contract. Otherwise, they are set to the
+uninformative type $\TNO$. We take the liberty of omitting uninformative
 type parameters, that is, we write $\TOPH$ for $\TOPH\ \TNO\ \TNO$.
@@
 $\inferrule{}{\TPUH \SubType \TADDR}$, $\inferrule{}{\TPUK \SubType
-  \TADDR}$, and $\inferrule{}{\TCONTRACT\ \TYPE\ \TYPEU \SubType \TPUH}$.
+  \TADDR}$, $\inferrule{}{\TCONTRACT\ \TYPE\ \TYPEU \SubType
+  \TCONTRACT\ \TYPE\ \TNO}$, $\inferrule{}{\TCONTRACT\ \TYPE\ \TNO
+  \SubType \TCONTRACT\ \TNO\ \TNO}$, and $\inferrule{}{\TCONTRACT\
+  \TNO\ \TNO \SubType \TPUH}$. Similarly for operation hashes: $\inferrule{}{\TOPH\ \TYPE\ \TYPEU \SubType
+  \TOPH\ \TYPE\ \TNO}$ and $\inferrule{}{\TOPH\ \TYPE\ \TNO
+  \SubType \TOPH\ \TNO\ \TNO}$. 
 A cast from $\TYPE$ to $\TYPEU$ is only allowed
@@
 
+We express the subtyping relation via explicit cast operations because
+the host language OCaml does not support subtyping. The rationale of
+the subtyping among contract types is determined by the usage
+pattern. If we wish to mix uses of different contracts with the same
+parameter type but different storage, then we cast them to the common
+type $\TCONTRACT\ \TYPE\ \TNO$. Once we have cast a contract to type
+$\TCONTRACT\ \TNO\ \TNO$, we can put it in a list with any other
+contract, but the only possible operation is querying its balance
+(after casting further to $\TADDR$). The function
+\lstinline/make_contract_from_hash/ mentioned in
+Section~\ref{sec:motivation} corresponds to a cast from $\TPUH$ to
+$\TCONTRACT\ \TYPE_p\ \TYPE_s$ where $\TYPE_p$ and $\TYPE_s$ are given
+by the parameters \lstinline/parameter/ and \lstinline/storage/,
+respectively.  The type parameters for operation
+hashes just communicate the parameters to the result of the
+$\CONTRACT$ operation, so their subtyping rules are analogous to the
+one for the contract type.
+
 Figure~\ref{fig:typing-expressions} presents selected typing rules for
@@
 $\JTypeCode\CODE\TYPE$ for the contract language, which we leave
-unspecified, and $\JTypeValue\STRING\TYPE$ for serialized values as
-stored on the blockchain. The latter judgment states $\STRING$ is
-a string parseable as a value of type $\TYPE$.
+unspecified. Figure~\ref{fig:typing-blockchain-operations} gives the
+typing of contract operations and queries. A standard transfer or
+contract invocation results in an uninformative operation
+hash. Originating a contract results in a fully typed operation hash,
+which may be turned into a typed constract handle by the $\CONTRACT$
+query. We can ask for the status of any operation hash, for the
+storage of a contract handle (if $\TYPE_s = \TNO$, we obtain a useless
+value with uninformative type $\TNO$), and for the balance of any address.
+% , and $\JTypeValue\STRING\TYPE$ for serialized values as
+% stored on the blockchain. The latter judgment states $\STRING$ is
+% a string parseable as a value of type $\TYPE$.
 \begin{figure}[tp]

### 2021-06-14 papers/execution-model/APLAS 2021/paper.tex
Add files via upload
Updating the introduction, the transition rules, and proofs

--- 2021-06-14 papers/execution-model/APLAS 2021/paper.tex
@@
 Building such oracles requires programmatic interfaces to implement the interactions. 
-However, current blockchains often provide non-programmatic interfaces, such as the Ethereum JSON-RPC API and the Tezos RPC API.
+However, current blockchains often provide non-programmatic interfaces, 
+such as the Ethereum JSON-RPC API and the Tezos RPC API. 
 We present a typed API for invoking contracts from OCaml programs. 
-Our type API supports the implementation of programs that safely interact with smart contracts on the blockchain.
-Such an API with a reliable computing facility and network connectivity is sufficient to self-provision an oracle.
-Moreover, our approach provides a type-safe facility instead of oracles, which are intrinsically untyped as they aim to provide a generic service.
+Our typed API supports the implementation of application programs/ oracles 
+that safely interact with smart contracts on the blockchain. 
+Such an API with a reliable computing facility and network 
+connectivity is sufficient to self-provision an oracle.
+ Moreover, our approach provides a type-safe facility instead of oracles, 
+ which are intrinsically untyped as they aim to provide a generic service.
 
@@
 whether there is an active transition for this sender (chkCount),
-whether the public hash is associated with a smart contract, whether the type of the input parameter matchs with the smart contract's parameter type (chkArg), and whether the fee is
+whether the public hash is associated with a smart contract on the blockchain, whether the type of the input parameter matchs with the smart contract's parameter type (chkArg), and whether the fee is
 sufficient. If these conditions are fulfilled, the transition forges
@@
 If the transaction is accepted, then the sender's counter is reset,
-the balances of sender and receiver are adjusted (updSucc), the smart contract storage and balance are updated (updConstr), and the time stamp increases.
+the balances of sender is adjusted (updSucc), the smart contract's storage and balance are updated (updConstr), and the time stamp increases.
 
@@
 Due to page limitations, not all transitions and their associated functions are presented in this paper, so the full proofs will be provided in an upcoming technical report.
-In this paper, since we only provide the proofs for Proposition 2 at 4 and 7.
+In this paper, we only provide the proofs for Proposition 2 at items 4 and 7.
 

### 2021-06-15 papers/execution-model/APLAS 2021/paper.tex
Add files via upload
Updated the proofs

@@
 connectivity is sufficient to self-provision an oracle.
- Moreover, our approach provides a type-safe facility instead of oracles, 
- which are intrinsically untyped as they aim to provide a generic service.
+ Moreover, our approach provides a type-safe facility instead of oracles, which are intrinsically untyped as they aim to provide a generic service.
 
@@
 \begin{proof}[4]
- After feeding into a node, the status of the operation is \STATUSPENDING\ according to the transition \TirName{ Node-Inject }.
-This operation could either be accepted by the blockchain on the condition that the elapsed time is less than 60 ($\TIME - \hat\TIME \le 60$), and then its status is \STATUSINCLUDED\ \TIME \ (the transition \TirName{ Block-Accept }) or it is timeout with the status \STATUSTIMEOUT\ (\TirName{ Block-Timeout}).
-When an operation is accepted or times out, its status is never changed.
-Therefore, we have
+ After feeding into a node, the status of the operation is \STATUSPENDING\ according to the transition \TirName{Node-Inject}.
+This operation could either be accepted by the blockchain on the condition that the elapsed time is less than 60 ($\TIME - \hat\TIME \le 60$), and then its status is \STATUSINCLUDED\ \TIME \ (the transition \TirName{Block-Accept}) or it is timed out with the status \STATUSTIMEOUT\ (\TirName{Block-Timeout}).
+When an operation is accepted or timed out, its status is never changed.
+Therefore, there are the following three cases:
 
  \begin{itemize}
- \item if the operation remains in \STATUSPENDING, then $\PENDING' (\OPH) = \PENDING (\OPH)$; 
- \item if the operation is timeout, then $\PENDING' (\OPH) = \Angle{\OP, \hat\TIME, \STATUSTIMEOUT}$ according to the transition \TirName{ Block-Timeout}; 
- \item if the operation is accepted, then $\PENDING' (\OPH) = \Angle{\OP, \hat\TIME, \STATUSINCLUDED\ \TIME }$, and $\TIME'=\TIME +1$ because the timestamp is incremented to one when an operation is accepted, according to the transition \TirName{ Block-Accept}.
+ \item if the operation remains the same (still in \STATUSPENDING, \STATUSINCLUDED\ or \STATUSTIMEOUT), then we have $\PENDING' (\OPH) = \PENDING (\OPH)$; 
+ \item if the operation is \STATUSPENDING\ and times out, then we have $\PENDING' (\OPH) = \Angle{\OP, \hat\TIME, \STATUSTIMEOUT}$ according to the transition \TirName{Block-Timeout}; 
+ \item if the operation is \STATUSPENDING, the time condition is satisfied, and then the operation is accepted, then we have $\PENDING' (\OPH) = \Angle{\OP, \hat\TIME, \STATUSINCLUDED\ \TIME }$, and $\TIME'=\TIME +1$ because the timestamp is incremented by one according to the transition \TirName{Block-Accept}.
  \end{itemize}
@@
 
-\begin{proof}[7]The function $\UPDATECOU(\MANAGERS, \PUK, \BOOLEAN)$ updates the flag of the counter of the account associated with the public key $\PUK$. The specification is as follows:
+\begin{proof}[7]To prove this point, let us consider the two related functions.
+The function $\UPDATECOU(\MANAGERS, \PUK, \BOOLEAN)$ updates the flag of the counter of the account associated with the public key $\PUK$.
+Its specification is as follows:
  \begin{itemize}
@@
 
-    Function $\UPDATESUCC(\MANAGERS, \PUK, \NTEZ, \MTEZ)$ updates the balance and the counter of the account that associates with the public key $\PUK$. The specification is as follows:
+    The function $\UPDATESUCC(\MANAGERS, \PUK, \NTEZ, \MTEZ)$ updates the balance and the counter of the account associated with the public key $\PUK$. Its specification is as follows:
  \begin{itemize}
-   \item[]  \UPDATESUCC($\PUK \mapsto \Angle{\BAL, (\NAT, \TRUE)}$, \PUK, \NTEZ, \MTEZ) = $ \PUK \mapsto \Angle{\BAL - \NTEZ - \MTEZ, (\NAT + 1, \FALSE)}$    
+   \item[]  \UPDATESUCC($\PUK \mapsto \Angle{\BAL, (\NAT, \TRUE)}$, \NTEZ, \MTEZ) = $ \PUK \mapsto \Angle{\BAL - \NTEZ - \MTEZ, (\NAT + 1, \FALSE)}$    
  \end{itemize}
 
-\noindent Then we have
+\noindent if $\MANAGERS (\PUK) =
+   \Angle{\BAL, \COU}$, 
+   then $\MANAGERS' (\PUK) =
+   \Angle{\BAL', \COU'}$ and we have the following points:
  \begin{itemize}
-   \item[-] $\COU.b=\TRUE$ means that the operation is injected and its status is \STATUSPENDING\ at \TIME according to the transition \TirName{Node-Inject}, and $\COU'.b=\FALSE$ means that the operation is accepted.
-According to the transition \TirName{Block-Accept} and the specification of the function \UPDATESUCC, the counter of the account is incremented by 1.
-This means $\COU.n' \in \{\COU.n,  \COU.n+1\}$.
-   \item[-] If the operation is still pending or it is time out, the country's number is changed in both cases. This means $\COU.n = \COU'.n$.
-   \item[-] If $\COU.n = \COU'.n$, the balance of the account is also changed since the balance  is only changed when the operation is accepted. This means $\BAL = \BAL'$.
+   \item[-] $\COU.b=\TRUE$ means that the operation is injected and its status is \STATUSPENDING\ at the time \TIME \ according to the transition \TirName{Node-Inject}.
+After that, there are only two cases where the counter's flag is reset to False.
+(1) If the operation is accepted, the counter's flag is reset ($\COU'.b=\FALSE$) according to the transition \TirName{Block-Accept} and the counter's value is incremented by 1 according to the specification of the function \UPDATESUCC\ ($\COU.n' =\COU.n+1$).
+(2) In another case, if the operation is timed out, the counter's flag is also reset to False, but the value of the counter remains the same ($\COU.n' =\COU$) according to the transition \TirName{Block-timeout}.
+That is, if $\COU.b=\TRUE$ and $\COU'.b=\FALSE$, then $\COU.n' \in \{\COU.n, \COU.n+1\}$;
+   \item[-] otherwise, if the operation is still \STATUSPENDING, the counter's value remains the same. This means $\COU.n = \COU'.n$; 
+   \item[-] and then $\COU.n = \COU'.n$ means that the operation is either still \STATUSPENDING\ or that it has timed out.
+Therefore, the balance of the account remains the same because the balance is only changed when the operation is accepted.
+This means $\BAL = \BAL'$.
  \end{itemize}

### 2021-06-16 papers/execution-model/APLAS 2021/paper.tex
Add files via upload
Updated the proofs

@@
 
+\begin{proof} Consider the proof of the second item of Lemma 3, which specifies the property on type for a smart contract invocation.
+A smart contract call \OP\ has the form \TRANSFER [\PARAMETER]\NTEZ\PUK\PUH\MTEZ.
+If $\PENDING (\OPH) = \Angle{\OP, \hat\TIME, \STATUS }$, then the operation $\OP$ is injected into the node.
+According to the transition \TirName{Node-Inject} for a smart contract invocation, the public key is valid and the public hash must be associated with a smart contract on the blockchain.
+This means $\PUK \in \DOM (\MANAGERS)$ and $\PUH\in \DOM (\CONTRACTORS)$.
+The chkArg function checks whether the type of the input parameter \PARAMETER\ matches the parameter type of the smart contract.
+If the casted type of the smart contract is $\Delta (\PUH) =\TPAIR\ \TYPE_p\ \TYPE_s$, then the type of the parameter  must be $\TYPE_p$.
+This means $\JTypeValue\PARAMETER {\TYPE_p}$.
+\end{proof}
+
 \section{Related Work}
@@
 \end{document}
+\end{proof}

### 2021-06-16 papers/execution-model/APLAS 2021/paper.tex
Add files via upload
intro & tweaked the space

@@
   % basicstyle=\ttfamily,
+  basicstyle=\fontsize{8}{9.6}\selectfont,
   morekeywords={parameter,storage,or,unit,mutez,pair,bool,address}, sensitive=false,
@@
 }
-\lstset{language=Caml}
+\lstset{
+  language=Caml,
+  captionpos=b,
+  aboveskip=-\smallskipamount,
+  belowskip=-\smallskipamount,
+  belowcaptionskip=0pt,
+  basicstyle=\fontsize{8}{9.6}\selectfont,
+  morekeywords={val}
+}
+
 \input{macros}
@@
   Smart contract applications on the blockchain can only reach their full potential if
-  they can be integrated with traditional software systems. Invoking
-  contracts and observing the state of the blockchain requires a
-  programmatic interface. We propose a typed API for this
+  they integrate seamlessly with traditional software systems via a
+  programmatic interface. This interface should provide for
+  originating and invoking contracts as well as observing the state of
+  the blockchain. We propose a typed API for this 
   purpose and establish some properties of the combined
@@
   is implemented in OCaml for the Tezos blockchain.
+
+\keywords{smart contract  \and embedded domain specific language \and types.}
 \end{abstract}
 
-\keywords{smart contract  \and embedded domain specific language \and types.}
 %
@@
 First generation blockchains were primarily geared towards supporting
-cryptocurrencies. The most prominent system of this kind is Bitcoin
-\cite{bitcoin-whitepaper}. Though Bitcoin already features a
+cryptocurrencies. Bitcoin is the most prominent system of this kind
+\cite{bitcoin-whitepaper}. Although Bitcoin already features a
 rudimentary programming language called Script, second generation
-blockchains like the Ethereum blockchain \cite{eth-whitepaper} feature
+blockchains like Ethereum \cite{eth-whitepaper} feature
 Turing-complete programming facilities, called 
@@
 blockchain, thus ensuring the integrity of the results. Third
-generation blockchains, like Tezos \cite{tezos-whitepaper}, are even adaptable to
-new requirements without breaking participating peers (no ``hard
-forks'' required).
+generation blockchains, like Tezos \cite{tezos-whitepaper}, are adaptable to
+new requirements without breaking participating peers (no  ``soft
+forks'' required and ``hard forks'' can be avoided).
 
@@
 weakness. They are fully deterministic in that they can only depend on
-data that is stored on the chain and on contract invocations, which are
-also stored on the chain. Moreover, the entire data as well as all
+data that is ultimately stored on the chain including the parameters
+of a contract invocation. Moreover, the code, the data, as well as all
 transactions are public. These properties make it hard to react to
-external stimuli like time triggers or events like an exchange rate or
-a share price hitting a limit.
-
-As smart contracts rarely live in isolation, it should be possible to
-integrate them with traditional software systems and to enable
-triggering contracts from outside the blockchain. Such triggers
-require trusted intermediaries that provide so-called oracles \cite{oracle-patterns,call-action-oracle}. A
-smart contract registers a request and a callback with an oracle. The
-oracle invokes the callback as soon as an answer is available.
-
-Building such oracles requires programmatic interfaces to implement the interactions. 
-However, current blockchains often provide non-programmatic interfaces, 
-such as the Ethereum JSON-RPC API and the Tezos RPC API. 
-We present a typed API for invoking contracts from OCaml programs. 
-Our typed API supports the implementation of application programs/ oracles 
+external stimuli like time triggers or events like a price exceeding a
+threshold unless these stimuli get translated to
+contract invocations.
+
+Arguably, smart contracts are more useful if they can be
+integrated with traditional software systems and thus triggered from
+outside the blockchain.  Oracles
+\cite{oracle-patterns,call-action-oracle} provide an approach for
+contracts to obtain outside information. A contract registers a
+request and a callback with an oracle. The oracle invokes the callback
+as soon as an answer is available. The issue of trustworthiness of the
+oracle arises because it is an entity outside of the blockchain, which
+injects information into an otherwise closed, trusted (or trustless)
+environment.
+
+However, oracles are expensive and there are other usecases for
+connecting a contract with traditional software. One example is
+automatizing procedures like managing an auction, automatic bidding in
+an auction, optimizing fees, or initiating delivery of goods to a
+customer. While some of these procedures are amenable to
+implementation as contracts, we might want to save the fee of running
+them on the blockchain. In particular, for actions that happen
+strictly within a single domain of trust, it is not worth running them
+on the blockchain. For example, automated bidding runs on behalf of
+a single peer.
+
+Building such automation requires a programmatic interface to implement the interactions. 
+Current blockchains mostly provide RPC interfaces, 
+such as the Ethereum JSON-RPC API and the Tezos RPC API, but they
+require cumbersome manipulation of string data in JSON format and do
+not provide static guarantees (except that the response to a
+well-formed JSON input is also a well-formed JSON output). 
+To improve on this situation
+we present a typed API for invoking contracts from OCaml programs. 
+Our typed API supports the implementation of application programs and oracles 
 that safely interact with smart contracts on the blockchain. 
-Such an API with a reliable computing facility and network 
-connectivity is sufficient to self-provision an oracle.
- Moreover, our approach provides a type-safe facility instead of oracles, which are intrinsically untyped as they aim to provide a generic service.
+Moreover, our approach provides a type-safe facility to communicate
+with contracts where data is automatically marshalled between OCaml
+and the blockchain. This interface is a step towards a seamless
+integration of contracts into traditional programs.
 
@@
 \begin{itemize}
+\item A typed API for originating and invoking contracts as well as
+  querying the state of the blockchain.
 \item An operational semantics for functional programs running
@@
 
+\begin{lstlisting}[language=michelson,numbers=none,float={tp},caption={Header of the auction contract},label={lst:auction-contract-header},captionpos=b,emph={close,bid},emphstyle=\underbar]
+parameter (or (unit %close)
+              (unit %bid)); # bid in transfer
+storage (pair bool          # bidding allowed
+         (pair address      # contract owner
+          address           # highest bidder's address
+        ));
+\end{lstlisting}
+\begin{lstlisting}[language=Caml,float={tp},caption={Getting the auction handle},label={lst:getting-auction-handle},numbers=none]
+# let auction = Cl.make_contract_hash auction_hash
+#     ~parameter:(Ct.Or (Ct.Unit, Ct.Unit))
+#     ~storage:(Ct.Pair (Ct.Bool, Ct.Pair (Ct.Addr, Ct.Addr))));;
+val auction :
+  ((unit, unit) Either.t,
+   bool * (Cl.Addr.t * Cl.Addr.t)) Cl.contract
+\end{lstlisting}
+\begin{lstlisting}[language=Caml,float={tp},caption={Bidding strategy},label={lst:bidding-strategy},numbers=none]
+let rec poll limit step =
+  let (bidding, (_, highest_bidder)) = Cl.get_storage auction;
+  let high_bid = Cl.get_balance auction;
+  if bidding && high_bid < limit then
+    (if highest_bidder <> my_address then  (* entrypoint %bid *)
+      try
+        Cl.call_contract auction
+          (right (min (high_bid + step, limit))) 
+      with
+      | Cl.FAILWITH message -> poll limit step;
+    Time.sleep(5 * 60);
+    poll limit step)
+\end{lstlisting}
 For concreteness, Listing~\ref{lst:auction-contract-header} shows the
@@
 address. The highest bid corresponds to the token balance of the contract.
-\begin{lstlisting}[language=michelson,numbers=none,float,caption={Header of the auction contract},label={lst:auction-contract-header},captionpos=b,emph={close,bid},emphstyle=\underbar]
-parameter (or (unit %close)
-              (unit %bid)); # bid in transfer
-storage (pair bool          # bidding allowed
-         (pair address      # contract owner
-          address           # highest bidder's address
-        ));
-\end{lstlisting}
-
-To avoid too much detail, we only outline the implementation of the entrypoints. The
+
+We only outline the implementation of the entrypoints. The
 \lstinline/%close/ entrypoint first checks its sender's address
@@
 
-We present some idealized code for % timed contract closing and
-strategic bidding as a separate program that interacts with the
+We present a program that implements
+strategic bidding by interacting with the
 blockchain.  The bidding strategy cannot be implemented as a smart
@@
 
-In preparation, we need to obtain a typed handle for the contract. We
-assume that \lstinline!Cl! is the module containing the contract
-library. The respective library function
-\lstinline!Cl.make_contract_from_hash!
+In Listing~\ref{lst:getting-auction-handle}, we use the library function
+\lstinline!Cl.make_contract_from_hash! to 
+obtain a typed handle for the contract.\footnote{\lstinline!Cl! is the module containing the contract
+  library.} The function
 takes the hash of the contract along with representations of
@@
 and storage type.
-\begin{lstlisting}[language=Caml,numbers=none,basicstyle=\small]
-# let auction = Cl.make_contract_hash auction_hash
-#     ~parameter:(Ct.Or (Ct.Unit, Ct.Unit))
-#     ~storage:(Ct.Pair (Ct.Bool, Ct.Pair (Ct.Addr, Ct.Addr))));;
-val auction :
-  ((unit, unit) Either.t,
-   bool * (Cl.Addr.t * Cl.Addr.t)) Cl.contract
-\end{lstlisting}
 
@@
 
-% \begin{lstlisting}[language=Caml,numbers=none,basicstyle=\small]
+% \begin{lstlisting}[language=Caml,numbers=none]
 % let _ = Cl.set_authority (my_address)
@@
 
-To implement the bidding strategy, we first check the state of the
+The implementation of the bidding strategy in Listing~\ref{lst:bidding-strategy} first checks the state of the
 contract to find the current highest bid. As long as bidding is
@@
 polling it every five minutes.
-
-\begin{lstlisting}[language=Caml,numbers=none,basicstyle=\small]
-let rec poll limit step =
-  let (bidding, (_, highest_bidder)) = Cl.get_storage auction;
-  let high_bid = Cl.get_balance auction;
-  if bidding && high_bid < limit then
-    (if highest_bidder <> my_address then  (* entrypoint %bid *)
-      try
-        Cl.call_contract auction
-          (right (min (high_bid + step, limit))) 
-      with
-      | Cl.FAILWITH message -> poll limit step;
-    Time.sleep(5 * 60);
-    poll limit step)
-\end{lstlisting}
 
@@
 \label{sec:execution-model}
-The context of our work is the Tezos blockchain \cite{tezos-whitepaper,tezos-intropaper}.
-Tezos is a self-amending blockchain that improves several aspects compared to established blockchains.
-Tezos proposes an original consensus algorithm called Liquid Proof of Stake that allows consensus not only on the state of its ledger, like Bitcoin \cite{bitcoin-whitepaper} or Ethereum \cite{eth-whitepaper}, but also on how the economic protocol and nodes should upgrade, and serves as a decentralized smart contract platform that focuses on formal methods to improve security.
+The context of our work is the Tezos blockchain
+\cite{tezos-whitepaper,tezos-intropaper}. Tezos is a self-amending
+blockchain that improves several aspects compared to established
+blockchains. Tezos proposes an original consensus algorithm,
+Liquid Proof of Stake, that applies not only to the state of
+its ledger, like Bitcoin \cite{bitcoin-whitepaper} or Ethereum
+\cite{eth-whitepaper}, but also to upgrades of the protocol and the software.
 
@@
 \end{figure}
-All queries and operations are started by programs, i.e., closed
+Queries and operations are started by closed
 expressions of type unit that run on the
 local node. Each program can send transactions on behalf of any
-account on the local node.  Figure~\ref{fig:syntax-expressions} defines the syntax of
-expressions, which describe the usual constructs of call-by-value PCF
-with sum, product, list, and option types, exceptions and fixpoint.
+account on the local node.  Figure~\ref{fig:syntax-expressions}
+defines the syntax of lambda calculus with sum, product, list, and option types, exceptions and fixpoint.
 Pattern matching is the only means to decompose values, cf.\ \PATTERN.
 
-Moreover, there are
-domain-specific primitive types and constants \CONSTANT\ to support blockchain
-operations, as well as several exceptional values collected in \ERROR.
+Domain-specific primitive types and constants \CONSTANT\ support blockchain
+interaction, as well as several exceptional values collected in \ERROR.
 There is syntax to initiate transfers and to originate contracts as
@@
 
-Types (also in Figure~\ref{fig:syntax-expressions}) comprise a
-collection of standard base types as well as 
+Types (also in Figure~\ref{fig:syntax-expressions}) comprise some base types as well as 
 functions, pairs, lists, sums, and option types. These types are
 chosen to match with built-in types of Michelson. 
-In addition, there
-are domain specific types of public hashes $\TPUH$ and public keys $\TPUK$ subsumed by
+There are domain specific types of public hashes $\TPUH$ and public keys $\TPUK$ subsumed by
 a type of addresses $\TADDR$. $\TCONTRACT\ \TYPE\ \TYPEU$ is the type of
@@
 
-The operational semantics is defined by several kinds of transitions depending on their scope:
+The operational semantics is defined by several kinds of transitions:
 \begin{enumerate}
@@
 Figure~\ref{fig:lifecycle-transaction} shows the transitions to start
-and finalize a transfer transaction, namely a smart contract invocation.
+and finalize a contract invocation.
 \TirName{Node-Inject} affects a local node and the blockchain. It
@@
 \end{figure}
-\begin{figure}[tp]
+\begin{figure}[t]
   \begin{mathpar}
@@
 When an operation is accepted or timed out, its status is never changed.
-Therefore, there are the following three cases:
+There are  three cases:
 
@@
    then $\MANAGERS' (\PUK) =
-   \Angle{\BAL', \COU'}$ and we have the following points:
+   \Angle{\BAL', \COU'}$ and we have:
  \begin{itemize}
@@
 \end{document}
-\end{proof}

### 2021-06-18 papers/execution-model/APLAS 2021/paper.tex
Add files via upload
Updated the proofs

@@
 \begin{proposition}
+\label{propo:1}
   The following properties are preserved by a step on a well-formed
@@
 \begin{proposition}
+\label{propo:2}
 If $[\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \BlockTrans{}
@@
    for all $\PUH \in \DOM (\CONTRACTORS)$,
-   $\CONTRACTORS (\PUH) = \Angle{ \CODE, \tilde\TIME, \BAL, \STORAGE}$
-   implies that $\PUH = \GENERATEHASH (\CODE, \tilde\TIME)$.
+    $\CONTRACTORS (\PUH)$ = $\Angle{ \CODE, \tilde\TIME, \BAL, \STORAGE}$
+   implies that $\PUH$ = $\GENERATEHASH (\CODE, \tilde\TIME)$.
 \end{enumerate}
@@
  After feeding into a node, the status of the operation is \STATUSPENDING\ according to the transition \TirName{Node-Inject}.
-This operation could either be accepted by the blockchain on the condition that the elapsed time is less than 60 ($\TIME - \hat\TIME \le 60$), and then its status is \STATUSINCLUDED\ \TIME \ (the transition \TirName{Block-Accept}) or it is timed out with the status \STATUSTIMEOUT\ (\TirName{Block-Timeout}).
+This operation could either be accepted by the blockchain on the condition that the elapsed time is less than 60 ($\TIME - \hat\TIME \le 60$), and then its status is \STATUSINCLUDED\ \TIME \ (the transition \TirName{Block-Accept}) or it is timed out with the  \STATUSTIMEOUT\ status (\TirName{Block-Timeout}).
 When an operation is accepted or timed out, its status is never changed.
-There are  three cases:
+Therefore, if $\PENDING (\OPH)$ = $\Angle{\OP,  \hat\TIME, \STATUS}$, then there are  three cases:
 
  \begin{itemize}
- \item if the operation remains the same (still in \STATUSPENDING, \STATUSINCLUDED\ or \STATUSTIMEOUT), then we have $\PENDING' (\OPH) = \PENDING (\OPH)$; 
- \item if the operation is \STATUSPENDING\ and times out, then we have $\PENDING' (\OPH) = \Angle{\OP, \hat\TIME, \STATUSTIMEOUT}$ according to the transition \TirName{Block-Timeout}; 
- \item if the operation is \STATUSPENDING, the time condition is satisfied, and then the operation is accepted, then we have $\PENDING' (\OPH) = \Angle{\OP, \hat\TIME, \STATUSINCLUDED\ \TIME }$, and $\TIME'=\TIME +1$ because the timestamp is incremented by one according to the transition \TirName{Block-Accept}.
+ \item [(1)] if the operation's status remains the same as $\STATUS$ (still in \STATUSPENDING, \STATUSINCLUDED\ or \STATUSTIMEOUT), then we have $\PENDING' (\OPH)$ = $\Angle{\OP,  \hat\TIME, \STATUS}$.
+This means $\PENDING' (\OPH)$ = $\PENDING (\OPH)$;
+ \item [(2)] if the operation's status is \STATUSPENDING\ (\STATUS\ = \STATUSPENDING), and then the operation is timed out, then we have $\PENDING' (\OPH)$ = $\Angle{\OP, \hat\TIME, \STATUSTIMEOUT}$ according to the transition \TirName{Block-Timeout};
+ \item [(3)] if the operation's status is \STATUSPENDING, the time condition is satisfied, and then the operation is accepted, then we have $\PENDING' (\OPH) = \Angle{\OP, \hat\TIME, \STATUSINCLUDED\ \TIME }$ and $\TIME'=\TIME +1$ because the timestamp is incremented by one according to the transition \TirName{Block-Accept}.
  \end{itemize}
-
+From (1), (2) and (3), the item \ref{item:7} of Proposition 2 is proved.
 \end{proof}
@@
  \begin{itemize}
-   \item[-] $\COU.b=\TRUE$ means that the operation is injected and its status is \STATUSPENDING\ at the time \TIME \ according to the transition \TirName{Node-Inject}.
+   \item[(1)] $\COU.b=\TRUE$ means that the operation is injected and its status is \STATUSPENDING\ at the time \TIME \ according to the transition \TirName{Node-Inject}.
 After that, there are only two cases where the counter's flag is reset to False.
-(1) If the operation is accepted, the counter's flag is reset ($\COU'.b=\FALSE$) according to the transition \TirName{Block-Accept} and the counter's value is incremented by 1 according to the specification of the function \UPDATESUCC\ ($\COU.n' =\COU.n+1$).
-(2) In another case, if the operation is timed out, the counter's flag is also reset to False, but the value of the counter remains the same ($\COU.n' =\COU$) according to the transition \TirName{Block-timeout}.
+If the operation is accepted, the counter's flag is reset ($\COU'.b=\FALSE$) according to the transition \TirName{Block-Accept} and the counter's value is incremented by 1 according to the specification of the function \UPDATESUCC\ ($\COU.n' =\COU.n+1$).
+In another case, if the operation is timed out, the counter's flag is also reset to False, but the value of the counter remains the same ($\COU.n' =\COU$) according to the transition \TirName{Block-timeout}.
 That is, if $\COU.b=\TRUE$ and $\COU'.b=\FALSE$, then $\COU.n' \in \{\COU.n, \COU.n+1\}$;
-   \item[-] otherwise, if the operation is still \STATUSPENDING, the counter's value remains the same. This means $\COU.n = \COU'.n$; 
-   \item[-] and then $\COU.n = \COU'.n$ means that the operation is either still \STATUSPENDING\ or that it has timed out.
+   \item[(2)] otherwise, if the operation is still \STATUSPENDING, the counter's value remains the same. This means $\COU.n = \COU'.n$; 
+   \item[(3)] and then $\COU.n = \COU'.n$ means that the operation is either still \STATUSPENDING\ or  it has timed out.
 Therefore, the balance of the account remains the same because the balance is only changed when the operation is accepted.
@@
  \end{itemize}
+
+ From (1), (2) and (3), the item \ref{item:4} of Proposition 2 is proved.
 \end{proof}
@@
 This means $\PUK \in \DOM (\MANAGERS)$ and $\PUH\in \DOM (\CONTRACTORS)$.
-The chkArg function checks whether the type of the input parameter \PARAMETER\ matches the parameter type of the smart contract.
+Moreover, the chkArg function checks whether the type of the input parameter \PARAMETER\ matches the parameter type of the smart contract.
 If the casted type of the smart contract is $\Delta (\PUH) =\TPAIR\ \TYPE_p\ \TYPE_s$, then the type of the parameter  must be $\TYPE_p$.
 This means $\JTypeValue\PARAMETER {\TYPE_p}$.
+Therefore, the item is proved.
 \end{proof}

### 2021-06-26 reports/2021-07-01/COOC-report.tex
Add files via upload

\documentclass[a4paper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{hyperref}

\title{Contract Orchestration for OCaml \\
  Progress Report 
}
\date{26 June 2021}
\author{Prof.\ Dr.\ Peter Thiemann, University of Freiburg, Germany}
\begin{document}
\maketitle{}

\section{Introduction}
\label{sec:introduction}

The Contract Orchestration for OCaml (COOC) project is funded by the Tezos foundation. Its overall goal  is to provide a framework that guarantees the correct orchestration of contract invocations from an application program in the OCaml language. This report is a continuation of the first report dated July 31, 2020.

\section{Timeline of Events}
\label{sec:timeline-events}

August 2020 - October 2020
\begin{itemize}
\item Since May 2020, Tamara Bernhardt, Master's student, has been employed as a student woker. She designed and implemented the Ocaml API that interacts with the Tezos node. The Ocaml API is based on the intensive use of the recently released Tezos library on Opam. The research  also aims at exploring the library intensively. The Ocaml API provides a programmatic interface that allows users to interact with the Tezos node, such as transferring tokens, invoking and initialising a smart contract, and querying the state of an operation. It leverages the Tezos client library with its built-in validation and pre-validation of operations to provide immediate feedback and avoid injections of invalid operations. In addition, the API extends these functions to handle the fee. A manager operation is issued starting with a low fee and repeated with the higher fee if it is rejected by the baker due to the low fee. It also handles return errors structurally. The implementation of the API can be found at the Github repository \cite{tezos-api}.
\end{itemize}

An application may perform some offline calculations before passing the result as a parameter to a smart contract on the blockchain to reduce the cost of gas and fees. However, the parameters should be checked for legitimacy, i.e., they should satisfy some specific properties. So we need a mechanism to check the validity of the assumptions before the contract is executed. It is not trivial to confirm these properties, as they  require a large amount of computation, often depending on the size of the parameter. Therefore, our goal is to design and implement a checking assertion that verifies the legitimacy of a smart contract parameter. The research proposal can be found at the expos\'{e} by Peter Thiemann \cite{expose}.

Consider a property that can be expressed with an explicit assertion in predicate logic. If we test the validity of a parameter within a smart contract, the test would consume additional cost according to the size of the parameter. However, we could do better by recruiting the validators of the contract for a distributed attempt to find a counterexample. To this end, we consider the negation of an assertion. The assertion can be checked by having each validator work independently. In this scenario, each validator only needs to be paid to generate a random value, say a random number, and perform a computation, which is a constant cost that is independent of the size of the parameter. To this end, our strategy is to extend the contract language with assertions that specify these logical formulas.
\\
\\
October 2020 - June 2021

Tamara Bernhardt worked her master's project on distributed assertion checking for Tezos smart contracts. The assertion is specified in its own syntax in a separate file from the contract implementation. This scenario requires a separate compiler for assertions in Michelson. The generated code is either combined with the contract implementation or stored separately on the blockchain. Tamara worked on grammar, lexer/parser, transformer and the compiler for the assertion language. 
\begin{itemize}
\item Defining grammar for the assertion language. Although the grammar is related to Michelson, it was designed to be as general as possible so that it can be adapted to different smart contract languages. There are two types of grammars: prefix and infix.
\item Implementing and extensively testing the lexer/parser using OCamllex and Menhir for the prefix style version.
\item Writing a backend transformer for a specific target. The backend interface is builted as a virtual library for which multiple implementations can be provided.
\item Implementing the compiler that generates the target code according to an on-chain orchestration scheme between the assertion and the parent contract.
\end{itemize}
At the end, she write the development document and then wrap it up in her thesis.

November 2020 - June 2021
\begin{itemize}
\item We recruited Julian Veigel to do his master's thesis with us. He was our student in the blockchain course. For his thesis, he will develop a checking assertion for Ethereum.  He and Tamara will collaborate on some parts of the assertion project, e.g. they might collaborate and/or share ideas on how to formulate this assertion and turn it into generators. However, they will need to implement different backends to translate assertions into Michelson and EVM respectively. The contribution of his works includes: 
\begin{itemize}
\item Exploring Ethereum's infrastructures, especially the recent release Ethereum 2.0.
\item Researching on the random number generator.
\item Writing a JSON generator that formally extracts the result of the lexer/parser into JSON. 
\item Working with Tamara on collecting use cases for interesting formulas.
\end{itemize}
\end{itemize}
December 2020 
\begin{itemize}
\item Ibrahim Njoum, a master's student in computer science, starts working on a project in my group. He is interested in programming languages and he has a compiler background. We assign him two main tasks: (1) implementing the lexer/parser with OCamllex and Menhir for the infix style of the current grammar, which is not yet implemented, and (2) continuing to work on the design and implementation of a safe-type OCaml API. The proposal for the safe-type OCaml API could be found at . He is currently enriching his background on Tezos smart contract, Ocaml, and OCamllex and Menhir. For the second task, he will need to dig deep into the Tezos library.
\end{itemize}
August 2020 - October 2020
\begin{itemize}
\item Ha and I have finished running the course ''Blockchain and Cryptocurrencies''. The lecture ended at the end of July, but the exercise was still running in August. We designed the exercise to help students confirm their understanding of the basic concepts of cryptocurrency and blockchain. We also focus on training students in blockchain programming. Students are required to implement some basic blockchain systems in Python, write smart contracts in Solidity and Michelson. In terms of Michelson, we guided the students to understand how the languages work and study its strong type system. For practice, we use some online tools that support coding and testing of smart contracts in Solidity, e.g. Remix ethereum and Michelson, e.g. Try michelson. Finally, we have included the final exam with an open time for 48 hours. The final exam covers the main concepts and programming tasks. The grading of the exam was completed and submitted at the end of October. At the end of the course, we received some feedback from the students. Some of them found the course interesting and some might consider doing research on Blockchain with us in the future.
\end{itemize}
August 2020
\begin{itemize} 
\item Ha and I have made progress on the execution model that models the interaction of an OCaml program with the Tezos blockchain. We are striving to make the model at the generic abstraction level so that it has enough detail to describe the interaction between contract calls on the blockchain and a program, but not specific to a typical blockchain system.

The current version can be found in the appendix model.pdf.
\end{itemize}

\section{Relation to the Contract}
\label{sec:relation-contract}

We have made progress on several points in the contract.
\begin{itemize}
\item to be written.
\end{itemize}

\section{Next Steps}
\label{sec:next-steps}
The assertion project is well on its way. However, there are a few items that need to be taken care of.

For Tezos, the assertion for contract C is compiled into a separate contract A(C). A(C) takes the argument x of C and tries to disprove the assertion by finding a counterexample.
\begin{itemize}
\item  implement the entire protocol. 
\end{itemize}

%Ibrahim will continue to work on his tasks. The expected deliverables are the Ocaml lexer/parser for the Infix style and the safe-type version of the Ocaml API.

%I and Ha will work on the blockchain course, the support for students on their work, and the execution model.
%\begin{itemize}
%\item Preparing for the second exam for the blockchain course.
%\item Running the blockchain course in the summer term.
%\item Competing the execution model and elaborating the execution model into the operational semantics of the full system called Mini-OCaml in the contract.

\bibliography{report}
\bibliographystyle{plainurl}
\end{document}

### 2021-06-29 reports/2021-07-01/COOC-report.tex
Add files via upload

@@
 }
-\date{26 June 2021}
+\date{\today}
 \author{Prof.\ Dr.\ Peter Thiemann, University of Freiburg, Germany}
@@
 
-August 2020 - October 2020
+\paragraph{August 2020 - October 2020} 
 \begin{itemize}
-\item Since May 2020, Tamara Bernhardt, Master's student, has been employed as a student woker.
+\item
+Since May 2020, Tamara Bernhardt, Master's student, has been employed as a student woker.
 She designed and implemented the Ocaml API that interacts with the Tezos node.
@@
 The implementation of the API can be found at the Github repository \cite{tezos-api}.
+
 \end{itemize}
-
 An application may perform some offline calculations before passing the result as a parameter to a smart contract on the blockchain to reduce the cost of gas and fees.
@@
 To this end, our strategy is to extend the contract language with assertions that specify these logical formulas.
-\\
-\\
-October 2020 - June 2021
 
-Tamara Bernhardt worked her master's project on distributed assertion checking for Tezos smart contracts.
+\paragraph{October 2020 - June 2021}
+\begin{itemize}
+\item Tamara Bernhardt worked her master's project on distributed assertion checking for Tezos smart contracts.
 The assertion is specified in its own syntax in a separate file from the contract implementation.
@@
 At the end, she write the development document and then wrap it up in her thesis.
+\end{itemize}
 
-November 2020 - June 2021
+\paragraph{November 2020 - June 2021}
 \begin{itemize}
@@
 He was our student in the blockchain course.
-For his thesis, he will develop a checking assertion for Ethereum.
+For his thesis, he will be developing a checking assertion for Ethereum.
 He and Tamara will collaborate on some parts of the assertion project, e.g.
-they might collaborate and/or share ideas on how to formulate this assertion and turn it into generators.
-However, they will need to implement different backends to translate assertions into Michelson and EVM respectively.
-The contribution of his works includes:
+they will collaborate on formulating this assertion and implementing it in generators and/or exchange ideas.
+He completed his thesis in mid-June.
+It deals with different approaches on how to implement such a validation process.
+The basic idea is to distribute the validation process to several nodes in the network, all testing different property cases.
+The goal is to reduce the cost while preserving basic properties such as decentralization and trust.
+All the approaches are discussed in detail and the most promising one is shown in an implementation.
+The contribution of his work includes:
 \begin{itemize}
-\item Exploring Ethereum's infrastructures, especially the recent release Ethereum 2.0.
-\item Researching on the random number generator.
-\item Writing a JSON generator that formally extracts the result of the lexer/parser into JSON. 
-\item Working with Tamara on collecting use cases for interesting formulas.
+\item exploring Ethereum infrastructures, especially the recent release of Ethereum 2.0.
+\item presenting different approaches and discuss their strengths and weaknesses.
+\item laying some mathematical groundwork to build a qualitative.
+\item an implementation with its components for one of the presented approaches.
 \end{itemize}
 \end{itemize}
-December 2020 
+
+\paragraph{April 2021}
 \begin{itemize}
-\item Ibrahim Njoum, a master's student in computer science, starts working on a project in my group.
-He is interested in programming languages and he has a compiler background.
-We assign him two main tasks: (1) implementing the lexer/parser with OCamllex and Menhir for the infix style of the current grammar, which is not yet implemented, and (2) continuing to work on the design and implementation of a safe-type OCaml API.
-The proposal for the safe-type OCaml API could be found at .
-He is currently enriching his background on Tezos smart contract, Ocaml, and OCamllex and Menhir.
-For the second task, he will need to dig deep into the Tezos library.
+\item Leqaa Ahmed, a bachelor student in computer science, starts her bachelor thesis in my group. 
 \end{itemize}
-August 2020 - October 2020
+
+Ha and I have been running the course “Blockchain and Cryptocurrencies”.
+This course builds on the book “Bitcoin and Cryptocurrency Technologies” by Narayanan and others.
+It covers seven weeks worth of material from the book; two weeks on Ethereum, Solidity, and its security issues; and two weeks on Tezos, with the bulk of material on Michelson.
+\paragraph{May 2020 - September 2020}
 \begin{itemize}
-\item Ha and I have finished running the course ''Blockchain and Cryptocurrencies''.
-The lecture ended at the end of July, but the exercise was still running in August.
-We designed the exercise to help students confirm their understanding of the basic concepts of cryptocurrency and blockchain.
-We also focus on training students in blockchain programming.
+\item We run the course for the first time.
+We designed the exercise to help students confirm their understanding of the basic concepts of cryptocurrency and blockchain and also focus on training students in blockchain programming.
 Students are required to implement some basic blockchain systems in Python, write smart contracts in Solidity and Michelson.
@@
 \end{itemize}
-August 2020
+
+\paragraph{April 2021 - September 2021}
 \begin{itemize} 
-\item Ha and I have made progress on the execution model that models the interaction of an OCaml program with the Tezos blockchain.
-We are striving to make the model at the generic abstraction level so that it has enough detail to describe the interaction between contract calls on the blockchain and a program, but not specific to a typical blockchain system.
+\item We are running the course for the second time.
+The basic content of the lecture and exercises has remained essentially the same, but has been adjusted according to feedback we have received from former students.
+We will be working on the new exam for this year, which will be in September.
+\end{itemize}
 
-The current version can be found in the appendix model.pdf.
+Ha and I have worked on the safe-interaction with Tezos blockchain.
+\paragraph{August 2020  - June 2021}
+\begin{itemize} 
+\item Tezos provides low-level interfaces, which work with loosely structured data in JSON format that is inconvenient to handle and offers few guarantees.
+Ha and I proposed Contract modules that provide a statically checked interface to interact with contracts on the Tezos blockchain.
+A module specification provides all types as well as information about potential failure conditions of the contract.
+The specification is checked against the contract implementation using symbolic execution.
+An OCaml module is generated that contains a function for each entrypoint of the contract.
+The types of these functions fully describe the interface including the failure conditions and guarantee type-safe and sometimes fail-safe invocation of the contract on the blockchain.
+
+Based on the result of the research, we have submited a short paper on towards contract modules for the Tezos blockchain to a workshop on formal Methods for Blockchains.
+
+\item Current blockchains mostly provide RPC interfaces, such as the Ethereum JSON-RPC API and the Tezos RPC API, but they require cumbersome manipulation of string data in JSON format and do not provide static
+guarantees (except that the response to a well-formed JSON input is also a well-formed JSON output).
+To improve on this situation, we propose a typed API for for originating and invoking contracts as well as observing the state of the blockchain and establish some properties of the combined system.
+Specifically, we provide an execution model that enables us to prove type-safe interaction between programs and the blockchain.
+We establish further properties of the model that give rise to requirements on the API.
+A prototype of the interface is implemented in OCaml for the Tezos blockchain.
+Our typed API supports the
+implementation of application programs and oracles that safely interact with
+smart contracts on the blockchain. Moreover, our approach provides a type-safe
+facility to communicate with contracts where data is automatically marshalled
+between OCaml and the blockchain. This interface is a step towards a seamless integration of contracts into traditional programs.
+
+As a result, we have submited a research paper to a conference on programming Languages and systems. The   
+Contributions of the paper is as follows:
+\begin{itemize}
+\item A typed API for originating and invoking contracts as well as querying the
+state of the blockchain.
+\item An operational semantics for functional programs running alongside smart
+contracts in a blockchain.
+\item Established various properties of the combined system with proofs in upcoming techreport.
+\item An implementation of a low-level OCaml-API to the Tezos blockchain, which corresponds to the operational semantics. 
+\end{itemize}
+
 \end{itemize}
@@
 \section{Next Steps}
-\label{sec:next-steps}
-The assertion project is well on its way. However, there are a few items that need to be taken care of.
 
-For Tezos, the assertion for contract C is compiled into a separate contract A(C). A(C) takes the argument x of C and tries to disprove the assertion by finding a counterexample.
 \begin{itemize}
-\item  implement the entire protocol. 
+\item  to be written.
 \end{itemize}
-
-%Ibrahim will continue to work on his tasks. The expected deliverables are the Ocaml lexer/parser for the Infix style and the safe-type version of the Ocaml API.
-
-%I and Ha will work on the blockchain course, the support for students on their work, and the execution model.
-%\begin{itemize}
-%\item Preparing for the second exam for the blockchain course.
-%\item Running the blockchain course in the summer term.
-%\item Competing the execution model and elaborating the execution model into the operational semantics of the full system called Mini-OCaml in the contract.
 

### 2021-06-30 reports/2021-07-01/COOC-report.tex
sync

@@
 \usepackage{hyperref}
+\usepackage{authblk}
 
@@
 }
-\date{\today}
-\author{Prof.\ Dr.\ Peter Thiemann, University of Freiburg, Germany}
+\author{Thi Thu Ha Doan}
+\author{Peter Thiemann}
+\affil{University of Freiburg, Germany}
 \begin{document}
@@
 This report is a continuation of the first report dated July 31, 2020.
+
+\subsection{Personnel}
+\label{sec:personnel}
+
+There is one full-time employee working on the project for the whole time period: Dr. Thi Thu Ha Doan (postdoctoral researcher).
+
+Student workers (part time as explained below): Tamara Bernhardt, Joshua Allgeier
 
@@
 \begin{itemize}
-\item Tamara Bernhardt worked her master's project on distributed assertion checking for Tezos smart contracts.
+\item Tamara Bernhardt worked her master's thesis (thesis work is generally unpaid, but supervised by Dr.\ Doan) on distributed  assertion checking for Tezos smart contracts.
 The assertion is specified in its own syntax in a separate file from the contract implementation.
-This scenario requires a separate compiler for assertions in Michelson.
+This scenario requires a separate compiler for assertions.
 The generated code is either combined with the contract implementation or stored separately on the blockchain.
-Tamara worked on grammar, lexer/parser, transformer and the compiler for the assertion language.
+Tamara worked on grammar, lexer/parser, transformer, and the compiler for the assertion language.
 \begin{itemize}
-\item Defining grammar for the assertion language.
-Although the grammar is related to Michelson, it was designed to be as general as possible so that it can be adapted to different smart contract languages.
-There are two types of grammars: prefix and infix.
+\item Defining the grammar for the assertion language.
+Although the underlying type structure is inspired by Michelson, it was designed to be as general as possible so that it can be adapted to different smart contract languages.
+As Tamara did not have  experience with parsing, she created a parser for a Scheme-style prefix syntax using Menhir.
+Another student was scheduled  to implement an alternative grammar inspired by OCaml syntax (as a term project), but he did not finish the work.
 \item Implementing and extensively testing the lexer/parser using OCamllex and Menhir for the prefix style version.
-\item Writing a backend transformer for a specific target. The backend interface is builted as a virtual library for which multiple implementations can be provided.
+\item Writing a backend transformer for a specific target. The backend interface is built as a virtual library for which multiple  implementations can be provided.
 \item Implementing the compiler that generates the target code according to an on-chain orchestration scheme between the assertion and the parent contract.
 \end{itemize}
-At the end, she write the development document and then wrap it up in her thesis.
+At the end, Tamara wrote the development document and then wrapped it up in her thesis.
 \end{itemize}
@@
 \begin{itemize}
-\item We recruited Julian Veigel to do his master's thesis with us.
-He was our student in the blockchain course.
-For his thesis, he will be developing a checking assertion for Ethereum.
-He and Tamara will collaborate on some parts of the assertion project, e.g.
-they will collaborate on formulating this assertion and implementing it in generators and/or exchange ideas.
-He completed his thesis in mid-June.
+\item We supervised the master's thesis of Julian Veigel.
+He developed a counterpart of the assertion checker for Ethereum.
+He  and Tamara collaborated on some parts of the assertion project, e.g., on assertion language and general analysis of the problem.
+Julian completed his thesis in mid-June.
 It deals with different approaches on how to implement such a validation process.
@@
 
+Julian's work is not directly related to Tezos and to the project's goals.
+Nevertheless, we gained a lot of understanding of the problem due to his contributions and due to the additional perspective provided by considering Ethereum.
+
 \paragraph{April 2021}
@@
 \item Leqaa Ahmed, a bachelor student in computer science, starts her bachelor thesis in my group.
+Her task is to further develop and strengthen the typing properties of our Tezos-API.
+She is mainly supervised by Dr.
+Doan.
 \end{itemize}
 
-Ha and I have been running the course “Blockchain and Cryptocurrencies”.
+Dr.
+Doan (mainly) and I have been running the course “Blockchain and Cryptocurrencies”.
 This course builds on the book “Bitcoin and Cryptocurrency Technologies” by Narayanan and others.
-It covers seven weeks worth of material from the book; two weeks on Ethereum, Solidity, and its security issues; and two weeks on Tezos, with the bulk of material on Michelson.
+Our implementation covers seven weeks worth of material from the book; two weeks on Ethereum, Solidity, and its security issues; and two weeks on Tezos, with the bulk of material on Michelson.
 \paragraph{May 2020 - September 2020}
 \begin{itemize}
-\item We run the course for the first time.
-We designed the exercise to help students confirm their understanding of the basic concepts of cryptocurrency and blockchain and also focus on training students in blockchain programming.
-Students are required to implement some basic blockchain systems in Python, write smart contracts in Solidity and Michelson.
+\item First instance of the course with 25 students.
+We created the lecture materials consisting of slides and videos.
+We designed numerous exercise tasks to help students confirm their understanding of the basic concepts of cryptocurrency and blockchain and also focus on training students in blockchain programming.
+Students are required to implement some basic blockchain systems in  Python.
+The they write smart contracts in Solidity and Michelson.
 In terms of Michelson, we guided the students to understand how the languages work and study its strong type system.
-For practice, we use some online tools that support coding and testing of smart contracts in Solidity, e.g.
-Remix ethereum and Michelson, e.g.
-Try michelson.
-Finally, we have included the final exam with an open time for 48 hours.
-The final exam covers the main concepts and programming tasks.
+For practice, we use some online tools that support coding and testing of smart contracts in Solidity (Remix ethereum) and Michelson (Try michelson).
+Finally, we conducted the final exam in the form of a take home exam during a time window of 48 hours.
+The final exam covers the main concepts and several programming tasks.
 The grading of the exam was completed and submitted at the end of October.
-At the end of the course, we received some feedback from the students.
-Some of them found the course interesting and some might consider doing research on Blockchain with us in the future.
 \end{itemize}
@@
 \begin{itemize} 
-\item We are running the course for the second time.
+\item Second instance of the course with 39 students.
 The basic content of the lecture and exercises has remained essentially the same, but has  been adjusted according to feedback we have received from former students.
-We will be working on the new exam for this year, which will be in September.
+Dr.\ Doan is conducting the weekly exercise sessions while lectures are mainly provided with recordings from the first instance.
+We plan to create one new lecture to be delivered in July.
+The exam will be in September in the same format as in the first instance.
 \end{itemize}
 
-Ha and I have worked on the safe-interaction with Tezos blockchain.
+Doan and Thiemann have worked on the safe interaction with contracts on the Tezos blockchain.
 \paragraph{August 2020  - June 2021}
@@
 \item Tezos provides low-level interfaces, which work with loosely structured data in JSON format that is inconvenient to handle and offers few guarantees.
-Ha and I proposed Contract modules that provide a statically checked interface to interact with contracts on the Tezos blockchain.
+We proposed Contract modules that provide a statically checked interface to interact with contracts on the Tezos blockchain.
 A module specification provides all types as well as information about potential failure conditions of the contract.
@@
 
-Based on the result of the research, we have submited a short paper on towards contract modules for the Tezos blockchain to a workshop on formal Methods for Blockchains.
+Based on the result of the research, we submitted a short paper titled ``Towards Contract Modules for the Tezos Blockchain''  to the workshop on Formal Methods for Blockchains (FMBC 2021).
 
@@
 
-As a result, we have submited a research paper to a conference on programming Languages and systems. The   
-Contributions of the paper is as follows:
+As a result, we submitted a research paper to the Asian Symposium on Programming Languages and Systems (APLAS 2021). The contributions of the paper are as follows:
 \begin{itemize}
@@
 \end{itemize}
-
 \end{itemize}
@@
 
+To support this paper, we implemented Michelsym, a prototype of a symbolic interpreter for Michelson. 
 \begin{itemize}

### 2021-06-30 reports/2021-07-01/COOC-report.tex
report-submitted

@@
 He developed a counterpart of the assertion checker for Ethereum.
-He  and Tamara collaborated on some parts of the assertion project, e.g., on assertion language and general analysis of the problem.
+He  and Tamara collaborated on some parts of the assertion project, e.g., on the assertion language and the general analysis of the problem (in particular, stastistical and economic aspects).
 Julian completed his thesis in mid-June.
@@
 
-Julian's work is not directly related to Tezos and to the project's goals.
-Nevertheless, we gained a lot of understanding of the problem due to his contributions and due to the additional perspective provided by considering Ethereum.
+Julian's work is not directly related to Tezos.
+Nevertheless, it contributed to the project goals because we gained a lot of insight into the problem due to the different perspective provided by considering Ethereum.
+Julian initiated and pursued the statistical analysis as well as the investigation of the economic aspects as part of his master's thesis.
 
@@
 This course builds on the book “Bitcoin and Cryptocurrency Technologies” by Narayanan and others.
-Our implementation covers seven weeks worth of material from the book; two weeks on Ethereum, Solidity, and its security issues; and two weeks on Tezos, with the bulk of material on Michelson.
+Our implementation of the course covers seven weeks worth of material from the book; two weeks on Ethereum, Solidity, and its security issues; and two weeks on Tezos, with the bulk of material on Michelson.
 \paragraph{May 2020 - September 2020}
@@
 We created the lecture materials consisting of slides and videos.
-We designed numerous exercise tasks to help students confirm their understanding of the basic concepts of cryptocurrency and blockchain and also focus on training students in blockchain programming.
+We designed numerous exercise tasks to help students confirm their understanding of the basic concepts of cryptocurrencies and blockchains.
+We also focus on training students in blockchain ``smart contract'' programming.
 Students are required to implement some basic blockchain systems in  Python.
@@
 \begin{itemize} 
-\item Tezos provides low-level interfaces, which work with loosely structured data in JSON format that is inconvenient to handle and offers few guarantees.
-We proposed Contract modules that provide a statically checked interface to interact with contracts on the Tezos blockchain.
+\item Tezos provides low-level interfaces, which work with loosely structured data in JSON format that offers few static guarantees.
+We proposed Contract Modules that provide a statically checked interface to interact with contracts on the Tezos blockchain.
 A module specification provides all types as well as information about potential failure conditions of the contract.
@@
 contracts in a blockchain.
-\item Established various properties of the combined system with proofs in upcoming techreport.
+\item Established various properties of the combined system.
 \item An implementation of a low-level OCaml-API to the Tezos blockchain, which corresponds to the operational semantics. 
@@
 \begin{itemize}
-\item to be written.
+\item Type system of OCaml and Michelson to ensure smooth interaction: this work is in progress in the submitted papers. Final steps to be taken in the work of Ms Leqaa Ahmed.
+\item Framework to guarantee orchestration
+  \begin{itemize}
+  \item First draft of contract modules provided in paper submitted to FMBC.
+  \item Compiler for contract modules: this is our next working item.
+  \item Behavioral type system:
+    We created a preliminary symbolic interpreter for checking contract module specifications.
+We plan to prototype the behavioral type system by extending the specifications with pre- and postconditions, as well as constraints on the possible call orders of the entrypoints.
+This approach gives us sufficient flexibility to investigate different designs using an encoding in first-order logic and using an SMT solver as a type checker for the system.
+  \end{itemize}
+\item (Linear types and typestate have not made it into OCaml so far, but)
+  \begin{itemize}
+  \item type-safe integration of Tezos-RPC calls in OCaml: see the paper submitted to APLAS
+  \item behavioral types with resource: this will be integrated in the SMT-based approach outlined above
+  \item type checker: will only make sense after evaluating the design space as explained above
+  \end{itemize}
+\item Mini-OCaml with operational semantics: see APLAS submission
+\item We are in the second year of teaching blockchain concepts (see above) and start getting traction with students (two master's theses finished, and currently  several Bachelor students on the topic).
+We are also offering an intensive course in OCaml to attract students to work on Tezos and project related tasks.
+\item We gave a presentation based on the current state of the project as part of the Nomadic Lab seminar series.
 \end{itemize}
@@
 
-To support this paper, we implemented Michelsym, a prototype of a symbolic interpreter for Michelson. 
+We plan to 
 \begin{itemize}
-\item  to be written.
+\item continue our teaching activities (the blockchain course, a seminar on the topic in the winter semester, another instance of the intensive OCaml course);
+\item implement code generation for contract modules;
+\item extend contract modules to contract specifications that include pre- and postconditions as well as permissible call sequences for entrypoints; 
+\item design and implement a checker for contract specifications based on Michelsym, our prototype symbolic interpreter for Michelson;
+\item complete the implementation of the type-safe interface (Leqaa Ahmed);
+\item finish the implementation of assertions (cf.\ the theses of Tamara Bernhardt and Julian Veigel), document the outcome in a paper.
 \end{itemize}
+We also plan to redesign the redesign the OCaml interface based on concepts from concurrent programming (promises / futures).
 

### 2021-08-01 papers/execution-model/APLAS 2021/2021-aplas-rebuttal.txt
review+rebuttal

Thanks to the reviewers for their insightful comments.

In a revision, we will address all specific comments, except where otherwise noted.

## reviewer 58A

* We agree that mechanizing the typing-related results is an important step forward. We are currently looking into it, but it's ongoing and hence not reported in the paper.
* Our initial examples were related to Oracles, but the work has moved away from that and we will update the text and related work to reflect that.
* *off-chain script runs on behalf of a single entity* this is indeed the case in our implementation. We will emphasize this in the revised version.
* *current approaches to verifiable clients* excellent point! we will add this aspect to our related work.

*Is the fact that contracts are deterministic a strength or a weakness?* It's mostly a strength, except for applications that require nondeterminism or some degree of impredictability, the most prominent example being (pseudo) random numbers.

*implementation does not seem polished enough* It's in constant flux as we are working against a moving target. Tezos has been updating its protocol and its library infrastructure in quite rapid succession. We are happy to add the interface in an appendix if it fits in the page limit.

*implementation for chkBal/chkPuh/etc* These are metafunctions used to describe the semantics of the blockchain transactions. The model functionality that is implemented in the Tezos client or the node.

*present your work as an extension to Michelson and its corresponding formalisation* we think that the present work is an excellent starting point for this endeavor. This way we have a blueprint for the formalization.

## reviewer 58B

We are sorry that our text does not make the need for the operational semantics sufficiently clear. In the end, we wish to state and prove properties of a system comprising OCaml code (multi-threaded or distributed) connected  via the API to Michelson contracts on the Tezos blockchain. This work is a first step in obtaining insight into the problem, next will be a formalization that connects with the Mi-Cho-Coq formalization of Michelson contracts, as mentioned by reviewer 58A.

## reviewer 58C

Let us comment on the weaknesses.

1. We started with a mini language, but were forced to add features as our work proceeded. We'll see what we can cut down.
2. *customized decision procedure* I'm not sure where this impression comes from, as we have no customized decision procedure. We do not give any indication of that in the paper and there is nothing special going on in type checking beyond OCaml's provisions. It would be advantageous to have subtyping, but as OCaml does not support subtyping, we decided to keep types separate and rely on cast operations that are checked at run time. BTW this approach is inspired by Michelson's design, which has similar casting operations, e.g., `IMPLICIT_CONTRACT` which casts from type `address` to type `contract unit`.
3. Soundness. We have a sketch of the type soundness proof on paper, but nothing typeset so far. It is structured as usual in type preservation and progress results. Progress is, of course, relative to the behavior of the blockchain (which we model as a gray box), so that any operation that requires interaction with the blockchain may be stuck temporarily.
4. Implementation. We'll be happy to make some space to discuss implementation details.

### 2021-08-06 papers/contract-modules/fmbc2021/fmbc-main.tex
first round of revisions

@@
 
-%\ccsdesc[100]{\textcolor{red}{Replace ccsdesc macro with valid one}}
 %%TODO mandatory: Please choose ACM 2012 classifications from
 %%https://dl.acm.org/ccs/ccs_flat.cfm
-\ccsdesc[100]{}
+\begin{CCSXML}
+<ccs2012>
+   <concept>
+       <concept_id>10011007.10011006.10011060.10011690</concept_id>
+       <concept_desc>Software and its engineering~Specification languages</concept_desc>
+       <concept_significance>500</concept_significance>
+       </concept>
+   <concept>
+       <concept_id>10011007.10011006.10011041.10010943</concept_id>
+       <concept_desc>Software and its engineering~Interpreters</concept_desc>
+       <concept_significance>300</concept_significance>
+       </concept>
+ </ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Software and its engineering~Specification languages}
+%\ccsdesc[300]{Software and its engineering~Interpreters}
 
@@
 %Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Access}
+\EventEditors{Bruno Bernardo and Diego Marmsoler}
 \EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
+\EventLongTitle{3rd International Workshop on Formal Methods for Blockchains (FMBC 2021)}
+\EventShortTitle{FMBC 2021}
+\EventAcronym{FMBC}
+\EventYear{2021}
+\EventDate{July 18-19, 2021}
+\EventLocation{Los Angeles, California, USA (Virtual Conference)}
 \EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
+\SeriesVolume{95}
+\ArticleNo{4}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Contract modules provide a clean, language-integrated way to interact
-with a blockchain. They abstract over underlying string-based
-interfaces and details like fee handling. They provide a high-level
-typed interface which reduces a contract invocation to a function call
-in the language.
+We propose contract modules that provide a clean, language-integrated
+way to interact with a blockchain from a host language (OCaml in our
+case). They abstract over underlying string-based interfaces and
+details like fee handling. They provide a high-level typed interface
+which reduces a contract invocation to a function call in the host
+language.
 
-Contract modules do not provide a fixed API, but
-rather generate a specialized interface for each contract. This
+The contract modules approach does not provide a fixed API, but
+rather generates a specific interface for each contract with one
+function for each entrypoint of the contract. This
 interface is statically checked against the contract implementation to
-ensure type safety and exception safety (every failure condition
-arising is handled by proper error reporting).
+ensure type safety and exception safety. That is, values passed to an
+interface function do not lead to type mismatches when invoking the
+underlying contract. Morever, every failure condition arising during
+contract execution is handled by proper error reporting according to
+the interface.
 
@@
 supports Michelson as its low-level contract language, and the
-language OCaml, which comes with an expressive polymorphic type system
+host language OCaml, which comes with an expressive polymorphic type system
 as well as a powerful module system that we
@@
 tokens (Tezzies) for their work. According to proof-of-stake,
-bakers and validators are just nodes elected by the Tezos network
+bakers and validators are nodes elected by the Tezos network
 according to their token balance.
 
-Each Tezos contract owns an account as well as some storage. Contracts
-are pure functions of type parameter $\times$ storage $\to$ operation
-list $\times$ storage. When a contract is invoked with a parameter,
+Each Tezos contract is associated with an account as well as some
+storage. Contracts are pure functions of type $\mathit{parameter} \times
+\mathit{storage} \to \mathit{operation\ list} \times
+\mathit{storage}$, where the types \textit{parameter} and
+\textit{storage} are depend on the specific contract while the type
+\textit{operation} is fixed by the Tezos system. When a contract is invoked with a parameter,
 the blockchain provides the current storage and updates it with the
-second, storage component of its return value. The first component is
-a list of blockchain operations (contract deployments, token
-transfers, contract invocations) that are executed transactionally
-after the first invocation terminates. Each invocation may be
+second, storage component of its return value. The first component of
+the return value is a list of blockchain operations (contract deployments, token
+transfers, contract invocations, and delegation of baking rights) that
+are executed transactionally after the first invocation terminates. Each invocation may be
 accompanied with an amount of tokens that are added to the current
-account balance of the contract.
+account balance of the callee contract.
 
-Contracts are implemented in the language Michelson, a fully typed
+Contracts are implemented in the language Michelson, a statically typed
 stack-based language. Each contract has fixed types for its parameter
@@
 deployed. Besides primitive types like unit, int, bool, address, and string,
-there are pairs, sums, functions, lists, and maps (and many more) that
+there are pairs, sums, functions, lists, and maps along with a range
+of domain-specific types (operation, key, signature, timestamp,
+key\_hash, contract, mutez --- for tokens, and so on) most of which
 can serve as types for storage and parameters.
@@
 \label{sec:an-auction-contract}
-\begin{lstlisting}[float,caption={Simple auction contract (auction.tz)},captionpos=b,label={lst:auction-header},language=michelson,numbers=none,emph={close,bid},emphstyle=\underbar]
+\begin{lstlisting}[float,caption={Simple auction contract (auction.tz)},captionpos=b,label={lst:auction-header},language=michelson,numbers=none,emph={close,bid,bidding,owner,hi_bidder},emphstyle=\underbar]
 parameter (or (unit %close) (unit %bid));
-storage (pair bool          # bidding allowed
-         (pair address      #  contract owner
-          address           # highest bidder's address
-        ));
+storage (pair (bool %bidding)
+              (pair (address %owner)
+                    (address %hi_bidder)));
 \end{lstlisting}
@@
 \lstinline/(true,(owner,owner))/ which indicates that bidding is
-allowed and the contract owner is currently also the highest
+allowed and the contract owner is currently the highest
 bidder. On deployment the owner deposits an initial balance to indicate the
@@
 
-To invoke this contract from an OCaml program, we'd like to generate an
+To invoke this contract from an OCaml program, we generate an
 OCaml module, say \lstinline/Auction/, from a specification of the
@@
 error monad that makes the failures explicit in a custom
-datatype.\footnote{Alternatively, this could be done using OCaml
-  exceptions, but we chose to stay within the monadic framework that
-  is already used by existing Tezos APIs.}
+datatype.\footnote{Alternatively, errors could be modeled using OCaml
+  exceptions, but we choose to stay within the monadic framework that
+  is used by existing Tezos APIs.}
 
@@
 the auction contract.  It declares the entrypoint \lstinline/bid/ as
-\lstinline/paid/, i.e., it needs to be invoked with a
-non-zero amount of tokens, it gives the pattern \lstinline/()/ for the
-input value of type \lstinline/unit/, and it specifies two possible
+\lstinline/paid/, i.e., it should be invoked with a
+non-zero amount of tokens, it states the pattern \lstinline/()/ for the
+input value of type \lstinline/unit/, and it specifies two 
 failure messages that we wish to deal with programmatically.
-The \lstinline/close/ entrypoint is similar, but requires no tokens.
+The \lstinline/close/ entrypoint is similar, but it is not
+\lstinline/pair/. This contract reflects the understanding of the
+programmer with the intention that the \lstinline/raises/ clauses
+cover all failures that can arise during execution of the respective
+entrypoint.
 
@@
 Listing~\ref{lst:generated-signature} contains an OCaml module
-signature as it could be generated from the contract module. The
+signature as it would be generated from the contract module. The
 module \lstinline/Tezos/ supposedly contains types and other low-level
@@
 
-We plan to check the contract by symbolic execution against its
-specification in the contract module. Here are some examples of
-checkable properties.
+We check the contract by symbolic execution against its
+specification in the contract module. Symbolic execution proceeds in
+the usual way by calculating a symbolic stack at each transition from
+one Michelson instruction to the next. The initial stack is calculated
+from the storage type, the parameter type, and the entrypoint.
+As we aim to keep symbolic
+values as concrete as possible, some instructions may turn out to be
+unreachable or only reachable under certain conditions. This way, we
+obtain, for each entrypoint, a set of final symbolic stacks along with
+a path condition indicating when this final state is
+reachable. Moreover, for each \lstinline/FAILWITH/ instruction we
+obtain a symbolic value for the reported message and a path condition
+indicating reachability of this instruction. We employ the SMT solver
+Z3 \cite{DBLP:conf/tacas/MouraB08,DBLP:conf/setss/BjornerMNW18} to
+check the feasibility of a path condition.
+
+Here are some simple examples of checkable properties.
 
@@
 It should not be possible to reach that instruction from an unpaid
-entrypoint  like \lstinline/close/.
+entrypoint  like \lstinline/close/. This property is straightforward
+to check from the path condition generated for the \lstinline/AMOUNT/
+instruction.
 
@@
 \lstinline/raises/ clause.
+
+For the simple auction contract the symbolic interpreter flags an
+omission in the contract module
+(Listing~\ref{lst:contract-module-example}). The problem is that
+bidding returns the previous highest bid as part of the transaction
+where the highest bidder is stored as a value of type
+\lstinline/address/.  However, to receive a token transfer, this
+address must by cast (by the Michelson implementation of the contract)
+to an implicit contract of Michelson type \lstinline/(contract unit)/. This cast is unavoidable as a
+value of contract type cannot be stored. However, the cast may fail and its failure leads to an
+error condition that is reported with a \lstinline/FAILWITH/ instruction that is not covered by the
+contract module.\footnote{We generated the Michelson code for this example using the Liquidity
+  compiler (\url{https://www.liquidity-lang.org/}). While the failures for \lstinline/closed/ and
+  \lstinline/too low/ are explicit in the source program, the compiler inserts the casts into the contract
+  type automatically using the error message \texttt{No entrypoint default with parameter type
+    unit}.}  The entrypoint for closing has the same issue with the address of the owner, who is
+scheduled to receive the balance of the contract.
+
+The best way to address this issue would be to assert that the addresses stored for the owner and
+the highest bidder always cast successly into the \lstinline/(contract unit)/ type so that the
+stated module type can be retained. Unfortunately, doing so requires control over the deployment of
+the contract where the storage is initialized and it is not clear whether deployment should be part
+of the API generated from a contract module.
+
+The quick fix is to add \lstinline/raises/ clauses for the \texttt{No entrypoing \dots}
+message. With this fix, we successfully check the module description against the Michelson
+implementation of its contract.
 
@@
 off-chain code needs to obtain properties like balance, storage etc of the
-contract, but this information is available from the Tezos node without a fee!
+contract, but this information is available from a Tezos node without a fee! Of course, such an
+off-chain check is prone to race conditions as concurrent contract invocations from other parties
+may interfere and change the data before our module gets a chance to invoke the contract. 
 We discuss two of the preconditions to highlight the properties that 
-need to be analyzed.
+need to be analyzed and where race conditions may interfere.
 
@@
 \lstinline/amount > balance/ fails, we can be sure that the contract
-invocation will also fail; either because some closed the auction or
+invocation will also fail; either because someone closed the auction or
 because the balance is at least as high as in the off-chain sample. 
@@
 
-Status: we are currently working on a prototype of the symbolic interpreter.
-% As future work, we
-% combine the contract module with our typed API designed to provide a
-% general type-safe programmatic API for the Tezos blockchain.
+Status: the symbolic interpreter works on Michelson files which results from compiling the examples
+provided with the Liquidity compiler. It generates human-readable output as well as output in the
+SMTlib format suitable for SMT-solvers like Z3.
+
+While our conceptual approch is applicable and would be beneficial for other blockchains, the actual
+implementation is very much tied to the Tezos blockchain. The key asset here is the symbolic
+interpreter which is hardcoded for Michelson and adapted to the peculiarities of the Tezos
+blockchain. By targeting Michelson, our work is applicable to all languages running on Tezos, but
+a similar tool would have to be developed from scratch for another blockchain.
 

### 2021-08-07 papers/contract-modules/fmbc2021/fmbc-main.tex
final version submitted

@@
   contract implementation using symbolic execution. An OCaml module is
-  generated that contains a function for each entrypoint of the
+  generated that contains a function for each entry point of the
   contract. The types of these functions fully describe the interface
@@
 rather generates a specific interface for each contract with one
-function for each entrypoint of the contract. This
+function for each entry point of the contract. This
 interface is statically checked against the contract implementation to
@@
 
+A Michelson contract has a single default entry point. However, the \textit{parameter} type is
+typically a sum type and each component of the sum can serve as a subsidiary entry point.
+
 \section{An auction contract}
@@
 header shown in Listing~\ref{lst:auction-header}. 
-This contract has two entrypoints, \lstinline/close/ and \lstinline/bid/,
+This contract has two entry points, \lstinline/close/ and \lstinline/bid/,
 expressed by giving the single parameter a sum type. To call the
-entrypoint \lstinline/close/ we invoke the contract with parameter \lstinline/Left ()/
+entry point \lstinline/close/ we invoke the contract with parameter \lstinline/Left ()/
 otherwise we use \lstinline/Right ()/, where \lstinline/()/ is the sole
@@
 minimum bid. Closing the contract transfers the balance to the
-owner. It is restricted to the owner. Closing as well as bidding fails
+owner. Closing is restricted to the owner. Closing as well as bidding fails
 if the auction is
@@
 bidder and the previous highest bidder is reimbursed. Otherwise,
-bidding fails, too.
+bidding fails.
 
@@
 \lstinline/close/ and \lstinline/bid/ corresponding to the
-entrypoints. The type of these entrypoints reflects further properties
-of these entrypoints as well as the ways in which an entrypoint might
+entry points. The type of these entry points reflects further properties
+of these entry points as well as the ways in which an entry point might
 fail.
@@
 Listing~\ref{lst:contract-module-example} shows a contract module for
-the auction contract.  It declares the entrypoint \lstinline/bid/ as
+the auction contract.  It declares the entry point \lstinline/bid/ as
 \lstinline/paid/, i.e., it should be invoked with a
@@
 failure messages that we wish to deal with programmatically.
-The \lstinline/close/ entrypoint is similar, but it is not
+The \lstinline/close/ entry point is similar, but it is not
 \lstinline/pair/. This contract reflects the understanding of the
@@
 cover all failures that can arise during execution of the respective
-entrypoint.
+entry point.
 
@@
 status, and \lstinline/monad/ is an internal monad type. The signature
-declares a function and an error type for each entrypoint.
+declares a function and an error type for each entry point.
 
@@
 the transaction fee, an argument for passing an amount of tokens
-(only for a paid entrypoint), the next argument would be for
+(only for a paid entry point), the next argument would be for
 the parameter; it is omitted here because its type is
@@
 We check the contract by symbolic execution against its
-specification in the contract module. Symbolic execution proceeds in
-the usual way by calculating a symbolic stack at each transition from
-one Michelson instruction to the next. The initial stack is calculated
-from the storage type, the parameter type, and the entrypoint.
+specification in the contract module. Symbolic execution proceeds by calculating a symbolic stack at
+each transition from 
+one Michelson instruction to the next. The symbolic interpreter is fully typed and rejects ill-typed
+Michelson programs, if the ill-typed part is reachable from the default entry point. The initial
+stack is calculated 
+from the storage type, the parameter type, and the entry point.
 As we aim to keep symbolic
@@
 unreachable or only reachable under certain conditions. This way, we
-obtain, for each entrypoint, a set of final symbolic stacks along with
+obtain, for each entry point, a set of final symbolic stacks along with
 a path condition indicating when this final state is
@@
 
-For each entrypoint, we collect the set of reachable instructions.
+For each entry point, we collect the set of reachable instructions.
 For example, the  \lstinline/AMOUNT/ instruction obtains the amount of
@@
 It should not be possible to reach that instruction from an unpaid
-entrypoint  like \lstinline/close/. This property is straightforward
+entry point  like \lstinline/close/. This property is straightforward
 to check from the path condition generated for the \lstinline/AMOUNT/
@@
 
-For the \lstinline/FAILWITH/ instructions, we also collect their
-arguments. The symbolic interpreter needs to retain concrete values as
-much as possible to obtain precise results at this point. Each
-argument to \lstinline/FAILWITH/ should be accounted for by one
+For each entry point, we collect the set of reachable \lstinline/FAILWITH/ instructions along with
+their path condition and their arguments. In most cases the symbolic interpreter finds a concrete
+argument for each \lstinline/FAILWITH/ instruction because the typical usage pattern is to push a
+concrete (string) value on the stack immediately preceding the \lstinline/FAILWITH/.
+It remains to check that each argument to \lstinline/FAILWITH/ should be accounted for by one
 \lstinline/raises/ clause.
 
-For the simple auction contract the symbolic interpreter flags an
+Checking the simple auction contract in this way already flags an
 omission in the contract module
@@
   type automatically using the error message \texttt{No entrypoint default with parameter type
-    unit}.}  The entrypoint for closing has the same issue with the address of the owner, who is
+    unit}.}  The entry point for closing has the same issue with the address of the owner, who is
 scheduled to receive the balance of the contract.
@@
 the highest bidder always cast successly into the \lstinline/(contract unit)/ type so that the
-stated module type can be retained. Unfortunately, doing so requires control over the deployment of
-the contract where the storage is initialized and it is not clear whether deployment should be part
-of the API generated from a contract module.
+stated module type can be retained. Unfortunately, doing so requires control over the initialization
+of the storage, which is part of the deployment of the contract. At present, our design for contract
+modules does not include support for the deployment of a contract. Moreover, it is not clear whether
+it makes sense to support it as there is no guarantee
+that a contract will be deployed using the API generated from a contract module.
 
@@
 message. With this fix, we successfully check the module description against the Michelson
-implementation of its contract.
+implementation of its contract. Another fix would be to rewrite the contract to enable the
+dynamic creation of auctions.
 
@@
 \label{sec:advanced-checking}
-\begin{lstlisting}[float,captionpos=b,caption={Enhanced contract module},label={lst:safer-contract-module}]
+\begin{lstlisting}[float,captionpos=b,caption={Enhanced contract module},label={lst:safer-contract-module},numbers=left]
 contract type SaferAuction = sig
@@
   requires bidding raises "closed"        (** auction closed*)
+  requires (SOURCE = owner) raises "not owner"
   ensures not bidding
-  requires (sender = owner) raises "not owner"
+  ensures (post.BALANCE = 0)
+  ensures (TRANSFER_TOKENS unit BALANCE hi_bidder)
 
@@
   requires bidding raises "closed"        (** auction closed*)
+  requires (AMOUNT > pre.BALANCE) raises "too low" (** low bid *)
   ensures bidding 
-  requires (amount > old.balance)
-  raises "too low"                 (** bid too low *)
-  ensures (balance >= old.balance)
-  ensures (owner = old.owner)
+  ensures (post.BALANCE = AMOUNT)
+  ensures (post.hi_bidder = SOURCE)
+  ensures (TRANSFER_TOKENS unit pre.BALANCE hi_bidder)
+
+  invariant (post.owner = owner)
+  invariant (post.bidding => bidding)
+  invariant (post.hi_bidder = hi_bidder or post.hi_bidder = SOURCE)
 end
@@
 As it is expensive to invoke a contract just to find out that it
-fails, we propose to extend entrypoint specifications with
-preconditions as shown in Listing~\ref{lst:safer-contract-module}. The
+fails, we propose to extend entry point specifications with
+preconditions along with some global invariants as shown in Listing~\ref{lst:safer-contract-module}. The
 idea is that the generated OCaml module tries to check the
@@
 may interfere and change the data before our module gets a chance to invoke the contract.
+
+Generally, a specification can refer to the values available to the contract. For example, the
+instructions \lstinline/SOURCE/\footnote{The execution of a Michelson contract is part of
+  a transaction, which can encompass several contract executions. The SOURCE of a Michelson contract
+  is the originator of the entire transaction.}, \lstinline/BALANCE/, and \lstinline/AMOUNT/ refer
+to the respective values. As the current \lstinline/BALANCE/ includes the \lstinline/AMOUNT/ sent
+with the transaction, we write \lstinline/pre.BALANCE/ ($=$ \lstinline/BALANCE/ $-$
+\lstinline/AMOUNT/) for the balance before the transaction starts and \lstinline/post.BALANCE/ for
+the balance after the transaction finishes. The latter is calculated by subtracting the amounts
+transferred from the current \lstinline/BALANCE/. The existence of a token transfer in the returned
+operation list is indicated by
+the respective \lstinline/TRANSFER_TOKENS/ instruction.  The components of the storage are referred
+to by name. We distinguish the outgoing storage by prepending \lstinline/post./ as in
+\lstinline/post.owner/.
+
+For each clause \lstinline/requires/ $\Phi$ \lstinline/raises/ $s$, we take the path condition
+$\Theta$ for a \lstinline/FAILWITH/ instruction with argument matching the string $s$ and check that
+$\Phi \wedge \Theta$ is not satisfiable in the context given by the initial stack for the entry point.
+
+From all \lstinline/requires/ $\Phi_i$ and \lstinline/ensures/ $\Psi_j$ clauses, we check that $\neg
+(\bigwedge\Phi_i \to \bigwedge \Psi_j)$ is unsatisfiable in the context given by the initial stack
+for the entry point and its corresponding final stack and path condition.
+
 We discuss two of the preconditions to highlight the properties that 
@@
 
-The precondition \lstinline/sender = owner/ of \lstinline/close/ can
+The precondition \lstinline/SOURCE = owner/ of \lstinline/close/ can
 be checked off-chain because the owner's address is part of the
 storage. However, it is in general unsound to perform such a test
-off-chain because the owner's address could change if an entrypoint
+off-chain because the owner's address could change if an entry point
 changes that component of the storage. To safely check this
-precondition, the analysis must determine that the owner component of
-the storage remains the same across all possible execution paths of
-the contract.
+precondition, all other entry points must preserve the \lstinline/owner/'s address, which is indeed
+the case by the postcondition in line~17. This postcondition is verified as outlined above.
 
-Moreover, the gathering of instructions must build path predicates,
-such that each \lstinline/FAILWITH/ instruction comes with a predicate
-that must be true to reach the instruction. In contract
-implementation, the path predicate is \lstinline/sender != owner/. As
-the conjunction of path predicate and precondition is unsatisfiable
-and because the \lstinline/owner/ component is constant, an off-chain
-test for \lstinline/sender = owner/ precisely predicts whether the
-failure condition arises.
+% Moreover, the gathering of instructions must build path predicates,
+% such that each \lstinline/FAILWITH/ instruction comes with a predicate
+% that must be true to reach the instruction. In contract
+% implementation, the path predicate is \lstinline/sender != owner/. As
+% the conjunction of path predicate and precondition is unsatisfiable
+% and because the \lstinline/owner/ component is constant, an off-chain
+% test for \lstinline/sender = owner/ precisely predicts whether the
+% failure condition arises.
 
 The situation is slightly more complex at the \lstinline/bid/
-entrypoint. The failure \lstinline/"closed"/ is guarded by
+entry point. The failure \lstinline/"closed"/ is guarded by
 \lstinline/bidding/. As the \lstinline/bidding/ component of the state can change,
-precise prediction is not possible. A closer look reveals some
+a precise prediction is not possible. A closer look reveals some
 subtlety. If \lstinline/bidding/ is true, then the flag may have
@@
 contract because \lstinline/bidding/ will never be reset to true.
-
-Hence the analysis should also record value transitions in the
-storage for non-failing executions. For \lstinline/bidding/
-\lstinline/bid/ transitions from true to true and \lstinline/close/
-transitions from true to false. Thus, if the off-chain check finds
-\lstinline/bidding/ $=$ false, then we can precisely predict that
-\lstinline/bid/ would fail and trigger the corresponding error without
-invoking the contract proper.
+We address this situation by verifying the global invariant
+\lstinline/post.bidding => bidding/.
 
@@
 monotonically. Thus, if the off-chain check
-\lstinline/amount > balance/ fails, we can be sure that the contract
+\lstinline/AMOUNT > pre.BALANCE/ fails, we can be sure that the contract
 invocation will also fail; either because someone closed the auction or
-because the balance is at least as high as in the off-chain sample. 
+because the balance is at least as high as in the off-chain sample. Checking \lstinline/pre.BALANCE/
+off-chain is particularly simple, because it is the current balance of the account.
+
+\section{Symbolic interpretation of Michelson}
+\label{sec:symb-interpr-mich}
+
+Michelsym, our symbolic interpreter for Michelson, works in two stages. In the first stage, it
+calculates symbolic stacks between each pair of reachable instructions. The underlying symbolic
+domain comprises all concrete values, supports the type system, and generates a term representation
+for symbolic values. Michelsym collects a path predicate that is extended at each conditional, but
+which remains uninterpreted. If symbolic execution reaches certain instructions (most notably
+\lstinline/FAILWITH/), Michelsym records the argument value and the path condition.
+
+Presently, Michelsym works on Michelson files which result from compiling the examples
+provided with the Liquidity compiler. It generates human-readable output as well as output in the
+SMTlib format suitable for SMT-solvers like Z3. This output needs to be weaved together manually
+with the formulas generated from a contract module.
+
+We plan to revise Michelsym so that it directly communicates with Z3 to directly check for
+unsatisfiable path conditions and to be better integrated with the contract module frontend.
+
 \section{Related work}
@@
 
-Status: the symbolic interpreter works on Michelson files which results from compiling the examples
-provided with the Liquidity compiler. It generates human-readable output as well as output in the
-SMTlib format suitable for SMT-solvers like Z3.
-
 While our conceptual approch is applicable and would be beneficial for other blockchains, the actual

### 2021-08-07 papers/contract-modules/fmbc2021/macros.tex
final version submitted

--- 2021-05-17 papers/contract-modules/fmbc2021/macros.tex
@@
   backgroundcolor=\color{pypypy},
-  morekeywords={module,contract,sig,val,paid,entrypoint,raises},
+  morekeywords={requires,ensures,invariant,sender,amount,balance,storage,hash,module,contract,sig,val,paid,entrypoint,raises},
   classoffset=1,
   morekeywords={nat,int,unit,string,or,pair,option,address,bool},
-  morekeywords={Tezos,pukh,tz,status,monad},
+  morekeywords={Tezos,pukh,mutez,status,monad},
   keywordstyle=\color{blue},

### 2021-08-23 papers/execution-model/APLAS 2021/paper.tex
Add files via upload
mostly formatting changes

@@
            \ERRPUK \mid \ERRPUH \mid \ERRARG \mid \ERRINIT\\
-	\EXPR & :: =  \CONSTANT \mid \STATUS \mid \ERROR \mid \VARIABLE \mid \lambda \VARIABLE. \EXPR\ 
+	\EXPR & :: =  \CONSTANT \mid \STATUS \mid \ERROR \mid \VARIABLE \mid \lambda \VARIABLE. \EXPR
 	\mid \EXPR\EXPR  %\mid \FST\ \EXPR \mid \SND\ \EXPR 	%\mid \NI \EI
@@
 
-    \inferrule{\JTypeCode \CODE{ \TPAIR\ \TYPE_p\
-        \TYPE_s}}{\JTypeExpr\TEnv\CODE{\TCODE\ \TYPE_p\ \TYPE_s}}
+    \inferrule{
+      \JTypeCode \CODE{ \TPAIR\ \TYPE_p\ \TYPE_s}
+    }{\JTypeExpr\TEnv\CODE{\TCODE\ \TYPE_p\ \TYPE_s}}
 
@@
   \inferrule{
-    \JTypeExpr\TEnv\EXPR{\TOPH\ \TYPE\ \TYPEU}
+    \JTypeExpr\TEnv\EXPR{\TOPH\ \TYPE\ \TYPEU} \\
+    \TYPE\ne\TNO \\ \TYPEU \ne\TNO
   }{
@@
 
-  \inferrule[Block-Accept]{
+  \inferrule[Block-Originate-Accept]{
     \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
@@
   \inferrule{
-    \JTypeExpr\cdot{ \EXPR_i}\TUNIT  }{
+    \JTypeExpr\cdot{ \EXPR_i}\TUNIT
+  }{
     \JTypeNode{[\overline{\EXPR}, \ACCOUNTS]}
@@
 
-  \inferrule{\JTypeBlockchain\Delta\BLOCKCHAIN \\
+  \inferrule{
+    \JTypeBlockchain\Delta\BLOCKCHAIN \\
     \JTypeNode{\NODE_i}
@@
 \begin{lemma}[Preservation]
-  If $\BLOCKCHAIN[\overline\NODE] \SystemTrans{} \BLOCKCHAIN'[\overline\NODE']$ and
-  $\JTypeBlockchain\Delta \BLOCKCHAIN$, then there is some
+  If $\BLOCKCHAIN[\overline\NODE] \SystemTrans{} \BLOCKCHAIN'[\overline{\NODE'}]$ and
+  $\JTypeConfig\Delta {\BLOCKCHAIN[\overline\NODE]}$, then there is some
   $\Delta' \supseteq \Delta$ such that
-  $\JTypeBlockchain{\Delta'}{ \BLOCKCHAIN'}$.
+  $\JTypeConfig{\Delta'}{ \BLOCKCHAIN'[\overline{\NODE'}]}$.
 \end{lemma}
@@
 This means $\JTypeValue\PARAMETER {\TYPE_p}$.
-Therefore, the item is proved.
+Therefore, this item is proved.
 \end{proof}
@@
 
+\input{appendix}
 \end{document}

### 2021-08-23 papers/execution-model/APLAS 2021/appendix.tex
proofs of preservation and progress

\clearpage
\appendix

\section{Type Soundness}
\label{sec:type-soundness}

\begin{lemma}[Canonical forms]\label{lemma:canonical-forms}
  Given a set of local accounts $\ACCOUNTS$, a blockchain
  $\BLOCKCHAIN$, and a typed value $\JTypeExpr\cdot \VAL \TYPE$.
  \begin{itemize}
  \item If $\TYPE=\TPUH$, then $\VAL=\PUH$ and $\PUH \in \DOM
    (\BLOCKCHAIN.\CONTRACTORS)$.
  \item If $\TYPE = \TPUK$, then $\VAL=\PUK$ and $\exists\PAK$ such
    that $(\PAK, \PUK) \in \ACCOUNTS$.
  \item If $\TYPE = \TADDR$, then $\VAL$ is $\PUH$ or $\PUK$.
  \item If $\TYPE = \TCONTRACT\ \TYPE_p\ \TYPE_s$, then $\VAL=\PUH$
    and $\PUH \in \DOM (\BLOCKCHAIN.\CONTRACTORS)$ and
    $\BLOCKCHAIN.\CONTRACTORS (\PUH) = (\CODE, \TIME, \BAL, \STORAGE)$
    such that $      \JTypeCode \CODE{ \TPAIR\ \TYPE_p\ \TYPE_s}$ and
    $\JTypeValue \STORAGE { \TYPE_s}$.
  \item If $\TYPE = \TCODE\ \TYPE\ \TYPEU$, then $\VAL = \CODE$ and
    $\JTypeCode \CODE{\TPAIR\ \TYPE\ \TYPEU}$.
  \item If $\TYPE = \TOPH\ \TYPE\ \TYPEU$, then $\VAL = \OPH$ and
    $\OPH\in \DOM (\BLOCKCHAIN.\PENDING)$ and $\BLOCKCHAIN.\PENDING
    (\OPH) = \Angle{\OP, \TIME, \STATUS}$ where $\TYPE=\TYPEU=\TNO$ if
    $\OP$ is a transfer and $\TYPE=\TYPE_p\ne\TNO$, $\TYPEU=\TYPE_s\ne\TNO$ if $\OP
    = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ$ and $\JTypeCode\CODE{
      \TPAIR\ \TYPE_p\ \TYPE_s}$.
  \item If $\TYPE = \TSTATUS$, then $\VAL \in \{\STATUSPENDING , \STATUSINCLUDING (\INT),
    \STATUSTIMEOUT\}$.
  \item If $\TYPE = \TEXCEPTION$, then $\VAL \in \{\ERRPRG, \ERRBAL, \ERRCOUNT, \ERRFEE,
    \ERRPUK, \ERRPUH, \ERRARG, \ERRINIT \}$.
  \item If $\TYPE = \TTEZ$, then $\VAL = \NTEZ$, a token amount.
  \item If $\TYPE = \TNO$, then $\VAL$ can be any syntactic value.
  \item If $\TYPE = \TINT$, then $\VAL = \INT$.
  \item If $\TYPE = \TUNIT$, then $\VAL = \SUNIT$.
  \item If $\TYPE = \TBOOL$, then $\VAL \in \{ \TRUE, \FALSE\}$.
  \item If $\TYPE = \TSTRING$, then $\VAL = \STRING$ a string.
  \item If $\TYPE = \TYPE\to\TYPEU$, then $\VAL = \lambda
    \VARIABLE. \EXPR$. 
  \item If $\TYPE = \TPAIR\ \TYPE\ \TYPEU$, then $\VAL = (\VAL',
    \VAL'')$ where $\JTypeExpr\cdot {\VAL'}\TYPE$ and $\JTypeExpr\cdot
    {\VAL''}\TYPEU$ in context $\ACCOUNTS$ and $\BLOCKCHAIN$.
  \item If $\TYPE = \TLIST\ \TYPE$, then either $\VAL = \NIL$ or $\VAL
    = \CONS\ {\VAL'}\ {\VAL''}$ where $\JTypeExpr\cdot{\VAL'}\TYPE$
    and $\JTypeExpr\cdot{\VAL''}{\TLIST\ \TYPE}$ in context
    $\ACCOUNTS$ and $\BLOCKCHAIN$.
  \item If $\TYPE = \TSUM\ \TYPE\ \TYPEU$, then either $\VAL = \LEFT\
    \VAL'$ where $\JTypeExpr\cdot {\VAL'}\TYPE$ or $\VAL= \RIGHT\
    \VAL''$ where $\JTypeExpr\cdot {\VAL''}\TYPEU$ in context
    $\ACCOUNTS$ and $\BLOCKCHAIN$.
  \item If $\TYPE = \TOPTION\ \TYPE$, then $\VAL = \NONE$ or $\VAL =
    \SOME\ \VAL'$ where $\JTypeExpr\cdot {\VAL'}\TYPE$ in context
    $\ACCOUNTS$ and $\BLOCKCHAIN$.
  \end{itemize}
\end{lemma}

\begin{lemma}[Subterm replacement]\label{lemma:subterm-replacement}
  If $\JTypeExpr\cdot{ \EC\EXPR}\TYPE$,
  $\JTypeExpr\cdot\EXPR \TYPE'$, and
  $\JTypeExpr\cdot{\EXPR'} \TYPE'$, then
  $\JTypeExpr\cdot{ \EC{\EXPR'}}\TYPE$.
\end{lemma}
\begin{proof}
  Induction on evaluation context $\ECN$ making use of the fact that
  an evaluation context does not bind variables.
\end{proof}

\begin{lemma}[Preservation for expressions]\label{lemma:type-preservation-expressions}
  If $\JTypeExpr\cdot{ \EXPR}\TYPE$ and $\EXPR \ExprTrans \EXPR'$,
  then  $\JTypeExpr\cdot{ \EXPR'}\TYPE$.
\end{lemma}
\begin{proof}
  Standard result: type preservation for simply typed lambda calculus
  with pairs, sums, and exceptions. Uses
  Lemma~\ref{lemma:subterm-replacement} for reductions in evaluation
  context. See, for instance, Types in
  Programming Languages by Benjamin Pierce.
\end{proof}

\begin{lemma}[Preservation]
  If $\BLOCKCHAIN[\overline\NODE] \SystemTrans{} \BLOCKCHAIN'[\overline{\NODE'}]$ and
  $\JTypeConfig\Delta {\BLOCKCHAIN[\overline\NODE]}$, then there is some
  $\Delta' \supseteq \Delta$ such that
  $\JTypeConfig{\Delta'}{ \BLOCKCHAIN'[\overline{\NODE'}]}$.
\end{lemma}
\begin{proof}
  The proof is by induction on the reduction relation
  $\BLOCKCHAIN[\overline\NODE] \SystemTrans{}
  \BLOCKCHAIN'[\overline\NODE']$ and inversion of the typing
  judgments. We only consider the exemplary reductions shown in the
  paper. We mark all components that belong to the reductum with 
  $'$ as in $\NODE'$.

  From $\JTypeConfig\Delta {\BLOCKCHAIN[\overline\NODE]}$ we obtain
  \begin{gather}
    \label{eq:1}
    \JTypeBlockchain\Delta\BLOCKCHAIN
    \\\label{eq:2}
    \JTypeNode{\NODE_i}
  \end{gather}
  From~\eqref{eq:1} we obtain
  \begin{gather}
    \label{eq:3}
    \DOM (\Delta) = \DOM (\BLOCKCHAIN.\CONTRACTORS)
    \intertext{and $\forall\PUH\in\DOM (\Delta)$}\label{eq:4}
    \Delta (\PUH) = \TPAIR\ \TYPE_p\ \TYPE_s
    \\\label{eq:5}
    \JTypeCode{\BLOCKCHAIN.\CONTRACTORS (\PUH).\CODE} {\TPAIR\ \TYPE_p\ \TYPE_s}
    \\
    \JTypeValue{\BLOCKCHAIN.\CONTRACTORS (\PUH).\STORAGE}{ \TYPE_s}
  \end{gather}
  From~\eqref{eq:2} we obtain, if $\NODE_i = [\overline{\EXPR_i},
  \ACCOUNTS_i]$, 
  \begin{gather}
    \label{eq:6}
    \JTypeExpr\cdot{ \EXPR_{ij}}\TUNIT
  \end{gather}

  \textbf{Reduction }$  \inferrule[Config-Node]
  {\NODE_0 \NodeTrans \NODE_0'}
  { {\BLOCKCHAIN[\NODE_0 :: \overline\NODE]}
    \SystemTrans
    {\BLOCKCHAIN[\NODE_0' :: \overline\NODE]}}$.

  The only possible reduction here is $  \inferrule[Node-Eval]
  {
    \EXPR \ExprTrans \EXPR'
  }{
    [\EC\EXPR :: \EXPRS, \ACCOUNTS] \NodeTrans{}
    [\EC{\EXPR'} :: \EXPRS, \ACCOUNTS]
  }$.

  From~\eqref{eq:6}, we know that $\JTypeExpr\cdot{ \EXPR}\TUNIT$. By
  Lemma~\ref{lemma:type-preservation-expressions}, $\JTypeExpr\cdot{
    \EXPR'}\TUNIT$, the types of the $\EXPRS$ are not affected, hence
  $\JTypeNode{\NODE_0' = [\EC{\EXPR'} :: \EXPRS, \ACCOUNTS]}$. None of the other
  nodes changed, neither did $\BLOCKCHAIN$, so that
  $\JTypeConfig\Delta{{\BLOCKCHAIN[\NODE_0' :: \overline\NODE]}}$.

  \clearpage
  \textbf{Reduction }$\inferrule[Config-System]{
    \NODE\|\BLOCKCHAIN \SystemTrans \NODE'\|\BLOCKCHAIN'
}{
    \BLOCKCHAIN[\NODE :: \overline{\NODE}] \SystemTrans
    \BLOCKCHAIN'[\NODE' :: \overline{\NODE}]
  }$.

  We need to consider the cases for $\SystemTrans$.

  \textbf{Subcase }$  \inferrule[Node-Inject]{
    \Angle{\PAK,\PUK} \in \ACCOUNTS \\
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKARG (\CONTRACTORS, \PUH, \PARAMETER) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUH (\CONTRACTORS, \PUH) \\
    \CHECKGAS (\CONTRACTORS, \PUH, \PARAMETER, \MTEZ) \\
    \OPH = \GENERATEOPH (\OP, \TIME) \\
    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ    
  }{
    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
      [\PENDING, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
    { [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \|
      [ \OPH \mapsto \Angle{\OP, \TIME, \STATUSPENDING}
      ::\PENDING,
      \UPDATECOU(\MANAGERS, \PUK, \TRUE),
      \CONTRACTORS,
      \TIME]
    }
  }$.
  Here $\NODE = [\EC\OP :: \EXPRS, \ACCOUNTS]$. We first check type
  preservation for the expression part. There are two typing rules for
  the transfer
  $\OP$, but only the one for contract invocation applies as the other
  one requires $\JTypeExpr\cdot{\PUH}\TPUK$, which does not hold.

  % For a token transfer
  % \begin{gather}
  %   \label{eq:7}
  %       \inferrule{
  %     \JTypeExpr\TEnv{\NTEZ}\TTEZ \\
  %     \JTypeExpr\TEnv{\PUK}\TPUK \\
  %     \JTypeExpr\TEnv{\PUH}\TPUK \\
  %     % \JTypeExpr\TEnv{\EXPR_3}{\TCONTRACT\ \TUNIT} \\
  %     \JTypeExpr\TEnv{\PARAMETER}\TUNIT \\
  %     \JTypeExpr\TEnv{\MTEZ}\TTEZ }{
  %     \JTypeExpr\TEnv{\TRANSFER[\PARAMETER]{\NTEZ}{\PUK}{\PUH}{\MTEZ}}\TOPH\
  %     \TNO\ \TNO
  %   }
  % \end{gather}

  For a contract invocation (specialized to empty environment)
  \begin{gather}
    \label{eq:8}
        \inferrule{
      \JTypeExpr\cdot{\NTEZ}\TTEZ \\
      \JTypeExpr\cdot{\PUK}\TPUK \\
      \JTypeExpr\cdot{\PUH}\TCONTRACT\ \TYPE_p\ \TYPE_s \\
      \JTypeExpr\cdot{\PARAMETER}{\TYPE_p} \\
      \JTypeExpr\cdot{\MTEZ}\TTEZ }{
      \JTypeExpr\cdot{\TRANSFER[\PARAMETER]{\NTEZ}{\PUK}{\PUH}{\MTEZ}}{\TOPH\
      \TNO\ \TNO}
    }
  \end{gather}
  The canoncical forms lemma~\ref{lemma:canonical-forms} is parameterized over the accounts
  $\ACCOUNTS$ of the local node and the current contractors
  $\BLOCKCHAIN.\CONTRACTORS$. Hence, we know that the arguments are
  legal, which is also checked by the rule.

  The reduct returns an operation hash $\OPH$ at type $\TOPH\ \TNO\
  \TNO$, which places no restrictions on the context of $\OPH$.

  Moreover, $\Delta' = \Delta$ and $\CONTRACTORS' = \CONTRACTORS$ as
  no new contract is originated.

  We conclude with Lemma~\ref{lemma:subterm-replacement} and
  reapplying \TirName{Config-System}.

  \textbf{Subcase }$\inferrule[Contract-Yes]{
    \JTypeCode\CODE{\TPAIR\ \TYPE\ \TYPEU} \\
    \BLOCKCHAIN.\CONTRACTORS (\PUH) =  \Angle{\CODE, \tilde\TIME, \NTEZ', \STRING'}
    % 
  }{
    { [\EC{\CAST\PUH\TPUH{\TCONTRACT\ \TYPE}}  :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
    }
    \SystemTrans
    { [\EC{\PUH} :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
    }
  }$.

  Immediate using Lemma~\ref{lemma:canonical-forms} and
  Lemma~\ref{lemma:subterm-replacement}.

  \textbf{Subcase }$\inferrule[Contract-No]{
    % \ADDR \in \DOM (\BLOCKCHAIN.\MANAGERS) \Rightarrow \TYPE\ne\TUNIT \\
    \BLOCKCHAIN.\CONTRACTORS (\PUH) = \Angle{\CODE, \tilde\TIME,
      \NTEZ', \STRING'} \Rightarrow {}
    \JTypeCode\CODE{\TPAIR\ \TYPE'\ \TYPEU} \wedge \TYPE \ne \TYPE' \\
  }{
    { [\EC{\CAST\PUH\TPUH{\TCONTRACT\ \TYPE}}  :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
    }
    \SystemTrans
    { [\EC{\RAISE\ \ERRPRG} :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
    }
  }$.

  The typing rule for $\RAISE$ can return any type. Hence, this is
  immediate by Lemma~\ref{lemma:subterm-replacement}.

  \textbf{Subcase }$\inferrule[Block-Originate]{
    \Angle{\PAK,\PUK} \in \ACCOUNTS \\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPRG (\CODE) \\
    \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ)  \\
    \CHECKINIT (\CODE, \STRING) \\
    % \OPH = \GENERATEOPH(\PUK, \CODE, \STRING, \NTEZ, \MTEZ, \TIME)
    % \\
    \OPH = \GENERATEOPH(\OP, \TIME) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ }{ [\EC\OP :: \EXPRS,
    \ACCOUNTS
    ] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \to \\
    [\EC{\OPH} :: \EXPRS, \ACCOUNTS] \| [\OPH \mapsto \Angle{\OP,
      \TIME, \STATUSPENDING} ::\PENDING,
    \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME] }$.

  Suppose that $\JTypeCode\CODE {\TPAIR\ \TYPE_p\ \TYPE_s}$. Then
  $\JTypeExpr\cdot\OP{\TOPH\ \TYPE_p\ \TYPE_s}$. But this is the type
  of the $\OPH$ in the reductum as it points to $\OP$ in
  $\PENDING$. Hence, the result is immediate by
  Lemma~\ref{lemma:subterm-replacement}.

  % \textbf{Subcase }$    \inferrule[Block-Accept-Query]{
  %   \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
  %   \PENDING (\OPH) =  \Angle{\OP,
  %     \hat\TIME, \STATUSINCLUDING\ \tilde\TIME} \\
  %   \PUH = \GENERATEHASH (\CODE, \tilde\TIME)
  %   % \CONTRACTORS (\PUH) =  \Angle{\CODE, \tilde\TIME, \NTEZ', \STRING'}
  % }{
  %   [\EC{\GETCONTRACT\ \OPH}  :: \EXPRS, \ACCOUNTS] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
  %   \SystemTrans 
  %   [\EC{ \PUH}  :: \EXPRS, \ACCOUNTS] \|  [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
  % }$.

  \textbf{Subcase }$\inferrule[Query-Balance-Implicit]{
    % \BLOCKCHAIN =
    % [\PENDING, \PUK \mapsto \Angle{\BAL, \COU} :: \MANAGERS,
    % \CONTRACTORS, \TIME]
    \BLOCKCHAIN.\MANAGERS (\PUK) = \Angle{\BAL,\COU}
  }{[\EC{\GETBALANCE\PUK} :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN
    \SystemTrans\ [\EC{\BAL} ::\EXPRS, \ACCOUNTS] \| \BLOCKCHAIN} $.

  The reduction replaces $\GETBALANCE\PUK$ of type $\TTEZ$ by $\BAL$
  of the same type. Hence, the result is immediate by
  Lemma~\ref{lemma:subterm-replacement}.

  \textbf{Subcase }$\inferrule[Query-Balance-Fail]{ \PUK \notin \DOM
    (\BLOCKCHAIN.\MANAGERS) \ }{[\EC{\GETBALANCE\PUK} :: \EXPRS,
    \ACCOUNTS] \| \BLOCKCHAIN \SystemTrans {[\EC{\RAISE\ \ERRPUK}
      ::\EXPRS, \ACCOUNTS] \| \BLOCKCHAIN}}$.

  Immediate by Lemma~\ref{lemma:subterm-replacement} because $\RAISE$
  can have any type.

  \clearpage
  \textbf{Reduction }$\inferrule[Config-Block]
  {\BLOCKCHAIN \BlockTrans \BLOCKCHAIN'}
  { \BLOCKCHAIN[{\overline\NODE}]
    \SystemTrans
    \BLOCKCHAIN'[{\overline\NODE}]}$.

  We need to considere cases for $\BlockTrans$.

  \textbf{Subcase }$\inferrule[Block-Accept]{
    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
    \TIME - \hat\TIME \le 60
  }{
    { 
      [\OPH \mapsto \Angle{\OP, \hat \TIME, \STATUSPENDING}
      ::\PENDING, \MANAGERS,
      \CONTRACTORS, \TIME]}
    \BlockTrans 
    {
      [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING}, \\
    { \UPDATESUCC (\MANAGERS, \PUK, \NTEZ, \MTEZ), 
      \UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \PARAMETER), \TIME +1]
    }
  }$.

  No typing-related properties are affected.

  \textbf{Subcase }$\inferrule[Block-Originate-Accept]{
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
    \PUH = \GENERATEHASH(\CODE, \TIME) \\
    \TIME-\hat\TIME  \le 60
  }{
    [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING} :: \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    \BlockTrans \\
    [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING, \UPDATESUCC
    (\MANAGERS, \PUK, \NTEZ, \MTEZ),\\ \PUH \mapsto  \Angle{\CODE, \TIME, \NTEZ, \STRING} :: \CONTRACTORS, \TIME+1]
  }$.

  This reduction extends $\CONTRACTORS$ with a new entry for
  $\PUH$. To preserve typing, we need to extend $\Delta$ with the
  binding $\PUH : \TPAIR\ \TYPE_p\ \TYPE_s$ where $\JTypeCode\CODE
  {\TPAIR\ \TYPE_p\ \TYPE_s}$. The generated code pointer is obtained
  with a query operation via the operation hash $\OPH$, which is also
  connected to the parameter and storage types.

  \textbf{Subcase }$  \inferrule[Block-Timeout]{
    \TIME-\hat\TIME > 60
  }{ 
    {[\OPH \mapsto \Angle{\OP, \hat \TIME, \STATUSPENDING}
     ::\PENDING, \MANAGERS,
      \CONTRACTORS, \TIME]}
    \BlockTrans \\
    { 
      [\OPH \mapsto \Angle{\OP, \hat \TIME, \STATUSTIMEOUT}
     :: \PENDING,  \UPDATECOU(\MANAGERS, \OP.\PUK, \FALSE),
      \CONTRACTORS, \TIME]}
  }$.

  No typing-related properties are affected.
\end{proof}

\clearpage
\begin{lemma}[Progress for expressions]\label{lemma:progress-expressions}
  If $\JTypeExpr\cdot{ \EXPR}\TYPE$, then either
  \begin{itemize}
  \item $\EXPR$ is a value,
  \item $\EXPR \ExprTrans \EXPR'$, or
  \item $\EXPR = \EC{\EXPR'}$ is a blockchain operation in an evaluation context:
    \begin{itemize}
    \item $\EXPR' = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ$;
    \item $\EXPR' = \ORIGINATE\NTEZ\PUK\CODE\INIT\MTEZ$;
    \item $\EXPR' = \QOP\ \VAL$;
    \item $\EXPR' = \CAST\VAL\TYPE\TYPEU$ where $\TYPEU \SubType \TYPE$.
    \end{itemize}
  \end{itemize}
\end{lemma}
\begin{proof}
  Standard result: progress for simply type lambda calculus with
  pairs, sums, and exceptions. Upcasts are resolved by identity
  reductions. The blockchain operations including downcasts are not
  handled by the $\ExprTrans$ relation. 
\end{proof}
\begin{lemma}[Progress]
  If $\JTypeConfig\Delta{\BLOCKCHAIN[\overline\NODE]}$, then either
  all expressions in all nodes are unit values or there is a
  configuration $\BLOCKCHAIN'[\overline\NODE']$ such that
  $\BLOCKCHAIN[\overline\NODE] \SystemTrans \BLOCKCHAIN'[\overline\NODE']$.
\end{lemma}
\begin{proof}
  From $\JTypeConfig\Delta {\BLOCKCHAIN[\overline\NODE]}$ we obtain
  \begin{gather}
    \label{eq:101}
    \JTypeBlockchain\Delta\BLOCKCHAIN
    \\\label{eq:102}
    \JTypeNode{\NODE_i}
  \end{gather}
  From~\eqref{eq:101} we obtain
  \begin{gather}
    \label{eq:103}
    \DOM (\Delta) = \DOM (\BLOCKCHAIN.\CONTRACTORS)
    \intertext{and $\forall\PUH\in\DOM (\Delta)$}\label{eq:4}
    \Delta (\PUH) = \TPAIR\ \TYPE_p\ \TYPE_s
    \\\label{eq:105}
    \JTypeCode{\BLOCKCHAIN.\CONTRACTORS (\PUH).\CODE} {\TPAIR\ \TYPE_p\ \TYPE_s}
    \\
    \JTypeValue{\BLOCKCHAIN.\CONTRACTORS (\PUH).\STORAGE}{ \TYPE_s}
  \end{gather}
  From~\eqref{eq:102} we obtain, if $\NODE_i = [\overline{\EXPR_i},
  \ACCOUNTS_i]$, 
  \begin{gather}
    \label{eq:106}
    \JTypeExpr\cdot{ \EXPR_{ij}}\TUNIT
  \end{gather}

  For each such $\EXPR_{ij}$, Lemma~\ref{lemma:progress-expressions}
  yields that either
  \begin{itemize}
  \item $\EXPR_{ij}$ is a value; as it has type $\TUNIT$, we obtain
    $\EXPR_{ij} = \SUNIT$ by Lemma~\ref{lemma:canonical-forms};
  \item $\EXPR_{ij} \ExprTrans \EXPR_{ij}'$, in which case the whole
    system makes a step; or
  \item $\EXPR_{ij} = \EC{\EXPR}$ where $\EXPR$ is a blockchain operation.
  \end{itemize}

  \textbf{Subcase } $\EXPR =
  \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ$. In this case, the
  \TirName{Node-Inject} reduction is in principle enabled:
  \begin{mathpar}
    \inferrule[Node-Inject]{
      \Angle{\PAK,\PUK} \in \ACCOUNTS \\
      \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
      \CHECKARG (\CONTRACTORS, \PUH, \PARAMETER) \\
      \CHECKCOU (\MANAGERS, \PUK) \\
      \CHECKPUH (\CONTRACTORS, \PUH) \\
      \CHECKGAS (\CONTRACTORS, \PUH, \PARAMETER, \MTEZ) \\
      \OPH = \GENERATEOPH (\OP, \TIME) \\
      \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ    
    }{
      { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
        [\PENDING, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
      { [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \|
        [ \OPH \mapsto \Angle{\OP, \TIME, \STATUSPENDING}
        ::\PENDING,
        \UPDATECOU(\MANAGERS, \PUK, \TRUE),
        \CONTRACTORS,
        \TIME]
      }
    }
  \end{mathpar}
  Thanks to the canonical forms Lemma~\ref{lemma:canonical-forms}, we
  know that $\Angle{\PAK,\PUK} \in \ACCOUNTS$, $\CHECKARG
  (\CONTRACTORS, \PUH, \PARAMETER)$ holds, and $\CHECKPUH
  (\CONTRACTORS, \PUH)$ holds. If one of the remaining checks fails,
  then one of the \TirName{Node-Reject} transitions throws an
  exception, so the configuration steps in every case.

  \textbf{Subcase } $\EXPR = \ORIGINATE\NTEZ\PUK\CODE\INIT\MTEZ$. In
  this case, the \TirName{Block-Originate} reduction is in principle
  enabled:
  \begin{mathpar}
    \inferrule[Block-Originate]{
      \Angle{\PAK,\PUK} \in \ACCOUNTS \\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
      \CHECKCOU (\MANAGERS, \PUK) \\
      \CHECKPRG (\CODE) \\
      \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ)  \\
      \CHECKINIT (\CODE, \STRING) \\
      % \OPH = \GENERATEOPH(\PUK, \CODE, \STRING, \NTEZ, \MTEZ, \TIME)
      % \\
      \OPH = \GENERATEOPH(\OP, \TIME) \\
      \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ }{ [\EC\OP :: \EXPRS,
      \ACCOUNTS
      ] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \to \\
      [\EC{\OPH} :: \EXPRS, \ACCOUNTS] \| [\OPH \mapsto \Angle{\OP,
        \TIME, \STATUSPENDING} ::\PENDING,
      \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME] }
  \end{mathpar}
  Thanks to the canonical forms Lemma~\ref{lemma:canonical-forms}, we
  know that $\Angle{\PAK,\PUK} \in \ACCOUNTS$, $\CHECKPRG (\CODE)$ holds, and $\CHECKINIT
  (\CODE, \STRING)$ holds. If one of the remaining checks fails,
  then one of the \TirName{Node-Reject} transitions throws an
  exception, so the configuration steps in every case.

  \textbf{Subcase } $\EXPR = \QOP\ \VAL$. If $\EXPR =
  \GETBALANCE\VAL$, then inversion tells us that $\JTypeExpr\cdot{
    \VAL}\TADDR$ and by canonical forms
  (Lemma~\ref{lemma:canonical-forms}), it must be that $\VAL$ has the
  form $\PUK$ or $\PUH$. In any case, the value is a meaningful
  address for the manager $\MANAGERS$. Depending on whether the
  address is in use, one of the reductions
  \TirName{Query-Balance-Implicit} or \TirName{Query-Balance-Fail} can
  execute. There are further analogous reductions handling the case where
  $\VAL=\PUH$ and we ask for the balance of a smart contract.

  Most queries behave like $\GETBALANCE\cdot$, except getting a
  contract handle from an operation hash:

  \textbf{Subcase }$\EXPR = \GETCONTRACT\VAL$. This query is somewhat
  special as it is handled with reduction
  \TirName{Block-Accept-Query}. By inversion and canonical forms
  (Lemma~\ref{lemma:canonical-forms}) we know that $\VAL = \OPH$ is a
  valid operation hash of type $\TCONTRACT\ \TYPE\ \TYPEU$ where
  $\TYPE\ne\TNO$ and $\TYPEU \ne\TNO$.

  However, this reduction is conditional on the state of the
  transaction; it requires the new contract to have status
  $\STATUSINCLUDED$. If the contract has status $\STATUSTIMEOUT$, then
  the query raises and exception, analogous to the
  \TirName{Query-Balance-Fail} reduction. If the contract has status
  $\STATUSPENDING$, then the expression is blocked, but the system can
  make a step using \TirName{Block-Originate-Accept} that changes the
  status from $\STATUSPENDING$ to $\STATUSINCLUDED$. Alternatively,
  \TirName{Block-Timeout} can make a step to change the status to
  $\STATUSTIMEOUT$. In any case, the system as a whole can make a reduction.

  \textbf{Subcase } $\EXPR = \CAST\VAL\TYPE\TYPEU$ where $\TYPEU \SubType \TYPE$.
  As an example, we consider the reductions \TirName{Contract-Yes} and
  \TirName{Contract-No}, where a cast is applied to a value of type
  $\TPUH$. By canonical forms, we know that the value has the
  form $\PUH \in \DOM (\BLOCKCHAIN.\CONTRACTORS)$. The code pointed to
  by this hash is checked at run time and results either in a $\PUH$
  at suitable contract type (-Yes reduction) or in raising an
  exception (-No reduction).

\end{proof}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% End:

### 2021-08-25 paper.tex
Add files via upload

--- 2021-08-23 papers/execution-model/APLAS 2021/paper.tex
@@
 
-\keywords{smart contract  \and embedded domain specific language \and types.}
+\keywords{smart contracts \and embedded domain specific languages \and types.}
 \end{abstract}
@@
 Turing-complete programming facilities, called 
-Smart Contracts. They provide robust trustworthy distributed computing
+\textit{smart contracts}. They provide robust trustworthy distributed computing
 facilities even though the programs run on a peer-to-peer network with
@@
 request and a callback with an oracle. The oracle invokes the callback
-as soon as an answer is available. The issue of trustworthiness of the
-oracle arises because it is an entity outside of the blockchain, which
-injects information into an otherwise closed, trusted (or trustless)
-environment.
-
-However, oracles are expensive and there are other usecases for
-connecting a contract with traditional software. One example is
-automatizing procedures like managing an auction, automatic bidding in
+as soon as an answer is available.
+%The issue of trustworthiness of the oracle arises because it is an entity outside of the blockchain, which njects information into an otherwise closed, trusted (or trustless) environment.
+%However, oracles are expensive and 
+There are other usecases for connecting a contract with traditional software. One example is
+automating procedures like managing an auction,  bidding in
 an auction, optimizing fees, or initiating delivery of goods to a
@@
 Current blockchains mostly provide RPC interfaces, 
-such as the Ethereum JSON-RPC API and the Tezos RPC API, but they
+such as the Ethereum JSON-RPC API \cite{ethereum-rpc} and the Tezos RPC API \cite{tezos-whitepaper}, but they
 require cumbersome manipulation of string data in JSON format and do
@@
 is deployed on the blockchain as a smart contract.
-% Once the contract is deployed, the
-% auction is open for bidding, but it should be closed after 48 hours. Such a timeout is a typical task for an oracle. Rather than
-% trusting a generic oracle, you prefer to roll your own mechanism that reliably closes the auction
-% after 48 hours have passed. So you want to write a program to do so. 
 Your bidding strategy may start at a certain amount and increase the bid until a
@@
 on external triggers.
-% Closing require scheduling the invocation of a
-% contract at a certain time.
 Bidding requires watching the current highest bid of the contract and
@@
 our particular example, the auction may fail with signaling the message
-\lstinline/"closed"/ or \lstinline/"bid to low"/. Our
+\lstinline/"closed"/ or \lstinline/"bid too low"/. Our
 code ignores this message for simplicity.
 
-This code is idealized in several respects. Originating or running a contract
-requires to propose a fee to the blockchain, which may or may not be
+This code is idealized in several respects. Originating or running a contract requires proposing a fee to the blockchain, which may or may not be
 accepted.
@@
 \end{definition}
+
+The execution model envisions off-chain programs interacting with smart contracts on the blockchain.
+The programs are defined using expression scripts, as shown in Figure~\ref{fig:syntax-expressions}.
+The off-chain scripts run on behalf of a single entity.
 
@@
 %\begin{definition}%[Contractor]
-A \emph{contractor} manages a smart contract. Contractors are
+A \emph{contractor} manages a single smart contract. Contractors are
 represented by a partial map $\CONTRACTORS : \TPUH \partialto
@@
       \CHECKINIT (\CODE, \STRING) \\
-      % \OPH = \GENERATEOPH(\PUK, \CODE, \STRING, \NTEZ, \MTEZ, \TIME)
-      % \\
       \OPH = \GENERATEOPH(\OP, \TIME) \\
-      \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ }{ [\EC\OP :: \EXPRS,
+      \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ }{ {[\EC\OP :: \EXPRS,
       \ACCOUNTS
-      ] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \to \\
-      [\EC{\OPH} :: \EXPRS, \ACCOUNTS] \| [\OPH \mapsto \Angle{\OP,
-        \TIME, \STATUSPENDING} ::\PENDING,
-      \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME] }
+      ] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]}    
+       \SystemTrans 
+      {[\EC{\OPH} :: \EXPRS, \ACCOUNTS] \| [\OPH \mapsto \Angle{\OP,
+        \TIME, \STATUSPENDING} ::\PENDING,} \\ {
+      \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME] }}
 
@@
   }{
-    [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING} :: \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
-    \BlockTrans \\
-     [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING, \UPDATESUCC
-      (\MANAGERS, \PUK, \NTEZ, \MTEZ),\\ \PUH \mapsto  \Angle{\CODE, \TIME, \NTEZ, \STRING} :: \CONTRACTORS, \TIME+1]
+    {[\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING} :: \PENDING, \MANAGERS, \CONTRACTORS, \TIME]} \BlockTrans    
+     {[\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING,} \\ { \UPDATESUCC
+      (\MANAGERS, \PUK, \NTEZ, \MTEZ),} 
+     {\PUH \mapsto  \Angle{\CODE, \TIME, \NTEZ, \STRING} :: \CONTRACTORS, \TIME+1]}
   }
@@
     \PUH = \GENERATEHASH (\CODE, \tilde\TIME)
-    % \CONTRACTORS (\PUH) =  \Angle{\CODE, \tilde\TIME, \NTEZ', \STRING'}
 }{
@@
 contract. These reductions force the local node to obtain information
-from the blockchain. The cast succeeds \TirName{Contract-Yes} on \PUH, if there is a
+from the blockchain. The cast succeeds on \PUH\ (`CONTRACT-YES'), if there is a
 contractor for \PUH\ such that the stored code has the parameter type
-expected by the cast. The cast fails \TirName{Contract-No}, if \PUH\
+expected by the cast. The cast fails (`CONTRACT-NO'), if \PUH\
 is invalid or if the types do not match.
@@
 \label{sec:properties}
-
+Having defined our execution model, we proceed to prove properties of the combined systems that ensure type-safe interaction between programs and the blockchain.
 \subsection{Properties of blockchain state transitions}
-
-Running a program that starts with valid references to accounts,
-operations, and contracts does not get corrupted by a transition.
+One interesting property we wish to prove is that the execution of a program that starts with valid references to accounts, operations, and contracts is not corrupted by a transition.
 \begin{proposition}
@@
  \item\label{item:6} invariant for contractors:
-   for all $\PUH \in \DOM (\CONTRACTORS)$,
+   for all $\PUH \in \DOM (\CONTRACTORS)$, \\
     $\CONTRACTORS (\PUH)$ = $\Angle{ \CODE, \tilde\TIME, \BAL, \STORAGE}$
@@
 sources and the blockchain network. A blockchain oracle is used to
-provide external data to smart contracts. Several researches have been
-done to provide oracle solutions for blockchain. Adler et al
+provide external data to smart contracts. There has been extensive research on providing oracle solutions for blockchain.  Adler et al
 \cite{blockchain-oracles} propose a framework to explain blockchain
@@
 provide developers with a guide for incorporating oracles into
-blockchain-based applications. Practically, the decentralized oracle
-network Chainlink \cite{chainlink-whitepaper} is being developed to
-provide reliable, tamper-proof input for smart contracts on any
-blockchain. For a specific application, a system called Town Crier
-\cite{town-crier} provides an authenticated data feed, sourced from
-HTTPS-enabled data websites, for smart contracts on Ethereum. George
-and Lesaege \cite{oracle-real-value} construct an oracle that can
-estimate the value of a real quantity, such as $R$.  
-For application to prediction markets, there are Truthcoin system
-\cite{truthcoin-whitepaper} and Astraea, a trustless decentralized
-oracle \cite{astraea}.
-
-The main problems with using a blockchain oracle are the untrusted
+blockchain-based applications. The main problems with using a blockchain oracle are the untrusted
 data provided maliciously or inaccurately \cite{trustworthy}. Ma at el
@@
 \cite{reliablity-oracles} provide a framework for performing
-reliability analysis of various blockchain oracle platforms. Closely
-following our work, Nielsen and Spitters \cite{interact-coq} present a
-model-executable specification of smart-contract execution in
-Coq. Their formalizations target Ethereum and Tezos.
+reliability analysis of various blockchain oracle platforms.
+
+%Practically, the decentralized oracle network Chainlink \cite{chainlink-whitepaper} is being developed to provide reliable, tamper-proof input for smart contracts on any blockchain.
+%For a specific application, a system called Town Crier \cite{town-crier} provides an authenticated data feed, sourced from HTTPS-enabled data websites, for smart contracts on Ethereum.
+George and Lesaege \cite{oracle-real-value} construct an oracle that can estimate the value of a real quantity, such as $R$.
+For application to prediction markets, there are Truthcoin system \cite{truthcoin-whitepaper} and Astraea, a trustless decentralized oracle \cite{astraea}.
+
+Current blockchains such as Ethereum \cite{eth-whitepaper} and Tezos \cite{tezos-whitepaper} often offer RPC APIs and use loosely structured data, such as a JSON-based format that is difficult for a programmatic program to handle.
+As a result, there is increasing work to provide better programmatic interfaces to blockchains.
+Web3.js \cite{web3.js} provides an Ethereum JavaScript API and offers Java Script users a convenient interface to interact with the Etherum blockchain.
+Later, Web3.py \cite{web3.py}, derived from Web3.js, is developed to provide a Python library for interacting with Ethereum.
+Our typed API not only supports for programmatic programs, but also provides verifiable interaction with the Tezos smart contract platform.
+% Closely following our work, Nielsen and Spitters \cite{interact-coq} present a model-executable specification of smart-contract execution in Coq. Their formalizations target Ethereum and Tezos.
 
@@
 blockchain programming and concurrent programs.
+The next step will be to formalize the typing-related results.
+The formalization could connect with the Mi-Cho-Coq  formalization of Michelson contracts \cite{DBLP:conf/fm/BernardoCHPT19}.
+In the end, we would like to state and prove properties of a system that contains OCaml code (multi-threaded or distributed) connected to Michelson contracts on the Tezos blockchain via the typed API.
 

### 2021-08-25 papers/execution-model/APLAS 2021/paper.tex
Add files via upload

@@
 request and a callback with an oracle. The oracle invokes the callback
-as soon as an answer is available. The issue of trustworthiness of the
-oracle arises because it is an entity outside of the blockchain, which
-injects information into an otherwise closed, trusted (or trustless)
-environment.
-
-However, oracles are expensive and there are other usecases for
-connecting a contract with traditional software. One example is
-automatizing procedures like managing an auction, automatic bidding in
+as soon as an answer is available.
+%The issue of trustworthiness of the oracle arises because it is an entity outside of the blockchain, which njects information into an otherwise closed, trusted (or trustless) environment.
+%However, oracles are expensive and
+
+There are other usecases for connecting a contract with traditional software. One example is
+automating procedures like managing an auction,  bidding in
 an auction, optimizing fees, or initiating delivery of goods to a

### 2021-08-25 papers/execution-model/APLAS 2021/paper.tex
Add files via upload

@@
 %The issue of trustworthiness of the oracle arises because it is an entity outside of the blockchain, which njects information into an otherwise closed, trusted (or trustless) environment.
-%However, oracles are expensive and
-
-There are other usecases for connecting a contract with traditional software. One example is
+
+However, oracles are expensive and there are other usecases for connecting a contract with traditional software. One example is
 automating procedures like managing an auction,  bidding in
@@
 \end{definition}
-
-The execution model envisions off-chain programs interacting with smart contracts on the blockchain.
-The programs are defined using expression scripts, as shown in Figure~\ref{fig:syntax-expressions}.
-The off-chain scripts run on behalf of a single entity.
 
@@
 Pattern matching is the only means to decompose values, cf.\ \PATTERN.
+The execution model envisions off-chain programs interacting with smart contracts on the blockchain.
+The programs are defined using expression scripts.
+The off-chain scripts run on behalf of a single entity.
 
@@
 a type of addresses $\TADDR$. $\TCONTRACT\ \TYPE\ \TYPEU$ is the type of
-a contract with parameter type $\TYPE$ and storage type $\TYPEU$. $\CODE\ \TYPE\ \TYPEU$
+a contract with parameter type $\TYPE$ and storage type $\TYPEU$. $\TCODE\ \TYPE\ \TYPEU$
 indicates a Michelson program with parameter type $\TYPE$ and storage
@@
 represented by a partial map $\CONTRACTORS : \TPUH \partialto
-\TCODE \times \TIME  \times \TBAL \times  \TSTORAGE$. If $\CONTRACTORS (\PUH) = \langle
-\CODE, \TIME, \BAL, \STORAGE \rangle $ is defined, then $\PUH$ is the
+\TCODE \times \TIME  \times \TBAL \times  \TSTORAGE$. If $\CONTRACTORS (\PUH)$ = $\langle
+\CODE,$ $\TIME, \BAL, \STORAGE \rangle $ is defined, then $\PUH$ is the
 public hash of a contract,
@@
     { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
-      [\PENDING, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
+      [\PENDING, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans 
    { [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \|
      [ \OPH \mapsto \Angle{\OP, \TIME, \STATUSPENDING}
-     ::\PENDING,
+     ::\PENDING,} \\ {
      \UPDATECOU(\MANAGERS, \PUK, \TRUE),
@@
   \inferrule[Node-Reject]{
-    \NEG\ \CHECKBAL (\BLOCKCHAIN.\MANAGERS, \OP.\PUK, \OP.\NTEZ, \OP.\MTEZ) \\
+    \NEG\ \CHECKBAL (\BLOCKCHAIN.\MANAGERS, \OP.\PUK, \OP.\NTEZ, \OP.\MTEZ) 
     }{
@@
       \CONTRACTORS, \TIME]}
-    \BlockTrans \\
+    \BlockTrans 
     { 
       [\OPH \mapsto \Angle{\OP, \hat \TIME, \STATUSTIMEOUT}
-     :: \PENDING,  \UPDATECOU(\MANAGERS, \OP.\PUK, \FALSE),
+     :: \PENDING,} \\ {\UPDATECOU(\MANAGERS, \OP.\PUK, \FALSE),
       \CONTRACTORS, \TIME]}
@@
 \begin{itemize}
-\item if $\OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ$, then
-  $\PUK, \PUK' \in \DOM (\MANAGERS)$;
+\item if $\OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ$, then \\
+  $\PUK, \PUK'$ $\in$ $\DOM (\MANAGERS)$;
 \item if $\OP = \TRANSFER[\PARAMETER]\NTEZ\PUK\PUH\MTEZ$, then
   \begin{itemize}
-  \item $\PUK \in \DOM (\MANAGERS)$ and $\PUH\in\DOM (\CONTRACTORS)$,
+  \item $\PUK \in \DOM (\MANAGERS)$ and $\PUH\in$$\DOM (\CONTRACTORS)$,
   \item $\JTypeValue\PARAMETER{ \TYPE_p}$ where $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$;

### 2021-08-26 papers/execution-model/APLAS 2021/paper.tex
Add files via upload
Small revision

@@
 
-However, oracles are expensive and there are other usecases for connecting a contract with traditional software. One example is
+%However, oracles are expensive and 
+There are other usecases for connecting a contract with traditional software. One example is
 automating procedures like managing an auction,  bidding in
@@
 themselves, we rather consider them as black boxes and probe their
-observable behavior. Tezos' smart contract language Michelson and its
+observable behavior. Tezos's smart contract language Michelson and its
 properties have been formalized elsewhere \cite{DBLP:conf/fm/BernardoCHPT19}.
@@
   \begin{itemize}
-  \item $\PUK \in \DOM (\MANAGERS)$ and $\PUH\in$$\DOM (\CONTRACTORS)$,
+  \item $\PUK \in \DOM (\MANAGERS)$ and $\PUH \in\DOM (\CONTRACTORS)$,
   \item $\JTypeValue\PARAMETER{ \TYPE_p}$ where $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$;
   \end{itemize}
-\item if $\OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ$ and $\STATUS =
-  \STATUSINCLUDED\ \TIME'$, then
+\item if $\OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ$ and $\STATUS = \STATUSINCLUDED\ \TIME'$, then
   \begin{itemize}
@@
 overcome this limitation by providing a bridge between the outside
-sources and the blockchain network. A blockchain oracle is used to
-provide external data to smart contracts. There has been extensive research on providing oracle solutions for blockchain.  Adler et al
+sources and the blockchain network.
+A blockchain oracle is used to provide external data for smart contracts.
+When the external data is available, an oracle invokes a smart contract with that information.
+The invocation can conveniently be made through a programmatic interface.
+There has been extensive research on providing oracle solutions for blockchain.
+Adler et al
 \cite{blockchain-oracles} propose a framework to explain blockchain

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/create_test.sh
michelson interpreter: upload BNF grammar & test contracts

@@ -1,0 +1,3 @@
+bnfc --ocaml-menhir -m -o test test.cf
+make -C test
+#./test_parser.sh

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/create_test_haskell.sh

@@ -1,0 +1,2 @@
+bnfc -d -m -o test_haskell test.cf && make -C test_haskell
+#./test_parser.sh

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/haskell_backend/Michelson/Abs.hs

@@ -1,0 +1,207 @@
+-- Haskell data types for the abstract syntax.
+-- Generated by the BNF converter.
+
+{-# LANGUAGE GeneralizedNewtypeDeriving #-}
+
+-- | The abstract syntax of language michelson.
+
+module Michelson.Abs where
+
+import Prelude (String)
+import qualified Prelude as C (Eq, Ord, Show, Read)
+import qualified Data.String
+
+data Prog = Code Instr [Instr]
+  deriving (C.Eq, C.Ord, C.Show, C.Read)
+
+data PairSeq = DPairSeq1 Data Data | DPairSeq2 Data PairSeq
+  deriving (C.Eq, C.Ord, C.Show, C.Read)
+
+data MapSeq = DMapSeq1 Data Data | DMapSeq2 Data Data MapSeq
+  deriving (C.Eq, C.Ord, C.Show, C.Read)
+
+data Data
+    = DInt Int
+    | DStr Str
+    | DByte Hex
+    | DUnit
+    | DTrue
+    | DFalse
+    | DPair2 PairSeq
+    | DLeft Data
+    | DRight Data
+    | DSome Data
+    | DNone
+    | DBlock [Data]
+    | DMap MapSeq
+    | DInstr Instr
+  deriving (C.Eq, C.Ord, C.Show, C.Read)
+
+data Instr
+    = IBLOCK [Instr]
+    | IDROP
+    | IDROP_N Nat
+    | IDUP
+    | IDUP_N Nat
+    | ISWAP
+    | IDIG_N Nat
+    | IDUG_N Nat
+    | IPUSH Typ Data
+    | ISOME
+    | INONE Typ
+    | IUNIT
+    | INEVER
+    | IIF_NONE [Instr] [Instr]
+    | IPAIR
+    | IPAIR_N Nat
+    | ICAR
+    | ICDR
+    | IUNPAIR
+    | IUNPAIR_N Nat
+    | ILEFT Typ
+    | IRIGHT Typ
+    | IIF_LEFT [Instr] [Instr]
+    | INIL Typ
+    | ICONS
+    | IIF_CONS [Instr] [Instr]
+    | ISIZE
+    | IEMPTY_SET CTyp
+    | IEMPTY_MAP CTyp Typ
+    | IEMPTY_BIG_MAP CTyp Typ
+    | IMAP [Instr]
+    | IITER [Instr]
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/haskell_backend/Michelson/ErrM.hs

@@ -1,0 +1,89 @@
+{-# LANGUAGE CPP #-}
+
+#if __GLASGOW_HASKELL__ >= 708
+---------------------------------------------------------------------------
+-- Pattern synonyms exist since ghc 7.8.
+
+-- | BNF Converter: Error Monad.
+--
+-- Module for backwards compatibility.
+--
+-- The generated parser now uses @'Either' String@ as error monad.
+-- This module defines a type synonym 'Err' and pattern synonyms
+-- 'Bad' and 'Ok' for 'Left' and 'Right'.
+
+{-# LANGUAGE PatternSynonyms #-}
+{-# LANGUAGE FlexibleInstances #-}
+
+module Michelson.ErrM where
+
+import Prelude             (id, const, Either(..), String)
+
+import Control.Monad       (MonadPlus(..))
+import Control.Applicative (Alternative(..))
+#if __GLASGOW_HASKELL__ >= 808
+import Control.Monad       (MonadFail(..))
+#endif
+
+-- | Error monad with 'String' error messages.
+type Err = Either String
+
+pattern Bad msg = Left msg
+pattern Ok  a   = Right a
+
+#if __GLASGOW_HASKELL__ >= 808
+instance MonadFail Err where
+  fail = Bad
+#endif
+
+instance Alternative Err where
+  empty           = Left "Err.empty"
+  (<|>) Left{}    = id
+  (<|>) x@Right{} = const x
+
+instance MonadPlus Err where
+  mzero = empty
+  mplus = (<|>)
+
+#else
+---------------------------------------------------------------------------
+-- ghc 7.6 and before: use old definition as data type.
+
+-- | BNF Converter: Error Monad
+
+-- Copyright (C) 2004  Author:  Aarne Ranta
+-- This file comes with NO WARRANTY and may be used FOR ANY PURPOSE.
+
+module Michelson.ErrM where
+
+-- the Error monad: like Maybe type with error msgs
+
+import Control.Applicative (Applicative(..), Alternative(..))
+import Control.Monad       (MonadPlus(..), liftM)
+
+data Err a = Ok a | Bad String
+  deriving (Read, Show, Eq, Ord)
+
+instance Monad Err where
+  return      = Ok
+  Ok a  >>= f = f a
+  Bad s >>= _ = Bad s
+
+instance Applicative Err where
+  pure = Ok
+  (Bad s) <*> _ = Bad s
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/haskell_backend/Michelson/Lex.hs

@@ -1,0 +1,612 @@
+{-# OPTIONS_GHC -fno-warn-unused-binds -fno-warn-missing-signatures #-}
+{-# LANGUAGE CPP,MagicHash #-}
+{-# LINE 3 "Michelson/Lex.x" #-}
+
+{-# OPTIONS -fno-warn-incomplete-patterns #-}
+{-# OPTIONS_GHC -w #-}
+
+{-# LANGUAGE PatternSynonyms #-}
+
+module Michelson.Lex where
+
+import Prelude
+
+import qualified Data.Bits
+import Data.Char     (ord)
+import Data.Function (on)
+import Data.Word     (Word8)
+
+#if __GLASGOW_HASKELL__ >= 603
+#include "ghcconfig.h"
+#elif defined(__GLASGOW_HASKELL__)
+#include "config.h"
+#endif
+#if __GLASGOW_HASKELL__ >= 503
+import Data.Array
+import Data.Array.Base (unsafeAt)
+#else
+import Array
+#endif
+#if __GLASGOW_HASKELL__ >= 503
+import GHC.Exts
+#else
+import GlaExts
+#endif
+alex_tab_size :: Int
+alex_tab_size = 8
+alex_base :: AlexAddr
+alex_base = AlexA#
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/haskell_backend/Michelson/Par.hs

@@ -1,0 +1,2377 @@
+{-# OPTIONS_GHC -w #-}
+{-# OPTIONS -XMagicHash -XBangPatterns -XTypeSynonymInstances -XFlexibleInstances -cpp #-}
+#if __GLASGOW_HASKELL__ >= 710
+{-# OPTIONS_GHC -XPartialTypeSignatures #-}
+#endif
+{-# OPTIONS_GHC -fno-warn-incomplete-patterns -fno-warn-overlapping-patterns #-}
+{-# LANGUAGE PatternSynonyms #-}
+
+module Michelson.Par
+  ( happyError
+  , myLexer
+  , pProg
+  ) where
+
+import Prelude
+
+import qualified Michelson.Abs
+import Michelson.Lex
+import qualified Data.Array as Happy_Data_Array
+import qualified Data.Bits as Bits
+import qualified GHC.Exts as Happy_GHC_Exts
+import Control.Applicative(Applicative(..))
+import Control.Monad (ap)
+
+-- parser produced by Happy Version 1.19.11
+
+newtype HappyAbsSyn  = HappyAbsSyn HappyAny
+#if __GLASGOW_HASKELL__ >= 607
+type HappyAny = Happy_GHC_Exts.Any
+#else
+type HappyAny = forall a . a
+#endif
+newtype HappyWrap4 = HappyWrap4 (Michelson.Abs.Int)
+happyIn4 :: (Michelson.Abs.Int) -> (HappyAbsSyn )
+happyIn4 x = Happy_GHC_Exts.unsafeCoerce# (HappyWrap4 x)
+{-# INLINE happyIn4 #-}
+happyOut4 :: (HappyAbsSyn ) -> HappyWrap4
+happyOut4 x = Happy_GHC_Exts.unsafeCoerce# x
+{-# INLINE happyOut4 #-}
+newtype HappyWrap5 = HappyWrap5 (Michelson.Abs.Nat)
+happyIn5 :: (Michelson.Abs.Nat) -> (HappyAbsSyn )
+happyIn5 x = Happy_GHC_Exts.unsafeCoerce# (HappyWrap5 x)
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/haskell_backend/Michelson/Print.hs

@@ -1,0 +1,348 @@
+{-# LANGUAGE CPP #-}
+{-# LANGUAGE FlexibleInstances #-}
+{-# LANGUAGE LambdaCase #-}
+#if __GLASGOW_HASKELL__ <= 708
+{-# LANGUAGE OverlappingInstances #-}
+#endif
+
+{-# OPTIONS_GHC -fno-warn-incomplete-patterns #-}
+
+-- | Pretty-printer for Michelson.
+--   Generated by the BNF converter.
+
+module Michelson.Print where
+
+import Prelude
+  ( ($), (.)
+  , Bool(..), (==), (<)
+  , Int, Integer, Double, (+), (-), (*)
+  , String, (++)
+  , ShowS, showChar, showString
+  , all, elem, foldr, id, map, null, replicate, shows, span
+  )
+import Data.Char ( Char, isSpace )
+import qualified Michelson.Abs
+
+-- | The top-level printing method.
+
+printTree :: Print a => a -> String
+printTree = render . prt 0
+
+type Doc = [ShowS] -> [ShowS]
+
+doc :: ShowS -> Doc
+doc = (:)
+
+render :: Doc -> String
+render d = rend 0 False (map ($ "") $ d []) ""
+  where
+  rend
+    :: Int        -- ^ Indentation level.
+    -> Bool       -- ^ Pending indentation to be output before next character?
+    -> [String]
+    -> ShowS
+  rend i p = \case
+      "["      :ts -> char '[' . rend i False ts
+      "("      :ts -> char '(' . rend i False ts
+      "{"      :ts -> onNewLine i     p . showChar   '{'  . new (i+1) ts
+      "}" : ";":ts -> onNewLine (i-1) p . showString "};" . new (i-1) ts
+      "}"      :ts -> onNewLine (i-1) p . showChar   '}'  . new (i-1) ts
+      [";"]        -> char ';'
+      ";"      :ts -> char ';' . new i ts
+      t  : ts@(s:_) | closingOrPunctuation s
+                   -> pending . showString t . rend i False ts
+      t        :ts -> pending . space t      . rend i False ts
+      []           -> id
+    where
+    -- Output character after pending indentation.
+    char :: Char -> ShowS
+    char c = pending . showChar c
+
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/haskell_backend/Michelson/Skel.hs

@@ -1,0 +1,221 @@
+-- Haskell module generated by the BNF converter
+
+{-# OPTIONS_GHC -fno-warn-unused-matches #-}
+
+module Michelson.Skel where
+
+import Prelude (($), Either(..), String, (++), Show, show)
+import qualified Michelson.Abs
+
+type Err = Either String
+type Result = Err String
+
+failure :: Show a => a -> Result
+failure x = Left $ "Undefined case: " ++ show x
+
+transInt :: Michelson.Abs.Int -> Result
+transInt x = case x of
+  Michelson.Abs.Int string -> failure x
+
+transNat :: Michelson.Abs.Nat -> Result
+transNat x = case x of
+  Michelson.Abs.Nat string -> failure x
+
+transStr :: Michelson.Abs.Str -> Result
+transStr x = case x of
+  Michelson.Abs.Str string -> failure x
+
+transHex :: Michelson.Abs.Hex -> Result
+transHex x = case x of
+  Michelson.Abs.Hex string -> failure x
+
+transProg :: Michelson.Abs.Prog -> Result
+transProg x = case x of
+  Michelson.Abs.Code instr instrs -> failure x
+
+transPairSeq :: Michelson.Abs.PairSeq -> Result
+transPairSeq x = case x of
+  Michelson.Abs.DPairSeq1 data_1 data_2 -> failure x
+  Michelson.Abs.DPairSeq2 data_ pairseq -> failure x
+
+transMapSeq :: Michelson.Abs.MapSeq -> Result
+transMapSeq x = case x of
+  Michelson.Abs.DMapSeq1 data_1 data_2 -> failure x
+  Michelson.Abs.DMapSeq2 data_1 data_2 mapseq -> failure x
+
+transData :: Michelson.Abs.Data -> Result
+transData x = case x of
+  Michelson.Abs.DInt int -> failure x
+  Michelson.Abs.DStr str -> failure x
+  Michelson.Abs.DByte hex -> failure x
+  Michelson.Abs.DUnit -> failure x
+  Michelson.Abs.DTrue -> failure x
+  Michelson.Abs.DFalse -> failure x
+  Michelson.Abs.DPair2 pairseq -> failure x
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/haskell_backend/Michelson/Test.hs

@@ -1,0 +1,76 @@
+-- Program to test parser, automatically generated by BNF Converter.
+
+module Main where
+
+import Prelude
+  ( ($), (.)
+  , Either(..)
+  , Int, (>)
+  , String, (++), concat, unlines
+  , Show, show
+  , IO, (>>), (>>=), mapM_, putStrLn
+  , FilePath
+  , getContents, readFile
+  )
+import System.Environment ( getArgs )
+import System.Exit        ( exitFailure, exitSuccess )
+import Control.Monad      ( when )
+
+import Michelson.Abs   ()
+import Michelson.Lex   ( Token, mkPosToken )
+import Michelson.Par   ( pProg, myLexer )
+import Michelson.Print ( Print, printTree )
+import Michelson.Skel  ()
+
+type Err        = Either String
+type ParseFun a = [Token] -> Err a
+type Verbosity  = Int
+
+putStrV :: Verbosity -> String -> IO ()
+putStrV v s = when (v > 1) $ putStrLn s
+
+runFile :: (Print a, Show a) => Verbosity -> ParseFun a -> FilePath -> IO ()
+runFile v p f = putStrLn f >> readFile f >>= run v p
+
+run :: (Print a, Show a) => Verbosity -> ParseFun a -> String -> IO ()
+run v p s =
+  case p ts of
+    Left err -> do
+      putStrLn "\nParse              Failed...\n"
+      putStrV v "Tokens:"
+      mapM_ (putStrV v . showPosToken . mkPosToken) ts
+      putStrLn err
+      exitFailure
+    Right tree -> do
+      putStrLn "\nParse Successful!"
+      showTree v tree
+      exitSuccess
+  where
+  ts = myLexer s
+  showPosToken ((l,c),t) = concat [ show l, ":", show c, "\t", show t ]
+
+showTree :: (Show a, Print a) => Int -> a -> IO ()
+showTree v tree = do
+  putStrV v $ "\n[Abstract Syntax]\n\n" ++ show tree
+  putStrV v $ "\n[Linearized tree]\n\n" ++ printTree tree
+
+usage :: IO ()
+usage = do
+  putStrLn $ unlines
+    [ "usage: Call with one of the following argument combinations:"
+    , "  --help          Display this help message."
+    , "  (no arguments)  Parse stdin verbosely."
+    , "  (files)         Parse content of files verbosely."
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_folder.sh

@@ -1,0 +1,7 @@
+search_dir="../test/test_files/tezos-master-tests_python-contracts_alpha/tests_python/contracts_alpha/opcodes"
+for entry in "$search_dir"/*
+do
+  echo "$entry"
+  ./ocaml_backend/TestMichelson $entry
+  echo
+done

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_haskell/Test/Abs.hs

@@ -1,0 +1,31 @@
+-- Haskell data types for the abstract syntax.
+-- Generated by the BNF converter.
+
+{-# LANGUAGE GeneralizedNewtypeDeriving #-}
+
+-- | The abstract syntax of language test.
+
+module Test.Abs where
+
+import Prelude (String)
+import qualified Prelude as C (Eq, Ord, Show, Read)
+import qualified Data.String
+
+data Prog = Code Instr [Instr]
+  deriving (C.Eq, C.Ord, C.Show, C.Read)
+
+data Instr = IPUSH CType Data | IADD
+  deriving (C.Eq, C.Ord, C.Show, C.Read)
+
+data Data = DInt Int
+  deriving (C.Eq, C.Ord, C.Show, C.Read)
+
+data CType = CInt
+  deriving (C.Eq, C.Ord, C.Show, C.Read)
+
+newtype Nat = Nat String
+  deriving (C.Eq, C.Ord, C.Show, C.Read, Data.String.IsString)
+
+newtype Int = Int String
+  deriving (C.Eq, C.Ord, C.Show, C.Read, Data.String.IsString)
+

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_haskell/Test/ErrM.hs

@@ -1,0 +1,89 @@
+{-# LANGUAGE CPP #-}
+
+#if __GLASGOW_HASKELL__ >= 708
+---------------------------------------------------------------------------
+-- Pattern synonyms exist since ghc 7.8.
+
+-- | BNF Converter: Error Monad.
+--
+-- Module for backwards compatibility.
+--
+-- The generated parser now uses @'Either' String@ as error monad.
+-- This module defines a type synonym 'Err' and pattern synonyms
+-- 'Bad' and 'Ok' for 'Left' and 'Right'.
+
+{-# LANGUAGE PatternSynonyms #-}
+{-# LANGUAGE FlexibleInstances #-}
+
+module Test.ErrM where
+
+import Prelude             (id, const, Either(..), String)
+
+import Control.Monad       (MonadPlus(..))
+import Control.Applicative (Alternative(..))
+#if __GLASGOW_HASKELL__ >= 808
+import Control.Monad       (MonadFail(..))
+#endif
+
+-- | Error monad with 'String' error messages.
+type Err = Either String
+
+pattern Bad msg = Left msg
+pattern Ok  a   = Right a
+
+#if __GLASGOW_HASKELL__ >= 808
+instance MonadFail Err where
+  fail = Bad
+#endif
+
+instance Alternative Err where
+  empty           = Left "Err.empty"
+  (<|>) Left{}    = id
+  (<|>) x@Right{} = const x
+
+instance MonadPlus Err where
+  mzero = empty
+  mplus = (<|>)
+
+#else
+---------------------------------------------------------------------------
+-- ghc 7.6 and before: use old definition as data type.
+
+-- | BNF Converter: Error Monad
+
+-- Copyright (C) 2004  Author:  Aarne Ranta
+-- This file comes with NO WARRANTY and may be used FOR ANY PURPOSE.
+
+module Test.ErrM where
+
+-- the Error monad: like Maybe type with error msgs
+
+import Control.Applicative (Applicative(..), Alternative(..))
+import Control.Monad       (MonadPlus(..), liftM)
+
+data Err a = Ok a | Bad String
+  deriving (Read, Show, Eq, Ord)
+
+instance Monad Err where
+  return      = Ok
+  Ok a  >>= f = f a
+  Bad s >>= _ = Bad s
+
+instance Applicative Err where
+  pure = Ok
+  (Bad s) <*> _ = Bad s
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_haskell/Test/Lex.hs

@@ -1,0 +1,504 @@
+{-# OPTIONS_GHC -fno-warn-unused-binds -fno-warn-missing-signatures #-}
+{-# LANGUAGE CPP,MagicHash #-}
+{-# LINE 3 "Test/Lex.x" #-}
+
+{-# OPTIONS -fno-warn-incomplete-patterns #-}
+{-# OPTIONS_GHC -w #-}
+
+{-# LANGUAGE PatternSynonyms #-}
+
+module Test.Lex where
+
+import Prelude
+
+import qualified Data.Bits
+import Data.Char     (ord)
+import Data.Function (on)
+import Data.Word     (Word8)
+
+#if __GLASGOW_HASKELL__ >= 603
+#include "ghcconfig.h"
+#elif defined(__GLASGOW_HASKELL__)
+#include "config.h"
+#endif
+#if __GLASGOW_HASKELL__ >= 503
+import Data.Array
+import Data.Array.Base (unsafeAt)
+#else
+import Array
+#endif
+#if __GLASGOW_HASKELL__ >= 503
+import GHC.Exts
+#else
+import GlaExts
+#endif
+alex_tab_size :: Int
+alex_tab_size = 8
+alex_base :: AlexAddr
+alex_base = AlexA#
+  "\xf8\xff\xff\xff\xf3\xff\xff\xff\xd6\xff\xff\xff\x07\x00\x00\x00\x00\x00\x00\x00\xe9\xff\xff\xff\x8c\x00\x00\x00\x9f\x00\x00\x00"#
+
+alex_table :: AlexAddr
+alex_table = AlexA#
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_haskell/Test/Par.hs

@@ -1,0 +1,821 @@
+{-# OPTIONS_GHC -w #-}
+{-# OPTIONS -XMagicHash -XBangPatterns -XTypeSynonymInstances -XFlexibleInstances -cpp #-}
+#if __GLASGOW_HASKELL__ >= 710
+{-# OPTIONS_GHC -XPartialTypeSignatures #-}
+#endif
+{-# OPTIONS_GHC -fno-warn-incomplete-patterns -fno-warn-overlapping-patterns #-}
+{-# LANGUAGE PatternSynonyms #-}
+
+module Test.Par
+  ( happyError
+  , myLexer
+  , pProg
+  ) where
+
+import Prelude
+
+import qualified Test.Abs
+import Test.Lex
+import qualified Data.Array as Happy_Data_Array
+import qualified Data.Bits as Bits
+import qualified GHC.Exts as Happy_GHC_Exts
+import Control.Applicative(Applicative(..))
+import Control.Monad (ap)
+
+-- parser produced by Happy Version 1.19.11
+
+newtype HappyAbsSyn  = HappyAbsSyn HappyAny
+#if __GLASGOW_HASKELL__ >= 607
+type HappyAny = Happy_GHC_Exts.Any
+#else
+type HappyAny = forall a . a
+#endif
+newtype HappyWrap4 = HappyWrap4 (Test.Abs.Nat)
+happyIn4 :: (Test.Abs.Nat) -> (HappyAbsSyn )
+happyIn4 x = Happy_GHC_Exts.unsafeCoerce# (HappyWrap4 x)
+{-# INLINE happyIn4 #-}
+happyOut4 :: (HappyAbsSyn ) -> HappyWrap4
+happyOut4 x = Happy_GHC_Exts.unsafeCoerce# x
+{-# INLINE happyOut4 #-}
+newtype HappyWrap5 = HappyWrap5 (Test.Abs.Int)
+happyIn5 :: (Test.Abs.Int) -> (HappyAbsSyn )
+happyIn5 x = Happy_GHC_Exts.unsafeCoerce# (HappyWrap5 x)
+{-# INLINE happyIn5 #-}
+happyOut5 :: (HappyAbsSyn ) -> HappyWrap5
+happyOut5 x = Happy_GHC_Exts.unsafeCoerce# x
+{-# INLINE happyOut5 #-}
+newtype HappyWrap6 = HappyWrap6 (Test.Abs.Prog)
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_haskell/Test/Print.hs

@@ -1,0 +1,166 @@
+{-# LANGUAGE CPP #-}
+{-# LANGUAGE FlexibleInstances #-}
+{-# LANGUAGE LambdaCase #-}
+#if __GLASGOW_HASKELL__ <= 708
+{-# LANGUAGE OverlappingInstances #-}
+#endif
+
+{-# OPTIONS_GHC -fno-warn-incomplete-patterns #-}
+
+-- | Pretty-printer for Test.
+--   Generated by the BNF converter.
+
+module Test.Print where
+
+import Prelude
+  ( ($), (.)
+  , Bool(..), (==), (<)
+  , Int, Integer, Double, (+), (-), (*)
+  , String, (++)
+  , ShowS, showChar, showString
+  , all, elem, foldr, id, map, null, replicate, shows, span
+  )
+import Data.Char ( Char, isSpace )
+import qualified Test.Abs
+
+-- | The top-level printing method.
+
+printTree :: Print a => a -> String
+printTree = render . prt 0
+
+type Doc = [ShowS] -> [ShowS]
+
+doc :: ShowS -> Doc
+doc = (:)
+
+render :: Doc -> String
+render d = rend 0 False (map ($ "") $ d []) ""
+  where
+  rend
+    :: Int        -- ^ Indentation level.
+    -> Bool       -- ^ Pending indentation to be output before next character?
+    -> [String]
+    -> ShowS
+  rend i p = \case
+      "["      :ts -> char '[' . rend i False ts
+      "("      :ts -> char '(' . rend i False ts
+      "{"      :ts -> onNewLine i     p . showChar   '{'  . new (i+1) ts
+      "}" : ";":ts -> onNewLine (i-1) p . showString "};" . new (i-1) ts
+      "}"      :ts -> onNewLine (i-1) p . showChar   '}'  . new (i-1) ts
+      [";"]        -> char ';'
+      ";"      :ts -> char ';' . new i ts
+      t  : ts@(s:_) | closingOrPunctuation s
+                   -> pending . showString t . rend i False ts
+      t        :ts -> pending . space t      . rend i False ts
+      []           -> id
+    where
+    -- Output character after pending indentation.
+    char :: Char -> ShowS
+    char c = pending . showChar c
+
+    -- Output pending indentation.
+    pending :: ShowS
+    pending = if p then indent i else id
+
+  -- Indentation (spaces) for given indentation level.
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_haskell/Test/Skel.hs

@@ -1,0 +1,39 @@
+-- Haskell module generated by the BNF converter
+
+{-# OPTIONS_GHC -fno-warn-unused-matches #-}
+
+module Test.Skel where
+
+import Prelude (($), Either(..), String, (++), Show, show)
+import qualified Test.Abs
+
+type Err = Either String
+type Result = Err String
+
+failure :: Show a => a -> Result
+failure x = Left $ "Undefined case: " ++ show x
+
+transNat :: Test.Abs.Nat -> Result
+transNat x = case x of
+  Test.Abs.Nat string -> failure x
+
+transInt :: Test.Abs.Int -> Result
+transInt x = case x of
+  Test.Abs.Int string -> failure x
+
+transProg :: Test.Abs.Prog -> Result
+transProg x = case x of
+  Test.Abs.Code instr instrs -> failure x
+
+transInstr :: Test.Abs.Instr -> Result
+transInstr x = case x of
+  Test.Abs.IPUSH ctype data_ -> failure x
+  Test.Abs.IADD -> failure x
+
+transData :: Test.Abs.Data -> Result
+transData x = case x of
+  Test.Abs.DInt int -> failure x
+
+transCType :: Test.Abs.CType -> Result
+transCType x = case x of
+  Test.Abs.CInt -> failure x

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_haskell/Test/Test.hs

@@ -1,0 +1,76 @@
+-- Program to test parser, automatically generated by BNF Converter.
+
+module Main where
+
+import Prelude
+  ( ($), (.)
+  , Either(..)
+  , Int, (>)
+  , String, (++), concat, unlines
+  , Show, show
+  , IO, (>>), (>>=), mapM_, putStrLn
+  , FilePath
+  , getContents, readFile
+  )
+import System.Environment ( getArgs )
+import System.Exit        ( exitFailure, exitSuccess )
+import Control.Monad      ( when )
+
+import Test.Abs   ()
+import Test.Lex   ( Token, mkPosToken )
+import Test.Par   ( pProg, myLexer )
+import Test.Print ( Print, printTree )
+import Test.Skel  ()
+
+type Err        = Either String
+type ParseFun a = [Token] -> Err a
+type Verbosity  = Int
+
+putStrV :: Verbosity -> String -> IO ()
+putStrV v s = when (v > 1) $ putStrLn s
+
+runFile :: (Print a, Show a) => Verbosity -> ParseFun a -> FilePath -> IO ()
+runFile v p f = putStrLn f >> readFile f >>= run v p
+
+run :: (Print a, Show a) => Verbosity -> ParseFun a -> String -> IO ()
+run v p s =
+  case p ts of
+    Left err -> do
+      putStrLn "\nParse              Failed...\n"
+      putStrV v "Tokens:"
+      mapM_ (putStrV v . showPosToken . mkPosToken) ts
+      putStrLn err
+      exitFailure
+    Right tree -> do
+      putStrLn "\nParse Successful!"
+      showTree v tree
+      exitSuccess
+  where
+  ts = myLexer s
+  showPosToken ((l,c),t) = concat [ show l, ":", show c, "\t", show t ]
+
+showTree :: (Show a, Print a) => Int -> a -> IO ()
+showTree v tree = do
+  putStrV v $ "\n[Abstract Syntax]\n\n" ++ show tree
+  putStrV v $ "\n[Linearized tree]\n\n" ++ printTree tree
+
+usage :: IO ()
+usage = do
+  putStrLn $ unlines
+    [ "usage: Call with one of the following argument combinations:"
+    , "  --help          Display this help message."
+    , "  (no arguments)  Parse stdin verbosely."
+    , "  (files)         Parse content of files verbosely."
+    , "  -s (files)      Silent mode. Parse content of files silently."
+    ]
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_haskell_parser.sh

@@ -1,0 +1,3 @@
+./haskell_backend/Michelson/Test test_contract.tz
+
+#echo "DROP; PUSH int -5; PUSH int 1;" | haskell_backend/Michelson/Test

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_parser.sh

@@ -1,0 +1,5 @@
+./ocaml_backend/TestMichelson test_contract.tz
+
+#echo "DROP; PUSH int -5; PUSH int 1;" |ocaml_backend/TestMichelson
+
+

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_test.sh

@@ -1,0 +1,3 @@
+./test/TestTest test_contract.tz
+
+#echo "DROP; PUSH int -5; PUSH int 1;" | test/TestTest

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_test_haskell.sh

@@ -1,0 +1,3 @@
+./test_haskell/Test/Test test_contract.tz
+
+#echo "DROP; PUSH int -5; PUSH int 1;" | test_haskell/Test/Test

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/create_haskell_parser.sh
ML interpreter: remove unneeded files

@@ -1,3 +1,0 @@
-bnfc -d -m -o haskell_backend michelson.cf
-make -C haskell_backend
-#./test_parser.sh

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/create_parser.sh

@@ -1,3 +1,0 @@
-bnfc --ocaml-menhir -m -o ocaml_backend michelson.cf
-make -C ocaml_backend
-#./test_parser.sh

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/create_test.sh

@@ -1,3 +1,0 @@
-bnfc --ocaml-menhir -m -o test test.cf
-make -C test
-#./test_parser.sh

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/create_test_haskell.sh

@@ -1,2 +1,0 @@
-bnfc -d -m -o test_haskell test.cf && make -C test_haskell
-#./test_parser.sh

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/haskell_backend/Michelson/Abs.hs

@@ -1,207 +1,0 @@
--- Haskell data types for the abstract syntax.
--- Generated by the BNF converter.
-
-{-# LANGUAGE GeneralizedNewtypeDeriving #-}
-
--- | The abstract syntax of language michelson.
-
-module Michelson.Abs where
-
-import Prelude (String)
-import qualified Prelude as C (Eq, Ord, Show, Read)
-import qualified Data.String
-
-data Prog = Code Instr [Instr]
-  deriving (C.Eq, C.Ord, C.Show, C.Read)
-
-data PairSeq = DPairSeq1 Data Data | DPairSeq2 Data PairSeq
-  deriving (C.Eq, C.Ord, C.Show, C.Read)
-
-data MapSeq = DMapSeq1 Data Data | DMapSeq2 Data Data MapSeq
-  deriving (C.Eq, C.Ord, C.Show, C.Read)
-
-data Data
-    = DInt Int
-    | DStr Str
-    | DByte Hex
-    | DUnit
-    | DTrue
-    | DFalse
-    | DPair2 PairSeq
-    | DLeft Data
-    | DRight Data
-    | DSome Data
-    | DNone
-    | DBlock [Data]
-    | DMap MapSeq
-    | DInstr Instr
-  deriving (C.Eq, C.Ord, C.Show, C.Read)
-
-data Instr
-    = IBLOCK [Instr]
-    | IDROP
-    | IDROP_N Nat
-    | IDUP
-    | IDUP_N Nat
-    | ISWAP
-    | IDIG_N Nat
-    | IDUG_N Nat
-    | IPUSH Typ Data
-    | ISOME
-    | INONE Typ
-    | IUNIT
-    | INEVER
-    | IIF_NONE [Instr] [Instr]
-    | IPAIR
-    | IPAIR_N Nat
-    | ICAR
-    | ICDR
-    | IUNPAIR
-    | IUNPAIR_N Nat
-    | ILEFT Typ
-    | IRIGHT Typ
-    | IIF_LEFT [Instr] [Instr]
-    | INIL Typ
-    | ICONS
-    | IIF_CONS [Instr] [Instr]
-    | ISIZE
-    | IEMPTY_SET CTyp
-    | IEMPTY_MAP CTyp Typ
-    | IEMPTY_BIG_MAP CTyp Typ
-    | IMAP [Instr]
-    | IITER [Instr]
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/haskell_backend/Michelson/ErrM.hs

@@ -1,89 +1,0 @@
-{-# LANGUAGE CPP #-}
-
-#if __GLASGOW_HASKELL__ >= 708
----------------------------------------------------------------------------
--- Pattern synonyms exist since ghc 7.8.
-
--- | BNF Converter: Error Monad.
---
--- Module for backwards compatibility.
---
--- The generated parser now uses @'Either' String@ as error monad.
--- This module defines a type synonym 'Err' and pattern synonyms
--- 'Bad' and 'Ok' for 'Left' and 'Right'.
-
-{-# LANGUAGE PatternSynonyms #-}
-{-# LANGUAGE FlexibleInstances #-}
-
-module Michelson.ErrM where
-
-import Prelude             (id, const, Either(..), String)
-
-import Control.Monad       (MonadPlus(..))
-import Control.Applicative (Alternative(..))
-#if __GLASGOW_HASKELL__ >= 808
-import Control.Monad       (MonadFail(..))
-#endif
-
--- | Error monad with 'String' error messages.
-type Err = Either String
-
-pattern Bad msg = Left msg
-pattern Ok  a   = Right a
-
-#if __GLASGOW_HASKELL__ >= 808
-instance MonadFail Err where
-  fail = Bad
-#endif
-
-instance Alternative Err where
-  empty           = Left "Err.empty"
-  (<|>) Left{}    = id
-  (<|>) x@Right{} = const x
-
-instance MonadPlus Err where
-  mzero = empty
-  mplus = (<|>)
-
-#else
----------------------------------------------------------------------------
--- ghc 7.6 and before: use old definition as data type.
-
--- | BNF Converter: Error Monad
-
--- Copyright (C) 2004  Author:  Aarne Ranta
--- This file comes with NO WARRANTY and may be used FOR ANY PURPOSE.
-
-module Michelson.ErrM where
-
--- the Error monad: like Maybe type with error msgs
-
-import Control.Applicative (Applicative(..), Alternative(..))
-import Control.Monad       (MonadPlus(..), liftM)
-
-data Err a = Ok a | Bad String
-  deriving (Read, Show, Eq, Ord)
-
-instance Monad Err where
-  return      = Ok
-  Ok a  >>= f = f a
-  Bad s >>= _ = Bad s
-
-instance Applicative Err where
-  pure = Ok
-  (Bad s) <*> _ = Bad s
-  (Ok f) <*> o  = liftM f o
-
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/haskell_backend/Michelson/Lex.hs

@@ -1,612 +1,0 @@
-{-# OPTIONS_GHC -fno-warn-unused-binds -fno-warn-missing-signatures #-}
-{-# LANGUAGE CPP,MagicHash #-}
-{-# LINE 3 "Michelson/Lex.x" #-}
-
-{-# OPTIONS -fno-warn-incomplete-patterns #-}
-{-# OPTIONS_GHC -w #-}
-
-{-# LANGUAGE PatternSynonyms #-}
-
-module Michelson.Lex where
-
-import Prelude
-
-import qualified Data.Bits
-import Data.Char     (ord)
-import Data.Function (on)
-import Data.Word     (Word8)
-
-#if __GLASGOW_HASKELL__ >= 603
-#include "ghcconfig.h"
-#elif defined(__GLASGOW_HASKELL__)
-#include "config.h"
-#endif
-#if __GLASGOW_HASKELL__ >= 503
-import Data.Array
-import Data.Array.Base (unsafeAt)
-#else
-import Array
-#endif
-#if __GLASGOW_HASKELL__ >= 503
-import GHC.Exts
-#else
-import GlaExts
-#endif
-alex_tab_size :: Int
-alex_tab_size = 8
-alex_base :: AlexAddr
-alex_base = AlexA#
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/haskell_backend/Michelson/Par.hs

@@ -1,2377 +1,0 @@
-{-# OPTIONS_GHC -w #-}
-{-# OPTIONS -XMagicHash -XBangPatterns -XTypeSynonymInstances -XFlexibleInstances -cpp #-}
-#if __GLASGOW_HASKELL__ >= 710
-{-# OPTIONS_GHC -XPartialTypeSignatures #-}
-#endif
-{-# OPTIONS_GHC -fno-warn-incomplete-patterns -fno-warn-overlapping-patterns #-}
-{-# LANGUAGE PatternSynonyms #-}
-
-module Michelson.Par
-  ( happyError
-  , myLexer
-  , pProg
-  ) where
-
-import Prelude
-
-import qualified Michelson.Abs
-import Michelson.Lex
-import qualified Data.Array as Happy_Data_Array
-import qualified Data.Bits as Bits
-import qualified GHC.Exts as Happy_GHC_Exts
-import Control.Applicative(Applicative(..))
-import Control.Monad (ap)
-
--- parser produced by Happy Version 1.19.11
-
-newtype HappyAbsSyn  = HappyAbsSyn HappyAny
-#if __GLASGOW_HASKELL__ >= 607
-type HappyAny = Happy_GHC_Exts.Any
-#else
-type HappyAny = forall a . a
-#endif
-newtype HappyWrap4 = HappyWrap4 (Michelson.Abs.Int)
-happyIn4 :: (Michelson.Abs.Int) -> (HappyAbsSyn )
-happyIn4 x = Happy_GHC_Exts.unsafeCoerce# (HappyWrap4 x)
-{-# INLINE happyIn4 #-}
-happyOut4 :: (HappyAbsSyn ) -> HappyWrap4
-happyOut4 x = Happy_GHC_Exts.unsafeCoerce# x
-{-# INLINE happyOut4 #-}
-newtype HappyWrap5 = HappyWrap5 (Michelson.Abs.Nat)
-happyIn5 :: (Michelson.Abs.Nat) -> (HappyAbsSyn )
-happyIn5 x = Happy_GHC_Exts.unsafeCoerce# (HappyWrap5 x)
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/haskell_backend/Michelson/Print.hs

@@ -1,348 +1,0 @@
-{-# LANGUAGE CPP #-}
-{-# LANGUAGE FlexibleInstances #-}
-{-# LANGUAGE LambdaCase #-}
-#if __GLASGOW_HASKELL__ <= 708
-{-# LANGUAGE OverlappingInstances #-}
-#endif
-
-{-# OPTIONS_GHC -fno-warn-incomplete-patterns #-}
-
--- | Pretty-printer for Michelson.
---   Generated by the BNF converter.
-
-module Michelson.Print where
-
-import Prelude
-  ( ($), (.)
-  , Bool(..), (==), (<)
-  , Int, Integer, Double, (+), (-), (*)
-  , String, (++)
-  , ShowS, showChar, showString
-  , all, elem, foldr, id, map, null, replicate, shows, span
-  )
-import Data.Char ( Char, isSpace )
-import qualified Michelson.Abs
-
--- | The top-level printing method.
-
-printTree :: Print a => a -> String
-printTree = render . prt 0
-
-type Doc = [ShowS] -> [ShowS]
-
-doc :: ShowS -> Doc
-doc = (:)
-
-render :: Doc -> String
-render d = rend 0 False (map ($ "") $ d []) ""
-  where
-  rend
-    :: Int        -- ^ Indentation level.
-    -> Bool       -- ^ Pending indentation to be output before next character?
-    -> [String]
-    -> ShowS
-  rend i p = \case
-      "["      :ts -> char '[' . rend i False ts
-      "("      :ts -> char '(' . rend i False ts
-      "{"      :ts -> onNewLine i     p . showChar   '{'  . new (i+1) ts
-      "}" : ";":ts -> onNewLine (i-1) p . showString "};" . new (i-1) ts
-      "}"      :ts -> onNewLine (i-1) p . showChar   '}'  . new (i-1) ts
-      [";"]        -> char ';'
-      ";"      :ts -> char ';' . new i ts
-      t  : ts@(s:_) | closingOrPunctuation s
-                   -> pending . showString t . rend i False ts
-      t        :ts -> pending . space t      . rend i False ts
-      []           -> id
-    where
-    -- Output character after pending indentation.
-    char :: Char -> ShowS
-    char c = pending . showChar c
-
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/haskell_backend/Michelson/Skel.hs

@@ -1,221 +1,0 @@
--- Haskell module generated by the BNF converter
-
-{-# OPTIONS_GHC -fno-warn-unused-matches #-}
-
-module Michelson.Skel where
-
-import Prelude (($), Either(..), String, (++), Show, show)
-import qualified Michelson.Abs
-
-type Err = Either String
-type Result = Err String
-
-failure :: Show a => a -> Result
-failure x = Left $ "Undefined case: " ++ show x
-
-transInt :: Michelson.Abs.Int -> Result
-transInt x = case x of
-  Michelson.Abs.Int string -> failure x
-
-transNat :: Michelson.Abs.Nat -> Result
-transNat x = case x of
-  Michelson.Abs.Nat string -> failure x
-
-transStr :: Michelson.Abs.Str -> Result
-transStr x = case x of
-  Michelson.Abs.Str string -> failure x
-
-transHex :: Michelson.Abs.Hex -> Result
-transHex x = case x of
-  Michelson.Abs.Hex string -> failure x
-
-transProg :: Michelson.Abs.Prog -> Result
-transProg x = case x of
-  Michelson.Abs.Code instr instrs -> failure x
-
-transPairSeq :: Michelson.Abs.PairSeq -> Result
-transPairSeq x = case x of
-  Michelson.Abs.DPairSeq1 data_1 data_2 -> failure x
-  Michelson.Abs.DPairSeq2 data_ pairseq -> failure x
-
-transMapSeq :: Michelson.Abs.MapSeq -> Result
-transMapSeq x = case x of
-  Michelson.Abs.DMapSeq1 data_1 data_2 -> failure x
-  Michelson.Abs.DMapSeq2 data_1 data_2 mapseq -> failure x
-
-transData :: Michelson.Abs.Data -> Result
-transData x = case x of
-  Michelson.Abs.DInt int -> failure x
-  Michelson.Abs.DStr str -> failure x
-  Michelson.Abs.DByte hex -> failure x
-  Michelson.Abs.DUnit -> failure x
-  Michelson.Abs.DTrue -> failure x
-  Michelson.Abs.DFalse -> failure x
-  Michelson.Abs.DPair2 pairseq -> failure x
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/haskell_backend/Michelson/Test.hs

@@ -1,76 +1,0 @@
--- Program to test parser, automatically generated by BNF Converter.
-
-module Main where
-
-import Prelude
-  ( ($), (.)
-  , Either(..)
-  , Int, (>)
-  , String, (++), concat, unlines
-  , Show, show
-  , IO, (>>), (>>=), mapM_, putStrLn
-  , FilePath
-  , getContents, readFile
-  )
-import System.Environment ( getArgs )
-import System.Exit        ( exitFailure, exitSuccess )
-import Control.Monad      ( when )
-
-import Michelson.Abs   ()
-import Michelson.Lex   ( Token, mkPosToken )
-import Michelson.Par   ( pProg, myLexer )
-import Michelson.Print ( Print, printTree )
-import Michelson.Skel  ()
-
-type Err        = Either String
-type ParseFun a = [Token] -> Err a
-type Verbosity  = Int
-
-putStrV :: Verbosity -> String -> IO ()
-putStrV v s = when (v > 1) $ putStrLn s
-
-runFile :: (Print a, Show a) => Verbosity -> ParseFun a -> FilePath -> IO ()
-runFile v p f = putStrLn f >> readFile f >>= run v p
-
-run :: (Print a, Show a) => Verbosity -> ParseFun a -> String -> IO ()
-run v p s =
-  case p ts of
-    Left err -> do
-      putStrLn "\nParse              Failed...\n"
-      putStrV v "Tokens:"
-      mapM_ (putStrV v . showPosToken . mkPosToken) ts
-      putStrLn err
-      exitFailure
-    Right tree -> do
-      putStrLn "\nParse Successful!"
-      showTree v tree
-      exitSuccess
-  where
-  ts = myLexer s
-  showPosToken ((l,c),t) = concat [ show l, ":", show c, "\t", show t ]
-
-showTree :: (Show a, Print a) => Int -> a -> IO ()
-showTree v tree = do
-  putStrV v $ "\n[Abstract Syntax]\n\n" ++ show tree
-  putStrV v $ "\n[Linearized tree]\n\n" ++ printTree tree
-
-usage :: IO ()
-usage = do
-  putStrLn $ unlines
-    [ "usage: Call with one of the following argument combinations:"
-    , "  --help          Display this help message."
-    , "  (no arguments)  Parse stdin verbosely."
-    , "  (files)         Parse content of files verbosely."
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_folder.sh

@@ -1,7 +1,0 @@
-search_dir="../test/test_files/tezos-master-tests_python-contracts_alpha/tests_python/contracts_alpha/opcodes"
-for entry in "$search_dir"/*
-do
-  echo "$entry"
-  ./ocaml_backend/TestMichelson $entry
-  echo
-done

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_haskell/Test/Abs.hs

@@ -1,31 +1,0 @@
--- Haskell data types for the abstract syntax.
--- Generated by the BNF converter.
-
-{-# LANGUAGE GeneralizedNewtypeDeriving #-}
-
--- | The abstract syntax of language test.
-
-module Test.Abs where
-
-import Prelude (String)
-import qualified Prelude as C (Eq, Ord, Show, Read)
-import qualified Data.String
-
-data Prog = Code Instr [Instr]
-  deriving (C.Eq, C.Ord, C.Show, C.Read)
-
-data Instr = IPUSH CType Data | IADD
-  deriving (C.Eq, C.Ord, C.Show, C.Read)
-
-data Data = DInt Int
-  deriving (C.Eq, C.Ord, C.Show, C.Read)
-
-data CType = CInt
-  deriving (C.Eq, C.Ord, C.Show, C.Read)
-
-newtype Nat = Nat String
-  deriving (C.Eq, C.Ord, C.Show, C.Read, Data.String.IsString)
-
-newtype Int = Int String
-  deriving (C.Eq, C.Ord, C.Show, C.Read, Data.String.IsString)
-

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_haskell/Test/ErrM.hs

@@ -1,89 +1,0 @@
-{-# LANGUAGE CPP #-}
-
-#if __GLASGOW_HASKELL__ >= 708
----------------------------------------------------------------------------
--- Pattern synonyms exist since ghc 7.8.
-
--- | BNF Converter: Error Monad.
---
--- Module for backwards compatibility.
---
--- The generated parser now uses @'Either' String@ as error monad.
--- This module defines a type synonym 'Err' and pattern synonyms
--- 'Bad' and 'Ok' for 'Left' and 'Right'.
-
-{-# LANGUAGE PatternSynonyms #-}
-{-# LANGUAGE FlexibleInstances #-}
-
-module Test.ErrM where
-
-import Prelude             (id, const, Either(..), String)
-
-import Control.Monad       (MonadPlus(..))
-import Control.Applicative (Alternative(..))
-#if __GLASGOW_HASKELL__ >= 808
-import Control.Monad       (MonadFail(..))
-#endif
-
--- | Error monad with 'String' error messages.
-type Err = Either String
-
-pattern Bad msg = Left msg
-pattern Ok  a   = Right a
-
-#if __GLASGOW_HASKELL__ >= 808
-instance MonadFail Err where
-  fail = Bad
-#endif
-
-instance Alternative Err where
-  empty           = Left "Err.empty"
-  (<|>) Left{}    = id
-  (<|>) x@Right{} = const x
-
-instance MonadPlus Err where
-  mzero = empty
-  mplus = (<|>)
-
-#else
----------------------------------------------------------------------------
--- ghc 7.6 and before: use old definition as data type.
-
--- | BNF Converter: Error Monad
-
--- Copyright (C) 2004  Author:  Aarne Ranta
--- This file comes with NO WARRANTY and may be used FOR ANY PURPOSE.
-
-module Test.ErrM where
-
--- the Error monad: like Maybe type with error msgs
-
-import Control.Applicative (Applicative(..), Alternative(..))
-import Control.Monad       (MonadPlus(..), liftM)
-
-data Err a = Ok a | Bad String
-  deriving (Read, Show, Eq, Ord)
-
-instance Monad Err where
-  return      = Ok
-  Ok a  >>= f = f a
-  Bad s >>= _ = Bad s
-
-instance Applicative Err where
-  pure = Ok
-  (Bad s) <*> _ = Bad s
-  (Ok f) <*> o  = liftM f o
-
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_haskell/Test/Lex.hs

@@ -1,504 +1,0 @@
-{-# OPTIONS_GHC -fno-warn-unused-binds -fno-warn-missing-signatures #-}
-{-# LANGUAGE CPP,MagicHash #-}
-{-# LINE 3 "Test/Lex.x" #-}
-
-{-# OPTIONS -fno-warn-incomplete-patterns #-}
-{-# OPTIONS_GHC -w #-}
-
-{-# LANGUAGE PatternSynonyms #-}
-
-module Test.Lex where
-
-import Prelude
-
-import qualified Data.Bits
-import Data.Char     (ord)
-import Data.Function (on)
-import Data.Word     (Word8)
-
-#if __GLASGOW_HASKELL__ >= 603
-#include "ghcconfig.h"
-#elif defined(__GLASGOW_HASKELL__)
-#include "config.h"
-#endif
-#if __GLASGOW_HASKELL__ >= 503
-import Data.Array
-import Data.Array.Base (unsafeAt)
-#else
-import Array
-#endif
-#if __GLASGOW_HASKELL__ >= 503
-import GHC.Exts
-#else
-import GlaExts
-#endif
-alex_tab_size :: Int
-alex_tab_size = 8
-alex_base :: AlexAddr
-alex_base = AlexA#
-  "\xf8\xff\xff\xff\xf3\xff\xff\xff\xd6\xff\xff\xff\x07\x00\x00\x00\x00\x00\x00\x00\xe9\xff\xff\xff\x8c\x00\x00\x00\x9f\x00\x00\x00"#
-
-alex_table :: AlexAddr
-alex_table = AlexA#
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_haskell/Test/Par.hs

@@ -1,821 +1,0 @@
-{-# OPTIONS_GHC -w #-}
-{-# OPTIONS -XMagicHash -XBangPatterns -XTypeSynonymInstances -XFlexibleInstances -cpp #-}
-#if __GLASGOW_HASKELL__ >= 710
-{-# OPTIONS_GHC -XPartialTypeSignatures #-}
-#endif
-{-# OPTIONS_GHC -fno-warn-incomplete-patterns -fno-warn-overlapping-patterns #-}
-{-# LANGUAGE PatternSynonyms #-}
-
-module Test.Par
-  ( happyError
-  , myLexer
-  , pProg
-  ) where
-
-import Prelude
-
-import qualified Test.Abs
-import Test.Lex
-import qualified Data.Array as Happy_Data_Array
-import qualified Data.Bits as Bits
-import qualified GHC.Exts as Happy_GHC_Exts
-import Control.Applicative(Applicative(..))
-import Control.Monad (ap)
-
--- parser produced by Happy Version 1.19.11
-
-newtype HappyAbsSyn  = HappyAbsSyn HappyAny
-#if __GLASGOW_HASKELL__ >= 607
-type HappyAny = Happy_GHC_Exts.Any
-#else
-type HappyAny = forall a . a
-#endif
-newtype HappyWrap4 = HappyWrap4 (Test.Abs.Nat)
-happyIn4 :: (Test.Abs.Nat) -> (HappyAbsSyn )
-happyIn4 x = Happy_GHC_Exts.unsafeCoerce# (HappyWrap4 x)
-{-# INLINE happyIn4 #-}
-happyOut4 :: (HappyAbsSyn ) -> HappyWrap4
-happyOut4 x = Happy_GHC_Exts.unsafeCoerce# x
-{-# INLINE happyOut4 #-}
-newtype HappyWrap5 = HappyWrap5 (Test.Abs.Int)
-happyIn5 :: (Test.Abs.Int) -> (HappyAbsSyn )
-happyIn5 x = Happy_GHC_Exts.unsafeCoerce# (HappyWrap5 x)
-{-# INLINE happyIn5 #-}
-happyOut5 :: (HappyAbsSyn ) -> HappyWrap5
-happyOut5 x = Happy_GHC_Exts.unsafeCoerce# x
-{-# INLINE happyOut5 #-}
-newtype HappyWrap6 = HappyWrap6 (Test.Abs.Prog)
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_haskell/Test/Print.hs

@@ -1,166 +1,0 @@
-{-# LANGUAGE CPP #-}
-{-# LANGUAGE FlexibleInstances #-}
-{-# LANGUAGE LambdaCase #-}
-#if __GLASGOW_HASKELL__ <= 708
-{-# LANGUAGE OverlappingInstances #-}
-#endif
-
-{-# OPTIONS_GHC -fno-warn-incomplete-patterns #-}
-
--- | Pretty-printer for Test.
---   Generated by the BNF converter.
-
-module Test.Print where
-
-import Prelude
-  ( ($), (.)
-  , Bool(..), (==), (<)
-  , Int, Integer, Double, (+), (-), (*)
-  , String, (++)
-  , ShowS, showChar, showString
-  , all, elem, foldr, id, map, null, replicate, shows, span
-  )
-import Data.Char ( Char, isSpace )
-import qualified Test.Abs
-
--- | The top-level printing method.
-
-printTree :: Print a => a -> String
-printTree = render . prt 0
-
-type Doc = [ShowS] -> [ShowS]
-
-doc :: ShowS -> Doc
-doc = (:)
-
-render :: Doc -> String
-render d = rend 0 False (map ($ "") $ d []) ""
-  where
-  rend
-    :: Int        -- ^ Indentation level.
-    -> Bool       -- ^ Pending indentation to be output before next character?
-    -> [String]
-    -> ShowS
-  rend i p = \case
-      "["      :ts -> char '[' . rend i False ts
-      "("      :ts -> char '(' . rend i False ts
-      "{"      :ts -> onNewLine i     p . showChar   '{'  . new (i+1) ts
-      "}" : ";":ts -> onNewLine (i-1) p . showString "};" . new (i-1) ts
-      "}"      :ts -> onNewLine (i-1) p . showChar   '}'  . new (i-1) ts
-      [";"]        -> char ';'
-      ";"      :ts -> char ';' . new i ts
-      t  : ts@(s:_) | closingOrPunctuation s
-                   -> pending . showString t . rend i False ts
-      t        :ts -> pending . space t      . rend i False ts
-      []           -> id
-    where
-    -- Output character after pending indentation.
-    char :: Char -> ShowS
-    char c = pending . showChar c
-
-    -- Output pending indentation.
-    pending :: ShowS
-    pending = if p then indent i else id
-
-  -- Indentation (spaces) for given indentation level.
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_haskell/Test/Skel.hs

@@ -1,39 +1,0 @@
--- Haskell module generated by the BNF converter
-
-{-# OPTIONS_GHC -fno-warn-unused-matches #-}
-
-module Test.Skel where
-
-import Prelude (($), Either(..), String, (++), Show, show)
-import qualified Test.Abs
-
-type Err = Either String
-type Result = Err String
-
-failure :: Show a => a -> Result
-failure x = Left $ "Undefined case: " ++ show x
-
-transNat :: Test.Abs.Nat -> Result
-transNat x = case x of
-  Test.Abs.Nat string -> failure x
-
-transInt :: Test.Abs.Int -> Result
-transInt x = case x of
-  Test.Abs.Int string -> failure x
-
-transProg :: Test.Abs.Prog -> Result
-transProg x = case x of
-  Test.Abs.Code instr instrs -> failure x
-
-transInstr :: Test.Abs.Instr -> Result
-transInstr x = case x of
-  Test.Abs.IPUSH ctype data_ -> failure x
-  Test.Abs.IADD -> failure x
-
-transData :: Test.Abs.Data -> Result
-transData x = case x of
-  Test.Abs.DInt int -> failure x
-
-transCType :: Test.Abs.CType -> Result
-transCType x = case x of
-  Test.Abs.CInt -> failure x

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_haskell/Test/Test.hs

@@ -1,76 +1,0 @@
--- Program to test parser, automatically generated by BNF Converter.
-
-module Main where
-
-import Prelude
-  ( ($), (.)
-  , Either(..)
-  , Int, (>)
-  , String, (++), concat, unlines
-  , Show, show
-  , IO, (>>), (>>=), mapM_, putStrLn
-  , FilePath
-  , getContents, readFile
-  )
-import System.Environment ( getArgs )
-import System.Exit        ( exitFailure, exitSuccess )
-import Control.Monad      ( when )
-
-import Test.Abs   ()
-import Test.Lex   ( Token, mkPosToken )
-import Test.Par   ( pProg, myLexer )
-import Test.Print ( Print, printTree )
-import Test.Skel  ()
-
-type Err        = Either String
-type ParseFun a = [Token] -> Err a
-type Verbosity  = Int
-
-putStrV :: Verbosity -> String -> IO ()
-putStrV v s = when (v > 1) $ putStrLn s
-
-runFile :: (Print a, Show a) => Verbosity -> ParseFun a -> FilePath -> IO ()
-runFile v p f = putStrLn f >> readFile f >>= run v p
-
-run :: (Print a, Show a) => Verbosity -> ParseFun a -> String -> IO ()
-run v p s =
-  case p ts of
-    Left err -> do
-      putStrLn "\nParse              Failed...\n"
-      putStrV v "Tokens:"
-      mapM_ (putStrV v . showPosToken . mkPosToken) ts
-      putStrLn err
-      exitFailure
-    Right tree -> do
-      putStrLn "\nParse Successful!"
-      showTree v tree
-      exitSuccess
-  where
-  ts = myLexer s
-  showPosToken ((l,c),t) = concat [ show l, ":", show c, "\t", show t ]
-
-showTree :: (Show a, Print a) => Int -> a -> IO ()
-showTree v tree = do
-  putStrV v $ "\n[Abstract Syntax]\n\n" ++ show tree
-  putStrV v $ "\n[Linearized tree]\n\n" ++ printTree tree
-
-usage :: IO ()
-usage = do
-  putStrLn $ unlines
-    [ "usage: Call with one of the following argument combinations:"
-    , "  --help          Display this help message."
-    , "  (no arguments)  Parse stdin verbosely."
-    , "  (files)         Parse content of files verbosely."
-    , "  -s (files)      Silent mode. Parse content of files silently."
-    ]
[…]

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_parser.sh

@@ -1,5 +1,0 @@
-./ocaml_backend/TestMichelson test_contract.tz
-
-#echo "DROP; PUSH int -5; PUSH int 1;" |ocaml_backend/TestMichelson
-
-

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_test.sh

@@ -1,3 +1,0 @@
-./test/TestTest test_contract.tz
-
-#echo "DROP; PUSH int -5; PUSH int 1;" | test/TestTest

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bncf/test_test_haskell.sh

@@ -1,3 +1,0 @@
-./test_haskell/Test/Test test_contract.tz
-
-#echo "DROP; PUSH int -5; PUSH int 1;" | test_haskell/Test/Test

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bnfc/create_haskell_parser.sh
ML interpreter: upload BNF grammar

@@ -1,0 +1,3 @@
+bnfc -d -m -o haskell_backend michelson.cf
+make -C haskell_backend
+#./test_parser.sh

### 2021-09-15 projects/ocaml_michelson-interpreter/src/bnfc/create_parser.sh

@@ -1,0 +1,3 @@
+bnfc --ocaml-menhir -m -o ocaml_backend michelson.cf
+make -C ocaml_backend
+#./test_parser.sh

### 2021-09-17 projects/ocaml_michelson-interpreter/src/bnfc/latex_language-specification.sh
ML-interpreter: add macro expansion for IFCMP(\op) & file cleanup

@@ -1,0 +1,1 @@
+bnfc --latex -o language-specification michelson.cf

### 2021-09-17 projects/ocaml_michelson-interpreter/src/bnfc/test_haskell_parser.sh

@@ -1,3 +1,0 @@
-./haskell_backend/Michelson/Test test_contract.tz
-
-#echo "DROP; PUSH int -5; PUSH int 1;" | haskell_backend/Michelson/Test

### 2021-09-17 projects/ocaml_michelson-interpreter/src/bnfc/test_macros.sh

@@ -1,0 +1,3 @@
+echo "Testing macro_expansion"
+./ocaml_backend/TestMichelson macro_expansion.tz
+

### 2021-09-17 projects/ocaml_michelson-interpreter/src/bnfc/test_test-files.sh

@@ -1,0 +1,10 @@
+topdir="../test/test_files/"
+find "$topdir" -type f \( -name '*.tz' \) -exec echo "Contract: {}" \; -exec ./ocaml_backend/TestMichelson {} \;
+
+#topdir="../test/test_files/contracts_alpha/opcodes"
+#for entry in "$topdir"/*
+#do
+#  echo "$entry"
+#  ./ocaml_backend/TestMichelson $entry
+#  echo
+#done

### 2021-10-01 projects/ocaml_michelson-interpreter/src/bnfc/create_parser.sh
ML interpreter: parser refactoring, most macros added

@@ -1,3 +1,3 @@
-bnfc --ocaml-menhir -m -o ocaml_backend michelson.cf
-make -C ocaml_backend
-#./test_parser.sh
+bnfc --ocaml-menhir -m -o ../lib/parser michelson.cf
+make -C ../lib/parser
+#./test_test-contract.sh

### 2021-10-01 projects/ocaml_michelson-interpreter/src/bnfc/test_macros.sh

@@ -1,3 +1,3 @@
 echo "Testing macro_expansion"
-./ocaml_backend/TestMichelson macro_expansion.tz
+../lib/parser/TestMichelson macro_expansion.tz
 

### 2021-10-01 projects/ocaml_michelson-interpreter/src/bnfc/test_test-contract.sh

@@ -1,4 +1,4 @@
-./ocaml_backend/TestMichelson test_contract.tz
+../lib/parser/TestMichelson test_contract.tz
 
 #echo "DROP; PUSH int -5; PUSH int 1;" |ocaml_backend/TestMichelson
 

### 2021-10-01 projects/ocaml_michelson-interpreter/src/bnfc/test_test-files.sh

@@ -1,10 +1,10 @@
 topdir="../test/test_files/"
-find "$topdir" -type f \( -name '*.tz' \) -exec echo "Contract: {}" \; -exec ./ocaml_backend/TestMichelson {} \;
+find "$topdir" -type f \( -name '*.tz' \) -exec echo "Contract: {}" \; -exec ../lib/parser/TestMichelson {} \;
 
 #topdir="../test/test_files/contracts_alpha/opcodes"
 #for entry in "$topdir"/*
 #do
 #  echo "$entry"
-#  ./ocaml_backend/TestMichelson $entry
+#  ../lib/parser/TestMichelson $entry
 #  echo
 #done

### 2022-01-10 papers/assertion_contract/paper.tex
Add files via upload

% APLAS 2021: Regular research papers should not exceed 18 pages in
% the Springer LNCS format(LaTeX template), including bibliography and
% figures.
% Lightweight double-blind: Author names and institutions must be
% omitted and References to the authors’ own related work should be in
% the third person 
%
\documentclass[runningheads]{llncs}
\pdfoutput=1
%\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{graphicx}
%\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathpartir}
\usepackage{graphicx}
%\usepackage{fixme}
%\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{listings}
\lstdefinelanguage{michelson}{
  % basicstyle=\ttfamily,
  basicstyle=\fontsize{8}{9.6}\selectfont,
  morekeywords={parameter,storage,or,unit,mutez,pair,bool,address}, sensitive=false,
  morecomment=[l]{\#},
  morecomment=[s]{/*}{*/},
  morestring=[b]",
}
\lstset{
  language=Caml,
  captionpos=b,
  aboveskip=-\smallskipamount,
  belowskip=-\smallskipamount,
  belowcaptionskip=0pt,
  basicstyle=\fontsize{8}{9.6}\selectfont,
  morekeywords={val}
}

\input{macros}

\begin{document}
%
\title{Assertion Contracts}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
%\author{Thi Thu Ha Doan\orcidID{0000-0001-7524-4497}\and Peter Thiemann\orcidID{0000-0002-9000-1239}}

%
%\authorrunning{Ha Doan, P. Thiemann}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
%\institute{University of Freiburg, Germany \\ \email{\{doanha,thiemann\}@informatik.uni-freiburg.de}
%}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}

\keywords{}
\end{abstract}

%
%
%
\section{Introduction}
\label{sec:introduction}
Every computation performed by a Smart Contract on the blockchain generates costs. Each
unit of computation and each unit of storage used by an algorithm must be paid for. To
avoid this cost, an application might perform some computation away from the blockchain
(i.e., off-chain) and submit the result as a parameter to a contract on the
blockchain. Typically, such a computation asserts certain properties of the 
submitted parameter.

However, this approach raises the issue that on the one hand the contract should take
advantage of the offchain computation and assume that the submitted parameter has
these properties, but on the other hand, the off-chain computation might be wrong and
submit illegal parameters. So, we need a mechanism that checks the validity of the
assumptions before the contract starts executing.

As an example, consider a contract that takes a prime number as a parameter.
\begin{lstlisting}[numbers=none]
contract Example {
  function (int p) public {
    // assume p is prime
    ...
  }
}
\end{lstlisting}
This assumption can be expressed with an explicit assertion in predicate logic.
\begin{gather}\label{eq:5}
  (\forall n) (2 \le n \le \sqrt p) \Rightarrow (p \mathbin{\%} n) \ne 0
\end{gather}
To test the validity of this assumption requires a loop in the contract, but the test would take
$O(\sqrt p)$ time (assuming constant time for computing the remainder) and thus produce extra cost
linear in $\sqrt p$ accordingly. 
However, we could do better by recruiting the validators of the contract for a distributed
effort to find a counterexample. To this end, we consider the negation of the assertion.
\begin{gather}\label{eq:4}
  (\exists n) (2 \le n \le \sqrt p) \wedge (p \mathbin{\%} n) = 0
\end{gather}
This assertion can be checked pointwise by having each validator independently choose a
random $n$ fulfilling $2 \le n \le 
\sqrt p$ and checking whether $(p \mathbin{\%} n) = 0$. If the remainder is $0$, the
validator found a counterexample, posts its veto to the P2P net, and stops further
exection. Otherwise, it accepts $p$ knowing that other points will be checked by other
validators.

In this scenario, each validator only needs to be paid to generate a random number and
perform a division, which is a constant cost independent from $p$.

Of course, this validation is only probabilistic, so its effectiveness depends on the
number of validators. One could say that the community of validators implements a Bloom
filter for the set of primes: if a value $p$ is rejected it is certainly not a prime (because
there exists a counterexample); if a value $p$ is not rejected it is prime with a
probability that depends on $p$ and the number of validators.

As another example, consider a contract that takes a sorted array of integers.
\begin{lstlisting}[numbers=none]
contract Sorted {
  function find (int[50] a, int v) public {
    // assume a is sorted
  }
}
\end{lstlisting}
The explicit assertion would be
\begin{gather}\label{eq:1}
  (\forall k) (0\le k <49) \Rightarrow a[k] \le a[k+1]
\end{gather}
While we can check this contract in $O(1)$ time, the constant factor is big! So we
consider its negation.
\begin{displaymath}
  (\exists k) (0\le k <49) \wedge a[k] > a[k+1]
\end{displaymath}
Again, we can have every validator generate a random number $k$. If the
condition is true for such $k$, then the validator found a counterexample for the sortedness
of the array. Otherwise, the validator relies on the other validators to check
different numbers.

To obtain an estimate of the number of validators needed to find a counterexample with
high probibility, 
let's assume the array is unsorted only at position $0$, the size of the array is $n$,
and the number of validators is $m$. Each validator independently has a probability of
$1/n$ to detect the problem and thus probability $\frac{n-1} n$ not to detect the
problem. Hence, if we assume that each $k$ is chosen independenty from a uniform distribution,
the probability that no validator checks at
position $0$ converges to $0$ as the number of validators approaches infinity.
\begin{displaymath}
  \lim_{m\to\infty}\frac{(n-1)^m}{n^m}
  = \lim_{m\to\infty} \left(\frac{n-1}{n}\right)^m
  = 0
\end{displaymath}

In Dafny (citation) \url{https://rise4fun.com/Dafny/tutorialcontent/guide#h29} you can
write
\begin{lstlisting}
forall j, k :: 0 <= j < k < a.Length ==> a[j] <= a[k]
\end{lstlisting}
to express that an array is sorted. This predicate is equivalent to the one given in
\eqref{eq:1}, but it might be more challenging to test. Its negation is
\begin{gather}
  \label{eq:2}
  (\exists j, k ) (0\le j< k < |a|) \wedge a[j] > a[k]
\end{gather}
So we'd have to generate two random numbers $j$ and $k$ such that the condition $0 \le
j < k < |a|$ is fulfilled.

Another condition that might be tested on an array is the heap condition
\begin{gather}
  \label{eq:3}
  (\forall i) (0 \le i < \lfloor|a|/2\rfloor) \Rightarrow a[i] \le a[2i+1] \wedge (2i+2
  < |a| \Rightarrow a[i] \le a[2i+2])
\end{gather}
\section{Primaries}
\label{sec:primaries}

\subsection{Smart Contract}
\label{subsec:smart-contract}

\subsection{Assertion Problem}
\label{subsec:problem}

\section{Distributed Assertion Protocol}
\label{sec:approach}
We propose an assertion verification approach for smart contracts. When a function is called with a parameter that needs to be verified, an assertion and its negation form are created for that parameter. The idea underlying our approach is that the assertion is distributed to be verified by validators. During the distribution, each validator strives to find a counterexample for the assertion. Each of these validators then checks only a random point or a small finite set  in the range of the parameter. Considering the example where a parameter $p$ is a prime number, the assertion in predicate logic for the parameter is 
\begin{gather}\label{eq:3a}
  (\forall n) (2 \le n \le \sqrt p) \Rightarrow (p \mathbin{\%} n) \ne 0
\end{gather}

\noindent and its negation form is

\begin{gather}\label{eq:3b}
  (\exists n) (2 \le n \le \sqrt p) \wedge (p \mathbin{\%} n) = 0
\end{gather}

\noindent each validator independently choose a
random $n$ in the range $2 \le n \le 
\sqrt p$ and checking whether $(p \mathbin{\%} n) = 0$. If the remainder is $0$, the
validator found a counterexample.

In our approach, there are three roles: 
\begin{itemize}
   \item the smart contract owner deploys and manages the smart contract, 
   \item the callers invoke the smart contract functions, and 
   \item the validators are involved in validating a parameter submitted by a caller. 
\end{itemize}

\noindent A caller invoking a function submit the parameter that needs to be validated to the blockchain. The parameter is forwarded to all nodes as validators in the network, which then validate it. Our method is depicted in Figure 1 (2).

Finding a counterexample for the assertion and announcing the result to the blockchain costs in terms of energy (computing power) and gas. There could be the case that it is very rare to find a counterexample, because a caller tries not to pass an unvalidated parameter. In this case, we need to encourage all validators running the program to validate the assertion. Therefore, there are two rewards in the form of cryptocurrency in order to motivate the validators to participate: (1) for a  counterexample found and (2) for a computational proof.  It requires a way to check a computation proof provided by a validator that proves that the validator actually run the program to find a counterfeit for the assertion, but none is found.

If any of the validators finds a violation of the assertion, the final transaction (call) is aborted. In our approach, the validator make an effor to find a counterexample for the assertion offline. Therefore, the validators interact with the smart contract to submit a  counterexample or a computation proof through smart contract function calls. 
\subsection{Smart Contract's Functions and Storage}
\subsubsection{Functions}
There can be several functions in a contract, we consider here the functions where one of the parameters must be validated. Because the parameter must be checked before the actual work can be done, we separate it into two functions: a caller first invokes an assertion function to pass the parameter for  verification and after the parameter is verified, a normal function with a assumion that a paramete is valid can be called to do the actual work.  A contract must contain the following three types of functions:

\begin{itemize}
\item The assertion functions, where callers submit their parameters to be verified, which are then distributed to all validators. 
\item  The work function that performs the task with the assumtion that the parameter is valid. 
\item The validation functions, which have two mode to check and promote either a proof or a counterexample sent by validators.
\end{itemize}

For example, the Example contract in which there is a work function that  takes a prime number as one of its parameters would include these three types of functions  as follows:

\begin{lstlisting}[numbers=none]

contract Example {
    \\ storage declarations
    ...
    \\ assertion functions
    function assertion(int p) public {
       ...
    } 
    \\ work functions
    function work(int p, ...) public {
       ...
    }
    \\ validation functions   
    function validator(...) public {
       ...
    }
    \\ other functions
    ...
}
\end{lstlisting}

%question: map or array and how to delete

\subsubsection{Storage}
When a caller submits a parameter to be validated, the parameter and its related information must be stored in storage for the validation process. For each submission, there should be a corresponding record, which contains the following data: (1) the parameter (or its hash), the caller's address, the timestamp indicating the approximate time when the caller submits the parameter, and the validating status containing such as the number of proofs it has received, the status if there is a counterexample. It could be the case that many parameters are submitted, then it makes sense to delete the data set after the processing with the parameter is completed. The selected data structure should be suitable for deletion both in terms of gas and reference to other records.  There are two possible cadicated data type for store such records : map and array.

For avobed example contract, assuming that a caller can only submit one parameter at a time, we can use a map that maps a caller address with the parameter hash and timestamp.

\begin{lstlisting}[numbers=none]

   struct Parameter {
        uint p_hash;
        uint timestamp;
    }
    mapping (address => Parameter) public parameters;

\end{lstlisting}

The contents of the storage are divided into two parts: (1) normal data for the operating of the smart contract and (2) assertion data, which stores all records of the submitted parameters that need to be validated.

\subsubsection{Offline Assertion Program}
To check the validity of a parameter, each validator independently runs a program that generates a negative formula for the parameter and then selects a random point in the parameter range to find a counterexample. The program is intended to run offline from the blockchain network and should be sent to all validators. In addition, the program must provide a calculation proof that can be submitted to the blockchain to receive an award. This trigger calculation should be generated identically for each run. There is more to learn about the program in the following part.
\begin{figure}
\centering
\includegraphics[scale=.6]{assertion_1}
\caption{Assertion Contract (1)}
\end{figure}

\subsection{Roles}
\subsubsection{Managing the contract and offline assertion program}
A contract is provided by its owner on the blockchain. In addition to the code of the contract on the blockchain, there is the offline assertion program to find a counterexample for a submitted parameter, and this code should be available to all validators. Let us discuss two ways to submit this program

\begin{itemize} 
\item the program code is stored inside the contract code. In this case, the code will be available on the blockchain. However, it could be expensive to store it on the blockchain, and especially impossible if the program is very large. (For discussion: and can be sent as data in a normal transmission). 
\item the program code is stored offline and should always be available to callers/validators on request. There are two ways to make it available to validators: (1) the program is stored on a source that the caller/validator can access, or the owner can make it available on request sent to a caller/validator when requested, and (2) when a caller invokes an assertion function, it should send the program to the network via messaging systems such as rakun in Eutherum, or the owner should send it to the network via postcard when deploying the contract, and in this case the interested validator should store it locally. \end{itemize}

\subsubsection{Interacting with the smart contract}
A caller must first pass the parameter, which must be checked before it is passed to the actual code, namely the normal function. The parameter then is supporsed to be verified by validators. We consider here two ways in which the call to the normal function can be handled after the parameter has been checked.

\begin{itemize}
\item The function is called by a caller after the process of checking the parameter is complete (Figure 1). There must be a constraint for calling this function. For example, the function can be called only after the parameter has been available for verification for a certain time, or there is a fixed number of proofs (computational proof without counterexample) that the parameter has received. The main point with this way is that we do not need to store the parameter, only its hash in the storage, and also the other parameters that do not need to be checked can only be submitted when the caller invokes the normal function. The caller must also transmit the timestamp when it presents the parameter for checking. With the hash of the parameter, the address of the caller, and the timestamp, a search in storage looks for the matching information and constraints to decide whether or not to run the code for the actual performance.
\item the function is called by the validate function (Figure 2). The good thing about this method is that the process of validating the parameter and calling the normal function is not visible to the user. However, there are two arguments against this way: (1) it is necessary to store the assertion parameter as well as others in memory, which comes at a high cost, and (2) since the function is called from the validation function, there should be a way to ensure that it is called when the parameter is valid and certain conditions are met. Also, it might be difficult to deal with timing constraints since these functions are passive. 
\end{itemize}

\paragraph{Submitting the parameter} A caller passes the parameter to be verified by calling an assertion function. The function then stores all the necessary information, namely the parameter hash (1) or the parameter (2), the caller's address, and the timestamp as in a record in the storage.  The record of the parameter, moreover, initial information to observe the progress of the verification of the parameter. e.g. how many evidences have been presented, whether a counterexample has been found,..etc. This information is used to check a proof or  counterexample submitted by a validator, and to decide when a normal function might be called for that parameter. The caller can then send this information, along with the offline assertion program, to all validators via a messaging system. (Discussion: should the function publish this information on the blockchain via the IDA in a transfer to all examiners as this is costly?).

\paragraph{Calling the normal function}
We consider the case where the nomal function is called by a caller after the parameter has been checked. Thus, the caller first passes its parameter to the assertion function and then waits a while to be sure that the parameter is checked. The record corresponding to the parameter stored in memory is updated when a proof or counterexample is presented. After some time has passed or enough evidence has been received from the validator. The caller calls the function with the current parameter and timestamp, which is matched against the stored parameter hash and timestamp. They must match and meet some other requirements, e.g. a certain amount of time must have passed and no counterexample must be found. If all requirements are met, the actual work is performed and the record of the parameter is deleted from memory to relieve the memory. If no record is found that matches the input data, the actual function is not executed with the input data.

\begin{figure}
\centering
\includegraphics[scale=.6]{assertion_2}
\caption{Assertion Contract (2)}
\end{figure}

\subsubsection{Validating a parameter}
When a parameter is sent to an validator, the validator runs the offline assertion program with the parameter to find a counterexample. If so, the validator submits the parameter to the blockchain to claim the reward. Otherwise, a computation proof is submitted, which should be automatically generated when the program is executed. A validator interacts with the contract in two ways: announce a counterexample  and submit a proof. The validator must clarify which parameter is verified by submitting the parameter, the address of the caller, and the timestamp. This information is then matched against the records in storage.

\begin{itemize}
\item Submission of proof: After running the program but finding no counterexample, the validator submits a computational proof to receive a reward for running the check. The proof should be unique for each run. Since the offline assertion program is the same for every validators, we need the address of the validator for each parameter to make the proof unique for each validator. This prevents the validator from copying a calculation proof from others. Also, since the proof cannot be stored in the blockchain or it would be too costly, a timestamp is added for the execution of the program to prevent an validator from using the same proof for multiple submission. Therefore, the proof should be generated from the program code. The proof is calculated based on the program provided. Each validator who runs the program enters the parameter, the address of the caller, the timestamp, and the time at which he or she runs the program, as well as his or her address. This information is unique and is used to calculate a unique hash for the checker.
\item Asserting a counterexample: a validator can submit a counterexample and that counterexample is then verified by the contract on the blockchain. If it is correct, there is an award to the validator and the function updates the store accordingly. There are two options: update the status or delete the record.

(Discussion: what happens if the parameter was checked but not executed by the contract caller. It will occupy the memory forever. Since a function is passive in this case, there should be a mode (function) executed by the owner to delete this parameter after some time. Also, the program is executed to check the parameter to find a counterexample. So basically it generates a random number (since it is offline, why do not we run the entire check - safe time) a limited number of proofs while it runs the check).
\end{itemize}
When the normal function is called by the check function, the storage stores the parameter in place of its hash and any other parameters required for the normal function. If certain requirements are met, the function is called when a validator submits the proof.

\section{A Prototype Implementation}
\section{Cost Analysis}
\section{Related work}
\section{Conclusion}
\bibliographystyle{splncs04}
\bibliography{bio}
\end{document}

T here must be of cuorse a way to check whether a paramater has been checked We considor here two case. 
(1) the function is called by the validtor funtion, then 
- addvantiex: the separation is transferent to the user, no need to check if the paramater is correct or not.
- disavanties: Expensive to store the parameter and may other parameter to excute after the assertion parameter is checked. The function is passive then need to make sure that it will be called after sometime.

(2) the function is called saparately. this means user need to call the function validate() first to ask for checking the parameter, then this call will be store in the storage (1) the hash of the parameter , (2) the caller address and timestamp arroundr time then the caller call the assertion () function. This information is used to check the proof or the counterexample) .

We consider here only the call to a assertion function. In the both seseinior (1) and (2), the caller firt need to call assetion () funtion to check her parameter. if the parameter is correct then the finction function(0 is called to perfrom the work. There are two way to call the fuction () by a caller or by the function validate(). This thing is depicted in (1) and (2).

A caller call the assertion () function to sumit the parameter. The parameter then is supporsed to be checked by validators. The information of the parameter need to be stored in oedered to check the proof or conterexample later when a valodator submit them and to know when the actual function is called to perform the work. it is not enough to store the parameter its self since we need to know who is the caller and whay time it is called since a caller can call at many time.  Thus, the store need to storeage incloides in two case
\begin{itemize}
\item if the function is called by the funtion validato. then the information need to submit besied the parameter is also other parameters that need to fetch in the function function(). the information need to be stored are the parameters, the caller address, the time stamstample. as in (1)
\item if it is called by the caller. The function will be called after somethime by a caller then the information to stopre is only the parameter hash, the caller address and the time stime
\end{itemize}

in both case, the record of the parameter need to initial information to absber the progeess of the checking the parameter. e.g how many proof have made, whether a counterexamole is found,..etc

the parameter then  it need to be send to these validators. The information that need to be broachcard includes the parameter, the caller address and the timestamp.  As we have dissuted, there are two ways to do that

\begin{itemize}
\item by caller via a messinge system e.g waku 
      \begin{itemize}
      \item no extral money need, can attached to program to find a counter exacmple and don't need to care about the zise of the program.
      \item the messing system is not offical and there are stll quite many problem with it
      \end{itemize}
\item by a transfer or via a transfer to the owner which attached in the MEDA fiwld. 
\end{itemize}

### 2022-01-10 papers/assertion-contract/paper.tex
Rename papers/assertion_contract/paper.tex to papers/assertion-contract/paper.tex
Update paper.tex

--- 2022-01-10 papers/assertion_contract/paper.tex
@@
 \end{document}
-
-T here must be of cuorse a way to check whether a paramater has been checked We considor here two case. 
-(1) the function is called by the validtor funtion, then 
-- addvantiex: the separation is transferent to the user, no need to check if the paramater is correct or not.
-- disavanties: Expensive to store the parameter and may other parameter to excute after the assertion parameter is checked.
-The function is passive then need to make sure that it will be called after sometime.
-
-(2) the function is called saparately.
-this means user need to call the function validate() first to ask for checking the parameter, then this call will be store in the storage (1) the hash of the parameter , (2) the caller address and timestamp arroundr time then the caller call the assertion () function.
-This information is used to check the proof or the counterexample) .
-
-We consider here only the call to a assertion function.
-In the both seseinior (1) and (2), the caller firt need to call assetion () funtion to check her parameter.
-if the parameter is correct then the finction function(0 is called to perfrom the work.
-There are two way to call the fuction () by a caller or by the function validate().
-This thing is depicted in (1) and (2).
-
-A caller call the assertion () function to sumit the parameter.
-The parameter then is supporsed to be checked by validators.
-The information of the parameter need to be stored in oedered to check the proof or conterexample later when a valodator submit them and to know when the actual function is called to perform the work.
-it is not enough to store the parameter its self since we need to know who is the caller and whay time it is called since a caller can call at many time.
-Thus, the store need to storeage incloides in two case
-\begin{itemize}
-\item if the function is called by the funtion validato.
-then the information need to submit besied the parameter is also other parameters that need to fetch in the function function().
-the information need to be stored are the parameters, the caller address, the time stamstample.
-as in (1)
-\item if it is called by the caller. The function will be called after somethime by a caller then the information to stopre is only the parameter hash, the caller address and the time stime
-\end{itemize}
-
-in both case, the record of the parameter need to initial information to absber the progeess of the checking the parameter. e.g how many proof have made, whether a counterexamole is found,..etc
-
-the parameter then  it need to be send to these validators.
-The information that need to be broachcard includes the parameter, the caller address and the timestamp.
-As we have dissuted, there are two ways to do that
-
-\begin{itemize}
-\item by caller via a messinge system e.g waku 
-      \begin{itemize}
-      \item no extral money need, can attached to program to find a counter exacmple and don't need to care about the zise of the program.
-      \item the messing system is not offical and there are stll quite many problem with it
-      \end{itemize}
-\item by a transfer or via a transfer to the owner which attached in the MEDA fiwld. 
-\end{itemize}

### 2022-01-10 papers/assertion-contract/paper.tex
Add files via upload

@@
 \item  The work function that performs the task with the assumtion that the parameter is valid. 
-\item The validation functions, which have two mode to check and promote either a proof or a counterexample sent by validators.
+\item The validate functions, which have two mode to check and promote either a proof or a counterexample sent by validators.
 \end{itemize}
@@
     \\ validation functions   
-    function validator(...) public {
+    function validate(...) public {
        ...
@@
 \subsubsection{Offline Assertion Program}
-To check the validity of a parameter, each validator independently runs a program that generates a negative formula for the parameter and then selects a random point in the parameter range to find a counterexample.
-The program is intended to run offline from the blockchain network and should be sent to all validators.
-In addition, the program must provide a calculation proof that can be submitted to the blockchain to receive an award.
-This trigger calculation should be generated identically for each run.
-There is more to learn about the program in the following part.
+To check the validity of a parameter, each validator independently runs aassertion program that generates a negation formula for the parameter and then selects a random point in the parameter range to find a counterexample.
+The assertion program should be sent to all validators and should be executed offline from the blockchain network.
+In addition, the program must provide a proof of computation that can be submitted to the blockchain to receive an award.
+This trigger computation proof should be generated identically for each run.
+In the following part, you will learn more about the offline assertion program.
 \begin{figure}
@@
 \includegraphics[scale=.6]{assertion_1}
-\caption{Assertion Contract (1)}
+\caption{Assertion Contract Ptotocol (1)}
 \end{figure}
@@
 \subsection{Roles}
-\subsubsection{Managing the contract and offline assertion program}
+\subsubsection{Managing the contract and offline assertion program.}
 A contract is provided by its owner on the blockchain.
-In addition to the code of the contract on the blockchain, there is the offline assertion program to find a counterexample for a submitted parameter, and this code should be available to all validators.
-Let us discuss two ways to submit this program
+In addition to the code of the contract on the blockchain, there is an offline assertion program to find a counterexample for a submitted parameter, and this code should be available to all validators.
+Let us discuss two ways to distribute this offline assertion program.
 
 \begin{itemize} 
-\item the program code is stored inside the contract code.
-In this case, the code will be available on the blockchain.
-However, it could be expensive to store it on the blockchain, and especially impossible if the program is very large.
-(For discussion: and can be sent as data in a normal transmission).
-\item the program code is stored offline and should always be available to callers/validators on request.
-There are two ways to make it available to validators: (1) the program is stored on a source that the caller/validator can access, or the owner can make it available on request sent to a caller/validator when requested, and (2) when a caller invokes an assertion function, it should send the program to the network via messaging systems such as rakun in Eutherum, or the owner should send it to the network via postcard when deploying the contract, and in this case the interested validator should store it locally.
+\item The program code is stored inside the contract code.
+In this case, the code is available on the blockchain.
+However, it could be expensive to store the code on the blockchain, and especially impossible if the program is very large.
+(For discussion: and can be sent as data in a normal transfer?).
+\item The program code is stored offline and should always be available to callers/validators upon request.
+There are two ways to make it available to validators: (1) the program is stored on a source that can be accessed by the caller/validator, or the owner can make it available on request, which is sent to a caller/validator on request, and (2) when a caller invokes an assertion function, it should send the program to the network via messaging systems such as waku in eutherum, or the owner should broadcast it to the network when deplying the contract, and in this case interested validators should store the code locally.
 \end{itemize}
 
-\subsubsection{Interacting with the smart contract}
-A caller must first pass the parameter, which must be checked before it is passed to the actual code, namely the normal function.
-The parameter then is supporsed to be verified by validators.
-We consider here two ways in which the call to the normal function can be handled after the parameter has been checked.
+\subsubsection{Interacting with the smart contract.}
+A caller must first pass the parameter to an assertion function before passing it for use in an actual code, namely a work function.
+The parameter is then distributed and to be checked by validators.
+We consider here two ways in which the call to the work function can be handled after the parameter has been validated.
 
 \begin{itemize}
-\item The function is called by a caller after the process of checking the parameter is complete (Figure 1).
-There must be a constraint for calling this function.
-For example, the function can be called only after the parameter has been available for verification for a certain time, or there is a fixed number of proofs (computational proof without counterexample) that the parameter has received.
-The main point with this way is that we do not need to store the parameter, only its hash in the storage, and also the other parameters that do not need to be checked can only be submitted when the caller invokes the normal function.
-The caller must also transmit the timestamp when it presents the parameter for checking.
-With the hash of the parameter, the address of the caller, and the timestamp, a search in storage looks for the matching information and constraints to decide whether or not to run the code for the actual performance.
-\item the function is called by the validate function (Figure 2).
+\item The work function is called by a caller after the process of checking the parameter is complete (Figure 1).
+There must be some restrictions on calling this function, for example, the function can be called only after the parameter has been available for verification for a certain time, or there is a fixed number of proofs (computational proof without counterexample) that the parameter has received.
+The main point with this method is that we do not need to store the parameter, only its hash in the storage, and the other parameters that do not need to be checked can also be submitted only when the caller invokes the work function.
+The caller must also transmit the timestamp when it presents the parameter for verification.
+With the hash of the parameter, the address of the caller and the timestamp, a search in the storage looks for the matching information and constraints to decide whether the work function should be executed or not.
+\item The function is called by the validator function (Figure 2).
 The good thing about this method is that the process of validating the parameter and calling the normal function is not visible to the user.
-However, there are two arguments against this way: (1) it is necessary to store the assertion parameter as well as others in memory, which comes at a high cost, and (2) since the function is called from the validation function, there should be a way to ensure that it is called when the parameter is valid and certain conditions are met.
+However, there are two arguments against this way: (1) it is necessary to store the parameter as well as others in storage, which comes at a high cost, and (2) since the function is called from the validate function, there should be a way to ensure that it is called when the parameter is valid and certain conditions are met.
 Also, it might be difficult to deal with timing constraints since these functions are passive.
@@
 
-\paragraph{Submitting the parameter} A caller passes the parameter to be verified by calling an assertion function.
-The function then stores all the necessary information, namely the parameter hash (1) or the parameter (2), the caller's address, and the timestamp as in a record in the storage.
-The record of the parameter, moreover, initial information to observe the progress of the verification of the parameter.
-e.g.
-how many evidences have been presented, whether a counterexample has been found,..etc.
-This information is used to check a proof or  counterexample submitted by a validator, and to decide when a normal function might be called for that parameter.
-The caller can then send this information, along with the offline assertion program, to all validators via a messaging system.
-(Discussion: should the function publish this information on the blockchain via the IDA in a transfer to all examiners as this is costly?).
+\paragraph{Submitting the parameter.} A caller passes the parameter to be checked by calling an assertion function.
+The function then stores all the necessary information, namely the parameter hash in Figure 1 (or the parameter in Figure 2), the caller's address, and the timestamp in memory as if in a record.
+The parameter's record also contains initial information to monitor the progress of the parameter's verification, e.g., how many computational proofs have been presented, whether a counterexample has been found, etc.
+This information is used to review a proof or counterexample presented by a validator, and to decide when a work function can be called for that parameter.
+The caller can then send this information along with the offline assertion program to all validators via a messaging system.
 
-\paragraph{Calling the normal function}
-We consider the case where the nomal function is called by a caller after the parameter has been checked.
-Thus, the caller first passes its parameter to the assertion function and then waits a while to be sure that the parameter is checked.
-The record corresponding to the parameter stored in memory is updated when a proof or counterexample is presented.
-After some time has passed or enough evidence has been received from the validator.
-The caller calls the function with the current parameter and timestamp, which is matched against the stored parameter hash and timestamp.
-They must match and meet some other requirements, e.g.
-a certain amount of time must have passed and no counterexample must be found.
-If all requirements are met, the actual work is performed and the record of the parameter is deleted from memory to relieve the memory.
-If no record is found that matches the input data, the actual function is not executed with the input data.
+(For discussion: should the function publish this information on the blockchain via the IDM in a transfer to all examiners as this is costly?).
+
+\paragraph{Calling a work function.}
+We consider the case where the work function is called by a caller after the parameter has been checked.
+Thus, the caller first passes its parameter to the assertion function and then waits a while to be sure that the parameter has been checked.
+The record corresponding to the parameter stored in the storage is updated when a proof or counterexample is presented.
+After some time has passed or enough proof has been received from the validators.
+The caller invokes the work function with the current parameter and timestamp, which is matched against the stored parameter hash and timestamp.
+They must match and satisfy some other conditions, e.g., a certain amount of time must have passed and no counterexample must be found.
+If all requirements are met, the actual work is done and the record of the parameter is deleted from memory to relieve the storage.
+If no record is found that matches the input data, the actual work with the input data is not performed.
 
@@
 \includegraphics[scale=.6]{assertion_2}
-\caption{Assertion Contract (2)}
+\caption{Assertion Contract Ptotocol(2)}
 \end{figure}
@@
 \subsubsection{Validating a parameter}
-When a parameter is sent to an validator, the validator runs the offline assertion program with the parameter to find a counterexample.
-If so, the validator submits the parameter to the blockchain to claim the reward.
+When a parameter is sent to an validator, the validator runs the offline assertion program to find a counterexample.
+If so, the validator submits the parameter to the blockchain to receive a reward.
 Otherwise, a computation proof is submitted, which should be automatically generated when the program is executed.
-A validator interacts with the contract in two ways: announce a counterexample  and submit a proof.
-The validator must clarify which parameter is verified by submitting the parameter, the address of the caller, and the timestamp.
-This information is then matched against the records in storage.
+A validator interacts with the contract in two ways: he can announce a counterexample and submit a calculation proof.
+The validator must clarify which parameter is being verified by submitting the parameter, the address of the caller, and the timestamp.
+This information is then matched with the records in the storage.
 
-\begin{itemize}
-\item Submission of proof: After running the program but finding no counterexample, the validator submits a computational proof to receive a reward for running the check.
+\paragraph{Submission of proof.} After running the program but finding no counterexample, the validator submits a computational proof to receive a reward for running the check.
 The proof should be unique for each run.
@@
 Also, since the proof cannot be stored in the blockchain or it would be too costly, a timestamp is added for the execution of the program to prevent an validator from using the same proof for multiple submission.
-Therefore, the proof should be generated from the program code.
-The proof is calculated based on the program provided.
+Therefore, the proof should be generated from the program and is calculated based on the parameter's information provided.
 Each validator who runs the program enters the parameter, the address of the caller, the timestamp, and the time at which he or she runs the program, as well as his or her address.
-This information is unique and is used to calculate a unique hash for the checker.
-\item Asserting a counterexample: a validator can submit a counterexample and that counterexample is then verified by the contract on the blockchain.
+This information is used to calculate an unique computation proof.
+\paragraph{Asserting a counterexample.} a validator can submit a counterexample and that counterexample is then verified by the contract on the blockchain.
 If it is correct, there is an award to the validator and the function updates the store accordingly.
@@
 
-(Discussion: what happens if the parameter was checked but not executed by the contract caller.
+(For discussion: what happens if the parameter was checked but not executed by the contract caller.
 It will occupy the memory forever.
@@
 So basically it generates a random number (since it is offline, why do not we run the entire check - safe time) a limited number of proofs while it runs the check).
-\end{itemize}
+
 When the normal function is called by the check function, the storage stores the parameter in place of its hash and any other parameters required for the normal function.

### 2022-01-11 papers/assertion-contract/paper.tex
Add files via upload

@@
 If any of the validators finds a violation of the assertion, the final transaction (call) is aborted.
-In our approach, the validator make an effor to find a counterexample for the assertion offline.
+In our approach, the validator make an effor to find a counterexample for the assertion off-chain.
 Therefore, the validators interact with the smart contract to submit a  counterexample or a computation proof through smart contract function calls.
@@
 
-\subsubsection{Offline Assertion Program}
+\subsubsection{Off-chain Assertion Program}
 To check the validity of a parameter, each validator independently runs aassertion program that generates a negation formula for the parameter and then selects a random point in the parameter range to find a counterexample.
-The assertion program should be sent to all validators and should be executed offline from the blockchain network.
+The assertion program should be sent to all validators and should be executed off-chain from the blockchain network.
 In addition, the program must provide a proof of computation that can be submitted to the blockchain to receive an award.
 This trigger computation proof should be generated identically for each run.
-In the following part, you will learn more about the offline assertion program.
+In the following part, you will learn more about the off-chain assertion program.
 \begin{figure}
@@
 \subsection{Roles}
-\subsubsection{Managing the contract and offline assertion program.}
+\subsubsection{Managing the contract and off-chain assertion program.}
 A contract is provided by its owner on the blockchain.
-In addition to the code of the contract on the blockchain, there is an offline assertion program to find a counterexample for a submitted parameter, and this code should be available to all validators.
-Let us discuss two ways to distribute this offline assertion program.
+In addition to the code of the contract on the blockchain, there is an off-chain assertion program to find a counterexample for a submitted parameter, and this code should be available to all validators.
+Let us discuss two ways to distribute this off-chain assertion program.
 
@@
 (For discussion: and can be sent as data in a normal transfer?).
-\item The program code is stored offline and should always be available to callers/validators upon request.
+\item The program code is stored off-chain and should always be available to callers/validators upon request.
 There are two ways to make it available to validators: (1) the program is stored on a source that can be accessed by the caller/validator, or the owner can make it available on request, which is sent to a caller/validator on request, and (2) when a caller invokes an assertion function, it should send the program to the network via messaging systems such as waku in eutherum, or the owner should broadcast it to the network when deplying the contract, and in this case interested validators should store the code locally.
@@
 This information is used to review a proof or counterexample presented by a validator, and to decide when a work function can be called for that parameter.
-The caller can then send this information along with the offline assertion program to all validators via a messaging system.
+The caller can then send this information along with the off-chain assertion program to all validators via a messaging system.
 
@@
 \subsubsection{Validating a parameter}
-When a parameter is sent to an validator, the validator runs the offline assertion program to find a counterexample.
+When a parameter is sent to an validator, the validator runs the off-chain assertion program to find a counterexample.
 If so, the validator submits the parameter to the blockchain to receive a reward.
@@
 The proof should be unique for each run.
-Since the offline assertion program is the same for every validators, we need the address of the validator for each parameter to make the proof unique for each validator.
+Since the off-chain assertion program is the same for every validators, we need the address of the validator for each parameter to make the proof unique for each validator.
 This prevents the validator from copying a calculation proof from others.
@@
 This information is used to calculate an unique computation proof.
-\paragraph{Asserting a counterexample.} a validator can submit a counterexample and that counterexample is then verified by the contract on the blockchain.
+\paragraph{Asserting a counterexample.} a validator can submit a counterexample and the counterexample is then checked by the contract on the blockchain.
 If it is correct, there is an award to the validator and the function updates the store accordingly.
@@
 Also, the program is executed to check the parameter to find a counterexample.
-So basically it generates a random number (since it is offline, why do not we run the entire check - safe time) a limited number of proofs while it runs the check).
+So basically it generates a random number (since it is off-chain, why do not we run the entire check - safe time) a limited number of proofs while it runs the check).
 
-When the normal function is called by the check function, the storage stores the parameter in place of its hash and any other parameters required for the normal function.
+When the normal function is called by the validate function, the storage stores the parameter in place of its hash and any other parameters required for the normal function.
 If certain requirements are met, the function is called when a validator submits the proof.

### 2022-02-16 papers/assertion-contract/appendix.tex
Add files via upload

\appendix
\chapter{Assertion Grammar in EBNF}\label{apx:grammar}
The following two versions of a grammar in extended Backus-Naur form (EBNF) implement the prefix and infix notations for the assertion syntax.

\section{Prefix Notation}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=,
				 caption=Assertion grammar with prefix notation]{assertion_grammar_prefix.txt}

\section{Infix Notation}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=,
				 caption=Assertion grammar with infix notation]{assertion_grammar_infix.txt}

### 2022-02-16 papers/assertion-contract/paper.tex
Add files via upload

@@
 \usepackage{listings}
-\lstdefinelanguage{michelson}{
-  % basicstyle=\ttfamily,
-  basicstyle=\fontsize{8}{9.6}\selectfont,
-  morekeywords={parameter,storage,or,unit,mutez,pair,bool,address}, sensitive=false,
-  morecomment=[l]{\#},
-  morecomment=[s]{/*}{*/},
-  morestring=[b]",
-}
-\lstset{
-  language=Caml,
-  captionpos=b,
-  aboveskip=-\smallskipamount,
-  belowskip=-\smallskipamount,
-  belowcaptionskip=0pt,
-  basicstyle=\fontsize{8}{9.6}\selectfont,
-  morekeywords={val}
-}
+\usepackage{titling}
 
 \input{macros}
+%\input{setup}
+
+% ------------------- colors -------------------
+\definecolor{darkgreen}{rgb}{0.0, 0.5, 0.0}
+\definecolor{UniBlue}{RGB}{0, 74, 153}
+\definecolor{UniRed}{RGB}{193, 0, 42}
+\definecolor{UniGrey}{RGB}{154, 155, 156}
+\definecolor{cverbbg}{gray}{0.93}
+
+\newcommand{\todo}[1]{\textbf{\textcolor{red}{(TODO: #1)}}}
 
@@
 \begin{abstract}
-
  \keywords{}
@@
 random $n$ in the range $2 \le n \le 
-\sqrt p$ and checking whether $(p \mathbin{\%} n) = 0$. If the remainder is $0$, the
-validator found a counterexample.
+\sqrt p$ and checking whether $(p \mathbin{\%} n) = 0$. If the remainder is $0$, the validator found a counterexample.
 
@@
 \begin{itemize}
-   \item the smart contract owner deploys and manages the smart contract, 
-   \item the callers invoke the smart contract functions, and 
-   \item the validators are involved in validating a parameter submitted by a caller. 
+   \item the owner deploys and manages a assertion contract, 
+   \item the callers invoke a assertion contract, and 
+   \item the validators are involved in validating the parameters. 
 \end{itemize}
 
-\noindent A caller invoking a function submit the parameter that needs to be validated to the blockchain.
-The parameter is forwarded to all nodes as validators in the network, which then validate it.
-Our method is depicted in Figure 1 (2).
+\noindent A caller submit a parameter that needs to be validated to the blockchain.
+The parameter is  then forwarded to all nodes as validators in the network, which then validate it.
+After the parameter is validated, the actual work that use the parameter is executed.
 
-Finding a counterexample for the assertion and announcing the result to the blockchain costs in terms of energy (computing power) and gas.
-There could be the case that it is very rare to find a counterexample, because a caller tries not to pass an unvalidated parameter.
-In this case, we need to encourage all validators running the program to validate the assertion.
-Therefore, there are two rewards in the form of cryptocurrency in order to motivate the validators to participate: (1) for a  counterexample found and (2) for a computational proof.
-It requires a way to check a computation proof provided by a validator that proves that the validator actually run the program to find a counterfeit for the assertion, but none is found.
+Finding a counterexample for an assertion and announcing the result to the blockchain costs in terms of energy (computing power) and gas.
+There could be the case that it is very rare to find a counterexample, because a caller tries not to pass an unvalid parameter to the blockchain.
+In this case, we need to encourage all validators running the program to validate the assertion even though no counterexample may be found.
+Therefore, there are two way to reward validators in the form of cryptocurrency in order to motivate the validators to participate: (1) for a  counterexample found and (2) for a computational proof that proves that the validator actually run the program to find a counterfeit for the assertion, but none is found.
 
-If any of the validators finds a violation of the assertion, the final transaction (call) is aborted.
+If any of the validators finds a violation of the assertion, the final call to the actual work is aborted.
 In our approach, the validator make an effor to find a counterexample for the assertion off-chain.
 Therefore, the validators interact with the smart contract to submit a  counterexample or a computation proof through smart contract function calls.
-\subsection{Smart Contract's Functions and Storage}
-\subsubsection{Functions}
-There can be several functions in a contract, we consider here the functions where one of the parameters must be validated.
-Because the parameter must be checked before the actual work can be done, we separate it into two functions: a caller first invokes an assertion function to pass the parameter for  verification and after the parameter is verified, a normal function with a assumion that a paramete is valid can be called to do the actual work.
-A contract must contain the following three types of functions:
+
+Because the parameter must be validated before the actual work can be done, a caller first invokes an assertion function in the on-chain validate contract to pass the parameter for  verification and after the parameter is verified, a work contract that performs the task with the assumption that the parameter is valid can be called.
+The work contract can only called by the on-chain validate contract when some conditions are satisfied.
+
+\paragraph{On-chain validation contract.} An on-chain validation contract must contain the following two functions:
 
 \begin{itemize}
-\item The assertion functions, where callers submit their parameters to be verified, which are then distributed to all validators. 
-\item  The work function that performs the task with the assumtion that the parameter is valid. 
-\item The validate functions, which have two mode to check and promote either a proof or a counterexample sent by validators.
+\item the assertion function, where callers submit their parameters to be verified, which are then distributed to all validators. 
+\item the on/off-chain assertion (validate function) to check and promote either a computational proof or a counterexample sent by validators.
 \end{itemize}
 
-For example, the Example contract in which there is a work function that  takes a prime number as one of its parameters would include these three types of functions  as follows:
+When a caller submits a parameter for validation, the parameter and associated information must be stored for the validation process.
+Since the parameter can be very large, we suggest storing only its hash.
+The hash is still sufficient to validate the validation process.
+The address of the caller should also be stored, and perhaps the timestamp indicating the approximate time the caller submitted the parameter.
+For each submission, there should be a corresponding record containing the associated data and validation status, such as the number of proofs received or the status if there is a counterexample.
+It could be the case that many parameters are submitted, then it may be useful to delete the record after the processing is completed with the parameter.
+There are two possible data structures for storing such records: map and array.
 
-\begin{lstlisting}[numbers=none]
-
-contract Example {
-    \\ storage declarations
-    ...
-    \\ assertion functions
-    function assertion(int p) public {
-       ...
-    } 
-    \\ work functions
-    function work(int p, ...) public {
-       ...
-    }
-    \\ validation functions   
-    function validate(...) public {
-       ...
-    }
-    \\ other functions
-    ...
-}
-\end{lstlisting}
-
-%question: map or array and how to delete
-
-\subsubsection{Storage}
-When a caller submits a parameter to be validated, the parameter and its related information must be stored in storage for the validation process.
-For each submission, there should be a corresponding record, which contains the following data: (1) the parameter (or its hash), the caller's address, the timestamp indicating the approximate time when the caller submits the parameter, and the validating status containing such as the number of proofs it has received, the status if there is a counterexample.
-It could be the case that many parameters are submitted, then it makes sense to delete the data set after the processing with the parameter is completed.
-The selected data structure should be suitable for deletion both in terms of gas and reference to other records.
-There are two possible cadicated data type for store such records : map and array.
-
-For avobed example contract, assuming that a caller can only submit one parameter at a time, we can use a map that maps a caller address with the parameter hash and timestamp.
+For example, if we assume that a caller can submit only one parameter at a time, we can use a map that associates the caller's address with the parameter's hash and timestamp.
 
@@
    struct Parameter {
-        uint p_hash;
-        uint timestamp;
+        bytes32 p_hash;
+        uint256 timestamp;
     }
     mapping (address => Parameter) public parameters;
+\end{lstlisting}
+
+\paragraph{On-chain work contract.}  The working contact can only be invoked by the on-chain validation contract after the parameter has been validated if no counterexample is found.
+The actual work is then performed with the passed parameter.
+
+\begin{lstlisting}[numbers=none]
+
+contract Work {
+
+    function work(...) public {
+       ...
+    } 
+}
+\end{lstlisting}
+
+\paragraph{Off-chain validate contract.}
+To check the validity of a parameter, each validator independently executes an off-chain validation contract that executes the same code on/off-chain assertion (the validate function) as in the on-chain validation contract.
+The on/off-chain validation should be sent to all validators and executed outside the blockchain network.
+The on/off-chain assertion (the validation function) in the on/off-chain validation plays the main role in our approach.
+It contains the negation formulas for parameters and takes a seed and a parameter as input.
+The seed is used to compute a random number to check the negation formulas of the parameter.
+The result of the calculation can be a counterexample, an award computation proof, or a non-award computation proof.
+
+A validator might try to run the off-chain validation contract many times to find either a counterexample or a proof of the price calculation.
+There could be many attempts before he receives an award.
+In the case of a non-award, the validator can run the code again with a different random number.
+If a counterexample or award is found, the validator passes the seed and parameter to the on-chain validation contract, which runs the same code on/off-chain assertion and must end up with the same result as the counterexample or award.
+
+\subsection{Managing on/off-chain contracts.}
+An on/off-chain assertion and on/off-chain validation contracts are provided by their owner.
+The owner deploy the on-chain validation contract and the work contract on the blockchain.
+The owner plays the main role in the design of the contracts.
+
+The on/off-chain assertion and off-chain validation contract are stored off the blockchain and should be available to callers/validators upon request at any time.
+There are two ways to make them available to validators: (1) the codes are stored on a repository that callers/validators can access, or the owner can make it available upon request sent to a caller/validator upon request, and (2) an owner/caller sends it to the network via messaging systems such as Waku in eutherum.
+The owners should send it to the network if they deploy the on-chain contracts, and in this case interested validators should store the code locally.
+In the same way, callers send it when they invoke an assertion function in the on-chain validation contract on the blockchain.
+%\end{itemize}
+
+\begin{figure}
+\centering
+\includegraphics[scale=.8]{owner}
+\caption{Managing on/off-chain assertion contracts.}
+\end{figure}
+
+\subsection{Interacting with the smart contract.}
+A caller must first submit the parameter to an assertion function in the on-chain validation contract before it can be used in the work contract.
+The parameter is then distributed and validated by validators.
+The process of validating the parameter and invoking the working contract is transparent to the user.
+It is sufficient to store the hash of the parameter, and the parameter is transmitted when a validator invokes the on/off-chain assertion in the on-chain validation contract on the blockchain.
+Since the work contract is invoked by the on-chain validation contract, there should be a way to ensure that it is only invoked when the parameter is valid and certain conditions are met, e.g., when it has received a sufficient number of proofs.
+
+A caller may need to supply some tokens for validating the parameter and calling the work function.
+In some cases where the validation process does not have a counterexample but does not meet some conditions, e.g., does not receive enough proofs from the validators, the owner has to do some tasks here to handle the refund since the functions in the smart contract are passive.
+Some time contracts could be used for this purpose.
+
+\begin{figure}
+\centering
+\includegraphics[scale=.6]{caller}
+\caption{Submitting a parameter to the on-chain assertion contract.}
+\end{figure}
+
+\paragraph{Submitting a parameter.} A caller passes the parameter to be checked by calling an assertion function.
+The function then stores all necessary information, namely the hash of the parameter, the address of the caller, and possibly the timestamp, as if in a record.
+The parameter's record also contains initial information for monitoring the progress of the parameter's verification, e.g., how many computational proofs have been presented, whether a counterexample has been found, etc.
+This information is used to review a proof or counterexample presented by a validator, and to decide when a work function can be called for that parameter.
+The caller can then send this information, along with the on/off-chain assertion and off-chain validation contract, to all validators via a messaging system.
+
+\subsection{Validating a parameter}
+When a parameter is sent to a validator, the validator executes the off-chain validation contract, which includes an on/off-chain assertion, to find a counterexample.
+If so, the validator submits the counterexample to the blockchain to receive a reward.
+Otherwise, a computation proof is submitted, which should be automatically generated when the program is executed.
+A validator interacts with the contract in two ways: it can announce a counterexample and submit a computation proof.
+The validator may need to clarify which parameter is being checked by submitting the parameter and the address of the caller, and possibly the timestamp.
+This information is then matched against the records in the storage.
+Since the on/off chain assertion is the same for every validator, we may need the address of the validator for each parameter to make the proof unique for each validator.
+A random number is combined with the validator's address to create a seed that is used to compute a random point in the parameter range to verify the validation of the parameter.
+This prevents the validator from copying a calculation proof from others.
+With this information, a validator performs the off-chain validation contract, i.e., the on/off-chain assertion (validate function).
+There can be three different outcomes: a counterexample, an award, or a non-award.
+If it is a counterexample or an award, the validator passes the seed to the blockchain, i.e., it calls the on-chain validation contract on the chain, which then executes basically the same code as the on/off-chain assertion.
+If the on-chain result is the same, the validator gets the reward.
+If the off-chain validation result is not correct, the validator can rerun the off-chain validation.
+We could store these proofs information on the storage until the processing of the parameter is complete to prevent multiple submissions by a validator.
+
+\paragraph{Submiting of a proof/a counterexample.} After executing the off-chain validation contract, the validator may submit a computational proof or counterexample to receive a reward.
+The submission contains the random number, the address of the validator, the parameter, and possibly other information.
+These are then used to calculate the seed, which then goes into the on/off-chain assertion along with the parameter.
+If the result is correct, there is an award to the validator and the function updates the record in the storage accordingly.
+The work contract is called when a validator submits the record.
+When  certain requirements are met.
+
+\begin{figure}
+\centering
+\includegraphics[scale=.8]{validator}
+\caption{Submitting a proof/a counterexample.}
+\end{figure}
+
+\paragraph{Calling a work function.}
+The work function is called by the on-chain validation contract once the parameter has been verified.
+Thus, the caller first passes its parameter to the assertion function and then waits a while to be sure that the parameter has been verified.
+The record corresponding to the parameter stored in the storage is updated when a proof or counterexample is presented.
+Some conditions must be met, e.g., after a certain amount of time has passed or enough evidence has been received from the validators.
+If an examiner submits the counterexample, the parameter is aborted from validating the process and the work function is never called.
+Otherwise, the work function is called when the computation proof is submitted and all conditions are met.
+
+ The on-chain validation contract calls the work contract with the current parameter and timestamp matched against the stored parameter hash and timestamp.
+They must match and satisfy some other conditions, such as a certain amount of time must have passed and no counterexample must be found.
+If all conditions are met, the actual work is done and the record of the parameter is deleted from memory to relieve the storage.
+If no record is found that matches the input data, the actual work with the input data is not performed.
+The work contract only allows the call from the on-chain validation contract.
+
+\section{Domain Specification Language for Assertion}
+We define a domain-specific high-level
+language to express assertions.
+\subsection{Assertion Grammar}
+The syntax of this language is described in two versions by the grammars: prefix and infix. The parser currently supports the prefix notation and correct
+operator precedences must be handled explicitly with parentheses. The syntax is inspired by OCaml and uses the same type notations as Michelson.
+
+An assertion begins with the keyword entrypoint and a signature consisting of an optional tag, denoted by \%, followed by a parameter pattern.
+Parameter patterns are similar to patterns in OCaml — they are templates that match shapes of data structures and bind identifiers to the components of them.
+The given parameter pattern must match exactly the parameter type of the entrypoint it is associated with.
+The body of an assertion can
+contain a nesting of quantifiers and conditions around exactly one assert expression, which tests a property. Conditions can be used to restrict the
+quantification domains or to impose any other constraints. For completeness,
+the existential quantifier is already included in the grammar, however the
+current version of the pipeline will reject any assertions containing it.
+How the assertions are associated with the respective entrypoint of the
+parent contract, depends on the Smart Contract language. In the case of
+Solidity, a tag that mirrors the function name is enough to link assertion and
+entrypoint. In Michelson contracts, on the other hand, entrypoints can be
+anonymous. Therefore, the assertions are linked to the entrypoints through
+the tags, the parameter type or both.
+
+\subsubsection{Parameter patterns.}
+Listing gives an overview of the parameter patterns supported in the assertion language.
+\begin{lstlisting}[numbers=none]
+
+< pattern > ::=
+	| '_ '
+	| nil
+	| none
+	| ( IDENT : < type >)
+	| IDENT
+	| ( pair < pattern > < pattern >)
+	| ( left < pattern >)
+	| ( right < pattern >)
+	| ( cons < pattern > < pattern >)
+	| ( some < pattern >)
 
@@
 
-The contents of the storage are divided into two parts: (1) normal data for the operating of the smart contract and (2) assertion data, which stores all records of the submitted parameters that need to be validated.
+\begin{lstlisting}[numbers=none]
 
-\subsubsection{Off-chain Assertion Program}
-To check the validity of a parameter, each validator independently runs aassertion program that generates a negation formula for the parameter and then selects a random point in the parameter range to find a counterexample.
-The assertion program should be sent to all validators and should be executed off-chain from the blockchain network.
-In addition, the program must provide a proof of computation that can be submitted to the blockchain to receive an award.
-This trigger computation proof should be generated identically for each run.
-In the following part, you will learn more about the off-chain assertion program.
-\begin{figure}
-\centering
-\includegraphics[scale=.6]{assertion_1}
-\caption{Assertion Contract Ptotocol (1)}
-\end{figure}
+( entrypoint % g ( pair ( cons a as ) _ ) ...)
+\end{lstlisting}
 
-\subsection{Roles}
-\subsubsection{Managing the contract and off-chain assertion program.}
-A contract is provided by its owner on the blockchain.
-In addition to the code of the contract on the blockchain, there is an off-chain assertion program to find a counterexample for a submitted parameter, and this code should be available to all validators.
-Let us discuss two ways to distribute this off-chain assertion program.
+AST
 
-\begin{itemize} 
-\item The program code is stored inside the contract code.
-In this case, the code is available on the blockchain.
-However, it could be expensive to store the code on the blockchain, and especially impossible if the program is very large.
-(For discussion: and can be sent as data in a normal transfer?).
-\item The program code is stored off-chain and should always be available to callers/validators upon request.
-There are two ways to make it available to validators: (1) the program is stored on a source that can be accessed by the caller/validator, or the owner can make it available on request, which is sent to a caller/validator on request, and (2) when a caller invokes an assertion function, it should send the program to the network via messaging systems such as waku in eutherum, or the owner should broadcast it to the network when deplying the contract, and in this case interested validators should store the code locally.
-\end{itemize}
+\begin{lstlisting}[numbers=none]
 
-\subsubsection{Interacting with the smart contract.}
-A caller must first pass the parameter to an assertion function before passing it for use in an actual code, namely a work function.
-The parameter is then distributed and to be checked by validators.
-We consider here two ways in which the call to the work function can be handled after the parameter has been validated.
+type ast =
+{ entrypoint : string option * pattern ; body : assertion }
 
-\begin{itemize}
-\item The work function is called by a caller after the process of checking the parameter is complete (Figure 1).
-There must be some restrictions on calling this function, for example, the function can be called only after the parameter has been available for verification for a certain time, or there is a fixed number of proofs (computational proof without counterexample) that the parameter has received.
-The main point with this method is that we do not need to store the parameter, only its hash in the storage, and the other parameters that do not need to be checked can also be submitted only when the caller invokes the work function.
-The caller must also transmit the timestamp when it presents the parameter for verification.
-With the hash of the parameter, the address of the caller and the timestamp, a search in the storage looks for the matching information and constraints to decide whether the work function should be executed or not.
-\item The function is called by the validator function (Figure 2).
-The good thing about this method is that the process of validating the parameter and calling the normal function is not visible to the user.
-However, there are two arguments against this way: (1) it is necessary to store the parameter as well as others in storage, which comes at a high cost, and (2) since the function is called from the validate function, there should be a way to ensure that it is called when the parameter is valid and certain conditions are met.
-Also, it might be difficult to deal with timing constraints since these functions are passive.
-\end{itemize}
+\end{lstlisting}
 
-\paragraph{Submitting the parameter.} A caller passes the parameter to be checked by calling an assertion function.
-The function then stores all the necessary information, namely the parameter hash in Figure 1 (or the parameter in Figure 2), the caller's address, and the timestamp in memory as if in a record.
-The parameter's record also contains initial information to monitor the progress of the parameter's verification, e.g., how many computational proofs have been presented, whether a counterexample has been found, etc.
-This information is used to review a proof or counterexample presented by a validator, and to decide when a work function can be called for that parameter.
-The caller can then send this information along with the off-chain assertion program to all validators via a messaging system.
+\subsection{Assertion Semantic}
+The validators are trying to solve the following formula in a distributed form.
 
-(For discussion: should the function publish this information on the blockchain via the IDM in a transfer to all examiners as this is costly?).
+\begin{gather}
+  \label{eq:2}
+  \exists i \in D_{i}. P_{i}
+\end{gather}
 
-\paragraph{Calling a work function.}
-We consider the case where the work function is called by a caller after the parameter has been checked.
-Thus, the caller first passes its parameter to the assertion function and then waits a while to be sure that the parameter has been checked.
-The record corresponding to the parameter stored in the storage is updated when a proof or counterexample is presented.
-After some time has passed or enough proof has been received from the validators.
-The caller invokes the work function with the current parameter and timestamp, which is matched against the stored parameter hash and timestamp.
-They must match and satisfy some other conditions, e.g., a certain amount of time must have passed and no counterexample must be found.
-If all requirements are met, the actual work is done and the record of the parameter is deleted from memory to relieve the storage.
-If no record is found that matches the input data, the actual work with the input data is not performed.
+\noindent The verification attempt requires to search for $i$ in the domain $D$ such that $P_{i}$, called a counterexample (or proof).
+For each distributed trial, each validator chooses a random $i$ $\in$ $D$ and checks $P_{i}$.
+The formula can be extended to multiple domains $D_{i}$, ..., $D_{k}$.
 
-\begin{figure}
-\centering
-\includegraphics[scale=.6]{assertion_2}
-\caption{Assertion Contract Ptotocol(2)}
-\end{figure}
+\begin{gather}
+  \label{eq:2}
+\exists i \in D_{i}, \exists j \in D_{j}, ..., \exists k \in D_{k}. P_{i, j, ...,k}
+\end{gather}
 
-\subsubsection{Validating a parameter}
-When a parameter is sent to an validator, the validator runs the off-chain assertion program to find a counterexample.
-If so, the validator submits the parameter to the blockchain to receive a reward.
-Otherwise, a computation proof is submitted, which should be automatically generated when the program is executed.
-A validator interacts with the contract in two ways: he can announce a counterexample and submit a calculation proof.
-The validator must clarify which parameter is being verified by submitting the parameter, the address of the caller, and the timestamp.
-This information is then matched with the records in the storage.
+\subsubsection{Transformer. }
+An assertion is formalized in the DSL. The formula is then transferred to its negation formula. 
+\begin{gather}
+  \label{eq:2}
+\neg (\forall i \in D_{i}. P_{i}) \equiv \exists i \in D_{i}. \neg P_{i}
+\end{gather}
 
-\paragraph{Submission of proof.} After running the program but finding no counterexample, the validator submits a computational proof to receive a reward for running the check.
-The proof should be unique for each run.
-Since the off-chain assertion program is the same for every validators, we need the address of the validator for each parameter to make the proof unique for each validator.
-This prevents the validator from copying a calculation proof from others.
-Also, since the proof cannot be stored in the blockchain or it would be too costly, a timestamp is added for the execution of the program to prevent an validator from using the same proof for multiple submission.
-Therefore, the proof should be generated from the program and is calculated based on the parameter's information provided.
-Each validator who runs the program enters the parameter, the address of the caller, the timestamp, and the time at which he or she runs the program, as well as his or her address.
-This information is used to calculate an unique computation proof.
-\paragraph{Asserting a counterexample.} a validator can submit a counterexample and the counterexample is then checked by the contract on the blockchain.
-If it is correct, there is an award to the validator and the function updates the store accordingly.
-There are two options: update the status or delete the record.
+\noindent Given an assertion
+\begin{gather}
+  \label{eq:2}
+\forall i \in D_{i},  \forall j \in D_{j},  ..., \forall k \in D_{k}. P_{i, j, ...,k}
+\end{gather}
 
-(For discussion: what happens if the parameter was checked but not executed by the contract caller.
-It will occupy the memory forever.
-Since a function is passive in this case, there should be a mode (function) executed by the owner to delete this parameter after some time.
-Also, the program is executed to check the parameter to find a counterexample.
-So basically it generates a random number (since it is off-chain, why do not we run the entire check - safe time) a limited number of proofs while it runs the check).
+\noindent it is then transformed to its negation, which is distributed to be verified by validators.
 
-When the normal function is called by the validate function, the storage stores the parameter in place of its hash and any other parameters required for the normal function.
-If certain requirements are met, the function is called when a validator submits the proof.
+\begin{gather}
+  \label{eq:2}
+\exists i \in D_{i},  \exists j \in D_{j},  ..., \exists k \in D_{k}. \neg P_{i, j, ...,k}
+\end{gather}
+
+%(2) For nested quantifiers: a formula that may contain one (or more ''forall" qualifier) then all of these ''forall" quantifiers is converted to ''exist" and all ''exist" quantifiers are kept the same and negative the predicate.
+%\begin{gather}
+%  \label{eq:2}
+%\forall i \in D_{i}, \exists j \in D_{j}, ..., \exists k \in D_{k}. (P_{i, j, ...,k})
+%\end{gather}
+
+%\begin{gather}
+%  \label{eq:2}
+%\exists i \in D_{i}, \exists j \in D_{j}, ..., \exists k \in D_{k}. \neg (P_{i, j, ...,k})
+%\end{gather}
+
+\subsubsection{Converter.} The main actor in our method is the on/off-chain assertion contract, which receives the parameter and a seed as input.
+The contract then generates a random number that is associated with a variable in the predicate $\neg P$.
+The result can be a counterexample, a computational proof with reward, or a computational proof without reward.
+A converter takes the AST of an assertion (AST for its negation) after the transformer step and returns the on/off-chain assertion contract written in Solidity (Michelson).
+To perform the conversion automatically, we restrict the semantics of the DSL.
+Variables are specified with \texttt{forall} quantifiers, which are then followed by \texttt{if} statements defining the scope of the variable.
+For example, the following assertion specifies the parameter \texttt{a} of type \texttt{int} for an entry point \texttt{prime}.
+The next line defines the variable \texttt{a} of type \texttt{int} and its range is defined in the next \texttt{if} statement, namely [2 a/2].
+Finally, the assertion is declared.
+
+\begin{lstlisting}[numbers=none]
+
+(entrypoint % prime (a : int)
+   (forall (n : int)
+         (if (and (ge 2 n) (le n (div a 2)))
+              (assert (not (eq (mod a n) 0))))))
+
+\end{lstlisting}
+
+%, which then is checked   For the implementation of the current method, the syntax support any type of parameter, but the conversion supports the sematic for some typical types.
+Namely $i$ can be identified with a number.
+in deep the domain, $D$ should be able to associate with a natural number.
+For this end, a validator submits a seed that is then used to calculate $i$ that detects $P_{i}$.
+For example, arrays of any type or strings that is an array of characters.
+There could be several properties of natural numbers as primes, even, old, co-primes, square numbers, ..etc.
+for array $i$ could be used to detect the element of an array (or character of string).
+In some cases, when the formula is $\forall$ i $\in$ D.
+($P_{i}$).
+The formula could be encoded an array of predicates.
+after an assertion is transferred to distributed form to be distributed.
+The most important in our approach is to design the validator contract that used both on-chain and off-chain computation.
+Our conversion converts an assertion to an on/off-chain assertion file that is used for validators to check a randomly chosen i.
+although our method and the assertion transformer works with all decide domain D.
+The convention will only work if the D is related to a natural number.
+Assumes that the range of a variable is 
+\begin{displaymath}
+r = [a, b] \land (b-a) > 0
+\end{displaymath}
+
+\noindent and a seed $s$, then the random number can be generate by
+
+\begin{displaymath}
+n = s / (b - a) + a.
+\end{displaymath}
+
+\noindent For the above assertion, we have  
+\begin{displaymath}
+r = [2 , a / 2] \land (a / 2 - 2) >= 0. 
+\end{displaymath}
+
+\noindent Given a random seed s, the $n$ could be generate by $s$.
+
+\begin{gather}
+n = s / (a / 2 - 2) + 2.
+\end{gather}
+
+The Converter generate a on/off-chain assertion program in Solidity as the follows.
+
+\begin{lstlisting}[numbers=none]
+
+pragma solidity >=0.7.0 <0.9.0;
+
+/**
+ * On/off-chain assertion contract 
+ * to check counterexamples/computation proofs
+ */
+contract Validator{
+
+    /**
+    * The difficulty for a computation proof
+    */
+    uint diff = 1;
+    uint public target = 2 ** (256 - diff);
+
+    /**
+    * The result: 0 = non-award, 1 = proof, 2 = counterexample
+    */
+
+    function validate(uint p, uint seed) 
+    public view returns (uint) {
+        uint range = p / 2 - 2; 
+        uint r = seed % range + 2;
+        uint cal = p % r;
+
+        uint result = 0; // an non-award computation proof 
+        if (cal == 0)  
+            result = 2; // a counterexample
+        else 
+            {
+                uint result_target = 
+                    uint (keccak256(abi.encodePacked(seed, cal)));
+                if (result_target <= target) 
+                    result = 1; // a computation proof    
+            }
+        return result;           
+    }
+}
+
+\end{lstlisting}
+
+For sorted array
+
+\begin{lstlisting}[numbers=none]
+
+(entrypoint % array (a : (list int))
+   (forall (n : int)
+      (forall (m : int)
+         (if (and (ge n 1) (le n (size a)))
+            (if (and (ge m 0) (lt m n))
+                  (assert (le (nth a n) (nth a m))))))))
+
+\end{lstlisting}
+
+\noindent We have:
+
+$r_{n}$ = [1, size a] with (size a - 1 $>$ 0)
+
+$r_{m}$ = [0, n] with (n - 0 $>$ 0)
+
+\begin{lstlisting}[numbers=none]
+
+pragma solidity >=0.7.0 <0.9.0;
+
+/**
+ * On/off-chain assertion contract 
+ * to check counterexamples/computation proofs
+ */
+contract Validator{
+
+    /**
+    * The difficulty for a computation proof
+    */
+    uint diff = 1;
+    uint public target = 2 ** (256 - diff);
+
+    /**
+    * The result: 0 = non-award, 1 = proof, 2 = counterexample
+    */
+
+    function validate(uint[] memory p, uint seed)
+    public view returns (uint) {
+        uint range_1 = p.length - 1; 
+        require(range_1 > 0, "invalid range");
+        uint n = seed_i % range_1 + 1;
+        uint range_2 = n;
+        require(range_2 > 0, "invalid range");
+        uint m = seed_j % range_2 ;
+
+        uint cal_1 = p[m];
+        uint cal_2 = p[n];
+
+        uint result = 0; // an non-award computation proof 
+        if (p[m] > p[n])  
+            result = 2; // a counterexample
+        else 
+            {
+            uint result_target = 
+                 int (keccak256(abi.encodePacked(seed, cal_1, cal_2)));
+            if (result_target <= target) 
+                result = 1; // a computation proof      
+        }             
+        return result;           
+    }
+}
+
+\end{lstlisting}
+
+For a heap
+
+\begin{lstlisting}[numbers=none]
+
+(entrypoint % heap (a : (list int))
+   (forall (n : int)
+         (if (and (ge n 1) (le n (size a)))
+                  (assert (lt (nth a n) (nth a (div (sub n 1) 2)))))))
+\end{lstlisting}
+
+\noindent We have:
+
+$r$ = [1, size a] with (size a - 1 $>$ 0)
+
+\begin{lstlisting}[numbers=none]
+pragma solidity >=0.7.0 <0.9.0;
+
+/**
+ * Validator Contract
+ * Check a counterexample/computation proof
+ */
+contract Validator{
+
+    /**
+    * The difficulty for a computation proof
+    */
+    uint diff = 1;
+    uint public target = 2 ** (256 - diff);
+
+    /**
+    * Check a counterexample/ computation proof
+    * The result from a validator
+    * 0 = non-award, 1 = proof, 2 = counterexample
+    */
+
+    function validate(uint[10] memory p, uint seed) 
+    public view returns (uint) {
+        uint range = p.length; 
+        uint k = seed % range + 1;
+
+        uint cal = p[k];
+
+        uint result = 0; // an non-award computation proof 
+        if (p[k] < p[(k - 1) / 2])  
+            result = 2; // a counterexample
+        else {
+            uint result_target = 
+                uint (keccak256(abi.encodePacked(seed, cal)));
+            if (result_target <= target) 
+                result = 1; // a computation proof      
+        }              
+        return result;           
+    }
+}
+
+\end{lstlisting}
+
+Coprimes number
+
+\begin{lstlisting}[numbers=none]
+(entrypoint % coprimes (pair (a : int) (b : int))
+   (forall (n : int)
+         (if (and (ge 2 n) (le n (if (ge a b) a b)))
+              (assert (not (and (eq (mod a n) 0) (eq (mod b n) 0)))))))
+\end{lstlisting}
+
+\noindent We have:
+
+$r$ = [2, (if (a $>=$ b) a b)] with ((if ($a >= b$) a b) - 2 $>$ 0)
+
+\begin{lstlisting}[numbers=none]
+
+pragma solidity >=0.7.0 <0.9.0;
+
+/**
+ * On/off-chain assertion contract 
+ * to check counterexamples/computation proofs
+ */
+contract Validator{
+
+    /**
+    * The difficulty for a computation proof
+    */
+    uint diff = 1;
+    uint public target = 2 ** (256 - diff);
+
+    /**
+    * The result: 0 = non-award, 1 = proof, 2 = counterexample
+    */
+
+    function validate(uint a, uint b, uint seed)
+    public view returns (uint) {
+        uint range;
+        if (a >= b) { range = a - 2; }
+        else {range = b - 2;}
+
+        uint r = seed % range + 2;
+        require(range != 0, "invalid range");
+
+        uint cal_1 = a % r;
+        uint cal_2 = b % r;
+
+        uint result = 0; // an non-award computation proof 
+        if ((a % r == 0) && (b % r == 0))  
+            result = 2; // a counterexample
+        else {
+            uint result_target = 
+                uint (keccak256(abi.encodePacked(seed, cal_1, cal_2)));
+            if (result_target <= target) 
+                result = 1; // a computation proof      
+        }              
+        return result;           
+    }
+}
+
+\end{lstlisting}
 
@@
 \section{Conclusion}
+
+\newpage
+\addcontentsline{toc}{chapter}{Appendix}
+\input{appendix}
+
+\newpage
 \bibliographystyle{splncs04}

### 2022-02-16 papers/assertion-contract/paper.tex
Define the on/off-chain assertion

@@
 %\usepackage{fixme}
-%\usepackage{xcolor}
+\usepackage{xcolor}
 \usepackage{hyperref}
@@
 We propose an assertion verification approach for smart contracts.
-When a function is called with a parameter that needs to be verified, an assertion and its negation form are created for that parameter.
 The idea underlying our approach is that the assertion is distributed to be verified by validators.
 During the distribution, each validator strives to find a counterexample for the assertion.
-Each of these validators then checks only a random point or a small finite set  in the range of the parameter.
+Each of these validators then checks only a random point in the range of the parameter.
 Considering the example where a parameter $p$ is a prime number, the assertion in predicate logic for the parameter is
@@
 \begin{itemize}
-   \item the owner deploys and manages a assertion contract, 
+   \item the owner deploys and manages assertion contracts, 
    \item the callers invoke a assertion contract, and 
-   \item the validators are involved in validating the parameters. 
+   \item the validators are involved in validating parameters. 
 \end{itemize}
@@
 Therefore, there are two way to reward validators in the form of cryptocurrency in order to motivate the validators to participate: (1) for a  counterexample found and (2) for a computational proof that proves that the validator actually run the program to find a counterfeit for the assertion, but none is found.
+If any of the validators finds a violation of the assertion, the final call to the actual work is aborted.
 
-If any of the validators finds a violation of the assertion, the final call to the actual work is aborted.
-In our approach, the validator make an effor to find a counterexample for the assertion off-chain.
-Therefore, the validators interact with the smart contract to submit a  counterexample or a computation proof through smart contract function calls.
+An validator finds a counterexample for an assertion outside the chain.
+Therefore, validators interact with the on-chain contract to convey a found counterexample or computational proof via a function call.
 
-Because the parameter must be validated before the actual work can be done, a caller first invokes an assertion function in the on-chain validate contract to pass the parameter for  verification and after the parameter is verified, a work contract that performs the task with the assumption that the parameter is valid can be called.
-The work contract can only called by the on-chain validate contract when some conditions are satisfied.
+Since the parameter must be validated before the actual work can be performed, a caller first invokes an assertion function in the on-chain validation contract to pass the parameter for verification.
+After the parameter is verified, a work contract can be invoked to perform the actual task assuming that the parameter is valid.
+The work contract can be invoked by the on-chain validation contract only if certain conditions are met.
 
@@
 \begin{itemize}
-\item the assertion function, where callers submit their parameters to be verified, which are then distributed to all validators. 
-\item the on/off-chain assertion (validate function) to check and promote either a computational proof or a counterexample sent by validators.
+\item the assertion function, where callers submit their parameters to be validated, which are then distributed to all validators. 
+\item the on/off-chain assertion (validate function) to check and promote either a computational proof or a counterexample sent by the validators.
 \end{itemize}
@@
 
-\paragraph{On-chain work contract.}  The working contact can only be invoked by the on-chain validation contract after the parameter has been validated if no counterexample is found.
+\paragraph{On-chain work contract.}  The work contact can only be invoked by the on-chain validation contract after the parameter has been validated if no counterexample is found.
 The actual work is then performed with the passed parameter.
 
-\begin{lstlisting}[numbers=none]
+\paragraph{Off-chain validation contract.}
+To check the validity of a parameter, each validator independently executes an off-chain validation contract that executes the on/off-chain assertion (the validate function), which is the same one used in the on-chain validation contract.
+The off-chain validation should be sent to all validators and executed outside the blockchain network.
+The on/off-chain assertion (the validate function) in the off-chain validation contract plays the main role in our approach.
+It contains the negation formulas of the assertion for parameters and takes a seed and a parameter as input.
+The seed is used to compute a random number to check the negation formulas.
+The result of the calculation can be a counterexample, an award computational proof, or a non-award computational proof.
 
-contract Work {
-
-    function work(...) public {
-       ...
-    } 
-}
-\end{lstlisting}
-
-\paragraph{Off-chain validate contract.}
-To check the validity of a parameter, each validator independently executes an off-chain validation contract that executes the same code on/off-chain assertion (the validate function) as in the on-chain validation contract.
-The on/off-chain validation should be sent to all validators and executed outside the blockchain network.
-The on/off-chain assertion (the validation function) in the on/off-chain validation plays the main role in our approach.
-It contains the negation formulas for parameters and takes a seed and a parameter as input.
-The seed is used to compute a random number to check the negation formulas of the parameter.
-The result of the calculation can be a counterexample, an award computation proof, or a non-award computation proof.
-
-A validator might try to run the off-chain validation contract many times to find either a counterexample or a proof of the price calculation.
+A validator might try to run the off-chain validation contract many times to find either a counterexample or a computational proof.
 There could be many attempts before he receives an award.
 In the case of a non-award, the validator can run the code again with a different random number.
-If a counterexample or award is found, the validator passes the seed and parameter to the on-chain validation contract, which runs the same code on/off-chain assertion and must end up with the same result as the counterexample or award.
+If a counterexample or award is found, the validator passes the seed together with the parameter to the on-chain validation contract, which runs the same on/off-chain assertion and must end up with the same result as the counterexample or award.
 
 \subsection{Managing on/off-chain contracts.}
-An on/off-chain assertion and on/off-chain validation contracts are provided by their owner.
-The owner deploy the on-chain validation contract and the work contract on the blockchain.
-The owner plays the main role in the design of the contracts.
+All contracts are provided by their owner. The owner plays the main role in the design of the contracts. The owner deploy the on-chain validation contract and the work contract on the blockchain.
 
 The on/off-chain assertion and off-chain validation contract are stored off the blockchain and should be available to callers/validators upon request at any time.
-There are two ways to make them available to validators: (1) the codes are stored on a repository that callers/validators can access, or the owner can make it available upon request sent to a caller/validator upon request, and (2) an owner/caller sends it to the network via messaging systems such as Waku in eutherum.
-The owners should send it to the network if they deploy the on-chain contracts, and in this case interested validators should store the code locally.
-In the same way, callers send it when they invoke an assertion function in the on-chain validation contract on the blockchain.
+There are two ways to make them available to validators: (1) the codes are stored on a repository that callers/validators can access, or the owner can make it available to a caller/validator upon request, and (2) an owner/caller sends it to the network via messaging systems such as Waku in eutherum.
+The owners should send it to the network once they deploy the on-chain contracts, and in this case interested validators should store the code locally.
+In the same way, callers could also send it when they invoke an assertion function in the on-chain validation contract on the blockchain.
 %\end{itemize}
@@
 
-\subsection{Interacting with the smart contract.}
+\subsection{Interacting with the on-chain validation contract.}
 A caller must first submit the parameter to an assertion function in the on-chain validation contract before it can be used in the work contract.
 The parameter is then distributed and validated by validators.
-The process of validating the parameter and invoking the working contract is transparent to the user.
+The process of validating the parameter and invoking the work contract is transparent to the user.
 It is sufficient to store the hash of the parameter, and the parameter is transmitted when a validator invokes the on/off-chain assertion in the on-chain validation contract on the blockchain.
@@
 
-A caller may need to supply some tokens for validating the parameter and calling the work function.
+A caller may need to supply some tokens for validating the parameter and calling the work contract.
+
 In some cases where the validation process does not have a counterexample but does not meet some conditions, e.g., does not receive enough proofs from the validators, the owner has to do some tasks here to handle the refund since the functions in the smart contract are passive.
@@
 The parameter's record also contains initial information for monitoring the progress of the parameter's verification, e.g., how many computational proofs have been presented, whether a counterexample has been found, etc.
-This information is used to review a proof or counterexample presented by a validator, and to decide when a work function can be called for that parameter.
-The caller can then send this information, along with the on/off-chain assertion and off-chain validation contract, to all validators via a messaging system.
+This information is used to review a proof or counterexample presented by a validator, and to decide when a work contract can be called for that parameter.
+The caller may then send this information, along with the on/off-chain assertion and off-chain validation contract, to all validators via a messaging system.
+
+\paragraph{Submitting of a computational proof/a counterexample.} After executing the off-chain validation contract, the validator may submit a computational proof or a counterexample to receive a reward.
+The submission contains the random number, the address of the validator, the parameter, and possibly other information.
+These are then used to calculate the seed, which then goes into the on/off-chain assertion along with the parameter.
+If the result is correct, there is an award to the validator and the record of the parameter in the storage accordingly is updated accordingly.
+When a computational proof is submitted and  certain requirements are met, the work contract is invoked.
 
@@
 When a parameter is sent to a validator, the validator executes the off-chain validation contract, which includes an on/off-chain assertion, to find a counterexample.
-If so, the validator submits the counterexample to the blockchain to receive a reward.
-Otherwise, a computation proof is submitted, which should be automatically generated when the program is executed.
-A validator interacts with the contract in two ways: it can announce a counterexample and submit a computation proof.
+A validator interacts with the contract in two ways: it can announce a counterexample and submit a computational proof.
+If a counterexample is found, the validator submits it to the blockchain to receive a reward.
+Otherwise, a computational proof may be submitted.
+The computational proof is automatically generated when the on/off-chain assertion program is executed.
 The validator may need to clarify which parameter is being checked by submitting the parameter and the address of the caller, and possibly the timestamp.
 This information is then matched against the records in the storage.
+
 Since the on/off chain assertion is the same for every validator, we may need the address of the validator for each parameter to make the proof unique for each validator.
 A random number is combined with the validator's address to create a seed that is used to compute a random point in the parameter range to verify the validation of the parameter.
-This prevents the validator from copying a calculation proof from others.
-With this information, a validator performs the off-chain validation contract, i.e., the on/off-chain assertion (validate function).
+This prevents the validator from copying a computational proof from others.
+With this information, a validator performs the off-chain validation contract, namely the on/off-chain assertion (validate function).
 There can be three different outcomes: a counterexample, an award, or a non-award.
-If it is a counterexample or an award, the validator passes the seed to the blockchain, i.e., it calls the on-chain validation contract on the chain, which then executes basically the same code as the on/off-chain assertion.
+If it is a counterexample or an award, the validator passes the seed to the blockchain, i.e., it calls the on-chain validation contract on the chain, which then executes the same on/off-chain assertion.
 If the on-chain result is the same, the validator gets the reward.
-If the off-chain validation result is not correct, the validator can rerun the off-chain validation.
+If the off-chain validation result is  non-award, the validator can rerun the off-chain validation.
 We could store these proofs information on the storage until the processing of the parameter is complete to prevent multiple submissions by a validator.
-
-\paragraph{Submiting of a proof/a counterexample.} After executing the off-chain validation contract, the validator may submit a computational proof or counterexample to receive a reward.
-The submission contains the random number, the address of the validator, the parameter, and possibly other information.
-These are then used to calculate the seed, which then goes into the on/off-chain assertion along with the parameter.
-If the result is correct, there is an award to the validator and the function updates the record in the storage accordingly.
-The work contract is called when a validator submits the record.
-When  certain requirements are met.
 
@@
 
-\paragraph{Calling a work function.}
-The work function is called by the on-chain validation contract once the parameter has been verified.
+\subsection{Calling a work function.}
+The work function can only called by the on-chain validation contract once the parameter has been verified.
 Thus, the caller first passes its parameter to the assertion function and then waits a while to be sure that the parameter has been verified.
@@
 Some conditions must be met, e.g., after a certain amount of time has passed or enough evidence has been received from the validators.
-If an examiner submits the counterexample, the parameter is aborted from validating the process and the work function is never called.
-Otherwise, the work function is called when the computation proof is submitted and all conditions are met.
+If a validator submits the counterexample, the parameter is aborted from the validating process and the work contract is never called.
+Otherwise, the work contract is called when the computational proof is submitted and all conditions are met.
 
@@
 \subsection{Assertion Semantic}
-The validators are trying to solve the following formula in a distributed form.
+A validator is trying to solve the following formula in a distributed form.
 
@@
 
-\noindent The verification attempt requires to search for $i$ in the domain $D$ such that $P_{i}$, called a counterexample (or proof).
+\noindent The verification attempt requires to search for $i$ in the domain $D$ such that $P_{i}$, called a counterexample.
 For each distributed trial, each validator chooses a random $i$ $\in$ $D$ and checks $P_{i}$.
@@
 \subsubsection{Converter.} The main actor in our method is the on/off-chain assertion contract, which receives the parameter and a seed as input.
-The contract then generates a random number that is associated with a variable in the predicate $\neg P$.
+The contract then generates a random number that is associated with a variable in the predicate.
 The result can be a counterexample, a computational proof with reward, or a computational proof without reward.
-A converter takes the AST of an assertion (AST for its negation) after the transformer step and returns the on/off-chain assertion contract written in Solidity (Michelson).
+A converter takes the AST of an assertion after the parser (or the AST for its negation after the transformer step) and returns the on/off-chain assertion contract written in Solidity (Michelson).
 To perform the conversion automatically, we restrict the semantics of the DSL.
-Variables are specified with \texttt{forall} quantifiers, which are then followed by \texttt{if} statements defining the scope of the variable.
-For example, the following assertion specifies the parameter \texttt{a} of type \texttt{int} for an entry point \texttt{prime}.
+Variables are specified with \texttt{forall} quantifiers, which are then followed by \texttt{if} statements defining the range of the variable.
+For example, the following assertion specifies the parameter \texttt{a} of type \texttt{int} for the entrypoint \texttt{prime}.
 The next line defines the variable \texttt{a} of type \texttt{int} and its range is defined in the next \texttt{if} statement, namely [2 a/2].
@@
 
-\noindent and a seed $s$, then the random number can be generate by
+\noindent and a seed $s$, then the random number in the range [a, b] can be generate by
 
 \begin{displaymath}
-n = s / (b - a) + a.
+n = (s\mod(b - a)) + a.
 \end{displaymath}
@@
 
-\noindent Given a random seed s, the $n$ could be generate by $s$.
+\noindent Given a random seed s, the $n$ $\in$ [2 , a / 2] could be generate by $s$.
 
 \begin{gather}
-n = s / (a / 2 - 2) + 2.
+n = (s\mod (a / 2 - 2)) + 2.
 \end{gather}
+
+Moreover, a computational proof is calculated based on Proof of work (as Bitcoin).
+Each computation calculates a hash based on its running the check of the predicate and then compare it with the target hash.
+The calculation has to be unique for each run to prevent copying of other validators or run a quick independent program to find a valid hash.
+To this end, we include the seed and the calculation of the predicate components to the hash.
+In this case, these above bad internal force can not be successful.
+A predicate is composed of the primitives with the following operations (\texttt{gt, lt, ge, le, or, xor, and, eq, neq, neg, not}).
+The operations are composed of one or more expressions.
+These expressions are then used to calculate the hash.
+
+For example, given the predicate
+
+\begin{lstlisting}[numbers=none]
+not (eq (mod a n) 0)
+\end{lstlisting}
+
+\noindent The expression \texttt{(mod a n)} is the used to calculate the hash.
 
@@
  * On/off-chain assertion contract 
- * to check counterexamples/computation proofs
+ * to check counterexamples/computational proofs
  */
@@
     /**
-    * The difficulty for a computation proof
+    * The difficulty for a computational proof
     */
@@
 
-        uint result = 0; // an non-award computation proof 
+        uint result = 0; // an non-award computational proof 
         if (cal == 0)  
@@
                 if (result_target <= target) 
-                    result = 1; // a computation proof    
+                    result = 1; // a computational proof    
             }
@@
 
-        uint result = 0; // an non-award computation proof 
+        uint result = 0; // an non-award computational proof 
         if (p[m] > p[n])  
@@
             if (result_target <= target) 
-                result = 1; // a computation proof      
+                result = 1; // a computational proof      
         }             
@@
  * Validator Contract
- * Check a counterexample/computation proof
+ * Check a counterexample/computational proof
  */
@@
     /**
-    * Check a counterexample/ computation proof
+    * Check a counterexample/ computational proof
     * The result from a validator
@@
 
-        uint cal = p[k];
+        uint cal_1 = p[k];
+        uint cal_2 = p[(k - 1) / 2];
 
-        uint result = 0; // an non-award computation proof 
-        if (p[k] < p[(k - 1) / 2])  
+        uint result = 0; // an non-award computational proof 
+        if (cal_1 < cal_2)  
             result = 2; // a counterexample
@@
             uint result_target = 
-                uint (keccak256(abi.encodePacked(seed, cal)));
+                uint (keccak256(abi.encodePacked(seed, cal_1, cal_2)));
             if (result_target <= target) 
-                result = 1; // a computation proof      
+                result = 1; // a computational proof      
         }              
@@
 
-        uint result = 0; // an non-award computation proof 
-        if ((a % r == 0) && (b % r == 0))  
+        uint result = 0; // an non-award computational proof 
+        if ((cal_1 == 0) && (cal_2 == 0))  
             result = 2; // a counterexample
@@
             if (result_target <= target) 
-                result = 1; // a computation proof      
+                result = 1; // a computational proof      
         }              
@@
 \newpage
-\addcontentsline{toc}{chapter}{Appendix}
 \input{appendix}

### 2022-02-17 papers/assertion-contract/paper.tex
update section 4.2

@@
 
-\subsubsection{Converter.} The main actor in our method is the on/off-chain assertion contract, which receives the parameter and a seed as input.
+\subsection{Converter - Generating an On/off-chain Assertion} The main actor in our method is the on/off-chain assertion contract, which receives the parameter and a seed as input.
 The contract then generates a random number that is associated with a variable in the predicate.
@@
 The convention will only work if the D is related to a natural number.
-Assumes that the range of a variable is 
+\subsubsection{Detecting the range.} Assumes that the range of a variable is 
 \begin{displaymath}
@@
 
-Moreover, a computational proof is calculated based on Proof of work (as Bitcoin).
+\subsubsection{Calculating a valid hash.} a computational proof is based on Proof of work (as Bitcoin).
 Each computation calculates a hash based on its running the check of the predicate and then compare it with the target hash.
@@
         uint result = 0; // an non-award computational proof 
-        if (p[m] > p[n])  
+        if (cal_1 > cal_2)  
             result = 2; // a counterexample
@@
 \newpage
+\addcontentsline{toc}{chapter}{Appendix}
 \input{appendix}

### 2022-02-17 papers/assertion-contract/paper.tex
update the code

@@
 
-    function validate(uint p, uint seed) 
+    function validate(uint a, uint seed) 
     public view returns (uint) {
-        uint range = p / 2 - 2; 
+        uint range = a / 2 - 2; 
         uint r = seed % range + 2;
-        uint cal = p % r;
+        uint cal = a % r;
+        bool p = (cal == 0);
 
         uint result = 0; // an non-award computational proof 
-        if (cal == 0)  
+        if (p)  
             result = 2; // a counterexample
@@
 
-    function validate(uint[] memory p, uint seed)
+    function validate(uint[] memory a, uint seed)
     public view returns (uint) {
-        uint range_1 = p.length - 1; 
+        uint range_1 = a.length - 1; 
         require(range_1 > 0, "invalid range");
-        uint n = seed_i % range_1 + 1;
+        uint n = seed % range_1 + 1;
         uint range_2 = n;
         require(range_2 > 0, "invalid range");
-        uint m = seed_j % range_2 ;
+        uint seed_1 = uint (keccak256(abi.encodePacked(seed, n)));
+        uint m = seed_1 % range_2 ;
 
-        uint cal_1 = p[m];
-        uint cal_2 = p[n];
+        uint cal_1 = a[m];
+        uint cal_2 = a[n];
+
+        bool p = (cal_1 > cal_2);
 
         uint result = 0; // an non-award computational proof 
-        if (cal_1 > cal_2)  
+        if (p)  
             result = 2; // a counterexample
@@
             uint result_target = 
-                 int (keccak256(abi.encodePacked(seed, cal_1, cal_2)));
+                uint (keccak256(abi.encodePacked(seed, cal_1, cal_2)));
             if (result_target <= target) 
@@
 
-    function validate(uint[10] memory p, uint seed) 
+    function validate(uint[10] memory a, uint seed) 
     public view returns (uint) {
-        uint range = p.length; 
+        uint range = a.length; 
         uint k = seed % range + 1;
 
-        uint cal_1 = p[k];
-        uint cal_2 = p[(k - 1) / 2];
+        uint cal_1 = a[k];
+        uint cal_2 = a[(k - 1) / 2];
+
+        bool p = (cal_1 < cal_2);
 
         uint result = 0; // an non-award computational proof 
-        if (cal_1 < cal_2)  
+        if (p)  
             result = 2; // a counterexample
@@
 
+        bool p = (cal_1 == 0) && (cal_2 == 0);
+
         uint result = 0; // an non-award computational proof 
-        if ((cal_1 == 0) && (cal_2 == 0))  
+        if (p)  
             result = 2; // a counterexample

### 2022-02-17 papers/assertion-contract/paper.tex
update 4.2

@@
 
-The Converter generate a on/off-chain assertion program in Solidity as the follows.
+\subsubsection{Examples.} The Converter generate a on/off-chain assertion program in Solidity as the follows.
+
+\paragraph{Prime numbers.}{ on/off-chain assertion program for primes numbers}
 
@@
     /**
-    * The result: 0 = non-award, 1 = proof, 2 = counterexample
+    * The result: 0 = non-award, 1 = proof, 
+    2 = counterexample
     */
@@
 
-For sorted array
+\paragraph{Sorted arrays.}{ on/off-chain assertion program for sorted arrays}
 
@@
 
-For a heap
+\paragraph{Heaps.}{ on/off-chain assertion program for heap arrays}
 
@@
          (if (and (ge n 1) (le n (size a)))
-                  (assert (lt (nth a n) (nth a (div (sub n 1) 2)))))))
+               (assert (lt (nth a n) 
+               (nth a (div (sub n 1) 2)))))))
 \end{lstlisting}
@@
     * The result from a validator
-    * 0 = non-award, 1 = proof, 2 = counterexample
+    * 0 = non-award, 1 = proof, 
+    2 = counterexample
     */
@@
 
-Coprimes number
+\paragraph{Coprime numbers.}{ on/off-chain assertion program for coprime numbers}
 
@@
          (if (and (ge 2 n) (le n (if (ge a b) a b)))
-              (assert (not (and (eq (mod a n) 0) (eq (mod b n) 0)))))))
+              (assert (not (and (eq (mod a n) 0) 
+              (eq (mod b n) 0)))))))
 \end{lstlisting}

### 2022-02-17 papers/assertion-contract/paper.tex
update 4.2

@@
 
-\subsubsection{Calculating a valid hash.} a computational proof is based on Proof of work (as Bitcoin).
+\subsubsection{Calculating a valid hash.} A computational proof is based on Proof of work (as Bitcoin).
 Each computation calculates a hash based on its running the check of the predicate and then compare it with the target hash.
@@
 In this case, these above bad internal force can not be successful.
-A predicate is composed of the primitives with the following operations (\texttt{gt, lt, ge, le, or, xor, and, eq, neq, neg, not}).
-The operations are composed of one or more expressions.
-These expressions are then used to calculate the hash.
 
-For example, given the predicate
+A predicate is formalized as an assert, which contains expressions in the DSL.
+Let $S$ = ($s_1$, $s_2$, ..., $s_n$) is the set of all expressions in the predicate that contains none of the following operations (\texttt{gt, lt, ge, le, or, xor, and, eq, neq, neg, not}).
+These expressions can then used to calculate the hash.
 
 \begin{lstlisting}[numbers=none]
-not (eq (mod a n) 0)
+uint current_hash = 
+     uint (keccak256(abi.encodePacked(seed, s1, s2, ..., sn)));
 \end{lstlisting}
 
-\noindent The expression \texttt{(mod a n)} is the used to calculate the hash.
+\noindent For example, given the predicate
+
+\begin{lstlisting}[numbers=none]
+p = not (eq (mod a n) 0)
+\end{lstlisting}
+
+\noindent We could ignore the constant expression, then the predicate has the expression \texttt{(mod a n)}, which can then be used to compute the hash.
+Let \texttt{cal} be the expression, then the hash is computed as follows.
+
+\begin{lstlisting}[numbers=none]
+uint current_hash = 
+     uint (keccak256(abi.encodePacked(seed, cal)));
+\end{lstlisting}
+
+\noindent This current hash is then compared to the target to find out if it is a valid hash for a computational award.
 
@@
             {
-                uint result_target = 
+                uint current_hash = 
                     uint (keccak256(abi.encodePacked(seed, cal)));
-                if (result_target <= target) 
+                if (current_hash <= target) 
                     result = 1; // a computational proof    
@@
             {
-            uint result_target = 
+            uint current_hash = 
                 uint (keccak256(abi.encodePacked(seed, cal_1, cal_2)));
-            if (result_target <= target) 
+            if (current_hash <= target) 
                 result = 1; // a computational proof      
@@
         else {
-            uint result_target = 
+            uint current_hash = 
                 uint (keccak256(abi.encodePacked(seed, cal_1, cal_2)));
-            if (result_target <= target) 
+            if (current_hash <= target) 
                 result = 1; // a computational proof      

### 2022-09-16 reports/2022-09-06/COOC-report.tex
report-09-2022

\documentclass[a4paper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{hyperref}
\usepackage{authblk}

\title{Contract Orchestration for OCaml \\
  Progress Report 
}
\author{Thi Thu Ha Doan}
\author{Peter Thiemann}
\affil{University of Freiburg, Germany}
\begin{document}
\maketitle{}

\section{Introduction}
\label{sec:introduction}

The Contract Orchestration for OCaml (COOC) project is funded by the Tezos foundation. Its overall goal  is to provide a framework that guarantees the correct orchestration of contract invocations from an application program in the OCaml language. This report is a continuation of the second report dated September 06, 2021.

\subsection{Personnel}
\label{sec:personnel}

There is one full-time employee working on the project for the whole time period: Dr. Thi Thu Ha Doan (postdoctoral researcher).

Student workers (part time as explained below):

\section{Timeline of Events}
\label{sec:timeline-events}
\paragraph{October 2021 - March 2022: The Tezos API} 
\begin{itemize}
\item Leqaa Ahmed, who worked on the Ocaml API as part of her bachelor's thesis, has worked extensively with the Tezos library in Ocaml. Interacting with smart contracts on this blockchain via the Ocaml libraries is completely understated. She has managed to develop the functions that get the parameter types for each entrypoint of a smart contract on the blockchain and then convert those types to the corresponding types defined in Ocaml. However, it has not yet fully implemented the typed API. Therefore, I have assigned a student, Julian Mundhahs, to work on it as part of his bachelor's project. His task is to fully develop and strengthen the typing features of our Tezos API.
\item Julian has successfully typed the API.The typed API allows interaction with smart contracts in a type-safe manner using native OCaml types. The types of the smart contract's arguments must be specified, which are then compared to the actual contract on the blockchain. If the types do not match, an error is raised. When a smart contract function is called, the official client libraries are called with a string representation of the actual argument. The library allows the arguments to be passed as their OCaml types. Since the type has already been checked, it is ensured that the contract can only be called with arguments of the correct type. 
\item  The current code of the Tezos API can be found on Github \cite{tezos-api-update}. There is also an environment that makes it easy to run a Tezos sandbox independent of the host system \cite{tezos-api-devenv}.
\end{itemize}

\paragraph{October 2021 - March 2022: Michelson One-step Execusion Interpreter} 
\begin{itemize}
\item When writing code in Michelson, you have to keep track of the stack and what happens to it with each instruction. This is awkward for a larger program, since you have to follow either mentally or in writing, or make do with the hard-to-understand interfaces. Hasan Berkay's project therefore aims to provide a snapshot of the stack before and after the execution of each instruction in a programmatically accessible data format. In this way, with a suitable complementary user interface, it is much easier to track each step along the entire execution of the script and better understand errors. 
\item The implementation was done in
JavaScript, using a Nearley grammar to parse the Michelson scripts and interpret the parsed script with the data entered by the user.
All execution is simulated sequentially and depends on user input, with chain manipulation instructions being mostly no-ops. 
\item In its current state, the interpreter is capable of working with instructions up to and including the Tezos protocol Babylon. Since no complementary user interface is yet available, user acceptance is limited so far; however, tests with a number of scripts have shown correct results and stack continuity.
\item The current code of the interpreter can be found on Github \cite{michelson-interpreter}.
\end{itemize}

\paragraph{October 2021 - March 2022: Blockchain Seminar Course} 
\begin{itemize}
\item Dr. Doan and I runed the seminar course "Blockchain and Cryptocurrencies." There are 35 students registered for the seminar. However, due to our limited capacity, we can only accommodate 13 students. 
\item During the seminar, students research various topics on blockchain and smart contracts, starting from the engineering of blockchain, such as blockchain consensus, bitcoin security and privacy, blockchain oracle, etc. to a smart contract, such as smart contract verification, smart contract securityand privacy, static analysis for smart contracts, etc. To complete the assignments, students research several blockchains, including the Tezos blockchain.
\end{itemize}

Doan and Thiemann have worked on the type-safe interaction with the Tezos blockchain, distributed verification of assertions, and contract modules, and a checker for Michelson smart contracts on various aspects.
n
\paragraph{December 2021: Presentation at APLAS Conferece}

\begin{itemize}
\item Thiemann gave a talk at the Asian Symposium on Programming Languages and Systems (APLAS 2021) (remotely due to the Covid situation). The talk is based on our paper on a typed programmatic interface to contracts on the blockchain, in which we propose a typed API for creating and invoking contracts and querying the state of the Tezos blockchain along with an operational semantics for functional programs running alongside smart contracts on a blockchain. During the talk, we will get some suggestions to improve our Tezos API.

\end{itemize}

\paragraph{September 2021 - June 2022: Distributed  Assertion Checking}
\begin{itemize}
\item Research on distributed assertion checking for smart contracts was conducted by two students, Tamara Bernhardt and Julian Veigel, as part of their master's thesis, with Tamara defining the grammar for the assertion language and Julian presenting different approaches and discussing their strengths and weaknesses. However, the approaches proposed by Tamara and Julian require changes  in the backend system (Tezos and Etherum). We therefore worked on a solution so that the approach can work without changes to the backend system.
\item 
The basic idea is to distribute the validation process among several nodes in the network, all testing different property cases. The goal is to reduce costs while preserving fundamental properties such as decentralization and trust. The senior is as follows. A caller submits a parameter that needs to be validated to the blockchain. The parameter is then forwarded to all nodes as validators in the network, which then validate it. After the parameter is validated, the actual work that uses the parameter is executed. The idea behind our approach is that validation is done separately from on-chain and off-chain processes. To check the validity of a parameter, each validator independently executes an off-chain validation contract that executes the off-chain assertion (the validation function), which is the same one used in the on-chain validation contract. The off-chain assertion in the off-chain validation contract plays the main role in our approach. It contains the negation formulas of the assertion for parameters and takes a seed and a parameter as input.

\item We define a domain-specific high-level language to express assertions. The main actor in our method is the on/off contract of an assertion. We propose an algorithm to automatically generate the on/off-chain assertion contract from an assertion written in our DSL. The algorithm is then implemented as a converter that takes the AST of an assertion after the parser (or the AST for its negation after the transformer step) and returns the on/off-chain assertion contract written in Solidity (Michelson). To perform the conversion automatically, we constrain the semantics of the DSL. So far, we have done:
\begin{itemize}
\item completing the design and implementation of a DSL to express the assertion (reused Tamara work).
\item proposing an algorithm to automatically convert an assertion to the on/off-chain smart contract.
\end{itemize}

\end{itemize}

\paragraph{October 2021 - September 2022: Contract Modules, and A Checker for Michelson}
\begin{itemize}
\item Thiemann gave a presentation at the Formal Methods for Blockchains (FMBC 2021) workshop on contract modules that provide a statically verified interface to interact with contracts on the Tezos blockchain.
\item The contract model, once generated from a contract module, is checked against the specification using symbolic execution. We have therefore worked on

\begin{itemize}
\item we are modelling symbolic execution for Michelson.
\item Thiemann implemented a symbolic execution for Michelson in Ocaml.
\item we explode Z3 solver as well as its library in Ocaml.
\end{itemize}

\item To build a checker for Michelson. We use the pre- and post-conditions to check a property. We first provide users with a DSL for the precondition and specify the property. The specification is then transferred to a formula in Z3 in Ocaml and then compared to the symbolic execution to check if a property is satisfied
\end{itemize}

\paragraph{June 2022 - September 2022}

Khaled Fayed works on exploring SMT checker for Solidity.
\paragraph{July 2022}
Hasan works on concolic execution to collect the condition paths.

\section{Relation to the Contract}
\label{sec:relation-contract}

We have made progress on several points in the contract.
\begin{itemize}
\item complete the implementation of the type-safe interface ;
\
\end{itemize}

\section{Next Steps}

We plan to 
\begin{itemize}
\item implements the converter for the Assertiom contract (for Tezos and Ethereum). 
\item package the document to a paper about Assertion Contract to a conference paper.
\item implement code generation for contract modules; 
\item extend contract modules to contract specifications that include pre-conditions, post-conditions, and allowable call sequences for entrypoints; 
\item design and implement a checker for contract specifications based on Michelsym.
\end{itemize}

\bibliography{report}
\bibliographystyle{plainurl}
\end{document}

### 2022-09-16 reports/2022-09-06/COOC-report.tex
update the time lines

@@
 There is one full-time employee working on the project for the whole time period: Dr. Thi Thu Ha Doan (postdoctoral researcher). 
-
-Student workers (part time as explained below):
-
 \section{Timeline of Events}
@@
 \item Leqaa Ahmed, who worked on the Ocaml API as part of her bachelor's thesis, has worked extensively with the Tezos library in Ocaml.
-Interacting with smart contracts on this blockchain via the Ocaml libraries is completely understated.
-She has managed to develop the functions that get the parameter types for each entrypoint of a smart contract on the blockchain and then convert those types to the corresponding types defined in Ocaml.
-However, it has not yet fully implemented the typed API.
+Interacting with smart contracts on this blockchain via the Ocaml libraries is deeply understated.
+After that, she has managed to implement a function that gets the parameter types for each entrypoint of a smart contract on the blockchain and then convert those types to the corresponding types defined in Ocaml.
+However, it has not yet fully implemented the types for the API.
 Therefore, I have assigned a student, Julian Mundhahs, to work on it as part of his bachelor's project.
@@
 \begin{itemize}
-\item Thiemann gave a presentation at the Formal Methods for Blockchains (FMBC 2021) workshop on contract modules that provide a statically verified interface to interact with contracts on the Tezos blockchain.
+\item Thiemann gave a presentation based on the beginning state of the Contract Modules at the Formal Methods for Blockchains (FMBC 2021) workshop.
+Our aim is to provide a statically verified interface to interact with contracts on the Tezos blockchain.
 \item The contract model, once generated from a contract module, is checked against the specification using symbolic execution. We have therefore worked on
@@
 \begin{itemize}
-\item we are modelling symbolic execution for Michelson.
+\item We symbolically model the interpreter for Michelson.
 \item Thiemann implemented a symbolic execution for Michelson in Ocaml.
@@
 
-\item To build a checker for Michelson.
+\item  As an other aim of our research to build a checker for Michelson.
 We use the pre- and post-conditions to check a property.
 We first provide users with a DSL for the precondition and specify the property.
-The specification is then transferred to a formula in Z3 in Ocaml and then compared to the symbolic execution to check if a property is satisfied
+The specification is then transferred to a formula in Z3 in Ocaml and then compared to the symbolic execution to check if a property is satisfied.
 \end{itemize}
 
-\paragraph{June 2022 - September 2022}
+\paragraph{June 2022 - October 2022} 
+\begin{itemize}
+\item Since we want to use an SMT solver, namely Z3  solver, as a type checker for the system and there is already an SMT checker for Solidity smart contract.
+It might be useful to explore the capabilities and facilities of SMT solvers for smart contract verification.
+I have commissioned Khaled Fayed to research the SMT checker for Solidity as part of his bachelor's project.
+\end{itemize}
 
-Khaled Fayed works on exploring SMT checker for Solidity.
 \paragraph{July 2022}
-Hasan works on concolic execution to collect the condition paths.
+\begin{itemize}
+\item The symbolic execution suffers from the state explosion.
+To check the precondition, it might be sufficient to collect the path conditions along with the execution.
+One possible way to do this is to use the concolic execution approach.
+I therefore assigned Hassan to look into concolic execution for Michelson as part of his bachelor's thesis.
+\end{itemize}
 
@@
 \begin{itemize}
-\item complete the implementation of the type-safe interface ;
-\
+\item A type-safe interaction between an Ocaml program and Michelson smart contracts on the Tezos blockchain. The work has been presented and published at APLAS 2021 conference. 
+\item The type Tezos API is completely implemented.
+
 \end{itemize}

### 2022-09-17 reports/2022-09-06/COOC-report.tex
Add files via upload

@@
 \begin{itemize}
-\item Thiemann gave a presentation based on the beginning state of the Contract Modules at the Formal Methods for Blockchains (FMBC 2021) workshop.
-Our aim is to provide a statically verified interface to interact with contracts on the Tezos blockchain.
+\item Thiemann gave a presentation on the initial state of contract modules at the Formal Methods for Blockchains (FMBC 2021) workshop.
+Contract modules aim to provide a statically verified interface for interacting with contracts on the Tezos blockchain.
 \item The contract model, once generated from a contract module, is checked against the specification using symbolic execution. We have therefore worked on
@@
 \begin{itemize}
-\item We symbolically model the interpreter for Michelson.
+\item We propose a symbolic execution model for Michelson that allows us to grant a type-safe invocation of the contract on the blockchain.
+Namely, the model allows us to express the pre- and post-conditions and specify the invariants from them.
+In addition, the model enables us to specify constraints on the possible call orders of the entrypoints
+
 \item Thiemann implemented a symbolic execution for Michelson in Ocaml.
-\item we explode Z3 solver as well as its library in Ocaml.
+Given a symbolic specification of an entrypoint, the symbolic execution yields the set of final states with the garter of path conditions.
+\item Given an invocation of a smart contract, the invocation can be checked  using these invariants and constraints, before deployment on the chain, where the call is possible to be successfully.
+The verification of invariants and constraints can be done using an SMT solver.
+For this purpose, we exploded the Z3 solver and its library into Ocaml.
 \end{itemize}
 
-\item  As an other aim of our research to build a checker for Michelson.
+\item Another goal of our research is to develop a checker for Michelson.
 We use the pre- and post-conditions to check a property.
-We first provide users with a DSL for the precondition and specify the property.
-The specification is then transferred to a formula in Z3 in Ocaml and then compared to the symbolic execution to check if a property is satisfied.
+We first provide users with a domain-specific language to specify the preconditions and the property.
+The specification is then transferred to a formula in Z3 in Ocaml and then transferred to symbolic execution to check if a property is satisfied.
+If a smart contract script is passed along with the property specification, the tool statically checks if these properties are satisfied.
 \end{itemize}
@@
 \begin{itemize}
-\item Since we want to use an SMT solver, namely Z3  solver, as a type checker for the system and there is already an SMT checker for Solidity smart contract.
-It might be useful to explore the capabilities and facilities of SMT solvers for smart contract verification.
+\item Since we plan to use an SMT solver, namely Z3  solver, as a type checker for the system and there is already an SMT checker for Solidity smart contract.
+It would be useful to explore the capabilities and facilities of SMT solvers for smart contract verification.
 I have commissioned Khaled Fayed to research the SMT checker for Solidity as part of his bachelor's project.
@@
 \begin{itemize}
-\item implements the converter for the Assertiom contract (for Tezos and Ethereum). 
+\item implement the converter for the Assertiom contract (for Tezos and Ethereum). 
 \item package the document to a paper about Assertion Contract to a conference paper.
-\item implement code generation for contract modules; 
-\item extend contract modules to contract specifications that include pre-conditions, post-conditions, and allowable call sequences for entrypoints; 
+\item implement code generation for Contract Modules; 
+\item extend Contract modules to contract specifications that include pre-conditions, post-conditions, and allowable call sequences for entrypoints; 
 \item design and implement a checker for contract specifications based on Michelsym.

### 2022-09-19 reports/2022-09-06/COOC-report.tex
update report and bib

@@
 \label{sec:timeline-events}
-\paragraph{October 2021 - March 2022: The Tezos API} 
+\paragraph{October 2021 - March 2022:  Tezos Typed API} 
 \begin{itemize}
@@
 However, it has not yet fully implemented the types for the API.
-Therefore, I have assigned a student, Julian Mundhahs, to work on it as part of his bachelor's project.
+Therefore, I assigned a student, Julian Mundhahs, to work on it as part of his bachelor's project.
 His task is to fully develop and strengthen the typing features of our Tezos API.
-\item Julian has successfully typed the API.The typed API allows interaction with smart contracts in a type-safe manner using native OCaml types.
+\item Julian has successfully typed the API.
+The typed API allows interaction with smart contracts in a type-safe manner using native OCaml types.
 The types of the smart contract's arguments must be specified, which are then compared to the actual contract on the blockchain.
@@
 However, due to our limited capacity, we can only accommodate 13 students.
-\item During the seminar, students research various topics on blockchain and smart contracts, starting from the engineering of blockchain, such as blockchain consensus, bitcoin security and privacy, blockchain oracle, etc.
+\item During the seminar, students research various topics on blockchain and smart contracts, starting from the engineering of blockchain, such as blockchain consensus, blockchain security and privacy, blockchain oracle, etc.
 to a smart contract, such as smart contract verification, smart contract securityand privacy, static analysis for smart contracts, etc.
@@
 Doan and Thiemann have worked on the type-safe interaction with the Tezos blockchain, distributed verification of assertions, and contract modules, and a checker for Michelson smart contracts on various aspects.
-n
 \paragraph{December 2021: Presentation at APLAS Conferece}
@@
 The talk is based on our paper on a typed programmatic interface to contracts on the blockchain, in which we propose a typed API for creating and invoking contracts and querying the state of the Tezos blockchain along with an operational semantics for functional programs running alongside smart contracts on a blockchain.
-During the talk, we will get some suggestions to improve our Tezos API.
+During the talk, we got some suggestions that helped to improve our Tezos API.
 
@@
 The senior is as follows.
-A caller submits a parameter that needs to be validated to the blockchain.
+A caller submits a parameter to the blockchain that needs to be validated.
 The parameter is then forwarded to all nodes as validators in the network, which then validate it.
 After the parameter is validated, the actual work that uses the parameter is executed.
-The idea behind our approach is that validation is done separately from on-chain and off-chain processes.
-To check the validity of a parameter, each validator independently executes an off-chain validation contract that executes the off-chain assertion (the validation function), which is the same one used in the on-chain validation contract.
-The off-chain assertion in the off-chain validation contract plays the main role in our approach.
-It contains the negation formulas of the assertion for parameters and takes a seed and a parameter as input.
-
-\item We define a domain-specific high-level language to express assertions.
-The main actor in our method is the on/off contract of an assertion.
+The idea behind our approach is that validation is done outside the chain, but the result of this process is then checked inside the chain.
+To check the validity of a parameter, each validator independently performs an off-chain assertion, which is the same as the one used in the on-chain validation assertion.
+The result is then submitted to the blockchain, which then uses the on-chain assertion to verify the submission.
+The off-chain assertion contains the negation formulas of the assertion for parameters and takes a seed and a parameter as input.
+\item We define a domain specific language (DSL) to express assertions.
+The main actor in our method is the on/off assertion contracts.
 We propose an algorithm to automatically generate the on/off-chain assertion contract from an assertion written in our DSL.
-The algorithm is then implemented as a converter that takes the AST of an assertion after the parser (or the AST for its negation after the transformer step) and returns the on/off-chain assertion contract written in Solidity (Michelson).
+The algorithm is then implemented as a converter that takes the AST of an assertion after the parser (or the AST for its negation after the transformer step) and returns the on/off-chain assertion contract written in Michelson (Solidity).
 To perform the conversion automatically, we constrain the semantics of the DSL.
@@
 \begin{itemize}
-\item We propose a symbolic execution model for Michelson that allows us to grant a type-safe invocation of the contract on the blockchain.
+\item We propose a symbolic execution model for Michelson that allows us to ensure type-safe invocation of the contract on the blockchain.
 Namely, the model allows us to express the pre- and post-conditions and specify the invariants from them.
-In addition, the model enables us to specify constraints on the possible call orders of the entrypoints
-
+In addition, we can use the model to impose constraints on the possible call orders of the entrypoints.
 \item Thiemann implemented a symbolic execution for Michelson in Ocaml.
-Given a symbolic specification of an entrypoint, the symbolic execution yields the set of final states with the garter of path conditions.
-\item Given an invocation of a smart contract, the invocation can be checked  using these invariants and constraints, before deployment on the chain, where the call is possible to be successfully.
-The verification of invariants and constraints can be done using an SMT solver.
-For this purpose, we exploded the Z3 solver and its library into Ocaml.
+Given a symbolic specification of an entrypoint, the symbolic execution returns the set of final states with the bundle of path conditions.
+\item Given an invocation of a smart contract, the invocation can be checked against these invariants and constraints before being used in the chain, where the invocation may succeed. 
+\item The verification of invariants and constraints can be done using an SMT solver. For this purpose, we exploded the Z3 solver and its library into Ocaml.
 \end{itemize}
 
-\item Another goal of our research is to develop a checker for Michelson.
-We use the pre- and post-conditions to check a property.
-We first provide users with a domain-specific language to specify the preconditions and the property.
-The specification is then transferred to a formula in Z3 in Ocaml and then transferred to symbolic execution to check if a property is satisfied.
-If a smart contract script is passed along with the property specification, the tool statically checks if these properties are satisfied.
+\item Another goal is to develop a checker for Michelson smart contracts.
+When a smart contract script is passed along with the property specification, the tool will statically check if these properties are satisfied.
+\begin{itemize}
+\item We first provide an environment for the user to specify the preconditions, postconditions, and properties. 
+\item The specification is then converted to formulas in Z3 in Ocaml, which are then combined with symbolic execution to check if the property is satisfied. 
+\end{itemize}
+
 \end{itemize}
@@
 \begin{itemize}
-\item Since we plan to use an SMT solver, namely Z3  solver, as a type checker for the system and there is already an SMT checker for Solidity smart contract.
-It would be useful to explore the capabilities and facilities of SMT solvers for smart contract verification.
+\item We plan to use an SMT solver, namely Z3  solver, as a type checker for the system and there is already an SMT checker for Solidity smart contract.
+It, therefore, would be useful to explore the capabilities and facilities of SMT solvers for smart contract verification.
 I have commissioned Khaled Fayed to research the SMT checker for Solidity as part of his bachelor's project.
@@
 \begin{itemize}
-\item A type-safe interaction between an Ocaml program and Michelson smart contracts on the Tezos blockchain. The work has been presented and published at APLAS 2021 conference. 
-\item The type Tezos API is completely implemented.
-
+\item A type-safe interaction between an Ocaml program and Michelson smart contracts on the Tezos blockchain.
+The work has been presented and published at APLAS 2021 conference \cite{DBLP:conf/fc/ThiemannAplas21}.
+\item The typed Tezos API is completely implemented.
+\item extend Contract modules to contract specifications that include pre-conditions, post-conditions, and allowable call sequences for entrypoints; 
 \end{itemize}
@@
 \begin{itemize}
+\item continuous our teaching activities (the blockchain course, a seminar on the topic in the winter semester).
 \item implement the converter for the Assertiom contract (for Tezos and Ethereum). 
-\item package the document to a paper about Assertion Contract to a conference paper.
-\item implement code generation for Contract Modules; 
-\item extend Contract modules to contract specifications that include pre-conditions, post-conditions, and allowable call sequences for entrypoints; 
+\item package the document to a paper about assertion contract to a conference paper.
+\item implement code generation for contract modules; 
+\item 
 \item design and implement a checker for contract specifications based on Michelsym.

### 2022-09-20 reports/2022-09-06/COOC-report.tex
update report and lib

@@
 \item A type-safe interaction between an Ocaml program and Michelson smart contracts on the Tezos blockchain.
-The work has been presented and published at APLAS 2021 conference \cite{DBLP:conf/fc/ThiemannAplas21}.
+The work was presented and published at APLAS 2021 conference \cite{DBLP:conf/fc/ThiemannAplas21}.
+\item The initial state of work on Contract modules was presented and published at the Formal Methods for Blockchains (FMBC 2021) workshop \cite{DBLP:conf/fc/ThiemannFmbc21}.
+
 \item The typed Tezos API is completely implemented.
-\item extend Contract modules to contract specifications that include pre-conditions, post-conditions, and allowable call sequences for entrypoints; 
+\item a symbolic execution model for Michelson that allows us to specify pre-conditions, post-conditions, and allowable call sequences for entrypoints; 
 \end{itemize}
@@
 \item implement code generation for contract modules; 
-\item 
-\item design and implement a checker for contract specifications based on Michelsym.
+\item implement a checker for contract specifications based on Michelsym.
 \end{itemize}

### 2022-09-20 reports/2022-09-06/COOC-report.tex
update report

@@
 \begin{itemize}
-\item Thiemann gave a presentation on the initial state of contract modules at the Formal Methods for Blockchains (FMBC 2021) workshop.
+\item Thiemann gave a presentation on the initial state of Contract modules at the Formal Methods for Blockchains (FMBC 2021) workshop.
 Contract modules aim to provide a statically verified interface for interacting with contracts on the Tezos blockchain.
@@
 \begin{itemize}
-\item We propose a symbolic execution model for Michelson that allows us to ensure type-safe invocation of the contract on the blockchain.
-Namely, the model allows us to express the pre- and post-conditions and specify the invariants from them.
+\item We proposed a symbolic execution model for Michelson that allows us to ensure type-safe invocation of the contract on the blockchain.
+Namely, the model allows us to express the pre- and post-conditions and then specify invariants.
 In addition, we can use the model to impose constraints on the possible call orders of the entrypoints.
@@
 Given a symbolic specification of an entrypoint, the symbolic execution returns the set of final states with the bundle of path conditions.
-\item Given an invocation of a smart contract, the invocation can be checked against these invariants and constraints before being used in the chain, where the invocation may succeed. 
+\item Given an invocation of a smart contract, the invocation can be checked against these invariants and constraints before being used in the chain, where the invocation may be succeed. 
 \item The verification of invariants and constraints can be done using an SMT solver. For this purpose, we exploded the Z3 solver and its library into Ocaml.
@@
 \begin{itemize}
-\item We first provide an environment for the user to specify the preconditions, postconditions, and properties. 
-\item The specification is then converted to formulas in Z3 in Ocaml, which are then combined with symbolic execution to check if the property is satisfied. 
+\item We first provided an environment for the user to specify the properties. 
+\item The specification is then converted to formulas in Z3 in Ocaml, which are then checked.  
 \end{itemize}
@@
 \begin{itemize}
-\item continuous our teaching activities (the blockchain course, a seminar on the topic in the winter semester).
-\item implement the converter for the Assertiom contract (for Tezos and Ethereum). 
-\item package the document to a paper about assertion contract to a conference paper.
+\item Teaching activities:
+\begin{itemize}
+\item continues our teaching activities (the blockchain course, a seminar on the topic in the winter semester).
+\item assigns more students interested in research on blockchain in general and Tezos in particular.
+\end{itemize}
+\item Assertion contract:
+\begin{itemize}
+\item implements the converter for assertion contracts.
+Given a specification in the assertion domain specification language of a parameter that needs to be verified, the converter automatically generates the on/off-chain assertions (for Tezos and Ethereum)
+\item implements the ecosystem for deploying assertion contracts on the network (for Tezos and Ethereum). 
+\item documents the results in a paper on assertion contracts.
+\end{itemize}
+
+\item Contract module and the checker for Michelsym smart contracts.
+\begin{itemize}
 \item implement code generation for contract modules; 
 \item implement a checker for contract specifications based on Michelsym.
+\end{itemize}
+
 \end{itemize}

### 2022-09-20 reports/2022-09-06/COOC-report.tex
update report

@@
 
-Doan and Thiemann have worked on the type-safe interaction with the Tezos blockchain, distributed verification of assertions, and contract modules, and a checker for Michelson smart contracts on various aspects.
+Doan and Thiemann have worked on various aspects of type-safe interaction with the Tezos blockchain, distributed verification of assertions and contract modules, and a checker for Michelson smart contracts.
+
 \paragraph{December 2021: Presentation at APLAS Conferece}
@@
 \begin{itemize}
-\item Thiemann gave a talk at the Asian Symposium on Programming Languages and Systems (APLAS 2021) (remotely due to the Covid situation).
-The talk is based on our paper on a typed programmatic interface to contracts on the blockchain, in which we propose a typed API for creating and invoking contracts and querying the state of the Tezos blockchain along with an operational semantics for functional programs running alongside smart contracts on a blockchain.
-During the talk, we got some suggestions that helped to improve our Tezos API.
-
+\item Thiemann gave a talk at the Asian Symposium on Programming Languages and Systems (APLAS 2021) (remote due to the Covid situation).
+The talk is based on our paper on a typed programmatic interface to contracts on the blockchain, in which we propose a typed API for creating and invoking contracts and querying the state of the Tezos blockchain, along with operational semantics for functional programs running alongside smart contracts on a blockchain.
+During the talk, we received some suggestions that helped us improve our Tezos API.
 \end{itemize}
@@
 The idea behind our approach is that validation is done outside the chain, but the result of this process is then checked inside the chain.
-To check the validity of a parameter, each validator independently performs an off-chain assertion, which is the same as the one used in the on-chain validation assertion.
+\item To check the validity of a parameter, each validator independently performs an off-chain assertion, which is the same as the one used in the on-chain assertion.
+The result of the calculation can be
+a counterexample, an award computational proof, or a non-award computational
+proof.
 The result is then submitted to the blockchain, which then uses the on-chain assertion to verify the submission.
-The off-chain assertion contains the negation formulas of the assertion for parameters and takes a seed and a parameter as input.
-\item We define a domain specific language (DSL) to express assertions.
-The main actor in our method is the on/off assertion contracts.
-We propose an algorithm to automatically generate the on/off-chain assertion contract from an assertion written in our DSL.
+The on/off-chain assertion contains the negation formulas of the assertion for parameters and takes a seed and a parameter as input.
+\item We define a assertion domain specific language (ADSL) to express assertions.
+The main actor in our method is the on/off-chain assertion contracts.
+We propose an algorithm to automatically generate the on/off-chain assertion contract from an assertion written in our ADSL.
 The algorithm is then implemented as a converter that takes the AST of an assertion after the parser (or the AST for its negation after the transformer step) and returns the on/off-chain assertion contract written in Michelson (Solidity).
-To perform the conversion automatically, we constrain the semantics of the DSL.
+To perform the conversion automatically, we constrain the semantics of the ADSL.
 So far, we have done:
 \begin{itemize}
-\item completing the design and implementation of a DSL to express the assertion (reused Tamara work).
-\item proposing an algorithm to automatically convert an assertion to the on/off-chain smart contract.
+\item completed the design and implementation of a ADSL to express the assertion (reused Tamara work).
+\item proposed an algorithm to automatically convert an assertion  written in ADSL to the on/off-chain assertion.
 \end{itemize}
@@
 \begin{itemize}
-\item We proposed a symbolic execution model for Michelson that allows us to ensure type-safe invocation of the contract on the blockchain.
-Namely, the model allows us to express the pre- and post-conditions and then specify invariants.
-In addition, we can use the model to impose constraints on the possible call orders of the entrypoints.
+\item We have proposed a symbolic execution model for Michelson that allows us to ensure safe invocations of a contract on the blockchain.
+The model allows us to express preconditions and postconditions and then specify invariants and constraints that are then used to ensure a secure invocation.
+We can also use the model to constrain the possible call sequences of the entrypoints.
 \item Thiemann implemented a symbolic execution for Michelson in Ocaml.
@@
 \item The typed Tezos API is completely implemented.
+\item The ADSL for specifying assertions for distributed checking and an alorithm to deploy the assertion on the blockchain system (Tezos and Ethereum).
 \item a symbolic execution model for Michelson that allows us to specify pre-conditions, post-conditions, and allowable call sequences for entrypoints; 

### 2022-09-26 reports/2022-09-06/COOC-report.tex
cosmetics

@@
 Since the type has already been checked, it is ensured that the contract can only be called with arguments of the correct type.
-\item  The current code of the Tezos API can be found on Github \cite{tezos-api-update}.
+\item  The current code of the Tezos API can be found on GitHub \cite{tezos-api-update}.
 There is also an environment that makes it easy to run a Tezos sandbox independent of the host system \cite{tezos-api-devenv}.
@@
 
-\paragraph{October 2021 - March 2022: Michelson One-step Execusion Interpreter} 
+\paragraph{October 2021 - March 2022: A Stepper for Michelson} 
 \begin{itemize}
 \item When writing code in Michelson, you have to keep track of the stack and what happens to it with each instruction.
-This is awkward for a larger program, since you have to follow either mentally or in writing, or make do with the hard-to-understand interfaces.
-Hasan Berkay's project therefore aims to provide a snapshot of the stack before and after the execution of each instruction in a programmatically accessible data format.
-In this way, with a suitable complementary user interface, it is much easier to track each step along the entire execution of the script and better understand errors.
+This is awkward for a larger program, since you have to follow either mentally or in writing.
+Hassan Berkay's project therefore aims to provide a snapshot of the stack before and after the execution of each instruction in a programmatically accessible data format.
+This way, with a suitable complementary user interface (which is currently under development), it is much easier to track each step along the entire execution of the script and better understand errors.
+We also intend to use this tool for teaching.
 \item The implementation was done in
@@
 All execution is simulated sequentially and depends on user input, with chain manipulation instructions being mostly no-ops. 
-\item In its current state, the interpreter is capable of working with instructions up to and including the Tezos protocol Babylon.
+\item In its current state, the stepper is capable of working with instructions up to and including the Tezos protocol Babylon.
 Since no complementary user interface is yet available, user acceptance is limited so far; however, tests with a number of scripts have shown correct results and stack continuity.
-\item The current code of the interpreter can be found on Github \cite{michelson-interpreter}.
+\item The current code of the stepper may be found on GitHub \cite{michelson-interpreter}.
 \end{itemize}
@@
 \begin{itemize}
-\item Dr.
-Doan and I runed the seminar course "Blockchain and Cryptocurrencies." There are 35 students registered for the seminar.
-However, due to our limited capacity, we can only accommodate 13 students.
+\item Dr. Doan and I offered the seminar course "Blockchain and Cryptocurrencies." There were 35 students registered for the seminar. However, due to limited capacity, we only accepted 13 students.  
 \item During the seminar, students research various topics on blockchain and smart contracts, starting from the engineering of blockchain, such as blockchain consensus, blockchain security and privacy, blockchain oracle, etc.
-to a smart contract, such as smart contract verification, smart contract securityand privacy, static analysis for smart contracts, etc.
-To complete the assignments, students research several blockchains, including the Tezos blockchain.
+to topics related to smart contracts, such as smart contract verification, smart contract security and privacy, static analysis for smart contracts, etc.
+To complete the assignments, students researched several blockchains, including the Tezos blockchain.
 \end{itemize}
@@
 
-\paragraph{December 2021: Presentation at APLAS Conferece}
+\paragraph{December 2021: Presentation at the APLAS Conference}
 
@@
 The goal is to reduce costs while preserving fundamental properties such as decentralization and trust.
-The senior is as follows.
+The revised approach is as follows.
 A caller submits a parameter to the blockchain that needs to be validated.
@@
 After the parameter is validated, the actual work that uses the parameter is executed.
-The idea behind our approach is that validation is done outside the chain, but the result of this process is then checked inside the chain.
+The idea behind our approach is that validation is done outside the chain, but the result of this process is then checked on the chain.
 \item To check the validity of a parameter, each validator independently performs an off-chain assertion, which is the same as the one used in the on-chain assertion.
-The result of the calculation can be
-a counterexample, an award computational proof, or a non-award computational
-proof.
-The result is then submitted to the blockchain, which then uses the on-chain assertion to verify the submission.
-The on/off-chain assertion contains the negation formulas of the assertion for parameters and takes a seed and a parameter as input.
-\item We define a assertion domain specific language (ADSL) to express assertions.
+The result of the calculation can be a counterexample or a proof-of-work that a  computational check was executed.
+Some of these checks earn a reward.
+The result is submitted to a contract on the blockchain, which uses the on-chain assertion to verify the submission.
+  % The on/off-chain assertion contains the negation formulas of the assertion for parameters and takes a seed and a parameter as input. 
+\item We defined a domain specific language to express assertions.
 The main actor in our method is the on/off-chain assertion contracts.
-We propose an algorithm to automatically generate the on/off-chain assertion contract from an assertion written in our ADSL.
-The algorithm is then implemented as a converter that takes the AST of an assertion after the parser (or the AST for its negation after the transformer step) and returns the on/off-chain assertion contract written in Michelson (Solidity).
-To perform the conversion automatically, we constrain the semantics of the ADSL.
+We propose an algorithm to automatically generate the on/off-chain assertion contract from an assertion written in our DSL.
+The algorithm is implemented as a converter that takes the AST of an assertion after the parser (or the AST for its negation after the transformer step) and returns the on/off-chain assertion contract written in Michelson.
+To perform the conversion automatically, we constrain the semantics of the DSL.
 So far, we have done:
 \begin{itemize}
-\item completed the design and implementation of a ADSL to express the assertion (reused Tamara work).
-\item proposed an algorithm to automatically convert an assertion  written in ADSL to the on/off-chain assertion.
+\item completed the design and implementation of the assertaion DSL (reused Tamara's work).
+\item proposed an algorithm to automatically convert an assertion to the on/off-chain assertion.
 \end{itemize}
@@
 \item Given an invocation of a smart contract, the invocation can be checked against these invariants and constraints before being used in the chain, where the invocation may be succeed. 
-\item The verification of invariants and constraints can be done using an SMT solver. For this purpose, we exploded the Z3 solver and its library into Ocaml.
+\item The verification of invariants and constraints can be done using an SMT solver. For this purpose, we explored the Z3 solver and its library into Ocaml.
 \end{itemize}
@@
 \end{itemize}
-
+\item We are currently extending this approach to type-state based specifications of multiple contracts / entrypoints.
+This approach is closely related to work on session types.
+This apparent connection has been used to advantage by other researchers, too.
 \end{itemize}
@@
 \begin{itemize}
-\item We plan to use an SMT solver, namely Z3  solver, as a type checker for the system and there is already an SMT checker for Solidity smart contract.
-It, therefore, would be useful to explore the capabilities and facilities of SMT solvers for smart contract verification.
-I have commissioned Khaled Fayed to research the SMT checker for Solidity as part of his bachelor's project.
+\item We plan to use an SMT solver, namely Z3, as a property checker for the system.
+As there is already a related checker for Solidity smart contract based on SMT, it is useful to  explore the capabilities and facilities of SMT solvers for smart contract verification.
+Our student  Khaled Fayed has been commissioned to research the SMT checker for Solidity as part of his bachelor's project.
 \end{itemize}
@@
 \begin{itemize}
-\item The symbolic execution suffers from the state explosion.
+\item Symbolic execution suffers from the state explosion.
 To check the precondition, it might be sufficient to collect the path conditions along with the execution.
@@
 
-\item The typed Tezos API is completely implemented.
-\item The ADSL for specifying assertions for distributed checking and an alorithm to deploy the assertion on the blockchain system (Tezos and Ethereum).
-\item a symbolic execution model for Michelson that allows us to specify pre-conditions, post-conditions, and allowable call sequences for entrypoints; 
+\item The typed OCaml-API for Tezos is completely implemented.
+\item The DSL for specifying assertions for distributed checking and an algorithm to  deploy the assertion on the blockchain system.
+\item A symbolic execution model for Michelson that allows us to specify pre-conditions, post-conditions, and allowable call sequences for entrypoints as well as between different contracts. 
 \end{itemize}
@@
 \begin{itemize}
-\item continues our teaching activities (the blockchain course, a seminar on the topic in the winter semester).
-\item assigns more students interested in research on blockchain in general and Tezos in particular.
+\item continue our teaching activities (the blockchain course, a seminar on the topic in the winter semester);
+\item find more students interested in research on blockchain in general and Tezos in particular.
 \end{itemize}
-\item Assertion contract:
+\item Assertion contracts:
 \begin{itemize}
-\item implements the converter for assertion contracts.
-Given a specification in the assertion domain specification language of a parameter that needs to be verified, the converter automatically generates the on/off-chain assertions (for Tezos and Ethereum)
-\item implements the ecosystem for deploying assertion contracts on the network (for Tezos and Ethereum). 
-\item documents the results in a paper on assertion contracts.
+\item implement the converter for assertion contracts.
+Given a specification in the assertion DSL of a parameter that needs to be verified, the converter automatically generates the on/off-chain assertions;
+\item implement the ecosystem for deploying assertion contracts on the network; 
+\item document our latest results in papers on assertion contracts and symbolic execution for Michelson;
+\item develop a dynamic logic as a formal basis for symbolic execution of Michelson.
 \end{itemize}
 
-\item Contract module and the checker for Michelsym smart contracts.
+\item Contract module and the checker for Michelson smart contracts:
 \begin{itemize}

### 2022-09-26 reports/2022-09-06/COOC-report.tex
spell checked

@@
 \item Research on distributed assertion checking for smart contracts was conducted by two students, Tamara Bernhardt and Julian Veigel, as part of their master's thesis, with Tamara defining the grammar for the assertion language and Julian presenting different approaches and discussing their strengths and weaknesses.
-However, the approaches proposed by Tamara and Julian require changes  in the backend system (Tezos and Etherum).
+However, the approaches proposed by Tamara and Julian require changes  in the backend system (Tezos and Ethereum).
 We therefore worked on a solution so that the approach can work without changes to the backend system.
@@
 \begin{itemize}
-\item completed the design and implementation of the assertaion DSL (reused Tamara's work).
+\item completed the design and implementation of the assertion DSL (reused Tamara's work).
 \item proposed an algorithm to automatically convert an assertion to the on/off-chain assertion.
@@
 \end{document}
+
+%  LocalWords:  Ocaml Ocaml Mundhahs tezos-api-devenv itemize Nearley
+%  LocalWords:  michelson-interpreter Veigel Ethereum concolic

### 2022-09-30 reports/proposal/proposal.tex
Add the proposal file

\documentclass[a4paper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{hyperref}
\usepackage{authblk}

\title{A Static Checked Interface and a Checker for Tezos Smart Contracts
}
\author{Peter Thiemann}
\author{Thi Thu Ha Doan}
\affil{University of Freiburg, Germany}
\begin{document}
\maketitle{}

\section{Executive Summary}
\label{sec:executive-summary}
The Tezos blockchain (like other blockchains) provides limited infrastructure for interacting with smart contracts on the chain. Programmatic interaction with a blockchain is often clumsy. Many interfaces only handle loosely structured data, often in JSON format, which is cumbersome to use and offers few guarantees. In addition, the safety of a contract call is not really guaranteed and it is difficult to handle a failed call. In many cases, smart contract invocations fail, even though some of these failures could be predicted before the invocation. In addition, smart contract developers have problems with formal verification of their smart contracts, which is an essential task due to the lack of platforms for formal verification of smart contracts.
The goals of this research are

\begin{itemize}
\item to provide statically checked interfaces wrapped in Contract modules to interact with contracts on the Tezos blockchain. This interface is statically checked against the contract implementation to ensure type safety and exception handling (any error condition that occurs is handled by an appropriate error message). One of the most important functions is static call checking to ensure call safety, or in other words, to prevent a failed call. 
\item to develop a checker for Tezos smart contracts that helps the developer to formally verify the smart contract before deployment.
\end{itemize}

This work is a continuation and extension of the Contract Orchestration for OCaml (COOC) project funded by the Tezos Foundation. The summary of the this work can be found on Github \cite{tezos-report}.

\section{Researchers}
\label{sec:researchers}
\paragraph{Peter Thiemann}
Peter Thiemann is a full professor for Informatics at Freiburg University.
His research focuses on programming and proving with types. Since 2004, he worked on
typing aspects as well as pragmatics of web programming. His contributions include client-server calculus, multi-tier programming, and protocol specialization, which are closely related to session types. With Neubauer, he was one of the first to propose and investigate multi-tier
programming. He served on the program committees of major programming languages conferences (POPL,
ICFP, OOPSLA, ESOP, ECOOP, LICS, CSF), was PC chair for ICFP, ESOP, and PPDP, and is cur-
rently chair of the ESOP steering committee. From 2015-2018 he served as vice-chair of ACM
SIGPLAN. He is also an associate editor of the Journal of Functional Programming.

\paragraph{Thi Thu Ha Doan} Thi Thu Ha Doan is a postdoctoral researcher at Freiburg University. Her research focuses on formal methods, formal verification, type and program, smart contracts, and blockchain. She has been a member of the program committees of APLAS 2022 and ICFEM 2022.

Peter Thiemann and Thi Thu Ha Doan have been working on the COOC project funded by the Tezos Foundation since 2020. Thiemann and Doan have worked on various aspects of type-safe interaction with the Tezos blockchain, distributed verification of assertions and Contract modules, and a checker for Michelson smart contracts. Together, we proposed a type-safe interaction between an Ocaml program and Michelson smart contracts on the Tezos blockchain. The typed OCaml API for Tezos was fully implemented. The work was presented and published at the APLAS 2021 conference \cite{DBLP:conf/fc/ThiemannAplas21}. The initial state of work on Contract modules was presented and published at the Formal Methods for Blockchains (FMBC 2021) workshop \cite{DBLP:conf/fc/ThiemannFmbc21}

\section{A Static Checked Programming Interfect}
\label{sec:checked-programming-interfect}
A Michelson contract may fail due to a programming condition caused by the FAILWITH statement. It terminates contract execution with an error message reported back to the caller. These conditions can be considered as preconditions for calling a smart contract in conjunction with an entry point. It is indeed expensive to invoke a contract and then find that it fails. Fortunately, some of these failures can be predicted by performing a static check before invocation.

The basic idea is that we create a contract module that attempts to check the preconditions outside the chain before the contract is invoked. Starting from a smart contract implementation, we automatically generate a contract module whose specification includes all types as well as information about possible failure conditions of the contract to ensure type-safe and sometimes fail-safe invocation of the contract on the blockchain. Contract modules provide a high-level interface that reduces a contract call to a function call in the language. Contract modules do not provide a fixed API, but generate a specific interface for each contract.

The specification is checked against the contract implementation by symbolic execution. Our work is related to the Tezos blockchain, which supports Michelson as a low-level contract language, and the OCaml language, which has an expressive polymorphic type system and a powerful module system that we extend with contract modules. We propose a symbolic execution model for Michelson in OCaml that allows us to guarantee secure invocations of a contract on the blockchain. The model allows us to formulate preconditions and postconditions, and then specify invariants and constraints that are used to guarantee a safe invocation. We can also use the model to constrain the possible invocation sequences of entry points. The contract model generated from a contract module is checked against the specification by symbolic execution. When a smart contract is invoked, the invocation can be checked against these invariants and constraints before it is used in the chain, calculating where the invocation may be succeed. The checking of invariants and constraints can be done with an SMT solver such as the Z3 solver and its library in Ocaml.

In the end, we would like to provide a platform that automatically generates the Contract module from a given smart contract specification in Michelson. The contract module guarantees a type-safe interaction and handles the error returned on a failed call. And it guarantees a safe invocation (on a failed invocation) by statically checking the correctness of the invocation before deployment.
\section{A Static Checker for Tezos Smart Contracts}
\label{sec:static-checker}
Verification of a smart contract is important because its implementation cannot be changed once it is deployed. However, there is not yet a sufficient tool to help developers of Tezos smart contracts to formally verify the contract. Therefore, another goal of our research is to develop a verification tool, a checker, for Michelson smart contracts. When a smart contract script is passed along with the specification of properties, the tool statically checks whether these properties are satisfied. In fact, symbolic execution could play the main role in checking properties. We first provide a domain-specific language (DSL) in which the user can specify the properties. The property specifications are then converted into formulas in Z3 in Ocaml, which are then checked against the smart contract implementation using symbolic execution.

Ultimately, we hope to provide a user-friendly checker for Tezos smart contract developers, where they only need to submit their contract implementation and the properties written in our DSL. The tool will statically check and report any invalid properties.

\section{Education and Dissemination}
\label{sec:education-dissemination}
In addition to our goal of publishing our work at high-profile conferences, we plan the following activities to teach and disseminate our work.
\begin{itemize}
\item Continue our teaching activities (the blockchain course, a seminar on the topic) and find more students interested in research on blockchain in general and Tezos in particular.
\item Once the tools we are developing are sufficiently mature, we will prepare tutorials for them, either at programming language research conferences or at venues aimed at a wider audience.
\end{itemize}

\bibliography{report}
\bibliographystyle{plainurl}
\end{document}

### 2022-09-30 reports/proposal/proposal.tex
updated

@@
 \item to provide statically checked interfaces wrapped in Contract modules to interact with contracts on the Tezos blockchain.
-This interface is statically checked against the contract implementation to ensure type safety and exception handling (any error condition that occurs is handled by an appropriate error message).
-One of the most important functions is static call checking to ensure call safety, or in other words, to prevent a failed call.
-\item to develop a checker for Tezos smart contracts that helps the developer to formally verify the smart contract before deployment.
+This interface statically checks against the contract implementation to ensure type safety and exception handling (any error condition that occurs is handled by an appropriate error message).
+One of the most important features is static call checking to ensure call safety, or in other words, to prevent a failed call.
+\item to develop a checker for Tezos to help developers formally check their smart contracts before deployment.
 \end{itemize}
@@
 Peter Thiemann and Thi Thu Ha Doan have been working on the COOC project funded by the Tezos Foundation since 2020.
-Thiemann and Doan have worked on various aspects of type-safe interaction with the Tezos blockchain, distributed verification of assertions and Contract modules, and a checker for Michelson smart contracts.
+Thiemann and Doan have worked on various aspects of type-safe interaction, distributed verification of assertions and Contract modules, and a checker for Michelson smart contracts.
 Together, we proposed a type-safe interaction between an Ocaml program and Michelson smart contracts on the Tezos blockchain.
@@
 It terminates contract execution with an error message reported back to the caller.
-These conditions can be considered as preconditions for calling a smart contract in conjunction with an entry point.
+These conditions can be considered as preconditions for calling a smart contract in conjunction with an entrypoint.
 It is indeed expensive to invoke a contract and then find that it fails.
@@
 
-The basic idea is that we create a contract module that attempts to check the preconditions outside the chain before the contract is invoked.
-Starting from a smart contract implementation, we automatically generate a contract module whose specification includes all types as well as information about possible failure conditions of the contract to ensure type-safe and sometimes fail-safe invocation of the contract on the blockchain.
+The basic idea is that we create a Contract module that attempts to check the preconditions outside the chain before the contract is invoked.
+Starting from a smart contract implementation, we automatically generate a Contract module whose specification includes all types as well as information about possible failure conditions of the contract to ensure type-safe and sometimes fail-safe invocation of the contract on the blockchain.
 Contract modules provide a high-level interface that reduces a contract call to a function call in the language.
@@
 
+Our work is related to the Tezos blockchain, which supports Michelson as a low-level contract language, and the OCaml language, which has an expressive polymorphic type system and a powerful module system that we extend with contract modules.
+We propose a symbolic execution model for Michelson that allows us to guarantee secure invocations of a contract on the blockchain.
+The model allows us to formulate preconditions and postconditions, and then specify invariants and constraints that are used to guarantee a safe invocation.
+We can also use the model to constrain the possible invocation sequences of entrypoints.
 The specification is checked against the contract implementation by symbolic execution.
-Our work is related to the Tezos blockchain, which supports Michelson as a low-level contract language, and the OCaml language, which has an expressive polymorphic type system and a powerful module system that we extend with contract modules.
-We propose a symbolic execution model for Michelson in OCaml that allows us to guarantee secure invocations of a contract on the blockchain.
-The model allows us to formulate preconditions and postconditions, and then specify invariants and constraints that are used to guarantee a safe invocation.
-We can also use the model to constrain the possible invocation sequences of entry points.
-The contract model generated from a contract module is checked against the specification by symbolic execution.
-When a smart contract is invoked, the invocation can be checked against these invariants and constraints before it is used in the chain, calculating where the invocation may be succeed.
+When a smart contract is invoked, the invocation can be checked against these invariants and constraints before it is used in the chain, where the invocation may be succeed.
 The checking of invariants and constraints can be done with an SMT solver such as the Z3 solver and its library in Ocaml.
@@
 The contract module guarantees a type-safe interaction and handles the error returned on a failed call.
-And it guarantees a safe invocation (on a failed invocation) by statically checking the correctness of the invocation before deployment.
+And it guarantees a safe invocation (or prevent a failed invocation) by statically checking the correctness of the invocation before deployment.
 \section{A Static Checker for Tezos Smart Contracts}

### 2022-09-30 reports/proposal/proposal.tex
updated

@@
 A Michelson contract may fail due to a programming condition caused by the FAILWITH statement.
-It terminates contract execution with an error message reported back to the caller.
-These conditions can be considered as preconditions for calling a smart contract in conjunction with an entrypoint.
+The execution of the contract is reported back to the caller with an error message.
+These conditions can be considered as a precondition for calling a smart contract in conjunction with an entrypoint.
 It is indeed expensive to invoke a contract and then find that it fails.
@@
 We propose a symbolic execution model for Michelson that allows us to guarantee secure invocations of a contract on the blockchain.
-The model allows us to formulate preconditions and postconditions, and then specify invariants and constraints that are used to guarantee a safe invocation.
+The model allows us to formulate preconditions and postconditions, and then specify invariants and constraints that guarantee a safe invocation.
 We can also use the model to constrain the possible invocation sequences of entrypoints.
 The specification is checked against the contract implementation by symbolic execution.
-When a smart contract is invoked, the invocation can be checked against these invariants and constraints before it is used in the chain, where the invocation may be succeed.
-The checking of invariants and constraints can be done with an SMT solver such as the Z3 solver and its library in Ocaml.
+When a smart contract is invoked, the invocation can be checked against these invariants and constraints before being used in the chain, where the invocation can succeed.
+Checking invariants and constraints can be done with an SMT solver like the Z3 solver and its library in Ocaml.
 
@@
 The contract module guarantees a type-safe interaction and handles the error returned on a failed call.
-And it guarantees a safe invocation (or prevent a failed invocation) by statically checking the correctness of the invocation before deployment.
+And it guarantees a safe invocation (or prevents a failed invocation) by statically checking the correctness of the invocation before deployment.
 \section{A Static Checker for Tezos Smart Contracts}

### 2022-10-11 reports/proposal/proposal.tex
as submitted

@@
 
-\title{A Static Checked Interface and a Checker for Tezos Smart Contracts
-}
+\title{A Statically Checked Interface and a Checker for Tezos Smart Contracts}
 \author{Peter Thiemann}
@@
 \label{sec:executive-summary}
-The Tezos blockchain (like other blockchains) provides limited infrastructure for interacting with smart contracts on the chain.
-Programmatic interaction with a blockchain is often clumsy.
-Many interfaces only handle loosely structured data, often in JSON format, which is cumbersome to use and offers few guarantees.
-In addition, the safety of a contract call is not really guaranteed and it is difficult to handle a failed call.
-In many cases, smart contract invocations fail, even though some of these failures could be predicted before the invocation.
-In addition, smart contract developers have problems with formal verification of their smart contracts, which is an essential task due to the lack of platforms for formal verification of smart contracts.
-The goals of this research are
+The Tezos blockchain (like other blockchains) provides a Web-based API and a client library for interacting with smart contracts on the chain.
+Programmatic interaction with a blockchain is often error prone.
+Web interfaces handle semi-structured data, often in JSON format, which is cumbersome to use and offers few guarantees.
+The client library also accepts data in a serialized format.
+Thus, the type safety of a contract call is not statically guaranteed and bad calls leads to run-time errors.
+
+Even type safe smart contract invocations may fail, if their preconditions are not fulfilled.
+Such failures are costly because transaction fees are wasted.
+Some of these failures can predicted before the invocation by probing the current state of the contract and exploiting known invariants and preconditions.
+While invariants can be established with a theorem prover, developers who are not experts in this area need automatic approaches to formal verification of  smart contracts.
+The goals of this research are:
 
 \begin{itemize}
-\item to provide statically checked interfaces wrapped in Contract modules to interact with contracts on the Tezos blockchain.
+\item to provide statically checked interfaces wrapped in Contract Modules to interact with contracts on the Tezos blockchain.
 This interface statically checks against the contract implementation to ensure type safety and exception handling (any error condition that occurs is handled by an appropriate error message).
-One of the most important features is static call checking to ensure call safety, or in other words, to prevent a failed call.
-\item to develop a checker for Tezos to help developers formally check their smart contracts before deployment.
+One of the most important features is to statically prevent a failed call;
+\item to develop an automatic checker for Michelson contracts to help developers formally specify the orchestration of their contracts and check their smart contracts before deployment.
 \end{itemize}
 
-This work is a continuation and extension of the Contract Orchestration for OCaml (COOC) project funded by the Tezos Foundation.
-The summary of the this work can be found on Github \cite{tezos-report}.
+This work is a continuation and extension of the Contract Orchestration for OCaml (COOC) project funded by the Tezos Foundation. The summary of this work can be found on Github \cite{tezos-report}.
 
@@
 \paragraph{Peter Thiemann}
-Peter Thiemann is a full professor for Informatics at Freiburg University.
+is a full professor for Informatics at Freiburg University.
 His research focuses on programming and proving with types. Since 2004, he worked on
@@
 programming. He served on the program committees of major programming languages conferences (POPL,
-ICFP, OOPSLA, ESOP, ECOOP, LICS, CSF), was PC chair for ICFP, ESOP, and PPDP, and is cur-
-rently chair of the ESOP steering committee. From 2015-2018 he served as vice-chair of ACM
+ICFP, OOPSLA, ESOP, ECOOP, LICS, CSF), was PC chair for ICFP, ESOP, and PPDP, and is currently chair of the POPL steering committee. From 2015-2018 he served as vice-chair of ACM
 SIGPLAN. He is also an associate editor of the Journal of Functional Programming.
 
-\paragraph{Thi Thu Ha Doan} Thi Thu Ha Doan is a postdoctoral researcher at Freiburg University.
+\paragraph{Thi Thu Ha Doan} is a postdoctoral researcher at Freiburg University.
+She is currently employed by the ongoing COOC project.
 Her research focuses on formal methods, formal verification, type and program, smart contracts, and blockchain.
@@
 
-Peter Thiemann and Thi Thu Ha Doan have been working on the COOC project funded by the Tezos Foundation since 2020.
+Doan and Thiemann have been working (with support by several student workers) on the COOC project funded by the Tezos Foundation  since 2020.
 Thiemann and Doan have worked on various aspects of type-safe interaction, distributed verification of assertions and Contract modules, and a checker for Michelson smart contracts.
-Together, we proposed a type-safe interaction between an Ocaml program and Michelson smart contracts on the Tezos blockchain.
+They proposed a type-safe interaction between an OCaml program and Michelson smart contracts on the Tezos blockchain.
 The typed OCaml API for Tezos was fully implemented.
-The work was presented and published at the APLAS 2021 conference \cite{DBLP:conf/fc/ThiemannAplas21}.
-The initial state of work on Contract modules was presented and published at the Formal Methods for Blockchains (FMBC 2021) workshop \cite{DBLP:conf/fc/ThiemannFmbc21}
+The work was presented and published at the APLAS 2021 conference \cite{DBLP:conf/aplas/DoanT21}.
+The initial state of work on Contract modules was presented and published at the Formal Methods for Blockchains (FMBC 2021) workshop \cite{DBLP:conf/cav/Doan021}.
 
-\section{A Static Checked Programming Interfect}
+\section{A Statically Checked Programming Interface}
 \label{sec:checked-programming-interfect}
-A Michelson contract may fail due to a programming condition caused by the FAILWITH statement.
-The execution of the contract is reported back to the caller with an error message.
-These conditions can be considered as a precondition for calling a smart contract in conjunction with an entrypoint.
-It is indeed expensive to invoke a contract and then find that it fails.
-Fortunately, some of these failures can be predicted by performing a static check before invocation.
 
-The basic idea is that we create a Contract module that attempts to check the preconditions outside the chain before the contract is invoked.
-Starting from a smart contract implementation, we automatically generate a Contract module whose specification includes all types as well as information about possible failure conditions of the contract to ensure type-safe and sometimes fail-safe invocation of the contract on the blockchain.
-Contract modules provide a high-level interface that reduces a contract call to a function call in the language.
-Contract modules do not provide a fixed API, but generate a specific interface for each contract.
+A Michelson contract fails if its execution runs into a \texttt{FAILWITH} statement.
+In this case, execution stops and the caller is notified with an error message.
+The transaction fee is still due, so failure is expensive.
+Verification of a contract avoids such failures by identifying/checking preconditions such that \texttt{FAILWITH} statements are not reachable.
+While full-blown verification with an interactive theorem prover is an option for sophisticated developers \cite{DBLP:conf/isola/BernardoCCJPT20}, we aim for an automatic solution.
 
-Our work is related to the Tezos blockchain, which supports Michelson as a low-level contract language, and the OCaml language, which has an expressive polymorphic type system and a powerful module system that we extend with contract modules.
-We propose a symbolic execution model for Michelson that allows us to guarantee secure invocations of a contract on the blockchain.
-The model allows us to formulate preconditions and postconditions, and then specify invariants and constraints that guarantee a safe invocation.
+The basic idea is that we consider ``Contract Modules'' that specify pre- and postconditions as well as contract orchestrations, i.e., valid sequences of contract invocations, i.e., uses of contract entrypoints.
+We generate code to check the preconditions off-chain before the contract is invoked.
+Starting from a smart contract implementation, we automatically generate a contract module whose specification includes all types as well as information about possible failure conditions of the contract to ensure mostly fail-safe invocation of the contract.
+We cannot guarantee full fail-safety due to possibly interleaved contract invocations from other parties.
+Contract modules provide a high-level, custom generated interface that reduces a contract call to a function call in the language.
+
+To obtain pre- and postconditions, we proposed a simple symbolic execution model for Michelson that allows us to guarantee secure invocations of a contract on the blockchain.
+%% The model allows us to formulate preconditions and postconditions, and then specify invariants and constraints that guarantee a  safe invocation. 
  We can also use the model to constrain the possible invocation sequences of entrypoints.
@@
 When a smart contract is invoked, the invocation can be checked against these invariants and constraints before being used in the chain, where the invocation can succeed.
-Checking invariants and constraints can be done with an SMT solver like the Z3 solver and its library in Ocaml.
+For our FMBC paper \cite{DBLP:conf/cav/Doan021}, we used Michelsym, a simple symbolic interpreter for Michelson.
+In this continuation project, we want to improve symbolic execution by incorporating an SMT solver like Z3 \cite{DBLP:conf/tacas/MouraB08}.
 
-In the end, we would like to provide a platform that automatically generates the Contract module from a given smart contract specification in Michelson.
-The contract module guarantees a type-safe interaction and handles the error returned on a failed call.
-And it guarantees a safe invocation (or prevents a failed invocation) by statically checking the correctness of the invocation before deployment.
 \section{A Static Checker for Tezos Smart Contracts}
 \label{sec:static-checker}
-Verification of a smart contract is important because its implementation cannot be changed once it is deployed.
-However, there is not yet a sufficient tool to help developers of Tezos smart contracts to formally verify the contract.
-Therefore, another goal of our research is to develop a verification tool, a checker, for Michelson smart contracts.
-When a smart contract script is passed along with the specification of properties, the tool statically checks whether these properties are satisfied.
-In fact, symbolic execution could play the main role in checking properties.
-We first provide a domain-specific language (DSL) in which the user can specify the properties.
-The property specifications are then converted into formulas in Z3 in Ocaml, which are then checked against the smart contract implementation using symbolic execution.
+
+Verification of a smart contract is important because its
+implementation cannot be changed once it is deployed. However,
+existing tools \cite{DBLP:conf/isola/BernardoCCJPT20} require a high
+level of sophistication in developers 
+to formally verify Michelson contracts. Therefore, another goal of
+our research  is to develop an automatic verification tool, a checker, for
+Michelson smart contracts. When a smart contract script is passed
+along with the specification of properties, the tool statically checks
+whether these properties are satisfied. We first provide a
+domain-specific language (DSL) in which the user can specify the
+properties. The property specifications are then converted into
+formulas in Z3 in OCaml, which are then checked against the smart
+contract implementation using symbolic execution.
 
@@
 
-\section{Education and Dissemination}
-\label{sec:education-dissemination}
-In addition to our goal of publishing our work at high-profile conferences, we plan the following activities to teach and disseminate our work.
+\section{Proposed Timeline and Activities}
+\label{sec:prop-timel-activ}
+
+\subsection{January 2023 - June 2023}
+
 \begin{itemize}
-\item Continue our teaching activities (the blockchain course, a seminar on the topic) and find more students interested in research on blockchain in general and Tezos in particular.
-\item Once the tools we are developing are sufficiently mature, we will prepare tutorials for them, either at programming language research conferences or at venues aimed at a wider audience.
+\item Activity: Development of a dynamic logic as a formal foundation for symbolic interpretation of Michelson. 
+\item Deliverable: Formalization (in Agda) of a dynamic logic for a core fragment of Michelson with soundness proof.
+\item Deliverable: Paper about this formalization (writeup starting July 2023).
 \end{itemize}
 
+\subsection{July 2023 - December 2023}
+\label{sec:july-2023-december}
+
+\begin{itemize}
+\item Activity: Implementation of symbolic interpreter for a core fragment of Michelson in OCaml based on an SMT solver, most likely on Z3. 
+\item Deliverable: Symbolic interpreter.
+\item Deliverable: Case studies with example contracts.
+\item Deliverable: Paper or tutorial on this tool (writeup starting January 2024)
+\end{itemize}
+
+\subsection{January 2024 - June 2024}
+\label{sec:january-2024-june}
+
+\begin{itemize}
+\item Activity: Design and implementation of a DSL for static contract properties. This DSL will compile to SMT and interface with the symbolic interpreter to perform verification.  
+\item Deliverable: Implementation of the DSL aka contract checker.
+\item Deliverable: Report on this tool.
+\end{itemize}
+
+\subsection{July 2024 - December 2024}
+\label{sec:july-2024-december}
+
+\begin{itemize}
+\item Activity: Complete design and implementation of the contract module DSL including contract orchestration. 
+\item Deliverable: Full implementation of contract modules.
+\item Deliverable: Followup on our FMBC paper. 
+\end{itemize}
+
+\section{Allocated Funds}
+\label{sec:allocated-funds}
+
+A total of 186,000 EUR distributed as follows:
+\begin{itemize}
+\item 160,000 EUR: one postdoc position for two years at 80,000 EUR per year.
+\item 12,000 EUR: part time student worker position for 12 months in total (help with implementation work).
+\item 12,000 EUR: travel funds for conference attendance (four conferences at 3000 EUR per conference). 
+\item 2,000 EUR: incidentals like replacement for broken server, broken laptop, etc.
+\end{itemize}
+
+\subsection{Remarks}
+\label{sec:remarks}
+
+\begin{itemize}
+\item
+  Travel funds should be applicable to all project participants:
+  student workers, postdoc, project lead.
+\item 
+  Funds for students, travel, and incidentals should be
+  interconvertible.
+\item 
+  The total amount of 186,000 EUR matches approximately the funds
+  remaining from the currently running COOC project.
+\end{itemize}
 \bibliography{report}

### 2022-12-06 meeting-notes/rollup-system/main.tex
First draft of Expose

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

\title{Expos\'{e} Master Thesis\\
  Rollup System for Layer 2 Scaling}
\author{Thi Thu Ha Doan \and  Peter Thiemann}
\date{December 2022}

\begin{document}

\maketitle

\section{Introduction}
The blockchain system has grown rapidly in recent years. However, the increased activity has come at a cost to use the network. Many blockchains have reached their capacity limits. The high demand on the network slows down transactions and increases gas prices, so a "scaling solution" is needed and becomes an urgent problem. The main goal of scalability is to increase transaction speed and throughput while ensuring decentralization and security.

Various scaling solutions have been proposed by both industry and academic circles. The solutions can be divided into two catalogues: first layer and second layer scaling solutions. The first layer scaling solutions (on-chain scaling) require changes to the blockchain protocol. For this solution, we can mention Proof-of-stake protocol and Sharding. Second layer scaling (off-chain scaling)  uses a separate network called layer 2 (L2) that runs on top of the main layer 1 (L1) network and derives the security guarantee from the main network. Current second layer scaling solutions include: State Channels, Sidechain, Plasma and Rollup.

Rollups is an off-chain scaling solution, which reduce computational overhead on the mainnet by moving computations and storage of out-of-chain state to L2. By publishing computation results on the chain, they preserve the security of the mainnet. Rollups can process a large number of transactions in a rollup batch and then send only some compressed summary data, defines the changes to be made to the state of the mainnet  to L1. This approach allows fixed costs to be spread across multiple transactions in each batch, thus reducing user charges. Rollups therefore provide a significant improvement in transaction throughput.

In rollup systems, users sign transactions and submit them to an aggregator (sequencer), which checks, orders, and executes these transactions. The aggregator then compresses the data into a rollup batch and publishes the batch as a single transaction on L1. There are two different ways to publish the data to the network. The first approach is optimistic rollup, which assumes that the off-chain transactions are valid and does not require validity proofs for off-chain transactions in the rollup batch. Another approach is zero-knowladge rollup (ZK rollup), in which the aggregator must publish proofs of validity. In contrast, an optimistic rollup responds to a fraud proof to determine where transactions are invalid. After a rollup batch is submitted on L1, anyone can challenge the results of a rollup transaction by computing a fraud proof.

%There are no delays when moving funds from a ZK-rollup because exit transactions are executed once the ZK-rollup contract verifies the validity proof. Conversely, withdrawing funds from optimistic rollups is subject to a delay to allow anyone to challenge the exit transaction with a fraud proof. Delays in transaction finality due to potential fraud challenges.

\begin{figure}[t]
\caption{Rollup systems}
\includegraphics[width=12cm]{rollup-batch}
\centering
\end{figure}

The goal of this work is to investigate the efficiency of the rollup scaling solution for the blockchain scaling problem. This work aim to explain the rollup technology in depth.  We design and implement a prototype of the rollup system that covers all the main architects of a rollup system, but keeps it as the core system.

\section{Design and Implementation of the Rollup System}
The rollup system is an off-chain scaling solution and operates on top of the main network. We tend to keep the prototype pure. The implementation contains the core components of a rollup system, but is able to extend the system if we want to enrich it for future research. For security, the system relies on a fraud proof process like in optimistic rollups. A fraud proof is an assertion that a state transition is invalid and therefore the entire batch should be reversed. The system targets the Etherum blockchain, which is the second largest blockchain and seriously suffers from a "scaling problem." The architect of the rollup system is shown in Fig~\ref{rollup-design}.
\begin{figure}[t]
\caption{Design of the rollup system}
\includegraphics[width=12cm]{rollup-design.png}
\centering
\label{rollup-design}
\end{figure}

\subsection{Interacting with the main network}
The operation of the rollup system is controlled by a smart contract deployed on-chain. The L2 system interacts with L1  through the smart contract. The contract receives and process rollup batches. It also stores and  updates the rollup system state (state root), and tracks user deposits. In addition, the contract provides functions to verify rollup batches in the challenge period.

Users must deposit money into the contract before they can use the system. The money is then locked into the contract and the user receives a corresponding amount that can be used in the rollup system.
\subsection{Submitting rollup batches}
The aggregator receives transactions signed and sent by users. In a rollup system, a transaction may come from a user in L2 via a direct peer-to-peer network or from L1 via an intermediate contract running on L1. However, here the rollup system only serves transactions from users in L2. After the aggregator receives the transactions from users, it verifies, orders, and executes them. The aggregator then bundles the off-chain transactions into a rollup batch and sends it to L1 via the smart contract. In this process, the transaction data is compressed and published on-chain as calldata. The published data contains the system state and the transaction batch in a highly compressed form. Since calldata is on-chain as part of the history logs, but is not stored in the smart contract, it is cheaper.

A system state ( Fig~\ref{rollup-batch-data}) is a term that refers to the available information about the rollup network at a given time. The state includes key information about the network such as accounts, balances, etc. It is organized as a Merkle tree and the root of this tree is the state root, which refers to the last state of the rollup system. Each state transition in the chain results in a new rollup state, which the aggregator determines by computing a new state root. This root state is hashed, sent, and stored in the on-chain smart contract. The aggregator must transmit both the previous and new state roots when it publishes rollup batches. If the previous state root matches the existing state root in the smart contract, the latter is discarded and replaced with the new state root (post state root).

\subsection{Data availability}

For example, the fact that a malicious aggregator can steal funds by publishing invalid transaction and root state. The security of the system relies on an honest verifier re-executing all transactions in a rollup batch and submitting fraud proofs to challenge invalid state transitions. Since rollup chain execution is based on the submitted transactions-ralated data, anyone can use this information to execute the rollup state and verify the correctness of the state transitions.
Data availability is critical because without access to the state data, the verifier cannot create fraud evidence to dispute invalid rollup batches. To this end, all necessary transaction information must be published in L1 so that the transaction can be re-run if necessary

However, if the full transaction data is published as calldata on the mainnet, this could be expensive. Therefore, the rollup system uses compression techniques to reduce the amount of transaction-related data. Compression of the data is achieved by publishing only the information required to deterministically re-execute the transaction. The batch of these transactions in compressed form is published on the chain as call data for the smart contract.
\begin{figure}[t]
\includegraphics[width=12cm]{rollup-batch-data}
\centering
\end{figure}
\subsection{Dispute period}
The system allows the aggregator to publish rollup batches without providing any proof of validity. However, to prevent any misbehaviour by the aggregator, the rollup system proposes a time period, called the challenge period, during which anyone can challenge a state transition. This actor is called a verifier in our model. Note that when rollup batches are published to L1, the aggregator must deposit a certain amount of funds that is locked until  the end of the challenge period. Similarly, the verifier must lock the same amount as the aggregator if it wishes to challenge the aggregator.

When a verifier initiates the dispute process by submitting a fraud proof claiming that a state transition is invalid and therefore the entire batch should be reversed, the system  re-executes transactions in the rollup batch on the main chain to calculate the post-root state determining who wins the challenge.  If this root state is different from the one submitted by the aggregator, the aggregator is penalised. As a result, half of the aggregator's deposit is transferred to the verifier and the other half is burned. If the verifier fails to prove the aggregator's misconduct, the same will happen to the verifier's deposit.

\section{Tasks}
\subsection{Survey on the current rollup technologies}
\begin{itemize}
    \item Optimistic rollups.
    \item ZK-rollups.
    \item The efficiency of rollups to Layer 2 scaling.
\end{itemize}
\subsection{Investing technologies}
\begin{itemize}
    \item The state tree and the state root.
    \item Data compression: several techniques to achieve transaction data compression and improve TPS rates. 
    \item Dispute progress.
\end{itemize}
\subsection{Developing the rollup system}
\begin{itemize}
    \item Design, code and deploy the smart contract on chain.
    \item Implement the layer 2 system.
    \item Develop the interface to interaction between L1 and L2.
\end{itemize}
\end{document}

### 2022-12-06 meeting-notes/rollup-system/main.tex
some revision are added

@@
 
-Rollups is an off-chain scaling solution, which reduce computational overhead on the mainnet by moving computations and storage of out-of-chain state to L2.
+Rollups is an off-chain scaling solution, which reduce computational overhead on the mainnet by moving computations and storage out-of-chain to L2.
 By publishing computation results on the chain, they preserve the security of the mainnet.
@@
 
-For example, the fact that a malicious aggregator can steal funds by publishing invalid transaction and root state.
-The security of the system relies on an honest verifier re-executing all transactions in a rollup batch and submitting fraud proofs to challenge invalid state transitions.
-Since rollup chain execution is based on the submitted transactions-ralated data, anyone can use this information to execute the rollup state and verify the correctness of the state transitions.
+Due to the fact that a malicious aggregator can steal funds by publishing invalid transaction and root state, the security of the system relies on an honest verifier re-executing transactions in a rollup batch and submitting fraud proofs to challenge invalid state transitions.
+Since the on-chain execution is based on the submitted transactions-related data, anyone can use this information to execute the rollup state and verify the correctness of the state transitions.
 Data availability is critical because without access to the state data, the verifier cannot create fraud evidence to dispute invalid rollup batches.
-To this end, all necessary transaction information must be published in L1 so that the transaction can be re-run if necessary
+Therefore, all necessary transaction information must be published in L1 so that these transactions can be re-run if necessary.
 

### 2022-12-06 meeting-notes/rollup-system/main.tex
some revisions made

@@
 \section{Introduction}
-The blockchain system has grown rapidly in recent years.
+The blockchain systems have grown rapidly in recent years.
 However, the increased activity has come at a cost to use the network.
@@
 
-Various scaling solutions have been proposed by both industry and academic circles.
+Various scaling solutions have been proposed by both industry and academic communities.
 The solutions can be divided into two catalogues: first layer and second layer scaling solutions.
@@
 Rollups is an off-chain scaling solution, which reduce computational overhead on the mainnet by moving computations and storage out-of-chain to L2.
-By publishing computation results on the chain, they preserve the security of the mainnet.
-Rollups can process a large number of transactions in a rollup batch and then send only some compressed summary data, defines the changes to be made to the state of the mainnet  to L1.
+Rollup systems inherit the security of the mainnet by publishing computation results on the chain as shown in Fig~\ref{rollup-batch}.
+Rollups process a large number of transactions in a rollup batch and then send only  compressed summary data, defines the changes to be made to the state of the mainnet  to L1.
 This approach allows fixed costs to be spread across multiple transactions in each batch, thus reducing user charges.
@@
 
+\begin{figure}[t]
+\caption{Rollup systems}
+\includegraphics[width=12cm]{rollup-batch}
+\label{rollup-batch}
+\centering
+\end{figure}
+
+The goal of this work is to investigate the efficiency of the rollup scaling solution for the blockchain scaling problem.
+This work aim to explain the rollup technology in depth.
+We design and implement a prototype of  rollup systems that covers all the main architects of a rollup system, but keeps it as the core system.
+
+\section{Design and Implementation of the Rollup System}
 In rollup systems, users sign transactions and submit them to an aggregator (sequencer), which checks, orders, and executes these transactions.
@@
 
-%There are no delays when moving funds from a ZK-rollup because exit transactions are executed once the ZK-rollup contract verifies the validity proof.
-Conversely, withdrawing funds from optimistic rollups is subject to a delay to allow anyone to challenge the exit transaction with a fraud proof.
-Delays in transaction finality due to potential fraud challenges.
-
-\begin{figure}[t]
-\caption{Rollup systems}
-\includegraphics[width=12cm]{rollup-batch}
-\centering
-\end{figure}
-
-The goal of this work is to investigate the efficiency of the rollup scaling solution for the blockchain scaling problem.
-This work aim to explain the rollup technology in depth.
-We design and implement a prototype of the rollup system that covers all the main architects of a rollup system, but keeps it as the core system.
-
-\section{Design and Implementation of the Rollup System}
-The rollup system is an off-chain scaling solution and operates on top of the main network.
 We tend to keep the prototype pure.
@@
 \centering
+\label{rollup-batch-data}
 \end{figure}

### 2022-12-06 meeting-notes/rollup-system/main.tex
some revisions made

@@
 \section{Introduction}
-The blockchain systems have grown rapidly in recent years.
-However, the increased activity has come at a cost to use the network.
+Blockchain systems have grown rapidly in recent years.
+However, the increased activity has come at a cost to the use of the network.
 Many blockchains have reached their capacity limits.
@@
 
-Rollups is an off-chain scaling solution, which reduce computational overhead on the mainnet by moving computations and storage out-of-chain to L2.
-Rollup systems inherit the security of the mainnet by publishing computation results on the chain as shown in Fig~\ref{rollup-batch}.
-Rollups process a large number of transactions in a rollup batch and then send only  compressed summary data, defines the changes to be made to the state of the mainnet  to L1.
-This approach allows fixed costs to be spread across multiple transactions in each batch, thus reducing user charges.
+Rollups are an off-chain scaling solution that reduces computational overhead in the main network by moving computation and storage off-chain to L2.
+Rollup systems inherit the security of the mainnet by publishing computation results on the chain, as shown in Fig~\ref{rollup-batch}.
+Rollups process a large number of transactions in a rollup batch and then send the compressed summary data defining the changes to the system state to L1.
+This approach allows fixed costs to be spread across multiple transactions in each rollup batch, reducing user charges.
 Rollups therefore provide a significant improvement in transaction throughput.
@@
 
-\section{Design and Implementation of the Rollup System}
-In rollup systems, users sign transactions and submit them to an aggregator (sequencer), which checks, orders, and executes these transactions.
-The aggregator then compresses the data into a rollup batch and publishes the batch as a single transaction on L1.
+\section{Design and Implementation of a Prototype for Rollup Systems}
+In rollup systems, users sign transactions and submit them to an aggregator (sequencer) that checks, orders, and executes these transactions.
+The aggregator then compresses the data into a rollup batch and compresses the batch with other necessary data (e.g., system state ) into a rollup block and publishes that rollup block as a single transaction on L1.
 There are two different ways to publish the data to the network.
-The first approach is optimistic rollup, which assumes that the off-chain transactions are valid and does not require validity proofs for off-chain transactions in the rollup batch.
+The first approach is optimistic rollup, which assumes that the off-chain transactions are valid and does not require validity proofs for the off-chain transactions in the rollup batch.
 Another approach is zero-knowladge rollup (ZK rollup), in which the aggregator must publish proofs of validity.
 In contrast, an optimistic rollup responds to a fraud proof to determine where transactions are invalid.
-After a rollup batch is submitted on L1, anyone can challenge the results of a rollup transaction by computing a fraud proof.
+After a rollup batch is submitted to L1, anyone can challenge the results of a rollup transaction by computing a fraud proof.
 
 We tend to keep the prototype pure.
-The implementation contains the core components of a rollup system, but is able to extend the system if we want to enrich it for future research.
-For security, the system relies on a fraud proof process like in optimistic rollups.
+The implementation contains only the core components of a rollup system, but is capable of extending the system if we want to enrich it for future research.
+For security, the system relies on a fraud detection procedure as in optimistic rollups.
 A fraud proof is an assertion that a state transition is invalid and therefore the entire batch should be reversed.
-The system targets the Etherum blockchain, which is the second largest blockchain and seriously suffers from a "scaling problem." The architect of the rollup system is shown in Fig~\ref{rollup-design}.
+The prototype targets the Etherum blockchain, which is the second largest blockchain and has an urgent "scaling problem." The architect of the prototype rollup system is shown in Fig~\ref{rollup-design}.
+
 \begin{figure}[t]
@@
 \subsection{Interacting with the main network}
-The operation of the rollup system is controlled by a smart contract deployed on-chain.
+The operation of the rollup system is controlled by a smart contract deployed on- chain.
 The L2 system interacts with L1 through the smart contract.
-The contract receives and process rollup batches.
-It also stores and  updates the rollup system state (state root), and tracks user deposits.
+The contract receives and processes rollup blocks.
+It also stores and updates the status of the rollup system and tracks user deposits.
 In addition, the contract provides functions to verify rollup batches in the challenge period.
+Users must deposit money into the smart contract before they can use the system.
+The money is then locked in the contract and the user receives a corresponding amount that can be used in the rollup system.
 
-Users must deposit money into the contract before they can use the system.
-The money is then locked into the contract and the user receives a corresponding amount that can be used in the rollup system.
 \subsection{Submitting rollup batches}

### 2022-12-06 meeting-notes/rollup-system/main.tex
Some revision made

@@
 \subsection{Interacting with the main network}
-The operation of the rollup system is controlled by a smart contract deployed on- chain.
+The operation of the rollup system is controlled by a smart contract deployed on-chain.
 The L2 system interacts with L1 through the smart contract.
@@
 In a rollup system, a transaction may come from a user in L2 via a direct peer-to-peer network or from L1 via an intermediate contract running on L1.
-However, here the rollup system only serves transactions from users in L2.
+However, in this prototype rollup system, for simplicity, only transactions that are transmitted by and originate from users in L2 are offered.
 After the aggregator receives the transactions from users, it verifies, orders, and executes them.
-The aggregator then bundles the off-chain transactions into a rollup batch and sends it to L1 via the smart contract.
-In this process, the transaction data is compressed and published on-chain as calldata.
-The published data contains the system state and the transaction batch in a highly compressed form.
-Since calldata is on-chain as part of the history logs, but is not stored in the smart contract, it is cheaper.
+The aggregator then bundles the off-chain transactions into a rollup batch and sends it to L1 via the smart contract call.
+In this process, the transaction data is compressed and published on-chain as call data.
+The published data contains the system state root and the transaction stack in a rollup block in a highly compressed form.
+Since the calldata is on-chain as part of the history logs, but not stored in the smart contract, it is less expensive.
 
-A system state ( Fig~\ref{rollup-batch-data}) is a term that refers to the available information about the rollup network at a given time.
+A system state constructed as shown in  Fig~\ref{rollup-batch-data} is a term that refers to the available information about the rollup system at a given time.
 The state includes key information about the network such as accounts, balances, etc.
@@
 This root state is hashed, sent, and stored in the on-chain smart contract.
-The aggregator must transmit both the previous and new state roots when it publishes rollup batches.
+The aggregator must transmit both the previous and new state roots when it publishes the rollup batches.
 If the previous state root matches the existing state root in the smart contract, the latter is discarded and replaced with the new state root (post state root).
@@
 
-Due to the fact that a malicious aggregator can steal funds by publishing invalid transaction and root state, the security of the system relies on an honest verifier re-executing transactions in a rollup batch and submitting fraud proofs to challenge invalid state transitions.
-Since the on-chain execution is based on the submitted transactions-related data, anyone can use this information to execute the rollup state and verify the correctness of the state transitions.
-Data availability is critical because without access to the state data, the verifier cannot create fraud evidence to dispute invalid rollup batches.
-Therefore, all necessary transaction information must be published in L1 so that these transactions can be re-run if necessary.
+Since a malicious aggregator can steal funds by publishing invalid transactions and root state, the security of the system relies on an honest verifier re-executing transactions in a rollup batch and submitting fraud proofs to challenge invalid state transitions.
+Since on-chain execution is based on submitted transaction-related data, anyone can use this information to execute rollup state and verify the correctness of state transitions.
+Therefore, data availability is critical because without access to the state data, the verifier cannot create fraud evidence to dispute invalid rollup batches.
+Therefore, all required transaction information must be published in L1 so that these transactions can be re-executed when needed.
 
@@
 \subsection{Dispute period}
-The system allows the aggregator to publish rollup batches without providing any proof of validity.
-However, to prevent any misbehaviour by the aggregator, the rollup system proposes a time period, called the challenge period, during which anyone can challenge a state transition.
+The system allows the aggregator to publish rollup batches without providing proof of validity.
+However, to prevent any misbehaviour by the aggregator, the rollup system proposes a period of time, called the challenge period, during which anyone can challenge a state transition.
 This actor is called a verifier in our model.
-Note that when rollup batches are published to L1, the aggregator must deposit a certain amount of funds that is locked until  the end of the challenge period.
+Note that when rollup batches are published on L1, the aggregator must deposit a certain amount of funds that is locked until the end of the challenge period.
 Similarly, the verifier must lock the same amount as the aggregator if it wishes to challenge the aggregator.
 
-When a verifier initiates the dispute process by submitting a fraud proof claiming that a state transition is invalid and therefore the entire batch should be reversed, the system  re-executes transactions in the rollup batch on the main chain to calculate the post-root state determining who wins the challenge.
-If this root state is different from the one submitted by the aggregator, the aggregator is penalised.
+When a verifier initiates the dispute process by submitting a fraud proof claiming that a state transition is invalid and therefore the entire batch should be reversed, the system reruns the transactions in the rollup batch on the master chain to calculate the post-root state that determines who wins the challenge.
+If this root state is different from the one specified by the aggregator, the aggregator is penalised.
 As a result, half of the aggregator's deposit is transferred to the verifier and the other half is burned.
@@
 \section{Tasks}
-\subsection{Survey on the current rollup technologies}
+\subsection{Survey of current rollup technologies}
 \begin{itemize} 
 \item Optimistic rollups. 
-    \item ZK-rollups.
-    \item The efficiency of rollups to Layer 2 scaling.
+\item ZK rollups. 
+\item The efficiency of rollups for Layer 2 scaling.
 \end{itemize}
-\subsection{Investing technologies}
+\subsection{Investment technologies}
 \begin{itemize} 
-    \item The state tree and the state root.
-    \item Data compression: several techniques to achieve transaction data compression and improve TPS rates. 
+\item The state tree and state root. 
+\item Data compression: various techniques for compressing transaction data. 
 \item Dispute progress.
 \end{itemize}
-\subsection{Developing the rollup system}
+\subsection{development of rollup system}
 \begin{itemize} 
-    \item Design, code and deploy the smart contract on chain.
+\item Design, code, and deploy the smart contract on the chain. 
 \item Implement the layer 2 system. 
-    \item Develop the interface to interaction between L1 and L2.
+\item Develop the interface for interaction between L1 and L2.
 \end{itemize}

### 2022-12-07 meeting-notes/rollup-system/main.tex
start revision

@@
 
-\section{Introduction}
-Blockchain systems have grown rapidly in recent years.
-However, the increased activity has come at a cost to the use of the network.
-Many blockchains have reached their capacity limits.
-The high demand on the network slows down transactions and increases gas prices, so a "scaling solution" is needed and becomes an urgent problem.
-The main goal of scalability is to increase transaction speed and throughput while ensuring decentralization and security.
+\section{Design and Implementation of a Prototype for Rollup Systems}
 
-Various scaling solutions have been proposed by both industry and academic communities.
-The solutions can be divided into two catalogues: first layer and second layer scaling solutions.
-The first layer scaling solutions (on-chain scaling) require changes to the blockchain protocol.
-For this solution, we can mention Proof-of-stake protocol and Sharding.
-Second layer scaling (off-chain scaling)  uses a separate network called layer 2 (L2) that runs on top of the main layer 1 (L1) network and derives the security guarantee from the main network.
-Current second layer scaling solutions include: State Channels, Sidechain, Plasma and Rollup.
+% Blockchain systems have grown rapidly in recent years. However, the increased activity has come at
+% a cost to the use of the network. Many blockchains have reached their capacity limits. The high
+% demand on the network slows down transactions and increases gas prices, so a "scaling solution" is
+% needed and becomes an urgent problem. The main goal of scalability is to increase transaction
+% speed and throughput while ensuring decentralization and security.
 
-Rollups are an off-chain scaling solution that reduces computational overhead in the main network by moving computation and storage off-chain to L2.
-Rollup systems inherit the security of the mainnet by publishing computation results on the chain, as shown in Fig~\ref{rollup-batch}.
-Rollups process a large number of transactions in a rollup batch and then send the compressed summary data defining the changes to the system state to L1.
-This approach allows fixed costs to be spread across multiple transactions in each rollup batch, reducing user charges.
-Rollups therefore provide a significant improvement in transaction throughput.
+% Various scaling solutions have been proposed by both industry and academic communities. The
+% solutions can be divided into two catalogues: first layer and second layer scaling solutions. The
+% first layer scaling solutions (on-chain scaling) require changes to the blockchain protocol. For
+% this solution, we can mention Proof-of-stake protocol and Sharding. Second layer scaling
+% (off-chain scaling)  uses a separate network called layer 2 (L2) that runs on top of the main
+% layer 1 (L1) network and derives the security guarantee from the main network. Current second
+% layer scaling solutions include: State Channels, Sidechain, Plasma and Rollup.
 
-\begin{figure}[t]
-\caption{Rollup systems}
-\includegraphics[width=12cm]{rollup-batch}
-\label{rollup-batch}
-\centering
-\end{figure}
+% Rollups are an off-chain scaling solution that reduces computational overhead in the main network
+% by moving computation and storage off-chain to L2. Rollup systems inherit the security of the
+% mainnet by publishing computation results on the chain, as shown in
+% Fig~\ref{rollup-batch}. Rollups process a large number of transactions in a rollup batch and then
+% send the compressed summary data defining the changes to the system state to L1. This approach
+% allows fixed costs to be spread across multiple transactions in each rollup batch, reducing user
+% charges. Rollups therefore provide a significant improvement in transaction throughput.
 
-The goal of this work is to investigate the efficiency of the rollup scaling solution for the blockchain scaling problem.
-This work aim to explain the rollup technology in depth.
-We design and implement a prototype of  rollup systems that covers all the main architects of a rollup system, but keeps it as the core system.
+% \begin{figure}[t]
+% \caption{Rollup systems}
+% \includegraphics[width=12cm]{rollup-batch}
+% \label{rollup-batch}
+% \centering
+% \end{figure}
 
-\section{Design and Implementation of a Prototype for Rollup Systems}
+The goal of this work is to investigate the design and implementation of a rollup system for the Ethereum blockchain. To make that palatable, we suggest a number of restrictions on the functionality:
+\begin{itemize}
+\item only transfers of Ether, i.e., there are no contracts on the rollup;
+\item optimistic rollup (less ambitious).
+\end{itemize}
+
+\subsection{Design considerations}
+\label{sec:design-consy}
+
 In rollup systems, users sign transactions and submit them to an aggregator (sequencer) that checks, orders, and executes these transactions.
@@
 
-We tend to keep the prototype pure.
-The implementation contains only the core components of a rollup system, but is capable of extending the system if we want to enrich it for future research.
-For security, the system relies on a fraud detection procedure as in optimistic rollups.
-A fraud proof is an assertion that a state transition is invalid and therefore the entire batch should be reversed.
-The prototype targets the Etherum blockchain, which is the second largest blockchain and has an urgent "scaling problem." The architect of the prototype rollup system is shown in Fig~\ref{rollup-design}.
+The design should contain only the core components of a rollup system, but is capable of extending
+the system if we want to enrich it for future research. For security, the system relies on a fraud
+detection procedure as in optimistic rollups. A fraud proof is an assertion that a state transition
+is invalid and therefore the entire batch should be reversed. The prototype targets the Etherum
+blockchain. Fig~\ref{rollup-design} sketches a possible architecture of the prototype rollup system.
 

### 2022-12-07 meeting-notes/rollup-system/main.tex
Make it less detail

@@
 In rollup systems, users sign transactions and submit them to an aggregator (sequencer) that checks, orders, and executes these transactions.
-The aggregator then compresses the data into a rollup batch and compresses the batch with other necessary data (e.g., system state ) into a rollup block and publishes that rollup block as a single transaction on L1.
+The aggregator then compresses the data into a rollup batch and compresses the batch with other necessary data (e.g., system state ) into a rollup block and publishes that rollup block as a single transaction on Layer 1 (L1).
 There are two different ways to publish the data to the network.
@@
 \subsection{Interacting with the main network}
-The operation of the rollup system is controlled by a smart contract deployed on-chain.
-The L2 system interacts with L1 through the smart contract.
-The contract receives and processes rollup blocks.
-It also stores and updates the status of the rollup system and tracks user deposits.
-In addition, the contract provides functions to verify rollup batches in the challenge period.
-Users must deposit money into the smart contract before they can use the system.
-The money is then locked in the contract and the user receives a corresponding amount that can be used in the rollup system.
+As depicted in Fig.~\ref{rollup-design}, the rollup system should include some main actors such as smart contract, aggregator, and verifier.
 
-\subsection{Submitting rollup batches}
+\subsubsection{On-chain smart contract}
+The operation of the rollup system is controlled by a smart contract that is deployed on-chain.
+Users must deposit funds into the smart contract before they can use the system.
+The funds is then locked in the contract and the user receives a corresponding amount that can be used in the rollup system.
+The smart contract is responsible  for the following tasks.
+\begin{itemize} 
+\item receives and processes rollup blocks; 
+\item stores and updates the status of the rollup system;  
+\item processes the dispute when it receives a fraud proof from a verifier in the challenge period.
+\end{itemize}
+
+\subsubsection{Aggregator}
+In a rollup system, a transaction can come from a user in layer 2 (L2) via a direct peer-to-peer network or from L1 via an intermediate contract running on L1.
+However, in this prototype rollup system, for simplicity, only transactions submitted by and originating from users in L2 are offered.
 The aggregator receives transactions signed and sent by users.
-In a rollup system, a transaction may come from a user in L2 via a direct peer-to-peer network or from L1 via an intermediate contract running on L1.
-However, in this prototype rollup system, for simplicity, only transactions that are transmitted by and originate from users in L2 are offered.
-After the aggregator receives the transactions from users, it verifies, orders, and executes them.
+After that, the aggregator
+\begin{itemize} 
+\item verifies, orders, and executes these transactions off-chain on L2; 
+\item bundles the transaction data in a rollup batch, compresses it, and forms a rollup block with this and other necessary data (e.g., system state ) to L1. 
+\end{itemize}
+%verifies, orders, and executes them.
 The aggregator then bundles the off-chain transactions into a rollup batch and sends it to L1 via the smart contract call.
@@
 
-A system state constructed as shown in  Fig~\ref{rollup-batch-data} is a term that refers to the available information about the rollup system at a given time.
+%A system state constructed as shown in  Fig~\ref{rollup-batch-data} is a term that refers to the available information about the rollup system at a given time.
 The state includes key information about the network such as accounts, balances, etc.
@@
 
+\subsubsection{Verifier}
+The system allows the aggregator to publish rollup batches without providing proof of validity.
+However, to prevent any misbehaviour by the aggregator, the rollup system proposes a period of time, called the challenge period, during which a verifier can challenge a state transition.
+Note that when rollup batches are published on L1, the aggregator must deposit a certain amount of funds that is locked until the end of the challenge period.
+Similarly, the verifier must lock the same amount as the aggregator when disputing the aggregator.
+
+When a verifier initiates the challenge process by submitting a fraud proof, the transactions in the rollup batch are re-executed on-chain to calculate the system state that determines who wins the challenge.
+If the aggregator is penalised, as a result, half of the aggregator's deposit is transferred to the verifier and the other half is burned.
+If the verifier fails to prove the aggregator's wrongdoing, the same will happen with the verifier's deposit.
+
+A verifier is responsible for
+\begin{itemize} 
+\item watches the rollup system to detect a published batch of invalid transactions and turns it into a fraud proof;
+\item starts the dispute process by submitting a fraud proof to L1 when it finds an invalid batch; 
+\item cooperates with L1 in the dispute process.
+\end{itemize}
+
 \subsection{Data availability}
+Since a malicious aggregator can steal funds by publishing invalid transactions and system states, the security of the system relies on an honest verifier re-executing transactions in a rollup batch and submitting fraud proofs to challenge invalid state transitions.
+Since on-chain execution is based on the submitted transaction batch, data availability is critical because without access to this data, the verifier cannot create fraud evidence.
+The published data contains the transaction batch and other necessary data in a rollup block in a highly compressed form.
+%A system state is a term that refers to the available information about the rollup system at a given time. 
+%The state includes key information about the network such as accounts, balances, etc.
 
-Since a malicious aggregator can steal funds by publishing invalid transactions and root state, the security of the system relies on an honest verifier re-executing transactions in a rollup batch and submitting fraud proofs to challenge invalid state transitions.
-Since on-chain execution is based on submitted transaction-related data, anyone can use this information to execute rollup state and verify the correctness of state transitions.
-Therefore, data availability is critical because without access to the state data, the verifier cannot create fraud evidence to dispute invalid rollup batches.
-Therefore, all required transaction information must be published in L1 so that these transactions can be re-executed when needed.
-
-However, if the full transaction data is published as calldata on the mainnet, this could be expensive.
+If the full transaction data is published on the mainnet, it could be expensive.
 Therefore, the rollup system uses compression techniques to reduce the amount of transaction-related data.
 Compression of the data is achieved by publishing only the information required to deterministically re-execute the transaction.
-The batch of these transactions in compressed form is published on the chain as call data for the smart contract.
-\begin{figure}[t]
-\includegraphics[width=12cm]{rollup-batch-data}
-\centering
-\label{rollup-batch-data}
-\end{figure}
-\subsection{Dispute period}
-The system allows the aggregator to publish rollup batches without providing proof of validity.
+The batch of these transactions in compressed form is published on-chain as calldata for the smart contract.
+
+%\begin{figure}[t]
+%\includegraphics[width=12cm]{rollup-batch-data}
+%\centering
+%\label{rollup-batch-data}
+%\end{figure}
+%\subsection{Dispute period}
+%The system allows the aggregator to publish rollup batches without providing proof of validity.
 However, to prevent any misbehaviour by the aggregator, the rollup system proposes a period of time, called the challenge period, during which anyone can challenge a state transition.
@@
 
-When a verifier initiates the dispute process by submitting a fraud proof claiming that a state transition is invalid and therefore the entire batch should be reversed, the system reruns the transactions in the rollup batch on the master chain to calculate the post-root state that determines who wins the challenge.
+%When a verifier initiates the dispute process by submitting a fraud proof claiming that a state transition is invalid and therefore the entire batch should be reversed, the system reruns the transactions in the rollup batch on the master chain to calculate the post-root state that determines who wins the challenge.
 If this root state is different from the one specified by the aggregator, the aggregator is penalised.
@@
 \end{itemize}
-\subsection{development of rollup system}
+\subsection{Development of rollup system}
 \begin{itemize} 
 \item Design, code, and deploy the smart contract on the chain. 
-\item Implement the layer 2 system. 
+\item Design and implement L2 system. 
 \item Develop the interface for interaction between L1 and L2.

### 2022-12-07 meeting-notes/rollup-system/main.tex
make it less details

@@
 \item verifies, orders, and executes these transactions off-chain on L2; 
-\item bundles the transaction data in a rollup batch, compresses it, and forms a rollup block with this and other necessary data (e.g., system state ) to L1. 
+\item bundles the transactions in a rollup batch, forms and publishes a rollup block to L1. 
 \end{itemize}
@@
 
-When a verifier initiates the challenge process by submitting a fraud proof, the transactions in the rollup batch are re-executed on-chain to calculate the system state that determines who wins the challenge.
+When a verifier initiates the challenge process by submitting a fraud proof, the transactions in the rollup batch are re-executed on-chain to determines who wins the challenge.
 If the aggregator is penalised, as a result, half of the aggregator's deposit is transferred to the verifier and the other half is burned.
@@
 \begin{itemize} 
-\item watches the rollup system to detect a published batch of invalid transactions and turns it into a fraud proof;
+\item watches the rollup system to detect a published batch with invalid transactions and turns it into a fraud proof;
 \item starts the dispute process by submitting a fraud proof to L1 when it finds an invalid batch; 
@@
 \subsection{Data availability}
-Since a malicious aggregator can steal funds by publishing invalid transactions and system states, the security of the system relies on an honest verifier re-executing transactions in a rollup batch and submitting fraud proofs to challenge invalid state transitions.
-Since on-chain execution is based on the submitted transaction batch, data availability is critical because without access to this data, the verifier cannot create fraud evidence.
-The published data contains the transaction batch and other necessary data in a rollup block in a highly compressed form.
+Since a malicious aggregator can steal funds by publishing invalid transactions, the security of the system relies on an honest verifier re-executing transactions in a rollup batch and submitting a fraud proof to challenge invalid state transitions.
+Since on-chain execution is based on the published data, the data availability is critical because without access to this data, the verifier cannot create fraud evidence.
+The data contains the transaction batch and other necessary data in a rollup block in a highly compressed form and is published on-chain as calldata for the smart contract.
 %A system state is a term that refers to the available information about the rollup system at a given time. 
@@
 Compression of the data is achieved by publishing only the information required to deterministically re-execute the transaction.
-The batch of these transactions in compressed form is published on-chain as calldata for the smart contract.
 

### 2022-12-08 meeting-notes/rollup-system/main.tex
spell-checked, some cosmetics

@@
 \item only transfers of Ether, i.e., there are no contracts on the rollup;
-\item optimistic rollup (less ambitious).
+\item optimistic rollup (less ambitious);
+\item only a single aggregator (rather than multiple, to avoid the need of a consensus protocol on the roll up).
 \end{itemize}
@@
 The first approach is optimistic rollup, which assumes that the off-chain transactions are valid and does not require validity proofs for the off-chain transactions in the rollup batch.
-Another approach is zero-knowladge rollup (ZK rollup), in which the aggregator must publish proofs of validity.
+Another approach is zero-knowledge rollup (ZK rollup), in which the aggregator must publish proofs of validity.
 In contrast, an optimistic rollup responds to a fraud proof to determine where transactions are invalid.
@@
 
-The design should contain only the core components of a rollup system, but is capable of extending
-the system if we want to enrich it for future research. For security, the system relies on a fraud
+The design should contain only the core components of a rollup system, but it should be designed for extensibility if we want to enrich it for future research.
+For security, the system relies on a fraud
 detection procedure as in optimistic rollups. A fraud proof is an assertion that a state transition
-is invalid and therefore the entire batch should be reversed. The prototype targets the Etherum
+is invalid and therefore the entire batch should be reversed. The prototype targets the Ethereum
 blockchain. Fig~\ref{rollup-design} sketches a possible architecture of the prototype rollup system.
@@
 \subsection{Interacting with the main network}
-As depicted in Fig.~\ref{rollup-design}, the rollup system should include some main actors such as smart contract, aggregator, and verifier.
+As depicted in Fig.~\ref{rollup-design}, the main actors of the rollup system are a moderating smart contract on the main chain, an aggregator, and a verifier.
 
@@
 The operation of the rollup system is controlled by a smart contract that is deployed on-chain.
-Users must deposit funds into the smart contract before they can use the system.
-The funds is then locked in the contract and the user receives a corresponding amount that can be used in the rollup system.
+Users must deposit funds into the smart contract before they can use the rollup.
+Funds are then locked in the contract and the user receives a corresponding amount of tokens on the rollup system.
 The smart contract is responsible  for the following tasks.
 \begin{itemize} 
-\item receives and processes rollup blocks; 
-\item stores and updates the status of the rollup system;  
-\item processes the dispute when it receives a fraud proof from a verifier in the challenge period.
+\item registering and deregistering users on the rollup;
+\item receiving and processing rollup block summaries; 
+\item storing and updating the status of the rollup system;  
+\item processing disputes when a verifier submits a fraud proof in the challenge period.
 \end{itemize}
@@
 However, to prevent any misbehaviour by the aggregator, the rollup system proposes a period of time, called the challenge period, during which a verifier can challenge a state transition.
-Note that when rollup batches are published on L1, the aggregator must deposit a certain amount of funds that is locked until the end of the challenge period.
+When rollup batches are published on L1, the aggregator must deposit a certain amount of funds that is locked until the end of the challenge period.
 Similarly, the verifier must lock the same amount as the aggregator when disputing the aggregator.
 
-When a verifier initiates the challenge process by submitting a fraud proof, the transactions in the rollup batch are re-executed on-chain to determines who wins the challenge.
+When a verifier initiates the challenge process by submitting a fraud proof, the transactions in the rollup batch are re-executed on-chain to determine who wins the challenge.
 If the aggregator is penalised, as a result, half of the aggregator's deposit is transferred to the verifier and the other half is burned.
@@
 \begin{itemize} 
-\item watches the rollup system to detect a published batch with invalid transactions and turns it into a fraud proof;
-\item starts the dispute process by submitting a fraud proof to L1 when it finds an invalid batch; 
-\item cooperates with L1 in the dispute process.
+\item watching the rollup system to detect a published batch with invalid transactions and turn it into a fraud proof;
+\item starting the dispute process by submitting a fraud proof to L1 when it finds an invalid batch; 
+\item cooperating with L1 in the dispute process.
 \end{itemize}
@@
 \subsection{Data availability}
-Since a malicious aggregator can steal funds by publishing invalid transactions, the security of the system relies on an honest verifier re-executing transactions in a rollup batch and submitting a fraud proof to challenge invalid state transitions.
+Since a malicious aggregator can steal funds by publishing invalid transactions, the security of the system relies on honest verifier(s) re-executing transactions in a rollup batch and submitting a fraud proof to challenge invalid state transitions.
 Since on-chain execution is based on the published data, the data availability is critical because without access to this data, the verifier cannot create fraud evidence.
@@
 
-If the full transaction data is published on the mainnet, it could be expensive.
+Publishing the full transaction data on the mainnet could be expensive.
 Therefore, the rollup system uses compression techniques to reduce the amount of transaction-related data.
@@
 \section{Tasks}
-\subsection{Survey of current rollup technologies}
+\subsection{Related work: Survey of current rollup technologies}
 \begin{itemize} 

### 2023-07-20 reports/2023-07-01/report.tex
submitted

--- 2022-10-11 reports/proposal/proposal.tex
@@
 
-\section{Executive Summary}
+\section{Report January-June 2023}
 \label{sec:executive-summary}
-The Tezos blockchain (like other blockchains) provides a Web-based API and a client library for interacting with smart contracts on the chain.
-Programmatic interaction with a blockchain is often error prone.
-Web interfaces handle semi-structured data, often in JSON format, which is cumbersome to use and offers few guarantees.
-The client library also accepts data in a serialized format.
-Thus, the type safety of a contract call is not statically guaranteed and bad calls leads to run-time errors.
 
-Even type safe smart contract invocations may fail, if their preconditions are not fulfilled.
-Such failures are costly because transaction fees are wasted.
-Some of these failures can predicted before the invocation by probing the current state of the contract and exploiting known invariants and preconditions.
-While invariants can be established with a theorem prover, developers who are not experts in this area need automatic approaches to formal verification of  smart contracts.
-The goals of this research are:
+We proposed the following activities and deliverables for the
+project. We started all planned activities for the reporting period
+and we already started some planned activities for the next period.
 
-\begin{itemize}
-\item to provide statically checked interfaces wrapped in Contract Modules to interact with contracts on the Tezos blockchain.
-This interface statically checks against the contract implementation to ensure type safety and exception handling (any error condition that occurs is handled by an appropriate error message).
-One of the most important features is to statically prevent a failed call;
-\item to develop an automatic checker for Michelson contracts to help developers formally specify the orchestration of their contracts and check their smart contracts before deployment.
-\end{itemize}
-
-This work is a continuation and extension of the Contract Orchestration for OCaml (COOC) project funded by the Tezos Foundation. The summary of this work can be found on Github \cite{tezos-report}.
-
-\section{Researchers}
-\label{sec:researchers}
-\paragraph{Peter Thiemann}
-is a full professor for Informatics at Freiburg University.
-His research focuses on programming and proving with types. Since 2004, he worked on
-typing aspects as well as pragmatics of web programming.
-His contributions include client-server calculus, multi-tier programming, and protocol specialization, which are closely related to session types.
-With Neubauer, he was one of the first to propose and investigate multi-tier
-programming. He served on the program committees of major programming languages conferences (POPL,
-ICFP, OOPSLA, ESOP, ECOOP, LICS, CSF), was PC chair for ICFP, ESOP, and PPDP, and is currently chair of the POPL steering committee. From 2015-2018 he served as vice-chair of ACM
-SIGPLAN. He is also an associate editor of the Journal of Functional Programming.
-
-\paragraph{Thi Thu Ha Doan} is a postdoctoral researcher at Freiburg University.
-She is currently employed by the ongoing COOC project.
-Her research focuses on formal methods, formal verification, type and program, smart contracts, and blockchain.
-She has been a member of the program committees of APLAS 2022 and ICFEM 2022.
-
-Doan and Thiemann have been working (with support by several student workers) on the COOC project funded by the Tezos Foundation  since 2020.
-Thiemann and Doan have worked on various aspects of type-safe interaction, distributed verification of assertions and Contract modules, and a checker for Michelson smart contracts.
-They proposed a type-safe interaction between an OCaml program and Michelson smart contracts on the Tezos blockchain.
-The typed OCaml API for Tezos was fully implemented.
-The work was presented and published at the APLAS 2021 conference \cite{DBLP:conf/aplas/DoanT21}.
-The initial state of work on Contract modules was presented and published at the Formal Methods for Blockchains (FMBC 2021) workshop \cite{DBLP:conf/cav/Doan021}.
-
-\section{A Statically Checked Programming Interface}
-\label{sec:checked-programming-interfect}
-
-A Michelson contract fails if its execution runs into a \texttt{FAILWITH} statement.
-In this case, execution stops and the caller is notified with an error message.
-The transaction fee is still due, so failure is expensive.
-Verification of a contract avoids such failures by identifying/checking preconditions such that \texttt{FAILWITH} statements are not reachable.
-While full-blown verification with an interactive theorem prover is an option for sophisticated developers \cite{DBLP:conf/isola/BernardoCCJPT20}, we aim for an automatic solution.
-
-The basic idea is that we consider ``Contract Modules'' that specify pre- and postconditions as well as contract orchestrations, i.e., valid sequences of contract invocations, i.e., uses of contract entrypoints.
-We generate code to check the preconditions off-chain before the contract is invoked.
-Starting from a smart contract implementation, we automatically generate a contract module whose specification includes all types as well as information about possible failure conditions of the contract to ensure mostly fail-safe invocation of the contract.
-We cannot guarantee full fail-safety due to possibly interleaved contract invocations from other parties.
-Contract modules provide a high-level, custom generated interface that reduces a contract call to a function call in the language.
-
-To obtain pre- and postconditions, we proposed a simple symbolic execution model for Michelson that allows us to guarantee secure invocations of a contract on the blockchain.
-%% The model allows us to formulate preconditions and postconditions, and then specify invariants and constraints that guarantee a  safe invocation. 
- We can also use the model to constrain the possible invocation sequences of entrypoints.
-The specification is checked against the contract implementation by symbolic execution.
-When a smart contract is invoked, the invocation can be checked against these invariants and constraints before being used in the chain, where the invocation can succeed.
-For our FMBC paper \cite{DBLP:conf/cav/Doan021}, we used Michelsym, a simple symbolic interpreter for Michelson.
-In this continuation project, we want to improve symbolic execution by incorporating an SMT solver like Z3 \cite{DBLP:conf/tacas/MouraB08}.
-
-\section{A Static Checker for Tezos Smart Contracts}
-\label{sec:static-checker}
-
-Verification of a smart contract is important because its
-implementation cannot be changed once it is deployed. However,
-existing tools \cite{DBLP:conf/isola/BernardoCCJPT20} require a high
-level of sophistication in developers 
-to formally verify Michelson contracts. Therefore, another goal of
-our research  is to develop an automatic verification tool, a checker, for
-Michelson smart contracts. When a smart contract script is passed
-along with the specification of properties, the tool statically checks
-whether these properties are satisfied. We first provide a
-domain-specific language (DSL) in which the user can specify the
-properties. The property specifications are then converted into
-formulas in Z3 in OCaml, which are then checked against the smart
-contract implementation using symbolic execution.
-
-Ultimately, we hope to provide a user-friendly checker for Tezos smart contract developers, where they only need to submit their contract implementation and the properties written in our DSL.
-The tool will statically check and report any invalid properties.
-
-\section{Proposed Timeline and Activities}
-\label{sec:prop-timel-activ}
+Currently, the project is on track and making good progress, but Ms.\ Doan is on maternal leave
+and it is unclear if she will take parental leave thereafter. If she
+does, it may lead to unforseeable delays.
 
@@
 \begin{itemize}
-\item Activity: Development of a dynamic logic as a formal foundation for symbolic interpretation of Michelson. 
-\item Deliverable: Formalization (in Agda) of a dynamic logic for a core fragment of Michelson with soundness proof.
-\item Deliverable: Paper about this formalization (writeup starting July 2023).
+\item Proposed activity: Development of a dynamic logic as a formal foundation for symbolic interpretation of Michelson. \\
+  $\Rightarrow$ This activity progressed significantly with the help of a master's
+  student supervised by Thiemann. The activity started later than
+  planned because the student was unavailable till the end of the
+  teaching period in March.
+\item Deliverable: Formalization (in Agda) of a dynamic logic for a core fragment of Michelson with soundness proof. \\
+  $\Rightarrow$ This deliverable is currently in beta and will be finished when the
+  master's thesis submission is due in September 2023.
+\item Deliverable: Paper about this formalization (writeup starting
+  July 2023). \\
+  $\Rightarrow$ The paper will be based on the master's thesis, so the final writing
+  starts after the submission in September. The goal is to submit to a
+  conference during the winter/early spring.
 \end{itemize}
@@
 \begin{itemize}
-\item Activity: Implementation of symbolic interpreter for a core fragment of Michelson in OCaml based on an SMT solver, most likely on Z3. 
-\item Deliverable: Symbolic interpreter.
+\item Activity: Implementation of symbolic interpreter for a core
+  fragment of Michelson in OCaml based on an SMT solver, most likely
+  on Z3. \\
+  $\Rightarrow$ This activity has been driven by Doan between January and June
+  2023. 
+\item Deliverable: Symbolic interpreter. \\
+  $\Rightarrow$ The current prototype of the symbolic interpreter is available here
+  \url{https://github.com/proglang/tezos-project/tree/master/static_checker}
 \item Deliverable: Case studies with example contracts.
-\item Deliverable: Paper or tutorial on this tool (writeup starting January 2024)
+\item Deliverable: Paper or tutorial on this tool (writeup starting
+  January 2024) \\
+  $\Rightarrow$ A draft is available here \url{https://github.com/proglang/tezos-project/tree/master/symbolic-execution/paper}
 \end{itemize}
@@
 \label{sec:january-2024-june}
+
+Not started.
 
@@
 
+Not started.
+
 \begin{itemize}
@@
 
-\section{Allocated Funds}
-\label{sec:allocated-funds}
-
-A total of 186,000 EUR distributed as follows:
-\begin{itemize}
-\item 160,000 EUR: one postdoc position for two years at 80,000 EUR per year.
-\item 12,000 EUR: part time student worker position for 12 months in total (help with implementation work).
-\item 12,000 EUR: travel funds for conference attendance (four conferences at 3000 EUR per conference). 
-\item 2,000 EUR: incidentals like replacement for broken server, broken laptop, etc.
-\end{itemize}
-
-\subsection{Remarks}
-\label{sec:remarks}
-
-\begin{itemize}
-\item
-  Travel funds should be applicable to all project participants:
-  student workers, postdoc, project lead.
-\item 
-  Funds for students, travel, and incidentals should be
-  interconvertible.
-\item 
-  The total amount of 186,000 EUR matches approximately the funds
-  remaining from the currently running COOC project.
-\end{itemize}
 \bibliography{report}

### 2023-10-05 papers/static-checker/ecoop2024/ecoop2024.tex
Add files via upload

%This is a template for producing reports for "Dagstuhl Reports".
%See dagrep-v2021.pdf for further information.

\documentclass[a4paper,UKenglish]{dagrep-v2021}
  %for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
  %for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
  %for section-numbered lemmas etc., use "numberwithinsect"
  %for producing a PDF according the PDF/A standard, add "pdfa"

\usepackage{microtype}%if unwanted, comment out or use option "draft"

\bibliographystyle{plain}%the recommnded bibstyle

\subject{Report from Dagstuhl Seminar 11013}
\title{Formal Verification Tool Based on Symbolic Execution for Smart Contract}
\titlerunning{11013 -- Seminar Sample}%optional

\author[1]{Thi Thu Ha Doan}
\author[2]{Peter Thiemann}
\affil[1]{University of Freiburg, Germany
  \texttt{doanha@informatik.uni-freiburg.de}}
\affil[2]{University of Freiburg, Germany
  \texttt{thiemann@informatik.uni-freiburg.de}}
\authorrunning{T.T.H Doan and P.Thiemann}%optional

\keywords{Smart Contract, Blockchain, Formal Verification, Symbolic Execution}%mandatory

%Organizer macros:%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\seminarnumber{11013}
\semdata{03.--07.~January, 2011 -- \url{https://www.dagstuhl.de/11013}}

\ccsdesc[100]{General and reference~General literature}
\ccsdesc[500]{Hardware~3D integrated circuits}
\ccsdesc[500]{Software and its engineering~Software design engineering}
\ccsdesc[300]{Networks~Network performance analysis}

\additionaleditors{Tom Collector}%optional
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Dagstuhl editorial office macros:%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\volumeinfo%(easychair interface)
  {John Q. Open and Joan R. Access}%editors
  {2}%number of editors
  {Seminar Sample}%event
  {1}%volume
  {1}%issue
  {1}%starting page number
\DOI{10.4230/DagRep.1.1.1}%(DagRep.<issue no>.<volume no>.<firstpage>)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

\begin{abstract}
In the context of blockchain technology, the immutability of smart contracts once implemented underscores the critical need to ensure their accuracy. Even in cases where smart contract implementations are not overly extensive and have undergone testing before deployment, the blockchain community has identified significant vulnerabilities in their design. In addition, the relatively new nature of smart contract languages has led to unforeseen errors due to a lack of familiarity with their intricacies. To overcome these challenges, formal verification emerges as a key solution to guarantee the correctness of smart contracts. In response to this need, we have developed a formal verification tool for smart contracts, particularly those written in Michelson. This tool uses symbolic execution to simulate the implementation of the smart contract language, helping to detect subtle errors that are difficult for smart contract developers to detect. In addition, our tool includes a domain-specific language that allows users to precisely specify contract properties. By interacting with an SMT solver, it can handle a wide range of properties. In particular, it streamlines the process of reviewing requirements, uncovering hidden errors, and validating user-defined properties. In summary, our research highlights the need for robust verification of smart contracts. We present a purpose-built tool that utilizes symbolic execution and a domain-specific language to improve the correctness of smart contracts and provide a comprehensive solution to mitigate potential pitfalls in blockchain-based applications.
\end{abstract}

\section{Executive Summary}
\summaryauthor[T.T.Ha Doan and P. Thiemann]{%
T.T.Ha Doan (University of Freiburg, Germany, doanha@informatik.uni-freiburg.de)\\
P. Thiemann (University of Freiburg, Germany, \\thiemann@informatik.uni-freiburg.de)
}

\license

This summary summarizes the outcomes of  our seminar. The seminar focused on\begin{itemize}
\item important issues,
\item relevant problems, and
\item adequate solutions.
\end{itemize}

As a major result from the seminar, the following problems have been identified: 
\begin{enumerate}
\item The problem of writing a brief, but concise executive summary.
\item The problem of collecting all abstracts from talks.
\item The problem of preparing summaries from working groups, open problem sessions, and panel discussions.
\end{enumerate}

\tableofcontents

%\newpage

\section{Introduction}

\end{document}

### 2023-11-13 papers/static-checker/ecoop2024/ecoop2024.tex
update the execution model

@@
 \usepackage{microtype}%if unwanted, comment out or use option "draft"
+\pdfoutput=1
+\usepackage[utf8]{inputenc}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{mathpartir}
+\usepackage{hyperref}
+\usepackage{listings}
+\usepackage{graphicx}
+\usepackage{comment}
+\usepackage{todonotes}
+\newcommand\pt{\todo[author=PT,inline]}
+\lstdefinelanguage{michelson}{
+  basicstyle=\fontsize{8}{9.6}\selectfont,
+  morekeywords={parameter,storage,or,unit,mutez,pair,bool,address}, sensitive=false,
+  morecomment=[l]{\#},
+  morecomment=[\STACK]{/*}{*/},
+  morestring=[b]",
+}
+\lstset{
+  language=Caml,
+  captionpos=b,
+  aboveskip=-\smallskipamount,
+  belowskip=-\smallskipamount,
+  belowcaptionskip=0pt,
+  basicstyle=\fontsize{8}{9.6}\selectfont,
+  morekeywords={val}
+}
+
+\input{macros}
 
@@
 
-\section{Executive Summary}
 \summaryauthor[T.T.Ha Doan and P. Thiemann]{%
@@
 
-This summary summarizes the outcomes of  our seminar. The seminar focused on\begin{itemize}
-\item important issues,
-\item relevant problems, and
-\item adequate solutions.
-\end{itemize}
-
-As a major result from the seminar, the following problems have been identified: 
-\begin{enumerate}
-\item The problem of writing a brief, but concise executive summary.
-\item The problem of collecting all abstracts from talks.
-\item The problem of preparing summaries from working groups, open problem sessions, and panel discussions.
-\end{enumerate}
-
 \tableofcontents
@@
 \section{Introduction}
+\label{sec:introduction}
 
+\section{Symblic Execution Model}
+\label{sec:symblic-execution-model}
+
+Let $\STACK = (\TermOne, \TYF) \STACKCONCAT (\TermTwo, \TYS) \STACKCONCAT \DOT
+\STACKCONCAT \EMPTYSTACK$ be a stack, where elements are types paired with terms.
+\\
+Let $\INSTRUCTION = \InstructionOne; \InstructionTwo; \DOT; \InstructionN$ be a sequence of instructions. 
+\\
+Let \PREDICATE\ be a predicate.
+
+\begin{definition}
+A system state of the symbolic execution is a tuple \\ $\STATE = [\INSTRUCTION, \STACK, \PREDICATE]$. Let $\SYSTEM = \{\STATEONE, \STATETWO, \DOT, \STATEN \}$ range over sets of system states.
+\end{definition}
+
+Let $S_{init}$   = (\KPAIR\ \VPAR\ \VSTORAGE, \TPAIR\ \TYF\ \TYS) \STACKCONCAT\EMPTYSTACK\ be the initial  stack, where \VPAR\ and \VSTORAGE\ are the terms that represent the parameter and the storage and \TYF\ and \TYS\ are their corresponding types, and  $S_{final}$   = (\PAIR\ \VOPERATIONLIST\ \VSTORAGE, \TPAIR\ (\TOPERATIONLIST) \TYS) \STACKCONCAT\EMPTYSTACK\ be  the final stack, where \VOPERATIONLIST\ repesents a operation list
+
+\begin{figure} []
+\begin{align*}
+T, U &::= \\
+   &\Mid\ \langle \text{comparable type}\rangle \\
+   &\Mid\ \text{option}\ \langle\text{type}\rangle \\
+   &\Mid\ \text{list}\ \langle\text{type}\rangle \\
+   &\Mid\ \text{set}\ \langle\text{comparable type}\rangle \\
+   &\Mid\ \text{operation} \\
+   &\Mid\ \text{contract}\ \langle\text{type}\rangle \\
+   &\Mid\ \text{ticket}\ \langle\text{comparable type}\rangle \\
+   &\Mid\ \text{pair}\ \langle\text{type}\rangle \langle\text{type}\rangle \\
+   &\Mid\ \text{or}\ \langle\text{type}\rangle \langle\text{type}\rangle \\
+   &\Mid\ \text{lambda}\ \langle\text{type}\rangle \langle\text{type}\rangle \\
+   &\Mid\ \text{map}\ \langle\text{comparable type}\rangle \langle\text{type}\rangle \\
+   &\Mid\ \text{big-map}\ \langle\text{comparable type}\rangle \langle\text{type}\rangle \\
+   &\Mid\ \text{bls12-381-g1} \\
+   &\Mid\ \text{bls12-381-g2} \\
+   &\Mid\ \text{bls12-381-fr} \\
+   &\Mid\ \text{sapling-transaction}\ \langle\text{natural number constant}\rangle \\
+   &\Mid\ \text{sapling-state}\ \langle\text{natural number constant}\rangle \\
+   &\Mid\ \text{chest} \\
+   &\Mid\ \text{chest-key} \\
+\langle\text{comparable type}\rangle ::= \\
+   &\Mid\ \text{unit} \\
+   &\Mid\ \text{never} \\
+   &\Mid\ \text{bool} \\
+   &\Mid\ \text{int}\\
+   &\Mid\ \text{nat}\\
+   &\Mid\ \text{string}\\
+   &\Mid\ \text{chain-id}\\
+   &\Mid\ \text{bytes}\\
+   &\Mid\ \text{mutez}\\
+   &\Mid\ \text{key-hash}\\
+   &\Mid\ \text{key}\\
+   &\Mid\ \text{signature}\\
+   &\Mid\ \text{timestamp}\\
+   &\Mid\ \text{address}\\
+   &\Mid\ \text{tx-rollup-l2-address}\\
+   &\Mid\ \text{option}\ \langle\text{comparable type}\rangle\\
+   &\Mid\ \text{or}\ \langle\text{comparable type}\rangle \langle\text{comparable type}\rangle\\
+   &\Mid\ \text{pair}\ \langle\text{comparable type}\rangle \langle\text{comparable type}\rangle \DOT \\
+\end{align*}
+\caption{Types}
+\label{fig:type}
+\end{figure}
+
+\begin{figure}[h]
+\begin{align*}
+\text{t} &::= \\
+   &\Mid\ \langle \text{variable} \rangle \\
+   &\Mid\ \langle \text{account constant} \rangle \\
+   &\Mid\ \langle \text{int constant} \rangle \\
+   &\Mid\ \langle \text{string constant} \rangle \\
+   &\Mid\ \langle \text{byte sequence constant} \rangle \\
+   &\Mid\ \UNIT \\
+   &\Mid\ \TRUE \\
+   &\Mid\ \FALSE \\
+   &\Mid\ \PAIR\ \text{t1 t2}\\
+   &\Mid\ \LEFT\ \text{t}\\
+   &\Mid\ \RIGHT\ \text{t}\\ 
+   &\Mid\ \SOME\ \text{t}\\
+   &\Mid\ \NONE \\
+   &\Mid\ \text{\{t ; ... \}}\\
+   &\Mid\ \text{\{ Elt t1 t2 ; ... \}}\\
+   &\Mid\ \{ \langle\text{instruction}\rangle; ... \}   \\
+\langle \text{variable} \rangle &::= \\ 
+   &\Mid\ \VAR\\
+\langle \text{account constant} \rangle &::= \\ 
+   &\Mid\ \text{balance} \\
+   &\Mid\ \text{amount} \\
+   &\Mid\ \text{sender} \\
+   &\Mid\ \text{source} \\
+   &\Mid\ \text{now} \\
+   &\Mid\ \text{level} \\
+   &\Mid\ \text{chain-id} \\
+   &\Mid\ \text{self}  \\
+   &\Mid\ \text{self-address}  \\
+   &\Mid\ \text{total-voting-power}  \\
+   &\Mid\ \text{voting-power}  \\
+\langle \text{natural number constant} \rangle &::= \\ 
+   &\Mid\ \text {[0-9]+} \\
+\langle \text{int constant} \rangle &::= \\
+  &\Mid\ \langle \text{natural number constant} \rangle \\
+  &\Mid\ \text{-} \langle \text{natural number constant} \rangle \\
+\langle\text{string constant}\rangle &::= \\
+  &\Mid\ \text{"} \langle \text{string content}\rangle\text{*"} \\
+\langle\text{instruction}\rangle &::= \\
+  &\Mid\ \DROP \\
+  &\Mid\ \DROP \langle\text{natural number constant}\rangle \\
+  &\text{...}
+\end{align*}
+\caption{Terms}
+\label{fig:term}
+\end{figure}
+
+\begin{figure}[h]
+\begin{align*}
+\text{p} &::= \\
+   &\Mid\ \langle \text{atomic formula} \rangle \\
+   &\Mid\ \NEG\ \text{p} \
+   \Mid\ \text{p}\ \CNF\ \text{q} \
+   \Mid\ \text{p}\ \DNF\ \text{q} \\
+\langle \text{atomic formula} \rangle &::= \\ 
+    &\Mid\ \langle \text{butop} \rangle \langle \text{bterm} \rangle\\ 
+   &\Mid\  \langle \text{bterm} \rangle  \langle \text{biop} \rangle \langle \text{bterm} \rangle\\ 
+\langle \text{butop} \rangle &::= \\
+   &\Mid\ \text{not} \\
+\langle \text{biop} \rangle &::= \\
+   &\Mid\ \text{$=$} \
+   \Mid\ \text{$>$} \
+   \Mid\ \text{$<$} \
+   \Mid\ \text{$>=$} \
+   \Mid\ \text{$=<$} \
+   \Mid\ \text{$!=$} \\
+   &\Mid\ \text{and}\ \Mid\ \text{or}\ \Mid\ \text{xor}\\
+\langle \text{bterm} \rangle &::= \\ 
+   &\Mid\ \text{t} \\
+   &\Mid\ \langle \text{unop} \rangle \text{t} \\ 
+   &\Mid\ \text{t}\ \langle \text{binop} \rangle \text{t}\\  
+\langle \text{unop} \rangle &::= \\ 
+   &\Mid\ \text{abs} \\
+   &\Mid\ \text{size} \\
+   &\Mid\ \text{int} \\
+   &\Mid\ \text{contract}  \langle \text{type} \rangle \\
+   &\Mid\ \text{isleft} \\
+   &\Mid\ \text{isnone} \\
+   &\Mid\ \text{neg} \\
+   &\Mid\ \text{blake2b} \\
+   &\Mid\ \text{hash-key} \\
+   &\Mid\ \text{keccak} \\
+   &\Mid\ \text{pairing-check} \\
+   &\Mid\ \text{sha256} \\
+   &\Mid\ \text{sha3} \\
+   &\Mid\ \text{sha512} \\
+   &\Mid\ \text{implicit-account} \\
+   &\Mid\ \text{check-sig} \\
+\langle \text{bitop} \rangle &::= \\ 
+   &\Mid\ \text{+}\ \Mid\ \text{-}\ \Mid\ \text{*}\ \Mid\ \text{/}
+\end{align*}
+\caption{Predicates}
+\label{fig:predicate}
+\end{figure}
+
+%\paragraph{Sequence actions.}
+%\begin{figure}[h]
+%\center
+%\includegraphics[width= 10 cm]{life-cycle-1}
+%\caption{Life-cycle for the auction contract.}
+%\label{fca1}
+%\end{figure}
+
+\pagebreak
+\subsection{Rules}
+The rule semantic is defined by several kinds of transitions:
+\begin{enumerate}
+\item \ExprTrans\ single-step evaluation of an expression in a system state,
+\item \StateTrans\ internal transitions of a system state, which is non-deterministic  as shown for instructions \ITER\ and \LOOP,
+\item \SystemTrans\ symbolic system transitions.
+\end{enumerate}
+
+\subsubsection{System rules}
+\begin{mathpar}
+\inferrule[INVALID-PRE]
+  { \NEG\ \PREDICATE
+  }{
+  \{[\INSTRUCTION, \STACK, \PREDICATE]\} \cup \SYSTEM \SystemTrans \SYSTEM}
+\end{mathpar}
+
+\subsubsection{Instruction rules}
+\paragraph{Control structures}
+%EXE
+\begin{mathpar}
+  \inferrule[EXEC]
+  {
+    [\INSTRUCTIONONE, (\StackOne, \TYF) \STACKCONCAT \EMPTYSTACK, 
+    Q]
+    \StateTrans^*
+    [ \EMPTYSTACK, (\StackOne', \TYS) \STACKCONCAT Q']
+  }{
+     [(\EXEC; \INSTRUCTION),   (\{\INSTRUCTIONONE\}, \TYF\ \rightarrow\ \TYS) \STACKCONCAT
+    (\StackOne, \TYF) \STACKCONCAT \STACK, \PREDICATE \wedge Q] 
+    \StateTrans \
+    [ \INSTRUCTION, (\StackOne', \TYS) \STACKCONCAT \STACK,
+    \PREDICATE \wedge Q']}
+\end{mathpar}
+
+%APPLY
+\begin{mathpar}
+  \inferrule[APPLY]
+  {
+  }{
+    [(\APPLY; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\{\INSTRUCTIONONE\}, \TLAMBDA\ (\TPAIR\ \TYF\  \TYS)\ \TYT) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\\ [\INSTRUCTION, (\{\PUSH\ \TYF\ \StackOne; \IPAIR; \INSTRUCTIONONE\}, \TLAMBDA\ \TYS\ \TYT ) \STACKCONCAT\STACK, \PREDICATE]}
+\end{mathpar}
+
+%LAMBLA
+\begin{mathpar}
+  \inferrule[LAMBDA]
+  {  
+  }{
+    [(\LAMBDA\ \TYF\ \TYS\ \{ \INSTRUCTIONONE \} ; \INSTRUCTION),\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, (\{\INSTRUCTIONONE\}, \TLAMBDA\ \TYF\ \rightarrow\ \TYS) \STACKCONCAT\STACK, \PREDICATE]}
+\end{mathpar}
+
+%IF
+\begin{mathpar}
+  \inferrule[IF-true]
+  {  
+  }{
+    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
+    \StateTrans\
+    [\INSTRUCTIONONE, \STACK, \PREDICATE\ \Wedge\ \StackOne]
+  }
+
+  \inferrule[IF-false]
+  {  
+  }{
+    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
+    \StateTrans\
+   [\INSTRUCTIONTWO, \STACK, \PREDICATE\ \Wedge\ \NEG\
+   \StackOne]
+ }
+\end{mathpar}
+
+%IF-LEFT-LEFT
+\begin{mathpar}
+  \inferrule[IF-LEFT-left]
+  {  
+  }{
+    [(\IFLEFT\ \INSTRUCTIONONE\ \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]
+    \StateTrans \
+    [\INSTRUCTIONONE, (\VariableX, \TYF) \STACKCONCAT\STACK,
+    \PREDICATE \wedge (\StackOne\ \EQUAL\ \LEFT\ \VariableX)]
+  }
+\end{mathpar}
+
+%IF-LEFT-RIGHT
+\begin{mathpar}
+  \inferrule[IF-LEFT-right]
+  {  
+  }{
+    [(\IFLEFT\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]
+    \StateTrans \
+    [\INSTRUCTIONTWO, (\VariableX, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQUAL\ \RIGHT\ \VariableX))]
+  }
+\end{mathpar}
+
+%IF_CONS
+\begin{mathpar}
+  \inferrule[IF-CONS-empty]
+  {  
+  }{
+    [(\IFCONS\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\  [\INSTRUCTIONTWO; \INSTRUCTION, \STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST)]}
+\end{mathpar}
+
+\begin{mathpar}
+  \inferrule[IF-CONS-nonempty]
+  {  
+  }{
+   [(\IFCONS\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\  \\ [\INSTRUCTIONONE, (\HEAD, \TY) \STACKCONCAT(\{ \TAIL \}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ ( \StackOne\ \EQUAL\ \{\HEAD; \STAIL \})]}
+\end{mathpar}
+
+%IF_NON
+\begin{mathpar}
+  \inferrule[IF-NONE-none]
+  {  
+  }{
+    [(\IFNONE\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TOPTION\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\   [\INSTRUCTIONONE; \INSTRUCTION, \STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \NONE)]}
+\end{mathpar}
+
+\begin{mathpar}
+  \inferrule[IF-NONE-some]
+  {  
+  }{
+    [(\IFNONE\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),   (\StackOne, \TOPTION\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\   [\INSTRUCTIONTWO,  (\VariableX, \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ ( \StackOne\ \EQUAL\ \SOME\ \VariableX)]}
+\end{mathpar}
+
+%LOOP
+\begin{mathpar}
+  \inferrule[LOOP-true]
+  {  
+  }{
+    [(\LOOP\ \INSTRUCTIONONE; \INSTRUCTION),  (\StackOne, \TBOOL)
+    \STACKCONCAT\STACK, \PREDICATE]
+    \StateTrans\
+    [(\INSTRUCTIONONE; \LOOP\ \INSTRUCTIONONE; \INSTRUCTION),
+    \STACK, \PREDICATE \wedge \StackOne]
+  }
+
+  \inferrule[LOOP-false]
+  {  
+  }{
+    [(\LOOP\ \INSTRUCTIONONE; \INSTRUCTION),  (\StackOne, \TBOOL) \STACKCONCAT\
+    \STACK, \PREDICATE]
+    \StateTrans\
+   [\INSTRUCTION, \STACK, \PREDICATE \wedge
+   (\NEG\StackOne)]
+   }
+\end{mathpar}
+
+%%ITER
+\begin{mathpar}
+  \inferrule[ITER-empty]
+  {  
+  }{
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, \STACK,  \PREDICATE\ \Wedge\  (\StackOne\ \EQUAL\ \EMPTYLIST)]
+  }
+\end{mathpar}
+
+\begin{mathpar}
+  \inferrule[ITER-nonempty]
+  {  [\ITER,  (\HEAD, \TY) \STACKCONCAT\STACK, 
+    Q]
+    \StateTrans^*
+    [ \EMPTYSTACK,  \STACK', Q']
+  }{
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE \wedge Q] \StateTrans \\ [(\TITER\ \INSTRUCTIONONE ; \INSTRUCTION), \{\STAIL\}\ \STACKCONCAT\STACK',  \PREDICATE\ \Wedge  ( \StackOne\ \EQUAL\ \{\HEAD; \STAIL \})  \wedge Q']
+  }
+\end{mathpar}
+
+\paragraph{Stack Manipulation}
+%DIG
+\begin{mathpar}
+\inferrule[DIG]
+  {
+   \FLEN(\A) \EQUAL\ \N
+  }
+  {[(\DIG\ \N ; \INSTRUCTION), \A\ \At\ (\StackOne, \TY) \STACKCONCAT\B, \PREDICATE] \StateTrans 
+[\INSTRUCTION, (\StackOne, \TY) \STACKCONCAT\A\ \At\ \B, \PREDICATE]}
+\end{mathpar}
+
+%DIP
+\begin{mathpar}
+  \inferrule[DIP]
+  {
+    [\INSTRUCTIONONE,  \STACK, Q]
+    \StateTrans^*
+    [\EMPTYSTACK,  \STACK_1, Q']
+  }
+  {[(\DIP\ \INSTRUCTIONONE; \INSTRUCTION), (\StackOne, \TY) \STACKCONCAT
+    \STACK, \PREDICATE \wedge Q]
+    \StateTrans 
+    [\INSTRUCTION, (\StackOne, \TY) \STACKCONCAT\STACK_1,
+    \PREDICATE \wedge Q']
+  }
+\end{mathpar}
+
+%DIP n
+\begin{mathpar}
+\inferrule[DIP n]
+  { 
+     \FLEN(\A) \EQUAL\ \N \\ [\INSTRUCTIONONE,  \B, Q]
+    \StateTrans^*
+    [\EMPTYSTACK,  \B_1, Q']
+  }
+  {[(\DIP\ \N\ \INSTRUCTIONONE; \INSTRUCTION), \A\ \At\ \B, \PREDICATE \wedge Q] \StateTrans 
+[(\INSTRUCTION), \A\ \At\ \B_1, \PREDICATE \wedge Q']}
+\end{mathpar}
+
+%PUSH
+\begin{mathpar}
+  \inferrule[PUSH]
+  {  
+  }{
+    [(\PUSH\ \TY\ \VariableX; \INSTRUCTION),\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, (\VariableX, \TY) \STACKCONCAT\STACK, \PREDICATE]}
+\end{mathpar}
+
+\paragraph{Arithmetic operations}
+%ADD
+\begin{mathpar}
+\inferrule[ADD]
+  {
+  }
+  {[(\ADD; \INSTRUCTION), (\StackOne, \TNAT) \STACKCONCAT(\StackTwo, \TNAT) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
+[\INSTRUCTION, (\VariableX, \TNAT) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\VariableX\ \EQUAL\ \StackOne\ \PLUS\ \StackTwo)]}
+\end{mathpar}
+
+%ABS
+\begin{mathpar}
+\inferrule[ABS]
+  {
+  }
+  {
+    [(\ABS; \INSTRUCTION), (\StackOne, \TINT) \STACKCONCAT \STACK,
+    \PREDICATE]
+    \StateTrans \
+    [\INSTRUCTION, (\VariableX, \TNAT) \STACKCONCAT \STACK,
+    \PREDICATE \wedge (\StackOne \ge 0 \Rightarrow \VariableX =
+    \StackOne) \wedge (\StackOne <0 \Rightarrow \VariableX = -\StackOne)]
+ }
+\end{mathpar}
+
+% COMPARE
+\begin{mathpar}
+\inferrule[COMPARE-nat]
+  {
+  }
+  {
+    [(\COMPARE ; \INSTRUCTION), (\StackOne, \TNAT) \STACKCONCAT (\StackTwo, \TNAT)
+    \STACKCONCAT \STACK, \PREDICATE ]
+    \SystemTrans \\
+    [\INSTRUCTION, (\VariableX, \TINT) \STACKCONCAT \STACK, \PREDICATE
+    \wedge\ (\StackOne > \StackTwo \Leftrightarrow \VariableX = 1)
+    \wedge\ (\StackOne = \StackTwo \Leftrightarrow \VariableX = 0) 
+    \wedge\ (\StackOne < \StackTwo \Leftrightarrow \VariableX = -1)]
+    }
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[COMPARE-some-some]
+  {
+  [\COMPARE,  (\VariableX, \TY) \STACKCONCAT (\VariableY, \TY) \STACKCONCAT\EMPTYSTACK, Q]
+    \StateTrans^*
+    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
+  }
+  {
+    [(\COMPARE ; \INSTRUCTION), (\StackOne, \TOPTION\ \TY) \STACKCONCAT (\StackTwo, \TOPTION\ \TY)
+    \STACKCONCAT \STACK, \PREDICATE \wedge Q]
+    \SystemTrans \\
+    [\INSTRUCTION, (\VariableA, \TINT) \STACKCONCAT \STACK,  \PREDICATE
+    \wedge (\StackOne\ \EQUAL\ \SOME\ \VariableX)
+    \wedge (\StackTwo\ \EQUAL\ \SOME\ \VariableY)
+    \wedge Q']
+    }
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[COMPARE-some-none]
+  {
+  }
+  {
+    [(\COMPARE ; \INSTRUCTION), (\StackOne, \TOPTION\ \TY) \STACKCONCAT (\StackTwo, \TOPTION\ \TY)
+    \STACKCONCAT \STACK, \PREDICATE]
+    \SystemTrans \\
+    [\INSTRUCTION, (1, \TINT) \STACKCONCAT \STACK,  \PREDICATE
+    \wedge (\StackOne\ \EQUAL\ \SOME\ \VariableX)
+    \wedge (\StackTwo\ \EQUAL\ \NONE)
+    ]
+    }
+\end{mathpar}
+
+\paragraph{Boolean operations}
+%XOR
+\begin{mathpar}
+\inferrule[XOR]
+  {
+  }
+  {[(\XOR; \INSTRUCTION), (\StackOne, \TBOOL) \STACKCONCAT(\StackTwo, \TBOOL) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
+[\INSTRUCTION, (\VariableX, \TBOOL) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\VariableX\ \EQUAL\ \StackOne\ \FXOR\ \StackTwo)]}
+\end{mathpar}
+
+\paragraph{Crytographic oprerations}
+%HASH-KEY
+\begin{mathpar}
+\inferrule[HASH-KEY]
+  {
+  }
+  {[(\HASHKEY; \INSTRUCTION), (\StackOne, \TBYTE) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
+[\INSTRUCTION, (\VariableX, \TBYTE) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\VariableX\ = \FHASHKEY(\StackOne))]}
+\end{mathpar}
+
+%AMOUNT
+\paragraph{Blockchain operations}
+\begin{mathpar}
+\inferrule[AMOUNT]
+  {
+  }
+  {[(\AMOUNT; \INSTRUCTION), \STACK, \PREDICATE] \StateTrans \
+[\INSTRUCTION, (\VAMOUNT, \TMUTEZ) \STACKCONCAT\STACK, \PREDICATE}
+\end{mathpar}
+
+%CONTRACT ty
+\begin{mathpar}
+\inferrule[CONTRACT TY - some]
+  {
+  }
+  {[(\CONTRACT\ \TY ; \INSTRUCTION), (\StackOne, \TADDR) \STACKCONCAT\STACK, \PREDICATE] \SystemTrans \
+[\INSTRUCTION, (\SOME\ \VariableX, \TOPTION\ (\TCONTRACT\ \TY)) \STACKCONCAT\STACK, \\ \PREDICATE \Wedge\ (\GETCONTRACTTYPE(\StackOne, \TY) = \SOME\ \VariableX)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[CONTRACT TY - none]
+  {
+  }
+  {[(\CONTRACT\ \TY ; \INSTRUCTION), (\StackOne, \TADDR) \STACKCONCAT\STACK, \PREDICATE] \SystemTrans \
+[\INSTRUCTION, \NONE \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\GETCONTRACTTYPE(\StackOne, \TY) = \NONE]}
+\end{mathpar}
+
+\paragraph{Operations on data structures}
+%CAR
+\begin{mathpar}
+\inferrule[\CAR]
+  {
+  }
+  {[(\CAR; \INSTRUCTION), (\StackOne, \TPAIR\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
+[\INSTRUCTION, (\VariableX, \TYF) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \PAIR\ \VariableX\ \VariableY)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[CONCAT]
+  {
+  }
+  {[(\CONCAT; \INSTRUCTION), (\StackOne, \TYLIST\ \TSTR) \STACKCONCAT\STACK,  \PREDICATE] \StateTrans 
+[\INSTRUCTION,  ("",  \TSTR) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[CONCAT]
+  {
+  [\CONCAT,  (\{\TAIL\}, \TYLIST\ \TSTR) \STACKCONCAT\EMPTYSTACK, Q]
+    \StateTrans^*
+    [\EMPTYSTACK, (\StackTwo,  \TSTR) \STACKCONCAT\EMPTYSTACK, Q']
+  }
+  {[(\CONCAT; \INSTRUCTION),  (\StackOne, \TYLIST\ \TSTR) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans \\
+[\INSTRUCTION, ( \HEAD\ \STRINGCONCAT\ \StackTwo, \TSTR) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ Q']}
+\end{mathpar}
+
+%MEM
+\begin{mathpar}
+\inferrule[MEM-empty]
+  {
+  }
+  {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
+[\INSTRUCTION, (\FALSE, \TBOOL) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackTwo\ \EQUAL\ \EMPTYSET)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[MEM-nonempty]
+  {
+  [\COMPARE, (\StackOne, \TYF) \STACKCONCAT (\K, \TYF) \STACKCONCAT\EMPTYSTACK, Q]
+    \StateTrans^*
+    [\EMPTYSTACK,  (\VariableB, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
+  }
+  {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans  \
+[\MEM; \INSTRUCTION, \StackOne\ \STACKCONCAT\{\LESS\ \M\ \MORE\} \STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackTwo\ \EQUAL\ \{\ELT\ \K\ \V; \LESS\ \M\ \MORE\})  \Wedge\ (\VariableB\ \EQUAL\ \ONE)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[MEM-nonempty]
+  {
+  [\COMPARE, (\StackOne, \TYF) \STACKCONCAT (\K, \TYF) \STACKCONCAT\EMPTYSTACK, Q]
+    \StateTrans^*
+    [\EMPTYSTACK,  (\VariableB, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
+  }
+  {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans  \\
+[\INSTRUCTION, (\TRUE, \TBOOL) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackTwo\ \EQUAL\ \{\ELT\ \K\ \V; \LESS\ \M\ \MORE\}) \Wedge\ (\VariableB\ \EQUAL\ \ZERO)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[MEM-nonempty]
+  {
+  [\COMPARE, (\StackOne, \TYF) \STACKCONCAT (\K, \TYF) \STACKCONCAT\EMPTYSTACK, Q]
+    \StateTrans^*
+    [\EMPTYSTACK,  (\VariableB, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
+  }
+  {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans  \\
+[\INSTRUCTION, (\FALSE, \TBOOL) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackTwo\ \EQUAL\ \{\ELT\ \K\ \V; \LESS\ \M\ \MORE\})  \Wedge\ (\VariableB\ \EQUAL\ \MINUS\ \ONE)]}
+\end{mathpar}
+
+%MAP
+\begin{mathpar}
+\inferrule[MAP-empty]
+  {
+  }
+  {[(\MAP\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
+[\INSTRUCTION, (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[MAP-nonempty]
+  {
+  [\INSTRUCTIONONE, (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q1]
+    \StateTrans^*
+    [\EMPTYSTACK,  (\PHEAD, \TY) \STACKCONCAT\EMPTYSTACK , Q1'] \\  [\MAP\ \INSTRUCTIONONE, (\{\TAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK , Q2]
+    \StateTrans^*
+    [\EMPTYSTACK,  (\{\PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK , Q2']
+  }
+  {[(\MAP\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1 \Wedge\ Q2 ] \StateTrans  \\
+[\INSTRUCTION, (\{\PHEAD; \PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1' \Wedge\ Q2'  \Wedge\ (\StackOne \EQUAL\ \{\HEAD; \TAIL\})]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[UPDATE-empty-true]
+  {
+  }
+  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE]\ \SystemTrans\  \\ [\INSTRUCTION, (\{\VariableX \}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\  \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST) \Wedge\ (\VariableB\ \EQUAL\ \TRUE)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[UPDATE-empty-false]
+  {
+  }
+  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE]\ \SystemTrans\  \\ [\INSTRUCTION, (\EMPTYLIST, \TYLIST\ \TY)\ \STACKCONCAT\STACK, \PREDICATE\  \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST) \Wedge\ (\VariableB\ \EQUAL\ \FALSE)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[UPDATE-nonempty-true]
+  {
+  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
+    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
+  }
+  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans
+[\INSTRUCTION, (\StackOne, \TYLIST\ \TY)
+\STACKCONCAT\STACK,\\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQUAL\ \TRUE) \Wedge\ (\VariableA\ \EQUAL\ \ZERO)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[UPDATE-nonempty-false]
+  {
+  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
+    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
+  }
+  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans  \\
+[\INSTRUCTION, (\{\TAIL\}, \TYLIST\ \TY)
+\STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQUAL\ \FALSE) \Wedge\ (\VariableA\ \EQUAL\ \ZERO)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[UPDATE-nonempty-true]
+  {
+  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
+    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
+  }
+  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans  \\
+[\INSTRUCTION, (\{\VariableX; \HEAD; \TAIL\}, \TYLIST\ \TY)
+\STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQUAL\ \TRUE) \Wedge\ (\VariableA\ \EQUAL\ \MINUS\ \ONE)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[UPDATE-nonempty-false]
+  {
+  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
+    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
+  }
+  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans\  \\
+[\INSTRUCTION, (\{\HEAD; \TAIL\}, \TYLIST\ \TY)
+\STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQUAL\ \FALSE) \Wedge\ (\VariableA\ \EQUAL\ \MINUS\ \ONE)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[UPDATE-nonempty-1]
+  {
+  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q1] \StateTrans^*
+    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q1'] \\
+ [\UPDATE, (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT( \{\TAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK, Q2] \StateTrans^* \\  [\EMPTYSTACK, ( \{\PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK, Q2']
+  }
+  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1 \Wedge\ Q2 ] \SystemTrans\  \\
+[\INSTRUCTION; (\{\HEAD; \PTAIL\}, \TYLIST\ \TY)
+\STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1' \Wedge\ Q2' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableA\ \EQUAL\ \ONE)]}
+\end{mathpar}
+
+\subsubsection{Operation on tickets}
+\subsubsection{FAILWITH}
+%FAILWITH
+\begin{mathpar}
+  \inferrule[FAILWITH]
+  {
+  }{[(\FAILWITH; \INSTRUCTION), (\StackOne,  \TY) \STACKCONCAT \STACK,  \PREDICATE] \StateTrans [\EMPTYSTACK, failwith (\StackOne) \STACKCONCAT\EMPTYSTACK, \PREDICATE]}
+\end{mathpar}
+\section {Domain Specific Language}
+\section {Static Checker}
+\section {Case Studies}
+\section {Related Work}
+\section {Conclusion}
 \end{document}

### 2023-11-28 papers/static-checker/ecoop2024/ecoop2024.tex
add sections
revise the tex file
Add system model

@@
 
-\section{Symblic Execution Model}
-\label{sec:symblic-execution-model}
-
-Let $\STACK = (\TermOne, \TYF) \STACKCONCAT (\TermTwo, \TYS) \STACKCONCAT \DOT
-\STACKCONCAT \EMPTYSTACK$ be a stack, where elements are types paired with terms.
-\\
-Let $\INSTRUCTION = \InstructionOne; \InstructionTwo; \DOT; \InstructionN$ be a sequence of instructions. 
-\\
-Let \PREDICATE\ be a predicate.
+\section{Symbolic Execution Model}
+\label{sec:symbolic-execution-model}
+\subsection{System Model}
+Michelson is the low-level smart contract language employed in the Tezos blockchain platform.
+It is characterized as a stack-based language, featuring high-level data types and primitives and integrates strict static type checking into its stack-based execution mode.
+
+The processing and manipulation of data during the execution of smart contracts are facilitated using a stack. A stack  can be written:
+\begin{itemize}
+\item[]  \EMPTYSTACK\ for the empty stack.
+\item[]  \HEAD\ \STACKCONCAT\ \NTAIL\ for the stack whose first value has type (\HEAD) and queue has stack type (\NTAIL).
+\end{itemize}
+
+Each piece of data in Michelson is assigned a specific type, and the language imposes restrictions preventing programmers from introducing custom types.
+Consider a stack denoted as $\STACK = (\TermOne, \TYF) \STACKCONCAT (\TermTwo, \TYS) \STACKCONCAT \DOT
+\STACKCONCAT \EMPTYSTACK$ where elements are types paired with terms.
+
+A Michelson program is a sequence of instructions executed in a sequential manner.
+Each instruction takes, as input, the stack produced by the preceding instruction and modifies it for the subsequent one.
+This sequential flow ensures that each instruction builds upon the state left by its predecessor in the program.
+Let $\INSTRUCTION = \InstructionOne; \InstructionTwo; \DOT; \InstructionN$ represent a sequence of instructions.
+
+While undergoing symbolic execution, branching may occur depending on the conditions, and these branching conditions are recorded as predicates.
+Let \PREDICATE\ represent a predicate expressed in conjunction form.
 
 \begin{definition}
-A system state of the symbolic execution is a tuple \\ $\STATE = [\INSTRUCTION, \STACK, \PREDICATE]$. Let $\SYSTEM = \{\STATEONE, \STATETWO, \DOT, \STATEN \}$ range over sets of system states.
+A symbolic execution's state is represented by the tuple $\STATE = [\INSTRUCTION, \STACK, \PREDICATE]$. Here, $\SYSTEM = \{\STATEONE, \STATETWO, \DOT, \STATEN \}$ range over sets of  states.
 \end{definition}
 
-Let $S_{init}$   = (\KPAIR\ \VPAR\ \VSTORAGE, \TPAIR\ \TYF\ \TYS) \STACKCONCAT\EMPTYSTACK\ be the initial  stack, where \VPAR\ and \VSTORAGE\ are the terms that represent the parameter and the storage and \TYF\ and \TYS\ are their corresponding types, and  $S_{final}$   = (\PAIR\ \VOPERATIONLIST\ \VSTORAGE, \TPAIR\ (\TOPERATIONLIST) \TYS) \STACKCONCAT\EMPTYSTACK\ be  the final stack, where \VOPERATIONLIST\ repesents a operation list
+The Michelson program takes as input a stack that consists of a single pair whose first element is an input value referred to as the parameter, and second element represents the content of the storage space.
+The program produces a stack as output, containing a single pair.
+The first element of this pair is the list of internal operations that the program intends to emit, and the second element is the new contents of the storage space.
+
+Define the initial stack as $S_{init}$   = (\KPAIR\ \VPAR\ \VSTORAGE, \TPAIR\ \TYF\ \TYS) \STACKCONCAT\EMPTYSTACK, where \VPAR\ and \VSTORAGE\ denote terms representing the parameter and the storage, and \TYF\ and \TYS\ are their corresponding types.
+Similarly, designate the final stack as $S_{final}$   = (\PAIR\ \VOPERATIONLIST\ \VSTORAGE, \TPAIR\ (\TOPERATIONLIST) \TYS) \STACKCONCAT\EMPTYSTACK, where \VOPERATIONLIST\ repesents a operation list.
+
+%\paragraph{Sequence actions.}
+%\begin{figure}[h]
+%\center
+%\includegraphics[width= 10 cm]{life-cycle-1}
+%\caption{Life-cycle for the auction contract.}
+%\label{fca1}
+%\end{figure}
+
+\pagebreak
+\subsection{Rules}
+
+Each instruction is defined by a rule on the system model. The rule semantic is defined by several kinds of transitions:
+\begin{enumerate}
+\item \ExprTrans\ single-step evaluation of an expression in a system state,
+\item \StateTrans\ internal transitions of a state, which is non-deterministic  as shown for loop instructions, such as \LOOP\ and \LOOP-LEFT,
+\item \SystemTrans\ symbolic system transitions.
+\end{enumerate}
+
+During the execution of symbolic analysis, numberous states are generated.
+However, certain states may be unreachable from a symbolic initial state.
+This occurs when the predicate \PREDICATE\ is unsatisfied.
+Consequently, a system state is disregarded when the predicate \PREDICATE\ is fail.
+
+\begin{mathpar}
+\inferrule[]
+  { \NEG\ \PREDICATE
+  }{
+  \{[\INSTRUCTION, \STACK, \PREDICATE]\} \cup \SYSTEM \SystemTrans \SYSTEM}
+\end{mathpar}
+There are various types of instructions in Michelson, categorized based on their functions.
+These include control structures, stack manipulation, arithmetic operations, boolean operations, cryptographic operations, and operations on data structures.
+In our model, we classify them into three main groups: basic instructions, branch instructions, and loop instructions.
+This categorization reflects how these instructions are handled within our specific model.
+\subsubsection{Basic Instructions}
+
+\paragraph{Control structures}
+%EXE
+\begin{mathpar}
+  \inferrule[EXEC]
+  {
+    [\INSTRUCTIONONE, (\StackOne, \TYF) \STACKCONCAT \EMPTYSTACK, 
+    Q]
+    \StateTrans^*
+    [ \EMPTYSTACK, (\StackOne', \TYS) \STACKCONCAT Q']
+  }{
+     [(\EXEC; \INSTRUCTION),   (\{\INSTRUCTIONONE\}, \TYF\ \rightarrow\ \TYS) \STACKCONCAT
+    (\StackOne, \TYF) \STACKCONCAT \STACK, \PREDICATE \wedge Q] 
+    \StateTrans \
+    [ \INSTRUCTION, (\StackOne', \TYS) \STACKCONCAT \STACK,
+    \PREDICATE \wedge Q']}
+\end{mathpar}
+
+%APPLY
+\begin{mathpar}
+  \inferrule[APPLY]
+  {
+  }{
+    [(\APPLY; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\{\INSTRUCTIONONE\}, \TLAMBDA\ (\TPAIR\ \TYF\  \TYS)\ \TYT) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\\ [\INSTRUCTION, (\{\PUSH\ \TYF\ \StackOne; \IPAIR; \INSTRUCTIONONE\}, \TLAMBDA\ \TYS\ \TYT ) \STACKCONCAT\STACK, \PREDICATE]}
+\end{mathpar}
+
+%LAMBLA
+\begin{mathpar}
+  \inferrule[LAMBDA]
+  {  
+  }{
+    [(\LAMBDA\ \TYF\ \TYS\ \{ \INSTRUCTIONONE \} ; \INSTRUCTION),\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, (\{\INSTRUCTIONONE\}, \TLAMBDA\ \TYF\ \rightarrow\ \TYS) \STACKCONCAT\STACK, \PREDICATE]}
+\end{mathpar}
+
+\paragraph{Stack Manipulation}
+%DIG
+\begin{mathpar}
+\inferrule[DIG]
+  {
+   \FLEN(\A) \EQUAL\ \N
+  }
+  {[(\DIG\ \N ; \INSTRUCTION), \A\ \At\ (\StackOne, \TY) \STACKCONCAT\B, \PREDICATE] \StateTrans 
+[\INSTRUCTION, (\StackOne, \TY) \STACKCONCAT\A\ \At\ \B, \PREDICATE]}
+\end{mathpar}
+
+%DIP
+\begin{mathpar}
+  \inferrule[DIP]
+  {
+    [\INSTRUCTIONONE,  \STACK, Q]
+    \StateTrans^*
+    [\EMPTYSTACK,  \STACK_1, Q']
+  }
+  {[(\DIP\ \INSTRUCTIONONE; \INSTRUCTION), (\StackOne, \TY) \STACKCONCAT
+    \STACK, \PREDICATE \wedge Q]
+    \StateTrans 
+    [\INSTRUCTION, (\StackOne, \TY) \STACKCONCAT\STACK_1,
+    \PREDICATE \wedge Q']
+  }
+\end{mathpar}
+
+%DIP n
+\begin{mathpar}
+\inferrule[DIP n]
+  { 
+     \FLEN(\A) \EQUAL\ \N \\ [\INSTRUCTIONONE,  \B, Q]
+    \StateTrans^*
+    [\EMPTYSTACK,  \B_1, Q']
+  }
+  {[(\DIP\ \N\ \INSTRUCTIONONE; \INSTRUCTION), \A\ \At\ \B, \PREDICATE \wedge Q] \StateTrans 
+[(\INSTRUCTION), \A\ \At\ \B_1, \PREDICATE \wedge Q']}
+\end{mathpar}
+
+%PUSH
+\begin{mathpar}
+  \inferrule[PUSH]
+  {  
+  }{
+    [(\PUSH\ \TY\ \VariableX; \INSTRUCTION),\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, (\VariableX, \TY) \STACKCONCAT\STACK, \PREDICATE]}
+\end{mathpar}
+
+\paragraph{Arithmetic operations}
+%ADD
+\begin{mathpar}
+\inferrule[ADD]
+  {
+  }
+  {[(\ADD; \INSTRUCTION), (\StackOne, \TNAT) \STACKCONCAT(\StackTwo, \TNAT) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
+[\INSTRUCTION, (\VariableX, \TNAT) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\VariableX\ \EQUAL\ \StackOne\ \PLUS\ \StackTwo)]}
+\end{mathpar}
+
+%ABS
+\begin{mathpar}
+\inferrule[ABS]
+  {
+  }
+  {
+    [(\ABS; \INSTRUCTION), (\StackOne, \TINT) \STACKCONCAT \STACK,
+    \PREDICATE]
+    \StateTrans \
+    [\INSTRUCTION, (\VariableX, \TNAT) \STACKCONCAT \STACK,
+    \PREDICATE \wedge (\StackOne \ge 0 \Rightarrow \VariableX =
+    \StackOne) \wedge (\StackOne <0 \Rightarrow \VariableX = -\StackOne)]
+ }
+\end{mathpar}
+
+% COMPARE
+\begin{mathpar}
+\inferrule[COMPARE-nat]
+  {
+  }
+  {
+    [(\COMPARE ; \INSTRUCTION), (\StackOne, \TNAT) \STACKCONCAT (\StackTwo, \TNAT)
+    \STACKCONCAT \STACK, \PREDICATE ]
+    \SystemTrans \\
+    [\INSTRUCTION, (\VariableX, \TINT) \STACKCONCAT \STACK, \PREDICATE
+    \wedge\ (\StackOne > \StackTwo \Leftrightarrow \VariableX = 1)
+    \wedge\ (\StackOne = \StackTwo \Leftrightarrow \VariableX = 0) 
+    \wedge\ (\StackOne < \StackTwo \Leftrightarrow \VariableX = -1)]
+    }
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[COMPARE-some-some]
+  {
+  [\COMPARE,  (\VariableX, \TY) \STACKCONCAT (\VariableY, \TY) \STACKCONCAT\EMPTYSTACK, Q]
+    \StateTrans^*
+    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
+  }
+  {
+    [(\COMPARE ; \INSTRUCTION), (\StackOne, \TOPTION\ \TY) \STACKCONCAT (\StackTwo, \TOPTION\ \TY)
+    \STACKCONCAT \STACK, \PREDICATE \wedge Q]
+    \SystemTrans \\
+    [\INSTRUCTION, (\VariableA, \TINT) \STACKCONCAT \STACK,  \PREDICATE
+    \wedge (\StackOne\ \EQUAL\ \SOME\ \VariableX)
+    \wedge (\StackTwo\ \EQUAL\ \SOME\ \VariableY)
+    \wedge Q']
+    }
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[COMPARE-some-none]
+  {
+  }
+  {
+    [(\COMPARE ; \INSTRUCTION), (\StackOne, \TOPTION\ \TY) \STACKCONCAT (\StackTwo, \TOPTION\ \TY)
+    \STACKCONCAT \STACK, \PREDICATE]
+    \SystemTrans \\
+    [\INSTRUCTION, (1, \TINT) \STACKCONCAT \STACK,  \PREDICATE
+    \wedge (\StackOne\ \EQUAL\ \SOME\ \VariableX)
+    \wedge (\StackTwo\ \EQUAL\ \NONE)
+    ]
+    }
+\end{mathpar}
+
+\paragraph{Boolean operations}
+%XOR
+\begin{mathpar}
+\inferrule[XOR]
+  {
+  }
+  {[(\XOR; \INSTRUCTION), (\StackOne, \TBOOL) \STACKCONCAT(\StackTwo, \TBOOL) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
+[\INSTRUCTION, (\VariableX, \TBOOL) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\VariableX\ \EQUAL\ \StackOne\ \FXOR\ \StackTwo)]}
+\end{mathpar}
+
+\paragraph{Crytographic oprerations}
+%HASH-KEY
+\begin{mathpar}
+\inferrule[HASH-KEY]
+  {
+  }
+  {[(\HASHKEY; \INSTRUCTION), (\StackOne, \TBYTE) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
+[\INSTRUCTION, (\VariableX, \TBYTE) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\VariableX\ = \FHASHKEY(\StackOne))]}
+\end{mathpar}
+
+%AMOUNT
+\paragraph{Blockchain operations}
+\begin{mathpar}
+\inferrule[AMOUNT]
+  {
+  }
+  {[(\AMOUNT; \INSTRUCTION), \STACK, \PREDICATE] \StateTrans \
+[\INSTRUCTION, (\VAMOUNT, \TMUTEZ) \STACKCONCAT\STACK, \PREDICATE}
+\end{mathpar}
+
+%CONTRACT ty
+\begin{mathpar}
+\inferrule[CONTRACT TY - some]
+  {
+  }
+  {[(\CONTRACT\ \TY ; \INSTRUCTION), (\StackOne, \TADDR) \STACKCONCAT\STACK, \PREDICATE] \SystemTrans \
+[\INSTRUCTION, (\SOME\ \VariableX, \TOPTION\ (\TCONTRACT\ \TY)) \STACKCONCAT\STACK, \\ \PREDICATE \Wedge\ (\GETCONTRACTTYPE(\StackOne, \TY) = \SOME\ \VariableX)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[CONTRACT TY - none]
+  {
+  }
+  {[(\CONTRACT\ \TY ; \INSTRUCTION), (\StackOne, \TADDR) \STACKCONCAT\STACK, \PREDICATE] \SystemTrans \
+[\INSTRUCTION, \NONE \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\GETCONTRACTTYPE(\StackOne, \TY) = \NONE]}
+\end{mathpar}
+
+\paragraph{Operations on data structures}
+%CAR
+\begin{mathpar}
+\inferrule[\CAR]
+  {
+  }
+  {[(\CAR; \INSTRUCTION), (\StackOne, \TPAIR\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
+[\INSTRUCTION, (\VariableX, \TYF) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \PAIR\ \VariableX\ \VariableY)]}
+\end{mathpar}
+
+\subsubsection{Branch Instructions}
+%IF
+\begin{mathpar}
+  \inferrule[IF-true]
+  {  
+  }{
+    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
+    \StateTrans\
+    [\INSTRUCTIONONE, \STACK, \PREDICATE\ \Wedge\ \StackOne]
+  }
+
+  \inferrule[IF-false]
+  {  
+  }{
+    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
+    \StateTrans\
+   [\INSTRUCTIONTWO, \STACK, \PREDICATE\ \Wedge\ \NEG\
+   \StackOne]
+ }
+\end{mathpar}
+
+%IF-LEFT-LEFT
+\begin{mathpar}
+  \inferrule[IF-LEFT-left]
+  {  
+  }{
+    [(\IFLEFT\ \INSTRUCTIONONE\ \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]
+    \StateTrans \
+    [\INSTRUCTIONONE, (\VariableX, \TYF) \STACKCONCAT\STACK,
+    \PREDICATE \wedge (\StackOne\ \EQUAL\ \LEFT\ \VariableX)]
+  }
+\end{mathpar}
+
+%IF-LEFT-RIGHT
+\begin{mathpar}
+  \inferrule[IF-LEFT-right]
+  {  
+  }{
+    [(\IFLEFT\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]
+    \StateTrans \
+    [\INSTRUCTIONTWO, (\VariableX, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQUAL\ \RIGHT\ \VariableX))]
+  }
+\end{mathpar}
+
+%IF_CONS
+\begin{mathpar}
+  \inferrule[IF-CONS-empty]
+  {  
+  }{
+    [(\IFCONS\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\  [\INSTRUCTIONTWO; \INSTRUCTION, \STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST)]}
+\end{mathpar}
+
+\begin{mathpar}
+  \inferrule[IF-CONS-nonempty]
+  {  
+  }{
+   [(\IFCONS\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\  \\ [\INSTRUCTIONONE, (\HEAD, \TY) \STACKCONCAT(\{ \TAIL \}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ ( \StackOne\ \EQUAL\ \{\HEAD; \STAIL \})]}
+\end{mathpar}
+
+%IF_NON
+\begin{mathpar}
+  \inferrule[IF-NONE-none]
+  {  
+  }{
+    [(\IFNONE\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TOPTION\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\   [\INSTRUCTIONONE; \INSTRUCTION, \STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \NONE)]}
+\end{mathpar}
+
+\begin{mathpar}
+  \inferrule[IF-NONE-some]
+  {  
+  }{
+    [(\IFNONE\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),   (\StackOne, \TOPTION\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\   [\INSTRUCTIONTWO,  (\VariableX, \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ ( \StackOne\ \EQUAL\ \SOME\ \VariableX)]}
+\end{mathpar}
+
+\subsubsection{Loop Instructions}
+\paragraph{While loops}
+%LOOP
+\begin{mathpar}
+  \inferrule[LOOP-true]
+  {  
+  }{
+    [(\LOOP\ \INSTRUCTIONONE; \INSTRUCTION),  (\StackOne, \TBOOL)
+    \STACKCONCAT\STACK, \PREDICATE]
+    \StateTrans\
+    [(\INSTRUCTIONONE; \LOOP\ \INSTRUCTIONONE; \INSTRUCTION),
+    \STACK, \PREDICATE \wedge \StackOne]
+  }
+
+  \inferrule[LOOP-false]
+  {  
+  }{
+    [(\LOOP\ \INSTRUCTIONONE; \INSTRUCTION),  (\StackOne, \TBOOL) \STACKCONCAT\
+    \STACK, \PREDICATE]
+    \StateTrans\
+   [\INSTRUCTION, \STACK, \PREDICATE \wedge
+   (\NEG\StackOne)]
+   }
+\end{mathpar}
+\paragraph{For loops}
+%%ITER
+\begin{mathpar}
+  \inferrule[ITER-empty]
+  {  
+  }{
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, \STACK,  \PREDICATE\ \Wedge\  (\StackOne\ \EQUAL\ \EMPTYLIST)]
+  }
+\end{mathpar}
+
+\begin{mathpar}
+  \inferrule[ITER-nonempty]
+  {  [\ITER,  (\HEAD, \TY) \STACKCONCAT\STACK, 
+    Q]
+    \StateTrans^*
+    [ \EMPTYSTACK,  \STACK', Q']
+  }{
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE \wedge Q] \StateTrans \\ [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), \{\STAIL\}\ \STACKCONCAT\STACK',  \PREDICATE \wedge Q' \Wedge  ( \StackOne\ \EQUAL\ \{\HEAD; \STAIL \}) ]
+  }
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[CONCAT]
+  {
+  }
+  {[(\CONCAT; \INSTRUCTION), (\StackOne, \TYLIST\ \TSTR) \STACKCONCAT\STACK,  \PREDICATE] \StateTrans 
+[\INSTRUCTION,  ("",  \TSTR) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[CONCAT]
+  {
+  [\CONCAT,  (\{\TAIL\}, \TYLIST\ \TSTR) \STACKCONCAT\EMPTYSTACK, Q]
+    \StateTrans^*
+    [\EMPTYSTACK, (\StackTwo,  \TSTR) \STACKCONCAT\EMPTYSTACK, Q']
+  }
+  {[(\CONCAT; \INSTRUCTION),  (\StackOne, \TYLIST\ \TSTR) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans \\
+[\INSTRUCTION, ( \HEAD\ \STRINGCONCAT\ \StackTwo, \TSTR) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ Q']}
+\end{mathpar}
+
+%MEM
+\begin{mathpar}
+\inferrule[MEM-empty]
+  {
+  }
+  {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
+[\INSTRUCTION, (\FALSE, \TBOOL) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackTwo\ \EQUAL\ \EMPTYSET)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[MEM-nonempty]
+  {
+  [\COMPARE, (\StackOne, \TYF) \STACKCONCAT (\K, \TYF) \STACKCONCAT\EMPTYSTACK, Q]
+    \StateTrans^*
+    [\EMPTYSTACK,  (\VariableB, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
+  }
+  {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans  \
+[\MEM; \INSTRUCTION, \StackOne\ \STACKCONCAT\{\LESS\ \M\ \MORE\} \STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackTwo\ \EQUAL\ \{\ELT\ \K\ \V; \LESS\ \M\ \MORE\})  \Wedge\ (\VariableB\ \EQUAL\ \ONE)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[MEM-nonempty]
+  {
+  [\COMPARE, (\StackOne, \TYF) \STACKCONCAT (\K, \TYF) \STACKCONCAT\EMPTYSTACK, Q]
+    \StateTrans^*
+    [\EMPTYSTACK,  (\VariableB, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
+  }
+  {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans  \\
+[\INSTRUCTION, (\TRUE, \TBOOL) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackTwo\ \EQUAL\ \{\ELT\ \K\ \V; \LESS\ \M\ \MORE\}) \Wedge\ (\VariableB\ \EQUAL\ \ZERO)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[MEM-nonempty]
+  {
+  [\COMPARE, (\StackOne, \TYF) \STACKCONCAT (\K, \TYF) \STACKCONCAT\EMPTYSTACK, Q]
+    \StateTrans^*
+    [\EMPTYSTACK,  (\VariableB, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
+  }
+  {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans  \\
+[\INSTRUCTION, (\FALSE, \TBOOL) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackTwo\ \EQUAL\ \{\ELT\ \K\ \V; \LESS\ \M\ \MORE\})  \Wedge\ (\VariableB\ \EQUAL\ \MINUS\ \ONE)]}
+\end{mathpar}
+
+%MAP
+\begin{mathpar}
+\inferrule[MAP-empty]
+  {
+  }
+  {[(\MAP\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
+[\INSTRUCTION, (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[MAP-nonempty]
+  {
+  [\INSTRUCTIONONE, (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q1]
+    \StateTrans^*
+    [\EMPTYSTACK,  (\PHEAD, \TY) \STACKCONCAT\EMPTYSTACK , Q1'] \\  [\MAP\ \INSTRUCTIONONE, (\{\TAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK , Q2]
+    \StateTrans^*
+    [\EMPTYSTACK,  (\{\PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK , Q2']
+  }
+  {[(\MAP\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1 \Wedge\ Q2 ] \StateTrans  \\
+[\INSTRUCTION, (\{\PHEAD; \PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1' \Wedge\ Q2'  \Wedge\ (\StackOne \EQUAL\ \{\HEAD; \TAIL\})]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[UPDATE-empty-true]
+  {
+  }
+  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE]\ \SystemTrans\  \\ [\INSTRUCTION, (\{\VariableX \}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\  \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST) \Wedge\ (\VariableB\ \EQUAL\ \TRUE)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[UPDATE-empty-false]
+  {
+  }
+  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE]\ \SystemTrans\  \\ [\INSTRUCTION, (\EMPTYLIST, \TYLIST\ \TY)\ \STACKCONCAT\STACK, \PREDICATE\  \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST) \Wedge\ (\VariableB\ \EQUAL\ \FALSE)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[UPDATE-nonempty-true]
+  {
+  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
+    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
+  }
+  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans
+[\INSTRUCTION, (\StackOne, \TYLIST\ \TY)
+\STACKCONCAT\STACK,\\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQUAL\ \TRUE) \Wedge\ (\VariableA\ \EQUAL\ \ZERO)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[UPDATE-nonempty-false]
+  {
+  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
+    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
+  }
+  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans  \\
+[\INSTRUCTION, (\{\TAIL\}, \TYLIST\ \TY)
+\STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQUAL\ \FALSE) \Wedge\ (\VariableA\ \EQUAL\ \ZERO)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[UPDATE-nonempty-true]
+  {
+  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
+    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
+  }
+  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans  \\
+[\INSTRUCTION, (\{\VariableX; \HEAD; \TAIL\}, \TYLIST\ \TY)
+\STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQUAL\ \TRUE) \Wedge\ (\VariableA\ \EQUAL\ \MINUS\ \ONE)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[UPDATE-nonempty-false]
+  {
+  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
+    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
+  }
+  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans\  \\
+[\INSTRUCTION, (\{\HEAD; \TAIL\}, \TYLIST\ \TY)
+\STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQUAL\ \FALSE) \Wedge\ (\VariableA\ \EQUAL\ \MINUS\ \ONE)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[UPDATE-nonempty-1]
+  {
+  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q1] \StateTrans^*
+    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q1'] \\
+ [\UPDATE, (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT( \{\TAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK, Q2] \StateTrans^* \\  [\EMPTYSTACK, ( \{\PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK, Q2']
+  }
+  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1 \Wedge\ Q2 ] \SystemTrans\  \\
+[\INSTRUCTION; (\{\HEAD; \PTAIL\}, \TYLIST\ \TY)
+\STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1' \Wedge\ Q2' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableA\ \EQUAL\ \ONE)]}
+\end{mathpar}
+
+\subsubsection{Operation on tickets}
+\subsubsection{FAILWITH}
+a Michelson program can fail, explicitly using a specific opcode
+
+%FAILWITH
+\begin{mathpar}
+  \inferrule[FAILWITH]
+  {
+  }{[(\FAILWITH; \INSTRUCTION), (\StackOne,  \TY) \STACKCONCAT \STACK,  \PREDICATE] \StateTrans [\EMPTYSTACK, failwith (\StackOne) \STACKCONCAT\EMPTYSTACK, \PREDICATE]}
+\end{mathpar}
+\subsection{Dealing with loops}
+\subsubsection{For loop: ITER}
+\subsubsection{While loops: \LOOP\ and \LOOP-LEFT}
+\section {Domain Specific Language}
+\section {Static Checker}
+\section {Case Studies}
+\subsection{USDtz}
+\subsection{Kolibri Oracle Contract}
+\section {Related Work}
+\section {Conclusion}
+\section {Appendix}
 
@@
 \end{figure}
-
-%\paragraph{Sequence actions.}
-%\begin{figure}[h]
-%\center
-%\includegraphics[width= 10 cm]{life-cycle-1}
-%\caption{Life-cycle for the auction contract.}
-%\label{fca1}
-%\end{figure}
-
-\pagebreak
-\subsection{Rules}
-The rule semantic is defined by several kinds of transitions:
-\begin{enumerate}
-\item \ExprTrans\ single-step evaluation of an expression in a system state,
-\item \StateTrans\ internal transitions of a system state, which is non-deterministic  as shown for instructions \ITER\ and \LOOP,
-\item \SystemTrans\ symbolic system transitions.
-\end{enumerate}
-
-\subsubsection{System rules}
-\begin{mathpar}
-\inferrule[INVALID-PRE]
-  { \NEG\ \PREDICATE
-  }{
-  \{[\INSTRUCTION, \STACK, \PREDICATE]\} \cup \SYSTEM \SystemTrans \SYSTEM}
-\end{mathpar}
-
-\subsubsection{Instruction rules}
+\subsubsection{Basic Instructions}
+
 \paragraph{Control structures}
@@
     [(\LAMBDA\ \TYF\ \TYS\ \{ \INSTRUCTIONONE \} ; \INSTRUCTION),\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, (\{\INSTRUCTIONONE\}, \TLAMBDA\ \TYF\ \rightarrow\ \TYS) \STACKCONCAT\STACK, \PREDICATE]}
-\end{mathpar}
-
-%IF
-\begin{mathpar}
-  \inferrule[IF-true]
-  {  
-  }{
-    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
-    \StateTrans\
-    [\INSTRUCTIONONE, \STACK, \PREDICATE\ \Wedge\ \StackOne]
-  }
-
-  \inferrule[IF-false]
-  {  
-  }{
-    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
-    \StateTrans\
-   [\INSTRUCTIONTWO, \STACK, \PREDICATE\ \Wedge\ \NEG\
-   \StackOne]
- }
-\end{mathpar}
-
-%IF-LEFT-LEFT
-\begin{mathpar}
-  \inferrule[IF-LEFT-left]
-  {  
-  }{
-    [(\IFLEFT\ \INSTRUCTIONONE\ \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]
-    \StateTrans \
-    [\INSTRUCTIONONE, (\VariableX, \TYF) \STACKCONCAT\STACK,
-    \PREDICATE \wedge (\StackOne\ \EQUAL\ \LEFT\ \VariableX)]
-  }
-\end{mathpar}
-
-%IF-LEFT-RIGHT
-\begin{mathpar}
-  \inferrule[IF-LEFT-right]
-  {  
-  }{
-    [(\IFLEFT\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]
-    \StateTrans \
-    [\INSTRUCTIONTWO, (\VariableX, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQUAL\ \RIGHT\ \VariableX))]
-  }
-\end{mathpar}
-
-%IF_CONS
-\begin{mathpar}
-  \inferrule[IF-CONS-empty]
-  {  
-  }{
-    [(\IFCONS\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\  [\INSTRUCTIONTWO; \INSTRUCTION, \STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST)]}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[IF-CONS-nonempty]
-  {  
-  }{
-   [(\IFCONS\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\  \\ [\INSTRUCTIONONE, (\HEAD, \TY) \STACKCONCAT(\{ \TAIL \}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ ( \StackOne\ \EQUAL\ \{\HEAD; \STAIL \})]}
-\end{mathpar}
-
-%IF_NON
-\begin{mathpar}
-  \inferrule[IF-NONE-none]
-  {  
-  }{
-    [(\IFNONE\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TOPTION\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\   [\INSTRUCTIONONE; \INSTRUCTION, \STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \NONE)]}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[IF-NONE-some]
-  {  
-  }{
-    [(\IFNONE\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),   (\StackOne, \TOPTION\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\   [\INSTRUCTIONTWO,  (\VariableX, \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ ( \StackOne\ \EQUAL\ \SOME\ \VariableX)]}
-\end{mathpar}
-
-%LOOP
-\begin{mathpar}
-  \inferrule[LOOP-true]
-  {  
-  }{
-    [(\LOOP\ \INSTRUCTIONONE; \INSTRUCTION),  (\StackOne, \TBOOL)
-    \STACKCONCAT\STACK, \PREDICATE]
-    \StateTrans\
-    [(\INSTRUCTIONONE; \LOOP\ \INSTRUCTIONONE; \INSTRUCTION),
-    \STACK, \PREDICATE \wedge \StackOne]
-  }
-
-  \inferrule[LOOP-false]
-  {  
-  }{
-    [(\LOOP\ \INSTRUCTIONONE; \INSTRUCTION),  (\StackOne, \TBOOL) \STACKCONCAT\
-    \STACK, \PREDICATE]
-    \StateTrans\
-   [\INSTRUCTION, \STACK, \PREDICATE \wedge
-   (\NEG\StackOne)]
-   }
-\end{mathpar}
-
-%%ITER
-\begin{mathpar}
-  \inferrule[ITER-empty]
-  {  
-  }{
-    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, \STACK,  \PREDICATE\ \Wedge\  (\StackOne\ \EQUAL\ \EMPTYLIST)]
-  }
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[ITER-nonempty]
-  {  [\ITER,  (\HEAD, \TY) \STACKCONCAT\STACK, 
-    Q]
-    \StateTrans^*
-    [ \EMPTYSTACK,  \STACK', Q']
-  }{
-    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE \wedge Q] \StateTrans \\ [(\TITER\ \INSTRUCTIONONE ; \INSTRUCTION), \{\STAIL\}\ \STACKCONCAT\STACK',  \PREDICATE\ \Wedge  ( \StackOne\ \EQUAL\ \{\HEAD; \STAIL \})  \wedge Q']
-  }
 \end{mathpar}
@@
 
+\subsubsection{Branch Instructions}
+%IF
+\begin{mathpar}
+  \inferrule[IF-true]
+  {  
+  }{
+    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
+    \StateTrans\
+    [\INSTRUCTIONONE, \STACK, \PREDICATE\ \Wedge\ \StackOne]
+  }
+
+  \inferrule[IF-false]
+  {  
+  }{
+    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
+    \StateTrans\
+   [\INSTRUCTIONTWO, \STACK, \PREDICATE\ \Wedge\ \NEG\
+   \StackOne]
+ }
+\end{mathpar}
+
+%IF-LEFT-LEFT
+\begin{mathpar}
+  \inferrule[IF-LEFT-left]
+  {  
+  }{
+    [(\IFLEFT\ \INSTRUCTIONONE\ \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]
+    \StateTrans \
+    [\INSTRUCTIONONE, (\VariableX, \TYF) \STACKCONCAT\STACK,
+    \PREDICATE \wedge (\StackOne\ \EQUAL\ \LEFT\ \VariableX)]
+  }
+\end{mathpar}
+
+%IF-LEFT-RIGHT
+\begin{mathpar}
+  \inferrule[IF-LEFT-right]
+  {  
+  }{
+    [(\IFLEFT\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]
+    \StateTrans \
+    [\INSTRUCTIONTWO, (\VariableX, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQUAL\ \RIGHT\ \VariableX))]
+  }
+\end{mathpar}
+
+%IF_CONS
+\begin{mathpar}
+  \inferrule[IF-CONS-empty]
+  {  
+  }{
+    [(\IFCONS\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\  [\INSTRUCTIONTWO; \INSTRUCTION, \STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST)]}
+\end{mathpar}
+
+\begin{mathpar}
+  \inferrule[IF-CONS-nonempty]
+  {  
+  }{
+   [(\IFCONS\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\  \\ [\INSTRUCTIONONE, (\HEAD, \TY) \STACKCONCAT(\{ \TAIL \}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ ( \StackOne\ \EQUAL\ \{\HEAD; \STAIL \})]}
+\end{mathpar}
+
+%IF_NON
+\begin{mathpar}
+  \inferrule[IF-NONE-none]
+  {  
+  }{
+    [(\IFNONE\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TOPTION\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\   [\INSTRUCTIONONE; \INSTRUCTION, \STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \NONE)]}
+\end{mathpar}
+
+\begin{mathpar}
+  \inferrule[IF-NONE-some]
+  {  
+  }{
+    [(\IFNONE\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),   (\StackOne, \TOPTION\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\   [\INSTRUCTIONTWO,  (\VariableX, \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ ( \StackOne\ \EQUAL\ \SOME\ \VariableX)]}
+\end{mathpar}
+
+\subsubsection{Loop Instructions}
+\paragraph{While loops}
+%LOOP
+\begin{mathpar}
+  \inferrule[LOOP-true]
+  {  
+  }{
+    [(\LOOP\ \INSTRUCTIONONE; \INSTRUCTION),  (\StackOne, \TBOOL)
+    \STACKCONCAT\STACK, \PREDICATE]
+    \StateTrans\
+    [(\INSTRUCTIONONE; \LOOP\ \INSTRUCTIONONE; \INSTRUCTION),
+    \STACK, \PREDICATE \wedge \StackOne]
+  }
+
+  \inferrule[LOOP-false]
+  {  
+  }{
+    [(\LOOP\ \INSTRUCTIONONE; \INSTRUCTION),  (\StackOne, \TBOOL) \STACKCONCAT\
+    \STACK, \PREDICATE]
+    \StateTrans\
+   [\INSTRUCTION, \STACK, \PREDICATE \wedge
+   (\NEG\StackOne)]
+   }
+\end{mathpar}
+\paragraph{For loops}
+%%ITER
+\begin{mathpar}
+  \inferrule[ITER-empty]
+  {  
+  }{
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, \STACK,  \PREDICATE\ \Wedge\  (\StackOne\ \EQUAL\ \EMPTYLIST)]
+  }
+\end{mathpar}
+
+\begin{mathpar}
+  \inferrule[ITER-nonempty]
+  {  [\ITER,  (\HEAD, \TY) \STACKCONCAT\STACK, 
+    Q]
+    \StateTrans^*
+    [ \EMPTYSTACK,  \STACK', Q']
+  }{
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE \wedge Q] \StateTrans \\ [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), \{\STAIL\}\ \STACKCONCAT\STACK',  \PREDICATE \wedge Q' \Wedge  ( \StackOne\ \EQUAL\ \{\HEAD; \STAIL \}) ]
+  }
+\end{mathpar}
+
 \begin{mathpar}
@@
 \subsubsection{FAILWITH}
+a Michelson program can fail, explicitly using a specific opcode
+
 %FAILWITH
@@
 \end{mathpar}
-\section {Domain Specific Language}
-\section {Static Checker}
-\section {Case Studies}
-\section {Related Work}
-\section {Conclusion}
+\subsection{Dealing with loops}
+\subsubsection{For loop: ITER}
+\subsubsection{While loops: \LOOP\ and \LOOP-LEFT}
 \end{document}

### 2023-11-28 papers/static-checker/ecoop2024/ecoop2024.tex
add instructions parts

@@
 \end{mathpar}
+
 There are various types of instructions in Michelson, categorized based on their functions.
@@
 This categorization reflects how these instructions are handled within our specific model.
-\subsubsection{Basic Instructions}
-
-\paragraph{Control structures}
-%EXE
-\begin{mathpar}
-  \inferrule[EXEC]
-  {
-    [\INSTRUCTIONONE, (\StackOne, \TYF) \STACKCONCAT \EMPTYSTACK, 
-    Q]
-    \StateTrans^*
-    [ \EMPTYSTACK, (\StackOne', \TYS) \STACKCONCAT Q']
-  }{
-     [(\EXEC; \INSTRUCTION),   (\{\INSTRUCTIONONE\}, \TYF\ \rightarrow\ \TYS) \STACKCONCAT
-    (\StackOne, \TYF) \STACKCONCAT \STACK, \PREDICATE \wedge Q] 
-    \StateTrans \
-    [ \INSTRUCTION, (\StackOne', \TYS) \STACKCONCAT \STACK,
-    \PREDICATE \wedge Q']}
-\end{mathpar}
-
-%APPLY
-\begin{mathpar}
-  \inferrule[APPLY]
-  {
-  }{
-    [(\APPLY; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\{\INSTRUCTIONONE\}, \TLAMBDA\ (\TPAIR\ \TYF\  \TYS)\ \TYT) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\\ [\INSTRUCTION, (\{\PUSH\ \TYF\ \StackOne; \IPAIR; \INSTRUCTIONONE\}, \TLAMBDA\ \TYS\ \TYT ) \STACKCONCAT\STACK, \PREDICATE]}
-\end{mathpar}
-
-%LAMBLA
-\begin{mathpar}
-  \inferrule[LAMBDA]
-  {  
-  }{
-    [(\LAMBDA\ \TYF\ \TYS\ \{ \INSTRUCTIONONE \} ; \INSTRUCTION),\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, (\{\INSTRUCTIONONE\}, \TLAMBDA\ \TYF\ \rightarrow\ \TYS) \STACKCONCAT\STACK, \PREDICATE]}
-\end{mathpar}
-
-\paragraph{Stack Manipulation}
-%DIG
-\begin{mathpar}
-\inferrule[DIG]
-  {
-   \FLEN(\A) \EQUAL\ \N
-  }
-  {[(\DIG\ \N ; \INSTRUCTION), \A\ \At\ (\StackOne, \TY) \STACKCONCAT\B, \PREDICATE] \StateTrans 
-[\INSTRUCTION, (\StackOne, \TY) \STACKCONCAT\A\ \At\ \B, \PREDICATE]}
-\end{mathpar}
-
-%DIP
-\begin{mathpar}
-  \inferrule[DIP]
-  {
-    [\INSTRUCTIONONE,  \STACK, Q]
-    \StateTrans^*
-    [\EMPTYSTACK,  \STACK_1, Q']
-  }
-  {[(\DIP\ \INSTRUCTIONONE; \INSTRUCTION), (\StackOne, \TY) \STACKCONCAT
-    \STACK, \PREDICATE \wedge Q]
-    \StateTrans 
-    [\INSTRUCTION, (\StackOne, \TY) \STACKCONCAT\STACK_1,
-    \PREDICATE \wedge Q']
-  }
-\end{mathpar}
-
-%DIP n
-\begin{mathpar}
-\inferrule[DIP n]
-  { 
-     \FLEN(\A) \EQUAL\ \N \\ [\INSTRUCTIONONE,  \B, Q]
-    \StateTrans^*
-    [\EMPTYSTACK,  \B_1, Q']
-  }
-  {[(\DIP\ \N\ \INSTRUCTIONONE; \INSTRUCTION), \A\ \At\ \B, \PREDICATE \wedge Q] \StateTrans 
-[(\INSTRUCTION), \A\ \At\ \B_1, \PREDICATE \wedge Q']}
-\end{mathpar}
-
-%PUSH
-\begin{mathpar}
-  \inferrule[PUSH]
-  {  
-  }{
-    [(\PUSH\ \TY\ \VariableX; \INSTRUCTION),\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, (\VariableX, \TY) \STACKCONCAT\STACK, \PREDICATE]}
-\end{mathpar}
-
-\paragraph{Arithmetic operations}
-%ADD
-\begin{mathpar}
-\inferrule[ADD]
-  {
-  }
-  {[(\ADD; \INSTRUCTION), (\StackOne, \TNAT) \STACKCONCAT(\StackTwo, \TNAT) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\VariableX, \TNAT) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\VariableX\ \EQUAL\ \StackOne\ \PLUS\ \StackTwo)]}
-\end{mathpar}
-
+\subsubsection{One-step Instructions}
+A one-step instruction only effects a system state itself, does not produce a new state, and halts the execution after a single operation.
+The ABS rule specifies the corresponding instruction that applies to the first element of the stack.
+This element must have the type of int and returns the positive value of its current value, which is of a natural number type.
+Another example, the COMPARE instruction compares the two first elements of a stack, both of which have a natural number type.
+It returns a result of either -1, 0, or 1 depending on the comperations of their values.
 %ABS
@@
 \begin{mathpar}
-\inferrule[COMPARE-nat]
+\inferrule[COMPARE]
   {
@@
 \end{mathpar}
-
-\begin{mathpar}
-\inferrule[COMPARE-some-some]
-  {
-  [\COMPARE,  (\VariableX, \TY) \STACKCONCAT (\VariableY, \TY) \STACKCONCAT\EMPTYSTACK, Q]
-    \StateTrans^*
-    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
-  }
-  {
-    [(\COMPARE ; \INSTRUCTION), (\StackOne, \TOPTION\ \TY) \STACKCONCAT (\StackTwo, \TOPTION\ \TY)
-    \STACKCONCAT \STACK, \PREDICATE \wedge Q]
-    \SystemTrans \\
-    [\INSTRUCTION, (\VariableA, \TINT) \STACKCONCAT \STACK,  \PREDICATE
-    \wedge (\StackOne\ \EQUAL\ \SOME\ \VariableX)
-    \wedge (\StackTwo\ \EQUAL\ \SOME\ \VariableY)
-    \wedge Q']
-    }
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[COMPARE-some-none]
-  {
-  }
-  {
-    [(\COMPARE ; \INSTRUCTION), (\StackOne, \TOPTION\ \TY) \STACKCONCAT (\StackTwo, \TOPTION\ \TY)
-    \STACKCONCAT \STACK, \PREDICATE]
-    \SystemTrans \\
-    [\INSTRUCTION, (1, \TINT) \STACKCONCAT \STACK,  \PREDICATE
-    \wedge (\StackOne\ \EQUAL\ \SOME\ \VariableX)
-    \wedge (\StackTwo\ \EQUAL\ \NONE)
-    ]
-    }
-\end{mathpar}
-
-\paragraph{Boolean operations}
-%XOR
-\begin{mathpar}
-\inferrule[XOR]
-  {
-  }
-  {[(\XOR; \INSTRUCTION), (\StackOne, \TBOOL) \STACKCONCAT(\StackTwo, \TBOOL) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\VariableX, \TBOOL) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\VariableX\ \EQUAL\ \StackOne\ \FXOR\ \StackTwo)]}
-\end{mathpar}
-
-\paragraph{Crytographic oprerations}
-%HASH-KEY
-\begin{mathpar}
-\inferrule[HASH-KEY]
-  {
-  }
-  {[(\HASHKEY; \INSTRUCTION), (\StackOne, \TBYTE) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\VariableX, \TBYTE) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\VariableX\ = \FHASHKEY(\StackOne))]}
-\end{mathpar}
-
-%AMOUNT
-\paragraph{Blockchain operations}
+\subsubsection{Multi-step Instructions}
+Multi-step instructions require the execution of a sub-sequence of instructions before returning to the main execution.
+The following rule models the instruction EXEC, which executes a function specified as a sequence of instructions denoted as \INSTRUCTIONONE\ in the rule.
+This instruction first applies the code of the function to the first element of the stack.
+It then places the result back into the main execution.
+\begin{mathpar}
+  \inferrule[EXEC]
+  {
+    [\INSTRUCTIONONE, (\StackOne, \TYF) \STACKCONCAT \EMPTYSTACK, 
+    Q]
+    \StateTrans^*
+    [ \EMPTYSTACK, (\StackOne', \TYS) \STACKCONCAT Q']
+  }{
+     [(\EXEC; \INSTRUCTION),   (\{\INSTRUCTIONONE\}, \TYF\ \rightarrow\ \TYS) \STACKCONCAT
+    (\StackOne, \TYF) \STACKCONCAT \STACK, \PREDICATE \wedge Q] 
+    \StateTrans \
+    [ \INSTRUCTION, (\StackOne', \TYS) \STACKCONCAT \STACK,
+    \PREDICATE \wedge Q']}
+\end{mathpar}
+
+The \DIP\ \N\ instruction delves into the first \N\ elements of a stack, applies the sequence of instructions denoted as \INSTRUCTIONONE\ to the remaining part of the stack, modifies a part of the predicate and subsequently pushes the result back into the main execution.
+%DIP n
+\begin{mathpar}
+\inferrule[\DIP\ \N]
+  { 
+     \FLEN(\A) \EQUAL\ \N \\ [\INSTRUCTIONONE,  \B, Q]
+    \StateTrans^*
+    [\EMPTYSTACK,  \B_1, Q']
+  }
+  {[(\DIP\ \N\ \INSTRUCTIONONE; \INSTRUCTION), \A\ \At\ \B, \PREDICATE \wedge Q] \StateTrans 
+[(\INSTRUCTION), \A\ \At\ \B_1, \PREDICATE \wedge Q']}
+\end{mathpar}
+\subsubsection{Blockchain Instructions}
+ Blockchain instructions make implicit use of data from an execution environment, derived from the current state of the blockchain (the context), from the transaction that triggered the contract, and from the block containing this transaction.
+We model these data as symbolic values, which satisfis some constrants.
+For example, the AMOUNT instruction adds to the stack the amount of tokens that sent together with the transcation which calls this smart contract.
+Here, the amount is modeled as a symbolic value donated as \VAMOUNT, which has \TMUTEZ\ type, which is a positive number value.
+
 \begin{mathpar}
@@
 
-%CONTRACT ty
-\begin{mathpar}
-\inferrule[CONTRACT TY - some]
-  {
-  }
-  {[(\CONTRACT\ \TY ; \INSTRUCTION), (\StackOne, \TADDR) \STACKCONCAT\STACK, \PREDICATE] \SystemTrans \
-[\INSTRUCTION, (\SOME\ \VariableX, \TOPTION\ (\TCONTRACT\ \TY)) \STACKCONCAT\STACK, \\ \PREDICATE \Wedge\ (\GETCONTRACTTYPE(\StackOne, \TY) = \SOME\ \VariableX)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[CONTRACT TY - none]
-  {
-  }
-  {[(\CONTRACT\ \TY ; \INSTRUCTION), (\StackOne, \TADDR) \STACKCONCAT\STACK, \PREDICATE] \SystemTrans \
-[\INSTRUCTION, \NONE \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\GETCONTRACTTYPE(\StackOne, \TY) = \NONE]}
-\end{mathpar}
-
-\paragraph{Operations on data structures}
-%CAR
-\begin{mathpar}
-\inferrule[\CAR]
-  {
-  }
-  {[(\CAR; \INSTRUCTION), (\StackOne, \TPAIR\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\VariableX, \TYF) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \PAIR\ \VariableX\ \VariableY)]}
-\end{mathpar}
-
+\subsubsection{Cryptographic Instructions}
+Cryptographic instructions in Michelson utilize built-in functions that manage cryptographic features.
+These functions are symbolically modeled in our framework, specifying their inputs and outputs.
+For instance, the instruction \SHA\ computes the cryptographic hash of the top of the stack using the SHA-256 cryptographic hash function.
+The function SHA-256 is symbolically represented as the function  \FSHA\  that takes an input of type \TBYTE\ and returns another byte value, constrained to a length of 256.
+%HASH-KEY
+\begin{mathpar}
+\inferrule[\SHA]
+  {
+  }
+  {[(\SHA; \INSTRUCTION), (\StackOne, \TBYTE) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
+[\INSTRUCTION, (\VariableX, \TBYTE) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\VariableX\ = \FSHA(\StackOne))]}
+\end{mathpar}
 \subsubsection{Branch Instructions}
+The Michelson language incorporates conditional branching, enabling the execution of specific code segments based on certain criteria.
+One of the instructions facilitating this is the IF {} {} construct.
+For example, the \IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO\ instruction allows the creation of branches in execution.
+It takes two sequences as arguments.
+Expecting a boolean value at the top of the stack, it consumes this top element.
+If the boolean is True, it executes the first provided sequence; otherwise, it executes the second sequence.
 %IF
 \begin{mathpar}
-  \inferrule[IF-true]
-  {  
-  }{
-    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
-    \StateTrans\
-    [\INSTRUCTIONONE, \STACK, \PREDICATE\ \Wedge\ \StackOne]
-  }
-
-  \inferrule[IF-false]
-  {  
-  }{
-    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
-    \StateTrans\
-   [\INSTRUCTIONTWO, \STACK, \PREDICATE\ \Wedge\ \NEG\
-   \StackOne]
- }
-\end{mathpar}
-
-%IF-LEFT-LEFT
-\begin{mathpar}
-  \inferrule[IF-LEFT-left]
-  {  
-  }{
-    [(\IFLEFT\ \INSTRUCTIONONE\ \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]
-    \StateTrans \
-    [\INSTRUCTIONONE, (\VariableX, \TYF) \STACKCONCAT\STACK,
-    \PREDICATE \wedge (\StackOne\ \EQUAL\ \LEFT\ \VariableX)]
-  }
-\end{mathpar}
-
-%IF-LEFT-RIGHT
-\begin{mathpar}
-  \inferrule[IF-LEFT-right]
-  {  
-  }{
-    [(\IFLEFT\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]
-    \StateTrans \
-    [\INSTRUCTIONTWO, (\VariableX, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQUAL\ \RIGHT\ \VariableX))]
-  }
-\end{mathpar}
-
-%IF_CONS
-\begin{mathpar}
-  \inferrule[IF-CONS-empty]
-  {  
-  }{
-    [(\IFCONS\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\  [\INSTRUCTIONTWO; \INSTRUCTION, \STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST)]}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[IF-CONS-nonempty]
-  {  
-  }{
-   [(\IFCONS\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\  \\ [\INSTRUCTIONONE, (\HEAD, \TY) \STACKCONCAT(\{ \TAIL \}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ ( \StackOne\ \EQUAL\ \{\HEAD; \STAIL \})]}
-\end{mathpar}
-
-%IF_NON
-\begin{mathpar}
-  \inferrule[IF-NONE-none]
-  {  
-  }{
-    [(\IFNONE\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TOPTION\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\   [\INSTRUCTIONONE; \INSTRUCTION, \STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \NONE)]}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[IF-NONE-some]
-  {  
-  }{
-    [(\IFNONE\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),   (\StackOne, \TOPTION\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\   [\INSTRUCTIONTWO,  (\VariableX, \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ ( \StackOne\ \EQUAL\ \SOME\ \VariableX)]}
+  \inferrule[IF]
+  {  
+  }{
+    \{[(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]\} \cup \SYSTEM 
+      \SystemTrans 
+    \{[\INSTRUCTIONONE, \STACK, \PREDICATE\ \Wedge\ \StackOne]\} \cup \{ [\INSTRUCTIONTWO, \STACK, \PREDICATE\ \Wedge\ \NEG\
+   \StackOne]\} \cup  \SYSTEM
+  }
+\end{mathpar}
+
+The \IFLEFT\ \INSTRUCTIONONE\  \INSTRUCTIONTWO\ instruction expects a or value at the top of the stack, it consumes this top element.
+If the value is Left, it executes the first provided sequence; otherwise, it executes the second sequence.
+%IF-LEFT
+\begin{mathpar}
+  \inferrule[IF-LEFT]
+  {  
+  }{
+    \{[(\IFLEFT\ \INSTRUCTIONONE\ \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]\}  \cup  \SYSTEM
+    \SystemTrans \\
+    \{[\INSTRUCTIONONE, (\VariableX, \TYF) \STACKCONCAT\STACK,
+    \PREDICATE \wedge (\StackOne\ \EQUAL\ \LEFT\ \VariableX)]\}  \cup  \{  [\INSTRUCTIONTWO, (\VariableX, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQUAL\ \RIGHT\ \VariableX))]\} \cup \SYSTEM
+  }
 \end{mathpar}
@@
 \subsubsection{Loop Instructions}
-\paragraph{While loops}
+In Michelson, there are several loop instructions that execute a loop over the data structure, such as ITER, MAP, MEMBER, SIZE and UPDATE on list, set, map or on the stack, such as LOOP and LOOP-LEFT.
+
+%%ITER
+\begin{mathpar}
+  \inferrule[ITER-empty]
+  {  
+  }{
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, \STACK,  \PREDICATE\ \Wedge\  (\StackOne\ \EQUAL\ \EMPTYLIST)]
+  }
+\end{mathpar}
+
+\begin{mathpar}
+  \inferrule[ITER-nonempty]
+  {  [\ITER,  (\HEAD, \TY) \STACKCONCAT\STACK, 
+    Q]
+    \StateTrans^*
+    [ \EMPTYSTACK,  \STACK', Q']
+  }{
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE \wedge Q] \StateTrans \\ [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), \{\STAIL\}\ \STACKCONCAT\STACK',  \PREDICATE \wedge Q' \Wedge  ( \StackOne\ \EQUAL\ \{\HEAD; \STAIL \}) ]
+  }
+\end{mathpar}
+
+Let us consider the \ITER\ instruction (for list), which applies to a stack \STACK, where the top element has type  (\TY\ \TYLIST) and the rest of the stack has type \TYA, returns the result stack of type \TYA.
+The \ITER\ instruction loops on the datastructure list.
+Typing
+\begin{mathpar}
+  \inferrule{\JTypeExpr\TEnv{\INSTRUCTION}{\TY : \TYA\ \SRightarrow\ \TYA}
+  }{
+      \JTypeExpr\TEnv{\ITER\ \INSTRUCTION}{\TYLIST\ \TY : \TYA\ \SRightarrow\ \TYA}
+    }
+\end{mathpar}
+
+Semantic
+
+\begin{mathpar}
+  \inferrule{
+  }{
+    \ITER\ \INSTRUCTION\ / \{ \} \STACKCONCAT\ \STACK\ \SRightarrow\  \STACK
+    }
+\end{mathpar}
+
+\begin{mathpar} 
+  \inferrule{\INSTRUCTION\  /  \VariableX\ \STACKCONCAT\ \STACK \SRightarrow\ \STACK'
+  }{
+    \ITER\ \INSTRUCTION\ / \{ \VariableX\ ; \TAIL\ \} \STACKCONCAT\ \STACK\ \SRightarrow\ \ITER\ \INSTRUCTION\ / \{ \TAIL\ \} \STACKCONCAT\ \STACK' 
+    }
+\end{mathpar}
+
+If a list \LIST\ is concrete, the intructuion simply loops until the list ends with an empty list construction.
+Here we consider the synbolic execution of \ITER\ when the list is a sybolic term or variable.
+
+The sequence of intructuions I is a lamda function  (\TLAMBDA\ (\TY\ : \TYA)\ \TYA) applied to the stack of type (\TY\ : \TYA), returning the stack of type \TYA.
+We can represent I as the function f that takes an element of type \TY\ and a stack of type \TYA\ and returns a stack of type \TYA.
+
+\begin{mathpar}
+  f : \TY\  \TYA\ \SRightarrow\ \TYA
+\end{mathpar}
+
+\begin{mathpar}
+  f  \VariableX\ \STACK =  (\TLAMBDA\ (\TY\ : \TYA)\ \TYA) (\VariableX\  \STACKCONCAT\ \STACK)
+\end{mathpar}
+
+or
+
+\begin{mathpar}
+  f  \VariableX\ \STACK = I / (\VariableX\  \STACKCONCAT\ \STACK)
+\end{mathpar}
+
+Let  
+\LIST\ \STACKCONCAT\ \STACK
+
+ be the stack just before applying the instruction ITER I, where \VariableX\ be the head of the list and \STACK\ be the rest of the stack .
+For first  loop, let  \STACK\ be f (\VariableX, \STACK).
+\STACK\ is the stack resulting from applying the function f to the element \VariableX\ and the stack \STACK.
+In other words, the stack \STACK\ is formed by applying the sequence of the instructions I to the stack \VariableX\ \STACKCONCAT\ \STACK.
+
+Let the result of applying the instruction \ITER\ I on the stack \LIST\ ::  \STACK\ be the stack S', then Z is resulted from the \FOLD\ function that applies the function f  to each element of the list \LIST\ and initial value is the stack \STACK.
+
+\begin{mathpar}
+S' =  \FOLD\ \STACK\ f   \LIST
+\end{mathpar}
+
+%MAP
+\begin{mathpar}
+\inferrule[MAP-empty]
+  {
+  }
+  {[(\MAP\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
+[\INSTRUCTION, (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[MAP-nonempty]
+  {
+  [\INSTRUCTIONONE, (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q1]
+    \StateTrans^*
+    [\EMPTYSTACK,  (\PHEAD, \TY) \STACKCONCAT\EMPTYSTACK , Q1'] \\  [\MAP\ \INSTRUCTIONONE, (\{\TAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK , Q2]
+    \StateTrans^*
+    [\EMPTYSTACK,  (\{\PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK , Q2']
+  }
+  {[(\MAP\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1 \Wedge\ Q2 ] \StateTrans  \\
+[\INSTRUCTION, (\{\PHEAD; \PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1' \Wedge\ Q2'  \Wedge\ (\StackOne \EQUAL\ \{\HEAD; \TAIL\})]}
+\end{mathpar}
+
 %LOOP
@@
 \end{mathpar}
-\paragraph{For loops}
-%%ITER
-\begin{mathpar}
-  \inferrule[ITER-empty]
-  {  
-  }{
-    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, \STACK,  \PREDICATE\ \Wedge\  (\StackOne\ \EQUAL\ \EMPTYLIST)]
-  }
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[ITER-nonempty]
-  {  [\ITER,  (\HEAD, \TY) \STACKCONCAT\STACK, 
-    Q]
-    \StateTrans^*
-    [ \EMPTYSTACK,  \STACK', Q']
-  }{
-    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE \wedge Q] \StateTrans \\ [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), \{\STAIL\}\ \STACKCONCAT\STACK',  \PREDICATE \wedge Q' \Wedge  ( \StackOne\ \EQUAL\ \{\HEAD; \STAIL \}) ]
-  }
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[CONCAT]
-  {
-  }
-  {[(\CONCAT; \INSTRUCTION), (\StackOne, \TYLIST\ \TSTR) \STACKCONCAT\STACK,  \PREDICATE] \StateTrans 
-[\INSTRUCTION,  ("",  \TSTR) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[CONCAT]
-  {
-  [\CONCAT,  (\{\TAIL\}, \TYLIST\ \TSTR) \STACKCONCAT\EMPTYSTACK, Q]
-    \StateTrans^*
-    [\EMPTYSTACK, (\StackTwo,  \TSTR) \STACKCONCAT\EMPTYSTACK, Q']
-  }
-  {[(\CONCAT; \INSTRUCTION),  (\StackOne, \TYLIST\ \TSTR) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans \\
-[\INSTRUCTION, ( \HEAD\ \STRINGCONCAT\ \StackTwo, \TSTR) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ Q']}
-\end{mathpar}
-
-%MEM
-\begin{mathpar}
-\inferrule[MEM-empty]
-  {
-  }
-  {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\FALSE, \TBOOL) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackTwo\ \EQUAL\ \EMPTYSET)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[MEM-nonempty]
-  {
-  [\COMPARE, (\StackOne, \TYF) \STACKCONCAT (\K, \TYF) \STACKCONCAT\EMPTYSTACK, Q]
-    \StateTrans^*
-    [\EMPTYSTACK,  (\VariableB, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
-  }
-  {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans  \
-[\MEM; \INSTRUCTION, \StackOne\ \STACKCONCAT\{\LESS\ \M\ \MORE\} \STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackTwo\ \EQUAL\ \{\ELT\ \K\ \V; \LESS\ \M\ \MORE\})  \Wedge\ (\VariableB\ \EQUAL\ \ONE)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[MEM-nonempty]
-  {
-  [\COMPARE, (\StackOne, \TYF) \STACKCONCAT (\K, \TYF) \STACKCONCAT\EMPTYSTACK, Q]
-    \StateTrans^*
-    [\EMPTYSTACK,  (\VariableB, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
-  }
-  {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans  \\
-[\INSTRUCTION, (\TRUE, \TBOOL) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackTwo\ \EQUAL\ \{\ELT\ \K\ \V; \LESS\ \M\ \MORE\}) \Wedge\ (\VariableB\ \EQUAL\ \ZERO)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[MEM-nonempty]
-  {
-  [\COMPARE, (\StackOne, \TYF) \STACKCONCAT (\K, \TYF) \STACKCONCAT\EMPTYSTACK, Q]
-    \StateTrans^*
-    [\EMPTYSTACK,  (\VariableB, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
-  }
-  {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans  \\
-[\INSTRUCTION, (\FALSE, \TBOOL) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackTwo\ \EQUAL\ \{\ELT\ \K\ \V; \LESS\ \M\ \MORE\})  \Wedge\ (\VariableB\ \EQUAL\ \MINUS\ \ONE)]}
-\end{mathpar}
-
-%MAP
-\begin{mathpar}
-\inferrule[MAP-empty]
-  {
-  }
-  {[(\MAP\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[MAP-nonempty]
-  {
-  [\INSTRUCTIONONE, (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q1]
-    \StateTrans^*
-    [\EMPTYSTACK,  (\PHEAD, \TY) \STACKCONCAT\EMPTYSTACK , Q1'] \\  [\MAP\ \INSTRUCTIONONE, (\{\TAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK , Q2]
-    \StateTrans^*
-    [\EMPTYSTACK,  (\{\PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK , Q2']
-  }
-  {[(\MAP\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1 \Wedge\ Q2 ] \StateTrans  \\
-[\INSTRUCTION, (\{\PHEAD; \PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1' \Wedge\ Q2'  \Wedge\ (\StackOne \EQUAL\ \{\HEAD; \TAIL\})]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[UPDATE-empty-true]
-  {
-  }
-  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE]\ \SystemTrans\  \\ [\INSTRUCTION, (\{\VariableX \}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\  \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST) \Wedge\ (\VariableB\ \EQUAL\ \TRUE)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[UPDATE-empty-false]
-  {
-  }
-  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE]\ \SystemTrans\  \\ [\INSTRUCTION, (\EMPTYLIST, \TYLIST\ \TY)\ \STACKCONCAT\STACK, \PREDICATE\  \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST) \Wedge\ (\VariableB\ \EQUAL\ \FALSE)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[UPDATE-nonempty-true]
-  {
-  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
-    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
-  }
-  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans
-[\INSTRUCTION, (\StackOne, \TYLIST\ \TY)
-\STACKCONCAT\STACK,\\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQUAL\ \TRUE) \Wedge\ (\VariableA\ \EQUAL\ \ZERO)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[UPDATE-nonempty-false]
-  {
-  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
-    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
-  }
-  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans  \\
-[\INSTRUCTION, (\{\TAIL\}, \TYLIST\ \TY)
-\STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQUAL\ \FALSE) \Wedge\ (\VariableA\ \EQUAL\ \ZERO)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[UPDATE-nonempty-true]
-  {
-  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
-    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
-  }
-  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans  \\
-[\INSTRUCTION, (\{\VariableX; \HEAD; \TAIL\}, \TYLIST\ \TY)
-\STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQUAL\ \TRUE) \Wedge\ (\VariableA\ \EQUAL\ \MINUS\ \ONE)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[UPDATE-nonempty-false]
-  {
-  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
-    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
-  }
-  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans\  \\
-[\INSTRUCTION, (\{\HEAD; \TAIL\}, \TYLIST\ \TY)
-\STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQUAL\ \FALSE) \Wedge\ (\VariableA\ \EQUAL\ \MINUS\ \ONE)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[UPDATE-nonempty-1]
-  {
-  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q1] \StateTrans^*
-    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q1'] \\
- [\UPDATE, (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT( \{\TAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK, Q2] \StateTrans^* \\  [\EMPTYSTACK, ( \{\PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK, Q2']
-  }
-  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1 \Wedge\ Q2 ] \SystemTrans\  \\
-[\INSTRUCTION; (\{\HEAD; \PTAIL\}, \TYLIST\ \TY)
-\STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1' \Wedge\ Q2' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableA\ \EQUAL\ \ONE)]}
-\end{mathpar}
-
-\subsubsection{Operation on tickets}
+
 \subsubsection{FAILWITH}
@@
 \end{mathpar}
-\subsection{Dealing with loops}
-\subsubsection{For loop: ITER}
-\subsubsection{While loops: \LOOP\ and \LOOP-LEFT}
 \section {Domain Specific Language}

### 2023-11-29 papers/static-checker/ecoop2024/ecoop2024.tex
Change the format

@@
-%This is a template for producing reports for "Dagstuhl Reports".
-%See dagrep-v2021.pdf for further information.
-
-\documentclass[a4paper,UKenglish]{dagrep-v2021}
+\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
+%This is a template for producing LIPIcs articles. 
+%See lipics-v2021-authors-guidelines.pdf for further information.
 %for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
@@
 %for section-numbered lemmas etc., use "numberwithinsect"
+%for enabling cleveref support, use "cleveref"
+%for enabling autoref support, use "autoref"
+%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
+%for enabling thm-restate support, use "thm-restate"
+%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
 %for producing a PDF according the PDF/A standard, add "pdfa"
 
+%\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
+%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
+
+%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
 \usepackage{microtype}%if unwanted, comment out or use option "draft"
@@
 
-\bibliographystyle{plain}%the recommnded bibstyle
-
-\subject{Report from Dagstuhl Seminar 11013}
-\title{Formal Verification Tool Based on Symbolic Execution for Smart Contract}
-\titlerunning{11013 -- Seminar Sample}%optional
-
-\author[1]{Thi Thu Ha Doan}
-\author[2]{Peter Thiemann}
-\affil[1]{University of Freiburg, Germany
-  \texttt{doanha@informatik.uni-freiburg.de}}
-\affil[2]{University of Freiburg, Germany
-  \texttt{thiemann@informatik.uni-freiburg.de}}
-\authorrunning{T.T.H Doan and P.Thiemann}%optional
-
-\keywords{Smart Contract, Blockchain, Formal Verification, Symbolic Execution}%mandatory
-
-%Organizer macros:%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\seminarnumber{11013}
-\semdata{03.--07.~January, 2011 -- \url{https://www.dagstuhl.de/11013}}
-
-\ccsdesc[100]{General and reference~General literature}
-\ccsdesc[500]{Hardware~3D integrated circuits}
-\ccsdesc[500]{Software and its engineering~Software design engineering}
-\ccsdesc[300]{Networks~Network performance analysis}
-
-\additionaleditors{Tom Collector}%optional
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%Dagstuhl editorial office macros:%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\volumeinfo%(easychair interface)
-  {John Q. Open and Joan R. Access}%editors
-  {2}%number of editors
-  {Seminar Sample}%event
-  {1}%volume
-  {1}%issue
-  {1}%starting page number
-\DOI{10.4230/DagRep.1.1.1}%(DagRep.<issue no>.<volume no>.<firstpage>)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliographystyle{plainurl}% the mandatory bibstyle
+
+\title{Formal Verification Tool Based on Symbolic Execution for Smart Contract} %TODO Please add
+
+%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line
+
+\author{Thi Thu Ha Doan}{University of Freiburg, Germany}{doanha@informatik.uni-freiburg.de}{https://orcid.org/0000−0001−7524−4497}{(Optional) author-specific funding acknowledgements}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
+Please provide at least the name of the affiliation and the country.
+The full address is optional.
+Use additional curly braces to indicate the correct name splitting when the last name consists of multiple name parts.
+
+\author{Peter Thiemann}{University of Freiburg, Germany}{thiemann@informatik.uni-freiburg.de}{https://orcid.org/0000−0002−9000−1239}{[funding]}
+
+\authorrunning{T.T.Ha Doan and P.Thiemann} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'
+
+\Copyright{T.T.Ha Doan and Peter Thiemann} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+
+\ccsdesc[100]{\textcolor{red}{Replace ccsdesc macro with valid one}} %TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
+
+\keywords{Smart Contract, Blockchain, Formal Verification, Symbolic Execution} %TODO mandatory; please add comma-separated list of keywords
+
+\category{} %optional, e.g. invited paper
+
+\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
+%\relatedversiondetails[linktext={opt.
+text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g.
+Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional
+
+%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
+%\supplementdetails[linktext={opt.
+text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
+Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
+
+%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
+Please enter author specific funding statements as fifth argument of the \author macro.
+
+\acknowledgements{I want to thank \dots}%optional
+
+%\nolinenumbers %uncomment to disable line numbering
+
+%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\EventEditors{John Q. Open and Joan R. Access}
+\EventNoEds{2}
+\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
+\EventShortTitle{CVIT 2016}
+\EventAcronym{CVIT}
+\EventYear{2016}
+\EventDate{December 24--27, 2016}
+\EventLocation{Little Whinging, United Kingdom}
+\EventLogo{}
+\SeriesVolume{42}
+\ArticleNo{23}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%TODO mandatory: add short abstract of the document
 \begin{abstract}
@@
 \end{abstract}
-
-\summaryauthor[T.T.Ha Doan and P. Thiemann]{%
-T.T.Ha Doan (University of Freiburg, Germany, doanha@informatik.uni-freiburg.de)\\
-P. Thiemann (University of Freiburg, Germany, \\thiemann@informatik.uni-freiburg.de)
-}
-
-\license
-
-\tableofcontents
-
-%\newpage
-
 \section{Introduction}
@@
 
-While undergoing symbolic execution, branching may occur depending on the conditions, and these branching conditions are recorded as predicates.
-Let \PREDICATE\ represent a predicate expressed in conjunction form.
-
+While undergoing symbolic execution,  a symbolic execution state assumes different values based on the constraints of symbolic values.
+Additionally, branching may occur depending on conditions, and both constraints and branching conditions are recorded as predicates.
+Let \PREDICATE\ symbolize a predicate expressed in conjunction form, capturing the conditions and constraints encountered during the symbolic execution process.
 \begin{definition}
@@
 \end{definition}
-
 The Michelson program takes as input a stack that consists of a single pair whose first element is an input value referred to as the parameter, and second element represents the content of the storage space.
@@
 \subsubsection{While loops: \LOOP\ and \LOOP-LEFT}
+
 \end{document}

### 2023-12-06 papers/static-checker/ecoop2024/ecoop2024.tex
update rules

@@
 
-\title{Formal Verification Tool Based on Symbolic Execution for Smart Contract} %TODO Please add
+\title{Formal Verification Framework Based on Symbolic Execution for Smart Contract} %TODO Please add
 
@@
 \subsection{System Model}
-Michelson is the low-level smart contract language employed in the Tezos blockchain platform.
-It is characterized as a stack-based language, featuring high-level data types and primitives and integrates strict static type checking into its stack-based execution mode.
-
-The processing and manipulation of data during the execution of smart contracts are facilitated using a stack. A stack  can be written:
+Michelson serves as the low-level smart contract language for the Tezos blockchain platform.
+The processing and manipulation of data during the execution of smart contracts are managed using a stack.
+The representation of a stack can be described as follows:
 \begin{itemize}
-\item[]  \EMPTYSTACK\ for the empty stack.
-\item[]  \HEAD\ \STACKCONCAT\ \NTAIL\ for the stack whose first value has type (\HEAD) and queue has stack type (\NTAIL).
+\item[]  \EMPTYSTACK\ represents the empty stack.
+\item[]  \HEAD\ \STACKCONCAT\ \NTAIL\ denotes a stack with the top element as \HEAD\ and the remaining stack as \NTAIL.
 \end{itemize}
-
-Each piece of data in Michelson is assigned a specific type, and the language imposes restrictions preventing programmers from introducing custom types.
-Consider a stack denoted as $\STACK = (\TermOne, \TYF) \STACKCONCAT (\TermTwo, \TYS) \STACKCONCAT \DOT
-\STACKCONCAT \EMPTYSTACK$ where elements are types paired with terms.
+\begin{figure} []
+\begin{align*}
+T, U &::= \\
+   &\Mid\ \langle \text{comparable type}\rangle \\
+   &\Mid\ \text{option}\ \langle\text{type}\rangle \\
+   &\Mid\ \text{list}\ \langle\text{type}\rangle \\
+   &\Mid\ \text{set}\ \langle\text{comparable type}\rangle \\
+   &\Mid\ \text{operation} \\
+   &\Mid\ \text{contract}\ \langle\text{type}\rangle \\
+   &\Mid\ \text{ticket}\ \langle\text{comparable type}\rangle \\
+   &\Mid\ \text{pair}\ \langle\text{type}\rangle \langle\text{type}\rangle \\
+   &\Mid\ \text{or}\ \langle\text{type}\rangle \langle\text{type}\rangle \\
+   &\Mid\ \text{lambda}\ \langle\text{type}\rangle \langle\text{type}\rangle \\
+   &\Mid\ \text{map}\ \langle\text{comparable type}\rangle \langle\text{type}\rangle \\
+   &\Mid\ \text{big-map}\ \langle\text{comparable type}\rangle \langle\text{type}\rangle \\
+   &\Mid\ \text{bls12-381-g1} \\
+   &\Mid\ \text{bls12-381-g2} \\
+   &\Mid\ \text{bls12-381-fr} \\
+   &\Mid\ \text{sapling-transaction}\ \langle\text{natural number constant}\rangle \\
+   &\Mid\ \text{sapling-state}\ \langle\text{natural number constant}\rangle \\
+   &\Mid\ \text{chest} \\
+   &\Mid\ \text{chest-key} \\
+\langle\text{comparable type}\rangle ::= \\
+   &\Mid\ \text{unit} \\
+   &\Mid\ \text{never} \\
+   &\Mid\ \text{bool} \\
+   &\Mid\ \text{int}\\
+   &\Mid\ \text{nat}\\
+   &\Mid\ \text{string}\\
+   &\Mid\ \text{chain-id}\\
+   &\Mid\ \text{bytes}\\
+   &\Mid\ \text{mutez}\\
+   &\Mid\ \text{key-hash}\\
+   &\Mid\ \text{key}\\
+   &\Mid\ \text{signature}\\
+   &\Mid\ \text{timestamp}\\
+   &\Mid\ \text{address}\\
+   &\Mid\ \text{tx-rollup-l2-address}\\
+   &\Mid\ \text{option}\ \langle\text{comparable type}\rangle\\
+   &\Mid\ \text{or}\ \langle\text{comparable type}\rangle \langle\text{comparable type}\rangle\\
+   &\Mid\ \text{pair}\ \langle\text{comparable type}\rangle \langle\text{comparable type}\rangle \DOT \\
+\end{align*}
+\caption{Types}
+\label{fig:type}
+\end{figure}
+Each piece of data in Michelson is assigned a specific type, and the language restricts programmers from introducing custom types.
+The complete list of types can be found in Figure \ref{fig:type}.
+To model the system, we use a stack in which each element is a pair consisting of term and its corresponding type.
+Terms are defined in Figure \ref{fig:term}.
+The stack is denoted as \STACK\ = (\TermOne, \TYF) \STACKCONCAT\ (\TermTwo, \TYS) \STACKCONCAT\ \DOT\ \STACKCONCAT\ \EMPTYSTACK\ where elements are types paired with terms.
 
@@
 Each instruction takes, as input, the stack produced by the preceding instruction and modifies it for the subsequent one.
-This sequential flow ensures that each instruction builds upon the state left by its predecessor in the program.
-Let $\INSTRUCTION = \InstructionOne; \InstructionTwo; \DOT; \InstructionN$ represent a sequence of instructions.
-
-While undergoing symbolic execution,  a symbolic execution state assumes different values based on the constraints of symbolic values.
-Additionally, branching may occur depending on conditions, and both constraints and branching conditions are recorded as predicates.
-Let \PREDICATE\ symbolize a predicate expressed in conjunction form, capturing the conditions and constraints encountered during the symbolic execution process.
+Let \INSTRUCTION\ = \InstructionOne; \InstructionTwo; \DOT\  \InstructionN\ represent a sequence of instructions.
+During symbolic execution,  the system state evolves, assuming different values based on the constraints of symbolic values.
+Moreover, branching may occur depending on conditions, and both constraints and branching conditions are recorded as predicates.
+Let \PREDICATE\ symbolize a predicate expressed in conjunction form, capturing the branching conditions and constraints encountered during the symbolic execution process.
 \begin{definition}
-A symbolic execution's state is represented by the tuple $\STATE = [\INSTRUCTION, \STACK, \PREDICATE]$. Here, $\SYSTEM = \{\STATEONE, \STATETWO, \DOT, \STATEN \}$ range over sets of  states.
+A symbolic execution state is represented by the tuple \STATE\ = [\INSTRUCTION, \STACK, \PREDICATE]. Here, \SYSTEM\ = \{\STATEONE, \STATETWO, \DOT, \STATEN \} range over sets of  states.
 \end{definition}
-The Michelson program takes as input a stack that consists of a single pair whose first element is an input value referred to as the parameter, and second element represents the content of the storage space.
-The program produces a stack as output, containing a single pair.
-The first element of this pair is the list of internal operations that the program intends to emit, and the second element is the new contents of the storage space.
-
-Define the initial stack as $S_{init}$   = (\KPAIR\ \VPAR\ \VSTORAGE, \TPAIR\ \TYF\ \TYS) \STACKCONCAT\EMPTYSTACK, where \VPAR\ and \VSTORAGE\ denote terms representing the parameter and the storage, and \TYF\ and \TYS\ are their corresponding types.
-Similarly, designate the final stack as $S_{final}$   = (\PAIR\ \VOPERATIONLIST\ \VSTORAGE, \TPAIR\ (\TOPERATIONLIST) \TYS) \STACKCONCAT\EMPTYSTACK, where \VOPERATIONLIST\ repesents a operation list.
-
-%\paragraph{Sequence actions.}
-%\begin{figure}[h]
-%\center
-%\includegraphics[width= 10 cm]{life-cycle-1}
-%\caption{Life-cycle for the auction contract.}
-%\label{fca1}
-%\end{figure}
-
-\pagebreak
+
+The smart contract program takes a stack as input, consisting of a single pair where the first element is an input value referred to as parameter denoted as \VPAR and the second element represents the content of the storage space denoted as \VSTORAGE.
+The program produces a stack as output, which is a single pair.
+The first element of this pair is the list of internal operations that the program intends to emit (\VOPERATIONLIST), and the second element is the new contents of the storage space.
+Let's define the initial stack as  \SINIT\   = (\KPAIR\ \VPAR\ \VSTORAGE, \TPAIR\ \TYF\ \TYS) \STACKCONCAT\ \EMPTYSTACK, where \VPAR\ and \VSTORAGE\ denote terms representing the parameter and the storage, and \TYF\ and \TYS\ are their corresponding types.
+Similarly, designate the final stack as \SFINAL\   = (\PAIR\ \VOPERATIONLIST\ \VSTORAGE, \TPAIR\ (\TOPERATIONLIST) \TYS) \STACKCONCAT\ \EMPTYSTACK, where \VOPERATIONLIST\ repesents a operation list.
+\begin{figure}[]
+\begin{align*}
+\text{t} &::= \\
+   &\Mid\ \langle \text{variable} \rangle \\
+   &\Mid\ \langle \text{account constant} \rangle \\
+   &\Mid\ \langle \text{int constant} \rangle \\
+   &\Mid\ \langle \text{string constant} \rangle \\
+   &\Mid\ \langle \text{byte sequence constant} \rangle \\
+   &\Mid\ \UNIT \\
+   &\Mid\ \NEVER \\
+   &\Mid\ \TRUE \\
+   &\Mid\ \FALSE \\
+   &\Mid\ \PAIR\ \text{t1 t2}\\
+   &\Mid\ \LEFT\ \text{t}\\
+   &\Mid\ \RIGHT\ \text{t}\\ 
+   &\Mid\ \SOME\ \text{t}\\
+   &\Mid\ \NONE \\
+   &\Mid\ \text{\{t ; ... \}}\\
+   &\Mid\ \text{\{ Elt t1 t2 ; ... \}}\\
+   &\Mid\ \{ \langle\text{instruction}\rangle; ... \}   \\
+\langle \text{variable} \rangle &::= \\ 
+   &\Mid\ \VAR\\
+\langle \text{account constant} \rangle &::= \\ 
+   &\Mid\ \text{balance} \\
+   &\Mid\ \text{amount} \\
+   &\Mid\ \text{sender} \\
+   &\Mid\ \text{source} \\
+   &\Mid\ \text{now} \\
+   &\Mid\ \text{level} \\
+   &\Mid\ \text{chain-id} \\
+   &\Mid\ \text{self}  \\
+   &\Mid\ \text{self-address}  \\
+   &\Mid\ \text{total-voting-power}  \\
+   &\Mid\ \text{voting-power}  \\
+\langle\text{instruction}\rangle &::= \\
+  &\Mid\ \DROP \\
+  &\Mid\ \DROP \langle\text{natural number constant}\rangle \\
+  &\text{...}
+\end{align*}
+\caption{Terms}
+\label{fig:term}
+\end{figure}
 \subsection{Rules}
-
 Each instruction is defined by a rule on the system model. The rule semantic is defined by several kinds of transitions:
@@
 
-During the execution of symbolic analysis, numberous states are generated.
-However, certain states may be unreachable from a symbolic initial state.
-This occurs when the predicate \PREDICATE\ is unsatisfied.
-Consequently, a system state is disregarded when the predicate \PREDICATE\ is fail.
+During the symbolic execution, numerous states are generated, but some may be unreachable from a symbolic initial state.
+This happens when the predicate \PREDICATE\ is unsatisfied, leading to the exclusion of a system state where the predicate fails.
 
@@
 \end{mathpar}
-
-There are various types of instructions in Michelson, categorized based on their functions.
-These include control structures, stack manipulation, arithmetic operations, boolean operations, cryptographic operations, and operations on data structures.
-In our model, we classify them into three main groups: basic instructions, branch instructions, and loop instructions.
+Michelson instructions are categorized based on their functions.
+These include such as control structures, stack manipulation, arithmetic operations, boolean operations, cryptographic operations, and operations on data structures.
+In our model, we classified them as one-step, multi-step, blockchain, cryptographic, branch, and loop instructions.
 This categorization reflects how these instructions are handled within our specific model.
 \subsubsection{One-step Instructions}
-A one-step instruction only effects a system state itself, does not produce a new state, and halts the execution after a single operation.
-The ABS rule specifies the corresponding instruction that applies to the first element of the stack.
-This element must have the type of int and returns the positive value of its current value, which is of a natural number type.
-Another example, the COMPARE instruction compares the two first elements of a stack, both of which have a natural number type.
-It returns a result of either -1, 0, or 1 depending on the comperations of their values.
+One-step instructions have a localized effect, modifying the system state directly without branching a new state, and they end the execution after a single operation.
+The ABS rule exemplifies such an instruction, operating on the first element of the stack.
+This element must be of type int, and the instruction returns the positive value of its current value, treated as a natural number.
 %ABS
@@
     \PREDICATE]
-    \StateTrans \
+    \StateTrans 
     [\INSTRUCTION, (\VariableX, \TNAT) \STACKCONCAT \STACK,
@@
 \end{mathpar}
-
+Another example is the COMPARE instruction for natural numbers, which compares the first two elements of the stack, both having a natural number type.
+It returns a result of either -1, 0, or 1 based on the comparison of their values.
 % COMPARE
@@
 \subsubsection{Multi-step Instructions}
-Multi-step instructions require the execution of a sub-sequence of instructions before returning to the main execution.
-The following rule models the instruction EXEC, which executes a function specified as a sequence of instructions denoted as \INSTRUCTIONONE\ in the rule.
-This instruction first applies the code of the function to the first element of the stack.
-It then places the result back into the main execution.
-\begin{mathpar}
-  \inferrule[EXEC]
+Multi-step instructions involve the execution of a sub-sequence of instructions before returning to the main execution.
+The rule below models the \EXEC\ instruction, which executes a function specified as a sequence of instructions denoted by \INSTRUCTIONONE\ in the rule.
+This instruction applies the code of the function to the first element of the stack and then places the result back into the main execution.
+\begin{mathpar}
+  \inferrule[\EXEC]
   {
@@
 The Michelson language incorporates conditional branching, enabling the execution of specific code segments based on certain criteria.
-One of the instructions facilitating this is the IF {} {} construct.
-For example, the \IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO\ instruction allows the creation of branches in execution.
+One of the instructions facilitating this is the \IF\ \{\} \{\} construct.
+For example, the \IF\ \{ \INSTRUCTIONONE\ \} \{ \INSTRUCTIONTWO\  \} instruction allows the creation of branches in execution.
 It takes two sequences as arguments.
@@
 \begin{mathpar}
-  \inferrule[IF]
-  {  
-  }{
-    \{[(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]\} \cup \SYSTEM 
-      \SystemTrans 
-    \{[\INSTRUCTIONONE, \STACK, \PREDICATE\ \Wedge\ \StackOne]\} \cup \{ [\INSTRUCTIONTWO, \STACK, \PREDICATE\ \Wedge\ \NEG\
-   \StackOne]\} \cup  \SYSTEM
-  }
-\end{mathpar}
-
-The \IFLEFT\ \INSTRUCTIONONE\  \INSTRUCTIONTWO\ instruction expects a or value at the top of the stack, it consumes this top element.
-If the value is Left, it executes the first provided sequence; otherwise, it executes the second sequence.
-%IF-LEFT
-\begin{mathpar}
-  \inferrule[IF-LEFT]
-  {  
-  }{
-    \{[(\IFLEFT\ \INSTRUCTIONONE\ \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]\}  \cup  \SYSTEM
-    \SystemTrans \\
-    \{[\INSTRUCTIONONE, (\VariableX, \TYF) \STACKCONCAT\STACK,
-    \PREDICATE \wedge (\StackOne\ \EQUAL\ \LEFT\ \VariableX)]\}  \cup  \{  [\INSTRUCTIONTWO, (\VariableX, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQUAL\ \RIGHT\ \VariableX))]\} \cup \SYSTEM
-  }
-\end{mathpar}
+  \inferrule[IF-true]
+  {  
+  }{
+    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
+    \StateTrans\
+    [\INSTRUCTIONONE, \STACK, \PREDICATE\ \Wedge\ \StackOne]
+  }
+
+  \inferrule[IF-false]
+  {  
+  }{
+    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
+    \StateTrans\
+   [\INSTRUCTIONTWO, \STACK, \PREDICATE\ \Wedge\ \NEG\
+   \StackOne]
+ }
+\end{mathpar}
+
+Another branch instruction is the IF-LEFT instruction, which is used for conditional execution based on the left or right branch of a tagged union (sum) type. 
+%IF-LEFT-LEFT
+\begin{mathpar}
+  \inferrule[IF-LEFT-left]
+  {  
+  }{
+    [(\IFLEFT\ \INSTRUCTIONONE\ \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]
+    \StateTrans \
+    [\INSTRUCTIONONE, (\VariableX, \TYF) \STACKCONCAT\STACK,
+    \PREDICATE \wedge (\StackOne\ \EQUAL\ \LEFT\ \VariableX)]
+  }
+\end{mathpar}
+
+%IF-LEFT-RIGHT
+\begin{mathpar}
+  \inferrule[IF-LEFT-right]
+  {  
+  }{
+    [(\IFLEFT\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]
+    \StateTrans \
+    [\INSTRUCTIONTWO, (\VariableX, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQUAL\ \RIGHT\ \VariableX))]
+  }
+\end{mathpar}
+These above rules collectively define the behavior of the IF-LEFT instruction based on the left or right branch of a tagged union type.
+This rule applies when the top element of the stack is a tagged union of type \TOR\ \TYF\ \TYS (either of type \TYF or \TYS), and the IF-LEFT instruction is followed by instructions \INSTRUCTIONONE\ and \INSTRUCTIONTWO.
+The first rule apply with the condition that the top element of the stack is of the form Left \VariableX\ (indicating the left branch of the union), it transitions to execute the instructions \INSTRUCTIONONE\ with the stack modified accordingly and the predicate is updated to include the condition that the top element of the stack is equal to Left \VariableX.
+Similerly, The second rule apply with the condition that  the top element is of the form Right \VariableX (indicating the right branch of the union), it transitions to execute the instructions \INSTRUCTIONTWO with the stack modified accordingly and the predicate is updated to include the condition that the top element of the stack is equal to Right \VariableX.
 
 \subsubsection{Loop Instructions}
-In Michelson, there are several loop instructions that execute a loop over the data structure, such as ITER, MAP, MEMBER, SIZE and UPDATE on list, set, map or on the stack, such as LOOP and LOOP-LEFT.
-
+Loops represent fundamental and powerful programming constructs.
+In computer programming, a loop is an instruction that iteratively executes a set of statements until a specific condition is met.
+In a loop structure, the program poses a question, and if the answer necessitates action, the associated code is executed.
+This questioning and execution process repeats until the condition is no longer met.
+Each iteration of this cycle is referred to as an iteration of the loop.
+In Michelson, various loop instructions facilitate the iteration over data structures, allowing for the manipulation and traversal of different data structures within the language.
+These loop instructions, including ITER, MAP, MEMBER, UPDATE, LOOP, and LOOP-LEFT, are designed for operations on lists, sets, maps, and the stack itself.
+Similar to other programming languages, Michelson categorizes loop instructions into two main types:
+\begin{itemize}
+\item[] "For" loops: there are sequence-based loops, such as ITER.
+\item[] "While" loops: these are predicates-based loops, illustrated by LOOP and LOOP-LEFT.
+\end{itemize}
+To illustrate the structures of  loops in Michelson, we can draw a parallel with OCaml syntax:
+\begin{verbatim}
+while <loop_condition> do
+   <loop_body>
+done
+\end{verbatim}
+This "while" loop structure involves a loop condition that is evaluated at the beginning of each iteration.
+If the condition holds true, the loop body is executed, and the process repeats until the condition becomes false.
+In Michelson, this pattern is evident in instructions like LOOP and LOOP-LEFT, which rely on predicate-based conditions for their iteration.
+\begin{verbatim}
+LOOP {<loop-body>}
+\end{verbatim}
+Additionally, Michelson features a "For" loop, where the index runs from the initial value to the final value:
+\begin{verbatim}
+for index = <initial_value> to <final_value> do
+  <loop_body>
+done
+\end{verbatim}
+This is represented by the ITER instruction:
+\begin{verbatim}
+ITER {<loop-body>}
+\end{verbatim}
+The fundamental concept underlying the definition of a loop is its loop condition, which is the predicate that must hold true for the loop to continue execution.
+In the case of while loops, the  loop condition is explicitly embedded in the loop syntax.
+In the case of for loops, the loop condition is more implicit.
+It can be rewritten as a while loop to make the  loop condition explicit.
+This "For" loop structure can also be expressed as a "while" loop:
+\begin{verbatim}
+index = 0
+while index < length(sequence) do
+  <loop_body>
+  index += 1
+done
+\end{verbatim}
+Here, the implicit loop condition asserts that the index of our sequence element is less than the length of the sequence.
+
+It's worth noting that, unlike imperative-style loops, Michelson does not explicitly contain their  loop condition. Instead, the  loop condition is established:
+\begin{itemize}
+ \item In the expressions preceding the loop for the first time entering the loop.
+ \item Inside the loop body for subsequent iterations.
+\end{itemize}
+
+The loop instructions in Michelson are applied to a stack, and the loop condition is checked with the first element of the stack.
+For a "while" loop the first element of the stack must be a boolean value and for the "for" loop, it must be a sequence data that the loop support, such as list, set and map.
+If we denote the function to retrieve the first element of a stack as "pop," the "while" loop instruction can be expressed as:
+\begin{verbatim}
+while pop(S) do
+   loop_body
+done
+\end{verbatim}
+and the "for" instruction is expressed as
+\begin{verbatim}
+index = 0
+while index < length(pop(S)) do
+  <loop_body>
+  index += 1
+done
+\end{verbatim}
+
+Certainly, let's continue exploring how these loop constructs are modeled in the symbolic execution. 
+\paragraph {\ITER}
+Consider the \ITER\ instruction for lists, which operates on a stack \STACK.
+Here, the top element of the stack has type (\TY\ \TYLIST), and the rest of the stack has type \TYA.
+The instruction returns a result stack of type \TYA.
+The \ITER\ instruction iterates over the data structure list.
+The corresponding typing rule is as follows:
+\begin{mathpar}
+  \inferrule{\JTypeExpr\TEnv{\INSTRUCTION}{\TY : \TYA\ \SRightarrow\ \TYA}
+  }{
+      \JTypeExpr\TEnv{\ITER\ \INSTRUCTION}{\TYLIST\ \TY : \TYA\ \SRightarrow\ \TYA}
+    }
+\end{mathpar}
+This typing rule ensures that if the loop body (\INSTRUCTION) has the type \TY\ : \TYA\ \SRightarrow\ \TYA, then the entire \ITER\ instruction, when applied to a stack with the top element of type (\TY\ \TYLIST) and the rest of the stack of type \TYA, produces a result stack of type \TYA.
+This facilitates symbolic iteration over a list while maintaining compatibility with further symbolic execution.
+
+We delve into the symbolic execution of \ITER\ when the list is a symbolic term.
 %%ITER
@@
 \end{mathpar}
-
+This rule handles the case where the list is empty, and thus the \ITER\ instruction does not iterate.
+The resulting state transitions to the next instruction with an updated stack that is actually the same as before entering the \ITER\ intruction and an augmented predicate \PREDICATE $\Wedge$ (\StackOne \EQUAL \EMPTYLIST).
 \begin{mathpar}
@@
 \end{mathpar}
-
-Let us consider the \ITER\ instruction (for list), which applies to a stack \STACK, where the top element has type  (\TY\ \TYLIST) and the rest of the stack has type \TYA, returns the result stack of type \TYA.
-The \ITER\ instruction loops on the datastructure list.
-Typing
-\begin{mathpar}
-  \inferrule{\JTypeExpr\TEnv{\INSTRUCTION}{\TY : \TYA\ \SRightarrow\ \TYA}
-  }{
-      \JTypeExpr\TEnv{\ITER\ \INSTRUCTION}{\TYLIST\ \TY : \TYA\ \SRightarrow\ \TYA}
-    }
-\end{mathpar}
-
-Semantic
-
-\begin{mathpar}
-  \inferrule{
-  }{
-    \ITER\ \INSTRUCTION\ / \{ \} \STACKCONCAT\ \STACK\ \SRightarrow\  \STACK
-    }
-\end{mathpar}
-
-\begin{mathpar} 
-  \inferrule{\INSTRUCTION\  /  \VariableX\ \STACKCONCAT\ \STACK \SRightarrow\ \STACK'
-  }{
-    \ITER\ \INSTRUCTION\ / \{ \VariableX\ ; \TAIL\ \} \STACKCONCAT\ \STACK\ \SRightarrow\ \ITER\ \INSTRUCTION\ / \{ \TAIL\ \} \STACKCONCAT\ \STACK' 
-    }
-\end{mathpar}
-
-If a list \LIST\ is concrete, the intructuion simply loops until the list ends with an empty list construction.
-Here we consider the synbolic execution of \ITER\ when the list is a sybolic term or variable.
-
-The sequence of intructuions I is a lamda function  (\TLAMBDA\ (\TY\ : \TYA)\ \TYA) applied to the stack of type (\TY\ : \TYA), returning the stack of type \TYA.
-We can represent I as the function f that takes an element of type \TY\ and a stack of type \TYA\ and returns a stack of type \TYA.
-
-\begin{mathpar}
-  f : \TY\  \TYA\ \SRightarrow\ \TYA
-\end{mathpar}
-
-\begin{mathpar}
-  f  \VariableX\ \STACK =  (\TLAMBDA\ (\TY\ : \TYA)\ \TYA) (\VariableX\  \STACKCONCAT\ \STACK)
-\end{mathpar}
-
-or
-
-\begin{mathpar}
-  f  \VariableX\ \STACK = I / (\VariableX\  \STACKCONCAT\ \STACK)
-\end{mathpar}
-
-Let  
-\LIST\ \STACKCONCAT\ \STACK
-
- be the stack just before applying the instruction ITER I, where \VariableX\ be the head of the list and \STACK\ be the rest of the stack .
-For first  loop, let  \STACK\ be f (\VariableX, \STACK).
-\STACK\ is the stack resulting from applying the function f to the element \VariableX\ and the stack \STACK.
-In other words, the stack \STACK\ is formed by applying the sequence of the instructions I to the stack \VariableX\ \STACKCONCAT\ \STACK.
-
-Let the result of applying the instruction \ITER\ I on the stack \LIST\ ::  \STACK\ be the stack S', then Z is resulted from the \FOLD\ function that applies the function f  to each element of the list \LIST\ and initial value is the stack \STACK.
-
-\begin{mathpar}
-S' =  \FOLD\ \STACK\ f   \LIST
-\end{mathpar}
-
+This rule handles the case where the list is non-empty.
+It symbolically executes the instructions \INSTRUCTIONONE\ within the \ITER\ block with the head of the list (\HEAD) removed from the stack and a subpart of the predicate Q.
+The resulting state transitions to a new stack (\STACK') and an updated predicate (\PREDICATE\ $\Wedge$ Q' $\Wedge$ (\StackOne \EQUAL \{\HEAD;\STAIL\}), where \{\STAIL\} represents the rest of the list.
+In summery, These rules capture the symbolic execution behavior of the \ITER\ instruction, considering both the cases where the list is empty and non-empty.
+
+When the sequence (list, set, map) is empty, the \ITER\ loop halts.
+Otherwise, it continues to execute its loop body, which applies to an element value of the list.
+For example, if a list \LIST\ is concrete, the instruction simply loops until the list ends with an empty list construction.
+The question arises: how do we deal with it symbolically when the list is a symbolic value?
+One solution could involve running the loop for a number of times to obtain the symbolic value.
+However, we aim for the result value to express the loop body more efficiently in a mathematical way and be capable of performing property checks.
+
+Let again consider the instruction \ITER \{ \INSTRUCTION\ \}.
+Semantically, \INSTRUCTION\ denote the loop body, which is a sequence of instructions.
+In fact, the sequence of instructions, \INSTRUCTION, represents a lambda function lambda (\TY\ : \TYA\ \SRightarrow\ \TYA) applied to a stack of type \TY:\TYA, resulting in a stack of type \TYA.
+Assuming that the first element of the stack is a list and  it is a non-empty.
+Then the list is in the form  \{\HEAD; \STAIL \}, and the rest of the stack is \STACKZERO\ = \StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ ...
+\STACKCONCAT\ \StackN.
+Then the \ITER\ \{ \INSTRUCTION\ \} instruction apply \M\ time of function \INSTRUCTION\ to the stack with each element  \HEADI\ of the list, where \M\ is the length of list.
+The result after the fist loop is \STACKONE\ = \StackOneOne\  \STACKCONCAT\ \StackTwoOne\ \STACKCONCAT\ ...
+\STACKCONCAT\ \StackNOne.
+Note that the type of the result stack must be the same as the prevoud stack.
+Let us assume that the element \I\ of the stack  \STACK\ has the type \TYI.
+Let the function  \FI\ that takes the head of the list and all elements of  the stack \STACKZERO\ as  \StackOne, \StackTwo, ...
+\StackN, donated  as \STACKZEROBAR\ and returns the i-element  \StackIOne\ of the stack \STACKONE.
+The lambda function is defined as a set of these subfunctions \FI.
+\begin{mathpar}
+\StackOneOne\ = \FOne\  \HEADZERO\ \STACKZEROBAR \\
+\StackTwoOne\ = \FTwo\  \HEADZERO\ \STACKZEROBAR \\
+...\\
+\StackNOne\ = \FN\  \HEADZERO\ \STACKZEROBAR 
+\end{mathpar}
+When the next loop is performed, the same function \FI\ is applied to the next element of the list and all element of the the stack \STACKONE\ and we get the \StackITwo.
+In the same way, the the loop is performed for \J\ time, we get the stack \STACKJ\ as follows:
+
+\begin{mathpar}
+\StackOneJ\ = \FOne\  \HEADJMINUS\ \STACKJMINUSBAR \\
+\StackTwoJ\ = \FTwo\  \HEADJMINUS\ \STACKJMINUSBAR \\
+...\\
+\StackNJ\ = \FN\  \HEADJMINUS\ \STACKJMINUSBAR 
+\end{mathpar}
+
+As result, we can reprensed the value of the stack after running the instruction \ITER\  as the result of a fold function that apply the function \FI\ to the list l with the inital value is \StackOneZero, \StackTwoZero, ...
+\StackNZero.
+\begin{mathpar}
+\StackOneM\ = \FOLD\ \FOne\ \STACKZEROBAR\  \LIST\  \\
+\StackTwoM\ = \FOLD\ \FTwo\  \STACKZEROBAR\ \LIST\  \\
+...\\
+\StackNM\ = \FOLD\ \FN\ \STACKZEROBAR\  \LIST
+\end{mathpar}
+
+Generally, we can represent the sequence of instructions \INSTRUCTION\ as the function \F\ that takes an element of type \TY\ of a list \LIST\ and a  stack \STACK\ of type \TYA\ and returns a stack of type \TYA.
+
+\begin{mathpar}
+\STACK'\ =  \FOLD\ \F\ \STACK\ \LIST
+\end{mathpar}
+
+Let consider an example \ITER\ \{ \ADD\ \} that apply to a stack \STACK\ that has a integer list as the top element and the rest \STACKZERO: 
+\begin{mathpar}
+\ITER\ \{ \ADD\ \} / \LIST\ \STACKCONCAT\ \STACKZERO
+\end{mathpar}
+Assumming that \STACKZERO\ = \StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ ...
+\STACKCONCAT\ \StackN.
+For the requirement of the \ADD\ instruction, the top element of the stack \STACKZERO, namely \StackOne, need to have the interger type.
+Let build the function \FOne.
+Assuming that the list \LIST\ is not empty as \{\HEAD; \STAIL \}, For each loop \ADD\ instruction adds each element of the list to the top element of the stack and then the rest of the stack is unchanged.
+\begin{mathpar}
+\FOne\ (\HEAD, \StackOne,  \StackTwo, ..., \StackN) = \HEAD\ + \StackOne\\
+\FTwo\ (\HEAD, \StackOne,  \StackTwo, ..., \StackN) = \StackTwo\\
+... \\
+\FN\ (\HEAD, \StackOne,  \StackTwo, ..., \StackN) = \StackN\\
+\end{mathpar}
+
+The function \FOne\ is the fucntion that take (\N\ + 1) intergers as inputs and result the sum of two first one 
+\begin{mathpar}
+\FOne\ (\X, \XOne, \XTwo, ..., \XN) = \X\ + \XOne
+\end{mathpar}
+since \XTwo, ..., \XN do not paricipaint in the calculation, we can omit them as
+\begin{mathpar}
+\FOne\ (\X, \XOne) = \X\ + \XOne
+\end{mathpar}
+The result of the first element of the stack after the \ITER\ \{ \ADD\ \} loop is.
+\begin{mathpar}
+\FOLD\ \FOne\ \StackOne\ \LIST
+\end{mathpar}
+Because the loop does not change the rest of the stack, for all funtion \FI\ for the element \StackI\ of the stack \STACK\ could consider as a identy function
+\begin{mathpar}
+\FI\ (\X, \XOne, ..., \XI, ..., \XN) = \XI
+\end{mathpar}
+So we can omit them in the implementation.
+
+The \FOLD\ function also can be used to symbolicly the result of other "for" loop intructions on sequence data structure such as CONCAT or SIZE.
+
+\paragraph {\MAP}
+The \ITER\ instruction and some other can be symbolicly implemented using \FOLD\ function applying on the sequance data structures as list, set and map.
+Let consider the \MAP\ instruction, where we can use a map function to symbolic the result of the instruction.
+Consider the  \MAP\ \{ \I \}   instruction for lists, which operates on a stack \STACK.
+Here, the top element of the stack has type (\TY\ \TYLIST), and the rest of the stack has type \TYA.
+The instruction returns a result stack of type (\TY\ \TYLIST) : \TYA.
+The \MAP\ instruction iterates over the data structure list.
+The corresponding typing rule is as follows:
+\begin{mathpar}
+  \inferrule{\JTypeExpr\TEnv{\INSTRUCTION}{\TY  \SRightarrow\ \TY'}
+  }{
+      \JTypeExpr\TEnv{\MAP\ \INSTRUCTION}{\TYLIST\ \TY : \TYA\ \SRightarrow\ \TYLIST\ \TY' : \TYA}
+    }
+\end{mathpar}
+This typing rule ensures that if the loop body (\INSTRUCTION) has the type \TY\ \SRightarrow\ \TY', then the entire \ITER\ instruction, when applied to a stack with the top element of type (\TY\ \TYLIST) and the rest of the stack of type \TYA, produces a result stack of type \TYLIST\ \TY' : \TYA.
+ The follow is the rules for the map intruction that apply to a list. 
 %MAP
@@
 \end{mathpar}
+
+now let consider how can we syboliclly the execution of the \MAP\ instruction.
+The list of instruction \I\ can be repeseted as a function \F\ that takes a input of type \TY\ and return an output of type \TY'.
+\begin{mathpar}
+\F\ : \TY\ \SRightarrow\ \TY
+\end{mathpar}
+The \MAP\ instruction loops on the list \LIST\ by applying the function \F\ to each element of the list \LIST.
+Symbolilly the result of the \MAP\ \{ \I \} to the list \LIST\ is the result of a map function  that apply the fucntion \F\ that represent of the sequence of instructions \I\ to the list.
+
+\begin{mathpar}
+\MAP\ \{ \I \} / \LIST\ :: \STACK\ \SRightarrow\ (map \F\ \LIST) ::  \STACK
+\end{mathpar}
+
+Consider the example as MAP \{ PUSH int 1; ADD \}, which apply to a stack with have a list of intergers \LIST\ as a top elemnt of the stack.
+The function expressed as \{ PUSH int 1; ADD \} basiclly adds the number 1 to each element of the list.
+For this kind of instruction the same technical could be apply.
+Let f is the function that is specified as the sequcne of instruction \I.
+f take a element of type int and returen another elemnt of type int
+
+\begin{mathpar}
+\F\ : \TINT \SRightarrow\ \TINT. \\
+\F\ \X\ = \X\ + 1 
+\end{mathpar}
+then the result of the loop is a stack with a list at the top whis have simbolic value as \FMAP\ \F\ \l. 
+\paragraph {\LOOP}
+Now let consider an example of the while loop, namely the \LOOP\ instruction that is a while loop.
+The \LOOP\ \{ \I\ \} intruction apply to a stack \STACK\ that has the top element is a boolean type.
+If a top element is true then and only then the loop body (\I) is executed.
+After the body of a loop is executed then control again goes back at the top element, and checked if it is true, the same process is executed until the top element becomes false.
+Once the value of the top element becomes false, the control goes out of the loop.
+The loop condition is calucated by the loop body and the result  back to the firt elevemnt of the stack.
+\begin{mathpar}
+  \inferrule{\JTypeExpr\TEnv{\INSTRUCTION}{\TYA  \SRightarrow\ \TBOOL\ : \TYA}
+  }{
+      \JTypeExpr\TEnv{\MAP\ \INSTRUCTION}{\TYLIST\ \TBOOL\ : \TYA\ \SRightarrow\ \TYA}
+    }
+\end{mathpar}
+
+The rules for \LOOP\ instruction.
 
@@
 \end{mathpar}
-
+ let \STACKZERO\ =  \StackZero\ \STACKCONCAT\ \StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ ...
+\STACKCONCAT\ \StackN, where  has the boolean type.
+Let \FI\ is the function that takes the top elemement of the stack and the rest of \N\ elements of the stack, which have types \TYF, \TYS, ...\TYI, ...\TYN\ noted as \TYABAR\ and return a single type of the element \I.
+\begin{mathpar}
+\FZero\ : \TBOOL\ \SRightarrow\  \TBOOL. \\
+... \\
+\FI\ : \TBOOL\ \TYF, \TYS, ...\TYI, ...\TYN\  \SRightarrow\  \TYI. \\
+....
+\end{mathpar}
+
+\begin{mathpar}
+\FZero\  \StackZero\ \StackOne\ ... \StackI\ ... \StackN\ =   \StackZeroOne. \\
+... \\
+\FI\  \StackZero\ \StackOne\ ... \StackI\ ... \StackN\ =   \StackIOne. \\
+....
+\end{mathpar}
 \subsubsection{FAILWITH}
@@
 \section {Domain Specific Language}
+Michelson, being a stack-based language, may be less familiar to many developers compared to popular languages like Python, Java, or C.
+To bridge this gap, several high-level languages such as LIGO, SmartPy, and Liquidity have been developed.
+These languages enable developers to write Tezos smart contracts in a more readable manner, resembling popular programming languages.
+Contracts written in these languages are then compiled down to Michelson.
+
+In addition, Tezos users, who don't have much knowleage about Michelson language may wish to verify smart contract code before deployment.
+Our framework aims to provide a tool that doesn't require users to be Michelson experts.
+We intend to design a domain-specific language that enables users to specify smart contract properties in a mathematical way, making it readable and easy  to understand.
+
+Given that our framework utilizes an SMT solver, specifically Z3, for property verification, we offer a language that allows users to express formulas compatible with the capabilities of the SMT solver (Z3).
+This empowers users to write formulas that the solver can effectively handle for property verification.
+
+One of the main challenges with formal verification is that it ofen requires the specifier to express the program code in a specification language.
+This poses two problems: it demands expertise in formal verification from the specifier and introduces a gap between the actual code and its specification.
+In our framework, this gap is eliminated as the exact Michelson code used for verification precisely corresponds to the real code.
+Users are not required to be formal verification experts.
+The necessary Michelson knowledge revolves around understanding data types and their usage when calling a smart contract on the Tezos blockchain, both as parameters and in storage.
+
+The grama of the DLS is as follows:
+
+\begin{verbatim}
+MContract ‘NAME' with
+Code := c
+Input := t1
+Output := t20
+Pre-condition := c1
+Post-condition := c2
+\end{verbatim}
+
+Where "MContract", "with", Code, Input, Output, Pre-condition and Post-condition are keywords.
+NAME is preplaced by the user contract name, we prpect to the capital to make it impressive clear.
+The c is repeced with the Michosonl contract code.
+in the input and output fild is to specify the input and ourpout paterm.
+Since Miachonl work on a stack.
+The input of the code should be a stack.
+As a real smart contract.
+Here assume that the stack have only one element as speicfy in the input partan and similarly th eoutput stack is the stack with only one element which is specified in output.
+For a real michesol smart contract code.
+The output have be a pair of operation list and a storage then the output is prepesent by the store in the storage after the execution is finished.
+
 \section {Static Checker}
+
 \section {Case Studies}
@@
 \end{figure}
+
 \subsubsection{Basic Instructions}
@@
 %IF
-\begin{mathpar}
-  \inferrule[IF-true]
-  {  
-  }{
-    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
-    \StateTrans\
-    [\INSTRUCTIONONE, \STACK, \PREDICATE\ \Wedge\ \StackOne]
-  }
-
-  \inferrule[IF-false]
-  {  
-  }{
-    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
-    \StateTrans\
-   [\INSTRUCTIONTWO, \STACK, \PREDICATE\ \Wedge\ \NEG\
-   \StackOne]
- }
-\end{mathpar}
-
-%IF-LEFT-LEFT
-\begin{mathpar}
-  \inferrule[IF-LEFT-left]
-  {  
-  }{
-    [(\IFLEFT\ \INSTRUCTIONONE\ \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]
-    \StateTrans \
-    [\INSTRUCTIONONE, (\VariableX, \TYF) \STACKCONCAT\STACK,
-    \PREDICATE \wedge (\StackOne\ \EQUAL\ \LEFT\ \VariableX)]
-  }
-\end{mathpar}
-
-%IF-LEFT-RIGHT
-\begin{mathpar}
-  \inferrule[IF-LEFT-right]
-  {  
-  }{
-    [(\IFLEFT\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]
-    \StateTrans \
-    [\INSTRUCTIONTWO, (\VariableX, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQUAL\ \RIGHT\ \VariableX))]
-  }
-\end{mathpar}
-
+
+\begin{mathpar}
+  \inferrule[IF]
+  {  
+  }{
+    \{[(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]\} \cup \SYSTEM 
+      \SystemTrans 
+    \{[\INSTRUCTIONONE, \STACK, \PREDICATE\ \Wedge\ \StackOne]\} \cup \{ [\INSTRUCTIONTWO, \STACK, \PREDICATE\ \Wedge\ \NEG\
+   \StackOne]\} \cup  \SYSTEM
+  }
+\end{mathpar}
+
+The \IFLEFT\ \INSTRUCTIONONE\  \INSTRUCTIONTWO\ instruction expects a or value at the top of the stack, it consumes this top element.
+If the value is Left, it executes the first provided sequence; otherwise, it executes the second sequence.
+%IF-LEFT
+\begin{mathpar}
+  \inferrule[IF-LEFT]
+  {  
+  }{
+    \{[(\IFLEFT\ \INSTRUCTIONONE\ \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]\}  \cup  \SYSTEM
+    \SystemTrans \\
+    \{[\INSTRUCTIONONE, (\VariableX, \TYF) \STACKCONCAT\STACK,
+    \PREDICATE \wedge (\StackOne\ \EQUAL\ \LEFT\ \VariableX)]\}  \cup  \{  [\INSTRUCTIONTWO, (\VariableX, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQUAL\ \RIGHT\ \VariableX))]\} \cup \SYSTEM
+  }
+\end{mathpar}
 %IF_CONS
@@
 \subsubsection{For loop: ITER}
+Semantic
+
+\begin{mathpar}
+  \inferrule{
+  }{
+    \ITER\ \INSTRUCTION\ / \{ \} \STACKCONCAT\ \STACK\ \SRightarrow\  \STACK
+    }
+\end{mathpar}
+
+\begin{mathpar} 
+  \inferrule{\INSTRUCTION\  /  \VariableX\ \STACKCONCAT\ \STACK \SRightarrow\ \STACK'
+  }{
+    \ITER\ \INSTRUCTION\ / \{ \VariableX\ ; \TAIL\ \} \STACKCONCAT\ \STACK\ \SRightarrow\ \ITER\ \INSTRUCTION\ / \{ \TAIL\ \} \STACKCONCAT\ \STACK' 
+    }
+\end{mathpar}
 \subsubsection{While loops: \LOOP\ and \LOOP-LEFT}

### 2023-12-07 papers/static-checker/ecoop2024/ecoop2024.tex
Update the loop section

@@
 For example, the AMOUNT instruction adds to the stack the amount of tokens that sent together with the transcation which calls this smart contract.
-Here, the amount is modeled as a symbolic value donated as \VAMOUNT, which has \TMUTEZ\ type, which is a positive number value.
+Here, the amount is modeled as a symbolic value donated as \VAMOUNT, which has \TMUTEZ\ type, which has a nature number value.
 
@@
 These above rules collectively define the behavior of the IF-LEFT instruction based on the left or right branch of a tagged union type.
-This rule applies when the top element of the stack is a tagged union of type \TOR\ \TYF\ \TYS (either of type \TYF or \TYS), and the IF-LEFT instruction is followed by instructions \INSTRUCTIONONE\ and \INSTRUCTIONTWO.
+This rule applies when the top element of the stack is a tagged union of type \TOR\ \TYF\ \TYS (either of type \TYF\ or \TYS), and the IF-LEFT instruction is followed by instructions \INSTRUCTIONONE\ and \INSTRUCTIONTWO.
 The first rule apply with the condition that the top element of the stack is of the form Left \VariableX\ (indicating the left branch of the union), it transitions to execute the instructions \INSTRUCTIONONE\ with the stack modified accordingly and the predicate is updated to include the condition that the top element of the stack is equal to Left \VariableX.
-Similerly, The second rule apply with the condition that  the top element is of the form Right \VariableX (indicating the right branch of the union), it transitions to execute the instructions \INSTRUCTIONTWO with the stack modified accordingly and the predicate is updated to include the condition that the top element of the stack is equal to Right \VariableX.
+Similerly, the second rule apply with the condition that  the top element is of the form Right \VariableX\ (indicating the right branch of the union), it transitions to execute the instructions \INSTRUCTIONTWO\ with the stack modified accordingly and the predicate is updated to include the condition that the top element of the stack is equal to Right \VariableX.
 
 \subsubsection{Loop Instructions}
-Loops represent fundamental and powerful programming constructs.
-In computer programming, a loop is an instruction that iteratively executes a set of statements until a specific condition is met.
-In a loop structure, the program poses a question, and if the answer necessitates action, the associated code is executed.
-This questioning and execution process repeats until the condition is no longer met.
-Each iteration of this cycle is referred to as an iteration of the loop.
-In Michelson, various loop instructions facilitate the iteration over data structures, allowing for the manipulation and traversal of different data structures within the language.
-These loop instructions, including ITER, MAP, MEMBER, UPDATE, LOOP, and LOOP-LEFT, are designed for operations on lists, sets, maps, and the stack itself.
-Similar to other programming languages, Michelson categorizes loop instructions into two main types:
+In Michelson, loops are fundamental constructs that repeatedly execute a set of instructions until a specific condition is met.
+There are various loop instructions, including ITER, MAP, CONCAT, SIZE, LOOP, and LOOP-LEFT, enable the manipulation and traversal of different data structures like lists, sets, maps, and the stack itself.
+
+Michelson, similar to other programming languages, classifies loop instructions into two main types:
 \begin{itemize}
-\item[] "For" loops: there are sequence-based loops, such as ITER.
-\item[] "While" loops: these are predicates-based loops, illustrated by LOOP and LOOP-LEFT.
+\item \KFOR\ loops: These are sequence-based loops, exemplified by ITER, MAP, CONCAT and SIZE.
+\item \KWHILE\ loops: These are predicates-based loops, illustrated by LOOP and LOOP-LEFT.
 \end{itemize}
-To illustrate the structures of  loops in Michelson, we can draw a parallel with OCaml syntax:
+To illustrate the structures of  loops, we can draw a parallel with OCaml syntax:
 \begin{verbatim}
@@
 \end{verbatim}
-This "while" loop structure involves a loop condition that is evaluated at the beginning of each iteration.
+This \KWHILE\  loop structure involves a loop condition that is evaluated at the beginning of each iteration.
 If the condition holds true, the loop body is executed, and the process repeats until the condition becomes false.
@@
 \end{verbatim}
-Additionally, Michelson features a "For" loop, where the index runs from the initial value to the final value:
+Additionally, Michelson features a \KFOR\ loop, where the index runs from the initial value to the final value:
 \begin{verbatim}
@@
 \end{verbatim}
-The fundamental concept underlying the definition of a loop is its loop condition, which is the predicate that must hold true for the loop to continue execution.
-In the case of while loops, the  loop condition is explicitly embedded in the loop syntax.
-In the case of for loops, the loop condition is more implicit.
-It can be rewritten as a while loop to make the  loop condition explicit.
-This "For" loop structure can also be expressed as a "while" loop:
+
+The fundamental concept underlying the definition of a loop is its loop condition, the predicate that must hold true for the loop to continue execution.
+In the case of \KWHILE\ loops, the  loop condition is explicitly embedded in the loop syntax.
+However, for the \KFOR\  loops, the loop condition is more implicit.
+A \KFOR\  loop can be rewritten as a  \KWHILE\ loop to make the  loop condition explicit:
 \begin{verbatim}
@@
 \end{verbatim}
-Here, the implicit loop condition asserts that the index of our sequence element is less than the length of the sequence.
-
-It's worth noting that, unlike imperative-style loops, Michelson does not explicitly contain their  loop condition. Instead, the  loop condition is established:
+Here, the implicit loop condition asserts that the index of the sequence element is less than the length of the sequence.
+
+It's important  to note that, unlike imperative-style loops, Michelson loop instructions do not explicitly contain their loop conditions. Instead, the  loop condition is established:
 \begin{itemize}
@@
 
-The loop instructions in Michelson are applied to a stack, and the loop condition is checked with the first element of the stack.
-For a "while" loop the first element of the stack must be a boolean value and for the "for" loop, it must be a sequence data that the loop support, such as list, set and map.
-If we denote the function to retrieve the first element of a stack as "pop," the "while" loop instruction can be expressed as:
+The loop instructions are applied to a stack, and the loop condition is checked with the top element of the stack.
+For a  \KWHILE\ loop the top element of the stack must have a boolean value and for the \KFOR\  loop, it must have a sequence data type, such as list, set or map.
+If we denote the function to retrieve the top element of a stack as "\FPOP," the  \KWHILE\ loop instruction can be expressed as:
 \begin{verbatim}
@@
 \end{verbatim}
-and the "for" instruction is expressed as
+and the \KFOR\  loop is expressed as:
 \begin{verbatim}
@@
 
-Certainly, let's continue exploring how these loop constructs are modeled in the symbolic execution. 
+Certainly, let's continue exploring how these loop constructs are modeled in our symbolic execution. 
 \paragraph {\ITER}
-Consider the \ITER\ instruction for lists, which operates on a stack \STACK.
-Here, the top element of the stack has type (\TY\ \TYLIST), and the rest of the stack has type \TYA.
-The instruction returns a result stack of type \TYA.
-The \ITER\ instruction iterates over the data structure list.
-The corresponding typing rule is as follows:
+Lets us consider the \ITER\ instruction, which iterates over the \TYLIST\ data structure. The corresponding typing rule is as follows:
 \begin{mathpar}
@@
 \end{mathpar}
-This typing rule ensures that if the loop body (\INSTRUCTION) has the type \TY\ : \TYA\ \SRightarrow\ \TYA, then the entire \ITER\ instruction, when applied to a stack with the top element of type (\TY\ \TYLIST) and the rest of the stack of type \TYA, produces a result stack of type \TYA.
+This typing rule ensures that if the loop body \INSTRUCTION\ has the type \TY\ : \TYA\ \SRightarrow\ \TYA, then the entire \ITER\ instruction, when applied to a stack with the top element of type \TY\ \TYLIST\ and the rest of the stack of type \TYA, produces a result stack of type \TYA.
 This facilitates symbolic iteration over a list while maintaining compatibility with further symbolic execution.
 
-We delve into the symbolic execution of \ITER\ when the list is a symbolic term.
+We delve into the symbolic execution of \ITER\ instruction when the list is a symbolic term.
 %%ITER
@@
 This rule handles the case where the list is empty, and thus the \ITER\ instruction does not iterate.
-The resulting state transitions to the next instruction with an updated stack that is actually the same as before entering the \ITER\ intruction and an augmented predicate \PREDICATE $\Wedge$ (\StackOne \EQUAL \EMPTYLIST).
+The resulting state transitions to the next instruction with an updated stack that is actually the same as before entering the \ITER\ intruction and an augmented predicate \PREDICATE\ $\Wedge$ (\StackOne \EQUAL \EMPTYLIST).
 \begin{mathpar}
@@
 \end{mathpar}
-This rule handles the case where the list is non-empty.
+The next rule handles the case where the list is non-empty.
 It symbolically executes the instructions \INSTRUCTIONONE\ within the \ITER\ block with the head of the list (\HEAD) removed from the stack and a subpart of the predicate Q.
 The resulting state transitions to a new stack (\STACK') and an updated predicate (\PREDICATE\ $\Wedge$ Q' $\Wedge$ (\StackOne \EQUAL \{\HEAD;\STAIL\}), where \{\STAIL\} represents the rest of the list.
-In summery, These rules capture the symbolic execution behavior of the \ITER\ instruction, considering both the cases where the list is empty and non-empty.
+In summery, these rules capture the symbolic execution behavior of the \ITER\ instruction, considering both the cases where the list is empty and non-empty.
 
 When the sequence (list, set, map) is empty, the \ITER\ loop halts.
-Otherwise, it continues to execute its loop body, which applies to an element value of the list.
-For example, if a list \LIST\ is concrete, the instruction simply loops until the list ends with an empty list construction.
+Otherwise, it continues to execute its loop body, which applies to an element of the list.
+If a list \LIST\ is concrete, the instruction simply loops until the list ends with an empty list construction.
 The question arises: how do we deal with it symbolically when the list is a symbolic value?
@@
 
-Let again consider the instruction \ITER \{ \INSTRUCTION\ \}.
+Let again consider the instruction \ITER\ \{\INSTRUCTION\}.
 Semantically, \INSTRUCTION\ denote the loop body, which is a sequence of instructions.
-In fact, the sequence of instructions, \INSTRUCTION, represents a lambda function lambda (\TY\ : \TYA\ \SRightarrow\ \TYA) applied to a stack of type \TY:\TYA, resulting in a stack of type \TYA.
+In fact, the sequence of instructions, \INSTRUCTION, represents a lambda function lambda (\TY\ : \TYA\ \SRightarrow\ \TYA) applied to a stack of type \TY\ :\TYA, resulting in a stack of type \TYA.
 Assuming that the first element of the stack is a list and  it is a non-empty.
@@
 \STACKCONCAT\ \StackN.
-Then the \ITER\ \{ \INSTRUCTION\ \} instruction apply \M\ time of function \INSTRUCTION\ to the stack with each element  \HEADI\ of the list, where \M\ is the length of list.
+Then the \ITER\ \{\INSTRUCTION\} instruction apply \M\ time of function representing \INSTRUCTION\ to the stack with each element  \HEADI\ of the list, where \M\ is the length of list.
 The result after the fist loop is \STACKONE\ = \StackOneOne\  \STACKCONCAT\ \StackTwoOne\ \STACKCONCAT\ ...
@@
 Let us assume that the element \I\ of the stack  \STACK\ has the type \TYI.
-Let the function  \FI\ that takes the head of the list and all elements of  the stack \STACKZERO\ as  \StackOne, \StackTwo, ...
+Let the function  \FI\ that takes the head \HEADZERO\ of the list and all elements of  the stack \STACKZERO\ as  \StackOne, \StackTwo, ...
 \StackN, donated  as \STACKZEROBAR\ and returns the i-element  \StackIOne\ of the stack \STACKONE.
-The lambda function is defined as a set of these subfunctions \FI.
+The function representing \INSTRUCTION\  is defined as a set of these subfunctions \FI.
 \begin{mathpar}
@@
 
-As result, we can reprensed the value of the stack after running the instruction \ITER\  as the result of a fold function that apply the function \FI\ to the list l with the inital value is \StackOneZero, \StackTwoZero, ...
-\StackNZero.
+As result, we can reprensed the value of the stack after running the instruction \ITER\  as the result of a fold function that apply the function \FI\ to the list l with the inital value is \StackOne, \StackTwo, ...
+\StackN\ as \STACKZEROBAR.
 \begin{mathpar}
@@
 
-Let consider an example \ITER\ \{ \ADD\ \} that apply to a stack \STACK\ that has a integer list as the top element and the rest \STACKZERO: 
+Let consider an example \ITER\ \{\ADD\} that applies to a stack \STACK\ that has a integer list as the top element and the rest \STACKZERO\ = \StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ ...
+\STACKCONCAT\ \StackN.
 \begin{mathpar}
@@
 \end{mathpar}
-Assumming that \STACKZERO\ = \StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ ...
-\STACKCONCAT\ \StackN.
-For the requirement of the \ADD\ instruction, the top element of the stack \STACKZERO, namely \StackOne, need to have the interger type.
-Let build the function \FOne.
-Assuming that the list \LIST\ is not empty as \{\HEAD; \STAIL \}, For each loop \ADD\ instruction adds each element of the list to the top element of the stack and then the rest of the stack is unchanged.
-\begin{mathpar}
-\FOne\ (\HEAD, \StackOne,  \StackTwo, ..., \StackN) = \HEAD\ + \StackOne\\
-\FTwo\ (\HEAD, \StackOne,  \StackTwo, ..., \StackN) = \StackTwo\\
+Because of the requirement of the \ADD\ instruction, the top element of the stack \STACKZERO, namely \StackOne, need to have the interger type.
+For each loop \ADD\ instruction adds each element of the list to the top element of the stack and then the rest of the stack is unchanged.
+Let build the function \FOne\ with the assumtion that the list \LIST\ is not empty as \{\HEAD; \STAIL \},
+\begin{mathpar}
+\FOne\ (\HEAD, \StackOne,  \StackTwo, \DOT, \StackN) = \HEAD\ + \StackOne\\
+\FTwo\ (\HEAD, \StackOne,  \StackTwo, \DOT, \StackN) = \StackTwo\\
 ... \\
-\FN\ (\HEAD, \StackOne,  \StackTwo, ..., \StackN) = \StackN\\
+\FN\ (\HEAD, \StackOne,  \StackTwo, \DOT, \StackN) = \StackN\\
 \end{mathpar}
@@
 \begin{mathpar}
-\FOne\ (\X, \XOne, \XTwo, ..., \XN) = \X\ + \XOne
-\end{mathpar}
-since \XTwo, ..., \XN do not paricipaint in the calculation, we can omit them as
+\FOne\ (\X, \XOne, \XTwo, \DOT, \XN) = \X\ + \XOne
+\end{mathpar}
+since \XTwo, \DOT, \XN\ do not paricipaint in the calculation, we can omit them as
 \begin{mathpar}
@@
 \end{mathpar}
-The result of the first element of the stack after the \ITER\ \{ \ADD\ \} loop is.
+The symbolic value of the top element of the stack after the \ITER\ \{\ADD\} loop is.
 \begin{mathpar}
@@
 \end{mathpar}
-Because the loop does not change the rest of the stack, for all funtion \FI\ for the element \StackI\ of the stack \STACK\ could consider as a identy function
-\begin{mathpar}
-\FI\ (\X, \XOne, ..., \XI, ..., \XN) = \XI
-\end{mathpar}
-So we can omit them in the implementation.
-
-The \FOLD\ function also can be used to symbolicly the result of other "for" loop intructions on sequence data structure such as CONCAT or SIZE.
+Because the loop does not change the rest of the stack, for all funtion \FI\ for the element \StackI\ of the stack \STACK\ could consider as an identy function, and then we can omit them in the implementation.
+\begin{mathpar}
+\FI\ (\X, \XOne, \DOT, \XI, \DOT, \XN) = \XI
+\end{mathpar}
+
+The \FOLD\ function also can be used to symbolicly the result of other \KFOR\ loop intructions, such as CONCAT and SIZE.
 
@@
 Let consider the \MAP\ instruction, where we can use a map function to symbolic the result of the instruction.
-Consider the  \MAP\ \{ \I \}   instruction for lists, which operates on a stack \STACK.
-Here, the top element of the stack has type (\TY\ \TYLIST), and the rest of the stack has type \TYA.
-The instruction returns a result stack of type (\TY\ \TYLIST) : \TYA.
-The \MAP\ instruction iterates over the data structure list.
+Consider the  \MAP\ \{\I\}   instruction for lists, which operates on a stack \STACK, whose the top element has type \TY\ \TYLIST, and the rest has type \TYA.
+The instruction returns a stack of type (\TY\ \TYLIST) : \TYA.
 The corresponding typing rule is as follows:
@@
   }{
-      \JTypeExpr\TEnv{\MAP\ \INSTRUCTION}{\TYLIST\ \TY : \TYA\ \SRightarrow\ \TYLIST\ \TY' : \TYA}
-    }
-\end{mathpar}
-This typing rule ensures that if the loop body (\INSTRUCTION) has the type \TY\ \SRightarrow\ \TY', then the entire \ITER\ instruction, when applied to a stack with the top element of type (\TY\ \TYLIST) and the rest of the stack of type \TYA, produces a result stack of type \TYLIST\ \TY' : \TYA.
- The follow is the rules for the map intruction that apply to a list. 
+      \JTypeExpr\TEnv{\MAP\ \INSTRUCTION}{\ \TY\ \TYLIST\ : \TYA\ \SRightarrow\ \TY'\ \TYLIST\  : \TYA}
+    }
+\end{mathpar}
+This typing rule ensures that if the loop body (\INSTRUCTION) has the type \TY\ \SRightarrow\ \TY', then the entire \ITER\ instruction produces a result stack of type \TY' \ \TYLIST\ : \TYA. 
 %MAP
@@
 \end{mathpar}
-
-now let consider how can we syboliclly the execution of the \MAP\ instruction.
-The list of instruction \I\ can be repeseted as a function \F\ that takes a input of type \TY\ and return an output of type \TY'.
+Let consider how can we syboliclly the execution of the \MAP\ instruction.
+The list of instruction \INSTRUCTION\ can be repeseted as a function \F\ that takes a input of type \TY\ and return an output of type \TY'.
 \begin{mathpar}
@@
 The \MAP\ instruction loops on the list \LIST\ by applying the function \F\ to each element of the list \LIST.
-Symbolilly the result of the \MAP\ \{ \I \} to the list \LIST\ is the result of a map function  that apply the fucntion \F\ that represent of the sequence of instructions \I\ to the list.
-
-\begin{mathpar}
-\MAP\ \{ \I \} / \LIST\ :: \STACK\ \SRightarrow\ (map \F\ \LIST) ::  \STACK
-\end{mathpar}
-
-Consider the example as MAP \{ PUSH int 1; ADD \}, which apply to a stack with have a list of intergers \LIST\ as a top elemnt of the stack.
+Symbolilly the result of the \MAP\ \{\INSTRUCTION\} to the list \LIST\ is the result of a map function  that apply the fucntion \F\ that represent of the sequence of instructions \I\ to the list.
+
+\begin{mathpar}
+\MAP\ \{\INSTRUCTION\} \Slash\ \LIST\ :: \STACK\ \SRightarrow\ (\FMAP\ \F\ \LIST) ::  \STACK
+\end{mathpar}
+
+Consider the example as MAP \{ PUSH int 1; ADD \}, which applies to a stack with have a list of intergers \LIST\ as the top elemnt of the stack.
 The function expressed as \{ PUSH int 1; ADD \} basiclly adds the number 1 to each element of the list.
-For this kind of instruction the same technical could be apply.
-Let f is the function that is specified as the sequcne of instruction \I.
-f take a element of type int and returen another elemnt of type int
-
+Let \F\ is the function that is specified as the sequcne of instruction \I.
+\F\ takes an element of type int and returen another elemnt of type int
 \begin{mathpar}
@@
 \end{mathpar}
-then the result of the loop is a stack with a list at the top whis have simbolic value as \FMAP\ \F\ \l. 
+Then the result of the loop is a stack which has a interger list at the top whose simbolic value is \FMAP\ \F\ \l.
+
 \paragraph {\LOOP}
@@
   }{
-      \JTypeExpr\TEnv{\MAP\ \INSTRUCTION}{\TYLIST\ \TBOOL\ : \TYA\ \SRightarrow\ \TYA}
+      \JTypeExpr\TEnv{\MAP\ \INSTRUCTION}{\TBOOL\ : \TYA\ \SRightarrow\ \TYA}
     }
@@
 \end{mathpar}
- let \STACKZERO\ =  \StackZero\ \STACKCONCAT\ \StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ ...
-\STACKCONCAT\ \StackN, where  has the boolean type.
-Let \FI\ is the function that takes the top elemement of the stack and the rest of \N\ elements of the stack, which have types \TYF, \TYS, ...\TYI, ...\TYN\ noted as \TYABAR\ and return a single type of the element \I.
+ let \STACKZERO\ =  \StackZero\ \STACKCONCAT\ \StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ \DOT \STACKCONCAT\ \StackN, where  has the boolean type.
+Let \FI\ is the function that takes the top elemement of the stack and the rest of \N\ elements of the stack, which have types \TYF, \TYS, \DOT\ \TYI, \DOT\ \TYN\ noted as \TYABAR\ and return a single type of the element \I.
 \begin{mathpar}
 \FZero\ : \TBOOL\ \SRightarrow\  \TBOOL. \\
-... \\
-\FI\ : \TBOOL\ \TYF, \TYS, ...\TYI, ...\TYN\  \SRightarrow\  \TYI. \\
-....
-\end{mathpar}
-
-\begin{mathpar}
-\FZero\  \StackZero\ \StackOne\ ... \StackI\ ... \StackN\ =   \StackZeroOne. \\
-... \\
-\FI\  \StackZero\ \StackOne\ ... \StackI\ ... \StackN\ =   \StackIOne. \\
-....
+\DOT \\
+\FI\ : \TBOOL\ \TYF, \TYS, \DOT\ \TYI, \DOT\ \TYN\  \SRightarrow\  \TYI. \\
+\DOT
+\end{mathpar}
+
+\begin{mathpar}
+\FZero\  \StackZero\ \StackOne\ \DOT\ \StackI\ \DOT\ \StackN\ =   \StackZeroOne. \\
+\DOT\ \\
+\FI\  \StackZero\ \StackOne\ \DOT\ \StackI\ \DOT\ \StackN\ =   \StackIOne. \\
+\DOT
 \end{mathpar}
 \subsubsection{FAILWITH}
-a Michelson program can fail, explicitly using a specific opcode
+A Michelson program can fail, explicitly using a specific opcode
 

### 2023-12-07 papers/static-checker/ecoop2024/ecoop2024.tex
update dsl section

@@
 \section {Domain Specific Language}
-Michelson, being a stack-based language, may be less familiar to many developers compared to popular languages like Python, Java, or C.
-To bridge this gap, several high-level languages such as LIGO, SmartPy, and Liquidity have been developed.
-These languages enable developers to write Tezos smart contracts in a more readable manner, resembling popular programming languages.
-Contracts written in these languages are then compiled down to Michelson.
-
-In addition, Tezos users, who don't have much knowleage about Michelson language may wish to verify smart contract code before deployment.
-Our framework aims to provide a tool that doesn't require users to be Michelson experts.
-We intend to design a domain-specific language that enables users to specify smart contract properties in a mathematical way, making it readable and easy  to understand.
-
-Given that our framework utilizes an SMT solver, specifically Z3, for property verification, we offer a language that allows users to express formulas compatible with the capabilities of the SMT solver (Z3).
-This empowers users to write formulas that the solver can effectively handle for property verification.
-
-One of the main challenges with formal verification is that it ofen requires the specifier to express the program code in a specification language.
+Michelson, as a stack-based language, may pose a challenge for developers less familiar with it compared to more mainstream languages like Python, Java, or C.
+To address this, several high-level languages such as LIGO, SmartPy, and Liquidity have been created.
+These languages provide a more readable syntax, resembling popular programming languages, allowing developers to write Tezos smart contracts more comfortably.
+These high-level contracts are then compiled down to Michelson.
+
+For Tezos users who may lack expertise in Michelson, there is a desire to verify smart contract code before interaction.
+Our framework addresses this by introducing a domain-specific language (DSL) that facilitates the specification of smart contract properties in a mathematical and readable format.
+The goal is to create a language that is accessible and easily understandable, even for users who are not Michelson experts.
+
+To achieve this, our framework employs an SMT solver, specifically Z3, for property verification.
+The DSL is designed to allow users to express formulas that align with the capabilities of the SMT solver (Z3).
+This empowers users to write formulas that the solver can effectively handle, facilitating property verification in a more user-friendly manner.
+
+One of the main challenges with formal verification is that it ofen requires the users to specify the system in a specification language.
 This poses two problems: it demands expertise in formal verification from the specifier and introduces a gap between the actual code and its specification.

### 2023-12-08 papers/static-checker/ecoop2024/ecoop2024.tex
update DSL section

@@
 \label{sec:introduction}
-
+Symbolic execution techniques encounter challenges related to state explosion, particularly when applied to large systems.
+Fortunately, the constraints of storing and running smart contracts on a blockchain platform impose size limitations, making them manageable for symbolic execution.
+
+In this work, we present the design of a domain-specific language for specifying smart contract properties and demonstrate the integration of symbolic execution with an SMT solver for formal verification of these properties.
 \section{Symbolic Execution Model}
@@
 Moreover, branching may occur depending on conditions, and both constraints and branching conditions are recorded as predicates.
-Let \PREDICATE\ symbolize a predicate expressed in conjunction form, capturing the branching conditions and constraints encountered during the symbolic execution process.
+Let \PREDICATE\ is a path predicate that is extended at each conditional and expressed in conjunction form, capturing the branching conditions and constraints encountered during the symbolic execution process.
 \begin{definition}
@@
 \subsubsection{FAILWITH}
-A Michelson program can fail, explicitly using a specific opcode
+A Michelson program can fail, employing a designated opcode. The \FAILWITH\ instruction aborts the ongoing program and reveals the top element of the stack.
 
@@
   {
-  }{[(\FAILWITH; \INSTRUCTION), (\StackOne,  \TY) \STACKCONCAT \STACK,  \PREDICATE] \StateTrans [\EMPTYSTACK, failwith (\StackOne) \STACKCONCAT\EMPTYSTACK, \PREDICATE]}
-\end{mathpar}
-\section {Domain Specific Language}
+  }{[(\FAILWITH; \INSTRUCTION), (\StackOne,  \TY) \STACKCONCAT \STACK,  \PREDICATE] \StateTrans [\EMPTYSTACK, (\FAIL\ (\StackOne)) \STACKCONCAT\EMPTYSTACK, \PREDICATE]}
+\end{mathpar}
+\section {Domain Specific Language For Smart Contract Property Specification}
 Michelson, as a stack-based language, may pose a challenge for developers less familiar with it compared to more mainstream languages like Python, Java, or C.
@@
 
-One of the main challenges with formal verification is that it ofen requires the users to specify the system in a specification language.
+One of the main challenges with formal verification is that it is often the requirement for users to express the system in a specialized specification language.
 This poses two problems: it demands expertise in formal verification from the specifier and introduces a gap between the actual code and its specification.
-In our framework, this gap is eliminated as the exact Michelson code used for verification precisely corresponds to the real code.
-Users are not required to be formal verification experts.
-The necessary Michelson knowledge revolves around understanding data types and their usage when calling a smart contract on the Tezos blockchain, both as parameters and in storage.
-
-The grama of the DLS is as follows:
-
+In our framework, this gap is eliminated as the exact Michelson code used for verification precisely corresponds to the actual code.
+Users are not obligated to possess formal verification expertise.
+
+The Michelson code, readily available on the Tezos blockchain, remains consistent across various high-level language platforms like LIGO, SmartPy, and Liquidity, all of which offer functions to compile programs into Michelson.
+This approach eliminates the need for users to be formal verification experts.
+The essential Michelson knowledge revolves around understanding data types and their usage when interacting with a smart contract on the Tezos blockchain, whether as parameters or in storage.
+
+Given a smart contract code c, the syntax of our property specification language is as follows: 
 \begin{verbatim}
-MContract ‘NAME' with
-Code := c
-Input := t1
-Output := t20
-Pre-condition := c1
-Post-condition := c2
+MContract ‘Name' with
+Code := {c}
+Input := t
+Output := t'
+Pre-condition := cd
+Post-condition := cd'
 \end{verbatim} 
-
-Where "MContract", "with", Code, Input, Output, Pre-condition and Post-condition are keywords.
-NAME is preplaced by the user contract name, we prpect to the capital to make it impressive clear.
-The c is repeced with the Michosonl contract code.
-in the input and output fild is to specify the input and ourpout paterm.
-Since Miachonl work on a stack.
-The input of the code should be a stack.
-As a real smart contract.
-Here assume that the stack have only one element as speicfy in the input partan and similarly th eoutput stack is the stack with only one element which is specified in output.
-For a real michesol smart contract code.
-The output have be a pair of operation list and a storage then the output is prepesent by the store in the storage after the execution is finished.
+Here, \KMCONTRACT, \KWITH, \KCODE, \KINPUT, \KOUTPUT, \KPRECONDI, and \KPOSTCONDI are keywords.
+The 'Name' is replaced by the contract name.
+In the input and output fields, the input and output patterns are specified.
+Since Michelson operates on a stack, we assume that the stack has only one element, as specified in the input pattern.
+Similarly, the output stack is assumed to be a stack with only one element, which is specified in the output field.
+As we have mentioned before, the output should be a pair consisting of an operation list and a storage.
+In our syntax, for verification purpose, we omit the operation list and then the output is represented by the patern of the value in the storage after the execution is finished.
+
+The input and output patterns represent Michelson terms, which can be either concrete values or symbolic values, including variables.
+When a variable appears for the first time, it needs to be accompanied by its corresponding type declaration.
+However, subsequent mentions can omit the type declaration.
+Formally, the pre and post-condition instances are formulas in first-order logic, and they can be handled by an SMT solver, namely the Z3 solver in our framework.
+The detail of the language grammar is described in in Figure \ref{}.
+
+Let's consider the following example of the property specification for the contract named Add:
+\begin{verbatim}
+MContract ‘Add' with
+Code := {UNPAIR; COMPARE; GE; 
+        IF {ADD}{PUSH string 'Unexpected pair'; FAILWITH}}
+Input := Pair (x : int) (y : int)
+Output := (z : int)
+Pre-condition := (x >= 5) | (y >= 3)
+Post-condition := (z >= 8)
+\end{verbatim}
+Here, the program takes as input a stack with only one element, which is a pair of two integers, symbolically specified in the Input field.
+It then unpairs the input pair to obtain two elements as two integers \VariableX\ and \VariableY.
+It then proceeds to destructure the input pair, yielding two integers, denoted as \VariableX\ and \VariableY.
+Subsequently, the program performs a comparison between these two integers.
+If \VariableX\ is greater than or equal to \VariableY, the program constructs a new stack with a solitary element at the top representing the sum of \VariableX\ and \VariableY, designated as \VariableZ.
+Otherwise, the execution terminates with an error message containing the content 'Unexpected pair.' The specification continues by defining pre and post conditions, where the precondition states the assumption that the integer \VariableX\ is greater than or equal to 5 and \VariableY\ is greater than or equal to 3.
+The postcondition asserts that the result sum \VariableZ\ is greater than or equal to 8.
 
 \section {Static Checker}
-
+Formulas that are used in assertions or added to solvers are terms of Boolean sort.
+Otherwise, terms of Boolean and non-Boolean sort may be mixed in any combination where sorts match up.
+Universal and existential quantifiers bind variables to the scope of the quantified formula.
 \section {Case Studies}

### 2023-12-12 papers/static-checker/ecoop2024/ecoop2024.tex
Write DSL section

@@
 \begin{itemize}
-\item[]  \EMPTYSTACK\ represents the empty stack.
-\item[]  \HEAD\ \STACKCONCAT\ \NTAIL\ denotes a stack with the top element as \HEAD\ and the remaining stack as \NTAIL.
+\item[]  \ensuremath{[\ ]} represents the empty stack.
+\item[]  \ensuremath{hd :: tl} denotes a stack with the top element as \ensuremath{hd} and the remaining stack as \ensuremath{tl}.
 \end{itemize}
@@
 \item \ExprTrans\ single-step evaluation of an expression in a system state,
-\item \StateTrans\ internal transitions of a state, which is non-deterministic  as shown for loop instructions, such as \LOOP\ and \LOOP-LEFT,
+\item \StateTrans\ internal transitions of a state, which is non-deterministic  as shown for loop instructions, such as \LOOP\ and \LOOPLEFT,
 \item \SystemTrans\ symbolic system transitions.
@@
     \PREDICATE]
-    \StateTrans 
-    [\INSTRUCTION, (\VariableX, \TNAT) \STACKCONCAT \STACK,
-    \PREDICATE \wedge (\StackOne \ge 0 \Rightarrow \VariableX =
-    \StackOne) \wedge (\StackOne <0 \Rightarrow \VariableX = -\StackOne)]
- }
-\end{mathpar}
-Another example is the COMPARE instruction for natural numbers, which compares the first two elements of the stack, both having a natural number type.
+    \StateTrans \\
+    [\INSTRUCTION, (\X, \TNAT) \STACKCONCAT \STACK,
+    \PREDICATE\ \wedge\ (\StackOne\ \GE\ \ZERO\ \Rightarrow\ \X\ =
+    \StackOne) \wedge\ (\StackOne\ \LT\ \ZERO\ \Rightarrow\ \X\ = \MINUS\ \StackOne)]
+ }
+\end{mathpar}
+Another example is the \COMPARE\ instruction for natural numbers, which compares the first two elements of the stack, both having a natural number type.
 It returns a result of either -1, 0, or 1 based on the comparison of their values.
@@
     \SystemTrans \\
-    [\INSTRUCTION, (\VariableX, \TINT) \STACKCONCAT \STACK, \PREDICATE
-    \wedge\ (\StackOne > \StackTwo \Leftrightarrow \VariableX = 1)
-    \wedge\ (\StackOne = \StackTwo \Leftrightarrow \VariableX = 0) 
-    \wedge\ (\StackOne < \StackTwo \Leftrightarrow \VariableX = -1)]
+    [\INSTRUCTION, (\X, \TINT) \STACKCONCAT \STACK, \PREDICATE
+    \wedge\ (\StackOne\ \GT\ \StackTwo\ \Leftrightarrow\ \X\ \EQ\ \ONE)
+    \wedge\ (\StackOne\ \EQ\ \StackTwo\ \Leftrightarrow\ \X\ \EQ\ \ZERO) 
+    \wedge\ (\StackOne\ \LT\ \StackTwo\ \Leftrightarrow\ \X\ \EQ\ \MINUS \ONE)]
     }
@@
     [\INSTRUCTIONONE, (\StackOne, \TYF) \STACKCONCAT \EMPTYSTACK, 
-    Q]
+    \Q]
     \StateTrans^*
-    [ \EMPTYSTACK, (\StackOne', \TYS) \STACKCONCAT Q']
+    [ \EMPTYSTACK, (\StackOne', \TYS) \STACKCONCAT \Q']
   }{
      [(\EXEC; \INSTRUCTION),   (\{\INSTRUCTIONONE\}, \TYF\ \rightarrow\ \TYS) \STACKCONCAT
-    (\StackOne, \TYF) \STACKCONCAT \STACK, \PREDICATE \wedge Q] 
+    (\StackOne, \TYF) \STACKCONCAT \STACK, \PREDICATE \wedge \Q] 
     \StateTrans \
     [ \INSTRUCTION, (\StackOne', \TYS) \STACKCONCAT \STACK,
-    \PREDICATE \wedge Q']}
+    \PREDICATE \wedge \Q']}
 \end{mathpar}
@@
   { 
-     \FLEN(\A) \EQUAL\ \N \\ [\INSTRUCTIONONE,  \B, Q]
+     \FLEN(\A) \EQ\ \N \\ [\INSTRUCTIONONE,  \B, \Q]
     \StateTrans^*
-    [\EMPTYSTACK,  \B_1, Q']
-  }
-  {[(\DIP\ \N\ \INSTRUCTIONONE; \INSTRUCTION), \A\ \At\ \B, \PREDICATE \wedge Q] \StateTrans 
-[(\INSTRUCTION), \A\ \At\ \B_1, \PREDICATE \wedge Q']}
+    [\EMPTYSTACK,  \B_1, \Q']
+  }
+  {[(\DIP\ \N\ \INSTRUCTIONONE; \INSTRUCTION), \A\ \At\ \B, \PREDICATE \wedge \Q] \StateTrans 
+[(\INSTRUCTION), \A\ \At\ \B_1, \PREDICATE \wedge \Q']}
 \end{mathpar}
@@
 We model these data as symbolic values, which satisfis some constrants.
-For example, the AMOUNT instruction adds to the stack the amount of tokens that sent together with the transcation which calls this smart contract.
-Here, the amount is modeled as a symbolic value donated as \VAMOUNT, which has \TMUTEZ\ type, which has a nature number value.
+For example, the \AMOUNT\ instruction adds to the stack the amount of tokens that sent together with the transcation which calls this smart contract.
+Here, the amount is modeled as a symbolic value donated as \CAMOUNT, which has \TMUTEZ\ type, which has a nature number value.
 
@@
   {[(\AMOUNT; \INSTRUCTION), \STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\VAMOUNT, \TMUTEZ) \STACKCONCAT\STACK, \PREDICATE}
+[\INSTRUCTION, (\CAMOUNT, \TMUTEZ) \STACKCONCAT \STACK, \PREDICATE]}
 \end{mathpar}
@@
   {[(\SHA; \INSTRUCTION), (\StackOne, \TBYTE) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\VariableX, \TBYTE) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\VariableX\ = \FSHA(\StackOne))]}
+[\INSTRUCTION, (\X, \TBYTE) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\X\ \EQ\ \FSHA(\StackOne))]}
 \end{mathpar}
@@
     \StateTrans \
-    [\INSTRUCTIONONE, (\VariableX, \TYF) \STACKCONCAT\STACK,
-    \PREDICATE \wedge (\StackOne\ \EQUAL\ \LEFT\ \VariableX)]
+    [\INSTRUCTIONONE, (\X, \TYF) \STACKCONCAT\STACK,
+    \PREDICATE \wedge (\StackOne\ \EQ\ \LEFT\ \X)]
   }
@@
     \StateTrans \
-    [\INSTRUCTIONTWO, (\VariableX, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQUAL\ \RIGHT\ \VariableX))]
-  }
-\end{mathpar}
-These above rules collectively define the behavior of the IF-LEFT instruction based on the left or right branch of a tagged union type.
-This rule applies when the top element of the stack is a tagged union of type \TOR\ \TYF\ \TYS (either of type \TYF\ or \TYS), and the IF-LEFT instruction is followed by instructions \INSTRUCTIONONE\ and \INSTRUCTIONTWO.
-The first rule apply with the condition that the top element of the stack is of the form Left \VariableX\ (indicating the left branch of the union), it transitions to execute the instructions \INSTRUCTIONONE\ with the stack modified accordingly and the predicate is updated to include the condition that the top element of the stack is equal to Left \VariableX.
-Similerly, the second rule apply with the condition that  the top element is of the form Right \VariableX\ (indicating the right branch of the union), it transitions to execute the instructions \INSTRUCTIONTWO\ with the stack modified accordingly and the predicate is updated to include the condition that the top element of the stack is equal to Right \VariableX.
+    [\INSTRUCTIONTWO, (\X, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQ\ \RIGHT\ \X))]
+  }
+\end{mathpar}
+These above rules collectively define the behavior of the \IFLEFT instruction based on the left or right branch of a tagged union type.
+This rule applies when the top element of the stack is a tagged union of type \TOR\ \TYF\ \TYS (either of type \TYF\ or \TYS), and the \IFLEFT instruction is followed by instructions \INSTRUCTIONONE\ and \INSTRUCTIONTWO.
+The first rule apply with the condition that the top element of the stack is of the form Left \X\ (indicating the left branch of the union), it transitions to execute the instructions \INSTRUCTIONONE\ with the stack modified accordingly and the predicate is updated to include the condition that the top element of the stack is equal to Left \X.
+Similerly, the second rule apply with the condition that  the top element is of the form Right \X\ (indicating the right branch of the union), it transitions to execute the instructions \INSTRUCTIONTWO\ with the stack modified accordingly and the predicate is updated to include the condition that the top element of the stack is equal to Right \X.
 
@@
 In Michelson, loops are fundamental constructs that repeatedly execute a set of instructions until a specific condition is met.
-There are various loop instructions, including ITER, MAP, CONCAT, SIZE, LOOP, and LOOP-LEFT, enable the manipulation and traversal of different data structures like lists, sets, maps, and the stack itself.
+There are various loop instructions, including \ITER, \MAP, \CONCAT, \SIZE, \LOOP, and \LOOPLEFT, enable the manipulation and traversal of different data structures like lists, sets, maps, and the stack itself.
 
@@
 \begin{itemize}
-\item \KFOR\ loops: These are sequence-based loops, exemplified by ITER, MAP, CONCAT and SIZE.
-\item \KWHILE\ loops: These are predicates-based loops, illustrated by LOOP and LOOP-LEFT.
+\item \KFOR\ loops: These are sequence-based loops, exemplified by \ITER, \MAP, \CONCAT\ and \SIZE.
+\item \KWHILE\ loops: These are predicates-based loops, illustrated by \LOOP and \LOOPLEFT.
 \end{itemize}
@@
   }{
-    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, \STACK,  \PREDICATE\ \Wedge\  (\StackOne\ \EQUAL\ \EMPTYLIST)]
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, \STACK,  \PREDICATE\ \Wedge\  (\StackOne\ \EQ\ \EMPTYLIST)]
   }
@@
 This rule handles the case where the list is empty, and thus the \ITER\ instruction does not iterate.
-The resulting state transitions to the next instruction with an updated stack that is actually the same as before entering the \ITER\ intruction and an augmented predicate \PREDICATE\ $\Wedge$ (\StackOne \EQUAL \EMPTYLIST).
+The resulting state transitions to the next instruction with an updated stack that is actually the same as before entering the \ITER\ intruction and an augmented predicate \PREDICATE\ $\Wedge$ (\StackOne \EQ \EMPTYLIST).
 \begin{mathpar}
@@
   }{
-    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE \wedge Q] \StateTrans \\ [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), \{\STAIL\}\ \STACKCONCAT\STACK',  \PREDICATE \wedge Q' \Wedge  ( \StackOne\ \EQUAL\ \{\HEAD; \STAIL \}) ]
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE \wedge Q] \StateTrans \\ [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), \{\STAIL\}\ \STACKCONCAT\STACK',  \PREDICATE \wedge Q' \Wedge  ( \StackOne\ \EQ\ \{\HEAD; \STAIL \}) ]
   }
@@
 It symbolically executes the instructions \INSTRUCTIONONE\ within the \ITER\ block with the head of the list (\HEAD) removed from the stack and a subpart of the predicate Q.
-The resulting state transitions to a new stack (\STACK') and an updated predicate (\PREDICATE\ $\Wedge$ Q' $\Wedge$ (\StackOne \EQUAL \{\HEAD;\STAIL\}), where \{\STAIL\} represents the rest of the list.
+The resulting state transitions to a new stack (\STACK') and an updated predicate (\PREDICATE\ $\Wedge$ Q' $\Wedge$ (\StackOne \EQ \{\HEAD;\STAIL\}), where \{\STAIL\} represents the rest of the list.
 In summery, these rules capture the symbolic execution behavior of the \ITER\ instruction, considering both the cases where the list is empty and non-empty.
@@
   {[(\MAP\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \ 
-[\INSTRUCTION, (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST)]}
+[\INSTRUCTION, (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQ\ \EMPTYLIST)]}
 \end{mathpar}
@@
   {[(\MAP\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1 \Wedge\ Q2 ] \StateTrans  \\
-[\INSTRUCTION, (\{\PHEAD; \PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1' \Wedge\ Q2'  \Wedge\ (\StackOne \EQUAL\ \{\HEAD; \TAIL\})]}
+[\INSTRUCTION, (\{\PHEAD; \PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1' \Wedge\ Q2'  \Wedge\ (\StackOne \EQ\ \{\HEAD; \TAIL\})]}
 \end{mathpar}
@@
 
-Given a smart contract code c, the syntax of our property specification language is as follows: 
-\begin{verbatim}
-MContract ‘Name' with
-Code := {c}
-Input := t
-Output := t'
-Pre-condition := cd
-Post-condition := cd'
-\end{verbatim} 
-Here, \KMCONTRACT, \KWITH, \KCODE, \KINPUT, \KOUTPUT, \KPRECONDI, and \KPOSTCONDI are keywords.
-The 'Name' is replaced by the contract name.
+The syntax of our property specification language is as follows: 
+\begin{lstlisting}[float,captionpos=b,caption={Smart contract property specification},label={lst:safer-contract-module},numbers=left]
+mcontract Name = spec
+code := {c}
+input := t
+output := t'
+pre-condition := cd
+post-condition := cd'
+\end{lstlisting}
+Here, \KMCONTRACT, \KWITH, \KCODE, \KINPUT, \KOUTPUT, \KPRECONDI, and \KPOSTCONDI\ are keywords.
+The \KNAME\ is replaced by the contract name.
 In the input and output fields, the input and output patterns are specified.
@@
 Let's consider the following example of the property specification for the contract named Add:
-\begin{verbatim}
-MContract ‘Add' with
-Code := {UNPAIR; COMPARE; GE; 
-        IF {ADD}{PUSH string 'Unexpected pair'; FAILWITH}}
-Input := Pair (x : int) (y : int)
-Output := (z : int)
-Pre-condition := (x >= 5) | (y >= 3)
-Post-condition := (z >= 8)
-\end{verbatim}
+\begin{lstlisting}[float,captionpos=b,caption={The specification of Add contracr},label={lst:safer-contract-module},numbers=left]
+mcontract Add = spec
+code := {UNPAIR; COMPARE; GE; 
+        IF {ADD}{PUSH string 'Unexpected Pair'; FAILWITH}}
+input := Pair (x : int) (y : int)
+output := (z : int)
+pre-condition := (x >= 5) | (y >= 3)
+post-condition := (z >= 8)
+\end{lstlisting}
 Here, the program takes as input a stack with only one element, which is a pair of two integers, symbolically specified in the Input field.
-It then unpairs the input pair to obtain two elements as two integers \VariableX\ and \VariableY.
-It then proceeds to destructure the input pair, yielding two integers, denoted as \VariableX\ and \VariableY.
+It then unpairs the input pair to obtain two elements as two integers \VX\ and \VY.
+It then proceeds to destructure the input pair, yielding two integers.
 Subsequently, the program performs a comparison between these two integers.
-If \VariableX\ is greater than or equal to \VariableY, the program constructs a new stack with a solitary element at the top representing the sum of \VariableX\ and \VariableY, designated as \VariableZ.
-Otherwise, the execution terminates with an error message containing the content 'Unexpected pair.' The specification continues by defining pre and post conditions, where the precondition states the assumption that the integer \VariableX\ is greater than or equal to 5 and \VariableY\ is greater than or equal to 3.
-The postcondition asserts that the result sum \VariableZ\ is greater than or equal to 8.
+If  \VX\ is greater than or equal to \VY, the program constructs a new stack with a solitary element at the top representing the sum of  \VX\ and \VY, designated as \VZ.
+Otherwise, the execution terminates with an error message containing the content 'Unexpected pair.' The specification continues by defining pre and post conditions, where the precondition states the assumption that the integer  \VX\ is greater than or equal to 5 and \VY\ is greater than or equal to 3.
+The postcondition asserts that the result sum \VZ\ is greater than or equal to 8.
+
+A smart contract may offer various functions for users to interact.
+Therefore, our language is designed to allow users to specify different functions, referred to as entrypoints, in Michelson.
+This design enables us to specify and verify all functions within a smart contract.
+Furthermore, this design allows us to describe and verify relationships between functions.
+The syntax is as follows:
+\begin{lstlisting}[float,captionpos=b,caption={Multiple entrypoint specification syntax},label={lst:safer-contract-module},numbers=left][h]
+mcontract Name = spec
+   entrypoint %a 
+      code := {c1}
+      input := t1
+      output := t1'
+      pre-condition := cd1
+      post-condition := cd1'
+   entrypoint %b 
+      code := {c2}
+      input := t2
+      output := t2'
+      pre-condition := cd2
+      post-condition := cd2'
+   entrypoint %c 
+      ...
+   < entrypoint relations>
+\end{lstlisting}
+where the entrypoint name is written after the \lstinline/%/ symbol and is followed by a property specification for the entrypoint.
+At the end of the specification is the entrypoint relation specification, which we will explain next.
+
+To illustrate this, let's consider the following auction smart contract.
+This contract has two entrypoints, bid and close, which serve as functions for bidding and closing the contract, respectively.
+The smart contract storage on the blockchain is a pair containing the first element as a boolean value that indicates whether the contract is still open for bidding or already closed.
+The second element is another nested pair, where the first element  stores the highest bidder's address, and the second element is the contract owner's address.
+
+Closing the contract transfers the balance to the owner and is restricted to the owner.
+Both closing and bidding operations fail if the auction is already closed.
+If bidding is open and the amount of tokens accompanying the bid exceeds the current highest bid, the current bidder replaces the previous highest bidder, and the previous highest bidder is reimbursed.
+Otherwise, bidding fails.
+
+Upon deployment, the owner deposits an initial balance to indicate the minimum bid.
+The contract is supposed to be deployed with the storage value  \lstinline/Pair True (Pair owner owner)/, indicating that bidding is allowed, and the contract owner is currently the highest bidder.
+
+\begin{lstlisting}[float,captionpos=b,caption={Multiple entrypoint specification syntax},label={lst:safer-contract-module},numbers=left]
+mcontract Auction = spec 
+  entrypoint %bid
+    code := {...}
+    input := Pair Unit (Pair (auction_open: bool) 
+                             (Pair (highest_bidder: mutez)
+                                   (contract_owner: address)))
+    output :=   Pair (new_contract_open: bool) 
+                     Pair (new_highest_bidder: address)
+                          (new_contract_owner: address))
+    pre-condition := (auction_open = true) |
+                     (Amount > Balance) 
+    post-condition := (Post_Balance = Amount) |
+                      (new_highest_bidder = Sender) |
+                      (new_contract_owner = contract_owner) |
+                      Transfer_token (Unit, Balance, highest_bidder) ;
+  entrypoint %close
+    code := {...}
+    input := Pair Unit (Pair (auction_open: bool) 
+                             (Pair (highest_bidder: mutez)
+                                   (contract_owner: address)))
+    output :=   Pair (new_contract_open: bool) 
+                     Pair (new_highest_bidder: address)
+                          (new_contract_owner: address))
+    pre-condition := (auction_open = true) |
+                     (Sender = contract_owner)                  
+    post-condition := (Post_Balance = 0) |
+                      Transfer_token (Unit, Balance, contract_owner) ;
+    (%create -> %close) with (auction_open = true)  && (Amount > Balance) | 
+    (%create  -> %close) with (auction_open = true) && (Sender > contract_owner) |
+    (%bid -> %bid) with (auction_open = true) && (Amount > Balance)  | 
+    (%bid -> %close) with (auction_open = true) && (Sender > Balance)  | 
+    not (%close -> %bid) |
+    not (%close -> %close)"
+\end{lstlisting}
+
+There are several properies that we want to grantuee in this contract.
+Lets take look at the specification for the auction contract.
+For the  \lstinline/bid/ entrypoint, the input stack is  the one with only one element, which is a pair consitting the parameter and the current storage.
+Here, the parameter is \lstinline/Unit/ of type \lstinline/unit/.
+The current storage represnted symbolicly as a nested pair, where the first element is the auction-open variable of type bool and the second element is an other pair consiting the highest-bidder of type address as the first element and the contract-owner variable of also type address as the second
+
+There are several properties that we want to guarantee in this contract.
+Let's take a look at the specification for the auction contract.
+For the \lstinline/bid/ entrypoint, the input stack is the one with only one element, which is a pair consisting of the parameter and the current storage.
+Here, the parameter is \lstinline/Unit/ of type \lstinline/unit/.
+The current storage is represented symbolically as a nested pair, where the first element is the \lstinline/auction_open/ variable of type \lstinline/bool/, and the second element is another pair consisting of the \lstinline/highest_bidder/ of type \lstinline/address/ as the first element and the \lstinline/contract_owner/ variable, also of type \lstinline/address/, as the second element.
+The output term should maintain the required pattern of the storage, where the values may be changed, and these changes are recorded in other symbolic variables.
+We add the prefix \lstinline/new/ to the old variable names to represent the new variables corresponding to the old ones
 
@@
   {
-   \FLEN(\A) \EQUAL\ \N
+   \FLEN(\A) \EQ\ \N
   }
@@
   { 
-     \FLEN(\A) \EQUAL\ \N \\ [\INSTRUCTIONONE,  \B, Q]
+     \FLEN(\A) \EQ\ \N \\ [\INSTRUCTIONONE,  \B, Q]
     \StateTrans^*
@@
   }{
-    [(\PUSH\ \TY\ \VariableX; \INSTRUCTION),\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, (\VariableX, \TY) \STACKCONCAT\STACK, \PREDICATE]}
+    [(\PUSH\ \TY\ \X; \INSTRUCTION),\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, (\X, \TY) \STACKCONCAT\STACK, \PREDICATE]}
 \end{mathpar}
@@
   {[(\ADD; \INSTRUCTION), (\StackOne, \TNAT) \STACKCONCAT(\StackTwo, \TNAT) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\VariableX, \TNAT) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\VariableX\ \EQUAL\ \StackOne\ \PLUS\ \StackTwo)]}
+[\INSTRUCTION, (\X, \TNAT) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\X\ \EQ\ \StackOne\ \PLUS\ \StackTwo)]}
 \end{mathpar}
@@
     \StateTrans \
-    [\INSTRUCTION, (\VariableX, \TNAT) \STACKCONCAT \STACK,
-    \PREDICATE \wedge (\StackOne \ge 0 \Rightarrow \VariableX =
-    \StackOne) \wedge (\StackOne <0 \Rightarrow \VariableX = -\StackOne)]
+    [\INSTRUCTION, (\X, \TNAT) \STACKCONCAT \STACK,
+    \PREDICATE \wedge (\StackOne \ge 0 \Rightarrow \X =
+    \StackOne) \wedge (\StackOne <0 \Rightarrow \X = -\StackOne)]
  }
@@
     \SystemTrans \\
-    [\INSTRUCTION, (\VariableX, \TINT) \STACKCONCAT \STACK, \PREDICATE
-    \wedge\ (\StackOne > \StackTwo \Leftrightarrow \VariableX = 1)
-    \wedge\ (\StackOne = \StackTwo \Leftrightarrow \VariableX = 0) 
-    \wedge\ (\StackOne < \StackTwo \Leftrightarrow \VariableX = -1)]
+    [\INSTRUCTION, (\X, \TINT) \STACKCONCAT \STACK, \PREDICATE
+    \wedge\ (\StackOne > \StackTwo \Leftrightarrow \X = 1)
+    \wedge\ (\StackOne = \StackTwo \Leftrightarrow \X = 0) 
+    \wedge\ (\StackOne < \StackTwo \Leftrightarrow \X = -1)]
     }
@@
   {
-  [\COMPARE,  (\VariableX, \TY) \STACKCONCAT (\VariableY, \TY) \STACKCONCAT\EMPTYSTACK, Q]
+  [\COMPARE,  (\X, \TY) \STACKCONCAT (\Y, \TY) \STACKCONCAT\EMPTYSTACK, Q]
     \StateTrans^*
@@
     [\INSTRUCTION, (\VariableA, \TINT) \STACKCONCAT \STACK,  \PREDICATE
-    \wedge (\StackOne\ \EQUAL\ \SOME\ \VariableX)
-    \wedge (\StackTwo\ \EQUAL\ \SOME\ \VariableY)
+    \wedge (\StackOne\ \EQ\ \SOME\ \X)
+    \wedge (\StackTwo\ \EQ\ \SOME\ \Y)
     \wedge Q']
@@
     [\INSTRUCTION, (1, \TINT) \STACKCONCAT \STACK,  \PREDICATE
-    \wedge (\StackOne\ \EQUAL\ \SOME\ \VariableX)
-    \wedge (\StackTwo\ \EQUAL\ \NONE)
+    \wedge (\StackOne\ \EQ\ \SOME\ \X)
+    \wedge (\StackTwo\ \EQ\ \NONE)
     ]
@@
   {[(\XOR; \INSTRUCTION), (\StackOne, \TBOOL) \STACKCONCAT(\StackTwo, \TBOOL) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\VariableX, \TBOOL) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\VariableX\ \EQUAL\ \StackOne\ \FXOR\ \StackTwo)]}
+[\INSTRUCTION, (\X, \TBOOL) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\X\ \EQ\ \StackOne\ \FXOR\ \StackTwo)]}
 \end{mathpar}
@@
   {[(\HASHKEY; \INSTRUCTION), (\StackOne, \TBYTE) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\VariableX, \TBYTE) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\VariableX\ = \FHASHKEY(\StackOne))]}
+[\INSTRUCTION, (\X, \TBYTE) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\X\ = \FHASHKEY(\StackOne))]}
 \end{mathpar}
@@
   {[(\AMOUNT; \INSTRUCTION), \STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\VAMOUNT, \TMUTEZ) \STACKCONCAT\STACK, \PREDICATE}
+[\INSTRUCTION, (\CAMOUNT, \TMUTEZ) \STACKCONCAT\STACK, \PREDICATE}
 \end{mathpar}
@@
   {[(\CONTRACT\ \TY ; \INSTRUCTION), (\StackOne, \TADDR) \STACKCONCAT\STACK, \PREDICATE] \SystemTrans \
-[\INSTRUCTION, (\SOME\ \VariableX, \TOPTION\ (\TCONTRACT\ \TY)) \STACKCONCAT\STACK, \\ \PREDICATE \Wedge\ (\GETCONTRACTTYPE(\StackOne, \TY) = \SOME\ \VariableX)]}
+[\INSTRUCTION, (\SOME\ \X, \TOPTION\ (\TCONTRACT\ \TY)) \STACKCONCAT\STACK, \\ \PREDICATE \Wedge\ (\GETCONTRACTTYPE(\StackOne, \TY) \EQ\ \SOME\ \X)]}
 \end{mathpar}
@@
   {[(\CAR; \INSTRUCTION), (\StackOne, \TPAIR\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\VariableX, \TYF) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \PAIR\ \VariableX\ \VariableY)]}
+[\INSTRUCTION, (\X, \TYF) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQ\ \PAIR\ \X\ \Y)]}
 \end{mathpar}
@@
     \SystemTrans \\
-    \{[\INSTRUCTIONONE, (\VariableX, \TYF) \STACKCONCAT\STACK,
-    \PREDICATE \wedge (\StackOne\ \EQUAL\ \LEFT\ \VariableX)]\}  \cup  \{  [\INSTRUCTIONTWO, (\VariableX, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQUAL\ \RIGHT\ \VariableX))]\} \cup \SYSTEM
+    \{[\INSTRUCTIONONE, (\X, \TYF) \STACKCONCAT\STACK,
+    \PREDICATE \wedge (\StackOne\ \EQ\ \LEFT\ \X)]\}  \cup  \{  [\INSTRUCTIONTWO, (\X, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQ\ \RIGHT\ \X))]\} \cup \SYSTEM
   }
@@
   }{
-    [(\IFCONS\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\  [\INSTRUCTIONTWO; \INSTRUCTION, \STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST)]}
+    [(\IFCONS\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\  [\INSTRUCTIONTWO; \INSTRUCTION, \STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQ\ \EMPTYLIST)]}
 \end{mathpar}
@@
   }{
-   [(\IFCONS\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\  \\ [\INSTRUCTIONONE, (\HEAD, \TY) \STACKCONCAT(\{ \TAIL \}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ ( \StackOne\ \EQUAL\ \{\HEAD; \STAIL \})]}
+   [(\IFCONS\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\  \\ [\INSTRUCTIONONE, (\HEAD, \TY) \STACKCONCAT(\{ \TAIL \}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ ( \StackOne\ \EQ\ \{\HEAD; \STAIL \})]}
 \end{mathpar}
@@
   }{
-    [(\IFNONE\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TOPTION\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\   [\INSTRUCTIONONE; \INSTRUCTION, \STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \NONE)]}
+    [(\IFNONE\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TOPTION\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\   [\INSTRUCTIONONE; \INSTRUCTION, \STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQ\ \NONE)]}
 \end{mathpar}
@@
   }{
-    [(\IFNONE\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),   (\StackOne, \TOPTION\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\   [\INSTRUCTIONTWO,  (\VariableX, \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ ( \StackOne\ \EQUAL\ \SOME\ \VariableX)]}
+    [(\IFNONE\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),   (\StackOne, \TOPTION\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\   [\INSTRUCTIONTWO,  (\X, \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ ( \StackOne\ \EQ\ \SOME\ \X)]}
 \end{mathpar}
@@
   {[(\CONCAT; \INSTRUCTION), (\StackOne, \TYLIST\ \TSTR) \STACKCONCAT\STACK,  \PREDICATE] \StateTrans 
-[\INSTRUCTION,  ("",  \TSTR) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST)]}
+[\INSTRUCTION,  ("",  \TSTR) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQ\ \EMPTYLIST)]}
 \end{mathpar}
@@
   {[(\CONCAT; \INSTRUCTION),  (\StackOne, \TYLIST\ \TSTR) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans \\
-[\INSTRUCTION, ( \HEAD\ \STRINGCONCAT\ \StackTwo, \TSTR) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ Q']}
+[\INSTRUCTION, ( \HEAD\ \STRINGCONCAT\ \StackTwo, \TSTR) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQ\ \{\HEAD; \TAIL\}) \Wedge\ Q']}
 \end{mathpar}
@@
   {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\FALSE, \TBOOL) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackTwo\ \EQUAL\ \EMPTYSET)]}
+[\INSTRUCTION, (\FALSE, \TBOOL) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackTwo\ \EQ\ \EMPTYSET)]}
 \end{mathpar}
@@
   {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans  \
-[\MEM; \INSTRUCTION, \StackOne\ \STACKCONCAT\{\LESS\ \M\ \MORE\} \STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackTwo\ \EQUAL\ \{\ELT\ \K\ \V; \LESS\ \M\ \MORE\})  \Wedge\ (\VariableB\ \EQUAL\ \ONE)]}
+[\MEM; \INSTRUCTION, \StackOne\ \STACKCONCAT\{\LESS\ \M\ \MORE\} \STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackTwo\ \EQ\ \{\ELT\ \K\ \V; \LESS\ \M\ \MORE\})  \Wedge\ (\VariableB\ \EQ\ \ONE)]}
 \end{mathpar}
@@
   {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans  \\
-[\INSTRUCTION, (\TRUE, \TBOOL) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackTwo\ \EQUAL\ \{\ELT\ \K\ \V; \LESS\ \M\ \MORE\}) \Wedge\ (\VariableB\ \EQUAL\ \ZERO)]}
+[\INSTRUCTION, (\TRUE, \TBOOL) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackTwo\ \EQ\ \{\ELT\ \K\ \V; \LESS\ \M\ \MORE\}) \Wedge\ (\VariableB\ \EQ\ \ZERO)]}
 \end{mathpar}
@@
   {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans  \\
-[\INSTRUCTION, (\FALSE, \TBOOL) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackTwo\ \EQUAL\ \{\ELT\ \K\ \V; \LESS\ \M\ \MORE\})  \Wedge\ (\VariableB\ \EQUAL\ \MINUS\ \ONE)]}
+[\INSTRUCTION, (\FALSE, \TBOOL) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackTwo\ \EQ\ \{\ELT\ \K\ \V; \LESS\ \M\ \MORE\})  \Wedge\ (\VariableB\ \EQ\ \MINUS\ \ONE)]}
 \end{mathpar}
@@
   {[(\MAP\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST)]}
+[\INSTRUCTION, (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQ\ \EMPTYLIST)]}
 \end{mathpar}
@@
   }
-  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE]\ \SystemTrans\  \\ [\INSTRUCTION, (\{\VariableX \}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\  \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST) \Wedge\ (\VariableB\ \EQUAL\ \TRUE)]}
+  {[(\UPDATE; \INSTRUCTION), (\X, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE]\ \SystemTrans\  \\ [\INSTRUCTION, (\{\X \}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\  \Wedge\ (\StackOne\ \EQ\ \EMPTYLIST) \Wedge\ (\VariableB\ \EQ\ \TRUE)]}
 \end{mathpar}
@@
   }
-  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE]\ \SystemTrans\  \\ [\INSTRUCTION, (\EMPTYLIST, \TYLIST\ \TY)\ \STACKCONCAT\STACK, \PREDICATE\  \Wedge\ (\StackOne\ \EQUAL\ \EMPTYLIST) \Wedge\ (\VariableB\ \EQUAL\ \FALSE)]}
+  {[(\UPDATE; \INSTRUCTION), (\X, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE]\ \SystemTrans\  \\ [\INSTRUCTION, (\EMPTYLIST, \TYLIST\ \TY)\ \STACKCONCAT\STACK, \PREDICATE\  \Wedge\ (\StackOne\ \EQ\ \EMPTYLIST) \Wedge\ (\VariableB\ \EQ\ \FALSE)]}
 \end{mathpar}
@@
   {
-  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
+  [\COMPARE, (\X, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
     [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
   }
-  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans
+  {[(\UPDATE; \INSTRUCTION), (\X, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans
 [\INSTRUCTION, (\StackOne, \TYLIST\ \TY)
-\STACKCONCAT\STACK,\\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQUAL\ \TRUE) \Wedge\ (\VariableA\ \EQUAL\ \ZERO)]}
+\STACKCONCAT\STACK,\\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQ\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQ\ \TRUE) \Wedge\ (\VariableA\ \EQ\ \ZERO)]}
 \end{mathpar}
@@
   {
-  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
+  [\COMPARE, (\X, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
     [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
   }
-  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans  \\
+  {[(\UPDATE; \INSTRUCTION), (\X, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans  \\
 [\INSTRUCTION, (\{\TAIL\}, \TYLIST\ \TY)
-\STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQUAL\ \FALSE) \Wedge\ (\VariableA\ \EQUAL\ \ZERO)]}
+\STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQ\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQ\ \FALSE) \Wedge\ (\VariableA\ \EQ\ \ZERO)]}
 \end{mathpar}
@@
   {
-  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
+  [\COMPARE, (\X, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
     [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
   }
-  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans  \\
-[\INSTRUCTION, (\{\VariableX; \HEAD; \TAIL\}, \TYLIST\ \TY)
-\STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQUAL\ \TRUE) \Wedge\ (\VariableA\ \EQUAL\ \MINUS\ \ONE)]}
+  {[(\UPDATE; \INSTRUCTION), (\X, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans  \\
+[\INSTRUCTION, (\{\X; \HEAD; \TAIL\}, \TYLIST\ \TY)
+\STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQ\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQ\ \TRUE) \Wedge\ (\VariableA\ \EQ\ \MINUS\ \ONE)]}
 \end{mathpar}
@@
   {
-  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
+  [\COMPARE, (\X, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
     [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
   }
-  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans\  \\
+  {[(\UPDATE; \INSTRUCTION), (\X, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans\  \\
 [\INSTRUCTION, (\{\HEAD; \TAIL\}, \TYLIST\ \TY)
-\STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQUAL\ \FALSE) \Wedge\ (\VariableA\ \EQUAL\ \MINUS\ \ONE)]}
+\STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQ\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQ\ \FALSE) \Wedge\ (\VariableA\ \EQ\ \MINUS\ \ONE)]}
 \end{mathpar}
@@
   {
-  [\COMPARE, (\VariableX, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q1] \StateTrans^*
+  [\COMPARE, (\X, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q1] \StateTrans^*
     [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q1'] \\
- [\UPDATE, (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT( \{\TAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK, Q2] \StateTrans^* \\  [\EMPTYSTACK, ( \{\PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK, Q2']
-  }
-  {[(\UPDATE; \INSTRUCTION), (\VariableX, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1 \Wedge\ Q2 ] \SystemTrans\  \\
+ [\UPDATE, (\X, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT( \{\TAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK, Q2] \StateTrans^* \\  [\EMPTYSTACK, ( \{\PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK, Q2']
+  }
+  {[(\UPDATE; \INSTRUCTION), (\X, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1 \Wedge\ Q2 ] \SystemTrans\  \\
 [\INSTRUCTION; (\{\HEAD; \PTAIL\}, \TYLIST\ \TY)
-\STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1' \Wedge\ Q2' \Wedge\ (\StackOne\ \EQUAL\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableA\ \EQUAL\ \ONE)]}
+\STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1' \Wedge\ Q2' \Wedge\ (\StackOne\ \EQ\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableA\ \EQ\ \ONE)]}
 \end{mathpar}
@@
 \begin{mathpar} 
-  \inferrule{\INSTRUCTION\  /  \VariableX\ \STACKCONCAT\ \STACK \SRightarrow\ \STACK'
-  }{
-    \ITER\ \INSTRUCTION\ / \{ \VariableX\ ; \TAIL\ \} \STACKCONCAT\ \STACK\ \SRightarrow\ \ITER\ \INSTRUCTION\ / \{ \TAIL\ \} \STACKCONCAT\ \STACK' 
+  \inferrule{\INSTRUCTION\  /  \X\ \STACKCONCAT\ \STACK \SRightarrow\ \STACK'
+  }{
+    \ITER\ \INSTRUCTION\ / \{ \X\ ; \TAIL\ \} \STACKCONCAT\ \STACK\ \SRightarrow\ \ITER\ \INSTRUCTION\ / \{ \TAIL\ \} \STACKCONCAT\ \STACK' 
     }

### 2023-12-13 papers/static-checker/ecoop2024/ecoop2024.tex
Write the DSL part

@@
 \end{itemize}
-To illustrate the structures of  loops, we can draw a parallel with OCaml syntax:
-\begin{verbatim}
+To illustrate the structures of  loops, we can draw a parallel with OCaml syntax as in Listing \ref{list:while-loop}.
+
+\begin{lstlisting}[caption={While loop.},label=list:while-loop,captionpos=t,float,abovecaptionskip=-\medskipamount]
 while <loop_condition> do
@@
 done
-\end{verbatim}
+\end{lstlisting}
 This \KWHILE\  loop structure involves a loop condition that is evaluated at the beginning of each iteration.
 If the condition holds true, the loop body is executed, and the process repeats until the condition becomes false.
-In Michelson, this pattern is evident in instructions like LOOP and LOOP-LEFT, which rely on predicate-based conditions for their iteration.
-\begin{verbatim}
-LOOP {<loop-body>}
-\end{verbatim}
-Additionally, Michelson features a \KFOR\ loop, where the index runs from the initial value to the final value:
-\begin{verbatim}
+In Michelson, this pattern is evident in instructions like LOOP and LOOP-LEFT, which rely on predicate-based conditions for their iteration: \lstinline/LOOP {<loop-body>}/.
+
+Additionally, Michelson features a \KFOR\ loop, where the index runs from the initial value to the final value as in Listing \ref{list:for-loop}.
+The \KFOR\ loop is represented by the ITER instruction: \lstinline/ITER {<loop-body>}/
+
+\begin{lstlisting}[caption={For loop.},label=list:for-loop,captionpos=t,float,abovecaptionskip=-\medskipamount]
 for index = <initial_value> to <final_value> do
@@
 done
-\end{verbatim}
-This is represented by the ITER instruction:
-\begin{verbatim}
-ITER {<loop-body>}
-\end{verbatim}
+\end{lstlisting}
 
@@
 However, for the \KFOR\  loops, the loop condition is more implicit.
-A \KFOR\  loop can be rewritten as a  \KWHILE\ loop to make the  loop condition explicit:
-\begin{verbatim}
+A \KFOR\  loop can be rewritten as a  \KWHILE\ loop to make the  loop condition explicit as showned in Listing \ref{list:express-for-using-while-loop}.
+\begin{lstlisting}[caption={Expressing a \KFOR\ loop using a \KWHILE\ loop.},label=list:express-for-using-while-loop,captionpos=t,float,abovecaptionskip=-\medskipamount]
 index = 0
@@
 done
-\end{verbatim}
+\end{lstlisting}
 Here, the implicit loop condition asserts that the index of the sequence element is less than the length of the sequence.
@@
 For a  \KWHILE\ loop the top element of the stack must have a boolean value and for the \KFOR\  loop, it must have a sequence data type, such as list, set or map.
-If we denote the function to retrieve the top element of a stack as "\FPOP," the  \KWHILE\ loop instruction can be expressed as:
-\begin{verbatim}
+If we denote the function to retrieve the top element of a stack as "\FPOP," the  \KWHILE\ loop instruction can be expressed as shown in Listing \ref{list:express-for-using-ocaml} and and the \KFOR\  loop is expressed as Listing \ref{list:express-while-using-ocaml}.
+\begin{lstlisting}[caption={Expressing Michelson \KWHILE\ loop using  Ocaml syntax.},label=list:express-for-using-ocaml,captionpos=t,float,abovecaptionskip=-\medskipamount]
 while pop(S) do
@@
 done
-\end{verbatim}
-and the \KFOR\  loop is expressed as:
-\begin{verbatim}
+\end{lstlisting}
+
+\begin{lstlisting}[caption={Expressing Michelson  \KFOR\ loop using Ocaml syntax.},label=list:express-while-using-ocaml,captionpos=t,float,abovecaptionskip=-\medskipamount]
 index = 0
@@
 done
-\end{verbatim}
+\end{lstlisting}
 
@@
   {  [\ITER,  (\HEAD, \TY) \STACKCONCAT\STACK, 
-    Q]
+    \Q]
     \StateTrans^*
-    [ \EMPTYSTACK,  \STACK', Q']
-  }{
-    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE \wedge Q] \StateTrans \\ [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), \{\STAIL\}\ \STACKCONCAT\STACK',  \PREDICATE \wedge Q' \Wedge  ( \StackOne\ \EQ\ \{\HEAD; \STAIL \}) ]
+    [ \EMPTYSTACK,  \STACK', \Q']
+  }{
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE \wedge \Q] \StateTrans \\ [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), \{\STAIL\}\ \STACKCONCAT\STACK',  \PREDICATE \wedge \Q' \Wedge  ( \StackOne\ \EQ\ \{\HEAD; \STAIL \}) ]
   }
@@
 It symbolically executes the instructions \INSTRUCTIONONE\ within the \ITER\ block with the head of the list (\HEAD) removed from the stack and a subpart of the predicate Q.
-The resulting state transitions to a new stack (\STACK') and an updated predicate (\PREDICATE\ $\Wedge$ Q' $\Wedge$ (\StackOne \EQ \{\HEAD;\STAIL\}), where \{\STAIL\} represents the rest of the list.
+The resulting state transitions to a new stack (\STACK') and an updated predicate (\PREDICATE\ $\Wedge$ \Q' $\Wedge$ (\StackOne \EQ \{\HEAD;\STAIL\}), where \{\STAIL\} represents the rest of the list.
 In summery, these rules capture the symbolic execution behavior of the \ITER\ instruction, considering both the cases where the list is empty and non-empty.
@@
   {
-  }{[(\FAILWITH; \INSTRUCTION), (\StackOne,  \TY) \STACKCONCAT \STACK,  \PREDICATE] \StateTrans [\EMPTYSTACK, (\FAIL\ (\StackOne)) \STACKCONCAT\EMPTYSTACK, \PREDICATE]}
+  }{[(\FAILWITH; \INSTRUCTION), (\StackOne,  \TY) \STACKCONCAT \STACK,  \PREDICATE] \StateTrans [\EMPTYSTACK, (\FAIL\ (\StackOne), \TFAILWITH) \STACKCONCAT\EMPTYSTACK, \PREDICATE]}
 \end{mathpar}
@@
 
-The syntax of our property specification language is as follows: 
-\begin{lstlisting}[float,captionpos=b,caption={Smart contract property specification},label={lst:safer-contract-module},numbers=left]
+\begin{lstlisting}[float,captionpos=b,caption={Smart contract property specification},label={lst:smart-contract-property-specification},numbers=left]
 mcontract Name = spec
@@
 \end{lstlisting}
+Listing \ref{lst:smart-contract-property-specification} shows the syntax of our property specification language.
 Here, \KMCONTRACT, \KWITH, \KCODE, \KINPUT, \KOUTPUT, \KPRECONDI, and \KPOSTCONDI\ are keywords.
@@
 In our syntax, for verification purpose, we omit the operation list and then the output is represented by the patern of the value in the storage after the execution is finished.
-
 The input and output patterns represent Michelson terms, which can be either concrete values or symbolic values, including variables.
@@
 Here, the program takes as input a stack with only one element, which is a pair of two integers, symbolically specified in the Input field.
-It then unpairs the input pair to obtain two elements as two integers \VX\ and \VY.
+It then unpairs the input pair to obtain two elements as two integers \lstinline/x/ and \lstinline/y/.
 It then proceeds to destructure the input pair, yielding two integers.
 Subsequently, the program performs a comparison between these two integers.
-If  \VX\ is greater than or equal to \VY, the program constructs a new stack with a solitary element at the top representing the sum of  \VX\ and \VY, designated as \VZ.
-Otherwise, the execution terminates with an error message containing the content 'Unexpected pair.' The specification continues by defining pre and post conditions, where the precondition states the assumption that the integer  \VX\ is greater than or equal to 5 and \VY\ is greater than or equal to 3.
-The postcondition asserts that the result sum \VZ\ is greater than or equal to 8.
+If  \lstinline/x/ is greater than or equal to \lstinline/y/, the program constructs a new stack with a solitary element at the top representing the sum of  \lstinline/x/ and \lstinline/y/, designated as \lstinline/z/.
+Otherwise, the execution terminates with an error message containing the content 'Unexpected pair.' The specification continues by defining pre and post conditions, where the precondition states the assumption that the integer  \lstinline/x/ is greater than or equal to 5 and \lstinline/y/ is greater than or equal to 3.
+Here, the symbol  \lstinline/|/ is the conjuration.
+The postcondition asserts that the result sum \lstinline/z/ is greater than or equal to 8.
 
@@
 The second element is another nested pair, where the first element  stores the highest bidder's address, and the second element is the contract owner's address.
+The current highest bid is reflected in the balance of the contract.
 
@@
 
-\begin{lstlisting}[float,captionpos=b,caption={Multiple entrypoint specification syntax},label={lst:safer-contract-module},numbers=left]
+\begin{lstlisting}[float,captionpos=b,caption={Auction contract specification},label={lst:auction-contract-specification},numbers=left]
 mcontract Auction = spec 
@@
                                    (contract_owner: address)))
-    output :=   Pair (new_contract_open: bool) 
-                     Pair (new_highest_bidder: address)
-                          (new_contract_owner: address))
-    pre-condition := (auction_open = true) |
-                     (Amount > Balance) 
-    post-condition := (Post_Balance = Amount) |
-                      (new_highest_bidder = Sender) |
-                      (new_contract_owner = contract_owner) |
-                      Transfer_token (Unit, Balance, highest_bidder) ;
+    output :=   Pair (post_auction_open: bool) 
+                     Pair (post_highest_bidder: address)
+                          (post_contract_owner: address))
+    pre-condition := auction_open |
+             Amount > Balance
+    post-condition := post_highest_bidder = Sender |
+             Post_Balance = Amount |
+             Transfer_token (Unit, Balance, highest_bidder) |
+             post_contract_owner = contract_owner ;
   entrypoint %close
@@
                                    (contract_owner: address)))
-    output :=   Pair (new_contract_open: bool) 
-                     Pair (new_highest_bidder: address)
-                          (new_contract_owner: address))
-    pre-condition := (auction_open = true) |
-                     (Sender = contract_owner)                  
-    post-condition := (Post_Balance = 0) |
+    output :=   Pair (post_auction_open: bool) 
+                     Pair (post_highest_bidder: address)
+                          (post_contract_owner: address))
+    pre-condition := auction_open |
+           Sender = contract_owner                
+    post-condition := not post_auction_open |
+          Post_Balance = 0 |
           Transfer_token (Unit, Balance, contract_owner) ;
-    (%create -> %close) with (auction_open = true)  && (Amount > Balance) | 
-    (%create  -> %close) with (auction_open = true) && (Sender > contract_owner) |
-    (%bid -> %bid) with (auction_open = true) && (Amount > Balance)  | 
-    (%bid -> %close) with (auction_open = true) && (Sender > Balance)  | 
+    (%create -> %bid) with (auction_open = true)  
+                      && (Amount > Balance) | 
+    (%create  -> %close) with (auction_open = true) 
+                      && (Sender = contract_owner) |
+    (%bid -> %bid) with (Amount > Balance)  | 
+    (%bid -> %close) with (Sender = contract_owner)  | 
     not (%close -> %bid) |
-    not (%close -> %close)"
+    not (%close -> %close)
 \end{lstlisting}
@@
 There are several properies that we want to grantuee in this contract.
-Lets take look at the specification for the auction contract.
+Lets take look at the specification for the auction contract in Listing \ref{lst:auction-contract-specification}.
+Here, we omit the Michelson code  of the smart contract due to its length.
 For the  \lstinline/bid/ entrypoint, the input stack is  the one with only one element, which is a pair consitting the parameter and the current storage.
 Here, the parameter is \lstinline/Unit/ of type \lstinline/unit/.
-The current storage represnted symbolicly as a nested pair, where the first element is the auction-open variable of type bool and the second element is an other pair consiting the highest-bidder of type address as the first element and the contract-owner variable of also type address as the second
+The current storage represnted symbolicly as a nested pair, where the first element is the auction-open variable of type bool and the second element is an other pair consiting the highest-bidder of type address as the first element and the contract-owner variable of also type address as the second.
 
@@
 The output term should maintain the required pattern of the storage, where the values may be changed, and these changes are recorded in other symbolic variables.
-We add the prefix \lstinline/new/ to the old variable names to represent the new variables corresponding to the old ones
+In this specification, we add the prefix \lstinline/post/ to the old variable names to represent the new variables corresponding to the old ones.
+
+The first property that we want to check is that if a user sends a bid to the contract by calling the \lstinline/bid/ entrypoint, such that the contract is still open for bidding and the bid is higher than the current bid (as specified in the  \lstinline/pre-condition/ field from line 10 to line 11 in Listing \ref{lst:auction-contract-specification}), then the bid should succeed.
+This means the highest bidder has to be updated to the sender (line 12 in the \lstinline/post-condition/ field), which is the address of the user, and the balance of the contract should be the amount sent along with the call (line 13).
+Moreover, the old highest bidder should receive their bid, which means the auction contract should transfer the \lstinline/Balance/ to the previous bidder, \lstinline/highest_bidder/ (line 14).
+ \lstinline/ Transfer_token (data, amount, address)/ is a predicate that represents a smart contract call with three arguments: the data sent along with the call, the amount, and the address of the receiver.
+When the call is just a token transfer, the data field has the value \lstinline/Unit/ of type \lstinline/unit/, indicating that this is just a token transfer with no additional data.
+Another important property is that the auction owner's address should not be changed.
+This means that after calling the \lstinline/bid/ entrypoint, the \lstinline/contract_owner/ should remain the same as before calling the entrypoint (line 15).
+The last property guarantees that when the contract owner (line 25) closes the open contract (line 24), the contract is first closed (line 26), and then money (\lstinline/Balance/) should be sent to the owner.
+This means the auction balance is now zero (lines 28 and 29).
+
+For a smart contract on the blockchain, the order of smart contract calls can be crucial.
+Here, we refer to it as entrypoint relation.
+An entrypoint relation can be specified as \lstinline/%a with cd -> %b/, where it includes the name \lstinline/a/ of the entrypoint followed by the symbol \lstinline/%/ and is followed by the keyword \lstinline/with/ in case conditions are specified as predicates.
+Next is the symbol \lstinline/->/, implying that from the entrypoint a that satisfies the condition \lstinline/cd/, it leads to the entrypoint \lstinline/b/.
+One smart contract specification can contain several entrypoint relations concatenated by the conjunction \lstinline/|/.
+There is a special entrypoint named \lstinline/create/ that indicates the contract state after deployment.
+
+Let's return to the auction contract.
+It is important to guarantee that after contract deployment with the  \lstinline/auction_open/ set to \TRUE, indicating that the contract is open for bidding, users should be able to bid on the contract or the contract owner should be able to close it (lines 29-31).
+Furthermore, the bid call can happen successfully after another if the new bid is higher than the previous one (line 33).
+The  \lstinline/close/ entrypoint could also be called after a bid call if the caller is the contract owner (line 34).
+However, it should not be possible to call the  \lstinline/bid/ entrypoint to bid on the contract after it is closed (line 35), and, of course, it cannot be closed again if it is already closed (line 36).
+This sequence could illustrate the life cycle of the auction contract, which is depicted in Figure \ref{fig:auction-life-cycle}.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.8\textwidth]{auction-life-cycle}
+    \caption{Auction contract life cycle}
+    \label{fig:auction-life-cycle}
+\end{figure}
 
 \section {Static Checker}
+The architect of the static checker is depicted as in Figure \ref{}.  The system includes
+
 Formulas that are used in assertions or added to solvers are terms of Boolean sort.
@@
 \section {Appendix}
-
-\begin{figure} []
-\begin{align*}
-T, U &::= \\
-   &\Mid\ \langle \text{comparable type}\rangle \\
-   &\Mid\ \text{option}\ \langle\text{type}\rangle \\
-   &\Mid\ \text{list}\ \langle\text{type}\rangle \\
-   &\Mid\ \text{set}\ \langle\text{comparable type}\rangle \\
-   &\Mid\ \text{operation} \\
-   &\Mid\ \text{contract}\ \langle\text{type}\rangle \\
-   &\Mid\ \text{ticket}\ \langle\text{comparable type}\rangle \\
-   &\Mid\ \text{pair}\ \langle\text{type}\rangle \langle\text{type}\rangle \\
-   &\Mid\ \text{or}\ \langle\text{type}\rangle \langle\text{type}\rangle \\
-   &\Mid\ \text{lambda}\ \langle\text{type}\rangle \langle\text{type}\rangle \\
-   &\Mid\ \text{map}\ \langle\text{comparable type}\rangle \langle\text{type}\rangle \\
-   &\Mid\ \text{big-map}\ \langle\text{comparable type}\rangle \langle\text{type}\rangle \\
-   &\Mid\ \text{bls12-381-g1} \\
-   &\Mid\ \text{bls12-381-g2} \\
-   &\Mid\ \text{bls12-381-fr} \\
-   &\Mid\ \text{sapling-transaction}\ \langle\text{natural number constant}\rangle \\
-   &\Mid\ \text{sapling-state}\ \langle\text{natural number constant}\rangle \\
-   &\Mid\ \text{chest} \\
-   &\Mid\ \text{chest-key} \\
-\langle\text{comparable type}\rangle ::= \\
-   &\Mid\ \text{unit} \\
-   &\Mid\ \text{never} \\
-   &\Mid\ \text{bool} \\
-   &\Mid\ \text{int}\\
-   &\Mid\ \text{nat}\\
-   &\Mid\ \text{string}\\
-   &\Mid\ \text{chain-id}\\
-   &\Mid\ \text{bytes}\\
-   &\Mid\ \text{mutez}\\
-   &\Mid\ \text{key-hash}\\
-   &\Mid\ \text{key}\\
-   &\Mid\ \text{signature}\\
-   &\Mid\ \text{timestamp}\\
-   &\Mid\ \text{address}\\
-   &\Mid\ \text{tx-rollup-l2-address}\\
-   &\Mid\ \text{option}\ \langle\text{comparable type}\rangle\\
-   &\Mid\ \text{or}\ \langle\text{comparable type}\rangle \langle\text{comparable type}\rangle\\
-   &\Mid\ \text{pair}\ \langle\text{comparable type}\rangle \langle\text{comparable type}\rangle \DOT \\
-\end{align*}
-\caption{Types}
-\label{fig:type}
-\end{figure}
-
-\begin{figure}[h]
-\begin{align*}
-\text{t} &::= \\
-   &\Mid\ \langle \text{variable} \rangle \\
-   &\Mid\ \langle \text{account constant} \rangle \\
-   &\Mid\ \langle \text{int constant} \rangle \\
-   &\Mid\ \langle \text{string constant} \rangle \\
-   &\Mid\ \langle \text{byte sequence constant} \rangle \\
-   &\Mid\ \UNIT \\
-   &\Mid\ \TRUE \\
-   &\Mid\ \FALSE \\
-   &\Mid\ \PAIR\ \text{t1 t2}\\
-   &\Mid\ \LEFT\ \text{t}\\
-   &\Mid\ \RIGHT\ \text{t}\\ 
-   &\Mid\ \SOME\ \text{t}\\
-   &\Mid\ \NONE \\
-   &\Mid\ \text{\{t ; ... \}}\\
-   &\Mid\ \text{\{ Elt t1 t2 ; ... \}}\\
-   &\Mid\ \{ \langle\text{instruction}\rangle; ... \}   \\
-\langle \text{variable} \rangle &::= \\ 
-   &\Mid\ \VAR\\
-\langle \text{account constant} \rangle &::= \\ 
-   &\Mid\ \text{balance} \\
-   &\Mid\ \text{amount} \\
-   &\Mid\ \text{sender} \\
-   &\Mid\ \text{source} \\
-   &\Mid\ \text{now} \\
-   &\Mid\ \text{level} \\
-   &\Mid\ \text{chain-id} \\
-   &\Mid\ \text{self}  \\
-   &\Mid\ \text{self-address}  \\
-   &\Mid\ \text{total-voting-power}  \\
-   &\Mid\ \text{voting-power}  \\
-\langle \text{natural number constant} \rangle &::= \\ 
-   &\Mid\ \text {[0-9]+} \\
-\langle \text{int constant} \rangle &::= \\
-  &\Mid\ \langle \text{natural number constant} \rangle \\
-  &\Mid\ \text{-} \langle \text{natural number constant} \rangle \\
-\langle\text{string constant}\rangle &::= \\
-  &\Mid\ \text{"} \langle \text{string content}\rangle\text{*"} \\
-\langle\text{instruction}\rangle &::= \\
-  &\Mid\ \DROP \\
-  &\Mid\ \DROP \langle\text{natural number constant}\rangle \\
-  &\text{...}
-\end{align*}
-\caption{Terms}
-\label{fig:term}
-\end{figure}
-
-\begin{figure}[h]
-\begin{align*}
-\text{p} &::= \\
-   &\Mid\ \langle \text{atomic formula} \rangle \\
-   &\Mid\ \NEG\ \text{p} \
-   \Mid\ \text{p}\ \CNF\ \text{q} \
-   \Mid\ \text{p}\ \DNF\ \text{q} \\
-\langle \text{atomic formula} \rangle &::= \\ 
-    &\Mid\ \langle \text{butop} \rangle \langle \text{bterm} \rangle\\ 
-   &\Mid\  \langle \text{bterm} \rangle  \langle \text{biop} \rangle \langle \text{bterm} \rangle\\ 
-\langle \text{butop} \rangle &::= \\
-   &\Mid\ \text{not} \\
-\langle \text{biop} \rangle &::= \\
-   &\Mid\ \text{$=$} \
-   \Mid\ \text{$>$} \
-   \Mid\ \text{$<$} \
-   \Mid\ \text{$>=$} \
-   \Mid\ \text{$=<$} \
-   \Mid\ \text{$!=$} \\
-   &\Mid\ \text{and}\ \Mid\ \text{or}\ \Mid\ \text{xor}\\
-\langle \text{bterm} \rangle &::= \\ 
-   &\Mid\ \text{t} \\
-   &\Mid\ \langle \text{unop} \rangle \text{t} \\ 
-   &\Mid\ \text{t}\ \langle \text{binop} \rangle \text{t}\\  
-\langle \text{unop} \rangle &::= \\ 
-   &\Mid\ \text{abs} \\
-   &\Mid\ \text{size} \\
-   &\Mid\ \text{int} \\
-   &\Mid\ \text{contract}  \langle \text{type} \rangle \\
-   &\Mid\ \text{isleft} \\
-   &\Mid\ \text{isnone} \\
-   &\Mid\ \text{neg} \\
-   &\Mid\ \text{blake2b} \\
-   &\Mid\ \text{hash-key} \\
-   &\Mid\ \text{keccak} \\
-   &\Mid\ \text{pairing-check} \\
-   &\Mid\ \text{sha256} \\
-   &\Mid\ \text{sha3} \\
-   &\Mid\ \text{sha512} \\
-   &\Mid\ \text{implicit-account} \\
-   &\Mid\ \text{check-sig} \\
-\langle \text{bitop} \rangle &::= \\ 
-   &\Mid\ \text{+}\ \Mid\ \text{-}\ \Mid\ \text{*}\ \Mid\ \text{/}
-\end{align*}
-\caption{Predicates}
-\label{fig:predicate}
-\end{figure}
-
-\subsubsection{Basic Instructions}
-
-\paragraph{Control structures}
-%EXE
-\begin{mathpar}
-  \inferrule[EXEC]
-  {
-    [\INSTRUCTIONONE, (\StackOne, \TYF) \STACKCONCAT \EMPTYSTACK, 
-    Q]
-    \StateTrans^*
-    [ \EMPTYSTACK, (\StackOne', \TYS) \STACKCONCAT Q']
-  }{
-     [(\EXEC; \INSTRUCTION),   (\{\INSTRUCTIONONE\}, \TYF\ \rightarrow\ \TYS) \STACKCONCAT
-    (\StackOne, \TYF) \STACKCONCAT \STACK, \PREDICATE \wedge Q] 
-    \StateTrans \
-    [ \INSTRUCTION, (\StackOne', \TYS) \STACKCONCAT \STACK,
-    \PREDICATE \wedge Q']}
-\end{mathpar}
-
-%APPLY
-\begin{mathpar}
-  \inferrule[APPLY]
-  {
-  }{
-    [(\APPLY; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\{\INSTRUCTIONONE\}, \TLAMBDA\ (\TPAIR\ \TYF\  \TYS)\ \TYT) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\\ [\INSTRUCTION, (\{\PUSH\ \TYF\ \StackOne; \IPAIR; \INSTRUCTIONONE\}, \TLAMBDA\ \TYS\ \TYT ) \STACKCONCAT\STACK, \PREDICATE]}
-\end{mathpar}
-
-%LAMBLA
-\begin{mathpar}
-  \inferrule[LAMBDA]
-  {  
-  }{
-    [(\LAMBDA\ \TYF\ \TYS\ \{ \INSTRUCTIONONE \} ; \INSTRUCTION),\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, (\{\INSTRUCTIONONE\}, \TLAMBDA\ \TYF\ \rightarrow\ \TYS) \STACKCONCAT\STACK, \PREDICATE]}
-\end{mathpar}
-
-\paragraph{Stack Manipulation}
-%DIG
-\begin{mathpar}
-\inferrule[DIG]
-  {
-   \FLEN(\A) \EQ\ \N
-  }
-  {[(\DIG\ \N ; \INSTRUCTION), \A\ \At\ (\StackOne, \TY) \STACKCONCAT\B, \PREDICATE] \StateTrans 
-[\INSTRUCTION, (\StackOne, \TY) \STACKCONCAT\A\ \At\ \B, \PREDICATE]}
-\end{mathpar}
-
-%DIP
-\begin{mathpar}
-  \inferrule[DIP]
-  {
-    [\INSTRUCTIONONE,  \STACK, Q]
-    \StateTrans^*
-    [\EMPTYSTACK,  \STACK_1, Q']
-  }
-  {[(\DIP\ \INSTRUCTIONONE; \INSTRUCTION), (\StackOne, \TY) \STACKCONCAT
-    \STACK, \PREDICATE \wedge Q]
-    \StateTrans 
-    [\INSTRUCTION, (\StackOne, \TY) \STACKCONCAT\STACK_1,
-    \PREDICATE \wedge Q']
-  }
-\end{mathpar}
-
-%DIP n
-\begin{mathpar}
-\inferrule[DIP n]
-  { 
-     \FLEN(\A) \EQ\ \N \\ [\INSTRUCTIONONE,  \B, Q]
-    \StateTrans^*
-    [\EMPTYSTACK,  \B_1, Q']
-  }
-  {[(\DIP\ \N\ \INSTRUCTIONONE; \INSTRUCTION), \A\ \At\ \B, \PREDICATE \wedge Q] \StateTrans 
-[(\INSTRUCTION), \A\ \At\ \B_1, \PREDICATE \wedge Q']}
-\end{mathpar}
-
-%PUSH
-\begin{mathpar}
-  \inferrule[PUSH]
-  {  
-  }{
-    [(\PUSH\ \TY\ \X; \INSTRUCTION),\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, (\X, \TY) \STACKCONCAT\STACK, \PREDICATE]}
-\end{mathpar}
-
-\paragraph{Arithmetic operations}
-%ADD
-\begin{mathpar}
-\inferrule[ADD]
-  {
-  }
-  {[(\ADD; \INSTRUCTION), (\StackOne, \TNAT) \STACKCONCAT(\StackTwo, \TNAT) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\X, \TNAT) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\X\ \EQ\ \StackOne\ \PLUS\ \StackTwo)]}
-\end{mathpar}
-
-%ABS
-\begin{mathpar}
-\inferrule[ABS]
-  {
-  }
-  {
-    [(\ABS; \INSTRUCTION), (\StackOne, \TINT) \STACKCONCAT \STACK,
-    \PREDICATE]
-    \StateTrans \
-    [\INSTRUCTION, (\X, \TNAT) \STACKCONCAT \STACK,
-    \PREDICATE \wedge (\StackOne \ge 0 \Rightarrow \X =
-    \StackOne) \wedge (\StackOne <0 \Rightarrow \X = -\StackOne)]
- }
-\end{mathpar}
-
-% COMPARE
-\begin{mathpar}
-\inferrule[COMPARE-nat]
-  {
-  }
-  {
-    [(\COMPARE ; \INSTRUCTION), (\StackOne, \TNAT) \STACKCONCAT (\StackTwo, \TNAT)
-    \STACKCONCAT \STACK, \PREDICATE ]
-    \SystemTrans \\
-    [\INSTRUCTION, (\X, \TINT) \STACKCONCAT \STACK, \PREDICATE
-    \wedge\ (\StackOne > \StackTwo \Leftrightarrow \X = 1)
-    \wedge\ (\StackOne = \StackTwo \Leftrightarrow \X = 0) 
-    \wedge\ (\StackOne < \StackTwo \Leftrightarrow \X = -1)]
-    }
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[COMPARE-some-some]
-  {
-  [\COMPARE,  (\X, \TY) \STACKCONCAT (\Y, \TY) \STACKCONCAT\EMPTYSTACK, Q]
-    \StateTrans^*
-    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
-  }
-  {
-    [(\COMPARE ; \INSTRUCTION), (\StackOne, \TOPTION\ \TY) \STACKCONCAT (\StackTwo, \TOPTION\ \TY)
-    \STACKCONCAT \STACK, \PREDICATE \wedge Q]
-    \SystemTrans \\
-    [\INSTRUCTION, (\VariableA, \TINT) \STACKCONCAT \STACK,  \PREDICATE
-    \wedge (\StackOne\ \EQ\ \SOME\ \X)
-    \wedge (\StackTwo\ \EQ\ \SOME\ \Y)
-    \wedge Q']
-    }
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[COMPARE-some-none]
-  {
-  }
-  {
-    [(\COMPARE ; \INSTRUCTION), (\StackOne, \TOPTION\ \TY) \STACKCONCAT (\StackTwo, \TOPTION\ \TY)
-    \STACKCONCAT \STACK, \PREDICATE]
-    \SystemTrans \\
-    [\INSTRUCTION, (1, \TINT) \STACKCONCAT \STACK,  \PREDICATE
-    \wedge (\StackOne\ \EQ\ \SOME\ \X)
-    \wedge (\StackTwo\ \EQ\ \NONE)
-    ]
-    }
-\end{mathpar}
-
-\paragraph{Boolean operations}
-%XOR
-\begin{mathpar}
-\inferrule[XOR]
-  {
-  }
-  {[(\XOR; \INSTRUCTION), (\StackOne, \TBOOL) \STACKCONCAT(\StackTwo, \TBOOL) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\X, \TBOOL) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\X\ \EQ\ \StackOne\ \FXOR\ \StackTwo)]}
-\end{mathpar}
-
-\paragraph{Crytographic oprerations}
-%HASH-KEY
-\begin{mathpar}
-\inferrule[HASH-KEY]
-  {
-  }
-  {[(\HASHKEY; \INSTRUCTION), (\StackOne, \TBYTE) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\X, \TBYTE) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\X\ = \FHASHKEY(\StackOne))]}
-\end{mathpar}
-
-%AMOUNT
-\paragraph{Blockchain operations}
-\begin{mathpar}
-\inferrule[AMOUNT]
-  {
-  }
-  {[(\AMOUNT; \INSTRUCTION), \STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\CAMOUNT, \TMUTEZ) \STACKCONCAT\STACK, \PREDICATE}
-\end{mathpar}
-
-%CONTRACT ty
-\begin{mathpar}
-\inferrule[CONTRACT TY - some]
-  {
-  }
-  {[(\CONTRACT\ \TY ; \INSTRUCTION), (\StackOne, \TADDR) \STACKCONCAT\STACK, \PREDICATE] \SystemTrans \
-[\INSTRUCTION, (\SOME\ \X, \TOPTION\ (\TCONTRACT\ \TY)) \STACKCONCAT\STACK, \\ \PREDICATE \Wedge\ (\GETCONTRACTTYPE(\StackOne, \TY) \EQ\ \SOME\ \X)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[CONTRACT TY - none]
-  {
-  }
-  {[(\CONTRACT\ \TY ; \INSTRUCTION), (\StackOne, \TADDR) \STACKCONCAT\STACK, \PREDICATE] \SystemTrans \
-[\INSTRUCTION, \NONE \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\GETCONTRACTTYPE(\StackOne, \TY) = \NONE]}
-\end{mathpar}
-
-\paragraph{Operations on data structures}
-%CAR
-\begin{mathpar}
-\inferrule[\CAR]
-  {
-  }
-  {[(\CAR; \INSTRUCTION), (\StackOne, \TPAIR\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\X, \TYF) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQ\ \PAIR\ \X\ \Y)]}
-\end{mathpar}
-
-\subsubsection{Branch Instructions}
-%IF
-
-\begin{mathpar}
-  \inferrule[IF]
-  {  
-  }{
-    \{[(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]\} \cup \SYSTEM 
-      \SystemTrans 
-    \{[\INSTRUCTIONONE, \STACK, \PREDICATE\ \Wedge\ \StackOne]\} \cup \{ [\INSTRUCTIONTWO, \STACK, \PREDICATE\ \Wedge\ \NEG\
-   \StackOne]\} \cup  \SYSTEM
-  }
-\end{mathpar}
-
-The \IFLEFT\ \INSTRUCTIONONE\  \INSTRUCTIONTWO\ instruction expects a or value at the top of the stack, it consumes this top element.
-If the value is Left, it executes the first provided sequence; otherwise, it executes the second sequence.
-%IF-LEFT
-\begin{mathpar}
-  \inferrule[IF-LEFT]
-  {  
-  }{
-    \{[(\IFLEFT\ \INSTRUCTIONONE\ \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]\}  \cup  \SYSTEM
-    \SystemTrans \\
-    \{[\INSTRUCTIONONE, (\X, \TYF) \STACKCONCAT\STACK,
-    \PREDICATE \wedge (\StackOne\ \EQ\ \LEFT\ \X)]\}  \cup  \{  [\INSTRUCTIONTWO, (\X, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQ\ \RIGHT\ \X))]\} \cup \SYSTEM
-  }
-\end{mathpar}
-%IF_CONS
-\begin{mathpar}
-  \inferrule[IF-CONS-empty]
-  {  
-  }{
-    [(\IFCONS\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\  [\INSTRUCTIONTWO; \INSTRUCTION, \STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQ\ \EMPTYLIST)]}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[IF-CONS-nonempty]
-  {  
-  }{
-   [(\IFCONS\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\  \\ [\INSTRUCTIONONE, (\HEAD, \TY) \STACKCONCAT(\{ \TAIL \}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ ( \StackOne\ \EQ\ \{\HEAD; \STAIL \})]}
-\end{mathpar}
-
-%IF_NON
-\begin{mathpar}
-  \inferrule[IF-NONE-none]
-  {  
-  }{
-    [(\IFNONE\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),  (\StackOne, \TOPTION\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\   [\INSTRUCTIONONE; \INSTRUCTION, \STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQ\ \NONE)]}
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[IF-NONE-some]
-  {  
-  }{
-    [(\IFNONE\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),   (\StackOne, \TOPTION\ \TY) \STACKCONCAT\STACK, \PREDICATE], \SYSTEM\ \StateTrans\   [\INSTRUCTIONTWO,  (\X, \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ ( \StackOne\ \EQ\ \SOME\ \X)]}
-\end{mathpar}
-
-\subsubsection{Loop Instructions}
-\paragraph{While loops}
-%LOOP
-\begin{mathpar}
-  \inferrule[LOOP-true]
-  {  
-  }{
-    [(\LOOP\ \INSTRUCTIONONE; \INSTRUCTION),  (\StackOne, \TBOOL)
-    \STACKCONCAT\STACK, \PREDICATE]
-    \StateTrans\
-    [(\INSTRUCTIONONE; \LOOP\ \INSTRUCTIONONE; \INSTRUCTION),
-    \STACK, \PREDICATE \wedge \StackOne]
-  }
-
-  \inferrule[LOOP-false]
-  {  
-  }{
-    [(\LOOP\ \INSTRUCTIONONE; \INSTRUCTION),  (\StackOne, \TBOOL) \STACKCONCAT\
-    \STACK, \PREDICATE]
-    \StateTrans\
-   [\INSTRUCTION, \STACK, \PREDICATE \wedge
-   (\NEG\StackOne)]
-   }
-\end{mathpar}
-\paragraph{For loops}
-%%ITER
-\begin{mathpar}
-  \inferrule[ITER-empty]
-  {  
-  }{
-    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, \STACK,  \PREDICATE\ \Wedge\  (\StackOne\ \EQ\ \EMPTYLIST)]
-  }
-\end{mathpar}
-
-\begin{mathpar}
-  \inferrule[ITER-nonempty]
-  {  [\ITER,  (\HEAD, \TY) \STACKCONCAT\STACK, 
-    Q]
-    \StateTrans^*
-    [ \EMPTYSTACK,  \STACK', Q']
-  }{
-    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE \wedge Q] \StateTrans \\ [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), \{\STAIL\}\ \STACKCONCAT\STACK',  \PREDICATE \wedge Q' \Wedge  ( \StackOne\ \EQ\ \{\HEAD; \STAIL \}) ]
-  }
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[CONCAT]
-  {
-  }
-  {[(\CONCAT; \INSTRUCTION), (\StackOne, \TYLIST\ \TSTR) \STACKCONCAT\STACK,  \PREDICATE] \StateTrans 
-[\INSTRUCTION,  ("",  \TSTR) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQ\ \EMPTYLIST)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[CONCAT]
-  {
-  [\CONCAT,  (\{\TAIL\}, \TYLIST\ \TSTR) \STACKCONCAT\EMPTYSTACK, Q]
-    \StateTrans^*
-    [\EMPTYSTACK, (\StackTwo,  \TSTR) \STACKCONCAT\EMPTYSTACK, Q']
-  }
-  {[(\CONCAT; \INSTRUCTION),  (\StackOne, \TYLIST\ \TSTR) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans \\
-[\INSTRUCTION, ( \HEAD\ \STRINGCONCAT\ \StackTwo, \TSTR) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQ\ \{\HEAD; \TAIL\}) \Wedge\ Q']}
-\end{mathpar}
-
-%MEM
-\begin{mathpar}
-\inferrule[MEM-empty]
-  {
-  }
-  {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\FALSE, \TBOOL) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackTwo\ \EQ\ \EMPTYSET)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[MEM-nonempty]
-  {
-  [\COMPARE, (\StackOne, \TYF) \STACKCONCAT (\K, \TYF) \STACKCONCAT\EMPTYSTACK, Q]
-    \StateTrans^*
-    [\EMPTYSTACK,  (\VariableB, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
-  }
-  {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans  \
-[\MEM; \INSTRUCTION, \StackOne\ \STACKCONCAT\{\LESS\ \M\ \MORE\} \STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackTwo\ \EQ\ \{\ELT\ \K\ \V; \LESS\ \M\ \MORE\})  \Wedge\ (\VariableB\ \EQ\ \ONE)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[MEM-nonempty]
-  {
-  [\COMPARE, (\StackOne, \TYF) \STACKCONCAT (\K, \TYF) \STACKCONCAT\EMPTYSTACK, Q]
-    \StateTrans^*
-    [\EMPTYSTACK,  (\VariableB, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
-  }
-  {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans  \\
-[\INSTRUCTION, (\TRUE, \TBOOL) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackTwo\ \EQ\ \{\ELT\ \K\ \V; \LESS\ \M\ \MORE\}) \Wedge\ (\VariableB\ \EQ\ \ZERO)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[MEM-nonempty]
-  {
-  [\COMPARE, (\StackOne, \TYF) \STACKCONCAT (\K, \TYF) \STACKCONCAT\EMPTYSTACK, Q]
-    \StateTrans^*
-    [\EMPTYSTACK,  (\VariableB, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
-  }
-  {[(\MEM; \INSTRUCTION), (\StackOne, \TYF) \STACKCONCAT(\StackTwo, \TYMAP\ \TYF\ \TYS) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \StateTrans  \\
-[\INSTRUCTION, (\FALSE, \TBOOL) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackTwo\ \EQ\ \{\ELT\ \K\ \V; \LESS\ \M\ \MORE\})  \Wedge\ (\VariableB\ \EQ\ \MINUS\ \ONE)]}
-\end{mathpar}
-
-%MAP
-\begin{mathpar}
-\inferrule[MAP-empty]
-  {
-  }
-  {[(\MAP\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQ\ \EMPTYLIST)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[MAP-nonempty]
-  {
-  [\INSTRUCTIONONE, (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q1]
-    \StateTrans^*
-    [\EMPTYSTACK,  (\PHEAD, \TY) \STACKCONCAT\EMPTYSTACK , Q1'] \\  [\MAP\ \INSTRUCTIONONE, (\{\TAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK , Q2]
-    \StateTrans^*
-    [\EMPTYSTACK,  (\{\PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK , Q2']
-  }
-  {[(\MAP\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1 \Wedge\ Q2 ] \StateTrans  \\
-[\INSTRUCTION, (\{\PHEAD; \PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1' \Wedge\ Q2'  \Wedge\ (\StackOne \EQ\ \{\HEAD; \TAIL\})]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[UPDATE-empty-true]
-  {
-  }
-  {[(\UPDATE; \INSTRUCTION), (\X, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE]\ \SystemTrans\  \\ [\INSTRUCTION, (\{\X \}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\  \Wedge\ (\StackOne\ \EQ\ \EMPTYLIST) \Wedge\ (\VariableB\ \EQ\ \TRUE)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[UPDATE-empty-false]
-  {
-  }
-  {[(\UPDATE; \INSTRUCTION), (\X, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE]\ \SystemTrans\  \\ [\INSTRUCTION, (\EMPTYLIST, \TYLIST\ \TY)\ \STACKCONCAT\STACK, \PREDICATE\  \Wedge\ (\StackOne\ \EQ\ \EMPTYLIST) \Wedge\ (\VariableB\ \EQ\ \FALSE)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[UPDATE-nonempty-true]
-  {
-  [\COMPARE, (\X, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
-    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
-  }
-  {[(\UPDATE; \INSTRUCTION), (\X, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans
-[\INSTRUCTION, (\StackOne, \TYLIST\ \TY)
-\STACKCONCAT\STACK,\\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQ\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQ\ \TRUE) \Wedge\ (\VariableA\ \EQ\ \ZERO)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[UPDATE-nonempty-false]
-  {
-  [\COMPARE, (\X, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
-    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
-  }
-  {[(\UPDATE; \INSTRUCTION), (\X, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans  \\
-[\INSTRUCTION, (\{\TAIL\}, \TYLIST\ \TY)
-\STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQ\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQ\ \FALSE) \Wedge\ (\VariableA\ \EQ\ \ZERO)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[UPDATE-nonempty-true]
-  {
-  [\COMPARE, (\X, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
-    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
-  }
-  {[(\UPDATE; \INSTRUCTION), (\X, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans  \\
-[\INSTRUCTION, (\{\X; \HEAD; \TAIL\}, \TYLIST\ \TY)
-\STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQ\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQ\ \TRUE) \Wedge\ (\VariableA\ \EQ\ \MINUS\ \ONE)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[UPDATE-nonempty-false]
-  {
-  [\COMPARE, (\X, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q] \StateTrans^*
-    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q']
-  }
-  {[(\UPDATE; \INSTRUCTION), (\X, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q] \SystemTrans\  \\
-[\INSTRUCTION, (\{\HEAD; \TAIL\}, \TYLIST\ \TY)
-\STACKCONCAT\STACK, \\ \PREDICATE\ \Wedge\ Q' \Wedge\ (\StackOne\ \EQ\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableB\ \EQ\ \FALSE) \Wedge\ (\VariableA\ \EQ\ \MINUS\ \ONE)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[UPDATE-nonempty-1]
-  {
-  [\COMPARE, (\X, \TY) \STACKCONCAT (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q1] \StateTrans^*
-    [\EMPTYSTACK,  (\VariableA, \TINT) \STACKCONCAT\EMPTYSTACK, Q1'] \\
- [\UPDATE, (\X, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT( \{\TAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK, Q2] \StateTrans^* \\  [\EMPTYSTACK, ( \{\PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK, Q2']
-  }
-  {[(\UPDATE; \INSTRUCTION), (\X, \TY) \STACKCONCAT(\VariableB, \TBOOL) \STACKCONCAT(\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1 \Wedge\ Q2 ] \SystemTrans\  \\
-[\INSTRUCTION; (\{\HEAD; \PTAIL\}, \TYLIST\ \TY)
-\STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1' \Wedge\ Q2' \Wedge\ (\StackOne\ \EQ\ \{\HEAD; \TAIL\}) \Wedge\ (\VariableA\ \EQ\ \ONE)]}
-\end{mathpar}
-
-\subsubsection{Operation on tickets}
-\subsubsection{FAILWITH}
-a Michelson program can fail, explicitly using a specific opcode
-
-%FAILWITH
-\begin{mathpar}
-  \inferrule[FAILWITH]
-  {
-  }{[(\FAILWITH; \INSTRUCTION), (\StackOne,  \TY) \STACKCONCAT \STACK,  \PREDICATE] \StateTrans [\EMPTYSTACK, failwith (\StackOne) \STACKCONCAT\EMPTYSTACK, \PREDICATE]}
-\end{mathpar}
-\subsection{Dealing with loops}
-\subsubsection{For loop: ITER}
-Semantic
-
-\begin{mathpar}
-  \inferrule{
-  }{
-    \ITER\ \INSTRUCTION\ / \{ \} \STACKCONCAT\ \STACK\ \SRightarrow\  \STACK
-    }
-\end{mathpar}
-
-\begin{mathpar} 
-  \inferrule{\INSTRUCTION\  /  \X\ \STACKCONCAT\ \STACK \SRightarrow\ \STACK'
-  }{
-    \ITER\ \INSTRUCTION\ / \{ \X\ ; \TAIL\ \} \STACKCONCAT\ \STACK\ \SRightarrow\ \ITER\ \INSTRUCTION\ / \{ \TAIL\ \} \STACKCONCAT\ \STACK' 
-    }
-\end{mathpar}
-\subsubsection{While loops: \LOOP\ and \LOOP-LEFT}
-
 \end{document}

### 2023-12-14 papers/static-checker/ecoop2024/ecoop2024.tex
write static checker part

@@
 \section {Domain Specific Language For Smart Contract Property Specification}
+\label{sec:domain-specific-language}
 Michelson, as a stack-based language, may pose a challenge for developers less familiar with it compared to more mainstream languages like Python, Java, or C.
@@
 The detail of the language grammar is described in in Figure \ref{}.
+Formulas that are used in assertions or added to solvers are terms of Boolean sort.
+Otherwise, terms of Boolean and non-Boolean sort may be mixed in any combination where sorts match up.
+Universal and existential quantifiers bind variables to the scope of the quantified formula.
 
@@
 \section {Static Checker}
-The architect of the static checker is depicted as in Figure \ref{}.  The system includes
+We verify the contract through symbolic execution against its specifications in the contract module.
+Symbolic execution involves calculating a symbolic stack at each transition from one Michelson instruction to the next.
+The symbolic interpreter is fully typed and rejects ill-typed Michelson programs, provided the ill-typed part is reachable from the default entry point.
+The initial stack is derived from the input pattern for each the entry point.
+To maintain symbolic values as concrete as possible, some instructions may be deemed unreachable or only reachable under specific conditions.
+This process yields, for each entry point, a set of final symbolic stacks accompanied by a path condition indicating when this final state is reachable.
+A state is discarded from the final state space if the path condition is not satisfied, indicating that the path is unreachable.
+Additionally, for each \FAILWITH\ instruction, we obtain a symbolic value for the reported message and a path condition indicating the reachability of this instruction.
+We employ the SMT solver Z3  to assess the feasibility of a path condition and to check smart contract properies specifying by pre and post conditions.
 
-Formulas that are used in assertions or added to solvers are terms of Boolean sort.
-Otherwise, terms of Boolean and non-Boolean sort may be mixed in any combination where sorts match up.
-Universal and existential quantifiers bind variables to the scope of the quantified formula.
+The architecture of the static checker is illustrated in Figure \ref{}.
+The system comprises three phases.
+The first phase involves user specification, where users provide the Michelson code of the contract and define the properties that the smart contract should satisfy.
+Subsequently, the code, along with the input pattern, is input to the interpreter to achieve symbolic execution.
+The path conditions are then fed into a Z3 converter, which transforms these symbolic terms into Z3 formulas.
+Concurrently, the property specification, specifically pre and post conditions, also undergoes conversion to Z3 formulas in the intermediate phase.
+The results of the symbolic execution and Z3 formulas are then input into the static checker, which verifies whether these properties hold for the smart contract implementation.
+This constitutes the verification phase.
+
+\subsection{User specification}
+In the user specification phase, users compose the specification in our domain-specific language using the syntax outlined in Section \ref{sec:domain-specific-language}.
+Note that Michelson code, whether authored by users, obtained from the Tezos blockchain, or compiled from higher-level languages, can be seamlessly employed within our framework.
+The specification is subsequently parsed into an Abstract Syntax Tree (AST) in OCaml.
+The code and the input pattern are then utilized as inputs for the interpreter during the intermediate phase to facilitate symbolic execution.
+In the next phase, the pre and post predicates are transformed into Z3 formulas by the Z3 converter tool.
+\subsection{Michelson interpreter and Z3 converter}
+The interpreter implements the execution model described in \ref{sec:symbolic-execution-model}.
+When provided with a concrete input, the interpreter produces a concrete value.
+In the presence of symbolic input, the result comprises a set of symbolic states represented as terms in OCaml.
+Due to Michelson being built in OCaml, the conversion of Michelson types or terms to their OCaml counterparts is straightforward.
+Each state contains the output stack, which has only one element consisting of an operation list and storage, along with the path conditions represented as predicates in conjunctive form.
+This output is then fed into the Z3 converter, which handles two different types of terms: assertion terms from the AST representing the pre and post-condition specifications, and terms resulting from the interpreter.
+We utilize the Z3 library in OCaml to construct this converter.
+Some adjustments are necessary to convert these terms into Z3 formulas.
+For example, as there is no natural number type (\TNAT) in Z3, the term is converted as an integer type, accompanied by constraints asserting that it is greater than or equal to zero.
+Several constants, such as \CAMOUNT, \CBALANCE, \CSENDER\ and cryptographic functions, such as \FSHA, \FHASHKEY\ are predefined in the environment that works for any smart contract specifications.
+\subsection{Static checker}
+The static checker now performs the verification process by employing symbolic execution against the property specification in the DSL.
+It utilizes the results from the previous phases, including symbolic execution, Z3 formulas representing pre and post conditions, and path conditions.
+The static checker performs three distinct features: the output check, fail condition and property check.
+
+\subsubsection{Output check} First is the output check, where the checker verifies whether the output pattern matches.
+It basiclly matches the output pattern with the correcspoding part in the final states resulting from the symbolic intepreter.
+When the input pattern is a concrete value, the checker can be used as a test to verify if the output aligns with the expectations specified in the output field.
+
+\subsubsection{Fail condition}
+
+\subsubsection{Property check}
+
+consider the code is as a black box
 \section {Case Studies}

### 2023-12-15 papers/static-checker/ecoop2024/ecoop2024.tex
write the static checker part

@@
 Universal and existential quantifiers bind variables to the scope of the quantified formula.
-
-Let's consider the following example of the property specification for the contract named Add:
-\begin{lstlisting}[float,captionpos=b,caption={The specification of Add contracr},label={lst:safer-contract-module},numbers=left]
+\begin{lstlisting}[float,captionpos=b,caption={The specification of Add contracr},label={lst:add-contract-specification},numbers=left]
 mcontract Add = spec
@@
 \end{lstlisting}
+Let's consider the  example of the property specification for the contract named Add as in Listing \ref{lst:add-contract-specification}.
 Here, the program takes as input a stack with only one element, which is a pair of two integers, symbolically specified in the Input field.
@@
 
-To illustrate this, let's consider the following auction smart contract.
-This contract has two entrypoints, bid and close, which serve as functions for bidding and closing the contract, respectively.
+To illustrate this, let's consider the  auction smart contract serving the auction events.
+The contract has two entrypoints, bid and close, which serve as functions for bidding and closing the contract, respectively.
 The smart contract storage on the blockchain is a pair containing the first element as a boolean value that indicates whether the contract is still open for bidding or already closed.
@@
 It utilizes the results from the previous phases, including symbolic execution, Z3 formulas representing pre and post conditions, and path conditions.
-The static checker performs three distinct features: the output check, fail condition and property check.
-
-\subsubsection{Output check} First is the output check, where the checker verifies whether the output pattern matches.
-It basiclly matches the output pattern with the correcspoding part in the final states resulting from the symbolic intepreter.
-When the input pattern is a concrete value, the checker can be used as a test to verify if the output aligns with the expectations specified in the output field.
+
+What the tool does is first build the input state from the input pattern, runs the symbolic interpreter on the input stack with the provided code to generate all symbolic execution states.
+It's important to note that all states are reachable from the initial state, as any unreachable states are discarded from the final state spaces using the Z3 solver to check the path condition predicate.
+Using the output pattern and the pre- and post-conditions converted by the Z3 conveter, the tool then performs different checks.
+The static checker offers three distinct features: output check, fail condition, and property check.
+
+\subsubsection{Output check} 
+The first check is the output check, where the checker verifies whether the output pattern matches.
+The final state contains a stack with only one element as \Stack\ \STACKCONCAT\ \EMPTYSTACK.
+There are two different forms of the final state.
+In the case where the code is given as incomplete smart contract code, the element \Stack\ contains just a normal term and its corresponding type as (\Term, \TY).
+However, in the case of a complete smart contract code, it has the form (\PAIR\ \VOPERATIONLIST\ \VSTORAGE, \TPAIR\ (\TOPERATIONLIST) \TYS) \STACKCONCAT\ \EMPTYSTACK, where \VSTORAGE\ is the term represting the storage and \VOPERATIONLIST\ repesents a operation list.
+Given an output pattern $ \tau$, the checker scans all the final states, which does not contain a failwith stack and checks whether the output pattern matches.
+In the former case, it matches $ \tau$  with the term \Term.
+In the latter case, it essentially matches with the corresponding part \VSTORAGE\ in the final states resulting from the symbolic interpreter.
+When the input pattern is a concrete value, the result from the interpreter is also concrete, and then the checker can be used as a test to verify if the output aligns with the expectations specified in the output field.
+
+Lets get back to the example in Listing \ref{lst:add-contract-specification}.
+This is an example of incomplete smart contract code.
+The specification states that the output of the code must be a stack that contains only one element of type \TINT\ as symbolicly representing as a variable \VZ\ of type \TINT.
+In this example, there are two final states, with the first one being a failwith state recording the failwith condition when the first element of the pair is less than the second element.
+The failwith state contains the message 'Unexpected Pair,' describing the reason for the failure.
+The second state is a reachable state that contains, at the top element, an integer value, which is the sum of the two elements of the pair.
+The tool results in \TRUE\ for the output check for this example, as expected by the code.
+However, this test could fail if, for example, the output pattern is incorrectly specified as a variable of type \TSTRING, \TMUTEZ, or even \TNAT, as the types wouldn't match with the actual result.
+If the input pattern is concrete, for instance, a pair of numbers 5 and 3 as Pair 5 3, then the expected output should be the number 8.
+This can be verified if the output pattern is also specified as a concrete value.
+
+The second example in Listing \ref{lst:auction-contract-specification} is the specification for a smart contract code.
+The output pattern represents the updated storage after executing the code.
+There are several final states resulting from the symbolic execution.
+The failwith state is ignored for the output check, and all other reachable states are matched with the output term.
+The result is \TRUE\ for this example.
 
 \subsubsection{Fail condition}
+A Michelson contract can fail due to a programmer-induced condition caused by the instruction \FAILWITH.
+It terminates contract execution with an error message reported back to the caller.
+This error message includes the top value on the stack.
+These failures are important in smart contract programming to guarantee that a smart contract call should not be successful under specific circumstances.
+Smart contract calls are expected to fail due to malicious behavior, such as an unauthorized caller or invalid arguments passed along the call.
+For example, the auction contract should not be closed by someone who is not the owner of the contract, and the bidding should not succeed if the bid is not strictly higher than the current highest bid.
+Several smart contract standards, such as , require the contract to fail with specific messages under some conditions.
+Therefore, it is essential to check the fail conditions of a contract.
+
+The static checker provides a feature to generate all fail conditions implemented in a smart contract code.
+The tool searches for all failwith states, resulting from an execution terminated by the \FAILWITH\ instruction, from the final state space, collects the path conditions and the recorded message.
+The result returned to users includes the fail condition together with the message.
+For example, for the specification in Listing \ref{lst:add-contract-specification}, the fail condition is recorded as \lstinline/(x < y): 'Unexpected Pair'/.
+For the auction contract, there are several fail conditions.
+For the entrypoint \lstinline/bid/, the fail condition is as shown in Listing \ref{lst:fail-condition-auction-contract-bid} and for the \lstinline/close/ entrypoint, it is recorded in Listing \ref{}.
+
+\begin{lstlisting}[float,captionpos=b,caption={Auction contract specification},label={lst:fail-condition-auction-contract},numbers=left]
+1. not (auction_open): 'Already closed'
+2. (auction_open = true) &&
+(Amount <= Balance): 'Not higher than the current highest bid'
+3. (auction_open = true) &&
+(Amount <= Balance) &&
+get_contract (Unit, highest_bidder) = None: 'Invalid address' 
+\end{lstlisting}
 

### 2023-12-18 papers/static-checker/ecoop2024/ecoop2024.tex
write the property check

@@
 output := (z : int)
-pre-condition := (x >= 5) | (y >= 3)
+pre-condition := (x >= 5) | (y > 3)
 post-condition := (z >= 8)
@@
     input := Pair Unit (Pair (auction_open: bool) 
-                             (Pair (highest_bidder: mutez)
+                             (Pair (highest_bidder: address)
                                    (contract_owner: address)))
@@
 Several constants, such as \CAMOUNT, \CBALANCE, \CSENDER\ and cryptographic functions, such as \FSHA, \FHASHKEY\ are predefined in the environment that works for any smart contract specifications.
+
+\paragraph{Dealing with loop formalization}
+As mentioned earlier, our execution model formalizes loops symbolically using the \FOLD\ and \FMAP\ functions.
+This approach has the advantage of allowing us to convert these loops into formulas compatible with certain SMT solvers, such as Z3, which support these functions.
+Specifically, Z3 provides \lstinline/seq.map fn s/, a map function on sequence \lstinline/s/, and \lstinline/(seq.foldl fn b s)/, a fold function with an initial value \lstinline/b/ on sequence \lstinline/s/.
+These functions are supported for checking assertions that contain them.
+Therefore, we can directly convert the symbolic results of loops into formulas in Z3.
 \subsection{Static checker}
@@
 For example, for the specification in Listing \ref{lst:add-contract-specification}, the fail condition is recorded as \lstinline/(x < y): 'Unexpected Pair'/.
+
 For the auction contract, there are several fail conditions.
-For the entrypoint \lstinline/bid/, the fail condition is as shown in Listing \ref{lst:fail-condition-auction-contract-bid} and for the \lstinline/close/ entrypoint, it is recorded in Listing \ref{}.
-
-\begin{lstlisting}[float,captionpos=b,caption={Auction contract specification},label={lst:fail-condition-auction-contract},numbers=left]
+For the entrypoint \lstinline/bid/, the fail condition is as shown in Listing \ref{lst:fail-condition-auction-contract-bid} and for the \lstinline/close/ entrypoint, it is recorded in Listing \ref{lst:fail-condition-auction-contract-close}.
+For the \lstinline/bid/ entrypoint, there are three fail conditions.
+First is if the auction is closed, and then if it is not, the contract checks if the amount is greater than the balance.
+If not, the call fails as well.
+The last fail happens when the auction is open, the amount is greater than the balance, but the highest bidder's address is invalid.
+Note that there are several addresses that are valid as Michelson addresses but are not associated with any real account on the Tezos blockchain, or the parameter's type is not correct, while the transfer can only succeed if it is the given parameter and the address is associated with an account with the correct parameter on the Tezos blockchain.
+Bidding returns the previous highest bid as part of the transaction where the highest bidder is stored as a value of type address.
+However, to receive a token transfer, this address must be cast (by the Michelson implementation of the contract) to an implicit contract of Michelson type (\TCONTRACT\ \TUNIT).
+This cast is unavoidable, as a value of contract type cannot be stored.
+However, the cast may fail, and its failure leads to an error condition that is reported with a \FAILWITH\ instruction in this implementation.
+In our framework, this cast fail case is shown in the fail condition, but in the user preconditions, it assumes that they are successfully casted.
+The \lstinline/close/ entrypoint has similar fail conditions when the auction is closed or the owner's address is uncastable.
+But the other fail condition is when the auction is open, but the sender who calls this entrypoint is not the owner of the contract, which was stored in the contract owner part.
+
+\begin{lstlisting}[float,captionpos=b,caption={Fail condition for Auction contract bid entrypoint },label={lst:fail-condition-auction-contract-bid},numbers=left]
 1. not (auction_open): 'Already closed'
@@
 
+\begin{lstlisting}[float,captionpos=b,caption={Fail condition for Auction contract close entrypoint},label={lst:fail-condition-auction-contract-close},numbers=left]
+1. Not (auction_open): 'Already closed'
+2. (auction_open = true) &&
+Sender != contract_owner): 'Not owner'
+3.  (auction_open = true) &&
+(Sender = contract_owner) &&
+get_contract (Unit, contract_owner) = None: 'Invalid address'
+\end{lstlisting}
+
+In this implementation of the auction contract, the failures are recorded as expected.
+The contract is designed to fail when the auction is closed, the bid is not greater than the old highest bid, or the caller is not the contract owner when attempting to close the contract as transferring the contract balance to their account as a part of the action.
+
 \subsubsection{Property check}
-
-consider the code is as a black box
+The static checker enables users to verify smart contract properties by providing pre and post condition specifications.
+A property is specified with the following clause:  \lstinline/pre-condtion : =/ $\mid$ $\Phi_{i}$ \lstinline/ post-condtion : =/   $\mid$ $\Psi_{j}$.
+This specification asserts that if all preconditions $\Phi_{i}$ hold before smart contract execution, then all $\Psi_{j}$ must become true after the execution.
+To verify this property, we explore all the paths $\Pi$ with the path condition $\Theta$ such that ($\bigwedge \Phi_{i}$ $\land$ $\Theta$) is satisfiable.
+We then check that for every path $\Pi$, $\neg$ ($\bigwedge \Phi_{i} \rightarrow \bigwedge \Psi_{j}$) is unsatisfiable in the context given by the input for the entry point and its corresponding final state and path condition.
+
+Consider the specification of the Add contract in Listing \ref{lst:add-contract-specification}.
+In this context, the two variables \lstinline/x/ and \lstinline/y/ are integers.
+The results of the symbolic execution are either a failwith state with the path condition as the predicate stating that the variable \lstinline/x/ is less than \lstinline/y/, or a state in which the final stack has only one element, which is a symbolic variable \lstinline/sbvar/ of type integer, with the path condition stating that the variable \lstinline/x/ is greater than or equal to \lstinline/y/ and the symbolic variable \lstinline/sbvar/ is equal to the sum of \lstinline/x/ and \lstinline/y/.
+For this specification, the failwith branch is discarded because the precondition is not satisfy with tha path condition, and then \lstinline/z/ is matched to the symbolic variable \lstinline/sbvar/ in the other branch.
+In this example, the checker then verifies that given the with the context asserting that (\lstinline/x/ >= \lstinline/y/) $\land$ (\lstinline/z/ = \lstinline/x/ + \lstinline/y/), $\neg$ ((\lstinline/x/ >= 5) $\land$ (\lstinline/y/ > 3) $\rightarrow$ (\lstinline/z/ >= 8)) is unsatisfiable.
+
+\subsubsection{Life-cycle check}
 \section {Case Studies}
 \subsection{USDtz}
+
 \subsection{Kolibri Oracle Contract}

### 2023-12-20 papers/static-checker/ecoop2024/ecoop2024.tex
write USDtz section

@@
 \subsection{USDtz}
+In a blockchain ecosystem, tokens represent digital assets that can be transferred between accounts.
+These tokens are securely stored and verified within the blockchain network.
+There are various types of tokens, including native tokens (cryptocurrencies) like Bitcoin, Ether, Tezos, and others.
+Additionally, tokens can be created through smart contracts on an existing blockchain.
+Two common categories are: (1) Fungible Tokens (FT), which are interchangeable and (2) Non-Fungible Tokens (NFTs), which represent unique digital assets, and each unit is distinct.
+Stablecoins, falling under fungible tokens, are designed to maintain a stable value by tracking the value of a fiat currency like USD or EUR.
+
+While you can create tokens that behave in any way that you want them to behave, implementing tokens that adhere to established standards is advisable for interoperability and compatibility across different platforms.
+A Token standard defines a set of rules and an interface that smart contracts must follow to ensure consistency and compatibility with decentralized exchanges, wallets, and other tools within the ecosystem.
+For example, ERC-20 is a standard used in Ethereum for implementing tokens.
+
+Tezos blockchain has its own set of standards called Financial Applications (FA).
+Two popular standards are: (1) FA 1.2, which is designed for fungible tokens, and FA 2, which is more versatile, accommodating both fungible and non-fungible tokens (NFTs).
+The detail of FA 1.2 is published in \ref{}.
+In this section, we verify USDtz \ref{}, which is an implementation of the FA 1.2 standard .
+Our goal is to confirm that the implementation aligns with the standard, ensuring its correctness.
+USDtz is written to the FA token standard and The USDtz smart-contract's initial deployment has been under the FA 1.2 standard.
+
+FA 1.2  includes functions such as transfer (transacting between users), approve (allowing one user to send tokens from another user's address), allowance (checking the amount of tokens available for a specific transaction), user balance (checking the balance of a user), and current supply (checking the total supply of tokens across all addresses).
+A contract which implements approvable ledger must have the following entrypoints:
+
+\begin{lstlisting}[float,captionpos=b,caption={FA 1.2 interface},label={lst:fail-condition-auction-contract-close},numbers=left]
+(address :from, (address :to, nat :value)) %transfer
+(address :spender, nat :value) %approve
+(view (address :owner, address :spender) nat) %getAllowance
+(view (address :owner) nat) %getBalance
+(view unit nat) %getTotalSupply
+\end{lstlisting}
 

### 2023-12-22 papers/static-checker/ecoop2024/ecoop2024.tex
write USD part

--- 2023-12-18 papers/static-checker/ecoop2024/ecoop2024.tex
@@
 Similarly, the output stack is assumed to be a stack with only one element, which is specified in the output field.
-As we have mentioned before, the output should be a pair consisting of an operation list and a storage.
-In our syntax, for verification purpose, we omit the operation list and then the output is represented by the patern of the value in the storage after the execution is finished.
+Our syntax allows to specify incomplete and complete smart contract code.
+For the complete smart contrat code, as we have mentioned before, the output should be a pair consisting of an operation list and a storage.In our syntax, for verification purposes, we exclude the operation list, and the output is solely represented by the pattern of the value in the storage after the execution concludes.
+In fact, for a complete smart contract code, in some cases, the output pattern can be omitted, given that the input pattern must be a pair of parameters and storage.
+This implies that the storage pattern is part of the input pattern.
+In such cases, the prefix 'post' is used before the variables in the input term to indicate the corresponding storage value after the execution.
 The input and output patterns represent Michelson terms, which can be either concrete values or symbolic values, including variables.
@@
 The output term should maintain the required pattern of the storage, where the values may be changed, and these changes are recorded in other symbolic variables.
-In this specification, we add the prefix \lstinline/post/ to the old variable names to represent the new variables corresponding to the old ones.
+In this specification, we add the prefix \lstinline/post/ to the old variable names to represent the new variables corresponding to the old ones.Note that the output pattern here could be safely removed, and the tool will automatically generate the output pattern to match the one specified here.
 
@@
 \subsection{USDtz}
+In a blockchain ecosystem, tokens represent digital assets that can be transferred between accounts.
+These tokens are securely stored and verified within the blockchain network.
+There are various types of tokens, including native tokens (cryptocurrencies) like Bitcoin, Ether, Tezos, and others.
+Additionally, tokens can be created through smart contracts on an existing blockchain.
+Two common categories are: (1) Fungible Tokens (FT), which are interchangeable and (2) Non-Fungible Tokens (NFTs), which represent unique digital assets, and each unit is distinct.
+Stablecoins, falling under fungible tokens, are designed to maintain a stable value by tracking the value of a fiat currency like USD or EUR.
+
+While you can create tokens that behave in any way that you want them to behave, implementing tokens that adhere to established standards is advisable for interoperability and compatibility across different platforms.
+A Token standard defines a set of rules and an interface that smart contracts must follow to ensure consistency and compatibility with decentralized exchanges, wallets, and other tools within the ecosystem.
+For example, ERC-20 is a stoken tandard used in Ethereum.
+
+Tezos blockchain has its own set of standards known as Financial Applications (FA).
+Two notable standards are: (1) FA 1.2, designed for fungible tokens, and (2) FA 2, a more versatile standard accommodating both fungible and non-fungible tokens (NFTs).
+The standard outlines a smart contract that functions as a ledger, associating identities with balances.
+This ledger is designed to facilitate token transfer operations and enable approvals for spending tokens from other accounts.
+Any contract aiming to implement the standard must incorporate the functions specified in Listing \ref{lst:fa12-interface} such as transfer (transacting between users), approve (allowing one user to send tokens from another user's address), allowance (browsing the amount of tokens available for an account to sending from another address), user balance (checking the balance of a user), and current supply (checking the total supply of tokens across all addresses).
+Further elaboration on the details of FA 1.2 can be found in \ref{}, and we will delve into these functions in subsequent sections.
+
+\begin{lstlisting}[float,captionpos=b,caption={FA 1.2 interface},label={lst:fa12-interface},numbers=left]
+(address :from, (address :to, nat :value)) %transfer
+(address :spender, nat :value) %approve
+(view (address :owner, address :spender) nat) %getAllowance
+(view (address :owner) nat) %getBalance
+(view unit nat) %getTotalSupply
+\end{lstlisting}
+
+In this section, we verify USDtz \ref{}, an implementation of the FA 1.2 standard.
+Our goal is to ensure that the implementation aligns with the standard, verifying its correctness.
+USDtz is a stablecoin and one of the first and longest-running coins on the Tezos blockchain, launched in September 2020.
+The smart contract is located at the address KT1LN4LPSqTMS7Sd2CJw4bbDGRkMv2t68Fy9, and the code can be found on the Tezos blockchain \ref{}.
+USDtz adheres to the FA token standard, and the initial deployment of the USDtz smart contract follows the FA 1.2 standard.
+The implementation consists of approximately 1000 instructions.
+It contains all of five entrypoints required in the FA 1.2 interface and four others.
+We will verify this smart contract for each of its entrypoints.
+Let's first examine how the approvable ledger is implemented in the USDtz smart contract.
+The ledger is a substantial map that links user addresses to a pair consisting of their balance and a map associating addresses with the amount of tokens allowed to be transferred from the user's account.
+The storage structure of the USDtz smart contract is illustrated in Listing \ref{lst:storage-udstz-contract}.
+
+\begin{lstlisting}[float,captionpos=b,caption={Storage of the USDtz smart contract},label={lst:storage-udstz-contract},numbers=left]
+  ( pair
+    ( big_map %ledger
+      ( address :user )
+      ( pair ( nat :balance ) ( map :approvals
+        ( address :spender )
+        ( nat :value ) ) ) )
+    ( pair ( address %admin ) 
+           ( pair ( bool %paused ) ( nat %totalSupply ) ) ) ) 
+\end{lstlisting}
+
+\subsubsection{transfer}
+As illustrated in Listing \ref{lst:fa12-interface}, the \lstinline/transfer/ entrypoint credits the account associated with the address provided in the \lstinline/to/ parameter, while debiting the account corresponding to the \lstinline/from/ parameter with the specified \lstinline/value/ amount.
+The FA 1.2 standard mandates that this call must fail under the following two conditions: (1) In the event of insufficient balance, this entrypoint MUST fail with the error \lstinline/NotEnoughBalance/, indicating insufficient funds in the sender's account to execute the transfer.
+The error MUST contain a \lstinline/pair (nat :value) (nat :present)/ pair, where \lstinline/value/ is the requested amount of tokens, and \lstinline/present/ is the available amount.
+(2) If the sender's account has no permission to withdraw the \lstinline/value/ amount of funds, the call will fail with the \lstinline/NotEnoughAllowance/ error, which also contains the same pair message as the first failure scenario.
+To verify these requirements, we unize the failwith condition of the tool and the result return as in Listing \ref{}.
 
 \subsection{Kolibri Oracle Contract}
-\section {Related Work}
 \section {Conclusion}

### 2023-12-22 papers/static-checker/ecoop2024/ecoop2024.tex
Usd tez

@@
 (2) If the sender's account has no permission to withdraw the \lstinline/value/ amount of funds, the call will fail with the \lstinline/NotEnoughAllowance/ error, which also contains the same pair message as the first failure scenario.
-To verify these requirements, we unize the failwith condition of the tool and the result return as in Listing \ref{}.
+To verify these requirements, we utilize the failwith condition feature of the tool and examine the returned results, as outlined in Listing \ref{}.
+
+The fundamental property that this entrypoint should satisfy is the decrement of the allowance of the sender's account by the \lstinline/value/ that has been sent.
+
+\subsubsection{approve}
+
+\subsubsection{getAllowance, getBalance and  getTotalSupply}
+These entrypoints are view entrypoints, and their results, as natural numbers, are sent back to specific addresses, which are smart contracts with entrypoints that have a parameter type of \lstinline/nat/.
+The property is that there should be no modification in the ledger when these entrypoints are called, and the correct information is sent to the users.
 

### 2023-12-27 papers/static-checker/ecoop2024/ecoop2024.tex
write USD tez

--- 2023-12-22 papers/static-checker/ecoop2024/ecoop2024.tex
@@
 This ledger is designed to facilitate token transfer operations and enable approvals for spending tokens from other accounts.
-Any contract aiming to implement the standard must incorporate the functions specified in Listing \ref{lst:fa12-interface} such as transfer (transacting between users), approve (allowing one user to send tokens from another user's address), allowance (browsing the amount of tokens available for an account to sending from another address), user balance (checking the balance of a user), and current supply (checking the total supply of tokens across all addresses).
+Any contract aiming to implement the standard must incorporate the functions specified in Listing \ref{lst:fa12-interface} such as transfer (transacting between users), approve (allowing one user to send tokens from another user's address), allowance (browsing the amount of tokens available for an account to sending from another address), user balance (checking the balance of a user), and current supply (checking the total supply of tokens across all addresses), where \lstinline/view a r = pair a (contract r)/ implies an view entrypoint.
+A view is an entrypoint which represents a computation that takes an argument of type \lstinline/a/ and a callback that result in a value of type \lstinline/r/.
+The callback in this case will be another contract address.
 Further elaboration on the details of FA 1.2 can be found in \ref{}, and we will delve into these functions in subsequent sections.
@@
 (2) If the sender's account has no permission to withdraw the \lstinline/value/ amount of funds, the call will fail with the \lstinline/NotEnoughAllowance/ error, which also contains the same pair message as the first failure scenario.
-To verify these requirements, we unize the failwith condition of the tool and the result return as in Listing \ref{}.
-
+To verify these requirements, we utilize the failwith condition feature of the tool and examine the returned results, as outlined in Listing \ref{}.
+
+The fundamental property that this entrypoint should satisfy is the decrement of the allowance of the sender's account by the \lstinline/value/ that has been sent.
+
+\subsubsection{approve}
+The crucial property to ensure the correctness of the approve entrypoint is that changing the allowance value from a non-zero value to another non-zero value is forbidden to prevent a corresponding attack vector \ref{}.
+The basic idea of this attack is that when a non-zero value update is allowed, the \lstinline/spender/ can attempt to spend the entire allowance before the new amount is updated and then spend again with the new value, resulting in a larger amount than actually allowed.
+This means the contract call must fail when both the parameter \lstinline/value/ is non-zero and the allowance of \lstinline/spender/ is also non-zero.
+We verify this property by generating the fail condition, and the result is that the non-zero value update is recorded as a fail condition, as shown in Listing \ref{}.
+This indicates that the implementation ensure the non-zero value update prevention.
+
+The other property is that in case the update is allowed, then the updated value needs to be recorded correctly in the storage.
+This property can be divided into two subproperties, which can be checked separately.
+The first property is that when the parameter \lstinline/value/ is zero, then the corresponding allowance value of the \lstinline/spender/ from the owner (which is \SENDER\ in this call) should be zero.
+This subproperty is specified as shown in Listing \ref{}.
+The second property is that when \lstinline/value/ is non-zero, requiring the allowance of the \lstinline/spender/ to be zero, then the \lstinline/value/ should be recorded in the storage after the call.
+To check this property, we specify the property as the pre and post conditions, as illustrated in Listing \ref{}.
+
+\subsubsection{getAllowance, getBalance and  getTotalSupply}
+These entrypoints are view entrypoints.
+View entrypoints are functions that retrieve information from the storage but don't make any changes to the smart contract state.
+As Listing \ref{lst:fa12-interface}, the results of these entrypoints are natural numbers, which are sent back to specific addresses, which are smart contracts with entrypoints that have a parameter type of \lstinline/nat/.
+The implementation of a view entrypoint must return the \lstinline/TRANSFER_TOKENS/ operation targeting the contract passed as an argument with precise information, namely the amount of tokens \lstinline/spender/ is allowed to spend from the \lstinline/owner/ for the \lstinline/getAllowance/ entrypoint, the balance of the owner \lstinline/owner/ for the \lstinline/getBalance/ entrypoint, and the total supply for the \lstinline/getTotalSupply/ entrypoint.
+Additionally, the transaction must transfer to the callback contract with an amount equal to \AMOUNT.
+In other words, all the tez passed to a view entrypoint are forwarded to the callback contract.
+Another important property is that there should be no modification in the ledger when these entrypoints are called.
+
+Let us now demonstrate how to verify the \lstinline/getBalance/ entrypoint, as shown in Listing \ref{lst:specification-get-balance} while two other entrypoints \lstinline/getAllowance/ and \lstinline/getTotalSupply/ entrypoints could be similarly specified.
+There are two cases to consider: (1) when the \lstinline/owner/ is in the \lstinline/ledger/ big map and (2) when it is not.
+For the former case, lines 5-8 specify that \lstinline/owner/ is in the \lstinline/ledger/ big map, as the \lstinline/Get_big_map/ function returns a value \lstinline/Some value/ of the \TOPTION\ type, and this \lstinline/value/ is a pair of a natural number \lstinline/k/ and a map \lstinline/m/.
+The post condition guarantees that the storage remains unchanged, as specified in lines 10-13, and the call returns a \lstinline/TRANSFER_TOKENS/ operation with the \lstinline/k/ number and \lstinline/Amount/ to the passed address \lstinline/c/.
+The precondition in lines 16-17 specifies the latter case when the \lstinline/owner/ does not exist in the big map \lstinline/ledger/; in this case, the number \lstinline/0/ should be sent, and again, the storage should remain unchanged.
+
+\begin{lstlisting}[float,captionpos=b,caption={Specification for the \lstinline/getBalance/ entrypoint},label={lst:specification-get-balance},numbers=left]
+Input := Pair (Pair (owner: address) (c: contract nat))
+  (Pair (ledger: big_map address (pair nat (map address nat))) 
+         (Pair (admin: address) 
+               (Pair (paused: bool) (total_supply: nat))))
+Pre-condition :=  Get_big_map (owner, ledger) = 
+  Some value: option (pair nat (map address nat)) |
+  value  = Pair (k: nat) (m: (map address nat))
+Post-condition := post_ledger = ledger |
+  post_admin = admin |
+  post_paused = paused |
+  post_total_supply = total_supply |
+  post_Balance = Balance | 
+  Transfer_token (k, Amount, c) ;
+
+Pre-condition :=  Get_big_map (owner, ledger) = 
+  None option (pair nat (map address nat)) 
+Post-condition := post_ledger = ledger |
+  post_admin = admin |
+  post_paused = paused |
+  post_total_supply = total_supply |
+  post_Balance = Balance | 
+  Transfer_token (0, Amount, c) ;
+\end{lstlisting}
+\subsubsection{Other entrypoints}
+The contract provides five additional entrypoints: \lstinline/mint/ to mint you own, \lstinline/burn/ to burn existing tokens, \lstinline/setAdministrator/ and \lstinline/getAdministrator/ to set up or retrieve the administrator of the smart contract, and \lstinline/setPause/ to pause the contract.
+To generate fail conditions, we detect that \lstinline/transfer/ or \lstinline/approve/ calls fail if the contract is in a paused state.
+Users or dapps should be aware of this when interacting with the smart contract.
+
+The \lstinline/mint/ and \lstinline/burn/ entrypoints affect the total supply, so they should be recorded consistently with the amount mined or burned.
+an important property is that only the admin is allowed to call these entrypoints.
+The same for the \lstinline/setPause/ entrypoint is that only the admin is allowed to set the pause value.
+
+The administrator plays a crucial role in this contract.
+Therefore, for the \lstinline/setAdministrator/ entrypoint, it needs to guarantee that only the current administrator can call this entrypoint, and the new administrator must match the address passed through the parameter.
+Another property to ensure is that, except for this entrypoint call, any other smart contract call to this contract should not change the administrator.
+
+All of the above-mentioned properties are specified and verified in our model, and the results show that these properties are guaranteed.
+This confidence assures us of the correctness of the smart contract code.
 \subsection{Kolibri Oracle Contract}

### 2023-12-28 papers/static-checker/ecoop2024/ecoop2024.tex
write oracle part

@@
 This means the contract call must fail when both the parameter \lstinline/value/ is non-zero and the allowance of \lstinline/spender/ is also non-zero.
-We verify this property by generating the fail condition, and the result is that the non-zero value update is recorded as a fail condition, as shown in Listing \ref{}.
+We verify this property by generating the fail condition, and the result is that the non-zero value update is recorded as a fail condition, as shown in Listing \ref{lst:approve-udstz-contract}.
 This indicates that the implementation ensure the non-zero value update prevention.
-
+\begin{lstlisting}[float,captionpos=b,caption={Fail conditions for the \lstinline/approve/ entrypoint},label={lst:approve-udstz-contract},numbers=left]
+1. paused: 'TokenOperationsArePaused'
+2. not paused &&
+   get_big_map (Sender, ledger) = Some sbvar &&
+   sbvar = Pair sbvar1 sbvar2 &&
+   get_map (spender, sbvar2) = Some sbvar3 &&
+   not (value = 0) &&
+   not (sbvar3 = 0): 'UnsafeAllowanceChange'
+\end{lstlisting}
 The other property is that in case the update is allowed, then the updated value needs to be recorded correctly in the storage.
@@
 The first property is that when the parameter \lstinline/value/ is zero, then the corresponding allowance value of the \lstinline/spender/ from the owner (which is \SENDER\ in this call) should be zero.
-This subproperty is specified as shown in Listing \ref{}.
+This subproperty is specified as shown in Listing \ref{lst:specification-approve}.
 The second property is that when \lstinline/value/ is non-zero, requiring the allowance of the \lstinline/spender/ to be zero, then the \lstinline/value/ should be recorded in the storage after the call.
 To check this property, we specify the property as the pre and post conditions, as illustrated in Listing \ref{}.
+
+\begin{lstlisting}[float,captionpos=b,caption={Specification for the \lstinline/approve/ entrypoint},label={lst:specification-approve},numbers=left]
+Input := Pair (Pair (owner: address) (c: contract nat))
+  (Pair (ledger: big_map address (pair nat (map address nat))) 
+         (Pair (admin: address) 
+               (Pair (paused: bool) (total_supply: nat))))
+Pre-condition := not paused |
+   get_big_map (Sender, ledger) = 
+   Some (v: option (pair nat (map address nat))) | 
+   v = Pair (n1: nat) (m: map address nat) |
+   get_map (spender, m) = Some (n2: nat) |
+   not (n2 = 0) |
+   (value = 0)
+Post-condition := get_big_map (Sender, post_ledger) = 
+   Some (post_v: option (pair nat (map address nat))) | 
+   post_v = Pair (post_n1: nat) (post_m: map address nat) |
+   get_map (spender, post_m) = Some (post_n2: nat) |
+   (post_n2 = 0) ;
+
+Pre-condition := not paused |
+   get_big_map (Sender, ledger) = 
+   Some (v: option (pair nat (map address nat))) | 
+   v = Pair (n1: nat) (m: map address nat) |
+   get_map (spender, m) = Some (n2: nat) |
+   (n2 = 0) |
+   not (value = 0)
+Post-condition := get_big_map (Sender, post_ledger) = 
+   Some (post_v: option (pair nat (map address nat))) | 
+   post_v = Pair (post_n1: nat) (post_m: map address nat) |
+   get_map (spender, post_m) = Some (post_n2: nat) |
+   (post_n2 = value) ;
+\end{lstlisting}
 
@@
                (Pair (paused: bool) (total_supply: nat))))
-Pre-condition :=  Get_big_map (owner, ledger) = 
-  Some value: option (pair nat (map address nat)) |
-  value  = Pair (k: nat) (m: (map address nat))
+Pre-condition :=  get_big_map (owner, ledger) = 
+  Some v: option (pair nat (map address nat)) |
+  v  = Pair (k: nat) (m: (map address nat))
 Post-condition := post_ledger = ledger |
@@
   post_Balance = Balance | 
-  Transfer_token (k, Amount, c) ;
-
-Pre-condition :=  Get_big_map (owner, ledger) = 
+  transfer_token (k, Amount, c) ;
+
+Pre-condition :=  get_big_map (owner, ledger) = 
   None option (pair nat (map address nat)) 
@@
   post_Balance = Balance | 
-  Transfer_token (0, Amount, c) ;
+  transfer_token (0, Amount, c) ;
 \end{lstlisting}
@@
 \subsection{Kolibri Oracle Contract}
+The potential of smart contracts is constrained by the inability to access external data sources.
+To address this limitation, oracles serve as a crucial link between external sources and the blockchain network.
+Blockchain oracles plays a pivotal role in furnishing external data for smart contracts.
+Certain essential properties must be satisfied by an oracle contract, including data approvability.
+This case study aims to illustrate the process of specifying and verifying an oracle contract by the static checker, using the Kolibri oracle contract as an exemple.
+
+The Kolibri oracle contract,  residing at the address KT1Tj6xknbwjyK5gyfESNR6WESBcP3yX1mmj, ensures the accuracy of external data for the Tezos-based stablecoin, Kolibri, by leveraging the Harbinger Price Feed.
+The contract initiates calls to a Harbinger Normalizer contract, check  on the returned values, normalizes them to suit the Kolibri system, and subsequently relays them to the client.
+The smart contract's parameters and storage details are outlined in Listing \ref{lst:kolibri-oracle-contract}.
+Key attributes stored by the Oracle include:
+\begin{itemize}
+\item \lstinline/harbingerContractAddress/: the address of the Harbinger Price Feed contract.
+ \item    \lstinline/state/: a natural number indicating the current state of the contract.
+The oracle contract operates as a simple state machine with two states: (1) \lstinline/IDLE/ and (2) \lstinline/WAITING_FOR_HARBINGER/.
+ \item    \lstinline/clientCallback/: a contract featuring a \TNAT\ entrypoint that stores state when the oracle awaits Harbinger data.
+ \item    \lstinline/governorContractAddress/: the address of the governor contract.
+ \item    \lstinline/maxDataDelaySec/: the maximum acceptable age of data received from Harbinger, measured in seconds.
+\end{itemize}
+The oracle offers various entrypoints to interact with the smart contract, including:
+\begin{itemize}
+\item    \lstinline/getXtzUsdPrice/: facilitates the retrieval, sanity check, and normalization of Harbinger data.
+\item    \lstinline/getXtzUsdPrice_callback/: serves as a callback mechanism to receive data from Harbinger.
+\item    \lstinline/default/: always intentionally fails to prevent the transfer of XTZ into the contract.
+\item    \lstinline/setMaxDataDelaySec/: enables the setting of the maximum acceptable age for data received from Harbinger.
+\item    \lstinline/setGovernorContract/: allows the setting of the Governor's address.
+\end{itemize}
+
+\begin{lstlisting}[float,captionpos=b,caption={Kolibri oracle contract},label={lst:kolibri-oracle-contract},numbers=left]
+parameter
+  ( or
+    ( or
+      ( unit %default )
+      ( contract %getXtzUsdRate nat ) )
+    ( or
+      ( pair %getXtzUsdRate_callback string 
+      ( pair timestamp nat ) )
+      ( or
+        ( address %setGovernorContract )
+        ( nat %setMaxDataDelaySec ) ) ) ) ;
+storage
+  ( pair
+    ( pair ( option %clientCallback address ) 
+          ( address %governorContractAddress ) )
+    ( pair ( address %harbingerContractAddress ) 
+          ( pair ( nat %maxDataDelaySec ) ( int %state ) ) ) ) ;
+\end{lstlisting}
+
 \section {Conclusion}

### 2023-12-29 papers/static-checker/ecoop2024/ecoop2024.tex
kolbri

@@
 
+The ability to generate fail conditions is a potent feature of our static checker, particularly in verifying access control properties across various smart contracts.
+Specifically, in numerous smart contract configurations, certain entrypoints are designated for invocation only by authorized entities, often exemplified by the contract owner.
+Consequently, these entrypoints must result in failure if the callers lack the necessary authorization.
+This crucial access control property is verified by examining the fail conditions of a smart contract, ensuring that unauthorized callers trigger the intended failures in the system.
+
 For the auction contract, there are several fail conditions.
@@
 parameter
-  ( or
-    ( or
-      ( unit %default )
-      ( contract %getXtzUsdRate nat ) )
-    ( or
-      ( pair %getXtzUsdRate_callback string 
-      ( pair timestamp nat ) )
-      ( or
-        ( address %setGovernorContract )
-        ( nat %setMaxDataDelaySec ) ) ) ) ;
+ (or
+   (or
+     (unit %default )
+     (contract nat %getXtzUsdRate ))
+   (or
+     (pair string (pair timestamp nat) %getXtzUsdRate_callback)
+     (or
+       (address %setGovernorContract)
+       (nat %setMaxDataDelaySec)))) ;
 storage
-  ( pair
-    ( pair ( option %clientCallback address ) 
-          ( address %governorContractAddress ) )
-    ( pair ( address %harbingerContractAddress ) 
-          ( pair ( nat %maxDataDelaySec ) ( int %state ) ) ) ) ;
-\end{lstlisting}
-
+ (pair
+   (pair (option %clientCallback address) 
+         (address %governorContractAddress))
+   (pair (address %harbingerContractAddress) 
+         (pair (nat %maxDataDelaySec) (int %state)))) ;
+\end{lstlisting}
+
+Another critical access control property pertains to the resettable nature of \lstinline/governorContractAddress/ and \lstinline/maxDataDelaySec/.
+While these parameters are designed to be reset, such actions should exclusively be carried out by the governor.
+Maintaining this restriction is paramount to prevent loss of control over the contract in the event of unauthorized resets.
+In practical terms, the entrypoints \lstinline/setGovernorContract/ and \lstinline/setMaxDataDelaySec/ must only be invocable by the governor.
+Any attempts by unauthorized callers to make these calls should result in failure to ensure the integrity of access control and prevent potential misuse of these critical parameters.
+
+The Kolibri oracle contract maintains a straightforward state machine comprising two states: (1) \lstinline/IDLE/ and (2) \lstinline/WAITING_FOR_HARBINGER/.
+From the \lstinline/IDLE/ state, the oracle can exclusively transition to the \lstinline/WAITING_FOR_HARBINGER/ state.
+The \lstinline/getXtzUsdPrice/ entrypoint is permissible only when the oracle is in the \lstinline/IDLE/ state, and invoking this entrypoint transitions the oracle to the \lstinline/WAITING_FOR_HARBINGER/ state.
+Notably, in the \lstinline/IDLE/ state, the value of \lstinline/clientCallback/ is always set to none.
+Conversely, from the \lstinline/WAITING_FOR_HARBINGER/ state, the oracle can only transition back to the \lstinline/IDLE/ state.
+The \lstinline/getXtzUsdPrice_callback/ entrypoint is allowable solely when the oracle is in the \lstinline/WAITING_FOR_HARBINGER/ state, and invoking this entrypoint results in the oracle transitioning to the \lstinline/IDLE/ state.
+In the \lstinline/WAITING_FOR_HARBINGER/ state, the value of \lstinline/clientCallback/ is always set to some.
+
+Several properties must be verified to ensure the correct functioning of the state machine.
+The initial property states that \lstinline/getXtzUsdPrice/ can only be invoked when in the \lstinline/IDLE/ state, while conversely, \lstinline/getXtzUsdPrice_callback/ can only be invoked when in the \lstinline/WAITING_FOR_HARBINGER/ state.
+The validation of this property involves examining the fail conditions of these two entrypoints.
+
+The subsequent property dictates that if \lstinline/getXtzUsdPrice/ is successfully executed, the state must transition to \lstinline/WAITING_FOR_HARBINGER/, and the parameters passed along with the call need to be stored in the \lstinline/clientCallback/ attribute of the storage.
+This property can be detailed as shown in Listing \ref{lst:kolibri-contract-specification}.
+
+The following property asserts that if \lstinline/getXtzUsdPrice_callback/ is successful, the state should revert to \lstinline/IDLE/, and there must be a transaction transferring the data to the client at the \lstinline/clientCallback/ attribute.
+This property is specified in Listing \ref{lst:kolibri-contract-specification}.
+
+The final property concerns the entrypoint relation between \lstinline/getXtzUsdPrice/ and \lstinline/getXtzUsdPrice_callback/ as depicted in Figure \ref{fig:kolibri-oracle-emtrypoint-relations}.
+From the \lstinline/getXtzUsdPrice/ entrypoint, the contract can only be called with \lstinline/getXtzUsdPrice_callback/ and then reverted.
+Invoking the \lstinline/getXtzUsdPrice/ entrypoint after another call or invoking the \lstinline/getXtzUsdPrice_callback/ entrypoint again is not allowed.
+This entrypoint relation property is specified as an entrypoint relation in Listing \ref{}.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.8\textwidth]{kolibri}
+    \caption{Kolibri oracle emtrypoint relations}
+    \label{fig:kolibri-oracle-emtrypoint-relations}
+\end{figure}
+
+\begin{lstlisting}[float,captionpos=b,caption={Kolibri oracle contract specification},label={lst:kolibri-contract-specification},numbers=left]
+mcontract Auction = spec 
+  storage := (Pair (Pair (client: option address) 
+     (governor: address))
+     (Pair (harbinger: address) 
+           (Pair (maxDelay: nat) (state: int))))
+  entrypoint %getXtzUsdRate
+    code := {...}
+    parameter := (c : contract nat) 
+    pre-condition := (Amount = 0) | (state = 0)
+    post-condition := (state = 1) | 
+       (client = Some Sender) ;
+  entrypoint %getXtzUsdRate_callback
+    code := {...}
+    parameter := Pair (s: string) 
+       (Pair (t: timestamp) (n: nat))
+    pre-condition :=  state = 1 |
+       Sender = harbinger  |
+       s = 'XTZ-USD' |
+       Now - t <= 30 |
+       client = Some a |
+       get_contract (nat, a) = Some c    
+    post-condition := state = 0 |
+       post_client = None |
+       transfer(n, 0, c) ;
+  entrypoint %setGovernorContract
+    code := {...}
+    parameter := (gover : address) 
+    pre-condition :=  (Sender = governor)                  
+    post-condition := (governor = gover) |
+       (post_maxDelay = maxDelay) |
+       (post_harbinger = harbinger) ;
+  entrypoint %setMaxDataDelaySec
+    code := {...}
+    parameter := (delay: nat)
+    pre-condition := (Sender = governor)             
+    post-condition := (maxDelay = delay) |
+       (post_client = client) |
+       (post_harbinger = harbinger) ;
+  (%getXtzUsdRate -> %getXtzUsdRate_callback) with
+     (Sender = harbinger)
+     && (s = 'XTZ-USD') 
+     && (Now - t <= 1800)  | 
+  (%getXtzUsdRate_callback  -> %getXtzUsdRate) with 
+    (Amount = 0) 
+  not (%getXtzUsdRate -> %getXtzUsdRate) |
+  not (%getXtzUsdRate_callback -> %getXtzUsdRate_callback)
+\end{lstlisting}
 \section {Conclusion}

### 2024-01-02 papers/static-checker/ecoop2024/ecoop2024.tex
revise static checker

@@
    &\Mid\ \FALSE \\
-   &\Mid\ \PAIR\ \text{t1 t2}\\
+   &\Mid\ \PAIR\ \text{t1 t2} \\
    &\Mid\ \LEFT\ \text{t}\\
@@
 
+\begin{figure}[]
+\begin{align*}
+\textbf{c} & ::= 
+    \text{Balance}
+   \Mid \text{post\_Balance}  
+   \Mid \text{Amount} 
+   \Mid \text{Sender} 
+   \Mid \text{Source} 
+   \Mid \text{Now} 
+   \Mid \text{Level} \\
+   &\Mid \text{Chain\_id} 
+   \Mid \text{Self\_address} 
+   \Mid \text{Total\_voting\_power} 
+   \Mid \text{Voting\_power} \\
+\textbf{e} & :: =  \textbf{i} \Mid  \textbf{s}  \Mid  \textbf{b} \Mid \textbf{c} \Mid (\text{x} : \text{T}) \\
+&\Mid \text{Unit}  \Mid \text{Never}  \Mid \text{True}  \Mid \text{False} \\
+&\Mid \text{Pair } \textbf{e } \textbf{e}  \Mid \text{Left } \textbf{e}  \Mid \text{Right } \textbf{e}  \Mid \text{Some } \textbf{e} \text{: T} \Mid \text{None T}  \\
+& \Mid \textbf{e} \text{ + } \textbf{e}\Mid \textbf{e} \text{ - } \textbf{e}  \Mid \textbf{e} \text{ * } \textbf{e} \Mid \textbf{e} \text{ \/ } \textbf{e} \Mid \textbf{e} \text{ \% } \textbf{e} \Mid \textbf{e} \text{ rem } \textbf{e} \\
+& \Mid \textbf{e} \text{ and } \textbf{e}\Mid \textbf{e} \text{ or } \textbf{e}  \Mid \textbf{e} \text{ nor } \textbf{e} \Mid  \text{ not } \textbf{e} \Mid \textbf{e} \text{ imply } \textbf{e} \\
+& \Mid \text{transfer\_token} (\textbf{e}, \textbf{e}, \textbf{e}) 
+ \Mid \text{get\_map} (\textbf{e}, \textbf{e}) 
+ \Mid \text{get\_big\_map} (\textbf{e}, \textbf{e}) \\
+& \Mid \text{get\_contract} (\textbf{e}, \textbf{e})  
+ \Mid \text{abs} (\textbf{e})  
+ \Mid \text{len} (\textbf{e})
+ \Mid \text{size} (\textbf{e})
+\Mid \textbf{e} \text{$\wedge$} \textbf{e}  \\
+\textbf{p} & :: = \textbf{e} \text{ = } \textbf{e} 
+\Mid \textbf{e} \text{ != } \textbf{e}
+\Mid \textbf{e} \text{ > } \textbf{e}
+\Mid \textbf{e} \text{ >= } \textbf{e}
+\Mid \textbf{e} \text{ < } \textbf{e}
+\Mid \textbf{e} \text{ <= } \textbf{e} \\
+&\Mid \text{forall} (\textbf{e}, \textbf{p})
+\Mid \text{exsit} (\textbf{e}, \textbf{p})
+\end{align*}
+\caption{Syntax of predicates, p}
+\label{fig:syntax-predicates}
+\end{figure}
+
 The Michelson code, readily available on the Tezos blockchain, remains consistent across various high-level language platforms like LIGO, SmartPy, and Liquidity, all of which offer functions to compile programs into Michelson.
@@
 Formally, the pre and post-condition instances are formulas in first-order logic, and they can be handled by an SMT solver, namely the Z3 solver in our framework.
-The detail of the language grammar is described in in Figure \ref{}.
+The specification language is constituted of predicates defined using the syntax defined as in Figure \ref{fig:syntax-predicates}.
 Formulas that are used in assertions or added to solvers are terms of Boolean sort.
@@
 The syntax is as follows:
-\begin{lstlisting}[float,captionpos=b,caption={Multiple entrypoint specification syntax},label={lst:safer-contract-module},numbers=left][h]
+\begin{lstlisting}[float,captionpos=b,caption={Multiple entrypoint specification syntax},label={lst:multiple-entrypoint-specification},numbers=left][h]
 mcontract Name = spec
@@
 
+\begin{lstlisting}[float,captionpos=b,caption={Multiple entrypoint specification syntax},label={lst:multiple-entrypoint-specification},numbers=left][h]
+mcontract Name = spec
+   storage := s
+   entrypoint %a 
+      code := {c1}
+      parameter := t1
+      pre-condition := cd1
+      post-condition := cd1'
+   entrypoint %b 
+      code := {c2}
+      parameter := t2
+      pre-condition := cd2
+      post-condition := cd2'
+   entrypoint %c 
+      ...
+   < entrypoint relations>
+\end{lstlisting}
+
 To illustrate this, let's consider the  auction smart contract serving the auction events.
@@
 mcontract Auction = spec 
+  storage := Pair (auction_open: bool) 
+                     Pair (highest_bidder: address)
+                          (contract_owner: address))
   entrypoint %bid
     code := {...}
-    input := Pair Unit (Pair (auction_open: bool) 
-                             (Pair (highest_bidder: address)
-                                   (contract_owner: address)))
-    output :=   Pair (post_auction_open: bool) 
-                     Pair (post_highest_bidder: address)
-                          (post_contract_owner: address))
-    pre-condition := auction_open |
-             Amount > Balance
-    post-condition := post_highest_bidder = Sender |
-             Post_Balance = Amount |
-             Transfer_token (Unit, Balance, highest_bidder) |
-             post_contract_owner = contract_owner ;
+    parameter := Unit 
+    pre-condition := auction_open 
+       && Amount > Balance
+    post-condition := post_highest_bidder = Sender 
+       && post_Balance = Amount 
+       && transfer_token (Unit, Balance, highest_bidder) 
+       && post_contract_owner = contract_owner ;
   entrypoint %close
     code := {...}
-    input := Pair Unit (Pair (auction_open: bool) 
-                             (Pair (highest_bidder: address)
-                                   (contract_owner: address)))
-    output :=   Pair (post_auction_open: bool) 
-                     Pair (post_highest_bidder: address)
-                          (post_contract_owner: address))
-    pre-condition := auction_open |
-           Sender = contract_owner                
-    post-condition := not post_auction_open |
-          Post_Balance = 0 |
-          Transfer_token (Unit, Balance, contract_owner) ;
+    parameter := Unit
+    pre-condition := auction_open 
+       && Sender = contract_owner                
+    post-condition := not post_auction_open 
+       && post_Balance = 0 
+       && transfer_token (Unit, Balance, contract_owner) ;
     (%create -> %bid) with (auction_open = true)  
-                      && (Amount > Balance) | 
-    (%create  -> %close) with (auction_open = true) 
-                      && (Sender = contract_owner) |
-    (%bid -> %bid) with (Amount > Balance)  | 
-    (%bid -> %close) with (Sender = contract_owner)  | 
-    not (%close -> %bid) |
-    not (%close -> %close)
+       && (Amount > Balance) 
+    | (%create  -> %close) with (auction_open = true) 
+       && (Sender = contract_owner)
+    | (%bid -> %bid) with (Amount > Balance)  
+    | (%bid -> %close) with (Sender = contract_owner)  
+    | not (%close -> %bid) 
+    | not (%close -> %close)
 \end{lstlisting}
@@
 The static checker enables users to verify smart contract properties by providing pre and post condition specifications.
-A property is specified with the following clause:  \lstinline/pre-condtion : =/ $\mid$ $\Phi_{i}$ \lstinline/ post-condtion : =/   $\mid$ $\Psi_{j}$.
+A property is specified with the following clause:  \lstinline/pre-condtion := &&/ $\Phi_{i}$ \lstinline/post-condtion := &&/ $\Psi_{j}$.
 This specification asserts that if all preconditions $\Phi_{i}$ hold before smart contract execution, then all $\Psi_{j}$ must become true after the execution.
@@
 The FA 1.2 standard mandates that this call must fail under the following two conditions: (1) In the event of insufficient balance, this entrypoint MUST fail with the error \lstinline/NotEnoughBalance/, indicating insufficient funds in the sender's account to execute the transfer.
-The error MUST contain a \lstinline/pair (nat :value) (nat :present)/ pair, where \lstinline/value/ is the requested amount of tokens, and \lstinline/present/ is the available amount.
 (2) If the sender's account has no permission to withdraw the \lstinline/value/ amount of funds, the call will fail with the \lstinline/NotEnoughAllowance/ error, which also contains the same pair message as the first failure scenario.
-To verify these requirements, we utilize the failwith condition feature of the tool and examine the returned results, as outlined in Listing \ref{}.
-
-The fundamental property that this entrypoint should satisfy is the decrement of the allowance of the sender's account by the \lstinline/value/ that has been sent.
+To verify these requirements, we utilize the failwith condition feature of the tool and examine the returned results, as outlined in Listing \ref{lst:transfer-udstz-contract}.
+\begin{lstlisting}[float,captionpos=b,caption={Fail conditions for the \lstinline/transfer/ entrypoint},label={lst:transfer-udstz-contract},numbers=left]
+1. paused: 'TokenOperationsArePaused'
+2. not paused &&
+   get_big_map (from, ledger) = None : 'NotEnoughBalance'
+3. not paused &&
+   get_big_map (from, ledger) = Some sbvar &&
+   sbvar = Pair sbvar1 sbvar2 &&
+   sbvar1 < value : 'NotEnoughBalance'
+4. not paused &&
+   get_big_map (from, ledger) = Some sbvar &&
+   sbvar = Pair sbvar1 sbvar2 &&
+   get_map (Sender, sbvar2) = Some sbvar3 &&
+   sbvar3 < value: 'NotEnoughAllowance'
+\end{lstlisting}
+The fundamental property that this entrypoint should satisfy is the decrement of the allowance of the sender's account by the \lstinline/value/ that has been sent as Listing \ref{lst:specification-transfer}.
+\begin{lstlisting}[float,captionpos=b,caption={Specification for the \lstinline/transfer/ entrypoint},label={lst:specification-transfer},numbers=left]
+mcontract UDStz = spec 
+   storage :=  Pair (ledger: big_map address 
+      (pair nat (map address nat))) 
+      (Pair (admin: address) 
+              (Pair (paused: bool) (total_supply: nat)))
+   entrpoint %transfer
+      parameter := Pair (from: address)
+         (Pair (to: address) (value: nat))
+      pre-condition := not paused 
+        && get_big_map (from, ledger) = 
+        && Some (v: option (pair nat (map address nat))) 
+        && (v = Pair (n1: nat) (m: map address nat))
+        && get_map (Sender, m) = Some (n2: nat) 
+        && (n1 >= value) && (n2 >= value)
+      post-condition := get_big_map (from, post_ledger) = 
+        && Some (post_v: option (pair nat (map address nat))) 
+        && post_v = Pair (post_n1: nat) (post_m: map address nat) 
+        && get_map (Sender, post_m) = Some (post_n2: nat) 
+        && (post_n1 = n1 - value) | (post_n2 = n2 - value)
+\end{lstlisting}
 
@@
 \begin{lstlisting}[float,captionpos=b,caption={Specification for the \lstinline/approve/ entrypoint},label={lst:specification-approve},numbers=left]
-Input := Pair (Pair (owner: address) (c: contract nat))
-  (Pair (ledger: big_map address (pair nat (map address nat))) 
-         (Pair (admin: address) 
-               (Pair (paused: bool) (total_supply: nat))))
-Pre-condition := not paused |
-   get_big_map (Sender, ledger) = 
-   Some (v: option (pair nat (map address nat))) | 
-   v = Pair (n1: nat) (m: map address nat) |
-   get_map (spender, m) = Some (n2: nat) |
-   not (n2 = 0) |
-   (value = 0)
-Post-condition := get_big_map (Sender, post_ledger) = 
-   Some (post_v: option (pair nat (map address nat))) | 
-   post_v = Pair (post_n1: nat) (post_m: map address nat) |
-   get_map (spender, post_m) = Some (post_n2: nat) |
-   (post_n2 = 0) ;
-
-Pre-condition := not paused |
-   get_big_map (Sender, ledger) = 
-   Some (v: option (pair nat (map address nat))) | 
-   v = Pair (n1: nat) (m: map address nat) |
-   get_map (spender, m) = Some (n2: nat) |
-   (n2 = 0) |
-   not (value = 0)
-Post-condition := get_big_map (Sender, post_ledger) = 
-   Some (post_v: option (pair nat (map address nat))) | 
-   post_v = Pair (post_n1: nat) (post_m: map address nat) |
-   get_map (spender, post_m) = Some (post_n2: nat) |
-   (post_n2 = value) ;
+entrpoint %approve
+   parameter := Pair (spender: address) (value: nat)
+   pre-condition := not paused 
+      && get_big_map (Sender, ledger) = 
+        Some (v: option (pair nat (map address nat))) 
+      && v = Pair (n1: nat) (m: map address nat) 
+      && get_map (spender, m) = Some (n2: nat) 
+      && not (n2 = 0) | (value = 0)
+   post-condition := get_big_map (Sender, post_ledger) = 
+        Some (post_v: option (pair nat (map address nat))) 
+      && post_v = Pair (post_n1: nat) (post_m: map address nat) 
+      && get_map (spender, post_m) = Some (post_n2: nat) 
+      && (post_n2 = 0) ;
+
+   pre-condition := not paused 
+      && get_big_map (Sender, ledger) = 
+        Some (v: option (pair nat (map address nat))) 
+      && v = Pair (n1: nat) (m: map address nat) 
+      && get_map (spender, m) = Some (n2: nat) 
+      && (n2 = 0) | not (value = 0)
+   post-condition := get_big_map (Sender, post_ledger) = 
+        Some (post_v: option (pair nat (map address nat))) 
+      && post_v = Pair (post_n1: nat) (post_m: map address nat) 
+      && get_map (spender, post_m) = Some (post_n2: nat) 
+      && (post_n2 = value) ;
 \end{lstlisting}
@@
 \begin{lstlisting}[float,captionpos=b,caption={Specification for the \lstinline/getBalance/ entrypoint},label={lst:specification-get-balance},numbers=left]
-Input := Pair (Pair (owner: address) (c: contract nat))
-  (Pair (ledger: big_map address (pair nat (map address nat))) 
-         (Pair (admin: address) 
-               (Pair (paused: bool) (total_supply: nat))))
-Pre-condition :=  get_big_map (owner, ledger) = 
-  Some v: option (pair nat (map address nat)) |
-  v  = Pair (k: nat) (m: (map address nat))
-Post-condition := post_ledger = ledger |
-  post_admin = admin |
-  post_paused = paused |
-  post_total_supply = total_supply |
-  post_Balance = Balance | 
-  transfer_token (k, Amount, c) ;
-
-Pre-condition :=  get_big_map (owner, ledger) = 
+entrypoint %getBalance
+   parameter := Pair (owner: address) (c: contract nat)
+   pre-condition :=  get_big_map (owner, ledger) = 
+        Some v: option (pair nat (map address nat)) 
+      && v  = Pair (k: nat) (m: (map address nat))
+   post-condition := post_ledger = ledger 
+      && post_admin = admin 
+      && post_paused = paused 
+      && post_total_supply = total_supply 
+      && post_Balance = Balance 
+      && transfer_token (k, Amount, c) ;
+
+   pre-condition :=  get_big_map (owner, ledger) = 
         None option (pair nat (map address nat)) 
-Post-condition := post_ledger = ledger |
-  post_admin = admin |
-  post_paused = paused |
-  post_total_supply = total_supply |
-  post_Balance = Balance | 
-  transfer_token (0, Amount, c) ;
+   post-condition := post_ledger = ledger 
+      && post_admin = admin 
+      && post_paused = paused 
+      && post_total_supply = total_supply 
+      && post_Balance = Balance 
+      && transfer_token (0, Amount, c) ;
 \end{lstlisting}
@@
     pre-condition := (Amount = 0) | (state = 0)
-    post-condition := (state = 1) | 
-       (client = Some Sender) ;
+    post-condition := (state = 1) 
+       && (client = Some Sender) ;
   entrypoint %getXtzUsdRate_callback
@@
        (Pair (t: timestamp) (n: nat))
-    pre-condition :=  state = 1 |
-       Sender = harbinger  |
-       s = 'XTZ-USD' |
-       Now - t <= 30 |
-       client = Some a |
-       get_contract (nat, a) = Some c    
-    post-condition := state = 0 |
-       post_client = None |
-       transfer(n, 0, c) ;
+    pre-condition :=  state = 1 
+       && Sender = harbinger  
+       && s = 'XTZ-USD' 
+       && Now - t <= 30 
+       && client = Some a 
+       && get_contract (nat, a) = Some c    
+    post-condition := state = 0 
+       && post_client = None 
+       && transfer(n, 0, c) ;
   entrypoint %setGovernorContract
@@
     pre-condition :=  (Sender = governor)                  
-    post-condition := (governor = gover) |
-       (post_maxDelay = maxDelay) |
-       (post_harbinger = harbinger) ;
+    post-condition := (governor = gover) 
+       && (post_maxDelay = maxDelay) 
+       && (post_harbinger = harbinger) ;
   entrypoint %setMaxDataDelaySec
@@
     pre-condition := (Sender = governor)             
-    post-condition := (maxDelay = delay) |
-       (post_client = client) |
-       (post_harbinger = harbinger) ;
+    post-condition := (maxDelay = delay) 
+       && (post_client = client) 
+       && (post_harbinger = harbinger) ;
   (%getXtzUsdRate -> %getXtzUsdRate_callback) with
@@
      && (s = 'XTZ-USD') 
-     && (Now - t <= 1800)  | 
-  (%getXtzUsdRate_callback  -> %getXtzUsdRate) with 
+     && (Now - t <= 1800)  
+  | (%getXtzUsdRate_callback  -> %getXtzUsdRate) with 
     (Amount = 0) 
-  not (%getXtzUsdRate -> %getXtzUsdRate) |
-  not (%getXtzUsdRate_callback -> %getXtzUsdRate_callback)
+  | not (%getXtzUsdRate -> %getXtzUsdRate) 
+  | not (%getXtzUsdRate_callback -> %getXtzUsdRate_callback)
 \end{lstlisting}

### 2024-01-03 papers/static-checker/ecoop2024/ecoop2024.tex
first round of changes
* reworded title
* abstract rewritten; integrated previous abstract text into introduction
* added contributions to introduction
* started conclusion and future work section
* added "Michelson" section
* moved DSL section before the discussion of symbolic execution (more technical -> move to back of paper)
* edited DSL section

@@
-\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
+\documentclass[a4paper,USenglish,cleveref, autoref, thm-restate]{lipics-v2021}
+
+%% final papers: 25 pages
+
 %This is a template for producing LIPIcs articles. 
@@
 
-%\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
+\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
 %\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
@@
 
-\title{Formal Verification Framework Based on Symbolic Execution for Smart Contract} %TODO Please add
+\title{A Formal Verification Framework for Smart Contracts Based on Symbolic Execution} %TODO Please add
 
@@
 
-\author{Thi Thu Ha Doan}{University of Freiburg, Germany}{doanha@informatik.uni-freiburg.de}{https://orcid.org/0000−0001−7524−4497}{(Optional) author-specific funding acknowledgements}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
+\author{Thi Thu Ha Doan}{University of Freiburg,
+  Germany}{doanha@informatik.uni-freiburg.de}{https://orcid.org/0000−0001−7524−4497}{Supported
+by the Tezos Foundation, grant COOC }%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
 Please provide at least the name of the affiliation and the country.
@@
 
-\author{Peter Thiemann}{University of Freiburg, Germany}{thiemann@informatik.uni-freiburg.de}{https://orcid.org/0000−0002−9000−1239}{[funding]}
-
-\authorrunning{T.T.Ha Doan and P.Thiemann} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'
+\author{Peter Thiemann}{University of Freiburg, Germany}{thiemann@informatik.uni-freiburg.de}{https://orcid.org/0000−0002−9000−1239}{}
+
+\authorrunning{T.T.Ha Doan and P. Thiemann} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'
 
@@
 
-\category{} %optional, e.g. invited paper
-
-\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
+%\category{} %optional, e.g. invited paper
+
+%\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
 %\relatedversiondetails[linktext={opt.
@@
 
-\acknowledgements{I want to thank \dots}%optional
+%\acknowledgements{I want to thank \dots}%optional
 
@@
 \begin{abstract}
-In the context of blockchain technology, the immutability of smart contracts once implemented underscores the critical need to ensure their accuracy.
-Even in cases where smart contract implementations are not overly extensive and have undergone testing before deployment, the blockchain community has identified significant vulnerabilities in their design.
-In addition, the relatively new nature of smart contract languages has led to unforeseen errors due to a lack of familiarity with their intricacies.
-To overcome these challenges, formal verification emerges as a key solution to guarantee the correctness of smart contracts.
-In response to this need, we have developed a formal verification tool for smart contracts, particularly those written in Michelson.
-This tool uses symbolic execution to simulate the implementation of the smart contract language, helping to detect subtle errors that are difficult for smart contract developers to detect.
-In addition, our tool includes a domain-specific language that allows users to precisely specify contract properties.
-By interacting with an SMT solver, it can handle a wide range of properties.
-In particular, it streamlines the process of reviewing requirements, uncovering hidden errors, and validating user-defined properties.
-In summary, our research highlights the need for robust verification of smart contracts.
-We present a purpose-built tool that utilizes symbolic execution and a domain-specific language to improve the correctness of smart contracts and provide a comprehensive solution to mitigate potential pitfalls in blockchain-based applications.
+Formal verification is a requirement for all but the simplest smart
+contracts on the blockchain. We developed XXX, a tool that is geared towards contracts
+implemented in Michelson, the smart contract language of the Tezos
+blockchain. It relies on symbolic execution and an SMT solver to
+derive verification conditions that can be checked against the user's
+specification. Specifications are written in a domain-specific
+language tailored to Michelson's execution model.
+
+We report the foundations of the design and implementation of XXX and
+conduct NNN case studies that demonstrate the expressiveness of our tool.
 \end{abstract}
+
 \section{Introduction}
 \label{sec:introduction}
-Symbolic execution techniques encounter challenges related to state explosion, particularly when applied to large systems.
-Fortunately, the constraints of storing and running smart contracts on a blockchain platform impose size limitations, making them manageable for symbolic execution.
-
-In this work, we present the design of a domain-specific language for specifying smart contract properties and demonstrate the integration of symbolic execution with an SMT solver for formal verification of these properties.
+
+Once a smart contract is published on a blockchain, it cannot be
+changed any more. Unfortunately, there are plenty of
+cases~\cite{examples-for-broken-smart-contracts} where the blockchain 
+community identified vulnerabilities in smart contracts despite
+extensive testing before deployment.
+In addition, the novel execution model of smart contract
+languages has led to unforeseen errors due to a lack of familiarity
+with their intricacies. These observations along with the contract's
+immutability underscore the need to ensure its correctness before deployment.
+
+Formal verification can guarantee the correctness of smart contracts.
+To this end we have developed XXX, a formal
+verification tool for smart contracts on the Tezos blockchain, written in
+Michelson, although our design is widely applicable. XXX relies on
+symbolic execution backed by an SMT solver to simulate the
+implementation of the smart contract language, helping to detect 
+subtle errors. In addition, XXX comes with a domain-specific language that
+allows users to precisely specify contract properties.
+% By interacting with an SMT solver, it can handle a wide range of properties.
+It streamlines the process of reviewing requirements,
+uncovering hidden errors, and validating user-defined properties.
+XXX provides a comprehensive solution to
+mitigate potential pitfalls in blockchain-based applications.
+
+In this work, we present the design of a domain-specific language for
+specifying smart contract properties and demonstrate the integration
+of symbolic execution for Michelson with an SMT solver for automatic
+formal verification of these properties.
+
+\begin{lstlisting}[float=tp,captionpos=b,caption={Auction contract specification (excerpt)},label={lst:auction-fragment}]
+mcontract Auction = spec 
+  storage := Pair (auction_open: bool) 
+                     Pair (highest_bidder: address)
+                          (contract_owner: address))
+  entrypoint %bid
+    code := {...}
+    parameter := Unit 
+    pre-condition := auction_open 
+       && Amount > Balance
+    post-condition := post_highest_bidder = Sender 
+       && post_Balance = Amount 
+       && transfer_token (Unit, Balance, highest_bidder) 
+       && post_contract_owner = contract_owner ;
+\end{lstlisting}
+As an example, Listing~\ref{lst:auction-fragment} contains an excerpt
+of the specification of an auction contract. The \texttt{storage}
+phrase describes the internal state (storage) of the contract
+consisting of three values named \lstinline|auction_open|,
+\lstinline|highest_bidder|, and \lstinline|contract_owner|.
+The actual specification consists of a precondition and a
+postcondition with the usual partial correctness semantics. The
+postcondition refers to components of the final storage by prefixing
+\lstinline|post_| to their name. The variables \lstinline|Balance|,
+\lstinline|Amount|, and \lstinline|Sender| correspond to the values
+returned by the like-named Michelson instructions that return the
+current balance of the contract, the amount transferred with the call,
+and the address of the caller (sender).
+
+Our symbolic interpreter calculates a postcondition predicate from the specified
+precondition. The SMT solver Z3 \cite{Z3} checks that this predicate
+implies the specified postcondition.
+
+Our contributions are as follows.
+\begin{enumerate}
+\item Design and implementation of the smart contract specification
+  language XXX.
+\item Design and implementation of a symbolic interpreter for a
+  significant subset of Michelson.
+\item Two case studies where we apply XXX to verify real life smart
+  contracts deployed on the Tezos blockchain:
+  \begin{itemize}
+  \item USDtz, an implementation of the FA~1.2 standard for financial
+    applications;
+  \item the Kolibri oracle contract that injects currency exchange
+    rates from an external system.
+  \end{itemize}
+\end{enumerate}
+
+\section{Michelson}
+\label{sec:background}
+
+Michelson is a stack-based language.
+A Michelson program specifies the type of its storage, the type of its single
+parameter, and a list of instructions for the underlying stack machine.
+A program starts on a stack with one element which contains a pair of
+the current storage value (taken from the blockchain) and the parameter value, as specified by the
+contract invocation.
+When it finishes, the stack must contain a single element with a pair
+of the final storage value (to be saved on the blockchain) and a list
+of instructions.
+These instructions may be token transfers or contract invocations,
+among other possibilities.
+
+Besides the standard datatypes (e.g., numbers, lists, pairs, sums)
+with the expected operations,
+Michelson supports a number of types and operations specific to blockchain applications (e.g.,
+\texttt{mutez} for tokens, \texttt{address} for blockchain addresses).
+
+Here is a simple example of a Michelson program:
+
+TO BE COMPLETED
+
+\pt{Introduce entrypoints}
+
+\pt{I don't think the next paragraph is strictly needed}
+Michelson, as a stack-based language, may pose a challenge for
+developers less familiar with it compared to more mainstream languages
+like Python, Java, or C. To address this, several high-level languages
+such as LIGO, SmartPy, and Liquidity have been created. These
+languages provide a more readable syntax, resembling popular
+programming languages, allowing developers to write Tezos smart
+contracts more comfortably. These high-level contracts are then
+compiled down to Michelson.
+
+\section {A Domain Specific Language For Smart Contract Property Specification}
+\label{sec:domain-specific-language}
+
+% For Tezos users who may lack expertise in Michelson, there is a desire
+% to verify smart contract code before interaction.
+Our framework contains a domain-specific language (DSL) that
+facilitates the specification of smart contract properties in a
+mathematical and readable format.
+The DSL is designed to allow users to write formulas that align with
+the capabilities of the underlying SMT solver (Z3).
+The goal is to create a language
+that is accessible, easily understandable even for users who are
+not Michelson experts, and guarantees formulas that the solver can handle effectively.
+
+% This empowers users to write formulas, facilitating property verification in a more user-friendly manner.
+
+% To achieve this, our framework employs an SMT solver, specifically Z3,
+% for property verification.
+
+One of the main challenges with formal verification is that users are
+often required to express  system properties in a specialized
+specification language. This requirement poses two problems: it
+demands expertise in formal verification from the specifier and
+introduces a gap between the actual code and its specification. In our
+framework, users are not obliged to possess formal verification
+expertise. A basic understanding of Michelson data types and their
+usage when interacting with a smart contract on the Tezos blockchain
+is sufficient.
+
+\begin{figure}[tp]
+\begin{align*}
+\textbf{c} & ::= 
+    \text{Balance}
+   \Mid \text{post\_Balance}
+   \Mid \text{Amount}
+   \Mid \text{Sender}
+   \Mid \text{Source} 
+   \Mid \text{Now}
+   \Mid \text{Level} \\
+   &\Mid \text{Chain\_id}
+   \Mid \text{Self\_address}
+   \Mid \text{Total\_voting\_power}
+   \Mid \text{Voting\_power} \\
+\textbf{e} & :: =  \textbf{i} \Mid  \textbf{s}  \Mid  \textbf{b} \Mid \textbf{c} \Mid (\text{x} : \text{T}) \\
+&\Mid \text{Unit}  \Mid \text{Never}  \Mid \text{True}  \Mid \text{False} \\
+&\Mid \text{Pair } \textbf{e } \textbf{e}  \Mid \text{Left } \textbf{e}  \Mid \text{Right } \textbf{e}  \Mid \text{Some } \textbf{e} \text{: T} \Mid \text{None T}  \\
+& \Mid \textbf{e} \text{ + } \textbf{e}\Mid \textbf{e} \text{ - } \textbf{e}  \Mid \textbf{e} \text{ * } \textbf{e} \Mid \textbf{e} \text{ \/ } \textbf{e} \Mid \textbf{e} \text{ \% } \textbf{e} \Mid \textbf{e} \text{ rem } \textbf{e} \\
+& \Mid \text{transfer\_token} (\textbf{e}, \textbf{e}, \textbf{e}) 
+ \Mid \text{get\_map} (\textbf{e}, \textbf{e}) 
+ \Mid \text{get\_big\_map} (\textbf{e}, \textbf{e}) \\
+& \Mid \text{get\_contract} (\textbf{e}, \textbf{e})  
+ \Mid \text{abs} (\textbf{e})  
+ \Mid \text{len} (\textbf{e})
+ \Mid \text{size} (\textbf{e})
+\Mid \textbf{e} \text{$\wedge$} \textbf{e}  \\
+\textbf{p} & :: = \textbf{e} \text{ = } \textbf{e} 
+\Mid \textbf{e} \text{ != } \textbf{e}
+\Mid \textbf{e} \text{ > } \textbf{e}
+\Mid \textbf{e} \text{ >= } \textbf{e}
+\Mid \textbf{e} \text{ < } \textbf{e}
+\Mid \textbf{e} \text{ <= } \textbf{e} \\
+&\Mid \text{forall} (\textbf{e}, \textbf{p})
+                                            \Mid \text{exist} (\textbf{e}, \textbf{p})
+                                            \Mid \textbf{p} \text{ and } \textbf{p}\Mid \textbf{p} \text{ or } \textbf{p}  \Mid \textbf{p} \text{ nor } \textbf{p} \Mid  \text{ not } \textbf{p} \Mid \textbf{p} \text{ imply } \textbf{p} \\
+\end{align*}
+\caption{Syntax of predicates, p}
+\label{fig:syntax-predicates}
+\end{figure}
+
+\begin{lstlisting}[float,captionpos=b,caption={Smart contract property specification},label={lst:smart-contract-property-specification},numbers=left]
+mcontract Name = spec
+  code := {...}
+  input := t
+  output := t'
+  pre-condition := cd
+  post-condition := cd'
+\end{lstlisting}
+Listing \ref{lst:smart-contract-property-specification} shows the
+syntax of our property specification language. Here, \KMCONTRACT,
+\KWITH, \KCODE, \KINPUT, \KOUTPUT, \KPRECONDI, and \KPOSTCONDI\ are
+keywords. The \KNAME\ is replaced by the contract name. In the input
+and output fields, the input and output patterns are specified. Since
+Michelson operates on a stack, we assume that the stack has only one
+element, as specified in the input pattern. Similarly, the output
+stack is assumed to be a stack with only one element, which is
+specified in the output field. Thus, the syntax allows us to specify
+incomplete contracts, too. For a complete smart contract, the output
+should be a pair consisting of an operation list and a storage.
+
+For verification purposes we elide the operation list and represent
+the output solely by the pattern of the value in the storage after the
+execution concludes. In some cases, the output pattern can be omitted
+for a complete contract, given that the input pattern must be a pair
+of parameters and storage. Hence the storage pattern is part of the
+input pattern. In such cases, the prefix \lstinline/post_/ is used
+before the variables from the input term to indicate the corresponding
+storage value after the execution.
+
+The input and output patterns represent Michelson terms, which can be
+either concrete values or symbolic values, including variables. When a
+variable appears for the first time, it needs to be accompanied by its
+corresponding type declaration. Subsequent mentions can omit the type
+declaration.  Formally, the pre- and postcondition instances are
+formulas in first-order logic that can be handled by an SMT solver (in
+our case, Z3). The specification language is constituted of predicates
+defined using the syntax defined in Figure
+\ref{fig:syntax-predicates}. Formulas that are used in assertions or
+added to solvers are terms of sort Boolean. Otherwise, terms of
+Boolean and non-Boolean sort may be mixed in any combination where
+sorts match up. Universal and existential quantifiers bind variables
+to the scope of the quantified formula. 
+\begin{lstlisting}[float,captionpos=b,caption={Specification of Add contract},label={lst:add-contract-specification},numbers=left]
+mcontract Add = spec
+  code := {UNPAIR; COMPARE; GE; 
+          IF {ADD}{PUSH string 'Unexpected Pair'; FAILWITH}}
+  input := Pair (x : int) (y : int)
+  output := (z : int)
+  pre-condition := (x >= 5) | (y > 3)
+  post-condition := (z >= 8)
+\end{lstlisting}
+
+Let us consider the contract \texttt{Add}  in Listing
+\ref{lst:add-contract-specification} as an   example of a property
+specification.  Here, the program takes as input a stack with only one
+element, which is a pair of two integers, symbolically specified in
+the \lstinline|input| field. The program unpairs the input pair to
+obtain two elements as two integers \lstinline/x/ and \lstinline/y/.
+Next, the program performs a comparison between
+these two integers. If \lstinline/x/ is greater than or equal to
+\lstinline/y/, the program constructs a new stack with a solitary
+element at the top representing the sum of  \lstinline/x/ and
+\lstinline/y/, designated as \lstinline/z/ by the \lstinline|output| directive. Otherwise, the execution
+terminates with an error message containing the content
+\lstinline|'Unexpected pair'|. The specification continues by defining
+pre- and postconditions, where the precondition states the assumption
+that the integer \lstinline/x/ is greater than or equal to 5 and \lstinline/y/
+is greater than or equal to 3. The symbol  \lstinline/|/ stands for
+logical disjunction. The postcondition asserts that the result
+\lstinline/z/ is greater than or equal to 8.
+
+In XXX, we can specify several entrypoints at the same
+time. This design enables us to specify and verify all entrypoints
+at once and also to describe and verify relationships between
+entrypoints.  The syntax is shown in Listing~\ref {lst:multiple-entrypoint-specification},
+\begin{lstlisting}[float,captionpos=b,caption={Multiple entrypoint specification syntax},label={lst:multiple-entrypoint-specification},numbers=left][h]
+mcontract Name = spec
+   entrypoint %a 
+      code := {c1}
+      input := t1
+      output := t1'
+      pre-condition := cd1
+      post-condition := cd1'
+   entrypoint %b 
+      code := {c2}
+      input := t2
+      output := t2'
+      pre-condition := cd2
+      post-condition := cd2'
+   entrypoint %c 
+      ...
+   <entrypoint relations>
+\end{lstlisting}
+where the entrypoint name is written after the \lstinline/%/ symbol
+and is followed by a property specification for the entrypoint. The
+specification finishes with specifying entrypoint relations,
+which we explain next.
+
+\pt{can we put the source code of the contract somewhere, e.g. in an appendix?}
+To illustrate entrypoint relations, let us consider a smart contract
+that models an online auction. The contract has two entrypoints,
+\lstinline|%bid| and \lstinline|%close|, which serve as functions for
+bidding and closing the contract, respectively.  The smart contract
+storage is a pair containing as its first element a boolean value
+\lstinline|auction_open| that indicates whether the contract is still
+open for bidding or already closed. The second element is another
+nested pair, where the first element stores the highest bidder's
+address, and the second element is the contract owner's address. The
+current highest bid is reflected in the balance of the contract.
+
+Closing the contract transfers the balance to the owner and is
+restricted to the owner. Both closing and bidding operations fail if
+the auction is already closed. If bidding is open and the amount of
+tokens accompanying the bid exceeds the current highest bid, the
+current bidder replaces the previous highest bidder, and the previous
+highest bidder is reimbursed. Otherwise, bidding fails.
+
+Upon deployment, the owner deposits an initial balance to indicate the minimum bid.
+The contract is supposed to be deployed with the storage value  \lstinline/Pair True (Pair owner owner)/, indicating that bidding is allowed, and the contract owner is currently the highest bidder.
+
+\begin{lstlisting}[float=tp,captionpos=b,caption={Auction contract specification},label={lst:auction-contract-specification},numbers=left]
+mcontract Auction = spec 
+  storage := Pair (auction_open: bool) 
+                     Pair (highest_bidder: address)
+                          (contract_owner: address))
+  entrypoint %bid
+    code := {...}
+    parameter := Unit 
+    pre-condition := auction_open 
+       && Amount > Balance
+    post-condition := post_highest_bidder = Sender 
+       && post_Balance = Amount 
+       && transfer_token (Unit, Balance, highest_bidder) 
+       && post_contract_owner = contract_owner ;
+
+  entrypoint %close
+    code := {...}
+    parameter := Unit
+    pre-condition := auction_open 
+       && Sender = contract_owner                
+    post-condition := not post_auction_open 
+       && post_Balance = 0 
+       && transfer_token (Unit, Balance, contract_owner) ;
+
+    (%create -> %bid) with (auction_open = true)  
+       && (Amount > Balance) 
+    | (%create  -> %close) with (auction_open = true) 
+       && (Sender = contract_owner)
+    | (%bid -> %bid) with (Amount > Balance)  
+    | (%bid -> %close) with (Sender = contract_owner)  
+    | not (%close -> %bid) 
+    | not (%close -> %close)
+\end{lstlisting}
+
+There are several properties that we want to guarantee for this
+contract. Let us have a look at the specification for the auction
+contract in Listing \ref{lst:auction-contract-specification}. We omit
+the Michelson code of the smart contract due to its length.  For the
+\lstinline/%bid/ entrypoint, the input stack has only one element,
+which is a pair consisting of the parameter and the current
+storage. The parameter is \lstinline/Unit/ of type \lstinline/unit/.
+The current storage is represented as a nested pair with the
+structure described by the \lstinline|storage| phrase. 
+The output term should maintain the required pattern of the storage,
+but the values may be changed and these changes are recorded in
+different symbolic variables. In this specification, we add the prefix
+\lstinline/post_/ to the variable names to refer to the storage
+returned by the program. The output pattern could be safely removed in
+this example because the tool automatically generates an output
+pattern corresponding the one specified here.
+
+Here is the first property that we want to check: if a user calls the
+\lstinline/%bid/ entrypoint, when the contract is still open for
+bidding and the bid (i.e., the amount transferred with the call) is
+higher than the current bid (as specified in the
+\lstinline/pre-condition/ field from line 10 to line 11 in Listing
+\ref{lst:auction-contract-specification}), then the bid should
+succeed.  In this case, the highest bidder has to be updated to the
+sender (line 12 in the \lstinline/post-condition/ field), which is the
+address of the caller, and the balance of the contract should be the
+amount sent along with the call (line 13). Moreover, the previous
+highest bidder should receive their bid, which means the auction
+contract should transfer the \lstinline/Balance/ to the previous
+bidder, \lstinline/highest_bidder/ (line 14). 
+The predicate \lstinline/Transfer_token (data, amount, address)/
+represents a smart contract call with three arguments: the data sent
+along with the call, the amount of tokesn, and the address of the
+receiver.  When the call is just a token transfer, the data field has
+the value \lstinline/Unit/ of type \lstinline/unit/, indicating that
+this is just a token transfer with no additional data. Another
+important property is that the auction owner's address should not be
+changed. That is, after calling the \lstinline/bid/ entrypoint, the
+\lstinline/contract_owner/ should remain the same as before (line
+15). The last property guarantees that when the contract owner (line
+25) closes the open contract (line 24), the contract is first closed
+(line 26), and then money (\lstinline/Balance/) should be sent to the
+owner. Hence, the final auction balance is zero (lines 28 and 29).
+
+For a smart contract on the blockchain, the order of smart contract
+calls can be crucial. We specify ordering constraints among calls with
+an entrypoint relation. An entrypoint relation can be specified as
+\lstinline/%a with cd -> %b/, which starts with the name
+\lstinline/%a/ of the entrypoint and is followed by the keyword
+\lstinline/with/ in case conditions are specified as predicates. The
+following symbol \lstinline/->/ indicates that from the entrypoint
+that satisfies the condition \lstinline/cd/, it is possible  to call
+the entrypoint \lstinline/%b/. One smart contract specification can
+contain several entrypoint relations concatenated by
+\lstinline/|/. There is a special entrypoint named \lstinline/create/
+that indicates the contract state after deployment.
+
+Let us return to the auction contract. It is important to guarantee
+that contract deployment sets the  \lstinline/auction_open/ flag to
+\TRUE, indicating that the contract is open for bidding, i.e., users
+should be able to bid on the contract or the contract owner should be
+able to close it (lines 29-31). Furthermore, the bid call can happen
+successfully after another if the new bid is higher than the previous
+one (line 33). The  \lstinline/%close/ entrypoint can be called
+anytime if the caller is the contract owner (line 34). However, it
+should not be possible to call the  \lstinline/%bid/ entrypoint after
+the auction is closed (line 35), and, of course, it cannot be closed
+again if it is already closed (line 36). This sequence  illustrates
+the life cycle of the auction contract, which is depicted in Figure
+\ref{fig:auction-life-cycle}.
+
+\begin{figure}[tp]
+    \centering
+    \includegraphics[width=0.8\textwidth]{auction-life-cycle}
+    \caption{Auction contract life cycle}
+    \label{fig:auction-life-cycle}
+\end{figure}
+
 \section{Symbolic Execution Model}
@@
 \end{mathpar}
-\section {Domain Specific Language For Smart Contract Property Specification}
-\label{sec:domain-specific-language}
-Michelson, as a stack-based language, may pose a challenge for developers less familiar with it compared to more mainstream languages like Python, Java, or C.
-To address this, several high-level languages such as LIGO, SmartPy, and Liquidity have been created.
-These languages provide a more readable syntax, resembling popular programming languages, allowing developers to write Tezos smart contracts more comfortably.
-These high-level contracts are then compiled down to Michelson.
-
-For Tezos users who may lack expertise in Michelson, there is a desire to verify smart contract code before interaction.
-Our framework addresses this by introducing a domain-specific language (DSL) that facilitates the specification of smart contract properties in a mathematical and readable format.
-The goal is to create a language that is accessible and easily understandable, even for users who are not Michelson experts.
-
-To achieve this, our framework employs an SMT solver, specifically Z3, for property verification.
-The DSL is designed to allow users to express formulas that align with the capabilities of the SMT solver (Z3).
-This empowers users to write formulas that the solver can effectively handle, facilitating property verification in a more user-friendly manner.
-
-One of the main challenges with formal verification is that it is often the requirement for users to express the system in a specialized specification language.
-This poses two problems: it demands expertise in formal verification from the specifier and introduces a gap between the actual code and its specification.
-In our framework, this gap is eliminated as the exact Michelson code used for verification precisely corresponds to the actual code.
-Users are not obligated to possess formal verification expertise.
-
-\begin{figure}[]
-\begin{align*}
-\textbf{c} & ::= 
-    \text{Balance}
-   \Mid \text{post\_Balance}  
-   \Mid \text{Amount} 
-   \Mid \text{Sender} 
-   \Mid \text{Source} 
-   \Mid \text{Now} 
-   \Mid \text{Level} \\
-   &\Mid \text{Chain\_id} 
-   \Mid \text{Self\_address} 
-   \Mid \text{Total\_voting\_power} 
-   \Mid \text{Voting\_power} \\
-\textbf{e} & :: =  \textbf{i} \Mid  \textbf{s}  \Mid  \textbf{b} \Mid \textbf{c} \Mid (\text{x} : \text{T}) \\
-&\Mid \text{Unit}  \Mid \text{Never}  \Mid \text{True}  \Mid \text{False} \\
-&\Mid \text{Pair } \textbf{e } \textbf{e}  \Mid \text{Left } \textbf{e}  \Mid \text{Right } \textbf{e}  \Mid \text{Some } \textbf{e} \text{: T} \Mid \text{None T}  \\
-& \Mid \textbf{e} \text{ + } \textbf{e}\Mid \textbf{e} \text{ - } \textbf{e}  \Mid \textbf{e} \text{ * } \textbf{e} \Mid \textbf{e} \text{ \/ } \textbf{e} \Mid \textbf{e} \text{ \% } \textbf{e} \Mid \textbf{e} \text{ rem } \textbf{e} \\
-& \Mid \textbf{e} \text{ and } \textbf{e}\Mid \textbf{e} \text{ or } \textbf{e}  \Mid \textbf{e} \text{ nor } \textbf{e} \Mid  \text{ not } \textbf{e} \Mid \textbf{e} \text{ imply } \textbf{e} \\
-& \Mid \text{transfer\_token} (\textbf{e}, \textbf{e}, \textbf{e}) 
- \Mid \text{get\_map} (\textbf{e}, \textbf{e}) 
- \Mid \text{get\_big\_map} (\textbf{e}, \textbf{e}) \\
-& \Mid \text{get\_contract} (\textbf{e}, \textbf{e})  
- \Mid \text{abs} (\textbf{e})  
- \Mid \text{len} (\textbf{e})
- \Mid \text{size} (\textbf{e})
-\Mid \textbf{e} \text{$\wedge$} \textbf{e}  \\
-\textbf{p} & :: = \textbf{e} \text{ = } \textbf{e} 
-\Mid \textbf{e} \text{ != } \textbf{e}
-\Mid \textbf{e} \text{ > } \textbf{e}
-\Mid \textbf{e} \text{ >= } \textbf{e}
-\Mid \textbf{e} \text{ < } \textbf{e}
-\Mid \textbf{e} \text{ <= } \textbf{e} \\
-&\Mid \text{forall} (\textbf{e}, \textbf{p})
-\Mid \text{exsit} (\textbf{e}, \textbf{p})
-\end{align*}
-\caption{Syntax of predicates, p}
-\label{fig:syntax-predicates}
-\end{figure}
-
-The Michelson code, readily available on the Tezos blockchain, remains consistent across various high-level language platforms like LIGO, SmartPy, and Liquidity, all of which offer functions to compile programs into Michelson.
-This approach eliminates the need for users to be formal verification experts.
-The essential Michelson knowledge revolves around understanding data types and their usage when interacting with a smart contract on the Tezos blockchain, whether as parameters or in storage.
-
-\begin{lstlisting}[float,captionpos=b,caption={Smart contract property specification},label={lst:smart-contract-property-specification},numbers=left]
-mcontract Name = spec
-code := {c}
-input := t
-output := t'
-pre-condition := cd
-post-condition := cd'
-\end{lstlisting}
-Listing \ref{lst:smart-contract-property-specification} shows the syntax of our property specification language.
-Here, \KMCONTRACT, \KWITH, \KCODE, \KINPUT, \KOUTPUT, \KPRECONDI, and \KPOSTCONDI\ are keywords.
-The \KNAME\ is replaced by the contract name.
-In the input and output fields, the input and output patterns are specified.
-Since Michelson operates on a stack, we assume that the stack has only one element, as specified in the input pattern.
-Similarly, the output stack is assumed to be a stack with only one element, which is specified in the output field.
-Our syntax allows to specify incomplete and complete smart contract code.
-For the complete smart contrat code, as we have mentioned before, the output should be a pair consisting of an operation list and a storage.In our syntax, for verification purposes, we exclude the operation list, and the output is solely represented by the pattern of the value in the storage after the execution concludes.
-In fact, for a complete smart contract code, in some cases, the output pattern can be omitted, given that the input pattern must be a pair of parameters and storage.
-This implies that the storage pattern is part of the input pattern.
-In such cases, the prefix 'post' is used before the variables in the input term to indicate the corresponding storage value after the execution.
-The input and output patterns represent Michelson terms, which can be either concrete values or symbolic values, including variables.
-When a variable appears for the first time, it needs to be accompanied by its corresponding type declaration.
-However, subsequent mentions can omit the type declaration.
-Formally, the pre and post-condition instances are formulas in first-order logic, and they can be handled by an SMT solver, namely the Z3 solver in our framework.
-The specification language is constituted of predicates defined using the syntax defined as in Figure \ref{fig:syntax-predicates}.
-Formulas that are used in assertions or added to solvers are terms of Boolean sort.
-Otherwise, terms of Boolean and non-Boolean sort may be mixed in any combination where sorts match up.
-Universal and existential quantifiers bind variables to the scope of the quantified formula.
-\begin{lstlisting}[float,captionpos=b,caption={The specification of Add contracr},label={lst:add-contract-specification},numbers=left]
-mcontract Add = spec
-code := {UNPAIR; COMPARE; GE; 
-        IF {ADD}{PUSH string 'Unexpected Pair'; FAILWITH}}
-input := Pair (x : int) (y : int)
-output := (z : int)
-pre-condition := (x >= 5) | (y > 3)
-post-condition := (z >= 8)
-\end{lstlisting}
-Let's consider the  example of the property specification for the contract named Add as in Listing \ref{lst:add-contract-specification}.
-Here, the program takes as input a stack with only one element, which is a pair of two integers, symbolically specified in the Input field.
-It then unpairs the input pair to obtain two elements as two integers \lstinline/x/ and \lstinline/y/.
-It then proceeds to destructure the input pair, yielding two integers.
-Subsequently, the program performs a comparison between these two integers.
-If  \lstinline/x/ is greater than or equal to \lstinline/y/, the program constructs a new stack with a solitary element at the top representing the sum of  \lstinline/x/ and \lstinline/y/, designated as \lstinline/z/.
-Otherwise, the execution terminates with an error message containing the content 'Unexpected pair.' The specification continues by defining pre and post conditions, where the precondition states the assumption that the integer  \lstinline/x/ is greater than or equal to 5 and \lstinline/y/ is greater than or equal to 3.
-Here, the symbol  \lstinline/|/ is the conjuration.
-The postcondition asserts that the result sum \lstinline/z/ is greater than or equal to 8.
-
-A smart contract may offer various functions for users to interact.
-Therefore, our language is designed to allow users to specify different functions, referred to as entrypoints, in Michelson.
-This design enables us to specify and verify all functions within a smart contract.
-Furthermore, this design allows us to describe and verify relationships between functions.
-The syntax is as follows:
-\begin{lstlisting}[float,captionpos=b,caption={Multiple entrypoint specification syntax},label={lst:multiple-entrypoint-specification},numbers=left][h]
-mcontract Name = spec
-   entrypoint %a 
-      code := {c1}
-      input := t1
-      output := t1'
-      pre-condition := cd1
-      post-condition := cd1'
-   entrypoint %b 
-      code := {c2}
-      input := t2
-      output := t2'
-      pre-condition := cd2
-      post-condition := cd2'
-   entrypoint %c 
-      ...
-   < entrypoint relations>
-\end{lstlisting}
-where the entrypoint name is written after the \lstinline/%/ symbol and is followed by a property specification for the entrypoint.
-At the end of the specification is the entrypoint relation specification, which we will explain next.
-
-\begin{lstlisting}[float,captionpos=b,caption={Multiple entrypoint specification syntax},label={lst:multiple-entrypoint-specification},numbers=left][h]
-mcontract Name = spec
-   storage := s
-   entrypoint %a 
-      code := {c1}
-      parameter := t1
-      pre-condition := cd1
-      post-condition := cd1'
-   entrypoint %b 
-      code := {c2}
-      parameter := t2
-      pre-condition := cd2
-      post-condition := cd2'
-   entrypoint %c 
-      ...
-   < entrypoint relations>
-\end{lstlisting}
-
-To illustrate this, let's consider the  auction smart contract serving the auction events.
-The contract has two entrypoints, bid and close, which serve as functions for bidding and closing the contract, respectively.
-The smart contract storage on the blockchain is a pair containing the first element as a boolean value that indicates whether the contract is still open for bidding or already closed.
-The second element is another nested pair, where the first element  stores the highest bidder's address, and the second element is the contract owner's address.
-The current highest bid is reflected in the balance of the contract.
-
-Closing the contract transfers the balance to the owner and is restricted to the owner.
-Both closing and bidding operations fail if the auction is already closed.
-If bidding is open and the amount of tokens accompanying the bid exceeds the current highest bid, the current bidder replaces the previous highest bidder, and the previous highest bidder is reimbursed.
-Otherwise, bidding fails.
-
-Upon deployment, the owner deposits an initial balance to indicate the minimum bid.
-The contract is supposed to be deployed with the storage value  \lstinline/Pair True (Pair owner owner)/, indicating that bidding is allowed, and the contract owner is currently the highest bidder.
-
-\begin{lstlisting}[float,captionpos=b,caption={Auction contract specification},label={lst:auction-contract-specification},numbers=left]
-mcontract Auction = spec 
-  storage := Pair (auction_open: bool) 
-                     Pair (highest_bidder: address)
-                          (contract_owner: address))
-  entrypoint %bid
-    code := {...}
-    parameter := Unit 
-    pre-condition := auction_open 
-       && Amount > Balance
-    post-condition := post_highest_bidder = Sender 
-       && post_Balance = Amount 
-       && transfer_token (Unit, Balance, highest_bidder) 
-       && post_contract_owner = contract_owner ;
-  entrypoint %close
-    code := {...}
-    parameter := Unit
-    pre-condition := auction_open 
-       && Sender = contract_owner                
-    post-condition := not post_auction_open 
-       && post_Balance = 0 
-       && transfer_token (Unit, Balance, contract_owner) ;
-    (%create -> %bid) with (auction_open = true)  
-       && (Amount > Balance) 
-    | (%create  -> %close) with (auction_open = true) 
-       && (Sender = contract_owner)
-    | (%bid -> %bid) with (Amount > Balance)  
-    | (%bid -> %close) with (Sender = contract_owner)  
-    | not (%close -> %bid) 
-    | not (%close -> %close)
-\end{lstlisting}
-
-There are several properies that we want to grantuee in this contract.
-Lets take look at the specification for the auction contract in Listing \ref{lst:auction-contract-specification}.
-Here, we omit the Michelson code  of the smart contract due to its length.
-For the  \lstinline/bid/ entrypoint, the input stack is  the one with only one element, which is a pair consitting the parameter and the current storage.
-Here, the parameter is \lstinline/Unit/ of type \lstinline/unit/.
-The current storage represnted symbolicly as a nested pair, where the first element is the auction-open variable of type bool and the second element is an other pair consiting the highest-bidder of type address as the first element and the contract-owner variable of also type address as the second.
-
-There are several properties that we want to guarantee in this contract.
-Let's take a look at the specification for the auction contract.
-For the \lstinline/bid/ entrypoint, the input stack is the one with only one element, which is a pair consisting of the parameter and the current storage.
-Here, the parameter is \lstinline/Unit/ of type \lstinline/unit/.
-The current storage is represented symbolically as a nested pair, where the first element is the \lstinline/auction_open/ variable of type \lstinline/bool/, and the second element is another pair consisting of the \lstinline/highest_bidder/ of type \lstinline/address/ as the first element and the \lstinline/contract_owner/ variable, also of type \lstinline/address/, as the second element.
-The output term should maintain the required pattern of the storage, where the values may be changed, and these changes are recorded in other symbolic variables.
-In this specification, we add the prefix \lstinline/post/ to the old variable names to represent the new variables corresponding to the old ones.Note that the output pattern here could be safely removed, and the tool will automatically generate the output pattern to match the one specified here.
-
-The first property that we want to check is that if a user sends a bid to the contract by calling the \lstinline/bid/ entrypoint, such that the contract is still open for bidding and the bid is higher than the current bid (as specified in the  \lstinline/pre-condition/ field from line 10 to line 11 in Listing \ref{lst:auction-contract-specification}), then the bid should succeed.
-This means the highest bidder has to be updated to the sender (line 12 in the \lstinline/post-condition/ field), which is the address of the user, and the balance of the contract should be the amount sent along with the call (line 13).
-Moreover, the old highest bidder should receive their bid, which means the auction contract should transfer the \lstinline/Balance/ to the previous bidder, \lstinline/highest_bidder/ (line 14).
- \lstinline/ Transfer_token (data, amount, address)/ is a predicate that represents a smart contract call with three arguments: the data sent along with the call, the amount, and the address of the receiver.
-When the call is just a token transfer, the data field has the value \lstinline/Unit/ of type \lstinline/unit/, indicating that this is just a token transfer with no additional data.
-Another important property is that the auction owner's address should not be changed.
-This means that after calling the \lstinline/bid/ entrypoint, the \lstinline/contract_owner/ should remain the same as before calling the entrypoint (line 15).
-The last property guarantees that when the contract owner (line 25) closes the open contract (line 24), the contract is first closed (line 26), and then money (\lstinline/Balance/) should be sent to the owner.
-This means the auction balance is now zero (lines 28 and 29).
-
-For a smart contract on the blockchain, the order of smart contract calls can be crucial.
-Here, we refer to it as entrypoint relation.
-An entrypoint relation can be specified as \lstinline/%a with cd -> %b/, where it includes the name \lstinline/a/ of the entrypoint followed by the symbol \lstinline/%/ and is followed by the keyword \lstinline/with/ in case conditions are specified as predicates.
-Next is the symbol \lstinline/->/, implying that from the entrypoint a that satisfies the condition \lstinline/cd/, it leads to the entrypoint \lstinline/b/.
-One smart contract specification can contain several entrypoint relations concatenated by the conjunction \lstinline/|/.
-There is a special entrypoint named \lstinline/create/ that indicates the contract state after deployment.
-
-Let's return to the auction contract.
-It is important to guarantee that after contract deployment with the  \lstinline/auction_open/ set to \TRUE, indicating that the contract is open for bidding, users should be able to bid on the contract or the contract owner should be able to close it (lines 29-31).
-Furthermore, the bid call can happen successfully after another if the new bid is higher than the previous one (line 33).
-The  \lstinline/close/ entrypoint could also be called after a bid call if the caller is the contract owner (line 34).
-However, it should not be possible to call the  \lstinline/bid/ entrypoint to bid on the contract after it is closed (line 35), and, of course, it cannot be closed again if it is already closed (line 36).
-This sequence could illustrate the life cycle of the auction contract, which is depicted in Figure \ref{fig:auction-life-cycle}.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.8\textwidth]{auction-life-cycle}
-    \caption{Auction contract life cycle}
-    \label{fig:auction-life-cycle}
-\end{figure}
 
 \section {Static Checker}
+\label{sec:static-checker-we}
 We verify the contract through symbolic execution against its specifications in the contract module.
@@
 \section {Conclusion}
-\section {Appendix}
+\label{sec:concl-sect-append}
+
+Symbolic execution is well known to suffer from challenges related to
+state explosion, particularly when applied to large
+systems. Fortunately, the constraints of storing and running smart
+contracts on a blockchain platform impose size limitations, making
+them manageable for symbolic execution.
+
+In future work, we want to extend XXX in two directions. 
+First, we want to address the interaction of several entrypoints by
+extending the specification language to state allowed sequences of
+contract invocations.
+
+Second, a Michelson returns a list of instructions, which may contain
+further contract invocations. Dealing with this kind of contracts
+requires an extension to the symbolic interpreter so that a sequence
+of contract invocations can be processed in one run.
+
+\bibliography{}
 \end{document}

### 2024-01-03 reports/2023-12-31/report.tex
end-of-year-report-dec-31-2023

--- 2023-07-20 reports/2023-07-01/report.tex
@@
 
-\section{Report January-June 2023}
+\section{Progress Report July 2023 - December 2023}
 \label{sec:executive-summary}
@@
 
-Currently, the project is on track and making good progress, but Ms.\ Doan is on maternal leave
-and it is unclear if she will take parental leave thereafter. If she
-does, it may lead to unforseeable delays.
+Currently, the project is slightly delayed but making good progress. Ms.\ Doan
+returned from  maternal leave in October 2023.
 
-\subsection{January 2023 - June 2023}
+\subsection{Proposed activities for January 2023 - June 2023}
 
 \begin{itemize}
-\item Proposed activity: Development of a dynamic logic as a formal foundation for symbolic interpretation of Michelson. \\
-  $\Rightarrow$ This activity progressed significantly with the help of a master's
-  student supervised by Thiemann. The activity started later than
-  planned because the student was unavailable till the end of the
-  teaching period in March.
+\item Activity: Development of a dynamic logic as a formal foundation for symbolic interpretation of Michelson. \\
+  $\Rightarrow$ This activity progressed significantly.  The master's
+  thesis has been completed in November and is currently under review (by the examiner).
 \item Deliverable: Formalization (in Agda) of a dynamic logic for a core fragment of Michelson with soundness proof. \\
-  $\Rightarrow$ This deliverable is currently in beta and will be finished when the
-  master's thesis submission is due in September 2023.
+  $\Rightarrow$ This deliverable is available  at
+  \url{https://github.com/Barnaboss/thesis-michelsonDL}. It will be
+  released after the thesis review period.
 \item Deliverable: Paper about this formalization (writeup starting
@@
   $\Rightarrow$ The paper will be based on the master's thesis, so the final writing
-  starts after the submission in September. The goal is to submit to a
-  conference during the winter/early spring.
+  starts after completion of the thesis review. The goal is to submit to a
+  conference during spring.
 \end{itemize}
 
-\subsection{July 2023 - December 2023}
+\subsection{Proposed activities for July 2023 - December 2023}
 \label{sec:july-2023-december}
@@
 \item Activity: Implementation of symbolic interpreter for a core
-  fragment of Michelson in OCaml based on an SMT solver, most likely
-  on Z3. \\
+  fragment of Michelson in OCaml based on the SMT solver Z3. \\
   $\Rightarrow$ This activity has been driven by Doan between January and June
-  2023. 
+  2023 and then further after her return from maternity leave. 
 \item Deliverable: Symbolic interpreter. \\
@@
   \url{https://github.com/proglang/tezos-project/tree/master/static_checker}
-\item Deliverable: Case studies with example contracts.
-\item Deliverable: Paper or tutorial on this tool (writeup starting
-  January 2024) \\
+\item Deliverable: Doan completed two case studies with example contracts.
+\item Deliverable: Paper or tutorial on this tool (writeup started,
+  submission planned for a deadline in spring) \\
   $\Rightarrow$ A draft is available here \url{https://github.com/proglang/tezos-project/tree/master/symbolic-execution/paper}
@@
 
-\subsection{January 2024 - June 2024}
+\subsection{Proposed activities for January 2024 - June 2024}
 \label{sec:january-2024-june}
@@
 
-\subsection{July 2024 - December 2024}
+\subsection{Properties activities for July 2024 - December 2024}
 \label{sec:july-2024-december}

### 2024-01-05 papers/static-checker/ecoop2024/ecoop2024.tex
section 2, 3, 4

@@
 \newcommand\pt{\todo[author=PT,inline]}
+\newcommand\atha{\todo[author={@Ha},inline]}
 \lstdefinelanguage{michelson}{
@@
 
-Michelson is a stack-based language.
-A Michelson program specifies the type of its storage, the type of its single
-parameter, and a list of instructions for the underlying stack machine.
+Michelson is a stack-based, statically typed functional programming language.
+A Michelson program is given by the type $S$ of its storage, the type $P$ of its single
+parameter, and a typed list of instructions for the underlying stack machine.
 A program starts on a stack with one element which contains a pair of
@@
 of the final storage value (to be saved on the blockchain) and a list
-of instructions.
-These instructions may be token transfers or contract invocations,
-among other possibilities.
-
-Besides the standard datatypes (e.g., numbers, lists, pairs, sums)
+of operations.
+These operations are syntactic commands like token transfers or
+contract invocations, among other possibilities.
+The program thus computes a function $P\times S \to O^* \times S$
+where $O$ is the type of operations.
+
+Besides the standard datatypes (e.g., numbers, lists, pairs, sums, functions)
 with the expected operations,
 Michelson supports a number of types and operations specific to blockchain applications (e.g.,
-\texttt{mutez} for tokens, \texttt{address} for blockchain addresses).
-
-Here is a simple example of a Michelson program:
-
-TO BE COMPLETED
-
-\pt{Introduce entrypoints}
-
-\pt{I don't think the next paragraph is strictly needed}
-Michelson, as a stack-based language, may pose a challenge for
-developers less familiar with it compared to more mainstream languages
-like Python, Java, or C. To address this, several high-level languages
+\texttt{mutez} for tokens, \texttt{address} for blockchain
+addresses). The type system in simple in the sense that it does not
+support quantification over types.
+
+Listing~\ref {lst:simple-program-add} contains a simple example of a Michelson program.
+\begin{lstlisting}[float=tp,captionpos=b,caption={A simple Michelson program},label={lst:simple-program-add},language=michelson]
+parameter int;
+storage   int;
+code  { 
+(*                 pair int int :: [] *)
+  DUP; UNPAIR;
+(*   int :: int :: pair int int :: [] *)
+  COMPARE; GE; 
+(*         bool :: pair int int :: [] *)
+  IF {UNPAIR; ADD}{PUSH string 'Unexpected Pair'; FAILWITH}
+      }
+\end{lstlisting}
+\atha{Explain the example program}
+\atha{Explain some important instructions for reference later on:
+  AMOUNT, BALANCE, FAILWITH, \dots}
+\atha{Introduce entrypoints}
+
+\atha{Add citations/references to the high-level languages.}
+While contracts may be implemented directly in Michelson, it can also
+be used as a compilation target. Indeed, several high-level languages
 such as LIGO, SmartPy, and Liquidity have been created. These
@@
 programming languages, allowing developers to write Tezos smart
-contracts more comfortably. These high-level contracts are then
-compiled down to Michelson.
+contracts more comfortably. Our tools are applicable to all of them
+because they compile to Michelson.
 
@@
 % to verify smart contract code before interaction.
-Our framework contains a domain-specific language (DSL) that
-facilitates the specification of smart contract properties in a
-mathematical and readable format.
+Our framework contains a domain-specific language (DSL) to specify
+mathematical properties of smart contracts.
 The DSL is designed to allow users to write formulas that align with
@@
 The goal is to create a language
-that is accessible, easily understandable even for users who are
+that is accessible and understandable for users who are
 not Michelson experts, and guarantees formulas that the solver can handle effectively.
@@
 &\Mid \text{Unit}  \Mid \text{Never}  \Mid \text{True}  \Mid \text{False} \\
-&\Mid \text{Pair } \textbf{e } \textbf{e}  \Mid \text{Left } \textbf{e}  \Mid \text{Right } \textbf{e}  \Mid \text{Some } \textbf{e} \text{: T} \Mid \text{None T}  \\
+&\Mid \text{Pair } \textbf{e } \textbf{e}  \Mid \text{Left } \textbf{e}  \Mid \text{Right } \textbf{e}  \Mid \text{Some } \textbf{e} \Mid \text{None T}  \\
 & \Mid \textbf{e} \text{ + } \textbf{e}\Mid \textbf{e} \text{ - } \textbf{e}  \Mid \textbf{e} \text{ * } \textbf{e} \Mid \textbf{e} \text{ \/ } \textbf{e} \Mid \textbf{e} \text{ \% } \textbf{e} \Mid \textbf{e} \text{ rem } \textbf{e} \\
@@
 
-\begin{lstlisting}[float,captionpos=b,caption={Smart contract property specification},label={lst:smart-contract-property-specification},numbers=left]
+\begin{lstlisting}[float=tp,captionpos=b,caption={Smart contract property specification},label={lst:smart-contract-property-specification},numbers=left]
 mcontract Name = spec
@@
 \end{lstlisting}
-Listing \ref{lst:smart-contract-property-specification} shows the
+
+\subsection{Simple contracts}
+\label{sec:simple-contracts}
+
+Listing~\ref{lst:smart-contract-property-specification} shows the
 syntax of our property specification language. Here, \KMCONTRACT,
@@
 keywords. The \KNAME\ is replaced by the contract name. In the input
-and output fields, the input and output patterns are specified. Since
+and output fields, the input and output patterns are specified.
+\atha{What patterns are supported? Patterns are not explained!}
+Since
 Michelson operates on a stack, we assume that the stack has only one
@@
 specified in the output field. Thus, the syntax allows us to specify
-incomplete contracts, too. For a complete smart contract, the output
+incomplete contracts, too.
+\pt{I disagree (though it would be a useful feature). To this end, there should be patterns to cover stacks
+  with more than one element. As it stands, the input pattern can only
+speak about the top of the stack and the output pattern only about the
+second component of the top of the stack, which is assumed to be a
+pair.\\
+Moreover, a specification might want to say something about the list
+of operations, too, e.g., that tokens are transferred to some address.}
+For a complete smart contract, the output
 should be a pair consisting of an operation list and a storage.
@@
 our case, Z3). The specification language is constituted of predicates
-defined using the syntax defined in Figure
-\ref{fig:syntax-predicates}. Formulas that are used in assertions or
+defined using the syntax defined in Figure~\ref{fig:syntax-predicates}. Formulas that are used in assertions or
 added to solvers are terms of sort Boolean. Otherwise, terms of
@@
 to the scope of the quantified formula.
+\atha{More explanation is needed about expressions and formulas. Why
+  do you support left and right, but not lists? Why Never? What is the
+meaning of transfer\_token, get\_map, get\_contract? The constants
+must be explained (though you could do that in
+Section~\ref{sec:background}). (Less common items could be omitted!)}
+
 \begin{lstlisting}[float,captionpos=b,caption={Specification of Add contract},label={lst:add-contract-specification},numbers=left]
@@
 terminates with an error message containing the content
-\lstinline|'Unexpected pair'|. The specification continues by defining
+\lstinline|'Unexpected pair'|.
+\atha{This Michelson code with its explanation might be an example for Section~\ref{sec:background}}
+The specification continues by defining
 pre- and postconditions, where the precondition states the assumption
@@
 \lstinline/z/ is greater than or equal to 8.
+\atha{This specification is meaningless. Why not use $x\ge y$ as
+  precondition and $z = x+y$ as postcondition?}
+
+\subsection{More than one entrypoint}
+\label{sec:more-than-one}
 
@@
 
-\pt{can we put the source code of the contract somewhere, e.g. in an appendix?}
+\atha{can we put the source code of the contract somewhere, e.g. in an appendix?}
 To illustrate entrypoint relations, let us consider a smart contract
@@
 
+\subsection{Entrypoint relations}
+\label{sec:entrypoint-relations}
+
 For a smart contract on the blockchain, the order of smart contract
@@
 \end{figure}
+
+\section{Static Checker}
+\label{sec:static-checker-we}
+
+We verify the contract against its specifications in the contract
+module by symbolic execution. Symbolic execution involves calculating
+a symbolic stack at each transition from one Michelson instruction to
+the next. The symbolic interpreter is fully typed and rejects
+ill-typed Michelson programs, provided the ill-typed part is reachable
+from the default entry point.  The initial stack is derived from the
+input pattern for each the entry point. To maintain symbolic values as
+concrete as possible, some instructions may be deemed unreachable or
+only reachable under specific conditions. This process yields, for
+each entry point, a set of final symbolic stacks accompanied by a path
+condition indicating when this final state is reachable. A state is
+discarded from the final state space if the path condition is not
+satisfiable, indicating that the path is unreachable. Additionally,
+for each \FAILWITH\ instruction, we obtain a symbolic value for the
+reported message and a path condition indicating the reachability of
+this instruction. We employ the SMT solver Z3  to assess the
+satisfiability of a path condition and to check smart contract
+properies specified by pre- and post conditions.
+
+The architecture of the static checker is illustrated in
+Figure~\ref{fig:architecture-of-static-checker}. The system comprises
+three phases. The first phase is user specification, where users
+provide the Michelson code of the contract and define the properties
+that the smart contract should satisfy. Subsequently, the symbolic
+interpreter is run on the code with the provided input pattern.  The
+path conditions are then fed into a Z3 converter, which transforms
+symbolic terms into Z3 formulas. Concurrently, the property
+specification, specifically pre- and post conditions, also undergoes
+conversion to Z3 formulas. The results of the symbolic execution and
+Z3 formulas are then input into the static checker, which verifies
+whether these properties hold for the smart contract
+implementation. This constitutes the verification phase.
+
+\subsection{User specification}
+\label{sec:user-specification}
+
+In the user specification phase, users compose the specification in
+our domain-specific language using the syntax outlined in
+Section~\ref{sec:domain-specific-language}. Michelson code, whether
+composed by users, obtained from the Tezos blockchain, or compiled
+from higher-level languages, can be seamlessly used within our
+framework. The specification is subsequently parsed into an Abstract
+Syntax Tree (AST) in OCaml. The code and the input pattern are then
+input to the symbolic interpreter. In the next phase, the pre- and
+post-predicates are transformed into Z3 formulas by the Z3 converter.
+
+\subsection{Michelson interpreter and Z3 converter}
+\label{sec:mich-interpr-z3}
+The symbolic interpreter implements the execution model described in
+Section~\ref{sec:symbolic-execution-model}. When provided with a
+concrete input, the interpreter produces a concrete value. In the
+presence of symbolic input, the result comprises a set of symbolic
+states represented as terms in OCaml. As Michelson's infrastructure is
+implemented in OCaml, the conversion of Michelson types or terms to
+their OCaml counterparts is straightforward. Each state contains the
+output stack, which has only one element consisting of an operation
+list and storage, along with the path conditions represented as
+predicates in conjunctive normal form. This output is then fed into
+the Z3 converter, which handles two different types of terms:
+assertion terms from the AST representing the pre- and post-condition
+specifications, and terms resulting from the interpreter. We utilize
+the Z3 library in OCaml to construct this converter. Some adjustments
+are necessary to convert these terms into Z3 formulas. For example, as
+there is no natural number type (\TNAT) in Z3, it is injected to Z3's
+integer type with a constraint asserting that the value is greater
+than or equal to zero. Several constants, such as \CAMOUNT, \CBALANCE,
+\CSENDER\ as well as cryptographic functions, such as \FSHA,
+\FHASHKEY\ are predefined in the environment that works for any smart
+contract specifications.
+
+% \paragraph{Dealing with loop formalization}
+% \label{sec:dealing-with-loop}
+Our execution model formalizes loops symbolically using the \FOLD\ and
+\FMAP\ functions (see
+Section~\ref{sec:symbolic-execution-model}). This approach has the
+advantage of allowing us to convert these loops into formulas
+compatible with certain SMT solvers, such as Z3, which support these
+functions. Specifically, Z3 provides \lstinline/seq.map fn s/, a map
+function on sequence \lstinline/s/, and
+\lstinline/(seq.foldl fn b s)/, a fold function with an initial value \lstinline/b/ on sequence
+\lstinline/s/. These functions are supported for checking assertions
+that contain them. Therefore, we can directly convert the symbolic
+results of loops into formulas in Z3. 
+\subsection{Static checker}
+\label{sec:static-checker}
+The static checker now performs the verification process by employing symbolic execution against the property specification in the DSL.
+It utilizes the results from the previous phases, including symbolic execution, Z3 formulas representing pre and post conditions, and path conditions.
+
+We first build the input state from the input pattern and run the
+symbolic interpreter on the input stack with the provided code to
+generate all symbolic execution states. Symbolic execution ensures
+that all states are reachable from the initial state, as any
+unreachable states are discarded from the final states as their path
+conditions are unsatisfiable. Using the output pattern and the pre-
+and post-conditions converted by the Z3 conveter, the tool then
+performs different checks. The static checker offers three distinct
+features: output check, fail condition, and property check.
+
+\subsubsection{Output check}
+\label{sec:output-check}
+The first check is the output check, where the checker verifies
+whether the output pattern matches. The final state contains a stack
+with only one element as \Stack\ \STACKCONCAT\ \EMPTYSTACK. There are
+two different forms of the final state. In the case where the code is
+given as incomplete smart contract code, the element \Stack\ contains
+just a normal term and its corresponding type as (\Term,
+\TY). However, in the case of a complete smart contract code, it has
+the form (\PAIR\ \VOPERATIONLIST\ \VSTORAGE, \TPAIR\ (\TOPERATIONLIST)
+\TYS) \STACKCONCAT\ \EMPTYSTACK, where \VSTORAGE\ is the term
+representing the storage and \VOPERATIONLIST\ repesents a operation
+list. Given an output pattern $ \tau$, the checker scans all the final
+states, which do not contain a failwith stack and checks whether the
+output pattern matches. In the former case, it matches $ \tau$  with
+the term \Term. In the latter case, it essentially matches with the
+corresponding part \VSTORAGE\ in the final states resulting from the
+symbolic interpreter. When the input pattern is a concrete value, the
+result from the interpreter is also concrete, and then the checker can
+be used to verify if the output aligns with the expectations
+specified in the output field.
+
+Listing~\ref{lst:add-contract-specification} contains an example of an
+incomplete smart contract code. The specification states that the
+output of the code must be a stack that contains only one element of
+type \TINT\, symbolically represented as a variable \VZ\ of type
+\TINT.  In this example, there are two final states, the first one
+being a failwith state recording the failwith condition when the first
+element of the pair is less than the second element. The failwith
+state contains the message \lstinline|'Unexpected Pair'|, which
+describes the reason for the failure. The second state is a reachable
+state that contains, in the top element, an integer value, which is
+the sum of the two elements of the pair. The output check succeeds for
+this example as expected. However, this test could fail if, for
+example, the output pattern is incorrectly specified as a variable of
+a type that does not match with the actual result. If the input
+pattern is concrete, for instance, a pair of numbers as in
+\lstinline|Pair 5 3|, then the expected output should be the number
+\lstinline|8|. To check this,  the output pattern may be specified as
+a concrete value.
+
+The second example in Listing \ref{lst:auction-contract-specification}
+is the specification for a smart contract code. The output pattern
+represents the updated storage after executing the code. There are
+several final states resulting from the symbolic execution. The
+failwith state is ignored for the output check, and all other
+reachable states are matched with the output term. The output check
+succeeds for this example.
+
+\subsubsection{Fail condition}
+\label{sec:fail-condition}
+A Michelson contract can fail due to a programmer-induced condition
+caused by the instruction \FAILWITH. It terminates contract execution
+with an error message reported back to the caller. This error message
+includes the top value on the stack. These failures are important in
+smart contract programming to guarantee that a smart contract call
+should not be successful under specific circumstances. Smart contract
+calls are expected to fail due to malicious behavior, such as an
+unauthorized caller or invalid arguments passed along the call. For
+example, the auction contract should not be closed by someone who is
+not the owner of the contract, and the bidding should not succeed if
+the bid is not strictly higher than the current highest bid. Several
+smart contract standards, such as
+\cite{@ha-supply-a-smart-contract-standard}, require the contract to fail
+with specific messages under certain conditions. Therefore, it is
+essential to check the fail conditions of a contract.
+
+The static checker provides a feature to generate all fail conditions
+implemented in a smart contract code. The tool searches for all
+failwith states, resulting from an execution terminated by the
+\FAILWITH\ instruction, from the final state space, collects the path
+conditions and the recorded message. The result returned to users
+includes the fail condition together with the message. For example,
+for the specification in Listing \ref{lst:add-contract-specification},
+the fail condition is recorded as
+\lstinline/(x < y): 'Unexpected Pair'/.
+
+The ability to generate fail conditions is a potent feature of our
+static checker, particularly in verifying access control properties
+across various smart contracts. Specifically, in numerous smart
+contract configurations, certain entrypoints are designated for
+invocation only by authorized entities, for instance, by the contract
+owner. Consequently, these entrypoints must result in failure if the
+callers lack the necessary authorization. This crucial access control
+property is verified by examining the fail conditions of a smart
+contract, ensuring that unauthorized callers trigger the intended
+failures in the system.
+
+The auction contract exhibits several fail conditions. For the
+entrypoint \lstinline/bid/, the fail condition is as shown in
+Listing~\ref{lst:fail-condition-auction-contract-bid} and for the
+\lstinline/close/ entrypoint, it is recorded in
+Listing~\ref{lst:fail-condition-auction-contract-close}. For the
+\lstinline/bid/ entrypoint, there are three fail conditions.  (1) If
+the auction is closed, (2) if the auction is open, but the amount less
+than or equal to the balance, (3) if the auction is open, the amount
+is greater than the balance, but the highest bidder's address is
+invalid. The last failure can happen because there are valid Michelson
+addresses, which are not associated with any real account on the Tezos
+blockchain, or the parameter's type is not correct: the transfer can
+only succeed if the address is associated with an account and the
+parameter supplied matches with the parameter expected by the Tezos
+blockchain. Bidding returns the previous highest bid as part of the
+transaction where the highest bidder is stored as a value of type
+address. However, to receive a token transfer, this address must be
+cast (by the Michelson implementation of the contract) to an implicit
+contract of Michelson type (\TCONTRACT\ \TUNIT). This cast is
+unavoidable, as a value of contract type cannot be stored.  However,
+the cast may fail for the reasons just discussed, and its failure
+leads to an error condition that is reported with a \FAILWITH\
+instruction in the implementation. In our framework, this cast failure
+shows up  as a fail condition, but the user's preconditions assume
+that casting is successful. The \lstinline/close/ entrypoint has
+similar fail conditions when the auction is closed or the owner's
+address is cannot be cast. The other fail condition occurs when the
+auction is open, but the sender who calls this entrypoint is not the
+owner of the contract, which was stored in the contract owner part.
+\atha{This discussion suggests that the specification is incomplete:
+  it should contain the assertion that the highest bidder as well as
+  the contract owner field are valid and point to a unit contract!}
+
+\begin{lstlisting}[float=tp,captionpos=b,caption={Fail condition for auction contract bid entrypoint },label={lst:fail-condition-auction-contract-bid},numbers=left]
+1. not (auction_open): 'Already closed'
+2. auction_open && (Amount <= Balance):
+   'Not higher than the current highest bid'
+3. auction_open && not (Amount <= Balance) && 
+   get_contract (Unit, highest_bidder) = None:
+   'Invalid address' 
+\end{lstlisting}
+
+\begin{lstlisting}[float=tp,captionpos=b,caption={Fail condition for auction contract close entrypoint},label={lst:fail-condition-auction-contract-close},numbers=left]
+1. not (auction_open): 'Already closed'
+2. auction_open && Sender != contract_owner): 'Not owner'
+3. auction_open && (Sender = contract_owner) &&
+   get_contract (Unit, contract_owner) = None:
+  'Invalid address'
+\end{lstlisting}
+
+In this implementation of the auction contract, the failures are
+recorded as expected. The contract is designed to fail when the
+auction is closed, the bid is not greater than the old highest bid, or
+the caller is not the contract owner when attempting to close the
+contract as transferring the contract balance to their account as a
+part of the action.
+
+\subsubsection{Property check}
+\label{sec:property-check}
+
+The static checker enables users to verify smart contract properties
+by providing pre- and post-condition specifications. A property is
+specified with the clause:  \lstinline/pre-condition := &&/
+$\Phi_{i}$ followed by \lstinline/post-condition := &&/ $\Psi_{j}$. This
+specification asserts that if all preconditions $\Phi_{i}$ hold before
+smart contract execution, then all $\Psi_{j}$ must hold after
+successful (i.e., without failure) termination. To verify this
+property, we explore all the paths $\Pi$ 
+with the path condition $\Theta$ such that ($\bigwedge \Phi_{i}$
+$\land$ $\Theta$) is satisfiable. We then check that for every path
+$\Pi$, $\neg$ ($\bigwedge \Phi_{i} \rightarrow \bigwedge \Psi_{j}$) is
+unsatisfiable in the context given by the input for the entry point
+and its corresponding final state and path condition.
+\atha{Don't you have to include $\Theta$ in the check for unsat?}
+
+Consider the specification of the Add contract in Listing
+\ref{lst:add-contract-specification}. In this context, the two
+variables \lstinline/x/ and \lstinline/y/ are integers. The results of
+the symbolic execution are either a failwith state with the path
+condition \lstinline/x/$<$\lstinline/y/,  or a state in which the
+final stack has only one element, which is a symbolic variable
+\lstinline/sbvar/ of type integer, with the path condition stating
+that the variable \lstinline/x/ is greater than or equal to
+\lstinline/y/ and the symbolic variable \lstinline/sbvar/ is equal to
+the sum of \lstinline/x/ and \lstinline/y/.  For this specification,
+the failwith branch is discarded because the precondition is not
+satisfy with tha path condition, and then \lstinline/z/ is matched to
+the symbolic variable \lstinline/sbvar/ in the other branch. In this
+example, the checker then verifies that given the with the context
+asserting that (\lstinline/x/ >= \lstinline/y/) $\land$ (\lstinline/z/
+= \lstinline/x/ + \lstinline/y/), $\neg$ ((\lstinline/x/ >= 5) $\land$
+(\lstinline/y/ > 3) $\rightarrow$ (\lstinline/z/ >= 8)) is
+unsatisfiable.
+\atha{I don't understand the last sentence/formula. Where does the
+  $z\ge8$ come from?}
+
+\subsubsection{Life-cycle check}
+\label{sec:life-cycle-check}
+\atha{To be completed}
+
+\section{Case Studies}
+\label{sec:case-stud-subs}
+
+This section reports two case studies that we conducted with the
+implemented system. Both case studies are real contracts deployed on
+the Tezos blockchain and are taken from the realm of financial
+applications.
+
+\subsection{USDtz}
+\label{sec:usdtz}
+
+In a blockchain ecosystem, tokens represent digital assets that can be
+transferred between accounts. These tokens are securely stored and
+verified within the blockchain network. There are various types of
+tokens, including native tokens (cryptocurrencies) like Bitcoin,
+Ether, Tezos, and others. Additionally, tokens can be created as
+overlays through smart contracts on an existing blockchain. Two common
+categories are: (1) Fungible Tokens (FT), which are interchangeable
+and (2) Non-Fungible Tokens (NFTs), which represent unique digital
+assets, and each unit is distinct. Stablecoins, falling under fungible
+tokens, are designed to maintain a stable value by tracking the value
+of a fiat currency like USD or EUR.
+\atha{add citations!}
+
+While designers can create tokens that behave in any way they want, it
+is advisable to implement tokens that adhere to established standards.
+This adherence guarantees interoperability and compatibility across
+different platforms. A token standard defines a set of rules and an
+interface that smart contracts must follow to ensure compatibility
+with decentralized exchanges, wallets, and other tools within the
+ecosystem. For example, ERC-20 is a token standard used in Ethereum.
+
+\atha{provide references for the standards!}
+The Tezos blockchain has its own set of standards known as Financial
+Applications (FA). Two notable standards are: (1) FA 1.2, designed for
+fungible tokens, and (2) FA 2, a more versatile standard accommodating
+both fungible and non-fungible tokens (NFTs). The standard outlines a
+smart contract that functions as a ledger, associating identities with
+balances. This ledger is designed to facilitate token transfer
+operations and enable approvals for spending tokens from other
+accounts. Any contract aiming to implement the standard must
+incorporate the functions specified in
+Listing~\ref{lst:fa12-interface} such as token transfer (transactions
+between users), approval (allowing one user to send tokens from
+another user's address),  allowance (browsing the amount of tokens
+available for an account to sending from another address), user
+balance (checking the balance of a user), and current supply (checking
+the total supply of tokens across all addresses), where
+\lstinline/view a r = pair a (contract r)/ implies an view entrypoint.
+A view is an entrypoint that takes an
+argument of type \lstinline/a/ and a callback that results in a value
+of type \lstinline/r/. The callback in this case will be another
+contract address. Further elaboration on the details of FA 1.2 can be
+found in \cite{financial-applications-1.2}, and we will delve into
+these functions in subsequent 
+sections.
+\atha{is that correct: ``callback that results in a value of type r''?
+I would have expected that the callback \textbf{expects} a value of
+type r.}
+
+\begin{lstlisting}[float=tp,captionpos=b,caption={FA 1.2 interface},label={lst:fa12-interface},numbers=left]
+(address :from, (address :to, nat :value))    %transfer
+(address :spender, nat :value)                %approve
+(view (address :owner, address :spender) nat) %getAllowance
+(view (address :owner) nat)                   %getBalance
+(view unit nat)                               %getTotalSupply
+\end{lstlisting}
+
+In this section, we verify USDtz \cite{USDtz-implementation}, an
+implementation of the FA 1.2 standard. Our goal is to ensure that the
+implementation aligns with the standard, verifying its
+correctness. USDtz is a stablecoin and one of the first and
+longest-running coins on the Tezos blockchain, launched in September
+2020. The smart contract is located at the address
+\texttt{KT1LN4LPSqTMS7Sd2CJw4bbDGRkMv2t68Fy9}, and the code can be
+found on the Tezos blockchain \cite{USDtz-address}. USDtz adheres to
+the FA token standard, and the initial deployment of the USDtz smart
+contract follows the FA 1.2 standard. 
+The implementation consists of approximately 1000 instructions. It
+contains all five entrypoints required in the FA 1.2 interface and
+four additional ones.  We will verify each entrypoint of this smart
+contract. First, we examine how the approvable ledger is implemented
+in the USDtz smart contract. The ledger is a substantial map that
+links user addresses to a pair consisting of their balance and a map
+associating addresses with the amount of tokens allowed to be
+transferred from that user's
+account. Listing~\ref{lst:storage-udstz-contract} shows the storage type of the
+USDtz smart contract.
+
+\begin{lstlisting}[float=tp,captionpos=b,caption={Storage of the USDtz smart contract},label={lst:storage-udstz-contract}]
+(pair
+  (big_map %ledger
+    (address :user)
+    (pair (nat :balance)
+          (map :approvals (address :spender) (nat :value))))
+  (pair (address %admin)
+        (pair (bool %paused) (nat %totalSupply))))
+\end{lstlisting}
+
+\subsubsection{transfer}
+As illustrated in Listing \ref{lst:fa12-interface}, the
+\lstinline/transfer/ entrypoint credits the account associated with
+the address provided in the \lstinline/to/ parameter, while debiting
+the account corresponding to the \lstinline/from/ parameter with the
+specified \lstinline/value/ amount. The FA 1.2 standard mandates that
+this call must fail under the following two conditions: (1) In the
+event of insufficient balance, this entrypoint MUST fail with the
+error \lstinline/NotEnoughBalance/, indicating insufficient funds in
+the sender's account to execute the transfer. (2) If the sender's
+account has no permission to withdraw the \lstinline/value/ amount of
+funds, the call will fail with the \lstinline/NotEnoughAllowance/
+error, which also contains the same pair message as the first failure
+scenario. To verify these requirements, we utilize the failwith
+condition feature of the tool and examine the returned results, as
+outlined in Listing~\ref{lst:transfer-udstz-contract}.
+\begin{lstlisting}[float,captionpos=b,caption={Fail conditions for the \lstinline/transfer/ entrypoint},label={lst:transfer-udstz-contract},numbers=left]
+1. paused: 'TokenOperationsArePaused'
+2. not paused &&
+   get_big_map (from, ledger) = None : 'NotEnoughBalance'
+3. not paused &&
+   get_big_map (from, ledger) = Some sbvar &&
+   sbvar = Pair sbvar1 sbvar2 &&
+   sbvar1 < value : 'NotEnoughBalance'
+4. not paused &&
+   get_big_map (from, ledger) = Some sbvar &&
+   sbvar = Pair sbvar1 sbvar2 &&
+   get_map (Sender, sbvar2) = Some sbvar3 &&
+   sbvar3 < value: 'NotEnoughAllowance'
+\end{lstlisting}
+The fundamental property that this entrypoint should satisfy is the decrement of the allowance of the sender's account by the \lstinline/value/ that has been sent as Listing \ref{lst:specification-transfer}.
+\begin{lstlisting}[float,captionpos=b,caption={Specification of the \lstinline/transfer/ entrypoint},label={lst:specification-transfer},numbers=left]
+mcontract USDtz = spec 
+   storage :=  Pair (ledger: big_map address 
+      (pair nat (map address nat))) 
+      (Pair (admin: address) 
+            (Pair (paused: bool) (total_supply: nat)))
+   entrypoint %transfer
+      parameter := Pair (from: address)
+         (Pair (to: address) (value: nat))
+      pre-condition := not paused 
+        && get_big_map (from, ledger) = 
+           Some (v: option (pair nat (map address nat))) 
+        && (v = Pair (n1: nat) (m: map address nat))
+        && get_map (Sender, m) = Some (n2: nat) 
+        && (n1 >= value) && (n2 >= value)
+      post-condition := get_big_map (from, post_ledger) = 
+           Some (post_v: option (pair nat (map address nat))) 
+        && post_v = Pair (post_n1: nat) (post_m: map address nat) 
+        && get_map (Sender, post_m) = Some (post_n2: nat) 
+        && (post_n1 = n1 - value) && (post_n2 = n2 - value)
+\end{lstlisting}
+
+\subsubsection{approve}
+\label{sec:approve}
+
+The \texttt{approve} entrypoint takes a spender address and an
+amount. It grants the spender the right to transfer that amount from
+the owner's account.
+
+The crucial property to ensure the correctness of the \texttt{approve}
+entrypoint is that changing the allowance value from a non-zero value
+to another non-zero value is forbidden to prevent a corresponding
+attack vector \cite{attack-vector}. The basic idea of this attack is
+that when a non-zero value update is allowed, the \lstinline/spender/
+can attempt to spend the entire allowance before the new amount is
+updated and then spend again with the new value, resulting in a larger
+amount than actually allowed. Hence, the contract call must fail when
+both the parameter \lstinline/value/ is non-zero and the allowance of
+\lstinline/spender/ is also non-zero. We verify this property by
+generating a fail condition, so that a non-zero value update is
+recorded as a fail condition, as shown in
+Listing~\ref{lst:approve-udstz-contract}. This condition indicates
+that the implementation ensures the non-zero value update prevention. 
+\begin{lstlisting}[float=tp,captionpos=b,caption={Fail conditions for the \lstinline/approve/ entrypoint},label={lst:approve-udstz-contract},numbers=left]
+1. paused: 'TokenOperationsArePaused'
+2. not paused &&
+   get_big_map (Sender, ledger) = Some sbvar &&
+   sbvar = Pair sbvar1 sbvar2 &&
+   get_map (spender, sbvar2) = Some sbvar3 &&
+   not (value = 0) &&
+   not (sbvar3 = 0): 'UnsafeAllowanceChange'
+\end{lstlisting}
+If the update is allowed, then the updated value needs to be recorded
+correctly in the storage. This property can be divided into two
+subproperties, which can be checked separately. Property 1: if the
+parameter \lstinline/value/ is zero, then the 
+corresponding allowance value of the \lstinline/spender/ from the
+owner (which is \SENDER\ in this call) should be zero. This
+subproperty is specified as shown in
+Listing~\ref{lst:specification-approve}. Property 2: if
+\lstinline/value/ is non-zero and the allowance of the \lstinline/spender/ is zero, then the \lstinline/value/ should be recorded in the storage after the call.
+We specify this property using pre- and post-conditions, as illustrated in Listing~\ref{lst:---approve---to-be-provided}.
+
+\begin{lstlisting}[float=tp,captionpos=b,caption={Specification of the \lstinline/approve/ entrypoint},label={lst:specification-approve},numbers=left]
+entrpoint %approve
+   parameter := Pair (spender: address) (value: nat)
+   pre-condition := not paused 
+      && get_big_map (Sender, ledger) = 
+        Some (v: option (pair nat (map address nat))) 
+      && v = Pair (n1: nat) (m: map address nat) 
+      && get_map (spender, m) = Some (n2: nat) 
+      && not (n2 = 0) | (value = 0)
+   post-condition := get_big_map (Sender, post_ledger) = 
+        Some (post_v: option (pair nat (map address nat))) 
+      && post_v = Pair (post_n1: nat) (post_m: map address nat) 
+      && get_map (spender, post_m) = Some (post_n2: nat) 
+      && (post_n2 = 0) ;
+
+   pre-condition := not paused 
+      && get_big_map (Sender, ledger) = 
+        Some (v: option (pair nat (map address nat))) 
+      && v = Pair (n1: nat) (m: map address nat) 
+      && get_map (spender, m) = Some (n2: nat) 
+      && (n2 = 0) | not (value = 0)
+   post-condition := get_big_map (Sender, post_ledger) = 
+        Some (post_v: option (pair nat (map address nat))) 
+      && post_v = Pair (post_n1: nat) (post_m: map address nat) 
+      && get_map (spender, post_m) = Some (post_n2: nat) 
+      && (post_n2 = value) ;
+\end{lstlisting}
+
+\subsubsection{getAllowance, getBalance,  getTotalSupply}
+\label{sec:getall-getb-gett}
+
+These entrypoints are view entrypoints. View entrypoints are functions
+that retrieve information from the storage but do not change the state
+of the smart contract. As indicated in
+Listing~\ref{lst:fa12-interface}, the results of these entrypoints are
+natural numbers, which are sent back to specific addresses, which must
+be tied to smart contracts with entrypoints that have a parameter type
+of \lstinline/nat/. The implementation of a view entrypoint must
+return the \lstinline/TRANSFER_TOKENS/ operation targeting the
+contract passed as an argument with precise information, namely the
+amount of tokens \lstinline/spender/ is allowed to spend from the
+\lstinline/owner/ for the \lstinline/getAllowance/ entrypoint, the
+balance of the owner \lstinline/owner/ for the \lstinline/getBalance/
+entrypoint, and the total supply for the \lstinline/getTotalSupply/
+entrypoint. Additionally, the transaction must transfer to the
+callback contract with an amount equal to \AMOUNT. In other words, all
+the Tezos-tokens passed to a view entrypoint are forwarded to the
+callback contract. Another important property is that there should be
+no modification in the ledger when these entrypoints are called.
+
+As an example, we demonstrate how to verify the \lstinline/getBalance/
+entrypoint,  shown in Listing~\ref{lst:specification-get-balance}. The
+other entrypoints \lstinline/getAllowance/ and
+\lstinline/getTotalSupply/ can be specified similarly.  There are two
+cases to consider: (1) if the \lstinline/owner/ is in the
+\lstinline/ledger/ big map and (2) if it is not. For the former case,
+lines 5-8 specify that \lstinline/owner/ is in the \lstinline/ledger/
+big map, as the \lstinline/Get_big_map/ function returns a value
+\lstinline/Some value/ of the \TOPTION\ type, and this
+\lstinline/value/ is a pair of a natural number \lstinline/k/ and a
+map \lstinline/m/. The postcondition guarantees that the storage
+remains unchanged, as specified in lines 10-13, and the call returns a
+\lstinline/TRANSFER_TOKENS/ operation with the \lstinline/k/ number
+and \lstinline/Amount/ to be passed to address \lstinline/c/. The
+precondition in lines 16-17 specifies the latter case when the
+\lstinline/owner/ does not exist in the big map \lstinline/ledger/; in
+this case, the number \lstinline/0/ should be sent, and again, the
+storage should remain unchanged.
+
+\begin{lstlisting}[float=tp,captionpos=b,caption={Specification of the \lstinline/getBalance/ entrypoint},label={lst:specification-get-balance},numbers=left]
+entrypoint %getBalance
+   parameter := Pair (owner: address) (c: contract nat)
+   pre-condition :=  get_big_map (owner, ledger) = 
+        Some v: option (pair nat (map address nat)) 
+      && v  = Pair (k: nat) (m: (map address nat))
+   post-condition := post_ledger = ledger 
+      && post_admin = admin 
+      && post_paused = paused 
+      && post_total_supply = total_supply 
+      && post_Balance = Balance 
+      && transfer_token (k, Amount, c) ;
+
+   pre-condition :=  get_big_map (owner, ledger) = 
+        None option (pair nat (map address nat)) 
+   post-condition := post_ledger = ledger 
+      && post_admin = admin 
+      && post_paused = paused 
+      && post_total_supply = total_supply 
+      && post_Balance = Balance 
+      && transfer_token (0, Amount, c) ;
+\end{lstlisting}
+\subsubsection{Further entrypoints}
+\label{sec:other-entrypoints}
+
+The contract provides five additional entrypoints: \lstinline/mint/ to
+mint you own tokens, \lstinline/burn/ to burn existing tokens,
+\lstinline/setAdministrator/ and \lstinline/getAdministrator/ to set
+up or retrieve the administrator of the smart contract, and
+\lstinline/setPause/ to pause the contract. To generate fail
+conditions, we detect that \lstinline/transfer/ or \lstinline/approve/
+calls fail if the contract is in a paused state. Users or dapps should
+be aware of this when interacting with the smart contract.
+
+The \lstinline/mint/ and \lstinline/burn/ entrypoints affect the total
+supply, so they should act consistently with the amount mined or
+burned. Obviously, only the administrator is allowed to call these
+entrypoints. The same holds for the \lstinline/setPause/ entrypoint.
+
+The administrator plays a crucial role in this contract. Therefore,
+for the \lstinline/setAdministrator/ entrypoint, it must be guaranteed
+that only the current administrator can call this entrypoint and the
+new administrator must match the address passed through the
+parameter. Another property to ensure is that, except for this
+entrypoint call, any other smart contract call to this contract should
+not change the administrator.
+
+All of the above-mentioned properties are specified and verified in
+our model. The results show that these properties are guaranteed,
+i.e., that the smart contract code is correct.
+
+\subsection{Kolibri Oracle Contract}
+\label{sec:kolibri-oracle-contr}
+The potential of smart contracts is constrained by the inability to
+access external data sources. To address this limitation, oracles
+serve as a crucial link between external sources and the blockchain
+network.  Blockchain oracles play a pivotal role in furnishing
+external data for smart contracts. Certain essential properties must
+be satisfied by an oracle contract, including data approvability. This
+case study aims to illustrate the process of specifying and verifying
+an oracle contract by the static checker, using the Kolibri oracle
+contract as an example.
+
+The Kolibri oracle contract,  residing at  address
+\texttt{KT1Tj6xknbwjyK5gyfESNR6WESBcP3yX1mmj}, ensures the accuracy of
+external data for the Tezos-based stablecoin Kolibri by leveraging
+the Harbinger Price Feed. The contract initiates calls to a Harbinger
+Normalizer contract, checks the returned values, normalizes them to
+suit the Kolibri system, and subsequently relays them to the
+client. The smart contract's parameters and storage details are
+outlined in Listing~\ref{lst:kolibri-oracle-contract}. Key attributes
+stored by the oracle include:
+\atha{Explain what the governor is!\\ How can a parameter have type contract?}
+\begin{itemize}
+\item \lstinline/harbingerContractAddress/: the address of the Harbinger Price Feed contract.
+ \item    \lstinline/state/: a natural number indicating the current state of the contract: (1) \lstinline/IDLE/ and (2) \lstinline/WAITING_FOR_HARBINGER/.
+ \item    \lstinline/clientCallback/: a contract featuring a \TNAT\ entrypoint that stores state when the oracle awaits Harbinger data.
+ \item    \lstinline/governorContractAddress/: the address of the governor contract.
+ \item    \lstinline/maxDataDelaySec/: the maximum acceptable age of data received from Harbinger, measured in seconds.
+\end{itemize}
+The oracle contract offers various entrypoints, including:
+\begin{itemize}
+\item    \lstinline/getXtzUsdPrice/: retrieval, sanity check, and normalization of Harbinger data.
+\item    \lstinline/getXtzUsdPrice_callback/: serves as a callback mechanism to receive data from Harbinger.
+\item    \lstinline/default/: always intentionally fails to prevent the transfer of XTZ into the contract.
+\item    \lstinline/setMaxDataDelaySec/: enables the setting of the maximum acceptable age for data received from Harbinger.
+\item    \lstinline/setGovernorContract/: allows the setting of the Governor's address.
+\end{itemize}
+
+\begin{lstlisting}[float,captionpos=b,caption={Kolibri oracle contract},label={lst:kolibri-oracle-contract},numbers=left]
+parameter
+ (or
+   (or
+     (unit %default)
+     (contract nat %getXtzUsdRate))
+   (or
+     (pair string (pair timestamp nat) %getXtzUsdRate_callback)
+     (or
+       (address %setGovernorContract)
+       (nat %setMaxDataDelaySec)))) ;
+storage
+ (pair
+   (pair (option %clientCallback address) 
+         (address %governorContractAddress))
+   (pair (address %harbingerContractAddress) 
+         (pair (nat %maxDataDelaySec) (int %state)))) ;
+\end{lstlisting}
+
+Another critical access control property is the resettable nature of \lstinline/governorContractAddress/ and \lstinline/maxDataDelaySec/.
+While these parameters are designed to be reset, such actions should exclusively be carried out by the governor.
+Maintaining this restriction is paramount to prevent loss of control over the contract in the event of unauthorized resets.
+In practical terms, the entrypoints \lstinline/setGovernorContract/ and \lstinline/setMaxDataDelaySec/ must only be invocable by the governor.
+Any attempts by unauthorized callers to make these calls should result in failure to ensure the integrity of access control and prevent potential misuse of these critical parameters.
+
+The Kolibri oracle contract maintains a straightforward state machine comprising two states: (1) \lstinline/IDLE/ and (2) \lstinline/WAITING_FOR_HARBINGER/.
+From the \lstinline/IDLE/ state, the oracle can exclusively transition to the \lstinline/WAITING_FOR_HARBINGER/ state.
+The \lstinline/getXtzUsdPrice/ entrypoint is permissible only when the oracle is in the \lstinline/IDLE/ state, and invoking this entrypoint transitions the oracle to the \lstinline/WAITING_FOR_HARBINGER/ state.
+Notably, in the \lstinline/IDLE/ state, the value of \lstinline/clientCallback/ is always set to none.
+Conversely, from the \lstinline/WAITING_FOR_HARBINGER/ state, the oracle can only transition back to the \lstinline/IDLE/ state.
+The \lstinline/getXtzUsdPrice_callback/ entrypoint is allowable solely when the oracle is in the \lstinline/WAITING_FOR_HARBINGER/ state, and invoking this entrypoint results in the oracle transitioning to the \lstinline/IDLE/ state.
+In the \lstinline/WAITING_FOR_HARBINGER/ state, the value of \lstinline/clientCallback/ is always set to some.
+
+Several properties must be verified to ensure the correct functioning of the state machine.
+The initial property states that \lstinline/getXtzUsdPrice/ can only be invoked when in the \lstinline/IDLE/ state, while conversely, \lstinline/getXtzUsdPrice_callback/ can only be invoked when in the \lstinline/WAITING_FOR_HARBINGER/ state.
+The validation of this property involves examining the fail conditions of these two entrypoints.
+
+The subsequent property dictates that if \lstinline/getXtzUsdPrice/ is successfully executed, the state must transition to \lstinline/WAITING_FOR_HARBINGER/, and the parameters passed along with the call need to be stored in the \lstinline/clientCallback/ attribute of the storage.
+This property can be detailed as shown in Listing \ref{lst:kolibri-contract-specification}.
+
+The following property asserts that if \lstinline/getXtzUsdPrice_callback/ is successful, the state should revert to \lstinline/IDLE/, and there must be a transaction transferring the data to the client at the \lstinline/clientCallback/ attribute.
+This property is specified in Listing \ref{lst:kolibri-contract-specification}.
+
+The final property concerns the entrypoint relation between
+\lstinline/getXtzUsdPrice/ and \lstinline/getXtzUsdPrice_callback/ as
+depicted in Figure \ref{fig:kolibri-oracle-emtrypoint-relations}. From
+the \lstinline/getXtzUsdPrice/ entrypoint, the contract can only be
+called with \lstinline/getXtzUsdPrice_callback/ and then
+reverted. Invoking the \lstinline/getXtzUsdPrice/ entrypoint after
+another call or invoking the \lstinline/getXtzUsdPrice_callback/
+entrypoint again is not allowed. This entrypoint relation property is
+specified as an entrypoint relation in
+Listing~\ref{lst:kolibri-oracle-entrypoint-relations-text}.
+
+\begin{figure}[tp]
+    \centering
+    \includegraphics[width=0.8\textwidth]{kolibri}
+    \caption{Kolibri oracle entrypoint relations}
+    \label{fig:kolibri-oracle-emtrypoint-relations}
+\end{figure}
+
+\begin{lstlisting}[float=tp,captionpos=b,caption={Kolibri oracle contract specification},label={lst:kolibri-contract-specification},numbers=left]
+mcontract Auction = spec 
+  storage := (Pair (Pair (client: option address) 
+     (governor: address))
+     (Pair (harbinger: address) 
+           (Pair (maxDelay: nat) (state: int))))
+  entrypoint %getXtzUsdRate
+    code := {...}
+    parameter := (c : contract nat) 
+    pre-condition := (Amount = 0) | (state = 0)
+    post-condition := (state = 1) 
+       && (client = Some Sender) ;
+  entrypoint %getXtzUsdRate_callback
+    code := {...}
+    parameter := Pair (s: string) 
+       (Pair (t: timestamp) (n: nat))
+    pre-condition :=  state = 1 
+       && Sender = harbinger  
+       && s = 'XTZ-USD' 
+       && Now - t <= 30 
+       && client = Some a 
+       && get_contract (nat, a) = Some c    
+    post-condition := state = 0 
+       && post_client = None 
+       && transfer(n, 0, c) ;
+  entrypoint %setGovernorContract
+    code := {...}
+    parameter := (gover : address) 
+    pre-condition :=  (Sender = governor)                  
+    post-condition := (governor = gover) 
+       && (post_maxDelay = maxDelay) 
+       && (post_harbinger = harbinger) ;
+  entrypoint %setMaxDataDelaySec
+    code := {...}
+    parameter := (delay: nat)
+    pre-condition := (Sender = governor)             
+    post-condition := (maxDelay = delay) 
+       && (post_client = client) 
+       && (post_harbinger = harbinger) ;
+  (%getXtzUsdRate -> %getXtzUsdRate_callback) with
+     (Sender = harbinger)
+     && (s = 'XTZ-USD') 
+     && (Now - t <= 1800)  
+  | (%getXtzUsdRate_callback  -> %getXtzUsdRate) with 
+    (Amount = 0) 
+  | not (%getXtzUsdRate -> %getXtzUsdRate) 
+  | not (%getXtzUsdRate_callback -> %getXtzUsdRate_callback)
+\end{lstlisting}
 
@@
   }{
-    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE \wedge \Q] \StateTrans \\ [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), \{\STAIL\}\ \STACKCONCAT\STACK',  \PREDICATE \wedge \Q' \Wedge  ( \StackOne\ \EQ\ \{\HEAD; \STAIL \}) ]
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE \wedge \Q] \StateTrans \\ [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), \{\STAIL\}\ \STACKCONCAT\STACK',  \PREDICATE \wedge \Q' \Wedge  (\StackOne\ \EQ\ \{\HEAD; \STAIL \}) ]
   }
@@
 
-\section {Static Checker}
-\label{sec:static-checker-we}
-We verify the contract through symbolic execution against its specifications in the contract module.
-Symbolic execution involves calculating a symbolic stack at each transition from one Michelson instruction to the next.
-The symbolic interpreter is fully typed and rejects ill-typed Michelson programs, provided the ill-typed part is reachable from the default entry point.
-The initial stack is derived from the input pattern for each the entry point.
-To maintain symbolic values as concrete as possible, some instructions may be deemed unreachable or only reachable under specific conditions.
-This process yields, for each entry point, a set of final symbolic stacks accompanied by a path condition indicating when this final state is reachable.
-A state is discarded from the final state space if the path condition is not satisfied, indicating that the path is unreachable.
-Additionally, for each \FAILWITH\ instruction, we obtain a symbolic value for the reported message and a path condition indicating the reachability of this instruction.
-We employ the SMT solver Z3  to assess the feasibility of a path condition and to check smart contract properies specifying by pre and post conditions.
-
-The architecture of the static checker is illustrated in Figure \ref{}.
-The system comprises three phases.
-The first phase involves user specification, where users provide the Michelson code of the contract and define the properties that the smart contract should satisfy.
-Subsequently, the code, along with the input pattern, is input to the interpreter to achieve symbolic execution.
-The path conditions are then fed into a Z3 converter, which transforms these symbolic terms into Z3 formulas.
-Concurrently, the property specification, specifically pre and post conditions, also undergoes conversion to Z3 formulas in the intermediate phase.
-The results of the symbolic execution and Z3 formulas are then input into the static checker, which verifies whether these properties hold for the smart contract implementation.
-This constitutes the verification phase.
-
-\subsection{User specification}
-In the user specification phase, users compose the specification in our domain-specific language using the syntax outlined in Section \ref{sec:domain-specific-language}.
-Note that Michelson code, whether authored by users, obtained from the Tezos blockchain, or compiled from higher-level languages, can be seamlessly employed within our framework.
-The specification is subsequently parsed into an Abstract Syntax Tree (AST) in OCaml.
-The code and the input pattern are then utilized as inputs for the interpreter during the intermediate phase to facilitate symbolic execution.
-In the next phase, the pre and post predicates are transformed into Z3 formulas by the Z3 converter tool.
-\subsection{Michelson interpreter and Z3 converter}
-The interpreter implements the execution model described in \ref{sec:symbolic-execution-model}.
-When provided with a concrete input, the interpreter produces a concrete value.
-In the presence of symbolic input, the result comprises a set of symbolic states represented as terms in OCaml.
-Due to Michelson being built in OCaml, the conversion of Michelson types or terms to their OCaml counterparts is straightforward.
-Each state contains the output stack, which has only one element consisting of an operation list and storage, along with the path conditions represented as predicates in conjunctive form.
-This output is then fed into the Z3 converter, which handles two different types of terms: assertion terms from the AST representing the pre and post-condition specifications, and terms resulting from the interpreter.
-We utilize the Z3 library in OCaml to construct this converter.
-Some adjustments are necessary to convert these terms into Z3 formulas.
-For example, as there is no natural number type (\TNAT) in Z3, the term is converted as an integer type, accompanied by constraints asserting that it is greater than or equal to zero.
-Several constants, such as \CAMOUNT, \CBALANCE, \CSENDER\ and cryptographic functions, such as \FSHA, \FHASHKEY\ are predefined in the environment that works for any smart contract specifications.
-
-\paragraph{Dealing with loop formalization}
-As mentioned earlier, our execution model formalizes loops symbolically using the \FOLD\ and \FMAP\ functions.
-This approach has the advantage of allowing us to convert these loops into formulas compatible with certain SMT solvers, such as Z3, which support these functions.
-Specifically, Z3 provides \lstinline/seq.map fn s/, a map function on sequence \lstinline/s/, and \lstinline/(seq.foldl fn b s)/, a fold function with an initial value \lstinline/b/ on sequence \lstinline/s/.
-These functions are supported for checking assertions that contain them.
-Therefore, we can directly convert the symbolic results of loops into formulas in Z3.
-\subsection{Static checker}
-The static checker now performs the verification process by employing symbolic execution against the property specification in the DSL.
-It utilizes the results from the previous phases, including symbolic execution, Z3 formulas representing pre and post conditions, and path conditions.
-
-What the tool does is first build the input state from the input pattern, runs the symbolic interpreter on the input stack with the provided code to generate all symbolic execution states.
-It's important to note that all states are reachable from the initial state, as any unreachable states are discarded from the final state spaces using the Z3 solver to check the path condition predicate.
-Using the output pattern and the pre- and post-conditions converted by the Z3 conveter, the tool then performs different checks.
-The static checker offers three distinct features: output check, fail condition, and property check.
-
-\subsubsection{Output check} 
-The first check is the output check, where the checker verifies whether the output pattern matches.
-The final state contains a stack with only one element as \Stack\ \STACKCONCAT\ \EMPTYSTACK.
-There are two different forms of the final state.
-In the case where the code is given as incomplete smart contract code, the element \Stack\ contains just a normal term and its corresponding type as (\Term, \TY).
-However, in the case of a complete smart contract code, it has the form (\PAIR\ \VOPERATIONLIST\ \VSTORAGE, \TPAIR\ (\TOPERATIONLIST) \TYS) \STACKCONCAT\ \EMPTYSTACK, where \VSTORAGE\ is the term represting the storage and \VOPERATIONLIST\ repesents a operation list.
-Given an output pattern $ \tau$, the checker scans all the final states, which does not contain a failwith stack and checks whether the output pattern matches.
-In the former case, it matches $ \tau$  with the term \Term.
-In the latter case, it essentially matches with the corresponding part \VSTORAGE\ in the final states resulting from the symbolic interpreter.
-When the input pattern is a concrete value, the result from the interpreter is also concrete, and then the checker can be used as a test to verify if the output aligns with the expectations specified in the output field.
-
-Lets get back to the example in Listing \ref{lst:add-contract-specification}.
-This is an example of incomplete smart contract code.
-The specification states that the output of the code must be a stack that contains only one element of type \TINT\ as symbolicly representing as a variable \VZ\ of type \TINT.
-In this example, there are two final states, with the first one being a failwith state recording the failwith condition when the first element of the pair is less than the second element.
-The failwith state contains the message 'Unexpected Pair,' describing the reason for the failure.
-The second state is a reachable state that contains, at the top element, an integer value, which is the sum of the two elements of the pair.
-The tool results in \TRUE\ for the output check for this example, as expected by the code.
-However, this test could fail if, for example, the output pattern is incorrectly specified as a variable of type \TSTRING, \TMUTEZ, or even \TNAT, as the types wouldn't match with the actual result.
-If the input pattern is concrete, for instance, a pair of numbers 5 and 3 as Pair 5 3, then the expected output should be the number 8.
-This can be verified if the output pattern is also specified as a concrete value.
-
-The second example in Listing \ref{lst:auction-contract-specification} is the specification for a smart contract code.
-The output pattern represents the updated storage after executing the code.
-There are several final states resulting from the symbolic execution.
-The failwith state is ignored for the output check, and all other reachable states are matched with the output term.
-The result is \TRUE\ for this example.
-
-\subsubsection{Fail condition}
-A Michelson contract can fail due to a programmer-induced condition caused by the instruction \FAILWITH.
-It terminates contract execution with an error message reported back to the caller.
-This error message includes the top value on the stack.
-These failures are important in smart contract programming to guarantee that a smart contract call should not be successful under specific circumstances.
-Smart contract calls are expected to fail due to malicious behavior, such as an unauthorized caller or invalid arguments passed along the call.
-For example, the auction contract should not be closed by someone who is not the owner of the contract, and the bidding should not succeed if the bid is not strictly higher than the current highest bid.
-Several smart contract standards, such as , require the contract to fail with specific messages under some conditions.
-Therefore, it is essential to check the fail conditions of a contract.
-
-The static checker provides a feature to generate all fail conditions implemented in a smart contract code.
-The tool searches for all failwith states, resulting from an execution terminated by the \FAILWITH\ instruction, from the final state space, collects the path conditions and the recorded message.
-The result returned to users includes the fail condition together with the message.
-For example, for the specification in Listing \ref{lst:add-contract-specification}, the fail condition is recorded as \lstinline/(x < y): 'Unexpected Pair'/.
-
-The ability to generate fail conditions is a potent feature of our static checker, particularly in verifying access control properties across various smart contracts.
-Specifically, in numerous smart contract configurations, certain entrypoints are designated for invocation only by authorized entities, often exemplified by the contract owner.
-Consequently, these entrypoints must result in failure if the callers lack the necessary authorization.
-This crucial access control property is verified by examining the fail conditions of a smart contract, ensuring that unauthorized callers trigger the intended failures in the system.
-
-For the auction contract, there are several fail conditions.
-For the entrypoint \lstinline/bid/, the fail condition is as shown in Listing \ref{lst:fail-condition-auction-contract-bid} and for the \lstinline/close/ entrypoint, it is recorded in Listing \ref{lst:fail-condition-auction-contract-close}.
-For the \lstinline/bid/ entrypoint, there are three fail conditions.
-First is if the auction is closed, and then if it is not, the contract checks if the amount is greater than the balance.
-If not, the call fails as well.
-The last fail happens when the auction is open, the amount is greater than the balance, but the highest bidder's address is invalid.
-Note that there are several addresses that are valid as Michelson addresses but are not associated with any real account on the Tezos blockchain, or the parameter's type is not correct, while the transfer can only succeed if it is the given parameter and the address is associated with an account with the correct parameter on the Tezos blockchain.
-Bidding returns the previous highest bid as part of the transaction where the highest bidder is stored as a value of type address.
-However, to receive a token transfer, this address must be cast (by the Michelson implementation of the contract) to an implicit contract of Michelson type (\TCONTRACT\ \TUNIT).
-This cast is unavoidable, as a value of contract type cannot be stored.
-However, the cast may fail, and its failure leads to an error condition that is reported with a \FAILWITH\ instruction in this implementation.
-In our framework, this cast fail case is shown in the fail condition, but in the user preconditions, it assumes that they are successfully casted.
-The \lstinline/close/ entrypoint has similar fail conditions when the auction is closed or the owner's address is uncastable.
-But the other fail condition is when the auction is open, but the sender who calls this entrypoint is not the owner of the contract, which was stored in the contract owner part.
-
-\begin{lstlisting}[float,captionpos=b,caption={Fail condition for Auction contract bid entrypoint },label={lst:fail-condition-auction-contract-bid},numbers=left]
-1. not (auction_open): 'Already closed'
-2. (auction_open = true) &&
-(Amount <= Balance): 'Not higher than the current highest bid'
-3. (auction_open = true) &&
-(Amount <= Balance) &&
-get_contract (Unit, highest_bidder) = None: 'Invalid address' 
-\end{lstlisting}
-
-\begin{lstlisting}[float,captionpos=b,caption={Fail condition for Auction contract close entrypoint},label={lst:fail-condition-auction-contract-close},numbers=left]
-1. Not (auction_open): 'Already closed'
-2. (auction_open = true) &&
-Sender != contract_owner): 'Not owner'
-3.  (auction_open = true) &&
-(Sender = contract_owner) &&
-get_contract (Unit, contract_owner) = None: 'Invalid address'
-\end{lstlisting}
-
-In this implementation of the auction contract, the failures are recorded as expected.
-The contract is designed to fail when the auction is closed, the bid is not greater than the old highest bid, or the caller is not the contract owner when attempting to close the contract as transferring the contract balance to their account as a part of the action.
-
-\subsubsection{Property check}
-The static checker enables users to verify smart contract properties by providing pre and post condition specifications.
-A property is specified with the following clause:  \lstinline/pre-condtion := &&/ $\Phi_{i}$ \lstinline/post-condtion := &&/ $\Psi_{j}$.
-This specification asserts that if all preconditions $\Phi_{i}$ hold before smart contract execution, then all $\Psi_{j}$ must become true after the execution.
-To verify this property, we explore all the paths $\Pi$ with the path condition $\Theta$ such that ($\bigwedge \Phi_{i}$ $\land$ $\Theta$) is satisfiable.
-We then check that for every path $\Pi$, $\neg$ ($\bigwedge \Phi_{i} \rightarrow \bigwedge \Psi_{j}$) is unsatisfiable in the context given by the input for the entry point and its corresponding final state and path condition.
-
-Consider the specification of the Add contract in Listing \ref{lst:add-contract-specification}.
-In this context, the two variables \lstinline/x/ and \lstinline/y/ are integers.
-The results of the symbolic execution are either a failwith state with the path condition as the predicate stating that the variable \lstinline/x/ is less than \lstinline/y/, or a state in which the final stack has only one element, which is a symbolic variable \lstinline/sbvar/ of type integer, with the path condition stating that the variable \lstinline/x/ is greater than or equal to \lstinline/y/ and the symbolic variable \lstinline/sbvar/ is equal to the sum of \lstinline/x/ and \lstinline/y/.
-For this specification, the failwith branch is discarded because the precondition is not satisfy with tha path condition, and then \lstinline/z/ is matched to the symbolic variable \lstinline/sbvar/ in the other branch.
-In this example, the checker then verifies that given the with the context asserting that (\lstinline/x/ >= \lstinline/y/) $\land$ (\lstinline/z/ = \lstinline/x/ + \lstinline/y/), $\neg$ ((\lstinline/x/ >= 5) $\land$ (\lstinline/y/ > 3) $\rightarrow$ (\lstinline/z/ >= 8)) is unsatisfiable.
-
-\subsubsection{Life-cycle check}
-\section {Case Studies}
-\subsection{USDtz}
-In a blockchain ecosystem, tokens represent digital assets that can be transferred between accounts.
-These tokens are securely stored and verified within the blockchain network.
-There are various types of tokens, including native tokens (cryptocurrencies) like Bitcoin, Ether, Tezos, and others.
-Additionally, tokens can be created through smart contracts on an existing blockchain.
-Two common categories are: (1) Fungible Tokens (FT), which are interchangeable and (2) Non-Fungible Tokens (NFTs), which represent unique digital assets, and each unit is distinct.
-Stablecoins, falling under fungible tokens, are designed to maintain a stable value by tracking the value of a fiat currency like USD or EUR.
-
-While you can create tokens that behave in any way that you want them to behave, implementing tokens that adhere to established standards is advisable for interoperability and compatibility across different platforms.
-A Token standard defines a set of rules and an interface that smart contracts must follow to ensure consistency and compatibility with decentralized exchanges, wallets, and other tools within the ecosystem.
-For example, ERC-20 is a stoken tandard used in Ethereum.
-
-Tezos blockchain has its own set of standards known as Financial Applications (FA).
-Two notable standards are: (1) FA 1.2, designed for fungible tokens, and (2) FA 2, a more versatile standard accommodating both fungible and non-fungible tokens (NFTs).
-The standard outlines a smart contract that functions as a ledger, associating identities with balances.
-This ledger is designed to facilitate token transfer operations and enable approvals for spending tokens from other accounts.
-Any contract aiming to implement the standard must incorporate the functions specified in Listing \ref{lst:fa12-interface} such as transfer (transacting between users), approve (allowing one user to send tokens from another user's address), allowance (browsing the amount of tokens available for an account to sending from another address), user balance (checking the balance of a user), and current supply (checking the total supply of tokens across all addresses), where \lstinline/view a r = pair a (contract r)/ implies an view entrypoint.
-A view is an entrypoint which represents a computation that takes an argument of type \lstinline/a/ and a callback that result in a value of type \lstinline/r/.
-The callback in this case will be another contract address.
-Further elaboration on the details of FA 1.2 can be found in \ref{}, and we will delve into these functions in subsequent sections.
-
-\begin{lstlisting}[float,captionpos=b,caption={FA 1.2 interface},label={lst:fa12-interface},numbers=left]
-(address :from, (address :to, nat :value)) %transfer
-(address :spender, nat :value) %approve
-(view (address :owner, address :spender) nat) %getAllowance
-(view (address :owner) nat) %getBalance
-(view unit nat) %getTotalSupply
-\end{lstlisting}
-
-In this section, we verify USDtz \ref{}, an implementation of the FA 1.2 standard.
-Our goal is to ensure that the implementation aligns with the standard, verifying its correctness.
-USDtz is a stablecoin and one of the first and longest-running coins on the Tezos blockchain, launched in September 2020.
-The smart contract is located at the address KT1LN4LPSqTMS7Sd2CJw4bbDGRkMv2t68Fy9, and the code can be found on the Tezos blockchain \ref{}.
-USDtz adheres to the FA token standard, and the initial deployment of the USDtz smart contract follows the FA 1.2 standard.
-The implementation consists of approximately 1000 instructions.
-It contains all of five entrypoints required in the FA 1.2 interface and four others.
-We will verify this smart contract for each of its entrypoints.
-Let's first examine how the approvable ledger is implemented in the USDtz smart contract.
-The ledger is a substantial map that links user addresses to a pair consisting of their balance and a map associating addresses with the amount of tokens allowed to be transferred from the user's account.
-The storage structure of the USDtz smart contract is illustrated in Listing \ref{lst:storage-udstz-contract}.
-
-\begin{lstlisting}[float,captionpos=b,caption={Storage of the USDtz smart contract},label={lst:storage-udstz-contract},numbers=left]
-  ( pair
-    ( big_map %ledger
-      ( address :user )
-      ( pair ( nat :balance ) ( map :approvals
-        ( address :spender )
-        ( nat :value ) ) ) )
-    ( pair ( address %admin ) 
-           ( pair ( bool %paused ) ( nat %totalSupply ) ) ) ) 
-\end{lstlisting}
-
-\subsubsection{transfer}
-As illustrated in Listing \ref{lst:fa12-interface}, the \lstinline/transfer/ entrypoint credits the account associated with the address provided in the \lstinline/to/ parameter, while debiting the account corresponding to the \lstinline/from/ parameter with the specified \lstinline/value/ amount.
-The FA 1.2 standard mandates that this call must fail under the following two conditions: (1) In the event of insufficient balance, this entrypoint MUST fail with the error \lstinline/NotEnoughBalance/, indicating insufficient funds in the sender's account to execute the transfer.
-(2) If the sender's account has no permission to withdraw the \lstinline/value/ amount of funds, the call will fail with the \lstinline/NotEnoughAllowance/ error, which also contains the same pair message as the first failure scenario.
-To verify these requirements, we utilize the failwith condition feature of the tool and examine the returned results, as outlined in Listing \ref{lst:transfer-udstz-contract}.
-\begin{lstlisting}[float,captionpos=b,caption={Fail conditions for the \lstinline/transfer/ entrypoint},label={lst:transfer-udstz-contract},numbers=left]
-1. paused: 'TokenOperationsArePaused'
-2. not paused &&
-   get_big_map (from, ledger) = None : 'NotEnoughBalance'
-3. not paused &&
-   get_big_map (from, ledger) = Some sbvar &&
-   sbvar = Pair sbvar1 sbvar2 &&
-   sbvar1 < value : 'NotEnoughBalance'
-4. not paused &&
-   get_big_map (from, ledger) = Some sbvar &&
-   sbvar = Pair sbvar1 sbvar2 &&
-   get_map (Sender, sbvar2) = Some sbvar3 &&
-   sbvar3 < value: 'NotEnoughAllowance'
-\end{lstlisting}
-The fundamental property that this entrypoint should satisfy is the decrement of the allowance of the sender's account by the \lstinline/value/ that has been sent as Listing \ref{lst:specification-transfer}.
-\begin{lstlisting}[float,captionpos=b,caption={Specification for the \lstinline/transfer/ entrypoint},label={lst:specification-transfer},numbers=left]
-mcontract UDStz = spec 
-   storage :=  Pair (ledger: big_map address 
-      (pair nat (map address nat))) 
-      (Pair (admin: address) 
-              (Pair (paused: bool) (total_supply: nat)))
-   entrpoint %transfer
-      parameter := Pair (from: address)
-         (Pair (to: address) (value: nat))
-      pre-condition := not paused 
-        && get_big_map (from, ledger) = 
-        && Some (v: option (pair nat (map address nat))) 
-        && (v = Pair (n1: nat) (m: map address nat))
-        && get_map (Sender, m) = Some (n2: nat) 
-        && (n1 >= value) && (n2 >= value)
-      post-condition := get_big_map (from, post_ledger) = 
-        && Some (post_v: option (pair nat (map address nat))) 
-        && post_v = Pair (post_n1: nat) (post_m: map address nat) 
-        && get_map (Sender, post_m) = Some (post_n2: nat) 
-        && (post_n1 = n1 - value) | (post_n2 = n2 - value)
-\end{lstlisting}
-
-\subsubsection{approve}
-The crucial property to ensure the correctness of the approve entrypoint is that changing the allowance value from a non-zero value to another non-zero value is forbidden to prevent a corresponding attack vector \ref{}.
-The basic idea of this attack is that when a non-zero value update is allowed, the \lstinline/spender/ can attempt to spend the entire allowance before the new amount is updated and then spend again with the new value, resulting in a larger amount than actually allowed.
-This means the contract call must fail when both the parameter \lstinline/value/ is non-zero and the allowance of \lstinline/spender/ is also non-zero.
-We verify this property by generating the fail condition, and the result is that the non-zero value update is recorded as a fail condition, as shown in Listing \ref{lst:approve-udstz-contract}.
-This indicates that the implementation ensure the non-zero value update prevention.
-\begin{lstlisting}[float,captionpos=b,caption={Fail conditions for the \lstinline/approve/ entrypoint},label={lst:approve-udstz-contract},numbers=left]
-1. paused: 'TokenOperationsArePaused'
-2. not paused &&
-   get_big_map (Sender, ledger) = Some sbvar &&
-   sbvar = Pair sbvar1 sbvar2 &&
-   get_map (spender, sbvar2) = Some sbvar3 &&
-   not (value = 0) &&
-   not (sbvar3 = 0): 'UnsafeAllowanceChange'
-\end{lstlisting}
-The other property is that in case the update is allowed, then the updated value needs to be recorded correctly in the storage.
-This property can be divided into two subproperties, which can be checked separately.
-The first property is that when the parameter \lstinline/value/ is zero, then the corresponding allowance value of the \lstinline/spender/ from the owner (which is \SENDER\ in this call) should be zero.
-This subproperty is specified as shown in Listing \ref{lst:specification-approve}.
-The second property is that when \lstinline/value/ is non-zero, requiring the allowance of the \lstinline/spender/ to be zero, then the \lstinline/value/ should be recorded in the storage after the call.
-To check this property, we specify the property as the pre and post conditions, as illustrated in Listing \ref{}.
-
-\begin{lstlisting}[float,captionpos=b,caption={Specification for the \lstinline/approve/ entrypoint},label={lst:specification-approve},numbers=left]
-entrpoint %approve
-   parameter := Pair (spender: address) (value: nat)
-   pre-condition := not paused 
-      && get_big_map (Sender, ledger) = 
-        Some (v: option (pair nat (map address nat))) 
-      && v = Pair (n1: nat) (m: map address nat) 
-      && get_map (spender, m) = Some (n2: nat) 
-      && not (n2 = 0) | (value = 0)
-   post-condition := get_big_map (Sender, post_ledger) = 
-        Some (post_v: option (pair nat (map address nat))) 
-      && post_v = Pair (post_n1: nat) (post_m: map address nat) 
-      && get_map (spender, post_m) = Some (post_n2: nat) 
-      && (post_n2 = 0) ;
-
-   pre-condition := not paused 
-      && get_big_map (Sender, ledger) = 
-        Some (v: option (pair nat (map address nat))) 
-      && v = Pair (n1: nat) (m: map address nat) 
-      && get_map (spender, m) = Some (n2: nat) 
-      && (n2 = 0) | not (value = 0)
-   post-condition := get_big_map (Sender, post_ledger) = 
-        Some (post_v: option (pair nat (map address nat))) 
-      && post_v = Pair (post_n1: nat) (post_m: map address nat) 
-      && get_map (spender, post_m) = Some (post_n2: nat) 
-      && (post_n2 = value) ;
-\end{lstlisting}
-
-\subsubsection{getAllowance, getBalance and  getTotalSupply}
-These entrypoints are view entrypoints.
-View entrypoints are functions that retrieve information from the storage but don't make any changes to the smart contract state.
-As Listing \ref{lst:fa12-interface}, the results of these entrypoints are natural numbers, which are sent back to specific addresses, which are smart contracts with entrypoints that have a parameter type of \lstinline/nat/.
-The implementation of a view entrypoint must return the \lstinline/TRANSFER_TOKENS/ operation targeting the contract passed as an argument with precise information, namely the amount of tokens \lstinline/spender/ is allowed to spend from the \lstinline/owner/ for the \lstinline/getAllowance/ entrypoint, the balance of the owner \lstinline/owner/ for the \lstinline/getBalance/ entrypoint, and the total supply for the \lstinline/getTotalSupply/ entrypoint.
-Additionally, the transaction must transfer to the callback contract with an amount equal to \AMOUNT.
-In other words, all the tez passed to a view entrypoint are forwarded to the callback contract.
-Another important property is that there should be no modification in the ledger when these entrypoints are called.
-
-Let us now demonstrate how to verify the \lstinline/getBalance/ entrypoint, as shown in Listing \ref{lst:specification-get-balance} while two other entrypoints \lstinline/getAllowance/ and \lstinline/getTotalSupply/ entrypoints could be similarly specified.
-There are two cases to consider: (1) when the \lstinline/owner/ is in the \lstinline/ledger/ big map and (2) when it is not.
-For the former case, lines 5-8 specify that \lstinline/owner/ is in the \lstinline/ledger/ big map, as the \lstinline/Get_big_map/ function returns a value \lstinline/Some value/ of the \TOPTION\ type, and this \lstinline/value/ is a pair of a natural number \lstinline/k/ and a map \lstinline/m/.
-The post condition guarantees that the storage remains unchanged, as specified in lines 10-13, and the call returns a \lstinline/TRANSFER_TOKENS/ operation with the \lstinline/k/ number and \lstinline/Amount/ to the passed address \lstinline/c/.
-The precondition in lines 16-17 specifies the latter case when the \lstinline/owner/ does not exist in the big map \lstinline/ledger/; in this case, the number \lstinline/0/ should be sent, and again, the storage should remain unchanged.
-
-\begin{lstlisting}[float,captionpos=b,caption={Specification for the \lstinline/getBalance/ entrypoint},label={lst:specification-get-balance},numbers=left]
-entrypoint %getBalance
-   parameter := Pair (owner: address) (c: contract nat)
-   pre-condition :=  get_big_map (owner, ledger) = 
-        Some v: option (pair nat (map address nat)) 
-      && v  = Pair (k: nat) (m: (map address nat))
-   post-condition := post_ledger = ledger 
-      && post_admin = admin 
-      && post_paused = paused 
-      && post_total_supply = total_supply 
-      && post_Balance = Balance 
-      && transfer_token (k, Amount, c) ;
-
-   pre-condition :=  get_big_map (owner, ledger) = 
-        None option (pair nat (map address nat)) 
-   post-condition := post_ledger = ledger 
-      && post_admin = admin 
-      && post_paused = paused 
-      && post_total_supply = total_supply 
-      && post_Balance = Balance 
-      && transfer_token (0, Amount, c) ;
-\end{lstlisting}
-\subsubsection{Other entrypoints}
-The contract provides five additional entrypoints: \lstinline/mint/ to mint you own, \lstinline/burn/ to burn existing tokens, \lstinline/setAdministrator/ and \lstinline/getAdministrator/ to set up or retrieve the administrator of the smart contract, and \lstinline/setPause/ to pause the contract.
-To generate fail conditions, we detect that \lstinline/transfer/ or \lstinline/approve/ calls fail if the contract is in a paused state.
-Users or dapps should be aware of this when interacting with the smart contract.
-
-The \lstinline/mint/ and \lstinline/burn/ entrypoints affect the total supply, so they should be recorded consistently with the amount mined or burned.
-an important property is that only the admin is allowed to call these entrypoints.
-The same for the \lstinline/setPause/ entrypoint is that only the admin is allowed to set the pause value.
-
-The administrator plays a crucial role in this contract.
-Therefore, for the \lstinline/setAdministrator/ entrypoint, it needs to guarantee that only the current administrator can call this entrypoint, and the new administrator must match the address passed through the parameter.
-Another property to ensure is that, except for this entrypoint call, any other smart contract call to this contract should not change the administrator.
-
-All of the above-mentioned properties are specified and verified in our model, and the results show that these properties are guaranteed.
-This confidence assures us of the correctness of the smart contract code.
-\subsection{Kolibri Oracle Contract}
-The potential of smart contracts is constrained by the inability to access external data sources.
-To address this limitation, oracles serve as a crucial link between external sources and the blockchain network.
-Blockchain oracles plays a pivotal role in furnishing external data for smart contracts.
-Certain essential properties must be satisfied by an oracle contract, including data approvability.
-This case study aims to illustrate the process of specifying and verifying an oracle contract by the static checker, using the Kolibri oracle contract as an exemple.
-
-The Kolibri oracle contract,  residing at the address KT1Tj6xknbwjyK5gyfESNR6WESBcP3yX1mmj, ensures the accuracy of external data for the Tezos-based stablecoin, Kolibri, by leveraging the Harbinger Price Feed.
-The contract initiates calls to a Harbinger Normalizer contract, check  on the returned values, normalizes them to suit the Kolibri system, and subsequently relays them to the client.
-The smart contract's parameters and storage details are outlined in Listing \ref{lst:kolibri-oracle-contract}.
-Key attributes stored by the Oracle include:
-\begin{itemize}
-\item \lstinline/harbingerContractAddress/: the address of the Harbinger Price Feed contract.
- \item    \lstinline/state/: a natural number indicating the current state of the contract.
-The oracle contract operates as a simple state machine with two states: (1) \lstinline/IDLE/ and (2) \lstinline/WAITING_FOR_HARBINGER/.
- \item    \lstinline/clientCallback/: a contract featuring a \TNAT\ entrypoint that stores state when the oracle awaits Harbinger data.
- \item    \lstinline/governorContractAddress/: the address of the governor contract.
- \item    \lstinline/maxDataDelaySec/: the maximum acceptable age of data received from Harbinger, measured in seconds.
-\end{itemize}
-The oracle offers various entrypoints to interact with the smart contract, including:
-\begin{itemize}
-\item    \lstinline/getXtzUsdPrice/: facilitates the retrieval, sanity check, and normalization of Harbinger data.
-\item    \lstinline/getXtzUsdPrice_callback/: serves as a callback mechanism to receive data from Harbinger.
-\item    \lstinline/default/: always intentionally fails to prevent the transfer of XTZ into the contract.
-\item    \lstinline/setMaxDataDelaySec/: enables the setting of the maximum acceptable age for data received from Harbinger.
-\item    \lstinline/setGovernorContract/: allows the setting of the Governor's address.
-\end{itemize}
-
-\begin{lstlisting}[float,captionpos=b,caption={Kolibri oracle contract},label={lst:kolibri-oracle-contract},numbers=left]
-parameter
- (or
-   (or
-     (unit %default )
-     (contract nat %getXtzUsdRate ))
-   (or
-     (pair string (pair timestamp nat) %getXtzUsdRate_callback)
-     (or
-       (address %setGovernorContract)
-       (nat %setMaxDataDelaySec)))) ;
-storage
- (pair
-   (pair (option %clientCallback address) 
-         (address %governorContractAddress))
-   (pair (address %harbingerContractAddress) 
-         (pair (nat %maxDataDelaySec) (int %state)))) ;
-\end{lstlisting}
-
-Another critical access control property pertains to the resettable nature of \lstinline/governorContractAddress/ and \lstinline/maxDataDelaySec/.
-While these parameters are designed to be reset, such actions should exclusively be carried out by the governor.
-Maintaining this restriction is paramount to prevent loss of control over the contract in the event of unauthorized resets.
-In practical terms, the entrypoints \lstinline/setGovernorContract/ and \lstinline/setMaxDataDelaySec/ must only be invocable by the governor.
-Any attempts by unauthorized callers to make these calls should result in failure to ensure the integrity of access control and prevent potential misuse of these critical parameters.
-
-The Kolibri oracle contract maintains a straightforward state machine comprising two states: (1) \lstinline/IDLE/ and (2) \lstinline/WAITING_FOR_HARBINGER/.
-From the \lstinline/IDLE/ state, the oracle can exclusively transition to the \lstinline/WAITING_FOR_HARBINGER/ state.
-The \lstinline/getXtzUsdPrice/ entrypoint is permissible only when the oracle is in the \lstinline/IDLE/ state, and invoking this entrypoint transitions the oracle to the \lstinline/WAITING_FOR_HARBINGER/ state.
-Notably, in the \lstinline/IDLE/ state, the value of \lstinline/clientCallback/ is always set to none.
-Conversely, from the \lstinline/WAITING_FOR_HARBINGER/ state, the oracle can only transition back to the \lstinline/IDLE/ state.
-The \lstinline/getXtzUsdPrice_callback/ entrypoint is allowable solely when the oracle is in the \lstinline/WAITING_FOR_HARBINGER/ state, and invoking this entrypoint results in the oracle transitioning to the \lstinline/IDLE/ state.
-In the \lstinline/WAITING_FOR_HARBINGER/ state, the value of \lstinline/clientCallback/ is always set to some.
-
-Several properties must be verified to ensure the correct functioning of the state machine.
-The initial property states that \lstinline/getXtzUsdPrice/ can only be invoked when in the \lstinline/IDLE/ state, while conversely, \lstinline/getXtzUsdPrice_callback/ can only be invoked when in the \lstinline/WAITING_FOR_HARBINGER/ state.
-The validation of this property involves examining the fail conditions of these two entrypoints.
-
-The subsequent property dictates that if \lstinline/getXtzUsdPrice/ is successfully executed, the state must transition to \lstinline/WAITING_FOR_HARBINGER/, and the parameters passed along with the call need to be stored in the \lstinline/clientCallback/ attribute of the storage.
-This property can be detailed as shown in Listing \ref{lst:kolibri-contract-specification}.
-
-The following property asserts that if \lstinline/getXtzUsdPrice_callback/ is successful, the state should revert to \lstinline/IDLE/, and there must be a transaction transferring the data to the client at the \lstinline/clientCallback/ attribute.
-This property is specified in Listing \ref{lst:kolibri-contract-specification}.
-
-The final property concerns the entrypoint relation between \lstinline/getXtzUsdPrice/ and \lstinline/getXtzUsdPrice_callback/ as depicted in Figure \ref{fig:kolibri-oracle-emtrypoint-relations}.
-From the \lstinline/getXtzUsdPrice/ entrypoint, the contract can only be called with \lstinline/getXtzUsdPrice_callback/ and then reverted.
-Invoking the \lstinline/getXtzUsdPrice/ entrypoint after another call or invoking the \lstinline/getXtzUsdPrice_callback/ entrypoint again is not allowed.
-This entrypoint relation property is specified as an entrypoint relation in Listing \ref{}.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.8\textwidth]{kolibri}
-    \caption{Kolibri oracle emtrypoint relations}
-    \label{fig:kolibri-oracle-emtrypoint-relations}
-\end{figure}
-
-\begin{lstlisting}[float,captionpos=b,caption={Kolibri oracle contract specification},label={lst:kolibri-contract-specification},numbers=left]
-mcontract Auction = spec 
-  storage := (Pair (Pair (client: option address) 
-     (governor: address))
-     (Pair (harbinger: address) 
-           (Pair (maxDelay: nat) (state: int))))
-  entrypoint %getXtzUsdRate
-    code := {...}
-    parameter := (c : contract nat) 
-    pre-condition := (Amount = 0) | (state = 0)
-    post-condition := (state = 1) 
-       && (client = Some Sender) ;
-  entrypoint %getXtzUsdRate_callback
-    code := {...}
-    parameter := Pair (s: string) 
-       (Pair (t: timestamp) (n: nat))
-    pre-condition :=  state = 1 
-       && Sender = harbinger  
-       && s = 'XTZ-USD' 
-       && Now - t <= 30 
-       && client = Some a 
-       && get_contract (nat, a) = Some c    
-    post-condition := state = 0 
-       && post_client = None 
-       && transfer(n, 0, c) ;
-  entrypoint %setGovernorContract
-    code := {...}
-    parameter := (gover : address) 
-    pre-condition :=  (Sender = governor)                  
-    post-condition := (governor = gover) 
-       && (post_maxDelay = maxDelay) 
-       && (post_harbinger = harbinger) ;
-  entrypoint %setMaxDataDelaySec
-    code := {...}
-    parameter := (delay: nat)
-    pre-condition := (Sender = governor)             
-    post-condition := (maxDelay = delay) 
-       && (post_client = client) 
-       && (post_harbinger = harbinger) ;
-  (%getXtzUsdRate -> %getXtzUsdRate_callback) with
-     (Sender = harbinger)
-     && (s = 'XTZ-USD') 
-     && (Now - t <= 1800)  
-  | (%getXtzUsdRate_callback  -> %getXtzUsdRate) with 
-    (Amount = 0) 
-  | not (%getXtzUsdRate -> %getXtzUsdRate) 
-  | not (%getXtzUsdRate_callback -> %getXtzUsdRate_callback)
-\end{lstlisting}
 \section {Conclusion}

### 2024-01-08 papers/static-checker/ecoop2024/ecoop2024.tex
minor
section 2

@@
 \label{sec:background}
+\lstset{language=michelson}
 
@@
 A program starts on a stack with one element which contains a pair of
-the current storage value (taken from the blockchain) and the parameter value, as specified by the
+the current storage value (taken from the blockchain) and the
+parameter value as specified by the
 contract invocation.
-When it finishes, the stack must contain a single element with a pair
+When the program finishes, the stack must contain a single element with a pair
 of the final storage value (to be saved on the blockchain) and a list
@@
 \texttt{mutez} for tokens, \texttt{address} for blockchain
-addresses). The type system in simple in the sense that it does not
+addresses). The type system is simple in the sense that it does not
 support quantification over types.
 
-Listing~\ref {lst:simple-program-add} contains a simple example of a Michelson program.
-\begin{lstlisting}[float=tp,captionpos=b,caption={A simple Michelson program},label={lst:simple-program-add},language=michelson]
+Listing~\ref {lst:simple-program-add} contains a short example of a Michelson program.
+\begin{lstlisting}[float=tp,captionpos=b,caption={A Michelson program},label={lst:simple-program-add}]
 parameter int;
@@
 (*       bool :: pair int int :: [] *)
-  IF {UNPAIR; ADD}{PUSH string 'Unexpected Pair'; FAILWITH}
-      }
-\end{lstlisting}
-\atha{Explain the example program}
-\atha{Explain some important instructions for reference later on:
-  AMOUNT, BALANCE, FAILWITH, \dots}
-\atha{Introduce entrypoints}
+   IF {UNPAIR; ADD} {PUSH string 'Unexpected Pair'; FAILWITH};
+(*                        int :: [] *)
+   NIL operation; PAIR
+}
+\end{lstlisting}
+This program first duplicates its input (\lstinline|DUP|), decomposes
+the pair $P\times S$ into its components (\lstinline|UNPAIR|),
+compares the two value on top of the stack (\lstinline|COMPARE|), and
+transforms the result into a boolean (\lstinline|GE|). The
+\lstinline|IF| instruction pops the boolean and either executes the
+first (for true) or second (for false) list of instructions. By now
+only the initial pair is on the stack. In the true branch,
+\lstinline|UNPAIR| decomposes, and then \lstinline|ADD| adds the
+components. In the false branch, the \lstinline|PUSH| instruction pushes
+a string message on the stack. The \lstinline|FAILWITH| instruction
+abort the contract execution: tokens are consumed, but the storage and
+the balance of the contract remain unchanged.
+
+We emerge from the conditional with just the result of the addition on
+the stack. The \lstinline|NIL| instruction pushes an empty list and
+\lstinline|PAIR| creates the requires pair of type $O^* \times S$.
+
+Each Tezos contract maintains a balance of tokens, which can be
+accessed from Michelson using the \lstinline|BALANCE|
+instruction. Contract invocations (aka token transfers) also come with
+tokens besides their data arguments. The \lstinline|AMOUNT|
+instruction pushes the number of tokens received on the stack. They
+are already included in the current balance of the contract. During the
+execution of a Michelson contract, these values are fixed.
+
+A contract may have several entrypoints. Entrypoints are encoded by
+using a sum type (call ``or type'' in Michelson). Each (nested) alternative in a sum can be
+given a name, which is used as the name for an entrypoint. A call to
+an entrypoint automatically adds the required \lstinline|LEFT| and
+\lstinline|RIGHT| constructors to the parameter.
 
@@
 because they compile to Michelson.
+\lstset{language=Caml}
 

### 2024-01-08 papers/static-checker/ecoop2024/ecoop2024.tex
revised symbolic execution

@@
 addresses). The type system is simple in the sense that it does not
-support quantification over types.
+support quantification over types. There are no user-defined types.
 
@@
 
-\section {A Domain Specific Language For Smart Contract Property Specification}
+\section{A Domain Specific Language For Smart Contract Property Specification}
 \label{sec:domain-specific-language}
@@
 \label{sec:symbolic-execution-model}
+
+We already learned about Michelson, the low-level smart contract
+language for the Tezos blockchain, and its stack-based nature in
+Section~\ref{sec:background}.  Here we consider the changes needed for
+symbolic execution of Michelson programs.
+
 \subsection{System Model}
-Michelson serves as the low-level smart contract language for the Tezos blockchain platform.
-The processing and manipulation of data during the execution of smart contracts are managed using a stack.
-The representation of a stack can be described as follows:
-\begin{itemize}
-\item[]  \ensuremath{[\ ]} represents the empty stack.
-\item[]  \ensuremath{hd :: tl} denotes a stack with the top element as \ensuremath{hd} and the remaining stack as \ensuremath{tl}.
-\end{itemize}
-\begin{figure} []
+\label{sec:system-model}
+\begin{figure}[tp]
 \begin{align*}
@@
 \end{figure}
-Each piece of data in Michelson is assigned a specific type, and the language restricts programmers from introducing custom types.
-The complete list of types can be found in Figure \ref{fig:type}.
-To model the system, we use a stack in which each element is a pair consisting of term and its corresponding type.
-Terms are defined in Figure \ref{fig:term}.
-The stack is denoted as \STACK\ = (\TermOne, \TYF) \STACKCONCAT\ (\TermTwo, \TYS) \STACKCONCAT\ \DOT\ \STACKCONCAT\ \EMPTYSTACK\ where elements are types paired with terms.
-
-A Michelson program is a sequence of instructions executed in a sequential manner.
-Each instruction takes, as input, the stack produced by the preceding instruction and modifies it for the subsequent one.
-Let \INSTRUCTION\ = \InstructionOne; \InstructionTwo; \DOT\  \InstructionN\ represent a sequence of instructions.
-During symbolic execution,  the system state evolves, assuming different values based on the constraints of symbolic values.
-Moreover, branching may occur depending on conditions, and both constraints and branching conditions are recorded as predicates.
-Let \PREDICATE\ is a path predicate that is extended at each conditional and expressed in conjunction form, capturing the branching conditions and constraints encountered during the symbolic execution process.
+
+Our symbolic model of a program state is a stack in which each element
+is a symbolic value, i.e., a pair consisting
+of term and its corresponding type. Terms are defined in
+Figure~\ref{fig:term}. Thus we write a stack as \STACK\ = (\TermOne,
+\TYF) \STACKCONCAT\ (\TermTwo, \TYS) \STACKCONCAT\ \DOT\ \STACKCONCAT\ 
+\EMPTYSTACK\ where \ensuremath{[\ ]} stands for the empty stack and
+\ensuremath{hd :: tl} denotes a stack with the top element as
+\ensuremath{hd} and the remaining stack as \ensuremath{tl}. 
+A selection of types is shown in Figure~\ref{fig:type}.
+
+A Michelson program is a sequence of instructions executed in a
+sequential manner. Each instruction takes, as input, the stack
+produced by the preceding instruction and modifies it for the
+subsequent one. Let \INSTRUCTION\ = \InstructionOne; \InstructionTwo;
+\DOT\  \InstructionN\ represent a sequence of instructions.
+
+During symbolic execution,  the system state evolves considering all
+values admitted by the constraints on symbolic values. Unless the
+input values are sufficiently known, symbolic execution may split the
+state, and both constraints and branching conditions are recorded as
+predicates. Let \PREDICATE\ be a path predicate that is extended at
+each conditional and expressed in conjunctive form, capturing the
+branching conditions and constraints encountered during the symbolic
+execution process. 
 \begin{definition}
-A symbolic execution state is represented by the tuple \STATE\ = [\INSTRUCTION, \STACK, \PREDICATE]. Here, \SYSTEM\ = \{\STATEONE, \STATETWO, \DOT, \STATEN \} range over sets of  states.
+A symbolic execution state is represented by a tuple \STATE\ =
+[\INSTRUCTION, \STACK, \PREDICATE].
+A symbolic system configuration, \SYSTEM\ = \{\STATEONE, \STATETWO,
+\DOT, \STATEN \}, is a set of  states.
 \end{definition}
 
-The smart contract program takes a stack as input, consisting of a single pair where the first element is an input value referred to as parameter denoted as \VPAR and the second element represents the content of the storage space denoted as \VSTORAGE.
-The program produces a stack as output, which is a single pair.
-The first element of this pair is the list of internal operations that the program intends to emit (\VOPERATIONLIST), and the second element is the new contents of the storage space.
-Let's define the initial stack as  \SINIT\   = (\KPAIR\ \VPAR\ \VSTORAGE, \TPAIR\ \TYF\ \TYS) \STACKCONCAT\ \EMPTYSTACK, where \VPAR\ and \VSTORAGE\ denote terms representing the parameter and the storage, and \TYF\ and \TYS\ are their corresponding types.
-Similarly, designate the final stack as \SFINAL\   = (\PAIR\ \VOPERATIONLIST\ \VSTORAGE, \TPAIR\ (\TOPERATIONLIST) \TYS) \STACKCONCAT\ \EMPTYSTACK, where \VOPERATIONLIST\ repesents a operation list.
+The smart contract program takes a stack as input, consisting of a
+single pair where the first element is an input value referred to as
+parameter denoted as \VPAR\ and the second element represents the
+content of the storage space denoted as \VSTORAGE. The program
+produces a stack as output, which is a single pair. The first element
+of this pair is the list of internal operations that the program
+intends to emit (\VOPERATIONLIST), and the second element is the new
+contents of the storage space.  We define the initial stack as
+\SINIT\   = (\KPAIR\ \VPAR\ \VSTORAGE, \TPAIR\ \TYF\ \TYS)
+\STACKCONCAT\ \EMPTYSTACK, where \VPAR\ and \VSTORAGE\ denote terms
+representing the parameter and the storage, and \TYF\ and \TYS\ are
+their corresponding types. Similarly, a final stack has the form
+\SFINAL\   = (\PAIR\ \VOPERATIONLIST\ \VSTORAGE, \TPAIR\
+(\TOPERATIONLIST) \TYS) \STACKCONCAT\ \EMPTYSTACK, where
+\VOPERATIONLIST\ repesents a operation list.
+
+The initial configuration is \SYSTEMINIT\ = \{[\INSTRUCTION, \SINIT, \TRUE] \}. 
 \begin{figure}[]
@@
 \subsection{Rules}
-Each instruction is defined by a rule on the system model. The rule semantic is defined by several kinds of transitions:
+Each instruction is defined by a rule on a system configuration. There
+are several kinds of transitions:
 \begin{enumerate}
-\item \ExprTrans\ single-step evaluation of an expression in a system state,
-\item \StateTrans\ internal transitions of a state, which is non-deterministic  as shown for loop instructions, such as \LOOP\ and \LOOPLEFT,
+% \item \ExprTrans\ single-step evaluation of an expression in a system state,
+\item \StateTrans\ internal transitions of a state, which is
+  non-deterministic  as shown for loop instructions, such as \LOOP\
+  and \LOOPLEFT, 
 \item \SystemTrans\ symbolic system transitions.
@@
 
-During the symbolic execution, numerous states are generated, but some may be unreachable from a symbolic initial state.
-This happens when the predicate \PREDICATE\ is unsatisfied, leading to the exclusion of a system state where the predicate fails.
-
+A system transition picks any state and replaces it by all distinct states that
+are reachable by internal transitions. It exploits the nondeterminism
+of the \StateTrans\ relation.
 \begin{mathpar}
   \inferrule[]
-  { \NEG\ \PREDICATE
+  { \STATE\ \StateTrans \STATEONE, \dots, \STATE\ \StateTrans \STATEN
+  }{
+  \{\STATE\} \cup \SYSTEM \SystemTrans \{ \STATEONE, \dots, \STATEN \}
+  \cup \SYSTEM}  
+\end{mathpar}
+In general, symbolic execution may generate unreachable
+states. A state is unreachable if its predicate \PREDICATE\ is  not
+satisfiable. Hence, we have a rule that drops unreachable states.
+\begin{mathpar}
+\inferrule[]
+  { \UNSAT\ \PREDICATE
   }{
@@
 \end{mathpar}
-Michelson instructions are categorized based on their functions.
-These include such as control structures, stack manipulation, arithmetic operations, boolean operations, cryptographic operations, and operations on data structures.
-In our model, we classified them as one-step, multi-step, blockchain, cryptographic, branch, and loop instructions.
-This categorization reflects how these instructions are handled within our specific model.
+The working of the symbolic interpreter may also be understood as a
+graph with symbolic states as nodes and internal transitions as
+edges. Such a representation makes it easier to perform multi-step
+subtransitions as they are required for some operations.
+
+Michelson instructions are categorized based on their functions. The
+categories include control structures, stack manipulation, arithmetic
+operations, boolean operations, cryptographic operations, and
+operations on data structures. In our model, we classify them as
+one-step, multi-step, blockchain, cryptographic, branch, and loop
+instructions. This categorization reflects how these instructions are
+handled within our specific model.
+
 \subsubsection{One-step Instructions}
-One-step instructions have a localized effect, modifying the system state directly without branching a new state, and they end the execution after a single operation.
-The ABS rule exemplifies such an instruction, operating on the first element of the stack.
-This element must be of type int, and the instruction returns the positive value of its current value, treated as a natural number.
-%ABS
-\begin{mathpar}
-\inferrule[ABS]
-  {
-  }
-  {
-    [(\ABS; \INSTRUCTION), (\StackOne, \TINT) \STACKCONCAT \STACK,
-    \PREDICATE]
-    \StateTrans \\
-    [\INSTRUCTION, (\X, \TNAT) \STACKCONCAT \STACK,
-    \PREDICATE\ \wedge\ (\StackOne\ \GE\ \ZERO\ \Rightarrow\ \X\ =
-    \StackOne) \wedge\ (\StackOne\ \LT\ \ZERO\ \Rightarrow\ \X\ = \MINUS\ \StackOne)]
- }
-\end{mathpar}
-Another example is the \COMPARE\ instruction for natural numbers, which compares the first two elements of the stack, both having a natural number type.
-It returns a result of either -1, 0, or 1 based on the comparison of their values.
+\label{sec:one-step-instr}
+One-step instructions have a localized effect, modifying the system
+state directly without branching a new state, and their execution is
+modeled with a single rule.
+% The ABS rule exemplifies such an
+% instruction, operating on the first element of the stack. This element
+% must be of type int, and the instruction returns the absolute value of
+% its argument as a natural number. To this end, the rule creates a
+% fresh variable, \X, and defines its value by a suitable predicate.
+% %ABS
+% \begin{mathpar}
+% \inferrule[ABS]
+%   { \X\ \FRESH
+%   }
+%   {
+%     [(\ABS; \INSTRUCTION), (\StackOne, \TINT) \STACKCONCAT \STACK,
+%     \PREDICATE]
+%     \StateTrans \\
+%     [\INSTRUCTION, (\X, \TNAT) \STACKCONCAT \STACK,
+%     \PREDICATE\ \wedge\ (\StackOne\ \GE\ \ZERO\ \Rightarrow\ \X\ =
+%     \StackOne) \wedge\ (\StackOne\ \LT\ \ZERO\ \Rightarrow\ \X\ = \MINUS\ \StackOne)]
+%  }
+% \end{mathpar}
+
+For example, the \COMPARE\ instruction for natural numbers compares
+the first two elements of the stack, both having a natural number
+type. It returns a result of either -1, 0, or 1 based on the
+comparison of their values. 
 % COMPARE
@@
 \inferrule[COMPARE]
-  {
+  { \X\ \FRESH
   }
@@
 
-The \DIP\ \N\ instruction delves into the first \N\ elements of a stack, applies the sequence of instructions denoted as \INSTRUCTIONONE\ to the remaining part of the stack, modifies a part of the predicate and subsequently pushes the result back into the main execution.
+The \DIP\ \N\ instruction skips over the first \N\ elements of a
+stack, applies the sequence of instructions denoted as
+\INSTRUCTIONONE\ to the remaining part of the stack, modifies a part
+of the predicate and subsequently pushes the result back into the main
+execution. 
 %DIP n
@@
   {[(\DIP\ \N\ \INSTRUCTIONONE; \INSTRUCTION), \A\ \At\ \B, \PREDICATE \wedge \Q] \StateTrans 
-[(\INSTRUCTION), \A\ \At\ \B_1, \PREDICATE \wedge \Q']}
+[\INSTRUCTION, \A\ \At\ \B_1, \PREDICATE \wedge \Q']}
 \end{mathpar}
 \subsubsection{Blockchain Instructions}
- Blockchain instructions make implicit use of data from an execution environment, derived from the current state of the blockchain (the context), from the transaction that triggered the contract, and from the block containing this transaction.
-We model these data as symbolic values, which satisfis some constrants.
-For example, the \AMOUNT\ instruction adds to the stack the amount of tokens that sent together with the transcation which calls this smart contract.
-Here, the amount is modeled as a symbolic value donated as \CAMOUNT, which has \TMUTEZ\ type, which has a nature number value.
+ Blockchain instructions make implicit use of data from the current
+ state of the blockchain (the context), from the transaction that
+ triggered the contract, and from the block containing this
+ transaction. As these values are constant during the execution of a
+ contract, we model them as fixed variable. For example, the \AMOUNT\
+ instruction pushes the amount of tokens on the stack that the
+ contract received from its caller. This amount is modeled as the
+ fixed variable \CAMOUNT, which has type \TMUTEZ.
 
@@
 
-\subsubsection{Cryptographic Instructions}
-Cryptographic instructions in Michelson utilize built-in functions that manage cryptographic features.
+% \subsubsection{Cryptographic Instructions}
+% Cryptographic instructions in Michelson utilize built-in functions that manage cryptographic features.
 These functions are symbolically modeled in our framework, specifying their inputs and outputs.
@@
 The function SHA-256 is symbolically represented as the function  \FSHA\  that takes an input of type \TBYTE\ and returns another byte value, constrained to a length of 256.
-%HASH-KEY
-\begin{mathpar}
-\inferrule[\SHA]
-  {
-  }
-  {[(\SHA; \INSTRUCTION), (\StackOne, \TBYTE) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\X, \TBYTE) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\X\ \EQ\ \FSHA(\StackOne))]}
-\end{mathpar}
+% %HASH-KEY
+% \begin{mathpar}
+% \inferrule[\SHA]
+%   {
+%   }
+%   {[(\SHA; \INSTRUCTION), (\StackOne, \TBYTE) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
+% [\INSTRUCTION, (\X, \TBYTE) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\X\ \EQ\ \FSHA(\StackOne))]}
+% \end{mathpar}
 \subsubsection{Branch Instructions}
-The Michelson language incorporates conditional branching, enabling the execution of specific code segments based on certain criteria.
-One of the instructions facilitating this is the \IF\ \{\} \{\} construct.
-For example, the \IF\ \{ \INSTRUCTIONONE\ \} \{ \INSTRUCTIONTWO\  \} instruction allows the creation of branches in execution.
-It takes two sequences as arguments.
-Expecting a boolean value at the top of the stack, it consumes this top element.
-If the boolean is True, it executes the first provided sequence; otherwise, it executes the second sequence.
+The simplest conditional in Michelson language is the \IF\ \{
+\INSTRUCTIONONE\ \} \{ \INSTRUCTIONTWO\  \} instruction. It expects
+and consumes a boolean value at the top of the stack. If the boolean
+is True, it executes \INSTRUCTIONONE; otherwise, it executes
+\INSTRUCTIONTWO. 
 %IF
@@
 
-Another branch instruction is the IF-LEFT instruction, which is used for conditional execution based on the left or right branch of a tagged union (sum) type. 
+Another branch instruction is the IF-LEFT instruction, which is used
+for conditional execution based on the left or right branch of a sum
+type.  
 %IF-LEFT-LEFT
@@
   \inferrule[IF-LEFT-left]
-  {  
+  {  \X\ \FRESH
   }{
@@
     \StateTrans \
-    [\INSTRUCTIONONE, (\X, \TYF) \STACKCONCAT\STACK,
+    [(\INSTRUCTIONONE; \INSTRUCTION), (\X, \TYF) \STACKCONCAT\STACK,
     \PREDICATE \wedge (\StackOne\ \EQ\ \LEFT\ \X)]
@@
   \inferrule[IF-LEFT-right]
-  {  
+  {    \X\ \FRESH
   }{
@@
     \StateTrans \
-    [\INSTRUCTIONTWO, (\X, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQ\ \RIGHT\ \X))]
+    [(\INSTRUCTIONTWO; \INSTRUCTION), (\X, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQ\ \RIGHT\ \X))]
   }
 \end{mathpar}
-These above rules collectively define the behavior of the \IFLEFT instruction based on the left or right branch of a tagged union type.
-This rule applies when the top element of the stack is a tagged union of type \TOR\ \TYF\ \TYS (either of type \TYF\ or \TYS), and the \IFLEFT instruction is followed by instructions \INSTRUCTIONONE\ and \INSTRUCTIONTWO.
-The first rule apply with the condition that the top element of the stack is of the form Left \X\ (indicating the left branch of the union), it transitions to execute the instructions \INSTRUCTIONONE\ with the stack modified accordingly and the predicate is updated to include the condition that the top element of the stack is equal to Left \X.
-Similerly, the second rule apply with the condition that  the top element is of the form Right \X\ (indicating the right branch of the union), it transitions to execute the instructions \INSTRUCTIONTWO\ with the stack modified accordingly and the predicate is updated to include the condition that the top element of the stack is equal to Right \X.
+These above rules define the behavior of the \IFLEFT instruction. The
+rule applies when the top element of the stack is a tagged union of
+type \TOR\ \TYF\ \TYS (either of type \TYF\ or \TYS), and the \IFLEFT
+instruction is followed by instructions \INSTRUCTIONONE\ and
+\INSTRUCTIONTWO. The first rule adds the condition that the top
+element of the stack is of the form Left \X\ (indicating the left
+branch of the union), it transitions to execute the instructions
+\INSTRUCTIONONE\ with the stack modified accordingly and the predicate
+is updated to include the condition that the top element of the stack
+is equal to Left \X. Similarly, the second rule handles the case Right\
+\X, mutatis mutandis.
 
 \subsubsection{Loop Instructions}
-In Michelson, loops are fundamental constructs that repeatedly execute a set of instructions until a specific condition is met.
-There are various loop instructions, including \ITER, \MAP, \CONCAT, \SIZE, \LOOP, and \LOOPLEFT, enable the manipulation and traversal of different data structures like lists, sets, maps, and the stack itself.
-
-Michelson, similar to other programming languages, classifies loop instructions into two main types:
-\begin{itemize}
-\item \KFOR\ loops: These are sequence-based loops, exemplified by \ITER, \MAP, \CONCAT\ and \SIZE.
-\item \KWHILE\ loops: These are predicates-based loops, illustrated by \LOOP and \LOOPLEFT.
-\end{itemize}
-To illustrate the structures of  loops, we can draw a parallel with OCaml syntax as in Listing \ref{list:while-loop}.
-
-\begin{lstlisting}[caption={While loop.},label=list:while-loop,captionpos=t,float,abovecaptionskip=-\medskipamount]
-while <loop_condition> do
-   <loop_body>
-done
-\end{lstlisting}
-This \KWHILE\  loop structure involves a loop condition that is evaluated at the beginning of each iteration.
+Michelson supports a number of loop instructions, including
+\LOOP\ and \LOOPLEFT, that  check the loop condition by examining the
+top of the stack. These loop instructions may not terminate, just like while-loops. There are further loop instructions, like \ITER\ and
+\MAP, specialized to traverse data structures like lists, sets, and maps. There are also
+some instructions that implicitly require looping like \CONCAT, and
+\SIZE. The latter kinds of loop instructions do always terminate.
+
+% Michelson, similar to other programming languages, classifies loop instructions into two main types:
+% \begin{itemize}
+% \item \KFOR\ loops: These are sequence-based loops, exemplified by \ITER, \MAP, \CONCAT\ and \SIZE.
+% \item \KWHILE\ loops: These are predicates-based loops, illustrated by \LOOP and \LOOPLEFT.
+% \end{itemize}
+% To illustrate the structures of  loops, we can draw a parallel with OCaml syntax as in Listing \ref{list:while-loop}.
+
+% \begin{lstlisting}[caption={While loop.},label=list:while-loop,captionpos=t,float,abovecaptionskip=-\medskipamount]
+% while <loop_condition> do
+%    <loop_body>
+% done
+% \end{lstlisting}
+% This \KWHILE\  loop structure involves a loop condition that is evaluated at the beginning of each iteration.
 If the condition holds true, the loop body is executed, and the process repeats until the condition becomes false.
@@
 
-Additionally, Michelson features a \KFOR\ loop, where the index runs from the initial value to the final value as in Listing \ref{list:for-loop}.
+% Additionally, Michelson features a \KFOR\ loop, where the index runs from the initial value to the final value as in Listing \ref{list:for-loop}.
 The \KFOR\ loop is represented by the ITER instruction: \lstinline/ITER {<loop-body>}/
 
-\begin{lstlisting}[caption={For loop.},label=list:for-loop,captionpos=t,float,abovecaptionskip=-\medskipamount]
-for index = <initial_value> to <final_value> do
-  <loop_body>
-done
-\end{lstlisting}
-
-The fundamental concept underlying the definition of a loop is its loop condition, the predicate that must hold true for the loop to continue execution.
+% \begin{lstlisting}[caption={For loop.},label=list:for-loop,captionpos=t,float,abovecaptionskip=-\medskipamount]
+% for index = <initial_value> to <final_value> do
+%   <loop_body>
+% done
+% \end{lstlisting}
+
+% The fundamental concept underlying the definition of a loop is its loop condition, the predicate that must hold true for the loop to continue execution.
 In the case of \KWHILE\ loops, the  loop condition is explicitly embedded in the loop syntax.
@@
 A \KFOR\  loop can be rewritten as a  \KWHILE\ loop to make the  loop condition explicit as showned in Listing \ref{list:express-for-using-while-loop}.
-\begin{lstlisting}[caption={Expressing a \KFOR\ loop using a \KWHILE\ loop.},label=list:express-for-using-while-loop,captionpos=t,float,abovecaptionskip=-\medskipamount]
-index = 0
-while index < length(sequence) do
-  <loop_body>
-  index += 1
-done
-\end{lstlisting}
-Here, the implicit loop condition asserts that the index of the sequence element is less than the length of the sequence.
-
-It's important  to note that, unlike imperative-style loops, Michelson loop instructions do not explicitly contain their loop conditions. Instead, the  loop condition is established:
-\begin{itemize}
- \item In the expressions preceding the loop for the first time entering the loop.
- \item Inside the loop body for subsequent iterations.
-\end{itemize}
-
-The loop instructions are applied to a stack, and the loop condition is checked with the top element of the stack.
+% \begin{lstlisting}[caption={Expressing a \KFOR\ loop using a \KWHILE\ loop.},label=list:express-for-using-while-loop,captionpos=t,float,abovecaptionskip=-\medskipamount]
+% index = 0
+% while index < length(sequence) do
+%   <loop_body>
+%   index += 1
+% done
+% \end{lstlisting}
+% Here, the implicit loop condition asserts that the index of the sequence element is less than the length of the sequence.
+
+%  do not explicitly contain their loop conditions. Instead, the  loop condition is established:
+% \begin{itemize}
+%  \item In the expressions preceding the loop for the first time entering the loop.
+%  \item Inside the loop body for subsequent iterations.
+% \end{itemize}
+
+% The loop instructions are applied to a stack, and the loop condition is checked with the top element of the stack.
 For a  \KWHILE\ loop the top element of the stack must have a boolean value and for the \KFOR\  loop, it must have a sequence data type, such as list, set or map.
 If we denote the function to retrieve the top element of a stack as "\FPOP," the  \KWHILE\ loop instruction can be expressed as shown in Listing \ref{list:express-for-using-ocaml} and and the \KFOR\  loop is expressed as Listing \ref{list:express-while-using-ocaml}.
-\begin{lstlisting}[caption={Expressing Michelson \KWHILE\ loop using  Ocaml syntax.},label=list:express-for-using-ocaml,captionpos=t,float,abovecaptionskip=-\medskipamount]
-while pop(S) do
-   loop_body
-done
-\end{lstlisting}
-
-\begin{lstlisting}[caption={Expressing Michelson  \KFOR\ loop using Ocaml syntax.},label=list:express-while-using-ocaml,captionpos=t,float,abovecaptionskip=-\medskipamount]
-index = 0
-while index < length(pop(S)) do
-  <loop_body>
-  index += 1
-done
-\end{lstlisting}
-
-Certainly, let's continue exploring how these loop constructs are modeled in our symbolic execution. 
+% \begin{lstlisting}[caption={Expressing Michelson \KWHILE\ loop using  Ocaml syntax.},label=list:express-for-using-ocaml,captionpos=t,float,abovecaptionskip=-\medskipamount]
+% while pop(S) do
+%    loop_body
+% done
+% \end{lstlisting}
+
+% \begin{lstlisting}[caption={Expressing Michelson  \KFOR\ loop using Ocaml syntax.},label=list:express-while-using-ocaml,captionpos=t,float,abovecaptionskip=-\medskipamount]
+% index = 0
+% while index < length(pop(S)) do
+%   <loop_body>
+%   index += 1
+% done
+% \end{lstlisting}
+
 \paragraph {\ITER}
-Lets us consider the \ITER\ instruction, which iterates over the \TYLIST\ data structure. The corresponding typing rule is as follows:
-\begin{mathpar}
-  \inferrule{\JTypeExpr\TEnv{\INSTRUCTION}{\TY : \TYA\ \SRightarrow\ \TYA}
+Lets us consider the \ITER\ instruction, which iterates over a
+list.\footnote{\ITER\ can also iterate over sets and maps, but the
+  details are very similar to the list case and hence omitted.} The
+corresponding typing rule is as follows: 
+\begin{mathpar}
+  \inferrule{\JTypeExpr\TEnv{\INSTRUCTION}{\TY \STACKCONCAT \TYA\ \SRightarrow\ \TYA}
   }{
-      \JTypeExpr\TEnv{\ITER\ \INSTRUCTION}{\TYLIST\ \TY : \TYA\ \SRightarrow\ \TYA}
+      \JTypeExpr\TEnv{\ITER\ \INSTRUCTION}{\TYLIST\ \TY \STACKCONCAT \TYA\ \SRightarrow\ \TYA}
     }
 \end{mathpar}
-This typing rule ensures that if the loop body \INSTRUCTION\ has the type \TY\ : \TYA\ \SRightarrow\ \TYA, then the entire \ITER\ instruction, when applied to a stack with the top element of type \TY\ \TYLIST\ and the rest of the stack of type \TYA, produces a result stack of type \TYA.
-This facilitates symbolic iteration over a list while maintaining compatibility with further symbolic execution.
-
-We delve into the symbolic execution of \ITER\ instruction when the list is a symbolic term.
+This typing rule ensures that if the loop body \INSTRUCTION\ has the type \TY\ \STACKCONCAT \TYA\ \SRightarrow\ \TYA, then the entire \ITER\ instruction, when applied to a stack with the top element of type \TY\ \TYLIST\ and the rest of the stack of type \TYA, produces a result stack of type \TYA.
+
+We consider rules for symbolic execution of the \ITER\ instruction.
 %%ITER
@@
 \end{mathpar}
-This rule handles the case where the list is empty, and thus the \ITER\ instruction does not iterate.
-The resulting state transitions to the next instruction with an updated stack that is actually the same as before entering the \ITER\ intruction and an augmented predicate \PREDICATE\ $\Wedge$ (\StackOne \EQ \EMPTYLIST).
+This rule handles the case where the list is empty, so that the \ITER\
+instruction just skips. The rule transitions to the next instruction
+after popping the empty list from the stack. We register emptiness in
+the predicate \PREDICATE\ $\Wedge$ (\StackOne \EQ \EMPTYLIST). 
 \begin{mathpar}
   \inferrule[ITER-nonempty]
-  {  [\ITER,  (\HEAD, \TY) \STACKCONCAT\STACK, 
-    \Q]
+  { \HEAD, \STAIL\ \FRESH \\
+    [\ITER,  (\HEAD, \TY) \STACKCONCAT\STACK, 
+    \PREDICATE]
     \StateTrans^*
-    [ \EMPTYSTACK,  \STACK', \Q']
+    [ \EMPTYSTACK,  \STACK', \PREDICATE']
   }{
-    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE \wedge \Q] \StateTrans \\ [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), \{\STAIL\}\ \STACKCONCAT\STACK',  \PREDICATE \wedge \Q' \Wedge  (\StackOne\ \EQ\ \{\HEAD; \STAIL \}) ]
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\
+    \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \\
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\STAIL, \TYLIST)\
+    \STACKCONCAT\STACK',  \PREDICATE' \Wedge  (\StackOne\
+    \EQ\ \{\HEAD; \STAIL \}) ] 
   }
 \end{mathpar}
-The next rule handles the case where the list is non-empty.
-It symbolically executes the instructions \INSTRUCTIONONE\ within the \ITER\ block with the head of the list (\HEAD) removed from the stack and a subpart of the predicate Q.
-The resulting state transitions to a new stack (\STACK') and an updated predicate (\PREDICATE\ $\Wedge$ \Q' $\Wedge$ (\StackOne \EQ \{\HEAD;\STAIL\}), where \{\STAIL\} represents the rest of the list.
-In summery, these rules capture the symbolic execution behavior of the \ITER\ instruction, considering both the cases where the list is empty and non-empty.
-
-When the sequence (list, set, map) is empty, the \ITER\ loop halts.
-Otherwise, it continues to execute its loop body, which applies to an element of the list.
-If a list \LIST\ is concrete, the instruction simply loops until the list ends with an empty list construction.
-The question arises: how do we deal with it symbolically when the list is a symbolic value?
-One solution could involve running the loop for a number of times to obtain the symbolic value.
-However, we aim for the result value to express the loop body more efficiently in a mathematical way and be capable of performing property checks.
-
-Let again consider the instruction \ITER\ \{\INSTRUCTION\}.
-Semantically, \INSTRUCTION\ denote the loop body, which is a sequence of instructions.
-In fact, the sequence of instructions, \INSTRUCTION, represents a lambda function lambda (\TY\ : \TYA\ \SRightarrow\ \TYA) applied to a stack of type \TY\ :\TYA, resulting in a stack of type \TYA.
-Assuming that the first element of the stack is a list and  it is a non-empty.
-Then the list is in the form  \{\HEAD; \STAIL \}, and the rest of the stack is \STACKZERO\ = \StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ ...
+The next rule handles the case where the list is non-empty. It
+symbolically executes the instructions \INSTRUCTIONONE\ within the
+\ITER\ block with the head of the list (\HEAD) replacing the list. The resulting state transitions to a
+new stack (\STACK') and an updated predicate (\PREDICATE' $\Wedge$
+(\StackOne \EQ \{\HEAD;\STAIL\})), where \STAIL represents the rest of the list. 
+These rules capture the symbolic execution behavior of the \ITER\
+instruction, considering both the cases where the list is empty and
+non-empty.
+
+If the initial list is concrete, the instruction terminates as it simply loops over the
+elements of the list. But how do we deal with \ITER\ if the list is a
+symbolic value?
+One solution could involve running
+the loop for a number of times to obtain the symbolic value. However,
+we can defer that decision by exploiting features of Z3.
+
+Let us again consider the instruction \ITER\
+\{\INSTRUCTION\}. The sequence of instructions \INSTRUCTION\ denotes
+the loop body. In fact, \INSTRUCTION\ can be considered a function of
+type (\TY\ \STACKCONCAT \TYA\ \SRightarrow\ \TYA) applied to a stack
+of type \TY\ \STACKCONCAT \TYA,
+resulting in a stack of type \TYA. If the first element of
+the stack is a list of the form \LIST\ = $x_1 \STACKCONCAT x_2 \STACKCONCAT
+\dots x_m \STACKCONCAT  [\ ]$, and the rest of the stack is \STACKZERO\ =
+\StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ ... \STACKCONCAT\
+\StackN. Then the \ITER\ \{\INSTRUCTION\} instruction applies a 
+function, sat \F, represented by \INSTRUCTION\ \M\ times to the stack, once
+with each element $x_i$ on top of the stack. The result after 
+the first iteration is \STACKONE\ = \StackOneOne\  \STACKCONCAT\
+\StackTwoOne\ \STACKCONCAT\ ... \STACKCONCAT\ \StackNOne = \F\ $x_1$
+\STACK. Then \STACKTWO = \F\ $x_1$ \STACKONE, and so on.
+% Typing of \ITER\ enforces that
+% the type of the result stack is the same as the previous
+% stack.
+% Call the function \FI\ that takes the head \HEADZERO\
+% of the list and all elements of  the stack \STACKZERO\ as  \StackOne,
+% \StackTwo, ... \StackN, given  as \STACKZEROBAR\ and returns the
+% i-element  \StackIOne\ of the stack \STACKONE. The function
+% representing \INSTRUCTION\  is defined as the vector of these subfunctions
+% \FI.  
+% \begin{mathpar}
+% \StackOneOne\ = \FOne\  \HEADZERO\ \STACKZEROBAR \\
+% \StackTwoOne\ = \FTwo\  \HEADZERO\ \STACKZEROBAR \\
+% ...\\
+% \StackNOne\ = \FN\  \HEADZERO\ \STACKZEROBAR 
+% \end{mathpar}
+% When the next loop is performed, the same function \FI\ is applied to the next element of the list and all element of the the stack \STACKONE\ and we get the \StackITwo.
+In the same way, the the loop is performed for \J\ time, we get the stack \STACKJ\ as follows:
+
+% \begin{mathpar}
+% \StackOneJ\ = \FOne\  \HEADJMINUS\ \STACKJMINUSBAR \\
+% \StackTwoJ\ = \FTwo\  \HEADJMINUS\ \STACKJMINUSBAR \\
+% ...\\
+% \StackNJ\ = \FN\  \HEADJMINUS\ \STACKJMINUSBAR 
+% \end{mathpar}
+
+We conclude, we can represent the value of the stack after running the
+instruction \ITER\  as the result of a fold function that applies the
+function \F\ to the list. This representation is advantageous because
+Z3 can handle functions defined using \FOLD\ directly.
+% \begin{mathpar}
+% \StackOneM\ = \FOLD\ \FOne\ \STACKZEROBAR\  \LIST\  \\
+% \StackTwoM\ = \FOLD\ \FTwo\  \STACKZEROBAR\ \LIST\  \\
+% ...\\
+% \StackNM\ = \FOLD\ \FN\ \STACKZEROBAR\  \LIST
+% \end{mathpar}
+
+% Generally, we can represent the sequence of instructions \INSTRUCTION\ as the function \F\ that takes an element of type \TY\ of a list \LIST\ and a  stack \STACK\ of type \TYA\ and returns a stack of type \TYA.
+
+\begin{mathpar}
+\STACK'\ =  \FOLD\ \F\ \STACK\ \LIST
+\end{mathpar}
+
+For example, consider \ITER\ \{\ADD\} that applies to a stack \STACK\ that has a integer list as the top element and the rest \STACKZERO\ = \StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ ...
 \STACKCONCAT\ \StackN.
-Then the \ITER\ \{\INSTRUCTION\} instruction apply \M\ time of function representing \INSTRUCTION\ to the stack with each element  \HEADI\ of the list, where \M\ is the length of list.
-The result after the fist loop is \STACKONE\ = \StackOneOne\  \STACKCONCAT\ \StackTwoOne\ \STACKCONCAT\ ...
-\STACKCONCAT\ \StackNOne.
-Note that the type of the result stack must be the same as the prevoud stack.
-Let us assume that the element \I\ of the stack  \STACK\ has the type \TYI.
-Let the function  \FI\ that takes the head \HEADZERO\ of the list and all elements of  the stack \STACKZERO\ as  \StackOne, \StackTwo, ...
-\StackN, donated  as \STACKZEROBAR\ and returns the i-element  \StackIOne\ of the stack \STACKONE.
-The function representing \INSTRUCTION\  is defined as a set of these subfunctions \FI.
-\begin{mathpar}
-\StackOneOne\ = \FOne\  \HEADZERO\ \STACKZEROBAR \\
-\StackTwoOne\ = \FTwo\  \HEADZERO\ \STACKZEROBAR \\
-...\\
-\StackNOne\ = \FN\  \HEADZERO\ \STACKZEROBAR 
-\end{mathpar}
-When the next loop is performed, the same function \FI\ is applied to the next element of the list and all element of the the stack \STACKONE\ and we get the \StackITwo.
-In the same way, the the loop is performed for \J\ time, we get the stack \STACKJ\ as follows:
-
-\begin{mathpar}
-\StackOneJ\ = \FOne\  \HEADJMINUS\ \STACKJMINUSBAR \\
-\StackTwoJ\ = \FTwo\  \HEADJMINUS\ \STACKJMINUSBAR \\
-...\\
-\StackNJ\ = \FN\  \HEADJMINUS\ \STACKJMINUSBAR 
-\end{mathpar}
-
-As result, we can reprensed the value of the stack after running the instruction \ITER\  as the result of a fold function that apply the function \FI\ to the list l with the inital value is \StackOne, \StackTwo, ...
-\StackN\ as \STACKZEROBAR.
-\begin{mathpar}
-\StackOneM\ = \FOLD\ \FOne\ \STACKZEROBAR\  \LIST\  \\
-\StackTwoM\ = \FOLD\ \FTwo\  \STACKZEROBAR\ \LIST\  \\
-...\\
-\StackNM\ = \FOLD\ \FN\ \STACKZEROBAR\  \LIST
-\end{mathpar}
-
-Generally, we can represent the sequence of instructions \INSTRUCTION\ as the function \F\ that takes an element of type \TY\ of a list \LIST\ and a  stack \STACK\ of type \TYA\ and returns a stack of type \TYA.
-
-\begin{mathpar}
-\STACK'\ =  \FOLD\ \F\ \STACK\ \LIST
-\end{mathpar}
-
-Let consider an example \ITER\ \{\ADD\} that applies to a stack \STACK\ that has a integer list as the top element and the rest \STACKZERO\ = \StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ ...
-\STACKCONCAT\ \StackN.
-\begin{mathpar}
-\ITER\ \{ \ADD\ \} / \LIST\ \STACKCONCAT\ \STACKZERO
-\end{mathpar}
-Because of the requirement of the \ADD\ instruction, the top element of the stack \STACKZERO, namely \StackOne, need to have the interger type.
-For each loop \ADD\ instruction adds each element of the list to the top element of the stack and then the rest of the stack is unchanged.
-Let build the function \FOne\ with the assumtion that the list \LIST\ is not empty as \{\HEAD; \STAIL \},
+\begin{mathpar}
+\ITER\ \{ \ADD\ \} \Slash \LIST\ \STACKCONCAT\ \STACKZERO
+\end{mathpar}
+The type of the \ADD\ instruction indicates that the top element of
+the stack \STACKZERO\ namely \StackOne, has type integer list. For
+each iteration, the \ADD\ instruction adds another element of the list
+to the top element of the stack and then the rest of the stack is
+unchanged.  Let us build the function \FOne\ with the assumption that the list \LIST\ is not empty as \{\HEAD; \STAIL \}, 
 \begin{mathpar}
@@
 
-The function \FOne\ is the fucntion that take (\N\ + 1) intergers as inputs and result the sum of two first one 
-\begin{mathpar}
-\FOne\ (\X, \XOne, \XTwo, \DOT, \XN) = \X\ + \XOne
-\end{mathpar}
-since \XTwo, \DOT, \XN\ do not paricipaint in the calculation, we can omit them as
+So \F\ is the function that takes an integer and a stack starting with
+an integer as inputs and returns a stack of the same length with the
+integer added to the top of the stack
+\begin{mathpar}
+\FOne\ (\X, \XOne \STACKCONCAT \XTwo \STACKCONCAT \DOT \XN
+\STACKCONCAT $[\ ]$) = \X\ + \XOne
+\end{mathpar}
+But as \XTwo\STACKCONCAT \DOT \STACKCONCAT \XN\ do not participate in
+the calculation, we can simplify the function to 
 \begin{mathpar}
@@
 \end{mathpar}
-The symbolic value of the top element of the stack after the \ITER\ \{\ADD\} loop is.
+The symbolic value of the top element of the stack after the \ITER\ \{\ADD\} loop is
 \begin{mathpar}
@@
 \end{mathpar}
-Because the loop does not change the rest of the stack, for all funtion \FI\ for the element \StackI\ of the stack \STACK\ could consider as an identy function, and then we can omit them in the implementation.
-\begin{mathpar}
-\FI\ (\X, \XOne, \DOT, \XI, \DOT, \XN) = \XI
-\end{mathpar}
-
-The \FOLD\ function also can be used to symbolicly the result of other \KFOR\ loop intructions, such as CONCAT and SIZE.
+As the loop body does not change the rest of the stack, we can omit
+the identity functions on the remaining components in an implementation.
+% \begin{mathpar}
+% \FI\ (\X, \XOne, \DOT, \XI, \DOT, \XN) = \XI
+% \end{mathpar}
+
+The \FOLD\ function also can be used to express the result of other
+loop instructions, such as CONCAT and SIZE, symbolically.
 
 \paragraph {\MAP}
-The \ITER\ instruction and some other can be symbolicly implemented using \FOLD\ function applying on the sequance data structures as list, set and map.
-Let consider the \MAP\ instruction, where we can use a map function to symbolic the result of the instruction.
-Consider the  \MAP\ \{\I\}   instruction for lists, which operates on a stack \STACK, whose the top element has type \TY\ \TYLIST, and the rest has type \TYA.
-The instruction returns a stack of type (\TY\ \TYLIST) : \TYA.
-The corresponding typing rule is as follows:
+
+% The \ITER\ instruction and some other can be symbolicly implemented
+% using \FOLD\ function applying on the sequance data structures as
+% list, set and map. 
+Next, we consider the \MAP\ instruction. While any \MAP\ instruction
+can be transformed to an \ITER\ instruction, it is more efficient to
+use a map function for the symbolic result of the instruction.
+
+Again we consider
+the  \MAP\ \{\I\}   instruction for lists, which operates on a stack
+\STACK, whose the top element has type \TY\ \TYLIST, and the rest has
+type \TYA. The instruction returns a stack of type (\TY\ \TYLIST) \STACKCONCAT
+\TYA. The corresponding typing rule is as follows: 
 \begin{mathpar}
@@
   }{
-      \JTypeExpr\TEnv{\MAP\ \INSTRUCTION}{\ \TY\ \TYLIST\ : \TYA\ \SRightarrow\ \TY'\ \TYLIST\  : \TYA}
+      \JTypeExpr\TEnv{\MAP\ \INSTRUCTION}{\ \TY\ \TYLIST\ \STACKCONCAT \TYA\ \SRightarrow\ \TY'\ \TYLIST\  \STACKCONCAT \TYA}
     }
 \end{mathpar}
-This typing rule ensures that if the loop body (\INSTRUCTION) has the type \TY\ \SRightarrow\ \TY', then the entire \ITER\ instruction produces a result stack of type \TY' \ \TYLIST\ : \TYA. 
+This typing rule ensures that if the loop body (\INSTRUCTION) has the
+type \TY\ \SRightarrow\ $\TY'$, then the entire \ITER\ instruction
+produces a result stack of type $\TY'$ \ \TYLIST\ \STACKCONCAT \TYA.
+
+The execution rules are similar in style to the ones for \ITER.
 %MAP
@@
 \end{mathpar}
-Let consider how can we syboliclly the execution of the \MAP\ instruction.
-The list of instruction \INSTRUCTION\ can be repeseted as a function \F\ that takes a input of type \TY\ and return an output of type \TY'.
-\begin{mathpar}
-\F\ : \TY\ \SRightarrow\ \TY
-\end{mathpar}
-The \MAP\ instruction loops on the list \LIST\ by applying the function \F\ to each element of the list \LIST.
-Symbolilly the result of the \MAP\ \{\INSTRUCTION\} to the list \LIST\ is the result of a map function  that apply the fucntion \F\ that represent of the sequence of instructions \I\ to the list.
+Let consider how we can avoid the symbolic iteration.
+The list of instructions \INSTRUCTIONONE\ can be represented as a function \F\ that takes a input of type \TY\ and returns an output of type $\TY'$.
+\begin{mathpar}
+\F\ : \TY\ \SRightarrow\ \TY'
+\end{mathpar}
+The \MAP\ instruction traverses the list \LIST\ by applying the
+function \F\ to each element. Symbolically the result of the \MAP\
+\{\INSTRUCTION\} to the list \LIST\ is the result of a map function
+that applies the function \F\ that represent of the sequence of
+instructions \I\ to the list.
 
@@
 
-Consider the example as MAP \{ PUSH int 1; ADD \}, which applies to a stack with have a list of intergers \LIST\ as the top elemnt of the stack.
-The function expressed as \{ PUSH int 1; ADD \} basiclly adds the number 1 to each element of the list.
-Let \F\ is the function that is specified as the sequcne of instruction \I.
-\F\ takes an element of type int and returen another elemnt of type int
+Consider the example as MAP \{ PUSH int 1; ADD \}, which applies to a
+stack with a list of integers \LIST\ on top of the stack. The function
+expressed as \{ PUSH int 1; ADD \} adds the number 1 to each element
+of the list.  Let \F\ be the function that is specified by the
+sequence of instructions \I. \F\ takes an element of type int and
+returns another element of type int.
 \begin{mathpar}
@@
 \end{mathpar}
-Then the result of the loop is a stack which has a interger list at the top whose simbolic value is \FMAP\ \F\ \l.
+Then the result of the loop is a stack which has a integer list at the top whose symbolic value is \FMAP\ \F\ \l.
 
 \paragraph {\LOOP}
-Now let consider an example of the while loop, namely the \LOOP\ instruction that is a while loop.
-The \LOOP\ \{ \I\ \} intruction apply to a stack \STACK\ that has the top element is a boolean type.
-If a top element is true then and only then the loop body (\I) is executed.
-After the body of a loop is executed then control again goes back at the top element, and checked if it is true, the same process is executed until the top element becomes false.
-Once the value of the top element becomes false, the control goes out of the loop.
-The loop condition is calucated by the loop body and the result  back to the firt elevemnt of the stack.
-\begin{mathpar}
-  \inferrule{\JTypeExpr\TEnv{\INSTRUCTION}{\TYA  \SRightarrow\ \TBOOL\ : \TYA}
+Finally, we consider a loop instruction that may not terminate. The
+\LOOP\ \{ \I\ \} instruction applies to a stack \STACK\ with a value
+of type boolean on top. If the top element is true, the loop body (\I)
+is executed. After the body of the loop is executed, then the top of
+the stack is checked again. This process repeats until the top element
+becomes false. Once the value of the top element becomes false, the
+\LOOP\ instruction is skipped.
+\begin{mathpar}
+  \inferrule{\JTypeExpr\TEnv{\INSTRUCTION}{\TYA  \SRightarrow\ \TBOOL\ \STACKCONCAT \TYA}
   }{
-      \JTypeExpr\TEnv{\MAP\ \INSTRUCTION}{\TBOOL\ : \TYA\ \SRightarrow\ \TYA}
+      \JTypeExpr\TEnv{\LOOP\ \INSTRUCTION}{\TBOOL\ \STACKCONCAT \TYA\ \SRightarrow\ \TYA}
     }
@@
 \end{mathpar}
- let \STACKZERO\ =  \StackZero\ \STACKCONCAT\ \StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ \DOT \STACKCONCAT\ \StackN, where  has the boolean type.
+%  let \STACKZERO\ =  \StackZero\ \STACKCONCAT\ \StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ \DOT \STACKCONCAT\ \StackN, where  has the boolean type.
 Let \FI\ is the function that takes the top elemement of the stack and the rest of \N\ elements of the stack, which have types \TYF, \TYS, \DOT\ \TYI, \DOT\ \TYN\ noted as \TYABAR\ and return a single type of the element \I.
-\begin{mathpar}
-\FZero\ : \TBOOL\ \SRightarrow\  \TBOOL. \\
-\DOT \\
-\FI\ : \TBOOL\ \TYF, \TYS, \DOT\ \TYI, \DOT\ \TYN\  \SRightarrow\  \TYI. \\
-\DOT
-\end{mathpar}
-
-\begin{mathpar}
-\FZero\  \StackZero\ \StackOne\ \DOT\ \StackI\ \DOT\ \StackN\ =   \StackZeroOne. \\
-\DOT\ \\
-\FI\  \StackZero\ \StackOne\ \DOT\ \StackI\ \DOT\ \StackN\ =   \StackIOne. \\
-\DOT
-\end{mathpar}
+% \begin{mathpar}
+% \FZero\ : \TBOOL\ \SRightarrow\  \TBOOL. \\
+% \DOT \\
+% \FI\ : \TBOOL\ \TYF, \TYS, \DOT\ \TYI, \DOT\ \TYN\  \SRightarrow\  \TYI. \\
+% \DOT
+% \end{mathpar}
+
+% \begin{mathpar}
+% \FZero\  \StackZero\ \StackOne\ \DOT\ \StackI\ \DOT\ \StackN\ =   \StackZeroOne. \\
+% \DOT\ \\
+% \FI\  \StackZero\ \StackOne\ \DOT\ \StackI\ \DOT\ \StackN\ =   \StackIOne. \\
+% \DOT
+% \end{mathpar}
 \subsubsection{FAILWITH}
@@
 
-\section {Conclusion}
+\section{Conclusion}
 \label{sec:concl-sect-append}
@@
 
-Second, a Michelson returns a list of instructions, which may contain
+Second, a Michelson program returns a list of instructions, which may contain
 further contract invocations. Dealing with this kind of contracts

### 2024-01-14 papers/static-checker/ecoop2024/ecoop2024.tex
write the life-cycle check and other revisions

@@
 We report the foundations of the design and implementation of XXX and
-conduct NNN case studies that demonstrate the expressiveness of our tool.
+conduct two case studies that demonstrate the expressiveness of our tool.
 \end{abstract}
@@
 changed any more. Unfortunately, there are plenty of
-cases~\cite{examples-for-broken-smart-contracts} where the blockchain 
+cases~\cite{dao,wallethack} where the blockchain 
 community identified vulnerabilities in smart contracts despite
@@
 \begin{lstlisting}[float=tp,captionpos=b,caption={Auction contract specification (excerpt)},label={lst:auction-fragment}]
-mcontract Auction = spec 
+mcontract auction = spec 
   storage := Pair (auction_open: bool) 
@@
     pre-condition := auction_open 
-       && Amount > Balance
-    post-condition := post_highest_bidder = Sender 
+       && Amount > Balance - Amount
+       && get_contract (unit, highest_bidder) = 
+          Some (c: contract unit)
+    post-condition := auction_open
+       && post_highest_bidder = Sender 
+       && post_contract_owner = contract_owner 
        && post_Balance = Amount 
-       && transfer_token (Unit, Balance, highest_bidder) 
-       && post_contract_owner = contract_owner ;
+       && transfer_token (Unit, Balance - Amount, c) ;
 \end{lstlisting}
@@
 Our symbolic interpreter calculates a postcondition predicate from the specified
-precondition. The SMT solver Z3 \cite{Z3} checks that this predicate
+precondition. The SMT solver Z3 \cite{z3} checks that this predicate
 implies the specified postcondition.
@@
 (*       bool :: pair int int :: [] *)
-   IF {UNPAIR; ADD} {PUSH string 'Unexpected Pair'; FAILWITH};
+   IF {UNPAIR; SUB} {PUSH string 'Unexpected Pair'; FAILWITH};
 (*                        int :: [] *)
@@
 only the initial pair is on the stack. In the true branch,
-\lstinline|UNPAIR| decomposes, and then \lstinline|ADD| adds the
+\lstinline|UNPAIR| decomposes, and then \lstinline|SUB| subtract the two 
 components. In the false branch, the \lstinline|PUSH| instruction pushes
@@
 is sufficient.
+\begin{figure}[tp]
+\begin{align*}
+\textbf{cpt} &::= 
+   \text{unit} 
+   \Mid\ \text{never} 
+   \Mid\ \text{bool} 
+   \Mid\ \text{int}
+   \Mid\ \text{nat}
+   \Mid\ \text{string}
+   \Mid\ \text{chain-id}
+   \Mid\ \text{bytes}
+   \Mid\ \text{mutez} \\
+   &\Mid\ \text{key-hash}
+   \Mid\ \text{key}
+   \Mid\ \text{signature}
+   \Mid\ \text{timestamp}
+   \Mid\ \text{address} \\
+   &\Mid\ \text{option}\ \textbf{cpt}
+   \Mid\ \text{or}\ \textbf{cpt}\ \textbf{cpt}
+   \Mid\ \text{pair}\ \textbf{cpt}\ \textbf{cpt} \\
+\text{T, U} &::= 
+    \text{cpt}
+   \Mid\ \text{option}\ \text{T}
+   \Mid\ \text{list}\ \text{T}
+   \Mid\ \text{set}\ \textbf{cpt} 
+   \Mid\ \text{operation} \\
+   &\Mid\ \text{contract}\ \text{T}
+   \Mid\ \text{ticket}\ \textbf{cpt} 
+   \Mid\ \text{pair}\ \text{T}\ \text{U}
+   \Mid\ \text{or}\ \text{T}\ \text{U}
+   \Mid\ \text{lambda}\ \text{T}\ \text{U} \\
+   &\Mid\ \text{map}\ \textbf{cpt}\ \text{T}
+   \Mid\ \text{big-map}\ \textbf{cpt}\ \text{T}
+   \Mid\ \text{chest} 
+   \Mid\ \text{chest-key}
+\end{align*}
+\caption{Types}
+\label{fig:type}
+\end{figure}
 
@@
    \Mid \text{Voting\_power} \\
-\textbf{e} & :: =  \textbf{i} \Mid  \textbf{s}  \Mid  \textbf{b} \Mid \textbf{c} \Mid (\text{x} : \text{T}) \\
-&\Mid \text{Unit}  \Mid \text{Never}  \Mid \text{True}  \Mid \text{False} \\
-&\Mid \text{Pair } \textbf{e } \textbf{e}  \Mid \text{Left } \textbf{e}  \Mid \text{Right } \textbf{e}  \Mid \text{Some } \textbf{e} \Mid \text{None T}  \\
-& \Mid \textbf{e} \text{ + } \textbf{e}\Mid \textbf{e} \text{ - } \textbf{e}  \Mid \textbf{e} \text{ * } \textbf{e} \Mid \textbf{e} \text{ \/ } \textbf{e} \Mid \textbf{e} \text{ \% } \textbf{e} \Mid \textbf{e} \text{ rem } \textbf{e} \\
+\textbf{t} &::= 
+   \textbf{n}: \text{nat}
+   \Mid\ \textbf{i}: \text{int}
+   \Mid\  \textbf{s}: \text{string} 
+   \Mid\  \textbf{b}: \text{bytes}
+   \Mid\  \textbf{c}  
+   \Mid\  \text{x} 
+   \Mid\ \text{x}: \text{T} \\
+   &\Mid\ \UNIT 
+   \Mid\ \NEVER 
+   \Mid\ \TRUE 
+   \Mid\ \FALSE 
+   \Mid\ \PAIR\ \text{t1 t2} \\
+   &\Mid\ \LEFT\ \text{t}\  \text{T}
+   \Mid\ \RIGHT\ \text{T}\ \text{t}
+   \Mid\ \SOME\ \text{t}
+   \Mid\ \NONE\ \text{T} 
+   \Mid\ \text{\{t ; ... \}}: \text{list T}
+   \Mid\ \text{\{t ; ... \}}: \text{set T} \\
+   &\Mid\ \text{\{ Elt t1 t2 ; ... \}}: \text{map T U}
+   \Mid\ \text{\{ Elt t1 t2 ; ... \}}: \text{big\_map T U} \\
+\textbf{e} & :: = \textbf{t}  \Mid \textbf{e} \text{ + } \textbf{e}\Mid \textbf{e} \text{ - } \textbf{e}  \Mid \textbf{e} \text{ * } \textbf{e} \Mid \textbf{e} \text{ / } \textbf{e} \Mid \textbf{e} \text{ \% } \textbf{e} \Mid \textbf{e} \text{ rem } \textbf{e} \\
 & \Mid \text{transfer\_token} (\textbf{e}, \textbf{e}, \textbf{e}) 
  \Mid \text{get\_map} (\textbf{e}, \textbf{e}) 
- \Mid \text{get\_big\_map} (\textbf{e}, \textbf{e}) \\
+ \Mid \text{get\_big\_map} (\textbf{e}, \textbf{e}) 
+ \Mid \text{check\_mem} (\textbf{e}, \textbf{e})  \\
 & \Mid \text{get\_contract} (\textbf{e}, \textbf{e})  
- \Mid \text{abs} (\textbf{e})  
+ \Mid \text{contain} (\textbf{e}, \textbf{e})  
+ \Mid \text{get\_substring} (\textbf{e}, \textbf{e}, \textbf{e})  
+ \Mid \text{check\_sig} (\textbf{e}, \textbf{e}, \textbf{e})  \\
+& \Mid \text{abs} (\textbf{e})  
+ \Mid \text{is\_nat} (\textbf{e})  
+ \Mid \text{to\_int} (\textbf{e})  
  \Mid \text{len} (\textbf{e})
+ \Mid \text{cons} (\textbf{e}, \textbf{e})
  \Mid \text{size} (\textbf{e})
-\Mid \textbf{e} \text{$\wedge$} \textbf{e}  \\
+\Mid \textbf{e} \text{ $\wedge$ } \textbf{e}  \\
 \textbf{p} & :: = \textbf{e} \text{ = } \textbf{e}
@@
 \end{align*}
-\caption{Syntax of predicates, p}
-\label{fig:syntax-predicates}
+\caption{Syntax of terms, t and predicates, p}
+\label{fig:syntax-terms-predicates}
 \end{figure}
 
-\begin{lstlisting}[float=tp,captionpos=b,caption={Smart contract property specification},label={lst:smart-contract-property-specification},numbers=left]
-mcontract Name = spec
+\begin{lstlisting}[float=tp,captionpos=b,caption={Smart contract property specification for a simple contract},label={lst:smart-contract-property-specification},numbers=left]
+mcontract name = spec
   code := {...}
@@
 Listing~\ref{lst:smart-contract-property-specification} shows the
-syntax of our property specification language. Here, \KMCONTRACT,
-\KWITH, \KCODE, \KINPUT, \KOUTPUT, \KPRECONDI, and \KPOSTCONDI\ are
+syntax of our property specification language for a simple contract. Here, \KMCONTRACT,
+\KSPEC, \KCODE, \KINPUT, \KOUTPUT, \KPRECONDI, and \KPOSTCONDI\ are
 keywords. The \KNAME\ is replaced by the contract name. In the input
-and output fields, the input and output patterns are specified.
-\atha{What patterns are supported? Patterns are not explained!}
+and output fields, the input and output terms are specified. 
+\atha{What terms are supported? terms are not explained!}
 Since
 Michelson operates on a stack, we assume that the stack has only one
-element, as specified in the input pattern. Similarly, the output
+element, as specified in the input term. Similarly, the output
 stack is assumed to be a stack with only one element, which is
@@
 incomplete contracts, too.
-\pt{I disagree (though it would be a useful feature). To this end, there should be patterns to cover stacks
-  with more than one element. As it stands, the input pattern can only
-speak about the top of the stack and the output pattern only about the
+\pt{I disagree (though it would be a useful feature). To this end, there should be terms to cover stacks
+  with more than one element. As it stands, the input term can only
+speak about the top of the stack and the output term only about the
 second component of the top of the stack, which is assumed to be a
@@
 of operations, too, e.g., that tokens are transferred to some address.}
-For a complete smart contract, the output
-should be a pair consisting of an operation list and a storage.
-
-For verification purposes we elide the operation list and represent
-the output solely by the pattern of the value in the storage after the
-execution concludes. In some cases, the output pattern can be omitted
-for a complete contract, given that the input pattern must be a pair
-of parameters and storage. Hence the storage pattern is part of the
-input pattern. In such cases, the prefix \lstinline/post_/ is used
+
+For a complete smart contract, the output should be a pair consisting of an operation list and the storage's state after the completion of the code.
+For verification purposes we elide the operation list and represent the output solely by the term of the value in the storage after the execution concludes.
+In some cases, the output term can be omitted
+for a complete contract, given that the input term must be a pair
+of parameters and storage. Hence the storage term is part of the
+input term. In such cases, the prefix \lstinline/post_/ is used
 before the variables from the input term to indicate the corresponding
@@
 
-The input and output patterns represent Michelson terms, which can be
-either concrete values or symbolic values, including variables. When a
-variable appears for the first time, it needs to be accompanied by its
+The input and output terms represent Michelson terms, which can be
+either concrete values or symbolic values, including variables. When a variable appears for the first time, it needs to be accompanied by its
 corresponding type declaration. Subsequent mentions can omit the type
@@
 formulas in first-order logic that can be handled by an SMT solver (in
-our case, Z3). The specification language is constituted of predicates
-defined using the syntax defined in Figure~\ref{fig:syntax-predicates}. Formulas that are used in assertions or
+our case, Z3).
+The specification language is constituted of predicates.
+The syntax terms and  predicates are defined in Figure~\ref{fig:syntax-terms-predicates}.
+Formulas that are used in assertions or
 added to solvers are terms of sort Boolean. Otherwise, terms of
@@
 
-\begin{lstlisting}[float,captionpos=b,caption={Specification of Add contract},label={lst:add-contract-specification},numbers=left]
-mcontract Add = spec
-  code := {UNPAIR; COMPARE; GE; 
-          IF {ADD}{PUSH string 'Unexpected Pair'; FAILWITH}}
+\begin{lstlisting}[float,captionpos=b,caption={Specification of Sub contract},label={lst:sub-contract-specification},numbers=left]
+mcontract sub = spec
+  code := {DUP; UNPAIR; COMPARE; GE; IF {UNPAIR; SUB} 
+          {PUSH string 'Unexpected Pair'; FAILWITH}}
   input := Pair (x : int) (y : int)
   output := (z : int)
-  pre-condition := (x >= 5) | (y > 3)
-  post-condition := (z >= 8)
+  pre-condition := (x >= y)
+  post-condition := (z = x - y) && (z >= 0)
 \end{lstlisting}
 
-Let us consider the contract \texttt{Add}  in Listing
-\ref{lst:add-contract-specification} as an   example of a property
+Let us consider the contract \texttt{Sub}  in Listing
+\ref{lst:sub-contract-specification} as an example of a property
 specification.  Here, the program takes as input a stack with only one
 element, which is a pair of two integers, symbolically specified in
-the \lstinline|input| field. The program unpairs the input pair to
-obtain two elements as two integers \lstinline/x/ and \lstinline/y/.
+the \lstinline|input| field. The program first duplicates the pair. It then unpairs the input pair to obtain two elements as two integers \lstinline/x/ and \lstinline/y/.
 Next, the program performs a comparison between
@@
 \lstinline/y/, the program constructs a new stack with a solitary
-element at the top representing the sum of  \lstinline/x/ and
+element at the top representing the subtract of  \lstinline/x/ and
 \lstinline/y/, designated as \lstinline/z/ by the \lstinline|output| directive. Otherwise, the execution
@@
 pre- and postconditions, where the precondition states the assumption
-that the integer \lstinline/x/ is greater than or equal to 5 and \lstinline/y/
-is greater than or equal to 3. The symbol  \lstinline/|/ stands for
-logical disjunction. The postcondition asserts that the result
-\lstinline/z/ is greater than or equal to 8.
+that the integer \lstinline/x/ is greater than or equal to  \lstinline/y/. The postcondition asserts that the result
+\lstinline/z/ is greater than or equal to the substract of \lstinline/x/ and \lstinline/y/, which is greater or equal to zero. The symbol \lstinline/&&/ stands for logical conjunction.
 \atha{This specification is meaningless. Why not use $x\ge y$ as
@@
 at once and also to describe and verify relationships between
-entrypoints.  The syntax is shown in Listing~\ref {lst:multiple-entrypoint-specification},
-\begin{lstlisting}[float,captionpos=b,caption={Multiple entrypoint specification syntax},label={lst:multiple-entrypoint-specification},numbers=left][h]
+entrypoints.  There are two options of the syntax as shown in Listing~\ref {lst:multiple-entrypoint-specification-1} and Listing~\ref {lst:multiple-entrypoint-specification-2},
+where the entrypoint name is written after the \lstinline/%/ symbol
+and is followed by a property specification for the entrypoint. The
+specification finishes with specifying entrypoint relations,
+which we explain next.
+
+\begin{lstlisting}[float,captionpos=b,caption={Multiple entrypoint specification syntax (option 1)},label={lst:multiple-entrypoint-specification-1},numbers=left][h]
 mcontract Name = spec
@@
    entrypoint %b 
-      code := {c2}
-      input := t2
-      output := t2'
-      pre-condition := cd2
-      post-condition := cd2'
-   entrypoint %c 
       ...
@@
 \end{lstlisting}
-where the entrypoint name is written after the \lstinline/%/ symbol
-and is followed by a property specification for the entrypoint. The
-specification finishes with specifying entrypoint relations,
-which we explain next.
+
+\begin{lstlisting}[float,captionpos=b,caption={Multiple entrypoint specification syntax (option 2)},label={lst:multiple-entrypoint-specification-2},numbers=left][h]
+mcontract Name = spec
+   storage := t1
+   entrypoint %a 
+      code := {c1}
+      parameter := t2
+      pre-condition := cd1
+      post-condition := cd1'
+   entrypoint %b 
+      ...
+   <entrypoint relations>
+\end{lstlisting}
 
@@
 \begin{lstlisting}[float=tp,captionpos=b,caption={Auction contract specification},label={lst:auction-contract-specification},numbers=left]
-mcontract Auction = spec 
+mcontract auction = spec 
   storage := Pair (auction_open: bool) 
@@
     pre-condition := auction_open 
-       && Amount > Balance
-    post-condition := post_highest_bidder = Sender 
+       && Amount > Balance - Amount
+       && get_contract (unit, highest_bidder) = 
+          Some (c: contract unit)
+    post-condition := auction_open
+       && post_highest_bidder = Sender 
+       && post_contract_owner = contract_owner 
        && post_Balance = Amount 
-       && transfer_token (Unit, Balance, highest_bidder) 
-       && post_contract_owner = contract_owner ;
+       && transfer_token (Unit, Balance - Amount, c);
 
@@
        && Sender = contract_owner  
+       && get_contract (unit, contract_owner) = 
+          Some (c: contract unit)              
     post-condition := not post_auction_open 
        && post_Balance = 0 
-       && transfer_token (Unit, Balance, contract_owner) ;
+       && transfer_token (Unit, Balance, c)
 
   (%create -> %bid) with (auction_open = true)  
-       && (Amount > Balance) 
+       and (Amount > Balance) 
+       and get_contract (unit, highest_bidder) = 
+           Some (c: contract unit)
   | (%create  -> %close) with (auction_open = true) 
-       && (Sender = contract_owner)
-    | (%bid -> %bid) with (Amount > Balance)  
+       and (Sender = contract_owner)
+       and get_contract (unit, contract_owner) = 
+          Some (c: contract unit)
+  | (%bid -> %bid) with (Amount > Balance - Amount) 
+       and get_contract (unit, highest_bidder) = 
+          Some (c: contract unit)
   | (%bid -> %close) with (Sender = contract_owner) 
+       and get_contract (unit, contract_owner) = 
+            Some (c: contract unit)
   | not (%close -> %bid)
@@
 structure described by the \lstinline|storage| phrase. 
-The output term should maintain the required pattern of the storage,
+The output term should maintain the required term of the storage,
 but the values may be changed and these changes are recorded in
@@
 \lstinline/post_/ to the variable names to refer to the storage
-returned by the program. The output pattern could be safely removed in
+returned by the program. The output term could be safely removed in
 this example because the tool automatically generates an output
-pattern corresponding the one specified here.
+term corresponding the one specified here.
 
@@
 from the default entry point.  The initial stack is derived from the
-input pattern for each the entry point. To maintain symbolic values as
+input term for each the entry point. To maintain symbolic values as
 concrete as possible, some instructions may be deemed unreachable or
@@
 that the smart contract should satisfy. Subsequently, the symbolic
-interpreter is run on the code with the provided input pattern.  The
+interpreter is run on the code with the provided input term.  The
 path conditions are then fed into a Z3 converter, which transforms
@@
 framework. The specification is subsequently parsed into an Abstract
-Syntax Tree (AST) in OCaml. The code and the input pattern are then
+Syntax Tree (AST) in OCaml. The code and the input term are then
 input to the symbolic interpreter. In the next phase, the pre- and
@@
 
-We first build the input state from the input pattern and run the
+We first build the input state from the input term and run the
 symbolic interpreter on the input stack with the provided code to
@@
 unreachable states are discarded from the final states as their path
-conditions are unsatisfiable. Using the output pattern and the pre-
+conditions are unsatisfiable. Using the output term and the pre-
 and post-conditions converted by the Z3 conveter, the tool then
@@
 The first check is the output check, where the checker verifies
-whether the output pattern matches. The final state contains a stack
+whether the output term matches. The final state contains a stack
 with only one element as \Stack\ \STACKCONCAT\ \EMPTYSTACK. There are
@@
 representing the storage and \VOPERATIONLIST\ repesents a operation
-list. Given an output pattern $ \tau$, the checker scans all the final
+list. Given an output term $ \tau$, the checker scans all the final
 states, which do not contain a failwith stack and checks whether the
-output pattern matches. In the former case, it matches $ \tau$  with
+output term matches. In the former case, it matches $ \tau$  with
 the term \Term. In the latter case, it essentially matches with the
 corresponding part \VSTORAGE\ in the final states resulting from the
-symbolic interpreter. When the input pattern is a concrete value, the
+symbolic interpreter. When the input term is a concrete value, the
 result from the interpreter is also concrete, and then the checker can
@@
 this example as expected. However, this test could fail if, for
-example, the output pattern is incorrectly specified as a variable of
+example, the output term is incorrectly specified as a variable of
 a type that does not match with the actual result. If the input
-pattern is concrete, for instance, a pair of numbers as in
+term is concrete, for instance, a pair of numbers as in
 \lstinline|Pair 5 3|, then the expected output should be the number
-\lstinline|8|. To check this,  the output pattern may be specified as
+\lstinline|8|. To check this,  the output term may be specified as
 a concrete value.
@@
 The second example in Listing \ref{lst:auction-contract-specification}
-is the specification for a smart contract code. The output pattern
+is the specification for a smart contract code. The output term
 represents the updated storage after executing the code. There are
@@
 1. not (auction_open): 'Already closed'
-2. auction_open && (Amount <= Balance):
+2. auction_open && (Amount <= Balance - Amount):
    'Not higher than the current highest bid'
-3. auction_open && not (Amount <= Balance) && 
-   get_contract (Unit, highest_bidder) = None:
-   'Invalid address' 
+3. auction_open && not (Amount <= Balance - Amount) && 
+   get_contract (unit, highest_bidder) = None:
+   'Invalid highest bidder address' 
 \end{lstlisting}
@@
 3. auction_open && (Sender = contract_owner) &&
-   get_contract (Unit, contract_owner) = None:
-  'Invalid address'
+   get_contract (unit, contract_owner) = None:
+  'Invalid contract owner address'
 \end{lstlisting}
@@
 $\land$ $\Theta$) is satisfiable. We then check that for every path
-$\Pi$, $\neg$ ($\bigwedge \Phi_{i} \rightarrow \bigwedge \Psi_{j}$) is
+$\Pi$, $\neg$ ($\bigwedge \Phi_{i}$ $\land$ $\Theta$ $\rightarrow \bigwedge \Psi_{j}$) is
 unsatisfiable in the context given by the input for the entry point
-and its corresponding final state and path condition.
+and its corresponding final state.
 \atha{Don't you have to include $\Theta$ in the check for unsat?}
 
-Consider the specification of the Add contract in Listing
-\ref{lst:add-contract-specification}. In this context, the two
+Consider the specification of the sub contract in Listing
+\ref{lst:sub-contract-specification}. In this context, the two
 variables \lstinline/x/ and \lstinline/y/ are integers. The results of
@@
 \lstinline/y/ and the symbolic variable \lstinline/sbvar/ is equal to
-the sum of \lstinline/x/ and \lstinline/y/.  For this specification,
+the substract of \lstinline/x/ and \lstinline/y/.  For this specification,
 the failwith branch is discarded because the precondition is not
-satisfy with tha path condition, and then \lstinline/z/ is matched to
+satisfy with the	 path condition, and then \lstinline/z/ is matched to
 the symbolic variable \lstinline/sbvar/ in the other branch. In this
-example, the checker then verifies that given the with the context
-asserting that (\lstinline/x/ >= \lstinline/y/) $\land$ (\lstinline/z/
-= \lstinline/x/ + \lstinline/y/), $\neg$ ((\lstinline/x/ >= 5) $\land$
-(\lstinline/y/ > 3) $\rightarrow$ (\lstinline/z/ >= 8)) is
+example, the checker then verifies that $\neg$ ((\lstinline/x/ >= y) $\land$ (\lstinline/z/
+= \lstinline/x/ - \lstinline/y/) $\rightarrow$ (\lstinline/z/ = \lstinline/x/ - \lstinline/y/) $\land$ (\lstinline/z/ >= 0)) is
 unsatisfiable.
@@
 \atha{To be completed}
+An entrypoint relation can be defined as \lstinline/%a with cd -> %b/, indicating that after invoking the entrypoint \lstinline/%a/, it is permissible to call the entrypoint \lstinline/%b/ if the condition \lstinline/cd/ is satisfied.
+The presence of the keyword \lstinline/not/ at the beginning signals an impossibility.
+Note that \lstinline/with cd/ may be omitted when no condition is needed.
+
+Let $S_a$ represent the set of all reachable states resulting from the execution of the call to the entrypoint \lstinline/%a/.
+Each $s_{i}$ in $S_a$ is associated with a path condition $\Theta_i$ and is represented as a stack containing a single element—a pair consisting of an operation list ($\VOPERATIONLIST_i$) and the storage $\VSTORAGE_i$.
+For each $s_{i}$, symbolic execution is performed on the entrypoint \lstinline/%b/ using input as a pair of the parameter and the storage $\VSTORAGE_i$, constrained by $\Theta_i$ and the condition \lstinline/cd/.
+In the execution state space, a state $s_{j}$ with the path condition $\Theta_j$ is considered reachable if ($\Theta_i$ $\land$ \lstinline/cd/ $\land$ $\Theta_j$) is satisfiable, and $\neg$ ($\Theta_i$ $\land$ \lstinline/cd/ $\rightarrow$ $\Theta_j$) is unsatisfiable.
+Let $S_b$ denote the set of these reachable states.
+If $S_b$ is empty or contains only failwith states, then it is impossible to invoke the entrypoint \lstinline/%b/ from the state $s_{i}$.
+Otherwise, it is considered a success.
+Let $R$ be the set containing all such states $s_{i}$ in $S_a$ where it is successful to call the entrypoint \lstinline/%b/ with the condition \lstinline/cd/.
+If $R$ is non-empty, then \lstinline/%a with cd -> %b/ holds.
+Otherwise, it is false, signifying \lstinline/not (%a with cd -> %b)/.
 
@@
 \begin{lstlisting}[float,captionpos=b,caption={Specification of the \lstinline/transfer/ entrypoint},label={lst:specification-transfer},numbers=left]
-mcontract USDtz = spec 
+mcontract usdtz = spec 
    storage :=  Pair (ledger: big_map address 
@@
  \item    \lstinline/governorContractAddress/: the address of the governor contract.
+The governor is the controler of the oracle contract as it is able to update on the contract such as reset the maximu time for data delay.
  \item    \lstinline/maxDataDelaySec/: the maximum acceptable age of data received from Harbinger, measured in seconds.
@@
 \begin{lstlisting}[float=tp,captionpos=b,caption={Kolibri oracle contract specification},label={lst:kolibri-contract-specification},numbers=left]
-mcontract Auction = spec 
+mcontract kolibri = spec 
   storage := (Pair (Pair (client: option address) 
@@
 \label{sec:system-model}
+
+Our symbolic model of a program state is a stack in which each element
+is a symbolic value, i.e., a pair consisting
+of term and its corresponding type. Terms are defined in
+Figure~\ref{fig:term}. Thus we write a stack as \STACK\ = (\TermOne,
+\TYF) \STACKCONCAT\ (\TermTwo, \TYS) \STACKCONCAT\ \DOT\ \STACKCONCAT\ 
+\EMPTYSTACK\ where \ensuremath{[\ ]} stands for the empty stack and
+\ensuremath{hd :: tl} denotes a stack with the top element as
+\ensuremath{hd} and the remaining stack as \ensuremath{tl}. 
+A selection of types is shown in Figure~\ref{fig:type}.
+
+A Michelson program is a sequence of instructions executed in a
+sequential manner. Each instruction takes, as input, the stack
+produced by the preceding instruction and modifies it for the
+subsequent one. Let \INSTRUCTION\ = \InstructionOne; \InstructionTwo;
+\DOT\  \InstructionN\ represent a sequence of instructions.
+
+During symbolic execution,  the system state evolves considering all
+values admitted by the constraints on symbolic values. Unless the
+input values are sufficiently known, symbolic execution may split the
+state, and both constraints and branching conditions are recorded as
+predicates. Let \PREDICATE\ be a path predicate that is extended at
+each conditional and expressed in conjunctive form, capturing the
+branching conditions and constraints encountered during the symbolic
+execution process. 
+\begin{definition}
+A symbolic execution state is represented by a tuple \STATE\ =
+[\INSTRUCTION, \STACK, \PREDICATE].
+A symbolic system configuration, \SYSTEM\ = \{\STATEONE, \STATETWO,
+\DOT, \STATEN \}, is a set of  states.
+\end{definition}
+
+The smart contract program takes a stack as input, consisting of a
+single pair where the first element is an input value referred to as
+parameter denoted as \VPAR\ and the second element represents the
+content of the storage space denoted as \VSTORAGE. The program
+produces a stack as output, which is a single pair. The first element
+of this pair is the list of internal operations that the program
+intends to emit (\VOPERATIONLIST), and the second element is the new
+contents of the storage space.  We define the initial stack as
+\SINIT\   = (\KPAIR\ \VPAR\ \VSTORAGE, \TPAIR\ \TYF\ \TYS)
+\STACKCONCAT\ \EMPTYSTACK, where \VPAR\ and \VSTORAGE\ denote terms
+representing the parameter and the storage, and \TYF\ and \TYS\ are
+their corresponding types. Similarly, a final stack has the form
+\SFINAL\   = (\PAIR\ \VOPERATIONLIST\ \VSTORAGE, \TPAIR\
+(\TOPERATIONLIST) \TYS) \STACKCONCAT\ \EMPTYSTACK, where
+\VOPERATIONLIST\ repesents a operation list.
+
+The initial configuration is \SYSTEMINIT\ = \{[\INSTRUCTION, \SINIT, \TRUE] \}.
+
+\subsection{Rules}
+Each instruction is defined by a rule on a system configuration. There
+are several kinds of transitions:
+\begin{enumerate}
+% \item \ExprTrans\ single-step evaluation of an expression in a system state,
+\item \StateTrans\ internal transitions of a state, which is
+  non-deterministic  as shown for loop instructions, such as \LOOP\
+  and \LOOPLEFT, 
+\item \SystemTrans\ symbolic system transitions.
+\end{enumerate}
+
+A system transition picks any state and replaces it by all distinct states that
+are reachable by internal transitions. It exploits the nondeterminism
+of the \StateTrans\ relation.
+\begin{mathpar}
+  \inferrule[]
+  { \STATE\ \StateTrans \STATEONE, \dots, \STATE\ \StateTrans \STATEN
+  }{
+  \{\STATE\} \cup \SYSTEM \SystemTrans \{ \STATEONE, \dots, \STATEN \}
+  \cup \SYSTEM}  
+\end{mathpar}
+In general, symbolic execution may generate unreachable
+states. A state is unreachable if its predicate \PREDICATE\ is  not
+satisfiable. Hence, we have a rule that drops unreachable states.
+\begin{mathpar}
+\inferrule[]
+  { \UNSAT\ \PREDICATE
+  }{
+  \{[\INSTRUCTION, \STACK, \PREDICATE]\} \cup \SYSTEM \SystemTrans \SYSTEM}
+\end{mathpar}
+The working of the symbolic interpreter may also be understood as a
+graph with symbolic states as nodes and internal transitions as
+edges. Such a representation makes it easier to perform multi-step
+subtransitions as they are required for some operations.
+
+Michelson instructions are categorized based on their functions. The
+categories include control structures, stack manipulation, arithmetic
+operations, boolean operations, cryptographic operations, and
+operations on data structures. In our model, we classify them as
+one-step, multi-step, blockchain, cryptographic, branch, and loop
+instructions. This categorization reflects how these instructions are
+handled within our specific model.
+
+\subsubsection{One-step Instructions}
+\label{sec:one-step-instr}
+One-step instructions have a localized effect, modifying the system
+state directly without branching a new state, and their execution is
+modeled with a single rule.
+% The ABS rule exemplifies such an
+% instruction, operating on the first element of the stack. This element
+% must be of type int, and the instruction returns the absolute value of
+% its argument as a natural number. To this end, the rule creates a
+% fresh variable, \X, and defines its value by a suitable predicate.
+% %ABS
+% \begin{mathpar}
+% \inferrule[ABS]
+%   { \X\ \FRESH
+%   }
+%   {
+%     [(\ABS; \INSTRUCTION), (\StackOne, \TINT) \STACKCONCAT \STACK,
+%     \PREDICATE]
+%     \StateTrans \\
+%     [\INSTRUCTION, (\X, \TNAT) \STACKCONCAT \STACK,
+%     \PREDICATE\ \wedge\ (\StackOne\ \GE\ \ZERO\ \Rightarrow\ \X\ =
+%     \StackOne) \wedge\ (\StackOne\ \LT\ \ZERO\ \Rightarrow\ \X\ = \MINUS\ \StackOne)]
+%  }
+% \end{mathpar}
+
+For example, the \COMPARE\ instruction for natural numbers compares
+the first two elements of the stack, both having a natural number
+type. It returns a result of either -1, 0, or 1 based on the
+comparison of their values. 
+% COMPARE
+\begin{mathpar}
+\inferrule[COMPARE]
+  { \X\ \FRESH
+  }
+  {
+    [(\COMPARE ; \INSTRUCTION), (\StackOne, \TNAT) \STACKCONCAT (\StackTwo, \TNAT)
+    \STACKCONCAT \STACK, \PREDICATE ]
+    \SystemTrans \\
+    [\INSTRUCTION, (\X, \TINT) \STACKCONCAT \STACK, \PREDICATE
+    \wedge\ (\StackOne\ \GT\ \StackTwo\ \Leftrightarrow\ \X\ \EQ\ \ONE)
+    \wedge\ (\StackOne\ \EQ\ \StackTwo\ \Leftrightarrow\ \X\ \EQ\ \ZERO) 
+    \wedge\ (\StackOne\ \LT\ \StackTwo\ \Leftrightarrow\ \X\ \EQ\ \MINUS \ONE)]
+    }
+\end{mathpar}
+\subsubsection{Multi-step Instructions}
+Multi-step instructions involve the execution of a sub-sequence of instructions before returning to the main execution.
+The rule below models the \EXEC\ instruction, which executes a function specified as a sequence of instructions denoted by \INSTRUCTIONONE\ in the rule.
+This instruction applies the code of the function to the first element of the stack and then places the result back into the main execution.
+\begin{mathpar}
+  \inferrule[\EXEC]
+  {
+    [\INSTRUCTIONONE, (\StackOne, \TYF) \STACKCONCAT \EMPTYSTACK, 
+    \Q]
+    \StateTrans^*
+    [ \EMPTYSTACK, (\StackOne', \TYS) \STACKCONCAT \Q']
+  }{
+     [(\EXEC; \INSTRUCTION),   (\{\INSTRUCTIONONE\}, \TYF\ \rightarrow\ \TYS) \STACKCONCAT
+    (\StackOne, \TYF) \STACKCONCAT \STACK, \PREDICATE \wedge \Q] 
+    \StateTrans \
+    [ \INSTRUCTION, (\StackOne', \TYS) \STACKCONCAT \STACK,
+    \PREDICATE \wedge \Q']}
+\end{mathpar}
+
+The \DIP\ \N\ instruction skips over the first \N\ elements of a
+stack, applies the sequence of instructions denoted as
+\INSTRUCTIONONE\ to the remaining part of the stack, modifies a part
+of the predicate and subsequently pushes the result back into the main
+execution. 
+%DIP n
+\begin{mathpar}
+\inferrule[\DIP\ \N]
+  { 
+     \FLEN(\A) \EQ\ \N \\ [\INSTRUCTIONONE,  \B, \Q]
+    \StateTrans^*
+    [\EMPTYSTACK,  \B_1, \Q']
+  }
+  {[(\DIP\ \N\ \INSTRUCTIONONE; \INSTRUCTION), \A\ \At\ \B, \PREDICATE \wedge \Q] \StateTrans 
+[\INSTRUCTION, \A\ \At\ \B_1, \PREDICATE \wedge \Q']}
+\end{mathpar}
+\subsubsection{Blockchain Instructions}
+ Blockchain instructions make implicit use of data from the current
+ state of the blockchain (the context), from the transaction that
+ triggered the contract, and from the block containing this
+ transaction. As these values are constant during the execution of a
+ contract, we model them as fixed variable. For example, the \AMOUNT\
+ instruction pushes the amount of tokens on the stack that the
+ contract received from its caller. This amount is modeled as the
+ fixed variable \CAMOUNT, which has type \TMUTEZ.
+
+\begin{mathpar}
+\inferrule[AMOUNT]
+  {
+  }
+  {[(\AMOUNT; \INSTRUCTION), \STACK, \PREDICATE] \StateTrans \
+[\INSTRUCTION, (\CAMOUNT, \TMUTEZ) \STACKCONCAT \STACK, \PREDICATE]}
+\end{mathpar}
+
+% \subsubsection{Cryptographic Instructions}
+% Cryptographic instructions in Michelson utilize built-in functions that manage cryptographic features.
+These functions are symbolically modeled in our framework, specifying their inputs and outputs.
+For instance, the instruction \SHA\ computes the cryptographic hash of the top of the stack using the SHA-256 cryptographic hash function.
+The function SHA-256 is symbolically represented as the function  \FSHA\  that takes an input of type \TBYTE\ and returns another byte value, constrained to a length of 256.
+% %HASH-KEY
+% \begin{mathpar}
+% \inferrule[\SHA]
+%   {
+%   }
+%   {[(\SHA; \INSTRUCTION), (\StackOne, \TBYTE) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
+% [\INSTRUCTION, (\X, \TBYTE) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\X\ \EQ\ \FSHA(\StackOne))]}
+% \end{mathpar}
+\subsubsection{Branch Instructions}
+The simplest conditional in Michelson language is the \IF\ \{
+\INSTRUCTIONONE\ \} \{ \INSTRUCTIONTWO\  \} instruction. It expects
+and consumes a boolean value at the top of the stack. If the boolean
+is True, it executes \INSTRUCTIONONE; otherwise, it executes
+\INSTRUCTIONTWO. 
+%IF
+\begin{mathpar}
+  \inferrule[IF-true]
+  {  
+  }{
+    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
+    \StateTrans\
+    [\INSTRUCTIONONE, \STACK, \PREDICATE\ \Wedge\ \StackOne]
+  }
+
+  \inferrule[IF-false]
+  {  
+  }{
+    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
+    \StateTrans\
+   [\INSTRUCTIONTWO, \STACK, \PREDICATE\ \Wedge\ \NEG\
+   \StackOne]
+ }
+\end{mathpar}
+
+Another branch instruction is the IF-LEFT instruction, which is used
+for conditional execution based on the left or right branch of a sum
+type.  
+%IF-LEFT-LEFT
+\begin{mathpar}
+  \inferrule[IF-LEFT-left]
+  {  \X\ \FRESH
+  }{
+    [(\IFLEFT\ \INSTRUCTIONONE\ \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]
+    \StateTrans \
+    [(\INSTRUCTIONONE; \INSTRUCTION), (\X, \TYF) \STACKCONCAT\STACK,
+    \PREDICATE \wedge (\StackOne\ \EQ\ \LEFT\ \X)]
+  }
+\end{mathpar}
+
+%IF-LEFT-RIGHT
+\begin{mathpar}
+  \inferrule[IF-LEFT-right]
+  {    \X\ \FRESH
+  }{
+    [(\IFLEFT\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]
+    \StateTrans \
+    [(\INSTRUCTIONTWO; \INSTRUCTION), (\X, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQ\ \RIGHT\ \X))]
+  }
+\end{mathpar}
+These above rules define the behavior of the \IFLEFT instruction. The
+rule applies when the top element of the stack is a tagged union of
+type \TOR\ \TYF\ \TYS (either of type \TYF\ or \TYS), and the \IFLEFT
+instruction is followed by instructions \INSTRUCTIONONE\ and
+\INSTRUCTIONTWO. The first rule adds the condition that the top
+element of the stack is of the form Left \X\ (indicating the left
+branch of the union), it transitions to execute the instructions
+\INSTRUCTIONONE\ with the stack modified accordingly and the predicate
+is updated to include the condition that the top element of the stack
+is equal to Left \X. Similarly, the second rule handles the case Right\
+\X, mutatis mutandis.
+
+\subsubsection{Loop Instructions}
+Michelson supports a number of loop instructions, including
+\LOOP\ and \LOOPLEFT, that  check the loop condition by examining the
+top of the stack. These loop instructions may not terminate, just like while-loops. There are further loop instructions, like \ITER\ and
+\MAP, specialized to traverse data structures like lists, sets, and maps. There are also
+some instructions that implicitly require looping like \CONCAT, and
+\SIZE. The latter kinds of loop instructions do always terminate.
+
+% Michelson, similar to other programming languages, classifies loop instructions into two main types:
+% \begin{itemize}
+% \item \KFOR\ loops: These are sequence-based loops, exemplified by \ITER, \MAP, \CONCAT\ and \SIZE.
+% \item \KWHILE\ loops: These are predicates-based loops, illustrated by \LOOP and \LOOPLEFT.
+% \end{itemize}
+% To illustrate the structures of  loops, we can draw a parallel with OCaml syntax as in Listing \ref{list:while-loop}.
+
+% \begin{lstlisting}[caption={While loop.},label=list:while-loop,captionpos=t,float,abovecaptionskip=-\medskipamount]
+% while <loop_condition> do
+%    <loop_body>
+% done
+% \end{lstlisting}
+% This \KWHILE\  loop structure involves a loop condition that is evaluated at the beginning of each iteration.
+If the condition holds true, the loop body is executed, and the process repeats until the condition becomes false.
+In Michelson, this term is evident in instructions like LOOP and LOOP-LEFT, which rely on predicate-based conditions for their iteration: \lstinline/LOOP {<loop-body>}/.
+
+% Additionally, Michelson features a \KFOR\ loop, where the index runs from the initial value to the final value as in Listing \ref{list:for-loop}.
+The \KFOR\ loop is represented by the ITER instruction: \lstinline/ITER {<loop-body>}/
+
+% \begin{lstlisting}[caption={For loop.},label=list:for-loop,captionpos=t,float,abovecaptionskip=-\medskipamount]
+% for index = <initial_value> to <final_value> do
+%   <loop_body>
+% done
+% \end{lstlisting}
+
+% The fundamental concept underlying the definition of a loop is its loop condition, the predicate that must hold true for the loop to continue execution.
+In the case of \KWHILE\ loops, the  loop condition is explicitly embedded in the loop syntax.
+However, for the \KFOR\  loops, the loop condition is more implicit.
+A \KFOR\  loop can be rewritten as a  \KWHILE\ loop to make the  loop condition explicit as showned in Listing \ref{list:express-for-using-while-loop}.
+% \begin{lstlisting}[caption={Expressing a \KFOR\ loop using a \KWHILE\ loop.},label=list:express-for-using-while-loop,captionpos=t,float,abovecaptionskip=-\medskipamount]
+% index = 0
+% while index < length(sequence) do
+%   <loop_body>
+%   index += 1
+% done
+% \end{lstlisting}
+% Here, the implicit loop condition asserts that the index of the sequence element is less than the length of the sequence.
+
+%  do not explicitly contain their loop conditions. Instead, the  loop condition is established:
+% \begin{itemize}
+%  \item In the expressions preceding the loop for the first time entering the loop.
+%  \item Inside the loop body for subsequent iterations.
+% \end{itemize}
+
+% The loop instructions are applied to a stack, and the loop condition is checked with the top element of the stack.
+For a  \KWHILE\ loop the top element of the stack must have a boolean value and for the \KFOR\  loop, it must have a sequence data type, such as list, set or map.
+If we denote the function to retrieve the top element of a stack as "\FPOP," the  \KWHILE\ loop instruction can be expressed as shown in Listing \ref{list:express-for-using-ocaml} and and the \KFOR\  loop is expressed as Listing \ref{list:express-while-using-ocaml}.
+% \begin{lstlisting}[caption={Expressing Michelson \KWHILE\ loop using  Ocaml syntax.},label=list:express-for-using-ocaml,captionpos=t,float,abovecaptionskip=-\medskipamount]
+% while pop(S) do
+%    loop_body
+% done
+% \end{lstlisting}
+
+% \begin{lstlisting}[caption={Expressing Michelson  \KFOR\ loop using Ocaml syntax.},label=list:express-while-using-ocaml,captionpos=t,float,abovecaptionskip=-\medskipamount]
+% index = 0
+% while index < length(pop(S)) do
+%   <loop_body>
+%   index += 1
+% done
+% \end{lstlisting}
+
+\paragraph {\ITER}
+Lets us consider the \ITER\ instruction, which iterates over a
+list.\footnote{\ITER\ can also iterate over sets and maps, but the
+  details are very similar to the list case and hence omitted.} The
+corresponding typing rule is as follows: 
+\begin{mathpar}
+  \inferrule{\JTypeExpr\TEnv{\INSTRUCTION}{\TY \STACKCONCAT \TYA\ \SRightarrow\ \TYA}
+  }{
+      \JTypeExpr\TEnv{\ITER\ \INSTRUCTION}{\TYLIST\ \TY \STACKCONCAT \TYA\ \SRightarrow\ \TYA}
+    }
+\end{mathpar}
+This typing rule ensures that if the loop body \INSTRUCTION\ has the type \TY\ \STACKCONCAT \TYA\ \SRightarrow\ \TYA, then the entire \ITER\ instruction, when applied to a stack with the top element of type \TY\ \TYLIST\ and the rest of the stack of type \TYA, produces a result stack of type \TYA.
+
+We consider rules for symbolic execution of the \ITER\ instruction.
+%%ITER
+\begin{mathpar}
+  \inferrule[ITER-empty]
+  {  
+  }{
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, \STACK,  \PREDICATE\ \Wedge\  (\StackOne\ \EQ\ \EMPTYLIST)]
+  }
+\end{mathpar}
+This rule handles the case where the list is empty, so that the \ITER\
+instruction just skips. The rule transitions to the next instruction
+after popping the empty list from the stack. We register emptiness in
+the predicate \PREDICATE\ $\Wedge$ (\StackOne \EQ \EMPTYLIST). 
+\begin{mathpar}
+  \inferrule[ITER-nonempty]
+  { \HEAD, \STAIL\ \FRESH \\
+    [\ITER,  (\HEAD, \TY) \STACKCONCAT\STACK, 
+    \PREDICATE]
+    \StateTrans^*
+    [ \EMPTYSTACK,  \STACK', \PREDICATE']
+  }{
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\
+    \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \\
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\STAIL, \TYLIST)\
+    \STACKCONCAT\STACK',  \PREDICATE' \Wedge  (\StackOne\
+    \EQ\ \{\HEAD; \STAIL \}) ] 
+  }
+\end{mathpar}
+The next rule handles the case where the list is non-empty. It
+symbolically executes the instructions \INSTRUCTIONONE\ within the
+\ITER\ block with the head of the list (\HEAD) replacing the list. The resulting state transitions to a
+new stack (\STACK') and an updated predicate (\PREDICATE' $\Wedge$
+(\StackOne \EQ \{\HEAD;\STAIL\})), where \STAIL represents the rest of the list. 
+These rules capture the symbolic execution behavior of the \ITER\
+instruction, considering both the cases where the list is empty and
+non-empty.
+
+If the initial list is concrete, the instruction terminates as it simply loops over the
+elements of the list. But how do we deal with \ITER\ if the list is a
+symbolic value?
+One solution could involve running
+the loop for a number of times to obtain the symbolic value. However,
+we can defer that decision by exploiting features of Z3.
+
+Let us again consider the instruction \ITER\
+\{\INSTRUCTION\}. The sequence of instructions \INSTRUCTION\ denotes
+the loop body. In fact, \INSTRUCTION\ can be considered a function of
+type (\TY\ \STACKCONCAT \TYA\ \SRightarrow\ \TYA) applied to a stack
+of type \TY\ \STACKCONCAT \TYA,
+resulting in a stack of type \TYA. If the first element of
+the stack is a list of the form \LIST\ = $x_1 \STACKCONCAT x_2 \STACKCONCAT
+\dots x_m \STACKCONCAT  [\ ]$, and the rest of the stack is \STACKZERO\ =
+\StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ ... \STACKCONCAT\
+\StackN. Then the \ITER\ \{\INSTRUCTION\} instruction applies a 
+function, sat \F, represented by \INSTRUCTION\ \M\ times to the stack, once
+with each element $x_i$ on top of the stack. The result after 
+the first iteration is \STACKONE\ = \StackOneOne\  \STACKCONCAT\
+\StackTwoOne\ \STACKCONCAT\ ... \STACKCONCAT\ \StackNOne = \F\ $x_1$
+\STACK. Then \STACKTWO = \F\ $x_1$ \STACKONE, and so on.
+% Typing of \ITER\ enforces that
+% the type of the result stack is the same as the previous
+% stack.
+% Call the function \FI\ that takes the head \HEADZERO\
+% of the list and all elements of  the stack \STACKZERO\ as  \StackOne,
+% \StackTwo, ... \StackN, given  as \STACKZEROBAR\ and returns the
+% i-element  \StackIOne\ of the stack \STACKONE. The function
+% representing \INSTRUCTION\  is defined as the vector of these subfunctions
+% \FI.  
+% \begin{mathpar}
+% \StackOneOne\ = \FOne\  \HEADZERO\ \STACKZEROBAR \\
+% \StackTwoOne\ = \FTwo\  \HEADZERO\ \STACKZEROBAR \\
+% ...\\
+% \StackNOne\ = \FN\  \HEADZERO\ \STACKZEROBAR 
+% \end{mathpar}
+% When the next loop is performed, the same function \FI\ is applied to the next element of the list and all element of the the stack \STACKONE\ and we get the \StackITwo.
+In the same way, the the loop is performed for \J\ time, we get the stack \STACKJ\ as follows:
+
+% \begin{mathpar}
+% \StackOneJ\ = \FOne\  \HEADJMINUS\ \STACKJMINUSBAR \\
+% \StackTwoJ\ = \FTwo\  \HEADJMINUS\ \STACKJMINUSBAR \\
+% ...\\
+% \StackNJ\ = \FN\  \HEADJMINUS\ \STACKJMINUSBAR 
+% \end{mathpar}
+
+We conclude, we can represent the value of the stack after running the
+instruction \ITER\  as the result of a fold function that applies the
+function \F\ to the list. This representation is advantageous because
+Z3 can handle functions defined using \FOLD\ directly.
+% \begin{mathpar}
+% \StackOneM\ = \FOLD\ \FOne\ \STACKZEROBAR\  \LIST\  \\
+% \StackTwoM\ = \FOLD\ \FTwo\  \STACKZEROBAR\ \LIST\  \\
+% ...\\
+% \StackNM\ = \FOLD\ \FN\ \STACKZEROBAR\  \LIST
+% \end{mathpar}
+
+% Generally, we can represent the sequence of instructions \INSTRUCTION\ as the function \F\ that takes an element of type \TY\ of a list \LIST\ and a  stack \STACK\ of type \TYA\ and returns a stack of type \TYA.
+
+\begin{mathpar}
+\STACK'\ =  \FOLD\ \F\ \STACK\ \LIST
+\end{mathpar}
+
+For example, consider \ITER\ \{\ADD\} that applies to a stack \STACK\ that has a integer list as the top element and the rest \STACKZERO\ = \StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ ...
+\STACKCONCAT\ \StackN.
+\begin{mathpar}
+\ITER\ \{ \ADD\ \} \Slash \LIST\ \STACKCONCAT\ \STACKZERO
+\end{mathpar}
+The type of the \ADD\ instruction indicates that the top element of
+the stack \STACKZERO\ namely \StackOne, has type integer list. For
+each iteration, the \ADD\ instruction adds another element of the list
+to the top element of the stack and then the rest of the stack is
+unchanged.  Let us build the function \FOne\ with the assumption that the list \LIST\ is not empty as \{\HEAD; \STAIL \}, 
+\begin{mathpar}
+\FOne\ (\HEAD, \StackOne,  \StackTwo, \DOT, \StackN) = \HEAD\ + \StackOne\\
+\FTwo\ (\HEAD, \StackOne,  \StackTwo, \DOT, \StackN) = \StackTwo\\
+... \\
+\FN\ (\HEAD, \StackOne,  \StackTwo, \DOT, \StackN) = \StackN\\
+\end{mathpar}
+
+So \F\ is the function that takes an integer and a stack starting with
+an integer as inputs and returns a stack of the same length with the
+integer added to the top of the stack
+\begin{mathpar}
+\FOne\ (\X, \XOne \STACKCONCAT \XTwo \STACKCONCAT \DOT \XN
+\STACKCONCAT $[\ ]$) = \X\ + \XOne
+\end{mathpar}
+But as \XTwo\STACKCONCAT \DOT \STACKCONCAT \XN\ do not participate in
+the calculation, we can simplify the function to 
+\begin{mathpar}
+\FOne\ (\X, \XOne) = \X\ + \XOne
+\end{mathpar}
+The symbolic value of the top element of the stack after the \ITER\ \{\ADD\} loop is
+\begin{mathpar}
+\FOLD\ \FOne\ \StackOne\ \LIST
+\end{mathpar}
+As the loop body does not change the rest of the stack, we can omit
+the identity functions on the remaining components in an implementation.
+% \begin{mathpar}
+% \FI\ (\X, \XOne, \DOT, \XI, \DOT, \XN) = \XI
+% \end{mathpar}
+
+The \FOLD\ function also can be used to express the result of other
+loop instructions, such as CONCAT and SIZE, symbolically.
+
+\paragraph {\MAP}
+
+% The \ITER\ instruction and some other can be symbolicly implemented
+% using \FOLD\ function applying on the sequance data structures as
+% list, set and map. 
+Next, we consider the \MAP\ instruction. While any \MAP\ instruction
+can be transformed to an \ITER\ instruction, it is more efficient to
+use a map function for the symbolic result of the instruction.
+
+Again we consider
+the  \MAP\ \{\I\}   instruction for lists, which operates on a stack
+\STACK, whose the top element has type \TY\ \TYLIST, and the rest has
+type \TYA. The instruction returns a stack of type (\TY\ \TYLIST) \STACKCONCAT
+\TYA. The corresponding typing rule is as follows: 
+\begin{mathpar}
+  \inferrule{\JTypeExpr\TEnv{\INSTRUCTION}{\TY  \SRightarrow\ \TY'}
+  }{
+      \JTypeExpr\TEnv{\MAP\ \INSTRUCTION}{\ \TY\ \TYLIST\ \STACKCONCAT \TYA\ \SRightarrow\ \TY'\ \TYLIST\  \STACKCONCAT \TYA}
+    }
+\end{mathpar}
+This typing rule ensures that if the loop body (\INSTRUCTION) has the
+type \TY\ \SRightarrow\ $\TY'$, then the entire \ITER\ instruction
+produces a result stack of type $\TY'$ \ \TYLIST\ \STACKCONCAT \TYA.
+
+The execution rules are similar in style to the ones for \ITER.
+%MAP
+\begin{mathpar}
+\inferrule[MAP-empty]
+  {
+  }
+  {[(\MAP\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \ 
+[\INSTRUCTION, (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQ\ \EMPTYLIST)]}
+\end{mathpar}
+
+\begin{mathpar}
+\inferrule[MAP-nonempty]
+  {
+  [\INSTRUCTIONONE, (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q1]
+    \StateTrans^*
+    [\EMPTYSTACK,  (\PHEAD, \TY) \STACKCONCAT\EMPTYSTACK , Q1'] \\  [\MAP\ \INSTRUCTIONONE, (\{\TAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK , Q2]
+    \StateTrans^*
+    [\EMPTYSTACK,  (\{\PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK , Q2']
+  }
+  {[(\MAP\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1 \Wedge\ Q2 ] \StateTrans  \\
+[\INSTRUCTION, (\{\PHEAD; \PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1' \Wedge\ Q2'  \Wedge\ (\StackOne \EQ\ \{\HEAD; \TAIL\})]}
+\end{mathpar}
+Let consider how we can avoid the symbolic iteration.
+The list of instructions \INSTRUCTIONONE\ can be represented as a function \F\ that takes a input of type \TY\ and returns an output of type $\TY'$.
+\begin{mathpar}
+\F\ : \TY\ \SRightarrow\ \TY'
+\end{mathpar}
+The \MAP\ instruction traverses the list \LIST\ by applying the
+function \F\ to each element. Symbolically the result of the \MAP\
+\{\INSTRUCTION\} to the list \LIST\ is the result of a map function
+that applies the function \F\ that represent of the sequence of
+instructions \I\ to the list.
+
+\begin{mathpar}
+\MAP\ \{\INSTRUCTION\} \Slash\ \LIST\ :: \STACK\ \SRightarrow\ (\FMAP\ \F\ \LIST) ::  \STACK
+\end{mathpar}
+
+Consider the example as MAP \{ PUSH int 1; ADD \}, which applies to a
+stack with a list of integers \LIST\ on top of the stack. The function
+expressed as \{ PUSH int 1; ADD \} adds the number 1 to each element
+of the list.  Let \F\ be the function that is specified by the
+sequence of instructions \I. \F\ takes an element of type int and
+returns another element of type int.
+\begin{mathpar}
+\F\ : \TINT \SRightarrow\ \TINT. \\
+\F\ \X\ = \X\ + 1 
+\end{mathpar}
+Then the result of the loop is a stack which has a integer list at the top whose symbolic value is \FMAP\ \F\ \l.
+
+\paragraph {\LOOP}
+Finally, we consider a loop instruction that may not terminate. The
+\LOOP\ \{ \I\ \} instruction applies to a stack \STACK\ with a value
+of type boolean on top. If the top element is true, the loop body (\I)
+is executed. After the body of the loop is executed, then the top of
+the stack is checked again. This process repeats until the top element
+becomes false. Once the value of the top element becomes false, the
+\LOOP\ instruction is skipped.
+\begin{mathpar}
+  \inferrule{\JTypeExpr\TEnv{\INSTRUCTION}{\TYA  \SRightarrow\ \TBOOL\ \STACKCONCAT \TYA}
+  }{
+      \JTypeExpr\TEnv{\LOOP\ \INSTRUCTION}{\TBOOL\ \STACKCONCAT \TYA\ \SRightarrow\ \TYA}
+    }
+\end{mathpar}
+
+The rules for \LOOP\ instruction.
+
+%LOOP
+\begin{mathpar}
+  \inferrule[LOOP-true]
+  {  
+  }{
+    [(\LOOP\ \INSTRUCTIONONE; \INSTRUCTION),  (\StackOne, \TBOOL)
+    \STACKCONCAT\STACK, \PREDICATE]
+    \StateTrans\
+    [(\INSTRUCTIONONE; \LOOP\ \INSTRUCTIONONE; \INSTRUCTION),
+    \STACK, \PREDICATE \wedge \StackOne]
+  }
+
+  \inferrule[LOOP-false]
+  {  
+  }{
+    [(\LOOP\ \INSTRUCTIONONE; \INSTRUCTION),  (\StackOne, \TBOOL) \STACKCONCAT\
+    \STACK, \PREDICATE]
+    \StateTrans\
+   [\INSTRUCTION, \STACK, \PREDICATE \wedge
+   (\NEG\StackOne)]
+   }
+\end{mathpar}
+%  let \STACKZERO\ =  \StackZero\ \STACKCONCAT\ \StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ \DOT \STACKCONCAT\ \StackN, where  has the boolean type.
+Let \FI\ is the function that takes the top elemement of the stack and the rest of \N\ elements of the stack, which have types \TYF, \TYS, \DOT\ \TYI, \DOT\ \TYN\ noted as \TYABAR\ and return a single type of the element \I.
+% \begin{mathpar}
+% \FZero\ : \TBOOL\ \SRightarrow\  \TBOOL. \\
+% \DOT \\
+% \FI\ : \TBOOL\ \TYF, \TYS, \DOT\ \TYI, \DOT\ \TYN\  \SRightarrow\  \TYI. \\
+% \DOT
+% \end{mathpar}
+
+% \begin{mathpar}
+% \FZero\  \StackZero\ \StackOne\ \DOT\ \StackI\ \DOT\ \StackN\ =   \StackZeroOne. \\
+% \DOT\ \\
+% \FI\  \StackZero\ \StackOne\ \DOT\ \StackI\ \DOT\ \StackN\ =   \StackIOne. \\
+% \DOT
+% \end{mathpar}
+\subsubsection{FAILWITH}
+A Michelson program can fail, employing a designated opcode. The \FAILWITH\ instruction aborts the ongoing program and reveals the top element of the stack.
+
+%FAILWITH
+\begin{mathpar}
+  \inferrule[FAILWITH]
+  {
+  }{[(\FAILWITH; \INSTRUCTION), (\StackOne,  \TY) \STACKCONCAT \STACK,  \PREDICATE] \StateTrans [\EMPTYSTACK, (\FAIL\ (\StackOne), \TFAILWITH) \STACKCONCAT\EMPTYSTACK, \PREDICATE]}
+\end{mathpar}
+
+\section{Conclusion}
+\label{sec:concl-sect-append}
+
+Symbolic execution is well known to suffer from challenges related to
+state explosion, particularly when applied to large
+systems. Fortunately, the constraints of storing and running smart
+contracts on a blockchain platform impose size limitations, making
+them manageable for symbolic execution.
+
+In future work, we want to extend XXX in two directions. 
+First, we want to address the interaction of several entrypoints by
+extending the specification language to state allowed sequences of
+contract invocations.
+
+Second, a Michelson program returns a list of instructions, which may contain
+further contract invocations. Dealing with this kind of contracts
+requires an extension to the symbolic interpreter so that a sequence
+of contract invocations can be processed in one run.
+
+\bibliography{ecoop2024}
+\end{document}
 \begin{figure}[tp]
@@
 \end{figure}
-
-Our symbolic model of a program state is a stack in which each element
-is a symbolic value, i.e., a pair consisting
-of term and its corresponding type. Terms are defined in
-Figure~\ref{fig:term}. Thus we write a stack as \STACK\ = (\TermOne,
-\TYF) \STACKCONCAT\ (\TermTwo, \TYS) \STACKCONCAT\ \DOT\ \STACKCONCAT\ 
-\EMPTYSTACK\ where \ensuremath{[\ ]} stands for the empty stack and
-\ensuremath{hd :: tl} denotes a stack with the top element as
-\ensuremath{hd} and the remaining stack as \ensuremath{tl}. 
-A selection of types is shown in Figure~\ref{fig:type}.
-
-A Michelson program is a sequence of instructions executed in a
-sequential manner. Each instruction takes, as input, the stack
-produced by the preceding instruction and modifies it for the
-subsequent one. Let \INSTRUCTION\ = \InstructionOne; \InstructionTwo;
-\DOT\  \InstructionN\ represent a sequence of instructions.
-
-During symbolic execution,  the system state evolves considering all
-values admitted by the constraints on symbolic values. Unless the
-input values are sufficiently known, symbolic execution may split the
-state, and both constraints and branching conditions are recorded as
-predicates. Let \PREDICATE\ be a path predicate that is extended at
-each conditional and expressed in conjunctive form, capturing the
-branching conditions and constraints encountered during the symbolic
-execution process. 
-\begin{definition}
-A symbolic execution state is represented by a tuple \STATE\ =
-[\INSTRUCTION, \STACK, \PREDICATE].
-A symbolic system configuration, \SYSTEM\ = \{\STATEONE, \STATETWO,
-\DOT, \STATEN \}, is a set of  states.
-\end{definition}
-
-The smart contract program takes a stack as input, consisting of a
-single pair where the first element is an input value referred to as
-parameter denoted as \VPAR\ and the second element represents the
-content of the storage space denoted as \VSTORAGE. The program
-produces a stack as output, which is a single pair. The first element
-of this pair is the list of internal operations that the program
-intends to emit (\VOPERATIONLIST), and the second element is the new
-contents of the storage space.  We define the initial stack as
-\SINIT\   = (\KPAIR\ \VPAR\ \VSTORAGE, \TPAIR\ \TYF\ \TYS)
-\STACKCONCAT\ \EMPTYSTACK, where \VPAR\ and \VSTORAGE\ denote terms
-representing the parameter and the storage, and \TYF\ and \TYS\ are
-their corresponding types. Similarly, a final stack has the form
-\SFINAL\   = (\PAIR\ \VOPERATIONLIST\ \VSTORAGE, \TPAIR\
-(\TOPERATIONLIST) \TYS) \STACKCONCAT\ \EMPTYSTACK, where
-\VOPERATIONLIST\ repesents a operation list.
-
-The initial configuration is \SYSTEMINIT\ = \{[\INSTRUCTION, \SINIT, \TRUE] \}. 
-\begin{figure}[]
-\begin{align*}
-\text{t} &::= \\
-   &\Mid\ \langle \text{variable} \rangle \\
-   &\Mid\ \langle \text{account constant} \rangle \\
-   &\Mid\ \langle \text{int constant} \rangle \\
-   &\Mid\ \langle \text{string constant} \rangle \\
-   &\Mid\ \langle \text{byte sequence constant} \rangle \\
-   &\Mid\ \UNIT \\
-   &\Mid\ \NEVER \\
-   &\Mid\ \TRUE \\
-   &\Mid\ \FALSE \\
-   &\Mid\ \PAIR\ \text{t1 t2} \\
-   &\Mid\ \LEFT\ \text{t}\\
-   &\Mid\ \RIGHT\ \text{t}\\
-   &\Mid\ \SOME\ \text{t}\\
-   &\Mid\ \NONE \\
-   &\Mid\ \text{\{t ; ... \}}\\
-   &\Mid\ \text{\{ Elt t1 t2 ; ... \}}\\
-   &\Mid\ \{ \langle\text{instruction}\rangle; ... \}   \\
-\langle \text{variable} \rangle &::= \\ 
-   &\Mid\ \VAR\\
-\langle \text{account constant} \rangle &::= \\ 
-   &\Mid\ \text{balance} \\
-   &\Mid\ \text{amount} \\
-   &\Mid\ \text{sender} \\
-   &\Mid\ \text{source} \\
-   &\Mid\ \text{now} \\
-   &\Mid\ \text{level} \\
-   &\Mid\ \text{chain-id} \\
-   &\Mid\ \text{self}  \\
-   &\Mid\ \text{self-address}  \\
-   &\Mid\ \text{total-voting-power}  \\
-   &\Mid\ \text{voting-power}  \\
-\langle\text{instruction}\rangle &::= \\
-  &\Mid\ \DROP \\
-  &\Mid\ \DROP \langle\text{natural number constant}\rangle \\
-  &\text{...}
-\end{align*}
-\caption{Terms}
-\label{fig:term}
-\end{figure}
-\subsection{Rules}
-Each instruction is defined by a rule on a system configuration. There
-are several kinds of transitions:
-\begin{enumerate}
-% \item \ExprTrans\ single-step evaluation of an expression in a system state,
-\item \StateTrans\ internal transitions of a state, which is
-  non-deterministic  as shown for loop instructions, such as \LOOP\
-  and \LOOPLEFT, 
-\item \SystemTrans\ symbolic system transitions.
-\end{enumerate}
-
-A system transition picks any state and replaces it by all distinct states that
-are reachable by internal transitions. It exploits the nondeterminism
-of the \StateTrans\ relation.
-\begin{mathpar}
-  \inferrule[]
-  { \STATE\ \StateTrans \STATEONE, \dots, \STATE\ \StateTrans \STATEN
-  }{
-  \{\STATE\} \cup \SYSTEM \SystemTrans \{ \STATEONE, \dots, \STATEN \}
-  \cup \SYSTEM}  
-\end{mathpar}
-In general, symbolic execution may generate unreachable
-states. A state is unreachable if its predicate \PREDICATE\ is  not
-satisfiable. Hence, we have a rule that drops unreachable states.
-\begin{mathpar}
-\inferrule[]
-  { \UNSAT\ \PREDICATE
-  }{
-  \{[\INSTRUCTION, \STACK, \PREDICATE]\} \cup \SYSTEM \SystemTrans \SYSTEM}
-\end{mathpar}
-The working of the symbolic interpreter may also be understood as a
-graph with symbolic states as nodes and internal transitions as
-edges. Such a representation makes it easier to perform multi-step
-subtransitions as they are required for some operations.
-
-Michelson instructions are categorized based on their functions. The
-categories include control structures, stack manipulation, arithmetic
-operations, boolean operations, cryptographic operations, and
-operations on data structures. In our model, we classify them as
-one-step, multi-step, blockchain, cryptographic, branch, and loop
-instructions. This categorization reflects how these instructions are
-handled within our specific model.
-
-\subsubsection{One-step Instructions}
-\label{sec:one-step-instr}
-One-step instructions have a localized effect, modifying the system
-state directly without branching a new state, and their execution is
-modeled with a single rule.
-% The ABS rule exemplifies such an
-% instruction, operating on the first element of the stack. This element
-% must be of type int, and the instruction returns the absolute value of
-% its argument as a natural number. To this end, the rule creates a
-% fresh variable, \X, and defines its value by a suitable predicate.
-% %ABS
-% \begin{mathpar}
-% \inferrule[ABS]
-%   { \X\ \FRESH
-%   }
-%   {
-%     [(\ABS; \INSTRUCTION), (\StackOne, \TINT) \STACKCONCAT \STACK,
-%     \PREDICATE]
-%     \StateTrans \\
-%     [\INSTRUCTION, (\X, \TNAT) \STACKCONCAT \STACK,
-%     \PREDICATE\ \wedge\ (\StackOne\ \GE\ \ZERO\ \Rightarrow\ \X\ =
-%     \StackOne) \wedge\ (\StackOne\ \LT\ \ZERO\ \Rightarrow\ \X\ = \MINUS\ \StackOne)]
-%  }
-% \end{mathpar}
-
-For example, the \COMPARE\ instruction for natural numbers compares
-the first two elements of the stack, both having a natural number
-type. It returns a result of either -1, 0, or 1 based on the
-comparison of their values. 
-% COMPARE
-\begin{mathpar}
-\inferrule[COMPARE]
-  { \X\ \FRESH
-  }
-  {
-    [(\COMPARE ; \INSTRUCTION), (\StackOne, \TNAT) \STACKCONCAT (\StackTwo, \TNAT)
-    \STACKCONCAT \STACK, \PREDICATE ]
-    \SystemTrans \\
-    [\INSTRUCTION, (\X, \TINT) \STACKCONCAT \STACK, \PREDICATE
-    \wedge\ (\StackOne\ \GT\ \StackTwo\ \Leftrightarrow\ \X\ \EQ\ \ONE)
-    \wedge\ (\StackOne\ \EQ\ \StackTwo\ \Leftrightarrow\ \X\ \EQ\ \ZERO) 
-    \wedge\ (\StackOne\ \LT\ \StackTwo\ \Leftrightarrow\ \X\ \EQ\ \MINUS \ONE)]
-    }
-\end{mathpar}
-\subsubsection{Multi-step Instructions}
-Multi-step instructions involve the execution of a sub-sequence of instructions before returning to the main execution.
-The rule below models the \EXEC\ instruction, which executes a function specified as a sequence of instructions denoted by \INSTRUCTIONONE\ in the rule.
-This instruction applies the code of the function to the first element of the stack and then places the result back into the main execution.
-\begin{mathpar}
-  \inferrule[\EXEC]
-  {
-    [\INSTRUCTIONONE, (\StackOne, \TYF) \STACKCONCAT \EMPTYSTACK, 
-    \Q]
-    \StateTrans^*
-    [ \EMPTYSTACK, (\StackOne', \TYS) \STACKCONCAT \Q']
-  }{
-     [(\EXEC; \INSTRUCTION),   (\{\INSTRUCTIONONE\}, \TYF\ \rightarrow\ \TYS) \STACKCONCAT
-    (\StackOne, \TYF) \STACKCONCAT \STACK, \PREDICATE \wedge \Q] 
-    \StateTrans \
-    [ \INSTRUCTION, (\StackOne', \TYS) \STACKCONCAT \STACK,
-    \PREDICATE \wedge \Q']}
-\end{mathpar}
-
-The \DIP\ \N\ instruction skips over the first \N\ elements of a
-stack, applies the sequence of instructions denoted as
-\INSTRUCTIONONE\ to the remaining part of the stack, modifies a part
-of the predicate and subsequently pushes the result back into the main
-execution. 
-%DIP n
-\begin{mathpar}
-\inferrule[\DIP\ \N]
-  { 
-     \FLEN(\A) \EQ\ \N \\ [\INSTRUCTIONONE,  \B, \Q]
-    \StateTrans^*
-    [\EMPTYSTACK,  \B_1, \Q']
-  }
-  {[(\DIP\ \N\ \INSTRUCTIONONE; \INSTRUCTION), \A\ \At\ \B, \PREDICATE \wedge \Q] \StateTrans 
-[\INSTRUCTION, \A\ \At\ \B_1, \PREDICATE \wedge \Q']}
-\end{mathpar}
-\subsubsection{Blockchain Instructions}
- Blockchain instructions make implicit use of data from the current
- state of the blockchain (the context), from the transaction that
- triggered the contract, and from the block containing this
- transaction. As these values are constant during the execution of a
- contract, we model them as fixed variable. For example, the \AMOUNT\
- instruction pushes the amount of tokens on the stack that the
- contract received from its caller. This amount is modeled as the
- fixed variable \CAMOUNT, which has type \TMUTEZ.
-
-\begin{mathpar}
-\inferrule[AMOUNT]
-  {
-  }
-  {[(\AMOUNT; \INSTRUCTION), \STACK, \PREDICATE] \StateTrans \
-[\INSTRUCTION, (\CAMOUNT, \TMUTEZ) \STACKCONCAT \STACK, \PREDICATE]}
-\end{mathpar}
-
-% \subsubsection{Cryptographic Instructions}
-% Cryptographic instructions in Michelson utilize built-in functions that manage cryptographic features.
-These functions are symbolically modeled in our framework, specifying their inputs and outputs.
-For instance, the instruction \SHA\ computes the cryptographic hash of the top of the stack using the SHA-256 cryptographic hash function.
-The function SHA-256 is symbolically represented as the function  \FSHA\  that takes an input of type \TBYTE\ and returns another byte value, constrained to a length of 256.
-% %HASH-KEY
-% \begin{mathpar}
-% \inferrule[\SHA]
-%   {
-%   }
-%   {[(\SHA; \INSTRUCTION), (\StackOne, \TBYTE) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \
-% [\INSTRUCTION, (\X, \TBYTE) \STACKCONCAT\STACK, \PREDICATE \Wedge\ (\X\ \EQ\ \FSHA(\StackOne))]}
-% \end{mathpar}
-\subsubsection{Branch Instructions}
-The simplest conditional in Michelson language is the \IF\ \{
-\INSTRUCTIONONE\ \} \{ \INSTRUCTIONTWO\  \} instruction. It expects
-and consumes a boolean value at the top of the stack. If the boolean
-is True, it executes \INSTRUCTIONONE; otherwise, it executes
-\INSTRUCTIONTWO. 
-%IF
-\begin{mathpar}
-  \inferrule[IF-true]
-  {  
-  }{
-    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
-    \StateTrans\
-    [\INSTRUCTIONONE, \STACK, \PREDICATE\ \Wedge\ \StackOne]
-  }
-
-  \inferrule[IF-false]
-  {  
-  }{
-    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
-    \StateTrans\
-   [\INSTRUCTIONTWO, \STACK, \PREDICATE\ \Wedge\ \NEG\
-   \StackOne]
- }
-\end{mathpar}
-
-Another branch instruction is the IF-LEFT instruction, which is used
-for conditional execution based on the left or right branch of a sum
-type.  
-%IF-LEFT-LEFT
-\begin{mathpar}
-  \inferrule[IF-LEFT-left]
-  {  \X\ \FRESH
-  }{
-    [(\IFLEFT\ \INSTRUCTIONONE\ \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]
-    \StateTrans \
-    [(\INSTRUCTIONONE; \INSTRUCTION), (\X, \TYF) \STACKCONCAT\STACK,
-    \PREDICATE \wedge (\StackOne\ \EQ\ \LEFT\ \X)]
-  }
-\end{mathpar}
-
-%IF-LEFT-RIGHT
-\begin{mathpar}
-  \inferrule[IF-LEFT-right]
-  {    \X\ \FRESH
-  }{
-    [(\IFLEFT\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TOR\ \TYF\ \TYS) \STACKCONCAT \STACK, \PREDICATE]
-    \StateTrans \
-    [(\INSTRUCTIONTWO; \INSTRUCTION), (\X, \TYS) \STACKCONCAT\STACK, \PREDICATE \wedge (\StackOne\ \EQ\ \RIGHT\ \X))]
-  }
-\end{mathpar}
-These above rules define the behavior of the \IFLEFT instruction. The
-rule applies when the top element of the stack is a tagged union of
-type \TOR\ \TYF\ \TYS (either of type \TYF\ or \TYS), and the \IFLEFT
-instruction is followed by instructions \INSTRUCTIONONE\ and
-\INSTRUCTIONTWO. The first rule adds the condition that the top
-element of the stack is of the form Left \X\ (indicating the left
-branch of the union), it transitions to execute the instructions
-\INSTRUCTIONONE\ with the stack modified accordingly and the predicate
-is updated to include the condition that the top element of the stack
-is equal to Left \X. Similarly, the second rule handles the case Right\
-\X, mutatis mutandis.
-
-\subsubsection{Loop Instructions}
-Michelson supports a number of loop instructions, including
-\LOOP\ and \LOOPLEFT, that  check the loop condition by examining the
-top of the stack. These loop instructions may not terminate, just like while-loops. There are further loop instructions, like \ITER\ and
-\MAP, specialized to traverse data structures like lists, sets, and maps. There are also
-some instructions that implicitly require looping like \CONCAT, and
-\SIZE. The latter kinds of loop instructions do always terminate.
-
-% Michelson, similar to other programming languages, classifies loop instructions into two main types:
-% \begin{itemize}
-% \item \KFOR\ loops: These are sequence-based loops, exemplified by \ITER, \MAP, \CONCAT\ and \SIZE.
-% \item \KWHILE\ loops: These are predicates-based loops, illustrated by \LOOP and \LOOPLEFT.
-% \end{itemize}
-% To illustrate the structures of  loops, we can draw a parallel with OCaml syntax as in Listing \ref{list:while-loop}.
-
-% \begin{lstlisting}[caption={While loop.},label=list:while-loop,captionpos=t,float,abovecaptionskip=-\medskipamount]
-% while <loop_condition> do
-%    <loop_body>
-% done
-% \end{lstlisting}
-% This \KWHILE\  loop structure involves a loop condition that is evaluated at the beginning of each iteration.
-If the condition holds true, the loop body is executed, and the process repeats until the condition becomes false.
-In Michelson, this pattern is evident in instructions like LOOP and LOOP-LEFT, which rely on predicate-based conditions for their iteration: \lstinline/LOOP {<loop-body>}/.
-
-% Additionally, Michelson features a \KFOR\ loop, where the index runs from the initial value to the final value as in Listing \ref{list:for-loop}.
-The \KFOR\ loop is represented by the ITER instruction: \lstinline/ITER {<loop-body>}/
-
-% \begin{lstlisting}[caption={For loop.},label=list:for-loop,captionpos=t,float,abovecaptionskip=-\medskipamount]
-% for index = <initial_value> to <final_value> do
-%   <loop_body>
-% done
-% \end{lstlisting}
-
-% The fundamental concept underlying the definition of a loop is its loop condition, the predicate that must hold true for the loop to continue execution.
-In the case of \KWHILE\ loops, the  loop condition is explicitly embedded in the loop syntax.
-However, for the \KFOR\  loops, the loop condition is more implicit.
-A \KFOR\  loop can be rewritten as a  \KWHILE\ loop to make the  loop condition explicit as showned in Listing \ref{list:express-for-using-while-loop}.
-% \begin{lstlisting}[caption={Expressing a \KFOR\ loop using a \KWHILE\ loop.},label=list:express-for-using-while-loop,captionpos=t,float,abovecaptionskip=-\medskipamount]
-% index = 0
-% while index < length(sequence) do
-%   <loop_body>
-%   index += 1
-% done
-% \end{lstlisting}
-% Here, the implicit loop condition asserts that the index of the sequence element is less than the length of the sequence.
-
-%  do not explicitly contain their loop conditions. Instead, the  loop condition is established:
-% \begin{itemize}
-%  \item In the expressions preceding the loop for the first time entering the loop.
-%  \item Inside the loop body for subsequent iterations.
-% \end{itemize}
-
-% The loop instructions are applied to a stack, and the loop condition is checked with the top element of the stack.
-For a  \KWHILE\ loop the top element of the stack must have a boolean value and for the \KFOR\  loop, it must have a sequence data type, such as list, set or map.
-If we denote the function to retrieve the top element of a stack as "\FPOP," the  \KWHILE\ loop instruction can be expressed as shown in Listing \ref{list:express-for-using-ocaml} and and the \KFOR\  loop is expressed as Listing \ref{list:express-while-using-ocaml}.
-% \begin{lstlisting}[caption={Expressing Michelson \KWHILE\ loop using  Ocaml syntax.},label=list:express-for-using-ocaml,captionpos=t,float,abovecaptionskip=-\medskipamount]
-% while pop(S) do
-%    loop_body
-% done
-% \end{lstlisting}
-
-% \begin{lstlisting}[caption={Expressing Michelson  \KFOR\ loop using Ocaml syntax.},label=list:express-while-using-ocaml,captionpos=t,float,abovecaptionskip=-\medskipamount]
-% index = 0
-% while index < length(pop(S)) do
-%   <loop_body>
-%   index += 1
-% done
-% \end{lstlisting}
-
-\paragraph {\ITER}
-Lets us consider the \ITER\ instruction, which iterates over a
-list.\footnote{\ITER\ can also iterate over sets and maps, but the
-  details are very similar to the list case and hence omitted.} The
-corresponding typing rule is as follows: 
-\begin{mathpar}
-  \inferrule{\JTypeExpr\TEnv{\INSTRUCTION}{\TY \STACKCONCAT \TYA\ \SRightarrow\ \TYA}
-  }{
-      \JTypeExpr\TEnv{\ITER\ \INSTRUCTION}{\TYLIST\ \TY \STACKCONCAT \TYA\ \SRightarrow\ \TYA}
-    }
-\end{mathpar}
-This typing rule ensures that if the loop body \INSTRUCTION\ has the type \TY\ \STACKCONCAT \TYA\ \SRightarrow\ \TYA, then the entire \ITER\ instruction, when applied to a stack with the top element of type \TY\ \TYLIST\ and the rest of the stack of type \TYA, produces a result stack of type \TYA.
-
-We consider rules for symbolic execution of the \ITER\ instruction.
-%%ITER
-\begin{mathpar}
-  \inferrule[ITER-empty]
-  {  
-  }{
-    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans\ [\INSTRUCTION, \STACK,  \PREDICATE\ \Wedge\  (\StackOne\ \EQ\ \EMPTYLIST)]
-  }
-\end{mathpar}
-This rule handles the case where the list is empty, so that the \ITER\
-instruction just skips. The rule transitions to the next instruction
-after popping the empty list from the stack. We register emptiness in
-the predicate \PREDICATE\ $\Wedge$ (\StackOne \EQ \EMPTYLIST). 
-\begin{mathpar}
-  \inferrule[ITER-nonempty]
-  { \HEAD, \STAIL\ \FRESH \\
-    [\ITER,  (\HEAD, \TY) \STACKCONCAT\STACK, 
-    \PREDICATE]
-    \StateTrans^*
-    [ \EMPTYSTACK,  \STACK', \PREDICATE']
-  }{
-    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\
-    \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \\
-    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\STAIL, \TYLIST)\
-    \STACKCONCAT\STACK',  \PREDICATE' \Wedge  (\StackOne\
-    \EQ\ \{\HEAD; \STAIL \}) ] 
-  }
-\end{mathpar}
-The next rule handles the case where the list is non-empty. It
-symbolically executes the instructions \INSTRUCTIONONE\ within the
-\ITER\ block with the head of the list (\HEAD) replacing the list. The resulting state transitions to a
-new stack (\STACK') and an updated predicate (\PREDICATE' $\Wedge$
-(\StackOne \EQ \{\HEAD;\STAIL\})), where \STAIL represents the rest of the list. 
-These rules capture the symbolic execution behavior of the \ITER\
-instruction, considering both the cases where the list is empty and
-non-empty.
-
-If the initial list is concrete, the instruction terminates as it simply loops over the
-elements of the list. But how do we deal with \ITER\ if the list is a
-symbolic value?
-One solution could involve running
-the loop for a number of times to obtain the symbolic value. However,
-we can defer that decision by exploiting features of Z3.
-
-Let us again consider the instruction \ITER\
-\{\INSTRUCTION\}. The sequence of instructions \INSTRUCTION\ denotes
-the loop body. In fact, \INSTRUCTION\ can be considered a function of
-type (\TY\ \STACKCONCAT \TYA\ \SRightarrow\ \TYA) applied to a stack
-of type \TY\ \STACKCONCAT \TYA,
-resulting in a stack of type \TYA. If the first element of
-the stack is a list of the form \LIST\ = $x_1 \STACKCONCAT x_2 \STACKCONCAT
-\dots x_m \STACKCONCAT  [\ ]$, and the rest of the stack is \STACKZERO\ =
-\StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ ... \STACKCONCAT\
-\StackN. Then the \ITER\ \{\INSTRUCTION\} instruction applies a 
-function, sat \F, represented by \INSTRUCTION\ \M\ times to the stack, once
-with each element $x_i$ on top of the stack. The result after 
-the first iteration is \STACKONE\ = \StackOneOne\  \STACKCONCAT\
-\StackTwoOne\ \STACKCONCAT\ ... \STACKCONCAT\ \StackNOne = \F\ $x_1$
-\STACK. Then \STACKTWO = \F\ $x_1$ \STACKONE, and so on.
-% Typing of \ITER\ enforces that
-% the type of the result stack is the same as the previous
-% stack.
-% Call the function \FI\ that takes the head \HEADZERO\
-% of the list and all elements of  the stack \STACKZERO\ as  \StackOne,
-% \StackTwo, ... \StackN, given  as \STACKZEROBAR\ and returns the
-% i-element  \StackIOne\ of the stack \STACKONE. The function
-% representing \INSTRUCTION\  is defined as the vector of these subfunctions
-% \FI.  
-% \begin{mathpar}
-% \StackOneOne\ = \FOne\  \HEADZERO\ \STACKZEROBAR \\
-% \StackTwoOne\ = \FTwo\  \HEADZERO\ \STACKZEROBAR \\
-% ...\\
-% \StackNOne\ = \FN\  \HEADZERO\ \STACKZEROBAR 
-% \end{mathpar}
-% When the next loop is performed, the same function \FI\ is applied to the next element of the list and all element of the the stack \STACKONE\ and we get the \StackITwo.
-In the same way, the the loop is performed for \J\ time, we get the stack \STACKJ\ as follows:
-
-% \begin{mathpar}
-% \StackOneJ\ = \FOne\  \HEADJMINUS\ \STACKJMINUSBAR \\
-% \StackTwoJ\ = \FTwo\  \HEADJMINUS\ \STACKJMINUSBAR \\
-% ...\\
-% \StackNJ\ = \FN\  \HEADJMINUS\ \STACKJMINUSBAR 
-% \end{mathpar}
-
-We conclude, we can represent the value of the stack after running the
-instruction \ITER\  as the result of a fold function that applies the
-function \F\ to the list. This representation is advantageous because
-Z3 can handle functions defined using \FOLD\ directly.
-% \begin{mathpar}
-% \StackOneM\ = \FOLD\ \FOne\ \STACKZEROBAR\  \LIST\  \\
-% \StackTwoM\ = \FOLD\ \FTwo\  \STACKZEROBAR\ \LIST\  \\
-% ...\\
-% \StackNM\ = \FOLD\ \FN\ \STACKZEROBAR\  \LIST
-% \end{mathpar}
-
-% Generally, we can represent the sequence of instructions \INSTRUCTION\ as the function \F\ that takes an element of type \TY\ of a list \LIST\ and a  stack \STACK\ of type \TYA\ and returns a stack of type \TYA.
-
-\begin{mathpar}
-\STACK'\ =  \FOLD\ \F\ \STACK\ \LIST
-\end{mathpar}
-
-For example, consider \ITER\ \{\ADD\} that applies to a stack \STACK\ that has a integer list as the top element and the rest \STACKZERO\ = \StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ ...
-\STACKCONCAT\ \StackN.
-\begin{mathpar}
-\ITER\ \{ \ADD\ \} \Slash \LIST\ \STACKCONCAT\ \STACKZERO
-\end{mathpar}
-The type of the \ADD\ instruction indicates that the top element of
-the stack \STACKZERO\ namely \StackOne, has type integer list. For
-each iteration, the \ADD\ instruction adds another element of the list
-to the top element of the stack and then the rest of the stack is
-unchanged.  Let us build the function \FOne\ with the assumption that the list \LIST\ is not empty as \{\HEAD; \STAIL \}, 
-\begin{mathpar}
-\FOne\ (\HEAD, \StackOne,  \StackTwo, \DOT, \StackN) = \HEAD\ + \StackOne\\
-\FTwo\ (\HEAD, \StackOne,  \StackTwo, \DOT, \StackN) = \StackTwo\\
-... \\
-\FN\ (\HEAD, \StackOne,  \StackTwo, \DOT, \StackN) = \StackN\\
-\end{mathpar}
-
-So \F\ is the function that takes an integer and a stack starting with
-an integer as inputs and returns a stack of the same length with the
-integer added to the top of the stack
-\begin{mathpar}
-\FOne\ (\X, \XOne \STACKCONCAT \XTwo \STACKCONCAT \DOT \XN
-\STACKCONCAT $[\ ]$) = \X\ + \XOne
-\end{mathpar}
-But as \XTwo\STACKCONCAT \DOT \STACKCONCAT \XN\ do not participate in
-the calculation, we can simplify the function to 
-\begin{mathpar}
-\FOne\ (\X, \XOne) = \X\ + \XOne
-\end{mathpar}
-The symbolic value of the top element of the stack after the \ITER\ \{\ADD\} loop is
-\begin{mathpar}
-\FOLD\ \FOne\ \StackOne\ \LIST
-\end{mathpar}
-As the loop body does not change the rest of the stack, we can omit
-the identity functions on the remaining components in an implementation.
-% \begin{mathpar}
-% \FI\ (\X, \XOne, \DOT, \XI, \DOT, \XN) = \XI
-% \end{mathpar}
-
-The \FOLD\ function also can be used to express the result of other
-loop instructions, such as CONCAT and SIZE, symbolically.
-
-\paragraph {\MAP}
-
-% The \ITER\ instruction and some other can be symbolicly implemented
-% using \FOLD\ function applying on the sequance data structures as
-% list, set and map. 
-Next, we consider the \MAP\ instruction. While any \MAP\ instruction
-can be transformed to an \ITER\ instruction, it is more efficient to
-use a map function for the symbolic result of the instruction.
-
-Again we consider
-the  \MAP\ \{\I\}   instruction for lists, which operates on a stack
-\STACK, whose the top element has type \TY\ \TYLIST, and the rest has
-type \TYA. The instruction returns a stack of type (\TY\ \TYLIST) \STACKCONCAT
-\TYA. The corresponding typing rule is as follows: 
-\begin{mathpar}
-  \inferrule{\JTypeExpr\TEnv{\INSTRUCTION}{\TY  \SRightarrow\ \TY'}
-  }{
-      \JTypeExpr\TEnv{\MAP\ \INSTRUCTION}{\ \TY\ \TYLIST\ \STACKCONCAT \TYA\ \SRightarrow\ \TY'\ \TYLIST\  \STACKCONCAT \TYA}
-    }
-\end{mathpar}
-This typing rule ensures that if the loop body (\INSTRUCTION) has the
-type \TY\ \SRightarrow\ $\TY'$, then the entire \ITER\ instruction
-produces a result stack of type $\TY'$ \ \TYLIST\ \STACKCONCAT \TYA.
-
-The execution rules are similar in style to the ones for \ITER.
-%MAP
-\begin{mathpar}
-\inferrule[MAP-empty]
-  {
-  }
-  {[(\MAP\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \ 
-[\INSTRUCTION, (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ (\StackOne\ \EQ\ \EMPTYLIST)]}
-\end{mathpar}
-
-\begin{mathpar}
-\inferrule[MAP-nonempty]
-  {
-  [\INSTRUCTIONONE, (\HEAD, \TY) \STACKCONCAT\EMPTYSTACK, Q1]
-    \StateTrans^*
-    [\EMPTYSTACK,  (\PHEAD, \TY) \STACKCONCAT\EMPTYSTACK , Q1'] \\  [\MAP\ \INSTRUCTIONONE, (\{\TAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK , Q2]
-    \StateTrans^*
-    [\EMPTYSTACK,  (\{\PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\EMPTYSTACK , Q2']
-  }
-  {[(\MAP\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1 \Wedge\ Q2 ] \StateTrans  \\
-[\INSTRUCTION, (\{\PHEAD; \PTAIL\}, \TYLIST\ \TY) \STACKCONCAT\STACK, \PREDICATE\ \Wedge\ Q1' \Wedge\ Q2'  \Wedge\ (\StackOne \EQ\ \{\HEAD; \TAIL\})]}
-\end{mathpar}
-Let consider how we can avoid the symbolic iteration.
-The list of instructions \INSTRUCTIONONE\ can be represented as a function \F\ that takes a input of type \TY\ and returns an output of type $\TY'$.
-\begin{mathpar}
-\F\ : \TY\ \SRightarrow\ \TY'
-\end{mathpar}
-The \MAP\ instruction traverses the list \LIST\ by applying the
-function \F\ to each element. Symbolically the result of the \MAP\
-\{\INSTRUCTION\} to the list \LIST\ is the result of a map function
-that applies the function \F\ that represent of the sequence of
-instructions \I\ to the list.
-
-\begin{mathpar}
-\MAP\ \{\INSTRUCTION\} \Slash\ \LIST\ :: \STACK\ \SRightarrow\ (\FMAP\ \F\ \LIST) ::  \STACK
-\end{mathpar}
-
-Consider the example as MAP \{ PUSH int 1; ADD \}, which applies to a
-stack with a list of integers \LIST\ on top of the stack. The function
-expressed as \{ PUSH int 1; ADD \} adds the number 1 to each element
-of the list.  Let \F\ be the function that is specified by the
-sequence of instructions \I. \F\ takes an element of type int and
-returns another element of type int.
-\begin{mathpar}
-\F\ : \TINT \SRightarrow\ \TINT. \\
-\F\ \X\ = \X\ + 1 
-\end{mathpar}
-Then the result of the loop is a stack which has a integer list at the top whose symbolic value is \FMAP\ \F\ \l.
-
-\paragraph {\LOOP}
-Finally, we consider a loop instruction that may not terminate. The
-\LOOP\ \{ \I\ \} instruction applies to a stack \STACK\ with a value
-of type boolean on top. If the top element is true, the loop body (\I)
-is executed. After the body of the loop is executed, then the top of
-the stack is checked again. This process repeats until the top element
-becomes false. Once the value of the top element becomes false, the
-\LOOP\ instruction is skipped.
-\begin{mathpar}
-  \inferrule{\JTypeExpr\TEnv{\INSTRUCTION}{\TYA  \SRightarrow\ \TBOOL\ \STACKCONCAT \TYA}
-  }{
-      \JTypeExpr\TEnv{\LOOP\ \INSTRUCTION}{\TBOOL\ \STACKCONCAT \TYA\ \SRightarrow\ \TYA}
-    }
-\end{mathpar}
-
-The rules for \LOOP\ instruction.
-
-%LOOP
-\begin{mathpar}
-  \inferrule[LOOP-true]
-  {  
-  }{
-    [(\LOOP\ \INSTRUCTIONONE; \INSTRUCTION),  (\StackOne, \TBOOL)
-    \STACKCONCAT\STACK, \PREDICATE]
-    \StateTrans\
-    [(\INSTRUCTIONONE; \LOOP\ \INSTRUCTIONONE; \INSTRUCTION),
-    \STACK, \PREDICATE \wedge \StackOne]
-  }
-
-  \inferrule[LOOP-false]
-  {  
-  }{
-    [(\LOOP\ \INSTRUCTIONONE; \INSTRUCTION),  (\StackOne, \TBOOL) \STACKCONCAT\
-    \STACK, \PREDICATE]
-    \StateTrans\
-   [\INSTRUCTION, \STACK, \PREDICATE \wedge
-   (\NEG\StackOne)]
-   }
-\end{mathpar}
-%  let \STACKZERO\ =  \StackZero\ \STACKCONCAT\ \StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ \DOT \STACKCONCAT\ \StackN, where  has the boolean type.
-Let \FI\ is the function that takes the top elemement of the stack and the rest of \N\ elements of the stack, which have types \TYF, \TYS, \DOT\ \TYI, \DOT\ \TYN\ noted as \TYABAR\ and return a single type of the element \I.
-% \begin{mathpar}
-% \FZero\ : \TBOOL\ \SRightarrow\  \TBOOL. \\
-% \DOT \\
-% \FI\ : \TBOOL\ \TYF, \TYS, \DOT\ \TYI, \DOT\ \TYN\  \SRightarrow\  \TYI. \\
-% \DOT
-% \end{mathpar}
-
-% \begin{mathpar}
-% \FZero\  \StackZero\ \StackOne\ \DOT\ \StackI\ \DOT\ \StackN\ =   \StackZeroOne. \\
-% \DOT\ \\
-% \FI\  \StackZero\ \StackOne\ \DOT\ \StackI\ \DOT\ \StackN\ =   \StackIOne. \\
-% \DOT
-% \end{mathpar}
-\subsubsection{FAILWITH}
-A Michelson program can fail, employing a designated opcode. The \FAILWITH\ instruction aborts the ongoing program and reveals the top element of the stack.
-
-%FAILWITH
-\begin{mathpar}
-  \inferrule[FAILWITH]
-  {
-  }{[(\FAILWITH; \INSTRUCTION), (\StackOne,  \TY) \STACKCONCAT \STACK,  \PREDICATE] \StateTrans [\EMPTYSTACK, (\FAIL\ (\StackOne), \TFAILWITH) \STACKCONCAT\EMPTYSTACK, \PREDICATE]}
-\end{mathpar}
-
-\section{Conclusion}
-\label{sec:concl-sect-append}
-
-Symbolic execution is well known to suffer from challenges related to
-state explosion, particularly when applied to large
-systems. Fortunately, the constraints of storing and running smart
-contracts on a blockchain platform impose size limitations, making
-them manageable for symbolic execution.
-
-In future work, we want to extend XXX in two directions. 
-First, we want to address the interaction of several entrypoints by
-extending the specification language to state allowed sequences of
-contract invocations.
-
-Second, a Michelson program returns a list of instructions, which may contain
-further contract invocations. Dealing with this kind of contracts
-requires an extension to the symbolic interpreter so that a sequence
-of contract invocations can be processed in one run.
-
-\bibliography{}
-\end{document}

### 2024-01-16 papers/static-checker/ecoop2024/ecoop2024.tex
add related work section

@@
 Formal verification is a requirement for all but the simplest smart
-contracts on the blockchain. We developed XXX, a tool that is geared towards contracts
+contracts on the blockchain. We developed SCV, a tool that is geared towards contracts
 implemented in Michelson, the smart contract language of the Tezos
@@
 
-We report the foundations of the design and implementation of XXX and
+We report the foundations of the design and implementation of SCV and
 conduct two case studies that demonstrate the expressiveness of our tool.
@@
 Formal verification can guarantee the correctness of smart contracts.
-To this end we have developed XXX, a formal
-verification tool for smart contracts on the Tezos blockchain, written in
-Michelson, although our design is widely applicable. XXX relies on
+To this end we have developed SCV, a formal
+verification tool for smart contracts on the Tezos blockchain \cite{tezos-whitepaper}, written in
+Michelson \cite{michelson}, although our design is widely applicable. SCV relies on
 symbolic execution backed by an SMT solver to simulate the
 implementation of the smart contract language, helping to detect 
-subtle errors. In addition, XXX comes with a domain-specific language that
+subtle errors. In addition, SCV comes with a domain-specific language that
 allows users to precisely specify contract properties.
@@
 uncovering hidden errors, and validating user-defined properties.
-XXX provides a comprehensive solution to
+SCV provides a comprehensive solution to
 mitigate potential pitfalls in blockchain-based applications.
@@
     pre-condition := auction_open 
-       && Amount > Balance - Amount
+       && Amount > pre_Balance 
        && get_contract (unit, highest_bidder) = 
@@
        && post_Balance = Amount 
-       && transfer_token (Unit, Balance - Amount, c) ;
+       && transfer_token (Unit, Old_Balance, c) ;
 \end{lstlisting}
@@
 postcondition refers to components of the final storage by prefixing
-\lstinline|post_| to their name. The variables \lstinline|Balance|,
+\lstinline|post_| to their name. The variables
 \lstinline|Amount|, and \lstinline|Sender| correspond to the values
-returned by the like-named Michelson instructions that return the
-current balance of the contract, the amount transferred with the call,
-and the address of the caller (sender).
+returned by the like-named Michelson instructions that return, the amount transferred with the call, and the address of the caller (sender).
+The variables \lstinline|pre_Balance| and \lstinline|post_Balance| represent the previous balance of the contract right before and after the call, respectively.
+The current balance of the contract returned by the instruction \BALANCE\ includes \lstinline|pre_Balance| and the \lstinline|Amount|.
 
@@
 \item Design and implementation of the smart contract specification
-  language XXX.
+  language SCV.
 \item Design and implementation of a symbolic interpreter for a
   significant subset of Michelson.
-\item Two case studies where we apply XXX to verify real life smart
+\item Two case studies where we apply SCV to verify real life smart
   contracts deployed on the Tezos blockchain:
@@
 
-\atha{Add citations/references to the high-level languages.}
 While contracts may be implemented directly in Michelson, it can also
 be used as a compilation target. Indeed, several high-level languages
-such as LIGO, SmartPy, and Liquidity have been created. These
-languages provide a more readable syntax, resembling popular
+such as LIGO \cite{ligo}, SmartPy \cite{smartpy}, and Liquidity \cite{liquidity} have been created. These languages provide a more readable syntax, resembling popular
 programming languages, allowing developers to write Tezos smart
@@
    \Mid\ \text{string}
-   \Mid\ \text{chain-id}
-   \Mid\ \text{bytes}
-   \Mid\ \text{mutez} \\
-   &\Mid\ \text{key-hash}
+   \Mid\ \text{chain-id} \\
+   & \Mid\ \text{bytes}
+   \Mid\ \text{mutez} 
+   \Mid\ \text{key-hash}
    \Mid\ \text{key}
    \Mid\ \text{signature}
-   \Mid\ \text{timestamp}
-   \Mid\ \text{address} \\
-   &\Mid\ \text{option}\ \textbf{cpt}
+   \Mid\ \text{timestamp} \\
+   & \Mid\ \text{address} 
+   \Mid\ \text{option}\ \textbf{cpt}
    \Mid\ \text{or}\ \textbf{cpt}\ \textbf{cpt}
@@
    \Mid\ \text{set}\ \textbf{cpt} 
-   \Mid\ \text{operation} \\
-   &\Mid\ \text{contract}\ \text{T}
-   \Mid\ \text{ticket}\ \textbf{cpt} 
-   \Mid\ \text{pair}\ \text{T}\ \text{U}
+   \Mid\ \text{operation} 
+   \Mid\ \text{contract}\ \text{T} \\
+  & \Mid\ \text{pair}\ \text{T}\ \text{U}
    \Mid\ \text{or}\ \text{T}\ \text{U}
-   \Mid\ \text{lambda}\ \text{T}\ \text{U} \\
-   &\Mid\ \text{map}\ \textbf{cpt}\ \text{T}
+   \Mid\ \text{lambda}\ \text{T}\ \text{U} 
+   \Mid\ \text{map}\ \textbf{cpt}\ \text{T}
    \Mid\ \text{big-map}\ \textbf{cpt}\ \text{T}
-   \Mid\ \text{chest} 
-   \Mid\ \text{chest-key}
 \end{align*}
 \caption{Types}
-\label{fig:type}
+\label{fig:types}
 \end{figure}
@@
 \textbf{c} & ::= 
-    \text{Balance}
+    \text{pre\_Balance}
    \Mid \text{post\_Balance}
@@
    &\Mid \text{Chain\_id}
-   \Mid \text{Self\_address}
-   \Mid \text{Total\_voting\_power}
-   \Mid \text{Voting\_power} \\
+   \Mid \text{Self\_address}\\
 \textbf{t} &::= 
@@
 \textbf{e} & :: = \textbf{t}  \Mid \textbf{e} \text{ + } \textbf{e}\Mid \textbf{e} \text{ - } \textbf{e}  \Mid \textbf{e} \text{ * } \textbf{e} \Mid \textbf{e} \text{ / } \textbf{e} \Mid \textbf{e} \text{ \% } \textbf{e} \Mid \textbf{e} \text{ rem } \textbf{e} \\
-& \Mid \text{transfer\_token} (\textbf{e}, \textbf{e}, \textbf{e}) 
- \Mid \text{get\_map} (\textbf{e}, \textbf{e}) 
- \Mid \text{get\_big\_map} (\textbf{e}, \textbf{e}) 
- \Mid \text{check\_mem} (\textbf{e}, \textbf{e})  \\
-& \Mid \text{get\_contract} (\textbf{e}, \textbf{e})  
- \Mid \text{contain} (\textbf{e}, \textbf{e})  
- \Mid \text{get\_substring} (\textbf{e}, \textbf{e}, \textbf{e})  
- \Mid \text{check\_sig} (\textbf{e}, \textbf{e}, \textbf{e})  \\
+& 
+ \Mid \text{get\_map} (\textbf{e1}, \textbf{e2}) 
+ \Mid \text{get\_big\_map} (\textbf{e1}, \textbf{e2})  \\
+ &\Mid \text{get\_contract} (\textbf{e1}, \textbf{e2})   
+ \Mid \text{get\_substring} (\textbf{e1}, \textbf{e2}, \textbf{e3})   \\
 & \Mid \text{abs} (\textbf{e})  
- \Mid \text{is\_nat} (\textbf{e})  
  \Mid \text{to\_int} (\textbf{e})  
@@
 \Mid \textbf{e} \text{ <= } \textbf{e} \\
-&\Mid \text{forall} (\textbf{e}, \textbf{p})
-\Mid \text{exist} (\textbf{e}, \textbf{p})
-\Mid \textbf{p} \text{ and } \textbf{p}\Mid \textbf{p} \text{ or } \textbf{p}  \Mid \textbf{p} \text{ nor } \textbf{p} \Mid  \text{ not } \textbf{p} \Mid \textbf{p} \text{ imply } \textbf{p} \\
+& \Mid \text{transfer\_token} (\textbf{e1}, \textbf{e2}, \textbf{e3})  
+ \Mid \text{is\_nat} (\textbf{e})  
+ \Mid \text{contain} (\textbf{e1}, \textbf{e2}) \\
+& \Mid \textbf{p} \text{ and } \textbf{p}\Mid \textbf{p} \text{ or } \textbf{p}  \Mid \textbf{p} \text{ nor } \textbf{p} \Mid  \text{ not } \textbf{p} \Mid \textbf{p} \text{ => } \textbf{p} \\
 \end{align*}
@@
 \label{sec:simple-contracts}
-
 Listing~\ref{lst:smart-contract-property-specification} shows the
@@
 and output fields, the input and output terms are specified.
-\atha{What terms are supported? terms are not explained!}
-Since
-Michelson operates on a stack, we assume that the stack has only one
+The input and output terms represent Michelson terms, which can be either concrete values or symbolic values, including variables.
+The terms are specified using the syntax defined in Fig.
+\ref{fig:syntax-terms-predicates}.
+A term \textbf{t} comprises constants of the sort \text{nat} (natural number), \text{int} (integer), \text{string} (string), and \text{b} (bytes) along with their respective types.
+As a syntactic sugar, the type can be omitted except for the type \text{nat} to distinguish it from integer numbers.
+It also encompasses all blockchain constants \textbf{c}, such as Amount and Sender.
+When a variable appears for the first time, it must be accompanied by its corresponding type declaration.
+Subsequent mentions can omit the type declaration.
+The language supports essential Michelson types, as shown in Fig.
+\ref{fig:types}, where \textbf{cpt} denotes comparable types.
+The types include basic data types such as integer, string, list, set, pair, option and map.
+Additionally, there are some typical types related to the blockchain, such as \text{mutez} and \text{contract T}, representing types for tokens and smart contracts on the Tezos blockchain, respectively.
+
+Since Michelson operates on a stack, we assume that the stack has only one
 element, as specified in the input term. Similarly, the output
 stack is assumed to be a stack with only one element, which is
-specified in the output field. Thus, the syntax allows us to specify
-incomplete contracts, too.
-\pt{I disagree (though it would be a useful feature). To this end, there should be terms to cover stacks
-  with more than one element. As it stands, the input term can only
-speak about the top of the stack and the output term only about the
-second component of the top of the stack, which is assumed to be a
-pair.\\
-Moreover, a specification might want to say something about the list
-of operations, too, e.g., that tokens are transferred to some address.}
-
+specified in the output field. The syntax allows us to specify both
+incomplete and complete smart contracts\footnote{The tool has been adapted to accommodate incomplete contract codes that take input stacks and produce output stacks with more than one element.
+This modification is feasible from a technical standpoint, as the current tool can effectively handle such cases.}.
 For a complete smart contract, the output should be a pair consisting of an operation list and the storage's state after the completion of the code.
 For verification purposes we elide the operation list and represent the output solely by the term of the value in the storage after the execution concludes.
-In some cases, the output term can be omitted
-for a complete contract, given that the input term must be a pair
+In some cases, the output term can be omitted for a complete contract, given that the input term must be a pair
 of parameters and storage. Hence the storage term is part of the
@@
 
-The input and output terms represent Michelson terms, which can be
-either concrete values or symbolic values, including variables. When a variable appears for the first time, it needs to be accompanied by its
-corresponding type declaration. Subsequent mentions can omit the type
-declaration.  Formally, the pre- and postcondition instances are
-formulas in first-order logic that can be handled by an SMT solver (in
-our case, Z3).
+Formally, the pre- and postcondition instances are formulas in first-order logic that can be handled by an SMT solver (in our case, Z3).
 The specification language is constituted of predicates.
-The syntax terms and  predicates are defined in Figure~\ref{fig:syntax-terms-predicates}.
-Formulas that are used in assertions or
-added to solvers are terms of sort Boolean. Otherwise, terms of
+The syntax predicates are defined in Figure~\ref{fig:syntax-terms-predicates}.
+Formulas that are used in assertions or added to solvers are terms of sort Boolean.
+Otherwise, terms of
 Boolean and non-Boolean sort may be mixed in any combination where
-sorts match up. Universal and existential quantifiers bind variables
-to the scope of the quantified formula.
-\atha{More explanation is needed about expressions and formulas. Why
-  do you support left and right, but not lists? Why Never? What is the
-meaning of transfer\_token, get\_map, get\_contract? The constants
-must be explained (though you could do that in
-Section~\ref{sec:background}). (Less common items could be omitted!)}
+sorts match up.
+Several functions are defined, such as the function \text{get\_map (e1, e2)} for accessing an element in a map.
+This function returns \text{None} if there is no key \text{e1} in the map \text{e1}, or the corresponding value of the key otherwise.
+Another function, \text{get\_contract (e1, e2)}, casts the address \text{e2} to a real contract on the Tezos blockchain.
+It returns \text{None} if there is no existing contract on the Tezos block chain with an entrypoint of type \text{e1} associated with the address \text{e2}, or it returns the contract otherwise.
+
+Some other functions are defined as predicates, such as \text{transfer\_token} (\text{e1}, \text{e2}, \text{e3}).
+This implies that there is an operation in the operation list, after executing the smart contract code, which indicates the transfer of \text{e2} amount of tokens to the address \text{e3} along with the data \text{e1}\footnote{While some additional functions and both universal and existential quantifiers are implemented, they pose no technical problems and are similar to existing supported functions.
+However, the conversion to Z3 formulas in the Z3 OCaml library takes some time.}.
 
@@
 
-Let us consider the contract \texttt{Sub}  in Listing
+Let us consider a fragment code of the contract \texttt{Sub}  in Listing
 \ref{lst:sub-contract-specification} as an example of a property
@@
 \lstinline|'Unexpected pair'|.
-\atha{This Michelson code with its explanation might be an example for Section~\ref{sec:background}}
+
 The specification continues by defining
@@
 that the integer \lstinline/x/ is greater than or equal to  \lstinline/y/. The postcondition asserts that the result
-\lstinline/z/ is greater than or equal to the substract of \lstinline/x/ and \lstinline/y/, which is greater or equal to zero. The symbol \lstinline/&&/ stands for logical conjunction.
-\atha{This specification is meaningless. Why not use $x\ge y$ as
-  precondition and $z = x+y$ as postcondition?}
+\lstinline/z/ is greater than or equal to the substract of \lstinline/x/ and \lstinline/y/, which is greater or equal to zero. The symbol \lstinline/&&/ stands for logical predicate conjunction.
 
@@
 \label{sec:more-than-one}
-
-In XXX, we can specify several entrypoints at the same
+In SCV, we can specify several entrypoints at the same
 time. This design enables us to specify and verify all entrypoints
 at once and also to describe and verify relationships between
-entrypoints.  There are two options of the syntax as shown in Listing~\ref {lst:multiple-entrypoint-specification-1} and Listing~\ref {lst:multiple-entrypoint-specification-2},
+entrypoints.
+Considering that, for a complete smart contract code, the input term includes the storage term before, and the output term represents the storage after the execution, there are two options of the syntax as shown in Listing~\ref {lst:multiple-entrypoint-specification-1} and Listing~\ref {lst:multiple-entrypoint-specification-2},
 where the entrypoint name is written after the \lstinline/%/ symbol
@@
 which we explain next.
+The first option should be used when you want to check the output term, which may not be simply similar to the storage part of the input term.
+In the second option, the input term is then the pair of the parameter term and the storage term.
+The output term is similar to the storage term, with all variables added with the prefix \lstinline/post_/.
 
@@
 
-\atha{can we put the source code of the contract somewhere, e.g. in an appendix?}
 To illustrate entrypoint relations, let us consider a smart contract
@@
     parameter := Unit 
-    pre-condition := auction_open 
-       && Amount > Balance - Amount
+    pre-condition := auction_open = true
+       && Amount > pre_Balance
        && get_contract (unit, highest_bidder) = 
           Some (c: contract unit)
-    post-condition := auction_open
+    post-condition := auction_open = true
        && post_highest_bidder = Sender 
@@
        && post_Balance = Amount 
-       && transfer_token (Unit, Balance - Amount, c);
-
+       && transfer_token (Unit, pre_Balance, c);
   entrypoint %close
@@
     parameter := Unit
-    pre-condition := auction_open 
+    pre-condition := auction_open = true
        && Sender = contract_owner  
@@
           Some (c: contract unit)              
-    post-condition := not post_auction_open 
+    post-condition := post_auction_open  = false
        && post_Balance = 0 
-       && transfer_token (Unit, Balance, c)
+       && transfer_token (Unit, pre_Balance + Amount, c)
 
   (%create -> %bid) with (auction_open = true)  
-       and (Amount > Balance) 
+       and (Amount > pre_Balance) 
        and get_contract (unit, highest_bidder) = 
@@
 higher than the current bid (as specified in the
-\lstinline/pre-condition/ field from line 10 to line 11 in Listing
-\ref{lst:auction-contract-specification}), then the bid should
+\lstinline/pre-condition/ field from line 8 to line 11 in Listing
+\ref{lst:auction-contract-specification}) and the address of the highest bidder can be cast to a real contract represented by the variable \lstinline/c/ of type \lstinline/contract unit/ on the blockchain (lines 22-23 ), then the bid should
 succeed.  In this case, the highest bidder has to be updated to the
-sender (line 12 in the \lstinline/post-condition/ field), which is the
+sender (line 13 in the \lstinline/post-condition/ field), which is the
 address of the caller, and the balance of the contract should be the
-amount sent along with the call (line 13). Moreover, the previous
+amount sent along with the call (line 14). Moreover, the previous
 highest bidder should receive their bid, which means the auction
-contract should transfer the \lstinline/Balance/ to the previous
-bidder, \lstinline/highest_bidder/ (line 14). 
-The predicate \lstinline/Transfer_token (data, amount, address)/
+contract should transfer the \lstinline/pre_Balance/ to the previous
+bidder, \lstinline/highest_bidder/ (line 16). 
+The predicate \lstinline/transfer_token (data, amount, address)/
 represents a smart contract call with three arguments: the data sent
@@
 \lstinline/contract_owner/ should remain the same as before (line
-15). The last property guarantees that when the contract owner (line
-25) closes the open contract (line 24), the contract is first closed
-(line 26), and then money (\lstinline/Balance/) should be sent to the
-owner. Hence, the final auction balance is zero (lines 28 and 29).
+14). The last property guarantees that when the contract owner closes the open contract (line 21), the contract is first closed
+(line 24), and then money (\lstinline/post_Balance + Amount/) should be sent to the
+owner. Hence, the final auction balance is zero (lines 25 and 26).
 
@@
 \label{sec:entrypoint-relations}
-
 For a smart contract on the blockchain, the order of smart contract
@@
 should be able to bid on the contract or the contract owner should be
-able to close it (lines 29-31). Furthermore, the bid call can happen
+able to close it (lines 28-35). Furthermore, the bid call can happen
 successfully after another if the new bid is higher than the previous
-one (line 33). The  \lstinline/%close/ entrypoint can be called
+one (line 36). The  \lstinline/%close/ entrypoint can be called
 anytime if the caller is the contract owner (line 34). However, it
 should not be possible to call the  \lstinline/%bid/ entrypoint after
-the auction is closed (line 35), and, of course, it cannot be closed
-again if it is already closed (line 36). This sequence  illustrates
+the auction is closed (line 42), and, of course, it cannot be closed
+again if it is already closed (line 43). This sequence  illustrates
 the life cycle of the auction contract, which is depicted in Figure
@@
 \label{sec:static-checker-we}
-
 We verify the contract against its specifications in the contract
@@
         Some (v: option (pair nat (map address nat))) 
-      && v = Pair (n1: nat) (m: map address nat) 
-      && get_map (spender, m) = Some (n2: nat) 
-      && not (n2 = 0) | (value = 0)
+      && v = Pair (n: nat) (m: map address nat) 
+      && get_map (spender, m) = Some (k: nat) 
+      && not (k = 0) | (value = 0)
    post-condition := get_big_map (Sender, post_ledger) = 
         Some (post_v: option (pair nat (map address nat))) 
-      && post_v = Pair (post_n1: nat) (post_m: map address nat) 
-      && get_map (spender, post_m) = Some (post_n2: nat) 
-      && (post_n2 = 0) ;
+      && post_v = Pair (post_n: nat) (post_m: map address nat) 
+      && get_map (spender, post_m) = Some (post_k: nat) 
+      && (post_k = 0) ;
 
@@
         Some (v: option (pair nat (map address nat))) 
-      && v = Pair (n1: nat) (m: map address nat) 
-      && get_map (spender, m) = Some (n2: nat) 
-      && (n2 = 0) | not (value = 0)
+      && v = Pair (n: nat) (m: map address nat) 
+      && get_map (spender, m) = Some (k: nat) 
+      && (k = 0) | not (value = 0)
    post-condition := get_big_map (Sender, post_ledger) = 
         Some (post_v: option (pair nat (map address nat))) 
-      && post_v = Pair (post_n1: nat) (post_m: map address nat) 
-      && get_map (spender, post_m) = Some (post_n2: nat) 
-      && (post_n2 = value) ;
+      && post_v = Pair (post_n: nat) (post_m: map address nat) 
+      && get_map (spender, post_m) = Some (post_k: nat) 
+      && (post_k = value) ;
 \end{lstlisting}
@@
        && post_client = None 
-       && transfer(n, 0, c) ;
+       && transfer_token(n, 0, c) ;
   entrypoint %setGovernorContract
@@
      (Sender = harbinger)
-     && (s = 'XTZ-USD') 
-     && (Now - t <= 1800)  
+     and (s = 'XTZ-USD') 
+     and (Now - t <= 1800)  
   | (%getXtzUsdRate_callback  -> %getXtzUsdRate) with 
@@
 
+\section{Related Work}
+\label{sec:related-work}
+Research on the formal verification of blockchain-based applications has experienced rapid growth in the last decade.
+Various techniques and frameworks have been applied to enhance the security and reliability of smart contracts on the blockchain.
+In this section, we discuss some key approaches, particularly those employing symbolic execution in the context of smart contracts.
+
+Symbolic execution has emerged as a powerful technique for systematically exploring program paths and identifying potential vulnerabilities in smart contracts.
+P.
+Tsankov et al.
+introduced SECUTIFY \cite{securify}, a tool that utilizes symbolic execution to perform practical security analysis on Ethereum smart contracts.
+It targets common vulnerability security patterns specified in a designated domain-specific language.
+SECUTIFY symbolically encodes the dependence graph of the contract in stratified Datalog to extract semantic information from the code.
+After obtaining semantic facts, it checks whether the security patterns hold or not.
+Similarly, Manticore \cite{manticore} and KEVM \cite{kevm} use symbolic execution to analyze Ethereum smart contracts.
+KEVM is an executable formal specification built with the K Framework for the Ethereum virtual machine's bytecode (EVM), a stack-based and low-level smart contract language for the Ethereum blockchain.
+Since tokens can hold a significant amount of value, they are often targeted for attacks.
+Therefore, several tools \cite{kevm, park} conduct case studies for the implementations of token standards.
+
+Several approaches use existing formal verification frameworks to ensure the correctness and security of smart contracts.
+S.
+Amani et al.
+\cite{isabelle} proposed the formal verification of Ethereum smart contracts in Isabelle/HOL.
+Hirai \cite{hirai} formalizes the EVM using Lem, a language to specify semantic definitions.
+The formal verification of smart contracts is achieved using the Isabelle proof assistant.
+Bernardo et al.
+\cite{micho} implemented Mi-Cho-Coq, a formalization of the semantics of Michelson using the Coq proof assistant.
+They also verified several Michelson contracts.
+
+Several tools for automated verification include solc-verify \cite{solc}, VerX \cite{verx}, and Oyente \cite{oyente}.
+solc-verify processes smart contracts written in Solidity and discharges verification conditions using modular program analysis and SMT solvers.
+It operates at the level of the contract source code, with properties specified as contract invariants and function pre- and post-conditions provided as annotations in the code by the developer.
+This approach offers a scalable, automated, and user-friendly formal verification solution for Solidity smart contracts.
+The core of solc-verify involves translating Solidity contracts to Boogie IVL (Intermediate Verification Language), a simple language designed for verification.
+
+While these approaches differ, they share a focus on common bugs (such as reentrancy, overflow or underflow, and frozen funds).
+Our tool provide an environment where users can reliably specify their own properties and identify contract-specific bugs.
+Our tool aims to rich specifications to supports manually specified full correctness specifications.
+
+Close to our approach are HELMHOLTZ \cite{helmholtz} and iContract \cite{icontract}.
+Y.
+Nishida et al.
+\cite{helmholtz} developed HELMHOLTZ, an automated verification tool for Michelson.
+While both research efforts aim to build a verification tool for smart contracts written in Michelson, HELMHOLTZ is based on the refinement type system, whereas ours relies on symbolic execution.
+Both tools use the SMT solver Z3 for property verification.
+HELMHOLTZ takes, as input, a Michelson program annotated with a user-defined specification expressed in a refinement type; it then typechecks the program against the specification using the refinement type system.
+Similar to our tool, it discharges verification conditions with the SMT solver Z3.
+If the code successfully typechecks, then the program is guaranteed to satisfy the specification.
+Both tools use a language for user specifications, with properties annotated inside the code by the developer.
+Here, we provide a separate specification language that users don't need to modify within the code.
+While their specification language is close to ML-like notations, our language supports logic formulas in first-order logic similar to Z3.
+While HELMHOLTZ conducts example case studies or examines some entry points of real contracts, our tool conducts two real case studies of running blockchain contracts, implementing significant subjects on the blockchain such as token standards and oracles.
+
+iContract targets the Solidity language.
+It also utilizes pre and post conditions, similar to our tool, to specify user properties.
+iContract supports contract invariants, loop invariants, and pre-/post conditions.
+It locally installs the Solidity compiler to compile a user-provided Solidity file into a JSON file containing the typed abstract syntax tree (AST).
+Then, iContract analyzes the AST to encode contracts into predicates using the Z3 library.
+They leverage the NatSpec format to define their own specifications.
+
 \section{Conclusion}
 \label{sec:concl-sect-append}
-
 Symbolic execution is well known to suffer from challenges related to
@@
 
-In future work, we want to extend XXX in two directions. 
+In future work, we want to extend SCV in two directions. 
 First, we want to address the interaction of several entrypoints by

### 2024-01-16 papers/static-checker/ecoop2024/ecoop2024.tex
general revise

@@
 an entrypoint relation. An entrypoint relation can be specified as
-\lstinline/%a with cd -> %b/, which starts with the name
+\lstinline/%a -> %b with cd/, which starts with the name
 \lstinline/%a/ of the entrypoint and is followed by the keyword
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{auction-life-cycle}
+    \includegraphics[width=1.1\textwidth]{auction-life-cycle}
     \caption{Auction contract life cycle}
@@
 
-The architecture of the static checker is illustrated in
-Figure~\ref{fig:architecture-of-static-checker}. The system comprises
-three phases. The first phase is user specification, where users
+%The architecture of the static checker is illustrated in Figure~\ref{fig:architecture-of-static-checker}. 
+The system comprises three phases. The first phase is user specification, where users
 provide the Michelson code of the contract and define the properties
@@
 representing the storage and \VOPERATIONLIST\ repesents a operation
-list. Given an output term $ \tau$, the checker scans all the final
+list. Given an output term $ \tau$, the checker scans all the reachable final
 states, which do not contain a failwith stack and checks whether the
@@
 
-Listing~\ref{lst:add-contract-specification} contains an example of an
+Listing~\ref{lst:sub-contract-specification} contains an example of an
 incomplete smart contract code. The specification states that the
@@
 state that contains, in the top element, an integer value, which is
-the sum of the two elements of the pair. The output check succeeds for
+the substract of the two elements of the pair. The output check succeeds for
 this example as expected. However, this test could fail if, for
@@
 \lstinline|Pair 5 3|, then the expected output should be the number
-\lstinline|8|. To check this,  the output term may be specified as
+\lstinline|2|. To check this,  the output term may be specified as
 a concrete value.
@@
 smart contract standards, such as
-\cite{@ha-supply-a-smart-contract-standard}, require the contract to fail
+\cite{erc, fa}, require the contract to fail
 with specific messages under certain conditions. Therefore, it is
@@
 includes the fail condition together with the message. For example,
-for the specification in Listing \ref{lst:add-contract-specification},
+for the specification in Listing \ref{lst:sub-contract-specification},
 the fail condition is recorded as
@@
 leads to an error condition that is reported with a \FAILWITH\
-instruction in the implementation. In our framework, this cast failure
-shows up  as a fail condition, but the user's preconditions assume
-that casting is successful. The \lstinline/close/ entrypoint has
+instruction in the implementation. The \lstinline/close/ entrypoint has
 similar fail conditions when the auction is closed or the owner's
@@
 owner of the contract, which was stored in the contract owner part.
-\atha{This discussion suggests that the specification is incomplete:
-  it should contain the assertion that the highest bidder as well as
-  the contract owner field are valid and point to a unit contract!}
 
 \begin{lstlisting}[float=tp,captionpos=b,caption={Fail condition for auction contract bid entrypoint },label={lst:fail-condition-auction-contract-bid},numbers=left]
-1. not (auction_open): 'Already closed'
-2. auction_open && (Amount <= Balance - Amount):
+1. not (auction_open = true): 'Already closed'
+2. (auction_open = true) && (Amount <= pre_Balance):
    'Not higher than the current highest bid'
-3. auction_open && not (Amount <= Balance - Amount) && 
+3. (auction_open = true) && (Amount > pre_Balance) && 
    get_contract (unit, highest_bidder) = None:
@@
 \begin{lstlisting}[float=tp,captionpos=b,caption={Fail condition for auction contract close entrypoint},label={lst:fail-condition-auction-contract-close},numbers=left]
-1. not (auction_open): 'Already closed'
-2. auction_open && Sender != contract_owner): 'Not owner'
-3. auction_open && (Sender = contract_owner) &&
+1. not (auction_open = true): 'Already closed'
+2. (auction_open = true) && (Sender != contract_owner): 
+    'Not the owner'
+3. (auction_open = true) && (Sender = contract_owner) &&
    get_contract (unit, contract_owner) = None:
@@
 $\land$ $\Theta$) is satisfiable. We then check that for every path
-$\Pi$, $\neg$ ($\bigwedge \Phi_{i}$ $\land$ $\Theta$ $\rightarrow \bigwedge \Psi_{j}$) is
-unsatisfiable in the context given by the input for the entry point
+$\Pi$, $\neg$ ($\bigwedge \Phi_{i}$ $\land$ $\Theta$ $\rightarrow \bigwedge \Psi_{j}$) is unsatisfiable in the context given by the input for the entry point
 and its corresponding final state.
-\atha{Don't you have to include $\Theta$ in the check for unsat?}
 
@@
 example, the checker then verifies that $\neg$ ((\lstinline/x/ >= y) $\land$ (\lstinline/z/
-= \lstinline/x/ - \lstinline/y/) $\rightarrow$ (\lstinline/z/ = \lstinline/x/ - \lstinline/y/) $\land$ (\lstinline/z/ >= 0)) is
-unsatisfiable.
-\atha{I don't understand the last sentence/formula. Where does the
-  $z\ge8$ come from?}
+= \lstinline/x/ - \lstinline/y/) $\rightarrow$ (\lstinline/z/ = \lstinline/x/ - \lstinline/y/) $\land$ (\lstinline/z/ >= 0)) is unsatisfiable.
 
@@
 \label{sec:life-cycle-check}
-\atha{To be completed}
-An entrypoint relation can be defined as \lstinline/%a with cd -> %b/, indicating that after invoking the entrypoint \lstinline/%a/, it is permissible to call the entrypoint \lstinline/%b/ if the condition \lstinline/cd/ is satisfied.
+An entrypoint relation can be defined as \lstinline/(%a -> %b) with cd/, indicating that after invoking the entrypoint \lstinline/%a/, it is permissible to call the entrypoint \lstinline/%b/ if the condition \lstinline/cd/ is satisfied.
 The presence of the keyword \lstinline/not/ at the beginning signals an impossibility.
@@
 Let $R$ be the set containing all such states $s_{i}$ in $S_a$ where it is successful to call the entrypoint \lstinline/%b/ with the condition \lstinline/cd/.
-If $R$ is non-empty, then \lstinline/%a with cd -> %b/ holds.
-Otherwise, it is false, signifying \lstinline/not (%a with cd -> %b)/.
+If $R$ is non-empty, then \lstinline/(%a -> %b) with cd/ holds.
+Otherwise, it is false, signifying \lstinline/not (%a  -> %b) with cd/.
 
@@
 of a fiat currency like USD or EUR.
-\atha{add citations!}
 
@@
 with decentralized exchanges, wallets, and other tools within the
-ecosystem. For example, ERC-20 is a token standard used in Ethereum.
-
-\atha{provide references for the standards!}
+ecosystem. For example, ERC-20 \cite{erc} is a token standard used in Ethereum.
+
 The Tezos blockchain has its own set of standards known as Financial
-Applications (FA). Two notable standards are: (1) FA 1.2, designed for
-fungible tokens, and (2) FA 2, a more versatile standard accommodating
+Applications (FA). Two notable standards are: (1) FA 1.2 \cite{fatzip}, designed for
+fungible tokens, and (2) FA 2 \cite{fatzips}, a more versatile standard accommodating
 both fungible and non-fungible tokens (NFTs). The standard outlines a
@@
 contract address. Further elaboration on the details of FA 1.2 can be
-found in \cite{financial-applications-1.2}, and we will delve into
+found in \cite{usdtz}, and we will delve into
 these functions in subsequent 
 sections.
-\atha{is that correct: ``callback that results in a value of type r''?
-I would have expected that the callback \textbf{expects} a value of
-type r.}
 
@@
 
-In this section, we verify USDtz \cite{USDtz-implementation}, an
+In this section, we verify USDtz \cite{usdtzimplemetation}, an
 implementation of the FA 1.2 standard. Our goal is to ensure that the
@@
 \texttt{KT1LN4LPSqTMS7Sd2CJw4bbDGRkMv2t68Fy9}, and the code can be
-found on the Tezos blockchain \cite{USDtz-address}. USDtz adheres to
+found on the Tezos blockchain \cite{tzstatsusdtz}. USDtz adheres to
 the FA token standard, and the initial deployment of the USDtz smart
@@
 condition feature of the tool and examine the returned results, as
-outlined in Listing~\ref{lst:transfer-udstz-contract}.
+outlined in Listing~\ref{lst:transfer-udstz-contract}\footnote{There may be some duplicates of the same failwith condition due to the branching of the symbolic interpreter.
+The results here are shortened.
+We are working on filtering them in the tool.}.
 \begin{lstlisting}[float,captionpos=b,caption={Fail conditions for the \lstinline/transfer/ entrypoint},label={lst:transfer-udstz-contract},numbers=left]
-1. paused: 'TokenOperationsArePaused'
-2. not paused &&
+1. (paused = true): 'TokenOperationsArePaused'
+2. not (paused = true) &&
    get_big_map (from, ledger) = None : 'NotEnoughBalance'
-3. not paused &&
+3. not (paused = true) &&
    get_big_map (from, ledger) = Some sbvar &&
@@
    sbvar1 < value : 'NotEnoughBalance'
-4. not paused &&
+4. not (paused = true) &&
    get_big_map (from, ledger) = Some sbvar &&
@@
         && get_big_map (from, ledger) = 
-           Some (v: option (pair nat (map address nat))) 
-        && (v = Pair (n1: nat) (m: map address nat))
-        && get_map (Sender, m) = Some (n2: nat) 
-        && (n1 >= value) && (n2 >= value)
+           Some (v: pair nat (map address nat))
+        && (v = Pair (n: nat) (m: map address nat))
+        && get_map (Sender, m) = Some (k: nat) 
+        && (n >= value) && (k >= value)
       post-condition := get_big_map (from, post_ledger) = 
            Some (post_v: option (pair nat (map address nat))) 
-        && post_v = Pair (post_n1: nat) (post_m: map address nat) 
-        && get_map (Sender, post_m) = Some (post_n2: nat) 
-        && (post_n1 = n1 - value) && (post_n2 = n2 - value)
+        && post_v = Pair (post_n: nat) (post_m: map address nat) 
+        && get_map (Sender, post_m) = Some (post_k: nat) 
+        && (post_n = n - value) && (post_k = k - value)
 \end{lstlisting}
@@
 \begin{lstlisting}[float=tp,captionpos=b,caption={Fail conditions for the \lstinline/approve/ entrypoint},label={lst:approve-udstz-contract},numbers=left]
-1. paused: 'TokenOperationsArePaused'
-2. not paused &&
+1. (paused = true): 'TokenOperationsArePaused'
+2. not (paused = true) &&
    get_big_map (Sender, ledger) = Some sbvar &&
@@
    parameter := Pair (spender: address) (value: nat)
-   pre-condition := not paused 
+   pre-condition := not (paused = true)
       && get_big_map (Sender, ledger) = 
-        Some (v: option (pair nat (map address nat))) 
+        Some (v: pair nat (map address nat))
       && v = Pair (n: nat) (m: map address nat) 
@@
    post-condition := get_big_map (Sender, post_ledger) = 
-        Some (post_v: option (pair nat (map address nat))) 
+        Some (post_v:  (pair nat (map address nat))
       && post_v = Pair (post_n: nat) (post_m: map address nat) 
@@
 
-   pre-condition := not paused 
+   pre-condition := not (paused = true) 
       && get_big_map (Sender, ledger) = 
@@
 
-The Kolibri oracle contract,  residing at  address
-\texttt{KT1Tj6xknbwjyK5gyfESNR6WESBcP3yX1mmj}, ensures the accuracy of
+The Kolibri oracle contract \cite{kolibri},  residing at  address
+\texttt{KT1Tj6xknbwjyK5gyfESNR6WESBcP3yX1mmj} \cite{tzstatskolibri}, ensures the accuracy of
 external data for the Tezos-based stablecoin Kolibri by leveraging
@@
 stored by the oracle include:
-\atha{Explain what the governor is!\\ How can a parameter have type contract?}
+
 \begin{itemize}
@@
        && s = 'XTZ-USD' 
-       && Now - t <= 30 
+       && Now - t <= maxDelay 
        && client = Some a 
@@
      and (s = 'XTZ-USD') 
-     and (Now - t <= 1800)  
+     and (Now - t <= maxDelay)  
   | (%getXtzUsdRate_callback  -> %getXtzUsdRate) with 
@@
 
+When verifying the entrypoint \lstinline/setMaxDataDelaySec/, we noticed an unmatched statement.
+In \cite{kolibri}, the Kolibri oracle is expected to perform two checks on data returned from Harbinger: (1) was the asset returned "XTZ-USD" and (2) was the asset updated in the last 30 minutes.
+We ran the fail condition check for both the \lstinline/setMaxDataDelaySec/ and \lstinline/getXtzUsdPrice_callback/ entrypoints as shown in Listing \ref{lst:setXtzUsdPrice_callback} and \ref{lst:setMaxDataDelaySec}.
+Upon examining the failwith conditions, we detected that there is no failwith if the data is more than 30 minutes (equal to 1800 seconds).
+We can add the predicate \lstinline/maxDelay <= 1800/ in the post condition of the entrypoint \lstinline/setMaxDataDelaySec/, but then the pre and post condition test fails.
+This means there is no constraint that the data is less than 30 minutes.
+This constraint is possibly set up by the governor and specified in the \lstinline/MaxDataDelaySec/ field.
+However, users calling this contract should be aware that it is possible for the governor to set any value (>=0) as desired.
+This could lead to providing out-of-date rates.
+\begin{lstlisting}[float=tp,captionpos=b,caption={Failwith condition for the entrypoint setXtzUsdPrice\_callback},label={lst:setXtzUsdPrice_callback},numbers=left]
+1. not (state = 1): 12
+2. (state = 1) && not (Sender = harbinger): 3
+3. (state = 1) &&  (Sender = harbinger) 
+&& not ('XTZUSD' = s): 14
+4. (state = 1) &&  (Sender = harbinger) && ('XTZUSD' = s)
+&& (Now - t >= 0) && (Now - t >= maxDelay): 17
+5. (state = 1) &&  (Sender = harbinger) && ('XTZUSD' = s)
+&& (Now - t >= 0) && (Now - t < maxDelay) 
+&& (client = Some sbvar) 
+&& get_contract (Nat, sbvar) = None: Unit
+6. (state = 1) &&  (Sender = harbinger) && ('XTZUSD' = s)
+&& (Now - t >= 0) && (Now - t < maxDelay) 
+&& (client = None): Unit
+7. (state = 1) &&  (Sender = harbinger) && Not (Now - t >= 0) 
+&& not ('XTZUSD' = s): Unit
+\end{lstlisting}
+
+\begin{lstlisting}[float=tp,captionpos=b,caption={Failwith condition for the entrypoint setMaxDataDelaySec},label={lst:setMaxDataDelaySec},numbers=left]
+not (Sender = governor): 4
+\end{lstlisting}
 \section{Symbolic Execution Model}
@@
     [\INSTRUCTIONONE, (\StackOne, \TYF) \STACKCONCAT \EMPTYSTACK, 
-    \Q]
+    \PREDICATE]
     \StateTrans^*
-    [ \EMPTYSTACK, (\StackOne', \TYS) \STACKCONCAT \Q']
+    [ \EMPTYSTACK, (\StackOne', \TYS) \STACKCONCAT \PREDICATE']
   }{
      [(\EXEC; \INSTRUCTION),   (\{\INSTRUCTIONONE\}, \TYF\ \rightarrow\ \TYS) \STACKCONCAT
-    (\StackOne, \TYF) \STACKCONCAT \STACK, \PREDICATE \wedge \Q] 
+    (\StackOne, \TYF) \STACKCONCAT \STACK, \PREDICATE] 
     \StateTrans \
     [ \INSTRUCTION, (\StackOne', \TYS) \STACKCONCAT \STACK,
-    \PREDICATE \wedge \Q']}
+    \PREDICATE]}
 \end{mathpar}
@@
   { 
-     \FLEN(\A) \EQ\ \N \\ [\INSTRUCTIONONE,  \B, \Q]
+     \FLEN(\A) \EQ\ \N \\ [\INSTRUCTIONONE,  \B, \PREDICATE]
     \StateTrans^*
-    [\EMPTYSTACK,  \B_1, \Q']
+    [\EMPTYSTACK,  \B_1, \PREDICATE']
   }
-  {[(\DIP\ \N\ \INSTRUCTIONONE; \INSTRUCTION), \A\ \At\ \B, \PREDICATE \wedge \Q] \StateTrans 
-[\INSTRUCTION, \A\ \At\ \B_1, \PREDICATE \wedge \Q']}
+  {[(\DIP\ \N\ \INSTRUCTIONONE; \INSTRUCTION), \A\ \At\ \B, \PREDICATE] \StateTrans 
+[\INSTRUCTION, \A\ \At\ \B_1, \PREDICATE]}
 \end{mathpar}
@@
 \bibliography{ecoop2024}
+\include{appendix}
 \end{document}
-\begin{figure}[tp]
-\begin{align*}
-T, U &::= \\
-   &\Mid\ \langle \text{comparable type}\rangle \\
-   &\Mid\ \text{option}\ \langle\text{type}\rangle \\
-   &\Mid\ \text{list}\ \langle\text{type}\rangle \\
-   &\Mid\ \text{set}\ \langle\text{comparable type}\rangle \\
-   &\Mid\ \text{operation} \\
-   &\Mid\ \text{contract}\ \langle\text{type}\rangle \\
-   &\Mid\ \text{ticket}\ \langle\text{comparable type}\rangle \\
-   &\Mid\ \text{pair}\ \langle\text{type}\rangle \langle\text{type}\rangle \\
-   &\Mid\ \text{or}\ \langle\text{type}\rangle \langle\text{type}\rangle \\
-   &\Mid\ \text{lambda}\ \langle\text{type}\rangle \langle\text{type}\rangle \\
-   &\Mid\ \text{map}\ \langle\text{comparable type}\rangle \langle\text{type}\rangle \\
-   &\Mid\ \text{big-map}\ \langle\text{comparable type}\rangle \langle\text{type}\rangle \\
-   &\Mid\ \text{bls12-381-g1} \\
-   &\Mid\ \text{bls12-381-g2} \\
-   &\Mid\ \text{bls12-381-fr} \\
-   &\Mid\ \text{sapling-transaction}\ \langle\text{natural number constant}\rangle \\
-   &\Mid\ \text{sapling-state}\ \langle\text{natural number constant}\rangle \\
-   &\Mid\ \text{chest} \\
-   &\Mid\ \text{chest-key} \\
-\langle\text{comparable type}\rangle ::= \\
-   &\Mid\ \text{unit} \\
-   &\Mid\ \text{never} \\
-   &\Mid\ \text{bool} \\
-   &\Mid\ \text{int}\\
-   &\Mid\ \text{nat}\\
-   &\Mid\ \text{string}\\
-   &\Mid\ \text{chain-id}\\
-   &\Mid\ \text{bytes}\\
-   &\Mid\ \text{mutez}\\
-   &\Mid\ \text{key-hash}\\
-   &\Mid\ \text{key}\\
-   &\Mid\ \text{signature}\\
-   &\Mid\ \text{timestamp}\\
-   &\Mid\ \text{address}\\
-   &\Mid\ \text{tx-rollup-l2-address}\\
-   &\Mid\ \text{option}\ \langle\text{comparable type}\rangle\\
-   &\Mid\ \text{or}\ \langle\text{comparable type}\rangle \langle\text{comparable type}\rangle\\
-   &\Mid\ \text{pair}\ \langle\text{comparable type}\rangle \langle\text{comparable type}\rangle \DOT \\
-\end{align*}
-\caption{Types}
-\label{fig:type}
-\end{figure}

### 2024-01-16 papers/static-checker/ecoop2024/ecoop2024.tex
general revision

@@
 with decentralized exchanges, wallets, and other tools within the
-ecosystem. For example, ERC-20 \cite{erc} is a token standard used in Ethereum.
+ecosystem. For example, ERC-20 \cite{erc} is a token standard used in Ethereum \cite{eth-whitepaper}.
 
 The Tezos blockchain has its own set of standards known as Financial
-Applications (FA). Two notable standards are: (1) FA 1.2 \cite{fatzip}, designed for
-fungible tokens, and (2) FA 2 \cite{fatzips}, a more versatile standard accommodating
+Applications (FA). Two notable standards are: (1) FA 1.2 \cite{fa}, designed for
+fungible tokens, and (2) FA 2 \cite{fas}, a more versatile standard accommodating
 both fungible and non-fungible tokens (NFTs). The standard outlines a
@@
 A view is an entrypoint that takes an
-argument of type \lstinline/a/ and a callback that results in a value
+argument of type \lstinline/a/ and a contract to callback that receives in a value
 of type \lstinline/r/. The callback in this case will be another
 contract address. Further elaboration on the details of FA 1.2 can be
-found in \cite{usdtz}, and we will delve into
+found in \cite{fatzip}, and we will delve into
 these functions in subsequent 
@@
          (Pair (to: address) (value: nat))
-      pre-condition := not paused 
+   pre-condition := not (paused  = true)
      && get_big_map (from, ledger) = 
@@
    post-condition := get_big_map (from, post_ledger) = 
-           Some (post_v: option (pair nat (map address nat))) 
+     Some (post_v:  pair nat (map address nat))
      && post_v = Pair (post_n: nat) (post_m: map address nat) 
@@
 subproperty is specified as shown in
-Listing~\ref{lst:specification-approve}. Property 2: if
+Listing~\ref{lst:specification-approve-1}. Property 2: if
 \lstinline/value/ is non-zero and the allowance of the \lstinline/spender/ is zero, then the \lstinline/value/ should be recorded in the storage after the call.
-We specify this property using pre- and post-conditions, as illustrated in Listing~\ref{lst:---approve---to-be-provided}.
-
-\begin{lstlisting}[float=tp,captionpos=b,caption={Specification of the \lstinline/approve/ entrypoint},label={lst:specification-approve},numbers=left]
+We specify this property using pre- and post-conditions, as illustrated in Listing~\ref{lst:specification-approve-2}.
+
+\begin{lstlisting}[float=tp,captionpos=b,caption={Specification of the \lstinline/approve/ entrypoint (Property 1)},label={lst:specification-approve-1},numbers=left]
 entrpoint %approve
@@
       && (post_k = 0) ;
-
+\end{lstlisting}
+\begin{lstlisting}[float=tp,captionpos=b,caption={Specification of the \lstinline/approve/ entrypoint (Property 2)},label={lst:specification-approve-2},numbers=left]
    pre-condition := not (paused = true) 
@@
 lines 5-8 specify that \lstinline/owner/ is in the \lstinline/ledger/
-big map, as the \lstinline/Get_big_map/ function returns a value
+big map, as the \lstinline/get_big_map/ function returns a value
 \lstinline/Some value/ of the \TOPTION\ type, and this
@@
       && post_total_supply = total_supply 
-      && post_Balance = Balance 
+      && post_Balance = pre_Balance 
       && transfer_token (k, Amount, c) ;
@@
       && post_total_supply = total_supply 
-      && post_Balance = Balance 
+      && post_Balance = pre_Balance 
       && transfer_token (0, Amount, c) ;
@@
  (or
-   (or
-     (unit %default)
-     (contract nat %getXtzUsdRate))
+   (or (unit %default) (contract nat %getXtzUsdRate))
    (or
@@
 The subsequent property dictates that if \lstinline/getXtzUsdPrice/ is successfully executed, the state must transition to \lstinline/WAITING_FOR_HARBINGER/, and the parameters passed along with the call need to be stored in the \lstinline/clientCallback/ attribute of the storage.
-This property can be detailed as shown in Listing \ref{lst:kolibri-contract-specification}.
 
 The following property asserts that if \lstinline/getXtzUsdPrice_callback/ is successful, the state should revert to \lstinline/IDLE/, and there must be a transaction transferring the data to the client at the \lstinline/clientCallback/ attribute.
-This property is specified in Listing \ref{lst:kolibri-contract-specification}.
 
@@
 another call or invoking the \lstinline/getXtzUsdPrice_callback/
-entrypoint again is not allowed. This entrypoint relation property is
-specified as an entrypoint relation in
-Listing~\ref{lst:kolibri-oracle-entrypoint-relations-text}.
-
+entrypoint again is not allowed.
+
+The specification of  the contract is showned in Listing \ref{lst:kolibri-contract-specification}. Here, we shortened the names of the variables for the storage.
 \begin{figure}[tp]
@@
 \end{lstlisting}
-
 When verifying the entrypoint \lstinline/setMaxDataDelaySec/, we noticed an unmatched statement.
@@
 
-Several tools for automated verification include solc-verify \cite{solc}, VerX \cite{verx}, and Oyente \cite{oyente}.
+There are exsiting tools for automated verification include solc-verify \cite{solc}, VerX \cite{verx}, and Oyente \cite{oyente}.
 solc-verify processes smart contracts written in Solidity and discharges verification conditions using modular program analysis and SMT solvers.
@@
 It also utilizes pre and post conditions, similar to our tool, to specify user properties.
-iContract supports contract invariants, loop invariants, and pre-/post conditions.
 It locally installs the Solidity compiler to compile a user-provided Solidity file into a JSON file containing the typed abstract syntax tree (AST).

### 2024-01-17 papers/static-checker/ecoop2024/ecoop2024.tex
update the pictures

@@
        && s = 'XTZ-USD' 
-       && Now - t <= maxDelay 
+       && Now - t < maxDelay 
+       && Now - t >= 0 
        && client = Some a 
@@
      (Sender = harbinger)
-     and (s = 'XTZ-USD') 
-     and (Now - t <= maxDelay)  
+     && (s = 'XTZ-USD') 
+     && (Now - t >= 0)  
+     && (Now - t < maxDelay)  
   | (%getXtzUsdRate_callback  -> %getXtzUsdRate) with 
@@
 5. (state = 1) &&  (Sender = harbinger) && ('XTZUSD' = s)
+&& not (Now - t >= 0): Unit
+6. (state = 1) &&  (Sender = harbinger) && ('XTZUSD' = s)
 && (Now - t >= 0) && (Now - t < maxDelay) 
@@
 && get_contract (Nat, sbvar) = None: Unit
-6. (state = 1) &&  (Sender = harbinger) && ('XTZUSD' = s)
+7. (state = 1) &&  (Sender = harbinger) && ('XTZUSD' = s)
 && (Now - t >= 0) && (Now - t < maxDelay) 
 && (client = None): Unit
-7. (state = 1) &&  (Sender = harbinger) && Not (Now - t >= 0) 
-&& not ('XTZUSD' = s): Unit
 \end{lstlisting}

### 2024-01-17 papers/static-checker/ecoop2024/ecoop2024.tex
update  kolibri pictures

@@
     parameter := (c : contract nat) 
-    pre-condition := (Amount = 0) | (state = 0)
+    pre-condition := (Amount = 0) && (state = 0)
+    get_contract (pair string (contract pair 
+    string (pair timestamp nat)), harbinger) = Some c
     post-condition := (state = 1) 

### 2024-01-17 papers/static-checker/ecoop2024/ecoop2024.tex
intro & abstract

@@
-\documentclass[a4paper,USenglish,cleveref, autoref, thm-restate]{lipics-v2021}
+\documentclass[a4paper,USenglish,cleveref, autoref,anonymous]{lipics-v2021}
 
@@
 
-\ccsdesc[100]{\textcolor{red}{Replace ccsdesc macro with valid one}} %TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
+\begin{CCSXML}
+<ccs2012>
+<concept>
+<concept_id>10011007.10010940.10010992.10010998.10011000</concept_id>
+<concept_desc>Software and its engineering~Automated static analysis</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+</ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Software and its engineering~Automated static analysis}
 
@@
 \begin{abstract}
-Formal verification is a requirement for all but the simplest smart
-contracts on the blockchain. We developed SCV, a tool that is geared towards contracts
-implemented in Michelson, the smart contract language of the Tezos
-blockchain. It relies on symbolic execution and an SMT solver to
-derive verification conditions that can be checked against the user's
+Formal verification is a requirement for all smart
+contracts on the blockchain. We developed SCV, a verification tool
+that is geared towards contracts implemented in Michelson, the smart
+contract language of the Tezos blockchain. It relies on symbolic execution to
+derive verification conditions that can be checked automatically against the user's
+specification. An SMT solver helps prune states during symbolic
+execution and check the verification conditions against the
 specification. Specifications are written in a domain-specific
@@
 We report the foundations of the design and implementation of SCV and
-conduct two case studies that demonstrate the expressiveness of our tool.
+conduct two case studies on real-life contracts that demonstrate the
+expressiveness of our tool.
 \end{abstract}
@@
 
-Once a smart contract is published on a blockchain, it cannot be
-changed any more. Unfortunately, there are plenty of
-cases~\cite{dao,wallethack} where the blockchain 
-community identified vulnerabilities in smart contracts despite
-extensive testing before deployment.
-In addition, the novel execution model of smart contract
-languages has led to unforeseen errors due to a lack of familiarity
-with their intricacies. These observations along with the contract's
-immutability underscore the need to ensure its correctness before deployment.
+A blockchain is a unique execution environment rooted in
+irreversible transactions. Smart contracts, which are programs
+designed for the blockchain, are also permanently stored within
+it. Consequently, once a smart contract is deployed on a blockchain,
+it cannot be changed anymore. Regrettably, numerous
+instances~\cite{dao,wallethack} have been documented where
+vulnerabilities in smart contracts were 
+identified by the blockchain community, resulting in substantial
+financial losses. Specifically, the distinctive execution model of
+smart contract languages has given rise to unforeseen errors due to a
+lack of familiarity with their complexities. These observations,
+combined with the immutability of contracts, underscore the need
+to ensure their correctness prior to deployment.
 
@@
 
-In this work, we present the design of a domain-specific language for
-specifying smart contract properties and demonstrate the integration
-of symbolic execution for Michelson with an SMT solver for automatic
-formal verification of these properties.
-
+Our starting point is the design of a domain-specific language for
+specifying smart contract properties.
 \begin{lstlisting}[float=tp,captionpos=b,caption={Auction contract specification (excerpt)},label={lst:auction-fragment}]
@@
 \lstinline|highest_bidder|, and \lstinline|contract_owner|.
-The actual specification consists of a precondition and a
+The contract has several entrypoints that may be invoked individually.
+
+There is a specification for each entrypoint. The example shows the
+one for  \lstinline|bid|, to place a bid on the auction. Each
+specification consists of a precondition and a 
 postcondition with the usual partial correctness semantics. The
@@
 \lstinline|post_| to their name. The variables
-\lstinline|Amount|, and \lstinline|Sender| correspond to the values
-returned by the like-named Michelson instructions that return, the amount transferred with the call, and the address of the caller (sender).
-The variables \lstinline|pre_Balance| and \lstinline|post_Balance| represent the previous balance of the contract right before and after the call, respectively.
-The current balance of the contract returned by the instruction \BALANCE\ includes \lstinline|pre_Balance| and the \lstinline|Amount|.
+\lstinline|Amount| and \lstinline|Sender| correspond to the values
+returned by the like-named Michelson instructions that return the
+amount transferred with the call and the address of the caller
+(sender).  The variables \lstinline|pre_Balance| and
+\lstinline|post_Balance| stand for the balance of the contract right
+before and after the call, respectively. The value returned by the
+Michelson instruction \BALANCE\ includes 
+\lstinline|pre_Balance| and the \lstinline|Amount|.
+This contract is our running example in
+Section~\ref{sec:more-than-one}, where further explanations may be found.
 
@@
 implies the specified postcondition.
+
+While there is already a considerable body of work that applies
+symbolic execution to the verification of smart contracts
+\cite{securify, manticore,kevm,park} (see
+Section~\ref{sec:related-work} for details), most of them are geared
+towards Ethereum, so that standard techniques for symbolic execution
+of imperative programs are applicable. Such groundwork does not exist
+for Michelson, which is a functional language running on a stack
+machine (see Section~\ref{sec:background}) with a sophisticated
+instruction set that includes high-level loops. For that reason, we had to
+develop symbolic execution for Michelson from ground up.
+
+Besides the Mi-Cho-Coq framework that relies on interactive theorem
+proving \cite{micho}, HELMHOLTZ \cite{helmholtz} is another automatic
+verifier for Michelson. However, the approach of HELMHOLTZ is significantly
+different from ours. They define a refinement type system to keep
+track of the properties of values in the storage and on the
+stack, so that verifying a program corresponds to typechecking against
+a specification type. Their type checker employs Z3 to discharge proof obligations.
 
@@
 
-Symbolic execution has emerged as a powerful technique for systematically exploring program paths and identifying potential vulnerabilities in smart contracts.
-P.
-Tsankov et al.
-introduced SECUTIFY \cite{securify}, a tool that utilizes symbolic execution to perform practical security analysis on Ethereum smart contracts.
-It targets common vulnerability security patterns specified in a designated domain-specific language.
-SECUTIFY symbolically encodes the dependence graph of the contract in stratified Datalog to extract semantic information from the code.
-After obtaining semantic facts, it checks whether the security patterns hold or not.
-Similarly, Manticore \cite{manticore} and KEVM \cite{kevm} use symbolic execution to analyze Ethereum smart contracts.
-KEVM is an executable formal specification built with the K Framework for the Ethereum virtual machine's bytecode (EVM), a stack-based and low-level smart contract language for the Ethereum blockchain.
-Since tokens can hold a significant amount of value, they are often targeted for attacks.
-Therefore, several tools \cite{kevm, park} conduct case studies for the implementations of token standards.
-
-Several approaches use existing formal verification frameworks to ensure the correctness and security of smart contracts.
-S.
-Amani et al.
-\cite{isabelle} proposed the formal verification of Ethereum smart contracts in Isabelle/HOL.
-Hirai \cite{hirai} formalizes the EVM using Lem, a language to specify semantic definitions.
-The formal verification of smart contracts is achieved using the Isabelle proof assistant.
-Bernardo et al.
-\cite{micho} implemented Mi-Cho-Coq, a formalization of the semantics of Michelson using the Coq proof assistant.
-They also verified several Michelson contracts.
+Symbolic execution has emerged as a powerful technique for
+systematically exploring program paths and identifying potential
+vulnerabilities in smart contracts. P. Tsankov et al. introduced
+SECURIFY \cite{securify}, a tool that utilizes symbolic execution to
+perform practical security analysis on Ethereum smart contracts. It
+targets common vulnerability security patterns specified in a
+designated domain-specific language. SECURIFY symbolically encodes the
+dependence graph of the contract in stratified Datalog to extract
+semantic information from the code. After obtaining semantic facts, it
+checks whether the security patterns hold or not. Similarly, Manticore
+\cite{manticore} and KEVM \cite{kevm} use symbolic execution to
+analyze Ethereum smart contracts. KEVM is an executable formal
+specification built with the K Framework for the Ethereum virtual
+machine's bytecode (EVM), a stack-based and low-level smart contract
+language for the Ethereum blockchain. Since tokens can hold a
+significant amount of value, they are often targeted for
+attacks. Therefore, several tools \cite{kevm,park} conduct case
+studies for the implementations of token standards.
+
+Several approaches use existing formal verification frameworks to
+ensure the correctness and security of smart contracts. S. Amani et
+al. \cite{isabelle} proposed the formal verification of Ethereum smart
+contracts in Isabelle/HOL. Hirai \cite{hirai} formalizes the EVM using
+Lem, a language to specify semantic definitions. The formal
+verification of smart contracts is achieved using the Isabelle proof
+assistant. Bernardo et al.~\cite{micho} implemented Mi-Cho-Coq, a
+formalization of the semantics of Michelson using the Coq proof
+assistant. They also verified several Michelson contracts.
 

### 2024-01-17 papers/static-checker/ecoop2024/ecoop2024.tex
michelson description

@@
 
+To invoke a Michelson contract on the Tezos blockchain, the caller has
+to provide tokens for gas and tokens to add to the contract's balance.
+The gas tokens are used account for the cost of running the contract;
+if contract execution runs out of gas, it is aborted before it can
+perform any visible change. The use of the balance is up to the
+discretion of the contract code.
+
 Listing~\ref {lst:simple-program-add} contains a short example of a Michelson program.
@@
 \end{lstlisting}
+\begin{lstlisting}[float=tp,captionpos=b,caption={A Michelson program
+with iteration},label={lst:simple-program-iter}]
+parameter list int;
+storage   int;
+code { 
+(*               pair (list int) int :: [] *)
+   UNPAIR;
+(*                   list int :: int :: [] *)
+   ITER {ADD};
+(*                               int :: [] *)
+   NIL operation; PAIR
+}
+\end{lstlisting}
+The code is interspersed with comments that indicate the types of
+values that are currently on the stack.
 This program first duplicates its input (\lstinline|DUP|), decomposes
 the pair $P\times S$ into its components (\lstinline|UNPAIR|),
-compares the two value on top of the stack (\lstinline|COMPARE|), and
+compares the two values on top of the stack (\lstinline|COMPARE|), and
 transforms the result into a boolean (\lstinline|GE|). The
@@
 only the initial pair is on the stack. In the true branch,
-\lstinline|UNPAIR| decomposes, and then \lstinline|SUB| subtract the two 
-components. In the false branch, the \lstinline|PUSH| instruction pushes
+\lstinline|UNPAIR| decomposes, and then \lstinline|SUB| subtracts the two 
+components. In the false branch, the \lstinline|PUSH| instruction puts
 a string message on the stack. The \lstinline|FAILWITH| instruction
-abort the contract execution: tokens are consumed, but the storage and
-the balance of the contract remain unchanged.
-
-We emerge from the conditional with just the result of the addition on
-the stack. The \lstinline|NIL| instruction pushes an empty list and
-\lstinline|PAIR| creates the requires pair of type $O^* \times S$.
+aborts the contract execution: the tokens provided with the invocation
+are consumed, but the storage and the balance of the contract remain
+unchanged.
+
+After the conditional the stack contains the result of the
+subtraction. The \lstinline|NIL| instruction pushes an empty list of
+operations and 
+\lstinline|PAIR| creates the required pair of type $O^* \times S$.
+
+Michelson has several instructions that perform
+iteration. Listing~\ref{lst:simple-program-iter} contains an example
+that uses the \lstinline|ITER| instruction to add a list of numbers
+(the parameter) to the storage. Like other looping instructions,
+\lstinline|ITER| takes a list of instructions that comprise the loop
+body (in this case just a single instruction \lstinline|ADD|) and
+expects a list to traverse on top of the stack. Essentially,
+\lstinline|ITER| runs the loop body for each element in the list,
+while allowing full access to the stack: each iteration consumes
+one list element and (potentially) transforms the whole stack
+while maintaining its shape/type.
 

### 2024-01-17 papers/static-checker/ecoop2024/ecoop2024.tex
kolibri specification

@@
       && get_map (spender, m) = Some (k: nat) 
-      && not (k = 0) | (value = 0)
+      && not (k = 0) && (value = 0)
    post-condition := get_big_map (Sender, post_ledger) = 
@@
       && get_map (spender, m) = Some (k: nat) 
-      && (k = 0) | not (value = 0)
+      && (k = 0) && not (value = 0)
    post-condition := get_big_map (Sender, post_ledger) = 

### 2024-01-17 papers/static-checker/ecoop2024/ecoop2024.tex
aution contract specification

@@
     parameter := Unit 
-    pre-condition := auction_open 
+    pre-condition := auction_open = true
        && Amount > pre_Balance 
@@
        && post_Balance = Amount 
-       && transfer_token (Unit, Old_Balance, c) ;
+       && transfer_token (Unit, pre_Balance, c) ;
 \end{lstlisting}

### 2024-01-17 papers/static-checker/ecoop2024/ecoop2024.tex
update koribli specification

@@
     code := {...}
-    parameter := (c : contract nat) 
+    parameter := (ct : contract nat) 
     pre-condition := (Amount = 0) && (state = 0)
@@
     string (pair timestamp nat)), harbinger) = Some c
-    post-condition := (state = 1) 
-       && (client = Some Sender) ;
+    post-condition := state = 1
+       && client = Some (b: address) ;
   entrypoint %getXtzUsdRate_callback
@@
      (Sender = harbinger)
-     && (s = 'XTZ-USD') 
-     && (Now - t >= 0)  
-     && (Now - t < maxDelay)  
+     and (s = 'XTZ-USD') 
+     and (Now - t >= 0)  
+     and (Now - t < maxDelay)  
   | (%getXtzUsdRate_callback  -> %getXtzUsdRate) with 
     (Amount = 0) 
+    and get_contract (pair string (contract pair 
+    string (pair timestamp nat)), harbinger) = Some c
   | not (%getXtzUsdRate -> %getXtzUsdRate) 

### 2024-01-17 papers/static-checker/ecoop2024/ecoop2024.tex
update some specifications

@@
           Some (c: contract unit)
-    post-condition := auction_open
+    post-condition := auction_open = true
        && post_highest_bidder = Sender 
@@
 \begin{lstlisting}[float,captionpos=b,caption={Multiple entrypoint specification syntax (option 1)},label={lst:multiple-entrypoint-specification-1},numbers=left][h]
-mcontract Name = spec
+mcontract name = spec
    entrypoint %a 
@@
 \begin{lstlisting}[float,captionpos=b,caption={Multiple entrypoint specification syntax (option 2)},label={lst:multiple-entrypoint-specification-2},numbers=left][h]
-mcontract Name = spec
+mcontract name = spec
    storage := t1
@@
           Some (c: contract unit)
-  | (%bid -> %bid) with (Amount > Balance - Amount) 
+  | (%bid -> %bid) with (Amount > pre_Balance) 
        and get_contract (unit, highest_bidder) = 
@@
        Some (v: pair nat (map address nat))
-     && (v = Pair (n: nat) (m: map address nat))
+     && v = Pair (n: nat) (m: map address nat)
      && get_map (Sender, m) = Some (k: nat) 
@@
 4. (state = 1) &&  (Sender = harbinger) && ('XTZUSD' = s)
-&& (Now - t >= 0) && (Now - t >= maxDelay): 17
+&& (Now - t >= 0) && not (Now - t < maxDelay): 17
 5. (state = 1) &&  (Sender = harbinger) && ('XTZUSD' = s)

### 2024-01-17 papers/static-checker/ecoop2024/ecoop2024.tex
entrypoint relation syntax update

@@
   (%create -> %bid) with (auction_open = true)  
-       and (Amount > pre_Balance) 
-       and get_contract (unit, highest_bidder) = 
+       && (Amount > pre_Balance) 
+       && get_contract (unit, highest_bidder) = 
            Some (c: contract unit)
   | (%create  -> %close) with (auction_open = true) 
-       and (Sender = contract_owner)
-       and get_contract (unit, contract_owner) = 
+       && (Sender = contract_owner)
+       && get_contract (unit, contract_owner) = 
           Some (c: contract unit)
   | (%bid -> %bid) with (Amount > pre_Balance) 
-       and get_contract (unit, highest_bidder) = 
+       && get_contract (unit, highest_bidder) = 
           Some (c: contract unit)
   | (%bid -> %close) with (Sender = contract_owner) 
-       and get_contract (unit, contract_owner) = 
+       && get_contract (unit, contract_owner) = 
             Some (c: contract unit)
@@
      (Sender = harbinger)
-     and (s = 'XTZ-USD') 
-     and (Now - t >= 0)  
-     and (Now - t < maxDelay)  
+     && (s = 'XTZ-USD') 
+     && (Now - t >= 0)  
+     && (Now - t < maxDelay)  
   | (%getXtzUsdRate_callback  -> %getXtzUsdRate) with 
     (Amount = 0) 
-    and get_contract (pair string (contract pair 
+    && get_contract (pair string (contract pair 
     string (pair timestamp nat)), harbinger) = Some c

### 2024-01-17 papers/static-checker/ecoop2024/ecoop2024.tex
Some minor in the code

@@
 1. not (auction_open = true): 'Already closed'
-2. (auction_open = true) && (Amount <= pre_Balance):
+2. (auction_open = true) && not (Amount > pre_Balance):
    'Not higher than the current highest bid'
@@
 1. not (auction_open = true): 'Already closed'
-2. (auction_open = true) && (Sender != contract_owner): 
+2. (auction_open = true) && not (Sender = contract_owner): 
     'Not the owner'
@@
 1. (paused = true): 'TokenOperationsArePaused'
-2. not (paused = true) &&
-   get_big_map (from, ledger) = None : 'NotEnoughBalance'
-3. not (paused = true) &&
-   get_big_map (from, ledger) = Some sbvar &&
-   sbvar = Pair sbvar1 sbvar2 &&
-   sbvar1 < value : 'NotEnoughBalance'
-4. not (paused = true) &&
-   get_big_map (from, ledger) = Some sbvar &&
-   sbvar = Pair sbvar1 sbvar2 &&
-   get_map (Sender, sbvar2) = Some sbvar3 &&
-   sbvar3 < value: 'NotEnoughAllowance'
+2. not (paused = true) 
+   && get_big_map (from, ledger) = None : 'NotEnoughBalance'
+3. not (paused = true) 
+   && get_big_map (from, ledger) = Some sbvar 
+   && sbvar = Pair sbvar1 sbvar2 
+   && not (sbvar1 >= value) : 'NotEnoughBalance'
+4. not (paused = true) 
+   && get_big_map (from, ledger) = Some sbvar 
+   && sbvar = Pair sbvar1 sbvar2 
+   && get_map (Sender, sbvar2) = Some sbvar3 
+   && sbvar1 >= value 
+   && not (sbvar3 >= value): 'NotEnoughAllowance'
 \end{lstlisting}
@@
 1. (paused = true): 'TokenOperationsArePaused'
-2. not (paused = true) &&
-   get_big_map (Sender, ledger) = Some sbvar &&
-   sbvar = Pair sbvar1 sbvar2 &&
-   get_map (spender, sbvar2) = Some sbvar3 &&
-   not (value = 0) &&
-   not (sbvar3 = 0): 'UnsafeAllowanceChange'
+2. not (paused = true) 
+   && get_big_map (Sender, ledger) = Some sbvar 
+   && sbvar = Pair sbvar1 sbvar2 
+   && get_map (spender, sbvar2) = Some sbvar3 
+   && not (value = 0) 
+   && not (sbvar3 = 0): 'UnsafeAllowanceChange'
 \end{lstlisting}

### 2024-01-17 papers/static-checker/ecoop2024/ecoop2024.tex
kolibri code and picture
code updated
cosmetics

@@
 \KSPEC, \KCODE, \KINPUT, \KOUTPUT, \KPRECONDI, and \KPOSTCONDI\ are
-keywords. The \KNAME\ is replaced by the contract name. In the input
-and output fields, the input and output terms are specified.
-The input and output terms represent Michelson terms, which can be either concrete values or symbolic values, including variables.
-The terms are specified using the syntax defined in Fig.
-\ref{fig:syntax-terms-predicates}.
-A term \textbf{t} comprises constants of the sort \text{nat} (natural number), \text{int} (integer), \text{string} (string), and \text{b} (bytes) along with their respective types.
-As a syntactic sugar, the type can be omitted except for the type \text{nat} to distinguish it from integer numbers.
-It also encompasses all blockchain constants \textbf{c}, such as Amount and Sender.
-When a variable appears for the first time, it must be accompanied by its corresponding type declaration.
-Subsequent mentions can omit the type declaration.
-The language supports essential Michelson types, as shown in Fig.
-\ref{fig:types}, where \textbf{cpt} denotes comparable types.
-The types include basic data types such as integer, string, list, set, pair, option and map.
-Additionally, there are some typical types related to the blockchain, such as \text{mutez} and \text{contract T}, representing types for tokens and smart contracts on the Tezos blockchain, respectively.
+keywords. The \KNAME\ is replaced by the contract name. The \KINPUT{}
+and \KOUTPUT{} fields specify the input and output terms, which are
+patterns on Michelson values that correspond to the top value of the
+initial and final stack. A pattern can be a concrete value or it may
+contain symbolic variables. Fig.~\ref{fig:syntax-terms-predicates}
+contains the grammar of terms: A term \textbf{t} can consist of
+constants of the sort \text{nat} (natural number), \text{int}
+(integer), \text{string} (string), and \text{b} (bytes) along with
+their respective types. The type annotation may be omitted except for
+the type \text{nat} to distinguish it from integer numbers.  It also
+encompasses all blockchain constants \textbf{c}, such as Amount and
+Sender. When a variable appears for the first time, it must be
+accompanied by its corresponding type declaration. Subsequent mentions
+can omit the type declaration. The language supports essential
+Michelson types, as shown in Fig.~\ref{fig:types}, where \textbf{cpt}
+denotes comparable types. Types include basic data types such as
+integer, string, list, set, pair, option, and map. Additionally, there
+are some typical types related to the blockchain, such as \text{mutez}
+and \text{contract T}, representing types for tokens and smart
+contracts with a parameter of type $T$ on the Tezos blockchain.
 
@@
 specified in the output field. The syntax allows us to specify both
-incomplete and complete smart contracts\footnote{The tool has been adapted to accommodate incomplete contract codes that take input stacks and produce output stacks with more than one element.
-This modification is feasible from a technical standpoint, as the current tool can effectively handle such cases.}.
-For a complete smart contract, the output should be a pair consisting of an operation list and the storage's state after the completion of the code.
-For verification purposes we elide the operation list and represent the output solely by the term of the value in the storage after the execution concludes.
-In some cases, the output term can be omitted for a complete contract, given that the input term must be a pair
+incomplete and complete smart contracts\footnote{The tool can
+  accommodate incomplete contract codes that take input stacks and
+  produce output stacks with more than one element, but this is
+  currently not reflected in the syntax.}. For a complete smart
+contract, the output should be a pair consisting of an operation list
+and the storage's state after the completion of the code.  For
+verification purposes we elide the operation list and represent the
+output solely by the term of the value in the storage after the
+execution concludes. In some cases, the output term can be omitted for
+a complete contract, given that the input term must be a pair 
 of parameters and storage. Hence the storage term is part of the
@@
 
-Formally, the pre- and postcondition instances are formulas in first-order logic that can be handled by an SMT solver (in our case, Z3).
-The specification language is constituted of predicates.
-The syntax predicates are defined in Figure~\ref{fig:syntax-terms-predicates}.
-Formulas that are used in assertions or added to solvers are terms of sort Boolean.
-Otherwise, terms of
+Formally, the pre- and postcondition instances are formulas in
+first-order logic that can be handled by an SMT solver (in our case,
+Z3). The specification language is built from
+predicates. Figure~\ref{fig:syntax-terms-predicates} defines the
+syntax of predicates. Formulas that are used in assertions or added to solvers are terms of sort Boolean. Otherwise, terms of
 Boolean and non-Boolean sort may be mixed in any combination where
-sorts match up.
-Several functions are defined, such as the function \text{get\_map (e1, e2)} for accessing an element in a map.
-This function returns \text{None} if there is no key \text{e1} in the map \text{e1}, or the corresponding value of the key otherwise.
-Another function, \text{get\_contract (e1, e2)}, casts the address \text{e2} to a real contract on the Tezos blockchain.
-It returns \text{None} if there is no existing contract on the Tezos block chain with an entrypoint of type \text{e1} associated with the address \text{e2}, or it returns the contract otherwise.
-
-Some other functions are defined as predicates, such as \text{transfer\_token} (\text{e1}, \text{e2}, \text{e3}).
-This implies that there is an operation in the operation list, after executing the smart contract code, which indicates the transfer of \text{e2} amount of tokens to the address \text{e3} along with the data \text{e1}\footnote{While some additional functions and both universal and existential quantifiers are implemented, they pose no technical problems and are similar to existing supported functions.
-However, the conversion to Z3 formulas in the Z3 OCaml library takes some time.}.
+sorts match up. Several functions are predefined, such as the function
+\text{get\_map (e1, e2)} for accessing an element in a map. This
+function returns \text{None} if there is no key \text{e1} in the map
+\text{e1}, or the corresponding value of the key otherwise. Another
+function, \text{get\_contract (e1, e2)}, casts the address \text{e2}
+to a real contract on the Tezos blockchain. It returns \text{None} if
+there is no existing contract on the Tezos block chain with an
+entrypoint of type \text{e1} associated with the address \text{e2}, or
+it returns the contract otherwise.
+
+Some other functions are defined as predicates, such as
+\text{transfer\_token} (\text{e1}, \text{e2}, \text{e3}). This
+predicate holds if there is an operation in the operation list, after
+executing the smart contract code, which indicates the transfer of
+\text{e2} amount of tokens to the address \text{e3} along with the
+parameter \text{e1}\footnote{It is straightforward to add further
+  predicates if a mapping to Z3 formulas can be defined.}.
 
@@
 
-Let us consider a fragment code of the contract \texttt{Sub}  in Listing
+Let us consider a code fragment of the contract \texttt{Sub}  in Listing
 \ref{lst:sub-contract-specification} as an example of a property
@@
 element, which is a pair of two integers, symbolically specified in
-the \lstinline|input| field. The program first duplicates the pair. It then unpairs the input pair to obtain two elements as two integers \lstinline/x/ and \lstinline/y/.
+the \lstinline|input| field. The program first duplicates the pair. It
+then unpairs the input pair to obtain two elements as two integers
+\lstinline/x/ and \lstinline/y/. 
 Next, the program performs a comparison between
@@
 that the integer \lstinline/x/ is greater than or equal to  \lstinline/y/. The postcondition asserts that the result
-\lstinline/z/ is greater than or equal to the substract of \lstinline/x/ and \lstinline/y/, which is greater or equal to zero. The symbol \lstinline/&&/ stands for logical predicate conjunction.
+\lstinline/z/ is greater than or equal to the substract of
+\lstinline/x/ and \lstinline/y/, which is greater or equal to
+zero. The symbol \lstinline/&&/ stands for logical predicate
+conjunction.
 
@@
 address, and the second element is the contract owner's address. The
-current highest bid is reflected in the balance of the contract.
+current highest bid is reflected in the balance of the contract before
+the next bid is invoked.
 
@@
 \lstinline/post_/ to the variable names to refer to the storage
-returned by the program. The output term could be safely removed in
-this example because the tool automatically generates an output
-term corresponding the one specified here.
+returned by the program.
+% The output term could be safely removed in
+% this example because the tool automatically generates an output
+% term corresponding the one specified here.
 
@@
 should be able to bid on the contract or the contract owner should be
-able to close it (lines 28-35). Furthermore, the bid call can happen
+able to close it (lines 28-35). Otherwise, the owner's original
+deposit is lost. Furthermore, the bid call can happen
 successfully after another if the new bid is higher than the previous

### 2024-01-17 papers/static-checker/ecoop2024/ecoop2024.tex
appendix
change the figures (kolibri) and (aution)

@@
     \centering
-    \includegraphics[width=1.1\textwidth]{auction-life-cycle}
+    \includegraphics[width=0.9\textwidth]{auction}
     \caption{Auction contract life cycle}
@@
 overlays through smart contracts on an existing blockchain. Two common
-categories are: (1) Fungible Tokens (FT), which are interchangeable
+categories are: (1) Fungible Tokens (FTs), which are interchangeable
 and (2) Non-Fungible Tokens (NFTs), which represent unique digital
@@
 4. not (paused = true) 
+   && get_big_map (from, ledger) = Some sbvar 
+   && sbvar = Pair sbvar1 sbvar2 
+   && get_map (Sender, sbvar2) = None: 'NotEnoughAllowance'
+5. not (paused = true) 
    && get_big_map (from, ledger) = Some sbvar 
@@
 \lstinline/ledger/ big map and (2) if it is not. For the former case,
-lines 5-8 specify that \lstinline/owner/ is in the \lstinline/ledger/
+lines 3-5 specify that \lstinline/owner/ is in the \lstinline/ledger/
 big map, as the \lstinline/get_big_map/ function returns a value
@@
 map \lstinline/m/. The postcondition guarantees that the storage
-remains unchanged, as specified in lines 10-13, and the call returns a
+remains unchanged, as specified in lines 6-11, and the call returns a
 \lstinline/TRANSFER_TOKENS/ operation with the \lstinline/k/ number
 and \lstinline/Amount/ to be passed to address \lstinline/c/. The
-precondition in lines 16-17 specifies the latter case when the
+precondition in lines 13-20 specifies the latter case when the
 \lstinline/owner/ does not exist in the big map \lstinline/ledger/; in
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{kolibri}
+    \includegraphics[width=0.8\textwidth]{kolibri(1)}
     \caption{Kolibri oracle entrypoint relations}
@@
     string (pair timestamp nat)), harbinger) = Some c
-    post-condition := state = 1
+    post-condition := post_state = 1
        && client = Some (b: address) ;
@@
        && get_contract (nat, a) = Some c    
-    post-condition := state = 0 
+    post-condition := post_state = 0 
        && post_client = None 
@@
     pre-condition :=  (Sender = governor)                  
-    post-condition := (governor = gover) 
+    post-condition := (post_governor = gover) 
        && (post_maxDelay = maxDelay) 
@@
     pre-condition := (Sender = governor)             
-    post-condition := (maxDelay = delay) 
+    post-condition := (post_maxDelay = delay) 
        && (post_client = client) 
@@
      && (Now - t < maxDelay)  
+     && client = Some a 
+     && get_contract (nat, a) = Some c    
   | (%getXtzUsdRate_callback  -> %getXtzUsdRate) with 
@@
 && (client = Some sbvar) 
-&& get_contract (Nat, sbvar) = None: Unit
+&& get_contract (nat, sbvar) = None: Unit
 7. (state = 1) &&  (Sender = harbinger) && ('XTZUSD' = s)
@@
 \bibliography{ecoop2024}
+\appendix
 \include{appendix}

### 2024-01-18 papers/static-checker/ecoop2024/ecoop2024.tex
final cosmetics

@@
 
-\title{A Formal Verification Framework for Smart Contracts Based on Symbolic Execution} %TODO Please add
+\title{A Formal Verification Framework for Tezos Smart Contracts Based on Symbolic Execution} %TODO Please add
 
@@
 verification tool for smart contracts on the Tezos blockchain \cite{tezos-whitepaper}, written in
-Michelson \cite{michelson}, although our design is widely applicable. SCV relies on
+Michelson \cite{michelson}. SCV relies on
 symbolic execution backed by an SMT solver to simulate the
@@
 
-Our contributions are as follows.
+Our contributions are as follows and supported by the upcoming
+artifact submission.
 \begin{enumerate}
@@
   significant subset of Michelson.
-\item Two case studies where we apply SCV to verify real life smart
-  contracts deployed on the Tezos blockchain:
+\item Two case studies that verify smart
+  contracts deployed on the Tezos blockchain with SCV:
   \begin{itemize}
@@
     applications;
-  \item the Kolibri oracle contract that injects currency exchange
+  \item Kolibri, an oracle contract that injects currency exchange
     rates from an external system.
@@
 if contract execution runs out of gas, it is aborted before it can
-perform any visible change. The use of the balance is up to the
-discretion of the contract code.
+perform any visible change. Use of the balance is up to the contract code.
 
@@
 
-\section{A Domain Specific Language For Smart Contract Property Specification}
+\section{SCV: A Domain Specific Language For Smart Contract Property Specification}
 \label{sec:domain-specific-language}
@@
 % to verify smart contract code before interaction.
-Our framework contains a domain-specific language (DSL) to specify
+Our framework SCV contains a domain-specific language to specify
 mathematical properties of smart contracts.
-The DSL is designed to allow users to write formulas that align with
+SCV is designed to allow users to write formulas that align with
 the capabilities of the underlying SMT solver (Z3).
@@
  \Mid \text{get\_big\_map} (\textbf{e1}, \textbf{e2})  \\
- &\Mid \text{get\_contract} (\textbf{e1}, \textbf{e2})   
+ &\Mid \text{get\_contract} (T, \textbf{e})   
  \Mid \text{get\_substring} (\textbf{e1}, \textbf{e2}, \textbf{e3})   \\
@@
  \Mid \text{contain} (\textbf{e1}, \textbf{e2}) \\
-& \Mid \textbf{p} \text{ and } \textbf{p}\Mid \textbf{p} \text{ or } \textbf{p}  \Mid \textbf{p} \text{ nor } \textbf{p} \Mid  \text{ not } \textbf{p} \Mid \textbf{p} \text{ => } \textbf{p} \\
+& \Mid \textbf{p} \text{ \&\& } \textbf{p}\Mid \textbf{p} \text{ or } \textbf{p}  
+% \Mid \textbf{p} \text{nor } \textbf{p} 
+\Mid  \text{ not } \textbf{p} \Mid \textbf{p} \text{ => } \textbf{p} \\
 \end{align*}
-\caption{Syntax of terms, t and predicates, p}
+\caption{Syntax of constants, \textbf{c}, terms, \textbf{t}, expressions, \textbf{e}, and predicates, \textbf{p}}
 \label{fig:syntax-terms-predicates}
@@
   output := t'
-  pre-condition := cd
-  post-condition := cd'
+  pre-condition := p
+  post-condition := p'
 \end{lstlisting}
@@
 function returns \text{None} if there is no key \text{e1} in the map
-\text{e1}, or the corresponding value of the key otherwise. Another
-function, \text{get\_contract (e1, e2)}, casts the address \text{e2}
-to a real contract on the Tezos blockchain. It returns \text{None} if
-there is no existing contract on the Tezos block chain with an
-entrypoint of type \text{e1} associated with the address \text{e2}, or
-it returns the contract otherwise.
+\text{e1}, or \text{Some(v)} if $v$ is the value mapped by the key. Another
+function, \text{get\_contract (T, e)}, casts the address \text{e}
+to a contract on the Tezos blockchain. It returns \text{None} if
+there is no contract on the Tezos blockchain with an
+entrypoint of type \text{T} associated with the address \text{e}, or
+it returns the contract in the form \text{Some(c)}.
 
@@
 \lstinline/x/ and \lstinline/y/, which is greater or equal to
-zero. The symbol \lstinline/&&/ stands for logical predicate
-conjunction.
+zero. The symbol \lstinline/&&/ stands for conjunction.
 
@@
       output := t1'
-      pre-condition := cd1
-      post-condition := cd1'
+      pre-condition := p1
+      post-condition := p1'
    entrypoint %b 
@@
       parameter := t2
-      pre-condition := cd1
-      post-condition := cd1'
+      pre-condition := p1
+      post-condition := p1'
    entrypoint %b 
@@
 an entrypoint relation. An entrypoint relation can be specified as
-\lstinline/%a -> %b with cd/, which starts with the name
+\lstinline/%a -> %b with p/, which starts with the name
 \lstinline/%a/ of the entrypoint and is followed by the keyword
@@
 following symbol \lstinline/->/ indicates that from the entrypoint
-that satisfies the condition \lstinline/cd/, it is possible  to call
+that satisfies the condition \lstinline/p/, it is possible  to call
 the entrypoint \lstinline/%b/. One smart contract specification can
@@
 \label{sec:static-checker}
-The static checker now performs the verification process by employing symbolic execution against the property specification in the DSL.
+The static checker now performs the verification process by employing symbolic execution against the property specification in SCV.
 It utilizes the results from the previous phases, including symbolic execution, Z3 formulas representing pre and post conditions, and path conditions.
@@
 \label{sec:life-cycle-check}
-An entrypoint relation can be defined as \lstinline/(%a -> %b) with cd/, indicating that after invoking the entrypoint \lstinline/%a/, it is permissible to call the entrypoint \lstinline/%b/ if the condition \lstinline/cd/ is satisfied.
+An entrypoint relation can be defined as \lstinline/(%a -> %b) with p/, indicating that after invoking the entrypoint \lstinline/%a/, it is permissible to call the entrypoint \lstinline/%b/ if the condition \lstinline/p/ is satisfied.
 The presence of the keyword \lstinline/not/ at the beginning signals an impossibility.
-Note that \lstinline/with cd/ may be omitted when no condition is needed.
+Note that \lstinline/with p/ may be omitted when no condition is needed.
 
@@
 Each $s_{i}$ in $S_a$ is associated with a path condition $\Theta_i$ and is represented as a stack containing a single element—a pair consisting of an operation list ($\VOPERATIONLIST_i$) and the storage $\VSTORAGE_i$.
-For each $s_{i}$, symbolic execution is performed on the entrypoint \lstinline/%b/ using input as a pair of the parameter and the storage $\VSTORAGE_i$, constrained by $\Theta_i$ and the condition \lstinline/cd/.
-In the execution state space, a state $s_{j}$ with the path condition $\Theta_j$ is considered reachable if ($\Theta_i$ $\land$ \lstinline/cd/ $\land$ $\Theta_j$) is satisfiable, and $\neg$ ($\Theta_i$ $\land$ \lstinline/cd/ $\rightarrow$ $\Theta_j$) is unsatisfiable.
+For each $s_{i}$, symbolic execution is performed on the entrypoint \lstinline/%b/ using input as a pair of the parameter and the storage $\VSTORAGE_i$, constrained by $\Theta_i$ and the condition \lstinline/p/.
+In the execution state space, a state $s_{j}$ with the path condition $\Theta_j$ is considered reachable if ($\Theta_i$ $\land$ \lstinline/p/ $\land$ $\Theta_j$) is satisfiable, and $\neg$ ($\Theta_i$ $\land$ \lstinline/p/ $\rightarrow$ $\Theta_j$) is unsatisfiable.
 Let $S_b$ denote the set of these reachable states.
@@
 Otherwise, it is considered a success.
-Let $R$ be the set containing all such states $s_{i}$ in $S_a$ where it is successful to call the entrypoint \lstinline/%b/ with the condition \lstinline/cd/.
-If $R$ is non-empty, then \lstinline/(%a -> %b) with cd/ holds.
-Otherwise, it is false, signifying \lstinline/not (%a  -> %b) with cd/.
+Let $R$ be the set containing all such states $s_{i}$ in $S_a$ where it is successful to call the entrypoint \lstinline/%b/ with the condition \lstinline/p/.
+If $R$ is non-empty, then \lstinline/(%a -> %b) with p/ holds.
+Otherwise, it is false, signifying \lstinline/not (%a  -> %b) with p/.
 
@@
 Section~\ref{sec:background}.  Here we consider the changes needed for
-symbolic execution of Michelson programs.
+symbolic execution of Michelson programs. We only discuss symbolic
+execution for some select instructions. The
+appendix~\ref{sec:concl-sect-append} specifies further instructions,
+but may be skipped by the reviewers.
 

### 2024-04-04 papers/assertion-contract/assertion_contract_app/paper.tex
first draft

% APLAS 2021: Regular research papers should not exceed 18 pages in
% the Springer LNCS format(LaTeX template), including bibliography and
% figures.
% Lightweight double-blind: Author names and institutions must be
% omitted and References to the authors’ own related work should be in
% the third person 
%
\documentclass[runningheads]{llncs}
\pdfoutput=1
%\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{graphicx}
%\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathpartir}
\usepackage{graphicx}
%\usepackage{fixme}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{titling}

%\input{macros}
%\input{setup}

% ------------------- colors -------------------
\definecolor{darkgreen}{rgb}{0.0, 0.5, 0.0}
\definecolor{UniBlue}{RGB}{0, 74, 153}
\definecolor{UniRed}{RGB}{193, 0, 42}
\definecolor{UniGrey}{RGB}{154, 155, 156}
\definecolor{cverbbg}{gray}{0.93}

\newcommand{\todo}[1]{\textbf{\textcolor{red}{(TODO: #1)}}}

\begin{document}
%
\title{Assertion Contracts}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Thi Thu Ha Doan\orcidID{0000-0001-7524-4497}\and Peter Thiemann\orcidID{0000-0002-9000-1239}}

%
%\authorrunning{Ha Doan, P. Thiemann}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
%\institute{University of Freiburg, Germany \\ \email{\{doanha,thiemann\}@informatik.uni-freiburg.de}
%}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
In some situations on the blockchain, verifying certain properties of a parameter requires significant gas costs or may even become infeasible due to the gas limits. This study proposed a distributed verification assertion protocol. The core concept involves distributing the negation form of the assertion to validators instead of verifying it on-chain. Validators’ off-chain attempts to find a solution to the negation form and discover a counterexample. When a counterexample is found, it can be submitted to the chain. In addition, we propose a proof-of-work-based incentive mechanism to encourage validators to participate in the distributed verification process. To operationalize these ideas, we suggest a practical model that addresses security concerns. Furthermore, we implemented a prototype of the proposed protocol and conducted a cost analysis to demonstrate the advantages of our method in terms of cryptocurrency, making it practically useful.
 \keywords{}
\end{abstract}
%
%
%
\section{Introduction}
\label{sec:introduction}
\section{Primaries}
\label{sec:primaries}

\section{Distributed Assertion Protocol}
\label{sec:approach}
We propose a novel method to verifying assertions for smart contracts on the blockchain. Our approach involves distributing the assertion verification process and moving it off chain. Only the verification results are submitted to the blockchain. Throughout this distribution, each validator endeavors to identify a counterexample to the assertion. Consequently, rather than checking the entire assertion, it only requires examining specific points on the chain. We propose a proof-of-work-based incentivization method for validators who discover a counterexample and for a portion of the computational effort, thereby incentivizing participation in the distributed verification process.

\subsection{Distributed assertions verification process}
In the context of a domain $A$ and a predicate $P$ on $A$, an assertion is formalized using the universal quantifier as follows:
\begin{gather}
  \label{eq:1}
\forall a \in A. P_{a}
\end{gather}

This formula can be extended to multiple domains as:

\begin{gather}
\label{eq:2}
\forall a \in A, \forall b \in B, \dots .P_{a, b, \dots}
\end{gather}

The negation of the assertion is represented by the existential quantifier formulas:

\begin{gather}
\label{eq:3}
\neg (\forall a \in A. P_{a}) \equiv \exists a \in A. \neg P_{a}
\end{gather}

And for multiple domains, it is as follows:

\begin{gather}
\label{eq:4}
\exists a \in A, \exists b \in B, \dots. \neg P_{a, b, \dots}
\end{gather}

To verify an assertion, it requires iterating over the domain $A$ within the contract. When the domain $A$ is large or the predicate $P$ is complex to evaluate, it incurs a significant amount of gas to perform the verification process on-chain.  Given the current high gas prices, this could result in substantial costs or even impossible due to gas limits. Our approach aims to alleviate this by distributing the negation of the assertion to validators. Each validator endeavors to find a counterexample of the assertion using this negation.

Specifically, each validator attempts to find a counterexample by identifying $a \in A$ such that the negation formula is satisfied. When a counterexample is found, the validator submits it, which is then verified on the chain. The amount of gas required for the computation to check the counterexample on-chain will likely be significantly less than verifying the assertion directly on the chain.

Considering the example where a parameter $p$ is a prime number, the assertion in predicate logic for the parameter is:
\begin{gather}\label{eq:3a}
  (\forall n) (2 \le n \le \sqrt p) \Rightarrow (p \mathbin{\%} n) \ne 0
\end{gather}

\noindent and its negation form is

\begin{gather}\label{eq:3b}
  (\exists n) (2 \le n \le \sqrt p) \wedge (p \mathbin{\%} n) = 0
\end{gather}

\noindent each validator try to genarate  a
random $n$ in the range $2 \le n \le 
\sqrt p$ and checking whether $(p \mathbin{\%} n) = 0$. If the remainder is $0$, the validator found a counterexample.

An other example, consider a contract that takes a sorted array of integers.
\begin{lstlisting}[numbers=none]
contract Sorted {
  function find (int[50] a, int v) public {
    // assume a is sorted
  }
}
\end{lstlisting}
The explicit assertion would be
\begin{gather}\label{eq:1}
  (\forall k) (0\le k <49) \Rightarrow a[k] \le a[k+1]
\end{gather}
While we can check this contract in $O(1)$ time, the constant factor is big! So we
consider its negation.
\begin{displaymath}
  (\exists k) (0\le k <49) \wedge a[k] > a[k+1]
\end{displaymath}
Each validator attempts to find the number $k$ such that the negation is true for such $k$, then the validator has found a counterexample for the sortedness of the array.

If any of the validators identify a violation of an assertion, the final call to the actual work function is aborted. However, if certain requirements are met, the work function is invoked with the parameter.
\subsection{Proof-of-work-based incentivization method}
Finding a counterexample is rewarded, incentivizing validators, but comes at the cost of computing resources. Instances of finding a counterexample may be rare, as callers typically avoid passing invalid parameters into the blockchain. If no counterexample emerges, the verification accuracy depends on the number of wisepoints generated to negate the assertion, with more validators increasing the certainty. Encouraging validators to engage in the verification process even without discovering a counterexample is crucial. Therefore, it is necessary to incentivize this effort. Moreover, it is logical to reward only a portion of the computational effort required. A significant concern arises regarding how to ensure that validators perform the verification computation off-chain to receive the reward, even when no counterexample is foundward.

We propose a proof-of-work-based method to incentivize participants in the distributed verification process. The proposed approach is outlined as follows:

\begin{itemize}
\item There are two ways to reward validators to encourage their participation: to discover a counterexample, and to provide computational proof that they have executed the program to search for a counterexample, even if none is found.
\item To prioritize the discovery of counterexamples, the reward for finding a counterexample is set significantly higher than that for providing a computational proof.
\item The computation of the negation formula is integrated into the computational proof to ensure that the validators cannot produce the proof without executing a negation check.
\item Because the rewards may be limited in quantity, validators are motivated to swiftly verify the parameters to claim the reward before others do so.
\end{itemize}
The next step is to devise a computation proof to incentivize computational effort by utilizing the proof of work concept. Initially, we establish a target hash $t$ that sets the required difficulty level to earn the reward. The objective of the validator is to generate a computation that produces a hash smaller than or equal to the target hash $t$. Seed $s$ was introduced in each verification process. Let $n$ denote the size of domain $A$. Each number $i$ in the range [1, $n$] corresponds to an element in $A$. The seed $s$ is a random number and then reduces modulo $n$ to obtain $i$, which is  associated with an element $a$ in $A$: 
\begin{gather}\label{}
i = s \mod n
\end{gather}
Consequently, each seed $s$ is linked with an element $a$ in the domain $A$, followed by the evaluation of the negation of the assertion $\neg P_{a}$. After conducting the negation check, either a counterexample is identified, or a hash is computed based on the seed $s$ along with the evaluation of the condition $\neg P_{a}$. This hash is then compared with the target hash to ascertain if it meets the criteria for a reward computation. The outcomes of the verification process include either a counterexample, a reward computation, or a non-reward computation.

During the distributed process, each validator consistently generates a seed $s$ and conducts the negation check until the outcome indicates either a counterexample or a reward computation. Upon achieving either of these outcomes, the validator is able to submit it on-chain to claim their reward. Both the counterexample and the computation proof are represented by the seed used, allowing the on-chain compoment to replicate the process to verify its validity. If the verification is successful, the validators will be entitled to receive their reward.

%The next question is associte a seed with an elemnt in the domain. Let $n$ be the size of the domain $A$.  We'll consider two cases: (1) when it is straightforward to associate a natural number $i$ to an element of $A$, such as a natural number, integer, or array, and (2) when it is not.

%In the first case, the seed $s$ is a random number. It is then modulated with the size $n$ to obtain $i$, which is then associated with an element $a$ in $A$.

%\begin{gather}\label{}
%i = s \mod n
%\end{gather}

%In the second case, when it is not straightforward to associate a natural number with an element of the domain, then the seed is limited to the elements of the domain. The concern in this case is that the target $t$ needs to be set up in such a way that there is a guarantee to possibly find a reward computation.

%Let's examine an assertion in smart contract languages such as Solidity and Michelson. An assertion is essentially a predicate logic expressed as a boolean formula computed from relational operators ($=$, $!=$, $>$, $<$, $>=$, $<=$), logical operators ($!$, $\&\&$, $\|$), and expressions. Let $\pi_{P_{a}}$ = {$e_1$, $e_2$, \dots } represent the set of expressions involved in the computation of the predicate $P_a$. The hash of the seed and these expressions ($s$, $\pi_{P_{a}}$) is then computed and compared with the target hash. Since the hash involves $\pi_{P_{a}}$, the validator needs to execute the condition check to find a reward computation.

\section{Practical model}
\subsection{Overview architect}
Distributed verification of assertions is indeed an intriguing concept, yet it faces the following security risks when proposing an incentive method:

\begin{itemize}
\item Front-running attacks: The system is vulnerable to front-running attacks, where an attacker closely monitors the mempool to intercept a seed representing a counterexample or a computation proof, subsequently stealing the reward.
\item Caller exploitation: A caller might exploit the system by running the negation check privately to identify the reward before submitting the parameter on-chain, thereby swiftly claiming the reward ahead of the other validators. 
\item Denial-of-service (DoS) attacks: The system is susceptible to DoS attacks, where a caller inundates the system with numerous invalid parameters, causing congestion and hindering its operation.
\item Reward manipulation: A validator may attempt to manipulate the reward system by resubmitting counterexamples or computation proofs multiple times to multiply their rewards.
\end{itemize}

This section presents a practical model that unifies theoretical principles and addresses the previously mentioned security concerns. The architectural design of this model is depicted in Figure \ref{fig.architect}. The model consists of two main entities: an on-chain assertion contract and off-chain validator contract. In our practical model, three distinct actors play key roles.
\begin{itemize}
\item Owner: responsible for deploying and overseeing both on-chain and off-chain contracts.
\item Callers: engage with on-chain contracts by initiating assertions and interacting with the system.
\item Validators: tasked with validating parameters and ensuring the integrity of the verification process.
\end{itemize}

\begin{figure}
\centering
\includegraphics[scale=.8]{assertion}
\caption{The architecture of the practical model}
\label{fig.architect}
\end{figure}

\subsubsection{On-chain assertion contract}
While additional functions may exist, the assertion contract must encompass the following two essential functions:
\begin{itemize}
\item The \lstinline|submit_parameter| function: Callers utilize this function to submit their parameters for validation. Subsequently, the parameter is distributedly verified by validators.
\item  The \lstinline|claim_reward| function: This function accepts a parameter and a seed as inputs, yielding a result indicating whether the computation from the seed results in a counterexample, a reward computation, or a non-reward computation.
\end{itemize}

While a random number alone is sufficient to indicate the associated element $a$ in the domain $A$, to prevent the front-running attack and the caller exploitation attack, we enhance the randomness of the seed by combining a random number with the validator's address and the timestamps indicating when the parameter is submitted on the chain to calculate the seed. This combination adds an extra level of security. For instance, we can convert the validator's address and timestamps to a numerical value and use this number in combination with a random number to compute the seed. This conversion can be achieved using functions such as \lstinline|init256| in Solidity, which transform an Ethereum address into a numerical value. In this system, even if other validators obtain a random number, they are unable to submit it successfully, as their combination with their address will not yield the correct seed that corresponds to a specific element in the domain. Additionally, a caller cannot run the check before submitting the parameter owing to the timestamp constraints. As a result, any attempt to submit manipulated or before-run seeds will fail to produce either a counterexample or reward computation.

\subsubsection{Storage}
When a parameter is submitted for verification, the following information is stored:
\begin{itemize}
\item Parameter: This includes the parameter itself. In cases where storing the parameter on-chain is impractical because of its size, it is recommended to store only its hash. Despite this, the hash remains sufficient for validation.
%\item Caller Address: This identifies the address of the caller who submitted the parameter. It serves purposes such as tracking submissions, preventing callers from resubmitting parameters, or preventing callers from claiming rewards for their own submitted parameters.
\item Timestamp: This indicates the approximate time when the parameter was submitted. This information is used to prevent caller exploitation security risks.
\item Verification Status Records: These records monitor the progress of the parameter's verification. They include details such as whether a counterexample or reward computation is found. Additionally, they contain information regarding the addresses of the validators and random numbers involved in the verification process. In some applications, multiple computational proofs may be allowed, leading to a list of these records. This information is crucial for determining when a work function can be invoked for that parameter, or when it should be discarded. The validators' addresses and random numbers can also be used to prevent reward-manipulation attacks. Indeed, because a validator with the same random number cannot be resubmitted, the random number serves as a unique identifier in the verification process. This uniqueness prevents validators from resubmitting the same computation proof multiple times to manipulate the rewards or disrupt the integrity of the verification process.
\end{itemize}
In certain applications, one may delete the records after processing is completed for the parameter, especially if a large number of parameters are submitted to manage storage efficiently.

\subsection{Deploying and managing on/off-chain contracts.}
On/off-chain contracts are provided and managed by their respective owners, who assume a primary role in their design. The owner deploys the assertion contract on the blockchain while storing the validator contract off the blockchain, thereby ensuring its accessibility to the validators. There are two approaches to making these contracts available to validators.
\begin{itemize}
\item The owner store the codes on a repository accessible to validators, or upon request, provide them directly to validators.
\item Alternatively, the owner broadcard the contracts to the network using messaging systems such as Waku in Ethereum. Owners should disseminate contracts to the network after deploying the on-chain assertion contracts. In this scenario, the interested validators are responsible for locally storing off-chain code.
\end{itemize}

\subsection{Submitting and verifying a parameter.} The primary entities interacting with the on-chain assertion contract are callers and validators. Callers submit parameters on-chain, while validators verify them off-chain. Subsequently, validators claim their findings of counterexamples or reward computations on-chain. 
\subsubsection{Submitting a parameter} 
Before a parameter can be utilized in the actual work function/contract, a caller must initially submit it via the submit-parameter function in the on-chain assertion contract. When submit the parameter, the caller may need to send along an amount of deposit stake. This deposit serves as a deterrent, as in the event of an invalid parameter, the deposit may be forfeited to prevent callers from submitting invalid parameters solving the DoS attack security risk. Furthermore, the caller may wish to broadcast their parameter to all validators via a messaging system when submitting it online.

%The work contact can only be invoked by the on-chain validation contract after the parameter has been validated if no counterexample is found. The actual work is then performed with the passed parameter.
\subsubsection{Off-chain verification}

After a parameter is submitted and stored on-chain, a validator can commence the verification process. To assess the validity of a parameter, each validator independently executes the off-chain validation contract. A validator may attempt to run the off-chain validation contract multiple times with different random seeds in order to find either a counterexample or a computational proof. It's possible that several attempts may be made before the validator receives an award. In cases where no award is obtained, the validator can rerun the code with a different seed. A function called find-seed could be implemented, which in turn calls the claim-reward function to locate a seed.

All events such as parameter submissions, the discovery of a counterexample, or the presentation of computational proofs can be broadcasted to the network using event emission. Validators can monitor these events to stay updated on the verification status in real-time.

\subsection{Claiming the reward} 
If validators discover a counterexample or an award computation, they provide the seed, a combination of a random number, the parameter's timestamp and the validator's address, along with the parameter to the on-chain assertion contract. The on-chain assertion contract then executes the same claim-reward function, which should yield the same result as the counterexample or award compuation found by the validator.  If the result is correct, there is an award to the validator and the record of the parameter in the storage is updated accordingly. %When a computational proof is submitted and  certain requirements are met, the work function/contract is invoked.

\subsection{Calling a work function}
A work function can indeed be encapsulated either as a private function in the assertion contract or implemented in another contract. In this process, a caller initiates the submission of a parameter for verification by invoking the submit-parameter function within the on-chain assertion contract. Upon successful verification of the parameter, a work contract can be triggered to execute the designated task, operating under the assumption of the parameter's validity.

The invocation of the work function or contract is carried out by the on-chain validation contract or a caller. This call is subject to specific requirements being met, ensuring that the task is executed only when the verification process has been successfully completed and the parameter is deemed valid. By enforcing strict conditions for the execution of the work function or contract based on the outcome of the verification process, the integrity and reliability of the system can be maintained.

The on-chain validation contract calls the work contract with the current parameter and its related information, which is then matched against the stored information of the corresponding parameter. They must match and satisfy additional conditions, such as a certain amount of time having passed, no counterexample being found, and receiving enough computation proofs. If all conditions are met, the actual work is executed, and the record of the parameter may be deleted from memory to free up storage. If no record is found that matches the input data, the actual work with the input data is not performed.

\section{Domain Specification Language for Assertion}
\section{Converter - Generating an Assertion Contracts} 
\section{Prototype Implementations}
\subsection{Sorted array}
%There are two possible data structures for storing such records: map and array. For example, if we assume that a caller can submit only one parameter at a time, we can use a map that associates the caller's address with the parameter's hash and timestamp.
%\begin{lstlisting}[numbers=none]
%   struct Parameter {
%        bytes32 p_hash;
%        uint256 timestamp;
%    }
% mapping (address => Parameter) public parameters;
%\end{lstlisting}

Returning to the sorted array example, given an array $a$ and a seed $s$, the verification function, which is used both on-chain and off-chain, can be implemented as follows in Solidity.
\begin{lstlisting}[numbers=none]
/* The difficulty is used to determine the computation effort.*/
uint diff = 100;
uint target = 2 ** (256 - diff);

/* The results: 0 = non-reward computation,
                1 = reward computation, 
                2 = counterexample 
*/

function verify_parameter(uint[] memory a, uint s)
public view returns (uint) {
  uint n = a.length - 1; 
  uint i = s % n;

  bool c = (a[i] > a[i + 1]);

  uint result = 0; /* an non-reward computational */ 
  if (c)  
    result = 2; /* a counterexample */
  else {
    uint current_hash = 
    uint (keccak256(abi.encodePacked(s, c, a[i], a[i + 1])));
    if (current_hash <= target) 
    result = 1; /* a reward computation */ 
  }

  return result;           
}

\end{lstlisting}

In the first case, the difficulty (\lstinline|diff|) determines the amount of computation effort needed to find a reward computation. The size of the domain here is denoted as \lstinline|n| which is one size less than the array size. Given the parameter as an array \lstinline|a|, the validator's address  \lstinline|val_addr| and a seed \lstinline|s| as input, the condition \lstinline|c| is the less than or equal comparison of two expressions, which are array elements \lstinline|a[i]| and \lstinline|a[i + 1]|, indicating that the array is not sorted. %So $\pi_{P_{i}}$ = \{\lstinline|a[i]|, \lstinline|a[i + 1]|\}. 
The condition is checked first to detect the counterexample. If not, the hash is computed to determine if it is less than the target hash. If so, a reward computation is found.

\subsection{Prime numbers.}

\begin{lstlisting}[numbers=none]

    /**
    * The difficulty for a computational proof
    */
    uint diff = 100;
    uint public target = 2 ** (256 - diff);

    /**
    * The result: 0 = non-award, 
                  1 = proof, 
                  2 = counterexample
    */

    function validate(uint a, uint seed) 
    public view returns (uint) {
        uint range = a / 2 - 2; 
        uint r = seed % range + 2;
        uint cal = a % r;
        bool p = (cal == 0);

        uint result = 0; // an non-award computational proof 
        if (p)  
            result = 2; // a counterexample
        else 
            {
                uint current_hash = 
                    uint (keccak256(abi.encodePacked(seed, cal)));
                if (current_hash <= target) 
                    result = 1; // a computational proof    
            }
        return result;           
    }
}

\end{lstlisting}

%\paragraph{Sorted arrays.}{ on/off-chain assertion program for sorted arrays}
%\begin{lstlisting}[numbers=none]
%pragma solidity >=0.7.0 <0.9.0;

%/**
% * On/off-chain assertion contract 
% * to check counterexamples/computational proofs
% */
%contract Validator{

 %   /**
 %    * The difficulty for a computational proof
 %    */
 %   uint diff = 1;
 %   uint public target = 2 ** (256 - diff); 
 %
 %   /**
 %  * The result: 0 = non-award, 1 = proof, 
 %   2 = counterexample
 %   */
 %
 %   function verify_parameter(uint[] memory a, uint seed)
 %   public view returns (uint) {
 %       uint range = a.length - 1; 
 %      require(range > 0, "invalid range");
 %       uint n = seed % range;
 %       
 %       bool p = (a[n] > a[n + 1]);
 %
 %       uint result = 0; // an non-award computational proof 
 %       
 %       if (p)  
 %           result = 2; // a counterexample
 %       else 
 %           {
 %           uint current_hash = 
 %               uint (keccak256(abi.encodePacked(seed, a[n], a[n + 1])));
 %           if (current_hash <= target) 
 %               result = 1; // a computational proof      
 %       }             
 %       return result;           
 %   }
%}

%\end{lstlisting}

\subsection{Heaps.}
\begin{lstlisting}[numbers=none]
    /**
    * The difficulty for a computational proof
    */
    uint diff = 100;
    uint public target = 2 ** (256 - diff);

    /**
    * Check a counterexample/ computational proof
    * The result from a validator
    * 0 = non-award, 1 = proof, 
    2 = counterexample
    */

    function validate(uint[10] memory a, uint seed) 
    public view returns (uint) {
        uint range = a.length; 
        uint k = seed % range + 1;

        uint cal_1 = a[k];
        uint cal_2 = a[(k - 1) / 2];

        bool p = (cal_1 < cal_2);

        uint result = 0; // an non-award computational proof 
        if (p)  
            result = 2; // a counterexample
        else {
            uint current_hash = 
                uint (keccak256(abi.encodePacked(seed, cal_1, cal_2)));
            if (current_hash <= target) 
                result = 1; // a computational proof      
        }              
        return result;           
    }
}

\end{lstlisting}

\subsection{Coprime numbers.}

\begin{lstlisting}[numbers=none]

    /**
    * The difficulty for a computational proof
    */
    uint diff = 100;
    uint public target = 2 ** (256 - diff);

    /**
    * The result: 0 = non-award, 1 = proof, 
    2 = counterexample
    */

    function validate(uint a, uint b, uint seed)
    public view returns (uint) {
        uint range;
        if (a >= b) { range = a - 2; }
        else {range = b - 2;}

        uint r = seed % range + 2;
        require(range != 0, "invalid range");

        uint cal_1 = a % r;
        uint cal_2 = b % r;

        bool p = (cal_1 == 0) && (cal_2 == 0);

        uint result = 0; // an non-award computational proof 
        if (p)  
            result = 2; // a counterexample
        else {
            uint current_hash = 
                uint (keccak256(abi.encodePacked(seed, cal_1, cal_2)));
            if (current_hash <= target) 
                result = 1; // a computational proof      
        }              
        return result;           
    }
}

\end{lstlisting}

\section{Cost Analysis}
\section{Related work}
\section{Conclusion}

%\newpage
%\addcontentsline{toc}{chapter}{Appendix}
%\input{appendix}

%Let's examine an assertion in smart contract languages such as Solidity and Michelson. An assertion is essentially a predicate logic expressed as a boolean formula computed from relational operators ($=$, $!=$, $>$, $<$, $>=$, $<=$), logical operators ($!$, $\&\&$, $\|$), and expressions. Let $\pi_{P_{a}}$ = {$e_1$, $e_2$, \dots } represent the set of expressions involved in the computation of the predicate $P_a$. The hash of the seed and these expressions ($s$, $\pi_{P_{a}}$) is then computed and compared with the target hash. Since the hash involves $\pi_{P_{a}}$, the validator needs to execute the condition check to find a reward computation.
\newpage
\bibliographystyle{splncs04}
\bibliography{bio}
\end{document}

### 2024-04-04 papers/assertion-contract/assertion_contract_app/paper.tex
rewise the paper

@@
 
+An assertion in smart contract languages, such as Solidity and Michelson, is essentially predicate logic expressed as a Boolean formula computed from relational operators ($=$, $!=$, $>$, $<$, $>=$, $<=$), logical operators ($!$, $\&\&$, $\|$), and expressions.
+To represent the set of expressions involved in the computation of the predicate $P_a$, let $\pi_{P_{a}}$ = {$e_1$, $e_2$, \dots }.
+The expressions $\pi_{P_a}$ can be used to compute the hash, which involves the validator executing the condition check to find a reward computation.
+
 \subsubsection{Storage}
@@
 Given the parameter as an array \lstinline|a|, the validator's address  \lstinline|val_addr| and a seed \lstinline|s| as input, the condition \lstinline|c| is the less than or equal comparison of two expressions, which are array elements \lstinline|a[i]| and \lstinline|a[i + 1]|, indicating that the array is not sorted.
-%So $\pi_{P_{i}}$ = \{\lstinline|a[i]|, \lstinline|a[i + 1]|\}.
+So $\pi_{P_{i}}$ = \{\lstinline|a[i]|, \lstinline|a[i + 1]|\}.
 The condition is checked first to detect the counterexample. If not, the hash is computed to determine if it is less than the target hash. If so, a reward computation is found.
@@
 \end{lstlisting}
-
-%\paragraph{Sorted arrays.}{ on/off-chain assertion program for sorted arrays}
-%\begin{lstlisting}[numbers=none]
-%pragma solidity >=0.7.0 <0.9.0;
-
-%/**
-% * On/off-chain assertion contract 
-% * to check counterexamples/computational proofs
-% */
-%contract Validator{
-
- %   /**
- %    * The difficulty for a computational proof
- %    */
- %   uint diff = 1;
- %   uint public target = 2 ** (256 - diff); 
- %
- %   /**
- %  * The result: 0 = non-award, 1 = proof, 
- %   2 = counterexample
- %   */
- %
- %   function verify_parameter(uint[] memory a, uint seed)
- %   public view returns (uint) {
- %       uint range = a.length - 1; 
- %      require(range > 0, "invalid range");
- %       uint n = seed % range;
- %       
- %       bool p = (a[n] > a[n + 1]);
- %
- %       uint result = 0; // an non-award computational proof 
- %       
- %       if (p)  
- %           result = 2; // a counterexample
- %       else 
- %           {
- %           uint current_hash = 
- %               uint (keccak256(abi.encodePacked(seed, a[n], a[n + 1])));
- %           if (current_hash <= target) 
- %               result = 1; // a computational proof      
- %       }             
- %       return result;           
- %   }
-%}
-
-%\end{lstlisting}
 

### 2024-04-09 papers/assertion-contract/assertion-contract-cons/paper.tex
Write Parameter Distributed Verification Approach

--- 2022-02-17 papers/assertion-contract/paper.tex
@@
 
-\input{macros}
+%\input{macros}
 %\input{setup}
@@
 %
-%\author{Thi Thu Ha Doan\orcidID{0000-0001-7524-4497}\and Peter Thiemann\orcidID{0000-0002-9000-1239}}
+\author{Thi Thu Ha Doan\orcidID{0000-0001-7524-4497}\and Peter Thiemann\orcidID{0000-0002-9000-1239}}
 
@@
 \begin{abstract}
+
  \keywords{}
 \end{abstract}
-
 %
@@
 \label{sec:introduction}
+
 Every computation performed by a Smart Contract on the blockchain generates costs. Each
@@
 
-To obtain an estimate of the number of validators needed to find a counterexample with
-high probibility, 
-let's assume the array is unsorted only at position $0$, the size of the array is $n$,
-and the number of validators is $m$. Each validator independently has a probability of
-$1/n$ to detect the problem and thus probability $\frac{n-1} n$ not to detect the
-problem. Hence, if we assume that each $k$ is chosen independenty from a uniform distribution,
-the probability that no validator checks at
-position $0$ converges to $0$ as the number of validators approaches infinity.
-\begin{displaymath}
-  \lim_{m\to\infty}\frac{(n-1)^m}{n^m}
-  = \lim_{m\to\infty} \left(\frac{n-1}{n}\right)^m
-  = 0
-\end{displaymath}
+%To obtain an estimate of the number of validators needed to find a counterexample with high probibility, let's assume the array is unsorted only at position $0$, the size of the array is $n$,and the number of validators is $m$.
+Each validator independently has a probability of $1/n$ to detect the problem and thus probability $\frac{n-1} n$ not to detect the problem.
+Hence, if we assume that each $k$ is chosen independenty from a uniform distribution, the probability that no validator checks at position $0$ converges to $0$ as the number of validators approaches infinity.
+%\begin{displaymath}
+%  \lim_{m\to\infty}\frac{(n-1)^m}{n^m}
+%  = \lim_{m\to\infty} \left(\frac{n-1}{n}\right)^m
+%  = 0
+%\end{displaymath}
 
@@
 \end{gather}
+
 \section{Primaries}
@@
 
-\subsection{Smart Contract}
-\label{subsec:smart-contract}
+\section{Parameter Distributed Verification Approach for Blockchain System}
+\label{sec:approach}
+In this section, we aim to introduce an approach leveraging distributed aspects to address the challenging verification issue within blockchain systems.
+Specifically, we focus on verifying a substantial parameter, crucial for executing a smart contract call.
 
-\subsection{Assertion Problem}
-\label{subsec:problem}
+Our attention is drawn to the verification problem, which can be articulated as a logical formula presented in conjunction form as follows:
 
-\section{Distributed Assertion Protocol}
-\label{sec:approach}
-We propose an assertion verification approach for smart contracts.
-The idea underlying our approach is that the assertion is distributed to be verified by validators.
-During the distribution, each validator strives to find a counterexample for the assertion.
-Each of these validators then checks only a random point in the range of the parameter.
-Considering the example where a parameter $p$ is a prime number, the assertion in predicate logic for the parameter is
-\begin{gather}\label{eq:3a}
-  (\forall n) (2 \le n \le \sqrt p) \Rightarrow (p \mathbin{\%} n) \ne 0
-\end{gather}
+\[ \bigwedge_{i = 1}^{n} P_{i} \]
 
-\noindent and its negation form is
+Verifying the formula centrally becomes resource-intensive, both in terms of time and computer resource when the number $n$ is big or when the predicates $P_{i}$ are complex to compute.
 
-\begin{gather}\label{eq:3b}
-  (\exists n) (2 \le n \le \sqrt p) \wedge (p \mathbin{\%} n) = 0
-\end{gather}
+For instance, the scenario mentioned above can be represented as follows. The verification of whether $p$ is a prime number can be formalized as:
 
-\noindent each validator independently choose a
-random $n$ in the range $2 \le n \le 
-\sqrt p$ and checking whether $(p \mathbin{\%} n) = 0$. If the remainder is $0$, the validator found a counterexample.
+\[ \bigwedge_{i = 2}^{|\sqrt p|} (p \mathbin{\%} i \neq 0) \]
 
-In our approach, there are three roles: 
-\begin{itemize}
-   \item the owner deploys and manages assertion contracts, 
-   \item the callers invoke a assertion contract, and 
-   \item the validators are involved in validating parameters. 
-\end{itemize}
+Similarly, ensuring the sorted property for an array of size nn can be expressed as:
 
-\noindent A caller submit a parameter that needs to be validated to the blockchain.
-The parameter is  then forwarded to all nodes as validators in the network, which then validate it.
-After the parameter is validated, the actual work that use the parameter is executed.
+\[ \bigwedge_{i = 0}^{n - 2} (a[i] \le a[i+1]) \]
 
-Finding a counterexample for an assertion and announcing the result to the blockchain costs in terms of energy (computing power) and gas.
-There could be the case that it is very rare to find a counterexample, because a caller tries not to pass an unvalid parameter to the blockchain.
-In this case, we need to encourage all validators running the program to validate the assertion even though no counterexample may be found.
-Therefore, there are two way to reward validators in the form of cryptocurrency in order to motivate the validators to participate: (1) for a  counterexample found and (2) for a computational proof that proves that the validator actually run the program to find a counterfeit for the assertion, but none is found.
-If any of the validators finds a violation of the assertion, the final call to the actual work is aborted.
+The fundamental concept of our approach is to disjoin this formula and distribute its components to validators in the network.
+Each validator endeavors to find a counterexample by solving $\neg P_{i}$.
+When a counterexample is discovered, the formula is proven to fail.
+If no counterexample is found, the correctness of the formula depends on the number of predicates  $P_{i}$ that have been checked.
 
-An validator finds a counterexample for an assertion outside the chain.
-Therefore, validators interact with the on-chain contract to convey a found counterexample or computational proof via a function call.
-
-Since the parameter must be validated before the actual work can be performed, a caller first invokes an assertion function in the on-chain validation contract to pass the parameter for verification.
-After the parameter is verified, a work contract can be invoked to perform the actual task assuming that the parameter is valid.
-The work contract can be invoked by the on-chain validation contract only if certain conditions are met.
-
-\paragraph{On-chain validation contract.} An on-chain validation contract must contain the following two functions:
-
-\begin{itemize}
-\item the assertion function, where callers submit their parameters to be validated, which are then distributed to all validators. 
-\item the on/off-chain assertion (validate function) to check and promote either a computational proof or a counterexample sent by the validators.
-\end{itemize}
-
-When a caller submits a parameter for validation, the parameter and associated information must be stored for the validation process.
-Since the parameter can be very large, we suggest storing only its hash.
-The hash is still sufficient to validate the validation process.
-The address of the caller should also be stored, and perhaps the timestamp indicating the approximate time the caller submitted the parameter.
-For each submission, there should be a corresponding record containing the associated data and validation status, such as the number of proofs received or the status if there is a counterexample.
-It could be the case that many parameters are submitted, then it may be useful to delete the record after the processing is completed with the parameter.
-There are two possible data structures for storing such records: map and array.
-
-For example, if we assume that a caller can submit only one parameter at a time, we can use a map that associates the caller's address with the parameter's hash and timestamp.
-
-\begin{lstlisting}[numbers=none]
-
-   struct Parameter {
-        bytes32 p_hash;
-        uint256 timestamp;
-    }
-    mapping (address => Parameter) public parameters;
-\end{lstlisting}
-
-\paragraph{On-chain work contract.}  The work contact can only be invoked by the on-chain validation contract after the parameter has been validated if no counterexample is found.
-The actual work is then performed with the passed parameter.
-
-\paragraph{Off-chain validation contract.}
-To check the validity of a parameter, each validator independently executes an off-chain validation contract that executes the on/off-chain assertion (the validate function), which is the same one used in the on-chain validation contract.
-The off-chain validation should be sent to all validators and executed outside the blockchain network.
-The on/off-chain assertion (the validate function) in the off-chain validation contract plays the main role in our approach.
-It contains the negation formulas of the assertion for parameters and takes a seed and a parameter as input.
-The seed is used to compute a random number to check the negation formulas.
-The result of the calculation can be a counterexample, an award computational proof, or a non-award computational proof.
-
-A validator might try to run the off-chain validation contract many times to find either a counterexample or a computational proof.
-There could be many attempts before he receives an award.
-In the case of a non-award, the validator can run the code again with a different random number.
-If a counterexample or award is found, the validator passes the seed together with the parameter to the on-chain validation contract, which runs the same on/off-chain assertion and must end up with the same result as the counterexample or award.
-
-\subsection{Managing on/off-chain contracts.}
-All contracts are provided by their owner. The owner plays the main role in the design of the contracts. The owner deploy the on-chain validation contract and the work contract on the blockchain.
-
-The on/off-chain assertion and off-chain validation contract are stored off the blockchain and should be available to callers/validators upon request at any time.
-There are two ways to make them available to validators: (1) the codes are stored on a repository that callers/validators can access, or the owner can make it available to a caller/validator upon request, and (2) an owner/caller sends it to the network via messaging systems such as Waku in eutherum.
-The owners should send it to the network once they deploy the on-chain contracts, and in this case interested validators should store the code locally.
-In the same way, callers could also send it when they invoke an assertion function in the on-chain validation contract on the blockchain.
-%\end{itemize}
-
-\begin{figure}
-\centering
-\includegraphics[scale=.8]{owner}
-\caption{Managing on/off-chain assertion contracts.}
-\end{figure}
-
-\subsection{Interacting with the on-chain validation contract.}
-A caller must first submit the parameter to an assertion function in the on-chain validation contract before it can be used in the work contract.
-The parameter is then distributed and validated by validators.
-The process of validating the parameter and invoking the work contract is transparent to the user.
-It is sufficient to store the hash of the parameter, and the parameter is transmitted when a validator invokes the on/off-chain assertion in the on-chain validation contract on the blockchain.
-Since the work contract is invoked by the on-chain validation contract, there should be a way to ensure that it is only invoked when the parameter is valid and certain conditions are met, e.g., when it has received a sufficient number of proofs.
-
-A caller may need to supply some tokens for validating the parameter and calling the work contract.
-
-In some cases where the validation process does not have a counterexample but does not meet some conditions, e.g., does not receive enough proofs from the validators, the owner has to do some tasks here to handle the refund since the functions in the smart contract are passive.
-Some time contracts could be used for this purpose.
-
-\begin{figure}
-\centering
-\includegraphics[scale=.6]{caller}
-\caption{Submitting a parameter to the on-chain assertion contract.}
-\end{figure}
-
-\paragraph{Submitting a parameter.} A caller passes the parameter to be checked by calling an assertion function.
-The function then stores all necessary information, namely the hash of the parameter, the address of the caller, and possibly the timestamp, as if in a record.
-The parameter's record also contains initial information for monitoring the progress of the parameter's verification, e.g., how many computational proofs have been presented, whether a counterexample has been found, etc.
-This information is used to review a proof or counterexample presented by a validator, and to decide when a work contract can be called for that parameter.
-The caller may then send this information, along with the on/off-chain assertion and off-chain validation contract, to all validators via a messaging system.
-
-\paragraph{Submitting of a computational proof/a counterexample.} After executing the off-chain validation contract, the validator may submit a computational proof or a counterexample to receive a reward.
-The submission contains the random number, the address of the validator, the parameter, and possibly other information.
-These are then used to calculate the seed, which then goes into the on/off-chain assertion along with the parameter.
-If the result is correct, there is an award to the validator and the record of the parameter in the storage accordingly is updated accordingly.
-When a computational proof is submitted and  certain requirements are met, the work contract is invoked.
-
-\subsection{Validating a parameter}
-When a parameter is sent to a validator, the validator executes the off-chain validation contract, which includes an on/off-chain assertion, to find a counterexample.
-A validator interacts with the contract in two ways: it can announce a counterexample and submit a computational proof.
-If a counterexample is found, the validator submits it to the blockchain to receive a reward.
-Otherwise, a computational proof may be submitted.
-The computational proof is automatically generated when the on/off-chain assertion program is executed.
-The validator may need to clarify which parameter is being checked by submitting the parameter and the address of the caller, and possibly the timestamp.
-This information is then matched against the records in the storage.
-
-Since the on/off chain assertion is the same for every validator, we may need the address of the validator for each parameter to make the proof unique for each validator.
-A random number is combined with the validator's address to create a seed that is used to compute a random point in the parameter range to verify the validation of the parameter.
-This prevents the validator from copying a computational proof from others.
-With this information, a validator performs the off-chain validation contract, namely the on/off-chain assertion (validate function).
-There can be three different outcomes: a counterexample, an award, or a non-award.
-If it is a counterexample or an award, the validator passes the seed to the blockchain, i.e., it calls the on-chain validation contract on the chain, which then executes the same on/off-chain assertion.
-If the on-chain result is the same, the validator gets the reward.
-If the off-chain validation result is  non-award, the validator can rerun the off-chain validation.
-We could store these proofs information on the storage until the processing of the parameter is complete to prevent multiple submissions by a validator.
-
-\begin{figure}
-\centering
-\includegraphics[scale=.8]{validator}
-\caption{Submitting a proof/a counterexample.}
-\end{figure}
-
-\subsection{Calling a work function.}
-The work function can only called by the on-chain validation contract once the parameter has been verified.
-Thus, the caller first passes its parameter to the assertion function and then waits a while to be sure that the parameter has been verified.
-The record corresponding to the parameter stored in the storage is updated when a proof or counterexample is presented.
-Some conditions must be met, e.g., after a certain amount of time has passed or enough evidence has been received from the validators.
-If a validator submits the counterexample, the parameter is aborted from the validating process and the work contract is never called.
-Otherwise, the work contract is called when the computational proof is submitted and all conditions are met.
-
- The on-chain validation contract calls the work contract with the current parameter and timestamp matched against the stored parameter hash and timestamp.
-They must match and satisfy some other conditions, such as a certain amount of time must have passed and no counterexample must be found.
-If all conditions are met, the actual work is done and the record of the parameter is deleted from memory to relieve the storage.
-If no record is found that matches the input data, the actual work with the input data is not performed.
-The work contract only allows the call from the on-chain validation contract.
-
-\section{Domain Specification Language for Assertion}
-We define a domain-specific high-level
-language to express assertions.
-\subsection{Assertion Grammar}
-The syntax of this language is described in two versions by the grammars: prefix and infix. The parser currently supports the prefix notation and correct
-operator precedences must be handled explicitly with parentheses. The syntax is inspired by OCaml and uses the same type notations as Michelson.
-
-An assertion begins with the keyword entrypoint and a signature consisting of an optional tag, denoted by \%, followed by a parameter pattern.
-Parameter patterns are similar to patterns in OCaml — they are templates that match shapes of data structures and bind identifiers to the components of them.
-The given parameter pattern must match exactly the parameter type of the entrypoint it is associated with.
-The body of an assertion can
-contain a nesting of quantifiers and conditions around exactly one assert expression, which tests a property. Conditions can be used to restrict the
-quantification domains or to impose any other constraints. For completeness,
-the existential quantifier is already included in the grammar, however the
-current version of the pipeline will reject any assertions containing it.
-How the assertions are associated with the respective entrypoint of the
-parent contract, depends on the Smart Contract language. In the case of
-Solidity, a tag that mirrors the function name is enough to link assertion and
-entrypoint. In Michelson contracts, on the other hand, entrypoints can be
-anonymous. Therefore, the assertions are linked to the entrypoints through
-the tags, the parameter type or both.
-
-\subsubsection{Parameter patterns.}
-Listing gives an overview of the parameter patterns supported in the assertion language.
-\begin{lstlisting}[numbers=none]
-
-< pattern > ::=
-	| '_ '
-	| nil
-	| none
-	| ( IDENT : < type >)
-	| IDENT
-	| ( pair < pattern > < pattern >)
-	| ( left < pattern >)
-	| ( right < pattern >)
-	| ( cons < pattern > < pattern >)
-	| ( some < pattern >)
-
-\end{lstlisting}
-
-\begin{lstlisting}[numbers=none]
-
-( entrypoint % g ( pair ( cons a as ) _ ) ...)
-\end{lstlisting}
-
-AST
-
-\begin{lstlisting}[numbers=none]
-
-type ast =
-{ entrypoint : string option * pattern ; body : assertion }
-
-\end{lstlisting}
-
-\subsection{Assertion Semantic}
-A validator is trying to solve the following formula in a distributed form.
-
-\begin{gather}
-  \label{eq:2}
-  \exists i \in D_{i}. P_{i}
-\end{gather}
-
-\noindent The verification attempt requires to search for $i$ in the domain $D$ such that $P_{i}$, called a counterexample.
-For each distributed trial, each validator chooses a random $i$ $\in$ $D$ and checks $P_{i}$.
-The formula can be extended to multiple domains $D_{i}$, ..., $D_{k}$.
-
-\begin{gather}
-  \label{eq:2}
-\exists i \in D_{i}, \exists j \in D_{j}, ..., \exists k \in D_{k}. P_{i, j, ...,k}
-\end{gather}
-
-\subsubsection{Transformer. }
-An assertion is formalized in the DSL. The formula is then transferred to its negation formula. 
-\begin{gather}
-  \label{eq:2}
-\neg (\forall i \in D_{i}. P_{i}) \equiv \exists i \in D_{i}. \neg P_{i}
-\end{gather}
-
-\noindent Given an assertion
-\begin{gather}
-  \label{eq:2}
-\forall i \in D_{i},  \forall j \in D_{j},  ..., \forall k \in D_{k}. P_{i, j, ...,k}
-\end{gather}
-
-\noindent it is then transformed to its negation, which is distributed to be verified by validators.
-
-\begin{gather}
-  \label{eq:2}
-\exists i \in D_{i},  \exists j \in D_{j},  ..., \exists k \in D_{k}. \neg P_{i, j, ...,k}
-\end{gather}
-
-%(2) For nested quantifiers: a formula that may contain one (or more ''forall" qualifier) then all of these ''forall" quantifiers is converted to ''exist" and all ''exist" quantifiers are kept the same and negative the predicate.
-%\begin{gather}
-%  \label{eq:2}
-%\forall i \in D_{i}, \exists j \in D_{j}, ..., \exists k \in D_{k}. (P_{i, j, ...,k})
-%\end{gather}
-
-%\begin{gather}
-%  \label{eq:2}
-%\exists i \in D_{i}, \exists j \in D_{j}, ..., \exists k \in D_{k}. \neg (P_{i, j, ...,k})
-%\end{gather}
-
-\subsection{Converter - Generating an On/off-chain Assertion} The main actor in our method is the on/off-chain assertion contract, which receives the parameter and a seed as input.
-The contract then generates a random number that is associated with a variable in the predicate.
-The result can be a counterexample, a computational proof with reward, or a computational proof without reward.
-A converter takes the AST of an assertion after the parser (or the AST for its negation after the transformer step) and returns the on/off-chain assertion contract written in Solidity (Michelson).
-To perform the conversion automatically, we restrict the semantics of the DSL.
-Variables are specified with \texttt{forall} quantifiers, which are then followed by \texttt{if} statements defining the range of the variable.
-For example, the following assertion specifies the parameter \texttt{a} of type \texttt{int} for the entrypoint \texttt{prime}.
-The next line defines the variable \texttt{a} of type \texttt{int} and its range is defined in the next \texttt{if} statement, namely [2 a/2].
-Finally, the assertion is declared.
-
-\begin{lstlisting}[numbers=none]
-
-(entrypoint % prime (a : int)
-   (forall (n : int)
-         (if (and (ge 2 n) (le n (div a 2)))
-              (assert (not (eq (mod a n) 0))))))
-
-\end{lstlisting}
-
-%, which then is checked   For the implementation of the current method, the syntax support any type of parameter, but the conversion supports the sematic for some typical types.
-Namely $i$ can be identified with a number.
-in deep the domain, $D$ should be able to associate with a natural number.
-For this end, a validator submits a seed that is then used to calculate $i$ that detects $P_{i}$.
-For example, arrays of any type or strings that is an array of characters.
-There could be several properties of natural numbers as primes, even, old, co-primes, square numbers, ..etc.
-for array $i$ could be used to detect the element of an array (or character of string).
-In some cases, when the formula is $\forall$ i $\in$ D.
-($P_{i}$).
-The formula could be encoded an array of predicates.
-after an assertion is transferred to distributed form to be distributed.
-The most important in our approach is to design the validator contract that used both on-chain and off-chain computation.
-Our conversion converts an assertion to an on/off-chain assertion file that is used for validators to check a randomly chosen i.
-although our method and the assertion transformer works with all decide domain D.
-The convention will only work if the D is related to a natural number.
-\subsubsection{Detecting the range.} Assumes that the range of a variable is 
+To estimate the number of validators needed to find a counterexample with a given probability $p$, let's assume the number of validators is $m$.
+Each validator independently has a probability of $p$ to check $P_{i}$.
+Hence, if we assume that each $P_{i}$ is chosen independently from a uniform distribution, the probability that a validator checks $P_{i}$ is
 \begin{displaymath}
-r = [a, b] \land (b-a) > 0
+ m. (\frac{1}{n})
+\end{displaymath}
+So, to detect the counterexample, assuming at $P_{i}$ the number of validators needed is as follows:
+\begin{displaymath}
+ m \ge p.n
 \end{displaymath}
 
-\noindent and a seed $s$, then the random number in the range [a, b] can be generate by
+This inequality indicates that the minimum number of validators required, $m$, is at least $p$ times the number $n$, to achieve the desired probability $p$ of detecting the counterexample.
+Indeed, the estimated number of validators plays a crucial role in designing the protocol for the approach.
+It serves as a fundamental parameter that influences various aspects of the protocol's design.
+\section{Toward the Design of the Protocol}
+\label{sec:design}
 
-\begin{displaymath}
-n = (s\mod(b - a)) + a.
-\end{displaymath}
+\section{Target Tezos Blockchain}
+\label{sec:tezos}
 
-\noindent For the above assertion, we have  
-\begin{displaymath}
-r = [2 , a / 2] \land (a / 2 - 2) >= 0. 
-\end{displaymath}
-
-\noindent Given a random seed s, the $n$ $\in$ [2 , a / 2] could be generate by $s$.
-
-\begin{gather}
-n = (s\mod (a / 2 - 2)) + 2.
-\end{gather}
-
-\subsubsection{Calculating a valid hash.} a computational proof is based on Proof of work (as Bitcoin).
-Each computation calculates a hash based on its running the check of the predicate and then compare it with the target hash.
-The calculation has to be unique for each run to prevent copying of other validators or run a quick independent program to find a valid hash.
-To this end, we include the seed and the calculation of the predicate components to the hash.
-In this case, these above bad internal force can not be successful.
-A predicate is composed of the primitives with the following operations (\texttt{gt, lt, ge, le, or, xor, and, eq, neq, neg, not}).
-The operations are composed of one or more expressions.
-These expressions are then used to calculate the hash.
-
-For example, given the predicate
-
-\begin{lstlisting}[numbers=none]
-not (eq (mod a n) 0)
-\end{lstlisting}
-
-\noindent The expression \texttt{(mod a n)} is the used to calculate the hash.
-
-The Converter generate a on/off-chain assertion program in Solidity as the follows.
-
-\begin{lstlisting}[numbers=none]
-
-pragma solidity >=0.7.0 <0.9.0;
-
-/**
- * On/off-chain assertion contract 
- * to check counterexamples/computational proofs
- */
-contract Validator{
-
-    /**
-    * The difficulty for a computational proof
-    */
-    uint diff = 1;
-    uint public target = 2 ** (256 - diff);
-
-    /**
-    * The result: 0 = non-award, 1 = proof, 2 = counterexample
-    */
-
-    function validate(uint a, uint seed) 
-    public view returns (uint) {
-        uint range = a / 2 - 2; 
-        uint r = seed % range + 2;
-        uint cal = a % r;
-        bool p = (cal == 0);
-
-        uint result = 0; // an non-award computational proof 
-        if (p)  
-            result = 2; // a counterexample
-        else 
-            {
-                uint result_target = 
-                    uint (keccak256(abi.encodePacked(seed, cal)));
-                if (result_target <= target) 
-                    result = 1; // a computational proof    
-            }
-        return result;           
-    }
-}
-
-\end{lstlisting}
-
-For sorted array
-
-\begin{lstlisting}[numbers=none]
-
-(entrypoint % array (a : (list int))
-   (forall (n : int)
-      (forall (m : int)
-         (if (and (ge n 1) (le n (size a)))
-            (if (and (ge m 0) (lt m n))
-                  (assert (le (nth a n) (nth a m))))))))
-
-\end{lstlisting}
-
-\noindent We have:
-
-$r_{n}$ = [1, size a] with (size a - 1 $>$ 0)
-
-$r_{m}$ = [0, n] with (n - 0 $>$ 0)
-
-\begin{lstlisting}[numbers=none]
-
-pragma solidity >=0.7.0 <0.9.0;
-
-/**
- * On/off-chain assertion contract 
- * to check counterexamples/computational proofs
- */
-contract Validator{
-
-    /**
-    * The difficulty for a computational proof
-    */
-    uint diff = 1;
-    uint public target = 2 ** (256 - diff);
-
-    /**
-    * The result: 0 = non-award, 1 = proof, 2 = counterexample
-    */
-
-    function validate(uint[] memory a, uint seed)
-    public view returns (uint) {
-        uint range_1 = a.length - 1; 
-        require(range_1 > 0, "invalid range");
-        uint n = seed % range_1 + 1;
-        uint range_2 = n;
-        require(range_2 > 0, "invalid range");
-        uint seed_1 = uint (keccak256(abi.encodePacked(seed, n)));
-        uint m = seed_1 % range_2 ;
-
-        uint cal_1 = a[m];
-        uint cal_2 = a[n];
-
-        bool p = (cal_1 > cal_2);
-
-        uint result = 0; // an non-award computational proof 
-        if (p)  
-            result = 2; // a counterexample
-        else 
-            {
-            uint result_target = 
-                uint (keccak256(abi.encodePacked(seed, cal_1, cal_2)));
-            if (result_target <= target) 
-                result = 1; // a computational proof      
-        }             
-        return result;           
-    }
-}
-
-\end{lstlisting}
-
-For a heap
-
-\begin{lstlisting}[numbers=none]
-
-(entrypoint % heap (a : (list int))
-   (forall (n : int)
-         (if (and (ge n 1) (le n (size a)))
-                  (assert (lt (nth a n) (nth a (div (sub n 1) 2)))))))
-\end{lstlisting}
-
-\noindent We have:
-
-$r$ = [1, size a] with (size a - 1 $>$ 0)
-
-\begin{lstlisting}[numbers=none]
-pragma solidity >=0.7.0 <0.9.0;
-
-/**
- * Validator Contract
- * Check a counterexample/computational proof
- */
-contract Validator{
-
-    /**
-    * The difficulty for a computational proof
-    */
-    uint diff = 1;
-    uint public target = 2 ** (256 - diff);
-
-    /**
-    * Check a counterexample/ computational proof
-    * The result from a validator
-    * 0 = non-award, 1 = proof, 2 = counterexample
-    */
-
-    function validate(uint[10] memory a, uint seed) 
-    public view returns (uint) {
-        uint range = a.length; 
-        uint k = seed % range + 1;
-
-        uint cal_1 = a[k];
-        uint cal_2 = a[(k - 1) / 2];
-
-        bool p = (cal_1 < cal_2);
-
-        uint result = 0; // an non-award computational proof 
-        if (p)  
-            result = 2; // a counterexample
-        else {
-            uint result_target = 
-                uint (keccak256(abi.encodePacked(seed, cal_1, cal_2)));
-            if (result_target <= target) 
-                result = 1; // a computational proof      
-        }              
-        return result;           
-    }
-}
-
-\end{lstlisting}
-
-Coprimes number
-
-\begin{lstlisting}[numbers=none]
-(entrypoint % coprimes (pair (a : int) (b : int))
-   (forall (n : int)
-         (if (and (ge 2 n) (le n (if (ge a b) a b)))
-              (assert (not (and (eq (mod a n) 0) (eq (mod b n) 0)))))))
-\end{lstlisting}
-
-\noindent We have:
-
-$r$ = [2, (if (a $>=$ b) a b)] with ((if ($a >= b$) a b) - 2 $>$ 0)
-
-\begin{lstlisting}[numbers=none]
-
-pragma solidity >=0.7.0 <0.9.0;
-
-/**
- * On/off-chain assertion contract 
- * to check counterexamples/computational proofs
- */
-contract Validator{
-
-    /**
-    * The difficulty for a computational proof
-    */
-    uint diff = 1;
-    uint public target = 2 ** (256 - diff);
-
-    /**
-    * The result: 0 = non-award, 1 = proof, 2 = counterexample
-    */
-
-    function validate(uint a, uint b, uint seed)
-    public view returns (uint) {
-        uint range;
-        if (a >= b) { range = a - 2; }
-        else {range = b - 2;}
-
-        uint r = seed % range + 2;
-        require(range != 0, "invalid range");
-
-        uint cal_1 = a % r;
-        uint cal_2 = b % r;
-
-        bool p = (cal_1 == 0) && (cal_2 == 0);
-
-        uint result = 0; // an non-award computational proof 
-        if (p)  
-            result = 2; // a counterexample
-        else {
-            uint result_target = 
-                uint (keccak256(abi.encodePacked(seed, cal_1, cal_2)));
-            if (result_target <= target) 
-                result = 1; // a computational proof      
-        }              
-        return result;           
-    }
-}
-
-\end{lstlisting}
-
-\section{A Prototype Implementation}
-\section{Cost Analysis}
-\section{Related work}
-\section{Conclusion}
-
-\newpage
-\addcontentsline{toc}{chapter}{Appendix}
-\input{appendix}
-
-\newpage
-\bibliographystyle{splncs04}
-\bibliography{bio}
 \end{document}

### 2024-04-11 papers/assertion-contract/assertion-contract-cons/paper.tex
write protocol

@@
 
-%To obtain an estimate of the number of validators needed to find a counterexample with high probibility, let's assume the array is unsorted only at position $0$, the size of the array is $n$,and the number of validators is $m$.
+To obtain an estimate of the number of validators needed to find a counterexample with high probibility, let's assume the array is unsorted only at position $0$, the size of the array is $n$,and the number of validators is $m$.
 Each validator independently has a probability of $1/n$ to detect the problem and thus probability $\frac{n-1} n$ not to detect the problem.
 Hence, if we assume that each $k$ is chosen independenty from a uniform distribution, the probability that no validator checks at position $0$ converges to $0$ as the number of validators approaches infinity.
-%\begin{displaymath}
-%  \lim_{m\to\infty}\frac{(n-1)^m}{n^m}
-%  = \lim_{m\to\infty} \left(\frac{n-1}{n}\right)^m
-%  = 0
-%\end{displaymath}
+\begin{displaymath}
+  \lim_{m\to\infty}\frac{(n-1)^m}{n^m}
+  = \lim_{m\to\infty} \left(\frac{n-1}{n}\right)^m
+  = 0
+\end{displaymath}
 
@@
 \label{sec:approach}
-In this section, we aim to introduce an approach leveraging distributed aspects to address the challenging verification issue within blockchain systems.
+A blockchain network comprises distributed nodes that collaborate through a consensus algorithm to establish a common state of the network.
+In this section, we aim to introduce an approach leveraging distributed aspect of blockchain network to address the challenging verification issue within blockchain systems.
 Specifically, we focus on verifying a substantial parameter, crucial for executing a smart contract call.
@@
 
-The fundamental concept of our approach is to disjoin this formula and distribute its components to validators in the network.
-Each validator endeavors to find a counterexample by solving $\neg P_{i}$.
+The fundamental concept of our approach is to disjoin this formula and distribute its components to nodes in the network, where each node endeavors to find a counterexample by solving $\neg P_{i}$.
+
+\begin{displaymath}
+\bigvee_{i = 1}^{n} \neg P_{i}
+\end{displaymath}
+
 When a counterexample is discovered, the formula is proven to fail.
-If no counterexample is found, the correctness of the formula depends on the number of predicates  $P_{i}$ that have been checked.
+Otherwise, the correctness of the formula depends on the number of predicates  $P_{i}$ that have been checked, but no counterexample is found.
 
-To estimate the number of validators needed to find a counterexample with a given probability $p$, let's assume the number of validators is $m$.
-Each validator independently has a probability of $p$ to check $P_{i}$.
-Hence, if we assume that each $P_{i}$ is chosen independently from a uniform distribution, the probability that a validator checks $P_{i}$ is
+To estimate the number of nodes needed to find a counterexample with a given probability $p$, let's assume the number of nodes is $m$.
+Each node independently has a probability of $p$ to check $P_{i}$.
+Hence, if we assume that each $P_{i}$ is chosen independently from a uniform distribution, the probability that a node checks $P_{i}$ is
 \begin{displaymath}
@@
 \end{displaymath}
-So, to detect the counterexample, assuming at $P_{i}$ the number of validators needed is as follows:
+So, to detect the counterexample, assuming at $P_{i}$ the number of nodes needed is as follows:
 \begin{displaymath}
@@
 
-This inequality indicates that the minimum number of validators required, $m$, is at least $p$ times the number $n$, to achieve the desired probability $p$ of detecting the counterexample.
+This inequality indicates that the minimum number of nodes required, $m$, is at least $p$ times the number $n$, to achieve the desired probability $p$ of detecting the counterexample.
 Indeed, the estimated number of validators plays a crucial role in designing the protocol for the approach.
@@
 \label{sec:design}
+In a blockchain system, a new block is added in each round.
+During each round, a node is designated as the block proposer, decided based on the consensus algorithm, and suggests a new block to the network.
+For example, this role is akin to the miner in Bitcoin, the proposer in Ethereum, and the baker in Tezos.
+Other nodes in the network act as validators, responsible for validating the proposed block.
+The number of validators varies between different systems; for instance, all full nodes validate in Bitcoin, whereas validators are limited and determined in each round in Ethereum and Tezos.
+
+In this section, we explore the design of protocol for the proposed approach.
+Our intention is not to propose a completely new consensus algorithm but to add a parameter distributed verification feature to an existing one.
+The outline of the design is as follows:
+\paragraph{Entering into the mempool} Let's assume $t$ is a transaction with the parameter $p$ that invokes a function of a smart contract requiring the parameter to be verified before further execution.
+Like any other normal transaction, $t$ is submitted to a node.
+The node then checks the transaction, adds it to its local mempool, and broadcasts $t$ to the network via a peer-to-peer gossip network.
+The transaction then waits in the mempool until it is included in the chain.
+\paragraph{Waiting for the distributed verification process} The transaction $t$ cannot be executed and added to the next block immediately by the block proposer but needs to wait for the distributed verification process.
+When a proposer processes the transaction $t$, in this case, the proposer can initiate the verification process and advertise the verification problems to other nodes via the peer-to-peer network.
+This transaction can then be moved to a list of transactions undergoing verification in the mempool, with some initial values for the verification process.
+For example, the negation formula to advertise to other nodes, along with the initial value of the condition such that the transaction will be processed if this condition is met.
+\paragraph{Receiving a counterexample} Each validator node attempts to find a counterexample.
+When a counterexample is found, it is advertised to the network.
+Other nodes, upon receiving the counterexample, verify it.
+Subsequently, the transaction is removed from the list of transactions undergoing verification in the mempool.
+\paragraph{Executing the validated transaction} If certain conditions are met and no counterexample is recored, the transaction could be included by the next block proposer.
+\paragraph{Incentivizing the participants}  In the context of standard transactions, both block proposers and validators have incentives to include transactions into new blocks and validate all transactions within the proposed block.
+In our distributed verification protocol, we similarly necessitate an incentive mechanism to motivate nodes to engage in the distributed verification process.
+Specifically, the block proposer, responsible for initiating the verification process, and the one who include the transaction into a new block will receive a fee.
+Furthermore, our protocol introduces incentives for discovering counterexamples, ensuring that validators who identify such instances are duly rewarded.
+
+Moreover, it may be rare that invalid parameters are submitted, there's a possibility that a validator may not receive any incentives, potentially leading them to ignore such transactions.
+Hence, it becomes necessary to incentivize a portion of the computing power.
+This entails rewarding validators who can demonstrate that they have conducted the verification process without discovering any counterexamples.
+However, it's prudent to incentivize only a fraction of the computational effort, rather than all of it, to prevent excessive burden on individual nodes.
+Otherwise, the process could become more resource-intensive than merely checking the parameters at a single node.
+To address this concern, we propose a proof-of-work-based incentive algorithm, which is elaborated upon in the subsequent section of this paper.
+
+\paragraph{Setting up the execution condition}  After undergoing the verification process, a transaction is included in the new block if it satisfies predefined conditions.
+These conditions serve as assurances of the correctness of the parameters.
+
+As mentioned earlier, to achieve a certain probability of verification, a minimum number of checks by validators is required.
+In some systems, there is a large number of validators in each round, while in others, such as Tezos blockchain, there is a fixed number, for instance, 32 validators.
+In scenarios where the number of validators is limited, a single validator may conduct multiple checks with one parameter.
+Hence, due to on the certain consensus mechanism, various methods may exist to calculate the condition.
+
+Based on a specific parameter, the block proposer, who initiates the verification process, determines the condition.
+It could be time-based, where a transaction may need to wait in a undergoing verification list for a specified duration, synchronized with the number of rounds elapsed, or it could be based on the number of computation proofs received.
+For the latter case, we present two methods to estimate it in the proof-of-work-based incentive system.
+\paragraph{Pre-paying and penalties} The smart contract caller submitting the transaction must include sufficient funds to cover fines in case a counterexample is discovered.
+These funds will be returned if no counterexample is found during the verification process.
+
+If a block proposer dishonestly includes a transaction that hasn't undergone the verification process, they will incur a penalty similar to including any other invalid transaction.
 

### 2024-04-12 papers/assertion-contract/assertion-contract-cons/paper.tex
resive

@@
 \usepackage{listings}
-\usepackage{titling}
 
@@
 %
-\title{Assertion Contracts}
+\title{Parameter Distributed Verification Approach for Blockchain System}
 %
@@
 \label{sec:approach}
-A blockchain network comprises distributed nodes that collaborate through a consensus algorithm to establish a common state of the network.
-In this section, we aim to introduce an approach leveraging distributed aspect of blockchain network to address the challenging verification issue within blockchain systems.
-Specifically, we focus on verifying a substantial parameter, crucial for executing a smart contract call.
+A blockchain network comprises distributed nodes that collaborate through a consensus algorithm to establish a common network state.
+In this section, we introduce an approach that leverages the distributed aspect of blockchain networks to address the challenging verification issues within blockchain systems.
+Specifically, we focus on verifying a substantial parameter crucial for executing a smart contract call.
 
-Our attention is drawn to the verification problem, which can be articulated as a logical formula presented in conjunction form as follows:
+We focus on the parameter verification problem, which can be expressed as a logical formula presented in conjunction form as follows:
+\begin{displaymath}
+\bigwedge_{i \in D_i} P_{i}
+\end{displaymath}
 
-\[ \bigwedge_{i = 1}^{n} P_{i} \]
-
-Verifying the formula centrally becomes resource-intensive, both in terms of time and computer resource when the number $n$ is big or when the predicates $P_{i}$ are complex to compute.
-
-For instance, the scenario mentioned above can be represented as follows. The verification of whether $p$ is a prime number can be formalized as:
-
-\[ \bigwedge_{i = 2}^{|\sqrt p|} (p \mathbin{\%} i \neq 0) \]
-
-Similarly, ensuring the sorted property for an array of size nn can be expressed as:
-
-\[ \bigwedge_{i = 0}^{n - 2} (a[i] \le a[i+1]) \]
-
-The fundamental concept of our approach is to disjoin this formula and distribute its components to nodes in the network, where each node endeavors to find a counterexample by solving $\neg P_{i}$.
+where $D_i$  is the domain and $P_i$  is a predicate. This formula can be extended to multiple domains.
 
 \begin{displaymath}
-\bigvee_{i = 1}^{n} \neg P_{i}
+\bigwedge_{i \in D_i, j \in D_j, \dots}^{} P_{i, j, \dots}
 \end{displaymath}
+Checking the formula centrally can be a very time-consuming and computer resource-intensive task, especially when the number $n$ is large or the predicates $P_i$ are complex to compute.
 
-When a counterexample is discovered, the formula is proven to fail.
-Otherwise, the correctness of the formula depends on the number of predicates  $P_{i}$ that have been checked, but no counterexample is found.
+For instance, the example mentioned above can be represented as follows. The verification of whether $p$ is a prime number can be formalized as:
+\begin{displaymath}
+ \bigwedge_{i \in [2, |\sqrt p|]} (p \mathbin{\%} i \neq 0)
+\end{displaymath}
+Similarly, ensuring the sorted property for an array of size $n$ can be expressed as:
+\begin{displaymath}
+\bigwedge_{i \in [0, n - 2]} (a[i] \le a[i+1])
+\end{displaymath}
+The fundamental concept of our approach is to disjoin this formula and distribute its components to nodes in the network, where each node attempts to find a counterexample by solving $\neg P_{i}$. 
+\begin{displaymath}
+\bigvee_{i \in D_i} \neg P_{i}
+\end{displaymath}
+When a counterexample is discovered, the formula fails. Otherwise, the correctness of the formula depends on the number of predicates  $P_{i}$ that have been checked, but no counterexample is found.
 
@@
 It serves as a fundamental parameter that influences various aspects of the protocol's design.
+\section{Use Cases and Their Formalization}
+\subsection{Number}
+\subsubsection{Prime numbers}
+\subsubsection{Coprime numbers}
+\subsection{List}
+\subsubsection{Sorted list}
+\subsubsection{Heap}
+\subsubsection{Tree}
+\subsection{Set}
+\subsubsection{Disjoint set}
+\subsection{CNF}
+\subsection{Nested Domain}
 \section{Toward the Design of the Protocol}
@@
 In a blockchain system, a new block is added in each round.
-During each round, a node is designated as the block proposer, decided based on the consensus algorithm, and suggests a new block to the network.
+During each round, a node is designated as the block proposer decided based on the consensus algorithm, and suggests a new block to the network.
 For example, this role is akin to the miner in Bitcoin, the proposer in Ethereum, and the baker in Tezos.
@@
 \paragraph{Waiting for the distributed verification process} The transaction $t$ cannot be executed and added to the next block immediately by the block proposer but needs to wait for the distributed verification process.
-When a proposer processes the transaction $t$, in this case, the proposer can initiate the verification process and advertise the verification problems to other nodes via the peer-to-peer network.
+When a block proposer processes the transaction $t$, in this case, the proposer can initiate the verification process and advertise the verification problems to other nodes via the peer-to-peer network.
 This transaction can then be moved to a list of transactions undergoing verification in the mempool, with some initial values for the verification process.
@@
 \paragraph{Incentivizing the participants}  In the context of standard transactions, both block proposers and validators have incentives to include transactions into new blocks and validate all transactions within the proposed block.
+A part of these incentives is paid by the system and the other is paid by transaction fee.
 In our distributed verification protocol, we similarly necessitate an incentive mechanism to motivate nodes to engage in the distributed verification process.
-Specifically, the block proposer, responsible for initiating the verification process, and the one who include the transaction into a new block will receive a fee.
+Specifically, the block proposers, the one who is responsible for initiating the verification process, and the one who includes the transaction $t$ into a new block will receive a fee.
 Furthermore, our protocol introduces incentives for discovering counterexamples, ensuring that validators who identify such instances are duly rewarded.
@@
 Otherwise, the process could become more resource-intensive than merely checking the parameters at a single node.
-To address this concern, we propose a proof-of-work-based incentive algorithm, which is elaborated upon in the subsequent section of this paper.
+To address this concern, we propose a proof-of-work-based incentive algorithm.
+The proof-of-work-based method incentivizes participants in the distributed verification process.
+The proposed approach is outlined as follows:
+
+\begin{itemize}
+\item There are two ways to reward validators to encourage their participation: to discover a counterexample and to provide computational proof that they have executed the program to search for a counterexample, even if none is found.
+\item To prioritize the discovery of counterexamples, the reward for finding a counterexample is set significantly higher than that for providing computational proof.
+\item The computation of the negation formula is integrated into the computational proof to ensure that the validators cannot produce the proof without executing a negation check.
+\end{itemize}
+
+The next step is to devise a computation proof to incentivize computational effort by utilizing the proof of work concept.
+Initially, we establish a target hash $t$ that sets the required difficulty level to earn the reward.
+The objective of the validator is to generate a computation that produces a hash smaller than or equal to the target hash $t$.
+
+During the distributed process, each validator conducts the negation check at the random $P_i$.
+After conducting the negation check, either a counterexample is identified, or a hash is computed based on the evaluation of the condition $\neg P_{i}$.
+This hash is then compared with the target hash to ascertain if it meets the criteria for a reward computation.
+The outcomes of the verification process include either a counterexample, a reward computation, or a non-reward computation.
+Upon achieving either a counterexample or a reward computation, the validator can advertise it to the p2p network and claim their reward.
+Both the counterexample and the computation proof are easily to be replicated and verified by other nodes.
+If the verification is successful, the validators will be entitled to receive their reward.
 
@@
 As mentioned earlier, to achieve a certain probability of verification, a minimum number of checks by validators is required.
-In some systems, there is a large number of validators in each round, while in others, such as Tezos blockchain, there is a fixed number, for instance, 32 validators.
-In scenarios where the number of validators is limited, a single validator may conduct multiple checks with one parameter.
-Hence, due to on the certain consensus mechanism, various methods may exist to calculate the condition.
+In some systems, there is a large number of validators in each round, while in others, such as the Tezos blockchain, there is a fixed number, for instance, 32 validators.
+In scenarios where the number of validators is limited, a single validator may conduct multiple checks with one parameter or the system could allow any full nodes to participate in the distributed verification process.
+Hence, due to the certain consensus mechanism, various methods may exist to calculate the condition.
 
@@
 It could be time-based, where a transaction may need to wait in a undergoing verification list for a specified duration, synchronized with the number of rounds elapsed, or it could be based on the number of computation proofs received.
-For the latter case, we present two methods to estimate it in the proof-of-work-based incentive system.
+For the latter case,  the difficulty for the target hash could be used in the way to estimes the number of validators who check the parameter until the transaction is included.
+
 \paragraph{Pre-paying and penalties} The smart contract caller submitting the transaction must include sufficient funds to cover fines in case a counterexample is discovered.
@@
 
+\todo{disscus and implement}
+
+\section{Experiment and Cost Analysis}
+\label{sec:cost-analysis}
 \end{document}

### 2024-04-17 papers/assertion-contract/assertion-contract-cons/paper.tex
write Tezos

@@
 
-We focus on the parameter verification problem, which can be expressed as a logical formula presented in conjunction form as follows:
+We narrow our attention down to the parameter verification problem, which can be expressed as a logical formula presented in conjunction form as follows:
 \begin{displaymath}
@@
 To estimate the number of nodes needed to find a counterexample with a given probability $p$, let's assume the number of nodes is $m$.
-Each node independently has a probability of $p$ to check $P_{i}$.
+Each node independently has a probability of $1/n$ to check $P_{i}$.
 Hence, if we assume that each $P_{i}$ is chosen independently from a uniform distribution, the probability that a node checks $P_{i}$ is
@@
 \label{sec:tezos}
+We implement the protocol for the Tezos blockchain.
+Embedding the protocol into Tezos smart contracts can be done in two ways: (1) integrating new instructions into Michelson, or (2) introducing a separate syntax for assertion.
+Opting for the latter idea, we make ensure that it does not impact the existing syntax of the Michelson language.
+Existing contracts can be seamlessly upgraded to the new protocol by providing an additional specification for assertions.
 
+The system architecture is shows in Fig.\ref{fig.architect} and here is it breakdown: Upon deploying the smart contract, which includes the standard Michelson code and an assertion specification written in a domain-specific language.
+The assertion undergoes analysis by a transformer to extract the domain $D$ and the negation formula $\neg P_i$.
+Together with the Michelson code, both the domain and the negation formula are stored.
+When a block proposer and validator seek a counterexample, a converter transforms the negation formula and domain into a target program for the blockchain, specifically an OCaml program in Tezos.
+These nodes then execute the program to identify the counterexample.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.65]{assertion-tezos}
+\caption{The architecture}
+\label{fig.architect}
+\end{figure}
 \todo{disscus and implement}
-
 \section{Experiment and Cost Analysis}

### 2024-05-21 papers/static-checker/aplas/paper.tex
down to 17 pages

% APLAS 2021: Regular research papers should not exceed 18 pages in
% the Springer LNCS format(LaTeX template), including bibliography and
% figures.
% Lightweight double-blind: Author names and institutions must be
% omitted and References to the authors’ own related work should be in
% the third person 
%
\documentclass[runningheads]{llncs}
\pdfoutput=1
%\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{comment}
\usepackage{graphicx}
%\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathpartir}
%\usepackage{fixme}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{adjustbox} % For adjusting box sizes
\lstdefinelanguage{michelson}{
  % basicstyle=\ttfamily,
  basicstyle=\fontsize{8}{9.6}\selectfont,
  morekeywords={parameter,storage,or,unit,mutez,pair,bool,address}, sensitive=false,
  morecomment=[l]{\#},
  morecomment=[s]{/*}{*/},
  morestring=[b]",
}
\lstset{
  language=Caml,
  captionpos=b,
  aboveskip=-\smallskipamount,
  belowskip=-\smallskipamount,
  belowcaptionskip=0pt,
  basicstyle=\fontsize{8}{9.6}\selectfont,
  morekeywords={val}
}

\input{macros}

\begin{document}
%
\title{A Formal Verification Framework for Tezos Smart Contracts Based on Symbolic Execution}
%
\titlerunning{A Formal Verification Framework for Tezos Smart Contracts}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
%\author{Thi Thu Ha Doan\orcidID{0000-0001-7524-4497}\and Peter Thiemann\orcidID{0000-0002-9000-1239}}

%
%\authorrunning{Ha Doan, P. Thiemann}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
%\institute{University of Freiburg, Germany \\
%  \email{\{doanha,thiemann\}@informatik.uni-freiburg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
We developed SCV, a verification tool that is geared towards contracts implemented in Michelson, the smart contract language of the Tezos blockchain. SCV relies on symbolic execution to derive verification conditions that can be checked automatically against the user's specifications by employing an SMT solver. These specifications are written in a domain-specific language. We present the fundamental principles behind the design and development of SCV. By pruning states during symbolic execution, SCV addresses the problem of state explosion. This approach has enabled us to conduct two case studies on real-life contracts, demonstrating the expressiveness of our tool.
\keywords{Smart Contract, Blockchain, Formal Verification, Symbolic Execution}
\end{abstract}
\section{Introduction}
\label{sec:introduction}
Since smart contracts are permanently stored on the blockchain, once a smart contract is deployed, it cannot be changed. Regrettably, numerous instances have been documented where vulnerabilities in smart contracts were identified by the blockchain community, resulting in substantial financial losses~\cite{dao,wallethack}. The distinctive execution model of smart contract languages has given rise to unforeseen errors due to a lack of familiarity with their complexities. These observations, combined with the immutability of contracts, underscore the need to ensure their correctness prior to deployment.

We have developed SCV, a formal verification tool for smart contracts on the Tezos blockchain \cite{tezos-whitepaper}, written in Michelson \cite{michelson}. SCV relies on symbolic execution backed by an SMT solver to simulate the implementation of the smart contract language, helping to detect subtle errors. Additionally, SCV comes with a domain-specific language to precisely specify smart contract properties, tailored to Michelson's execution model and inspired by Z3. Each specification consists of Michelson code, a precondition, and a postcondition with the usual partial correctness semantics. Our symbolic interpreter calculates a postcondition predicate from the specified precondition. The SMT solver Z3 \cite{z3} checks that this predicate implies the specified postcondition.

%We have implemented approximately 85\% of the Michelson instructions, including most of the major-use instructions. The remaining instructions were not implemented primarily due to time constraints rather than technical limitations.

%One of the main challenges with formal verification is that users are often required to specify a system and express its properties in a specialized specification language. This requirement poses two problems: it demands expertise in formal verification from the specifier and introduces a gap between the actual code and its specification. In our framework, the actual Michelson code is used and users are not obliged to possess formal verification expertise. A basic understanding of Michelson data types and their usage when interacting with a smart contract on the Tezos blockchain is sufficient.

While there is already a considerable body of work applying symbolic execution to the verification of smart contracts \cite{securify, manticore, kevm, park} (see Section~\ref{sec:related-work} for details), most of these efforts are designed for Ethereum, where standard techniques for symbolic execution of imperative programs are applicable. Such groundwork does not exist for Michelson, which is a functional language running on a stack machine (see Section~\ref{sec:background}) with a sophisticated instruction set that includes high-level loops. For that reason, we had to develop symbolic execution for Michelson from the ground up.

Besides the Mi-Cho-Coq framework that relies on interactive theorem proving \cite{micho}, HELMHOLTZ \cite{helmholtz} is another automatic verifier for Michelson. However, the approach of HELMHOLTZ is significantly different from ours. HELMHOLTZ defines a refinement type system to keep track of the properties of values in the storage and on the stack, so that verifying a program corresponds to type-checking against a specification type. Furthermore, these tools generally conduct experiments with sample smart contract codes containing about 100 instructions. The HELMHOLTZ experiment primarily replicates issues previously identified by Mi-Cho-Coq. Although HELMHOLTZ analyzes one real-world contract, it only examines a portion of the code. In contrast, our tool is capable of handling entire contracts with hundreds or even thousands of instructions.

Our contributions are as follows.
\begin{enumerate}
\item Design and implementation of the SCV domain specification language.
\item Design and implementation of a symbolic interpreter for a significant subset of Michelson. 
\item Two case studies verifying smart contracts on the Tezos blockchain:
  \begin{itemize}
  \item USDtz, an implementation of the FA~1.2 standard for financial applications;
  \item Kolibri, an oracle contract that injects currency exchange rates from an external system.
  \end{itemize}
\end{enumerate}

SCV utilizes an SMT solver to eliminate invalid states during symbolic execution, addressing the problem of state explosion. This capability enabled SCV to conduct two case studies involving real smart contracts that have been operational on the Tezos blockchain for quite some time. Despite extensive testing, a flaw was reported in the Kolibri oracle contract. In conclusion, SCV streamlines the process of uncovering hidden errors and validating user-defined properties. It provides a comprehensive solution to mitigate potential pitfalls in blockchain-based applications.

Several high-level languages, such as LIGO \cite{ligo}, SmartPy \cite{smartpy}, and Liquidity \cite{liquidity}, provide a more readable syntax resembling popular programming languages. This allows developers to write Tezos smart contracts more comfortably. Our tools are applicable to all these languages because they compile to Michelson.
\section{Michelson}
\label{sec:background}
\lstset{language=michelson}
\begin{lstlisting}[float=tp,captionpos=b,caption={A Michelson program},label={lst:simple-program-add}]
parameter int;
storage   int;
code {                (* pair int int :: [] *)
  DUP; UNPAIR;        (* int :: int :: pair int int :: [] *) 
  COMPARE; GE;        (* bool :: pair int int :: [] *)
  IF {UNPAIR; SUB} {PUSH string 'Unexpected Pair'; FAILWITH};
                      (* int :: [] *)
  NIL operation; PAIR (* pair (list operation) int :: [] *)
}
\end{lstlisting}
Michelson is a stack-based, statically typed functional programming language. A program is defined by the type $S$ of its storage, the type $P$ of its single parameter, and a typed list of instructions for the underlying stack machine. It starts on a stack with one element containing a pair of the current storage value (taken from the blockchain) and the parameter value specified by the contract invocation. When the program finishes, the stack must contain a single element with a pair of the final storage value (to be saved on the blockchain) and a list of operations. These operations are syntactic commands, such as token transfers or contract invocations, among other possibilities. Thus, the program computes a function $P \times S \to O^* \times S$, where $O$ is the type of operations.

Besides the standard datatypes (e.g., numbers, lists, pairs, sums, functions) with the expected operations, Michelson supports a number of types and operations specific to blockchain applications (e.g., \texttt{mutez} for tokens) as shown in Fig.~\ref{fig:types}, where \textbf{cpt} denotes comparable types. The type system does not support quantification over types, and there are no user-defined types.

Listing~\ref{lst:simple-program-add} contains a short example of a Michelson program. The code is interspersed with comments indicating the types of values currently on the stack. This program first duplicates its input (\lstinline|DUP|), decomposes the pair $P \times S$ into its components (\lstinline|UNPAIR|), compares the two values on top of the stack (\lstinline|COMPARE|), and transforms the result into a boolean (\lstinline|GE|). The \lstinline|IF| instruction pops the boolean and either executes the first (for true) or second (for false) list of instructions. At this point, only the initial pair remains on the stack. In the true branch, \lstinline|UNPAIR| decomposes the pair, and \lstinline|SUB| subtracts the two components. In the false branch, the \lstinline|PUSH| instruction puts a string message on the stack. The \lstinline|FAILWITH| instruction aborts the contract execution: the tokens provided with the invocation are consumed, but the storage and balance of the contract remain unchanged. Finally, the \lstinline|NIL| instruction pushes an empty list of operations, and \lstinline|PAIR| creates the required pair of type $O^* \times S$.

A contract may have several entrypoints. Entrypoints are encoded by
using a sum type (call ``or type'' in Michelson). Each (nested) alternative in a sum can be
given a name, which is used as the name for an entrypoint. A call to
an entrypoint automatically adds the required \lstinline|LEFT| and
\lstinline|RIGHT| constructors to the parameter.
\lstset{language=Caml}
\section{SCV: A Domain Specific Language For Smart Contract Property Specification}
\label{sec:domain-specific-language}
SCV contains a domain-specific language to specify smart contract properties, aiming to be user-friendly for non-experts and compatible with SMT solvers. 
\begin{figure}[tp]
\begin{align*}
\textbf{cpt} &::= 
   \text{unit} 
   \Mid\text{never} 
   \Mid\text{bool} 
   \Mid\ \text{int}
   \Mid\text{nat}
   \Mid\text{string}
   \Mid\text{chain-id} 
    \Mid\text{bytes}
   \Mid\text{mutez} 
   \Mid\text{key-hash} \\
   &\Mid\text{key}
   \Mid \text{signature}
   \Mid \text{timestamp} 
   \Mid \text{address} 
   \Mid \text{option}\ \textbf{cpt}
   \Mid \text{or}\ \textbf{cpt}\ \textbf{cpt}
   \Mid \text{pair}\ \textbf{cpt}\ \textbf{cpt} \\
\text{T, U} &::= 
    \text{cpt}
   \Mid \text{option}\ \text{T}
   \Mid \text{list}\ \text{T}
   \Mid \text{set}\ \textbf{cpt} 
   \Mid \text{operation} 
   \Mid \text{contract}\ \text{T} \\
  & \Mid \text{pair}\ \text{T}\ \text{U}
   \Mid \text{or}\ \text{T}\ \text{U}
   \Mid \text{lambda}\ \text{T}\ \text{U} 
   \Mid \text{map}\ \textbf{cpt}\ \text{T}
   \Mid \text{big-map}\ \textbf{cpt}\ \text{T}
\end{align*}
\caption{Types}
\label{fig:types}
\end{figure}
\subsection{Basic syntax}
\label{sec:basic-syntax}
Listing~\ref{lst:sub-contract-specification} shows the specification of the \texttt{sub} contract in the SCV language. Here, \KMCONTRACT, \KSPEC, \KCODE, \KINPUT, \KOUTPUT, \KPRECONDI, and \KPOSTCONDI\ are keywords. The \KINPUT{} and \KOUTPUT{} fields specify the input and output patterns, which are terms on Michelson values.

Figure~\ref{fig:syntax-terms-predicates} contains the syntax of terms: A term \textbf{t} can consist of constants of the sort \text{nat} (natural number), \text{int} (integer), \text{string} (string), and \text{b} (bytes) along with their respective types. The type annotation may be omitted except for the type \text{nat} to distinguish it from integers. It also encompasses all blockchain constants \textbf{c}. When a variable appears for the first time, it must be accompanied by its type declaration. Subsequent mentions can omit the type declaration.

Since Michelson operates on a stack, we assume that the initial stack and the output stack each have only one element, as specified in the input term and the output term, respectively. The syntax allows us to specify both incomplete and complete smart contracts. For a complete smart contract, the output should be a pair consisting of an operation list and the storage's state after the completion of the code. For verification purposes, we elide the operation list and represent the output solely by the term of the value in the storage after execution concludes. %Michelson code, whether composed by users, obtained from the Tezos blockchain, or compiled from higher-level languages, can be seamlessly used within our framework.

The pre- and post-condition instances are formulas in first-order logic that can be handled by an SMT solver (specifically, Z3 in our case). The specification language is constructed from predicates. Formulas used in assertions or added to solvers are terms of Boolean type. Non-Boolean terms may also be used, and they can be mixed in any combination where types match appropriately.

Several predefined functions include \text{get\_map(e1, e2)}, which accesses an element in a map. If there is no key \text{e1} in the map \text{e2}, the function returns \text{None}; otherwise, it returns \text{Some(v)} where $v$ is the mapped value. Another function, \text{get\_contract(T, e)}, converts the address \text{e} to a contract on the Tezos blockchain. If no contract with an entrypoint of type \text{T} is associated with the address \text{e}, it returns \text{None}; otherwise, it returns the contract as \text{Some(c)}.

Certain functions are defined as predicates, such as \text{transfer\_token(e1, e2, e3)}. This predicate holds true if, after executing the smart contract code, there is an operation in the operation list indicating the transfer of \text{e2} tokens to address \text{e3} along with parameter \text{e1}\footnote{Additional predicates can be straightforwardly added if a mapping to Z3 formulas is defined.}.
\begin{lstlisting}[float,captionpos=b,caption={Specification of  the \lstinline/sub/ contract},label={lst:sub-contract-specification},numbers=left]
mcontract sub = spec
  code := {DUP; UNPAIR; COMPARE; GE; IF {UNPAIR; SUB} 
          {PUSH string 'Unexpected Pair'; FAILWITH}}
  input := Pair (x : int) (y : int)
  output := (z : int)
  pre-condition := (x >= y)
  post-condition := (z = x - y) && (z >= 0)
\end{lstlisting}

In Listing \ref{lst:sub-contract-specification}, the program takes as input a stack with only one
element, which is a pair of two integer variables \lstinline/x/ and \lstinline/y/, symbolically specified in the \lstinline|input| field. 
The specification continues by defining the output term as a variable \lstinline/z/ of interger, and 
pre- and post-conditions, where the precondition states the assumption
that the integer \lstinline/x/ is greater than or equal to  \lstinline/y/. The postcondition asserts that the result
\lstinline/z/ is equal to the substract of
\lstinline/x/ and \lstinline/y/, which is greater or equal to
zero. The symbol \lstinline/&&/ stands for conjunction. 
\begin{figure}[tp]
\begin{align*}
\textbf{c} & ::= 
    \text{pre\_Balance}
   \Mid \text{post\_Balance}
   \Mid \text{Amount}
   \Mid \text{Sender}
   \Mid \text{Source} 
   \Mid \text{Now}
   \Mid \text{Level} \\
   &\Mid \text{Chain\_id}
   \Mid \text{Self\_address}\\
\textbf{t} &::= 
   \textbf{n}: \text{nat}
   \Mid \textbf{i}: \text{int}
   \Mid  \textbf{s}: \text{string} 
   \Mid  \textbf{b}: \text{bytes}
   \Mid  \textbf{c}  
   \Mid  \text{x} 
   \Mid \text{x}: \text{T} 
   \Mid \UNIT 
   \Mid \NEVER 
   \Mid \TRUE \\
   &\Mid \FALSE 
   \Mid \PAIR\ \text{t1 t2}
   \Mid \LEFT\ \text{t}\  \text{T}
   \Mid \RIGHT\ \text{T}\ \text{t}
   \Mid \SOME\ \text{t}
   \Mid \NONE\ \text{T} 
   \Mid \text{\{t ; ... \}}: \text{list T} \\
   &\Mid \text{\{t ; ... \}}: \text{set T} 
   \Mid \text{\{ Elt t1 t2 ; ... \}}: \text{map T U}
   \Mid \text{\{ Elt t1 t2 ; ... \}}: \text{big\_map T U} \\
\textbf{e} & :: = \textbf{t}  \Mid \textbf{e} \text{ + } \textbf{e}\Mid \textbf{e} \text{ - } \textbf{e}  \Mid \textbf{e} \text{ * } \textbf{e} \Mid \textbf{e} \text{ / } \textbf{e} \Mid \textbf{e} \text{ \% } \textbf{e} \Mid \textbf{e} \text{ rem } \textbf{e} \\
& 
 \Mid \text{get\_map} (\textbf{e1}, \textbf{e2}) 
 \Mid \text{get\_big\_map} (\textbf{e1}, \textbf{e2})  
 \Mid \text{mem} (\textbf{e1}, \textbf{e2})  
 \Mid \text{get\_contract} (T, \textbf{e})    \\
& \Mid \text{abs} (\textbf{e})  
 \Mid \text{to\_int} (\textbf{e})  
 \Mid \text{from\_int} (\textbf{e})  
 \Mid \text{len} (\textbf{e})
 \Mid \text{cons} (\textbf{e}, \textbf{e})
 \Mid \text{size} (\textbf{e})
\Mid \textbf{e} \text{ $\wedge$ } \textbf{e}  \\
\textbf{p} & :: = \textbf{e} \text{ = } \textbf{e}
\Mid \textbf{e} \text{ $!=$ } \textbf{e}
\Mid \textbf{e} \text{ $>$ } \textbf{e}
\Mid \textbf{e} \text{ $>=$ } \textbf{e}
\Mid \textbf{e} \text{ $<$ } \textbf{e}
\Mid \textbf{e} \text{ $<=$ } \textbf{e} \\
& \Mid \text{transfer\_token} (\textbf{e1}, \textbf{e2}, \textbf{e3})  
 \Mid \text{is\_nat} (\textbf{e})  
 \Mid \text{contain} (\textbf{e1}, \textbf{e2}) 
 \Mid \text{forall} (\textbf{e1}, \textbf{e2})
\Mid \text{exist} (\textbf{e1}, \textbf{e2}) \\
& \Mid \textbf{p} \text{ \&\& } \textbf{p}\Mid \textbf{p} \text{ or } \textbf{p}  
% \Mid \textbf{p} \text{nor } \textbf{p} 
\Mid  \text{ not } \textbf{p} \Mid \textbf{p} \text{ $=>$ } \textbf{p} \\
\end{align*}
\caption{Syntax of constants, \textbf{c}, terms, \textbf{t}, expressions, \textbf{e}, and predicates, \textbf{p}}
\label{fig:syntax-terms-predicates}
\end{figure}
\subsection{Multiple entrypoints}
\label{sec:multiple-entrypoint}
The design of SCV enables us to verify all entrypoints
at once and to describe relationships between entrypoints. The entrypoint name is written after the \lstinline/%/ symbol and is followed by a property specification for the entrypoint.  The specification finishes with specifying entrypoint relations, which we explain next. For a smart contract, the input term includes the storage term before, and the output term represents the storage after the execution. Thus, there are two options of the syntax. The first option similar to the basic syntax with the entrypoint specific.  
In the second option, the input term is then the pair of the parameter term and the storage term. The prefix \lstinline/post_/ is used before the variables from the storage term to indicate the corresponding storage value after the execution.

Let us have a look at the specification for the auction
contract that models an online auction in Listing \ref{lst:auction-contract-specification}. The contract has two entry points, \lstinline|%bid| and \lstinline|%close|, which serve as functions for bidding and closing the contract, respectively. The smart contract storage is a pair containing, as its first element, a boolean value \lstinline|open| that indicates whether the contract is still open for bidding or already closed. The second element is another nested pair, where the first element \lstinline|highest| stores the highest bidder's address, and the second element \lstinline|owner| is the contract owner's address. The current highest bid is reflected in the balance of the contract before the next bid is invoked. We omit the Michelson code of the smart contract due to its length.  For the \lstinline/%bid/ entrypoint, the parameter is \lstinline/Unit/ of type \lstinline/unit/.
The current storage is described by the \lstinline|storage| phrase.

Closing the contract transfers the balance to the owner and is restricted to the owner. Both closing and bidding operations fail if the auction is already closed. If bidding is open and the amount of tokens accompanying the bid exceeds the current highest bid, the current bidder replaces the previous highest bidder, and the previous highest bidder is reimbursed. Otherwise, bidding fails. Upon deployment, the owner deposits an initial balance to indicate the minimum bid. The contract should be deployed with the storage value \lstinline|Pair True (Pair owner owner)|, indicating that bidding is allowed, and the contract owner is currently the highest bidder.

\begin{lstlisting}[float=tp,captionpos=b,caption={Auction contract specification},label={lst:auction-contract-specification},numbers=left]
mcontract auction = spec 
 storage := Pair (open: bool) 
                 (Pair (highest: address) (owner: address))
 entrypoint %bid
  code := {...}
  parameter := Unit 
  pre-condition := open = true && Amount > pre_Balance
   && get_contract (unit, highest) = Some (c: contract unit)
  post-condition := open = true && post_highest = Sender 
   && post_Balance = Amount && post_owner = owner 
   && transfer_token (Unit, pre_Balance, c);
 entrypoint %close
  ...
 (%create -> %bid) with ...
 | (%create  -> %close) with ...
 | (%bid -> %bid) with (Amount > pre_Balance) 
  && get_contract (unit, highest) = Some (c: contract unit)
 | (%bid -> %close) with (Sender = owner) 
  && get_contract (unit, owner) = Some (c: contract unit)
 | not (%close -> %bid) | not (%close -> %close)
\end{lstlisting}

%There are several properties that we want to guarantee for this contract. 
The first property is that if a user calls the \lstinline|%bid| entrypoint when the contract is still open for bidding and the bid is higher than the current bid (as specified in the \lstinline|pre-condition| field at line 7), and the address of the highest bidder can be cast to a real contract represented by the variable \lstinline|c| of type \lstinline|contract unit| on the blockchain (line 8), then the bid should succeed. In this case, the highest bidder must be updated to the sender, which is the address of the caller (line 9 in the \lstinline|post-condition| field), and the balance of the contract should be the amount sent along with the call (line 10). Moreover, the previous highest bidder should receive their bid back, which means the auction contract should transfer the \lstinline|pre_Balance| to the previous bidder, \lstinline|highest| (line 11). Another property guarantees that the auction owner's address should not be changed after calling the \lstinline/bid/ entrypoint (line 10). 
\subsection{Entrypoint relations}
\label{sec:entrypoint-relations}
Since the order of smart contract
calls can be crucial, we specify ordering constraints among calls with
 entrypoint relations. An entrypoint relation can be specified as
\lstinline/%a -> %b with p/, which starts with the name
\lstinline/%a/ of the entrypoint and is followed by the keyword
\lstinline/with/ in case conditions are specified as predicates. The
following symbol \lstinline/->/ indicates that from the entrypoint
that satisfies the condition \lstinline/p/, it is possible  to call
the entrypoint \lstinline/%b/. One specification can
contain several entrypoint relations concatenated by
\lstinline/|/. There is a special entrypoint named \lstinline/create/
that indicates the contract state after deployment.

Let us return to the auction contract. It is important to guarantee
that  the bid call can happen successfully after another if the new bid is higher than the previous
one (lines 16-17). The  \lstinline/%close/ entrypoint can be called
anytime after bidding if the caller is the contract owner (lines 18-19). However, it
should not be possible to call the  \lstinline/%bid/ entrypoint after
the auction is closed, and, of course, it cannot be closed
again if it is already closed (line 20).  Furthermore, contract deployment sets the  \lstinline/open/ flag to
\TRUE, indicating that the contract is open for bidding, i.e., users
should be able to bid on the contract or the contract owner should be
able to close it. Otherwise, the owner's original
deposit is lost. This sequence  illustrates
the life cycle of the auction contract, which is depicted in Figure
\ref{fig:auction-life-cycle}. Other properties related to the \lstinline|%close| entrypoint and the life cycle are omitted here, but the full specification can be found in the Appendix and in \cite{}.

\begin{figure}[tp]
    \centering
    \includegraphics[width=0.9\textwidth]{auction}
    \caption{Auction contract life cycle}
    \label{fig:auction-life-cycle}
\end{figure}

\section{Static Checker}
\label{sec:static-checker-we}
The architecture of the static checker is illustrated in Figure~\ref{fig:architecture-of-static-checker}. Users write specifications in the SCV DSL, which are then parsed into an Abstract Syntax Tree (AST) in OCaml. The input term along with the code is passed to the symbolic interpreter, while the output term and the pre- and post-conditions are fed to the static checker. The symbolic interpreter, which is fully typed and rejects ill-typed programs, then runs symbolic execution on the code with the provided input, where the initial stack is derived from the input term.

When a branch occurs, the interpreter sends the path condition to the Z3 converter to convert it into Z3 formulas, which are then passed to the Z3 solver to check whether the path conditions are satisfied. The result of this check determines the interpreter's action; if satisfied, the branch is added, otherwise, it is abandoned. This branch check significantly reduces the number of execution states, especially for stack-based languages like Michelson, where the programmer may need to perform the same check multiple times.

Once the symbolic execution finishes, the results (i.e., all reachable states) are sent to the static checker. Each state contains the post-storage updated after execution, the list of operations to emit, and the path conditions. The static checker then performs the following tasks: output check, property check, and generation of all fail conditions.

We utilize the Z3 library in OCaml to construct the Z3 converter. Some adjustments are necessary to convert these terms into Z3 formulas. For instance, since Z3 does not have a natural number type (\TNAT), it is mapped to Z3's integer type with an additional constraint asserting that the value is greater than or equal to zero. Several constants, such as \CAMOUNT\ and \CBALANCE, as well as cryptographic functions are predefined in the environment that applies to any smart contract specifications.

\begin{figure}[tp]
    \centering
    \includegraphics[width=1\textwidth]{scv}
    \caption{The architecture of the static checker}
    \label{fig:architecture-of-static-checker}
\end{figure}

Consider the specification of the \lstinline/sub/ contract, the results of
the symbolic execution are either a failwith state with the path
condition \lstinline/x/$<$\lstinline/y/,  or a state in which the
final stack has only one element, which is a symbolic variable
\lstinline/sbvar/ of type integer, with the path condition stating
that the variable \lstinline/x/ is greater than or equal to
\lstinline/y/ and  \lstinline/sbvar/ is equal to
the substract of \lstinline/x/ and \lstinline/y/.

We have implemented approximately 85\% of the Michelson instructions, including most of the major-use instructions. The remaining instructions were not implemented primarily due to time constraints rather than technical limitations.

\subsection{Output check}
\label{sec:output-check}
For an incomplete smart contract, the output term of the symbolic execution has the form of a term \Term\ and its type \TY. For a complete smart contract, it takes the form (\PAIR\ \VOPERATIONLIST\ \VSTORAGE, \TPAIR\ (\TOPERATIONLIST) \TYS) \STACKCONCAT\ \EMPTYSTACK, where \VSTORAGE\ represents the storage and \VOPERATIONLIST\ represents the operation list. Given an output term specified as $\tau$, the checker scans all reachable final states that do not contain a failwith stack and checks whether the output term matches. In the former case, it matches $\tau$ with the term \Term. In the latter case, it matches with \VSTORAGE.

For instance, in the \lstinline|sub| contract, the output check ignores the states where the failwith occurs and verifies whether the output term \lstinline|z| matches with the symbolic output term in the other state. It succeeds for this example as expected. However, this test could fail if, for example, the output term is incorrectly specified as a variable of a type that does not match the actual result.

\subsection{Fail conditions}
\label{sec:fail-conditions}
A Michelson contract can fail due to conditions introduced by the programmer, triggered by the \FAILWITH\ instruction along with an error message. Failures play a crucial role in smart contract programming to ensure that certain conditions lead to contract termination, such as unauthorized caller attempts (access control properties) or invalid arguments. Various smart contract standards, including \cite{erc, fa}, mandate specific fail conditions.

The static checker includes a feature to generate all fail conditions encountered in a smart contract. This tool identifies all instances where execution terminates due to the \FAILWITH\ instruction, collecting the associated path conditions and error messages. Users receive a comprehensive report detailing each fail condition along with its corresponding message. This capability is particularly powerful for verifying access control properties and other critical aspects across different smart contracts.

For instance, the entrypoint \lstinline|bid| has three fail conditions, as shown in Listing~\ref{lst:fail-condition-auction-contract-bid}: (1) If the auction is closed, (2) if the auction is open but the bid amount is less than or equal to the current balance, and (3) if the auction is open, the bid amount exceeds the balance, but the address of the highest bidder is invalid.

\begin{lstlisting}[float=tp,captionpos=b,caption={Fail condition for auction contract bid entrypoint },label={lst:fail-condition-auction-contract-bid},numbers=left]
1. not (open = true): 'Already closed'
2. (open = true) && not (Amount > pre_Balance):
   'Not higher than the current highest bid'
3. (open = true) && (Amount > pre_Balance) && 
   get_contract (unit, highest) = None: 'Invalid address' 
\end{lstlisting}
\subsection{Property check}
\label{sec:property-check}
%The SCV verify smart contract properties by using pre- and post-condition specifications. 
A property is
specified with the clause:  \lstinline/pre-condition := &&/
$\Phi_{i}$ followed by \lstinline/post-condition := &&/ $\Psi_{j}$. This
specification asserts that if all preconditions $\Phi_{i}$ hold before
smart contract execution, then all $\Psi_{j}$ must hold after
successful (i.e., without failure) termination. To verify this
property, the tool explore all the paths $\Pi$ 
with the path condition $\Theta$ such that ($\bigwedge \Phi_{i}$
$\land$ $\Theta$) is satisfiable. It then check that for every path
$\Pi$, $\neg$ ($\bigwedge \Phi_{i}$ $\land$ $\Theta$ $\rightarrow \bigwedge \Psi_{j}$) is unsatisfiable in the context given by the input for the entrypoint
and its final state. For example, for the \lstinline/sub/ contract, the failwith branch is discarded because the precondition is not satisfy with the path condition, and then \lstinline/z/ is matched to
the symbolic variable \lstinline/sbvar/ in the other branch. In this
example, the checker then verifies that $\neg$ ((\lstinline/x/ $>=$ y) $\land$ (\lstinline/z/
= \lstinline/x/ $-$ \lstinline/y/) $\rightarrow$ (\lstinline/z/ $=$ \lstinline/x/ $-$ \lstinline/y/) $\land$ (\lstinline/z/ $>=$ 0)) is unsatisfiable.

\subsection{Life-cycle check}
\label{sec:life-cycle-check}
An entrypoint relation can be defined as \lstinline/(%a -> %b) with p/, indicating that after invoking the entrypoint \lstinline/%a/, it is permissible to call the entrypoint \lstinline/%b/ if the condition \lstinline/p/ is satisfied. The presence of the keyword \lstinline/not/ at the beginning signals an impossibility. Note that \lstinline/with p/ may be omitted when no condition is needed.

Let $S_a$ represent the set of all reachable states resulting from the execution of the call to the entrypoint \lstinline/%a/. Each $s_{i}$ in $S_a$ is associated with a path condition $\Theta_i$ and is represented as a stack containing a single element—a pair consisting of an operation list ($\VOPERATIONLIST_i$) and the storage $\VSTORAGE_i$. For each $s_{i}$, symbolic execution is performed on the entrypoint \lstinline/%b/ using input as a pair of the parameter and the storage $\VSTORAGE_i$, constrained by $\Theta_i$ and the condition \lstinline/p/. In the execution state space, a state $s_{j}$ with the path condition $\Theta_j$ is considered reachable if ($\Theta_i$ $\land$ \lstinline/p/ $\land$ $\Theta_j$) is satisfiable, and $\neg$ ($\Theta_i$ $\land$ \lstinline/p/ $\rightarrow$ $\Theta_j$) is unsatisfiable. Let $S_b$ denote the set of these reachable states. If $S_b$ is empty or contains only failwith states, then it is impossible to invoke the entrypoint \lstinline/%b/ from the state $s_{i}$. Otherwise, it is considered a success. Let $R$ be the set containing all such states $s_{i}$ in $S_a$ where it is successful to call the entrypoint \lstinline/%b/ with the condition \lstinline/p/. If $R$ is non-empty, then \lstinline/(%a -> %b) with p/ holds. Otherwise, it is false, signifying \lstinline/not (%a  -> %b) with p/.
\section{Case Studies}
\label{sec:case-stud-subs}

This section reports two case studies which are taken from the realm of financial applications deployed on the Tezos blockchain.

\subsection{USDtz}
\label{sec:usdtz}
In a blockchain ecosystem, tokens function as digital assets that can be transferred between accounts. These tokens come in various types, which include native tokens (cryptocurrencies) like Bitcoin and Tezos, as well as digital tokens created through smart contracts on an existing blockchain.

It is advisable to implement tokens that adhere to established standards, such as ERC-20 \cite{erc} for Ethereum \cite{eth-whitepaper}, ensuring interoperability and compatibility across different platforms. A token standard specifies a set of rules and an interface that smart contracts must adhere to. The Tezos blockchain has its own set of standards known as Financial Applications (FA) in which FA 1.2 \cite{fa} is designed for fungible tokens.
\begin{lstlisting}[float=tp,captionpos=b,caption={FA 1.2 interface},label={lst:fa12-interface},numbers=left]
(address :from, (address :to, nat :value))    %transfer
(address :spender, nat :value)                %approve
(view (address :owner, address :spender) nat) %getAllowance
(view (address :owner) nat)                   %getBalance
(view unit nat)                               %getTotalSupply
\end{lstlisting}

Any contract aiming to implement the FA 1.2 standard must incorporate the functions specified in Listing~\ref{lst:fa12-interface}. We verify USDtz \cite{usdtzimplemetation, tzstatsusdtz}, an implementation of the FA 1.2 standard. The goal is to ensure that the implementation aligns with the standard, verifying its correctness. USDtz is designed to maintain a stable value by pegging it to a fiat currency like USD or EUR, and it has been operational on the Tezos blockchain for a significant period.

The implementation consists of approximately 1000 instructions, covering the five required entrypoints for the FA 1.2 standard and four additional ones. The storage contains a ledger (\lstinline/ledger/), which is a substantial map linking user addresses (\lstinline/user/) to a pair consisting of their balance (\lstinline/balance/) and a map (\lstinline/approvals/) associating addresses (\lstinline/spender/) with the amount of tokens (\lstinline/value/) allowed to be transferred from that user's account. It also includes additional information such as the admin address (\lstinline/admin/), total supply (\lstinline/totalSupply/), and the smart contract state (\lstinline/paused/).

The \lstinline/transfer/ entrypoint credits the account associated with the address provided in the \lstinline/to/ parameter while debiting the account corresponding to the \lstinline/from/ parameter with the specified \lstinline/value/ amount. According to the FA 1.2 standard, this call must fail under two specific conditions: (1) The entrypoint must fail with the error \lstinline/NotEnoughBalance/ if the sender's account lacks sufficient funds. (2) If the sender's account does not have permission to withdraw the specified \lstinline/value/ amount, the call will fail with the \lstinline/NotEnoughAllowance/ error. To verify these requirements, we utilize the failwith condition feature of our tool and examine the returned results, some of which are outlined in Listing~\ref{lst:transfer-udstz-contract}. The fail condition results confirm these stipulations.
\begin{lstlisting}[float,captionpos=b,caption={The not enough balance fail condition for the \lstinline/transfer/ entrypoint},label={lst:transfer-udstz-contract},numbers=left]
not (paused = true) 
&& get_big_map (from, ledger) = Some sbvar 
&& sbvar = Pair sbvar1 sbvar2 
&& not (sbvar1 >= value) : 'NotEnoughBalance'
\end{lstlisting}
Another essential property is ensuring that the allowance of the sender's account is decremented and the receiver's account is incremented by the \lstinline/value/ that has been sent. This specification is verified to ensure compliance with the contract's intended behavior.

The \texttt{approve} entrypoint grants the spender the right to transfer a specified amount from the owner's account. The contract prohibits changing the allowance value from a non-zero value to another non-zero value to prevent a known attack vector \cite{attack-vector}. This attack exploits the ability to spend the entire allowance before an update and then again after, resulting in a larger amount being spent than allowed. Therefore, the contract call must fail if both the parameter \lstinline/value/ and the current allowance of \lstinline/spender/ are non-zero. We verify this critical property by generating fail conditions to check whenever such a non-zero value update results in a fail condition as Listing \ref{lst:approve-udstz-contract}.
\begin{lstlisting}[float=tp,captionpos=b,caption={The non-zero value fail condition for the \lstinline/approve/ entrypoint},label={lst:approve-udstz-contract},numbers=left]
not (paused = true) 
&& get_big_map(Sender, ledger) = Some sbvar 
&& sbvar = Pair sbvar1 sbvar2 
&& get_map(spender, sbvar2) = Some sbvar3 
&& not(value = 0) && not(sbvar3 = 0): 'UnsafeAllowanceChange'
\end{lstlisting}

When the update is allowed, the updated value must be correctly recorded in the storage. This can be divided into two sub-properties: (1) if the parameter \lstinline/value/ is zero, then the corresponding allowance value of the \lstinline/spender/ from the owner (which is \SENDER\ in this call) should be zero, and (2) if \lstinline/value/ is non-zero and the allowance of the \lstinline/spender/ is zero, then the \lstinline/value/ should be recorded in the storage after the call. We specify these properties using pre- and post-conditions, as illustrated in Listing~\ref{lst:specification-approve-1} for the first property.

The \lstinline/getAllowance/, \lstinline/getBalance/, and \lstinline/getTotalSupply/ entrypoints are view entrypoints that retrieve information from the storage without altering the state of the smart contract. For a view entrypoint implementation, it's crucial to return the \lstinline/TRANSFER_TOKENS/ operation targeted at the specified contract with accurate details. Another important property is that all Tezos tokens passed to a view entrypoint should be forwarded to the callback contract, and there should be no modifications made to the ledger. This ensures that view entrypoints maintain their non-modifying nature, strictly adhering to the expected behavior in blockchain environments.

We specified and verified all the properties mentioned above and others. The results confirm that these properties are guaranteed, ensuring the correctness of the smart contract code.
\begin{lstlisting}[float=tp,captionpos=b,caption={Specification of the \lstinline/approve/ entrypoint (Property 1)},label={lst:specification-approve-1},numbers=left]
entrpoint %approve
 parameter := Pair (spender: address) (value: nat)
 pre-condition := not (paused = true)
  && get_big_map (Sender, ledger) = 
     Some (v: pair nat (map address nat))
  && v = Pair (n: nat) (m: map address nat) 
  && get_map (spender, m) = Some (k: nat) 
  && not (k = 0) && (value = 0)
 post-condition := get_big_map (Sender, post_ledger) = 
    Some (post_v:  (pair nat (map address nat))
  && post_v = Pair (post_n: nat) (post_m: map address nat) 
  && get_map (spender, post_m) = Some (post_k: nat) 
  && (post_k = 0) ;
\end{lstlisting}

\subsection{Kolibri Oracle Contract}
\label{sec:kolibri-oracle-contr}
The potential of smart contracts is constrained by their inability to access external data sources. To address this limitation, oracles play a pivotal role in providing external data for smart contracts. Since certain essential properties must be satisfied by an oracle contract, including data approvability, this case study illustrates the process of specifying and verifying an oracle contract using SCV, with the Kolibri oracle contract \cite{kolibri} as an example.

The Kolibri oracle contract ensures the accuracy of external data for the Tezos-based stablecoin Kolibri by leveraging the Harbinger Price Feed. The contract initiates calls to a Harbinger Normalizer contract, checks the returned values, normalizes them to suit the Kolibri system, and subsequently relays them to the client. Key attributes stored by the oracle include: the address of the Harbinger contract (\lstinline/harbinger/) \footnote{Here, we shortened the names of the variables for the storage.}, the current state of the contract (\lstinline/state/), a callback contract awaiting Harbinger data (\lstinline/client/), the address of the governor contract (\lstinline/governor/), and the maximum acceptable age of data received from Harbinger (\lstinline/maxDelay/). The oracle contract offers various entrypoints, including:
\begin{itemize}
\item \lstinline/getXtzUsdPrice/: Processes the client request and calls the Harbinger contract.
\item \lstinline/getXtzUsdPrice_callback/: Relays the Harbinger price to the client.
\item \lstinline/setMaxDelaySec/: Resets the \lstinline/maxDelay/ attribute.
\item \lstinline/setGovernorContract/: Allows setting the Governor's address.
\end{itemize}

The Kolibri oracle maintains a state machine with two states: (1) \lstinline/IDLE/ and (2) \lstinline/WAITING_FOR_HARBINGER/. The \lstinline/getXtzUsdPrice/ entrypoint is permissible only when the oracle is in the \lstinline/IDLE/ state; invoking this entrypoint transitions the oracle to the \lstinline/WAITING_FOR_HARBINGER/ state. Conversely, the \lstinline/getXtzUsdPrice_callback/ entrypoint is allowable solely when the oracle is in the \lstinline/WAITING_FOR_HARBINGER/ state; invoking this entrypoint results in the oracle transitioning back to the \lstinline/IDLE/ state. The value of \lstinline/client/ is always set to \lstinline/none/ in the \lstinline/IDLE/ state and to \lstinline/some/ in the other state. We verify this property by examining the fail conditions of these two entrypoints and verifying the entrypoint relation between \lstinline/getXtzUsdPrice/ and \lstinline/getXtzUsdPrice_callback/.

The two subsequent properties dictate that if \lstinline/getXtzUsdPrice/ is successfully executed, the parameters must be stored in the \lstinline/client/ attribute. \\ If \lstinline/getXtzUsdPrice_callback/ is successful, there must be a transaction transferring the data to the client at the \lstinline/client/. These properties are checked by using pre- and post-conditions. Futhermore, the critical access control property is that the entrypoints \lstinline/setGovernorContract/ and \lstinline/setMaxDelaySec/ must only be invocable by the governor. Any attempts by unauthorized callers to these entrypoints should result in failure.

When verifying the entrypoint \lstinline/setMaxDataDelaySec/, we noticed an unmatched statement. According to \cite{kolibri}, the Kolibri oracle is expected to perform two checks on data returned from Harbinger: (1) confirming the asset returned is 'XTZ-USD' and (2) verifying the asset was updated within the last 30 minutes. We conducted fail condition checks for both the \lstinline/setMaxDelaySec/ and \lstinline/getXtzUsdPrice_callback/ entrypoints, but these conditions were not enforced. Specifically, upon examining the failwith conditions, we detected that there is no failwith if the data is more than 30 minutes (equal to 1800 seconds).

We then add the predicate \lstinline/post_maxDelay <= 1800/ in the post condition of the entrypoint \lstinline/setMaxDataDelaySec/ as shown in Listing \ref{lst:setMaxDataDelaySec}, but then the pre and post condition test fails. This means there is no constraint that the data is less than 30 minutes. This constraint is possibly set up by the governor and specified in the \lstinline/MaxDataDelaySec/ field. However, users calling this contract should be aware that it is possible for the governor to set any value ($>=0$) as desired. This could lead to providing out-of-date rates.

\begin{lstlisting}[float=tp,captionpos=b,caption={The specification of the setMaxDataDelaySec entrypoint},label={lst:setMaxDataDelaySec},numbers=left]
entrypoint %setMaxDataDelaySec
 code := {...}
 parameter := delay: nat
 pre-condition := Sender = governor            
 post-condition := post_maxDelay = delay 
 && post_harbinger = harbinger && post_maxDelay <= 1800
\end{lstlisting}

The complete specifications and experimental results for the examples and case studies can be found in the appendix~\ref{sec:concl-sect-append} or accessed online at \cite{}.
\section{Symbolic Execution Model}
\label{sec:symbolic-execution-model} 
We address the changes required for symbolic execution of Michelson programs, focusing on a selection of instructions. The
appendix~\ref{sec:concl-sect-append} specifies further instructions,
but may be skipped by the reviewers.

\subsection{System Model}
\label{sec:system-model}
Our symbolic model of a program state consists of a stack where each element is a symbolic value, represented as a pair comprising a Michelson term and its type: \STACK\ = (\TermOne, \TYF) \STACKCONCAT\ (\TermTwo, \TYS) \STACKCONCAT\ \DOT\ \STACKCONCAT\ \EMPTYSTACK. Here, \ensuremath{[\ ]} represents the empty stack, and \ensuremath{hd :: tl} denotes a stack with \ensuremath{hd} as the top element and \ensuremath{tl} as the remaining stack. Let \INSTRUCTION\ = \InstructionOne; \InstructionTwo; \DOT\ \InstructionN\ be a sequence of instructions, and \PREDICATE\ be a path predicate expressed in conjunctive form, capturing the branching conditions.
\begin{definition}
A symbolic execution state is represented by a tuple \STATE\ =
[\INSTRUCTION, \STACK, \PREDICATE].
A system configuration, \SYSTEM\ = \{\STATEONE, \STATETWO,
\DOT, \STATEN \}, is a set of  states.
\end{definition}

\subsection{Rules}
An instruction is defined by rules on a system configuration. There are two kinds of transitions: (1) \StateTrans\ internal transitions of a state, which are non-deterministic, and (2) \SystemTrans\ system transitions, which pick any state and replace it with all distinct states reachable by internal transitions, exploiting the non-determinism of the \StateTrans\ relation.

A state is unreachable if its predicate \PREDICATE\ is  not
satisfiable. The following rule drops unreachable states.
\begin{mathpar}
\inferrule[]
  { \UNSAT\ \PREDICATE
  }{
  \{[\INSTRUCTION, \STACK, \PREDICATE]\} \cup \SYSTEM \SystemTrans \SYSTEM}
\end{mathpar}
The symbolic interpreter works as a graph with states as nodes and transitions as edges. This representation simplifies performing multi-step subtransitions needed for some operations.

The semantics of the symbolic rules for the instructions adhere to the formal definitions of the Michelson language as outlined in \cite{} and \cite{}.These rules are classified based on how we handle them in our model.

\paragraph{One-step instructions}
One-step instructions directly modify the system state without branching, have a localized effect, and are modeled with a single rule.
\paragraph{Multi-step instructions}
Multi-step instructions involve the execution of a sub-sequence of instructions before returning to the main execution. The rule below models the \EXEC\ instruction, which executes a function specified as a sequence of instructions denoted by \INSTRUCTIONONE\ in the rule. This instruction applies the code of the function to the first element of the stack and then places the result back into the main execution.
\begin{mathpar}
  \inferrule[]
  { [\INSTRUCTIONONE, (\StackOne, \TYF) \STACKCONCAT \EMPTYSTACK, 
    \PREDICATE]
    \StateTrans^*
    [ \EMPTYSTACK, (\StackOne', \TYS) \STACKCONCAT \PREDICATE']}{[(\EXEC; \INSTRUCTION),   (\{\INSTRUCTIONONE\}, \TYF\ \rightarrow\ \TYS) \STACKCONCAT
    (\StackOne, \TYF) \STACKCONCAT \STACK, \PREDICATE] 
    \StateTrans \
    [ \INSTRUCTION, (\StackOne', \TYS) \STACKCONCAT \STACK,
    \PREDICATE]}
\end{mathpar}
\paragraph{Blockchain instructions}
 Blockchain instructions, such as the \AMOUNT\
 instruction make implicit use of data from the transaction, the block and the current state of the blockchain. As these values are constant during the execution of a contract, we model them as fixed variable. 
\paragraph{Branch instructions}
The \IF\ \{\INSTRUCTIONONE\} \{\INSTRUCTIONTWO\} instruction expects
and consumes a boolean value at the top of the stack. If the boolean
is True, it executes \INSTRUCTIONONE; otherwise, it executes
\INSTRUCTIONTWO. 
Other branch instructions, such as IF-LEFT and IF-NONE are handled in the similar way.

\begin{mathpar}
  \inferrule[]
  { }{
    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
    \StateTrans\
    \{[\INSTRUCTIONONE, \STACK, \PREDICATE\ \Wedge\ \StackOne],   [\INSTRUCTIONTWO, \STACK, \PREDICATE\ \Wedge\ \NEG\
   \StackOne]\}} 
\end{mathpar}
\paragraph{Loop instructions}
The loop instructions, including
\LOOP\ and \LOOPLEFT\ check the loop condition by examining the
top of the stack. These loop instructions may not terminate, just like while-loops. There are further loop instructions, like \ITER\ and
\MAP, specialized to traverse data structures like lists, sets, and maps. There are also
some instructions that implicitly require looping like \CONCAT, and
\SIZE. The latter kinds of loop instructions do always terminate.

Let us first take look at the terminate loops. The following rule handles the  \ITER\ loop for  the non-empty list \footnote{\ITER\ can also iterate over sets and maps, but the
  details are very similar to the list case and hence omitted.} while the \ITER\ loop terminates when the list is empty. 
\begin{mathpar}
  \inferrule[]
  { \HEAD, \STAIL\ \FRESH \\
    [\ITER,  (\HEAD, \TY) \STACKCONCAT\STACK, 
    \PREDICATE]
    \StateTrans^*
    [ \EMPTYSTACK,  \STACK', \PREDICATE']
  }{
    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\
    \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \\
    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\STAIL, \TYLIST\ \TY)\
    \STACKCONCAT\STACK',  \PREDICATE' \Wedge  (\StackOne\
    \EQ\ \{\HEAD; \STAIL \}) ] 
  }
\end{mathpar}
It symbolically executes the instructions \INSTRUCTIONONE\ within the
\ITER\ block with the head of the list (\HEAD) replacing the list. The resulting state transitions to a
new stack (\STACK') and an updated predicate (\PREDICATE' $\Wedge$
(\StackOne \EQ \{\HEAD;\STAIL\})), where \STAIL\ represents the rest of the list.

How do we deal with \ITER\ if the list is a symbolic value?
One solution could involve running the loop for a number of times to obtain the symbolic value. However, we can defer that decision by exploiting features of Z3. 
In fact, the loop body \INSTRUCTIONONE\ can be considered a function applied to a stack
of type \TY\ \STACKCONCAT\ \TYA,
resulting in a stack of type \TYA. If the first element of
the stack is a list of the form \LIST\ = $x_1 \STACKCONCAT x_2 \STACKCONCAT
\dots x_m \STACKCONCAT  [\ ]$, and the rest of the stack is \STACKZERO\ =
\StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ ... \STACKCONCAT\
\StackN. Then the \ITER\ \{\INSTRUCTIONONE\} instruction applies a 
function, sat \F, represented by \INSTRUCTIONONE\ \M\ times to the stack, once
with each element $x_i$ of the list \LIST\ on top of the stack. The result after 
the first iteration is \STACKONE\ = \StackOneOne\  \STACKCONCAT\
\StackTwoOne\ \STACKCONCAT\ ... \STACKCONCAT\ \StackNOne = \F\ $x_1$
\STACK, and so on. In conclude, we can represent the result stack as the result of a fold function that applies  \F\ to the list. The \FOLD\ function also can be used to express the result of other loop instructions, such as CONCAT and SIZE, symbolically. 
\begin{mathpar}
\STACK'\ =  \FOLD\ \F\ \STACK\ \LIST
\end{mathpar}

In similar stragtery, symbolically the result of the \MAP\
\{\INSTRUCTION\} to the list \LIST\ is the result of a map function
that applies the function \F\ that represent of the sequence of
instructions \I\ to the list. 
\begin{mathpar}
\MAP\ \{\INSTRUCTIONONE\} \Slash\ \LIST\ :: \STACK\ \SRightarrow\ (\FMAP\ \F\ \LIST) ::  \STACK
\end{mathpar}

Finally, we consider a loop instruction that may not terminate, such as \LOOP\ and and \LOOPLEFT. 
When the input to the symbolic execution consists of concrete values, an unbounded loop causes the interpreter to iterate for a significant number of times until it halts with an exception indicating an unfinished loop. This mirrors the behavior observed in the actual execution of Tezos contracts, where the loop continues until it runs out of gas, terminating the computation with an out-of-gas error. For a symbolic value, the stack type is determined before the loop is executed. We abstract the result of the loop  and the loop condition as the abstract function results. 
This abstraction helps detect whether the loop is unbounded, such as when the condition result of the function is always true.

In separate work (which is currently in submission), we have designed a dynamic logic tailored to Michelson as a formal foundation for the implementation of SCV. We have a soundness proof of this logic formalized in the Agda proof assistant, which is omitted here due to the pages limit.
\section{Related Work}
\label{sec:related-work}
%Research on the formal verification of blockchain-based applications has experienced rapid growth in the last decade.

In this section, we discuss some key approaches, particularly those employing symbolic execution in the context of smart contracts. P. Tsankov et al. introduced
SECURIFY \cite{securify}, a tool that utilizes symbolic execution to
perform practical security analysis on Ethereum smart contracts. It
targets common vulnerability security patterns specified in a
designated domain-specific language. 
Similarly, Manticore
\cite{manticore} and KEVM \cite{kevm} also target Ethereum smart contracts. KEVM is an executable formal
specification built with the K Framework.
Since tokens can hold a significant amount of value, they are often targeted for
attacks. Therefore, several tools \cite{kevm,park} conduct case
studies for the implementations of token standards.

Several approaches use existing formal verification frameworks to
ensure the correctness and security of smart contracts. S. Amani et
al. \cite{isabelle} proposed the formal verification of Ethereum smart
contracts in Isabelle/HOL. Hirai \cite{hirai} formalizes the EVM using
Lem, a language to specify semantic definitions.

There are exsiting tools for automated verification include solc-verify \cite{solc}, VerX \cite{verx}, and Oyente \cite{oyente}. solc-verify processes smart contracts written in Solidity and discharges verification conditions using modular program analysis and SMT solvers.
While these approaches differ, they share a focus on common bugs (such as reentrancy, overflow or underflow, and frozen funds). Our tool provide an environment where users can reliably specify their own properties and identify contract-specific bugs. Our tool aims to rich specifications to supports manually specified full correctness specifications.

Close to our approach are HELMHOLTZ \cite{helmholtz} and Mi-Cho-Coq ~\cite{micho} as discussed in Section \ref{}. In HELMHOLTZ, properties annotated inside the code by the developer. Here, we provide a separate specification language that users don't need to modify within the code. 
Similar to our tool, iContract \cite{icontract} based on synbolic execution utilizes pre and post conditions to specify user properties, but targets the Solidity language.

\section{Conclusion}
\label{sec:concl-sect-append}
Symbolic execution is well known to suffer from challenges related to
state explosion, particularly when applied to large
systems. Tackling this problem in the implemetation of the tool, our tool conducts two real case studies of running blockchain contracts, implementing significant subjects on the blockchain such as token standards and oracles.

In future work, we want to extend SCV in two directions. 
First, we want to address the interaction of several entrypoints by
extending the specification language to state allowed sequences of
contract invocations.  Second, a Michelson program returns a list of instructions, which may contain
further contract invocations. Dealing with this kind of contracts
requires an extension to the symbolic interpreter so that a sequence
of contract invocations can be processed in one run.

\newpage
\bibliographystyle{splncs04}
\bibliography{bio}

\newpage
\include{appendix}
\end{document}

### 2024-06-04 papers/static-checker/aplas/paper.tex
The last version

@@
 \begin{abstract}
-We developed SCV, a verification tool that is geared towards contracts implemented in Michelson, the smart contract language of the Tezos blockchain.
-SCV relies on symbolic execution to derive verification conditions that can be checked automatically against the user's specifications by employing an SMT solver.
+We developed SCV, a verification tool geared towards contracts implemented in Michelson, the smart contract language of the Tezos blockchain.
+SCV utilizes symbolic execution to derive verification conditions that can be checked automatically against user specifications using an SMT solver.
 These specifications are written in a domain-specific language.
 We present the fundamental principles behind the design and development of SCV.
-By pruning states during symbolic execution, SCV addresses the problem of state explosion.
+By pruning states during symbolic execution, SCV effectively addresses the problem of state explosion.
 This approach has enabled us to conduct two case studies on real-life contracts, demonstrating the expressiveness of our tool.
@@
 \label{sec:introduction}
-Since smart contracts are permanently stored on the blockchain, once a smart contract is deployed, it cannot be changed.
+Since smart contracts are permanently stored on the blockchain, once deployed, a smart contract cannot be changed.
 Regrettably, numerous instances have been documented where vulnerabilities in smart contracts were identified by the blockchain community, resulting in substantial financial losses~\cite{dao,wallethack}.
 The distinctive execution model of smart contract languages has given rise to unforeseen errors due to a lack of familiarity with their complexities.
-These observations, combined with the immutability of contracts, underscore the need to ensure their correctness prior to deployment.
+These factors, combined with the immutability of contracts, underscore the need to ensure their correctness prior to deployment.
 
@@
 SCV relies on symbolic execution backed by an SMT solver to simulate the implementation of the smart contract language, helping to detect subtle errors.
-Additionally, SCV comes with a domain-specific language to precisely specify smart contract properties, tailored to Michelson's execution model and inspired by Z3.
+Additionally, SCV includes a domain-specific language for precisely specifying smart contract properties, tailored to Michelson's execution model and inspired by Z3.
 Each specification consists of Michelson code, a precondition, and a postcondition with the usual partial correctness semantics.
 Our symbolic interpreter calculates a postcondition predicate from the specified precondition.
-The SMT solver Z3 \cite{z3} checks that this predicate implies the specified postcondition.
+The SMT solver Z3 \cite{z3} then checks that this predicate implies the specified postcondition.
 
-%We have implemented approximately 85\% of the Michelson instructions, including most of the major-use instructions.
-The remaining instructions were not implemented primarily due to time constraints rather than technical limitations.
-
-%One of the main challenges with formal verification is that users are often required to specify a system and express its properties in a specialized specification language.
-This requirement poses two problems: it demands expertise in formal verification from the specifier and introduces a gap between the actual code and its specification.
-In our framework, the actual Michelson code is used and users are not obliged to possess formal verification expertise.
-A basic understanding of Michelson data types and their usage when interacting with a smart contract on the Tezos blockchain is sufficient.
-
-While there is already a considerable body of work applying symbolic execution to the verification of smart contracts \cite{securify, manticore, kevm, park} (see Section~\ref{sec:related-work} for details), most of these efforts are designed for Ethereum, where standard techniques for symbolic execution of imperative programs are applicable.
+While there is already a considerable body of work applying symbolic execution to the verification of smart contracts \cite{securify,manticore,kevm,park} (see Section~\ref{sec:related-work} for details), most of these efforts are designed for Ethereum, where standard techniques for symbolic execution of imperative programs are applicable.
 Such groundwork does not exist for Michelson, which is a functional language running on a stack machine (see Section~\ref{sec:background}) with a sophisticated instruction set that includes high-level loops.
@@
 
+SCV utilizes an SMT solver to eliminate invalid states during symbolic execution, addressing the problem of state explosion.
+This capability enabled SCV to conduct two case studies involving real smart contracts that have been operational on the Tezos blockchain for quite some time.
+Despite extensive testing, a flaw was reported in the Kolibri oracle contract.
+In conclusion, SCV streamlines the process of uncovering hidden errors and validating user-defined properties.
+It provides a comprehensive solution to mitigate potential pitfalls in blockchain-based applications.
+
 Our contributions are as follows.
@@
 \end{enumerate}
-
-SCV utilizes an SMT solver to eliminate invalid states during symbolic execution, addressing the problem of state explosion.
-This capability enabled SCV to conduct two case studies involving real smart contracts that have been operational on the Tezos blockchain for quite some time.
-Despite extensive testing, a flaw was reported in the Kolibri oracle contract.
-In conclusion, SCV streamlines the process of uncovering hidden errors and validating user-defined properties.
-It provides a comprehensive solution to mitigate potential pitfalls in blockchain-based applications.
 
@@
 
-Since Michelson operates on a stack, we assume that the initial stack and the output stack each have only one element, as specified in the input term and the output term, respectively.
+Since Michelson operates on a stack, we assume that the input stack and the output stack each have only one element, as specified in the input term and the output term, respectively.
 The syntax allows us to specify both incomplete and complete smart contracts.
@@
 The specification continues by defining the output term as a variable \lstinline/z/ of interger, and 
-pre- and post-conditions, where the precondition states the assumption
+pre and postconditions, where the precondition states the assumption
 that the integer \lstinline/x/ is greater than or equal to  \lstinline/y/. The postcondition asserts that the result
@@
 Let us have a look at the specification for the auction
-contract that models an online auction in Listing \ref{lst:auction-contract-specification}.
+contract that models an online auction in Listing \ref{lst:auction-contract-specification1}.
 The contract has two entry points, \lstinline|%bid| and \lstinline|%close|, which serve as functions for bidding and closing the contract, respectively.
@@
 
-\begin{lstlisting}[float=tp,captionpos=b,caption={Auction contract specification},label={lst:auction-contract-specification},numbers=left]
+\begin{lstlisting}[float=tp,captionpos=b,caption={Auction contract specification},label={lst:auction-contract-specification1},numbers=left]
 mcontract auction = spec 
@@
 Moreover, the previous highest bidder should receive their bid back, which means the auction contract should transfer the \lstinline|pre_Balance| to the previous bidder, \lstinline|highest| (line 11).
-Another property guarantees that the auction owner's address should not be changed after calling the \lstinline/bid/ entrypoint (line 10).
+Another property guarantees that the auction owner's address should not be changed after calling the \lstinline/bid/ entrypoint (line 10) and the auction should be still open (line 9).
 \subsection{Entrypoint relations}
@@
 the life cycle of the auction contract, which is depicted in Figure
-\ref{fig:auction-life-cycle}. Other properties related to the \lstinline|%close| entrypoint and the life cycle are omitted here, but the full specification can be found in the Appendix and in \cite{}.
+\ref{fig:auction-life-cycle}.
+Other properties related to the \lstinline|%close| entrypoint and the life cycle are omitted here due to page limits.
+%, but the full specification can be found in the Appendix and is available online at \cite{scv}.
 
@@
 The architecture of the static checker is illustrated in Figure~\ref{fig:architecture-of-static-checker}.
-Users write specifications in the SCV DSL, which are then parsed into an Abstract Syntax Tree (AST) in OCaml.
-The input term along with the code is passed to the symbolic interpreter, while the output term and the pre- and post-conditions are fed to the static checker.
+Users write specifications in the SCV language, which are then parsed into an Abstract Syntax Tree (AST) in OCaml.
+The input term along with the code is passed to the symbolic interpreter, while the output term and the pre and postconditions are fed to the static checker.
 The symbolic interpreter, which is fully typed and rejects ill-typed programs, then runs symbolic execution on the code with the provided input, where the initial stack is derived from the input term.
@@
 the symbolic execution are either a failwith state with the path
-condition \lstinline/x/$<$\lstinline/y/,  or a state in which the
+condition \lstinline/x/ $<$ \lstinline/y/,  or a state in which the
 final stack has only one element, which is a symbolic variable
@@
 For an incomplete smart contract, the output term of the symbolic execution has the form of a term \Term\ and its type \TY.
-For a complete smart contract, it takes the form (\PAIR\ \VOPERATIONLIST\ \VSTORAGE, \TPAIR\ (\TOPERATIONLIST) \TYS) \STACKCONCAT\ \EMPTYSTACK, where \VSTORAGE\ represents the storage and \VOPERATIONLIST\ represents the operation list.
+For a complete smart contract, it takes the form \PAIR\ \VOPERATIONLIST\ \VSTORAGE, \TPAIR\ (\TOPERATIONLIST) \TYS, where \VSTORAGE\ represents the storage and \VOPERATIONLIST\ represents the operation list.
 Given an output term specified as $\tau$, the checker scans all reachable final states that do not contain a failwith stack and checks whether the output term matches.
@@
 
-For instance, in the \lstinline|sub| contract, the output check ignores the states where the failwith occurs and verifies whether the output term \lstinline|z| matches with the symbolic output term in the other state.
+For instance, in the \lstinline|sub| contract, the output check ignores the states where the failwith occurs and verifies whether the output term \lstinline|z| matches with the symbolic output term \lstinline/sbvar/ in the other state.
 It succeeds for this example as expected.
@@
 Failures play a crucial role in smart contract programming to ensure that certain conditions lead to contract termination, such as unauthorized caller attempts (access control properties) or invalid arguments.
-Various smart contract standards, including \cite{erc, fa}, mandate specific fail conditions.
+Various smart contract standards, including \cite{erc,fa}, mandate specific fail conditions.
 
@@
 Any contract aiming to implement the FA 1.2 standard must incorporate the functions specified in Listing~\ref{lst:fa12-interface}.
-We verify USDtz \cite{usdtzimplemetation, tzstatsusdtz}, an implementation of the FA 1.2 standard.
+We verify USDtz \cite{usdtzimplemetation,tzstatsusdtz}, an implementation of the FA 1.2 standard.
 The goal is to ensure that the implementation aligns with the standard, verifying its correctness.
@@
 (2) If the sender's account does not have permission to withdraw the specified \lstinline/value/ amount, the call will fail with the \lstinline/NotEnoughAllowance/ error.
-To verify these requirements, we utilize the failwith condition feature of our tool and examine the returned results, some of which are outlined in Listing~\ref{lst:transfer-udstz-contract}.
+To verify these requirements, we utilize the failwith condition feature of our tool and examine the returned results, one of which is outlined in Listing~\ref{lst:transfer-udstz-contract}.
 The fail condition results confirm these stipulations.
-\begin{lstlisting}[float,captionpos=b,caption={The not enough balance fail condition for the \lstinline/transfer/ entrypoint},label={lst:transfer-udstz-contract},numbers=left]
+\begin{lstlisting}[float,captionpos=b,caption={The \lstinline/NotEnoughBalance/ fail condition for the \lstinline/transfer/ entrypoint},label={lst:transfer-udstz-contract},numbers=left]
 not (paused = true) 
@@
 Therefore, the contract call must fail if both the parameter \lstinline/value/ and the current allowance of \lstinline/spender/ are non-zero.
-We verify this critical property by generating fail conditions to check whenever such a non-zero value update results in a fail condition as Listing \ref{lst:approve-udstz-contract}.
-\begin{lstlisting}[float=tp,captionpos=b,caption={The non-zero value fail condition for the \lstinline/approve/ entrypoint},label={lst:approve-udstz-contract},numbers=left]
+We verify this critical property by generating fail conditions to check whenever such a non-zero value update results in a fail condition as Listing \ref{lst:approve-udstz-contract-z}.
+\begin{lstlisting}[float=tp,captionpos=b,caption={The non-zero value fail condition for the \lstinline/approve/ entrypoint},label={lst:approve-udstz-contract-z},numbers=left]
 not (paused = true) 
@@
 This can be divided into two sub-properties: (1) if the parameter \lstinline/value/ is zero, then the corresponding allowance value of the \lstinline/spender/ from the owner (which is \SENDER\ in this call) should be zero, and (2) if \lstinline/value/ is non-zero and the allowance of the \lstinline/spender/ is zero, then the \lstinline/value/ should be recorded in the storage after the call.
-We specify these properties using pre- and post-conditions, as illustrated in Listing~\ref{lst:specification-approve-1} for the first property.
+We specify these properties using pre- and post-conditions, as illustrated in Listing~\ref{lst:specification-approve-p1} for the first property.
 
@@
 We specified and verified all the properties mentioned above and others. The results confirm that these properties are guaranteed, ensuring the correctness of the smart contract code.
-\begin{lstlisting}[float=tp,captionpos=b,caption={Specification of the \lstinline/approve/ entrypoint (Property 1)},label={lst:specification-approve-1},numbers=left]
+\begin{lstlisting}[float=tp,captionpos=b,caption={Specification of the \lstinline/approve/ entrypoint (Property 1)},label={lst:specification-approve-p1},numbers=left]
 entrpoint %approve
@@
 The \lstinline/getXtzUsdPrice/ entrypoint is permissible only when the oracle is in the \lstinline/IDLE/ state; invoking this entrypoint transitions the oracle to the \lstinline/WAITING_FOR_HARBINGER/ state.
-Conversely, the \lstinline/getXtzUsdPrice_callback/ entrypoint is allowable solely when the oracle is in the \lstinline/WAITING_FOR_HARBINGER/ state; invoking this entrypoint results in the oracle transitioning back to the \lstinline/IDLE/ state.
+Conversely, the\\ \lstinline/getXtzUsdPrice_callback/ entrypoint is allowable solely when the oracle is in the \lstinline/WAITING_FOR_HARBINGER/ state; invoking this entrypoint results in the oracle transitioning back to the \lstinline/IDLE/ state.
 The value of \lstinline/client/ is always set to \lstinline/none/ in the \lstinline/IDLE/ state and to \lstinline/some/ in the other state.
-We verify this property by examining the fail conditions of these two entrypoints and verifying the entrypoint relation between \lstinline/getXtzUsdPrice/ and \lstinline/getXtzUsdPrice_callback/.
+We verify this property by examining the fail conditions of these two entrypoints and verifying the entrypoint relations between \lstinline/getXtzUsdPrice/ and \lstinline/getXtzUsdPrice_callback/.
 
@@
 \\ If \lstinline/getXtzUsdPrice_callback/ is successful, there must be a transaction transferring the data to the client at the \lstinline/client/.
-These properties are checked by using pre- and post-conditions.
+These properties are checked by using pre and postconditions.
 Futhermore, the critical access control property is that the entrypoints \lstinline/setGovernorContract/ and \lstinline/setMaxDelaySec/ must only be invocable by the governor.
@@
 
-We then add the predicate \lstinline/post_maxDelay <= 1800/ in the post condition of the entrypoint \lstinline/setMaxDataDelaySec/ as shown in Listing \ref{lst:setMaxDataDelaySec}, but then the pre and post condition test fails.
+We then add the predicate \lstinline/post_maxDelay <= 1800/ in the post condition of the entrypoint \lstinline/setMaxDataDelaySec/ as shown in Listing \ref{lst:setMaxDataDelaySec1}, but then the pre and post condition test fails.
 This means there is no constraint that the data is less than 30 minutes.
@@
 
-\begin{lstlisting}[float=tp,captionpos=b,caption={The specification of the setMaxDataDelaySec entrypoint},label={lst:setMaxDataDelaySec},numbers=left]
+\begin{lstlisting}[float=tp,captionpos=b,caption={The specification of the \lstinline/setMaxDataDelaySec/ entrypoint},label={lst:setMaxDataDelaySec1},numbers=left]
 entrypoint %setMaxDataDelaySec
@@
  pre-condition := Sender = governor            
- post-condition := post_maxDelay = delay 
- && post_harbinger = harbinger && post_maxDelay <= 1800
+ post-condition := post_harbinger = harbinger 
+ && post_governor = gover
+ && post_maxDelay = delay && post_maxDelay <= 1800
 \end{lstlisting}
 
-The complete specifications and experimental results for the examples and case studies can be found in the appendix~\ref{sec:concl-sect-append} or accessed online at \cite{}.
+The complete specifications and experimental results for the examples and case studies can be found in the appendix~\ref{sec:appendix} or accessed online at \cite{scv}.
 \section{Symbolic Execution Model}
@@
 \label{sec:system-model}
-Our symbolic model of a program state consists of a stack where each element is a symbolic value, represented as a pair comprising a Michelson term and its type: \STACK\ = (\TermOne, \TYF) \STACKCONCAT\ (\TermTwo, \TYS) \STACKCONCAT\ \DOT\ \STACKCONCAT\ \EMPTYSTACK.
+Our symbolic model of a program state consists of a stack where each element is a symbolic value, represented as a pair comprising a Michelson term and its type.
+Thus, we write a stack as \STACK\ = (\TermOne, \TYF) \STACKCONCAT\ (\TermTwo, \TYS) \STACKCONCAT\ \DOT\ \STACKCONCAT\ \EMPTYSTACK.
 Here, \ensuremath{[\ ]} represents the empty stack, and \ensuremath{hd :: tl} denotes a stack with \ensuremath{hd} as the top element and \ensuremath{tl} as the remaining stack.
@@
 
-The semantics of the symbolic rules for the instructions adhere to the formal definitions of the Michelson language as outlined in \cite{} and \cite{}.These rules are classified based on how we handle them in our model.
+The semantics of the symbolic rules for the instructions adhere to the formal definitions of the Michelson language as outlined in \cite{michelson,michelson1}.
+In our model, these instructions are classified based on how we handle them into one-step, multi-step, blockchain, cryptographic, branch, and loop instructions.
+%This categorization reflects how these instructions are handled within our specific model.
 
-\paragraph{One-step instructions}
+%\paragraph{One-step instructions}
 One-step instructions directly modify the system state without branching, have a localized effect, and are modeled with a single rule.
-\paragraph{Multi-step instructions}
+
+%\paragraph{Multi-step instructions}
 Multi-step instructions involve the execution of a sub-sequence of instructions before returning to the main execution.
@@
 \end{mathpar}
-\paragraph{Blockchain instructions}
+%\paragraph{Blockchain instructions}
+
 Blockchain instructions, such as the \AMOUNT\
@@
 As these values are constant during the execution of a contract, we model them as fixed variable.
-\paragraph{Branch instructions}
-The \IF\ \{\INSTRUCTIONONE\} \{\INSTRUCTIONTWO\} instruction expects
-and consumes a boolean value at the top of the stack. If the boolean
+
+%\paragraph{Branch instructions}
+Branch instructions, such as \IF\{\INSTRUCTIONONE\}\{\INSTRUCTIONTWO\} and \IF-LEFT\{\INSTRUCTIONONE\}\{\INSTRUCTIONTWO\} consume a value at the top of the stack. If the branch condition
 is True, it executes \INSTRUCTIONONE; otherwise, it executes
 \INSTRUCTIONTWO. 
-Other branch instructions, such as IF-LEFT and IF-NONE are handled in the similar way.
+%Other branch instructions, such as IF-LEFT and IF-NONE are handled in the similar way.
 
@@
 \end{mathpar}
-\paragraph{Loop instructions}
+%\paragraph{Loop instructions}
+
 The loop instructions, including
@@
 
-Let us first take look at the terminate loops. The following rule handles the  \ITER\ loop for  the non-empty list \footnote{\ITER\ can also iterate over sets and maps, but the
-  details are very similar to the list case and hence omitted.} while the \ITER\ loop terminates when the list is empty. 
+Let us first take look at the terminate loops.
+The following rule handles the  \ITER\ loop for  the non-empty list\footnote{\ITER\ can also iterate over sets and maps, but the details are very similar to the list case and hence omitted.}, while the \ITER\ loop terminates when the list is empty.
 \begin{mathpar}
@@
 How do we deal with \ITER\ if the list is a symbolic value?
-One solution could involve running the loop for a number of times to obtain the symbolic value. However, we can defer that decision by exploiting features of Z3. 
+One solution could involve running the loop a certain number of times to obtain the symbolic value.
+However, we can defer that decision by abstracting the result.
 In fact, the loop body \INSTRUCTIONONE\ can be considered a function applied to a stack
@@
 \StackTwoOne\ \STACKCONCAT\ ... \STACKCONCAT\ \StackNOne = \F\ $x_1$
-\STACK, and so on.
+\STACKZERO, and so on.
 In conclude, we can represent the result stack as the result of a fold function that applies  \F\ to the list.
@@
 \begin{mathpar}
-\STACK'\ =  \FOLD\ \F\ \STACK\ \LIST
+\STACK'\ =  \FOLD\ \F\ \STACKZERO\ \LIST
 \end{mathpar}
 
-In similar stragtery, symbolically the result of the \MAP\
-\{\INSTRUCTION\} to the list \LIST\ is the result of a map function
-that applies the function \F\ that represent of the sequence of
-instructions \I\ to the list. 
+In a similar strategy, symbolically, the result of the \MAP\ {\INSTRUCTIONONE} instruction applied to the list \LIST\ is the result of a map function that applies the function \F\ (representing the sequence of instructions \INSTRUCTIONONE) to the list.
 \begin{mathpar}
@@
 
-Finally, we consider a loop instruction that may not terminate, such as \LOOP\ and and \LOOPLEFT. 
+Finally, we consider a loop instruction that may not terminate, such as \LOOP\ and \LOOPLEFT. 
 When the input to the symbolic execution consists of concrete values, an unbounded loop causes the interpreter to iterate for a significant number of times until it halts with an exception indicating an unfinished loop.
-This mirrors the behavior observed in the actual execution of Tezos contracts, where the loop continues until it runs out of gas, terminating the computation with an out-of-gas error.
+This mirrors the behavior observed in the actual execution of smart contracts, where the loop continues until it runs out of gas, terminating the computation with an out-of-gas error.
 For a symbolic value, the stack type is determined before the loop is executed.
 We abstract the result of the loop  and the loop condition as the abstract function results.
-This abstraction helps detect whether the loop is unbounded, such as when the condition result of the function is always true.
+This abstraction helps detect whether the loop is unbounded, such as when the abstract function of the loop condition always results  true.
 
-In separate work (which is currently in submission), we have designed a dynamic logic tailored to Michelson as a formal foundation for the implementation of SCV.
-We have a soundness proof of this logic formalized in the Agda proof assistant, which is omitted here due to the pages limit.
+In separate work (currently under submission), we have designed a dynamic logic tailored to Michelson as a formal foundation for the implementation of SCV.
+We have formalized a soundness proof of this logic in the Agda proof assistant, which is omitted here due to the page limitation.
 \section{Related Work}
@@
 
-Close to our approach are HELMHOLTZ \cite{helmholtz} and Mi-Cho-Coq ~\cite{micho} as discussed in Section \ref{}.
-In HELMHOLTZ, properties annotated inside the code by the developer.
-Here, we provide a separate specification language that users don't need to modify within the code.
-Similar to our tool, iContract \cite{icontract} based on synbolic execution utilizes pre and post conditions to specify user properties, but targets the Solidity language.
+Close to our approach are HELMHOLTZ \cite{helmholtz} and Mi-Cho-Coq \cite{micho}, as discussed in Section \ref{sec:introduction}.
+In HELMHOLTZ, properties are annotated inside the code by the developer, which requires modifying the code.
+In contrast, we provide a separate specification language, so users do not need to modify the code.
+Similar to our tool, iContract \cite{icontract} utilizes symbolic execution and pre and postconditions to specify user properties, but it targets the Solidity language.
 
@@
 \label{sec:concl-sect-append}
-Symbolic execution is well known to suffer from challenges related to
-state explosion, particularly when applied to large
-systems.
-Tackling this problem in the implemetation of the tool, our tool conducts two real case studies of running blockchain contracts, implementing significant subjects on the blockchain such as token standards and oracles.
+Symbolic execution is well known to suffer from challenges related to state explosion, particularly when applied to large systems.
+To address this problem, our tool mitigates state explosion and has been applied to two real case studies of running blockchain contracts, focusing on significant subjects such as token standards and oracles.
 

### 2024-06-20 reports/2024-06-30/report.tex
draft report

--- 2024-01-03 reports/2023-12-31/report.tex
@@
 
-\section{Progress Report July 2023 - December 2023}
+\section{Progress Report January 2024 - June 2024}
 \label{sec:executive-summary}
@@
 
-Currently, the project is slightly delayed but making good progress. Ms.\ Doan
-returned from  maternal leave in October 2023.
+Currently, the project is still behind schedule, but making good
+progress after Ms.\ Doan's return from  maternal leave in October 2023.
 
@@
 \item Activity: Development of a dynamic logic as a formal foundation for symbolic interpretation of Michelson. \\
-  $\Rightarrow$ This activity progressed significantly.  The master's
-  thesis has been completed in November and is currently under review (by the examiner).
+  $\Rightarrow$  The master's thesis has been completed in November and grading is complete.
 \item Deliverable: Formalization (in Agda) of a dynamic logic for a core fragment of Michelson with soundness proof. \\
   $\Rightarrow$ This deliverable is available  at
-  \url{https://github.com/Barnaboss/thesis-michelsonDL}. It will be
-  released after the thesis review period.
+  \url{https://github.com/Tezos-Project-Uni-Freiburg/michelson-dynamic-logic}. It will be
+  released as an artifact at the time the paper is published.
 \item Deliverable: Paper about this formalization (writeup starting
   July 2023). \\
-  $\Rightarrow$ The paper will be based on the master's thesis, so the final writing
-  starts after completion of the thesis review. The goal is to submit to a
-  conference during spring.
+  $\Rightarrow$ The paper is based on the master's thesis. The Agda code
+  from the thesis as well as the text had to undergo significant
+  revision. The paper was submitted to ECOOP on April 18 and has been
+  conditionally accepted. The revision is due July 7.
 \end{itemize}
@@
 \item Deliverable: Doan completed two case studies with example contracts.
-\item Deliverable: Paper or tutorial on this tool (writeup started,
-  submission planned for a deadline in spring) \\
-  $\Rightarrow$ A draft is available here \url{https://github.com/proglang/tezos-project/tree/master/symbolic-execution/paper}
+\item Deliverable: Paper or tutorial on this tool (writeup finished,
+  first submission January 18, second submission May 31) \\
+  $\Rightarrow$ Current submission is available here \url{https://github.com/proglang/tezos-project/tree/master/symbolic-execution/paper}
 \end{itemize}

### 2024-06-26 papers/assertion-contract/assertion_contract_app/paper.tex
Some revisions are made

@@
 \usepackage{titling}
+
+\usepackage{tikz}
+\usepackage{amsmath}
+\usetikzlibrary{shapes.geometric, arrows}
+
+\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
+\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=orange!30]
+\tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30]
+\tikzstyle{arrow} = [thick,->,>=stealth]
 
@@
 \begin{abstract}
-In some situations on the blockchain, verifying certain properties of a parameter requires significant gas costs or may even become infeasible due to the gas limits.
-This study proposed a distributed verification assertion protocol.
-The core concept involves distributing the negation form of the assertion to validators instead of verifying it on-chain.
-Validators’ off-chain attempts to find a solution to the negation form and discover a counterexample.
-When a counterexample is found, it can be submitted to the chain.
-In addition, we propose a proof-of-work-based incentive mechanism to encourage validators to participate in the distributed verification process.
+In certain blockchain scenarios, verifying properties of a parameter requires significant gas costs or may even be infeasible due to gas limits.
+This study proposes a distributed assertion verification protocol to address this issue.
+The core idea is to distribute the negation of the assertion to validators, who then attempt to find a counterexample off-chain.
+If a counterexample is found, it can be submitted on-chain.
+Additionally, a proof-of-work-based incentive mechanism is proposed to encourage validators to participate in the distributed verification process.
+
 To operationalize these ideas, we suggest a practical model that addresses security concerns.
-Furthermore, we implemented a prototype of the proposed protocol and conducted a cost analysis to demonstrate the advantages of our method in terms of cryptocurrency, making it practically useful.
+We also implemented a prototype of the proposed protocol and conducted a cost analysis to demonstrate the advantages of our method in terms of cryptocurrency, proving its practical utility
  \keywords{}
@@
 \label{sec:approach}
-We propose a novel method to verifying assertions for smart contracts on the blockchain.
-Our approach involves distributing the assertion verification process and moving it off chain.
-Only the verification results are submitted to the blockchain.
-Throughout this distribution, each validator endeavors to identify a counterexample to the assertion.
-Consequently, rather than checking the entire assertion, it only requires examining specific points on the chain.
-We propose a proof-of-work-based incentivization method for validators who discover a counterexample and for a portion of the computational effort, thereby incentivizing participation in the distributed verification process.
+We propose a novel method for verifying parameter assertions in smart contracts on the blockchain.
+Our approach distributes the assertion verification process and moves it off-chain, with only the verification results being submitted to the blockchain.
+
+In this distributed process, each validator attempts to identify a counterexample to the assertion.
+Upon finding one, the validator submits the counterexample on-chain.
+Consequently, instead of verifying the entire assertion, the on-chain contract only needs to check specific points.
+
+To implement this idea, we propose a proof-of-work-based incentivization method in which validators are rewarded for discovering counterexamples, and some are rewarded for their computational efforts, thus encouraging participation in the distributed verification process.
 
@@
 
-To verify an assertion, it requires iterating over the domain $A$ within the contract.
+To verify these assertions, it requires iterating over the domain $A$ within the contract.
 When the domain $A$ is large or the predicate $P$ is complex to evaluate, it incurs a significant amount of gas to perform the verification process on-chain.
 Given the current high gas prices, this could result in substantial costs or even impossible due to gas limits.
+
 Our approach aims to alleviate this by distributing the negation of the assertion to validators.
 Each validator endeavors to find a counterexample of the assertion using this negation.
+Specifically, each validator attempts to find a counterexample by identifying $a \in A$ such that the negation formula is satisfied $\neg P_{a}$.
+When a counterexample is found, the validator submits it, which is then re-verified on-chain.
 
-Specifically, each validator attempts to find a counterexample by identifying $a \in A$ such that the negation formula is satisfied.
-When a counterexample is found, the validator submits it, which is then verified on the chain.
-The amount of gas required for the computation to check the counterexample on-chain will likely be significantly less than verifying the assertion directly on the chain.
+Since only one specific point is checked on-chain, the amount of gas required for the computation to check the counterexample is likely to be significantly less than verifying the entire assertion directly on-chain.
+
+If any of the validators identify a violation of an assertion, the final call to the actual work function is aborted.
+However, if certain requirements are met, the work function is invoked with the parameter.
 
@@
 Each validator attempts to find the number $k$ such that the negation is true for such $k$, then the validator has found a counterexample for the sortedness of the array.
-
-If any of the validators identify a violation of an assertion, the final call to the actual work function is aborted.
-However, if certain requirements are met, the work function is invoked with the parameter.
 \subsection{Proof-of-work-based incentivization method}
@@
 If no counterexample emerges, the verification accuracy depends on the number of wisepoints generated to negate the assertion, with more validators increasing the certainty.
+
 Encouraging validators to engage in the verification process even without discovering a counterexample is crucial.
@@
 
+\subsubsection{Outlines}
 We propose a proof-of-work-based method to incentivize participants in the distributed verification process. The proposed approach is outlined as follows:
@@
 \end{itemize}
+\subsubsection{Computation Proof}
 The next step is to devise a computation proof to incentivize computational effort by utilizing the proof of work concept.
-Initially, we establish a target hash $t$ that sets the required difficulty level to earn the reward.
+We use a target hash $t$ that sets the required difficulty level to earn the reward.
 The objective of the validator is to generate a computation that produces a hash smaller than or equal to the target hash $t$.
-Seed $s$ was introduced in each verification process.
+
+The key problem is how to reproduce the computation proof off-chain to on-chain.
+To this end, a seed $s$ is introduced in each verification process.
 Let $n$ denote the size of domain $A$.
 Each number $i$ in the range [1, $n$] corresponds to an element in $A$.
-The seed $s$ is a random number and then reduces modulo $n$ to obtain $i$, which is  associated with an element $a$ in $A$:
-\begin{gather}\label{}
-i = s \mod n
-\end{gather}
-Consequently, each seed $s$ is linked with an element $a$ in the domain $A$, followed by the evaluation of the negation of the assertion $\neg P_{a}$.
+The seed $s$ then reduces modulo $n$ to obtain $i$, which is  associated with an element $a$ in $A$.
+
+The sequence of operations can be described by the following steps:
+\begin{enumerate}
+\item Generate a random seed $s$: 
+\begin{align}
+s \in \mathbb{N} 
+\end{align}
+where $s$ is a random natural number.
+\item Calculate $n$ as the size of the domain $A$: 
+\begin{align}
+n = |A|
+\end{align}
+where $\mid A \mid$ denotes the number of elements in the domain $A$.
+\item Determine $i \in [1, n]$ using the modulo operation:
+\begin{align}
+i = (s \mod n) + 1
+\end{align}
+\item Find the corresponding element $a$ in $A$:
+\begin{align}
+a=A[i]
+\end{align}
+where $A[i]$ denotes the $i$-th element in $A$.
+\item Calculate the hash \( t_s \) corresponding to the seed \( s \):
+\begin{align}
+t_s = \text{hash}(s, \text{eval}(\neg P_{a}))
+\end{align}
+where \(\text{hash}\) is the hash function and \(\text{eval}\) is the function that returns the significant components of the evaluation of the negation \(\neg P_{a}\).
+
+For example, it returns \(a[i]\) and \(a[i + 1]\) in the evaluation of the negation predicate \(a[i] < a[i+1]\) in the sorted array example.
+\end{enumerate}
+
+%Consequently, each seed $s$ is linked with an element $a$ in the domain $A$, followed by the evaluation of the negation of the assertion $\neg P_{a}$.
+
 After conducting the negation check, either a counterexample is identified, or a hash is computed based on the seed $s$ along with the evaluation of the condition $\neg P_{a}$.
@@
 
-During the distributed process, each validator consistently generates a seed $s$ and conducts the negation check until the outcome indicates either a counterexample or a reward computation.
+During the distributed process, each validator may generate a seed $s$ and conducts the negation check until the outcome indicates either a counterexample or a reward computation.
 Upon achieving either of these outcomes, the validator is able to submit it on-chain to claim their reward.
@@
 \section{Practical model}
-\subsection{Overview architect}
+\subsection{Security risks}
 Distributed verification of assertions is indeed an intriguing concept, yet it faces the following security risks when proposing an incentive method:
 
-\begin{itemize}
+\begin{enumerate}
 \item Front-running attacks: The system is vulnerable to front-running attacks, where an attacker closely monitors the mempool to intercept a seed representing a counterexample or a computation proof, subsequently stealing the reward.
@@
 \item Reward manipulation: A validator may attempt to manipulate the reward system by resubmitting counterexamples or computation proofs multiple times to multiply their rewards.
-\end{itemize}
-
+\end{enumerate}
+\subsection{Overview architect}
 This section presents a practical model that unifies theoretical principles and addresses the previously mentioned security concerns.
@@
 \begin{itemize}
-\item Owner: responsible for deploying and overseeing both on-chain and off-chain contracts.
-\item Callers: engage with on-chain contracts by initiating assertions and interacting with the system.
-\item Validators: tasked with validating parameters and ensuring the integrity of the verification process.
+\item[•] Owner: responsible for deploying and overseeing both on-chain and off-chain contracts.
+\item[•] Callers: engage with on-chain contracts by initiating assertions and interacting with the system.
+\item[•] Validators: tasked with validating parameters and ensuring the integrity of the verification process.
 \end{itemize}
@@
 
-\subsubsection{On-chain assertion contract}
+While a random number alone is sufficient to indicate the associated element $a$ in the domain $A$, to prevent the front-running attack and the caller exploitation attack, we enhance the randomness of the seed by combining a random number with the validator's address and the timestamps indicating when the parameter is submitted on the chain to calculate the seed.
+In deeds, the validator's address and timestamps are converted to numerical values and use these numbers in combination with a random number to compute the seed.
+This combination adds an extra level of security.
+\begin{enumerate}
+\item 
+Seed calculation: The seed is enhanced by combining a random number with the validator's address and timestamps.
+Let's denote the random number by $r$, the validator's address by $addr$, and the timestamp by $t$.
+\begin{equation}
+r \in \mathbb{N}, \quad \text{addr} \in \text{Addresses}, \quad t \in \text{Timestamps}
+\end{equation}
+\item Conversion of address and timestamp: The address and timestamp are converted to numerical values using appropriate functions.
+\begin{equation}
+\text{addr\_num} = \text{init256}(\text{addr}) \\
+ \quad t_{\text{num}} = \text{convert}(t)
+\end{equation}
+\item Combination to compute the seed: The seed $s$ is computed by combining these numerical values.
+\begin{equation}
+s = \text{hash}(r, \text{addr\_num}, t_{\text{num}})
+\end{equation}
+where \(\text{hash}\) is a hash function that takes the three numerical values and returns a numerical value \( s \).
+\end{enumerate}
+
+\textbf{Security Features}:
+\begin{itemize}
+    \item Front-running attacks: Other validators cannot use the random number $r$ alone because the combination with their address and timestamp will not produce the same seed $s$.
+    \item Caller exploitation: The timestamp constraints prevent the caller from running the check before submitting the parameter.
+\end{itemize}
+%In this system, even if other validators obtain a random number, they are unable to submit it successfully, as their combination with their address will not yield the correct seed that corresponds to a specific element in the domain.
+Additionally, a caller cannot run the check before submitting the parameter owing to the timestamp constraints.
+As a result, any attempt to submit manipulated or before-run seeds will fail to produce either a counterexample or reward computation.
+The address conversion can be achieved using functions such as \lstinline|init256| in Solidity, which transform an Ethereum address into a numerical value.
+
+An assertion in smart contract languages, such as Solidity and Michelson, is essentially predicate logic expressed as a Boolean formula computed from relational operators, logical operators, and expressions.
+\begin{align}
+\text{Relational operators: } & =, \neq, >, <, \geq, \leq \\
+\text{Logical operators: } & \neg, \land, \lor
+\end{align}
+Let $\pi_{P_{a}}$ represent the set of expressions involved in the computation of the predicate $P_a$.
+\begin{equation}
+\pi_{P_{a}} = \{ e_1, e_2, \ldots \}
+\end{equation}
+where $e_i$ are the expressions involved in the computation of the predicate $P_a$.
+
+ The expressions $\pi_{P_a}$ can be used to compute the hash, which involves the validator executing the condition check to find a reward computation.
+\begin{equation}
+t_s = \text{hash}(s, \pi_{P_{a}})
+\end{equation}
+where:
+\begin{itemize}
+    \item $s$ is the seed.
+    \item $\pi_{P_{a}}$ is the set of expressions used in the computation of the predicate $P_a$.
+    \item \text{hash} is the hash function that computes the hash based on the seed and the set of expressions $\pi_{P_{a}}$.
+\end{itemize}
+\textbf{On-chain assertion contract}:
 While additional functions may exist, the assertion contract must encompass the following two essential functions:
@@
 \end{itemize}
-
-While a random number alone is sufficient to indicate the associated element $a$ in the domain $A$, to prevent the front-running attack and the caller exploitation attack, we enhance the randomness of the seed by combining a random number with the validator's address and the timestamps indicating when the parameter is submitted on the chain to calculate the seed.
-This combination adds an extra level of security.
-For instance, we can convert the validator's address and timestamps to a numerical value and use this number in combination with a random number to compute the seed.
-This conversion can be achieved using functions such as \lstinline|init256| in Solidity, which transform an Ethereum address into a numerical value.
-In this system, even if other validators obtain a random number, they are unable to submit it successfully, as their combination with their address will not yield the correct seed that corresponds to a specific element in the domain.
-Additionally, a caller cannot run the check before submitting the parameter owing to the timestamp constraints.
-As a result, any attempt to submit manipulated or before-run seeds will fail to produce either a counterexample or reward computation.
-
-An assertion in smart contract languages, such as Solidity and Michelson, is essentially predicate logic expressed as a Boolean formula computed from relational operators ($=$, $!=$, $>$, $<$, $>=$, $<=$), logical operators ($!$, $\&\&$, $\|$), and expressions.
-To represent the set of expressions involved in the computation of the predicate $P_a$, let $\pi_{P_{a}}$ = {$e_1$, $e_2$, \dots }.
-The expressions $\pi_{P_a}$ can be used to compute the hash, which involves the validator executing the condition check to find a reward computation.
-
-\subsubsection{Storage}
-When a parameter is submitted for verification, the following information is stored:
+\textbf{Off-chain assertion contract}:
+Since the off-chain contract runs off-chain, it can be implemented according to the validator's preferences.
+However, the crucial point is that the off-chain contract must use the exact same \lstinline|claim_reward| function when attempting to find a counterexample or a computation proof.
+Additionally, it should support a function that assists the validator in finding a seed to earn a reward.
+\\ \textbf{Storage}:
+When a parameter is submitted for verification, the following information should be stored:
 \begin{itemize}
-\item Parameter: This includes the parameter itself.
-In cases where storing the parameter on-chain is impractical because of its size, it is recommended to store only its hash.
+\item Parameter: this includes the parameter itself.
+In cases where storing the parameter on-chain is impractical because of its size, it could be possible to store only its hash.
 Despite this, the hash remains sufficient for validation.
@@
 It serves purposes such as tracking submissions, preventing callers from resubmitting parameters, or preventing callers from claiming rewards for their own submitted parameters.
-\item Timestamp: This indicates the approximate time when the parameter was submitted. This information is used to prevent caller exploitation security risks.
-\item Verification Status Records: These records monitor the progress of the parameter's verification.
-They include details such as whether a counterexample or reward computation is found.
-Additionally, they contain information regarding the addresses of the validators and random numbers involved in the verification process.
-In some applications, multiple computational proofs may be allowed, leading to a list of these records.
-This information is crucial for determining when a work function can be invoked for that parameter, or when it should be discarded.
-The validators' addresses and random numbers can also be used to prevent reward-manipulation attacks.
-Indeed, because a validator with the same random number cannot be resubmitted, the random number serves as a unique identifier in the verification process.
-This uniqueness prevents validators from resubmitting the same computation proof multiple times to manipulate the rewards or disrupt the integrity of the verification process.
+\item Timestamp: this indicates the approximate time when the parameter was submitted. This information is used to prevent caller exploitation security risks as explained above.
+\item Verification Status Records: the records are to monitor the progress of the parameter's verification.
 \end{itemize}
+
+The verification status records a counterexample and reward computations found. For that, it should include the following details:
+\begin{itemize}
+    \item The addresses of the validators.
+    \item The random number $r$ used in the verification process.
+\end{itemize}
+
+In some applications, multiple computational proofs may be allowed. This record is crucial for determining when a work function can be invoked for a given parameter or when it should be discarded.
+
 In certain applications, one may delete the records after processing is completed for the parameter, especially if a large number of parameters are submitted to manage storage efficiently.
 
+\textbf{Security Features}:
+The validators' addresses and the random number $r$ play a vital role in preventing reward-manipulation attacks.
+A validator cannot resubmit with the same $r$.
+Therefore, this uniqueness prevents validators from submitting the same computation proof or a counterexample multiple times.
 \subsection{Deploying and managing on/off-chain contracts.}
@@
 The owner deploys the assertion contract on the blockchain while storing the validator contract off the blockchain, thereby ensuring its accessibility to the validators.
+
 There are two approaches to making these contracts available to validators.
@@
 When submit the parameter, the caller may need to send along an amount of deposit stake.
-This deposit serves as a deterrent, as in the event of an invalid parameter, the deposit may be forfeited to prevent callers from submitting invalid parameters solving the DoS attack security risk.
 Furthermore, the caller may wish to broadcast their parameter to all validators via a messaging system when submitting it online.
 
+\textbf{Security Features}: 
+The deposit serves as a deterrent, as in the event of an invalid parameter, the deposit may be forfeited to prevent callers from submitting invalid parameters solving the DoS attack security risk. 
 %The work contact can only be invoked by the on-chain validation contract after the parameter has been validated if no counterexample is found.
@@
 To assess the validity of a parameter, each validator independently executes the off-chain validation contract.
-A validator may attempt to run the off-chain validation contract multiple times with different random seeds in order to find either a counterexample or a computational proof.
+A validator may attempt to run the off-chain validation contract multiple times with different random numbers in order to find either a counterexample or a computational proof.
 It's possible that several attempts may be made before the validator receives an award.
-In cases where no award is obtained, the validator can rerun the code with a different seed.
 A function called find-seed could be implemented, which in turn calls the claim-reward function to locate a seed.
@@
 \subsection{Claiming the reward} 
-If validators discover a counterexample or an award computation, they provide the seed, a combination of a random number, the parameter's timestamp and the validator's address, along with the parameter to the on-chain assertion contract.
-The on-chain assertion contract then executes the same claim-reward function, which should yield the same result as the counterexample or award compuation found by the validator.
+If validators discover a counterexample or an award computation, they provide the seed, a combination of a random number, the parameter's timestamp and the validator's address to the on-chain assertion contract.
+The on-chain assertion contract then executes the same claim-reward function, which should yield the same result.
 If the result is correct, there is an award to the validator and the record of the parameter in the storage is updated accordingly.
@@
 The invocation of the work function or contract is carried out by the on-chain validation contract or a caller.
-This call is subject to specific requirements being met, ensuring that the task is executed only when the verification process has been successfully completed and the parameter is deemed valid.
+This call is subject to specific requirements being met, ensuring that the task is executed only when the verification process has been successfully completed and the parameter is deemed valid, such as a certain amount of time having passed, no counterexample being found, and receiving enough computation proofs.
+If all conditions are met, the actual work is executed, and the record of the parameter may be deleted from memory to free up storage.
+
 By enforcing strict conditions for the execution of the work function or contract based on the outcome of the verification process, the integrity and reliability of the system can be maintained.
 
-The on-chain validation contract calls the work contract with the current parameter and its related information, which is then matched against the stored information of the corresponding parameter.
+%The on-chain validation contract calls the work contract with the current parameter and its related information, which is then matched against the stored information of the corresponding parameter.
 They must match and satisfy additional conditions, such as a certain amount of time having passed, no counterexample being found, and receiving enough computation proofs.
@@
 
-\section{Domain Specification Language for Assertion}
-\section{Converter - Generating an Assertion Contracts} 
+%\section{Domain Specification Language for Assertion}
+%\section{Converter - Generating an Assertion Contracts} 
 \section{Prototype Implementations}
+\note{TODO}
 \subsection{Sorted array}

### 2024-06-27 papers/assertion-contract/assertion_contract_app/paper.tex
Some formulas are added

@@
 \subsubsection{Computation Proof}
-The next step is to devise a computation proof to incentivize computational effort by utilizing the proof of work concept.
-We use a target hash $t$ that sets the required difficulty level to earn the reward.
+The next step is to devise a computation proof to incentivize computational effort by utilizing the proof-of-work concept.
+We introduce a target hash $t$ that sets the required difficulty level to earn the reward.
 The objective of the validator is to generate a computation that produces a hash smaller than or equal to the target hash $t$.
 
-The key problem is how to reproduce the computation proof off-chain to on-chain.
-To this end, a seed $s$ is introduced in each verification process.
+A key challenge is reproducing the computation proof off-chain to on-chain.
+To address this, we introduce a seed $s$ in each verification process.
 Let $n$ denote the size of domain $A$.
-Each number $i$ in the range [1, $n$] corresponds to an element in $A$.
-The seed $s$ then reduces modulo $n$ to obtain $i$, which is  associated with an element $a$ in $A$.
+Each number $i$ in the range $[1, n]$ corresponds to an element in $A$.
+The seed $s$ is reduced modulo $n$ to obtain $i$, which is associated with an element $a$ in $A$.
+\paragraph{Estimate the number of seeds:} We first estimate the number of seeds needed to find a counterexample with a given expected probability.
 
-The sequence of operations can be described by the following steps:
+Let's assume the unsatisfied element is only at the first element $a_0$ in $A$, the size of the domain is $n$, and the number of seeds is $m$.
+Each seed independently has a probability of $1/n$ to detect the problem and a probability of $\frac{n-1}{n}$ not to detect the problem.
+Hence, if we assume that each seed associated with an element $a$ in $A$ is chosen independently from a uniform distribution, the probability that no validator checks the element $a_0$ converges to $0$ as the number of seeds approaches infinity:
+
+\[
+  \lim_{m \to \infty} \frac{(n-1)^m}{n^m} = \lim_{m \to \infty} \left( \frac{n-1}{n} \right)^m = 0
+\]
+
+Depending on the expected probability to detect the problem, the number of seeds to generate can be determined.
+Assume that $p$ is the probability of finding at least one counterexample.
+To calculate the number of seeds $m$ needed to achieve a given expected probability $p$ of finding a counterexample, we can use the complementary probability.
+We have:
+\begin{itemize}
+\item The probability of a single seed failing to find a counterexample is $\frac{n-1}{n}$.
+\item The probability of all $m$ seeds failing to find a counterexample is $\left(\frac{n-1}{n}\right)^m$.
+\item Therefore, the probability of at least one of the $m$ seeds finding a counterexample is:
+\[
+p = 1 - \left(\frac{n-1}{n}\right)^m
+\]
+\end{itemize}
+
+Rearranging to solve for \( m \):
+
+\[
+\left(\frac{n-1}{n}\right)^m = 1 - p
+\]
+
+Taking the natural logarithm on both sides:
+
+\[
+\ln\left(\left(\frac{n-1}{n}\right)^m\right) = \ln(1 - p)
+\]
+
+\[
+m \ln\left(\frac{n-1}{n}\right) = \ln(1 - p)
+\]
+
+Solving for \( m \):
+
+\[
+m = \frac{\ln(1 - p)}{\ln\left(\frac{n-1}{n}\right)}
+\]
+
+%For example, given \( n = 10000 \) and \( p = 0.8 \), the number of seeds \( m \) needed to achieve the desired probability is calculated as follows:
+%\[
+%m = \frac{\ln(1 - 0.8)}{\ln\left(1 - \frac{1}{10000}\right)}
+%\]
+
+%\[
+%m = \frac{\ln(0.2)}{\ln\left(1 - 0.0001\right)}
+%\]
+
+%\[
+%m = \frac{-1.6094}{\ln(0.9999)}
+%\]
+
+%\[
+%m = \frac{-1.6094}{-0.0001}
+%\]
+
+%\[
+%m \approx 16094
+%\]
+
+%Therefore, approximately \( 16094 \) seeds are needed to have an \( 80\% \) chance of finding a counterexample.
+
+\paragraph{Set up the taget hash:}
+The above seed number $m$ can then be used to set up the target hash $t$.
+The target hash $t$ can be calculated based on a desired difficulty level.
+In proof-of-work systems, difficulty is typically adjusted to ensure that the average efforts to find a valid hash.
+The target hash $t$ is often calculated by taking the maximum possible hash value and dividing it by the difficulty level:
+\[
+t = \frac{H_{\text{max}}}{D}
+\]
+
+Where:
+\begin{itemize}
+  \item \( H_{\text{max}} \) is the maximum possible hash value.
+  \item \( D \) is the difficulty level, which can be adjusted based on the expected number of trials.
+\end{itemize}
+
+Given the expected number of seeds to generate, 
+the difficulty level $D$ can be adjusted accordingly.  bTypically, $D$ is set to ensure that a valid hash is found approximately once every $m$ trials.
+
+If we want the probality of finding a valid hash to be $\frac{1}{m}$, then:
+\[
+D=m
+\]
+
+For a 256-bit hash, $H_{\text{max}}$ is $2^{256} - 1 $.  using the maximum hash value and the difficulty level, the target hash $t$ is:
+
+\[
+\frac{2^{256} - 1}{m}
+\]
+
+\paragraph{Find a seed:}
+The sequence of operations to find a seed can be described by the following steps:
 \begin{enumerate}
@@
 where $A[i]$ denotes the $i$-th element in $A$.
+\item Perform the negation check $\neg P_{a}$ to detect a counterexample if any.
+
 \item Calculate the hash \( t_s \) corresponding to the seed \( s \):
@@
 For example, it returns \(a[i]\) and \(a[i + 1]\) in the evaluation of the negation predicate \(a[i] < a[i+1]\) in the sorted array example.
+\item Compare \( t_s \) to the target hash to determin whether it is a reward computation.
 \end{enumerate}
@@
 
-%\section{Domain Specification Language for Assertion}
-%\section{Converter - Generating an Assertion Contracts} 
+\section{Domain Specification Language for Assertion}
+\note{To discuss: if it make sense to design}
+\section{Converter - Generating an Assertion Contracts} 
+\note{To discuss: if it make sense to implement}
 \section{Prototype Implementations}

### 2024-07-19 papers/assertion-contract/assertion_contract_app/paper.tex
Costs Analysis

@@
 \usepackage{titling}
-
+\usepackage{pgfplots}
+\pgfplotsset{compat=1.17}
 \usepackage{tikz}
@@
 Given the expected number of seeds to generate, 
-the difficulty level $D$ can be adjusted accordingly.  bTypically, $D$ is set to ensure that a valid hash is found approximately once every $m$ trials.
+the difficulty level $D$ can be adjusted accordingly. Typically, $D$ is set to ensure that a valid hash is found approximately once every $m$ trials.
 
@@
 
+\section{Cost Analysis}
+This section considers the cost of the distributed verification method and its comparison with on-chain verification method.
+
+\subsection{Transaction Execution Costs}
+Let's first look at the transaction costs in terms of gas.
+To process and execute a transaction on the blockchain, users must pay costs in the form of gas.
+The total gas costs can be broken down into five parts:
+
+\begin{enumerate}
+\item Base cost: Fixed costs associated with initiating a transaction. They include basic operations such as:
+\begin{itemize}
+\item Calculating the transaction hash.
+\item Verifying the signature.
+\item Subtracting the balance from the sender.
+\item Adding the balance to the recipient.
+\end{itemize}
+In Ethereum, for example, a simple transfer of ETH from one address to another costs 21,000 gas.
+\item Data cost: Gas cost associated with the size of the data payload of the transaction when a contract with input data is invoked or a new contract is set up.
+This includes the costs per data byte, with non-zero bytes being more expensive than zero bytes.
+For Ethereum, for example, these data costs are as follows:
+\begin{itemize}
+    \item 68 gas per byte of non-zero data.
+    \item 4 gas per byte of zero data.
+\end{itemize}
+
+\item Computational cost: The gas consumed to perform individual operations specified in the smart contract code.
+This includes all computational tasks required to process a transaction or perform contract functions.
+These include:
+\begin{itemize}
+    \item Arithmetic operations: Basic mathematical operations such as addition, subtraction, multiplication, and division.
+    \item Logical operations: Logical operations such as AND, OR, NOT, etc.
+    \item Control flow operations: Operations that influence the execution flow, such as jumps, conditions, and function calls.
+    \item Cryptographic operations: Hashing functions (e.g., keccak256) and other cryptographic operations.
+    \item Memory operations: Allocation of and access to memory during contract execution.
+\end{itemize}
+
+\item Storage cost: Storage operations are more expensive than computational operations because they involve writing to the blockchain's persistent storage. The costs include:
+\begin{itemize}
+    \item Writing to storage: For example, in Ethereum, it costs 20,000 gas when setting a non-zero value from zero, and 5,000 gas when updating an existing value.
+    \item Reading from storage: On Ethereum, it costs 100 gas per operation.
+\end{itemize}
+
+\item Refund gas: In some cases, certain operations can lead to a gas refund. For example, in Ethereum:
+\begin{itemize}
+    \item Self-destructing contracts: Calling SELFDESTRUCT on a contract returns a portion of the gas.
+    \item SSTORE with zero: Setting a storage value to zero can refund gas if it was previously a non-zero value.
+\end{itemize}
+
+\end{enumerate}
+
+In conclusion, the total gas cost of a transaction (also called the execution cost) includes the base cost, data cost, computational cost, and storage cost.
+\subsection{Comparative Analysis of On-Chain and Offline Methods}
+Let's break down the gas costs to compare on-chain and off-chain verification.
+
+Consider the total gas $G_{on}$ for on-chain verification.
+Let $G_{parameter}$ denote the intrinsic gas, which includes the base gas and the data cost that primarily depend on the size of the parameter $p$.
+The total gas includes the intrinsic gas, the gas for storing the parameter (which is optional, depending on the application), the computation gas (which includes $n$ times the gas to check the parameter $G_{check}$, where $G_{check}$ checks the condition at each point of the parameter and $n$ is the size of the parameter), and the gas to perform the actual computation work $G_{run}$.
+
+For our offline distributed verification method, let's assume that the parameter is valid, and now we consider the cost to verify the parameter and perform the actual work.
+Let $m$ be the number of proofs required to ensure the correctness of the parameter.
+Thus, the offline method costs the gas for submitting the parameter, the gas to store the parameter (or its hash), $m$ times the gas to submit the seed, check the condition of the parameter point associated with the seed, the gas to compute the hash and compare it with the target hash, and of course the gas to run the computation of the actual work.
+
+\subsubsection{On-Chain Verification Method (\( G_{on} \))}
+
+\begin{equation}
+G_{on} = G_{parameter} + [G_{storage}] + n \cdot G_{check} + G_{run}
+\end{equation}
+
+\begin{itemize}
+    \item \( G_{parameter} \): Intrinsic gas, which includes base gas and data cost based on the size of the parameter \( p \).
+    \item \( [G_{storage}] \): Optional gas for storing the parameter. Not all applications require this.
+    \item \( G_{check} \): Gas for checking the condition at each of the \( n \) points of the parameter.
+    \item \( G_{run} \): Gas for performing the actual work (computation).
+\end{itemize}
+
+\subsubsection{Offline Distributed Verification Method (\( G_{off} \))}
+
+\begin{equation}
+G_{off} = G_{parameter} + G_{storage} + m \cdot (G_{seed} + G_{check} + G_{hash}) + G_{run}
+\end{equation}
+
+\begin{itemize}
+    \item \( G_{parameter} \): Intrinsic gas for submitting the parameter.
+    \item \( G_{storage} \): Gas for storing the parameter or its hash.
+    \item \( G_{seed} + G_{check} + G_{hash} \): Gas for each of the \( m \) seeds to:
+    \begin{itemize}
+        \item Submit the seed (\( G_{seed} \)).
+        \item Check the condition of the parameter point associated with the seed (\( G_{check} \)).
+        \item Compute the hash and compare it with the target hash (\( G_{hash} \)).
+    \end{itemize}
+    \item \( G_{run} \): Gas for performing the actual work (computation).
+\end{itemize}
+
+\subsubsection{Comparative Analysis}
+
+\paragraph*{Intrinsic Cost}
+\begin{itemize}
+    \item Both methods incur the intrinsic gas cost \( G_{parameter} \).
+\end{itemize}
+
+\paragraph*{Storage Cost}
+\begin{itemize}
+    \item The on-chain method has an optional storage cost \( [G_{storage}] \), while the offline method always includes the storage cost \( G_{storage} \).
+\end{itemize}
+
+\paragraph*{Parameter Checking}
+\begin{itemize}
+    \item In the on-chain method, the parameter check cost is \( n \cdot G_{check} \), where \( n \) is the size of the parameter.
+    \item In the offline method, this cost is \( m \cdot G_{check} \), where \( m \) is the number of seeds.
+Typically, \( m \) is significantly smaller than \( n \), as seeds represent a subset of checks.
+\end{itemize}
+
+\paragraph*{Additional Costs in the Offline Method}
+\begin{itemize}
+    \item The offline method includes \( m \cdot G_{seed} \) for submitting each seed.
+    \item It also includes \( m \cdot G_{hash} \) for computing and comparing hashes, which the on-chain method does not explicitly incur.
+\end{itemize}
+
+\paragraph*{Computation Costs}
+\begin{itemize}
+    \item Both methods have the same computation cost \( G_{run} \).
+\end{itemize}
+
+\subsubsection*{Comparison}
+
+\begin{itemize}
+    \item \textbf{On-Chain Verification Method (\( G_{on} \))}:
+    \begin{itemize}
+        \item More suited for scenarios where all data and checks must be performed directly on the blockchain.
+        \item Potentially higher cost due to \( n \cdot G_{check} \) if \( n \) (size of the parameter) is large.
+It gets worse when the check is complicated and the parameter is larger, which means \( G_{check} \) is high and \( n \) is large.
+    \end{itemize}
+
+    \item \textbf{Offline Distributed Verification Method (\( G_{off} \))}:
+    \begin{itemize}
+        \item More efficient for large datasets since it reduces the number of checks to \( m \) seeds, where \( m \) is usually much smaller than \( n \).
+        \item Incurs additional costs for \( G_{seed} \) and \( G_{hash} \), but these are often outweighed by the savings from reducing the number of checks.
+        \item The most concern is the cost to store the parameter for the verification process.
+In case the parameter needs to be stored anyway then there is no need to concern, but for the opposite case, this cost needs to be taken into account when estimating the cost of the method.
+Consider storing its hash instead since the hash could still be enough to verify the parameter, but then the \( G_{seed} \) will be increased.
+    \end{itemize}
+\end{itemize}
+
+Let \( G_{base} \) be the sum of the gas costs for submitting the parameter, storing it, and running it:
+\[
+G_{base} = G_{parameter} + G_{storage} + G_{run}
+\]
+
+Let \( G_{m} \) be the sum of the gas costs to perform \( m \) times the parameter checkpoint:
+\[
+G_{m} = m \cdot (G_{seed} + G_{check} + G_{hash})
+\]
+
+In case the base gas does not contain the storage gas, then the \( G_m \) gas includes it.
+
+Figure \ref{fig:gas_compare} shows the gas consumption for both methods.
+The red line shows the gas consumed by the on-chain verification method, which increases linearly with the size of the parameter.
+The blue line shows the gas cost by the offline distributed method.
+We can see that in the beginning, when the size of the parameter is small, it costs more with the offline method than with the on-chain method, but at one point it will show its benefits.
+
+\begin{figure}
+  \centering
+  \begin{tikzpicture}
+    \begin{axis}[
+        title={Gas Consumption Chart},
+        xlabel={Parameter size},
+        ylabel={Gas},
+        grid=both,
+        major grid style={line width=.2pt,draw=gray!50},
+        minor grid style={line width=.1pt,draw=gray!20},
+        xtick={1,2,3,4,5,6,7,8},
+        xticklabels={1,2,3,,,,n,},
+        ytick={1,2,3,4,5,6,7,8},
+        yticklabels={$G_{base} + G_{check}$,$G_{base} + 2 \cdot G_{check}$, $G_{base} + 3 \cdot G_{check}$,,$G_{base}+ G_m$,,$G_{base} + n \cdot G_{check}$,},
+    ]
+      \addplot[
+        color=red,
+        mark=square,
+        ]
+        coordinates {
+        (1,1)(2,2)(3,3)(4,4)(5,5)(6,6)(7,7)
+        };
+        % Add custom labels as nodes
+      %\node at (axis cs:1,1) [anchor=north] {$(1, m)$};
+      %\node at (axis cs:2,2) [anchor=north] {$(2, g_3)$};
+      %\node at (axis cs:3,3) [anchor=north] {$(3, a)$};
+      %\node at (axis cs:4,4) [anchor=north] {$(4, b)$};
+      %\node at (axis cs:5,5) [anchor=north] {$(5, c)$};
+
+         \addplot[
+        color=blue,
+        mark=square,
+        ]
+        coordinates {
+        (1,5)(2,5)(3,5)(4,5)(5,5)(6,5)(7,5)
+        };
+    \end{axis}
+  \end{tikzpicture}
+  \caption{Gas Comparison (Storage)}
+  \label{fig:gas_compare}
+\end{figure}
+
+%\begin{figure}
+%  \centering
+% \begin{tikzpicture}
+%     \begin{axis}[
+%         title={Simple Line Chart},
+%         xlabel={Parameter size},
+%         ylabel={Gas},
+%         grid=both,
+%         major grid style={line width=.2pt,draw=gray!50},
+%         minor grid style={line width=.1pt,draw=gray!20},
+ %        xtick={1,2,3,4,5,6,7,8},
+%         xticklabels={1,2,3,,,,n,},
+%         ytick={1,2,3,4,5,6,7,8},
+%         yticklabels={$G_{base} + G_{check}$,$G_{base} + 2.G_{check}$, $G_{base} + 3.G_{check}$,,$G_{base}+ G_{storage}+G_m$,,$G_{base} + n.G_{check}$,},
+%     ]
+%       \addplot[
+%         color=red,
+%         mark=square,
+%         ]
+%         coordinates {
+%         (1,1)(2,2)(3,3)(4,4)(5,5)(6,6)(7,7)
+%         };
+        % Add custom labels as nodes
+      %\node at (axis cs:1,1) [anchor=north] {$(1, m)$};
+      %\node at (axis cs:2,2) [anchor=north] {$(2, g_3)$};
+      %\node at (axis cs:3,3) [anchor=north] {$(3, a)$};
+      %\node at (axis cs:4,4) [anchor=north] {$(4, b)$};
+      %\node at (axis cs:5,5) [anchor=north] {$(5, c)$};
+
+%          \addplot[
+%         color=blue,
+%         mark=square,
+%         ]
+%         coordinates {
+%         (1,5)(2,5)(3,5)(4,5)(5,5)(6,5)(7,5)
+%         };
+%     \end{axis}
+%   \end{tikzpicture}
+%   \caption{Gas comparation (non-storage)}
+%   \label{fig:gas_compare_nonstorage}
+% \end{figure}
+Overall, the offline method (\( G_{off} \)) is generally more cost-effective for large parameters as it reduces the number of on-chain checks from \( n \) to \( m \).
+However, the exact cost-effectiveness depends on the relative sizes of \( n \) and \( m \), the parameter storing gas, and the specific gas costs of \( G_{seed} \) and \( G_{hash} \).
 \section{Domain Specification Language for Assertion}
@@
 \section{Cost Analysis}
+
 \section{Related work}

### 2024-07-23 papers/assertion-contract/assertion_contract_app/paper.tex
Major revise

@@
 \usetikzlibrary{shapes.geometric, arrows}
+\usepackage{comment}
 
@@
 \label{sec:introduction}
+
 \section{Primaries}
@@
 
-\section{Distributed Assertion Protocol}
+\section{Distributed Assertions Verification Process}
 \label{sec:approach}
-We propose a novel method for verifying parameter assertions in smart contracts on the blockchain.
-Our approach distributes the assertion verification process and moves it off-chain, with only the verification results being submitted to the blockchain.
-
-In this distributed process, each validator attempts to identify a counterexample to the assertion.
-Upon finding one, the validator submits the counterexample on-chain.
-Consequently, instead of verifying the entire assertion, the on-chain contract only needs to check specific points.
-
-To implement this idea, we propose a proof-of-work-based incentivization method in which validators are rewarded for discovering counterexamples, and some are rewarded for their computational efforts, thus encouraging participation in the distributed verification process.
-
-\subsection{Distributed assertions verification process}
+\subsection{Assertions verification problem}
 In the context of a domain $A$ and a predicate $P$ on $A$, an assertion is formalized using the universal quantifier as follows:
@@
 \end{gather}
+
+To verify these assertions, it requires iterating over the domain $A$ within the contract.
+When the domain $A$ is large or the predicate $P$ is complex to evaluate, it incurs a significant amount of gas to perform the verification process on-chain.
+Given the current high gas prices, this could result in substantial costs or even impossible due to gas limits.
+
+\subsection{Distributed verification method}
+We propose a novel method for verifying parameter assertions in smart contracts on the blockchain.
+Our approach distributes the assertion verification process and moves it off-chain, with only the verification results being submitted to the blockchain.
 
@@
 
-To verify these assertions, it requires iterating over the domain $A$ within the contract.
-When the domain $A$ is large or the predicate $P$ is complex to evaluate, it incurs a significant amount of gas to perform the verification process on-chain.
-Given the current high gas prices, this could result in substantial costs or even impossible due to gas limits.
+Our approach aims to alleviate the expensive gas comsuming by distributing the negation of the assertion to validators.
 
-Our approach aims to alleviate this by distributing the negation of the assertion to validators.
 Each validator endeavors to find a counterexample of the assertion using this negation.
@@
 
+Consequently, instead of verifying the entire assertion, the on-chain contract only needs to check specific points.
 Since only one specific point is checked on-chain, the amount of gas required for the computation to check the counterexample is likely to be significantly less than verifying the entire assertion directly on-chain.
+
+%In this distributed process, each validator attempts to identify a counterexample to the assertion.
+Upon finding one, the validator submits the counterexample on-chain.
+Consequently, instead of verifying the entire assertion, the on-chain contract only needs to check specific points.
 
@@
 
-\noindent each validator try to genarate  a
+Each validator try to find  a
 random $n$ in the range $2 \le n \le 
-\sqrt p$ and checking whether $(p \mathbin{\%} n) = 0$. If the remainder is $0$, the validator found a counterexample.
+\sqrt p$ such that $(p \mathbin{\%} n) = 0$. If the remainder is $0$, the validator found a counterexample.
 
@@
 Each validator attempts to find the number $k$ such that the negation is true for such $k$, then the validator has found a counterexample for the sortedness of the array.
-\subsection{Proof-of-work-based incentivization method}
+
+\section{Proof-of-work-based incentivization method}
 Finding a counterexample is rewarded, incentivizing validators, but comes at the cost of computing resources.
@@
 Therefore, it is necessary to incentivize this effort.
-Moreover, it is logical to reward only a portion of the computational effort required.
-A significant concern arises regarding how to ensure that validators perform the verification computation off-chain to receive the reward, even when no counterexample is foundward.
+%Moreover, it is logical to reward only a portion of the computational effort required.
+However, to prioritize the discovery of counterexamples, the reward for finding a counterexample is set significantly higher than that for providing a computational proof.
 
-\subsubsection{Outlines}
+We propose a proof-of-work-based incentivization method in which validators are rewarded for discovering counterexamples, and some are rewarded for their computational efforts, thus encouraging participation in the distributed verification process.
+\subsection{Outlines}
+A significant concern arises regarding how to ensure that validators perform the verification computation off-chain, even when no counterexample is foundward.
+
 We propose a proof-of-work-based method to incentivize participants in the distributed verification process.  The proposed approach is outlined as follows:
+\begin{itemize}
+%\item There are two ways to reward validators to encourage their participation: to discover a counterexample, and to provide computational proof that they have executed the program to search for a counterexample, even if none is found.
+\item We utilize the proof-of-work concept by introducing a target hash $t$ that sets the required difficulty level to earn the computation reward. 
+\item The objective of the validator is to find a computation proof that smaller than or equal to the target hash $t$.
+\item The computation of the negation formula is integrated into the computational proof to ensure that the validators cannot produce the proof without executing a negation check.
+\end{itemize}
+%Because the rewards may be limited in quantity, validators are motivated to swiftly verify the parameters to claim the reward before others do so. 
+\subsection{Computation proof}
+The next question is how to devise a computational proof to incentivize computational effort.
+The key challenge is how to involve the negation check in the computational proof and how to reproduce the computational proof off-chain to on-chain with a reasonable gas cost.
+To address this, we introduce a seed $s$ in each verification process.
 
-\begin{itemize}
-\item There are two ways to reward validators to encourage their participation: to discover a counterexample, and to provide computational proof that they have executed the program to search for a counterexample, even if none is found.
-\item To prioritize the discovery of counterexamples, the reward for finding a counterexample is set significantly higher than that for providing a computational proof.
-\item The computation of the negation formula is integrated into the computational proof to ensure that the validators cannot produce the proof without executing a negation check.
-\item Because the rewards may be limited in quantity, validators are motivated to swiftly verify the parameters to claim the reward before others do so.
-\end{itemize}
-\subsubsection{Computation Proof}
-The next step is to devise a computation proof to incentivize computational effort by utilizing the proof-of-work concept.
-We introduce a target hash $t$ that sets the required difficulty level to earn the reward.
-The objective of the validator is to generate a computation that produces a hash smaller than or equal to the target hash $t$.
+Let \( n \) denote the size of the domain \( A \).
+Each number \( i \) in the range \([1, n]\) corresponds to an element in \( A \).
+The seed \( s \) is a random number, and we can reduce it modulo \( n \) to obtain \( i \), which is associated with an element \( a \) in \( A \).
 
-A key challenge is reproducing the computation proof off-chain to on-chain.
-To address this, we introduce a seed $s$ in each verification process.
-Let $n$ denote the size of domain $A$.
-Each number $i$ in the range $[1, n]$ corresponds to an element in $A$.
-The seed $s$ is reduced modulo $n$ to obtain $i$, which is associated with an element $a$ in $A$.
 \paragraph{Estimate the number of seeds:} We first estimate the number of seeds needed to find a counterexample with a given expected probability.
@@
 Each seed independently has a probability of $1/n$ to detect the problem and a probability of $\frac{n-1}{n}$ not to detect the problem.
-Hence, if we assume that each seed associated with an element $a$ in $A$ is chosen independently from a uniform distribution, the probability that no validator checks the element $a_0$ converges to $0$ as the number of seeds approaches infinity:
+Hence, if we assume that each seed associated with an element $a$ in $A$ is chosen independently from a uniform distribution, the probability that no seed checks the element $a_0$ converges to $0$ as the number of seeds approaches infinity:
 
@@
 Depending on the expected probability to detect the problem, the number of seeds to generate can be determined.
+
 Assume that $p$ is the probability of finding at least one counterexample.
-To calculate the number of seeds $m$ needed to achieve a given expected probability $p$ of finding a counterexample, we can use the complementary probability.
-We have:
+The complementary probability is used to calculate the number of seeds $m$ needed to achieve a given expected probability $p$ of finding a counterexample.
 \begin{itemize}
@@
 \item The probability of all $m$ seeds failing to find a counterexample is $\left(\frac{n-1}{n}\right)^m$.
-\item Therefore, the probability of at least one of the $m$ seeds finding a counterexample is:
+\item The probability of at least one of the $m$ seeds finding a counterexample is:
 \[
@@
 \]
+\paragraph{Conduct a computation proof:} The computation of the negation formula is integrated into the computational proof to ensure that the validators cannot produce the proof without executing a negation check.
 
+Lets \(\text{eval}\) be the function that returns the significant components of the evaluation of the negation \(\neg P_{a}\).
+For example, it returns \(a[i]\) and \(a[i + 1]\) in the evaluation of the negation predicate \(a[i] < a[i+1]\) in the sorted array example.
+
+Thus, the computation hash includes the seed  \( s \) and \(\text{eval}\). 
+\begin{align}
+t_s = \text{hash}(s, \text{eval}(\neg P_{a}))
+\end{align}
 \paragraph{Find a seed:}
@@
 
-\item Calculate the hash \( t_s \) corresponding to the seed \( s \):
-\begin{align}
-t_s = \text{hash}(s, \text{eval}(\neg P_{a}))
-\end{align}
-where \(\text{hash}\) is the hash function and \(\text{eval}\) is the function that returns the significant components of the evaluation of the negation \(\neg P_{a}\).
-
-For example, it returns \(a[i]\) and \(a[i + 1]\) in the evaluation of the negation predicate \(a[i] < a[i+1]\) in the sorted array example.
+\item If no counterexample is found, calculate the hash \( t_s \) corresponding to the seed \( s \).
 \item Compare \( t_s \) to the target hash to determin whether it is a reward computation.
@@
 
+\begin{comment}
+\begin{tikzpicture}[node distance=2cm]
+
+    % Nodes
+    \node (start) [startstop] {Generate random seed $s$};
+    \node (calc_n) [process, below of=start] {Calculate $n = |A|$};
+    \node (calc_i) [process, below of=calc_n] {Determine $i = (s \mod n) + 1$};
+    \node (find_a) [process, below of=calc_i] {Find $a = A[i]$};
+    \node (neg_check) [process, below of=find_a] {Perform negation check $\neg P_a$};
+    \node (counterexample) [decision, below of=neg_check, yshift=-1cm] {Counterexample found?};
+    \node (calc_hash) [process, below of=counterexample, yshift=-1cm] {Calculate hash $t_s$};
+    \node (compare) [process, below of=calc_hash] {Compare $t_s$ to target hash};
+    \node (non_reward) [startstop, right of=counterexample, xshift=3cm] {No Counterexample};
+    \node (reward) [startstop, right of=compare, xshift=3cm] {Reward Computation};
+    \node (submit) [process, below of=compare, yshift=-1cm] {Submit on-chain to claim reward};
+    \node (submit_counter) [process, below of=counterexample, yshift=-1cm] {Submit on-chain to claim reward};
+
+    % Arrows
+    \draw [arrow] (start) -- (calc_n);
+    \draw [arrow] (calc_n) -- (calc_i);
+    \draw [arrow] (calc_i) -- (find_a);
+    \draw [arrow] (find_a) -- (neg_check);
+    \draw [arrow] (neg_check) -- (counterexample);
+    \draw [arrow] (counterexample) -- node[anchor=east] {Yes} (submit_counter);
+    \draw [arrow] (counterexample) -- node[anchor=south] {No} (calc_hash);
+    \draw [arrow] (calc_hash) -- (compare);
+    \draw [arrow] (compare) -- node[anchor=south] {No} (non_reward);
+    \draw [arrow] (compare) -- node[anchor=south] {Yes} (reward);
+    \draw [arrow] (reward) |- (submit);
+    \draw [arrow] (submit_counter) -| (submit);
+
+\end{tikzpicture}
+\end{comment}
 %Consequently, each seed $s$ is linked with an element $a$ in the domain $A$, followed by the evaluation of the negation of the assertion $\neg P_{a}$.
@@
 \item Denial-of-service (DoS) attacks: The system is susceptible to DoS attacks, where a caller inundates the system with numerous invalid parameters, causing congestion and hindering its operation.
-\item Reward manipulation: A validator may attempt to manipulate the reward system by resubmitting counterexamples or computation proofs multiple times to multiply their rewards.
+%\item Reward manipulation: A validator may attempt to manipulate the reward system by resubmitting counterexamples or computation proofs multiple times to multiply their rewards.
 \end{enumerate}
@@
 
-In some applications, multiple computational proofs may be allowed. This record is crucial for determining when a work function can be invoked for a given parameter or when it should be discarded.
+%In some applications, multiple computational proofs may be allowed. This record is crucial for determining when a work function can be invoked for a given parameter or when it should be discarded.
 
@@
 For our offline distributed verification method, let's assume that the parameter is valid, and now we consider the cost to verify the parameter and perform the actual work.
-Let $m$ be the number of proofs required to ensure the correctness of the parameter.
-Thus, the offline method costs the gas for submitting the parameter, the gas to store the parameter (or its hash), $m$ times the gas to submit the seed, check the condition of the parameter point associated with the seed, the gas to compute the hash and compare it with the target hash, and of course the gas to run the computation of the actual work.
+%Let $m$ be the number of proofs required to ensure the correctness of the parameter.
+Thus, the offline method costs the gas for submitting the parameter, the gas to store the parameter (or its hash), the gas to submit the seed, check the condition of the parameter point associated with the seed, the gas to compute the hash and compare it with the target hash, and of course the gas to run the computation of the actual work.
 
@@
 \begin{equation}
-G_{off} = G_{parameter} + G_{storage} + m \cdot (G_{seed} + G_{check} + G_{hash}) + G_{run}
+G_{off} = G_{parameter} + G_{storage} +   (G_{seed} + G_{check} + G_{hash}) + G_{run}
 \end{equation}
@@
     \item \( G_{storage} \): Gas for storing the parameter or its hash.
-    \item \( G_{seed} + G_{check} + G_{hash} \): Gas for each of the \( m \) seeds to:
+    \item \( G_{seed} + G_{check} + G_{hash} \): Gas for 
     \begin{itemize}
@@
     \item In the on-chain method, the parameter check cost is \( n \cdot G_{check} \), where \( n \) is the size of the parameter.
-    \item In the offline method, this cost is \( m \cdot G_{check} \), where \( m \) is the number of seeds.
-Typically, \( m \) is significantly smaller than \( n \), as seeds represent a subset of checks.
+    \item In the offline method, this cost is \( G_{check} \).
 \end{itemize}
@@
 \begin{itemize}
-    \item The offline method includes \( m \cdot G_{seed} \) for submitting each seed.
-    \item It also includes \( m \cdot G_{hash} \) for computing and comparing hashes, which the on-chain method does not explicitly incur.
+    \item The offline method includes \(  G_{seed} \) for submitting each seed.
+    \item It also includes \(  G_{hash} \) for computing and comparing hashes, which the on-chain method does not explicitly incur.
 \end{itemize}
@@
 
-Let \( G_{m} \) be the sum of the gas costs to perform \( m \) times the parameter checkpoint:
+Since the centralize verification process only costs in term of gas and the distrbiuted process uses the proof of work incentive, we converts the reward in term of gas.
+Lets $G_{reward}$ be the gas, which is price for finding the proof.
+Let \( G_{proof} \) be the sum of the gas costs to perform and reward the  computation proof.
 \[
-G_{m} = m \cdot (G_{seed} + G_{check} + G_{hash})
+G_{proof} = G_{seed} + G_{check} + G_{hash} + G_{reward} 
 \]
 
-In case the base gas does not contain the storage gas, then the \( G_m \) gas includes it.
+In case the base gas does not contain the storage gas, then the \( G_{proof} \) gas includes it.
 
@@
         ytick={1,2,3,4,5,6,7,8},
-        yticklabels={$G_{base} + G_{check}$,$G_{base} + 2 \cdot G_{check}$, $G_{base} + 3 \cdot G_{check}$,,$G_{base}+ G_m$,,$G_{base} + n \cdot G_{check}$,},
+        yticklabels={$G_{base} + G_{check}$,$G_{base} + 2 \cdot G_{check}$, $G_{base} + 3 \cdot G_{check}$,,$G_{base}+ G_{proof}$,,$G_{base} + n \cdot G_{check}$,},
     ]
@@
 % \end{figure}
-Overall, the offline method (\( G_{off} \)) is generally more cost-effective for large parameters as it reduces the number of on-chain checks from \( n \) to \( m \).
-However, the exact cost-effectiveness depends on the relative sizes of \( n \) and \( m \), the parameter storing gas, and the specific gas costs of \( G_{seed} \) and \( G_{hash} \).
+Overall, the offline method (\( G_{off} \)) is generally more cost-effective for large parameters as it reduces the number of on-chain checks from \( n \) to 1.
+However, the exact cost-effectiveness depends on the relative sizes of \( n \), the parameter storing gas, and the specific gas costs of \( G_{seed} \), \( G_{hash} \) and \( G_{reward} \).
 \section{Domain Specification Language for Assertion}

### 2024-07-24 papers/assertion-contract/assertion_contract_app/paper.tex
restructure

@@
 In certain blockchain scenarios, verifying properties of a parameter requires significant gas costs or may even be infeasible due to gas limits.
-This study proposes a distributed assertion verification protocol to address this issue.
-The core idea is to distribute the negation of the assertion to validators, who then attempt to find a counterexample off-chain.
-If a counterexample is found, it can be submitted on-chain.
+This study proposes a distributed verification protocol to address this issue.
+The core idea is to distribute the negation of the assertion of a property to validators, who then attempt to find a counterexample off-chain.
+If a counterexample is found, it can be submitted and verified on-chain.
 Additionally, a proof-of-work-based incentive mechanism is proposed to encourage validators to participate in the distributed verification process.
 
-To operationalize these ideas, we suggest a practical model that addresses security concerns.
-We also implemented a prototype of the proposed protocol and conducted a cost analysis to demonstrate the advantages of our method in terms of cryptocurrency, proving its practical utility
+To operationalize these ideas, we suggest a practical model that addresses potential security concerns.
+We  implemented a prototype of the proposed protocol and conducted a cost analysis to demonstrate the advantages of our method in terms of cryptocurrency, proving its practical utility.
  \keywords{}
@@
 
-\section{Distributed Assertions Verification Process}
-\label{sec:approach}
+\section{Assertions Verification On-chain}
+\label{sec:assertion-verification-onchain}
 \subsection{Assertions verification problem}
+
 In the context of a domain $A$ and a predicate $P$ on $A$, an assertion is formalized using the universal quantifier as follows:
@@
 Given the current high gas prices, this could result in substantial costs or even impossible due to gas limits.
-
+\subsection{Use Cases}
+
+\section{Distributed Assertions Verification}
+\label{sec:distributed-assertion-verification}
 \subsection{Distributed verification method}
@@
 
-If any of the validators identify a violation of an assertion, the final call to the actual work function is aborted.
+%If any of the validators identify a violation of an assertion, the final call to the actual work function is aborted.
 However, if certain requirements are met, the work function is invoked with the parameter.
@@
 
-\section{Proof-of-work-based incentivization method}
+\subsection{Proof-of-work-based incentivization}
 Finding a counterexample is rewarded, incentivizing validators, but comes at the cost of computing resources.
@@
 %Moreover, it is logical to reward only a portion of the computational effort required.
-However, to prioritize the discovery of counterexamples, the reward for finding a counterexample is set significantly higher than that for providing a computational proof.
+%However, to prioritize the discovery of counterexamples, the reward for finding a counterexample is set significantly higher than that for providing a computational proof.
 
 We propose a proof-of-work-based incentivization method in which validators are rewarded for discovering counterexamples, and some are rewarded for their computational efforts, thus encouraging participation in the distributed verification process.
-\subsection{Outlines}
-A significant concern arises regarding how to ensure that validators perform the verification computation off-chain, even when no counterexample is foundward.
-
-We propose a proof-of-work-based method to incentivize participants in the distributed verification process.  The proposed approach is outlined as follows:
-\begin{itemize}
-%\item There are two ways to reward validators to encourage their participation: to discover a counterexample, and to provide computational proof that they have executed the program to search for a counterexample, even if none is found.
+\subsubsection{Outlines}
+%We propose a proof-of-work-based method to incentivize participants in the distributed verification process. 
+A significant concern arises regarding how to recheck the counterexample and how to ensure that validators perform the verification computation off-chain in case no counterexample is found.
+
+The proposed proof-of-work-based incentivization method is outlined as follows:
+\begin{itemize}
+    \item The counterexample is submitted in the form of the indication of the element where the assertion is invalid.
+    \item To prioritize the discovery of counterexamples, the reward for finding a counterexample is set significantly higher than that for providing a computational proof.
     \item We utilize the proof-of-work concept by introducing a target hash $t$ that sets the required difficulty level to earn the computation reward.
-\item The objective of the validator is to find a computation proof that smaller than or equal to the target hash $t$.
+    \item The objective of the validator is to find a counterexample or a computation proof that is smaller than or equal to the target hash $t$.
     \item The computation of the negation formula is integrated into the computational proof to ensure that the validators cannot produce the proof without executing a negation check.
@@
 %Because the rewards may be limited in quantity, validators are motivated to swiftly verify the parameters to claim the reward before others do so. 
-\subsection{Computation proof}
+\subsubsection{Computation proof}
 The next question is how to devise a computational proof to incentivize computational effort.
@@
 
-\paragraph{Estimate the number of seeds:} We first estimate the number of seeds needed to find a counterexample with a given expected probability.
+\paragraph{Estimate the number of seeds:} We first estimate the number of seeds needed to find a counterexample with a given expected probability, assuming the worst case where only one validator participates.
 
@@
 
-The verification status records a counterexample and reward computations found. For that, it should include the following details:
+In some applications, multiple computational proofs may be allowed.
+This record is crucial for determining when a work function can be invoked for a given parameter or when it should be discarded.
+The verification status records a counterexample and reward computations found.
+For that, it should include the following details:
 \begin{itemize}

### 2024-07-30 papers/assertion-contract/assertion_contract_app/paper.tex
major revision

@@
 \tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=orange!30]
-\tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30]
+\tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
 \tikzstyle{arrow} = [thick,->,>=stealth]
@@
 \label{sec:introduction}
-
-\section{Primaries}
-\label{sec:primaries}
-
-\section{Assertions Verification On-chain}
-\label{sec:assertion-verification-onchain}
-\subsection{Assertions verification problem}
-
-In the context of a domain $A$ and a predicate $P$ on $A$, an assertion is formalized using the universal quantifier as follows:
-\begin{gather}
-  \label{eq:1}
-\forall a \in A. P_{a}
-\end{gather}
-
-This formula can be extended to multiple domains as:
-
-\begin{gather}
-\label{eq:2}
-\forall a \in A, \forall b \in B, \dots .P_{a, b, \dots}
-\end{gather}
-
-To verify these assertions, it requires iterating over the domain $A$ within the contract.
-When the domain $A$ is large or the predicate $P$ is complex to evaluate, it incurs a significant amount of gas to perform the verification process on-chain.
-Given the current high gas prices, this could result in substantial costs or even impossible due to gas limits.
-\subsection{Use Cases}
-
-\section{Distributed Assertions Verification}
-\label{sec:distributed-assertion-verification}
-\subsection{Distributed verification method}
-We propose a novel method for verifying parameter assertions in smart contracts on the blockchain.
-Our approach distributes the assertion verification process and moves it off-chain, with only the verification results being submitted to the blockchain.
-
-The negation of the assertion is represented by the existential quantifier formulas:
-
-\begin{gather}
-\label{eq:3}
-\neg (\forall a \in A. P_{a}) \equiv \exists a \in A. \neg P_{a}
-\end{gather}
-
-And for multiple domains, it is as follows:
-
-\begin{gather}
-\label{eq:4}
-\exists a \in A, \exists b \in B, \dots. \neg P_{a, b, \dots}
-\end{gather}
-
-Our approach aims to alleviate the expensive gas comsuming by distributing the negation of the assertion to validators.
-
-Each validator endeavors to find a counterexample of the assertion using this negation.
-Specifically, each validator attempts to find a counterexample by identifying $a \in A$ such that the negation formula is satisfied $\neg P_{a}$.
-When a counterexample is found, the validator submits it, which is then re-verified on-chain.
-
-Consequently, instead of verifying the entire assertion, the on-chain contract only needs to check specific points.
-Since only one specific point is checked on-chain, the amount of gas required for the computation to check the counterexample is likely to be significantly less than verifying the entire assertion directly on-chain.
-
-%In this distributed process, each validator attempts to identify a counterexample to the assertion.
-Upon finding one, the validator submits the counterexample on-chain.
-Consequently, instead of verifying the entire assertion, the on-chain contract only needs to check specific points.
-
-%If any of the validators identify a violation of an assertion, the final call to the actual work function is aborted.
-However, if certain requirements are met, the work function is invoked with the parameter.
-
 Considering the example where a parameter $p$ is a prime number, the assertion in predicate logic for the parameter is:
@@
 Each validator attempts to find the number $k$ such that the negation is true for such $k$, then the validator has found a counterexample for the sortedness of the array.
-
-\subsection{Proof-of-work-based incentivization}
-Finding a counterexample is rewarded, incentivizing validators, but comes at the cost of computing resources.
+\section{Primaries}
+\label{sec:primaries}
+
+\section{On-chain Assertions Verification}
+\label{sec:assertion-verification-onchain}
+\subsection{Problem}
+
+In the context of a domain $A$ and a predicate $P$ on $A$, an assertion is formalized using the universal quantifier as follows:
+\begin{gather}
+  \label{eq:1}
+\forall a \in A. P_{a}
+\end{gather}
+
+This formula can be extended to multiple domains as:
+
+\begin{gather}
+\label{eq:2}
+\forall a \in A, \forall b \in B, \dots .P_{a, b, \dots}
+\end{gather}
+
+It requires iterating over the domain \( A \) within the contract to verify these assertions:
+\begin{gather}
+  \label{eq:3}
+  \bigwedge_{a \in A} P(a)
+\end{gather}
+
+For multiple domains, the verification process can be expressed as:
+\begin{gather}
+  \label{eq:4}
+  \bigwedge_{a \in A} \bigwedge_{b \in B} \dots P(a, b, \dots)
+\end{gather}
+
+When the domain $A$ is large or the predicate $P$ is complex to evaluate, it incurs a significant amount of gas to perform the verification process on-chain.
+Given the current high gas prices, this could result in substantial costs or even impossible due to gas limits.
+\subsection{Use Cases}
+
+\section{Distributed Assertions Verification}
+\label{sec:distributed-assertion-verification}
+\subsection{Distributed Verification Approach}
+We propose a novel approach for verifying parameter assertions in smart contracts on the blockchain.
+Our approach distributes the assertion verification process and moves it off-chain, with only the verification results being submitted to the blockchain.
+
+The negation of the assertion is represented by the existential quantifier formulas:
+
+\begin{gather}
+\label{eq:3}
+\neg \left( \bigwedge_{a \in A} P(a) \right) \equiv \exists a \in A. \neg P(a)
+\end{gather}
+
+And for multiple domains, it is as follows:
+
+\begin{gather}
+\label{eq:4}
+\neg \left( \bigwedge_{a \in A} \bigwedge_{b \in B} \dots P(a, b, \dots) \right) \equiv \exists a \in A, \exists b \in B, \dots . \neg P(a, b, \dots)
+\end{gather}
+Each validator endeavors to find a counterexample of the assertion using this negation.
+Specifically, each validator attempts to find a counterexample by identifying $a \in A$ such that the negation formula is satisfied $\neg P(a)$.
+When a counterexample is found, the validator submits it, which is then re-verified on-chain.
+
+The assertions are checked off-chain, and only the results of these checks (whether any assertion was violated) are submitted to the blockchain.
+This reduces the computational load on the blockchain while ensuring the integrity of the contract.
+
+Our approach aims to alleviate the expensive gas comsuming.
+Instead of verifying the entire assertion, the on-chain contract only needs to check specific points.
+Since only some specific points are checked on-chain, the amount of gas required for the computation to check the counterexample is likely to be significantly less than verifying the entire assertion directly on-chain.
+
+\subsection{Proof-of-work-based Incentivization}
+Finding a counterexample is rewarded, incentivizing validators but at the cost of computing resources.
 Instances of finding a counterexample may be rare, as callers typically avoid passing invalid parameters into the blockchain.
-If no counterexample emerges, the verification accuracy depends on the number of wisepoints generated to negate the assertion, with more validators increasing the certainty.
-
-Encouraging validators to engage in the verification process even without discovering a counterexample is crucial.
-Therefore, it is necessary to incentivize this effort.
+If no counterexample emerges, the verification accuracy depends on the number of attempts to negate the assertion, with more validators increasing the certainty.
+Therefore, it is crucial to encourage validators to engage in the verification process even without discovering a counterexample.
+%It is necessary to incentivize this effort.
 %Moreover, it is logical to reward only a portion of the computational effort required.
@@
 
-We propose a proof-of-work-based incentivization method in which validators are rewarded for discovering counterexamples, and some are rewarded for their computational efforts, thus encouraging participation in the distributed verification process.
+We propose a proof-of-work-based incentivization method where validators are rewarded for discovering counterexamples, and others are rewarded for their computational efforts.
+This approach encourages participation in the distributed verification process, ensuring thorough validation even without the discovery of counterexamples.
+
+A significant concern arises regarding how to recheck the counterexample and ensure that validators perform the verification computation off-chain if no counterexample is found.
 \subsubsection{Outlines}
-%We propose a proof-of-work-based method to incentivize participants in the distributed verification process. 
-A significant concern arises regarding how to recheck the counterexample and how to ensure that validators perform the verification computation off-chain in case no counterexample is found.
-
-The proposed proof-of-work-based incentivization method is outlined as follows:
+Our proposed proof-of-work-based incentivization method is outlined as follows:
 \begin{itemize}
@@
 \item To prioritize the discovery of counterexamples, the reward for finding a counterexample is set significantly higher than that for providing a computational proof.
-    \item We utilize the proof-of-work concept by introducing a target hash $t$ that sets the required difficulty level to earn the computation reward.
-    \item The objective of the validator is to find a counterexample or a computation proof that is smaller than or equal to the target hash $t$.
+\item We utilize the proof-of-work concept by introducing a target hash \( t \) that sets the required difficulty level to earn the computation reward.
+\item The objective of the validator is to find a counterexample or a computation proof that is smaller than or equal to the target hash \( t \).
 \item The computation of the negation formula is integrated into the computational proof to ensure that the validators cannot produce the proof without executing a negation check.
@@
 %Because the rewards may be limited in quantity, validators are motivated to swiftly verify the parameters to claim the reward before others do so. 
-\subsubsection{Computation proof}
+\subsubsection{Reward computation}
 The next question is how to devise a computational proof to incentivize computational effort.
@@
 
-Let's assume the unsatisfied element is only at the first element $a_0$ in $A$, the size of the domain is $n$, and the number of seeds is $m$.
+Let's assume the unsatisfied element is only at the first element $a_0$ in $A$, and the number of seeds is $m$.
 Each seed independently has a probability of $1/n$ to detect the problem and a probability of $\frac{n-1}{n}$ not to detect the problem.
@@
 \paragraph{Set up the taget hash:}
-The above seed number $m$ can then be used to set up the target hash $t$.
+The above number of seed $m$ can then be used to set up the target hash $t$.
 The target hash $t$ can be calculated based on a desired difficulty level.
@@
 \]
-\paragraph{Conduct a computation proof:} The computation of the negation formula is integrated into the computational proof to ensure that the validators cannot produce the proof without executing a negation check.
-
-Lets \(\text{eval}\) be the function that returns the significant components of the evaluation of the negation \(\neg P_{a}\).
+\paragraph{Conduct a computation proof:} The computation of the negation formula is integrated into a computational proof to ensure that the validators cannot produce the proof without executing a negation check.
+
+Lets \(\text{eval}\) be the function that returns the significant components of the evaluation of the negation \(\neg P(a)\).
 For example, it returns \(a[i]\) and \(a[i + 1]\) in the evaluation of the negation predicate \(a[i] < a[i+1]\) in the sorted array example.
@@
 \begin{align}
-t_s = \text{hash}(s, \text{eval}(\neg P_{a}))
+t_s = \text{hash}(s, \text{eval}(\neg P(a)))
 \end{align}
@@
 \end{align}
-\item Find the corresponding element $a$ in $A$:
+\item Associate \( i \) with the corresponding element $a$ in $A$:
 \begin{align}
@@
 where $A[i]$ denotes the $i$-th element in $A$.
-\item Perform the negation check $\neg P_{a}$ to detect a counterexample if any.
+\item Perform the negation check $\neg P(a)$ to detect a counterexample if any.
 
@@
 
-\begin{comment}
 \begin{tikzpicture}[node distance=2cm]
@@
     % Nodes
-    \node (start) [startstop] {Generate random seed $s$};
-    \node (calc_n) [process, below of=start] {Calculate $n = |A|$};
-    \node (calc_i) [process, below of=calc_n] {Determine $i = (s \mod n) + 1$};
-    \node (find_a) [process, below of=calc_i] {Find $a = A[i]$};
-    \node (neg_check) [process, below of=find_a] {Perform negation check $\neg P_a$};
-    \node (counterexample) [decision, below of=neg_check, yshift=-1cm] {Counterexample found?};
-    \node (calc_hash) [process, below of=counterexample, yshift=-1cm] {Calculate hash $t_s$};
-    \node (compare) [process, below of=calc_hash] {Compare $t_s$ to target hash};
-    \node (non_reward) [startstop, right of=counterexample, xshift=3cm] {No Counterexample};
-    \node (reward) [startstop, right of=compare, xshift=3cm] {Reward Computation};
-    \node (submit) [process, below of=compare, yshift=-1cm] {Submit on-chain to claim reward};
-    \node (submit_counter) [process, below of=counterexample, yshift=-1cm] {Submit on-chain to claim reward};
+    \node (calc_n) [process] {$n = |A|$};
+    \node (start) [startstop, below of=calc_n] {$s$};
+    \node (calc_i) [process, below of=start] {$i = (s \mod n) + 1$};
+    \node (find_a) [process, below of=calc_i] {$a = A[i]$};
+    \node (counterexample) [decision, below of=find_a, yshift=-0.5cm] {$\neg P(a)$};
+    \node (calc_hash) [process, below of=counterexample, yshift=-0.5cm] {$t_s = \text{hash}(s, \text{eval}(\neg P(a)))$};
+    \node (compare) [decision, below of=calc_hash, yshift=-0.5cm] {$t_s <= t$};
+    \node (submit) [startstop, below of=compare, yshift=-0.5cm] {Submit on-chain};
 
     % Arrows
-    \draw [arrow] (start) -- (calc_n);
-    \draw [arrow] (calc_n) -- (calc_i);
+    \draw [arrow] (calc_n) -- (start);
+    \draw [arrow] (start) -- (calc_i);
     \draw [arrow] (calc_i) -- (find_a);
-    \draw [arrow] (find_a) -- (neg_check);
-    \draw [arrow] (neg_check) -- (counterexample);
-    \draw [arrow] (counterexample) -- node[anchor=east] {Yes} (submit_counter);
-    \draw [arrow] (counterexample) -- node[anchor=south] {No} (calc_hash);
+    \draw [arrow] (find_a) -- (counterexample);
+    \draw [arrow] (counterexample) -- node[midway, above, sloped, anchor=center, yshift=0.5em] {No} (calc_hash);
     \draw [arrow] (calc_hash) -- (compare);
-    \draw [arrow] (compare) -- node[anchor=south] {No} (non_reward);
-    \draw [arrow] (compare) -- node[anchor=south] {Yes} (reward);
-    \draw [arrow] (reward) |- (submit);
-    \draw [arrow] (submit_counter) -| (submit);
+    %\draw [arrow] (compare) -- node[anchor=south] {Yes} (submit);
+    \draw [arrow] (compare) -- (submit) node[midway, above, sloped, anchor=center, yshift=0.5em] {Yes};
+    % Right-angle arrow from counterexample to submit
+	\draw [arrow] (counterexample.east) -| node[pos=0.25, above] {Yes} ([xshift=2cm]submit.east) |- (submit);
+	\draw [arrow] (compare.west) -| node[pos=0.75, left] {No} ([xshift=-2cm]counterexample.west) |- (start);
 
 \end{tikzpicture}
-\end{comment}
+
 %Consequently, each seed $s$ is linked with an element $a$ in the domain $A$, followed by the evaluation of the negation of the assertion $\neg P_{a}$.
@@
 The model consists of two main entities: an on-chain assertion contract and off-chain validator contract.
-In our practical model, three distinct actors play key roles.
+\subsubsection{Three main actors.} In our practical model, three distinct actors play key roles.
 \begin{itemize}
@@
 \end{figure}
-
+\subsubsection{Calculate seed.}
 While a random number alone is sufficient to indicate the associated element $a$ in the domain $A$, to prevent the front-running attack and the caller exploitation attack, we enhance the randomness of the seed by combining a random number with the validator's address and the timestamps indicating when the parameter is submitted on the chain to calculate the seed.
@@
 
-An assertion in smart contract languages, such as Solidity and Michelson, is essentially predicate logic expressed as a Boolean formula computed from relational operators, logical operators, and expressions.
+\subsubsection{The evaluation of the negation predicate.} An assertion in smart contract languages, such as Solidity and Michelson, is essentially predicate logic expressed as a Boolean formula computed from relational operators, logical operators, and expressions.
 \begin{align}
@@
 \end{itemize}
-\textbf{On-chain assertion contract}:
+\subsubsection{On-chain assertion contract.}
 While additional functions may exist, the assertion contract must encompass the following two essential functions:
@@
 \end{itemize}
-\textbf{Off-chain assertion contract}:
+\subsubsection{Off-chain assertion contract.}
 Since the off-chain contract runs off-chain, it can be implemented according to the validator's preferences.
@@
 Additionally, it should support a function that assists the validator in finding a seed to earn a reward.
-\\ \textbf{Storage}:
+\subsubsection{Storage.}
 When a parameter is submitted for verification, the following information should be stored:
@@
 \item Timestamp: this indicates the approximate time when the parameter was submitted. This information is used to prevent caller exploitation security risks as explained above.
-\item Verification Status Records: the records are to monitor the progress of the parameter's verification.
 \end{itemize}
@@
 In some applications, multiple computational proofs may be allowed.
+There are a record to monitor the progress of the parameter's verification.
 This record is crucial for determining when a work function can be invoked for a given parameter or when it should be discarded.
 The verification status records a counterexample and reward computations found.
-For that, it should include the following details:
-\begin{itemize}
-    \item The addresses of the validators.
-    \item The random number $r$ used in the verification process.
-\end{itemize}
+For that, it should include the following details of the addresses of the validators and the random number $r$ used in the verification process.
 
 %In some applications, multiple computational proofs may be allowed. This record is crucial for determining when a work function can be invoked for a given parameter or when it should be discarded.
-
-In certain applications, one may delete the records after processing is completed for the parameter, especially if a large number of parameters are submitted to manage storage efficiently.
 
@@
 Therefore, this uniqueness prevents validators from submitting the same computation proof or a counterexample multiple times.
+
+%In certain applications, one may delete the records after processing is completed for the parameter, especially if a large number of parameters are submitted to manage storage efficiently.
 \subsection{Deploying and managing on/off-chain contracts.}
@@
 \subsubsection{Submitting a parameter} 
-Before a parameter can be utilized in the actual work function/contract, a caller must initially submit it via the submit-parameter function in the on-chain assertion contract.
-When submit the parameter, the caller may need to send along an amount of deposit stake.
-Furthermore, the caller may wish to broadcast their parameter to all validators via a messaging system when submitting it online.
+Before a parameter can be utilized in the actual work function or contract, a caller must initially submit it via the submit-parameter function in the on-chain assertion contract.
+When submitting the parameter, the caller need to send a deposit stake in the form of a native token or pay gas fees for storing the parameter.
+This stake is claimed by a validator who finds a counterexample, either in the form of the native token or as a gas refund from releasing the storage as the invalid parameter is deleted.
 
 \textbf{Security Features}: 
-The deposit serves as a deterrent, as in the event of an invalid parameter, the deposit may be forfeited to prevent callers from submitting invalid parameters solving the DoS attack security risk. 
+The deposit serves as a deterrent, as in the event of an invalid parameter, the deposit may be forfeited to prevent callers from submitting such parameters solving the DoS attack security risk.
+
+Upon the submission of a parameter, an event can be emitted, allowing validators to receive updates by monitoring the blockchain for the parameter submission event.
+Additionally, the caller may choose to broadcast their parameter to all validators via a messaging system when submitting it online.
+
 %The work contact can only be invoked by the on-chain validation contract after the parameter has been validated if no counterexample is found.
@@
 This call is subject to specific requirements being met, ensuring that the task is executed only when the verification process has been successfully completed and the parameter is deemed valid, such as a certain amount of time having passed, no counterexample being found, and receiving enough computation proofs.
-If all conditions are met, the actual work is executed, and the record of the parameter may be deleted from memory to free up storage.
-
-By enforcing strict conditions for the execution of the work function or contract based on the outcome of the verification process, the integrity and reliability of the system can be maintained.
+If all conditions are met, the actual work is executed, and in some application, the record of the parameter may be deleted from memory to free up storage.
+
+%By enforcing strict conditions for the execution of the work function or contract based on the outcome of the verification process, the integrity and reliability of the system can be maintained.
 
@@
 This includes the costs per data byte, with non-zero bytes being more expensive than zero bytes.
+
  For Ethereum, for example, these data costs are as follows:
@@
 \begin{itemize}
-    \item The on-chain method has an optional storage cost \( [G_{storage}] \), while the offline method always includes the storage cost \( G_{storage} \).
+    \item The on-chain method has an optional storage cost \( [G_{storage}] \), while the offline method always includes the storage cost \( G_{storage} \). %(but only to store its hash in some case).
 \end{itemize}
@@
 \end{itemize}
-
-\subsubsection*{Comparison}
-
-\begin{itemize}
-    \item \textbf{On-Chain Verification Method (\( G_{on} \))}:
-    \begin{itemize}
-        \item More suited for scenarios where all data and checks must be performed directly on the blockchain.
-        \item Potentially higher cost due to \( n \cdot G_{check} \) if \( n \) (size of the parameter) is large.
-It gets worse when the check is complicated and the parameter is larger, which means \( G_{check} \) is high and \( n \) is large.
-    \end{itemize}
-
-    \item \textbf{Offline Distributed Verification Method (\( G_{off} \))}:
-    \begin{itemize}
-        \item More efficient for large datasets since it reduces the number of checks to \( m \) seeds, where \( m \) is usually much smaller than \( n \).
-        \item Incurs additional costs for \( G_{seed} \) and \( G_{hash} \), but these are often outweighed by the savings from reducing the number of checks.
-        \item The most concern is the cost to store the parameter for the verification process.
-In case the parameter needs to be stored anyway then there is no need to concern, but for the opposite case, this cost needs to be taken into account when estimating the cost of the method.
-Consider storing its hash instead since the hash could still be enough to verify the parameter, but then the \( G_{seed} \) will be increased.
-    \end{itemize}
-\end{itemize}
-
 Let \( G_{base} \) be the sum of the gas costs for submitting the parameter, storing it, and running it:
@@
 % \end{figure}
-Overall, the offline method (\( G_{off} \)) is generally more cost-effective for large parameters as it reduces the number of on-chain checks from \( n \) to 1.
+
+\subsubsection*{Comparison}
+
+\begin{itemize}
+    \item \textbf{On-Chain Verification Method (\( G_{on} \))}:
+    \begin{itemize}
+        \item More suited for scenarios where all data and checks must be performed directly on the blockchain.
+        \item Potentially higher cost due to \( n \cdot G_{check} \) if \( n \) (size of the parameter) is large.
+It gets worse when the check is complicated and the parameter is larger, which means \( G_{check} \) is high and \( n \) is large.
+    \end{itemize}
+
+    \item \textbf{Offline Distributed Verification Method (\( G_{off} \))}:
+    \begin{itemize}
+        \item More efficient for large datasets since it reduces the number of checks. % to \( m \) seeds, where \( m \) is usually much smaller than \( n \).
+        \item Incurs additional costs for \( G_{seed} \) and \( G_{hash} \), but these are often outweighed by the savings from reducing the number of checks.
+        \item The most concern is the cost to store the parameter for the verification process.
+In case the parameter needs to be stored anyway then there is no need to concern, but for the opposite case, this cost needs to be taken into account when estimating the cost of the method.
+Consider storing its hash instead since the hash could still be enough to verify the parameter.
+%, but then the \( G_{seed} \) will be increased.
+    \end{itemize}
+\end{itemize}
+
+Overall, the offline method (\( G_{off} \)) is generally more cost-effective for large parameters as it reduces the number of on-chain checks.
 However, the exact cost-effectiveness depends on the relative sizes of \( n \), the parameter storing gas, and the specific gas costs of \( G_{seed} \), \( G_{hash} \) and \( G_{reward} \).

### 2024-08-01 papers/assertion-contract/assertion_contract_app/paper.tex
Experiments

@@
 \usepackage{comment}
+\usepackage{array}
+\usepackage{booktabs}
 
@@
 \]
-
-%For example, given \( n = 10000 \) and \( p = 0.8 \), the number of seeds \( m \) needed to achieve the desired probability is calculated as follows:
-%\[
-%m = \frac{\ln(1 - 0.8)}{\ln\left(1 - \frac{1}{10000}\right)}
-%\]
-
-%\[
-%m = \frac{\ln(0.2)}{\ln\left(1 - 0.0001\right)}
-%\]
-
-%\[
-%m = \frac{-1.6094}{\ln(0.9999)}
-%\]
-
-%\[
-%m = \frac{-1.6094}{-0.0001}
-%\]
-
-%\[
-%m \approx 16094
-%\]
-
-%Therefore, approximately \( 16094 \) seeds are needed to have an \( 80\% \) chance of finding a counterexample.
 
@@
 
-Figure \ref{fig:gas_compare} shows the gas consumption for both methods.
+Figure \ref{fig:gas_compare} shows the gas consumption for both methods assuming that $G_{base}$ remains unchanged regardless of the parameter size.
 The red line shows the gas consumed by the on-chain verification method, which increases linearly with the size of the parameter.
@@
 \section{Prototype Implementations}
-\note{TODO}
+\subsection{Decentralize Selling Flatform}
+\subsubsection{On-chain verification}
+\subsubsection{Off-chain distributed verification}
+\subsubsection{Gas comperation}
+\begin{table}[h]
+\centering
+\caption{Gas Consumption Comparison}
+\begin{tabular}{c|>{\centering\arraybackslash}p{3cm}|>{\centering\arraybackslash}p{3cm}|c}
+\toprule
+Parameter Size & Line 1 Gas Consumption & Line 2 Gas Consumption & Difference \\
+\midrule
+05  &  504225   &  578196   &  -73971   \\
+10  &  903555   &  908838   &  -5283   \\
+20  &  1842037  &  1804283  &  37754  \\
+30  &  2797283  &  2733927  &  63356  \\
+50  &  4708543  &  4593215  &  115328 \\
+70  &  6714839  &  6545213  &  169626 \\
+100 &  9581470  &  9333977  &  247493 \\
+120 &  11492538 &  11193157 &  299381 \\
+150 &  14359469 &  13981933 &  377536 \\
+170 &  16270716 &  15841101 &  429615 \\
+200 &  19137934 &  18629877 &  508057 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{tikzpicture}
+\begin{axis}[
+    title={Gas Consumption Comparison},
+    xlabel={Parameter Size},
+    ylabel={Gas Consumption},
+    legend pos=north west,
+    grid=major,
+    width=10cm,
+    height=6cm
+]
+
+% Line 1 data
+\addplot[
+    color=blue,
+    mark=*,
+    ]
+    coordinates {
+    (5, 504225) (10, 903555) (20, 1842037) (30, 2797283) (50, 4708543) (70, 6714839) (100, 9581470) (120, 11492538) (150, 14359469) (170, 16270716) (200, 19137934)
+    };
+    \addlegendentry{Centralize}
+
+% Line 2 data
+\addplot[
+    color=red,
+    mark=square*,
+    ]
+    coordinates {
+    (5, 578196) (10, 908838) (20, 1804283) (30, 2733927) (50, 4593215) (70, 6545213) (100, 9333977) (120, 11193157) (150, 13981933) (170, 15841101) (200, 18629877)
+    };
+    \addlegendentry{Decentralize}
+
+\end{axis}
+\end{tikzpicture}
+
+\begin{tikzpicture}
+\begin{axis}[
+    title={Difference in Gas Consumption},
+    xlabel={Parameter Size},
+    ylabel={Difference in Gas Consumption},
+    legend pos=north west,
+    grid=major,
+    width=10cm,
+    height=6cm
+]
+
+% Difference data
+\addplot[
+    color=green,
+    mark=square*,
+    ]
+    coordinates {
+    (5, -73971) (10, -5283) (20, 37754) (30, 63356) (50, 115328) (70, 169626) (100, 247493) (120, 299381) (150, 377536) (170, 429615) (200, 508057)
+    };
+    \addlegendentry{Difference}
+
+\end{axis}
+\end{tikzpicture}
+
 \subsection{Sorted array}

### 2024-08-07 papers/assertion-contract/assertion_contract_app/paper.tex
Some revision

@@
 \usepackage{booktabs}
-
+\usepackage{hyperref}
 \tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
@@
 \end{gather}
-Each validator endeavors to find a counterexample of the assertion using this negation.
+Validators endeavor to find counterexamples of the assertion using this negation.
 Specifically, each validator attempts to find a counterexample by identifying $a \in A$ such that the negation formula is satisfied $\neg P(a)$.
@@
 
-\paragraph{Estimate the number of seeds:} We first estimate the number of seeds needed to find a counterexample with a given expected probability, assuming the worst case where only one validator participates.
+\paragraph{Estimate the number of seeds:} We first estimate the number of seeds needed to find a counterexample with a given expected probability.
+%, assuming the worst case where only one validator participates.
 
@@
 \end{align}
-\paragraph{Find a seed:}
-The sequence of operations to find a seed can be described by the following steps:
-\begin{enumerate}
-\item Generate a random seed $s$: 
+\paragraph{On-chain re-verification:}
+Given a submitted seed $s$: 
 \begin{align}
@@
 where $s$ is a random natural number.
+
+The on-chain contract will recompute to determine whether the submitted seed produces a counterexample, qualifies for a computation reward, or does not qualify for a reward.
+The rechecking process is as follows:
+\begin{enumerate}
 \item Calculate $n$ as the size of the domain $A$: 
@@
 where $\mid A \mid$ denotes the number of elements in the domain $A$.
+%\item Generate a random seed $s$: 
+%\begin{align}
+%s \in \mathbb{N} 
+%\end{align}
+%where $s$ is a random natural number.
 \item Determine $i \in [1, n]$ using the modulo operation:
@@
 \end{enumerate}
-
+\paragraph{Find a seed:}
+The sequence of operations to find a seed can be described in Fig. \ref{fig:find_seed}.
+
+\begin{figure}
+    \centering
 \begin{tikzpicture}[node distance=2cm]
@@
 \end{tikzpicture}
+\caption{Finding a reward seed.}
+\label{fig:find_seed}
+\end{figure}
 
@@
 \end{figure}
+\subsubsection{On-chain assertion contract.}
+While additional functions may exist, the assertion contract must encompass the following two essential functions:
+\begin{itemize}
+\item The \lstinline|submit_parameter| function: Callers utilize this function to submit their parameters for validation. Subsequently, the parameter is distributedly verified by validators.
+\item  The \lstinline|claim_reward| function: This function accepts a parameter and a seed as inputs, yielding a result indicating whether the computation from the seed results in a counterexample, a reward computation, or a non-reward computation.
+\end{itemize}
+\subsubsection{Off-chain assertion contract.}
+Since the off-chain contract runs off-chain, it can be implemented according to the validator's preferences.
+However, the crucial point is that the off-chain contract must use the exact same \lstinline|claim_reward| function when attempting to find a counterexample or a computation proof.
+Additionally, it should support a function that assists the validator in finding a seed to earn a reward.
+\subsubsection{Storage.}
+When a parameter is submitted for verification, the following information should be stored:
+\begin{itemize}
+\item Parameter: this includes the parameter itself.
+In cases where storing the parameter on-chain is impractical because of its size, it could be possible to store only its hash.
+Despite this, the hash remains sufficient for validation.
+%\item Caller Address: This identifies the address of the caller who submitted the parameter.
+It serves purposes such as tracking submissions, preventing callers from resubmitting parameters, or preventing callers from claiming rewards for their own submitted parameters.
+\item Timestamp: this indicates the approximate time when the parameter was submitted. This information is used to prevent caller exploitation security risks as explained above.
+\end{itemize}
+
+In some applications, multiple computational proofs may be allowed.
+There are a record to monitor the progress of the parameter's verification.
+This record is crucial for determining when a work function can be invoked for a given parameter or when it should be discarded.
+The verification status records a counterexample and reward computations found.
+For that, it should include the following details of the addresses of the validators and the random number $r$ used in the verification process.
+
 \subsubsection{Calculate seed.}
@@
 \end{itemize}
-\subsubsection{On-chain assertion contract.}
-While additional functions may exist, the assertion contract must encompass the following two essential functions:
-\begin{itemize}
-\item The \lstinline|submit_parameter| function: Callers utilize this function to submit their parameters for validation. Subsequently, the parameter is distributedly verified by validators.
-\item  The \lstinline|claim_reward| function: This function accepts a parameter and a seed as inputs, yielding a result indicating whether the computation from the seed results in a counterexample, a reward computation, or a non-reward computation.
-\end{itemize}
-\subsubsection{Off-chain assertion contract.}
-Since the off-chain contract runs off-chain, it can be implemented according to the validator's preferences.
-However, the crucial point is that the off-chain contract must use the exact same \lstinline|claim_reward| function when attempting to find a counterexample or a computation proof.
-Additionally, it should support a function that assists the validator in finding a seed to earn a reward.
-\subsubsection{Storage.}
-When a parameter is submitted for verification, the following information should be stored:
-\begin{itemize}
-\item Parameter: this includes the parameter itself.
-In cases where storing the parameter on-chain is impractical because of its size, it could be possible to store only its hash.
-Despite this, the hash remains sufficient for validation.
-%\item Caller Address: This identifies the address of the caller who submitted the parameter.
-It serves purposes such as tracking submissions, preventing callers from resubmitting parameters, or preventing callers from claiming rewards for their own submitted parameters.
-\item Timestamp: this indicates the approximate time when the parameter was submitted. This information is used to prevent caller exploitation security risks as explained above.
-\end{itemize}
-
-In some applications, multiple computational proofs may be allowed.
-There are a record to monitor the progress of the parameter's verification.
-This record is crucial for determining when a work function can be invoked for a given parameter or when it should be discarded.
-The verification status records a counterexample and reward computations found.
-For that, it should include the following details of the addresses of the validators and the random number $r$ used in the verification process.
 
@@
 However, the exact cost-effectiveness depends on the relative sizes of \( n \), the parameter storing gas, and the specific gas costs of \( G_{seed} \), \( G_{hash} \) and \( G_{reward} \).
-\section{Domain Specification Language for Assertion}
-\note{To discuss: if it make sense to design}
-\section{Converter - Generating an Assertion Contracts} 
-\note{To discuss: if it make sense to implement}
+%\section{Domain Specification Language for Assertion}
+%\note{To discuss: if it make sense to design}
+%\section{Converter - Generating an Assertion Contracts} 
+%\note{To discuss: if it make sense to implement}
 \section{Prototype Implementations}
 \subsection{Decentralize Selling Flatform}
+The Decentralized Selling Platform contract is a decentralized application that allows users to create their own selling platforms, list items for sale, and facilitate transactions between buyers and sellers.
+
+The \texttt{DecentralizedSellingPlatform} contract provides a structured way for users to manage and trade items in a decentralized manner.
+Sellers can create platforms, list items, and set prices, while buyers can purchase items directly from these platforms.
+%The use of custom errors and events helps in efficient gas usage and provides transparency and traceability for transactions and updates within the platform.
+
+Each seller owns a selling flatform, which includes a list of items. Each item includes:
+\begin{itemize}
+    \item \texttt{name}: The name of the item.
+    \item \texttt{forSale}: A boolean indicating whether the item is available for sale.
+    \item \texttt{price}: The price of the item in wei.
+    \item \texttt{owner}: The address of the item's owner.
+\end{itemize}
+
+\texttt{sellingPlatform} maps each seller's address to an array of their items.
+
+The contract contains the following main functions for selling and buying items from a flatform:
+
+\begin{itemize}
+ \item \texttt{createSellingPlatform(Item[] memory \_items)}:
+Allows users to create a selling platform if they pay the minimum fee and the items are sorted.
+
+ \item \texttt{buyItem(address \_sellerAddress, string memory \_name)}:
+Allows users to buy an item if it is for sale and they pay the required price. Transfers ownership and funds appropriately.
+
+ \item \texttt{addNewItem(Item calldata \_item)}:
+Allows sellers to add a new item to their platform, ensuring it doesn't already exist and is inserted in the correct order.
+
+ \item \texttt{setForSale(address \_sellerAddress, string memory \_name, bool \_forSale)}:
+Allows item owners to update the for sale status of their items.
+ \item \texttt{setPrice(address \_sellerAddress, string memory \_name, uint \_price)}:
+Allows item owners to update the price of their items.
+\item \texttt{listSellingItems(address sellerAddress)}:
+Lists all items from a seller's platform.
+\end{itemize}
+
+The most important assertion of the contract is that the list of items have to be sorted by the item name when a seller want to create their selling flatform.
+All of other function workd with the assumiion that the list is sorted.
+So if the list is not sorted all these functions are failed on operating.´
 \subsubsection{On-chain verification}
+We first implement the contract with the on-chain verification. Then we need to define a function to check if a list of item is sorted by their name.
+
+Namely, the function \texttt{isSorted(Item[] memory \_items)} checks if an array of items is sorted by name. This function basicly iter over the list to check if all the elents is at the plates.
+
+\begin{lstlisting}[numbers=none]
+   function isSorted(Item[] memory _items) internal pure returns (bool) {
+        for (uint256 i = 1; i < _items.length; i++) {
+            if (compareStrings(_items[i - 1].name, _items[i].name) == 1) {
+                return false;
+            }
+        }
+        return true;
+    }
+\end{lstlisting}
+
+The function \texttt{createSellingPlatform(Item[] memory \_items)}  then calls this function to grantee that the list is sorted before create the flatform.
+\begin{lstlisting}[numbers=none]
+
+     if (!isSorted(_items)) revert ListItemIsNotSorted();
+\end{lstlisting}    
+ Below is a detailed description of its functionality and components:
+
+\paragraph{Data Structures}
+\begin{itemize}
+\item Item Structure
+
+\item sellingPlatform maps each seller's address to an array of their items.
+\begin{itemize}
+    \item Maps each seller's address to an array of their items.
+\end{itemize}
+\end{itemize}
+\paragraph{Errors}
+
+The contract defines several custom errors to handle specific conditions efficiently, reducing gas usage compared to using \texttt{require} with error strings:
+\begin{itemize}
+    \item \texttt{ListItemIsNotSorted}: The list of items is not sorted by name.
+    \item \texttt{NotItemOwner}: Thrown when the caller is not the owner of the item.
+    \item \texttt{NotForSale}: The item is not for sale.
+    \item \texttt{InsufficientAmount}: The sent amount is less than the item's price.
+    \item \texttt{NotExistingItem}: The item does not exist.
+    \item \texttt{ItemAlreadyExists}: The item already exists.
+    \item \texttt{InvalidItemData}: The item data is invalid.
+    \item \texttt{NotEnoughFee}: The amount is less than the minimum fee.
+\end{itemize}
+
+\paragraph{Events}
+
+The contract defines several events to log important actions:
+\begin{itemize}
+    \item \texttt{ItemAdded}: A new item is added.
+    \item \texttt{ItemBought}: An item is bought.
+    \item \texttt{ItemForSaleUpdated}: An item's for sale status is updated.
+    \item \texttt{ItemPriceUpdated}: An item's price is updated.
+\end{itemize}
+
+\paragraph{State Variables}
+
+\begin{itemize}
+    \item \texttt{minimum\_fee}: The minimum fee required to create a selling platform.
+    \item \texttt{owner}: The address of the contract owner.
+\end{itemize}
+
+\paragraph{Constructor}
+
+Initializes the contract, setting the owner and the initial minimum fee.
+
+\paragraph{Modifiers}
+
+\begin{itemize}
+    \item \texttt{onlyOwner}: Ensures that only the contract owner can execute certain functions.
+\end{itemize}
+
+\paragraph{Functions}
+
+\begin{itemize}
+ \item \texttt{setFee(uint256 \_minimum\_fee)}: Allows the owner to set the minimum fee for creating a selling platform.
+
+ \item \texttt{compareStrings(string memory a, string memory b)}:
+Compares two strings lexicographically.
+
+ \item  \texttt{isSorted(Item[] memory \_items)}:
+Checks if an array of items is sorted by name.
+
+ \item \texttt{createSellingPlatform(Item[] memory \_items)}:
+Allows users to create a selling platform if they pay the minimum fee and the items are sorted.
+
+ \item \texttt{buyItem(address \_sellerAddress, string memory \_name)}:
+Allows users to buy an item if it is for sale and they pay the required price. Transfers ownership and funds appropriately.
+
+ \item \texttt{addNewItem(Item calldata \_item)}:
+Allows sellers to add a new item to their platform, ensuring it doesn't already exist and is inserted in the correct order.
+
+ \item \texttt{setForSale(address \_sellerAddress, string memory \_name, bool \_forSale)}:
+Allows item owners to update the for sale status of their items.
+ \item \texttt{setPrice(address \_sellerAddress, string memory \_name, uint \_price)}:
+Allows item owners to update the price of their items.
+\item \texttt{listSellingItems(address sellerAddress)}:
+Lists all items from a seller's platform.
+\end{itemize}
+
 \subsubsection{Off-chain distributed verification}
+\subsection{DecentralizedSellingPlatform Smart Contract}
+
+The Solidity smart contract, \texttt{DecentralizedSellingPlatform}, extends an imported \texttt{SellingPlatform} contract.
+It facilitates decentralized item trading with various features such as adding, buying, and listing items, as well as parameter submission for distributed verification.
+Below is an overview of its components and functionality:
+
+\subsubsection{State Variables}
+\begin{itemize}
+    \item \texttt{HASH\_MAX}: A constant representing the maximum possible value for a 256-bit integer.
+    \item \texttt{probability}, \texttt{minimumDeposit}, \texttt{rewardPrice}, \texttt{counterexamplePrice}: Variables related to the verification and reward mechanism.
+    \item \texttt{owner}: The address of the contract owner.
+\end{itemize}
+
+\subsubsection{Constructor}
+Initializes the contract by setting the owner to the deployer and setting default values for probability and minimum deposit.
+
+\subsubsection{Modifiers}
+\begin{itemize}
+    \item \texttt{onlyOwner}: Ensures that only the contract owner can execute certain functions.
+    \item \texttt{onlyVerified}: Ensures the caller is verified.
+    \item \texttt{notVerified}: Ensures the caller is not verified.
+\end{itemize}
+
+\subsubsection{Custom Errors}
+Various custom errors like \texttt{NotItemOwner}, \texttt{NotForSale}, \texttt{InsufficientAmount}, etc., to handle specific failure cases.
+
+\subsubsection{Events}
+\begin{itemize}
+    \item \texttt{ParameterSubmitted}, \texttt{ItemAdded}, \texttt{ItemBought}, \texttt{ItemForSaleUpdated}, \texttt{ItemPriceUpdated}, \texttt{ProofVerified}: These events are emitted during corresponding actions within the contract.
+\end{itemize}
+
+\subsubsection{Core Functions}
+\begin{itemize}
+    \item \texttt{setProbability}: Allows the owner to set the probability value.
+    \item \texttt{setFee}: Allows the owner to set the minimum deposit, reward price, and counterexample price.
+    \item \texttt{calculateTargetHash}, \texttt{calculateM}, \texttt{ln}: Internal functions to calculate target hashes and other related computations for verification.
+    \item \texttt{submitParameter}: Allows sellers to submit their items for verification, ensuring a deposit is made.
+    \item \texttt{claimReward}: Allows validators to claim rewards if they find a proof or counterexample during verification.
+    \item \texttt{buyItem}: Allows a verified buyer to purchase an item from a seller.
+    \item \texttt{addNewItem}: Allows verified sellers to add new items to their selling platform.
+    \item \texttt{setForSale}: Allows item owners to set the sale status of their items.
+    \item \texttt{setPrice}: Allows item owners to set the price of their items.
+    \item \texttt{listSellingItems}: Returns the list of items a seller has listed for sale.
+\end{itemize}
+
+\subsubsection{Verification Process}
+\begin{itemize}
+    \item \texttt{submitParameter}: Sellers submit items for verification.
+    \item \texttt{claimReward}: Validators can claim rewards based on the verification result.
+If a counterexample is found, the seller's platform is reset and the validator is rewarded.
+If the proof is valid, the seller's platform is marked as verified.
+\end{itemize}
+
+\subsubsection{Error Handling}
+Various custom errors ensure specific and clear error messages are thrown for different failure cases, enhancing the contract's robustness.
+
+\subsubsection{Summary}
+The \texttt{DecentralizedSellingPlatform} contract provides a comprehensive framework for decentralized item trading with built-in verification and reward mechanisms, ensuring secure and fair transactions between sellers and buyers.
+
 \subsubsection{Gas comperation}
@@
 \toprule
-Parameter Size & Line 1 Gas Consumption & Line 2 Gas Consumption & Difference \\
+Parameter Size & On-chain & Off-chain & Gas save \\
 \midrule
@@
     };
-    \addlegendentry{Centralize}
+    \addlegendentry{On-chain}
 
@@
     };
-    \addlegendentry{Decentralize}
+    \addlegendentry{Off-chain}
 
@@
 \begin{axis}[
-    title={Difference in Gas Consumption},
+    title={Amount of Gas Save for off-chain to on-chain },
     xlabel={Parameter Size},
-    ylabel={Difference in Gas Consumption},
+    ylabel={Gas Save},
     legend pos=north west,
@@
     };
-    \addlegendentry{Difference}
+    \addlegendentry{Off-chain}
 
@@
 \end{tikzpicture}
-
+\begin{comment}
 \subsection{Sorted array}
@@
 \section{Cost Analysis}
+\end{comment}
 
@@
 \section{Conclusion}
-
+\section{Appendix}
+\begin{lstlisting}[numbers=none]
+// SPDX-License-Identifier: MIT
+pragma solidity ^0.8.8;
+
+contract DecentralizedSellingPlatform {
+    // Structure to represent an item
+    struct Item {
+        string name;
+        bool forSale;
+        uint256 price;
+        address payable owner;
+    }
+
+    // Mapping to keep track of selling platforms for each seller
+    mapping(address => Item[]) public sellingPlatform;
+
+    // Error declarations
+    error ListItemIsNotSorted(); // When the item list is not sorted by item name
+    error NotItemOwner(); // When the caller is not the owner of the item
+    error NotForSale(); // When the item is not for sale
+    error InsufficientAmount(); // When the sent amount is less than the item price
+    error NotExistingItem(); // When the item does not exist
+    error ItemAlreadyExists(); // When the item already exists
+    error InvalidItemData(); // When the item data is invalid
+    error NotEnoughFee(); // When the deposit is less than expected
+
+    // Event declarations
+    event ItemAdded(address indexed seller, string name, uint256 price);
+    event ItemBought(address indexed buyer, address indexed seller, string name, uint256 price);
+    event ItemForSaleUpdated(address indexed seller, string name, bool forSale);
+    event ItemPriceUpdated(address indexed seller, string name, uint256 price);
+
+    uint256 public minimum_fee;
+    address public owner;
+
+    // Constructor to set the contract owner and initial minimum fee
+    constructor(uint256 _minimum_fee) {
+        owner = msg.sender;
+        minimum_fee = _minimum_fee;
+    }
+
+    // Modifier to restrict access to owner-only functions
+    modifier onlyOwner() {
+        require(msg.sender == owner, "Caller is not the owner");
+        _;
+    }
+
+    // Function to set the minimum fee for creating a selling platform
+    function setFee(uint256 _minimum_fee) public onlyOwner {
+        minimum_fee = _minimum_fee;
+    }
+
+    // Function to compare two strings lexicographically
+    function compareStrings(string memory a, string memory b) internal pure returns (int) {
+        bytes memory bytesA = bytes(a);
+        bytes memory bytesB = bytes(b);
+        uint minLength = bytesA.length;
+        if (bytesB.length < minLength) {
+            minLength = bytesB.length;
+        }
+
+        for (uint i = 0; i < minLength; i++) {
+            if (bytesA[i] < bytesB[i]) {
+                return -1;
+            } else if (bytesA[i] > bytesB[i]) {
+                return 1;
+            }
+        }
+
+        if (bytesA.length < bytesB.length) {
+            return -1;
+        } else if (bytesA.length > bytesB.length) {
+            return 1;
+        } else {
+            return 0;
+        }
+    }
+
+    // Internal function to check if an array of items is sorted by item name
+    function isSorted(Item[] memory _items) internal pure returns (bool) {
+        for (uint256 i = 1; i < _items.length; i++) {
+            if (compareStrings(_items[i - 1].name, _items[i].name) == 1) {
+                return false;
+            }
+        }
+        return true;
+    }
+
+    // Function to create a selling platform with a list of items
+    function createSellingPlatform(Item[] memory _items) public payable {
+        if (msg.value < minimum_fee) revert NotEnoughFee();
+        if (!isSorted(_items)) revert ListItemIsNotSorted();
+        for (uint i = 0; i < _items.length; i++) {
+            sellingPlatform[msg.sender].push(_items[i]);
+        }
+    }
+
+    // Function to buy an item from a seller's platform using the item name
+    function buyItem(address _sellerAddress, string memory _name) public payable {
+        Item[] storage items = sellingPlatform[_sellerAddress];
+        for (uint256 i = 0; i < items.length; i++) {
+            if (compareStrings(items[i].name, _name) == 0) {
+                if (!items[i].forSale) revert NotForSale();
+                if (msg.value < items[i].price) revert InsufficientAmount();
+                address payable oldOwner = items[i].owner;
+                items[i].owner = payable(msg.sender);
+                items[i].forSale = false;
+                oldOwner.transfer(msg.value);
+                emit ItemBought(msg.sender, _sellerAddress, _name, items[i].price);
+                return;
+            }
+        }
+        revert NotExistingItem();
+    }
+
+    // Function to add a new item to the seller's platform
+    function addNewItem(Item calldata _item) public {
+        if (bytes(_item.name).length <= 0 || _item.price < 0) {revert InvalidItemData();}
+        Item[] storage items = sellingPlatform[msg.sender];
+        uint256 i = 0;
+
+        // Find the correct insertion point
+        while (i < items.length && compareStrings(_item.name, items[i].name) > 0) {
+            i++;
+        }
+
+        // Ensure the item doesn't already exist
+        if (i < items.length && compareStrings(_item.name, items[i].name) == 0) {
+            revert ItemAlreadyExists();
+        }
+
+        // Shift items to the right to make space for the new item
+        items.push();
+        for (uint256 j = items.length - 1; j > i; j--) {
+            items[j] = items[j - 1];
+        }
+
+        // Insert the new item
+        items[i] = _item;
+        emit ItemAdded(msg.sender, _item.name, _item.price);
+    }
+
+    // Function to set the for sale status of an item by the item owner
+    function setForSale(address _sellerAddress, string memory _name, bool _forSale) public {
+        Item[] storage items = sellingPlatform[_sellerAddress];
+        uint256 i = 0;
+        while (i < items.length && compareStrings(_name, items[i].name) > 0) {
+            i++;
+        }
+        if (i >= items.length || compareStrings(_name, items[i].name) != 0) revert NotExistingItem();
+        if (items[i].owner != msg.sender) revert NotItemOwner();
+        items[i].forSale = _forSale;
+        emit ItemForSaleUpdated(_sellerAddress, _name, _forSale);
+    }
+
+    // Function to set the price of an item by the item owner
+    function setPrice(address _sellerAddress, string memory _name, uint _price) public {
+        Item[] storage items = sellingPlatform[_sellerAddress];
+        uint256 i = 0;
+        while (i < items.length && compareStrings(_name, items[i].name) > 0) {
+            i++;
+        }
+        if (i >= items.length || compareStrings(_name, items[i].name) != 0) revert NotExistingItem();
+        if (items[i].owner != msg.sender) revert NotItemOwner();
+        items[i].price = _price;
+        emit ItemPriceUpdated(_sellerAddress, _name, _price);
+    }
+
+    // Function to list all items from a seller's platform
+    function listSellingItems(address sellerAddress) public view returns (Item[] memory) {
+        return sellingPlatform[sellerAddress];
+    }
+}
+
+\end{lstlisting}
+
+\begin{lstlisting}[numbers=none]
+// SPDX-License-Identifier: MIT
+pragma solidity ^0.8.8;
+
+contract SellingPlatform {
+
+    // Structure to represent an item
+    struct Item {
+        string name;
+        bool forSale;
+        uint256 price;
+        address payable owner;
+    }
+
+    // Structure to represent a parameter, including a list of items, a timestamp, and a verification status
+    struct Parameter {
+        Item[] items;
+        uint timestamp;
+        bool verified;
+    }
+
+    // Mapping to store the selling platform data for each address
+    mapping(address => Parameter) public sellingPlatform;
+
+    enum ProofResult {NonReward, Reward, Counterexample}
+
+    // Function to compare two strings lexicographically
+    function compareStrings(string memory a, string memory b) public pure returns (int) {
+        bytes memory bytesA = bytes(a);
+        bytes memory bytesB = bytes(b);
+        uint minLength = bytesA.length;
+        if (bytesB.length < minLength) {
+            minLength = bytesB.length;
+        }
+
+        for (uint i = 0; i < minLength; i++) {
+            if (bytesA[i] < bytesB[i]) {
+                return -1;
+            } else if (bytesA[i] > bytesB[i]) {
+                return 1;
+            }
+        }
+
+        if (bytesA.length < bytesB.length) {
+            return -1;
+        } else if (bytesA.length > bytesB.length) {
+            return 1;
+        } else {
+            return 0;
+        }
+    }
+
+    // Function to verify a proof and return a status code
+    // Returns:
+    // 0 if it is a non-reward computational proof,
+    // 1 if it is a reward computation proof,
+    // 2 if it is a counterexample.
+    function verify_proof(
+        Item[] memory _items,
+        uint _seed,
+        address _validator,
+        uint _timestamp,
+        uint _target
+    ) internal pure returns (ProofResult) {
+        uint n = _items.length - 1; 
+        uint addrToNumber = uint160(_validator);
+        uint i = (_seed + addrToNumber + _timestamp) % n;
+
+        int c = compareStrings(_items[i].name, _items[i + 1].name);
+        if (c == 0)  {
+            return ProofResult.Counterexample;
+        } else {
+            uint current_hash = uint(
+                keccak256(abi.encodePacked(_seed, _validator, _timestamp, _items[i].name, _items[i + 1].name))
+            );
+            if (current_hash <= _target) {
+                return ProofResult.Reward;
+            }
+        }
+        return ProofResult.NonReward;        
+    }   
+}
+
+\end{lstlisting}
+
+\begin{lstlisting}[numbers=none]
+// SPDX-License-Identifier: MIT
+pragma solidity ^0.8.8;
+
+import "./SellingPlatform.sol";
+
+contract DecentralizedSellingPlatform is SellingPlatform {
+    // Custom errors
+    error NotItemOwner(); // When the caller is not the owner of the item
+    error NotForSale(); // When the item is not for sale
+    error InsufficientAmount(); // When the sent amount is less than the item price
+    error NotExistingItem(); // When the item does not exist
+    error ItemAlreadyExists(); // When the item already exists
+    error InvalidItemData(); // When the item data is invalid
+    error NotEnoughDeposit(); // When the deposit is less than expected
+    error AlreadyVerified(); // When the parameter is already verified
+    error NotVerified(); // When the parameter has not yet been verified
+    error NotOwner(); // When the sender is not the owner of the contract
+    error InvalidProbability(); // When a probability is invalid
+    error NotReasonableFee(); //When the fee is set up not reasonale
+    // Event declarations
+    event ParameterSubmitted(address indexed seller, uint timestamp);
+    event ItemAdded(address indexed seller, string name, uint256 price);
+    event ItemBought(address indexed buyer, address indexed seller, string name, uint256 price);
+    event ItemForSaleUpdated(address indexed seller, string name, bool forSale);
+    event ItemPriceUpdated(address indexed seller, string name, uint256 price);
+    event ProofVerified(address indexed seller, ProofResult result);
+
+    uint256 constant HASH_MAX = type(uint256).max; // 2^256 - 1
+    uint256 public probability;
+    uint256 public minimumDeposit;
+    uint256 public rewardPrice;
+    uint256 public counterexamplePrice;
+    address public owner;
+
+    constructor() {
+        owner = msg.sender;
+        probability = 80;
+        minimumDeposit = 400 gwei;
+        rewardPrice = 100 gwei;
+        counterexamplePrice = 200 gwei;
+    }
+    // Only owner
+    modifier onlyOwner {
+        if (msg.sender != owner) { revert NotOwner(); }
+        _;
+    }
+    // Only verified
+    modifier onlyVerified(address _sellerAddress) {
+        if (!sellingPlatform[_sellerAddress].verified) { revert NotVerified(); }
+        _;
+    }
+    // Only not verified
+    modifier notVerified(address _sellerAddress) {
+        if (sellingPlatform[_sellerAddress].verified) { revert AlreadyVerified(); }
+        _;
+    }
+    // Function for the owner to set up the probability
+    function setProbability(uint256 _probability) public onlyOwner {
+        if (_probability > 100) revert InvalidProbability(); 
+        probability = _probability;
+    }
+    // Function for the owner to set up the minimum deposit
+    function setFee(uint256 _minimumDeposit, uint256 _rewardPrice, uint256 _counterexamplePrice) public onlyOwner {
+        if (_minimumDeposit < _rewardPrice + _counterexamplePrice) revert NotReasonableFee();
+        minimumDeposit = _minimumDeposit;
+        rewardPrice = _rewardPrice;
+        counterexamplePrice = _counterexamplePrice;
+    }
+    // Function to calculate the target hash
+    function calculateTargetHash(uint256 n, uint256 pNumerator, uint256 pDenominator)
+        internal
+        pure
+        returns (uint256)
+    {
+        uint256 p = (pNumerator * 1e18) / pDenominator;
+        uint256 m = calculateM(n, p);
+        return HASH_MAX / m;
+    }
+    // Function to calculate the number of seeds required
+    function calculateM(uint256 n, uint256 p) internal pure returns (uint256) {
+        uint256 ln1MinusP = ln(1e18 - p);
+        uint256 lnNMinus1DivN = ln((n - 1) * 1e18 / n);
+        uint256 m = (ln1MinusP * 1e18) / lnNMinus1DivN;
+        return m / 1e18; // Adjust for precision
+    }
+    // Function to calculate ln
+    function ln(uint256 x) internal pure returns (uint256) {
+        uint256 y = x;
+        uint256 result = 0;
+        while (y > 1e18) {
+            y >>= 1;
+            result += 693147180000000000; // ln(2) * 1e18
+        }
+        return result;
+    }
+    // Function for sellers to submit their parameters, which is a list of items for distributed verification process
+    function submitParameter(Item[] calldata _items) public payable {
+        if (msg.value < minimumDeposit) revert NotEnoughDeposit();
+        Item[] storage items = sellingPlatform[msg.sender].items;
+        for (uint i = 0; i < _items.length; i++) {
+            items.push(_items[i]);
+        }
+        sellingPlatform[msg.sender].timestamp = block.timestamp;
+        sellingPlatform[msg.sender].verified = false;
+        emit ParameterSubmitted(msg.sender, block.timestamp);
+    }
+    // Function for validators to claim their rewards when they find a computation proof or a counterexample
+    function claimReward(address _sellerAddress, uint _seed) public notVerified(_sellerAddress) {
+        Item[] memory items = sellingPlatform[msg.sender].items;
+        uint target = calculateTargetHash(items.length, probability, 100);
+        ProofResult result = verify_proof(items, _seed, msg.sender, sellingPlatform[_sellerAddress].timestamp, target);
+
+        if (result == ProofResult.Counterexample) {
+            emit ProofVerified(_sellerAddress, result);
+            delete sellingPlatform[_sellerAddress];
+            payable(msg.sender).transfer(counterexamplePrice);
+        } else if (result == ProofResult.Reward) {
+            emit ProofVerified(_sellerAddress, result);
+            sellingPlatform[_sellerAddress].verified = true;
+            payable(msg.sender).transfer(rewardPrice);
+        }
+    }
+    // Function to buy an item from a seller's platform using the item name
+    function buyItem(address _sellerAddress, string memory _name) public payable onlyVerified(_sellerAddress) {
+        Item[] storage items = sellingPlatform[_sellerAddress].items;
+        for (uint256 i = 0; i < items.length; i++) {
+            if (compareStrings(items[i].name, _name) == 0) {
+                if (!items[i].forSale) revert NotForSale();
+                if (msg.value < items[i].price) revert InsufficientAmount();
+                address payable oldOwner = items[i].owner;
+                items[i].owner = payable(msg.sender);
+                items[i].forSale = false; // Mark item as not for sale after purchase
+                oldOwner.transfer(msg.value);
+                emit ItemBought(msg.sender, _sellerAddress, _name, items[i].price);
+                return;
+            }
+        }
+        revert NotExistingItem();
+    }
+    // Function for the seller to add a new item to the seller's platform
+    function addNewItem(Item calldata _item) public onlyVerified(msg.sender) {
+        if (bytes(_item.name).length <= 0 || _item.price < 0) {revert InvalidItemData();}
+        Item[] storage items = sellingPlatform[msg.sender].items;
+        uint256 i = 0;
+
+        while (i < items.length && compareStrings(_item.name, items[i].name) > 0) {
+            i++;
+        }
+
+        if (i < items.length && compareStrings(_item.name, items[i].name) == 0) {
+            revert ItemAlreadyExists();
+        }
+
+        items.push();
+        for (uint256 j = items.length - 1; j > i; j--) {
+            items[j] = items[j - 1];
+        }
+
+        items[i] = _item;
+        emit ItemAdded(msg.sender, _item.name, _item.price);
+    }
+    // Function for the owner of the item to set the for sale status of an item by the item owner
+    function setForSale(address _sellerAddress, string memory _name, bool _forSale) public onlyVerified(_sellerAddress) {
+        Item[] storage items = sellingPlatform[_sellerAddress].items;
+        uint256 i = 0;
+        while (i < items.length && compareStrings(_name, items[i].name) > 0) {
+            i++;
+        }
+        if (i >= items.length || compareStrings(_name, items[i].name) != 0) revert NotExistingItem();
+        if (items[i].owner != msg.sender) revert NotItemOwner();
+        items[i].forSale = _forSale;
+        emit ItemForSaleUpdated(_sellerAddress, _name, _forSale);
+    }
+    // Function for the owner of an item to set the price of an item by the item owner
+    function setPrice(address _sellerAddress, string memory _name, uint _price) public onlyVerified(_sellerAddress) {
+        Item[] storage items = sellingPlatform[_sellerAddress].items;
+        uint256 i = 0;
+        while (i < items.length && compareStrings(_name, items[i].name) > 0) {
+            i++;
+        }
+        if (i >= items.length || compareStrings(_name, items[i].name) != 0) revert NotExistingItem();
+        if (items[i].owner != msg.sender) revert NotItemOwner();
+        items[i].price = _price;
+        emit ItemPriceUpdated(_sellerAddress, _name, _price);
+    }
+    // Function to reveal the list of items from a seller's platform
+    function listSellingItems(address sellerAddress) public view returns (Item[] memory) {
+        return sellingPlatform[sellerAddress].items;
+    }
+}
+
+\end{lstlisting}
 %\newpage
@@
 Since the hash involves $\pi_{P_{a}}$, the validator needs to execute the condition check to find a reward computation.
+
 \newpage
@@
 \bibliography{bio}
+
 \end{document}

### 2024-08-08 papers/assertion-contract/assertion_contract_app/paper.tex
some revision made

@@
 The explicit assertion would be
-\begin{gather}\label{eq:1}
+\begin{gather}\label{eq:1a}
   (\forall k) (0\le k <49) \Rightarrow a[k] \le a[k+1]
@@
 \begin{gather}
-  \label{eq:1}
+  \label{eq:1b}
 \forall a \in A. P_{a}
@@
 \label{sec:distributed-assertion-verification}
-\subsection{Distributed Verification Approach}
+\subsection{Off-chain Distributed Verification Approach}
 We propose a novel approach for verifying parameter assertions in smart contracts on the blockchain.
@@
 
-The negation of the assertion is represented by the existential quantifier formulas:
+Assertions are checked off-chain, and only the results of these checks (indicating whether any assertion was violated) are submitted and re-verified to the blockchain.
+This reduces the computational load on the blockchain while ensuring the integrity of the contract.
+
+The outline of our approach is as follows:
+\begin{enumerate}
+\item Determinte the negation fomular of an assertion: The negation of the assertion \ref{eq:3} is represented by the existential quantifier formulas:
 
 \begin{gather}
-\label{eq:3}
+\label{eq:5}
 \neg \left( \bigwedge_{a \in A} P(a) \right) \equiv \exists a \in A. \neg P(a)
@@
 
-And for multiple domains, it is as follows:
+And for multiple domains \ref{eq:4}, it is as follows:
 
 \begin{gather}
-\label{eq:4}
+\label{eq:6}
 \neg \left( \bigwedge_{a \in A} \bigwedge_{b \in B} \dots P(a, b, \dots) \right) \equiv \exists a \in A, \exists b \in B, \dots . \neg P(a, b, \dots)
 \end{gather}
-Validators endeavor to find counterexamples of the assertion using this negation.
+\item Off-chain verification: Validators endeavor to find counterexamples of the assertion using this negation off-chain.
 Specifically, each validator attempts to find a counterexample by identifying $a \in A$ such that the negation formula is satisfied $\neg P(a)$.
-When a counterexample is found, the validator submits it, which is then re-verified on-chain.
-
-The assertions are checked off-chain, and only the results of these checks (whether any assertion was violated) are submitted to the blockchain.
-This reduces the computational load on the blockchain while ensuring the integrity of the contract.
+\item On-chain re-verification: When a counterexample is found, the validator submits it, which is then re-verified on-chain. 
+\end{enumerate}
 
@@
 Since only some specific points are checked on-chain, the amount of gas required for the computation to check the counterexample is likely to be significantly less than verifying the entire assertion directly on-chain.
-
-\subsection{Proof-of-work-based Incentivization}
+\subsection{Proof-of-Work-Based Incentivization Mechanism}
 Finding a counterexample is rewarded, incentivizing validators but at the cost of computing resources.
@@
 
-We propose a proof-of-work-based incentivization method where validators are rewarded for discovering counterexamples, and others are rewarded for their computational efforts.
+We propose a proof-of-work-based incentivization mechanism where validators are rewarded for discovering counterexamples, and others are rewarded for their computational efforts.
 This approach encourages participation in the distributed verification process, ensuring thorough validation even without the discovery of counterexamples.
 
-A significant concern arises regarding how to recheck the counterexample and ensure that validators perform the verification computation off-chain if no counterexample is found.
+A significant concern arises regarding how to recheck the counterexample and a computation efforts on-chain and ensure that validators perform the verification computation off-chain if no counterexample is found.
 \subsubsection{Outlines}
-Our proposed proof-of-work-based incentivization method is outlined as follows:
+Our proposed proof-of-work-based incentivization mechanism is outlined as follows:
 \begin{itemize}
@@
 \item The objective of the validator is to find a counterexample or a computation proof that is smaller than or equal to the target hash \( t \).
-\item The computation of the negation formula is integrated into the computational proof to ensure that the validators cannot produce the proof without executing a negation check.
+\item The computation of the negation formula is integrated into a computational proof to ensure that the validators cannot produce the proof without executing a negation check.
 \end{itemize}
@@
 Let \( n \) denote the size of the domain \( A \). 
+\begin{align}
+n = |A|
+\end{align}
+where $\mid A \mid$ denotes the number of elements in the domain $A$.
+
 Each number \( i \) in the range \([1, n]\) corresponds to an element in \( A \). 
+\begin{align}
+a=A[i]
+\end{align}
+where $A[i]$ denotes the $i$-th element in $A$.
+
 The seed \( s \) is a random number, and we can reduce it modulo \( n \) to obtain \( i \), which is associated with an element \( a \) in \( A \).
+\begin{align}
+i = (s \mod n) + 1
+\end{align}
 
@@
 \]
-\paragraph{Conduct a computation proof:} The computation of the negation formula is integrated into a computational proof to ensure that the validators cannot produce the proof without executing a negation check.
+\paragraph{Conduct a computation hash:} The computation of the negation formula is integrated into a computational proof to ensure that the validators cannot produce the proof without executing a negation check.
 
@@
 \end{align}
-\paragraph{On-chain re-verification:}
+\subsubsection{On-chain re-verification}
 Given a submitted seed $s$: 
@@
 \begin{enumerate}
-\item Calculate $n$ as the size of the domain $A$: 
-\begin{align}
-n = |A|
-\end{align}
-where $\mid A \mid$ denotes the number of elements in the domain $A$.
-%\item Generate a random seed $s$: 
-%\begin{align}
-%s \in \mathbb{N} 
-%\end{align}
-%where $s$ is a random natural number.
-\item Determine $i \in [1, n]$ using the modulo operation:
-\begin{align}
-i = (s \mod n) + 1
-\end{align}
-\item Associate \( i \) with the corresponding element $a$ in $A$:
-\begin{align}
-a=A[i]
-\end{align}
-where $A[i]$ denotes the $i$-th element in $A$.
+\item Calculate $n$ as the size of the domain $A$.
+\item Determine the tagert $t$.
+\item Calculate $i \in [1, n]$ based on $s$ using the modulo operation.
+\item Associate \( i \) with the corresponding element $a$ in $A$.
 \item Perform the negation check $\neg P(a)$ to detect a counterexample if any.
-
 \item If no counterexample is found, calculate the hash \( t_s \) corresponding to the seed \( s \).
@@
 \end{enumerate}
-\paragraph{Find a seed:}
-The sequence of operations to find a seed can be described in Fig. \ref{fig:find_seed}.
+
+After conducting the negation check, either a counterexample is identified, or a hash is computed based on the seed $s$ along with the evaluation of the condition $\neg P_{a}$.
+This hash is then compared with the target hash to ascertain if it meets the criteria for a reward computation.
+The outcomes of the verification process include either a counterexample, a reward computation, or a non-reward computation.
+\subsubsection{Find a seed}
+The sequence of operations to find a seed can be described in Fig.
+\ref{fig:find_seed}.
+During the distributed process, each validator may generate a seed $s$ and conducts the negation check until the outcome indicates either a counterexample or a reward computation.
+Upon achieving either of these outcomes, the validator is able to submit it on-chain to claim their reward.
+Both the counterexample and the computation proof are represented by the seed used, allowing the on-chain compoment to replicate the process to verify its validity.
+If the verification is successful, the validators will be entitled to receive their reward.
 
@@
 \begin{tikzpicture}[node distance=2cm]
-
     % Nodes
@@
     \node (submit) [startstop, below of=compare, yshift=-0.5cm] {Submit on-chain};
-
     % Arrows
@@
 	\draw [arrow] (compare.west) -| node[pos=0.75, left] {No} ([xshift=-2cm]counterexample.west) |- (start);
-
 \end{tikzpicture}
@@
 %Consequently, each seed $s$ is linked with an element $a$ in the domain $A$, followed by the evaluation of the negation of the assertion $\neg P_{a}$.
-
-After conducting the negation check, either a counterexample is identified, or a hash is computed based on the seed $s$ along with the evaluation of the condition $\neg P_{a}$.
-This hash is then compared with the target hash to ascertain if it meets the criteria for a reward computation.
-The outcomes of the verification process include either a counterexample, a reward computation, or a non-reward computation.
-
-During the distributed process, each validator may generate a seed $s$ and conducts the negation check until the outcome indicates either a counterexample or a reward computation.
-Upon achieving either of these outcomes, the validator is able to submit it on-chain to claim their reward.
-Both the counterexample and the computation proof are represented by the seed used, allowing the on-chain compoment to replicate the process to verify its validity.
-If the verification is successful, the validators will be entitled to receive their reward.
 

### 2024-08-08 papers/assertion-contract/assertion_contract_app/paper.tex
Some revision made

@@
 \usepackage{tikz}
+\usetikzlibrary{positioning}
 \usepackage{amsmath}
@@
 
+Note that $p$ is the probability obtained when only one validator participates in the verification process.
+As more validators become involved, the probability of discovering a counterexample increases.
 \paragraph{Set up the taget hash:}
@@
 The outcomes of the verification process include either a counterexample, a reward computation, or a non-reward computation.
-\subsubsection{Find a seed}
+\subsubsection{Off-chain verification}
+In order to win a reward, either for discovering a counterexample or providing a computation proof, a validator must run the negation check off-chain.
+Due to the setup of the target hash, a validator needs to generate approximately $m$ seeds to have a chance of discovering a counterexample or a computation proof, thereby ensuring the validity or revealing the invalidity of a parameter.
+
 The sequence of operations to find a seed can be described in Fig.
@@
 Upon achieving either of these outcomes, the validator is able to submit it on-chain to claim their reward.
+
 Both the counterexample and the computation proof are represented by the seed used, allowing the on-chain compoment to replicate the process to verify its validity.
@@
 The architectural design of this model is depicted in Figure \ref{fig.architect}.
-The model consists of two main entities: an on-chain assertion contract and off-chain validator contract.
-\subsubsection{Three main actors.} In our practical model, three distinct actors play key roles.
-\begin{itemize}
-\item[•] Owner: responsible for deploying and overseeing both on-chain and off-chain contracts.
-\item[•] Callers: engage with on-chain contracts by initiating assertions and interacting with the system.
-\item[•] Validators: tasked with validating parameters and ensuring the integrity of the verification process.
-\end{itemize}
-
+The model consists of two main entities: the on-chain assertion contract and the off-chain validator program.
+\paragraph{Main actors.} Three distinct actors play key roles.
+\begin{itemize}
+\item Owner: responsible for deploying and overseeing both on-chain and off-chain components.
+\item Callers: engage with on-chain contracts by initiating assertions and interacting with the system.
+\item Validators: tasked with validating parameters and ensuring the integrity of the verification process.
+\end{itemize}
+\paragraph{On-chain assertion contract.}
+While additional functions may exist, the assertion contract must encompass the following two essential functions:
+\begin{itemize}
+\item The \lstinline|submit_parameter| function: Callers utilize this function to submit their parameters for validation. Subsequently, the parameter is distributedly verified by validators.
+\item  The \lstinline|claim_reward| function: This function accepts a parameter and a seed as inputs, yielding a result indicating whether the computation from the seed results in a counterexample, a reward computation, or a non-reward computation.
+\end{itemize}
+\paragraph{Off-chain assertion contract.}
+Since the off-chain contract runs off-chain, it can be implemented according to the validator's preferences.
+However, the crucial point is that the off-chain contract must use the exact same \lstinline|claim_reward| function when attempting to find a counterexample or a computation proof.
+Additionally, it should support a function that assists the validator in finding a seed to earn a reward.
+\paragraph{Storage.}
+When a parameter is submitted for verification, the following information should be stored:
+\begin{itemize}
+\item Parameter: this includes the parameter itself.
+In cases where storing the parameter on-chain is impractical because of its size, it could be possible to store only its hash.
+Despite this, the hash remains sufficient for validation.
+\item Timestamp: this indicates the approximate time when the parameter was submitted. This information is used to prevent caller exploitation security risks as explained above.
+\end{itemize}
+
+In some applications, multiple computational proofs may be allowed.
+There are a record to monitor the progress of the parameter's verification.
+This record is crucial for determining when a work function can be invoked for a given parameter or when it should be discarded.
+The verification status records a counterexample and reward computations found.
+For that, it should include the following details of the addresses of the validators and the random number $r$ used in the verification process.
 \begin{figure}
@@
 \end{figure}
-\subsubsection{On-chain assertion contract.}
-While additional functions may exist, the assertion contract must encompass the following two essential functions:
-\begin{itemize}
-\item The \lstinline|submit_parameter| function: Callers utilize this function to submit their parameters for validation. Subsequently, the parameter is distributedly verified by validators.
-\item  The \lstinline|claim_reward| function: This function accepts a parameter and a seed as inputs, yielding a result indicating whether the computation from the seed results in a counterexample, a reward computation, or a non-reward computation.
-\end{itemize}
-\subsubsection{Off-chain assertion contract.}
-Since the off-chain contract runs off-chain, it can be implemented according to the validator's preferences.
-However, the crucial point is that the off-chain contract must use the exact same \lstinline|claim_reward| function when attempting to find a counterexample or a computation proof.
-Additionally, it should support a function that assists the validator in finding a seed to earn a reward.
-\subsubsection{Storage.}
-When a parameter is submitted for verification, the following information should be stored:
-\begin{itemize}
-\item Parameter: this includes the parameter itself.
-In cases where storing the parameter on-chain is impractical because of its size, it could be possible to store only its hash.
-Despite this, the hash remains sufficient for validation.
-%\item Caller Address: This identifies the address of the caller who submitted the parameter.
-It serves purposes such as tracking submissions, preventing callers from resubmitting parameters, or preventing callers from claiming rewards for their own submitted parameters.
-\item Timestamp: this indicates the approximate time when the parameter was submitted. This information is used to prevent caller exploitation security risks as explained above.
-\end{itemize}
-
-In some applications, multiple computational proofs may be allowed.
-There are a record to monitor the progress of the parameter's verification.
-This record is crucial for determining when a work function can be invoked for a given parameter or when it should be discarded.
-The verification status records a counterexample and reward computations found.
-For that, it should include the following details of the addresses of the validators and the random number $r$ used in the verification process.
 

### 2024-08-09 papers/assertion-contract/assertion_contract_app/paper.tex
revise the practical model

@@
 \label{sec:distributed-assertion-verification}
-\subsection{Off-chain Distributed Verification Approach}
-We propose a novel approach for verifying parameter assertions in smart contracts on the blockchain.
-Our approach distributes the assertion verification process and moves it off-chain, with only the verification results being submitted to the blockchain.
-
-Assertions are checked off-chain, and only the results of these checks (indicating whether any assertion was violated) are submitted and re-verified to the blockchain.
-This reduces the computational load on the blockchain while ensuring the integrity of the contract.
+\subsection{Off-chain Verification Approach}
+We propose a novel approach for verifying parameter assertions in blockchain-based smart contracts.
+Our approach distributes the assertion verification process and moves it off-chain, with only the verification outcomes being sent to the blockchain.
+
+Assertions are validated off-chain, and only the results (specifying whether any assertions were violated) are submitted and re-verified on the blockchain.
+This approach minimizes the computational burden on the blockchain while maintaining the integrity of the contract.
 
@@
 \end{gather}
-\item Off-chain verification: Validators endeavor to find counterexamples of the assertion using this negation off-chain.
+\item Off-chain verification: The negation formulas is then distributed to validators. Validators endeavor to find counterexamples of the assertion using this negation off-chain.
+
 Specifically, each validator attempts to find a counterexample by identifying $a \in A$ such that the negation formula is satisfied $\neg P(a)$. 
@@
 \begin{enumerate}
+\item Denial-of-service (DoS) attacks: The system is susceptible to DoS attacks, where a caller inundates the system with numerous invalid parameters, causing congestion and hindering its operation.
 \item Front-running attacks: The system is vulnerable to front-running attacks, where an attacker closely monitors the mempool to intercept a seed representing a counterexample or a computation proof, subsequently stealing the reward.
-\item Caller exploitation: A caller might exploit the system by running the negation check privately to identify the reward before submitting the parameter on-chain, thereby swiftly claiming the reward ahead of the other validators.
-\item Denial-of-service (DoS) attacks: The system is susceptible to DoS attacks, where a caller inundates the system with numerous invalid parameters, causing congestion and hindering its operation.
-%\item Reward manipulation: A validator may attempt to manipulate the reward system by resubmitting counterexamples or computation proofs multiple times to multiply their rewards.
+\item Caller exploitation: A caller might exploit the system by running the negation check privately to (1) identify the reward before submitting the parameter on-chain, thereby swiftly claiming the reward ahead of the other validators, (2) fake the compuatation proofs before a counterexample can be found by other validators.
+\item Reward manipulation: For a system that allows multiple rewards.
+A validator may attempt to manipulate the reward system by resubmitting counterexamples or computation proofs multiple times to multiply their rewards.
 \end{enumerate}
@@
 The architectural design of this model is depicted in Figure \ref{fig.architect}.
-The model consists of two main entities: the on-chain assertion contract and the off-chain validator program.
-\paragraph{Main actors.} Three distinct actors play key roles.
-\begin{itemize}
-\item Owner: responsible for deploying and overseeing both on-chain and off-chain components.
-\item Callers: engage with on-chain contracts by initiating assertions and interacting with the system.
-\item Validators: tasked with validating parameters and ensuring the integrity of the verification process.
-\end{itemize}
+%\paragraph{Main actors.} Three distinct actors play key roles.
+%\begin{itemize}
+%\item Owner: responsible for deploying and overseeing both on-chain and off-chain components.
+%\item Callers: engage with on-chain contracts by initiating assertions and interacting with the system.
+%\item Validators: tasked with validating parameters and ensuring the integrity of the verification process.
+%\end{itemize}
+\subsubsection{Main compoments.} The model consists of two main entities: the on-chain assertion contract and the off-chain validator program.
 \paragraph{On-chain assertion contract.}
@@
 \begin{itemize}
-\item The \lstinline|submit_parameter| function: Callers utilize this function to submit their parameters for validation. Subsequently, the parameter is distributedly verified by validators.
-\item  The \lstinline|claim_reward| function: This function accepts a parameter and a seed as inputs, yielding a result indicating whether the computation from the seed results in a counterexample, a reward computation, or a non-reward computation.
-\end{itemize}
-\paragraph{Off-chain assertion contract.}
-Since the off-chain contract runs off-chain, it can be implemented according to the validator's preferences.
-However, the crucial point is that the off-chain contract must use the exact same \lstinline|claim_reward| function when attempting to find a counterexample or a computation proof.
+\item The \( submit\_parameter \) function: Callers utilize this function to submit their parameters for validation. %Subsequently, the parameter is distributedly verified by validators.
+\item  The \( claim\_reward \) function: This function accepts a seed (or may some others) as inputs, yielding a result indicating whether the computation from the seed results in a counterexample, a reward computation, or a non-reward computation.
+\end{itemize}
+\paragraph{Off-chain validator program.}
+Since the off-chain program runs off-chain, it can be implemented according to the validator's preferences.
+However, the crucial point is that the off-chain contract must use the exact same \( claim\_reward \) function when attempting to find a counterexample or a computation proof.
 Additionally, it should support a function that assists the validator in finding a seed to earn a reward.
@@
 Despite this, the hash remains sufficient for validation.
-\item Timestamp: this indicates the approximate time when the parameter was submitted. This information is used to prevent caller exploitation security risks as explained above.
-\end{itemize}
-
-In some applications, multiple computational proofs may be allowed.
+\item Timestamp: this indicates the approximate time when the parameter was submitted. %This information is used to prevent caller exploitation security risks as explained above.
+\end{itemize}
+
+%In some applications, multiple computational proofs may be allowed.
 There are a record to monitor the progress of the parameter's verification.
@@
 
-\subsubsection{Calculate seed.}
-While a random number alone is sufficient to indicate the associated element $a$ in the domain $A$, to prevent the front-running attack and the caller exploitation attack, we enhance the randomness of the seed by combining a random number with the validator's address and the timestamps indicating when the parameter is submitted on the chain to calculate the seed.
-In deeds, the validator's address and timestamps are converted to numerical values and use these numbers in combination with a random number to compute the seed.
-This combination adds an extra level of security.
-\begin{enumerate}
-\item 
-Seed calculation: The seed is enhanced by combining a random number with the validator's address and timestamps.
-Let's denote the random number by $r$, the validator's address by $addr$, and the timestamp by $t$.
-\begin{equation}
-r \in \mathbb{N}, \quad \text{addr} \in \text{Addresses}, \quad t \in \text{Timestamps}
-\end{equation}
-\item Conversion of address and timestamp: The address and timestamp are converted to numerical values using appropriate functions.
-\begin{equation}
-\text{addr\_num} = \text{init256}(\text{addr}) \\
- \quad t_{\text{num}} = \text{convert}(t)
-\end{equation}
-\item Combination to compute the seed: The seed $s$ is computed by combining these numerical values.
-\begin{equation}
-s = \text{hash}(r, \text{addr\_num}, t_{\text{num}})
-\end{equation}
-where \(\text{hash}\) is a hash function that takes the three numerical values and returns a numerical value \( s \).
-\end{enumerate}
-
-\textbf{Security Features}:
-\begin{itemize}
-    \item Front-running attacks: Other validators cannot use the random number $r$ alone because the combination with their address and timestamp will not produce the same seed $s$.
-    \item Caller exploitation: The timestamp constraints prevent the caller from running the check before submitting the parameter.
-\end{itemize}
-%In this system, even if other validators obtain a random number, they are unable to submit it successfully, as their combination with their address will not yield the correct seed that corresponds to a specific element in the domain.
-Additionally, a caller cannot run the check before submitting the parameter owing to the timestamp constraints.
-As a result, any attempt to submit manipulated or before-run seeds will fail to produce either a counterexample or reward computation.
-The address conversion can be achieved using functions such as \lstinline|init256| in Solidity, which transform an Ethereum address into a numerical value.
-
+\subsubsection{Deploying and managing on/off-chain contracts.}
+On/off-chain contracts are provided and managed by their respective owners.%, who assume a primary role in their design. 
+The owner deploys the assertion contract on the blockchain while storing the validator program off the blockchain, thereby ensuring its accessibility to the validators.
+There are two ways to making these contracts available to validators.
+\begin{itemize}
+\item The owner stores the codes on a repository accessible to validators, or upon request, provide them directly to validators.
+\item The owner broadcards the contracts to the network using messaging systems such as Waku in Ethereum.
+In this scenario, the interested validators are responsible for locally storing off-chain code.
+\end{itemize}
+\subsubsection{Submitting a parameter.} %The primary entities interacting with the on-chain assertion contract are callers and validators.
+Callers submit parameters on-chain, while validators verify them off-chain.
+Subsequently, validators claim their findings of counterexamples or reward computations on-chain.
+Before a parameter can be utilized in the actual work function or contract, a caller must initially submit it via the submit-parameter function in the on-chain assertion contract.
+%When submitting the parameter, the caller need to send a deposit stake in the form of a native token or pay gas fees for storing the parameter.
+This stake is claimed by a validator who finds a counterexample, either in the form of the native token or as a gas refund from releasing the storage as the invalid parameter is deleted.
+%\textbf{Security Features}: 
+%The deposit serves as a deterrent, as in the event of an invalid parameter, the deposit may be forfeited to prevent callers from submitting such parameters solving the DoS attack security risk.
+
+Upon the submission of a parameter, an event can be emitted, allowing validators to receive updates by monitoring the blockchain for the parameter submission event.
+Additionally, the caller may choose to broadcast their parameter to all validators via a messaging system when submitting it online.
+%The work contact can only be invoked by the on-chain validation contract after the parameter has been validated if no counterexample is found.
+The actual work is then performed with the passed parameter.
+\subsubsection{Off-chain verification}
+After a parameter is submitted and stored on-chain, a validator can commence the verification process.
+To assess the validity of a parameter, each validator independently executes the off-chain validation program.
+
+A validator may attempt to try multiple times with different random seeds in order to find either a counterexample or a computational proof.
+%It's possible that several attempts may be made before the validator receives an award.
+A function called find-seed could be implemented, which in turn calls the claim-reward function to locate a seed.
+
+All events such as parameter submissions, the discovery of a counterexample, or the presentation of computational proofs can be broadcasted to the network using event emission.
+Validators can monitor these events to stay updated on the verification status in real-time.
+\subsubsection{Claiming the reward} 
+If validators discover a counterexample or an award computation, they provide the seed%, a combination of a random number, the parameter's timestamp and the validator's address 
+to the on-chain assertion contract.
+
+The on-chain assertion contract then executes the same claim-reward function, which should yield the same result.
+If the result is correct, there is an award to the validator.
+%and the record of the parameter in the storage is updated accordingly.
+%When a computational proof is submitted and  certain requirements are met, the work function/contract is invoked.
+
+\subsubsection{Calling a work function}
+A work function can indeed be encapsulated either as a private function in the assertion contract or implemented in another contract.
+In this process, a caller initiates the submission of a parameter for verification by invoking the submit-parameter function within the on-chain assertion contract.
+Upon successful verification of the parameter, a work contract can be triggered to execute the designated task, operating under the assumption of the parameter's validity.
+
+The invocation of the work function or contract is carried out by the on-chain validation contract or a caller.
+This call is subject to specific requirements being met, ensuring that the task is executed only when the verification process has been successfully completed and the parameter is deemed valid, such as a certain amount of time having passed, no counterexample being found, and receiving enough computation proofs.
+If all conditions are met, the actual work is executed, and in some application, the record of the parameter may be deleted from memory to free up storage.
 \subsubsection{The evaluation of the negation predicate.} An assertion in smart contract languages, such as Solidity and Michelson, is essentially predicate logic expressed as a Boolean formula computed from relational operators, logical operators, and expressions.
@@
 \end{itemize}
-
-%In some applications, multiple computational proofs may be allowed. This record is crucial for determining when a work function can be invoked for a given parameter or when it should be discarded.
-
-\textbf{Security Features}:
+\subsection{Security Features}
+\subsubsection{DoS attacks}
+When submitting the parameter, the caller need to send a deposit stake in the form of a native token.
+This stake is claimed by a validator who finds a counterexample.
+This stake returns to the caller when the parameter is verified.
+
+The deposit serves as a deterrent, as in the event of an invalid parameter, the deposit may be forfeited to prevent callers from submitting such parameters solving the DoS attack security risk. 
+\subsubsection{Front-running attacks}
+While a random number $r$ alone as a seed is sufficient to indicate the associated element $a$ in the domain $A$, to prevent the front-running attack, we enhance the randomness of the seed by combining a random number with the validator's address to calculate the seed.
+In deeds, the validator's address is converted to numerical values and use these numbers in combination with a random number to compute the seed.
+
+Let's denote the validator's address by $addr$.
+\begin{equation}
+\quad \text{addr} \in \text{Addresses}
+\end{equation}
+
+The address is converted to numerical values.
+\begin{equation}
+\text{addr\_num} = \text{init256}(\text{addr})
+\end{equation}
+
+This combination adds an extra level of security.
+So even watching the mempool and get the random number, a malicious validators cannot use the same random number $r$  because the combination with their address will not produce the same seed $s$.
+\subsubsection{Caller exploitation attack}
+A caller may run the validator program for their parameters before submitting it on-chain and the quickly submit it right after submitting the parameters to either get the computation reward or prove the valid of their parameters before  counterexamples found by other validators.
+
+To prevent this security sisk, the block timestamps indicating when the parameter is submitted on the chain is included to calculate the seed.
+The seed is enhanced by combining a random number with the validator's address and timestamps.
+
+ Let's denote the timestamp by $t$.
+\begin{equation}
+\quad t \in \text{Timestamps}
+\end{equation}
+
+The seed $s$ is computed by combining these numerical values.
+\begin{equation}
+s = \text{hash}(r, \text{addr\_num}, t)
+\end{equation}
+where \(\text{hash}\) is a hash function that takes the three numerical values and returns a numerical value \( s \).
+As a result, any attempt to submit manipulated or before-run seeds will fail to produce either a counterexample or reward computation.
+
+Moreover, some application may want to set up a time fame such that a parameter can only valid if this amout of time is passed.
+This grantee enough time for validators to valide the parameter.
+Then, the parameter is valid if and only if a certain amount of time having passed, no counterexample being found, and receiving enough computation proofs.
+\subsubsection{Reward manipulation attack}
+In some applications, multiple computational proofs may be allowed.
+There are a record to monitor the progress of the parameter's verification.
+Namely, it includes the following details of the addresses of the validators and the random number $r$ used in the verification process.
+This record is crucial for preventing reward manipulation attack as a validator can not reclaim a new reward with the same random number.
+
 The validators' addresses and the random number $r$ play a vital role in preventing reward-manipulation attacks.
@@
 Therefore, this uniqueness prevents validators from submitting the same computation proof or a counterexample multiple times.
+%\subsection{Seed calculation}
+%The validator's address and timestamps are converted to numerical values and use these numbers in combination with a random number to compute the seed.
+This combination adds an extra level of security.
+%\begin{enumerate}
+%\item 
+%Seed calculation: The seed is enhanced by combining a random number with the validator's address and timestamps.
+Let's denote the random number by $r$, the validator's address by $addr$, and the timestamp by $t$.
+%\begin{equation}s
+%r \in \mathbb{N}, \quad \text{addr} \in %\text{Addresses}, \quad t \in \text{Timestamps}
+%\end{equation}
+%\item Conversion of address and timestamp: The address and timestamp are converted to numerical values using appropriate functions.
+%\begin{equation}
+%\text{addr\_num} = \text{init256}(\text{addr}) \\
+% \quad t_{\text{num}} = \text{convert}(t)
+%\end{equation}
+%\item Combination to compute the seed: The seed $s$ is computed by combining these numerical values.
+%\begin{equation}
+%s = \text{hash}(r, \text{addr\_num}, t_{\text{num}})
+%\end{equation}
+%where \(\text{hash}\) is a hash function that takes the three numerical values and returns a numerical value \( s \).
+%\end{enumerate}
+
+%\textbf{Security Features}:
+%\begin{itemize}
+%    \item Front-running attacks: Other validators cannot use the random number $r$ alone because the combination with their address and timestamp will not produce the same seed $s$.
+%    \item Caller exploitation: The timestamp constraints prevent the caller from running the check before submitting the parameter.
+%\end{itemize}
+%In this system, even if other validators obtain a random number, they are unable to submit it successfully, as their combination with their address will not yield the correct seed that corresponds to a specific element in the domain.
+Additionally, a caller cannot run the check before submitting the parameter owing to the timestamp constraints.
+ %The address conversion can be achieved using functions such as \lstinline|init256| in Solidity, which transform an Ethereum address into a numerical value.
+
+%In some applications, multiple computational proofs may be allowed. This record is crucial for determining when a work function can be invoked for a given parameter or when it should be discarded.
+
+%\textbf{Security Features}:
+%The validators' addresses and the random number $r$ play a vital role in preventing reward-manipulation attacks.
+A validator cannot resubmit with the same $r$.
+Therefore, this uniqueness prevents validators from submitting the same computation proof or a counterexample multiple times.
 
 %In certain applications, one may delete the records after processing is completed for the parameter, especially if a large number of parameters are submitted to manage storage efficiently.
-\subsection{Deploying and managing on/off-chain contracts.}
-On/off-chain contracts are provided and managed by their respective owners, who assume a primary role in their design.
-The owner deploys the assertion contract on the blockchain while storing the validator contract off the blockchain, thereby ensuring its accessibility to the validators.
-
-There are two approaches to making these contracts available to validators.
-\begin{itemize}
-\item The owner store the codes on a repository accessible to validators, or upon request, provide them directly to validators.
-\item Alternatively, the owner broadcard the contracts to the network using messaging systems such as Waku in Ethereum.
-Owners should disseminate contracts to the network after deploying the on-chain assertion contracts.
-In this scenario, the interested validators are responsible for locally storing off-chain code.
-\end{itemize}
-
-\subsection{Submitting and verifying a parameter.} The primary entities interacting with the on-chain assertion contract are callers and validators.
-Callers submit parameters on-chain, while validators verify them off-chain.
-Subsequently, validators claim their findings of counterexamples or reward computations on-chain.
-\subsubsection{Submitting a parameter} 
-Before a parameter can be utilized in the actual work function or contract, a caller must initially submit it via the submit-parameter function in the on-chain assertion contract.
-When submitting the parameter, the caller need to send a deposit stake in the form of a native token or pay gas fees for storing the parameter.
-This stake is claimed by a validator who finds a counterexample, either in the form of the native token or as a gas refund from releasing the storage as the invalid parameter is deleted.
-
-\textbf{Security Features}: 
-The deposit serves as a deterrent, as in the event of an invalid parameter, the deposit may be forfeited to prevent callers from submitting such parameters solving the DoS attack security risk.
-
-Upon the submission of a parameter, an event can be emitted, allowing validators to receive updates by monitoring the blockchain for the parameter submission event.
-Additionally, the caller may choose to broadcast their parameter to all validators via a messaging system when submitting it online.
-
-%The work contact can only be invoked by the on-chain validation contract after the parameter has been validated if no counterexample is found.
-The actual work is then performed with the passed parameter.
-\subsubsection{Off-chain verification}
-
-After a parameter is submitted and stored on-chain, a validator can commence the verification process.
-To assess the validity of a parameter, each validator independently executes the off-chain validation contract.
-A validator may attempt to run the off-chain validation contract multiple times with different random numbers in order to find either a counterexample or a computational proof.
-It's possible that several attempts may be made before the validator receives an award.
-A function called find-seed could be implemented, which in turn calls the claim-reward function to locate a seed.
-
-All events such as parameter submissions, the discovery of a counterexample, or the presentation of computational proofs can be broadcasted to the network using event emission.
-Validators can monitor these events to stay updated on the verification status in real-time.
-
-\subsection{Claiming the reward} 
-If validators discover a counterexample or an award computation, they provide the seed, a combination of a random number, the parameter's timestamp and the validator's address to the on-chain assertion contract.
-The on-chain assertion contract then executes the same claim-reward function, which should yield the same result.
-If the result is correct, there is an award to the validator and the record of the parameter in the storage is updated accordingly.
-%When a computational proof is submitted and  certain requirements are met, the work function/contract is invoked.
-
-\subsection{Calling a work function}
-A work function can indeed be encapsulated either as a private function in the assertion contract or implemented in another contract.
-In this process, a caller initiates the submission of a parameter for verification by invoking the submit-parameter function within the on-chain assertion contract.
-Upon successful verification of the parameter, a work contract can be triggered to execute the designated task, operating under the assumption of the parameter's validity.
-
-The invocation of the work function or contract is carried out by the on-chain validation contract or a caller.
-This call is subject to specific requirements being met, ensuring that the task is executed only when the verification process has been successfully completed and the parameter is deemed valid, such as a certain amount of time having passed, no counterexample being found, and receiving enough computation proofs.
-If all conditions are met, the actual work is executed, and in some application, the record of the parameter may be deleted from memory to free up storage.
 

### 2024-08-16 papers/static-checker/aplas/paper.tex
camera-ready

@@
-% APLAS 2021: Regular research papers should not exceed 18 pages in
+% APLAS 2024: Regular research papers should not exceed 17 pages in
 % the Springer LNCS format(LaTeX template), including bibliography and
@@
 \pdfoutput=1
-%\usepackage[english]{babel}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{amssymb}
-\usepackage{comment}
 \usepackage{graphicx}
-%\usepackage[colorinlistoftodos]{todonotes}
 \usepackage{mathpartir}
-%\usepackage{fixme}
 \usepackage{xcolor}
@@
 \usepackage{listings}
-\usepackage{adjustbox} % For adjusting box sizes
+
 \lstdefinelanguage{michelson}{
-  % basicstyle=\ttfamily,
+  basicstyle=\ttfamily,
   basicstyle=\fontsize{8}{9.6}\selectfont,
@@
   morestring=[b]",
-}
-\lstset{
-  language=Caml,
-  captionpos=b,
-  aboveskip=-\smallskipamount,
-  belowskip=-\smallskipamount,
-  belowcaptionskip=0pt,
-  basicstyle=\fontsize{8}{9.6}\selectfont,
-  morekeywords={val}
 }
@@
 %
-%\author{Thi Thu Ha Doan\orcidID{0000-0001-7524-4497}\and Peter Thiemann\orcidID{0000-0002-9000-1239}}
+\author{Thi Thu Ha Doan\orcidID{0000-0001-7524-4497}\and Peter Thiemann\orcidID{0000-0002-9000-1239}}
 
 %
-%\authorrunning{Ha Doan, P. Thiemann}
+\authorrunning{Ha Doan, P. Thiemann}
 % First names are abbreviated in the running head.
@@
 %
-%\institute{University of Freiburg, Germany \\
-%  \email{\{doanha,thiemann\}@informatik.uni-freiburg.de}}
+\institute{University of Freiburg, Germany \\
+  \email{\{doanha,thiemann\}@informatik.uni-freiburg.de}}
 %
@@
 \label{sec:background}
-\lstset{language=michelson}
-\begin{lstlisting}[float=tp,captionpos=b,caption={A Michelson program},label={lst:simple-program-add}]
-parameter int;
-storage   int;
-code {                (* pair int int :: [] *)
-  DUP; UNPAIR;        (* int :: int :: pair int int :: [] *) 
-  COMPARE; GE;        (* bool :: pair int int :: [] *)
-  IF {UNPAIR; SUB} {PUSH string 'Unexpected Pair'; FAILWITH};
-                      (* int :: [] *)
-  NIL operation; PAIR (* pair (list operation) int :: [] *)
-}
-\end{lstlisting}
 Michelson is a stack-based, statically typed functional programming language.
@@
 The type system does not support quantification over types, and there are no user-defined types.
-
-Listing~\ref{lst:simple-program-add} contains a short example of a Michelson program.
-The code is interspersed with comments indicating the types of values currently on the stack.
-This program first duplicates its input (\lstinline|DUP|), decomposes the pair $P \times S$ into its components (\lstinline|UNPAIR|), compares the two values on top of the stack (\lstinline|COMPARE|), and transforms the result into a boolean (\lstinline|GE|).
-The \lstinline|IF| instruction pops the boolean and either executes the first (for true) or second (for false) list of instructions.
-At this point, only the initial pair remains on the stack.
-In the true branch, \lstinline|UNPAIR| decomposes the pair, and \lstinline|SUB| subtracts the two components.
-In the false branch, the \lstinline|PUSH| instruction puts a string message on the stack.
-The \lstinline|FAILWITH| instruction aborts the contract execution: the tokens provided with the invocation are consumed, but the storage and balance of the contract remain unchanged.
-Finally, the \lstinline|NIL| instruction pushes an empty list of operations, and \lstinline|PAIR| creates the required pair of type $O^* \times S$.
-
-A contract may have several entrypoints. Entrypoints are encoded by
-using a sum type (call ``or type'' in Michelson). Each (nested) alternative in a sum can be
-given a name, which is used as the name for an entrypoint. A call to
-an entrypoint automatically adds the required \lstinline|LEFT| and
-\lstinline|RIGHT| constructors to the parameter.
-\lstset{language=Caml}
-\section{SCV: A Domain Specific Language For Smart Contract Property Specification}
-\label{sec:domain-specific-language}
-SCV contains a domain-specific language to specify smart contract properties, aiming to be user-friendly for non-experts and compatible with SMT solvers. 
 \begin{figure}[tp]
@@
 \end{figure}
+
+Listing~\ref{lst:simple-program-add} contains a short example of a Michelson program.
+The code is interspersed with comments indicating the types of values currently on the stack.
+This program first duplicates its input (\lstinline|DUP|), decomposes the pair $P \times S$ into its components (\lstinline|UNPAIR|), compares the two values on top of the stack (\lstinline|COMPARE|), and transforms the result into a boolean (\lstinline|GE|).
+The \lstinline|IF| instruction pops the boolean and either executes the first (for true) or second (for false) list of instructions.
+At this point, only the initial pair remains on the stack.
+In the true branch, \lstinline|UNPAIR| decomposes the pair, and \lstinline|SUB| subtracts the two components.
+In the false branch, the \lstinline|PUSH| instruction puts a string message on the stack.
+The \lstinline|FAILWITH| instruction aborts the contract execution: the tokens provided with the invocation are consumed, but the storage and balance of the contract remain unchanged.
+Finally, the \lstinline|NIL| instruction pushes an empty list of operations, and \lstinline|PAIR| creates the required pair of type $O^* \times S$.
+
+A contract may have several entrypoints. Entrypoints are encoded by
+using a sum type (call ``or type'' in Michelson). Each (nested) alternative in a sum can be
+given a name, which is used as the name for an entrypoint. A call to
+an entrypoint automatically adds the required \lstinline|LEFT| and
+\lstinline|RIGHT| constructors to the parameter.
+\lstset{language=michelson}
+\begin{lstlisting}[float,captionpos=b,caption={A Michelson program},label={lst:simple-program-add}]
+parameter int;
+storage   int;
+code {                (* pair int int :: [] *)
+  DUP; UNPAIR;        (* int :: int :: pair int int :: [] *) 
+  COMPARE; GE;        (* bool :: pair int int :: [] *)
+  IF {UNPAIR; SUB} {PUSH string 'Unexpected Pair'; FAILWITH};
+                      (* int :: [] *)
+  NIL operation; PAIR (* pair (list operation) int :: [] *)}
+\end{lstlisting}
+\section{SCV: A Domain Specific Language For Smart Contract Property Specification}
+\label{sec:domain-specific-language}
+SCV contains a domain-specific language to specify smart contract properties, aiming to be user-friendly for non-experts and compatible with SMT solvers. 
 \subsection{Basic syntax}
@@
 Since Michelson operates on a stack, we assume that the input stack and the output stack each have only one element, as specified in the input term and the output term, respectively.
-The syntax allows us to specify both incomplete and complete smart contracts.
-For a complete smart contract, the output should be a pair consisting of an operation list and the storage's state after the completion of the code.
+The syntax allows us to specify either a fragment of Michelson code or a complete program.
+For a complete Michelson program, the output should be a pair consisting of an operation list and the state of the storage after code execution,  as described in Section \ref{sec:background}.
 For verification purposes, we elide the operation list and represent the output solely by the term of the value in the storage after execution concludes.
-%Michelson code, whether composed by users, obtained from the Tezos blockchain, or compiled from higher-level languages, can be seamlessly used within our framework.
 
-The pre- and post-condition instances are formulas in first-order logic that can be handled by an SMT solver (specifically, Z3 in our case).
+The pre and postcondition instances are formulas in first-order logic that can be handled by an SMT solver (specifically, Z3 in our case).
 The specification language is constructed from predicates.
@@
 This predicate holds true if, after executing the smart contract code, there is an operation in the operation list indicating the transfer of \text{e2} tokens to address \text{e3} along with parameter \text{e1}\footnote{Additional predicates can be straightforwardly added if a mapping to Z3 formulas is defined.}.
+%\lstset{language=michelson}
 \begin{lstlisting}[float,captionpos=b,caption={Specification of  the \lstinline/sub/ contract},label={lst:sub-contract-specification},numbers=left]
@@
 that the integer \lstinline/x/ is greater than or equal to  \lstinline/y/. The postcondition asserts that the result
-\lstinline/z/ is equal to the substract of
+\lstinline/z/ is equal to the subtract of
 \lstinline/x/ and \lstinline/y/, which is greater or equal to
@@
 Thus, there are two options of the syntax.
-The first option similar to the basic syntax with the entrypoint specific.
+The first option is similar to the basic syntax with the entrypoint specific.
 In the second option, the input term is then the pair of the parameter term and the storage term.
@@
 The smart contract storage is a pair containing, as its first element, a boolean value \lstinline|open| that indicates whether the contract is still open for bidding or already closed.
-The second element is another nested pair, where the first element \lstinline|highest| stores the highest bidder's address, and the second element \lstinline|owner| is the contract owner's address.
+The second element is another nested pair, where the element \lstinline|highest| stores the highest bidder's address, and the element \lstinline|owner| is the contract owner's address.
 The current highest bid is reflected in the balance of the contract before the next bid is invoked.
@@
 Closing the contract transfers the balance to the owner and is restricted to the owner.
-Both closing and bidding operations fail if the auction is already closed.
+Both closing and bidding operations must fail if the auction is already closed.
 If bidding is open and the amount of tokens accompanying the bid exceeds the current highest bid, the current bidder replaces the previous highest bidder, and the previous highest bidder is reimbursed.
@@
 The contract should be deployed with the storage value \lstinline|Pair True (Pair owner owner)|, indicating that bidding is allowed, and the contract owner is currently the highest bidder.
-
 \begin{lstlisting}[float=tp,captionpos=b,caption={Auction contract specification},label={lst:auction-contract-specification1},numbers=left]
@@
 
-%There are several properties that we want to guarantee for this contract. 
 The first property is that if a user calls the \lstinline|%bid| entrypoint when the contract is still open for bidding and the bid is higher than the current bid (as specified in the \lstinline|pre-condition| field at line 7), and the address of the highest bidder can be cast to a real contract represented by the variable \lstinline|c| of type \lstinline|contract unit| on the blockchain (line 8), then the bid should succeed.
@@
 \lstinline/with/ in case conditions are specified as predicates. The
-following symbol \lstinline/->/ indicates that from the entrypoint
-that satisfies the condition \lstinline/p/, it is possible  to call
-the entrypoint \lstinline/%b/. One specification can
-contain several entrypoint relations concatenated by
+following symbol \lstinline/->/ indicates that after invoking the entrypoint \lstinline/%a/, it is possible  to call
+the entrypoint \lstinline/%b/ if the condition \lstinline/p/ holds. One specification can contain several entrypoint relations concatenated by
 \lstinline/|/. There is a special entrypoint named \lstinline/create/
@@
 the life cycle of the auction contract, which is depicted in Figure
-\ref{fig:auction-life-cycle}.
-Other properties related to the \lstinline|%close| entrypoint and the life cycle are omitted here due to page limits.
-%, but the full specification can be found in the Appendix and is available online at \cite{scv}.
-
+\ref{fig:auction-life-cycle}. Other properties related to the \lstinline|%close| entrypoint and the life cycle are omitted here due to page limits.
 \begin{figure}[tp]
@@
 
+\section{Symbolic Execution Model}
+\label{sec:symbolic-execution-model} 
+We already learned about Michelson, the low-level smart contract
+language for the Tezos blockchain, and its stack-based nature in
+Section~\ref{sec:background}.  Here we address the changes needed for symbolic execution of Michelson programs, focusing on a selection of instructions. 
+\subsection{System Model}
+\label{sec:system-model}
+Our symbolic model of a program state consists of a stack where each element is a symbolic value, represented as a pair comprising a Michelson term and its type.
+Thus, we write a stack as \STACK\ = (\TermOne, \TYF) \STACKCONCAT\ (\TermTwo, \TYS) \STACKCONCAT\ \DOT\ \STACKCONCAT\ \EMPTYSTACK.
+Here, \ensuremath{[\ ]} represents the empty stack, and \ensuremath{hd :: tl} denotes a stack with \ensuremath{hd} as the top element and \ensuremath{tl} as the remaining stack.
+Let \INSTRUCTION\ = \InstructionOne; \InstructionTwo; \DOT; \InstructionN\ be a sequence of instructions, and \PREDICATE\ be a path predicate  expressed in conjunctive form, capturing the branching conditions.
+\begin{definition}
+A symbolic execution state is represented by a tuple \STATE\ =
+[\INSTRUCTION, \STACK, \PREDICATE].
+A system configuration, \SYSTEM\ = \{\STATEONE, \STATETWO,
+\DOT, \STATEN \}, is a set of  states.
+\end{definition}
+\subsection{Rules}
+An instruction is defined by rules on a system configuration.
+There are two kinds of transitions: (1) \StateTrans\ internal transitions of a state, which are non-deterministic, and (2) \SystemTrans\ system transitions, which pick any state and replace it with all distinct states reachable by internal transitions, exploiting the non-determinism of the \StateTrans\ relation.
+
+A state is unreachable if its predicate \PREDICATE\ is  not
+satisfiable. The following rule drops unreachable states.
+\begin{mathpar}
+\inferrule[]
+  { \UNSAT\ \PREDICATE
+  }{
+  \{[\INSTRUCTION, \STACK, \PREDICATE]\} \cup \SYSTEM \SystemTrans \SYSTEM}
+\end{mathpar}
+The symbolic interpreter works as a graph with states as nodes and transitions as edges. This representation simplifies performing multi-step subtransitions needed for some operations.
+
+The semantics of the symbolic rules for the instructions adhere to the formal definitions of the Michelson language as outlined in \cite{michelson,michelson1}.
+In our model, these instructions are classified based on how we handle them into one-step, multi-step, blockchain, cryptographic, branch, and loop instructions.
+
+One-step instructions directly modify the system state without branching, have a localized effect, and are modeled with a single rule.
+
+Multi-step instructions involve the execution of a sub-sequence of instructions before returning to the main execution.
+The rule below models the \EXEC\ instruction, which executes a function specified as a sequence of instructions denoted by \INSTRUCTIONONE\ in the rule.
+This instruction applies the code of the function to the first element of the stack and then places the result back into the main execution.
+\begin{mathpar}
+  \inferrule[]
+  { [\INSTRUCTIONONE, (\StackOne, \TYF) \STACKCONCAT \EMPTYSTACK, 
+    \PREDICATE]
+    \StateTrans^*
+    [ \EMPTYSTACK, (\StackOne', \TYS) \STACKCONCAT \EMPTYSTACK, \PREDICATE']}{[(\EXEC; \INSTRUCTION),   (\{\INSTRUCTIONONE\}, \TYF\ \rightarrow\ \TYS) \STACKCONCAT
+    (\StackOne, \TYF) \STACKCONCAT \STACK, \PREDICATE] 
+    \StateTrans \
+    [ \INSTRUCTION, (\StackOne', \TYS) \STACKCONCAT \STACK,
+    \PREDICATE']}
+\end{mathpar} 
+Here, $\StateTrans^*$ represents the execution of multiple steps in a sequence of internal transitions.
+
+Blockchain instructions, such as the \AMOUNT\
+ instruction make implicit use of data from the transaction, the block and the current state of the blockchain.
+As these values are constant during the execution of a contract, we model them as fixed variables.
+
+Branch instructions, such as \IF\{\INSTRUCTIONONE\}\{\INSTRUCTIONTWO\} consume a value at the top of the stack. If the branch condition
+is True, it executes \INSTRUCTIONONE; otherwise, it executes
+\INSTRUCTIONTWO. 
+\begin{mathpar}
+  \inferrule[]
+  { }{
+    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
+    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
+    \StateTrans\
+    \{[\INSTRUCTIONONE, \STACK, \PREDICATE\ \Wedge\ \StackOne],   [\INSTRUCTIONTWO, \STACK, \PREDICATE\ \Wedge\ \NEG\
+   \StackOne]\}} 
+\end{mathpar}
+
+The loop instructions, including \LOOP\ check the loop condition by examining the
+top of the stack. These loop instructions may not terminate, just like while-loops. There are further loop instructions, like \ITER\ and
+\MAP, specialized to traverse data structures like lists, sets, and maps. There are also
+some instructions that implicitly require looping like \CONCAT, and
+\SIZE. The latter kinds of loop instructions do always terminate.
+
+Let us first take look at the terminate loops, such as the \ITER\ instruction, which iterates over a
+list. The corresponding typing rule for the \ITER\ instruction is as follows: 
+\begin{mathpar}
+  \inferrule{\JTypeExpr\TEnv{\INSTRUCTION}{\TY \STACKCONCAT \TYA\ \SRightarrow\ \TYA}
+  }{
+      \JTypeExpr\TEnv{\ITER\ \INSTRUCTION}{\TYLIST\ \TY \STACKCONCAT \TYA\ \SRightarrow\ \TYA}
+    }
+\end{mathpar}
+This rule ensures that if the loop body \INSTRUCTION\ has the type \TY\ \STACKCONCAT\ \TYA\ \SRightarrow\ \TYA, then the entire \ITER\ instruction, when applied to a stack with the top element of type \TY\ \TYLIST\ and the rest of the stack of type \TYA, produces a result stack of type \TYA.
+
+The following rule handles the  \ITER\ loop for  the non-empty list\footnote{\ITER\ can also iterate over sets and maps, but the details are very similar to the list case and hence omitted.}, while the \ITER\ loop terminates when the list is empty.
+\begin{mathpar}
+  \inferrule[]
+  { \HEAD, \STAIL\ \FRESH \\
+    [\INSTRUCTIONONE,  (\HEAD, \TY) \STACKCONCAT\STACK, 
+    \PREDICATE]
+    \StateTrans^*
+    [ \EMPTYSTACK,  \STACK', \PREDICATE']
+  }{
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\
+    \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \\
+    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\STAIL, \TYLIST\ \TY)
+    \STACKCONCAT\STACK',  \PREDICATE' \Wedge  (\StackOne\
+    \EQ\ \{\HEAD; \STAIL \}) ] 
+  }
+\end{mathpar}
+It symbolically executes the instructions \INSTRUCTIONONE\ within the
+\ITER\ block with the head of the list (\HEAD) replacing the list. The resulting state transitions to a
+new stack (\STACK') and an updated predicate (\PREDICATE' $\Wedge$
+(\StackOne\ \EQ\ \{\HEAD; \STAIL\})), where \STAIL\ represents the rest of the list.
+
+If the list is concrete, the instruction terminates as it simply loops over the elements
+of the list.
+How do we deal with \ITER\ if the list is a symbolic value?
+One solution could involve running the loop a certain number of times to obtain the symbolic value.
+However, we can defer that decision by abstracting the result.
+
+The loop body \INSTRUCTIONONE\ can be considered as a function, say \F,  applied to a stack
+of type \TY\ ::\ \TYA, resulting in a stack of type \TYA. 
+%\begin{mathpar}
+%\Gamma\ \vdash\  \F\ :\ \TY\ ::\ \TYA\ \SRightarrow\ \TYA
+%\end{mathpar}
+If the first element of
+the stack is a list \LIST, and the rest of the stack is \STACKZERO\ =
+\StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ ... \STACKCONCAT\
+\StackN.
+Assuming the size of the list \LIST\ is $m$, the \ITER\ {\INSTRUCTIONONE} instruction applies the function \F\ to the stack $m$ times, once for each element of the list \LIST.
+By unfolding the list once as \{\HEAD; \STAIL\}, the result after
+the first iteration is \STACKONE\ = \StackOneOne\  \STACKCONCAT\
+\StackTwoOne\ \STACKCONCAT\ ... \STACKCONCAT\ \StackNOne = \F\ \HEAD\
+\STACKZERO, and so on.
+
+We can represent the value of the stack after running the
+instruction \ITER\  as the result of a fold function that applies the
+function \F\ to the list. 
+\begin{mathpar}
+\STACK'\ =  \FOLD\ \F\ \STACKZERO\ \LIST
+\end{mathpar}
+The \FOLD\ function also can be used to express the result of other loop instructions, such as CONCAT and SIZE, symbolically.
+
+The similar strategy can be employed for the \MAP\ {\INSTRUCTIONONE} instruction.
+\begin{mathpar}
+\MAP\ \{\INSTRUCTIONONE\} \Slash\ \LIST\ :: \STACK
+\end{mathpar}
+The outcome of the \MAP\ \{\INSTRUCTIONONE\} instruction is the result of a map function that applies the function \F\ representing the sequence of instructions \INSTRUCTIONONE\ to the list \LIST. 
+\begin{mathpar}
+(\FMAP\ \F\ \LIST) ::  \STACK
+\end{mathpar}
+
+Finally, we consider a loop instruction that may not terminate, such as \LOOP. 
+When the input to the symbolic execution consists of concrete values, an unbounded loop causes the interpreter to iterate for a significant number of times until it halts with an exception indicating an unfinished loop.
+This mirrors the behavior observed in the actual execution of smart contracts, where the loop continues until it runs out of gas, terminating the computation with an out-of-gas error.
+
+For a symbolic value, the stack type is determined before the loop is executed.
+We unfold the symbolic value once, execute the loop to determine the operation function, and then abstract the result of the loop and loop condition as function results.
+This abstraction helps detect whether the loop is unbounded, such as when the abstract function of the loop condition always results  true.
+
+In separate work \cite{dynamic-logic}, we have designed a dynamic logic tailored to Michelson as a formal foundation for the implementation of SCV.
+We have formalized a soundness proof of this logic in the Agda proof assistant.
 \section{Static Checker}
@@
 Several constants, such as \CAMOUNT\ and \CBALANCE, as well as cryptographic functions are predefined in the environment that applies to any smart contract specifications.
-
 \begin{figure}[tp]
@@
 \end{figure}
+
+We have implemented approximately 85\% of the Michelson instructions, including most of the major-use instructions.
+The remaining instructions were not implemented primarily due to time constraints rather than technical limitations.
 
@@
 \lstinline/y/ and  \lstinline/sbvar/ is equal to
-the substract of \lstinline/x/ and \lstinline/y/.
-
-We have implemented approximately 85\% of the Michelson instructions, including most of the major-use instructions.
-The remaining instructions were not implemented primarily due to time constraints rather than technical limitations.
-
+the subtract of \lstinline/x/ and \lstinline/y/. 
 \subsection{Output check}
 \label{sec:output-check}
-For an incomplete smart contract, the output term of the symbolic execution has the form of a term \Term\ and its type \TY.
+For a fragment of Michelson code, the output term of the symbolic execution has the form of a term \Term\ and its type \TY.
 For a complete smart contract, it takes the form \PAIR\ \VOPERATIONLIST\ \VSTORAGE, \TPAIR\ (\TOPERATIONLIST) \TYS, where \VSTORAGE\ represents the storage and \VOPERATIONLIST\ represents the operation list.
-Given an output term specified as $\tau$, the checker scans all reachable final states that do not contain a failwith stack and checks whether the output term matches.
+Given an output term specified as $\tau$, the checker scans all reachable final states that do not contain a failwith stack and checks whether $\tau$ matches with the output term.
 In the former case, it matches $\tau$ with the term \Term.
@@
 However, this test could fail if, for example, the output term is incorrectly specified as a variable of a type that does not match the actual result.
-
 \subsection{Fail conditions}
@@
 For instance, the entrypoint \lstinline|bid| has three fail conditions, as shown in Listing~\ref{lst:fail-condition-auction-contract-bid}: (1) If the auction is closed, (2) if the auction is open but the bid amount is less than or equal to the current balance, and (3) if the auction is open, the bid amount exceeds the balance, but the address of the highest bidder is invalid.
-
-\begin{lstlisting}[float=tp,captionpos=b,caption={Fail condition for auction contract bid entrypoint },label={lst:fail-condition-auction-contract-bid},numbers=left]
+%\lstset{language=michelson}
+\begin{lstlisting}[float=tp,captionpos=b,caption={Fail condition for auction contract bid entrypoint},label={lst:fail-condition-auction-contract-bid},numbers=left]
 1. not (open = true): 'Already closed'
@@
 \label{sec:property-check}
-%The SCV verify smart contract properties by using pre- and post-condition specifications. 
 A property is
@@
 = \lstinline/x/ $-$ \lstinline/y/) $\rightarrow$ (\lstinline/z/ $=$ \lstinline/x/ $-$ \lstinline/y/) $\land$ (\lstinline/z/ $>=$ 0)) is unsatisfiable.
-
 \subsection{Life-cycle check}
 \label{sec:life-cycle-check}
-An entrypoint relation can be defined as \lstinline/(%a -> %b) with p/, indicating that after invoking the entrypoint \lstinline/%a/, it is permissible to call the entrypoint \lstinline/%b/ if the condition \lstinline/p/ is satisfied.
+An entrypoint relation can be defined as \lstinline/(%a -> %b) with p/, indicating that after invoking the entrypoint \lstinline/%a/, it is permissible to call the entrypoint \lstinline/%b/ if the condition \lstinline/p/ holds.
 The presence of the keyword \lstinline/not/ at the beginning signals an impossibility.
@@
 \label{sec:case-stud-subs}
-
 This section reports two case studies which are taken from the realm of financial applications deployed on the Tezos blockchain. 
-
 \subsection{USDtz}
@@
 \begin{lstlisting}[float=tp,captionpos=b,caption={FA 1.2 interface},label={lst:fa12-interface},numbers=left]
-(address :from, (address :to, nat :value))    %transfer
-(address :spender, nat :value)                %approve
-(view (address :owner, address :spender) nat) %getAllowance
-(view (address :owner) nat)                   %getBalance
+pair (address:from, pair (address:to, nat:value)) %transfer
+pair (address:spender, nat:value)           %approve
+(view pair (address:owner, address:spender) nat) %getAllowance
+(view (address:owner) nat)                  %getBalance
 (view unit nat)                             %getTotalSupply
@@
 
-Any contract aiming to implement the FA 1.2 standard must incorporate the functions specified in Listing~\ref{lst:fa12-interface}.
+Any contract aiming to implement the FA 1.2 standard must incorporate the functions specified in Listing~\ref{lst:fa12-interface}, where
+\lstinline/view a r = pair a (contract r)/ implies an view entrypoint.
+A view is an entrypoint that takes an argument of type \lstinline/a/ and a contract to callback that receives in a value of type \lstinline/r/. 
 We verify USDtz \cite{usdtzimplemetation,tzstatsusdtz}, an implementation of the FA 1.2 standard.
@@
 (2) If the sender's account does not have permission to withdraw the specified \lstinline/value/ amount, the call will fail with the \lstinline/NotEnoughAllowance/ error.
-To verify these requirements, we utilize the failwith condition feature of our tool and examine the returned results, one of which is outlined in Listing~\ref{lst:transfer-udstz-contract}.
+To verify these requirements, we utilize the failwith condition feature of our tool and examine the returned results, one of which is outlined in Listing~\ref{lst:transfer-udstz-contract-z}.
 The fail condition results confirm these stipulations.
-\begin{lstlisting}[float,captionpos=b,caption={The \lstinline/NotEnoughBalance/ fail condition for the \lstinline/transfer/ entrypoint},label={lst:transfer-udstz-contract},numbers=left]
+\begin{lstlisting}[float,captionpos=b,caption={The \lstinline/NotEnoughBalance/ fail condition for the \lstinline/transfer/ entrypoint},label={lst:transfer-udstz-contract-z},numbers=left]
 not (paused = true) 
@@
 \end{lstlisting}
+
 Another essential property is ensuring that the allowance of the sender's account is decremented and the receiver's account is incremented by the \lstinline/value/ that has been sent.
@@
 This can be divided into two sub-properties: (1) if the parameter \lstinline/value/ is zero, then the corresponding allowance value of the \lstinline/spender/ from the owner (which is \SENDER\ in this call) should be zero, and (2) if \lstinline/value/ is non-zero and the allowance of the \lstinline/spender/ is zero, then the \lstinline/value/ should be recorded in the storage after the call.
-We specify these properties using pre- and post-conditions, as illustrated in Listing~\ref{lst:specification-approve-p1} for the first property.
+We specify these properties using pre and postconditions, as illustrated in Listing~\ref{lst:specification-approve-p1} for the first property.
 
@@
 \end{lstlisting}
-
 \subsection{Kolibri Oracle Contract}
@@
 We conducted fail condition checks for both the \lstinline/setMaxDelaySec/ and \lstinline/getXtzUsdPrice_callback/ entrypoints, but these conditions were not enforced.
-Specifically, upon examining the failwith conditions, we detected that there is no failwith if the data is more than 30 minutes (equal to 1800 seconds).
+Specifically, upon examining the failwith conditions, we detected that there is no failwith when the data is more than 30 minutes (equal to 1800 seconds).
 
-We then add the predicate \lstinline/post_maxDelay <= 1800/ in the post condition of the entrypoint \lstinline/setMaxDataDelaySec/ as shown in Listing \ref{lst:setMaxDataDelaySec1}, but then the pre and post condition test fails.
-This means there is no constraint that the data is less than 30 minutes.
+We then add the predicate \lstinline/post_maxDelay <= 1800/ in the postcondition of the entrypoint \lstinline/setMaxDataDelaySec/ as shown in Listing \ref{lst:setMaxDataDelaySec1}, but then the pre and postcondition test fails.
+This means there is no constraint enforcing that the data must be less than or equal to 30 minutes.
 This constraint is possibly set up by the governor and specified in the \lstinline/MaxDataDelaySec/ field.
@@
 This could lead to providing out-of-date rates.
-
 \begin{lstlisting}[float=tp,captionpos=b,caption={The specification of the \lstinline/setMaxDataDelaySec/ entrypoint},label={lst:setMaxDataDelaySec1},numbers=left]
@@
 
-The complete specifications and experimental results for the examples and case studies can be found in the appendix~\ref{sec:appendix} or accessed online at \cite{scv}.
-\section{Symbolic Execution Model}
-\label{sec:symbolic-execution-model} 
-We address the changes required for symbolic execution of Michelson programs, focusing on a selection of instructions. The
-appendix~\ref{sec:concl-sect-append} specifies further instructions,
-but may be skipped by the reviewers.
-
-\subsection{System Model}
-\label{sec:system-model}
-Our symbolic model of a program state consists of a stack where each element is a symbolic value, represented as a pair comprising a Michelson term and its type.
-Thus, we write a stack as \STACK\ = (\TermOne, \TYF) \STACKCONCAT\ (\TermTwo, \TYS) \STACKCONCAT\ \DOT\ \STACKCONCAT\ \EMPTYSTACK.
-Here, \ensuremath{[\ ]} represents the empty stack, and \ensuremath{hd :: tl} denotes a stack with \ensuremath{hd} as the top element and \ensuremath{tl} as the remaining stack.
-Let \INSTRUCTION\ = \InstructionOne; \InstructionTwo; \DOT\ \InstructionN\ be a sequence of instructions, and \PREDICATE\ be a path predicate  expressed in conjunctive form, capturing the branching conditions.
-\begin{definition}
-A symbolic execution state is represented by a tuple \STATE\ =
-[\INSTRUCTION, \STACK, \PREDICATE].
-A system configuration, \SYSTEM\ = \{\STATEONE, \STATETWO,
-\DOT, \STATEN \}, is a set of  states.
-\end{definition}
-
-\subsection{Rules}
-An instruction is defined by rules on a system configuration.
-There are two kinds of transitions: (1) \StateTrans\ internal transitions of a state, which are non-deterministic, and (2) \SystemTrans\ system transitions, which pick any state and replace it with all distinct states reachable by internal transitions, exploiting the non-determinism of the \StateTrans\ relation.
-
-A state is unreachable if its predicate \PREDICATE\ is  not
-satisfiable. The following rule drops unreachable states.
-\begin{mathpar}
-\inferrule[]
-  { \UNSAT\ \PREDICATE
-  }{
-  \{[\INSTRUCTION, \STACK, \PREDICATE]\} \cup \SYSTEM \SystemTrans \SYSTEM}
-\end{mathpar}
-The symbolic interpreter works as a graph with states as nodes and transitions as edges. This representation simplifies performing multi-step subtransitions needed for some operations.
-
-The semantics of the symbolic rules for the instructions adhere to the formal definitions of the Michelson language as outlined in \cite{michelson,michelson1}.
-In our model, these instructions are classified based on how we handle them into one-step, multi-step, blockchain, cryptographic, branch, and loop instructions.
-%This categorization reflects how these instructions are handled within our specific model.
-
-%\paragraph{One-step instructions}
-One-step instructions directly modify the system state without branching, have a localized effect, and are modeled with a single rule.
-
-%\paragraph{Multi-step instructions}
-Multi-step instructions involve the execution of a sub-sequence of instructions before returning to the main execution.
-The rule below models the \EXEC\ instruction, which executes a function specified as a sequence of instructions denoted by \INSTRUCTIONONE\ in the rule.
-This instruction applies the code of the function to the first element of the stack and then places the result back into the main execution.
-\begin{mathpar}
-  \inferrule[]
-  { [\INSTRUCTIONONE, (\StackOne, \TYF) \STACKCONCAT \EMPTYSTACK, 
-    \PREDICATE]
-    \StateTrans^*
-    [ \EMPTYSTACK, (\StackOne', \TYS) \STACKCONCAT \PREDICATE']}{[(\EXEC; \INSTRUCTION),   (\{\INSTRUCTIONONE\}, \TYF\ \rightarrow\ \TYS) \STACKCONCAT
-    (\StackOne, \TYF) \STACKCONCAT \STACK, \PREDICATE] 
-    \StateTrans \
-    [ \INSTRUCTION, (\StackOne', \TYS) \STACKCONCAT \STACK,
-    \PREDICATE]}
-\end{mathpar}
-%\paragraph{Blockchain instructions}
-
-Blockchain instructions, such as the \AMOUNT\
- instruction make implicit use of data from the transaction, the block and the current state of the blockchain.
-As these values are constant during the execution of a contract, we model them as fixed variable.
-
-%\paragraph{Branch instructions}
-Branch instructions, such as \IF\{\INSTRUCTIONONE\}\{\INSTRUCTIONTWO\} and \IF-LEFT\{\INSTRUCTIONONE\}\{\INSTRUCTIONTWO\} consume a value at the top of the stack. If the branch condition
-is True, it executes \INSTRUCTIONONE; otherwise, it executes
-\INSTRUCTIONTWO. 
-%Other branch instructions, such as IF-LEFT and IF-NONE are handled in the similar way.
-
-\begin{mathpar}
-  \inferrule[]
-  { }{
-    [(\IF\ \INSTRUCTIONONE\  \INSTRUCTIONTWO; \INSTRUCTION),
-    (\StackOne, \TBOOL) \STACKCONCAT\STACK, \PREDICATE]
-    \StateTrans\
-    \{[\INSTRUCTIONONE, \STACK, \PREDICATE\ \Wedge\ \StackOne],   [\INSTRUCTIONTWO, \STACK, \PREDICATE\ \Wedge\ \NEG\
-   \StackOne]\}} 
-\end{mathpar}
-%\paragraph{Loop instructions}
-
-The loop instructions, including
-\LOOP\ and \LOOPLEFT\ check the loop condition by examining the
-top of the stack. These loop instructions may not terminate, just like while-loops. There are further loop instructions, like \ITER\ and
-\MAP, specialized to traverse data structures like lists, sets, and maps. There are also
-some instructions that implicitly require looping like \CONCAT, and
-\SIZE. The latter kinds of loop instructions do always terminate.
-
-Let us first take look at the terminate loops.
-The following rule handles the  \ITER\ loop for  the non-empty list\footnote{\ITER\ can also iterate over sets and maps, but the details are very similar to the list case and hence omitted.}, while the \ITER\ loop terminates when the list is empty.
-\begin{mathpar}
-  \inferrule[]
-  { \HEAD, \STAIL\ \FRESH \\
-    [\ITER,  (\HEAD, \TY) \STACKCONCAT\STACK, 
-    \PREDICATE]
-    \StateTrans^*
-    [ \EMPTYSTACK,  \STACK', \PREDICATE']
-  }{
-    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\StackOne, \TYLIST\
-    \TY) \STACKCONCAT\STACK, \PREDICATE] \StateTrans \\
-    [(\ITER\ \INSTRUCTIONONE ; \INSTRUCTION), (\STAIL, \TYLIST\ \TY)\
-    \STACKCONCAT\STACK',  \PREDICATE' \Wedge  (\StackOne\
-    \EQ\ \{\HEAD; \STAIL \}) ] 
-  }
-\end{mathpar}
-It symbolically executes the instructions \INSTRUCTIONONE\ within the
-\ITER\ block with the head of the list (\HEAD) replacing the list. The resulting state transitions to a
-new stack (\STACK') and an updated predicate (\PREDICATE' $\Wedge$
-(\StackOne \EQ \{\HEAD;\STAIL\})), where \STAIL\ represents the rest of the list.
-
-How do we deal with \ITER\ if the list is a symbolic value?
-One solution could involve running the loop a certain number of times to obtain the symbolic value.
-However, we can defer that decision by abstracting the result.
-In fact, the loop body \INSTRUCTIONONE\ can be considered a function applied to a stack
-of type \TY\ \STACKCONCAT\ \TYA,
-resulting in a stack of type \TYA. If the first element of
-the stack is a list of the form \LIST\ = $x_1 \STACKCONCAT x_2 \STACKCONCAT
-\dots x_m \STACKCONCAT  [\ ]$, and the rest of the stack is \STACKZERO\ =
-\StackOne\  \STACKCONCAT\ \StackTwo\ \STACKCONCAT\ ... \STACKCONCAT\
-\StackN. Then the \ITER\ \{\INSTRUCTIONONE\} instruction applies a 
-function, sat \F, represented by \INSTRUCTIONONE\ \M\ times to the stack, once
-with each element $x_i$ of the list \LIST\ on top of the stack. The result after 
-the first iteration is \STACKONE\ = \StackOneOne\  \STACKCONCAT\
-\StackTwoOne\ \STACKCONCAT\ ... \STACKCONCAT\ \StackNOne = \F\ $x_1$
-\STACKZERO, and so on.
-In conclude, we can represent the result stack as the result of a fold function that applies  \F\ to the list.
-The \FOLD\ function also can be used to express the result of other loop instructions, such as CONCAT and SIZE, symbolically.
-\begin{mathpar}
-\STACK'\ =  \FOLD\ \F\ \STACKZERO\ \LIST
-\end{mathpar}
-
-In a similar strategy, symbolically, the result of the \MAP\ {\INSTRUCTIONONE} instruction applied to the list \LIST\ is the result of a map function that applies the function \F\ (representing the sequence of instructions \INSTRUCTIONONE) to the list.
-\begin{mathpar}
-\MAP\ \{\INSTRUCTIONONE\} \Slash\ \LIST\ :: \STACK\ \SRightarrow\ (\FMAP\ \F\ \LIST) ::  \STACK
-\end{mathpar}
-
-Finally, we consider a loop instruction that may not terminate, such as \LOOP\ and \LOOPLEFT. 
-When the input to the symbolic execution consists of concrete values, an unbounded loop causes the interpreter to iterate for a significant number of times until it halts with an exception indicating an unfinished loop.
-This mirrors the behavior observed in the actual execution of smart contracts, where the loop continues until it runs out of gas, terminating the computation with an out-of-gas error.
-For a symbolic value, the stack type is determined before the loop is executed.
-We abstract the result of the loop  and the loop condition as the abstract function results.
-This abstraction helps detect whether the loop is unbounded, such as when the abstract function of the loop condition always results  true.
-
-In separate work (currently under submission), we have designed a dynamic logic tailored to Michelson as a formal foundation for the implementation of SCV.
-We have formalized a soundness proof of this logic in the Agda proof assistant, which is omitted here due to the page limitation.
+The complete specifications and experimental results for the examples and case studies can be accessed online at \cite{scv}.
 \section{Related Work}
 \label{sec:related-work}
-%Research on the formal verification of blockchain-based applications has experienced rapid growth in the last decade.
-
 In this section, we discuss some key approaches, particularly those employing symbolic execution in the context of smart contracts. P. Tsankov et al. introduced
@@
 In contrast, we provide a separate specification language, so users do not need to modify the code.
-Similar to our tool, iContract \cite{icontract} utilizes symbolic execution and pre and postconditions to specify user properties, but it targets the Solidity language.
-
+Similar to our tool, iContract \cite{icontract} utilizes symbolic execution and pre and postconditions to specify user properties, but the iContract work and our work differ in target language, DSL design, and functionality.
 \section{Conclusion}
@@
 
+Our tool has several limitations.
+SCV relies on Z3, which may struggle with very large or complex problems, potentially returning \texttt{unknown} if it cannot determine satisfiability.
+Additionally, the tool does not yet handle gas consumption or support external calls.
 In future work, we want to extend SCV in two directions. 
@@
 of contract invocations can be processed in one run.
-
 \newpage
@@
 \bibliography{bio}
-
-\newpage
-\include{appendix}
+%\newpage
+%\include{appendix}
 \end{document}

### 2024-08-23 papers/static-checker/aplas/paper.tex
cosmetics & spell checking

@@
 \label{sec:introduction}
-Since smart contracts are permanently stored on the blockchain, once deployed, a smart contract cannot be changed.
-Regrettably, numerous instances have been documented where vulnerabilities in smart contracts were identified by the blockchain community, resulting in substantial financial losses~\cite{dao,wallethack}.
+
+Once a smart contract is deployed on the blockchain, it becomes permanent and cannot be altered.
+Regrettably, numerous cases have been documented where vulnerabilities
+in smart contracts were identified and exploited by bad actors in the blockchain community, resulting in substantial financial losses~\cite{dao,wallethack}.
 The distinctive execution model of smart contract languages has given rise to unforeseen errors due to a lack of familiarity with their complexities.
@@
 
-We have developed SCV, a formal verification tool for smart contracts on the Tezos blockchain \cite{tezos-whitepaper}, written in Michelson \cite{michelson}.
-SCV relies on symbolic execution backed by an SMT solver to simulate the implementation of the smart contract language, helping to detect subtle errors.
-Additionally, SCV includes a domain-specific language for precisely specifying smart contract properties, tailored to Michelson's execution model and inspired by Z3.
+We have developed SCV, a formal verification tool for smart contracts
+on the Tezos blockchain \cite{tezos-whitepaper}, written in Michelson
+\cite{michelson}. SCV relies on symbolic execution backed by an SMT
+solver to simulate the implementation of the smart contract language,
+helping to detect subtle errors. Additionally, SCV includes a
+domain-specific language for precisely specifying smart contract
+properties, tailored to Michelson's execution model and informed by
+the capabilities of Z3.
 Each specification consists of Michelson code, a precondition, and a postcondition with the usual partial correctness semantics.
@@
 
-While there is already a considerable body of work applying symbolic execution to the verification of smart contracts \cite{securify,manticore,kevm,park} (see Section~\ref{sec:related-work} for details), most of these efforts are designed for Ethereum, where standard techniques for symbolic execution of imperative programs are applicable.
-Such groundwork does not exist for Michelson, which is a functional language running on a stack machine (see Section~\ref{sec:background}) with a sophisticated instruction set that includes high-level loops.
-For that reason, we had to develop symbolic execution for Michelson from the ground up.
+While there is already a considerable body of work applying symbolic
+execution to the verification of smart contracts
+\cite{securify,manticore,kevm,park} (see
+Section~\ref{sec:related-work} for details), most of these efforts are
+targeted at Ethereum, where standard techniques for symbolic execution
+of imperative programs are applicable. Such groundwork does not exist
+for Michelson, which is a functional language running on a stack
+machine (see Section~\ref{sec:background}) with a sophisticated
+instruction set that includes high-level loops. For that reason, we
+had to develop symbolic execution for Michelson from scratch.
 
-Besides the Mi-Cho-Coq framework that relies on interactive theorem proving \cite{micho}, HELMHOLTZ \cite{helmholtz} is another automatic verifier for Michelson.
-However, the approach of HELMHOLTZ is significantly different from ours.
-HELMHOLTZ defines a refinement type system to keep track of the properties of values in the storage and on the stack, so that verifying a program corresponds to type-checking against a specification type.
-Furthermore, these tools generally conduct experiments with sample smart contract codes containing about 100 instructions.
-The HELMHOLTZ experiment primarily replicates issues previously identified by Mi-Cho-Coq.
-Although HELMHOLTZ analyzes one real-world contract, it only examines a portion of the code.
-In contrast, our tool is capable of handling entire contracts with hundreds or even thousands of instructions.
+Besides the Mi-Cho-Coq framework that relies on interactive theorem
+proving \cite{micho}, HELMHOLTZ \cite{helmholtz} is another automatic
+verifier for Michelson. However, the approach of HELMHOLTZ is
+significantly different from ours. HELMHOLTZ defines a refinement type
+system to keep track of the properties of values in the storage and on
+the stack, so that verifying a program corresponds to type-checking
+against a specification type.
+Furthermore, the reported experiments with these tools consider sample
+smart contract codes of about 100 instructions. The HELMHOLTZ
+experiments primarily replicate issues previously identified by
+Mi-Cho-Coq. Although HELMHOLTZ analyzes one real-world contract, it
+only examines a portion of the code. In contrast, our tool is capable
+of handling entire contracts with hundreds or even thousands of
+instructions.
 
-SCV utilizes an SMT solver to eliminate invalid states during symbolic execution, addressing the problem of state explosion.
-This capability enabled SCV to conduct two case studies involving real smart contracts that have been operational on the Tezos blockchain for quite some time.
-Despite extensive testing, a flaw was reported in the Kolibri oracle contract.
-In conclusion, SCV streamlines the process of uncovering hidden errors and validating user-defined properties.
-It provides a comprehensive solution to mitigate potential pitfalls in blockchain-based applications.
+SCV utilizes an SMT solver to eliminate invalid states during symbolic
+execution, addressing the problem of state explosion. This capability
+enabled us to conduct two case studies involving real-world smart contracts
+that have been operational on the Tezos blockchain for quite some
+time. Despite extensive testing, a flaw was reported in the Kolibri
+oracle contract. In conclusion, SCV streamlines the process of
+uncovering hidden errors and validating user-defined properties. It
+provides a comprehensive solution to mitigate potential pitfalls in
+blockchain-based applications.
 
@@
 \begin{enumerate}
-\item Design and implementation of the SCV domain specification language.
+\item Design and implementation of the SCV specification language.
 \item Design and implementation of a symbolic interpreter for a significant subset of Michelson. 
-\item Two case studies verifying smart contracts on the Tezos blockchain:
+\item Two case studies verifying smart contracts deployed on the Tezos blockchain:
   \begin{itemize}
@@
 
-Several high-level languages, such as LIGO \cite{ligo}, SmartPy \cite{smartpy}, and Liquidity \cite{liquidity}, provide a more readable syntax resembling popular programming languages.
-This allows developers to write Tezos smart contracts more comfortably.
-Our tools are applicable to all these languages because they compile to Michelson.
+Several high-level languages for smart contracts, such as LIGO
+\cite{ligo}, SmartPy \cite{smartpy}, and Liquidity \cite{liquidity},
+support writing smart contracts for Tezos. Our tools
+are applicable to all these languages because they compile to
+Michelson. 
 \section{Michelson}
@@
 Besides the standard datatypes (e.g., numbers, lists, pairs, sums, functions) with the expected operations, Michelson supports a number of types and operations specific to blockchain applications (e.g., \texttt{mutez} for tokens) as shown in Fig.~\ref{fig:types}, where \textbf{cpt} denotes comparable types.
-The type system does not support quantification over types, and there are no user-defined types.
+The type system does not support quantification over types and there are no user-defined types.
 \begin{figure}[tp]
@@
 Finally, the \lstinline|NIL| instruction pushes an empty list of operations, and \lstinline|PAIR| creates the required pair of type $O^* \times S$.
-
-A contract may have several entrypoints. Entrypoints are encoded by
-using a sum type (call ``or type'' in Michelson). Each (nested) alternative in a sum can be
-given a name, which is used as the name for an entrypoint. A call to
-an entrypoint automatically adds the required \lstinline|LEFT| and
-\lstinline|RIGHT| constructors to the parameter.
 \lstset{language=michelson}
@@
 \end{lstlisting}
+
+A contract may have several entrypoints. Entrypoints are encoded by
+using a sum type (called ``or type'' in Michelson). Each (nested)
+alternative in a sum type can be
+given a name, which is used as the name for an entrypoint. A call to
+an entrypoint automatically adds the required \lstinline|LEFT| and
+\lstinline|RIGHT| constructors of the sum type to the parameter.
 \section{SCV: A Domain Specific Language For Smart Contract Property Specification}
 \label{sec:domain-specific-language}
-SCV contains a domain-specific language to specify smart contract properties, aiming to be user-friendly for non-experts and compatible with SMT solvers. 
+SCV comes with a domain-specific language for specifying smart
+contract properties, which is user-friendly for non-experts and compatible with SMT solvers. 
 \subsection{Basic syntax}
@@
 Figure~\ref{fig:syntax-terms-predicates} contains the syntax of terms: A term \textbf{t} can consist of constants of the sort \text{nat} (natural number), \text{int} (integer), \text{string} (string), and \text{b} (bytes) along with their respective types.
-The type annotation may be omitted except for the type \text{nat} to distinguish it from integers.
+The type annotation may be omitted except for the type \text{nat} to distinguish from integers.
 It also encompasses all blockchain constants \textbf{c}.
@@
 
-Since Michelson operates on a stack, we assume that the input stack and the output stack each have only one element, as specified in the input term and the output term, respectively.
+As Michelson operates on a stack, we assume that the input stack and the output stack each have exactly one element, as specified in the input term and the output term, respectively.
 The syntax allows us to specify either a fragment of Michelson code or a complete program.
@@
 
-The pre and postcondition instances are formulas in first-order logic that can be handled by an SMT solver (specifically, Z3 in our case).
-The specification language is constructed from predicates.
-Formulas used in assertions or added to solvers are terms of Boolean type.
-Non-Boolean terms may also be used, and they can be mixed in any combination where types match appropriately.
-
-Several predefined functions include \text{get\_map(e1, e2)}, which accesses an element in a map.
+The pre- and postcondition instances are formulas in first-order logic that can be handled by an SMT solver (specifically, Z3 in our case). 
+% The specification language is constructed from predicates. Formulas
+% used in assertions or added to solvers are terms of Boolean
+% type. Non-Boolean terms may also be used, and they can be mixed in
+% any combination where types match appropriately. 
+%
+There are several predefined functions including \text{get\_map(e1, e2)}, which accesses an element in a map.
 If there is no key \text{e1} in the map \text{e2}, the function returns \text{None}; otherwise, it returns \text{Some(v)} where $v$ is the mapped value.
@@
 Certain functions are defined as predicates, such as \text{transfer\_token(e1, e2, e3)}.
-This predicate holds true if, after executing the smart contract code, there is an operation in the operation list indicating the transfer of \text{e2} tokens to address \text{e3} along with parameter \text{e1}\footnote{Additional predicates can be straightforwardly added if a mapping to Z3 formulas is defined.}.
+This predicate holds true if, after executing the smart contract code, there is an operation in the operation list indicating the transfer of \text{e2} tokens to address \text{e3} along with parameter \text{e1}\footnote{Additional predicates can be added if a mapping to Z3 formulas is defined.}.
 %\lstset{language=michelson}
@@
 
-In Listing \ref{lst:sub-contract-specification}, the program takes as input a stack with only one
+In Listing \ref{lst:sub-contract-specification}, the program takes as input a stack with one
 element, which is a pair of two integer variables \lstinline/x/ and \lstinline/y/, symbolically specified in the \lstinline|input| field. 
-The specification continues by defining the output term as a variable \lstinline/z/ of interger, and 
-pre and postconditions, where the precondition states the assumption
-that the integer \lstinline/x/ is greater than or equal to  \lstinline/y/. The postcondition asserts that the result
+The specification continues by defining the output term as a variable
+\lstinline/z/ of type integer, a precondition stating
+that the integer \lstinline/x/ is greater than or equal to
+\lstinline/y/, and a postcondition asserting that the result
 \lstinline/z/ is equal to the subtract of
@@
 the life cycle of the auction contract, which is depicted in Figure
-\ref{fig:auction-life-cycle}. Other properties related to the \lstinline|%close| entrypoint and the life cycle are omitted here due to page limits.
+\ref{fig:auction-life-cycle}. Other properties related to the \lstinline|%close| entrypoint and the life cycle are omitted here due to space limitations.
 \begin{figure}[tp]
@@
 \end{mathpar}
-The symbolic interpreter works as a graph with states as nodes and transitions as edges. This representation simplifies performing multi-step subtransitions needed for some operations.
+The symbolic interpreter works on a graph with states as nodes and transitions as edges. This representation simplifies performing multi-step sub-transitions needed for some operations.
 
-The semantics of the symbolic rules for the instructions adhere to the formal definitions of the Michelson language as outlined in \cite{michelson,michelson1}.
+The semantics of the symbolic rules for the instructions adhere to the formal definition of the Michelson language as outlined in \cite{michelson,michelson1}.
 In our model, these instructions are classified based on how we handle them into one-step, multi-step, blockchain, cryptographic, branch, and loop instructions.
@@
     \StateTrans\
-    \{[\INSTRUCTIONONE, \STACK, \PREDICATE\ \Wedge\ \StackOne],   [\INSTRUCTIONTWO, \STACK, \PREDICATE\ \Wedge\ \NEG\
+    \{[\INSTRUCTIONONE; \INSTRUCTION, \STACK, \PREDICATE\ \Wedge\
+    \StackOne],   [\INSTRUCTIONTWO; \INSTRUCTION, \STACK, \PREDICATE\ \Wedge\ \NEG\
    \StackOne]\}} 
@@
 
-Let us first take look at the terminate loops, such as the \ITER\ instruction, which iterates over a
-list. The corresponding typing rule for the \ITER\ instruction is as follows: 
+We first look at the terminating loops, such as the \ITER\ instruction, which iterates over a
+list. The typing rule for the \ITER\ instruction is as follows: 
 \begin{mathpar}
@@
 \label{sec:static-checker-we}
-The architecture of the static checker is illustrated in Figure~\ref{fig:architecture-of-static-checker}.
-Users write specifications in the SCV language, which are then parsed into an Abstract Syntax Tree (AST) in OCaml.
-The input term along with the code is passed to the symbolic interpreter, while the output term and the pre and postconditions are fed to the static checker.
-The symbolic interpreter, which is fully typed and rejects ill-typed programs, then runs symbolic execution on the code with the provided input, where the initial stack is derived from the input term.
+The architecture of the static checker is illustrated in
+Figure~\ref{fig:architecture-of-static-checker}. Users write
+specifications in the SCV language, which are then parsed into an
+Abstract Syntax Tree (AST) in OCaml. The input term along with the
+code is passed to the symbolic interpreter, while the output term and
+the pre- and postconditions are fed to the static checker. The
+symbolic interpreter then runs the code with the provided input, where
+the initial stack is derived from the input term.
 
@@
 
-We have implemented approximately 85\% of the Michelson instructions, including most of the major-use instructions.
-The remaining instructions were not implemented primarily due to time constraints rather than technical limitations.
+We have implemented approximately 85\% of the Michelson instructions,
+including the most frequently used instructions. The remaining instructions were not implemented due to time constraints rather than technical limitations.
 
@@
 \label{sec:output-check}
-For a fragment of Michelson code, the output term of the symbolic execution has the form of a term \Term\ and its type \TY.
-For a complete smart contract, it takes the form \PAIR\ \VOPERATIONLIST\ \VSTORAGE, \TPAIR\ (\TOPERATIONLIST) \TYS, where \VSTORAGE\ represents the storage and \VOPERATIONLIST\ represents the operation list.
-Given an output term specified as $\tau$, the checker scans all reachable final states that do not contain a failwith stack and checks whether $\tau$ matches with the output term.
-In the former case, it matches $\tau$ with the term \Term.
-In the latter case, it matches with \VSTORAGE.
+For a fragment of Michelson code, the output term of the symbolic
+execution has the form of a term \Term\ and its type \TY. For a
+complete smart contract, it takes the form \PAIR\ \VOPERATIONLIST\
+\VSTORAGE, \TPAIR\ (\TOPERATIONLIST) \TYS, where \VOPERATIONLIST\
+represents the operation list and \VSTORAGE\ represents
+the storage. Given
+an output term specified as $\tau$, the checker scans all reachable
+final states that do not contain a failwith stack and checks whether
+$\tau$ matches the output term. In the former case, it matches
+$\tau$ with the term \Term. In the latter case, it matches with
+\VSTORAGE.
 
-For instance, in the \lstinline|sub| contract, the output check ignores the states where the failwith occurs and verifies whether the output term \lstinline|z| matches with the symbolic output term \lstinline/sbvar/ in the other state.
+For instance, in the \lstinline|sub| contract, the output check ignores the states where the failwith occurs and verifies whether the output term \lstinline|z| matches the symbolic output term \lstinline/sbvar/ in the other state.
 It succeeds for this example as expected.
@@
 The static checker includes a feature to generate all fail conditions encountered in a smart contract.
-This tool identifies all instances where execution terminates due to the \FAILWITH\ instruction, collecting the associated path conditions and error messages.
+SCV identifies all instances where execution terminates due to the \FAILWITH\ instruction, collecting the associated path conditions and error messages.
 Users receive a comprehensive report detailing each fail condition along with its corresponding message.
-This capability is particularly powerful for verifying access control properties and other critical aspects across different smart contracts.
+This capability enables verifying access control properties and other critical aspects across different smart contracts.
 
@@
 successful (i.e., without failure) termination. To verify this
-property, the tool explore all the paths $\Pi$ 
+property, the tool explores all the paths $\Pi$ 
 with the path condition $\Theta$ such that ($\bigwedge \Phi_{i}$
@@
 $\Pi$, $\neg$ ($\bigwedge \Phi_{i}$ $\land$ $\Theta$ $\rightarrow \bigwedge \Psi_{j}$) is unsatisfiable in the context given by the input for the entrypoint
-and its final state.
-For example, for the \lstinline/sub/ contract, the failwith branch is discarded because the precondition is not satisfy with the path condition, and then \lstinline/z/ is matched to
+and its final state. For example, for the \lstinline/sub/ contract, the failwith branch is discarded because the precondition does not satisfy the path condition, and then \lstinline/z/ is matched to
 the symbolic variable \lstinline/sbvar/ in the other branch. In this
-example, the checker then verifies that $\neg$ ((\lstinline/x/ $>=$ y) $\land$ (\lstinline/z/
+example, the checker finds that $\neg$ ((\lstinline/x/ $>=$ y) $\land$ (\lstinline/z/
 = \lstinline/x/ $-$ \lstinline/y/) $\rightarrow$ (\lstinline/z/ $=$ \lstinline/x/ $-$ \lstinline/y/) $\land$ (\lstinline/z/ $>=$ 0)) is unsatisfiable.
@@
 \label{sec:life-cycle-check}
-An entrypoint relation can be defined as \lstinline/(%a -> %b) with p/, indicating that after invoking the entrypoint \lstinline/%a/, it is permissible to call the entrypoint \lstinline/%b/ if the condition \lstinline/p/ holds.
-The presence of the keyword \lstinline/not/ at the beginning signals an impossibility.
-Note that \lstinline/with p/ may be omitted when no condition is needed.
+An entrypoint relation can be defined as \lstinline/(%a -> %b) with
+p/, indicating that after invoking the entrypoint \lstinline/%a/, it
+is permissible to call the entrypoint \lstinline/%b/ if the condition
+\lstinline/p/ holds. The presence of the keyword \lstinline/not/ at
+the beginning signals an impossibility. The suffix \lstinline/with p/ may be omitted when no condition is needed.
 
@@
 The goal is to ensure that the implementation aligns with the standard, verifying its correctness.
-USDtz is designed to maintain a stable value by pegging it to a fiat currency like USD or EUR, and it has been operational on the Tezos blockchain for a significant period.
+USDtz is designed to maintain a stable value by pegging it to a fiat currency like USD or EUR.
+It has been operational on the Tezos blockchain for a significant time.
 
@@
 To address this limitation, oracles play a pivotal role in providing external data for smart contracts.
-Since certain essential properties must be satisfied by an oracle contract, including data approvability, this case study illustrates the process of specifying and verifying an oracle contract using SCV, with the Kolibri oracle contract \cite{kolibri} as an example.
+Since certain essential properties must be satisfied by an oracle contract, including data accountability, this case study illustrates the process of specifying and verifying an oracle contract using SCV, with the Kolibri oracle contract \cite{kolibri} as an example.
 
@@
 These properties are checked by using pre and postconditions.
-Futhermore, the critical access control property is that the entrypoints \lstinline/setGovernorContract/ and \lstinline/setMaxDelaySec/ must only be invocable by the governor.
+Furthermore, the critical access control property is that the entrypoints \lstinline/setGovernorContract/ and \lstinline/setMaxDelaySec/ must only be invocable by the governor.
 Any attempts by unauthorized callers to these entrypoints should result in failure.
@@
 
-There are exsiting tools for automated verification include solc-verify \cite{solc}, VerX \cite{verx}, and Oyente \cite{oyente}.
+There are existing tools for automated verification include solc-verify \cite{solc}, VerX \cite{verx}, and Oyente \cite{oyente}.
 solc-verify processes smart contracts written in Solidity and discharges verification conditions using modular program analysis and SMT solvers.

### 2024-10-01 papers/assertion-contract/fc2025/paper.tex
create

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{pgfplots}
\usepackage{array}
\usepackage{booktabs}
\usepackage{tikz}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
%
\usetikzlibrary{shapes.geometric, arrows}
\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=0.6cm,text centered, draw=black, fill=red!30]
\tikzstyle{process} = [rectangle, minimum width=4cm, minimum height=0.8cm, text centered, draw=black, fill=orange!30]
\tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=0.4cm, text centered, draw=black, fill=blue!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

\lstdefinelanguage{solidity}{
  backgroundcolor=\color{pink!20},
  keywords={contract, function, public, int},
  keywordstyle=\bfseries\color{blue},
  commentstyle=\itshape\color{green!40!black},
  basicstyle=\ttfamily,
  morecomment=[l]{//},
  morecomment=[s]{/*}{*/},
  morestring=[b]",
  sensitive=true
}
\begin{document}
%
\title{Contribution Title}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Thi Thu Ha Doan\orcidID{0000-0001-7524-4497}\and Peter Thiemann\orcidID{0000-0002-9000-1239}}
%
\authorrunning{Ha Doan, P. Thiemann}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Freiburg, Germany \\
  \email{\{doanha,thiemann\}@informatik.uni-freiburg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
In certain blockchain scenarios, verifying the properties of parameters may require significant gas costs or be infeasible due to gas limits. This study proposes a distributed verification protocol to address these challenges. The core concept involves offloading the verification process to validators, who attempt to find counterexamples or proofs off-chain. If a counterexample is discovered, it can be submitted for re-verification on-chain. If validated, the parameter is discarded; otherwise, the correctness of the parameter is guaranteed through a proof-of-work incentive mechanism, encouraging validators to participate in the distributed verification process. To implement these ideas, we propose a practical model that also tackles potential security concerns. We developed a prototype of the protocol and conducted a cost analysis, demonstrating its gas efficiency and practical utility.
\keywords{blockchain, off-chain verification, gas optimization, proof-of-work, distributed verification}
\end{abstract}
%
%
%
\section{Introduction}
\label{sec:introduction}
\lstset{language=solidity}
A smart contract is a critical component of blockchain technology, with applications ranging from simple tasks like auctions to more complex systems such as decentralized markets. However, broader adoption of smart contracts faces challenges, with gas costs being among the most significant. Every computation performed by a smart contract on the blockchain incurs a cost, as each unit of computation and storage consumed by an algorithm must be paid for due to the burden it places on the system.

When users (or other contracts) invoke a function in a smart contract, they must provide input data, known as parameters. In many cases, these parameters require verification. For instance, to minimize gas costs, an application might perform some computation off-chain and submit the result as a parameter to a smart contract. Such computations typically assert certain properties of the submitted parameters.

Another scenario involves interactions with external data sources. Since smart contracts cannot directly access off-chain data, blockchain oracles supply this information. When external data becomes available, an oracle invokes a smart contract with the relevant information.

However, while the contract should leverage off-chain computations or external data and assume that the submitted parameters are valid, there is a risk that off-chain computations could be incorrect, submitting invalid parameters, or that oracles could provide faulty data. Therefore, a mechanism is needed to verify these assumptions before the contract begins execution.

Unfortunately, most current applications cannot efficiently verify complex parameters on-chain due to the high gas costs associated with such computations. This limitation restricts many applications that require parameter verification during smart contract execution. The primary goal of this paper is to propose an approach that validates complex parameter assumptions while minimizing gas costs, without sacrificing computational efficiency.

Consider a contract that takes a prime number as a parameter:
\begin{lstlisting}[numbers=none]
contract Example {
  function (int p) public {
    // assume p is prime
    ...
  }
}
\end{lstlisting}
This assumption can be expressed as an explicit assertion in predicate logic:
\begin{gather*}
\label{eq1}
  (\forall n) (2 \leq n \leq \sqrt{p}) \Rightarrow (p \mathbin{\%} n) \ne 0
\end{gather*}
Checking the validity of this assumption requires a loop in the contract. The test would take \(O(\sqrt{p})\) time (assuming constant time for computing the remainder) and produce extra cost linear in \(\sqrt{p}\).

Similarly, consider a contract that requires a sorted array of integers as input:

\begin{lstlisting}[numbers=none]
contract Sorted {
  function find (int[100] a, int v) public {
    // assume a is sorted
  }
}
\end{lstlisting}
The explicit assertion would be:
\begin{gather*}\label{}
  (\forall k) (0\leq k <99) \Rightarrow a[k] \leq a[k+1]
\end{gather*}
This check can be performed in \(O(1)\) time, but the associated constant factor makes it costly.

However, we could do better by recruiting the validators of the contract for a distributed effort to find a counterexample off-chain. To this end, we consider the negation of these assertions.

For the prime number example, the negation is:
\begin{gather*}\label{}
  (\exists n) (2 \leq n \leq \sqrt{p}) \wedge (p \mathbin{\%} n) = 0
\end{gather*}
This assertion can be checked pointwise by having each validator independently choose a random \(n\) fulfilling \(2 \leq n \leq \sqrt{p}\) and checking whether \((p \mathbin{\%} n) = 0\). If the remainder is \(0\), the validator has found a counterexample and submits its veto to the on-chain contract, which then verifies the counterexample. If valid, the contract halts further execution with that parameter. If no counterexample is found, \(p\) is accepted, assuming other validators have checked other points.

For the sorted array example, the negation is:
\begin{gather*}\label{}
  (\exists k) (0\leq k <99) \wedge a[k] > a[k+1]
\end{gather*}
Again, we can have every validator generate a random number \(k\). If the condition is true for such \(k\), the validator has found a counterexample for the sortedness of the array. Otherwise, the validator relies on others to check different indices.

Instead of looping and checking all points on-chain, only one or some points are checked. The checking process can be performed off-chain with no gas cost, and only the result of the verification process needs to be validated on-chain. By shifting much of the verification off-chain, our propsed approach significantly reduces gas costs, as only counterexample verification occurs on-chain.

This approach substantially reduces on-chain gas costs by moving most of the verification work off-chain. However, it introduces challenges related to incentivizing validators, ensuring the cost-effectiveness of on-chain verifications, and providing correctness guarantees when no counterexamples are found.

To address these challenges, we propose a proof-of-work-based incentive mechanism that encourages validator participation and ensures that parameters meet the desired properties with a high level of confidence. The detailed methodology of this approach are discussed in Section \ref{sec:offchain-distributed-verification-approach}.

To realize our novel approach, we propose a practical model that implements the approach and addresses security concerns. We then develop a prototype of the practical model for a decentralized marketplace application using Solidity on the Ethereum blockchain.

The contributions of this paper include:
\begin{itemize}
    \item A novel approach for verifying computationally expensive parameters (in terms of gas cost) for smart contracts on the blockchain.
    \item A proof-of-work-based incentive mechanism that motivates validators to participate in the distributed verification process and ensures the correctness of the submitted parameter with a high expected probability.
    \item A practical model that realizes the proposed novel approach, along with a prototype implementation of the model for a Solidity smart contract application on the Ethereum blockchain.
\end{itemize}

The paper is structured as follows: The next section defines the parameter verification problems and presents use cases. Section \ref{sec:offchain-distributed-verification-approach} proposes the novel approach, while Section \ref{sec:practical-model} introduces its practical model. Section \ref{sec:gas-cost-analysis} analyzes the gas costs, comparing our proposed approach with the on-chain method. Section \ref{sec:prototype-implementation} details the prototype implementation. Section \ref{sec:related-work} discusses related work, and Section \ref{sec:concludes} concludes the paper.
\section{Parameter Assertion Verification On-chain}
\label{sec:parameter-assertion-verification-onchain}
Our work focuses on parameters that are computationally expensive to verify on-chain. Specifically, we address cases where verifying a parameter assertion requires loops within the contract and the assertion can be formalized using universal or existential quantifiers.
\subsection{Parameter Assertion Formalization}
\paragraph{Universal Quantifier Formalization}
An assertion can be formalized using the universal quantifier as follows:
\begin{gather}
  \label{eq:1}
  \forall a \in A. \, P(a)
\end{gather}
This formula can be extended to assertions over multiple domains as:
\begin{gather}
  \label{eq:2}
  \forall a \in A, \, \forall b \in B, \, \dots \, P(a, b, \dots)
\end{gather}
\paragraph{Existential Quantifier Formalization}
In cases where an assertion involves the existence of an element, it can be formalized using existential quantifiers as follows:
\begin{gather}
  \label{eq:3}
  \exists a \in A. \, P(a)
\end{gather}
This formula can also be extended to assertions over multiple domains:
\begin{gather}
  \label{eq:4}
  \exists a \in A, \, \exists b \in B, \, \dots \, P(a, b, \dots)
\end{gather}
\subsection{On-chain Verification}
Verifying these assertions on-chain requires iterating over the domain \(A\) within the contract. For the fomulas \ref{eq:5}, the verification fomulas is as follows.
\begin{gather}
  \label{eq:5}
  \bigwedge_{a \in A} P(a)
\end{gather}
For multiple domains, the verification process becomes:
\begin{gather}
  \label{eq:6}
  \bigwedge_{a \in A, b \in B, \dots} \dots P(a, b, \dots)
\end{gather}
Verifying these assertions in  the existential quantifier formalization requires iterating over the domain \(A\) until finding an element \(a\) that satisfies the predicate:
\begin{gather}
  \label{eq:7}
  \bigvee_{a \in A} P(a)
\end{gather}

For multiple domains, the verification process becomes:
\begin{gather}
  \label{eq:8}
  \bigvee_{a \in A, b \in B, \dots} \dots P(a, b, \dots)
\end{gather}
When the domain \(A\) is large or the predicate \(P\) is complex to evaluate, performing the verification on-chain incurs significant gas costs or even make the verification process infeasible due to gas limits. Given the current high gas prices, this can result in substantial costs.
\subsection{Use Cases}
Smart contract languages like Solidity, Vyper, Michelson, and Plutus support common data types such as numbers, booleans, strings, bytes, arrays, sets, and maps. Many properties of these types can be expressed using universal quantifiers, requiring loops for verification in smart contracts, but can often be disproven by a counterexample or proven with a proof. Below are key properties for each type:
\subsubsection{Numbers}
Number types exhibit some properties that are crucial in cryptographic applications, such as primality and coprimeness. For example, the condition for two numbers \(a\) and \(b\) to be coprime is:
\begin{gather*}
\label{}
(\forall n \in \mathbb{N}) \ (2 \leq n \leq \min(a, b)) \Rightarrow \neg((a \mod n = 0) \wedge (b \mod n = 0))
\end{gather*}
\subsubsection{Booleans}
SAT problems involve determining if there exists an assignment of variables that makes a formula \( F \) in propositional logic true. Verifying if a given assignment satisfies a formula \( F \), which is usually in Conjunctive Normal Form (CNF), requires looping over variables and clauses. Although finding a satisfying assignment is NP-complete, verifying an assignment takes \( O(n \times m) \), where \( n \) is the number of clauses and \( m \) is the number of variables.
\subsubsection{Strings}
String properties that require iteration include uniqueness (no repeated characters), character set membership, lexicographical order, pattern matching, and forbidden substrings. For instance, verifying that a string \(s\) does not contain a forbidden substring \(f\) of length \(k\) can be expressed as:
\begin{gather*}
(\forall i) \ (0 \leq i \leq n - k) \Rightarrow s[i, i+1, \dots, i+k-1] \neq f
\end{gather*}
\subsubsection{Bytes}
Verifying byte arrays often requires loops for properties like uniformity, sorted order, specific byte patterns, uniqueness, valid range, and alternating patterns. For example, to check if all bytes in an array \(b\) lie within a range \([l, u]\), the condition is:
\begin{gather*}
(\forall i) \ (0 \leq i \leq n) \Rightarrow l \leq b[i] \leq u
\end{gather*}
\subsubsection{Arrays (or Lists)}
Common properties of arrays include sortedness, uniqueness, boundedness, monotonicity, symmetry, cyclic structure, and constant values. %A tree-based structure like a max-heap, where each parent node is greater than or equal to its children, can be checked as:
Tree-based structures like heaps can also be built from arrays, with properties such as the heap property. For example, in a max-heap, each parent node is greater than or equal to its children. This property can be expressed as:
\begin{gather*}
(\forall i) \ a[i] \geq a[2i+1] \land a[i] \geq a[2i+2]
\end{gather*}
\subsubsection{Sets}
Set properties like subset verification, disjoint sets, element uniqueness, set equality, and set intersection often require loops. For example, verifying that two sets \(A\) and \(B\) share at least one element can be expressed as:
\begin{gather*}
(\exists a \in A) (\exists b \in B)\ a = b
\end{gather*}
Such properties can be computationally expensive for large sets.
\section{Off-chain Distributed Verification Approach}
\label{sec:offchain-distributed-verification-approach}
\subsection{The Outline of the Approach}
We propose a novel approach for verifying parameter assertions in blockchain-based smart contracts. Our approach distributes the verification process off-chain, submitting only the outcomes to the blockchain for re-verification. This strategy aims to significantly reduce the computational burden on the blockchain while maintaining the integrity of the contract.

Our approach takes into account the key principle that assertions expressed with universal quantifiers can be disproven by counterexamples, while those with existential quantifiers can be proven with valid proofs. These counterexamples or proofs serve as checkpoints, representing specific elements within the domain.

The outline of our approach is as follows:
\paragraph{\textbf{Determine the checkpoint formula.}}
The first step is to establish the checkpoint formula used to identify counterexamples or proofs. For assertions with universal quantifiers, as shown in Equation~\ref{eq:1}, the checkpoint formula is the negation of the original assertion and is expressed using an existential quantifier as follows: 
\begin{gather}
\label{eq:9}
(\exists a \in A) \ \neg P(a)
\end{gather}
For assertions over multiple domains, as in Equation~\ref{eq:2}, the checkpoint formula becomes:
\begin{gather}
\label{eq:10}
(\exists a \in A) (\exists b \in B) \dots  \neg P(a, b, \dots)
\end{gather}
In the case of existential quantifier assertions, as in Equation~\ref{eq:3} and Equation~\ref{eq:4}, the checkpoint formula remains the same as the original assertion.
\paragraph{\textbf{Off-chain distributed effors.}}These checkpoint formulas are then distributed to validators. Off-chain, the validators attempt to find counterexamples or proofs by identifying some \( a \in A \) such that the checkpoint formula is satisfied. For universal quantifier formalizations, this means finding \( a \) where \( \neg P(a) \) holds, and for existential quantifier formalizations, finding \( a \) where \( P(a) \) is true.
\paragraph{\textbf{On-chain re-verification.}} Once a counterexample or proof involving an element \( a \) is found, the validator submits it to the blockchain, where it is re-verified by evaluating \( \neg P(a) \) or \( P(a) \) on-chain. For assertions with universal quantifiers, when a counterexample is successfully verified on-chain, the parameter assertion is proven to be invalid. Otherwise, it is considered valid, assuming that other points are checked by other validators. For assertions with existential quantifiers, the parameter assertion remains invalid until a proof is submitted and successfully re-checked on-chain.
\paragraph{\textbf{Incentivization Mechanism.}} Finding a counterexample or proof incentivizes validators but requires computational resources. However, counterexamples are rare since callers typically avoid submitting invalid parameters to the blockchain. When no counterexample is found, the accuracy of the verification depends on the number of attempts made to check other checkpoints to disprove the assertion. More validators involved in the process increases the confidence in the correctness of the parameter. Therefore, an incentivization mechanism is crucial to guarantee the correctness of the parameter assertion with high confidence in the absence of a counterexample. To encourage participation, validators are rewarded for both finding counterexamples and contributing computational effort. However, counterexample discovery is prioritized with a substantially higher reward compared to providing a computational proof.
%\end{enumerate}

This approach aims to lessen the burden on the blockchain and reduce the high gas costs associated with on-chain verification. Instead of verifying the entire assertion, the smart contract checks only specific points (counterexamples or proofs). By limiting the number of checkpoints verified on-chain, the required gas is significantly lower than if the entire assertion were verified directly.
\subsection{Proof-of-Work-Based Incentivization Mechanism}
The computational effort is represented by a computation proof, which is then submitted on-chain by the validator to claim their reward. This approach encourages participation in the distributed verification process, ensuring thorough validation even without the discovery of counterexamples.

However, significant challenges arise regarding (1) how to recheck the counterexample and the computation efforts on-chain at a reasonable gas cost, (2) how to ensure a significant number of checkpoints have been performed before a computation reward is issued, in order to guarantee an expected probability of correctness for the parameter, and (3) how to ensure that validators actually perform the checkpoint formula off-chain when no counterexample is found but a computation reward is provided.

To overcome these challenges, we propose a proof-of-work-based incentivization mechanism. We utilize the proof-of-work concept by introducing a target hash \( t \), which sets the required difficulty level to earn the computation reward. The basic idea is that each verification process introduces a target hash. The validator attempts to perform the negation check and compute a hash that is less than or equal to the given target hash. The objective of the validator is to find either a counterexample or a computation that produces a hash smaller than or equal to the target hash \( t \).
\subsubsection{Introduce a seed} To recheck the counterexample or computation proof on-chain at a reasonable gas cost, the counterexample or computation proof should be submitted on-chain in the form of the indication of the element \( a \in A \) where the assertion is invalid, in the case of a counterexample. The on-chain re-verification process is then straightforward, simply requiring the evaluation of \( \neg P(a) \).

The next challenge is how to generate a random hash for each computation and devise a computational proof to incentivize computational effort. To address this, we introduce a seed \( s \) in each verification process.

Let \( n \) denote the size of the domain \( A \). 
\begin{gather*}
n = |A|
\end{gather*}
where \(|A| \) denotes the number of elements in the domain $A$.

Each number \( i \) in the range \([1, n]\) corresponds to an element in \( A \). 
\begin{gather*}
a=A[i]
\end{gather*}
where $A[i]$ denotes the $i$-th element in $A$.

The seed \( s \) is a random number. 
\begin{gather*}
s \in \mathbb{N} 
\end{gather*}
The seed $s$  is then reduced with modulo \( n \) to obtain \( i \), which is associated with an element \( a \) in \( A \).
\begin{gather}
\label{eq:11}
i = (s\mod n) + 1
\end{gather}
\subsubsection{Estimate the number of seeds:} To ensure that a sufficient number of checkpoints have been checked before a computational proof is found, we first estimate the number of seeds required to find a counterexample with the desired probability of correctness.

Assuming the unsatisfied element is only the first element \( a_0 \) in \( A \) and the number of seeds is \( m \), each seed independently has a probability of \( \frac{1}{n} \) to detect the issue and \( \frac{n-1}{n} \) not to. If each seed associated with an element \( a \) in \( A \) is chosen uniformly and independently, the probability that no seed checks \( a_0 \) approaches 0 as \( m \) increases:
\begin{gather*}
\lim_{m \to \infty} \frac{(n-1)^m}{n^m} = \lim_{m \to \infty} \left( \frac{n-1}{n} \right)^m = 0
\end{gather*}

To determine the number of seeds needed based on the expected probability of detecting a problem, we define \( p \) as the expected probability of finding at least one counterexample. 
\begin{itemize}
    \item The probability of a single seed failing to find a counterexample is \( \frac{n-1}{n} \).
    \item The probability of all \( m \) seeds failing is \( \left( \frac{n-1}{n} \right)^m \).
    \item Thus, the probability of at least one seed finding a counterexample is:
\begin{gather*}
  p = 1 - \left( \frac{n-1}{n} \right)^m
\end{gather*}
\end{itemize}
Rearranging this gives:
\begin{gather*}
\left( \frac{n-1}{n} \right)^m = 1 - p
\end{gather*}
Taking the natural logarithm:
\begin{gather*}
m \ln\left( \frac{n-1}{n} \right) = \ln(1 - p)
\end{gather*}
Solving for \( m \):
\begin{gather}
\label{eq:12}
m = \frac{\ln(1 - p)}{\ln\left( \frac{n-1}{n} \right)}
\end{gather}

So the number of the seeds to achive the expected propety $p$ is great or at least equal to $m$. Note that, \( p \) represents the probability when only one validator participates. As more validators are involved, the probability of discovering a counterexample increases.
\subsubsection{Set up the taget hash:}
The above number of seed $m$ can then be used to set up the target hash $t$. The target hash $t$ can be calculated based on a desired difficulty level. In proof-of-work systems, difficulty is typically adjusted to ensure that the average efforts to find a valid hash. The target hash $t$ is often calculated by taking the maximum possible hash value and dividing it by the difficulty level.

Given the expected number of seeds to generate, 
the difficulty level \( D \) can be adjusted accordingly. Typically, \( D \) is set to ensure that a valid hash is found approximately once every \( m \) trials.

If we want the probality of finding a valid hash to be $\frac{1}{m}$, then \( D \) equal to \( m \):
\begin{gather}
\label{eq:13}
t = \frac{H_{\text{max}}}{m}
\end{gather}

Where \( H_{\text{max}} \) is the maximum possible hash value and \( m \) is the difficulty level, which can be adjusted based on the expected number of trials.
\subsubsection{Conduct a Computation Hash:} To ensure that a computational proof includes the negation check, the computation of the checkpoint formula is integrated into the proof process. This guarantees that validators must execute the negation check as part of producing the computation proof.

For each element \( a \), let \(\pi_{P_{a}}\) be the function that returns the essential components of evaluating the negation \(\neg P(a)\). The computation hash thus incorporates both the seed \( s \) and \(\pi_{P_{a}}\), ensuring proper validation.

\begin{gather}
\label{eq:14}
t_s = \text{hash}(s, \pi_{P_{a}})
\end{gather}
where \(\text{hash}\) is a cryptographic hash function used to compute the hash value.

Assertions in smart contract languages, such as Solidity and Michelson, are often represented as predicate logic, expressed through Boolean formulas. These are composed of relational operators like \( =, \neq, >, <, \geq, \leq \), logical operators such as \( \neg, \land, \lor\), and corresponding expressions.

Thus, \(\pi_{P_{a}}\) represents the set of expressions involved in evaluating the predicate \(P_a\).
\begin{gather*}
\pi_{P_{a}} = \{ e_1, e_2, \ldots \}
\end{gather*}
where \(e_i\) are the expressions that contribute to the computation of the predicate \(P_a\).

%For example, for each element \( i \), it returns \(a[i]\) and \(a[i + 1]\) in the evaluation of the negation predicate \( a[i] < a[i+1] \) in the sorted array example.

%The expressions $\pi_{P_a}$ can be used to compute the hash, which involves the validator executing the condition check to find a reward computation.
%\begin{equation}
%t_s = \text{hash}(s, \pi_{P_{a}})
%\end{equation}
%where:
%\begin{itemize}
%    \item $s$ is the seed.
%    \item $\pi_{P_{a}}$ is the set of expressions used in the computation of the predicate $P_a$.
%    \item \text{hash} is the hash function that computes the hash based on the seed and the set of expressions $\pi_{P_{a}}$.
%\end{itemize}
\subsection{Off-chain distributed verification}
For applications where the parameter assertion can be expressed using an existential quantifier, the validation process is relatively straightforward. Validators attempt to find a proof off-chain and submit it on-chain, where it is re-verified. If the proof is valid, the parameter is considered correct, and the validator is rewarded.

However, for assertions involving universal quantifiers, the process becomes more complex. First, the size \( n \) of the domain \( A \) is calculated. Then, using the expected probability to ensure the correctness of the parameter assertion in the absence of a counterexample, the target hash is computed. Due to the setup of the target hash, a validator needs to generate approximately \( m \) seeds to have a chance of discovering either a counterexample or a computational proof, thereby confirming the validity or revealing the invalidity of the parameter.

The process of finding a valid seed is outlined in Fig. \ref{fig:find_seed}. During this distributed process, each validator generates a seed \( s \) and performs the negation check until they either identify a counterexample or a computation proof for a reward. Once one of these outcomes is achieved, the validator can submit it on-chain to claim their reward.

Both the counterexample and the computational proof are encoded by the seed, allowing the on-chain component to replicate and verify the result. If the verification is successful, the validator receives the reward.
\begin{figure}[t]
    \centering
\begin{tikzpicture}[node distance=1.2cm]
    % Nodes
    \node (calc_n) [process] {\parbox{4cm}{\centering $n = |A|$ \\ $t_s$}}; 
    \node (start) [startstop, below of=calc_n] {Generate $s$};
    \node (calc_i) [process, below of=start] {\parbox{4cm}{\centering $i = (s \mod n) + 1$ \\ $a = A[i]$}};
    \node (counterexample) [decision, below of=calc_i, yshift=-0.5cm] {$\neg P(a)$};
    \node (calc_hash) [process, below of=counterexample, yshift=-0.5cm] {$t_s = \text{hash}(s, \text{eval}(\neg P(a)))$};
    \node (compare) [decision, below of=calc_hash, yshift=-0.5cm] {$t_s <= t$};
    \node (submit) [startstop, below of=compare, yshift=-0.5cm] {Submit on-chain};
    % Arrows
    \draw [arrow] (calc_n) -- (start);
    \draw [arrow] (start) -- (calc_i);
    \draw [arrow] (calc_i) -- (counterexample);
    \draw [arrow] (counterexample) -- node[midway, above, sloped, anchor=center, yshift=0.5em] {No} (calc_hash);
    \draw [arrow] (calc_hash) -- (compare);
    \draw [arrow] (compare) -- (submit) node[midway, above, sloped, anchor=center, yshift=0.5em] {Yes};
	\draw [arrow] (counterexample.east) -| node[pos=0.25, above] {Yes} ([xshift=2cm]submit.east) |- (submit);
	\draw [arrow] (compare.west) -| node[pos=0.75, left] {No} ([xshift=-2cm]counterexample.west) |- (start);
\end{tikzpicture}
\caption{Finding a reward seed.}
\label{fig:find_seed}
\end{figure}
\subsection{On-chain re-verification}
Given a submitted seed \( s \), the on-chain contract verifies whether the seed produces a counterexample or a valid computational proof eligible for a reward. The verification process follows these steps:
\begin{enumerate}
    \item Compute \( n \), the size of the domain \( A \).
    \item Identify the target value \( t \).
    \item Determine \( i \in [1, n] \) from \( s \) using the modulo operation, and associate \( i \) with the corresponding element \( a \) in \( A \).
    \item Perform the check \( \neg P(a) \) to see if \( a \) is a counterexample.
    \item If no counterexample is found, compute the hash \( t_s \) derived from the seed \( s \).
    \item Compare \( t_s \) to the target hash \( t \) to check if it qualifies for a reward.
\end{enumerate}

Following this process, the contract will either identify a counterexample or compute a hash based on the seed \( s \) and the evaluation \( \neg P(a) \). The computed hash is then compared to the target hash to determine if it qualifies for a reward. The possible outcomes are: finding a counterexample, validating a reward computation, or determining no reward computation.
\section{Practical Model}
\label{sec:practical-model}
\subsection{Security risks}
Off-chain distributed verification of assertions is indeed an intriguing concept, yet it faces the following security risks when proposing an incentive method:

\begin{enumerate}
\item Denial-of-service (DoS) attacks: The system is susceptible to DoS attacks, where a caller inundates the system with numerous invalid parameters, causing congestion and hindering its operation.
\item Front-running attacks: The system is vulnerable to front-running attacks, where an attacker closely monitors the mempool to intercept a seed representing a counterexample or a computation proof, subsequently stealing the reward.
\item Caller exploitation: A caller might exploit the system by running the negation check privately to (1) identify the reward before submitting the parameter on-chain, thereby swiftly claiming the reward ahead of the other validators, (2) fake the compuatation proofs before a counterexample can be found by other validators.
\item Reward manipulation: For a system that allows multiple rewards. A validator may attempt to manipulate the reward system by resubmitting counterexamples or computation proofs multiple times to multiply their rewards.
\end{enumerate}
\subsection{Overview architect}
This section presents a practical model that unifies theoretical principles and addresses the previously mentioned security concerns. The architectural design of this model is depicted in Figure \ref{fig.architect}.  
\subsubsection{Main compoments.} The model consists of two main entities: the on-chain assertion contract and the off-chain validator program.
\paragraph{On-chain assertion contract.}
While additional functions may exist, the assertion contract must encompass the following two essential functions:
\begin{itemize}
\item The \( submit\_parameter \) function: Callers utilize this function to submit their parameters for validation. %Subsequently, the parameter is distributedly verified by validators.
\item  The \( claim\_reward \) function: This function accepts a seed (or may some others) as inputs, yielding a result indicating whether the computation from the seed results in a counterexample, a reward computation, or a non-reward computation.
\end{itemize}
\paragraph{Off-chain validator program.}
Since the off-chain program runs off-chain, it can be implemented according to the validator's preferences. However, the crucial point is that the off-chain contract must use the exact same \( claim\_reward \) function when attempting to find a counterexample or a computation proof. Additionally, it should support a function that assists the validator in finding a seed to earn a reward.
\paragraph{Storage.}
When a parameter is submitted for verification, the following information should be stored:
\begin{itemize}
\item Parameter: this includes the parameter itself. In cases where storing the parameter on-chain is impractical because of its size, it could be possible to store only its hash. Despite this, the hash remains sufficient for validation.
\item Timestamp: this indicates the approximate time when the parameter was submitted.
\end{itemize}
\begin{figure}
\centering
\includegraphics[scale=.8]{assertion}
\caption{The architecture of the practical model}
\label{fig.architect}
\end{figure}

\subsubsection{Deploying and managing on/off-chain contracts.}
On/off-chain contracts are provided and managed by their respective owners. The owner deploys the assertion contract on the blockchain while storing the validator program off the blockchain, thereby ensuring its accessibility to the validators. There are two ways to making these contracts available to validators.
\begin{itemize}
\item The owner stores the codes on a repository accessible to validators, or upon request, provide them directly to validators.
\item The owner broadcards the contracts to the network using messaging systems such as Waku in Ethereum. In this scenario, the interested validators are responsible for locally storing off-chain code.
\end{itemize}
\subsubsection{Submitting a parameter.} 
Before a parameter can be utilized in the actual work function or contract, a caller must initially submit it via the submit-parameter function in the on-chain assertion contract.

Upon the submission of a parameter, an event can be emitted, allowing validators to receive updates by monitoring the blockchain for the parameter submission event. Additionally, the caller may choose to broadcast their parameter to all validators via a messaging system when submitting it online.
\subsubsection{Off-chain verification}
After a parameter is submitted and stored on-chain, a validator can commence the verification process. To assess the validity of a parameter, each validator independently executes the off-chain validation program.

A validator may attempt to try multiple times with different random seeds in order to find either a counterexample or a computational proof. A function called find-seed could be implemented, which in turn calls the claim-reward function to locate a seed.

All events such as parameter submissions, the discovery of a counterexample, or the presentation of computational proofs can be broadcasted to the network using event emission. Validators can monitor these events to stay updated on the verification status in real-time. 
\subsubsection{Calling a work function}
A work function can indeed be encapsulated either as a private function in the assertion contract or implemented in another contract. In this process, a caller initiates the submission of a parameter for verification by invoking the submit-parameter function within the on-chain assertion contract. Upon successful verification of the parameter, a work contract can be triggered to execute the designated task, operating under the assumption of the parameter's validity.

The invocation of the work function or contract is carried out by the on-chain validation contract or a caller. This call is subject to specific requirements being met, ensuring that the task is executed only when the verification process has been successfully completed and the parameter is deemed valid, such as a certain amount of time having passed, no counterexample being found, and receiving enough computation proofs. If all conditions are met, the actual work is executed, and in some application, the record of the parameter may be deleted from memory to free up storage.
\subsection{Security Features}
\subsubsection{DoS attacks}
When submitting the parameter, the caller need to send a deposit stake in the form of a native token. This stake is claimed by a validator who finds a counterexample. This stake returns to the caller when the parameter is verified.

The deposit serves as a deterrent, as in the event of an invalid parameter, the deposit may be forfeited to prevent callers from submitting such parameters solving the DoS attack security risk. 
\subsubsection{Front-running attacks}
While a random number $r$ alone as a seed is sufficient to indicate the associated element $a$ in the domain $A$, to prevent the front-running attack, we enhance the randomness of the seed by combining a random number with the validator's address to calculate the seed. In deeds, the validator's address is converted to numerical values and use these numbers in combination with a random number to compute the seed.

Let's denote the validator's address by $addr$: \(\quad \text{addr} \in \text{Addresses}\)

The address is converted to numerical values.
\begin{equation}
\text{addr\_num} = \text{init256}(\text{addr})
\end{equation}

This combination adds an extra level of security. So even watching the mempool and get the random number, a malicious validators cannot use the same random number $r$  because the combination with their address will not produce the same seed $s$.
\subsubsection{Caller exploitation attack}
A caller may run the validator program for their parameters before submitting it on-chain and the quickly submit it right after submitting the parameters to either get the computation reward or prove the valid of their parameters before  counterexamples found by other validators.

To prevent this security sisk, the block timestamps indicating when the parameter is submitted on the chain is included to calculate the seed. The seed is enhanced by combining a random number with the validator's address and timestamps.

 Let's denote the timestamp by \( t \in \text{Timestamps}\). The seed $s$ is computed by combining these numerical values.
\begin{equation}
s = \text{hash}(r, \text{addr\_num}, t)
\end{equation}
where \(\text{hash}\) is a hash function that takes the three numerical values and returns a numerical value \( s \).
As a result, any attempt to submit manipulated or before-run seeds will fail to produce either a counterexample or reward computation.

Moreover, some application may want to set up a time fame such that a parameter can only valid if this amout of time is passed. This grantee enough time for validators to valide the parameter. Then, the parameter is valid if and only if a certain amount of time having passed, no counterexample being found, and receiving enough computation proofs. 
\subsubsection{Reward manipulation attack}
In some applications, multiple computational proofs may be allowed. There are a record to monitor the progress of the parameter's verification. Namely, it includes the following details of the addresses of the validators and the random number $r$ used in the verification process. This record is crucial for preventing reward manipulation attack as a validator can not reclaim a new reward with the same random number.

The validators' addresses and the random number $r$ play a vital role in preventing reward-manipulation attacks. A validator cannot resubmit with the same $r$. Therefore, this uniqueness prevents validators from submitting the same computation proof or a counterexample multiple times.
\section{Gas Cost Analysis}
\label{sec:gas-cost-analysis}
This section evaluates the cost of the proposed distributed verification method and compares it to traditional on-chain verification.
\subsection{Transaction Execution Costs}
Transaction costs, measured in gas, can be divided into five key components:
\begin{enumerate}
\item Base cost: Fixed cost for initiating a transaction, covering operations like hashing, signature verification, and balance updates. For instance, transferring ETH in Ethereum costs 21,000 gas.
\item Data cost: Gas tied to the size of the transaction’s data payload, with non-zero bytes incurring higher costs than zero bytes.
\item Computational cost: Gas for executing smart contract operations, such as arithmetic, logic, control flow, cryptography, and memory tasks.
\item Storage cost: Higher than computation, as it involves writing to persistent storage. %In Ethereum, writing a new value costs 20,000 gas, updates cost 5,000 gas, and reading costs 100 gas.
\item Refund gas: Gas refunded for specific operations, like using SELFDESTRUCT or resetting storage values to zero.
\end{enumerate}
Thus, the total gas cost (execution cost) includes base, data, computational, and storage costs.
\subsection{Comparative Analysis of On-Chain and Offline Distributed Methods}
We can compare the gas costs of on-chain and off-chain verification by breaking down the components.
\subsubsection{On-chain verification gas costs}
Let \( G_{parameter} \) represent the intrinsic gas cost, which includes the base gas and data cost, primarily dependent on the size of the parameter \( p \). The total on-chain verification gas cost \( G_{on} \), as expressed in Equation \ref{on-gas}, consists of several parts:
\begin{itemize}
    \item The intrinsic gas \( G_{parameter} \),
    \item Optional storage gas \( G_{storage} \) (depending on whether the parameter is stored),
    \item Checking computation gas, which includes \( n \) checks of the parameter, each costing \( G_{check} \), where \( n \) is the size of the parameter,
    \item The gas for executing the actual work computation \( G_{run} \).
\end{itemize}
\begin{equation}
\label{on-gas}
G_{on} = G_{parameter} + [G_{storage}] + n \cdot G_{check} + G_{run}
\end{equation}
If the parameter is invalid, the gas for running the actual computation \( G_{run} \) is not required.
\subsubsection{Off-chain verification gas costs}
For our offline distributed verification method, we consider the gas costs associated with verifying the parameter and performing the actual work. The total cost includes the gas to :
\begin{itemize}
    \item submit the parameter, \( G_{parameter} \),
    \item store the parameter (or its hash), \( G_{storage} \),
    \item submit the seed, \( G_{seed} \),
    \item check the checkpoint corresponding to the seed, \( G_{check} \),
    \item compute the hash and compare it with the target hash, \( G_{hash} \),
    \item run the computation, \( G_{run} \), if the parameter is valid.
\end{itemize}
The total gas cost for the off-chain method is given by Equation \ref{gas-off}:
\begin{equation}
\label{gas-off}
G_{off} = G_{parameter} + G_{storage} + (G_{seed} + G_{check} + G_{hash}) + G_{run}
\end{equation}
\subsubsection{Comparative Analysis}
Let's compare the gas costs of both methods across different factors.

\paragraph*{Intrinsic Cost} Both methods incur the same intrinsic gas cost, \( G_{parameter} \).

\paragraph*{Storage Cost} The on-chain method has an optional storage cost \( [G_{storage}] \), while the offline method always includes \( G_{storage} \), although it may only store the parameter’s hash in some cases.

\paragraph*{Parameter Checking} In the on-chain method, the parameter check costs \( n \cdot G_{check} \), where \( n \) is the parameter size. In the offline method, this cost is reduced to \( G_{check} \).

\paragraph*{Additional Costs in the Offline Method} The offline method incurs additional costs for submitting seeds \( G_{seed} \) and computing/comparing hashes \( G_{hash} \), which the on-chain method does not require.

\paragraph*{Computation Costs} Both methods share the same computation cost, \( G_{run} \).

Let \( G_{base} \) represent the sum of the gas costs for submitting, storing, and running the parameter:

\[
G_{base} = G_{parameter} + [G_{storage}] + G_{run}
\]

Since centralized verification only incurs gas costs, while the distributed process uses a proof-of-work incentive, we convert the reward into gas terms. Let \( G_{reward} \) denote the gas equivalent of the reward for finding a counterexample or computation proof. Let \( G_{proof} \) represent the total gas cost to perform and reward the computation proof:

\[
G_{proof} = G_{seed} + G_{check} + G_{hash} + G_{reward}
\]

If the base gas does not include storage gas, then \( G_{proof} \) will factor it in.

Figure \ref{fig:gas_compare} illustrates the gas consumption for both methods, assuming \( G_{base} \) remains unchanged regardless of parameter size. The red line represents the gas consumed by the on-chain verification method, which scales linearly with the parameter size. The blue line shows the gas cost of the offline distributed method. Initially, when the parameter size is small, the offline method is more costly, but as the parameter size grows, the offline method becomes more efficient.
\begin{figure}
  \centering
  \begin{tikzpicture}
    \begin{axis}[
        title={Gas Consumption Chart},
        xlabel={Parameter size},
        ylabel={Gas},
        grid=both,
        major grid style={line width=.2pt,draw=gray!50},
        minor grid style={line width=.1pt,draw=gray!20},
        xtick={1,2,3,4,5,6,7,8},
        xticklabels={1,2,3,,,,n,},
        ytick={1,2,3,4,5,6,7,8},
        yticklabels={$G_{base} + G_{check}$,$G_{base} + 2 \cdot G_{check}$, $G_{base} + 3 \cdot G_{check}$,,$G_{base}+ G_{proof}$,,$G_{base} + n \cdot G_{check}$,},
    ]
      \addplot[
        color=red,
        mark=square,
        ]
        coordinates {
        (1,1)(2,2)(3,3)(4,4)(5,5)(6,6)(7,7)
        };
         \addplot[
        color=blue,
        mark=square,
        ]
        coordinates {
        (1,5)(2,5)(3,5)(4,5)(5,5)(6,5)(7,5)
        };
    \end{axis}
  \end{tikzpicture}
  \caption{Gas Comparison (Storage)}
  \label{fig:gas_compare}
\end{figure}
The on-Chain Verification Method is more suited for scenarios where all data and checks must be performed directly on the blockchain. It is potentially higher cost due to \( n \cdot G_{check} \) if \( n \) (size of the parameter) is large. It gets worse when the check is complicated and the parameter is larger, which means \( G_{check} \) is high and \( n \) is large.

The proposed offline Distributed Verification Method (\( G_{off} \)) is more efficient for large datasets since it reduces the number of checks. It does incurs additional costs for \( G_{seed} \) and \( G_{hash} \), but these are often outweighed by the savings from reducing the number of checks. The most concern is the cost to store the parameter for the verification process. In case the parameter needs to be stored anyway then there is no need to concern, but for the opposite case, this cost needs to be taken into account when estimating the cost of the method. Consider storing its hash instead since the hash could still be enough to verify the parameter.

Overall, the offline method (\( G_{off} \)) is generally more cost-effective for large parameters as it reduces the number of on-chain checks. However, the exact cost-effectiveness depends on the relative sizes of \( n \), the parameter storing gas, and the specific gas costs of \( G_{seed} \), \( G_{hash} \) and \( G_{reward} \).
\section{Prototype Implementations}
\label{sec:prototype-implementation}
This section discusses the Decentralized Selling Platform (DSP) application. Initially, the application is implemented as a smart contract on the Ethereum blockchain, with the parameter assertion verified directly on-chain. We then demonstrate how our proposed approach can improve (in term of gas save) the implementation by distributing the verification process off-chain.
\subsection{Decentralized Selling Platform}
The DSP application offers a decentralized solution for users to manage and trade items. It enables sellers to create their own platforms, list items, and facilitate transactions with buyers. Sellers can set up platforms, list items with prices, and buyers can purchase directly from these platforms.

Each item consists of:
\begin{itemize}
    \item \texttt{name}: The item's name.
    \item \texttt{forSale}: Boolean indicating if the item is for sale.
    \item \texttt{price}: The item's price in wei.
    \item \texttt{owner}: The item's owner's address.
\end{itemize}

The DSP application provides the following key functions:

\begin{itemize}
    \item \texttt{createSellingPlatform(items)}: Allows users to create a selling platform with the list of items \texttt{items}, provided they pay a fee and the items are sorted by name.
    \item \texttt{buyItem(sellingPlatform, name)}: Lets buyers purchase an item \texttt{name} from a given \texttt{sellingPlatform} if it is for sale and the price is paid. Ownership and funds are transferred accordingly.
    \item \texttt{addNewItem(sellingPlatform, item)}: Enables the platform owner to add a new \texttt{item} to their \texttt{sellingPlatform}, ensuring the list remains sorted.
\end{itemize}

Additional functions, such as \texttt{setForSale} and \texttt{setPrice}, allow item owners to update the sale status and price of their items.

The most critical assertion in the contract is that the list of items must be sorted by name when a seller creates their selling platform. All other functions rely on this assumption, and if the list is not sorted, the operations will fail.
\subsection{Implementation of the Application with On-chain Parameter Verification}
We begin by implementing the application as a smart contract on the Ethereum blockchain, where the parameter assertion is verified directly on-chain.

Each seller manages their own selling platform. In Solidity, this can be implemented using a mapping that associates each seller's address with a list of items:
\begin{lstlisting}[numbers=none]
mapping(address => Item[]) public sellingPlatform;
\end{lstlisting}

Let \( len \) represent the function that returns the size of an item list. The formal assertion of the sorted list using a universal quantifier is given in Equation \ref{eq:1}:
\[
(\forall i) (0 \leq i < len(items) - 1) \Rightarrow items[i].name \leq items[i+1].name
\]

We define a function to check if the list of items is sorted by their names. This function iterates through the list, comparing adjacent elements using the \texttt{compareStrings} function. If any unsorted element is found, the function returns \texttt{false}. Otherwise, it returns \texttt{true} if all items are in order:
\begin{lstlisting}[numbers=none]
for (uint256 i = 0; i < items.length - 1; i++) {
  if (compareStrings(items[i].name, items[i + 1].name) 
     == 1) { return false; }
}
\end{lstlisting}

The \texttt{createSellingPlatform} function calls this sorting check function to ensure that the list of items is sorted before creating the platform.

Other functions mentioned earlier are implemented straightforwardly in the contract, assuming the item list is always sorted.

%all of the functions emit an event when it is successly preform such as new flatform is create or the item is seting for sale. 
\subsection{Applying the Proposed Approach to Off-chain Distributed Verification}
In this section, we demonstrate how to apply our proposed method to implement the DSP application, where the parameter verification process is distributed and moved off-chain.

Instead of verifying the item list \texttt{items} directly on-chain, we offload the verification to a distributed process.

\subsubsection{System Setup}
Following the proposed approach, we first define the key components to set up the system.

\paragraph{Determine the Checkpoint Formula}
The checkpoint formula is derived using Equation \ref{eq:3} as follows:
\[
\exists i, 0 \leq i < len(items) - 1, \; items[i].name > items[i+1].name
\]
This formula identifies any instance where the item list is not sorted by name.

\paragraph{Introduce the Seed}
Given a random seed \( s \), the seed is associated with the \( i+1 \)-th element of the item list, namely \( items[i] \), where \( i = s \mod n \) and \( n \) is the length of the item list.

\paragraph{Estimate the Number of Seeds}
Let \( P \) represent the probability that a computation proof will confirm the item list is sorted. The number of seeds \( m \) is estimated using Equation \ref{eq:12}:
\[
m = \frac{\ln(1 - P)}{\ln\left( \frac{P-1}{P} \right)}
\]
This calculation determines the expected number of seeds required to find a proof.

\paragraph{Set up the Target Hash}
Using a 256-bit hash, the maximum hash value \( H_{\text{max}} \) is \( 2^{256} - 1 \). The target hash \( t \) is computed using \( m \) as follows:
\[
t = \frac{H_{\text{max}}}{m}
\]
This sets the target difficulty for finding a valid proof.

\paragraph{Conduct a Computation Hash}
The negation formula of the parameter assertion is \( items[i].name > items[i+1].name \). The essential components for evaluating the formula for item \( i \) are:
\[
\pi_{P_{a}} = \{ items[i].name, items[i + 1].name \}
\]
To prevent front-running and exploitation attacks, as described in the practical model, the computation hash includes the seed, the validator's address, the timestamp of the item list submission, and the essential evaluation components:
\[
t_s = \text{hash}(s, \text{addr\_num}, t, items[i].name, items[i + 1].name)
\]
This ensures the integrity of the verification process while protecting against attacks.
\subsubsection{On-chain Contract}
As described in the practical model, the system includes two components: the on-chain smart contract and the off-chain verification program. The on-chain contract incorporates all the state variables and functions from the DSP on-chain contract, as described in \ref{}. However, to implement our proposed approach, it includes additional state variables, such as \texttt{probability}, \texttt{minimumDeposit}, \texttt{rewardPrice}, and \texttt{counterexamplePrice}, which are related to the verification and reward mechanism. The contract also contains some extra functions specific to this approach.

When a user invokes the \texttt{createSellingPlatform(items)} function, the item list is submitted and stored as a record with two additional pieces of information. First, a \texttt{timestamp}, indicating when it was submitted, and second, a \texttt{status}, which is a boolean initially set to \texttt{false}. The caller must deposit a certain amount of money for the verification process, which will be forfeited as a penalty if the item list is found to be unsorted.

The parameter (item list) then enters a waiting state to be verified. As long as the \texttt{status} remains \texttt{false}, no actions such as selling or updating the item list can occur. If a counterexample is found, the parameter record is deleted, and the caller incurs a penalty. However, if a computation proof is submitted and successfully verified on-chain, the \texttt{status} switches to \texttt{true}, allowing further actions on the item list, such as sales or updates.

The on-chain contract includes a crucial function named \texttt{claimReward(sellingPlatform, seed)}, which accepts the selling platform address and a seed as inputs. This function checks whether the submission is a counterexample or a valid computation proof. Additionally, the contract includes functions to perform necessary calculations to set up the target hash for verification.

The \texttt{DecentralizedSellingPlatform} contract provides a robust framework for decentralized item trading, incorporating off-chain verification and reward mechanisms to ensure secure, efficient, and fair transactions between sellers and buyers.
\subsubsection{Off-chain program}
\subsubsection{Gas Savings} We conducted experiments based on the size of the item array and compared the gas consumption between on-chain verification and our proposed off-chain approach. The results are shown in Table \ref{gas-save} and illustrated in Figure \ref{gas-compare}. As the size of the item array increases, the gas savings also increase. The data shows that with an array size of only 50, the proposed approach saves approximately 115,328 gas. Naturally, the final savings in terms of the native token depend on the computation reward setup.

The smart contract can be further optimized by handling smaller arrays directly on-chain, while for larger arrays, the off-chain verification approach would be deployed. From this gas savings analysis, it shows that combining on-chain and off-chain methods can be beneficial. Specifically, when a parameter is submitted, if the item array is relatively small, on-chain verification can be sufficient. However, for larger arrays, the verification process should shift off-chain to save on gas costs.
\begin{table}[h]
\label{gas-save}
\centering
\caption{Gas Save}
\begin{tabular}{c|>{\centering\arraybackslash}p{3cm}|>{\centering\arraybackslash}p{3cm}|c}
\toprule
Parameter Size & On-chain & Off-chain & Gas save \\
\midrule
05  &  504225   &  578196   &  -73971   \\
10  &  903555   &  908838   &  -5283   \\
20  &  1842037  &  1804283  &  37754  \\
30  &  2797283  &  2733927  &  63356  \\
50  &  4708543  &  4593215  &  115328 \\
70  &  6714839  &  6545213  &  169626 \\
100 &  9581470  &  9333977  &  247493 \\
120 &  11492538 &  11193157 &  299381 \\
150 &  14359469 &  13981933 &  377536 \\
170 &  16270716 &  15841101 &  429615 \\
200 &  19137934 &  18629877 &  508057 \\
\bottomrule
\end{tabular}
\end{table}

%\begin{tikzpicture}
%\begin{axis}[
%    title={Gas Consumption Comparison},
%    xlabel={Parameter Size},
%    ylabel={Gas Consumption},
%    legend pos=north west,
%    grid=major,
%    width=10cm,
%    height=6cm
%]

% Line 1 data
%\addplot[
%    color=blue,
%    mark=*,
%    ]
%    coordinates {
%    (5, 504225) (10, 903555) (20, 1842037) (30, 2797283) (50, 4708543) (70, 6714839) (100, 9581470) (120, 11492538) (150, 14359469) (170, 16270716) (200, 19137934)
%    };
%    \addlegendentry{On-chain}

% Line 2 data
%\addplot[
%    color=red,
%    mark=square*,
%    ]
%    coordinates {
%    (5, 578196) (10, 908838) (20, 1804283) (30, 2733927) (50, 4593215) (70, 6545213) (100, 9333977) (120, 11193157) (150, 13981933) (170, 15841101) (200, 18629877)
%    };
 %   \addlegendentry{Off-chain}

%\end{axis}
%\end{tikzpicture}

\begin{tikzpicture}
\label{gas-compare}
\begin{axis}[
    title={Amount of Gas Save for off-chain to on-chain },
    xlabel={Parameter Size},
    ylabel={Gas Save},
    legend pos=north west,
    grid=major,
    width=10cm,
    height=6cm
]

% Difference data
\addplot[
    color=green,
    mark=square*,
    ]
    coordinates {
    (5, -73971) (10, -5283) (20, 37754) (30, 63356) (50, 115328) (70, 169626) (100, 247493) (120, 299381) (150, 377536) (170, 429615) (200, 508057)
    };
    \addlegendentry{Off-chain}

\end{axis}
\end{tikzpicture}

\section{Related work}
\label{sec:related-work}
\section{Conclusion}
\label{sec:conclusion}
\newpage
\bibliographystyle{splncs04}
\bibliography{bio}

\end{document}

### 2024-10-08 papers/assertion-contract/fc2025/paper.tex
major revise

@@
 %
-\title{Contribution Title}
+\title{Gas-Efficient Parameter Verification for Blockchain Smart Contracts Using Off-Chain Validators}
 %
-%\titlerunning{Abbreviated paper title}
+\titlerunning{Off-Chain Parameter Verification Approach: Gas-Efficient}
 % If the paper title is too long for the running head, you can set
@@
 However, broader adoption of smart contracts faces challenges, with gas costs being among the most significant.
-Every computation performed by a smart contract on the blockchain incurs a cost, as each unit of computation and storage consumed by an algorithm must be paid for due to the burden it places on the system.
+Every computation performed by a smart contract on the blockchain incurs a cost, as each unit of computation and storage consumed by an algorithm must be paid for due to the burden it places on the system \cite{eth-whitepaper,yellowpaper}.
 
@@
     // assume p is prime 
-    ...
-  }
+  ... }
 }
@@
     // assume a is sorted 
-  }
+  ... } 
 }
@@
 Section \ref{sec:prototype-implementation} details the prototype implementation.
-Section \ref{sec:related-work} discusses related work, and Section \ref{sec:concludes} concludes the paper.
+Section \ref{sec:related-work} discusses related work, and Section \ref{sec:conclusion} concludes the paper.
 \section{Parameter Assertion Verification On-chain}
@@
 Below are key properties for each type:
-\subsubsection{Numbers}
+\paragraph{\textbf{Numbers}}
 Number types exhibit some properties that are crucial in cryptographic applications, such as primality and coprimeness. For example, the condition for two numbers \(a\) and \(b\) to be coprime is:
@@
 \end{gather*}
-\subsubsection{Booleans}
+\paragraph{\textbf{Booleans}}
 SAT problems involve determining if there exists an assignment of variables that makes a formula \( F \) in propositional logic true.
@@
 Although finding a satisfying assignment is NP-complete, verifying an assignment takes \( O(n \times m) \), where \( n \) is the number of clauses and \( m \) is the number of variables.
-\subsubsection{Strings}
+\paragraph{\textbf{Strings}}
 String properties that require iteration include uniqueness (no repeated characters), character set membership, lexicographical order, pattern matching, and forbidden substrings.
@@
 \end{gather*}
-\subsubsection{Bytes}
+\paragraph{\textbf{Bytes}}
 Verifying byte arrays often requires loops for properties like uniformity, sorted order, specific byte patterns, uniqueness, valid range, and alternating patterns.
@@
 \end{gather*}
-\subsubsection{Arrays (or Lists)}
+\paragraph{\textbf{Arrays (or Lists)}}
 Common properties of arrays include sortedness, uniqueness, boundedness, monotonicity, symmetry, cyclic structure, and constant values.
@@
 \end{gather*}
-\subsubsection{Sets}
+\paragraph{\textbf{Sets}}
 Set properties like subset verification, disjoint sets, element uniqueness, set equality, and set intersection often require loops.
@@
 \end{itemize}
-Rearranging this gives:
-\begin{gather*}
-\left( \frac{n-1}{n} \right)^m = 1 - p
-\end{gather*}
-Taking the natural logarithm:
-\begin{gather*}
-m \ln\left( \frac{n-1}{n} \right) = \ln(1 - p)
-\end{gather*}
+%Rearranging this gives:
+%\begin{gather*}
+%\left( \frac{n-1}{n} \right)^m = 1 - p
+%\end{gather*}
+%Taking the natural logarithm:
+%\begin{gather*}
+%m \ln\left( \frac{n-1}{n} \right) = \ln(1 - p)
+%\end{gather*}
 Solving for \( m \):
@@
 \paragraph{On-chain assertion contract.}
-While additional functions may exist, the assertion contract must encompass the following two essential functions:
+While additional functions may exist, the assertion contract must encompass the following two essential functions (or similar functions):
 \begin{itemize}
-\item The \( submit\_parameter \) function: Callers utilize this function to submit their parameters for validation. %Subsequently, the parameter is distributedly verified by validators.
-\item  The \( claim\_reward \) function: This function accepts a seed (or may some others) as inputs, yielding a result indicating whether the computation from the seed results in a counterexample, a reward computation, or a non-reward computation.
+\item The \( submitParameter \) function: Callers utilize this function to submit their parameters for validation. %Subsequently, the parameter is distributedly verified by validators.
+\item  The \( claimReward \) function: This function accepts a seed (or may some others) as inputs, yielding a result indicating whether the computation from the seed results in a counterexample, a reward computation, or a non-reward computation.
 \end{itemize}
@@
 Since the off-chain program runs off-chain, it can be implemented according to the validator's preferences.
-However, the crucial point is that the off-chain contract must use the exact same \( claim\_reward \) function when attempting to find a counterexample or a computation proof.
+However, the crucial point is that the off-chain contract must use the exact same \( claimReward \) function when attempting to find a counterexample or a computation proof.
 Additionally, it should support a function that assists the validator in finding a seed to earn a reward.
+
+All events such as parameter submissions, the discovery of a counterexample, or the presentation of computational proofs can be broadcasted to the network using event emission.
+Validators can monitor these events to stay updated on the verification status in real-time.
 \paragraph{Storage.}
@@
 \centering
-\includegraphics[scale=.8]{assertion}
+\includegraphics[scale=.8]{assertion1}
 \caption{The architecture of the practical model}
@@
 \end{figure}
+\subsubsection{Deploying and managing on/off-chain contracts.}
+The respective owner is responsible for deploying the on-chain contract and ensuring that the off-chain program is accessible to validators.
+There are two approaches to make the program available to validators:
+\begin{itemize}
+   \item The owner may store the program code in a repository that is accessible to validators or provide it directly to them upon request.
+	\item Alternatively, the owner can broadcast the program to the network using messaging systems like Waku in Ethereum, allowing interested validators to store the off-chain code locally.
+\end{itemize}
 
-\subsubsection{Deploying and managing on/off-chain contracts.}
-On/off-chain contracts are provided and managed by their respective owners.
-The owner deploys the assertion contract on the blockchain while storing the validator program off the blockchain, thereby ensuring its accessibility to the validators.
-There are two ways to making these contracts available to validators.
-\begin{itemize}
-\item The owner stores the codes on a repository accessible to validators, or upon request, provide them directly to validators.
-\item The owner broadcards the contracts to the network using messaging systems such as Waku in Ethereum.
-In this scenario, the interested validators are responsible for locally storing off-chain code.
-\end{itemize}
-\subsubsection{Submitting a parameter.} 
-Before a parameter can be utilized in the actual work function or contract, a caller must initially submit it via the submit-parameter function in the on-chain assertion contract.
+%\subsubsection{On and Off.} 
+%Before a parameter can be utilized in the actual work function or contract, a caller must initially submit it via the submit-parameter function in the on-chain assertion contract.
 
-Upon the submission of a parameter, an event can be emitted, allowing validators to receive updates by monitoring the blockchain for the parameter submission event.
+%Upon the submission of a parameter, an event can be emitted, allowing validators to receive updates by monitoring the blockchain for the parameter submission event.
 Additionally, the caller may choose to broadcast their parameter to all validators via a messaging system when submitting it online.
-\subsubsection{Off-chain verification}
-After a parameter is submitted and stored on-chain, a validator can commence the verification process.
+%\subsubsection{Off-chain verification}
+%After a parameter is submitted and stored on-chain, a validator can commence the verification process.
 To assess the validity of a parameter, each validator independently executes the off-chain validation program.
 
-A validator may attempt to try multiple times with different random seeds in order to find either a counterexample or a computational proof.
+%A validator may attempt to try multiple times with different random seeds in order to find either a counterexample or a computational proof.
 A function called find-seed could be implemented, which in turn calls the claim-reward function to locate a seed.
 
-All events such as parameter submissions, the discovery of a counterexample, or the presentation of computational proofs can be broadcasted to the network using event emission.
+%All events such as parameter submissions, the discovery of a counterexample, or the presentation of computational proofs can be broadcasted to the network using event emission.
 Validators can monitor these events to stay updated on the verification status in real-time.
 \subsubsection{Calling a work function}
-A work function can indeed be encapsulated either as a private function in the assertion contract or implemented in another contract.
-In this process, a caller initiates the submission of a parameter for verification by invoking the submit-parameter function within the on-chain assertion contract.
-Upon successful verification of the parameter, a work contract can be triggered to execute the designated task, operating under the assumption of the parameter's validity.
+A work function can be encapsulated as a private function within the assertion contract or implemented in a separate contract.
+A caller submits a parameter for verification through the on-chain assertion contract.
+Once verified, the work contract is triggered to perform its task under the assumption that the parameter is valid.
 
-The invocation of the work function or contract is carried out by the on-chain validation contract or a caller.
-This call is subject to specific requirements being met, ensuring that the task is executed only when the verification process has been successfully completed and the parameter is deemed valid, such as a certain amount of time having passed, no counterexample being found, and receiving enough computation proofs.
-If all conditions are met, the actual work is executed, and in some application, the record of the parameter may be deleted from memory to free up storage.
+The work function or contract is invoked by the on-chain validation contract or caller, but only if specific conditions are met, such as sufficient verification proofs, no counterexamples, and a waiting period.
+Upon fulfilling all requirements, the task is executed, and in some cases, the parameter record may be deleted to free up storage.
 \subsection{Security Features}
 \subsubsection{DoS attacks}
-When submitting the parameter, the caller need to send a deposit stake in the form of a native token.
-This stake is claimed by a validator who finds a counterexample.
-This stake returns to the caller when the parameter is verified.
+When submitting a parameter, the caller must provide a deposit in native tokens.
+This deposit is claimed by a validator if a counterexample is found or returned if the parameter is verified.
+The deposit discourages invalid submissions and mitigates the risk of DoS attacks.
+\subsubsection{Front-running attacks}
+To prevent front-running attacks, the seed \( s \) is calculated by combining a random number \( r \) with the validator's address, rather than using \( r \) alone.
+This approach enhances security, as a malicious validator cannot reuse \( r \) from the mempool - its combination with their own address will yield a different seed \( s \).
 
-The deposit serves as a deterrent, as in the event of an invalid parameter, the deposit may be forfeited to prevent callers from submitting such parameters solving the DoS attack security risk. 
-\subsubsection{Front-running attacks}
-While a random number $r$ alone as a seed is sufficient to indicate the associated element $a$ in the domain $A$, to prevent the front-running attack, we enhance the randomness of the seed by combining a random number with the validator's address to calculate the seed.
-In deeds, the validator's address is converted to numerical values and use these numbers in combination with a random number to compute the seed.
+%While a random number $r$ alone as a seed is sufficient to indicate the associated element $a$ in the domain $A$, to prevent the front-running attack, we enhance the randomness of the seed by combining a random number with the validator's address to calculate the seed.
 
-Let's denote the validator's address by $addr$: \(\quad \text{addr} \in \text{Addresses}\)
+%This combination adds an extra level of security.
+So even watching the mempool and get the random number, a malicious validators cannot use the same random number $r$  because the combination with their address will not produce the same seed $s$.
 
-The address is converted to numerical values.
-\begin{equation}
-\text{addr\_num} = \text{init256}(\text{addr})
-\end{equation}
+ %In deeds, the validator's address is converted to numerical values and use these numbers in combination with a random number to compute the seed.
 
-This combination adds an extra level of security.
+%Let's denote the validator's address by $addr$: \(\quad \text{addr} \in \text{Addresses}\)
+
+%The address is converted to numerical values.
+%\begin{equation}
+%\text{addr\_num} = \text{init256}(\text{addr})
+%\end{equation}
+
+%This combination adds an extra level of security.
 So even watching the mempool and get the random number, a malicious validators cannot use the same random number $r$  because the combination with their address will not produce the same seed $s$.
 \subsubsection{Caller exploitation attack}
-A caller may run the validator program for their parameters before submitting it on-chain and the quickly submit it right after submitting the parameters to either get the computation reward or prove the valid of their parameters before  counterexamples found by other validators.
+%A caller may execute the validator program for their parameters before submitting on-chain, attempting to claim a reward or validate their parameter before others find counterexamples.
+To mitigate the caller exploitation risk, the seed \( s \) is computed using the block timestamp \( t \) indicating when the parameter is submitted, random number \( r \), and validator's address.
+The timestamp \( t \in \text{Timestamps} \) is included to prevent preemptive submission, and the seed \( s \) is calculated as:
+\begin{equation}
+s = \text{hash}(r, \text{addr}, t)
+\end{equation}
+where \(\text{hash}\) is a cryptographic hash function. This ensures that manipulated or pre-run seeds fail to produce counterexamples or rewards.
+%Additionally, applications can enforce a time frame such that a parameter is valid only if enough time has passed for verification.
+A parameter is valid if, after this time, no counterexample is found and sufficient computation proofs are received.
+\subsubsection{Reward manipulation attack}
+In some applications, multiple computational proofs are allowed, and a record is maintained to track the parameter's verification progress.
+This record contains validator addresses and the random number \( r \) used in each verification.
 
-To prevent this security sisk, the block timestamps indicating when the parameter is submitted on the chain is included to calculate the seed.
-The seed is enhanced by combining a random number with the validator's address and timestamps.
-
- Let's denote the timestamp by \( t \in \text{Timestamps}\). The seed $s$ is computed by combining these numerical values.
-\begin{equation}
-s = \text{hash}(r, \text{addr\_num}, t)
-\end{equation}
-where \(\text{hash}\) is a hash function that takes the three numerical values and returns a numerical value \( s \).
-As a result, any attempt to submit manipulated or before-run seeds will fail to produce either a counterexample or reward computation.
-
-Moreover, some application may want to set up a time fame such that a parameter can only valid if this amout of time is passed.
-This grantee enough time for validators to valide the parameter.
-Then, the parameter is valid if and only if a certain amount of time having passed, no counterexample being found, and receiving enough computation proofs.
-\subsubsection{Reward manipulation attack}
-In some applications, multiple computational proofs may be allowed.
-There are a record to monitor the progress of the parameter's verification.
-Namely, it includes the following details of the addresses of the validators and the random number $r$ used in the verification process.
-This record is crucial for preventing reward manipulation attack as a validator can not reclaim a new reward with the same random number.
-
-The validators' addresses and the random number $r$ play a vital role in preventing reward-manipulation attacks.
-A validator cannot resubmit with the same $r$.
-Therefore, this uniqueness prevents validators from submitting the same computation proof or a counterexample multiple times.
+The inclusion of validators' addresses and \( r \) is crucial in preventing reward manipulation, as it ensures that a validator cannot resubmit with the same \( r \), thereby preventing repeated claims for the same computation proof or counterexample.
 \section{Gas Cost Analysis}
@@
 \subsection{Comparative Analysis of On-Chain and Offline Distributed Methods}
-We can compare the gas costs of on-chain and off-chain verification by breaking down the components.
-\subsubsection{On-chain verification gas costs}
-Let \( G_{parameter} \) represent the intrinsic gas cost, which includes the base gas and data cost, primarily dependent on the size of the parameter \( p \).
-The total on-chain verification gas cost \( G_{on} \), as expressed in Equation \ref{on-gas}, consists of several parts:
+We compare the gas costs of on-chain and off-chain verification by breaking down their components.
+\subsubsection{On-chain Verification Gas Costs}
+Let \( G_{parameter} \) represent the intrinsic gas cost, which includes base and data costs, primarily depending on the size of the parameter \( p \).
+The total on-chain gas cost \( G_{on} \), given in Equation \ref{on-gas}, includes:
 \begin{itemize}
-    \item The intrinsic gas \( G_{parameter} \),
-    \item Optional storage gas \( G_{storage} \) (depending on whether the parameter is stored),
-    \item Checking computation gas, which includes \( n \) checks of the parameter, each costing \( G_{check} \), where \( n \) is the size of the parameter,
-    \item The gas for executing the actual work computation \( G_{run} \).
+    \item Intrinsic gas \( G_{parameter} \),
+    \item Optional storage gas \( G_{storage} \),
+    \item Gas for \( n \) parameter checks, each costing \( G_{check} \),
+    \item Execution gas \( G_{run} \), if the parameter is valid.
 \end{itemize}
@@
 \end{equation}
-If the parameter is invalid, the gas for running the actual computation \( G_{run} \) is not required.
-\subsubsection{Off-chain verification gas costs}
-For our offline distributed verification method, we consider the gas costs associated with verifying the parameter and performing the actual work. The total cost includes the gas to :
+
+\subsubsection{Off-chain Verification Gas Costs}
+The off-chain verification gas costs include similar components to on-chain verification but differ in several key aspects.
+Instead of \( n \) parameter checks, only a single check is required.
+Moreover, storage cost \( G_{storage} \) is mandatory, and additional components are needed as follows:
 \begin{itemize}
-    \item submit the parameter, \( G_{parameter} \),
-    \item store the parameter (or its hash), \( G_{storage} \),
-    \item submit the seed, \( G_{seed} \),
-    \item check the checkpoint corresponding to the seed, \( G_{check} \),
-    \item compute the hash and compare it with the target hash, \( G_{hash} \),
-    \item run the computation, \( G_{run} \), if the parameter is valid.
+    \item Submit the seed, \( G_{seed} \),
+    \item Compute and compare the hash, \( G_{hash} \).
 \end{itemize}
-The total gas cost for the off-chain method is given by Equation \ref{gas-off}:
+The total off-chain gas cost is given by Equation \ref{gas-off}:
 \begin{equation}
@@
 \end{equation}
+
 \subsubsection{Comparative Analysis}
-Let's compare the gas costs of both methods across different factors.
+We compare the gas costs of both verification methods.
 
-\paragraph*{Intrinsic Cost} Both methods incur the same intrinsic gas cost, \( G_{parameter} \).
+\paragraph*{Intrinsic Cost} Both methods incur the same intrinsic cost, \( G_{parameter} \).
 
-\paragraph*{Storage Cost} The on-chain method has an optional storage cost \( [G_{storage}] \), while the offline method always includes \( G_{storage} \), although it may only store the parameter’s hash in some cases.
+\paragraph*{Storage Cost} On-chain storage cost \( [G_{storage}] \) is optional, whereas the offline method always includes \( G_{storage} \), which may store only the parameter's hash.
 
-\paragraph*{Parameter Checking} In the on-chain method, the parameter check costs \( n \cdot G_{check} \), where \( n \) is the parameter size.
-In the offline method, this cost is reduced to \( G_{check} \).
+\paragraph*{Parameter Checking} The on-chain method incurs \( n \cdot G_{check} \) for parameter checking, while the offline method reduces this to \( G_{check} \).
 
-\paragraph*{Additional Costs in the Offline Method} The offline method incurs additional costs for submitting seeds \( G_{seed} \) and computing/comparing hashes \( G_{hash} \), which the on-chain method does not require.
+\paragraph*{Additional Costs} The offline method includes costs for seed submission \( G_{seed} \) and hash computation \( G_{hash} \), which are not required on-chain.
 
-\paragraph*{Computation Costs} Both methods share the same computation cost, \( G_{run} \).
+\paragraph*{Computation Costs} Both methods share the computation cost, \( G_{run} \).
 
-Let \( G_{base} \) represent the sum of the gas costs for submitting, storing, and running the parameter:
-
+Define \( G_{base} \) as the sum of submission, storage, and computation costs:
 \[
@@
 
-Since centralized verification only incurs gas costs, while the distributed process uses a proof-of-work incentive, we convert the reward into gas terms.
-Let \( G_{reward} \) denote the gas equivalent of the reward for finding a counterexample or computation proof.
-Let \( G_{proof} \) represent the total gas cost to perform and reward the computation proof:
-
+The offline distributed process uses a proof-of-work incentive; let \( G_{reward} \) be the gas equivalent reward for counterexamples or proofs.
+The total verification cost for proof \( G_{proof} \) is:
 \[
@@
 
-If the base gas does not include storage gas, then \( G_{proof} \) will factor it in.
+Figure \ref{fig:gas_compare} compares gas consumption between methods, with \( G_{base} \) assumed constant.
+The red line (on-chain) scales linearly with parameter size \( n \), while the blue line (offline) initially incurs higher costs but becomes more efficient as \( n \) grows.
 
-Figure \ref{fig:gas_compare} illustrates the gas consumption for both methods, assuming \( G_{base} \) remains unchanged regardless of parameter size.
-The red line represents the gas consumed by the on-chain verification method, which scales linearly with the parameter size.
-The blue line shows the gas cost of the offline distributed method.
-Initially, when the parameter size is small, the offline method is more costly, but as the parameter size grows, the offline method becomes more efficient.
+The on-chain method is best for scenarios requiring direct blockchain checks, but it becomes costly when \( n \) and \( G_{check} \) are large.
+The proposed offline method (\( G_{off} \)) is more efficient for large parameters, despite additional \( G_{seed} \) and \( G_{hash} \) costs, which are often outweighed by savings in reduced checks.
+
+For the offline method, the main concern is \( G_{storage} \).
+If storing the parameter is required, this cost is negligible, but if not, it must be considered, potentially storing only the parameter's hash for verification.
+
+Overall, the offline method (\( G_{off} \)) is generally more cost-effective for large parameters, depending on \( n \), \( G_{storage} \), and specific values of \( G_{seed} \), \( G_{hash} \), and \( G_{reward} \).
 \begin{figure}
@@
   \end{tikzpicture}
-  \caption{Gas Comparison (Storage)}
+  \caption{Gas Cost Comparison}
   \label{fig:gas_compare}
 \end{figure}
-The on-Chain Verification Method is more suited for scenarios where all data and checks must be performed directly on the blockchain.
-It is potentially higher cost due to \( n \cdot G_{check} \) if \( n \) (size of the parameter) is large.
-It gets worse when the check is complicated and the parameter is larger, which means \( G_{check} \) is high and \( n \) is large.
-
-The proposed offline Distributed Verification Method (\( G_{off} \)) is more efficient for large datasets since it reduces the number of checks.
-It does incurs additional costs for \( G_{seed} \) and \( G_{hash} \), but these are often outweighed by the savings from reducing the number of checks.
-The most concern is the cost to store the parameter for the verification process.
-In case the parameter needs to be stored anyway then there is no need to concern, but for the opposite case, this cost needs to be taken into account when estimating the cost of the method.
-Consider storing its hash instead since the hash could still be enough to verify the parameter.
-
-Overall, the offline method (\( G_{off} \)) is generally more cost-effective for large parameters as it reduces the number of on-chain checks.
-However, the exact cost-effectiveness depends on the relative sizes of \( n \), the parameter storing gas, and the specific gas costs of \( G_{seed} \), \( G_{hash} \) and \( G_{reward} \).
 \section{Prototype Implementations}
 \label{sec:prototype-implementation}
-This section discusses the Decentralized Selling Platform (DSP) application.
-Initially, the application is implemented as a smart contract on the Ethereum blockchain, with the parameter assertion verified directly on-chain.
-We then demonstrate how our proposed approach can improve (in term of gas save) the implementation by distributing the verification process off-chain.
+
+This section outlines the implementation of the Decentralized Selling Platform (DSP) application.
+Initially, the application is deployed as a smart contract on the Ethereum blockchain, where the parameter verification is handled directly on-chain.
+We then showcase how the proposed off-chain verification approach can significantly improve the implementation by reducing gas costs.
+
 \subsection{Decentralized Selling Platform}
-The DSP application offers a decentralized solution for users to manage and trade items.
-It enables sellers to create their own platforms, list items, and facilitate transactions with buyers.
+
+The DSP application provides a decentralized framework for users to manage and trade items.
+It allows sellers to establish their own platforms, list items for sale, and facilitate transactions with buyers.
 Sellers can set up platforms, list items with prices, and buyers can purchase directly from these platforms.
 
-Each item consists of:
+Each item in the platform is characterized by:
+
 \begin{itemize}
-    \item \texttt{name}: The item's name.
-    \item \texttt{forSale}: Boolean indicating if the item is for sale.
-    \item \texttt{price}: The item's price in wei.
-    \item \texttt{owner}: The item's owner's address.
+    \item \texttt{product}: A struct representing the product, including its name and producer.
+    \item \texttt{forSale}: A boolean indicating whether the item is available for sale.
+    \item \texttt{price}: The price of the item, specified in wei.
+    \item \texttt{owner}: The Ethereum address of the current item owner.
 \end{itemize}
 
-The DSP application provides the following key functions:
+The DSP application provides several key functions:
 
 \begin{itemize}
-    \item \texttt{createSellingPlatform(items)}: Allows users to create a selling platform with the list of items \texttt{items}, provided they pay a fee and the items are sorted by name.
-    \item \texttt{buyItem(sellingPlatform, name)}: Lets buyers purchase an item \texttt{name} from a given \texttt{sellingPlatform} if it is for sale and the price is paid.
+    \item \texttt{createSellingPlatform(items)}: Allows users to create a selling platform containing a list of items (\texttt{items}), provided they pay the required deposit and ensure the items are sorted by name.
+    \item \texttt{buyItem(sellingPlatform, product)}: Enables buyers to purchase a specified \texttt{product} from a particular \texttt{sellingPlatform}, provided the item is listed for sale and the correct price is paid.
 Ownership and funds are transferred accordingly.
-    \item \texttt{addNewItem(sellingPlatform, item)}: Enables the platform owner to add a new \texttt{item} to their \texttt{sellingPlatform}, ensuring the list remains sorted.
+    \item \texttt{addNewItem(sellingPlatform, item)}: Allows platform owners to add a new \texttt{item} to their \texttt{sellingPlatform}, ensuring the item list remains sorted.
 \end{itemize}
 
-Additional functions, such as \texttt{setForSale} and \texttt{setPrice}, allow item owners to update the sale status and price of their items.
+Additionally, functions like \texttt{setForSale} and \texttt{setPrice} enable item owners to update the sale status and price of their items.
 
-The most critical assertion in the contract is that the list of items must be sorted by name when a seller creates their selling platform.
-All other functions rely on this assumption, and if the list is not sorted, the operations will fail.
+To approximate the behavior of a typical selling platform application, our implementation allows items with the same product name but different producers.
+Additionally, the application provides a search function, \texttt{searchItems}, which enables users to search for items by product name.
+To optimize gas costs for users performing operations such as buying, reselling, updating, or searching items, the item list is maintained in sorted order based on product names.
+
+Therefore, a critical assertion in the contract is that the list of items must be sorted by product name when a seller creates their selling platform.
+All subsequent operations rely on this condition, and if the list is unsorted, these operations will fail.
 \subsection{Implementation of the Application with On-chain Parameter Verification}
-We begin by implementing the application as a smart contract on the Ethereum blockchain, where the parameter assertion is verified directly on-chain.
 
-Each seller manages their own selling platform. In Solidity, this can be implemented using a mapping that associates each seller's address with a list of items:
+We begin by implementing the application as a smart contract on the Ethereum blockchain, where the verification of parameters is conducted directly on-chain.
+
+Each seller manages their own selling platform. In Solidity, this can be achieved using a \texttt{mapping} that associates each seller's address with a list of items:
+
 \begin{lstlisting}[numbers=none]
@@
 
-Let \( len \) represent the function that returns the size of an item list. The formal assertion of the sorted list using a universal quantifier is given in Equation \ref{eq:1}:
+Let \( \text{len} \) represent the function that returns the size of the item list.
+The formal assertion ensuring that the list is sorted, using a universal quantifier, is given by Equation \ref{eq:1}:
 \[
-(\forall i) (0 \leq i < len(items) - 1) \Rightarrow items[i].name \leq items[i+1].name
+(\forall i) (0 \leq i < len(items) - 1) \Rightarrow items[i].product.name \leq items[i+1].product.name
 \]
 
-We define a function to check if the list of items is sorted by their names.
+\label{eq:sorted_assertion}
+
+To verify this, we define a function that checks whether the list of items is sorted by name.
 This function iterates through the list, comparing adjacent elements using the \texttt{compareStrings} function.
 If any unsorted element is found, the function returns \texttt{false}.
-Otherwise, it returns \texttt{true} if all items are in order:
+Otherwise, it returns \texttt{true} if the items are properly ordered:
+
 \begin{lstlisting}[numbers=none]
 for (uint256 i = 0; i < items.length - 1; i++) {
-  if (compareStrings(items[i].name, items[i + 1].name) 
-     == 1) { return false; }
+  if (compareStrings(items[i].product.name, 
+  items[i + 1].product.name) == 1) { return false; }
 }
@@
 
-The \texttt{createSellingPlatform} function calls this sorting check function to ensure that the list of items is sorted before creating the platform.
+The \texttt{createSellingPlatform} function invokes this sorting check to ensure that the item list is ordered before allowing the platform to be created.
 
-Other functions mentioned earlier are implemented straightforwardly in the contract, assuming the item list is always sorted.
+Other functions mentioned previously are implemented in the contract, assuming the item list is always sorted.
+\subsection{Applying the Proposed Approach to Off-chain Distributed Verification}
 
-%all of the functions emit an event when it is successly preform such as new flatform is create or the item is seting for sale. 
-\subsection{Applying the Proposed Approach to Off-chain Distributed Verification}
 In this section, we demonstrate how to apply our proposed method to implement the DSP application, where the parameter verification process is distributed and moved off-chain.
@@
 \[
-\exists i, 0 \leq i < len(items) - 1, \; items[i].name > items[i+1].name
+(\exists i) (0 \leq i < \text{len(items)} - 1) \ \text{items}[i].\text{product.name} > \text{items}[i+1].\text{product.name}
 \]
@@
 \paragraph{Introduce the Seed}
-Given a random seed \( s \), the seed is associated with the \( i+1 \)-th element of the item list, namely \( items[i] \), where \( i = s \mod n \) and \( n \) is the length of the item list.
+Given a random seed \( s \), the seed is associated with the \( i+1 \)-th element of the item list, namely \( \text{items}[i] \), where \( i = s \mod n \) and \( n \) is the length of the item list.
 
@@
 \[
-m = \frac{\ln(1 - P)}{\ln\left( \frac{P-1}{P} \right)}
+m = \frac{\ln(1 - P)}{\ln\left( \frac{P - 1}{P} \right)}
 \]
@@
 \paragraph{Conduct a Computation Hash}
-The negation formula of the parameter assertion is \( items[i].name > items[i+1].name \). The essential components for evaluating the formula for item \( i \) are:
+The essential components for evaluating the negation formula of the parameter assertion for item \( i \) are:
 \[
-\pi_{P_{a}} = \{ items[i].name, items[i + 1].name \}
+\pi_{P_{a}} = \{ \text{items}[i].\text{product.name}, \text{items}[i+1].\text{product.name} \}
 \]
@@
 \[
-t_s = \text{hash}(s, \text{addr\_num}, t, items[i].name, items[i + 1].name)
+t_s = \text{hash}(s, \text{addr}, t, \pi_{P_{a}})
 \]
-This ensures the integrity of the verification process while protecting against attacks.
+This ensures the integrity of the verification process while protecting against these security attacks.
+
 \subsubsection{On-chain Contract}
 As described in the practical model, the system includes two components: the on-chain smart contract and the off-chain verification program.
-The on-chain contract incorporates all the state variables and functions from the DSP on-chain contract, as described in \ref{}.
-However, to implement our proposed approach, it includes additional state variables, such as \texttt{probability}, \texttt{minimumDeposit}, \texttt{rewardPrice}, and \texttt{counterexamplePrice}, which are related to the verification and reward mechanism.
-The contract also contains some extra functions specific to this approach.
+The on-chain contract incorporates all the state variables and functions from the DSP on-chain contract, as described in Section~\ref{}.
+However, to implement our proposed approach, it includes additional state variables and functions, such as \texttt{rewardPrice}, \texttt{counterexamplePrice}, and other extra functions specific to this approach.
 
-When a user invokes the \texttt{createSellingPlatform(items)} function, the item list is submitted and stored as a record with two additional pieces of information.
-First, a \texttt{timestamp}, indicating when it was submitted, and second, a \texttt{status}, which is a boolean initially set to \texttt{false}.
+When a user invokes the \texttt{createSellingPlatform(items)} function, the item list is submitted and stored as a record with two additional pieces of information: a \texttt{timestamp}, indicating when it was submitted, and a \texttt{status}, which is a boolean initially set to \texttt{false}.
 The caller must deposit a certain amount of money for the verification process, which will be forfeited as a penalty if the item list is found to be unsorted.
@@
 The parameter (item list) then enters a waiting state to be verified.
-As long as the \texttt{status} remains \texttt{false}, no actions such as selling or updating the item list can occur.
+As long as the \texttt{status} remains \texttt{false}, no actions, such as selling or updating the item list, can occur.
 If a counterexample is found, the parameter record is deleted, and the caller incurs a penalty.
@@
 The \texttt{DecentralizedSellingPlatform} contract provides a robust framework for decentralized item trading, incorporating off-chain verification and reward mechanisms to ensure secure, efficient, and fair transactions between sellers and buyers.
+
+All of the functions emit an event when they are successfully performed, such as when a new platform is created or an item is set for sale.
 \subsubsection{Off-chain program}
-\subsubsection{Gas Savings} We conducted experiments based on the size of the item array and compared the gas consumption between on-chain verification and our proposed off-chain approach.
+The off-chain program is built using JavaScript with the Ether.js library.
+The program listens for events when a platform is submitted (or created).
+Once this event occurs, it triggers a function that generates a random seed \( s \), which is used to either find a counterexample or compute a valid proof.
+When one of these outcomes is achieved, the program calls the on-chain \texttt{claimReward} function to claim the associated reward.
+\subsubsection{Gas Savings} The on-chain verification contract is avaible at \cite{} and the on-chain contract for our proposed approach is on the blockchain at \cite{}.
+The off-chain program is stored at \ref{}.
+We conducted experiments based on the size of the item array and compared the gas consumption between on-chain verification and our proposed off-chain approach.
 The results are shown in Table \ref{gas-save} and illustrated in Figure \ref{gas-compare}.
@@
 \centering
-\caption{Gas Save}
+\caption{On-chain and Off-chain Parameter Verification Gas Comsuming}
 \begin{tabular}{c|>{\centering\arraybackslash}p{3cm}|>{\centering\arraybackslash}p{3cm}|c}
@@
 \begin{axis}[
-    title={Amount of Gas Save for off-chain to on-chain },
+    title={Gas Save for Off-chain  Approach Compare to On-chain Approach},
     xlabel={Parameter Size},
-    ylabel={Gas Save},
+    ylabel={Gas Amount},
     legend pos=north west,
@@
     };
-    \addlegendentry{Off-chain}
+    \addlegendentry{Gas Save}
 
@@
 \label{sec:related-work}
+
 \section{Conclusion}
 \label{sec:conclusion}
+This paper proposes a method for parameter verification in smart contracts on the blockchain.
+The method addresses the challenge of performing computationally expensive verification processes directly on-chain.
+The core idea is to offload the verification process to an off-chain system, with only the verification results being submitted on-chain.
+To implement this approach, we propose an incentive mechanism that encourages validators to participate in the verification process while ensuring the correctness of the parameters when deemed valid.
+Our gas cost analysis demonstrates the benefits of this approach, particularly when dealing with large parameters that are costly to verify on-chain.
 \newpage

### 2024-10-09 papers/assertion-contract/fc2025/paper.tex
some resivion made

@@
 For assertions with existential quantifiers, the parameter assertion remains invalid until a proof is submitted and successfully re-checked on-chain.
-\paragraph{\textbf{Incentivization Mechanism.}} Finding a counterexample or proof incentivizes validators but requires computational resources.
-However, counterexamples are rare since callers typically avoid submitting invalid parameters to the blockchain.
-When no counterexample is found, the accuracy of the verification depends on the number of attempts made to check other checkpoints to disprove the assertion.
-More validators involved in the process increases the confidence in the correctness of the parameter.
-Therefore, an incentivization mechanism is crucial to guarantee the correctness of the parameter assertion with high confidence in the absence of a counterexample.
-To encourage participation, validators are rewarded for both finding counterexamples and contributing computational effort.
-However, counterexample discovery is prioritized with a substantially higher reward compared to providing a computational proof.
-%\end{enumerate}
+\paragraph{\textbf{Incentivization Mechanism.}} Validators are incentivized to find counterexamples or provide proofs, which require computational resources.
+Since counterexamples are rare (as callers avoid submitting invalid parameters), confidence in correctness grows with more validator attempts at different checkpoints.
+Thus, incentivization is crucial for ensuring correctness in the absence of counterexamples.Validators are rewarded for both finding counterexamples and contributing computational proofs, with  counterexample discovery prioritized through higher rewards.
 
-This approach aims to lessen the burden on the blockchain and reduce the high gas costs associated with on-chain verification.
-Instead of verifying the entire assertion, the smart contract checks only specific points (counterexamples or proofs).
-By limiting the number of checkpoints verified on-chain, the required gas is significantly lower than if the entire assertion were verified directly.
+This approach reduces the blockchain's burden and lowers gas costs by verifying only specific checkpoints, rather than performing full on-chain verification.
 \subsection{Proof-of-Work-Based Incentivization Mechanism}
@@
 We compare the gas costs of both verification methods.
-
-\paragraph*{Intrinsic Cost} Both methods incur the same intrinsic cost, \( G_{parameter} \).
-
-\paragraph*{Storage Cost} On-chain storage cost \( [G_{storage}] \) is optional, whereas the offline method always includes \( G_{storage} \), which may store only the parameter's hash.
-
-\paragraph*{Parameter Checking} The on-chain method incurs \( n \cdot G_{check} \) for parameter checking, while the offline method reduces this to \( G_{check} \).
-
-\paragraph*{Additional Costs} The offline method includes costs for seed submission \( G_{seed} \) and hash computation \( G_{hash} \), which are not required on-chain.
-
-\paragraph*{Computation Costs} Both methods share the computation cost, \( G_{run} \).
+Both methods incur the same intrinsic cost, \( G_{parameter} \).
+On-chain storage cost \( [G_{storage}] \) is optional, whereas the offline method always includes \( G_{storage} \), which may store only the parameter's hash.
+The on-chain method incurs \( n \cdot G_{check} \) for parameter checking, while the offline method reduces this to \( G_{check} \).
+The offline method includes costs for seed submission \( G_{seed} \) and hash computation \( G_{hash} \), which are not required for the on-chain method.
+Finally, both methods share the computation cost, \( G_{run} \).
 
@@
 \label{sec:prototype-implementation}
-
-This section outlines the implementation of the Decentralized Selling Platform (DSP) application.
-Initially, the application is deployed as a smart contract on the Ethereum blockchain, where the parameter verification is handled directly on-chain.
-We then showcase how the proposed off-chain verification approach can significantly improve the implementation by reducing gas costs.
-
+This section presents the implementation of the Decentralized Selling Platform (DSP) application.
+Initially, the DSP is deployed as a smart contract on the Ethereum blockchain, where parameter verification occurs on-chain.
+We then demonstrate how an off-chain verification approach can significantly reduce gas costs.
 \subsection{Decentralized Selling Platform}
-
-The DSP application provides a decentralized framework for users to manage and trade items.
-It allows sellers to establish their own platforms, list items for sale, and facilitate transactions with buyers.
-Sellers can set up platforms, list items with prices, and buyers can purchase directly from these platforms.
+The DSP application provides a decentralized framework for managing and trading items.
+Sellers can create platforms, list items, and facilitate buyer transactions.
+Buyers can directly purchase items listed for sale.
 
 Each item in the platform is characterized by:
-
 \begin{itemize}
@@
 \end{itemize}
+The DSP application provides several key functions:
+\begin{itemize}
+    \item \texttt{createSellingPlatform(items)}: Creates a selling platform with a list of sorted items.
+    \item \texttt{buyItem(sellingPlatform, product)}: Enables buyers to purchase an item if listed for sale at the correct price, with ownership and funds transferred.
+    \item \texttt{addNewItem(sellingPlatform, item)}: Adds a new \texttt{item} to an existing platform, keeping the list sorted.
+\end{itemize}
+Additional functions like \texttt{setForSale} and \texttt{setPrice} allow item owners to update the sale status and price.
+To approximate the behavior of a typical selling platform, our implementation permits items with the same product name but different producers.
+The \texttt{searchItems} function allows users to search by product name.
 
-The DSP application provides several key functions:
-
-\begin{itemize}
-    \item \texttt{createSellingPlatform(items)}: Allows users to create a selling platform containing a list of items (\texttt{items}), provided they pay the required deposit and ensure the items are sorted by name.
-    \item \texttt{buyItem(sellingPlatform, product)}: Enables buyers to purchase a specified \texttt{product} from a particular \texttt{sellingPlatform}, provided the item is listed for sale and the correct price is paid.
-Ownership and funds are transferred accordingly.
-    \item \texttt{addNewItem(sellingPlatform, item)}: Allows platform owners to add a new \texttt{item} to their \texttt{sellingPlatform}, ensuring the item list remains sorted.
-\end{itemize}
-
-Additionally, functions like \texttt{setForSale} and \texttt{setPrice} enable item owners to update the sale status and price of their items.
-
-To approximate the behavior of a typical selling platform application, our implementation allows items with the same product name but different producers.
-Additionally, the application provides a search function, \texttt{searchItems}, which enables users to search for items by product name.
-To optimize gas costs for users performing operations such as buying, reselling, updating, or searching items, the item list is maintained in sorted order based on product names.
-
-Therefore, a critical assertion in the contract is that the list of items must be sorted by product name when a seller creates their selling platform.
-All subsequent operations rely on this condition, and if the list is unsorted, these operations will fail.
+To optimize gas costs for buying, reselling, updating, and searching, the item list is kept sorted by product name.
+Therefore, a critical requirement is that items must be sorted when creating a selling platform.
+If the list is unsorted, all related operations will fail.
 \subsection{Implementation of the Application with On-chain Parameter Verification}
-
 We begin by implementing the application as a smart contract on the Ethereum blockchain, where the verification of parameters is conducted directly on-chain.
@@
 
-Let \( \text{len} \) represent the function that returns the size of the item list.
-The formal assertion ensuring that the list is sorted, using a universal quantifier, is given by Equation \ref{eq:1}:
+To ensure the list is sorted, let \( \text{len} \) be the function that returns the size of the item list. The formal assertion using a universal quantifier given by Equation \ref{eq:1} is as follows:
 \[
@@
 \]
-
-\label{eq:sorted_assertion}
 
@@
 Otherwise, it returns \texttt{true} if the items are properly ordered:
-
 \begin{lstlisting}[numbers=none]
@@
 \end{lstlisting}
+The \texttt{createSellingPlatform} function invokes this check to verify sorting before platform creation.
+Other functions mentioned previously are implemented in the contract, assuming  the list remains sorted.
 
-The \texttt{createSellingPlatform} function invokes this sorting check to ensure that the item list is ordered before allowing the platform to be created.
+All functions emit events when successfully performed, such as platform creation or item updates.
+\subsection{Applying the Proposed Approach to Off-chain Distributed Verification}
+This section presents the implementation of the DSP application using the proposed off-chain distributed verification.
+\subsubsection{System Setup}
+Following the proposed approach, we define the key components to set up the system. 
+\paragraph{Checkpoint Formula}
+The checkpoint formula for identifying unsorted items, given by Equation \ref{eq:3}, is:
+\[
+(\exists i) \; (0 \leq i < \text{len(items)} - 1) \ \text{items}[i].\text{product.name} > \text{items}[i+1].\text{product.name}
+\]
+\paragraph{Introduce the Seed}
+The seed \( s \) is associated with the \( i+1 \)-th element of the item list, where \( i = s \mod n \) and \( n \) is the length of the list.
 
-Other functions mentioned previously are implemented in the contract, assuming the item list is always sorted.
-\subsection{Applying the Proposed Approach to Off-chain Distributed Verification}
-
-In this section, we demonstrate how to apply our proposed method to implement the DSP application, where the parameter verification process is distributed and moved off-chain.
-
-Instead of verifying the item list \texttt{items} directly on-chain, we offload the verification to a distributed process.
-
-\subsubsection{System Setup}
-Following the proposed approach, we first define the key components to set up the system.
-
-\paragraph{Determine the Checkpoint Formula}
-The checkpoint formula is derived using Equation \ref{eq:3} as follows:
-\[
-(\exists i) (0 \leq i < \text{len(items)} - 1) \ \text{items}[i].\text{product.name} > \text{items}[i+1].\text{product.name}
-\]
-This formula identifies any instance where the item list is not sorted by name.
-
-\paragraph{Introduce the Seed}
-Given a random seed \( s \), the seed is associated with the \( i+1 \)-th element of the item list, namely \( \text{items}[i] \), where \( i = s \mod n \) and \( n \) is the length of the item list.
-
-\paragraph{Estimate the Number of Seeds}
-Let \( P \) represent the probability that a computation proof will confirm the item list is sorted. The number of seeds \( m \) is estimated using Equation \ref{eq:12}:
+\paragraph{Number of Seeds}
+The expected number of seeds \( m \) is estimated using Equation \ref{eq:12}, where \( P \) represents the given expected probability:
 \[
@@
 \]
-This calculation determines the expected number of seeds required to find a proof.
 
-\paragraph{Set up the Target Hash}
-Using a 256-bit hash, the maximum hash value \( H_{\text{max}} \) is \( 2^{256} - 1 \). The target hash \( t \) is computed using \( m \) as follows:
+\paragraph{Target Hash}
+The target hash \( t \) is computed using a 256-bit maximum hash value \( H_{\text{max}} = 2^{256} - 1 \):
 \[
@@
 \]
-This sets the target difficulty for finding a valid proof.
 
-\paragraph{Conduct a Computation Hash}
-The essential components for evaluating the negation formula of the parameter assertion for item \( i \) are:
+\paragraph{Computation Hash}
+The negation formula components for item \( i \) are:
 \[
@@
 \]
-This ensures the integrity of the verification process while protecting against these security attacks.
+\subsubsection{On-chain Contract}
+The system consists of an on-chain smart contract and an off-chain verification program.
+The on-chain contract extends the DSP contract (Section~\ref{}) with additional variables and functions, such as \texttt{rewardPrice} and \texttt{counterexamplePrice}, to support off-chain verification.
 
-\subsubsection{On-chain Contract}
-As described in the practical model, the system includes two components: the on-chain smart contract and the off-chain verification program.
-The on-chain contract incorporates all the state variables and functions from the DSP on-chain contract, as described in Section~\ref{}.
-However, to implement our proposed approach, it includes additional state variables and functions, such as \texttt{rewardPrice}, \texttt{counterexamplePrice}, and other extra functions specific to this approach.
+When \texttt{createSellingPlatform(items)} is invoked, the item list is submitted with a \texttt{timestamp} and \texttt{status}, initially set to \texttt{false}.
+The caller deposits funds, forfeited if the item list is unsorted.
+The parameter waits in this state until verified.
+If a counterexample is found, the record is deleted, and the caller incurs a penalty.
+If verified successfully, \texttt{status} switches to \texttt{true}, enabling further actions, such as sales or updates.
 
-When a user invokes the \texttt{createSellingPlatform(items)} function, the item list is submitted and stored as a record with two additional pieces of information: a \texttt{timestamp}, indicating when it was submitted, and a \texttt{status}, which is a boolean initially set to \texttt{false}.
-The caller must deposit a certain amount of money for the verification process, which will be forfeited as a penalty if the item list is found to be unsorted.
-
-The parameter (item list) then enters a waiting state to be verified.
-As long as the \texttt{status} remains \texttt{false}, no actions, such as selling or updating the item list, can occur.
-If a counterexample is found, the parameter record is deleted, and the caller incurs a penalty.
-However, if a computation proof is submitted and successfully verified on-chain, the \texttt{status} switches to \texttt{true}, allowing further actions on the item list, such as sales or updates.
-
-The on-chain contract includes a crucial function named \texttt{claimReward(sellingPlatform, seed)}, which accepts the selling platform address and a seed as inputs.
-This function checks whether the submission is a counterexample or a valid computation proof.
-Additionally, the contract includes functions to perform necessary calculations to set up the target hash for verification.
-
-The \texttt{DecentralizedSellingPlatform} contract provides a robust framework for decentralized item trading, incorporating off-chain verification and reward mechanisms to ensure secure, efficient, and fair transactions between sellers and buyers.
-
-All of the functions emit an event when they are successfully performed, such as when a new platform is created or an item is set for sale.
+The contract includes the \texttt{claimReward(sellingPlatform, seed)} function, which checks if the submission is a counterexample or a valid proof. 
 \subsubsection{Off-chain program}
@@
 When one of these outcomes is achieved, the program calls the on-chain \texttt{claimReward} function to claim the associated reward.
-\subsubsection{Gas Savings} The on-chain verification contract is avaible at \cite{} and the on-chain contract for our proposed approach is on the blockchain at \cite{}.
+\subsection{Gas Savings}
+The on-chain verification contract is deployed at \cite{}, while the proposed on-chain contract is available at \cite{}.
 The off-chain program is stored at \ref{}.
-We conducted experiments based on the size of the item array and compared the gas consumption between on-chain verification and our proposed off-chain approach.
-The results are shown in Table \ref{gas-save} and illustrated in Figure \ref{gas-compare}.
-As the size of the item array increases, the gas savings also increase.
-The data shows that with an array size of only 50, the proposed approach saves approximately 115,328 gas.
-Naturally, the final savings in terms of the native token depend on the computation reward setup.
+We conducted experiments to compare gas consumption between on-chain verification and the proposed off-chain approach, based on item list size.
+The results are presented in Table \ref{gas-save} and illustrated in Figure \ref{gas-compare}.
+As the item list size increases, gas savings also increase; for instance, with an array size of 50, the proposed approach saves approximately 115,328 gas.
+Actual savings in native tokens depend on the computation reward setup.
 
-The smart contract can be further optimized by handling smaller arrays directly on-chain, while for larger arrays, the off-chain verification approach would be deployed.
-From this gas savings analysis, it shows that combining on-chain and off-chain methods can be beneficial.
-Specifically, when a parameter is submitted, if the item array is relatively small, on-chain verification can be sufficient.
-However, for larger arrays, the verification process should shift off-chain to save on gas costs.
+This smart contract application can be optimized by using on-chain verification for smaller lists and off-chain verification for larger ones.
+This hybrid approach can provide optimal gas efficiency: on-chain verification is sufficient for small item lists, while shifting to off-chain verification for larger lists significantly reduces gas costs.
+
 \begin{table}[h]
@@
 \end{table}
-
-%\begin{tikzpicture}
-%\begin{axis}[
-%    title={Gas Consumption Comparison},
-%    xlabel={Parameter Size},
-%    ylabel={Gas Consumption},
-%    legend pos=north west,
-%    grid=major,
-%    width=10cm,
-%    height=6cm
-%]
-
-% Line 1 data
-%\addplot[
-%    color=blue,
-%    mark=*,
-%    ]
-%    coordinates {
-%    (5, 504225) (10, 903555) (20, 1842037) (30, 2797283) (50, 4708543) (70, 6714839) (100, 9581470) (120, 11492538) (150, 14359469) (170, 16270716) (200, 19137934)
-%    };
-%    \addlegendentry{On-chain}
-
-% Line 2 data
-%\addplot[
-%    color=red,
-%    mark=square*,
-%    ]
-%    coordinates {
-%    (5, 578196) (10, 908838) (20, 1804283) (30, 2733927) (50, 4593215) (70, 6545213) (100, 9333977) (120, 11193157) (150, 13981933) (170, 15841101) (200, 18629877)
-%    };
- %   \addlegendentry{Off-chain}
-
-%\end{axis}
-%\end{tikzpicture}
 
@@
 \label{sec:related-work}
-
 \section{Conclusion}
@@
 \bibliography{bio}
-
 \end{document}

### 2024-10-10 papers/assertion-contract/fc2025/paper.tex
Update citations and related work section

@@
 \lstset{language=solidity}
-A smart contract is a critical component of blockchain technology, with applications ranging from simple tasks like auctions to more complex systems such as decentralized markets.
+A smart contract \cite{szabo1997smartcontracts,eth-whitepaper,tezos-whitepaper} is a critical component of blockchain technology, with applications ranging from simple tasks like auctions to more complex systems such as decentralized markets.
 However, broader adoption of smart contracts faces challenges, with gas costs being among the most significant.
-Every computation performed by a smart contract on the blockchain incurs a cost, as each unit of computation and storage consumed by an algorithm must be paid for due to the burden it places on the system \cite{eth-whitepaper,yellowpaper}.
+Every computation performed by a smart contract on the blockchain incurs a cost, as each unit of computation and storage consumed by an algorithm must be paid for due to the burden it places on the system \cite{eth-whitepaper,eth-yellowpaper,gas-cost}.
 
@@
 Another scenario involves interactions with external data sources.
-Since smart contracts cannot directly access off-chain data, blockchain oracles supply this information.
+Since smart contracts cannot directly access off-chain data, blockchain oracles \cite{blockchain-oracles,oracle-patterns,astraea,chainlink-whitepaper} supply this information.
 When external data becomes available, an oracle invokes a smart contract with the relevant information.
@@
 \subsection{Use Cases}
-Smart contract languages like Solidity, Vyper, Michelson, and Plutus support common data types such as numbers, booleans, strings, bytes, arrays, sets, and maps.
+Smart contract languages like Solidity \cite{solidity}, Vyper \cite{vyper}, Michelson \cite{michelson,michelson1}, and Plutus \cite{plutus} support common data types such as numbers, booleans, strings, bytes, arrays, sets, and maps.
 Many properties of these types can be expressed using universal quantifiers, requiring loops for verification in smart contracts, but can often be disproven by a counterexample or proven with a proof.
@@
 To overcome these challenges, we propose a proof-of-work-based incentivization mechanism.
-We utilize the proof-of-work concept by introducing a target hash \( t \), which sets the required difficulty level to earn the computation reward.
+We utilize the proof-of-work concept \cite{dwork1992pow,nakamoto2008bitcoin} by introducing a target hash \( t \), which sets the required difficulty level to earn the computation reward.
 The basic idea is that each verification process introduces a target hash.
@@
 \end{gather}
-\subsubsection{Estimate the number of seeds:} To ensure that a sufficient number of checkpoints have been checked before a computational proof is found, we first estimate the number of seeds required to find a counterexample with the desired probability of correctness.
+\subsubsection{Estimate the number of seeds:} To ensure that a sufficient number of checkpoints have been checked before a computational proof is found, we first estimate the number of seeds required to find a counterexample with the desired probability of correctness \cite{ross2014probability,feller1968probability}.
 
@@
 \subsubsection{Set up the taget hash:}
-The above number of seed $m$ can then be used to set up the target hash $t$.
+The above number of seed $m$ can then be used to set up the target hash \cite{nakamoto2008bitcoin,bonneau2015sok}.
 The target hash $t$ can be calculated based on a desired difficulty level.
@@
 \subsection{Transaction Execution Costs}
-Transaction costs, measured in gas, can be divided into five key components:
+Transaction costs \cite{eth-yellowpaper,chen2019underoptimized,victor2019measuring}, measured in gas, can be divided into five key components:
 \begin{enumerate}
@@
 \label{sec:related-work}
+Smart contracts have been widely adopted to automate and secure decentralized applications.
+However, intensive on-chain computation can lead to high gas costs or exceed gas limits.
+To address this, many approaches focus on moving computations off-chain and distributing the verification process.
+
+Layer 2 solutions like Plasma \cite{plasma-whitepaper} move heavy computation to a separate child chain anchored to the Ethereum Mainnet, improving scalability but not suited for parameter verification.
+More recently, optimistic rollups \cite{optimisticrollups} and zk-rollups \cite{zkrollups} emerged, offloading computation while preserving security.
+Optimistic rollups allow challenges through fraud proofs, similar to our counterexample mechanism, while zk-rollups use cryptographic proofs.
+However, both focus on transaction throughput, not complex parameter verification.
+
+Decentralized oracle networks like Chainlink \cite{chainlink} enable off-chain data validation but are designed for fetching external data, not parameter verification.
+Their incentive model also differs from our proof-of-work mechanism.
+
+zk-SNARKs and zk-STARKs \cite{groth2016snarks} allow efficient on-chain verification but are computationally demanding, making them impractical for continuous validation.
+Privacy-focused solutions like Hawk \cite{7546538} leverage hybrid on-chain/off-chain computation, aligning with our approach.
+Arbitrum \cite{10.5555/3277203.3277305} also supports off-chain computation, but primarily at the consensus level.
+
+Our work builds on these foundations by proposing a distributed, incentive-driven off-chain verification model to improve gas efficiency and enable counterexample searches.
+Unlike prior approaches, our method focuses on parameter verification using a distributed network of validators.
+The proof-of-work mechanism incentivizes validators, ensuring correctness without the high costs of on-chain verification.
 \section{Conclusion}

### 2024-10-12 papers/assertion-contract/fc2025/paper.tex
submitted version

@@
 %
-\author{Thi Thu Ha Doan\orcidID{0000-0001-7524-4497}\and Peter Thiemann\orcidID{0000-0002-9000-1239}}
+%\author{Thi Thu Ha Doan\orcidID{0000-0001-7524-4497}\and Peter Thiemann\orcidID{0000-0002-9000-1239}}
 %
-\authorrunning{Ha Doan, P. Thiemann}
+%\authorrunning{Ha Doan, P. Thiemann}
 % First names are abbreviated in the running head.
@@
 %
-\institute{University of Freiburg, Germany \\
-  \email{\{doanha,thiemann\}@informatik.uni-freiburg.de}}
+%\institute{University of Freiburg, Germany \\
+%  \email{\{doanha,thiemann\}@informatik.uni-freiburg.de}}
 %
@@
 If validated, the parameter is discarded; otherwise, the correctness of the parameter is guaranteed through a proof-of-work incentive mechanism, encouraging validators to participate in the distributed verification process.
-To implement these ideas, we propose a practical model that also tackles potential security concerns.
+To implement these ideas, we propose a practical model that tackles potential security concerns.
 We developed a prototype of the protocol and conducted a cost analysis, demonstrating its gas efficiency and practical utility.
@@
     // assume p is prime 
-  ... }
-}
+  ... }}
 \end{lstlisting}
@@
 
-Similarly, consider a contract that requires a sorted array of integers as input:
-
-\begin{lstlisting}[numbers=none]
-contract Sorted {
-  function find (int[100] a, int v) public {
-    // assume a is sorted 
-  ... } 
-}
-\end{lstlisting}
+Similarly, consider a contract that requires a sorted array \(a\)  of the size \(n\)  of integers as input. 
+%\begin{lstlisting}[numbers=none]
+%contract Sorted {
+%  function find (int[100] a, int v) public {
+%    // assume a is sorted
+%  ...}}
+%\end{lstlisting}
 The explicit assertion would be:
 \begin{gather*}\label{}
-  (\forall k) (0\leq k <99) \Rightarrow a[k] \leq a[k+1]
+  (\forall k) (0\leq k <n) \Rightarrow a[k] \leq a[k+1]
 \end{gather*}
@@
 \begin{gather*}\label{}
-  (\exists k) (0\leq k <99) \wedge a[k] > a[k+1]
+  (\exists k) (0\leq k <n) \wedge a[k] > a[k+1]
 \end{gather*}
@@
 \label{sec:parameter-assertion-verification-onchain}
-Our work focuses on parameters that are computationally expensive to verify on-chain.
-Specifically, we address cases where verifying a parameter assertion requires loops within the contract and the assertion can be formalized using universal or existential quantifiers.
+Our work targets parameters that are computationally expensive to verify on-chain, particularly when verification involves loops within the contract.
+We focus on assertions that can be expressed using universal or existential quantifiers.
 \subsection{Parameter Assertion Formalization}
 \paragraph{Universal Quantifier Formalization}
-An assertion can be formalized using the universal quantifier as follows:
-\begin{gather}
-  \label{eq:1}
-  \forall a \in A. \, P(a)
-\end{gather}
-This formula can be extended to assertions over multiple domains as:
-\begin{gather}
-  \label{eq:2}
-  \forall a \in A, \, \forall b \in B, \, \dots \, P(a, b, \dots)
-\end{gather}
+An parameter assertion can be formalized using the universal quantifier over the domain \(A\) as:
+\begin{equation} \label{eq:1}
+    \forall a \in A, \, P(a)
+\end{equation}
+For multiple domains:
+\begin{equation} \label{eq:2}
+    \forall a \in A, \, \forall b \in B, \, \dots, \, P(a, b, \dots)
+\end{equation}
+
 \paragraph{Existential Quantifier Formalization}
-In cases where an assertion involves the existence of an element, it can be formalized using existential quantifiers as follows:
-\begin{gather}
-  \label{eq:3}
-  \exists a \in A. \, P(a)
-\end{gather}
-This formula can also be extended to assertions over multiple domains:
-\begin{gather}
-  \label{eq:4}
-  \exists a \in A, \, \exists b \in B, \, \dots \, P(a, b, \dots)
-\end{gather}
+For assertions involving the existence of an element, we use existential quantifiers:
+\begin{equation} \label{eq:3}
+    \exists a \in A, \, P(a)
+\end{equation}
+Extended to multiple domains:
+\begin{equation} \label{eq:4}
+    \exists a \in A, \, \exists b \in B, \, \dots, \, P(a, b, \dots)
+\end{equation}
 \subsection{On-chain Verification}
-Verifying these assertions on-chain requires iterating over the domain \(A\) within the contract. For the fomulas \ref{eq:5}, the verification fomulas is as follows.
-\begin{gather}
-  \label{eq:5}
-  \bigwedge_{a \in A} P(a)
-\end{gather}
-For multiple domains, the verification process becomes:
-\begin{gather}
-  \label{eq:6}
-  \bigwedge_{a \in A, b \in B, \dots} \dots P(a, b, \dots)
-\end{gather}
-Verifying these assertions in  the existential quantifier formalization requires iterating over the domain \(A\) until finding an element \(a\) that satisfies the predicate:
-\begin{gather}
-  \label{eq:7}
-  \bigvee_{a \in A} P(a)
-\end{gather}
+Verifying these assertions on-chain involves iterating over the domain \(A\)\footnote{For multiple domains, the verification process requires iterating over all domains} within the contract.
+For formula \ref{eq:1}, the verification is expressed as: \(   \bigwedge_{a \in A} P(a)\).
 
-For multiple domains, the verification process becomes:
-\begin{gather}
-  \label{eq:8}
-  \bigvee_{a \in A, b \in B, \dots} \dots P(a, b, \dots)
-\end{gather}
-When the domain \(A\) is large or the predicate \(P\) is complex to evaluate, performing the verification on-chain incurs significant gas costs or even make the verification process infeasible due to gas limits.
-Given the current high gas prices, this can result in substantial costs.
+´For the existential quantifier formalization as in formula \ref{eq:3}, verification requires iterating over \(A\) until an element \(a\) is found that satisfies \(P\): \(\bigvee_{a \in A} P(a)\).
+
+When \(A\) is large or \(P\) is complex to evaluate, this process can incur significant gas costs or even become infeasible due to gas limits.
+Given the current high gas prices, this could result in substantial expenses.
 \subsection{Use Cases}
-Smart contract languages like Solidity \cite{solidity}, Vyper \cite{vyper}, Michelson \cite{michelson,michelson1}, and Plutus \cite{plutus} support common data types such as numbers, booleans, strings, bytes, arrays, sets, and maps.
-Many properties of these types can be expressed using universal quantifiers, requiring loops for verification in smart contracts, but can often be disproven by a counterexample or proven with a proof.
-Below are key properties for each type:
+Smart contract languages like Solidity \cite{solidity}, Vyper \cite{vyper}, Michelson \cite{michelson,michelson1}, and Plutus \cite{plutus} support common data types such as numbers, booleans, strings, bytes, arrays, sets.
+Many properties of these types use quantifiers, requiring loops for verification but can often be disproven by a counterexample or proven formally.
+Key properties for each type are outlined below:
 \paragraph{\textbf{Numbers}}
-Number types exhibit some properties that are crucial in cryptographic applications, such as primality and coprimeness. For example, the condition for two numbers \(a\) and \(b\) to be coprime is:
-\begin{gather*}
-\label{}
-(\forall n \in \mathbb{N}) \ (2 \leq n \leq \min(a, b)) \Rightarrow \neg((a \mod n = 0) \wedge (b \mod n = 0))
-\end{gather*}
+Number types have some properties that are vital in cryptographic applications, such as primality and coprimeness. %For instance, the condition for two numbers \(a\) and \(b\) to be coprime is:
+%\begin{equation*}
+%(\forall n) \ (2 \leq n \leq \min(a, b)) \Rightarrow \neg((a \mod n = 0) \wedge (b \mod n = 0))
+%\end{equation*}
 \paragraph{\textbf{Booleans}}
-SAT problems involve determining if there exists an assignment of variables that makes a formula \( F \) in propositional logic true.
-Verifying if a given assignment satisfies a formula \( F \), which is usually in Conjunctive Normal Form (CNF), requires looping over variables and clauses.
-Although finding a satisfying assignment is NP-complete, verifying an assignment takes \( O(n \times m) \), where \( n \) is the number of clauses and \( m \) is the number of variables.
+SAT problems determine if there is an assignment of variables that makes a formula \( F \) in propositional logic true.
+Verifying whether a given assignment satisfies \( F \), typically in Conjunctive Normal Form (CNF), involves iterating over variables and clauses.
+While finding a satisfying assignment is NP-complete, verifying one takes \( O(n \times m) \), where \( n \) is the number of clauses and \( m \) is the number of variables.
 \paragraph{\textbf{Strings}}
-String properties that require iteration include uniqueness (no repeated characters), character set membership, lexicographical order, pattern matching, and forbidden substrings.
-For instance, verifying that a string \(s\) does not contain a forbidden substring \(f\) of length \(k\) can be expressed as:
-\begin{gather*}
-(\forall i) \ (0 \leq i \leq n - k) \Rightarrow s[i, i+1, \dots, i+k-1] \neq f
-\end{gather*}
+String properties that require iteration include uniqueness, character set membership, lexicographical order, pattern matching, and forbidden substrings.
+%For example, verifying that a string \(s\) lacks a forbidden substring \(f\) of length \(k\) is expressed as:
+%\begin{gather*}
+%(\forall i) \ (0 \leq i \leq n - k) \Rightarrow s[i, i+1, \dots, i+k-1] \neq f
+%\end{gather*}
 \paragraph{\textbf{Bytes}}
-Verifying byte arrays often requires loops for properties like uniformity, sorted order, specific byte patterns, uniqueness, valid range, and alternating patterns.
-For example, to check if all bytes in an array \(b\) lie within a range \([l, u]\), the condition is:
+Verifying byte arrays often involves loops for properties such as uniformity, sorted order, specific byte patterns, uniqueness, valid range, and alternating patterns.
+For instance, to check if all bytes in an array \(b\) are within a range \([l, u]\), the condition is:
 \begin{gather*}
@@
 \end{gather*}
-Such properties can be computationally expensive for large sets.
-\section{Off-chain Distributed Verification Approach}
+%Such properties can be computationally expensive for large sets.
+\section{Gas-Efficient Off-chain Distributed Parameter Verification Approach}
 \label{sec:offchain-distributed-verification-approach}
 \subsection{The Outline of the Approach}
-We propose a novel approach for verifying parameter assertions in blockchain-based smart contracts.
-Our approach distributes the verification process off-chain, submitting only the outcomes to the blockchain for re-verification.
-This strategy aims to significantly reduce the computational burden on the blockchain while maintaining the integrity of the contract.
-
-Our approach takes into account the key principle that assertions expressed with universal quantifiers can be disproven by counterexamples, while those with existential quantifiers can be proven with valid proofs.
-These counterexamples or proofs serve as checkpoints, representing specific elements within the domain.
+We propose a novel approach for verifying parameter assertions in blockchain-based smart contracts by offloading the verification process off-chain and submitting only the results for on-chain re-verification.
+Our approach leverages the principle that assertions with universal quantifiers can be disproven by counterexamples, while those with existential quantifiers can be proven with valid proofs.
+These counterexamples or proofs act as checkpoints, representing specific elements within the domain.
 
@@
 The first step is to establish the checkpoint formula used to identify counterexamples or proofs.
-For assertions with universal quantifiers, as shown in Equation~\ref{eq:1}, the checkpoint formula is the negation of the original assertion and is expressed using an existential quantifier as follows:
+For assertions with universal quantifiers, the checkpoint formula is the negation of the original assertion and is expressed using an existential quantifier as follows:
 \begin{gather}
@@
 \end{gather}
-For assertions over multiple domains, as in Equation~\ref{eq:2}, the checkpoint formula becomes:
+For assertions over multiple domains, the checkpoint formula becomes:
 \begin{gather}
@@
 \end{gather}
-In the case of existential quantifier assertions, as in Equation~\ref{eq:3} and Equation~\ref{eq:4}, the checkpoint formula remains the same as the original assertion.
-\paragraph{\textbf{Off-chain distributed effors.}}These checkpoint formulas are then distributed to validators.
-Off-chain, the validators attempt to find counterexamples or proofs by identifying some \( a \in A \) such that the checkpoint formula is satisfied.
-For universal quantifier formalizations, this means finding \( a \) where \( \neg P(a) \) holds, and for existential quantifier formalizations, finding \( a \) where \( P(a) \) is true.
-\paragraph{\textbf{On-chain re-verification.}} Once a counterexample or proof involving an element \( a \) is found, the validator submits it to the blockchain, where it is re-verified by evaluating \( \neg P(a) \) or \( P(a) \) on-chain.
-For assertions with universal quantifiers, when a counterexample is successfully verified on-chain, the parameter assertion is proven to be invalid.
-Otherwise, it is considered valid, assuming that other points are checked by other validators.
-For assertions with existential quantifiers, the parameter assertion remains invalid until a proof is submitted and successfully re-checked on-chain.
+In the case of existential quantifier assertions, the checkpoint formula remains the same as the original assertion.
+\paragraph{\textbf{Off-chain distributed effors.}} These checkpoint formulas are distributed to validators, who then work off-chain to find counterexamples or proofs by identifying some \( a \in A \) that satisfies the checkpoint formula.
+For universal quantifiers, this involves finding \( a \) where \( \neg P(a) \) holds, while for existential quantifiers, it requires finding \( a \) where \( P(a) \) is true.
+\paragraph{\textbf{On-chain re-verification.}} After finding a counterexample or proof involving an element \( a \), the validator submits it to the blockchain for on-chain re-verification by evaluating \( \neg P(a) \) or \( P(a) \).
+For universal quantifiers, a verified counterexample invalidates the assertion; otherwise, it is assumed valid if other points are verified by other validators.
+For existential quantifiers, the assertion remains invalid until a proof is submitted and verified on-chain.
 \paragraph{\textbf{Incentivization Mechanism.}} Validators are incentivized to find counterexamples or provide proofs, which require computational resources.
@@
 
-This approach reduces the blockchain's burden and lowers gas costs by verifying only specific checkpoints, rather than performing full on-chain verification.
+Overall, the approach reduces the blockchain's computational load while preserving contract integrity.
+By verifying only specific checkpoints instead of full on-chain verification, it lowers the blockchain's burden and reduces gas costs.
 \subsection{Proof-of-Work-Based Incentivization Mechanism}
-The computational effort is represented by a computation proof, which is then submitted on-chain by the validator to claim their reward.
-This approach encourages participation in the distributed verification process, ensuring thorough validation even without the discovery of counterexamples.
+The computational effort is represented by a computation proof, submitted on-chain by the validator to claim a reward.
+This incentivizes participation in distributed verification, ensuring thorough validation even without finding counterexamples.
 
-However, significant challenges arise regarding (1) how to recheck the counterexample and the computation efforts on-chain at a reasonable gas cost, (2) how to ensure a significant number of checkpoints have been performed before a computation reward is issued, in order to guarantee an expected probability of correctness for the parameter, and (3) how to ensure that validators actually perform the checkpoint formula off-chain when no counterexample is found but a computation reward is provided.
+Challenges include: (1) rechecking counterexamples and computation efforts on-chain at low gas costs, (2) ensuring sufficient checkpoints are performed before rewarding computation, guaranteeing a probability of correctness, and (3) verifying that validators perform the checkpoint formula off-chain when no counterexample is found.
 
-To overcome these challenges, we propose a proof-of-work-based incentivization mechanism.
-We utilize the proof-of-work concept \cite{dwork1992pow,nakamoto2008bitcoin} by introducing a target hash \( t \), which sets the required difficulty level to earn the computation reward.
-The basic idea is that each verification process introduces a target hash.
-The validator attempts to perform the negation check and compute a hash that is less than or equal to the given target hash.
-The objective of the validator is to find either a counterexample or a computation that produces a hash smaller than or equal to the target hash \( t \).
-\subsubsection{Introduce a seed} To recheck the counterexample or computation proof on-chain at a reasonable gas cost, the counterexample or computation proof should be submitted on-chain in the form of the indication of the element \( a \in A \) where the assertion is invalid, in the case of a counterexample.
-The on-chain re-verification process is then straightforward, simply requiring the evaluation of \( \neg P(a) \).
+To address these, we propose a proof-of-work-based mechanism.
+Using the proof-of-work concept \cite{dwork1992pow,nakamoto2008bitcoin}, a target hash \( t \) sets the difficulty level for earning rewards.
+Each verification introduces a target hash, and the validator performs the checkpoint, computing a hash.
+The validator’s goal is to find a counterexample or produce a hash  that is less than or equal to \( t \).
+\subsubsection{Introduce a seed} 
+Let the element \( a \in A \) be where the assertion fails, either as a counterexample or as the computation proof found.
+To recheck this on-chain at a reasonable gas cost, it should be submitted as the element \( a \in A \) or as an indication of it.
+The on-chain re-verification then simply evaluates \( \neg P(a) \).
+The next challenge is generating a random hash for each checkpoint computation to provide computational proof.
+We address these by introducing a seed \( s \) in each verification process.
 
-The next challenge is how to generate a random hash for each computation and devise a computational proof to incentivize computational effort.
-To address this, we introduce a seed \( s \) in each verification process.
+Let \( n \) denote the size of the domain \( A \), where \( n = |A| \) and \(|A|\) is the number of elements in \( A \).
+Each number \( i \) in the range \([1, n]\) corresponds to an element in \( A \), such that \( a = A[i] \), where \( A[i] \) denotes the \( i \)-th element of \( A \).
 
-Let \( n \) denote the size of the domain \( A \). 
-\begin{gather*}
-n = |A|
-\end{gather*}
-where \(|A| \) denotes the number of elements in the domain $A$.
-
-Each number \( i \) in the range \([1, n]\) corresponds to an element in \( A \). 
-\begin{gather*}
-a=A[i]
-\end{gather*}
-where $A[i]$ denotes the $i$-th element in $A$.
-
-The seed \( s \) is a random number. 
-\begin{gather*}
-s \in \mathbb{N} 
-\end{gather*}
-The seed $s$  is then reduced with modulo \( n \) to obtain \( i \), which is associated with an element \( a \) in \( A \).
-\begin{gather}
+We introduce a seed \( s \), a random number \( s \in \mathbb{N} \). The seed \( s \) is reduced modulo \( n \) to obtain \( i \), which is then associated with an element \( a \) in \( A \):
+\begin{equation}
 \label{eq:11}
-i = (s\mod n) + 1
-\end{gather}
-\subsubsection{Estimate the number of seeds:} To ensure that a sufficient number of checkpoints have been checked before a computational proof is found, we first estimate the number of seeds required to find a counterexample with the desired probability of correctness \cite{ross2014probability,feller1968probability}.
+i = (s \mod n) + 1
+\end{equation}
+\subsubsection{Estimate the Number of Seeds:} To ensure a sufficient number of checkpoints are checked before finding a computational proof, we estimate the number of seeds required to find a counterexample with the desired probability of correctness \cite{ross2014probability,feller1968probability}.
 
@@
 \end{itemize}
-%Rearranging this gives:
-%\begin{gather*}
-%\left( \frac{n-1}{n} \right)^m = 1 - p
-%\end{gather*}
-%Taking the natural logarithm:
-%\begin{gather*}
-%m \ln\left( \frac{n-1}{n} \right) = \ln(1 - p)
-%\end{gather*}
 Solving for \( m \):
-\begin{gather}
+\begin{equation}
 \label{eq:12}
 m = \frac{\ln(1 - p)}{\ln\left( \frac{n-1}{n} \right)}
-\end{gather}
+\end{equation}
 
-So the number of the seeds to achive the expected propety $p$ is great or at least equal to $m$.
-Note that, \( p \) represents the probability when only one validator participates.
+Therefore, the number of seeds required to achieve the expected probability \( p \) is at least \( m \).
+Note that \( p \) represents the probability when only one validator participates.
 As more validators are involved, the probability of discovering a counterexample increases.
-\subsubsection{Set up the taget hash:}
-The above number of seed $m$ can then be used to set up the target hash \cite{nakamoto2008bitcoin,bonneau2015sok}.
-The target hash $t$ can be calculated based on a desired difficulty level.
-In proof-of-work systems, difficulty is typically adjusted to ensure that the average efforts to find a valid hash.
-The target hash $t$ is often calculated by taking the maximum possible hash value and dividing it by the difficulty level.
+\subsubsection{Set up the Target Hash:}
+The number of seeds \( m \) can be used to set up the target hash \cite{nakamoto2008bitcoin,bonneau2015sok}.
+The target hash \( t \) is calculated based on a desired difficulty level.
+In proof-of-work systems, difficulty is typically adjusted to ensure that the average effort to find a valid hash matches the desired rate.
+The target hash \( t \) is often determined by taking the maximum possible hash value and dividing it by the difficulty level.
 
-Given the expected number of seeds to generate, 
-the difficulty level \( D \) can be adjusted accordingly. Typically, \( D \) is set to ensure that a valid hash is found approximately once every \( m \) trials.
-
-If we want the probality of finding a valid hash to be $\frac{1}{m}$, then \( D \) equal to \( m \):
-\begin{gather}
+Given the expected number of seeds, the difficulty level \( D \) can be adjusted accordingly.
+Typically, \( D \) is set to ensure that a valid hash is found approximately once every \( m \) trials.
+If we want the probability of finding a valid hash to be \( \frac{1}{m} \), then \( D \) is set to \( m \):
+\begin{equation}
 \label{eq:13}
 t = \frac{H_{\text{max}}}{m}
-\end{gather}
+\end{equation}
+Where \( H_{\text{max}} \) is the maximum possible hash value, and \( m \) is the difficulty level, adjusted based on the expected number of trials.
+\subsubsection{Conduct a Computation Hash:} To ensure a computational proof includes the negation check, the checkpoint formula is integrated into the proof process, requiring validators to execute it as part of producing the proof.
 
-Where \( H_{\text{max}} \) is the maximum possible hash value and \( m \) is the difficulty level, which can be adjusted based on the expected number of trials.
-\subsubsection{Conduct a Computation Hash:} To ensure that a computational proof includes the negation check, the computation of the checkpoint formula is integrated into the proof process.
-This guarantees that validators must execute the negation check as part of producing the computation proof.
+For each element \( a \), let \(\pi_{P_{a}}\) represent the components for evaluating the checkpoint \(\neg P(a)\).
+The computation hash combines the seed \( s \) and \(\pi_{P_{a}}\) to ensure validation.
 
-For each element \( a \), let \(\pi_{P_{a}}\) be the function that returns the essential components of evaluating the negation \(\neg P(a)\).
-The computation hash thus incorporates both the seed \( s \) and \(\pi_{P_{a}}\), ensuring proper validation.
-
-\begin{gather}
+\begin{equation}
 \label{eq:14}
 t_s = \text{hash}(s, \pi_{P_{a}})
-\end{gather}
-where \(\text{hash}\) is a cryptographic hash function used to compute the hash value.
+\end{equation}
+where \(\text{hash}\) is a cryptographic hash function.
 
-Assertions in smart contract languages, such as Solidity and Michelson, are often represented as predicate logic, expressed through Boolean formulas.
-These are composed of relational operators like \( =, \neq, >, <, \geq, \leq \), logical operators such as \( \neg, \land, \lor\), and corresponding expressions.
+Assertions in smart contract languages are represented as predicate logic expressed through Boolean formulas.
+These formulas are composed of relational operators like \( =, \neq, >, <, \geq, \leq \) and logical operators such as \( \neg, \land, \lor \), along with corresponding expressions.
 
-Thus, \(\pi_{P_{a}}\) represents the set of expressions involved in evaluating the predicate \(P_a\).
-\begin{gather*}
+Thus, \(\pi_{P_{a}}\) denotes the set of expressions used to evaluate \(P_a\):
+\begin{equation*}
 \pi_{P_{a}} = \{ e_1, e_2, \ldots \}
-\end{gather*}
-where \(e_i\) are the expressions that contribute to the computation of the predicate \(P_a\).
+\end{equation*}
+where \(e_i\) are the expressions contributing to the computation of \(P_a\).
+\subsection{Off-chain Distributed Verification}
+For assertions using an existential quantifier, validation is straightforward: validators find a proof off-chain and submit it on-chain for re-verification.
+If valid, the parameter is confirmed, and the validator is rewarded.
 
-%For example, for each element \( i \), it returns \(a[i]\) and \(a[i + 1]\) in the evaluation of the negation predicate \( a[i] < a[i+1] \) in the sorted array example.
+For universal quantifier assertions, the process is more complex.
+The size \( n \) of the domain \( A \) is calculated, and the target hash is computed based on the expected probability of correctness.
+Validators generate approximately \( m \) seeds to find either a counterexample or a computational proof, confirming or invalidating the parameter.
 
-%The expressions $\pi_{P_a}$ can be used to compute the hash, which involves the validator executing the condition check to find a reward computation.
-%\begin{equation}
-%t_s = \text{hash}(s, \pi_{P_{a}})
-%\end{equation}
-%where:
-%\begin{itemize}
-%    \item $s$ is the seed.
-%    \item $\pi_{P_{a}}$ is the set of expressions used in the computation of the predicate $P_a$.
-%    \item \text{hash} is the hash function that computes the hash based on the seed and the set of expressions $\pi_{P_{a}}$.
-%\end{itemize}
-\subsection{Off-chain distributed verification}
-For applications where the parameter assertion can be expressed using an existential quantifier, the validation process is relatively straightforward.
-Validators attempt to find a proof off-chain and submit it on-chain, where it is re-verified.
-If the proof is valid, the parameter is considered correct, and the validator is rewarded.
+As shown in Fig.
+\ref{fig:find_seed}, validators generate a seed \( s \) and perform the checkpoint until they find a counterexample or computation proof.
+They then submit the result on-chain to claim their reward.
 
-However, for assertions involving universal quantifiers, the process becomes more complex.
-First, the size \( n \) of the domain \( A \) is calculated.
-Then, using the expected probability to ensure the correctness of the parameter assertion in the absence of a counterexample, the target hash is computed.
-Due to the setup of the target hash, a validator needs to generate approximately \( m \) seeds to have a chance of discovering either a counterexample or a computational proof, thereby confirming the validity or revealing the invalidity of the parameter.
-
-The process of finding a valid seed is outlined in Fig.
-\ref{fig:find_seed}.
-During this distributed process, each validator generates a seed \( s \) and performs the negation check until they either identify a counterexample or a computation proof for a reward.
-Once one of these outcomes is achieved, the validator can submit it on-chain to claim their reward.
-
-Both the counterexample and the computational proof are encoded by the seed, allowing the on-chain component to replicate and verify the result.
-If the verification is successful, the validator receives the reward.
+Both counterexamples and proofs are encoded by the seed, enabling on-chain verification. If successful, the validator receives the reward.
 \begin{figure}[t]
@@
     \node (counterexample) [decision, below of=calc_i, yshift=-0.5cm] {$\neg P(a)$};
-    \node (calc_hash) [process, below of=counterexample, yshift=-0.5cm] {$t_s = \text{hash}(s, \text{eval}(\neg P(a)))$};
+    \node (calc_hash) [process, below of=counterexample, yshift=-0.5cm] {$t_s = \text{hash}(s,\pi_{P_{a}})$};
     \node (compare) [decision, below of=calc_hash, yshift=-0.5cm] {$t_s <= t$};
@@
 \end{figure}
-\subsection{On-chain re-verification}
-Given a submitted seed \( s \), the on-chain contract verifies whether the seed produces a counterexample or a valid computational proof eligible for a reward.
-The verification process follows these steps:
-\begin{enumerate}
-    \item Compute \( n \), the size of the domain \( A \).
-    \item Identify the target value \( t \).
-    \item Determine \( i \in [1, n] \) from \( s \) using the modulo operation, and associate \( i \) with the corresponding element \( a \) in \( A \).
-    \item Perform the check \( \neg P(a) \) to see if \( a \) is a counterexample.
-    \item If no counterexample is found, compute the hash \( t_s \) derived from the seed \( s \).
-    \item Compare \( t_s \) to the target hash \( t \) to check if it qualifies for a reward.
-\end{enumerate}
+\subsection{On-chain Re-verification}
+Given a submitted seed \( s \), the on-chain contract verifies if it produces a counterexample or a valid computational proof for a reward.
+The process involves: (1) Compute \( n \), the size of the domain \( A \), (2) Identify the target value \( t \), (3) Determine \( i \in [1, n] \) from \( s \) using modulo, and associate it with the element \( a \in A \), (4) Check \( \neg P(a) \) for a counterexample, (5) If none, compute the hash \( t_s \) from \( s \), and (6) Compare \( t_s \) to the target hash \( t \) to check reward eligibility.
 
-Following this process, the contract will either identify a counterexample or compute a hash based on the seed \( s \) and the evaluation \( \neg P(a) \).
-The computed hash is then compared to the target hash to determine if it qualifies for a reward.
-The possible outcomes are: finding a counterexample, validating a reward computation, or determining no reward computation.
+The contract either identifies a counterexample or computes a hash based on \( s \) and \( \neg P(a) \), then compares it to \( t \) to decide if a reward is given.
 \section{Practical Model}
 \label{sec:practical-model}
-\subsection{Security risks}
-Off-chain distributed verification of assertions is indeed an intriguing concept, yet it faces the following security risks when proposing an incentive method:
+\subsection{Security Risks}
+Off-chain distributed verification presents several security risks:
+\begin{enumerate}
+\item Denial-of-service (DoS) attacks: Attackers can flood the system with invalid parameters, causing congestion and disrupting operations.
+\item Front-running attacks: Attackers can monitor the mempool to intercept seeds representing counterexamples or proofs, stealing rewards.
+\item Caller exploitation: Callers may privately run negation checks to (1) claim rewards before others or (2) fake computation proofs before a counterexample is found.
+\item Reward manipulation: Validators might resubmit counterexamples or proofs multiple times to manipulate and multiply rewards.
+\end{enumerate}
+\subsection{Architectural Overview}
+This section presents a practical model that combines theoretical principles and addresses security concerns. The architecture is shown in Figure \ref{fig.architect}.
+The model has two key entities: the on-chain assertion contract and the off-chain validator program. 
+\paragraph{On-chain assertion contract.} The contract includes two essential functions: (1) \( submitParameter \), used by callers to submit parameters for validation, and (2) \( claimReward \), which accepts a seed and determines if it results in a counterexample, a reward, or no reward.
+\paragraph{Off-chain Validator Program.}
+The off-chain program must use the same \( claimReward \) function for finding counterexamples or proofs and assist validators in finding seeds for rewards.
+Events like parameter submissions, counterexamples, or proofs can be broadcast via event emission for real-time monitoring.
 
-\begin{enumerate}
-\item Denial-of-service (DoS) attacks: The system is susceptible to DoS attacks, where a caller inundates the system with numerous invalid parameters, causing congestion and hindering its operation.
-\item Front-running attacks: The system is vulnerable to front-running attacks, where an attacker closely monitors the mempool to intercept a seed representing a counterexample or a computation proof, subsequently stealing the reward.
-\item Caller exploitation: A caller might exploit the system by running the negation check privately to (1) identify the reward before submitting the parameter on-chain, thereby swiftly claiming the reward ahead of the other validators, (2) fake the compuatation proofs before a counterexample can be found by other validators.
-\item Reward manipulation: For a system that allows multiple rewards.
-A validator may attempt to manipulate the reward system by resubmitting counterexamples or computation proofs multiple times to multiply their rewards.
-\end{enumerate}
-\subsection{Overview architect}
-This section presents a practical model that unifies theoretical principles and addresses the previously mentioned security concerns.
-The architectural design of this model is depicted in Figure \ref{fig.architect}.
-\subsubsection{Main compoments.} The model consists of two main entities: the on-chain assertion contract and the off-chain validator program.
-\paragraph{On-chain assertion contract.}
-While additional functions may exist, the assertion contract must encompass the following two essential functions (or similar functions):
-\begin{itemize}
-\item The \( submitParameter \) function: Callers utilize this function to submit their parameters for validation. %Subsequently, the parameter is distributedly verified by validators.
-\item  The \( claimReward \) function: This function accepts a seed (or may some others) as inputs, yielding a result indicating whether the computation from the seed results in a counterexample, a reward computation, or a non-reward computation.
-\end{itemize}
-\paragraph{Off-chain validator program.}
-Since the off-chain program runs off-chain, it can be implemented according to the validator's preferences.
-However, the crucial point is that the off-chain contract must use the exact same \( claimReward \) function when attempting to find a counterexample or a computation proof.
-Additionally, it should support a function that assists the validator in finding a seed to earn a reward.
-
-All events such as parameter submissions, the discovery of a counterexample, or the presentation of computational proofs can be broadcasted to the network using event emission.
-Validators can monitor these events to stay updated on the verification status in real-time.
+The owner deploys the on-chain contract and makes the off-chain program available by either (1) storing the code in a repository or (2) broadcasting it via messaging systems like Waku in Ethereum for local storage by validators.
 \paragraph{Storage.}
-When a parameter is submitted for verification, the following information should be stored:
-\begin{itemize}
-\item Parameter: this includes the parameter itself.
-In cases where storing the parameter on-chain is impractical because of its size, it could be possible to store only its hash.
-Despite this, the hash remains sufficient for validation.
-\item Timestamp: this indicates the approximate time when the parameter was submitted.
-\end{itemize}
+When a parameter is submitted for verification, the following should be stored: (1) The parameter itself, or if too large, only its hash, which is sufficient for validation, and (2) the timestamp of when the parameter was submitted.
 \begin{figure}
 \centering
-\includegraphics[scale=.8]{assertion1}
+\includegraphics[scale=.6]{assertion1}
 \caption{The architecture of the practical model}
@@
 \end{figure}
-\subsubsection{Deploying and managing on/off-chain contracts.}
-The respective owner is responsible for deploying the on-chain contract and ensuring that the off-chain program is accessible to validators.
-There are two approaches to make the program available to validators:
-\begin{itemize}
-   \item The owner may store the program code in a repository that is accessible to validators or provide it directly to them upon request.
-	\item Alternatively, the owner can broadcast the program to the network using messaging systems like Waku in Ethereum, allowing interested validators to store the off-chain code locally.
-\end{itemize}
-
-%\subsubsection{On and Off.} 
-%Before a parameter can be utilized in the actual work function or contract, a caller must initially submit it via the submit-parameter function in the on-chain assertion contract.
-
-%Upon the submission of a parameter, an event can be emitted, allowing validators to receive updates by monitoring the blockchain for the parameter submission event.
-Additionally, the caller may choose to broadcast their parameter to all validators via a messaging system when submitting it online.
-%\subsubsection{Off-chain verification}
-%After a parameter is submitted and stored on-chain, a validator can commence the verification process.
-To assess the validity of a parameter, each validator independently executes the off-chain validation program.
-
-%A validator may attempt to try multiple times with different random seeds in order to find either a counterexample or a computational proof.
-A function called find-seed could be implemented, which in turn calls the claim-reward function to locate a seed.
-
-%All events such as parameter submissions, the discovery of a counterexample, or the presentation of computational proofs can be broadcasted to the network using event emission.
-Validators can monitor these events to stay updated on the verification status in real-time.
-\subsubsection{Calling a work function}
-A work function can be encapsulated as a private function within the assertion contract or implemented in a separate contract.
-A caller submits a parameter for verification through the on-chain assertion contract.
-Once verified, the work contract is triggered to perform its task under the assumption that the parameter is valid.
-
-The work function or contract is invoked by the on-chain validation contract or caller, but only if specific conditions are met, such as sufficient verification proofs, no counterexamples, and a waiting period.
-Upon fulfilling all requirements, the task is executed, and in some cases, the parameter record may be deleted to free up storage.
+\paragraph{Calling a Work Function}
+The work function, either private or in a separate contract, is triggered after successful verification, assuming the parameter is valid.
+It is invoked only when conditions like sufficient proofs and no counterexamples are met.
 \subsection{Security Features}
-\subsubsection{DoS attacks}
-When submitting a parameter, the caller must provide a deposit in native tokens.
-This deposit is claimed by a validator if a counterexample is found or returned if the parameter is verified.
-The deposit discourages invalid submissions and mitigates the risk of DoS attacks.
-\subsubsection{Front-running attacks}
-To prevent front-running attacks, the seed \( s \) is calculated by combining a random number \( r \) with the validator's address, rather than using \( r \) alone.
-This approach enhances security, as a malicious validator cannot reuse \( r \) from the mempool - its combination with their own address will yield a different seed \( s \).
-
-%While a random number $r$ alone as a seed is sufficient to indicate the associated element $a$ in the domain $A$, to prevent the front-running attack, we enhance the randomness of the seed by combining a random number with the validator's address to calculate the seed.
-
-%This combination adds an extra level of security.
-So even watching the mempool and get the random number, a malicious validators cannot use the same random number $r$  because the combination with their address will not produce the same seed $s$.
-
- %In deeds, the validator's address is converted to numerical values and use these numbers in combination with a random number to compute the seed.
-
-%Let's denote the validator's address by $addr$: \(\quad \text{addr} \in \text{Addresses}\)
-
-%The address is converted to numerical values.
-%\begin{equation}
-%\text{addr\_num} = \text{init256}(\text{addr})
-%\end{equation}
-
-%This combination adds an extra level of security.
-So even watching the mempool and get the random number, a malicious validators cannot use the same random number $r$  because the combination with their address will not produce the same seed $s$.
-\subsubsection{Caller exploitation attack}
-%A caller may execute the validator program for their parameters before submitting on-chain, attempting to claim a reward or validate their parameter before others find counterexamples.
-To mitigate the caller exploitation risk, the seed \( s \) is computed using the block timestamp \( t \) indicating when the parameter is submitted, random number \( r \), and validator's address.
-The timestamp \( t \in \text{Timestamps} \) is included to prevent preemptive submission, and the seed \( s \) is calculated as:
+\paragraph{DoS Attacks}
+Callers must provide a deposit when submitting a parameter.
+This deposit is claimed by a validator if a counterexample is found or returned if the parameter is verified, discouraging invalid submissions and mitigating DoS attacks.
+\paragraph{Front-running Attacks}
+To prevent front-running, the seed \( s \) is calculated by combining a random number \( r \) with the validator's address.
+This ensures a malicious validator cannot reuse \( r \) from the mempool, as the combination will yield a different seed \( s \).
+\paragraph{Caller Exploitation}
+The seed \( s \) is computed using the block timestamp \( t \), random number \( r \), and validator's address to prevent preemptive submission. The seed is calculated as:
 \begin{equation}
@@
 \end{equation}
-where \(\text{hash}\) is a cryptographic hash function. This ensures that manipulated or pre-run seeds fail to produce counterexamples or rewards.
-%Additionally, applications can enforce a time frame such that a parameter is valid only if enough time has passed for verification.
-A parameter is valid if, after this time, no counterexample is found and sufficient computation proofs are received.
-\subsubsection{Reward manipulation attack}
-In some applications, multiple computational proofs are allowed, and a record is maintained to track the parameter's verification progress.
-This record contains validator addresses and the random number \( r \) used in each verification.
-
-The inclusion of validators' addresses and \( r \) is crucial in preventing reward manipulation, as it ensures that a validator cannot resubmit with the same \( r \), thereby preventing repeated claims for the same computation proof or counterexample.
+ensuring manipulated seeds fail to produce counterexamples or rewards.
+\paragraph{Reward Manipulation}
+For applications allowing multiple proofs, a record tracks the parameter's verification progress, including validator addresses and \( r \) values.
+This prevents validators from resubmitting with the same \( r \), stopping repeated claims for the same proof or counterexample.
 \section{Gas Cost Analysis}
@@
 This section evaluates the cost of the proposed distributed verification method and compares it to traditional on-chain verification.
-\subsection{Transaction Execution Costs}
-Transaction costs \cite{eth-yellowpaper,chen2019underoptimized,victor2019measuring}, measured in gas, can be divided into five key components:
-\begin{enumerate}
-\item Base cost: Fixed cost for initiating a transaction, covering operations like hashing, signature verification, and balance updates. For instance, transferring ETH in Ethereum costs 21,000 gas.
-\item Data cost: Gas tied to the size of the transaction’s data payload, with non-zero bytes incurring higher costs than zero bytes.
-\item Computational cost: Gas for executing smart contract operations, such as arithmetic, logic, control flow, cryptography, and memory tasks.
-\item Storage cost: Higher than computation, as it involves writing to persistent storage. %In Ethereum, writing a new value costs 20,000 gas, updates cost 5,000 gas, and reading costs 100 gas.
-\item Refund gas: Gas refunded for specific operations, like using SELFDESTRUCT or resetting storage values to zero.
-\end{enumerate}
-Thus, the total gas cost (execution cost) includes base, data, computational, and storage costs.
-\subsection{Comparative Analysis of On-Chain and Offline Distributed Methods}
+%\subsection{Transaction Execution Costs}
+%Transaction costs \cite{eth-yellowpaper,chen2019underoptimized,victor2019measuring}, measured in gas, can be divided into five key components:
+%\begin{enumerate}
+%\item Base cost: Fixed cost for initiating a transaction, covering operations like hashing, signature verification, and balance updates. For instance, transferring ETH in Ethereum costs 21,000 gas.
+%\item Data cost: Gas tied to the size of the transaction’s data payload, with non-zero bytes incurring higher costs than zero bytes.
+%\item Computational cost: Gas for executing smart contract operations, such as arithmetic, logic, control flow, cryptography, and memory tasks.
+%\item Storage cost: Higher than computation, as it involves writing to persistent storage. %In Ethereum, writing a new value costs 20,000 gas, updates cost 5,000 gas, and reading costs 100 gas.
+%\item Refund gas: Gas refunded for specific operations, like using SELFDESTRUCT or resetting storage values to zero.
+%\end{enumerate}
+%Thus, the total gas cost (execution cost) includes base, data, computational, and storage costs.
+%\subsection{Comparative Analysis of On-Chain and Offline Distributed Methods}
 We compare the gas costs of on-chain and off-chain verification by breaking down their components.
-\subsubsection{On-chain Verification Gas Costs}
-Let \( G_{parameter} \) represent the intrinsic gas cost, which includes base and data costs, primarily depending on the size of the parameter \( p \).
-The total on-chain gas cost \( G_{on} \), given in Equation \ref{on-gas}, includes:
-\begin{itemize}
-    \item Intrinsic gas \( G_{parameter} \),
-    \item Optional storage gas \( G_{storage} \),
-    \item Gas for \( n \) parameter checks, each costing \( G_{check} \),
-    \item Execution gas \( G_{run} \), if the parameter is valid.
-\end{itemize}
-\begin{equation}
+
+\subsubsection{On-chain Verification}
+Transaction costs \cite{eth-yellowpaper,chen2019underoptimized,victor2019measuring}, measured in gas, can be divided into key components.
+Let \( G_{parameter} \) represent the intrinsic gas cost, including base and data costs, primarily based on the size \( n \) of the parameter.
+The total on-chain gas cost \( G_{on} \) is:
+\begin{equation*}
 \label{on-gas}
 G_{on} = G_{parameter} + [G_{storage}] + n \cdot G_{check} + G_{run}
-\end{equation}
-
-\subsubsection{Off-chain Verification Gas Costs}
-The off-chain verification gas costs include similar components to on-chain verification but differ in several key aspects.
+\end{equation*}
+where \( G_{storage} \) is optional storage gas, \( G_{check} \) is the gas cost per parameter check, and \( G_{run} \) is the execution gas if the parameter is valid.
+\subsubsection{Off-chain Distributed Verification}
+Off-chain verification gas costs include similar components to on-chain verification but with key differences.
 Instead of \( n \) parameter checks, only a single check is required.
-Moreover, storage cost \( G_{storage} \) is mandatory, and additional components are needed as follows:
-\begin{itemize}
-    \item Submit the seed, \( G_{seed} \),
-    \item Compute and compare the hash, \( G_{hash} \).
-\end{itemize}
-The total off-chain gas cost is given by Equation \ref{gas-off}:
-\begin{equation}
+Additionally, the storage cost \( G_{storage} \) is mandatory, and new components are introduced: submitting the seed, \( G_{seed} \), and computing and comparing the hash, \( G_{hash} \).
+The total off-chain gas cost is:
+\begin{equation*}
 \label{gas-off}
 G_{off} = G_{parameter} + G_{storage} + (G_{seed} + G_{check} + G_{hash}) + G_{run}
-\end{equation}
-
+\end{equation*}
 \subsubsection{Comparative Analysis}
-We compare the gas costs of both verification methods.
-Both methods incur the same intrinsic cost, \( G_{parameter} \).
-On-chain storage cost \( [G_{storage}] \) is optional, whereas the offline method always includes \( G_{storage} \), which may store only the parameter's hash.
-The on-chain method incurs \( n \cdot G_{check} \) for parameter checking, while the offline method reduces this to \( G_{check} \).
-The offline method includes costs for seed submission \( G_{seed} \) and hash computation \( G_{hash} \), which are not required for the on-chain method.
-Finally, both methods share the computation cost, \( G_{run} \).
+We compare the gas costs of both methods.
+Both incur the same intrinsic cost, \( G_{parameter} \).
+On-chain storage \( [G_{storage}] \) is optional, while the off-chain method always includes \( G_{storage} \), possibly storing only the parameter's hash.
+The on-chain method incurs \( n \cdot G_{check} \) for parameter checks, while the off-chain method reduces this to \( G_{check} \), with added costs for seed submission \( G_{seed} \) and hash computation \( G_{hash} \).
+Both share the computation cost, \( G_{run} \).
 
@@
 
-The offline distributed process uses a proof-of-work incentive; let \( G_{reward} \) be the gas equivalent reward for counterexamples or proofs.
-The total verification cost for proof \( G_{proof} \) is:
+In the off-chain method, a proof-of-work incentive is used, with \( G_{reward} \) as the gas-equivalent reward for counterexamples or proofs. The total verification cost \( G_{proof} \) is:
 \[
@@
 
-Figure \ref{fig:gas_compare} compares gas consumption between methods, with \( G_{base} \) assumed constant.
-The red line (on-chain) scales linearly with parameter size \( n \), while the blue line (offline) initially incurs higher costs but becomes more efficient as \( n \) grows.
+Figure \ref{fig:gas_compare} compares gas consumption.
+The red line (on-chain) scales linearly with \( n \), while the blue line (off-chain) incurs higher initial costs but becomes more efficient as \( n \) grows.
 
-The on-chain method is best for scenarios requiring direct blockchain checks, but it becomes costly when \( n \) and \( G_{check} \) are large.
-The proposed offline method (\( G_{off} \)) is more efficient for large parameters, despite additional \( G_{seed} \) and \( G_{hash} \) costs, which are often outweighed by savings in reduced checks.
+The on-chain method suits direct checks but becomes costly as \( n \) and \( G_{check} \) increase.
+The off-chain method (\( G_{off} \)) is more efficient for large parameters, as \( G_{seed} \) and \( G_{hash} \) are outweighed by savings in checks.
+If storing the parameter is required, \( G_{storage} \) is small, but otherwise, only the hash may be stored.
 
-For the offline method, the main concern is \( G_{storage} \).
-If storing the parameter is required, this cost is negligible, but if not, it must be considered, potentially storing only the parameter's hash for verification.
-
-Overall, the offline method (\( G_{off} \)) is generally more cost-effective for large parameters, depending on \( n \), \( G_{storage} \), and specific values of \( G_{seed} \), \( G_{hash} \), and \( G_{reward} \).
+Overall, \( G_{off} \) is more cost-effective for large parameters, depending on \( n \), \( G_{storage} \), and values of \( G_{seed} \), \( G_{hash} \), and \( G_{reward} \).
 \begin{figure}
@@
         title={Gas Consumption Chart},
-        xlabel={Parameter size},
+        xlabel={Parameter Size},
         ylabel={Gas},
@@
         };
+        \addlegendentry{on-chain}
          \addplot[
@@
         };
+        \addlegendentry{off-chain}
     \end{axis}
@@
 This section presents the implementation of the Decentralized Selling Platform (DSP) application.
-Initially, the DSP is deployed as a smart contract on the Ethereum blockchain, where parameter verification occurs on-chain.
-We then demonstrate how an off-chain verification approach can significantly reduce gas costs.
+Initially deployed as a smart contract on Ethereum for on-chain parameter verification, we demonstrate how off-chain verification reduces gas costs.
+The code is available at \cite{dsp}.
+
 \subsection{Decentralized Selling Platform}
-The DSP application provides a decentralized framework for managing and trading items.
-Sellers can create platforms, list items, and facilitate buyer transactions.
-Buyers can directly purchase items listed for sale.
+DSP provides a decentralized system for managing and trading items. Sellers create platforms, list items, and buyers can purchase them directly.
 
-Each item in the platform is characterized by:
-\begin{itemize}
-    \item \texttt{product}: A struct representing the product, including its name and producer.
-    \item \texttt{forSale}: A boolean indicating whether the item is available for sale.
-    \item \texttt{price}: The price of the item, specified in wei.
-    \item \texttt{owner}: The Ethereum address of the current item owner.
-\end{itemize}
-The DSP application provides several key functions:
-\begin{itemize}
-    \item \texttt{createSellingPlatform(items)}: Creates a selling platform with a list of sorted items.
-    \item \texttt{buyItem(sellingPlatform, product)}: Enables buyers to purchase an item if listed for sale at the correct price, with ownership and funds transferred.
-    \item \texttt{addNewItem(sellingPlatform, item)}: Adds a new \texttt{item} to an existing platform, keeping the list sorted.
-\end{itemize}
-Additional functions like \texttt{setForSale} and \texttt{setPrice} allow item owners to update the sale status and price.
-To approximate the behavior of a typical selling platform, our implementation permits items with the same product name but different producers.
-The \texttt{searchItems} function allows users to search by product name.
+Each item includes: (1) \texttt{product}: The product name and producer, (2) \texttt{forSale}: Availability status, (3) \texttt{price}: The price in wei, and (4) \texttt{owner}: The current owner’s Ethereum address.
 
-To optimize gas costs for buying, reselling, updating, and searching, the item list is kept sorted by product name.
-Therefore, a critical requirement is that items must be sorted when creating a selling platform.
-If the list is unsorted, all related operations will fail.
-\subsection{Implementation of the Application with On-chain Parameter Verification}
-We begin by implementing the application as a smart contract on the Ethereum blockchain, where the verification of parameters is conducted directly on-chain.
+Key functions: \texttt{createSellingPlatform(items)} to create a platform with sorted items, and \texttt{buyItem(sellingPlatform, product)} to purchase items, transferring ownership and funds.
+Functions like \texttt{setForSale} and \texttt{setPrice} update sale status and price.
+Items can share the same product name but have different producers, and users can search by product name.
 
-Each seller manages their own selling platform. In Solidity, this can be achieved using a \texttt{mapping} that associates each seller's address with a list of items:
-
+To optimize gas costs, the item list must be sorted by product name. If unsorted, all related operations will fail.
+\subsection{Implementation with On-chain Parameter Verification}
+Each seller manages their platform using a \texttt{mapping} linking their address to a list of items:
 \begin{lstlisting}[numbers=none]
@@
 \end{lstlisting}
+The contract includes a function to check if items are sorted by name, using \texttt{compareStrings} to compare adjacent elements.
+If unsorted, it returns \texttt{false}; otherwise, \texttt{true}.
+The \texttt{createSellingPlatform} function calls this check before platform creation.
+\subsection{Applying the Proposed Approach}
+We define key components, such as the checkpoint formula for identifying unsorted items.
+The seed \( s \) is tied to the \( i \)-th item, the expected seeds \( m \) are estimated, and the target hash \( t \) is computed.
 
-To ensure the list is sorted, let \( \text{len} \) be the function that returns the size of the item list. The formal assertion using a universal quantifier given by Equation \ref{eq:1} is as follows:
-\[
-(\forall i) (0 \leq i < len(items) - 1) \Rightarrow items[i].product.name \leq items[i+1].product.name
-\]
+The on-chain assertion contract extends the DSP contract with functions like \texttt{rewardPrice} and \texttt{counterexamplePrice} for off-chain verification.
+When \texttt{createSellingPlatform} is invoked, the item list is submitted with a \texttt{timestamp} and \texttt{status} (initially \texttt{false}).
+The caller deposits funds, forfeited if the list is unsorted.
+If a counterexample is found, the record is deleted, and the caller is penalized.
+If verified, \texttt{status} changes to \texttt{true}, enabling further actions.
 
-To verify this, we define a function that checks whether the list of items is sorted by name.
-This function iterates through the list, comparing adjacent elements using the \texttt{compareStrings} function.
-If any unsorted element is found, the function returns \texttt{false}.
-Otherwise, it returns \texttt{true} if the items are properly ordered:
-\begin{lstlisting}[numbers=none]
-for (uint256 i = 0; i < items.length - 1; i++) {
-  if (compareStrings(items[i].product.name, 
-  items[i + 1].product.name) == 1) { return false; }
-}
-\end{lstlisting}
-The \texttt{createSellingPlatform} function invokes this check to verify sorting before platform creation.
-Other functions mentioned previously are implemented in the contract, assuming  the list remains sorted.
+The contract includes \texttt{claimReward(sellingPlatform, seed)} to verify if a submission is a counterexample or valid proof.
 
-All functions emit events when successfully performed, such as platform creation or item updates.
-\subsection{Applying the Proposed Approach to Off-chain Distributed Verification}
-This section presents the implementation of the DSP application using the proposed off-chain distributed verification.
-\subsubsection{System Setup}
-Following the proposed approach, we define the key components to set up the system. 
-\paragraph{Checkpoint Formula}
-The checkpoint formula for identifying unsorted items, given by Equation \ref{eq:3}, is:
-\[
-(\exists i) \; (0 \leq i < \text{len(items)} - 1) \ \text{items}[i].\text{product.name} > \text{items}[i+1].\text{product.name}
-\]
-\paragraph{Introduce the Seed}
-The seed \( s \) is associated with the \( i+1 \)-th element of the item list, where \( i = s \mod n \) and \( n \) is the length of the list.
+The off-chain program, built in JavaScript with Ether.js, listens for platform submission events.
+It generates a random seed \( s \), used to find a counterexample or valid proof, then calls \texttt{claimReward} on-chain to claim the reward.
+\subsection{Gas Savings}
+We compared gas consumption between on-chain verification and the proposed off-chain approach based on item list size.
+Table \ref{gas-save} show that gas savings increase with list size; for example, an array of 50 items saves around 115,328 gas.
+Actual savings in tokens depend on the reward setup.
 
-\paragraph{Number of Seeds}
-The expected number of seeds \( m \) is estimated using Equation \ref{eq:12}, where \( P \) represents the given expected probability:
-\[
-m = \frac{\ln(1 - P)}{\ln\left( \frac{P - 1}{P} \right)}
-\]
-
-\paragraph{Target Hash}
-The target hash \( t \) is computed using a 256-bit maximum hash value \( H_{\text{max}} = 2^{256} - 1 \):
-\[
-t = \frac{H_{\text{max}}}{m}
-\]
-
-\paragraph{Computation Hash}
-The negation formula components for item \( i \) are:
-\[
-\pi_{P_{a}} = \{ \text{items}[i].\text{product.name}, \text{items}[i+1].\text{product.name} \}
-\]
-To prevent front-running and exploitation attacks, as described in the practical model, the computation hash includes the seed, the validator's address, the timestamp of the item list submission, and the essential evaluation components:
-\[
-t_s = \text{hash}(s, \text{addr}, t, \pi_{P_{a}})
-\]
-\subsubsection{On-chain Contract}
-The system consists of an on-chain smart contract and an off-chain verification program.
-The on-chain contract extends the DSP contract (Section~\ref{}) with additional variables and functions, such as \texttt{rewardPrice} and \texttt{counterexamplePrice}, to support off-chain verification.
-
-When \texttt{createSellingPlatform(items)} is invoked, the item list is submitted with a \texttt{timestamp} and \texttt{status}, initially set to \texttt{false}.
-The caller deposits funds, forfeited if the item list is unsorted.
-The parameter waits in this state until verified.
-If a counterexample is found, the record is deleted, and the caller incurs a penalty.
-If verified successfully, \texttt{status} switches to \texttt{true}, enabling further actions, such as sales or updates.
-
-The contract includes the \texttt{claimReward(sellingPlatform, seed)} function, which checks if the submission is a counterexample or a valid proof. 
-\subsubsection{Off-chain program}
-The off-chain program is built using JavaScript with the Ether.js library.
-The program listens for events when a platform is submitted (or created).
-Once this event occurs, it triggers a function that generates a random seed \( s \), which is used to either find a counterexample or compute a valid proof.
-When one of these outcomes is achieved, the program calls the on-chain \texttt{claimReward} function to claim the associated reward.
-\subsection{Gas Savings}
-The on-chain verification contract is deployed at \cite{}, while the proposed on-chain contract is available at \cite{}.
-The off-chain program is stored at \ref{}.
-We conducted experiments to compare gas consumption between on-chain verification and the proposed off-chain approach, based on item list size.
-The results are presented in Table \ref{gas-save} and illustrated in Figure \ref{gas-compare}.
-As the item list size increases, gas savings also increase; for instance, with an array size of 50, the proposed approach saves approximately 115,328 gas.
-Actual savings in native tokens depend on the computation reward setup.
-
-This smart contract application can be optimized by using on-chain verification for smaller lists and off-chain verification for larger ones.
-This hybrid approach can provide optimal gas efficiency: on-chain verification is sufficient for small item lists, while shifting to off-chain verification for larger lists significantly reduces gas costs.
-
+This smart contract can be optimized by using on-chain verification for small lists and off-chain for larger ones, achieving optimal gas efficiency.
 \begin{table}[h]
@@
 \end{table}
-
-\begin{tikzpicture}
-\label{gas-compare}
-\begin{axis}[
-    title={Gas Save for Off-chain  Approach Compare to On-chain Approach},
-    xlabel={Parameter Size},
-    ylabel={Gas Amount},
-    legend pos=north west,
-    grid=major,
-    width=10cm,
-    height=6cm
-]
-
-% Difference data
-\addplot[
-    color=green,
-    mark=square*,
-    ]
-    coordinates {
-    (5, -73971) (10, -5283) (20, 37754) (30, 63356) (50, 115328) (70, 169626) (100, 247493) (120, 299381) (150, 377536) (170, 429615) (200, 508057)
-    };
-    \addlegendentry{Gas Save}
-
-\end{axis}
-\end{tikzpicture}
-
 \section{Related work}
@@
 
-Layer 2 solutions like Plasma \cite{plasma-whitepaper} move heavy computation to a separate child chain anchored to the Ethereum Mainnet, improving scalability but not suited for parameter verification.
+Layer 2 solutions like Plasma \cite{plasma-whitepaper} shift heavy computation to a child chain anchored to Ethereum Mainnet, improving scalability but not suited for parameter verification.
 More recently, optimistic rollups \cite{optimisticrollups} and zk-rollups \cite{zkrollups} emerged, offloading computation while preserving security.
-Optimistic rollups allow challenges through fraud proofs, similar to our counterexample mechanism, while zk-rollups use cryptographic proofs.
+Optimistic rollups allow challenges via fraud proofs, similar to our counterexample mechanism, while zk-rollups use cryptographic proofs.
 However, both focus on transaction throughput, not complex parameter verification.
@@
 Decentralized oracle networks like Chainlink \cite{chainlink} enable off-chain data validation but are designed for fetching external data, not parameter verification.
-Their incentive model also differs from our proof-of-work mechanism.
+Their incentive model differs from our proof-of-work mechanism.
 
@@
 \label{sec:conclusion}
-This paper proposes a method for parameter verification in smart contracts on the blockchain.
-The method addresses the challenge of performing computationally expensive verification processes directly on-chain.
-The core idea is to offload the verification process to an off-chain system, with only the verification results being submitted on-chain.
-To implement this approach, we propose an incentive mechanism that encourages validators to participate in the verification process while ensuring the correctness of the parameters when deemed valid.
-Our gas cost analysis demonstrates the benefits of this approach, particularly when dealing with large parameters that are costly to verify on-chain.
+This paper proposes a method for parameter verification in blockchain smart contracts by offloading expensive on-chain verification to an off-chain system, submitting only the results on-chain.
+We introduce an incentive mechanism to encourage validator participation while ensuring parameter correctness.
+Our gas cost analysis shows significant benefits, especially for large, costly parameters.
+
+Future work includes developing an automated tool to convert heavy on-chain verification to the off-chain system, with a specification language for defining parameter properties, automatically generating smart contract functions and off-chain programs.
 \newpage
